### 2017-09-28 main.tex
Project created

\documentclass[twocolumn]{aastex61}
\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext}
\usepackage[T1]{fontenc}
\usepackage{apjfonts} 
\usepackage[figure,figure*]{hypcap}
\usepackage{multirow}
\usepackage{mathtools}
\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref

\shorttitle{Feedback with Individual Stars}
\shortauthors{Emerick, Bryan, Mac-Low}
\newcommand{\msun}{M$_{\odot}$}
\newcommand{\ccunit}{cm$^{-3}$}

\begin{document}

\title{Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case}
%Unstable Star Formation for the Lowest Mass Dwarf Galaxies
\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Greg Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
\author{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}

\begin{abstract}
\textbf{Saving this for after the first iteration}
\end{abstract}

\keywords{Galaxy -- Hydrodynamics -- Simulation -- Feedback}

\section{Introduction}

Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade. Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc. \citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses. On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM. This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}. See both \cite{SomervilleDave2015} and \cite{NaabOstriker2016} for recent reviews on these topics.

These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution. In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense. In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships. For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.

There is a considerable body of work examining the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}, nearly all of which are implemented with smooth particle hydrodynamics (SPH) schemes. Only recently have chemical evolution models been implemented in grid-based codes \citep{Few2012,Few2014,Vorobyov2015}. This is a vital and complimentary approach given the well known differences between hydrodynamics implementations \citep[e.g][]{Agertz2007,AGORA,AGORA2}. In particular, metal mixing must be handled through a sub-grid model in standard SPH schemes \citep[e.g.][]{Shen2010} that generally must be tuned to some degree to obtain reasonable results. The differences in how one handles this mixing can lead to problems in connecting the results of galactic chemical evolution models with the fundamental physics that drives the evolution \citep{Revaz2016}. We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mash refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies.

The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. Doing so with dwarf galaxies in particular is advantageous as their small physical scales and low star formation rates allow for greater physical realism without excessive computational expense. 
We follow recent work that used low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution. For example, \citet{Forbes2016} found that a self-consistent model of photoelectric heating in dwarf galaxies is an important channel of feedback. \citet{Hu2016} and \citet{Hu2017} examined the relative importance in galaxy evolution of supernovae, photoelectric heating, detailed ISM chemistry, and an approximate method for stellar ionizing radiation.

Increasing resolution, while more expensive, generally makes it easier to model physical processes in galaxy evolution. However, at high particle mass resolution ($\lesssim 10^3$ M$_{\odot}$), the standard treatment of star particles as simple stellar populations (SSP) breaks down. At these masses the IMF is no longer fully sampled, requiring a fundamentally different approach to how the simulated particles inject feedback and yields. Although there are solutions to this issue, each incurs additional model complexity with associated uncertainties. We refer the reader to \cite{Revaz2016} for a detailed accounting of this issue and possible means of addressing it. Naively, the best solution is to push towards galaxy scale simulations removing the SSP formalism and following stars individually. This allows for a detailed, star-by-star accounting of both stellar feedback and chemical enrichment without having to implement an additional sub-grid model to address the limitations of SSPs. In this work, we follow stars as individual star particles for the first time in a galaxy scale simulation.

Our work builds upon our current understanding of galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation. Using star-by-star modeling, we are able to capture in more detail the stellar yields from individual stars released over their lifetime. In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This opens an exciting new channel for testing models of galaxy evolution by enabling us to leverage current and ongoing observations probing the detailed chemical abundances of stars in the Milky Way and Local Group. \textbf{(citations to obs campaigns - GAIA, RAVE, APOGEE, etc.).}

This paper is the first in a series of papers examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. In this paper we introduce a new method of modeling for feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}. For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type 1a supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer. In addition, we couple to a self-consistent set of stellar yields tables from the to track stellar yields from massive star stellar winds, AGB star winds, and supernovae. We describe each mode of our multi-channel feedback implementation in detail below, and briefly discuss their implementation in a set of isolated dwarf galaxy simulations.

Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete -- yet brief -- summary of the included physics.

\section{Methods}
\label{sec:methods}
In brief, we produce high resolution galaxy scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic UV background. We use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation, and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure. In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner (LW) dissociation of molecular hydrogen. We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors. We follow yields for 12 individual metal species, chemically tagging each star with the associated local gas abundances for each species. These methods are discussed in detail below.

\subsection{Hydrodynamics and Gravity}

We use the adaptive mesh refinement (AMR) hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodyanamical evolution and detailed feedback physics in a set of high resolution, isolated, low mass dwarf galaxies. \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions. We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick. Specifically, simulations presented here were conducted at changeset 445de816fd99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies. We compute the total gravitational potential from gas self-gravity, stars, and static background dark matter potential. The collisionless star particles are evolved with a particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.

The computational domain in an AMR simulation is adaptively refined up to a designated resolution limit for a given set of refinement criteria. We require that the Jeans length be resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution. Our maximum resolution in the initial comparison simulations presented here is 2.5 pc, but our peak resolution in our fiducial set of lower mass galaxies is 1.5~pc (see Emerick et. al. in prep). At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation. Studies have shown that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation \citep{Truelove1997}.

We set the star formation density threshold to the point which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial collapse once its Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.

\subsection{Chemistry and Cooling Physics}
\label{sec:chemistry}

We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset 59adc76b3130.} \texttt{Grackle} is a freely available, open source multi-code library, designed to interface with a wide variety of astrophysical codes. We outline specific model choices made in our simulations and refer the reader to \citep{GrackleMethod} for a detailed discussion of the code. We apply the \cite{Glover2008} three body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and {2005ApJ...626..627O} as included in \texttt{Grackle}. However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$) with the broken power law scalings from \cite{Remy-Ruyer2014}. For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the the default behavior in \texttt{Grackle}.

Metal line cooling is modeled using pre-computed \texttt{Cloudy}\footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \cite{HM2012} UV metagalactic background. As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background. Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities. We use re-computed metal line tables consistent with the self-shielding approximation. Our effective cooling curve and these new tables are publicly available in the main \texttt{Grackle} repository. These are both discussed in greater detail in Appendix ~\ref{appendix:cooling}.

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order resolve individual star formation on galaxy scales, we implement a stochastic star formation algorithm adopted from \cite{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass. Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M_{\rm gas} > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and $M_{\rm max,*}$ is the maximum star mass (100 M$_{\odot}$). No star formation occurs when $M_{\rm gas} < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode does not produce negative densities.

We make the common ansantz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, one's choice of $\epsilon_{\rm f}$ is irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
The the gas mass converted to stars in a time step, $dt$, is
\begin{equation}
M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
\end{equation}
In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \cite{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we random sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$. We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and maximum stellar mass of 100 M$_{\odot}$.

Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion. Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 14 individual species abundances (H, He, and the 12 metals) we follow in our simulations. Stars evolve throughout the simulation, losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation. For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.

Finally, each star is marked as a ``must refine" particle, requiring that each star be surrounded by a four-cell region at the highest level of refinement. This ensures that both stellar winds and supernovae feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.

\subsection{Stellar Properties}
\label{sec:properties}
Given their birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to each star, as well as an effective temperature ($T_{\rm eff}$) and surface gravity ($g$), used in computing radiation properties (see Section \ref{sec:ionizing radiation}). We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$. Although $T_{\rm eff}$ and $g$ evolve over time for stars, modifying stellar radiative properties, following a stellar evolution track for each of our stars is beyond the scope of this work. We instead fix these properties at their zero age main sequence values.

\subsection{Stellar Feedback and Chemical Yields}

\subsubsection{Stellar Yields}
\label{sec:yields}
For the first time in galaxy scale simulations, we track galactic chemodynamical evolution using stellar yields as ejected from star particles that represent individual stars. We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep[][Ritter et. al. in prep]{Pignatari2016}. This grid includes yields from the AGB phase of stars between 1 and 7 M$_{\odot}$, as well as yields from both stellar winds and core collapse supernova of massive stars over 12 to 25 M$_{\odot}$. We compliment these tables to track stellar winds for stars more massive than 25 M$_{\odot}$ using tables from Slemer et. al. (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}; we ignore supernovae yields from these stars (see below). We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth. Although we can follow an arbitrary number of metal species, practical considerations prevent this in any given simulation. We refer the reader to previous uses of the NuGrid yields in one zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion on how various model uncertainties can influence galactic chemical evolution.

Above some mass, $M_{\rm trans}$, within the unsampled range of 7 to 12 M$_{\odot}$ stars do not undergo AGB wind phases and end their lives as core collapse supernovae. Where this transition occurs is uncertain, but is commonly taken to be around 8 - 10 M$_{\odot}$. This is a free parameter in our model, but we take $M_{\rm trans} = 8$ M$_{\odot}$ as our fiducial value. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass eject their stellar yields via ``massive" stellar winds at a constant mass loss rate throughout their lifetime, ending their lives as a core collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35 - 40 Myr), and the energy injection from these winds. \cite{Cote2017} explores how one's choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.

There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[][and references therein]{Cote2016}. Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable/unstable regimes as a function of mass \citep{Heger2003}. Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no mass or energy ejection.

Type Ia supernova are an important additional source of galactic chemical enrichment. These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams. We use the Type Ia supernova yields given in \cite{Thielemann1986}, adopting a Type Ia supernova model as discussed in Section~\ref{sec:Type Ia}.

\subsubsection{Stellar Winds}
\label{sec:stellar winds}
Stellar winds are important sources of early (massive stars) and late (AGB stars) enrichment and feedback in galaxies. Although the energy injected via winds over the lifetime of a cluster of stars is much less than that of supernovae and radiation, stellar winds are potentially important sources of pre-supernova feedback. In both AGB phase winds and massive star winds we inject the feedback energy in a 3-cell radius spherical region centered on the emitting star particle assuming full thermalization of the wind kinetic energy. The total injected energy in timestep $\Delta t$ is therefore $E_{\rm wind} = \dot{M}\Delta t \times v^2_{\rm wind} + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass ($\dot{M}\Delta t$) given the star's interpolated $T_{\rm eff}$. We use a monte-carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge if the injection region that is a result of mapping a spherical injection region to cubic grid cells.

We assume constant mass loss rates for all winds as set by the yields tables and either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars). 
%Properly modeling stellar winds requires sub-parsec resolution, which is problematic in galaxy-scale simulations. 
Massive star stellar winds have typical velocities on order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}. Satisfying the Courant time step becomes prohibitively expensive following this gas ($dt \sim$~100~yr), particularly as stellar wind bubbles have typical temperatures of 2 $\times$ 10$^{6}$ K \citep{Weaver1977}. For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}. In our case, we fix massive star stellar winds to $v_{\rm wind} = 1$~km~s$^{-1}$ for stars above 8 M$_{\odot}$. Our initial tests show that turning off energy injection from stellar winds does not significantly affect the global star formation rate of our galaxies. Due to the substantial additional computational expense of following stellar winds for Gyr timescales, we reserve examining the detailed importance of winds to future work. These points are discussed in more detail in Section \ref{sec:stellar winds discussion}.

% Injecting 10$^{3}$ km s$^{-1}$ gas onto the grid at these scales leads to super heated, shocked gas at unphysical temperatures of about 10$^{8-9}$ K, particularly when injecting into very low density media. This can lead to painfully short time step sizes and crashes in the hydrodynamics solver. We adopt the common solution of artifiially reducing the wind velocity from massive stars, choosing $v_{\rm wind} = 500$~km~s$^{-1}$ for stars above 8 M$_{\odot}$. However, this can still be problematic once the star evacuates the local ISM and injects its energy to very low density ($n \lesssim 10^{-3}$ \ccunit) gas. We address this issue by mass loading our winds when injection would lead to wind bubble temperatures in the spherical source region above a maximum temperature typical of wind bubble. This is a free parameter that we take to be 2 $\times$ 10$^{6}$ K \citep{Weaver1977}. Mass loading in this manner is (in effect) a sub-grid model for the unresolved ISM mixing at the boundary layer of the wind bubble, which is in fact the source of a majority of the gas mass within the wind bubble \citep{Weaver1977}. We take the metal species abundances of the mass loaded ISM to be the average cold / warm ISM abundance on each grid to prevent artificially inflating/deflating the overall abundances. We discuss our ability to resolve typical single star wind bubble properties in Appendix ~\ref{appendix:stellar winds}.

%parameterized in this work with the STARBURST99 wind model, \citep{Leitherer1992}:
%\begin{multline}
%{\rm log} \left[ v_{\rm wind} {\rm (km~s^{-1})} \right] = 1.23 - 0.30~{\rm log}~\left[L{\rm (L_{\odot})}\right] \\
% + 0.55~{\rm log}\left[M({\rm M_{\odot}})\right] + 0.64~{\rm log}\left[T_{\rm eff}(K)\right] \\
% + 0.13~{\rm log}\left[Z({\rm Z_{\odot}})\right].
%\end{multline}

Stars that undergo an AGB phase only deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks. AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$. For simplicity, we adopt a fixed AGB phase wind velocity of 20 km s$^{-1}$ for all AGB stars.

\subsubsection{Core Collapse Supernovae}
\label{sec: core collapse}
Stars between  $M_{\rm thresh} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse supernovae, ejecting mass and yields as determined by the NuGrid stellar yield tables at 10$^{51}$ erg of thermal energy. Due to the high resolution (1.5 - 2.5 pc depending on galaxy size) of our simulations, we generally well resolve the Sedov phase of each supernova explosion (see Appendix~\ref{appendix:supernova}). We find injecting thermal energy alone in a 3 cell radius spherical region around the star particle to be sufficient to resolve the supernovae explosions. We continue to track any remaining stellar mass after the SNe as a massive ``remnant" tracer particle. In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment through X-ray binaries and neutron-star-neutron-star merger events which, while rare, could be important in long term galaxy evolution.
\textbf{Should I reference a few recent hydro sims that included these feedback sources? - AE}

\subsubsection{Type Ia Supernova}
\label{sec:Type Ia}
We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors. At the end of their life, we assign a new mass to these particles following the initial to final mass relation of \cite{Salaris2009}. \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
%or, 
%\[
%M_{\rm WD} = 
%\begin{cases}
%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
%\end{cases}
%\]
%where $M_{\rm *}$ is the initial mass of the WD progenitor.
We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WD's that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}. We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution (DTD) model. \textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):} The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope and normalization are observables, and $\eta$ the fraction of stars which can form SN Ia progenitors that \textit{will} explode as a SN Ia within a Hubble time. The value for $\eta$ depends on the normalization of the DTD (an observable), as well as one's choice of IMF and mass range of potential SN Ia progenitors (as given above). This fraction is given as
\begin{equation}
\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
\end{equation}
where $N_{\rm Ia}/M_{\rm SF}$ is the DTD normalization, which represents the fraction of stars that form SN Ia progenitors, $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF ($dN/dm$), and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates. The DTD slope, $\beta$, is of order unity, with typical values between 1.0 and 1.2 (see \cite{Maoz2014} for a recent review). $N_{\rm Ia}/M_{\rm SF}$ represents the number of SN Ia per mass of star formation; this can be derived by taking observed values of the SNIa rate and integrating over a Hubble time. Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}. We adopt 1.2 \cite{Maoz2010} and 0.8$\times 10^{-3}$ M$_{\odot}^{-1}$ \cite{GraurMaoz2013} for our fiducial values of $\beta$ and $N_{\rm Ia}/M_{\rm SF}$. Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.

Finally, the probability a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor is taken as

\begin{equation}
P(t) = \dot{P}(t)dt = \eta \frac{ t^{-\beta}}{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau} dt,
\end{equation}

where $t_{\rm o}$ is the formation time of the WD and the denominator normalizes the total probability to $\eta$. This naturally accounts for both a prompt and delayed Type Ia supernova population in our simulations.
In practice, we invert the cumulative probability distribution to assign an exact time at which a given WD will explode, rather than making a random number draw for every WD particle every time step as $\eta$ is small.

\subsubsection{Ionizing Radiation}
\label{sec:ionizing radiation}
Radiation feedback (ionization, ionization heating, and radiation pressure) is an important source of pre-SN feedback in galaxies. HII regions carved out by stellar radiation change the ISM structure where SNe eventually explode, generally increasing their dynamical importance. However, when accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily through channels carved through dense clouds. Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with limited application in full radiation hydrodynamics simulations \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due the additional computational expense of direct ray tracing. As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through ray tracing methods described below. In this particular work, we use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).

Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer as coupled to the hydrodynamics of the simulation. We follow \ion{H}{1} and \ion{He}{1} ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen. Radiation pressure is expected to be an important source of feedback only in more massive galaxies; we explore this point further in this work.

We adopt the \ion{H}{1} and \ion{He}{1} ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}. We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star. Stars less massive than about 15 M$_{\odot}$ are generally off of the OSTAR2002 grid, and massive stars with sub-solar metallicity generally have effective temperatures above the OSTAR2002 grid. In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}). \citep{Dale2012} demonstrated that uncertainties on order of a few in the ionizing radiation rates are not significant in giant molecular cloud (GMC) scale simulations.
%Generally, the ionizing fluxes from high temperature black bodies underestimate the OSTAR2002 flux, and lower temperature black bodies overestimate the flux by a factor of 2-5 and 10-1000 respectively.

Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}). The average energy for \ion{H}{1} and \ion{He}{1} ionizing photons changes significantly over the OSTAR2002 temperature range ($log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$), ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.

We also include the effects of radiation pressure on HI. This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}. We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared. This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}. However, the importance of multiple scattering is still unclear. Other works have shown the effect to only increase the radiation pressure by a factor on order of unity \citep{Krumholz2012,Krumholz2013}. Due to these uncertainties, and given that we focus on low metallicity dwarf galaxies with low dust content, we ignore this effect.

\subsubsection{Diffusive Heating}
\label{sec:diffusive heating}
We include two forms of diffusive heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \cite{HM2012}, and 2) localized photoelectric (PE) heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars. Photoelectric heating can be a dominant heating mechanism in the ISM \citep{Parravano2003} of the Milky Way, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}. However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contended \citep{Hu2016,Hu2017}. Generally, models for PE heating and LW radiation in hydrodynamic simulations of galaxies adopted a constant value or a static, radial profile. Only recently has the localization and time variation of these processes been considered.

Self-shielding of gas against the metagalactic UV background is important in high resolution simulations, particularly for low-mass, low metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy. We have implemented the \cite{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background (see \citep{GrackleMethod} for more details of this implementation). We assume HeI ionization generally follows HI. This allows us to approximate HeI self-shielding using the same form (A. Rahmati, private communication). We ignore HeII photoionization from the UV background entirely. Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \cite{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \texttt{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

%Ignoring this effect leads to an overestimation of the cooling rates when in the self-shielding regime. %We refer to \cite{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \cite{Gracklemethod} for its specific implementation, as used here.

We assume the FUV luminosity for each our stars is everywhere optically thin. The FUV flux in each cell is summed over contributions from each star. We parameterize the local photoelectric heating rate following \cite{BakesTielens1994}, \cite{Wolfire2003}, and \cite{Bergin2004}, where 
\begin{equation}
\label{eq:PE}
\Gamma_{\rm pe} = 1.3 \times 10^{-24} \epsilon n_{\rm H} G_{\rm eff} D \left[{\rm erg~s~cm^{-3}}\right]
\end{equation}
where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\rm{exp}(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust to gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}. Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \cite{Hu2016} and \cite{Hu2017}.

$D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \cite{Remy-Ruyer2014} (see Section~\ref{sec:chemistry}). The extremely low dust to gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a $D$ that scales linearly with metallicity at very low metallicity. At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$ \ccunit. Given that the ambient density of the ISM is generally 1 - 10 cm$^{-3}$, we can safely assume the FUV field to be optically thin. However, we do include a localized attenuation prescription which may influence high density or metal enriched regions of the galaxy. We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.

Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density ($n_e$). This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; each of which are not followed directly in these simulations. Instead, we use a log-linear fit of $\epsilon$ as a function of $n_{\rm H}$ from the \cite{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$. %This is a compromise between adoption a constant efficiency, as in \cite{Forbes2016}, and a more detailed model with more detailed non-equillibrium chemistry \cite[e.x.][]{Hu2016}.

\subsubsection{Lyman-Werner Radiation}
\label{sec:LW}
In addition to the LW radiation from the UV background, we account for localized LW flux from each of our stars to compute the total, local H$_2$ dissociation rates. Given the local LW flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section. We account for approximate H$_2$ self-shielding against these sources of LW flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.

%
% CR section moved to missing physics
%
%\subsubsection{Cosmic Rays}
%\label{sec:cosmic rays}
%Cosmic rays may be a signficant source of feedback within star forming galaxies, capable of driving galactic outflows. Recent work has shown that CR's are capable of providing a significant additional pressure support within the ISM \citep{SalemBryan2014, SalemBryanHummels, GirichidisCR, Pakmor2016}, and are capable of producing more realistic galaxy gas halos \citep{SalemBryanCorlies}. We include cosmic rays coupled to the hydrodynamics of our simulation using a two-fluid model with adiabatic index $\gamma = 5/3$, as described in \citep{SalemBryan2014}. Cosmic ray energy is injected as some fraction, $f_{\rm CR}$, of the total supernova rate; we adopt $f_{\rm CR}$ with the fiducial value of 0.1. We include isotropic cosmic ray diffusion as described with the diffusion coefficient, $\kappa_{\rm CR} = 3.0\times10^{28}$. We refer the reader to \citep{SalemBryan2014} for a study of the effects different values for $f_{\rm CR}$, $\kappa_{\rm CR}$, and the CR adiabatic index has on galaxy evolution.

%Recent work has examined the impact anisotropic diffusion of cosmic rays along magnetic fields has on galaxy evolution \citep{GirichidisCR, Pakmor2016} and galactic winds generated from cosmic ray feedback \citep{GirichidisCR, Simpson2016}. Including magnetic fields can substantially change the effect of cosmic ray feedback provided $\mu$G level, ordered magnetic fields develop within the galaxy, as is the case for more massive disk galaxies. However, the magnetic field properties of small, ultrafaint dwarf galaxies are poorly understood. These small, puffy galaxies may be completely unable to sustain ordered magnetic fields, damping the effects of anisotropic diffusion as cosmic ray diffusion through random, tangled magnetic fields is approximately isotropic. We do not expect anisotropic diffusion and magnetic fields to have a significant impact on the effectiveness of cosmic ray feedback for ultrafaint dwarf galaxies, but this stands to be an important area of future research.

\section{Galaxy Initial Conditions}
\label{sec:IC}
The dwarf galaxy presented in this work a comparison simulation to the ``compact'' dwarf galaxy simulated in \cite{Hu2017}. There are some minor qualitative differences due to differences in initialization scheme. The gaseous disk of our galaxy is initialized as an exponential disk as used in \cite{Tonnesen2009} and \cite{Salem2015}. This is given as
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm gas}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm gas}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 1$~kpc, $b_{\rm gas} = 0.35$~kpc, and a total gas mass of $M_{\rm T,gas} = 4.0\times 10^7$~M$_{\odot}$. We include a static \citet{MiyamotoNagai1975} stellar background potential with total mass $M_{*} = 2\times 10^7 \rm{M_{\odot}}$ and the same scale height as the gas disk. This potential is given as
\begin{equation}
\Phi_* (R,z) = GM_{*}\left[R^2 + \left(a_* + \sqrt{z^2 + b_*^2}\right)^2\right]^{-1/2}.
\end{equation}
Our dwarf galaxy is embedded in a static, background, \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 10^{10} \rm{M_{\odot}}$, $R_{\rm vir}~=~44$~kpc and r$_{\rm s} = 4.4$~kpc. This gives a maximum circular velocity $V_{\rm max} = 36.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.43$~kpc. We note \cite{Hu2017} uses a NFW profile with the same concentration, giving $V_{\rm max} = 37.6$~km~s$^{-1}$ at $R_{\rm vmax}~=~9.5$~kpc. This is the most significant difference between our two initial conditions. The temperature of the gas disk is set by enforcing initial hydrostatic equilibrium with both the background stellar and dark matter potentials. The initial gas metallicity is set to 0.1 Z$_{\odot}$.

Following the initialization procedure of \cite{Hu2017}, we use artificial supernova driving to disturb the initially smooth gas profile. This generates realistic ISM turbulence and density structures and prevents the otherwise uniform collapse of the gas to a thin disk that rapidly undergoes a large burst of star formation. The supernova driving occurs at random positions throughout the gas disk in regular intervals of 0.5 Myr until 10 Myr after the first star forms. This SNe rate corresponds to the equilibrium SFR of this galaxy in \cite{Hu2017}, or $1.2\times 10^{-3}$~M$_{\odot}$~yr$^{-1}$. To maintain effective supernova driving, these explosions are uncorrelated with the local gas density \citep{Gatto2017}. The yields from these artificial supernovae are set to not affect the chemical evolution of the galaxy, but to maintain constant local gas abundances.

We simulate two realizations of the same dwarf galaxy in order to approximately test the effects of using radiative transfer to track stellar ionizing radiation as compared to a more approximate model. The first, our fiducial model, includes all physics as discussed above. The second uses all physics, but approximates the downside of approximate radiative feedback models by limiting ionizing radiation to local regions around the star particle, deleting photons that travel more than 50 pc. This is a very conservative mimicry of a Stromgren type approximation for photoionization feedback \citep[e.g.][]{Hopkins2012,Hu2017}, which is often used instead of full radiative transfer. Briefly, this generally photoionizes all gas within the Stromgren radius of a given star, expanding the region to account for overlapping HII regions by making estimates of the local density dependent recombination rate to determine if the region should be expanded. This, along with lack of angular information, can mass-bias the ionizing radiation, preferentially depositing most of the ionizing flux in local denser regions even though this ionizing radiation may be able to travel farther. Allowing photons to propagate normally within 50 pc effectively assumes this approximation is entirely consistent with radiative transfer within 50 pc, and asks the question as to whether or not longer distance photon propagation is important for galaxy evolution. We refer to these two galaxies as our ``fiducial'' and ``shortrad'' models for the remainder of this work.

% move leo P stuff to another paper: Each of the dwarf galaxies presented in this paper are modeled after the current observed properties of the Local Group ultrafaint dwarf galaxy Leo P. Leo P is remarkable for its large gas to stellar ratio, Mgas = XXX Mstar = XXX, and presence of ongoing star formation -- SFR = XX. HI observations of Leo P constrain its dynamical mass interior to XX pc to be XX Msun. Each of our dwarf galaxies are embedded in a fixed, constant Burkert dark matter profile, of which we adopt a scale radius of 395 pc. This implies a total virial mass of XXX Msun and virial radius of XXX kpc, using the definition of Bryan et. al. 199x. 
% The galaxy temperature is set such that the gas is in hydrostatic equilibrium with the background dark matter halo, ignoring the self-gravity of the gas. We adopt the initial gas phase metal fraction of  metal fraction of $Z = 4.3\times10^{-4}$, which is within the span of SFH modeled metallicities of Leo P presented in Fig. 8 of \cite{McQuinn2015a}; we note this is slightly lower than the observed current metallicity of Leo P, with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$, or $Z \sim 5.4\times10^{-4}$ adopting $Z_{\odot} = 0.018$ from \cite{Asplund2009}.

\section{Results}
\label{sec:results}

The shortrad galaxy agrees fairly well with the results found in both \citep{Hu2016} and \citep{Hu2017}, in terms of both morphological structure and star formation properties. This is in contrast to the results found in \citep{Forbes2016}, for reasons outlined in the discussion of \citet{Hu2017}. However, our full physics simulation, while similar to \citep{Hu2017}, shows significant differences. This is discussed in detail below.

\begin{figure*}
\includegraphics[width=0.23\linewidth]{panel/HI_sndriving.png}
\includegraphics[width=0.23\linewidth]{panel/H2_sndriving.png}
\includegraphics[width=0.23\linewidth]{panel/G_o_sndriving.png}
\includegraphics[width=0.23\linewidth]{panel/temperature_sndriving.png}\\
\vspace{0.1cm}
\includegraphics[width=0.23\linewidth]{panel/HI_shortrad.png}
\includegraphics[width=0.23\linewidth]{panel/H2_shortrad.png}
\includegraphics[width=0.23\linewidth]{panel/G_o_shortrad.png}
\includegraphics[width=0.23\linewidth]{panel/temperature_shortrad.png}
\caption{Projections of our fiducial galaxy (top) and shortrad galaxy (bottom) at the end of the simulation time. The left two panels are integrated projections through the full disk, giving HI and H$_2$ column density. On the right, we show thin, face-on projections of G$_{o}$ and temperature in the central 50 pc of the disk. We note both the strange dark region in the top $G_o$ plot and the white boxes at the edges of the thin projections are artifacts of the visualization process, and are not present in the simulation.\textbf{yes plot fonts and label sizes need fixing - AE}}
\label{fig:panel}
\end{figure*}

\subsection{Morphological Structure}
\label{sec:structure}
We show edge-on (left) and face-on (right) projections of our fiducial galaxy (top) and shortrad (bottom) at the end of the simulation time in Figure~\ref{fig:panel}. The left two panels are number density weighted projections through the full disk, giving HI and H$_2$ column density. The right hand panels show face-on projections through thin (50 pc) slabs at the center of the galaxy for the interstellar radiation field normalized to the MW value in the solar neighborhood, or $G_o$, and gas temperature. In general, the shortrad simulation is visually consistent with that found in \citep{Hu2016,Hu2017}, exhibiting a thick, puffy disk with a relatively smooth HI column and an H$_2$ distribution that is more confined to the plane of the galaxy and is roughly uniformly distributed. Looking at the fiducial simulation, it is clear that the ray-tracing radiative transfer produces a significant change in the galactic structure. Both the HI and H$_2$ are significantly more disturbed, with notable gaps in the HI column caused by regions carved out by the ionizing radiation, and with significantly less uniform H$_2$ column, from molecular hydrogen destroyed through ionization heating.

\begin{figure}
\includegraphics[width=0.9\linewidth]{panel/sndriving_particles}\\
\vspace{0.1cm}
\includegraphics[width=0.9\linewidth]{panel/shortrad_particles}
\caption{Face on, density weighted projections of gas number density for both galaxies. Each of the black points represents a single particle (star) in the simulation, and can be a living star, a white dwarf, a massless tracer originating from a Type Ia explosion, or a SNII remnant. The population is dominated by low mass stars; only a fraction of these particles have active feedback (winds, radiation, supernovae) at any one moment. \textbf{yes plot fonts and label sizes need fixing - AE}}
\label{fig:number density}
\end{figure}

The differences are further emphasized in the temperature projections, where a visually more significant fraction of the gas in the fiducial simulations sits at temperatures near 10$^4$~K, and much less sits at very low ($\sim$ 10 K) temperatures. The differences between gas phase in these simulations is discussed in Section~\ref{sec:phase}. The ISRF of both galaxies is quite similar, though since the ISRF in our model is generated by massive stars alone, it reflects the SFR over the previous 10 - 40 Myr, which is in fact similar in both galaxies (see Section~\ref{sec:sfr}).

Finally, in Figure~\ref{fig:number density} we present face-on projections of gas number density in both galaxies, marking each star particle in the simulation with an individual black point. Although the particles obscure some of the structure in the disk, the same general differences noted above are visible here. In particular, the fiducial simulation has significantly more disturbed gas morphology with larger regions of low density gas, and less dense gas structures.

\subsection{SFR and Mass Evolution}
\label{sec:sfr}

\begin{figure*}
\includegraphics[width=0.32\linewidth]{sfr_comparison}
\includegraphics[width=0.32\linewidth]{stars_mass_comparison}
\includegraphics[width=0.32\linewidth]{HI_mass_comparison}
\caption{The 10 Myr averaged SFR (left), stellar mass (middle), and disk HI mass (right) for each galaxy. \textbf{need to increase font sizes and y axis lim}}
\label{fig:SFR}
\end{figure*}

In Figure ~\ref{fig:SFR} we compare the star formation rates of both simulations (left), along with the stellar mass evolution (middle), and HI mass evolution (right). The peak and average SFRs for each galaxy over the 270~Myr simulation time are comparable, with a peak at roughly $0.04$~M$_{\odot}$~yr$^{-1}$ and an average of about $1.1~\times~10^{-3}$~M$_{\odot}$~yr$^{-1}$ in each simulation. However, the SFR evolution is qualitatively different, with the fiducial run exhibiting a $\sim$80~Myr period of minimal, patchy star formation between 125~Myr and 200~Myr ($<\rm{SFR}>~=~2.2\times~10^{-5}~$M$_{\odot}$~yr$^{-1}$). Although there is a lull in star formation during this time in the shortrad case, star formation is continuous. This difference is due solely to the long-range effects of stellar ionizing radiation, though we cannot also rule out the possibility that it also makes SN feedback more effective. It is apparent in this simulation that stellar radiation feedback is effective at suppressing star formation galaxy wide, not just locally.

\begin{figure}
\includegraphics[width=0.9\linewidth]{HI_surface_density}
\caption{\textbf{Coloring / style needs to change} Time averaged HI surface density profiles (dashed line) for both galaxies over the simulation time. The hatched regions show one standard deviation from the mean in each radial bin. Although there is noticeable variance in the HI profile in both galaxies, it is significantly greater for the full physics simulation. Truncating the ionizing photons to local regions alone results in a steadier and on average greater amount of HI at all but the very outer edge of the galaxy.}
\label{fig:HI profile evolution}
\end{figure}

The long-range effects of the ionization are clear in the HI evolution of these galaxies (middle). The presence of stellar ionizing radiation throughout the galaxy decreases the amount of HI gas present in the disk by a factor of $\sim$4, by the end of the simulation time. Figure~\ref{fig:HI profile evolution} shows the average HI surface density profile of each galaxy over the course of the simulation time, with the filled regions indicating one standard deviation from the mean. These differences in evolution lead to differences in metal production and distribution in these two galaxies, discussed further in \ref{sec:chemical evolution}.

\subsection{Phase Diagrams}
\label{sec:phase}

Figure~\ref{fig:phase} gives a comparison of the phase diagrams for each simulation, averaged over the final 150 Myr of simulation time. There are a few distinct regions in the left diagram that one can easily distinguish. There is an overdensity at low temperatures and densities ($\sim$~100~K and between $n = 0.1$~cm$^{-3}$ and $n = 1.0$~cm$^{-3}$) which extends somewhat to higher densities. This regime marks the approximate density regime where gas self-shielding against the UVB becomes significant (see Fig. 3 of \citet{Rahmati2013}). The large extensions to low densities and high temperatures mark gas heated during initial SNe injection and subsequent shock heated gas. Finally, there are two overdensities at temperatures around 10$^{4}$ K. The larger, and lower, of the two is hot phase of the the equillibrium cooling curve, and is obvious in the right hand diagram as well. However, the higher of the two is less pronounced in the right hand diagram. This is photoionized gas that has been photoheated to around $T = 2\times 10^4$~K.

Comparing these two diagrams it is apparent that the stellar ionizing radiation significantly impacts the detailed properties of the galaxy's ISM in regions well outside our artificial truncation radius of 50 pc. This radiation is able to prevent the cooling of dense gas to the very low temperatures seen in the right hand diagram and maintains a significant amount of photoheated gas at temperatures around 10$^4$~K.

\begin{figure*}
\includegraphics[width=0.45\linewidth]{sndriving_phase.png}
\includegraphics[width=0.45\linewidth]{shortrad_phase.png}
\caption{The temperature-number density phase diagrams for both simulations, averaged over the last 150 Myr of simulation time.}
\label{fig:phase}
\end{figure*}

\subsection{Chemical Evolution} %and Metal Enriched Outflows}
\label{sec:chemical evolution}
Although our simulations are long enough to begin to discuss morphological and dynamical differences between the galaxies, they are too short to focus in detail in chemodynamical evolution. For this reason, we make only a brief comparison between these two galaxies, saving a more detailed examination for our simulations of lower mass dwarf galaxies run for $\sim$Gyr timescales (Emerick et. al. in prep).

\begin{figure}
\includegraphics[width=0.9\linewidth]{element_mass_comparison_fraction}
\caption{Ratio of amount of mass in a given mutually exclusive phase (disk, halo, and stars) between the fiducial and shortrad simulations. The halo ratio has been multiplied by 0.5 for clarity. We caution against making any interpretation of Mn and ratios for the s and r-process elements (Y, Ba, and Eu) as there is very little mass of these elements produced in the $\sim$100 Myr timescales examined here. \textbf{comment: I thought of a few different ways of conveying this information, but all were painful to look at or make (e.x. double bar graph showing fractional element dist)... this was the least painful, but open to suggestions}.}
\label{fig:element mass ratio}
\end{figure}

In Figure~\ref{fig:element mass ratio} we divide the total mass of each element contained in each of three regimes (stars, disk, or halo) of the fiducial simulation by the mass in the shortrad simulation (i.e. $>$ 1 means more mass in the given in the given phase in the fiducial simulation). We multiply the halo ratio, defined as all elements outside the disk but within the virial radius, by 0.5 for clarity. Although the total metal production in each galaxy is similar, the partitioning of those metals differs significantly.

The fiducial simulation contains more (by a factor of 3 to 5) mass in a given species in the halo than the shortrad simulation. The additional feedback produced by tracing radiation outside 50 pc from each stars effectively drives gas and metals out of the disk. Most of this gas driven into the halo is still contained well within R$_{\rm vir}$ of this galaxy. It is unclear whether or not the additional feedback in the fiducial model will be able to move gas farther out into the halo. We note that a majority of the produced mass is still in the disk for each simulation, which is why the disk ratios are around unity. Though it varies for each element, the halo masses represent 10-20\% of the disk mass for the fiducial simulation, and 3-5\% for the shortrad simulation.

The feedback differences also impact the stellar metal abundance evolution in each galaxy. On average, the total mass of each element locked away in stars in the shortrad simulation is roughly twice as much as that contained in stars in the fiducial simulation. This is somewhat surprising because not only does the fiducial simulation have a slightly greater stellar mass by the end of the 270 Myr run time (2 $\times$ 10$^4$ M$_{\odot}$), but it also forms more of its stars later than the shortrad simulation. Naively, this should mean there would be more mass in a given element locked in the fiducial simulation stars as it has both more mass in stars and there has been slightly more time for produced metals to mix with the ISM and into these stars. This implies that differences in feedback evolution can lead to potentially significant differences in stellar abundances.

We caution against any interpretation of the ratio for Mn and the ratios for the s-process and r-process elements (Y, Ba, and Eu) as there is very little mass in these species in either simulation. However, we do point out that the ratios for N are qualitatively different than each other element. There is more N in the shortrad disk than the fullrad and its ratios are all much closer to unity than any other element. We suspect this is because, at these low metallicities, the IMF weighted N production is dominated by stellar winds of massive stars around $8 - 10$~M$_{\odot}$ and AGB stars\footnote{Although AGB stars are less relevant on these timescales. The lifetime of a 5 M$_{\odot}$ star at these metallicities is on order of 100 Myr} . However, IMF weighted production for the other species are dominated by SNe. This means most of the N produced is injected in a wind phase. This is more easily retained and mixed in the ISM than the other elements which are injected with much higher energy in SNe. These initial results immediately suggest that differences in both included feedback and mechanisms for yield injection can create discernible differences in stellar abundance patterns. How abundance variations like this evolve over longer timescales in lower mass dwarf galaxies is the subject of ongoing work (Emerick et. al. in prep.).

\textbf{I did have a panel plot showing column for each element here, but decided to take it out. Might be worth putting in panel comparison for a few elements, but not sure. Suggestions? - AE}
%\begin{figure*}
%\includegraphics[width=0.9\linewidth]{DD0204_elements}
%\caption{Panel plot of elements \textbf{PLACEHOLDER FOR NOW}}
%\label{fig:elements panel}
%\end{figure*}

\section{Discussion}
\label{sec:discussion}

\subsection{Comparison to Previous Work}
\textbf{I am going back and forth on how much this is needed given the above comparison to Hu's simulations. Thoughts? - AE}
% still not sure what to do here...

\subsection{Missing Physics}
Although we include detailed physics in our simulations, there remains additional physics that may be relevant.These are discussed below.

\subsubsection{Full Stellar Wind Model}
\label{sec:stellar winds discussion}
As discussed previously, our stellar wind model significantly reduces the injected wind velocity from $\sim$1000 km s$^{-1}$ to 1 km s$^{-1}$. Although our model is capable of generating realistic stellar winds with temperature profiles and radial evolution comparable to those expected from analytic calculations \citep{Weaver1977}, the hot, fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical. When considered in isolation, stellar winds are an important source of pre-SN feedback and do dramatically influence the dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}. However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or GMCs \citep{Dale2014}. They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}. Although they likely have no dynamical importance, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.

%old comment: (need to ref or back up this claim: see Dale et al. 2014 for individual clouds, while the right panel of Fig 2 in Shull \& Saken 1995 shows that the integrated wind energy from a cluster is about 10\% that of the supernovae -M).

\subsubsection{Cosmic Rays and Magnetic Fields}
Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017} and simulations of both isolated \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017} and cosmological galaxies \citep{SalemBryanHummels}. These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows with different phases and velocities than those driven through stellar feedback alone \citep{SalemBryanCorlies}. Modeling cosmic rays is challenging, however, as they encompass a wide range of energies (give range), with significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}. Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy. In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM. Modeling cosmic ray feedback completely requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena. Finally, including MHD presents additional difficulties in untangling the effects each individual feedback mechanism on galaxy chemodynamics.

We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested. Mechanically, including cosmic ray feedback in our model is trivial. However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to a later work.

\subsection{Detailed Dust Model}
The dust content of our galaxy is modeled only approximately, scaling with the cell-to-cell variations in gas metallicity. Explicitly following the dust content in our galaxy, even crudely, could introduce significant variations in local cooling and heating rates. Accounting for metals trapped in a dust phase would produce additional variations in the cooling rates and potentially changes to the galactic chemodynamical evolution. \textbf{Should we actually discuss this? If so I definitely need more info and references - AE}.

\subsection{Detailed Stellar Evolution and Binary Stars}
\textbf{I haven't written anything for this because not sure if its worth including. Definitely something I'm interested in exploring and it will make a difference, but it is likely lower on my priority list. Would it be worth mentioning how this can effect things (longer lived ionization in binary stars, delayed SNe, etc.)?}

\section{Conclusion}
\textbf{You can ignore this for now, I'm saving it after the first iteration (AE)}
We present a new method for simulating the evolution of low mass galaxies with detailed feedback and chemical enrichment as traced through individual star particles. This model follows multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia supernovae, ionizing radiation followed through radiative transfer, photoelectric heating, and LW radiation. This is in addition to the detailed cooling, heating, and chemistry followed through Grackle, including a self-consistent model for gas self-shielding from the metagalactic UVB.

In this work, we showed the results of a pair of comparison simulations to the isolated dwarf galaxies simulations previously in \citep{Hu2016} and \citep{Hu2017}. \textbf{will finish once discussion is done}

In future works we will investigate in detail the role each individual feedback process has in governing the chemodynamical evolution of isolated, low mass dwarf galaxies. These simulations will demonstrate how feedback affects metal mixing within the ISM and the enrichment of future stellar populations, in addition to how feedback influence metal ejection into, and possibly beyond, the galaxy's dark matter halo. \textbf{will finish at very end}

%\bibliographystyle{apj}
%\bibliography{msbib}

\bibliographystyle{yahapj}
\bibliography{msbib}

\appendix

\section{Stellar Radiation Properties}
\label{appendix:radiation}
We detail the radiation properties of our model stars as a function of stellar mass and metallicity, both of which are assigned directly from an IMF and from the local gas properties respectively. The stellar radiation properties are a determined from the OSTAR2002 grid \citep{Lanz2003} (or as integrated from an adjusted black body curve for stars off of the OSTAR2002 grid) given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set. In Figure~\ref{fig:stellar radiation properties} we plot the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and LW (middle right) luminosities, and finally the HI ionizing radiation photon energy (bottom left) and HeI ionizing photon energy (bottom right). We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass. This requires two factors for each radiation type, one for low mass and one for high mass stars. We use the following multiplicative factors to adjust the black body spectrum for HI and HeI radiation respectively: [0.1, 3.2] and [0.0001, 4.0]. We do not find this adjustment to be necessary for the FUV and LW radiation bands.

The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid. A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency dependent absorption cross section. We tested this approach using the frequency dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \texttt{http://www.pa.uky.edu/~verner/photo.html}} The black body approximation is accurate to within 5\%, yet substantially easier to compute on the fly as integrals over the black body spectrum can be expressed as infinite series that rapidly converge to high precision. Unlike the ionizing radiation, we assume constant FUV and LW band energies for each star, at 9.8 eV and 12.8 eV respectively.

\begin{figure}
\centering
\includegraphics[width=0.4\linewidth]{Q0}
\includegraphics[width=0.4\linewidth]{Q1}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{L_FUV}
\includegraphics[width=0.4\linewidth]{L_LW}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{E0}
\includegraphics[width=0.4\linewidth]{E1}
\caption{Radiation properties for our model stars. Note, we only track radiation from stars above
8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
\label{fig:stellar radiation properties}
\end{figure}

\section{Typical Gas Densities in Supernova Injection Regions}
\label{appendix:supernova}

Modeling supernova feedback with the injection of thermal energy alone can lead to rapid over cooling of the injected energy, and a significant underestimate of the effects of supernova feedback. Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time. However, physically consistent solutions have been employed \citep[e.g][]{Simpson2016} which inject a mixture of kinetic and thermal energy, whose ratio of kinetic to thermal energy injection depends on resolution and/or local gas density. This over cooling problem improves with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each supernova. We take advantage of our high ($\sim$ pc) scale resolution and employ a simple thermal energy injection model for our supernova feedback. Here we demonstrate how well this resolves our supernovae in the comparison simulation presented in this work.

The left panel of Figure ~\ref{fig:supernova histogram} gives the distributions of the max (orange) and average (black) ISM number densities in the supernova injection regions for each supernovae in the simulations presented in this work. As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$. For most supernovae, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-supernova feedback included in our simulations. The right panel of Figure ~\ref{fig:supernova histogram} gives the fractional distribution of the calculated radius of pressure driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \cite{Simpson2016}, given as
\[
R_{\rm PDS} = 
\begin{cases*}
49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z $\le$ 0.01 \\
18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z $\ge$ 0.01 \\
\end{cases*}
\]
where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$. \cite{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the supernova explosion with thermal energy injection alone, assuming uniform density in the injection region. In practice, the injection region is never uniform. We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each supernova. As shown, a majority of supernovae are resolved (to the right of the 4.5$\Delta x$ line), but that up to 10\% are somewhat under-resolved. In general, these are supernova explosions from the most massive (i.e. most prompt) stars. We do not expect that resolving these supernovae will dramatically alter our results, but note that simulations presented in future work will examine lower mass galaxies at higher resolution than those presented here. In those, the supernovae are more resolved, but we note that using our feedback model at resolutions much less than 2 pc will require adopting a different injection mechanism.

% We use a spherically symmetric thermal dump method of modelling supernova explosions. This is the simplest method possible, but can often result in rapid overcooling of the heated gas, effectively underestimating the effectiveness of supernova feedback. Solutions to this problem can often be ad hoc (e.g. briefly turning off cooling) in low resolution, large cosmological simulations. However, recent work has shown injecting some fraction of this thermal energy directly as kinetic energy or momentum alleviates this issue without sacrificing physical realism. However, it has been shown that simple thermal energy injection is sufficient for parsec scale (or better) resolutions, provided the supernova do not occur in very high density regions; if resolved, thermal injection converges with kinetic energy / momentum injection methods. Resolving these explosions with thermal energy injection alone depends ultimately on the grid resolution, background density and ISM structure, the background cooling/heating physics used, and the size and shape of the injection region. Here, we perform a resolution test of our thermal injection method over four uniform densities (0.1 \ccunit, 1.0 \ccunit, 10.0 \ccunit, and 100.0 \ccunit) for both a 8.0 \msun and 25.0 \msun star, comparing to both the analytic solution and results using kinetic energy injection from \cite{Simpson2015}. These results are presented in Figure~\ref{fig:supernova tests}. We note these are heavily idealized cases. In general in our simulations, pre-SN feedback from stellar winds and radiation will reduce the typical densities within which our supernova explosions occur. In addition, supernova will generally be clustered, meaning each SN will reducing the typical density for each subsequent SN in that region. In Figure~\ref{fig:supernova histogram} we plot a histogram of the typical peak and average gas densities in the 3 cell injection region of each supernova in the XXXX XXXXX simulation. As shown, some of the supernova explode in high density regions around 100 \ccunit and are likely under-resolved, but a majority will be resolved.

\begin{figure}
\centering
\includegraphics[width=0.4\linewidth]{sn_density_hist}
\includegraphics[width=0.4\linewidth]{sn_radius_hist}
\caption{Distribution of peak and average gas densities (left) in the injection region of each of the supernovae from simulation XXX. On the right, we show the radius of the pressure driven snowplow phase of the supernova, computed using the average and peak densities, for each supernova. The vertical lines give one and three cell widths. As shown, a fraction of these SN are certainly under resolved, with R$_{\rm PDS}$ less than the size of the initial injection region, but a majority are resolved. \textbf{font sizes and labels need improving - AE}}
\label{fig:supernova histogram}
\end{figure}

%\section{Stellar Wind Model}
%\label{appendix:stellar winds}
%
% This is still probably a good idea to do at some point, but save for if/when
% we have a paper using full stellar winds where this matters - AE (Jul. 19 2017)
%
%Discuss wind properties and evolution in a hand full of isolated star runs (don't need to do a resolution study... kinda) and compare to Weaver et. al. 1977 analytic results. Really we won't resolve the winds at high densities, but that is OK... as long as the wind bubbles are > 3*dx (the injection size) we are generally going to be fine... aka as long as the SN explosion goes off in wind bubble gas and not dense ISM that shouldn't be there..

\section{Cooling Rates}
\label{appendix:cooling}
Figure ~\ref{fig:cooling} shows the combined primordial and metal line cooling (dashed) and heating (dotted) rates at three characteristic densities for Z = 0.01 Z$_{\odot}$, closer to the metallicities of our fiducial set of dwarf galaxy simulations (Emerick et. al. in prep). The solid lines give the absolute value of the net cooling rate, which more clearly indicates the regime at low temperatures where heating dominates. The curve as shown includes the z = 0 \cite{HM2012} metagalactic UVB.

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{cooling_curve}
\caption{The total heating and cooling rates extracted from the core of a Jeans-length sized cloud irradiated by a \cite{HM2012} metagalactic background as modeled in \textsc{Cloudy}. The absolute value of the net cooling rate is shown with solid lines.}
\label{fig:cooling}
\end{figure}

We note that this cooling curve shows only an approximation of the local cooling and heating rates used in the simulations for two reasons. First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal line cooling and heating rates are used. The actual primordial heating and cooling rates are calculated self-consistently using the non-equillibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \cite{Rahmati2013}. However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations. Second, this figure ignores the contributions to the heating rate from the variable interstellar radiation field, namely the stellar contribution to photoelectric heating, heating from LW dissociation, and ionization heating. We describe how we obtain the metal line cooling rates below and quantify the change in using these updated tables. 
%Therefore, the heating rates shown are approximate lower limits to the true heating experienced by any given cell in the simulation.

The cooling curves used in this work correct a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with self-shielding approximations. Previous work in \cite{Hu2017} details this inconsistency. In short, adopting tabulated metal cooling rates computed under the assumption of an optically thin UV background overestimates the electron fraction in regimes where self-shielding is important, about $-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$, leading to an overestimation of the metal cooling rates. We demonstrate this effect in Figure~\ref{fig:cooling comparison}, which gives |cooling - heating| for our full model at $Z = 0.1~Z_{\odot}$ (black) as compared to a model using the optically thin metal line cooling rates (orange) at a range of densities. The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher. In low temperature regions, this can significantly shift the inferred equilibrium temperature.

The cooling curve shown in Figure~\ref{fig:cooling} avoids this discrepancy using re-computed metal line cooling tables. We have made these tables publicly available in the main distribution of \texttt{Grackle}. For densities where self-shielding is important, we computed \texttt{Cloudy} models of 1D clouds at each temperature and density pair with a physical size corresponding to the Jeans length. In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud. We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UVB. These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}. In computing these tables we had to include the CR ionization that dominates in optically thick clouds. Without this effect, \texttt{Cloudy} becomes unstable in entirely neutral regions. We adopted a CR ionization rate of 10\% the MW value, though we note varying this from 1\% to 100\% the MW value did not have an effect on the extracted metal line cooling rates.

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
\caption{The absolute value of the net cooling rate (|cooling - heating|) in two models that account for self-shielding of primordial gas against a metagalactic UV background. Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the un-corrected (i.e. optically thin) metal line cooling rates.}
\label{fig:cooling comparison}
\end{figure}

%\section{Pre-SN Feedback with and without radiation}

%\section{Code}
%(likely just do this as a short blurb in acknowledgements)

%A one-zone chemical evolution and feedback model was constructed to provide rapid testing and examination of the feedback and yield properties of each of our stars in our model. This code is publically available at https://github.com/aemerick/onez. In the simplest case, one can generate a series of star particles and examine their resulting properties, including wind and supernova yields, as a function of mass and metallicity. Included also are more complicated examples of running the full one-zone model. Support currently only exists for running in a non-cosmological mode with a constant star formation rate. In addition, this one-zone model uses star-by-star modelling and becomes extremely inefficient at large particle counts. Future develop will better optimize this code, allow for variable input or evolving star formation rates, cosmological evolution, and parallelism.

%\appendix
%\section{appendix section}

\end{document}

### 2017-10-13 main.tex
Update on Overleaf.

@@
 
-\title{Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case}
+\title{REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case}
 %Unstable Star Formation for the Lowest Mass Dwarf Galaxies
@@
 In addition, we couple to a self-consistent set of stellar yields tables from the to track stellar yields from massive star stellar winds, AGB star winds, and supernovae.
-We describe each mode of our multi-channel feedback implementation in detail below, and briefly discuss their implementation in a set of isolated dwarf galaxy simulations.
+We describe each mode of our multi-channel feedback implementation in detail below, and briefly discuss their implementation in an isolated dwarf galaxy simulation.
 
@@
 \label{sec:IC}
-The dwarf galaxy presented in this work a comparison simulation to the ``compact'' dwarf galaxy simulated in \cite{Hu2017}.
-There are some minor qualitative differences due to differences in initialization scheme.
-The gaseous disk of our galaxy is initialized as an exponential disk as used in \cite{Tonnesen2009} and \cite{Salem2015}.
-This is given as
+The galaxy presented in this work is constructed to be similar to the observed properties of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, but is not intended to be a matched model to this galaxy.
+Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4}$ adopting $Z_{\odot} = 0.018$ from \cite{Asplund2009}.
+Our dwarf galaxy is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citep{McQuinn2015}.
+
+The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equillibrium with a static, background dark matter potential.
+The gas profile follows \cite{Tonnesen2009} and \cite{Salem2015}, or
 \begin{equation}
@@
 where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm gas}$ is approximately 70\% of the total gas mass.
-We set $a_{\rm gas} = 1$~kpc, $b_{\rm gas} = 0.35$~kpc, and a total gas mass of $M_{\rm T,gas} = 4.0\times 10^7$~M$_{\odot}$.
-We include a static \citet{MiyamotoNagai1975} stellar background potential with total mass $M_{*} = 2\times 10^7 \rm{M_{\odot}}$ and the same scale height as the gas disk.
-This potential is given as
-\begin{equation}
-\Phi_* (R,z) = GM_{*}\left[R^2 + \left(a_* + \sqrt{z^2 + b_*^2}\right)^2\right]^{-1/2}.
-\end{equation}
-Our dwarf galaxy is embedded in a static, background, \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 10^{10} \rm{M_{\odot}}$, $R_{\rm vir}~=~44$~kpc and r$_{\rm s} = 4.4$~kpc.
-This gives a maximum circular velocity $V_{\rm max} = 36.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.43$~kpc.
-We note \cite{Hu2017} uses a NFW profile with the same concentration, giving $V_{\rm max} = 37.6$~km~s$^{-1}$ at $R_{\rm vmax}~=~9.5$~kpc.
-This is the most significant difference between our two initial conditions.
-The temperature of the gas disk is set by enforcing initial hydrostatic equilibrium with both the background stellar and dark matter potentials.
-The initial gas metallicity is set to 0.1 Z$_{\odot}$.
+We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$.
+We adopt a Burkert \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5^{8} \rm{M_{\odot}}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc.
+This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc.
+These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc, or $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012} (need more cite).
+We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in a future work.
 
-Following the initialization procedure of \cite{Hu2017}, we use artificial supernova driving to disturb the initially smooth gas profile.
-This generates realistic ISM turbulence and density structures and prevents the otherwise uniform collapse of the gas to a thin disk that rapidly undergoes a large burst of star formation.
-The supernova driving occurs at random positions throughout the gas disk in regular intervals of 0.5 Myr until 10 Myr after the first star forms.
-This SNe rate corresponds to the equilibrium SFR of this galaxy in \cite{Hu2017}, or $1.2\times 10^{-3}$~M$_{\odot}$~yr$^{-1}$.
-To maintain effective supernova driving, these explosions are uncorrelated with the local gas density \citep{Gatto2017}.
-The yields from these artificial supernovae are set to not affect the chemical evolution of the galaxy, but to maintain constant local gas abundances.
-
-We simulate two realizations of the same dwarf galaxy in order to approximately test the effects of using radiative transfer to track stellar ionizing radiation as compared to a more approximate model.
-The first, our fiducial model, includes all physics as discussed above.
-The second uses all physics, but approximates the downside of approximate radiative feedback models by limiting ionizing radiation to local regions around the star particle, deleting photons that travel more than 50 pc.
-This is a very conservative mimicry of a Stromgren type approximation for photoionization feedback \citep[e.g.][]{Hopkins2012,Hu2017}, which is often used instead of full radiative transfer.
-Briefly, this generally photoionizes all gas within the Stromgren radius of a given star, expanding the region to account for overlapping HII regions by making estimates of the local density dependent recombination rate to determine if the region should be expanded.
-This, along with lack of angular information, can mass-bias the ionizing radiation, preferentially depositing most of the ionizing flux in local denser regions even though this ionizing radiation may be able to travel farther.
-Allowing photons to propagate normally within 50 pc effectively assumes this approximation is entirely consistent with radiative transfer within 50 pc, and asks the question as to whether or not longer distance photon propagation is important for galaxy evolution.
-We refer to these two galaxies as our ``fiducial'' and ``shortrad'' models for the remainder of this work.
-
-% move leo P stuff to another paper: Each of the dwarf galaxies presented in this paper are modeled after the current observed properties of the Local Group ultrafaint dwarf galaxy Leo P.
-Leo P is remarkable for its large gas to stellar ratio, Mgas = XXX Mstar = XXX, and presence of ongoing star formation -- SFR = XX.
-HI observations of Leo P constrain its dynamical mass interior to XX pc to be XX Msun.
-Each of our dwarf galaxies are embedded in a fixed, constant Burkert dark matter profile, of which we adopt a scale radius of 395 pc.
-This implies a total virial mass of XXX Msun and virial radius of XXX kpc, using the definition of Bryan et.
-al.
-199x.
-% The galaxy temperature is set such that the gas is in hydrostatic equilibrium with the background dark matter halo, ignoring the self-gravity of the gas.
-We adopt the initial gas phase metal fraction of  metal fraction of $Z = 4.3\times10^{-4}$, which is within the span of SFH modeled metallicities of Leo P presented in Fig.
-8 of \cite{McQuinn2015a}; we note this is slightly lower than the observed current metallicity of Leo P, with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$, or $Z \sim 5.4\times10^{-4}$ adopting $Z_{\odot} = 0.018$ from \cite{Asplund2009}.
+Following the initialization procedure of \cite{Hu2017}, we use artificial supernova driving to generate realistic densities and turbulent properties in the galaxy ISM.
+This additionally prevents an otherwise uniform collapse of the gas disk.
+The supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}.
+We stop the artificial driving 25~Myr after the first star particle forms.
+These artificial supernova do not drive chemical evolution of the galaxy, containing metal yields corresponding to the mean ISM abundances.
 
@@
 
-The shortrad galaxy agrees fairly well with the results found in both \citep{Hu2016} and \citep{Hu2017}, in terms of both morphological structure and star formation properties.
-This is in contrast to the results found in \citep{Forbes2016}, for reasons outlined in the discussion of \citet{Hu2017}.
-However, our full physics simulation, while similar to \citep{Hu2017}, shows significant differences.
-This is discussed in detail below.
+%\begin{figure*}
+%\includegraphics[width=0.23\linewidth]
 
-\begin{figure*}
-\includegraphics[width=0.23\linewidth]{panel/HI_sndriving.png}
-\includegraphics[width=0.23\linewidth]{panel/H2_sndriving.png}
-\includegraphics[width=0.23\linewidth]{panel/G_o_sndriving.png}
-\includegraphics[width=0.23\linewidth]{panel/temperature_sndriving.png}\\
-\vspace{0.1cm}
-\includegraphics[width=0.23\linewidth]{panel/HI_shortrad.png}
-\includegraphics[width=0.23\linewidth]{panel/H2_shortrad.png}
-\includegraphics[width=0.23\linewidth]{panel/G_o_shortrad.png}
-\includegraphics[width=0.23\linewidth]{panel/temperature_shortrad.png}
-\caption{Projections of our fiducial galaxy (top) and shortrad galaxy (bottom) at the end of the simulation time.
+%\begin{figure*}
+%\includegraphics[width=0.23\linewidth]{panel/HI_sndriving.png}
+%\includegraphics[width=0.23\linewidth]{panel/H2_sndriving.png}
+%\includegraphics[width=0.23\linewidth]{panel/G_o_sndriving.png}
+%\includegraphics[width=0.23\linewidth]{panel/temperature_sndriving.png}\\
+%\vspace{0.1cm}
+%\includegraphics[width=0.23\linewidth]{panel/HI_shortrad.png}
+%\includegraphics[width=0.23\linewidth]{panel/H2_shortrad.png}
+%\includegraphics[width=0.23\linewidth]{panel/G_o_shortrad.png}
+%\includegraphics[width=0.23\linewidth]{panel/temperature_shortrad.png}
+%\caption{Projections of our fiducial galaxy (top) and shortrad galaxy (bottom) at the end of the simulation time.
 The left two panels are integrated projections through the full disk, giving HI and H$_2$ column density.
@@
 We note both the strange dark region in the top $G_o$ plot and the white boxes at the edges of the thin projections are artifacts of the visualization process, and are not present in the simulation.\textbf{yes plot fonts and label sizes need fixing - AE}}
-\label{fig:panel}
-\end{figure*}
+%\label{fig:panel}
+%\end{figure*}
 
@@
 
-\begin{figure}
-\includegraphics[width=0.9\linewidth]{panel/sndriving_particles}\\
-\vspace{0.1cm}
-\includegraphics[width=0.9\linewidth]{panel/shortrad_particles}
-\caption{Face on, density weighted projections of gas number density for both galaxies.
+%\begin{figure}
+%\includegraphics[width=0.9\linewidth]{panel/sndriving_particles}\\
+%\vspace{0.1cm}
+%\includegraphics[width=0.9\linewidth]{panel/shortrad_particles}
+%\caption{Face on, density weighted projections of gas number density for both galaxies.
 Each of the black points represents a single particle (star) in the simulation, and can be a living star, a white dwarf, a massless tracer originating from a Type Ia explosion, or a SNII remnant.
@@
 \textbf{yes plot fonts and label sizes need fixing - AE}}
-\label{fig:number density}
-\end{figure}
+%\label{fig:number density}
+%\end{figure}
 
@@
 
-\begin{figure*}
-\includegraphics[width=0.32\linewidth]{sfr_comparison}
-\includegraphics[width=0.32\linewidth]{stars_mass_comparison}
-\includegraphics[width=0.32\linewidth]{HI_mass_comparison}
-\caption{The 10 Myr averaged SFR (left), stellar mass (middle), and disk HI mass (right) for each galaxy. \textbf{need to increase font sizes and y axis lim}}
-\label{fig:SFR}
-\end{figure*}
+%\begin{figure*}
+%\includegraphics[width=0.32\linewidth]{sfr_comparison}
+%\includegraphics[width=0.32\linewidth]{stars_mass_comparison}
+%\includegraphics[width=0.32\linewidth]{HI_mass_comparison}
+%\caption{The 10 Myr averaged SFR (left), stellar mass (middle), and disk HI mass (right) for each galaxy. \textbf{need to increase font sizes and y axis lim}}
+%\label{fig:SFR}
+%\end{figure*}
 
@@
 
-\begin{figure}
-\includegraphics[width=0.9\linewidth]{HI_surface_density}
-\caption{\textbf{Coloring / style needs to change} Time averaged HI surface density profiles (dashed line) for both galaxies over the simulation time.
+%\begin{figure}
+%\includegraphics[width=0.9\linewidth]{HI_surface_density}
+%\caption{\textbf{Coloring / style needs to change} Time averaged HI surface density profiles (dashed line) for both galaxies over the simulation time.
 The hatched regions show one standard deviation from the mean in each radial bin.
@@
 Truncating the ionizing photons to local regions alone results in a steadier and on average greater amount of HI at all but the very outer edge of the galaxy.}
-\label{fig:HI profile evolution}
-\end{figure}
+%\label{fig:HI profile evolution}
+%\end{figure}
 
@@
 
+\subsection{Outflow Properties}
+\label{sec:outflows}
+
+Show mass loading factors as a function of time here at all radii.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{outflow_velocity_distribution}
+\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
+The outflowing material is multiphase, broken into WNM, WIM, and HIM.
+See XXX for definitions of these regimes.
+We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$K.
+There is little to no outflowing mass in the CNM or molecular phases.}
+\label{fig:outflow_velocity}
+\end{figure}
+
+Detailed outflow properties, beyond outflow rates and mass loading factors, are important discriminators between the model dependent feedback physics included in galaxy simulations.
+(this has been shown previously with XX XX XX producing very different outflow properties depending on what physics is included).
+In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
+Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{1} or below.
+This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities.
+The distribution has a very long tail out to and beyond 500 km s$^{-1}$.
+These dominant launching mechanism in this simulation are supernovae (Emerick et.
+al.
+in prep), generating a rapidly moving and volume filling HIM.
+However, as shown the HIM comprises very little of the outflow by mass.
+Most of the outflowing gas comes from the warm phase, pushed out by the high pressure, fast moving HIM.
+Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
+The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
+
+Final paragraph on metallicity of outflowing material.
+
 \subsection{Phase Diagrams}
@@
 
-Figure~\ref{fig:phase} gives a comparison of the phase diagrams for each simulation, averaged over the final 150 Myr of simulation time.
-There are a few distinct regions in the left diagram that one can easily distinguish.
-There is an overdensity at low temperatures and densities ($\sim$~100~K and between $n = 0.1$~cm$^{-3}$ and $n = 1.0$~cm$^{-3}$) which extends somewhat to higher densities.
-This regime marks the approximate density regime where gas self-shielding against the UVB becomes significant (see Fig.
-3 of \citet{Rahmati2013}).
-The large extensions to low densities and high temperatures mark gas heated during initial SNe injection and subsequent shock heated gas.
-Finally, there are two overdensities at temperatures around 10$^{4}$ K.
-The larger, and lower, of the two is hot phase of the the equillibrium cooling curve, and is obvious in the right hand diagram as well.
-However, the higher of the two is less pronounced in the right hand diagram.
-This is photoionized gas that has been photoheated to around $T = 2\times 10^4$~K.
+Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
+We define five different gas phases following those defined in (Cite Draine ISM): molecular, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
+See Appendix (ref) for a quantitative definition of these phases.
+Each of these exist in our simulations, and are regulated by the complex interplay between turbulence, self-gravity, and stellar feedback throughout the galaxy's evolution.
+Here we discuss the phase properties of the gas throughout the simulation box and within the ISM of our dwarf galaxy.
 
-Comparing these two diagrams it is apparent that the stellar ionizing radiation significantly impacts the detailed properties of the galaxy's ISM in regions well outside our artificial truncation radius of 50 pc.
-This radiation is able to prevent the cooling of dense gas to the very low temperatures seen in the right hand diagram and maintains a significant amount of photoheated gas at temperatures around 10$^4$~K.
+Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas in the simulation domain, averaged over the final 50 Myr of simulation time.
+One can readily identify the two most massive regions of gas in the simulation, a low density, warm phase produced through ionization and supernovae heating, and a cold, high density phase which makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
+[discuss what is / is not in disk from this diagram]
 
 \begin{figure*}
-\includegraphics[width=0.45\linewidth]{sndriving_phase.png}
-\includegraphics[width=0.45\linewidth]{shortrad_phase.png}
-\caption{The temperature-number density phase diagrams for both simulations, averaged over the last 150 Myr of simulation time.}
+\includegraphics[width=0.45\linewidth]{phase_diagram.png}
+\caption{The full-box temperature vs. number density phase diagram of our dwarf galaxy simulation, averaged over the final 50 Myr of simulation time.}
 \label{fig:phase}
+\end{figure*}
+
+The mass of the ISM in our dwarf galaxy is dominated by the CNM over the entire simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
+Together, the CNM and WNM comprise roughly 90\% of the galaxy's gas mass.
+The hotter WIM and HIM contain little mass, but by far dominate the ISM volume, as shown in the right panel.
+(more here)
+
+\begin{figure*}
+\includegraphics[width=0.45\linewidth]{mass_fraction_evolution.png}
+\includegraphics[width=0.45\linewidth]{volume_fraction_evolution.png}
+\caption{The evolution of the mass and volume fractions for each phase of our galaxy's ISM. This figures only consider gas present within the disk of the galaxy.}
+\label{fig:ISM_evolution}
 \end{figure*}
@@
 
-\begin{figure}
-\includegraphics[width=0.9\linewidth]{element_mass_comparison_fraction}
-\caption{Ratio of amount of mass in a given mutually exclusive phase (disk, halo, and stars) between the fiducial and shortrad simulations.
+%\begin{figure}
+%\includegraphics[width=0.9\linewidth]{element_mass_comparison_fraction}
+%\caption{Ratio of amount of mass in a given mutually exclusive phase (disk, halo, and stars) between the fiducial and shortrad simulations.
 The halo ratio has been multiplied by 0.5 for clarity.
@@
 this was the least painful, but open to suggestions}.}
-\label{fig:element mass ratio}
-\end{figure}
+%\label{fig:element mass ratio}
+%\end{figure}
 
@@
 \includegraphics[width=0.4\linewidth]{sn_radius_hist}
-\caption{Distribution of peak and average gas densities (left) in the injection region of each of the supernovae from simulation XXX.
-On the right, we show the radius of the pressure driven snowplow phase of the supernova, computed using the average and peak densities, for each supernova.
-The vertical lines give one and three cell widths.
-As shown, a fraction of these SN are certainly under resolved, with R$_{\rm PDS}$ less than the size of the initial injection region, but a majority are resolved.
-\textbf{font sizes and labels need improving - AE}}
+\caption{Distribution of peak and average gas densities (left) in the injection region of each of the supernovae from the simulation.
+On the right, we give the distribution of the radius of the pressure driven snowplow phase for each supernova assuming a uniform medium at either the peak or average density in the injection region.
+The vertical lines give one and 4.5 cell widths.
+As shown, a fraction of these SN are certainly under resolved, with R$_{\rm PDS}$ less than a single cell size, but a majority are resolved.}
 \label{fig:supernova histogram}

### 2017-10-18 main.tex
Update on Overleaf.

@@
 To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic UV background.
-We use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation, and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$).
+We use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$).
 Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback.
@@
 We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors.
-We follow yields for 12 individual metal species, chemically tagging each star with the associated local gas abundances for each species.
-These methods are discussed in detail below.
+We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star with the associated local gas abundances for each species.
+These methods are discussed in full detail below.
 
 \subsection{Hydrodynamics and Gravity}
+\label{sec:hydro}
 
@@
 We require that the Jeans length be resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution.
-Our maximum resolution in the initial comparison simulations presented here is 2.5 pc, but our peak resolution in our fiducial set of lower mass galaxies is 1.5~pc (see Emerick et.
-al.
-in prep).
+Our maximum resolution in the simulations presented here is 1.8 pc.
 At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation.
@@
 This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
+The use of a pressure floor is common in galaxy scale simulations with limited dynamic range.
+(\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out.
+Leave it in?})
 
@@
 We outline specific model choices made in our simulations and refer the reader to \citep{GrackleMethod} for a detailed discussion of the code.
-We apply the \cite{Glover2008} three body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and {2005ApJ...626..627O} as included in \texttt{Grackle}.
+We apply the \cite{Glover2008} three body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
 However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$) with the broken power law scalings from \cite{Remy-Ruyer2014}.
 For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the the default behavior in \texttt{Grackle}.
+% Since we assume a dust abundance that depends only on metallicity, we do not track dust destruction or creation, which may play an important role regulating detailed ISM properties.
+(Vogelsberger is working on this directly but no papers yet...
+will cite if it gets submitted by then)
 
@@
 Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities.
-We use re-computed metal line tables consistent with the self-shielding approximation.
-Our effective cooling curve and these new tables are publicly available in the main \texttt{Grackle} repository.
+To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.
+We have made these new tables public in the main \texttt{Grackle} repository.
 These are both discussed in greater detail in Appendix ~\ref{appendix:cooling}.
@@
 We make the common ansantz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
-At high resolution, one's choice of $\epsilon_{\rm f}$ is irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
+At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
 %but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
@@
 Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
-Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 14 individual species abundances (H, He, and the 12 metals) we follow in our simulations.
+Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with 17 individual species abundances (H, He, and the 15 metals) we follow in our simulations.
 Stars evolve throughout the simulation, losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation.
@@
 We stop the artificial driving 25~Myr after the first star particle forms.
-These artificial supernova do not drive chemical evolution of the galaxy, containing metal yields corresponding to the mean ISM abundances.
+These artificial supernova do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
 
@@
 \label{sec:structure}
-We show edge-on (left) and face-on (right) projections of our fiducial galaxy (top) and shortrad (bottom) at the end of the simulation time in Figure~\ref{fig:panel}.
-The left two panels are number density weighted projections through the full disk, giving HI and H$_2$ column density.
-The right hand panels show face-on projections through thin (50 pc) slabs at the center of the galaxy for the interstellar radiation field normalized to the MW value in the solar neighborhood, or $G_o$, and gas temperature.
-In general, the shortrad simulation is visually consistent with that found in \citep{Hu2016,Hu2017}, exhibiting a thick, puffy disk with a relatively smooth HI column and an H$_2$ distribution that is more confined to the plane of the galaxy and is roughly uniformly distributed.
-Looking at the fiducial simulation, it is clear that the ray-tracing radiative transfer produces a significant change in the galactic structure.
-Both the HI and H$_2$ are significantly more disturbed, with notable gaps in the HI column caused by regions carved out by the ionizing radiation, and with significantly less uniform H$_2$ column, from molecular hydrogen destroyed through ionization heating.
 
-%\begin{figure}
-%\includegraphics[width=0.9\linewidth]{panel/sndriving_particles}\\
-%\vspace{0.1cm}
-%\includegraphics[width=0.9\linewidth]{panel/shortrad_particles}
-%\caption{Face on, density weighted projections of gas number density for both galaxies.
-Each of the black points represents a single particle (star) in the simulation, and can be a living star, a white dwarf, a massless tracer originating from a Type Ia explosion, or a SNII remnant.
-The population is dominated by low mass stars; only a fraction of these particles have active feedback (winds, radiation, supernovae) at any one moment.
-\textbf{yes plot fonts and label sizes need fixing - AE}}
-%\label{fig:number density}
-%\end{figure}
+We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images over the simulation time, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
+Each figure gives density weighted projections of number density (first row), temperature slices (second row), HI column density projections (third row), and O column density projections (fourth row), at four different times in the simulation \textit{(list times here)}.
+In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points.
+\textit{(discuss properties and any interesting characteristics here)}
 
-The differences are further emphasized in the temperature projections, where a visually more significant fraction of the gas in the fiducial simulations sits at temperatures near 10$^4$~K, and much less sits at very low ($\sim$ 10 K) temperatures.
-The differences between gas phase in these simulations is discussed in Section~\ref{sec:phase}.
-The ISRF of both galaxies is quite similar, though since the ISRF in our model is generated by massive stars alone, it reflects the SFR over the previous 10 - 40 Myr, which is in fact similar in both galaxies (see Section~\ref{sec:sfr}).
+\begin{figure*}
+\centering
+\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
+\caption{Edge on projections (placeholder)}
+\label{fig:panel_x}
+\end{figure*}
 
-Finally, in Figure~\ref{fig:number density} we present face-on projections of gas number density in both galaxies, marking each star particle in the simulation with an individual black point.
-Although the particles obscure some of the structure in the disk, the same general differences noted above are visible here.
-In particular, the fiducial simulation has significantly more disturbed gas morphology with larger regions of low density gas, and less dense gas structures.
+\begin{figure*}
+\centering
+\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
+\caption{Face on projections (placeholder)}
+\label{fig:panel_z}
+\end{figure*}
 
@@
 \label{sec:sfr}
+
+\textit{ Give plots here showing SFR + SNR, HI mass evolution, and stellar mass evolution.
+Would be nice to combine this somehow into as few plots as possible.
+Discuss evolution (this is likely the largest change with simulation time (will we hit a quiescent period??))}
 
@@
 
-In Figure ~\ref{fig:SFR} we compare the star formation rates of both simulations (left), along with the stellar mass evolution (middle), and HI mass evolution (right).
-The peak and average SFRs for each galaxy over the 270~Myr simulation time are comparable, with a peak at roughly $0.04$~M$_{\odot}$~yr$^{-1}$ and an average of about $1.1~\times~10^{-3}$~M$_{\odot}$~yr$^{-1}$ in each simulation.
-However, the SFR evolution is qualitatively different, with the fiducial run exhibiting a $\sim$80~Myr period of minimal, patchy star formation between 125~Myr and 200~Myr ($<\rm{SFR}>~=~2.2\times~10^{-5}~$M$_{\odot}$~yr$^{-1}$).
-Although there is a lull in star formation during this time in the shortrad case, star formation is continuous.
-This difference is due solely to the long-range effects of stellar ionizing radiation, though we cannot also rule out the possibility that it also makes SN feedback more effective.
-It is apparent in this simulation that stellar radiation feedback is effective at suppressing star formation galaxy wide, not just locally.
-
-%\begin{figure}
-%\includegraphics[width=0.9\linewidth]{HI_surface_density}
-%\caption{\textbf{Coloring / style needs to change} Time averaged HI surface density profiles (dashed line) for both galaxies over the simulation time.
-The hatched regions show one standard deviation from the mean in each radial bin.
-Although there is noticeable variance in the HI profile in both galaxies, it is significantly greater for the full physics simulation.
-Truncating the ionizing photons to local regions alone results in a steadier and on average greater amount of HI at all but the very outer edge of the galaxy.}
-%\label{fig:HI profile evolution}
-%\end{figure}
-
-The long-range effects of the ionization are clear in the HI evolution of these galaxies (middle).
-The presence of stellar ionizing radiation throughout the galaxy decreases the amount of HI gas present in the disk by a factor of $\sim$4, by the end of the simulation time.
-Figure~\ref{fig:HI profile evolution} shows the average HI surface density profile of each galaxy over the course of the simulation time, with the filled regions indicating one standard deviation from the mean.
-These differences in evolution lead to differences in metal production and distribution in these two galaxies, discussed further in \ref{sec:chemical evolution}.
-
 \subsection{Outflow Properties}
@@
 
-Show mass loading factors as a function of time here at all radii.
+Recent works expect large outflows from low mass dwarf galaxies, with mass loading factors on order of 10 - 1000 (cite fire etc.).
+Comparatively, Hu et.
+al.
+find more modest mass loading factors for their dwarf galaxies, simulated with a comparable set of detailed feedback physics, though in a more massive dwarf galaxies, as this work.
+In Figure~\ref{fig:mass_loading} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
+We follow \cite{Muratov2015} in defining our mass outflow, taking the outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius, or $\dot{M}_{\rm outflow} = \sum M_{\rm gas} \times v_{\rm r} / dL$.
+We choose $dL = 0.1 R_{\rm vir}$, or 2.74 kpc.
+
+The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 R$_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
+We use the 10 Myr averaged SFR to compute the mass loading rates.
+The outflow rate at 0.1 R$_{\rm vir}$ is high, corresponding to mass loading factors on order of 50 - 100 throughout the simulation time.
+This quickly declines towards larger radii, however, with effectively zero outflow past the virial radius.
+\cite{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20-40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift.
+Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \cite{Muratov2015}, but perhaps slightly below the typical values.
+Interestingly, the v$_{\rm c}$ $\sim$ 30 km s$^{-1}$ halos examined in \cite{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
+Using a fit provided in \cite{Muratov2015} to extrapolate and compare at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few lower than what we find.
+These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
+We note, however, that our results are much closer to the \citep{Muratov2015} results than those in \cite{Hu2016,Hu2017}, which find mass loading factors at 0.05 R$_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^10$ M$_{\odot}$.
+
+% figure here of mass loading and mass outflow rates
+\begin{figure*}
+\centering
+\includegraphics[width=0.45\linewidth]{total_mass_outflow}
+\includegraphics[width=0.45\linewidth]{total_mass_loading}
+\caption{Spherical mass outflow rates and mass loading rates over time at 4 different radii from the galaxy.}
+\label{fig:mass_outflow}
+\end{figure*}
+
+Detailed outflow properties, beyond outflow rates and mass loading factors, are important discriminators between the model dependent feedback physics included in galaxy simulations.
+(this has been shown previously with XX XX XX producing very different outflow properties depending on what physics is included).
+In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
+Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{1}$ or below.
+This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities.
+The distribution has a very long tail out to and beyond 500 km s$^{-1}$.
+These dominant launching mechanism in this simulation are supernovae (Emerick et.
+al.
+in prep), generating a rapidly moving and volume filling HIM.
+However, as shown the HIM comprises very little of the outflow by mass.
+Most of the outflowing gas comes from the warm phase, pushed out by the high pressure, fast moving HIM.
+Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
+The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
 
@@
 \end{figure}
-
-Detailed outflow properties, beyond outflow rates and mass loading factors, are important discriminators between the model dependent feedback physics included in galaxy simulations.
-(this has been shown previously with XX XX XX producing very different outflow properties depending on what physics is included).
-In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
-Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{1} or below.
-This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities.
-The distribution has a very long tail out to and beyond 500 km s$^{-1}$.
-These dominant launching mechanism in this simulation are supernovae (Emerick et.
-al.
-in prep), generating a rapidly moving and volume filling HIM.
-However, as shown the HIM comprises very little of the outflow by mass.
-Most of the outflowing gas comes from the warm phase, pushed out by the high pressure, fast moving HIM.
-Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
-The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
 
@@
 
-\begin{figure*}
+\begin{figure}
 \includegraphics[width=0.45\linewidth]{phase_diagram.png}
@@
 \label{fig:phase}
-\end{figure*}
+\end{figure}
 
@@
 \begin{figure*}
+\centering
 \includegraphics[width=0.45\linewidth]{mass_fraction_evolution.png}
@@
 
-\subsection{Chemical Evolution} %and Metal Enriched Outflows}
+\subsection{Interstellar Radiation Field}
+\label{sec:ISRF}
+
+The ISRF of our galaxy varies dramatically in both space and time.
+This is not surprising in the low star formation rate regime, where at any given point in space or time there are only a few massive, radiating stars.
+In Figure~\ref{fig:ISRF} we present 1D volume averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time.
+The top panel shows the average $G_{\rm o}$, or the ISRF flux between 6 - 13.6 eV normalized to the value in the solar neighborhood of the Milky Way (see Section XX).
+The contribution from the metagalactic background is below the lower vertical axis limit on this plot.
+The shaded region gives the minimum and maximum value of $G_{\rm o}$ in the sampled time range.
+As shown, regions typically experience fluctuations of an order of magnitude across the galaxy of the ISRF.
+Interestingly, the central 200 pc does not contain the peak of the ISRF in the galaxy.
+This is likely a transient property of the galaxy, however, and is a by-product of the inside-out star formation of this dwarf galaxy.
+By the end of the simulation the feedback from stars produced in the central region has reduced the SFR compared to outer parts of the galaxy.
+The latter is thus host to more radiating young stars.
+
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{G_o_profile} \\
+\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
+\caption{1D radial profiles of the ISRF in our galaxy in three different bands, time-averaged over the final 50 Myr of simulation time.
+The top panel gives $G_{\rm o}$, or the flux of radiation between 6 - 13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position.
+The bottom panel gives the HI and HeI ionizing stellar radiation flux, showing average value and maximum values only.
+For these fields the minimum value reaches zero at some point over the examined period at all radii.}
+\label{fig:ISRF}
+\end{figure}
+
+The bottom panel gives the ionizing photon fluxes (HI and HeI) from ionizing photons from the stellar radiation \texttt{only}.
+Since these fields are tracked directly with ray-tracing radiative transfer, the profiles encode information about local attenuation of these photons from dense, neutral gas.
+This is the main driver of the differences between these fields and $G_{\rm o}$.
+In addition, we only show the average line and shade to the maximum value at any given position, since the minimum value reaches zero at all radii at some point over the 50 Myr examined.
+As shown, this causes the profile to vary much more dramatically at all radii.
+However, the same general trend is preserved of less radiation in the inner 200 pc than the region between 200 and 400 pc.
+The rapid drop off beyond 400 pc is due to the rapid attenuation of ionizing photons by the cold gas at large radii (see Figure~\ref{fig:panel}).
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
+\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
+\caption{\textbf{THESE PLOTS ARE SINGLE SNAPSHOT PLACEHOLDERS, AND NOT TIME AVERAGED} Time averaged 2D radial profile plots of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
+Here, we include all gas within 25 pc of the midplane of our dwarf galaxy.
+We note the large difference in color scale between the two plots.
+Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
+This gas readily appears in the $G_{\rm o}$ since we assume it to be optically thin, though do apply a localized shielding approximation.}
+\label{fig:ISRF}
+\end{figure*}
+
+These plots are useful to understand the time-varying properties of the ISRF in a spatially averaged sense.
+However, the local variations for individual regions can be much larger than is illustrated in these profiles.
+In Figure~\ref{fig:ISRF_2D} we present a 2D profile of $G_{\rm o}$ averaged over the final 50 Myr of the simulation time, which effectively captures the large spikes in local ISRF from recent star forming regions.
+The 1D profiles accurately capture the averaged heating / ionizing effects of the ISRF in our galaxy, which helps reduce star formation by increase the thermal pressure support and equillibrium temperature of the ISM, yet it is these spikes that act as important local feedback to shut off star formation in dense, collapsing regions that satisfy our star formation criteria.
+
+\subsection{Chemical Evolution} 
 \label{sec:chemical evolution}
-Although our simulations are long enough to begin to discuss morphological and dynamical differences between the galaxies, they are too short to focus in detail in chemodynamical evolution.
-For this reason, we make only a brief comparison between these two galaxies, saving a more detailed examination for our simulations of lower mass dwarf galaxies run for $\sim$Gyr timescales (Emerick et.
-al.
-in prep).
-
-%\begin{figure}
-%\includegraphics[width=0.9\linewidth]{element_mass_comparison_fraction}
-%\caption{Ratio of amount of mass in a given mutually exclusive phase (disk, halo, and stars) between the fiducial and shortrad simulations.
-The halo ratio has been multiplied by 0.5 for clarity.
-We caution against making any interpretation of Mn and ratios for the s and r-process elements (Y, Ba, and Eu) as there is very little mass of these elements produced in the $\sim$100 Myr timescales examined here.
-\textbf{comment: I thought of a few different ways of conveying this information, but all were painful to look at or make (e.x.
-double bar graph showing fractional element dist)...
-this was the least painful, but open to suggestions}.}
-%\label{fig:element mass ratio}
-%\end{figure}
-
-In Figure~\ref{fig:element mass ratio} we divide the total mass of each element contained in each of three regimes (stars, disk, or halo) of the fiducial simulation by the mass in the shortrad simulation (i.e.
-$>$ 1 means more mass in the given in the given phase in the fiducial simulation).
-We multiply the halo ratio, defined as all elements outside the disk but within the virial radius, by 0.5 for clarity.
-Although the total metal production in each galaxy is similar, the partitioning of those metals differs significantly.
-
-The fiducial simulation contains more (by a factor of 3 to 5) mass in a given species in the halo than the shortrad simulation.
-The additional feedback produced by tracing radiation outside 50 pc from each stars effectively drives gas and metals out of the disk.
-Most of this gas driven into the halo is still contained well within R$_{\rm vir}$ of this galaxy.
-It is unclear whether or not the additional feedback in the fiducial model will be able to move gas farther out into the halo.
-We note that a majority of the produced mass is still in the disk for each simulation, which is why the disk ratios are around unity.
-Though it varies for each element, the halo masses represent 10-20\% of the disk mass for the fiducial simulation, and 3-5\% for the shortrad simulation.
-
-The feedback differences also impact the stellar metal abundance evolution in each galaxy.
-On average, the total mass of each element locked away in stars in the shortrad simulation is roughly twice as much as that contained in stars in the fiducial simulation.
-This is somewhat surprising because not only does the fiducial simulation have a slightly greater stellar mass by the end of the 270 Myr run time (2 $\times$ 10$^4$ M$_{\odot}$), but it also forms more of its stars later than the shortrad simulation.
-Naively, this should mean there would be more mass in a given element locked in the fiducial simulation stars as it has both more mass in stars and there has been slightly more time for produced metals to mix with the ISM and into these stars.
-This implies that differences in feedback evolution can lead to potentially significant differences in stellar abundances.
-
-We caution against any interpretation of the ratio for Mn and the ratios for the s-process and r-process elements (Y, Ba, and Eu) as there is very little mass in these species in either simulation.
-However, we do point out that the ratios for N are qualitatively different than each other element.
-There is more N in the shortrad disk than the fullrad and its ratios are all much closer to unity than any other element.
-We suspect this is because, at these low metallicities, the IMF weighted N production is dominated by stellar winds of massive stars around $8 - 10$~M$_{\odot}$ and AGB stars\footnote{Although AGB stars are less relevant on these timescales.
-The lifetime of a 5 M$_{\odot}$ star at these metallicities is on order of 100 Myr} .
-However, IMF weighted production for the other species are dominated by SNe.
-This means most of the N produced is injected in a wind phase.
-This is more easily retained and mixed in the ISM than the other elements which are injected with much higher energy in SNe.
-These initial results immediately suggest that differences in both included feedback and mechanisms for yield injection can create discernible differences in stellar abundance patterns.
-How abundance variations like this evolve over longer timescales in lower mass dwarf galaxies is the subject of ongoing work (Emerick et.
+Observations of Local Group dwarf galaxies have shown that they retain very little of the total amount of metals they are expected to produced, given their star formation histories (examples and citations).
+In Figure~\ref{fig:metal_evolution} we show the fraction of metals retained within the disk / expelled into the halo of our galaxy over time, along with a break down of the locations of each metal species by the end of the simulation time.
+As shown in the top panel, a majority of each metal tracer species is found outside the disk of the galaxy, in the galaxy halo.
+In total, 70\% of the tracer metal species produced lie out side of the disk of our galaxy.
+Interestingly, the exact fraction is not uniform across metal species.
+Most notably, Nitrogen, is preferentially retained by the galaxy over the other species.
+Roughly 40\% of the Nitrogen produced remains in the disk, as compared to 30\% of Oxygen and 25\% of Iron, for example.
+This difference is entirely feedback driving.
+At our galaxy's metallicity, the IMF weighted production of Nitrogen rests entirely with the stellar winds of stars between 8 and 10 M$_{\odot}$; there is little to no N production in supernovae at this metallicity.
+The rest of the species either have very little stellar wind production, produced solely in supernovae, or have similar production levels between both supernovae and stellar winds (e.x.
+Oxygen).
+The injection of N to the galaxy at typically lower energies than supernovae means N is preferentially retained within the ISM, rather than ejected through supernovae driven outflows.
+In truth the stars that produce the most Nitrogen do eventually explode as supernovae, sweeping up local Nitrogen into outflows.
+However, clearly some of this Nitrogen is able to mix more effectively within the ISM than the other metal species.
+How abundance variations like this evolve over longer timescales and with varying feedback physics is the subject of ongoing work (Emerick et.
 al.
@@
 
-\textbf{I did have a panel plot showing column for each element here, but decided to take it out. Might be worth putting in panel comparison for a few elements, but not sure. Suggestions? - AE}
-%\begin{figure*}
-%\includegraphics[width=0.9\linewidth]{DD0204_elements}
-%\caption{Panel plot of elements \textbf{PLACEHOLDER FOR NOW}}
-%\label{fig:elements panel}
-%\end{figure*}
+\begin{figure}
+\includegraphics[width=0.9\linewidth]{species_bar.png}\\
+\includegraphics[width=0.9\linewidth]{species_bar_disk.png}
+\caption{The fraction of each species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone each in phase of the ISM (bottom).}
+\label{fig:species_fractions}
+\end{figure}
+
+The bottom panel illustrates where these metals are partitioned within the ISM of the galaxy at the end of the simulation time.
+Clearly the metals retained by the galaxy are roughly evenly partitioned between the CNM, WNM, and WIM.
+The HIM in the galaxy disk seems to contain relatively little metals, which runs counterintuitive to the fact that most metals are initially injected in this phase in supernovae explosions.
+However, any given parcel of gas in this phase is short-lived, either cooling and mixing into the rest of the phases of the ISM or is rapidly ejected from the galaxy in metal-enriched outflows.
+(significance to observations of these variations?
+Should I get into more detail about abundances in these gas phases or save for future paper?
+leaning towards saving)
+
+\subsection{Stellar Properties}
+We plot the $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ ratio for all star particles in our simulation that are ``alive'' in Figure~\ref{fig:stellar_abundance}.
+This represents stars that have not gone supernovae or have otherwise formed a compact object.
+Here, $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$, and the notation [X/Y] denotes the ratio of the abundance of species X over Y, relative to the solar value, or [X/Y] = log(X/Y) - log(X$_{\odot}$/Y$_{\odot}$).
+All stars in this plot are colored by their age.
+
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{alpha_over_fe}
+\caption{The $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$
+diagram for all stars in our simulation, colored by their age. Here, we define $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$}
+\label{fig:stellar_abundance}
+\end{figure}
+
+As expected, there is a noticeable trend of stellar age with [Fe/H]; especially in our case as the overall iron abundance is gradually increasing, yet we do not have any accretion of primordial material.
+Interestingly, the few stars with the highest [Fe/H], between -3 and -2, are not the most recently formed; the most recent star formation is clustered around [Fe/H] between -3 and -4.
+
+We note the ``knee'' like feature at very low [Fe/H] is not the characteristic knee seen in $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ space, corresponding to the period when iron enrichment from SNIa begins to make a significant contribution to the galactic chemical evolution.
+This generally occurs after roughly 1 Gyr of stellar evolution, far longer than the XXX Myr simulated here.
+The origin of this feature and the longer term chemical evolution of this galaxy will be investigated in a future work.
 
@@
 \subsection{Comparison to Previous Work}
-\textbf{I am going back and forth on how much this is needed given the above comparison to Hu's simulations. Thoughts? - AE}
+\textbf{Probably need to discuss similarities / differences to Hu simulations here, as well as Forbes, and some FIRE stuff.
+But not totally sure how much detail I should go into and where to focus.
+Thoughts?}
 % still not sure what to do here...
@@
 \subsection{Detailed Dust Model}
+\textbf{Should we discuss this? If so I definitely need more info and references - AE}.
 The dust content of our galaxy is modeled only approximately, scaling with the cell-to-cell variations in gas metallicity.
@@
 Accounting for metals trapped in a dust phase would produce additional variations in the cooling rates and potentially changes to the galactic chemodynamical evolution.
-\textbf{Should we actually discuss this?
-If so I definitely need more info and references - AE}.
 
 \subsection{Detailed Stellar Evolution and Binary Stars}
-\textbf{I haven't written anything for this because not sure if its worth including.
-Definitely something I'm interested in exploring and it will make a difference, but it is likely lower on my priority list.
-Would it be worth mentioning how this can effect things (longer lived ionization in binary stars, delayed SNe, etc.)?}
+\textbf{Definitely a question that comes up a lot whenever I say our simulations are star-by-star and detailed (as in ``but what about binary stars''?).
+Do we need to discuss this here as a quick paragraph about how it would affect feedback properties (namely radiation and different stellar lifetimes)?}
 
@@
 
-In this work, we showed the results of a pair of comparison simulations to the isolated dwarf galaxies simulations previously in \citep{Hu2016} and \citep{Hu2017}.
-\textbf{will finish once discussion is done}
+In this work, we presented the initial results of these methods applied to the evolution of an isolated, low mass dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
 

### 2017-10-19 main.tex
Update on Overleaf.

@@
 \label{sec:results}
+\textit{intro text}
 
-%\begin{figure*}
-%\includegraphics[width=0.23\linewidth]
-
-%\begin{figure*}
-%\includegraphics[width=0.23\linewidth]{panel/HI_sndriving.png}
-%\includegraphics[width=0.23\linewidth]{panel/H2_sndriving.png}
-%\includegraphics[width=0.23\linewidth]{panel/G_o_sndriving.png}
-%\includegraphics[width=0.23\linewidth]{panel/temperature_sndriving.png}\\
-%\vspace{0.1cm}
-%\includegraphics[width=0.23\linewidth]{panel/HI_shortrad.png}
-%\includegraphics[width=0.23\linewidth]{panel/H2_shortrad.png}
-%\includegraphics[width=0.23\linewidth]{panel/G_o_shortrad.png}
-%\includegraphics[width=0.23\linewidth]{panel/temperature_shortrad.png}
-%\caption{Projections of our fiducial galaxy (top) and shortrad galaxy (bottom) at the end of the simulation time.
-The left two panels are integrated projections through the full disk, giving HI and H$_2$ column density.
-On the right, we show thin, face-on projections of G$_{o}$ and temperature in the central 50 pc of the disk.
-We note both the strange dark region in the top $G_o$ plot and the white boxes at the edges of the thin projections are artifacts of the visualization process, and are not present in the simulation.\textbf{yes plot fonts and label sizes need fixing - AE}}
-%\label{fig:panel}
-%\end{figure*}
-
-\subsection{Morphological Structure}
+\subsection{Morphological Structure and Evolution}
 \label{sec:structure}
@@
 In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points.
-\textit{(discuss properties and any interesting characteristics here)}
+\textit{(discuss properties and any interesting characteristics here...
+maybe give a table of scale height, scale radius, half light radius, at each of these times?)}
 
@@
 \includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
-\caption{Edge on projections (placeholder)}
+\caption{textbf{Draft figure - need to pretty up and finalize fields and times.} Edge-on views of our dwarf galaxy at four different times in its evolution, beginning with the time at first star formation and ending at XXX Myr.
+Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving HI column density (third row) and O column density (fourth row).
+Additionally, each individual main sequence star particle is shown in the number density projections as a single black dot.}
 \label{fig:panel_x}
 \end{figure*}
+
+The gas disk is is thin outside the stellar radius of our galaxy, but is still resolved.
+In Figure~\ref{fig:scale_height} we plot the scale height of our gas disk as a function of radius for various times over the simulation evolution, including the initial conditions.
+At the outer edges of the cold disk, the scale height is roughly 15 pc.
+Prior to the first star formed, the scale height in the inner 200 pc is roughly 20 pc.
+Though small, each of these scale heights are resolved at our maximum resolution of 1.8 pc.
+However, the typical scale heights are much larger after the onset of stellar feedback, roughly 100-200 pc at various above/below the stellar disk.
+The stellar feedback produces vertical density profiles that decrease slowly with height above/below the midplane, leading to these large scale heights.
+(\textit{I have a very rough couple sentences here on the mass-weighted height of the disk, but commented it out...}
+%We additionally compute the mass weighted height of the disk, defined as $H = (\sum{Mz^2}/\sum{M})^{1/2}$, where the summation is over each gas cell, as a function of radius (not shown here).
+$H$ is generally larger than the scale height by a factor of 2, but is comparable to the scale height at radii with ongoing star formation, indicating a particularly uniform-then-truncated density distribution.
+At large radii, away from active star formation, $H$ is roughly 50 pc, or $\sim$ 3 times the scale height.
 
@@
 \includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
-\caption{Face on projections (placeholder)}
+\caption{\textbf{Draft figure - need to pretty up and finalize fields}. Same as Figure~\ref{fig:panel_x}, but showing face-on projections/slices.}
 \label{fig:panel_z}
 \end{figure*}
+
+The increased gravitational potential towards the center of our dwarf galaxy leads to an inside-out star formation evolution, whereby star formation propagates from the inner regions outward during the galaxy's evolution.
+This is obvious in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
+This region quickly becomes volume-filled with warm and hot gas generated from radiation feedback and supernovae.
+Both the ISM and the halo gas is multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident by the temperature slices in both panels.
+
+Interestingly, there is significant structure well above the gas disk in the form of dense clouds and filamentary features, as seen in the edge-on projections.
+These gas cold gas clumps appear to have typical sizes on order of $\sim$ 10 pc, but with tails that can extend up to 100 pc.
+These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy.
+These clumps have typical velocities on order of a few to 10 km s$^{-1}$, and appear to survive for 10 - 100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk.
+The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.975\linewidth]{scale_height}
+\caption{\textbf{VERY ROUGH DRAFT FIGURE:}\textit{Current scale height computation is approximate only...
+need to write a better method which will help with some of the noisiness of the result, and not be prone to over/underestimating}.
+The average gas disk scale height as a function of radius for the last XX Myr of simulation time (black) as compared to the uniform initial conditions (blue) and the scale height profile immediately before the first star formed (orange).}
+\label{fig:scale_height}
+\end{figure}
 
@@
 
-\textit{ Give plots here showing SFR + SNR, HI mass evolution, and stellar mass evolution.
-Would be nice to combine this somehow into as few plots as possible.
-Discuss evolution (this is likely the largest change with simulation time (will we hit a quiescent period??))}
+\textit{Discuss evolution in Figure~\ref{fig:sfr_mass_evolution} (this is may have the largest qualitative change with more simulation time (will we hit a quiescent period??))}
 
-%\begin{figure*}
-%\includegraphics[width=0.32\linewidth]{sfr_comparison}
-%\includegraphics[width=0.32\linewidth]{stars_mass_comparison}
-%\includegraphics[width=0.32\linewidth]{HI_mass_comparison}
-%\caption{The 10 Myr averaged SFR (left), stellar mass (middle), and disk HI mass (right) for each galaxy. \textbf{need to increase font sizes and y axis lim}}
-%\label{fig:SFR}
-%\end{figure*}
+\begin{figure*}
+\centering
+\includegraphics[width=0.475\linewidth]{sfr_snr}
+\includegraphics[width=0.475\linewidth]{mass_evolution}
+\caption{The star formation rate and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left), along with the evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy (right).}
+\label{fig:sfr_mass_evolution}
+\end{figure*}
 
@@
 \begin{figure}
-\includegraphics[width=0.45\linewidth]{phase_diagram.png}
+\centering
+\includegraphics[width=0.95\linewidth]{phase_diagram.png}
 \caption{The full-box temperature vs. number density phase diagram of our dwarf galaxy simulation, averaged over the final 50 Myr of simulation time.}
@@
 The mass of the ISM in our dwarf galaxy is dominated by the CNM over the entire simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
-Together, the CNM and WNM comprise roughly 90\% of the galaxy's gas mass.
-The hotter WIM and HIM contain little mass, but by far dominate the ISM volume, as shown in the right panel.
-(more here)
+However, the volume is dominated by both the WIM and HIM gas phases, as shown in the right panel.
+Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
+Together, the CNM and WNM comprise roughly 90\% of the galaxy's mass throughout its entire evolution.
+The WNM represents roughly 30\% of the volume at the end of the simulation, while the volume of the CNM is completely negligible.
+Together, the two warm phases, WNM and WIM, comprise a majority of the ISM volume, the rest occupied by the HIM.
 

### 2017-10-23 main.tex
Update on Overleaf.

@@
 
+We make extensive use of the open-source \textsc{yt} toolkit \citep{yt} in the analysis of these simulations.
+All of the analysis scripts used for this work can be found at https://github.com/aemerick/galaxy-analysis.
+
 \subsection{Morphological Structure and Evolution}
@@
 
-\textit{Discuss evolution in Figure~\ref{fig:sfr_mass_evolution} (this is may have the largest qualitative change with more simulation time (will we hit a quiescent period??))}
+We present the star formation rate (SFR) and core collapse supernova rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.
+By the end of the simulation, there have been no Type 1a supernovae.
+Within the first 40 Myr of evolution the SFR rises quickly to between $2-4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, and remains at this level with fluctuations of about a factor of 2 at most.\footnote{The granularity in our star formation algorithm creates a lower limit in the SFR that depends on the period over which the SFR is measured ($\Delta t$).
+Since we produce stars in $\sim 100$ M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
+For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$.} Averaging over the entire simulation time since the first star was formed, we obtain a $<\rm{SFR}> = 2.34 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
+(compare to observed galaxies given gas mass).
+
+At initialization, the H and He of our dwarf galaxy is entirely neutral, with no molecular hydrogen component.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\% of the total mass in the galaxy's disk.
+The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases to about 25\% as the total amount of mass in the disk decreases through feedback driven winds.
+Small drops in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback.
+Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008, Mcquin2012,Amorin2016}.
 
@@
 \includegraphics[width=0.475\linewidth]{mass_evolution}
-\caption{The star formation rate and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left), along with the evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy (right).}
+\caption{The SFR and core collapse SNR in our dwarf galaxy in 10 Myr bins (left), along with the evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy (right).
+Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and SNR.}
 \label{fig:sfr_mass_evolution}
@@
 Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
-We define five different gas phases following those defined in (Cite Draine ISM): molecular, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
-See Appendix (ref) for a quantitative definition of these phases.
+We define five different gas phases following those defined in \citep{Draine2011}: molecular, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
+See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
 Each of these exist in our simulations, and are regulated by the complex interplay between turbulence, self-gravity, and stellar feedback throughout the galaxy's evolution.
@@
 
+\section{Gas Phases of the ISM}
+\label{appendix:phases}
+
+To aid with comparison to other works, we reproduce our definitions for the various phases of the ISM, as adopted from \cite{Draine2011} Table 1.3.
+These are used consistently throughout this analysis.
+These definitions are constructed to be mutually exclusive and implicitly assume gas within a given phase is in static equilibrium within that phase.
+
+\begin{enumerate}
+\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
+\item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
+\item Warm Neutral Medium (WNM): $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$
+\item Cold Neutral Medium (CNM): \textbf{MAY CHANGE} $T < 10^2$ K, $n < 100$ cm$^{-3}$
+\item Molecular: \textbf{MAY CHANGE} $T < 10^2$, $n > 100$ cm$^{-3}$
+\end{enumerate}
+
 \section{Stellar Radiation Properties}

### 2017-11-10 main.tex
Update on Overleaf.

--- 2017-10-19 main.tex
@@
 \shorttitle{Feedback with Individual Stars}
-\shortauthors{Emerick, Bryan, Mac-Low}
+\shortauthors{Emerick, Bryan, Mac Low}
 \newcommand{\msun}{M$_{\odot}$}
@@
 This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}.
-See both \cite{SomervilleDave2015} and \cite{NaabOstriker2016} for recent reviews on these topics.
+See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.
 
@@
 
-There is a considerable body of work examining the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}, nearly all of which are implemented with smooth particle hydrodynamics (SPH) schemes.
-Only recently have chemical evolution models been implemented in grid-based codes \citep{Few2012,Few2014,Vorobyov2015}.
-This is a vital and complimentary approach given the well known differences between hydrodynamics implementations \citep[e.g][]{Agertz2007,AGORA,AGORA2}.
-In particular, metal mixing must be handled through a sub-grid model in standard SPH schemes \citep[e.g.][]{Shen2010} that generally must be tuned to some degree to obtain reasonable results.
-The differences in how one handles this mixing can lead to problems in connecting the results of galactic chemical evolution models with the fundamental physics that drives the evolution \citep{Revaz2016}.
+Due to its complexity, the detailed interstellar medium (ISM) and chemical abundance properties, beyond total metallicity, are sensitive tests of the underlying physical processes that govern galaxy evolution.
+Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
+There is a considerable body of work examining the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
+These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017} and more detailed quantities such as metallicity distribution functions (MDFs) and abundance evolution of individual species \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
+However, there is a general lack of numerical diversity in these works, as a majority are implemented in some flavor of smooth particle hydrodynamics (SPH) schemes.
+Given the known differences between hydrodynamics implementations \citep{Agertz2007,AGORA,AGORA2}, extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.
+Additionally, grid-based schemes are able to generally avoid issues with metal mixing, one of the largest model uncertainties in standard SPH codes.
+
+The native SPH scheme is incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
+This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017} which, while sophisticated, must still generally be fine-tuned.
+Even more, a given parameterization is not necessarily applicable generally \citep{Revaz2016}, though recent studies have shown great improvements to this end \citep{Escala2017}.
+Metal mixing efficiencies my also vary species-by-species (refs), as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
+In part, this is because mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) in which they are injected to the ISM.
+The variations in how one handles sub-grid metal injection and metal mixing schemes can lead to challenges in connecting models back to the fundamental physics that drives galactic evolution.
 We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mash refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies.
 
+Although increasing physical resolution reduces one's reliance on sub-grid physics, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations (SSPs) \citep[as studied in detail in ][]{Revaz2016} do not make physical sense.
+Below 10$^4$ M$_{\odot}$, SSPs begin to no longer fully sample the IMF, and can no longer be considered average representations of stellar populations; this becomes conceptually problematic at SSP masses comparable to or below the mass of the most massive star ($\sim 100$ M$_{\odot}$).
+Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Rosdahl2015,Kroupa2013}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
+Perhaps the most naive solution, though untenable for large scale simulations, is to remove the SSP formalism and track stars as individual particles.
+In this work, we follow stars as individual star particles, allowing us to place unprecedented detail on our accounting of stellar feedback processes and chemical enrichment.
+
 The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms.
-Doing so with dwarf galaxies in particular is advantageous as their small physical scales and low star formation rates allow for greater physical realism without excessive computational expense.
-We follow recent work that used low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution.
-For example, \citet{Forbes2016} found that a self-consistent model of photoelectric heating in dwarf galaxies is an important channel of feedback.
-\citet{Hu2016} and \citet{Hu2017} examined the relative importance in galaxy evolution of supernovae, photoelectric heating, detailed ISM chemistry, and an approximate method for stellar ionizing radiation.
-
-Increasing resolution, while more expensive, generally makes it easier to model physical processes in galaxy evolution.
-However, at high particle mass resolution ($\lesssim 10^3$ M$_{\odot}$), the standard treatment of star particles as simple stellar populations (SSP) breaks down.
-At these masses the IMF is no longer fully sampled, requiring a fundamentally different approach to how the simulated particles inject feedback and yields.
-Although there are solutions to this issue, each incurs additional model complexity with associated uncertainties.
-We refer the reader to \cite{Revaz2016} for a detailed accounting of this issue and possible means of addressing it.
-Naively, the best solution is to push towards galaxy scale simulations removing the SSP formalism and following stars individually.
-This allows for a detailed, star-by-star accounting of both stellar feedback and chemical enrichment without having to implement an additional sub-grid model to address the limitations of SSPs.
-In this work, we follow stars as individual star particles for the first time in a galaxy scale simulation.
-
-Our work builds upon our current understanding of galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
+We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution.
+For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies.
+\citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
+Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
 Using star-by-star modeling, we are able to capture in more detail the stellar yields from individual stars released over their lifetime.
 In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
-This opens an exciting new channel for testing models of galaxy evolution by enabling us to leverage current and ongoing observations probing the detailed chemical abundances of stars in the Milky Way and Local Group.
-\textbf{(citations to obs campaigns - GAIA, RAVE, APOGEE, etc.).}
+This opens an exciting new channel for testing models of galaxy evolution by enabling us to leverage current and ongoing observations probing the detailed chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
 
@@
 We outline specific model choices made in our simulations and refer the reader to \citep{GrackleMethod} for a detailed discussion of the code.
-We apply the \cite{Glover2008} three body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
-However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$) with the broken power law scalings from \cite{Remy-Ruyer2014}.
-For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the the default behavior in \texttt{Grackle}.
+We apply the \citet{Glover2008} three body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
+However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$) with the broken power law scalings from \citet{Remy-Ruyer2014}.
+For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
 % Since we assume a dust abundance that depends only on metallicity, we do not track dust destruction or creation, which may play an important role regulating detailed ISM properties.
@@
 
-Metal line cooling is modeled using pre-computed \texttt{Cloudy}\footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \cite{HM2012} UV metagalactic background.
+Metal line cooling is modeled using pre-computed \texttt{Cloudy}\footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
 As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
@@
 \label{sec:star formation}
-In order resolve individual star formation on galaxy scales, we implement a stochastic star formation algorithm adopted from \cite{Goldbaum2015,Goldbaum2016}.
+In order resolve individual star formation on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
 Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
@@
 In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution.
-We therefore allow star formation to proceed stochastically, following the methods in \cite{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses.
+We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses.
 In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
@@
 For the first time in galaxy scale simulations, we track galactic chemodynamical evolution using stellar yields as ejected from star particles that represent individual stars.
-We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep[][Ritter et.
-al.
-in prep]{Pignatari2016}.
+We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}.
 This grid includes yields from the AGB phase of stars between 1 and 7 M$_{\odot}$, as well as yields from both stellar winds and core collapse supernova of massive stars over 12 to 25 M$_{\odot}$.
@@
 Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35 - 40 Myr), and the energy injection from these winds.
-\cite{Cote2017} explores how one's choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.
+\citet{Cote2017} explores how one's choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.
 
-There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[][and references therein]{Cote2016}.
+There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}.
 Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable/unstable regimes as a function of mass \citep{Heger2003}.
@@
 These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
-We use the Type Ia supernova yields given in \cite{Thielemann1986}, adopting a Type Ia supernova model as discussed in Section~\ref{sec:Type Ia}.
+We use the Type Ia supernova yields given in \citet{Thielemann1986}, adopting a Type Ia supernova model as discussed in Section~\ref{sec:Type Ia}.
 
@@
 We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors.
-At the end of their life, we assign a new mass to these particles following the initial to final mass relation of \cite{Salaris2009}.
+At the end of their life, we assign a new mass to these particles following the initial to final mass relation of \citet{Salaris2009}.
 \textbf{I originally reproduced the equations here, but it is currently commented out.
@@
 We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution (DTD) model.
-\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):} The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope and normalization are observables, and $\eta$ the fraction of stars which can form SN Ia progenitors that \textit{will} explode as a SN Ia within a Hubble time.
+%\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):} 
+The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope and normalization are observables, and $\eta$ the fraction of stars which can form SN Ia progenitors that \textit{will} explode as a SN Ia within a Hubble time.
 The value for $\eta$ depends on the normalization of the DTD (an observable), as well as one's choice of IMF and mass range of potential SN Ia progenitors (as given above).
@@
 where $N_{\rm Ia}/M_{\rm SF}$ is the DTD normalization, which represents the fraction of stars that form SN Ia progenitors, $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF ($dN/dm$), and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
-The DTD slope, $\beta$, is of order unity, with typical values between 1.0 and 1.2 (see \cite{Maoz2014} for a recent review).
+The DTD slope, $\beta$, is of order unity, with typical values between 1.0 and 1.2 (see \citet{Maoz2014} for a recent review).
 $N_{\rm Ia}/M_{\rm SF}$ represents the number of SN Ia per mass of star formation; this can be derived by taking observed values of the SNIa rate and integrating over a Hubble time.
 Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
-We adopt 1.2 \cite{Maoz2010} and 0.8$\times 10^{-3}$ M$_{\odot}^{-1}$ \cite{GraurMaoz2013} for our fiducial values of $\beta$ and $N_{\rm Ia}/M_{\rm SF}$.
+We adopt 1.2 \citet{Maoz2010} and 0.8$\times 10^{-3}$ M$_{\odot}^{-1}$ \citet{GraurMaoz2013} for our fiducial values of $\beta$ and $N_{\rm Ia}/M_{\rm SF}$.
 Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.
@@
 \label{sec:diffusive heating}
-We include two forms of diffusive heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \cite{HM2012}, and 2) localized photoelectric (PE) heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars.
+We include two forms of diffusive heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citet{HM2012}, and 2) localized photoelectric (PE) heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars.
 Photoelectric heating can be a dominant heating mechanism in the ISM \citep{Parravano2003} of the Milky Way, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
@@
 Self-shielding of gas against the metagalactic UV background is important in high resolution simulations, particularly for low-mass, low metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy.
-We have implemented the \cite{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background (see \citep{GrackleMethod} for more details of this implementation).
+We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background (see \citep{GrackleMethod} for more details of this implementation).
 We assume HeI ionization generally follows HI.
@@
 We ignore HeII photoionization from the UV background entirely.
-Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \cite{Hu2017}).
+Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \citet{Hu2017}).
 As mentioned previously, we have re-computed metal line cooling tables using \texttt{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
@@
 %Ignoring this effect leads to an overestimation of the cooling rates when in the self-shielding regime.
-%We refer to \cite{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \cite{Gracklemethod} for its specific implementation, as used here.
+%We refer to \citet{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \citet{Gracklemethod} for its specific implementation, as used here.
 
@@
 The FUV flux in each cell is summed over contributions from each star.
-We parameterize the local photoelectric heating rate following \cite{BakesTielens1994}, \cite{Wolfire2003}, and \cite{Bergin2004}, where
+We parameterize the local photoelectric heating rate following \citet{BakesTielens1994}, \citet{Wolfire2003}, and \citet{Bergin2004}, where
 \begin{equation}
@@
 where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\rm{exp}(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust to gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
-Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \cite{Hu2016} and \cite{Hu2017}.
+Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016} and \citet{Hu2017}.
 
-$D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \cite{Remy-Ruyer2014} (see Section~\ref{sec:chemistry}).
+$D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014} (see Section~\ref{sec:chemistry}).
 The extremely low dust to gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a $D$ that scales linearly with metallicity at very low metallicity.
@@
 This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; each of which are not followed directly in these simulations.
-Instead, we use a log-linear fit of $\epsilon$ as a function of $n_{\rm H}$ from the \cite{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
-%This is a compromise between adoption a constant efficiency, as in \cite{Forbes2016}, and a more detailed model with more detailed non-equillibrium chemistry \cite[e.x.][]{Hu2016}.
+Instead, we use a log-linear fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
+%This is a compromise between adoption a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equillibrium chemistry \citet[e.x.][]{Hu2016}.
 
@@
 The galaxy presented in this work is constructed to be similar to the observed properties of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, but is not intended to be a matched model to this galaxy.
-Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4}$ adopting $Z_{\odot} = 0.018$ from \cite{Asplund2009}.
+Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4}$ adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}.
 Our dwarf galaxy is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citep{McQuinn2015}.
@@
 The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equillibrium with a static, background dark matter potential.
-The gas profile follows \cite{Tonnesen2009} and \cite{Salem2015}, or
+The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, or
 \begin{equation}
@@
 
-Following the initialization procedure of \cite{Hu2017}, we use artificial supernova driving to generate realistic densities and turbulent properties in the galaxy ISM.
+Following the initialization procedure of \citet{Hu2017}, we use artificial supernova driving to generate realistic densities and turbulent properties in the galaxy ISM.
 This additionally prevents an otherwise uniform collapse of the gas disk.
@@
 \label{sec:results}
-\textit{intro text}
+We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:star formation}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first \textbf{200 Myr} after the first star forms.
+Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.\footnote{All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset \textbf{changeset number}.}
 
@@
 
-We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images over the simulation time, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
+We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
 Each figure gives density weighted projections of number density (first row), temperature slices (second row), HI column density projections (third row), and O column density projections (fourth row), at four different times in the simulation \textit{(list times here)}.
 In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points.
-\textit{(discuss properties and any interesting characteristics here...
-maybe give a table of scale height, scale radius, half light radius, at each of these times?)}
+Towards the end of the simulation time, the half light radius is $389 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
+
+The increased gravitational potential towards the center of our dwarf galaxy leads to an inside-out star formation evolution, whereby star formation propagates from the inner regions outward during the galaxy's evolution.
+This is obvious in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
+This region quickly becomes volume-filled with both warm and hot gas generated from radiation feedback and supernovae respectively.
+Both the ISM and the halo gas is multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident by the temperature slices in both panels.
+The ISM properties are quantified further in Section~\ref{sec:phase}.
 
@@
 
-The gas disk is is thin outside the stellar radius of our galaxy, but is still resolved.
-In Figure~\ref{fig:scale_height} we plot the scale height of our gas disk as a function of radius for various times over the simulation evolution, including the initial conditions.
-At the outer edges of the cold disk, the scale height is roughly 15 pc.
-Prior to the first star formed, the scale height in the inner 200 pc is roughly 20 pc.
-Though small, each of these scale heights are resolved at our maximum resolution of 1.8 pc.
-However, the typical scale heights are much larger after the onset of stellar feedback, roughly 100-200 pc at various above/below the stellar disk.
-The stellar feedback produces vertical density profiles that decrease slowly with height above/below the midplane, leading to these large scale heights.
-(\textit{I have a very rough couple sentences here on the mass-weighted height of the disk, but commented it out...}
+The gas disk is is thin outside the stellar radius of our galaxy, but is resolved at all radii.
+In Figure~\ref{fig:scale_height} we plot the scale height of our gas disk as a function of radius averaged over the last 20 Myr of simulation time (black), at the initial conditions (blue), and just before first star formation (orange).
+At the outer edges of the disk, beyond regions of ongoing star formation, the scale height is $\sim 15$ pc, comparable to the scale height in the inner 200 pc prior to first star formation.
+Though small, both of these scale heights are resolved at our maximum resolution, 1.8 pc; we note that without feedback, our gas disk would continue to cool and collapse to an uresolved, razor thin disk.
+For the majority of the galaxy, stellar feedback sets the scale height.
+Heating, from both stellar radiation and supernovae, lifts gas above the midplane and generating scale heights between 40 and 100 pc within the half light radius.
+Effective galactic winds have carved out most of the gas within the inner 40 pc, distributing it somewhat smoothly above/below the midplane, leading to the significantly larger scale heights.
+This is made clear in the density panels if Fig~\ref{fig:panel_x}, where regions of active star formation show a general lack of the dense, cool gas that creates the smaller scale heights at larger radii.
 %We additionally compute the mass weighted height of the disk, defined as $H = (\sum{Mz^2}/\sum{M})^{1/2}$, where the summation is over each gas cell, as a function of radius (not shown here).
@@
 
-The increased gravitational potential towards the center of our dwarf galaxy leads to an inside-out star formation evolution, whereby star formation propagates from the inner regions outward during the galaxy's evolution.
-This is obvious in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
-This region quickly becomes volume-filled with warm and hot gas generated from radiation feedback and supernovae.
-Both the ISM and the halo gas is multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident by the temperature slices in both panels.
-
 Interestingly, there is significant structure well above the gas disk in the form of dense clouds and filamentary features, as seen in the edge-on projections.
-These gas cold gas clumps appear to have typical sizes on order of $\sim$ 10 pc, but with tails that can extend up to 100 pc.
+These gas cold gas clumps appear to have typical sizes on order of $\sim$ 10 pc, but with lower density tails that can extend up to 100 pc.
 These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy.
-These clumps have typical velocities on order of a few to 10 km s$^{-1}$, and appear to survive for 10 - 100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk.
+These clumps have typical velocities on order of a few to tens of km s$^{-1}$, and appear to survive for 10 - 100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk.
 The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work.
+This is exciting given recent \citep[e.g.][]{Zheng2017} and ongoing \citep{Zheng2017HST} observational observational work examining the disk-halo interface in nearby galaxies.
 
@@
 \includegraphics[width=0.975\linewidth]{scale_height}
-\caption{\textbf{VERY ROUGH DRAFT FIGURE:}\textit{Current scale height computation is approximate only...
-need to write a better method which will help with some of the noisiness of the result, and not be prone to over/underestimating}.
-The average gas disk scale height as a function of radius for the last XX Myr of simulation time (black) as compared to the uniform initial conditions (blue) and the scale height profile immediately before the first star formed (orange).}
+\caption{The average gas disk scale height as a function of radius for the last 20 Myr of simulation time (black) as compared to the uniform initial conditions (blue) and the scale height profile immediately before the first star formed (orange).}
 \label{fig:scale_height}
@@
 
-\textit{Discuss evolution in Figure~\ref{fig:sfr_mass_evolution} (this is may have the largest qualitative change with more simulation time (will we hit a quiescent period??))}
+We present the star formation rate (SFR) and core collapse supernova rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.
+By the end of the simulation, there have been no Type 1a supernovae.
+Within the first 40 Myr of evolution the SFR rises quickly to between $2-4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, and remains at this level with fluctuations of about a factor of 2 or less.\footnote{The granularity in our star formation algorithm creates a lower limit in the SFR that depends on the period over which the SFR is measured ($\Delta t$).
+Since we produce stars in $\sim 100$ M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
+For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$.
+Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense.
+Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.} Averaging over the entire simulation time since the first star was formed, we obtain a $<\rm{SFR}> = 2.34 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
+The star formation rate of our model galaxy as compared to observed galaxies is discussed further in Section~\ref{sec:observation}.
+
+At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about \textbf{$6 \times 10^5$ M$_{\odot}$, or roughly 17\%} of the total mass in the galaxy's disk.
+The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases to about \textbf{25\%} as the total amount of mass in the disk decreases through feedback driven winds.
+Small drops in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback.
+Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
+The molecular properties of our galaxy is discussed further in context with other works in Section~\ref{sec:observation}.
 
@@
 \includegraphics[width=0.475\linewidth]{mass_evolution}
-\caption{The star formation rate and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left), along with the evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy (right).}
+\caption{Left: The SFR and core collapse SNR in our dwarf galaxy in 10 Myr bins (left).
+Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy over time.
+Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and SNR.}
 \label{fig:sfr_mass_evolution}
@@
 
-\subsection{Outflow Properties}
-\label{sec:outflows}
-
-Recent works expect large outflows from low mass dwarf galaxies, with mass loading factors on order of 10 - 1000 (cite fire etc.).
-Comparatively, Hu et.
-al.
-find more modest mass loading factors for their dwarf galaxies, simulated with a comparable set of detailed feedback physics, though in a more massive dwarf galaxies, as this work.
-In Figure~\ref{fig:mass_loading} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
-We follow \cite{Muratov2015} in defining our mass outflow, taking the outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius, or $\dot{M}_{\rm outflow} = \sum M_{\rm gas} \times v_{\rm r} / dL$.
-We choose $dL = 0.1 R_{\rm vir}$, or 2.74 kpc.
-
-The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 R$_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
-We use the 10 Myr averaged SFR to compute the mass loading rates.
-The outflow rate at 0.1 R$_{\rm vir}$ is high, corresponding to mass loading factors on order of 50 - 100 throughout the simulation time.
-This quickly declines towards larger radii, however, with effectively zero outflow past the virial radius.
-\cite{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20-40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift.
-Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \cite{Muratov2015}, but perhaps slightly below the typical values.
-Interestingly, the v$_{\rm c}$ $\sim$ 30 km s$^{-1}$ halos examined in \cite{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
-Using a fit provided in \cite{Muratov2015} to extrapolate and compare at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few lower than what we find.
-These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
-We note, however, that our results are much closer to the \citep{Muratov2015} results than those in \cite{Hu2016,Hu2017}, which find mass loading factors at 0.05 R$_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^10$ M$_{\odot}$.
-
-% figure here of mass loading and mass outflow rates
-\begin{figure*}
-\centering
-\includegraphics[width=0.45\linewidth]{total_mass_outflow}
-\includegraphics[width=0.45\linewidth]{total_mass_loading}
-\caption{Spherical mass outflow rates and mass loading rates over time at 4 different radii from the galaxy.}
-\label{fig:mass_outflow}
-\end{figure*}
-
-Detailed outflow properties, beyond outflow rates and mass loading factors, are important discriminators between the model dependent feedback physics included in galaxy simulations.
-(this has been shown previously with XX XX XX producing very different outflow properties depending on what physics is included).
-In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
-Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{1}$ or below.
-This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities.
-The distribution has a very long tail out to and beyond 500 km s$^{-1}$.
-These dominant launching mechanism in this simulation are supernovae (Emerick et.
-al.
-in prep), generating a rapidly moving and volume filling HIM.
-However, as shown the HIM comprises very little of the outflow by mass.
-Most of the outflowing gas comes from the warm phase, pushed out by the high pressure, fast moving HIM.
-Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
-The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{outflow_velocity_distribution}
-\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-The outflowing material is multiphase, broken into WNM, WIM, and HIM.
-See XXX for definitions of these regimes.
-We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$K.
-There is little to no outflowing mass in the CNM or molecular phases.}
-\label{fig:outflow_velocity}
-\end{figure}
-
-Final paragraph on metallicity of outflowing material.
-
-\subsection{Phase Diagrams}
+\subsection{Phase Diagrams and ISM Properties}
 \label{sec:phase}
 
-Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
-We define five different gas phases following those defined in (Cite Draine ISM): molecular, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
-See Appendix (ref) for a quantitative definition of these phases.
+Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy \textbf{too strong of a claim?}.
+We define five different gas phases following those defined in \citep{Draine2011}: molecular, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
+See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
 Each of these exist in our simulations, and are regulated by the complex interplay between turbulence, self-gravity, and stellar feedback throughout the galaxy's evolution.
@@
 One can readily identify the two most massive regions of gas in the simulation, a low density, warm phase produced through ionization and supernovae heating, and a cold, high density phase which makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
-[discuss what is / is not in disk from this diagram]
+\textbf{not completely sure what to talk about here for the diagram}
 
@@
 The mass of the ISM in our dwarf galaxy is dominated by the CNM over the entire simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
-However, the volume is dominated by both the WIM and HIM gas phases, as shown in the right panel.
+Together, the CNM and WNM comprise roughly 90\% of the galaxy's mass throughout most of its evolution.
+While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume each, though the two warm phases dominate.
+The volume fractions are subject to significantly more fluctuations over time, due to the low SFR and SNR of our galaxy.
 Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-Together, the CNM and WNM comprise roughly 90\% of the galaxy's mass throughout its entire evolution.
-The WNM represents roughly 30\% of the volume at the end of the simulation, while the volume of the CNM is completely negligible.
-Together, the two warm phases, WNM and WIM, comprise a majority of the ISM volume, the rest occupied by the HIM.
+These results are in some contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}.
+In short, they find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass.
+Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few.
 
@@
 \centering
-\includegraphics[width=0.45\linewidth]{mass_fraction_evolution.png}
-\includegraphics[width=0.45\linewidth]{volume_fraction_evolution.png}
+\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
+\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
 \caption{The evolution of the mass and volume fractions for each phase of our galaxy's ISM. This figures only consider gas present within the disk of the galaxy.}
@@
 
-The ISRF of our galaxy varies dramatically in both space and time.
-This is not surprising in the low star formation rate regime, where at any given point in space or time there are only a few massive, radiating stars.
+The ISRF of our galaxy varies dramatically in both space and time, as has been deomonstrated previously in works modelling varying radiation fields \citep{Parravano2003,Hu2017}.
+This is especially not surprising in the low SFR regime, where there can be large fluctuations in proximity to a massive, radiating star over time.
 In Figure~\ref{fig:ISRF} we present 1D volume averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time.
@@
 The shaded region gives the minimum and maximum value of $G_{\rm o}$ in the sampled time range.
-As shown, regions typically experience fluctuations of an order of magnitude across the galaxy of the ISRF.
+As shown, regions typically experience fluctuations in the ISRF of an order of magnitude.
 Interestingly, the central 200 pc does not contain the peak of the ISRF in the galaxy.
-This is likely a transient property of the galaxy, however, and is a by-product of the inside-out star formation of this dwarf galaxy.
+This is likely a transient property, however, and is a by-product of the inside-out star formation of this dwarf galaxy.
 By the end of the simulation the feedback from stars produced in the central region has reduced the SFR compared to outer parts of the galaxy.
@@
 As shown, this causes the profile to vary much more dramatically at all radii.
-However, the same general trend is preserved of less radiation in the inner 200 pc than the region between 200 and 400 pc.
-The rapid drop off beyond 400 pc is due to the rapid attenuation of ionizing photons by the cold gas at large radii (see Figure~\ref{fig:panel}).
+However, the same general trend is preserved of less radiation in the inner 200 pc than the region between 200 and 400 pc, and an order of magnitude or more fluctuation at all radii.
+The rapid drop off beyond 400 pc is due to the rapid attenuation of ionizing photons by the cold gas at large radii (see Figure~\ref{fig:panel_x}).
 
@@
 \includegraphics[width=0.45\linewidth]{q_o_2D_phase}
-\caption{\textbf{THESE PLOTS ARE SINGLE SNAPSHOT PLACEHOLDERS, AND NOT TIME AVERAGED} Time averaged 2D radial profile plots of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
+\caption{Single-snapshot 2D radial profile plots of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
 Here, we include all gas within 25 pc of the midplane of our dwarf galaxy.
@@
 This gas readily appears in the $G_{\rm o}$ since we assume it to be optically thin, though do apply a localized shielding approximation.}
-\label{fig:ISRF}
+\label{fig:ISRF_2D}
 \end{figure*}
@@
 The 1D profiles accurately capture the averaged heating / ionizing effects of the ISRF in our galaxy, which helps reduce star formation by increase the thermal pressure support and equillibrium temperature of the ISM, yet it is these spikes that act as important local feedback to shut off star formation in dense, collapsing regions that satisfy our star formation criteria.
+This point will be examined in more detail in future work with comparison simulations using different feedback processes (Emerick et.
+al.
+in prep).
+
+\subsection{Outflow Properties}
+\label{sec:outflows}
+
+Recent cosmological simulations of dwarf galaxies with detailed feedback over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors on order of 10 - 1000 \citep{Muratov2015}.
+However, comparable work of idealized dwarf galaxies with detailed feedback and physics models find more modest mass loading factors \citep{Hu2016,Hu2017}.
+In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
+We follow \citet{Muratov2015} defining the mass outflow rate ($\dot{M}_{\rm outflow}$) at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius.
+In other words, $\dot{M}_{\rm outflow} = \sum M_{\rm gas} \times v_{\rm r} / dL$.
+We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.
+
+The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
+We use the 10 Myr averaged SFR to compute the mass loading rates.
+The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50 - 100 throughout the simulation time.
+This quickly declines towards larger radii, however, with effectively zero outflow past the virial radius.
+\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20-40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift.
+Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below the typical values.
+
+Interestingly, the v$_{\rm c}$ $\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
+Using a fit provided in \citet{Muratov2015} to extrapolate and compare at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
+These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
+We note, however, that our results are much closer to the \citep{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly much smaller mass loading factors at 0.25 $R_{\rm vir}$.
+
+% figure here of mass loading and mass outflow rates
+\begin{figure*}
+\centering
+\includegraphics[width=0.45\linewidth]{total_mass_outflow}
+\includegraphics[width=0.45\linewidth]{total_mass_loading}
+\caption{Spherical mass outflow rates and mass loading rates over time at 4 different radii from the galaxy.}
+\label{fig:mass_outflow}
+\end{figure*}
+
+Detailed outflow properties, beyond outflow rates and mass loading factors, are important discriminators between the model dependent feedback physics included in galaxy simulations.
+\textbf{(do I need an example of this in recent work?)}.
+In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
+Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{1}$ or below.
+This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities.
+The distribution has a very long tail out to and beyond 500 km s$^{-1}$.
+The dominant launching mechanism in this simulation are supernovae (Emerick et.
+al.
+in prep), generating a rapidly moving and volume filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
+However, as shown, the HIM comprises very little of the outflow by mass.
+Most of the outflowing gas comes from the warm phase, pushed out by the high pressure, fast moving HIM.
+Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
+The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{outflow_velocity_distribution}
+\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
+The outflowing material is multiphase, broken into WNM, WIM, and HIM.
+See XXX for definitions of these regimes.
+We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$K.
+There is little to no outflowing mass in the CNM or molecular phases.}
+\label{fig:outflow_velocity}
+\end{figure}
+
+Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
+This has been better quantified recently both observationally \citep[e.g.][]{Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Angles-Alcazar2017,Muratov2017}.
+In Figure~\ref{fig:outflow_metallicity} we show the average ISM metallicity (black), halo metallicity (blue), and outflow metallicities (orange) at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
+The ISM metallicity evolves minimally from the initial conditions in this time, while the halo and outflow properties change significantly.
+It is apparent from this figure that the outflows are preferentially metal enriched, as the halo increases in metallicity by a factor of $\sim 2$ in the simulation time.
+Although most of gas mass in the halo (outside the disk) remains is within 0.2 $R_{\rm vir}$ (see Section~\ref{sec:obs_metals}), the mass that does make it out far and out side the halo is metal enriched by a factor of $\sim$5-6 compared to the ISM.
+This is in contrast with the results from \citet{Muratov2017}, which generally shows $Z_{\rm outflow} \simeq Z_{\rm ISM}$ at $0.25~R_{\rm vir}$ and $Z_{\rm outflow} < Z_{\rm ISM}$ at $1.0~R_{\rm vir}$, though both with some scatter that reaches above $Z_{\rm outflow} > Z_{\rm ISM}$, especially at high redshift.
+However, we note that our simulations certainly do not contain a cosmologically realistic CGM and do not include ongoing cosmological accretion of pristine gas; this will certainly lower the typical halo and outflow metallicities, possibly more in agreement with the findings of \citet{Muratov2017}.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{metallicity_evolution}
+\caption{The mass-weighted average metallicity of our dwarf galaxy's ISM, halo, and outflowing gas at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
+The halo is defined as the region outside of the disk, yet inside the virial radius.}
+\label{fig:outflow_metallicity}
+\end{figure}
 
@@
 \label{sec:chemical evolution}
-Observations of Local Group dwarf galaxies have shown that they retain very little of the total amount of metals they are expected to produced, given their star formation histories (examples and citations).
-In Figure~\ref{fig:metal_evolution} we show the fraction of metals retained within the disk / expelled into the halo of our galaxy over time, along with a break down of the locations of each metal species by the end of the simulation time.
+Observations of Local Group dwarf galaxies have shown that they retain very little of the total amount of metals they are expected to have produced, given their star formation histories (see Section~\ref{sec:observation}).
+In Figure~\ref{fig:species_fractions} we show the fraction of metals retained within the disk / expelled into the halo of our galaxy over time, along with a break down of the locations of each metal species by the end of the simulation time.
 As shown in the top panel, a majority of each metal tracer species is found outside the disk of the galaxy, in the galaxy halo.
-In total, 70\% of the tracer metal species produced lie out side of the disk of our galaxy.
+In total, \textbf{85\%} of the tracer metal species produced lie outside of the disk of our galaxy.
 Interestingly, the exact fraction is not uniform across metal species.
 Most notably, Nitrogen, is preferentially retained by the galaxy over the other species.
-Roughly 40\% of the Nitrogen produced remains in the disk, as compared to 30\% of Oxygen and 25\% of Iron, for example.
-This difference is entirely feedback driving.
-At our galaxy's metallicity, the IMF weighted production of Nitrogen rests entirely with the stellar winds of stars between 8 and 10 M$_{\odot}$; there is little to no N production in supernovae at this metallicity.
-The rest of the species either have very little stellar wind production, produced solely in supernovae, or have similar production levels between both supernovae and stellar winds (e.x.
-Oxygen).
-The injection of N to the galaxy at typically lower energies than supernovae means N is preferentially retained within the ISM, rather than ejected through supernovae driven outflows.
-In truth the stars that produce the most Nitrogen do eventually explode as supernovae, sweeping up local Nitrogen into outflows.
-However, clearly some of this Nitrogen is able to mix more effectively within the ISM than the other metal species.
+
+Roughly \textbf{35\%} of the N produced remains in the disk, as compared to \textbf{15\%} of O and \textbf{15\%} of Fe, for example.
+This difference is entirely feedback driven, but a coincidence of our particular galaxy conditions.
+At our galaxy's metallicity, the IMF weighted production of N rests entirely with the stellar winds of stars between 8 and 10 M$_{\odot}$; there is little to no N production in supernovae at this metallicity.
+The rest of the species either have very little stellar wind production, produced solely in supernovae, or have similar production levels between both supernovae and stellar winds (like O, for example).
+The typically lower injection energies of N into the galaxy than the SN injected elements means N is preferentially retained within the ISM, and not as effectively ejected through outflows.
+In truth, the stars that produce N do eventually explode as supernovae, sweeping up some fraction of the wind produced N into outflows.
+However, clearly some of this N is able to mix more effectively within the ISM than the other metal species.
 How abundance variations like this evolve over longer timescales and with varying feedback physics is the subject of ongoing work (Emerick et.
@@
 The bottom panel illustrates where these metals are partitioned within the ISM of the galaxy at the end of the simulation time.
-Clearly the metals retained by the galaxy are roughly evenly partitioned between the CNM, WNM, and WIM.
-The HIM in the galaxy disk seems to contain relatively little metals, which runs counterintuitive to the fact that most metals are initially injected in this phase in supernovae explosions.
-However, any given parcel of gas in this phase is short-lived, either cooling and mixing into the rest of the phases of the ISM or is rapidly ejected from the galaxy in metal-enriched outflows.
-(significance to observations of these variations?
-Should I get into more detail about abundances in these gas phases or save for future paper?
-leaning towards saving)
+The CNM contains roughly 50-60\% of each species, with the CNM and WNM together accounting for most of the metals in the galaxy.
+The WIM contains only $\sim$ 10\% of each species, with the HIM containing very little.
+This may be counterintuitive to the fact that most metals are initially injected into the galaxy in either the WIM or HIM phases.
+However, the disk metals represent only a small fraction of the total metals produced.
+Much of the metals are effectively removed from the disk into the halo (see Section~\ref{sec:outflows}).
+It is apparently that the remaining metals quickly mix or cool into denser gas phases.
 
-\subsection{Stellar Properties}
+\subsection{Stellar Abundances}
+\label{sec:stellar properties}
 We plot the $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ ratio for all star particles in our simulation that are ``alive'' in Figure~\ref{fig:stellar_abundance}.
 This represents stars that have not gone supernovae or have otherwise formed a compact object.
-Here, $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$, and the notation [X/Y] denotes the ratio of the abundance of species X over Y, relative to the solar value, or [X/Y] = log(X/Y) - log(X$_{\odot}$/Y$_{\odot}$).
-All stars in this plot are colored by their age.
+Here, $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$, and the notation [X/Y] denotes the ratio of the abundance of species X over Y, relative to the solar value, or log([X/Y]) = log(X/Y) - log(X$_{\odot}$/Y$_{\odot}$).
+All stars are colored by their age.
 
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{alpha_over_fe}
+\includegraphics[width=0.95\linewidth]{alpha_over_fe_hist}
 \caption{The $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$
-diagram for all stars in our simulation, colored by their age. Here, we define $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$}
+diagram for all stars in our simulation, colored by their age. Here, we define $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$. Each histogram shows counts, normalized to the peak in each distribution.}
 \label{fig:stellar_abundance}
@@
 We note the ``knee'' like feature at very low [Fe/H] is not the characteristic knee seen in $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ space, corresponding to the period when iron enrichment from SNIa begins to make a significant contribution to the galactic chemical evolution.
-This generally occurs after roughly 1 Gyr of stellar evolution, far longer than the XXX Myr simulated here.
-The origin of this feature and the longer term chemical evolution of this galaxy will be investigated in a future work.
+This generally occurs after roughly 1 Gyr of stellar evolution, far longer than the \textbf{170} Myr simulated here.
+% The origin of this feature and the longer term chemical evolution of this galaxy will be investigated in a future work.
 
@@
 \subsection{Comparison to Previous Work}
-\textbf{Probably need to discuss similarities / differences to Hu simulations here, as well as Forbes, and some FIRE stuff.
-But not totally sure how much detail I should go into and where to focus.
-Thoughts?}
-% still not sure what to do here...
+\textbf{At the moment, doing a lot of this throughout paper. Not certain if I need an explicit, separate discussion here.}
+
+\subsection{Comparison to Observed Low Mass Dwarf Galaxies}
+\label{sec:observation}
+
+\subsubsection{Gas and Star Formation}
+\label{sec:gas_sf}
+
+The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, Tollerud2015, Sand2015}.
+However, the sample of isolated dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
+In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) law (left) for low mass galaxies, and the extended Schmidt law (ESL) (right) which has been shown recently to be extend to low mass, low metallicity dwarf galaxies \citep{Roychowdhury2017}.
+We plot our galaxy every 1 Myr in these diagrams, showing the significant temporal variation in both spaces.
+Although these quantities are conceptually simple, due to how these values are measured observationally it is challenging to make a direct comparison to simulations, particularly in defining the geometric region to measure the surface densities.
+We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs following what is described in \citet{Roychowdhury2014}.
+We define $\Sigma_{\rm sfr} = \dot{M}_{*, \rm{10 Myr}} / A_{*, \rm{10 Myr}}$, where $\dot{M}_{*, \rm{10 Myr}}$ is the SFR measured over the preceding 10 Myr, and $A_{*, \rm{10 Myr}}$ is the disk defined out to the farthest star formed within the previous 10 Myr.
+Likewise, $\Sigma_{\rm gas} = M_{\rm gas, 10 Myr} / A_{*, \rm{10 Myr}}$, where M$_{\rm gas, 10 Myr}$ is the total gas mass within this defined disk.
+However, the total gas content cannot be determined observationally, particularly for low mass dwarf galaxies with a virtually unmeasurable H$_2$ content.
+Therefore, we present $\Sigma_{\rm gas}$ as measured directly in the simulations (green/purple points) and the observational equivalent, or $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He, and where there is no correction for H$_2$ (plasma points).
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution}
+\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution}
+\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every 1 Myr for the total gas surface density computed from the simulations, and an observational analog derived using the HI content (see text for details).}
+\label{fig:KS}
+\end{figure*}
+
+In both panels, we also include recent observational constraints from these relationships.
+We include the KS fits from \citet{Shi2011} with 1$\sigma$ errors (black), the fits from \citet{Roychowdhury2014} (blue), and the individual points from the recent SHIELD sample \citep{Teich2016}; we include only the fit and 1$\sigma$ errors from \citep{Shi2011} for the ESL (black), which have been shown to match well for dwarf galaxies at these surface densities \citep{Roychowdhury2017}.
+In both relationships our simulations fit well around the median observed fit, spanning the 1 $\sigma$ variations about the mean.
+This is a remarkable result.
+In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
+It is non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, but signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
+This result is consistent with recent galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics (\textit{relevant citations})
+
+The molecular gas content of low mass dwarf galaxies like this is generally considered to be small, (references).
+Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas fractions anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
+Given As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ typically of 0.17 - 0.20, in between this range, but significantly above the few percent often found in models.
+This means ignoring the $H_2$ component of our galaxies leads to an average shift of 0.24 dex to the right in the KS relationship, and 0.24 dex right and down in the ESL.
+This does not lead to a significant disagreement with the observed relationships, but would constitute a quantitative change to the observed fits if our $f_{\rm H_2}$ is robust for low mass, low metallicity dwarf galaxies.
+However, our non-equillibrium chemical model for $H_2$ formation and destruction is relatively simple, and does not account for C and O chemistry, a detailed dust model, or cosmic rays; all of which may significantly affect $f_{\rm H_2}$.
+Simulations in \citet{Hu2016} and \citet{Hu2017}, which contain a more detailed non-equillibrium chemistry model than included here, give very low $f_{\rm H_2}$, below $10^{-4}$ for their full feedback simulations; even their simulations without any radiation feedback only reach $f_{\rm H_2} \sim 2 \times 10^{-3}$.
+However, their simulated dwarf galaxies are more massive ($M_{\rm vir} = 10^{10} M_{\odot}$) and higher metallicity ($Z = 0.1 Z_{\odot}$) than those examined here.
+This disagreement warrants additional investigation, particularly as making predictions for the H$_2$ content of low mass dwarf galaxies is valuable.
+We do note that there is some possible observational evidence for higher than expected ($\sim 15$ \%) molecular fractions \citep{Schruba2017}, though this still remains highly uncertain.
+
+\subsubsection{Metal Retention}
+\label{sec:obs_metals}
+
+Unfortunately, these high resolution simulations are not (yet) run for the $\sim$ Gyr timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at z = 0.
+However, we can compare to a key observable, the ejection / retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from stellar evolution models based on the galaxy's star formation history.
+This can be done readily with Milky Way dSph's, whose stars seem to retain very little of the expected metals produced, on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
+However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
+Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low mass dwarf galaxy close enough to the Milky Way to conduct this experiment and with an observable HII region, necessary for determining gas phase abundances.
+Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
+As discussed in Section~\ref{sec:chemical evolution}, roughly \textbf{95\%} of the tracked metals produced throughout the simulation time no longer reside within the galaxy's disk.
+At the end of our simulation, we agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
+Although more than half of these metals are expected to be re-accreted \citep{Angles-Alcazar2017}, it is still possible that, at any moment, most of the metals that have been produced lie outside the galaxy disk.
+We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.
+
+It is interesting to consider where these metals lie outside of the galaxy's disk, in the CGM or ejected into the IGM, and their eventual fate.
+While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of a $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero $\sim$ 60\% of ejected gas is recycled over time, while 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
+In our case, no metals have been ejected outside the virial radius; this is possibly not surprising however given that metals ejected outside the halo would need to travel with an average velocity of 150 km s$^{-1}$ for the entirety of our simulation time.
+\textbf{32\%} of all metals lie within 1 kpc of the center of our galaxy, \textbf{75\%} within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and only \textbf{10\%} outside $R_{\rm vir}$.
+Over time, the re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
+Re-cycling of metal enriched gas, could be a significant source of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) returns.
+Unfortunately, we cannot yet speak to how this gas evolves over time, but will investigate this in future work with our feedback model.
 
@@
 They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
-Although they likely have no dynamical importance, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.
+Although they likely have minimal dynamical importance, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.
 
@@
 \textbf{Definitely a question that comes up a lot whenever I say our simulations are star-by-star and detailed (as in ``but what about binary stars''?).
-Do we need to discuss this here as a quick paragraph about how it would affect feedback properties (namely radiation and different stellar lifetimes)?}
+Do we need to discuss this here as a quick paragraph about how it would affect feedback properties (namely radiation and different stellar lifetimes)?} \citep{Ma2016-binary}
 
@@
 \appendix
+
+\section{Gas Phases of the ISM}
+\label{appendix:phases}
+
+To aid in comparison to other works, we define our ISM phases here, as adopted from \citet{Draine2011} Table 1.3 and used consistently throughout this analysis.
+By construction, these phases are mutually exclusive.
+In the below, $f_{\rm H_2}$ is the molecular hydrogen fraction by abundance.
+
+\begin{enumerate}
+\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
+\item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
+\item Warm Neutral Medium (WNM): $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$
+\item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
+\item Molecular: \textbf{MAY CHANGE} $T < 10^2$, $f_{\rm H_2} > 0.5$
+\end{enumerate}
 
@@
 For most supernovae, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-supernova feedback included in our simulations.
-The right panel of Figure ~\ref{fig:supernova histogram} gives the fractional distribution of the calculated radius of pressure driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \cite{Simpson2016}, given as
+The right panel of Figure ~\ref{fig:supernova histogram} gives the fractional distribution of the calculated radius of pressure driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}, given as
 \[
@@
 where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$.
-\cite{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the supernova explosion with thermal energy injection alone, assuming uniform density in the injection region.
+\citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the supernova explosion with thermal energy injection alone, assuming uniform density in the injection region.
 In practice, the injection region is never uniform.
@@
 Resolving these explosions with thermal energy injection alone depends ultimately on the grid resolution, background density and ISM structure, the background cooling/heating physics used, and the size and shape of the injection region.
-Here, we perform a resolution test of our thermal injection method over four uniform densities (0.1 \ccunit, 1.0 \ccunit, 10.0 \ccunit, and 100.0 \ccunit) for both a 8.0 \msun and 25.0 \msun star, comparing to both the analytic solution and results using kinetic energy injection from \cite{Simpson2015}.
+Here, we perform a resolution test of our thermal injection method over four uniform densities (0.1 \ccunit, 1.0 \ccunit, 10.0 \ccunit, and 100.0 \ccunit) for both a 8.0 \msun and 25.0 \msun star, comparing to both the analytic solution and results using kinetic energy injection from \citet{Simpson2015}.
 These results are presented in Figure~\ref{fig:supernova tests}.
@@
 The solid lines give the absolute value of the net cooling rate, which more clearly indicates the regime at low temperatures where heating dominates.
-The curve as shown includes the z = 0 \cite{HM2012} metagalactic UVB.
+The curve as shown includes the z = 0 \citet{HM2012} metagalactic UVB.
 
@@
 \includegraphics[width=0.95\linewidth]{cooling_curve}
-\caption{The total heating and cooling rates extracted from the core of a Jeans-length sized cloud irradiated by a \cite{HM2012} metagalactic background as modeled in \textsc{Cloudy}.
+\caption{The total heating and cooling rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic background as modeled in \textsc{Cloudy}.
 The absolute value of the net cooling rate is shown with solid lines.}
@@
 First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal line cooling and heating rates are used.
-The actual primordial heating and cooling rates are calculated self-consistently using the non-equillibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \cite{Rahmati2013}.
+The actual primordial heating and cooling rates are calculated self-consistently using the non-equillibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}.
 However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations.
@@
 
-The cooling curves used in this work correct a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with self-shielding approximations.
-Previous work in \cite{Hu2017} details this inconsistency.
+The cooling curves used in this work corrects a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with self-shielding approximations.
+Previous work in \citet{Hu2017} details this inconsistency.
 In short, adopting tabulated metal cooling rates computed under the assumption of an optically thin UV background overestimates the electron fraction in regimes where self-shielding is important, about $-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$, leading to an overestimation of the metal cooling rates.
@@
 Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the un-corrected (i.e.
-optically thin) metal line cooling rates.}
+optically thin) metal line cooling rates.
+The regimes where heating dominates are plotted with dashed lines for clarity.}
 \label{fig:cooling comparison}
@@
 
+\section{Resolution Study}
+\label{appendix:resolution study}
+Insert some light resolution study details here.
+Ultimately this will be somewhat difficult as we need to go into how this is challenging since star formation criteria will change as resolution scales.
 %\section{Pre-SN Feedback with and without radiation}

### 2017-11-16 main.tex
Update on Overleaf.

@@
 
-\begin{figure}
+\begin{figure*}
 \includegraphics[width=0.9\linewidth]{species_bar.png}\\
@@
 \label{fig:species_fractions}
-\end{figure}
+\end{figure*}
 
@@
 \label{sec:stellar properties}
+\textbf{This section needs work.
+As per discussion with Keith and Kathryn, displaying abundance evolution like this is confusing and misleading.
+Switch to discussion of mass / abundance fraction evolution of individual specie(s).}
 We plot the $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ ratio for all star particles in our simulation that are ``alive'' in Figure~\ref{fig:stellar_abundance}.

### 2017-11-17 main.tex
General comments in main-mm.pdf. Other changes made directly in main.tex, silently for minor typos, commented with %mm otherwise.

@@
 These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017} and more detailed quantities such as metallicity distribution functions (MDFs) and abundance evolution of individual species \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
-However, there is a general lack of numerical diversity in these works, as a majority are implemented in some flavor of smooth particle hydrodynamics (SPH) schemes.
+However, there is a general lack of numerical diversity in these works, as a majority are implemented in some flavor of smoothed particle hydrodynamics (SPH) schemes.
 Given the known differences between hydrodynamics implementations \citep{Agertz2007,AGORA,AGORA2}, extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.
@@
 Even more, a given parameterization is not necessarily applicable generally \citep{Revaz2016}, though recent studies have shown great improvements to this end \citep{Escala2017}.
-Metal mixing efficiencies my also vary species-by-species (refs), as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
-In part, this is because mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) in which they are injected to the ISM.
+Metal mixing efficiencies may also vary species-by-species (refs), as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
+In part, this is because mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources)
+%mm in which they are injected to
+    that injects metals into 
+the ISM.
 The variations in how one handles sub-grid metal injection and metal mixing schemes can lead to challenges in connecting models back to the fundamental physics that drives galactic evolution.
-We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mash refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies.
-
-Although increasing physical resolution reduces one's reliance on sub-grid physics, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations (SSPs) \citep[as studied in detail in ][]{Revaz2016} do not make physical sense.
+We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mesh refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies.
+
+Although increasing physical resolution reduces 
+%mm one's 
+reliance on sub-grid physics, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations \citep[SSPs; as studied in detail in ][]{Revaz2016} do not make physical sense.
 Below 10$^4$ M$_{\odot}$, SSPs begin to no longer fully sample the IMF, and can no longer be considered average representations of stellar populations; this becomes conceptually problematic at SSP masses comparable to or below the mass of the most massive star ($\sim 100$ M$_{\odot}$).
 Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Rosdahl2015,Kroupa2013}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
-Perhaps the most naive solution, though untenable for large scale simulations, is to remove the SSP formalism and track stars as individual particles.
-In this work, we follow stars as individual star particles, allowing us to place unprecedented detail on our accounting of stellar feedback processes and chemical enrichment.
+%mm Perhaps the most naive, 
+   The most straightforward
+solution, though untenable for large scale simulations, is to remove the SSP formalism entirely and simply track stars as individual particles. In this work, we 
+%mm follow stars as individual star particles, allowing us to place unprecedented detail on our
+     do this, allowing unprecedented detail in our
+ accounting of stellar feedback processes and chemical enrichment.
 
@@
 Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
+
 Using star-by-star modeling, we are able to capture in more detail the stellar yields from individual stars released over their lifetime.
@@
 For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type 1a supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer.
-In addition, we couple to a self-consistent set of stellar yields tables from the to track stellar yields from massive star stellar winds, AGB star winds, and supernovae.
-We describe each mode of our multi-channel feedback implementation in detail below, and briefly discuss their implementation in an isolated dwarf galaxy simulation.
-
-Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete -- yet brief -- summary of the included physics.
+In addition, we couple to a self-consistent set of stellar yields
+%mm tables from the
+to track stellar yields from massive star stellar winds, AGB star winds, and supernovae. We describe each mode of our multi-channel feedback 
+%mm implementation 
+in detail below, and briefly discuss their implementation in an isolated dwarf galaxy simulation.
+
+Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.
 

### 2017-11-17 main.tex
section 2.0

@@
 \label{sec:methods}
-In brief, we produce high resolution galaxy scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
+In 
+%mm brief, 
+     summary, 
+we produce high-resolution galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
 This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
 To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic UV background.
-We use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$).
+We
+%mm 
+    assume collisional ionization equilibrium for all other elements in order to
+use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$).
 Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback.
@@
 We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors.
-We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star with the associated local gas abundances for each species.
-These methods are discussed in full detail below.
+We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star
+%mm
+   as it forms
+with the associated local gas abundances for each species. These methods are discussed in full detail below.
 

### 2017-11-20 main.tex
revisions through 2.5.1

@@
 
-We set the star formation density threshold to the point which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}).
+We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}).
 Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
@@
 We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset 59adc76b3130.} \texttt{Grackle} is a freely available, open source multi-code library, designed to interface with a wide variety of astrophysical codes.
-We outline specific model choices made in our simulations and refer the reader to \citep{GrackleMethod} for a detailed discussion of the code.
-We apply the \citet{Glover2008} three body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
+We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.
+We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
 However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$) with the broken power law scalings from \citet{Remy-Ruyer2014}.
@@
 \label{sec:star formation}
-In order resolve individual star formation on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
+In order to resolve individual star formation on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
 Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
@@
 
-We make the common ansantz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
+We make the common ansatz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
 At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
 %but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
-The the gas mass converted to stars in a time step, $dt$, is
+The gas mass converted to stars in a time step, $dt$, is
 \begin{equation}
@@
 In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
-If it does, we random sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$.
+If it does, we random sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$.
 We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and maximum stellar mass of 100 M$_{\odot}$.
@@
 Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
-Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with 17 individual species abundances (H, He, and the 15 metals) we follow in our simulations.
-Stars evolve throughout the simulation, losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation.
+Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
+Stars evolve during the simulation, by losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation.
 For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.
@@
 \label{sec:properties}
-Given their birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to each star, as well as an effective temperature ($T_{\rm eff}$) and surface gravity ($g$), used in computing radiation properties (see Section \ref{sec:ionizing radiation}).
+Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}).
 We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$.
@@
 This grid includes yields from the AGB phase of stars between 1 and 7 M$_{\odot}$, as well as yields from both stellar winds and core collapse supernova of massive stars over 12 to 25 M$_{\odot}$.
-We compliment these tables to track stellar winds for stars more massive than 25 M$_{\odot}$ using tables from Slemer et.
+We complement these tables with tables from Slemer et.
 al.
-(in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}; we ignore supernovae yields from these stars (see below).
+(in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014} to track stellar winds for stars more massive than 25 M$_{\odot}$.
+We ignore supernova yields from these stars (see next paragraph).
 We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth.
-Although we can follow an arbitrary number of metal species, practical considerations prevent this in any given simulation.
-We refer the reader to previous uses of the NuGrid yields in one zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion on how various model uncertainties can influence galactic chemical evolution.
-
-Above some mass, $M_{\rm trans}$, within the unsampled range of 7 to 12 M$_{\odot}$ stars do not undergo AGB wind phases and end their lives as core collapse supernovae.
-Where this transition occurs is uncertain, but is commonly taken to be around 8 - 10 M$_{\odot}$.
-This is a free parameter in our model, but we take $M_{\rm trans} = 8$ M$_{\odot}$ as our fiducial value.
+Although we can follow an arbitrary number of metal species, practical considerations
+%mm 
+   of memory use 
+prevent this in any given simulation.
+We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
+
+Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse supernovae.
+Where this transition occurs is uncertain, but is commonly taken to be around 8--10~M$_{\odot}$.
+This is a free parameter in our model, but we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value.
 In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
-Stars above this mass eject their stellar yields via ``massive" stellar winds at a constant mass loss rate throughout their lifetime, ending their lives as a core collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics).
-Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35 - 40 Myr), and the energy injection from these winds.
-\citet{Cote2017} explores how one's choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.
+Stars above this mass
+%mm
+    are assumed to
+eject their stellar yields via 
+%mm ``massive" 
+   line-driven
+stellar winds at a constant mass loss rate throughout their lifetime
+%mm ,
+  (neglecting Wolf-Rayet and luminous blue variable phases),
+ending their lives as a core-collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics).
+Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
+\citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.
 
 There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}.
-Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable/unstable regimes as a function of mass \citep{Heger2003}.
-Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no mass or energy ejection.
-
-Type Ia supernova are an important additional source of galactic chemical enrichment.
+Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
+Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no
+%mm
+    further
+mass or energy ejection.
+
+Type Ia supernovae are an important additional source of galactic chemical enrichment.
 These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
 We use the Type Ia supernova yields given in \citet{Thielemann1986}, adopting a Type Ia supernova model as discussed in Section~\ref{sec:Type Ia}.
+%mm
+    We emphasize that we only track Type Ia supernovae occurring within the 
+    population of stars formed in this model, neglecting supernovae from any 
+    pre-existing population.
 
@@
 \label{sec:stellar winds}
-Stellar winds are important sources of early (massive stars) and late (AGB stars) enrichment and feedback in galaxies.
+Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
 Although the energy injected via winds over the lifetime of a cluster of stars is much less than that of supernovae and radiation, stellar winds are potentially important sources of pre-supernova feedback.

### 2017-11-21 main.tex
added a citation to Reissl et al. 2017, further updates in section 2

@@
 Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
-Although the energy injected via winds over the lifetime of a cluster of stars is much less than that of supernovae and radiation, stellar winds are potentially important sources of pre-supernova feedback.
-In both AGB phase winds and massive star winds we inject the feedback energy in a 3-cell radius spherical region centered on the emitting star particle assuming full thermalization of the wind kinetic energy.
+Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from supernovae and radiation, stellar winds are potentially important sources of pre-supernova feedback.
+%mm For both AGB winds and massive stellar winds
+    In models that include feedback energy from stellar winds from both AGB and 
+    massive stars, 
+we inject the feedback energy in a three-cell radius spherical region centered on the emitting star particle, assuming full thermalization of the wind kinetic energy.
 The total injected energy in timestep $\Delta t$ is therefore $E_{\rm wind} = \dot{M}\Delta t \times v^2_{\rm wind} + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass ($\dot{M}\Delta t$) given the star's interpolated $T_{\rm eff}$.
-We use a monte-carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge if the injection region that is a result of mapping a spherical injection region to cubic grid cells.
-
-We assume constant mass loss rates for all winds as set by the yields tables and either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars). 
+We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells.
+We assume constant mass loss rates for all winds as set by the yields tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars). 
 %Properly modeling stellar winds requires sub-parsec resolution, which is problematic in galaxy-scale simulations.
-Massive star stellar winds have typical velocities on order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}.
+
+Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}.
 Satisfying the Courant time step becomes prohibitively expensive following this gas ($dt \sim$~100~yr), particularly as stellar wind bubbles have typical temperatures of 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
 For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
-In our case, we fix massive star stellar winds to $v_{\rm wind} = 1$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-Our initial tests show that turning off energy injection from stellar winds does not significantly affect the global star formation rate of our galaxies.
-Due to the substantial additional computational expense of following stellar winds for Gyr timescales, we reserve examining the detailed importance of winds to future work.
+In our case, we fix massive stellar winds to $v_{\rm wind} = 1$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
+Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies.
+Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work.
 These points are discussed in more detail in Section \ref{sec:stellar winds discussion}.
@@
 
-Stars that undergo an AGB phase only deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks.
+Stars that only undergo an AGB phase deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks.
 AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$.
-For simplicity, we adopt a fixed AGB phase wind velocity of 20 km s$^{-1}$ for all AGB stars.
+For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars.
 
@@
 Stars between  $M_{\rm thresh} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse supernovae, ejecting mass and yields as determined by the NuGrid stellar yield tables at 10$^{51}$ erg of thermal energy.
-Due to the high resolution (1.5 - 2.5 pc depending on galaxy size) of our simulations, we generally well resolve the Sedov phase of each supernova explosion (see Appendix~\ref{appendix:supernova}).
-We find injecting thermal energy alone in a 3 cell radius spherical region around the star particle to be sufficient to resolve the supernovae explosions.
-We continue to track any remaining stellar mass after the SNe as a massive ``remnant" tracer particle.
+Due to the high resolution (1.5--2.5 pc depending on galaxy size) of our simulations, we generally resolve the Sedov phase of each supernova explosion well (see Appendix~\ref{appendix:supernova}).
+We find injecting thermal energy alone in a three-cell radius spherical region around the star particle to be sufficient to resolve the supernova explosions.
+We continue to track any remaining stellar mass after the supernovae as a massive ``remnant" tracer particle.
 In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment through X-ray binaries and neutron-star-neutron-star merger events which, while rare, could be important in long term galaxy evolution.
-\textbf{Should I reference a few recent hydro sims that included these feedback sources? - AE}
+\textbf{Should I reference a few recent hydro sims that included these feedback sources? - AE  
+%mm
+Can't hurt if they are ready to hand. Not high priority, though. M-M}
 
@@
 We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors.
-At the end of their life, we assign a new mass to these particles following the initial to final mass relation of \citet{Salaris2009}.
-\textbf{I originally reproduced the equations here, but it is currently commented out.
-- AE}
+At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
+%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
 %or, 
@@
 We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WD's that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.
+
 We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution (DTD) model. 
@@
 Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
-We adopt 1.2 \citet{Maoz2010} and 0.8$\times 10^{-3}$ M$_{\odot}^{-1}$ \citet{GraurMaoz2013} for our fiducial values of $\beta$ and $N_{\rm Ia}/M_{\rm SF}$.
+We adopt 1.2 \citep{Maoz2010} and 0.8$\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013} for our fiducial values of $\beta$ and $N_{\rm Ia}/M_{\rm SF}$.
 Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.
@@
 However, when accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily through channels carved through dense clouds.
-Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with limited application in full radiation hydrodynamics simulations \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due the additional computational expense of direct ray tracing.
-As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through ray tracing methods described below.
-In this particular work, we use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).
+Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with limited application in full radiation hydrodynamics simulations \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
+As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through ray tracing methods described below.
+%mm In this particular work, we 
+  We here
+use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).
 
@@
 In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).
-\citep{Dale2012} demonstrated that uncertainties on order of a few in the ionizing radiation rates are not significant in giant molecular cloud (GMC) scale simulations.
+\citet{Dale2012} demonstrated that uncertainties on order of a few in the ionizing radiation rates are not significant in giant molecular cloud (GMC) scale simulations.
 %Generally, the ionizing fluxes from high temperature black bodies underestimate the OSTAR2002 flux, and lower temperature black bodies overestimate the flux by a factor of 2-5 and 10-1000 respectively.
@@
 Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}).
-The average energy for \ion{H}{1} and \ion{He}{1} ionizing photons changes significantly over the OSTAR2002 temperature range ($log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$), ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
-
-We also include the effects of radiation pressure on HI.
+The average energy for \ion{H}{1} and \ion{He}{1} ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
+
+We also include the effects of radiation pressure on \ion{H}{1}.
 This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}.
@@
 However, the importance of multiple scattering is still unclear.
-Other works have shown the effect to only increase the radiation pressure by a factor on order of unity \citep{Krumholz2012,Krumholz2013}.
+Other works have shown the effect to only increase the radiation pressure by a factor on order of unity \citep{Krumholz2012,Krumholz2013,Reissl2017}.
 Due to these uncertainties, and given that we focus on low metallicity dwarf galaxies with low dust content, we ignore this effect.

### 2017-11-21 main.tex
HI -> \ion{H}{1} etc. everywhere. Other small changes

@@
 Radiation feedback (ionization, ionization heating, and radiation pressure) is an important source of pre-SN feedback in galaxies.
-HII regions carved out by stellar radiation change the ISM structure where SNe eventually explode, generally increasing their dynamical importance.
+\ion{H}{2} regions carved out by stellar radiation change the ISM structure where SNe eventually explode, generally increasing their dynamical importance.
 However, when accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily through channels carved through dense clouds.
@@
 However, the importance of multiple scattering is still unclear.
-Other works have shown the effect to only increase the radiation pressure by a factor on order of unity \citep{Krumholz2012,Krumholz2013,Reissl2017}.
-Due to these uncertainties, and given that we focus on low metallicity dwarf galaxies with low dust content, we ignore this effect.
+Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017}.
+Due to these uncertainties, and given that we focus on low-metallicity dwarf galaxies with low dust content, we ignore this effect.
 
@@
 \label{sec:diffusive heating}
-We include two forms of diffusive heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citet{HM2012}, and 2) localized photoelectric (PE) heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars.
-Photoelectric heating can be a dominant heating mechanism in the ISM \citep{Parravano2003} of the Milky Way, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
-However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contended \citep{Hu2016,Hu2017}.
-Generally, models for PE heating and LW radiation in hydrodynamic simulations of galaxies adopted a constant value or a static, radial profile.
+We include two forms of diffusive heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars.
+Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
+However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}.
+Generally, models for photoelectric heating and LW radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile.
 Only recently has the localization and time variation of these processes been considered.
 
-Self-shielding of gas against the metagalactic UV background is important in high resolution simulations, particularly for low-mass, low metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy.
-We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background (see \citep{GrackleMethod} for more details of this implementation).
-We assume HeI ionization generally follows HI.
-This allows us to approximate HeI self-shielding using the same form (A.
+Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy.
+We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background (see \citep{GrackleMethod} for more details of this implementation).
+We assume \ion{He}{1} ionization generally follows \ion{H}{1}.
+This allows us to approximate \ion{He}{1} self-shielding using the same form (A.
 Rahmati, private communication).
-We ignore HeII photoionization from the UV background entirely.
+We ignore \ion{He}{2} photoionization from the UV background entirely.
 Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \citet{Hu2017}).
@@
 This additionally prevents an otherwise uniform collapse of the gas disk.
-The supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}.
+The supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
 We stop the artificial driving 25~Myr after the first star particle forms.
@@
 We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-Each figure gives density weighted projections of number density (first row), temperature slices (second row), HI column density projections (third row), and O column density projections (fourth row), at four different times in the simulation \textit{(list times here)}.
+Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and O column density projections (fourth row), at four different times in the simulation \textit{(list times here)}.
 In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points.
@@
 \caption{textbf{Draft figure - need to pretty up and finalize fields and times.} Edge-on views of our dwarf galaxy at four different times in its evolution, beginning with the time at first star formation and ending at XXX Myr.
-Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving HI column density (third row) and O column density (fourth row).
+Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and O column density (fourth row).
 Additionally, each individual main sequence star particle is shown in the number density projections as a single black dot.}
@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about \textbf{$6 \times 10^5$ M$_{\odot}$, or roughly 17\%} of the total mass in the galaxy's disk.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about \textbf{$6 \times 10^5$ M$_{\odot}$, or roughly 17\%} of the total mass in the galaxy's disk.
 The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases to about \textbf{25\%} as the total amount of mass in the disk decreases through feedback driven winds.
@@
 \caption{Left: The SFR and core collapse SNR in our dwarf galaxy in 10 Myr bins (left).
-Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy over time.
+Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy over time.
 Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and SNR.}
@@
 The top panel gives $G_{\rm o}$, or the flux of radiation between 6 - 13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position.
-The bottom panel gives the HI and HeI ionizing stellar radiation flux, showing average value and maximum values only.
+The bottom panel gives the \ion{H}{1} and \ion{He}{1} ionizing stellar radiation flux, showing average value and maximum values only.
 For these fields the minimum value reaches zero at some point over the examined period at all radii.}
@@
 
-The bottom panel gives the ionizing photon fluxes (HI and HeI) from ionizing photons from the stellar radiation \texttt{only}.
+The bottom panel gives the ionizing photon fluxes (\ion{H}{1} and \ion{He}{1}) from ionizing photons from the stellar radiation \texttt{only}.
 Since these fields are tracked directly with ray-tracing radiative transfer, the profiles encode information about local attenuation of these photons from dense, neutral gas.
@@
 \includegraphics[width=0.45\linewidth]{q_o_2D_phase}
-\caption{Single-snapshot 2D radial profile plots of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
+\caption{Single-snapshot 2D radial profile plots of the ISRF in two flux bands, $G_{\rm o}$ and \ion{H}{1} ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
 Here, we include all gas within 25 pc of the midplane of our dwarf galaxy.
 We note the large difference in color scale between the two plots.
-Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
+Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to \ion{H}{1} ionizing radiation, it does not show up in the \ion{H}{1} ionizing radiation diagram.
 This gas readily appears in the $G_{\rm o}$ since we assume it to be optically thin, though do apply a localized shielding approximation.}
@@
 
-The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, Tollerud2015, Sand2015}.
+The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted \ion{H}{1} surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, Tollerud2015, Sand2015}.
 However, the sample of isolated dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
@@
 \includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution}
-\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every 1 Myr for the total gas surface density computed from the simulations, and an observational analog derived using the HI content (see text for details).}
+\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every 1 Myr for the total gas surface density computed from the simulations, and an observational analog derived using the \ion{H}{1} content (see text for details).}
 \label{fig:KS}
@@
 However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
-Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low mass dwarf galaxy close enough to the Milky Way to conduct this experiment and with an observable HII region, necessary for determining gas phase abundances.
+Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low mass dwarf galaxy close enough to the Milky Way to conduct this experiment and with an observable \ion{H}{2} region, necessary for determining gas phase abundances.
 Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
@@
 The stellar radiation properties are a determined from the OSTAR2002 grid \citep{Lanz2003} (or as integrated from an adjusted black body curve for stars off of the OSTAR2002 grid) given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Figure~\ref{fig:stellar radiation properties} we plot the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and LW (middle right) luminosities, and finally the HI ionizing radiation photon energy (bottom left) and HeI ionizing photon energy (bottom right).
+In Figure~\ref{fig:stellar radiation properties} we plot the ionizing photon luminosities for \ion{H}{1} (top left) and \ion{He}{1} (top right) for each star, the FUV (middle left) and LW (middle right) luminosities, and finally the \ion{H}{1} ionizing radiation photon energy (bottom left) and \ion{He}{1} ionizing photon energy (bottom right).
 We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
 This requires two factors for each radiation type, one for low mass and one for high mass stars.
-We use the following multiplicative factors to adjust the black body spectrum for HI and HeI radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
+We use the following multiplicative factors to adjust the black body spectrum for \ion{H}{1} and \ion{He}{1} radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
 We do not find this adjustment to be necessary for the FUV and LW radiation bands.

### 2017-11-21 main.tex
through 2.5.6

@@
 
-We assume the FUV luminosity for each our stars is everywhere optically thin.
-The FUV flux in each cell is summed over contributions from each star.
-We parameterize the local photoelectric heating rate following \citet{BakesTielens1994}, \citet{Wolfire2003}, and \citet{Bergin2004}, where
+%mm We assume the FUV luminosity for each our stars is everywhere optically thin. The 
+     We assume the galaxy is mostly optically thin to stellar FUV.  Therefore, the stellar
+%
+FUV flux in each cell is summed over the contributions from each star
+%mm 
+   with a local approximation to the attenuation within dense cells applied. 
+We parameterize the local photoelectric heating rate \citep{BakesTielens1994,Wolfire2003,Bergin2004}
 \begin{equation}
 \label{eq:PE}
-\Gamma_{\rm pe} = 1.3 \times 10^{-24} \epsilon n_{\rm H} G_{\rm eff} D \left[{\rm erg~s~cm^{-3}}\right]
+\Gamma_{\rm pe} = (1.3 \times 10^{-24} \mbox{~erg~s~cm}^{-3}) \epsilon n_{\rm H} G_{\rm eff} D 
 \end{equation}
 where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\rm{exp}(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust to gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
-Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016} and \citet{Hu2017}.
-
-$D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014} (see Section~\ref{sec:chemistry}).
+Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
+
+$D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
 The extremely low dust to gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a $D$ that scales linearly with metallicity at very low metallicity.
-At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$ \ccunit.
-Given that the ambient density of the ISM is generally 1 - 10 cm$^{-3}$, we can safely assume the FUV field to be optically thin.
-However, we do include a localized attenuation prescription which may influence high density or metal enriched regions of the galaxy.
+At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit.
+Given that the ambient density of the ISM is generally 1--10~cm$^{-3}$, we can safely assume the FUV field to be optically thin.
+However, we do include a localized attenuation prescription that may influence high-density or metal-enriched regions of the galaxy.
 We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.
 
-Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density ($n_e$).
-This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; each of which are not followed directly in these simulations.
+Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
+This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; none of which are followed directly in these simulations.
 Instead, we use a log-linear fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.

### 2017-11-21 main.tex
section 3 finished

@@
 \label{sec:IC}
-The galaxy presented in this work is constructed to be similar to the observed properties of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, but is not intended to be a matched model to this galaxy.
-Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4}$ adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}.
-Our dwarf galaxy is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citep{McQuinn2015}.
+The galaxy presented in this work is constructed to be similar to the observed properties of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
+Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4} Z_{\odot}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}.
+Our dwarf galaxy is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
 
 The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equillibrium with a static, background dark matter potential.
-The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, or
+The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
 \begin{equation}
@@
 We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$.
-We adopt a Burkert \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5^{8} \rm{M_{\odot}}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc.
+We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5\times 10^{8} \mbox{ M_{\odot}}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc.
 This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc.
@@
 
-Following the initialization procedure of \citet{Hu2017}, we use artificial supernova driving to generate realistic densities and turbulent properties in the galaxy ISM.
-This additionally prevents an otherwise uniform collapse of the gas disk.
-The supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
+Following the initialization procedure of \citet{Hu2017}, we use artificial supernova driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
+This additionally prevents an otherwise uniform collapse of the gas disk
+%mm
+   at the beginning of the simulation.
+These supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
 We stop the artificial driving 25~Myr after the first star particle forms.
-These artificial supernova do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
+These artificial supernovae do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
+%mm
+    We do not include any other effects from the stellar population that would have caused these   
+    supernovae.
 

### 2017-11-21 main.tex
into 4.2

@@
 \includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
-\caption{textbf{Draft figure - need to pretty up and finalize fields and times.} Edge-on views of our dwarf galaxy at four different times in its evolution, beginning with the time at first star formation and ending at XXX Myr.
+\caption{\textbf{Draft figure - need to pretty up and finalize fields and times.} Edge-on views of our dwarf galaxy at four different times in its evolution, beginning with the time at first star formation and ending at XXX Myr.
 Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and O column density (fourth row).
@@
 
-The gas disk is is thin outside the stellar radius of our galaxy, but is resolved at all radii.
-In Figure~\ref{fig:scale_height} we plot the scale height of our gas disk as a function of radius averaged over the last 20 Myr of simulation time (black), at the initial conditions (blue), and just before first star formation (orange).
+The gas disk is thin outside the stellar radius of our galaxy, but is resolved at all radii.
+In Figure~\ref{fig:scale_height} we plot the scale height of our gas disk as a function of radius at the initial conditions (blue), just before first star formation (orange), and averaged over the last 20 Myr of simulation time (black).
 At the outer edges of the disk, beyond regions of ongoing star formation, the scale height is $\sim 15$ pc, comparable to the scale height in the inner 200 pc prior to first star formation.
@@
 These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy.
-These clumps have typical velocities on order of a few to tens of km s$^{-1}$, and appear to survive for 10 - 100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk.
+These clumps have typical velocities on order of a few to tens of kilometers per second, and appear to survive for 10--100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk.
 The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work.
@@
 
-\subsection{SFR and Mass Evolution}
+\subsection{Star Formation Rate and Mass Evolution}
 \label{sec:sfr}
 
-We present the star formation rate (SFR) and core collapse supernova rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.
+We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.
 By the end of the simulation, there have been no Type 1a supernovae.
-Within the first 40 Myr of evolution the SFR rises quickly to between $2-4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, and remains at this level with fluctuations of about a factor of 2 or less.\footnote{The granularity in our star formation algorithm creates a lower limit in the SFR that depends on the period over which the SFR is measured ($\Delta t$).
-Since we produce stars in $\sim 100$ M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
+Within the first 40 Myr of evolution the SFR rises quickly to between $2-4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, and remains at this level with fluctuations of about a factor of 2 or less.
+Averaging over the entire simulation time since the first star was formed, we obtain a $<\rm{SFR}> = 2.34 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
+The star formation rate of our model galaxy as compared to observed galaxies is discussed further in Section~\ref{sec:observation}.
+
+%mm \footnote{  [This is rather too long for a footnote, I think.]
+The granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period over which the SFR is measured $\Delta t$.
+Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
 For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$.
 Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense.
-Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.} Averaging over the entire simulation time since the first star was formed, we obtain a $<\rm{SFR}> = 2.34 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
-The star formation rate of our model galaxy as compared to observed galaxies is discussed further in Section~\ref{sec:observation}.
+Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.
 
@@
 \includegraphics[width=0.475\linewidth]{mass_evolution}
-\caption{Left: The SFR and core collapse SNR in our dwarf galaxy in 10 Myr bins (left).
+\caption{Left: The SFR and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left).
 Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy over time.
-Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and SNR.}
+Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.}
 \label{fig:sfr_mass_evolution}
@@
 While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume each, though the two warm phases dominate.
-The volume fractions are subject to significantly more fluctuations over time, due to the low SFR and SNR of our galaxy.
+The volume fractions are subject to significantly more fluctuations over time, due to the low SFR and supernova rate of our galaxy.
 Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.

### 2017-11-26 main.tex
into section 4.4

@@
 In this paper we introduce a new method of modeling for feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}.
-For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type 1a supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer.
+For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer.
 In addition, we couple to a self-consistent set of stellar yields
@@
 We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.
-By the end of the simulation, there have been no Type 1a supernovae.
-Within the first 40 Myr of evolution the SFR rises quickly to between $2-4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, and remains at this level with fluctuations of about a factor of 2 or less.
-Averaging over the entire simulation time since the first star was formed, we obtain a $<\rm{SFR}> = 2.34 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
+(By the end of the simulation, there have been no Type Ia supernovae.) Within the first 40 Myr of evolution the SFR rises quickly to between $2-4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, and remains at this level with fluctuations of about a factor of 2 or less.
+Averaging over the entire simulation time since the first star was formed, we obtain  $<\rm{SFR}> = 2.34 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
 The star formation rate of our model galaxy as compared to observed galaxies is discussed further in Section~\ref{sec:observation}.
@@
 %mm \footnote{  [This is rather too long for a footnote, I think.]
-The granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period over which the SFR is measured $\Delta t$.
+The granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
 Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
@@
 Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
-The molecular properties of our galaxy is discussed further in context with other works in Section~\ref{sec:observation}.
+The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
 
@@
 
-Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy \textbf{too strong of a claim?}.
-We define five different gas phases following those defined in \citep{Draine2011}: molecular, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
+Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy. 
+%mm \textbf{too strong of a claim?}. [No, it's quite true: you just need a cooling curve balanced against diffuse and SN heating.] 
+We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
 See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-Each of these exist in our simulations, and are regulated by the complex interplay between turbulence, self-gravity, and stellar feedback throughout the galaxy's evolution.
-Here we discuss the phase properties of the gas throughout the simulation box and within the ISM of our dwarf galaxy.
+Each of these exist in our simulations, and are regulated by the complex interplay between
+%mm
+   cooling, 
+turbulence, self-gravity, and 
+%mm 
+    diffuse and shock heating from 
+stellar feedback throughout the galaxy's evolution. Here we discuss the phase properties of the gas throughout the simulation box and within the ISM of our dwarf galaxy.
 
@@
 \includegraphics[width=0.95\linewidth]{phase_diagram.png}
-\caption{The full-box temperature vs. number density phase diagram of our dwarf galaxy simulation, averaged over the final 50 Myr of simulation time.}
+\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation, averaged over the final 50 Myr of simulation time, and showing the whole simulation domain.}
 \label{fig:phase}
@@
 \includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
-\caption{The evolution of the mass and volume fractions for each phase of our galaxy's ISM. This figures only consider gas present within the disk of the galaxy.}
+\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. This figure only includes gas present within the disk of the galaxy.}
 \label{fig:ISM_evolution}
@@
 
-The ISRF of our galaxy varies dramatically in both space and time, as has been deomonstrated previously in works modelling varying radiation fields \citep{Parravano2003,Hu2017}.
-This is especially not surprising in the low SFR regime, where there can be large fluctuations in proximity to a massive, radiating star over time.
+The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields 
+%mm 
+   both as expected from stellar positions in our own galaxy \citep{Parravano2003},
+   and in models including radiation \citep[e.g.][]{Hu2017}. 
+This is particularly not surprising in the low SFR regime, where there can be large fluctuations over time 
+%mm in proximity to a massive, radiating star. 
+    as individual massive stars form, move about, and evolve.
 In Figure~\ref{fig:ISRF} we present 1D volume averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time.

### 2017-11-26 main.tex
finished 4.4

@@
 
-\subsubsection{Diffusive Heating}
+%mm \subsubsection{Diffusive Heating}
+         \subsubsection{Diffuse  Heating}
 \label{sec:diffusive heating}
-We include two forms of diffusive heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars.
+We include two forms of 
+%mm diffusive 
+   diffuse
+heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars.
 Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
@@
 %mm 
-   both as expected from stellar positions in our own galaxy \citep{Parravano2003},
+   both as expected from stellar motions in our own galaxy \citep{Parravano2003},
    and in models including radiation \citep[e.g.][]{Hu2017}. 
-This is particularly not surprising in the low SFR regime, where there can be large fluctuations over time 
+This is particularly not surprising in our low SFR regime, where there can be large fluctuations over time 
 %mm in proximity to a massive, radiating star. 
     as individual massive stars form, move about, and evolve.
-In Figure~\ref{fig:ISRF} we present 1D volume averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time.
-The top panel shows the average $G_{\rm o}$, or the ISRF flux between 6 - 13.6 eV normalized to the value in the solar neighborhood of the Milky Way (see Section XX).
-The contribution from the metagalactic background is below the lower vertical axis limit on this plot.
-The shaded region gives the minimum and maximum value of $G_{\rm o}$ in the sampled time range.
-As shown, regions typically experience fluctuations in the ISRF of an order of magnitude.
+In Figure~\ref{fig:ISRF} we present 
+%mm 1D volume-
+    azimuthally averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time. The top panel shows 
+%mm the average value of 
+$G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sect.~\ref{sec:diffusive heating}).
+(The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.)
+%mm The shaded region gives the minimum and maximum value of $G_{\rm o}$ in the sampled time range. [redundant with caption] 
+%mm As shown, regions typically experience  
+    This shows that any given point experiences
+fluctuations in the ISRF of an order of magnitude.
 Interestingly, the central 200 pc does not contain the peak of the ISRF in the galaxy.
@@
 \includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
-\caption{1D radial profiles of the ISRF in our galaxy in three different bands, time-averaged over the final 50 Myr of simulation time.
-The top panel gives $G_{\rm o}$, or the flux of radiation between 6 - 13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position.
-The bottom panel gives the \ion{H}{1} and \ion{He}{1} ionizing stellar radiation flux, showing average value and maximum values only.
-For these fields the minimum value reaches zero at some point over the examined period at all radii.}
+\caption{
+%mm 1D radial
+    Azimuthally averaged radial 
+profiles of the ISRF in our galaxy in three different bands, time-averaged over the final 50 Myr of simulation time.
+The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
+The bottom panel gives the \ion{H}{1} and \ion{He}{1} ionizing stellar radiation flux, showing average and maximum values only.
+For these fields the minimum value reaches zero at some point during the examined period at all radii.}
 \label{fig:ISRF}
@@
 
-The bottom panel gives the ionizing photon fluxes (\ion{H}{1} and \ion{He}{1}) from ionizing photons from the stellar radiation \texttt{only}.
-Since these fields are tracked directly with ray-tracing radiative transfer, the profiles encode information about local attenuation of these photons from dense, neutral gas.
+The bottom panel gives the ionizing photon fluxes for \ion{H}{1} and \ion{He}{1} from %mm ionizing photons from the 
+stellar radiation 
+%mm \texttt{only}.
+   {\em only}. 
+Since these fields are tracked directly using ray-tracing radiative transfer, the profiles encode information about local attenuation of these photons from dense, neutral gas.
 This is the main driver of the differences between these fields and $G_{\rm o}$.
-In addition, we only show the average line and shade to the maximum value at any given position, since the minimum value reaches zero at all radii at some point over the 50 Myr examined.
-As shown, this causes the profile to vary much more dramatically at all radii.
-However, the same general trend is preserved of less radiation in the inner 200 pc than the region between 200 and 400 pc, and an order of magnitude or more fluctuation at all radii.
+%mm In addition, we only show the average line and shade to the maximum value at any given position, since the minimum value reaches zero at all radii at some point over the 50 Myr examined.
+As shown, this causes the profile to
+   The ionizing fields
+vary much more dramatically at all radii.
+However, the same general trend is preserved of less radiation in the inner 200 pc than in the region between 200 and 400 pc, and an order of magnitude or more fluctuation at all radii.
 The rapid drop off beyond 400 pc is due to the rapid attenuation of ionizing photons by the cold gas at large radii (see Figure~\ref{fig:panel_x}).
@@
 However, the local variations for individual regions can be much larger than is illustrated in these profiles.
-In Figure~\ref{fig:ISRF_2D} we present a 2D profile of $G_{\rm o}$ averaged over the final 50 Myr of the simulation time, which effectively captures the large spikes in local ISRF from recent star forming regions.
-The 1D profiles accurately capture the averaged heating / ionizing effects of the ISRF in our galaxy, which helps reduce star formation by increase the thermal pressure support and equillibrium temperature of the ISM, yet it is these spikes that act as important local feedback to shut off star formation in dense, collapsing regions that satisfy our star formation criteria.
-This point will be examined in more detail in future work with comparison simulations using different feedback processes (Emerick et.
-al.
-in prep).
+In Figure~\ref{fig:ISRF_2D} we present %mm a 2D profile of $G_{\rm o}$ averaged
+    the full distribution of $G_{\rm o}$ over the final 50 Myr of the simulation time, which effectively captures the large spikes in local ISRF from recent star forming regions.
+The azimuthally averaged profiles accurately capture the averaged heating and ionizing effects of the ISRF in our galaxy, which helps reduce star formation by increasing the thermal pressure support and equilibrium temperature of the ISM, yet it is the spikes that act as important local feedback to shut off star formation in dense, collapsing regions that satisfy our star formation criteria.
+This point will be examined in more detail in future work with comparison simulations using different feedback processes.
+%mm (Emerick et. al. in prep).  [I'd only insert the reference when there is an actual astro-ph number to support it.]
 

### 2017-11-27 main.tex
finished 4.5

@@
 
-Recent cosmological simulations of dwarf galaxies with detailed feedback over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors on order of 10 - 1000 \citep{Muratov2015}.
-However, comparable work of idealized dwarf galaxies with detailed feedback and physics models find more modest mass loading factors \citep{Hu2016,Hu2017}.
+Recent cosmological simulations of dwarf galaxies with 
+%mm detailed 
+feedback over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors on order of 100--1000 \citep{Muratov2015}.
+However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
 In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
-We follow \citet{Muratov2015} defining the mass outflow rate ($\dot{M}_{\rm outflow}$) at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius.
-In other words, $\dot{M}_{\rm outflow} = \sum M_{\rm gas} \times v_{\rm r} / dL$.
+We follow \citet{Muratov2015} defining the mass outflow rate ($\dot{M}_{\rm outflow}$) at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
+\begin{equation} \label{eq:dotM}
+\dot{M}_{\rm outflow} = \sum M_{\rm gas} \times v_{\rm r} / dL.
+\end{equation} 
 We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.
@@
 We use the 10 Myr averaged SFR to compute the mass loading rates.
-The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50 - 100 throughout the simulation time.
+The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time.
 This quickly declines towards larger radii, however, with effectively zero outflow past the virial radius.
-\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20-40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift.
-Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below the typical values.
-
-Interestingly, the v$_{\rm c}$ $\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
+\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift.
+Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below their typical values.
+
+Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
 Using a fit provided in \citet{Muratov2015} to extrapolate and compare at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
@@
 \includegraphics[width=0.45\linewidth]{total_mass_loading}
-\caption{Spherical mass outflow rates and mass loading rates over time at 4 different radii from the galaxy.}
+\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
 \label{fig:mass_outflow}
@@
 Detailed outflow properties, beyond outflow rates and mass loading factors, are important discriminators between the model dependent feedback physics included in galaxy simulations. 
-\textbf{(do I need an example of this in recent work?)}.
+%mm \textbf{(do I need an example of this in recent work?)}. [maybe soften to "can help discriminate?"]
 In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
-Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{1}$ or below.
+Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{-1}$ or below.
 This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities.
-The distribution has a very long tail out to and beyond 500 km s$^{-1}$.
+The distribution has a very long tail out to and beyond 500~km~s$^{-1}$.
 The dominant launching mechanism in this simulation are supernovae (Emerick et.
 al.
-in prep), generating a rapidly moving and volume filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
+in prep), generating a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
 However, as shown, the HIM comprises very little of the outflow by mass.
@@
 The outflowing material is multiphase, broken into WNM, WIM, and HIM.
-See XXX for definitions of these regimes.
+See Section~\ref{sec:phase} for definitions of these regimes.
 We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$K.
@@
 It is apparent from this figure that the outflows are preferentially metal enriched, as the halo increases in metallicity by a factor of $\sim 2$ in the simulation time.
-Although most of gas mass in the halo (outside the disk) remains is within 0.2 $R_{\rm vir}$ (see Section~\ref{sec:obs_metals}), the mass that does make it out far and out side the halo is metal enriched by a factor of $\sim$5-6 compared to the ISM.
-This is in contrast with the results from \citet{Muratov2017}, which generally shows $Z_{\rm outflow} \simeq Z_{\rm ISM}$ at $0.25~R_{\rm vir}$ and $Z_{\rm outflow} < Z_{\rm ISM}$ at $1.0~R_{\rm vir}$, though both with some scatter that reaches above $Z_{\rm outflow} > Z_{\rm ISM}$, especially at high redshift.
-However, we note that our simulations certainly do not contain a cosmologically realistic CGM and do not include ongoing cosmological accretion of pristine gas; this will certainly lower the typical halo and outflow metallicities, possibly more in agreement with the findings of \citet{Muratov2017}.
+Although most of the gas mass in the halo (outside the disk) remains within 0.2 $R_{\rm vir}$ (see Section~\ref{sec:obs_metals}), the mass that does make it
+%mm out far and out side the halo
+   to the outer reaches of the halo or beyond 
+is metal enriched by a factor of $\sim$5--6 compared to the ISM.
+This is in contrast with the results from \citet{Muratov2017}, which generally show $Z_{\rm outflow} \simeq Z_{\rm ISM}$ at $0.25~R_{\rm vir}$ and $Z_{\rm outflow} < Z_{\rm ISM}$ at $1.0~R_{\rm vir}$, though both with some scatter that reaches
+%mm above 
+$Z_{\rm outflow} > Z_{\rm ISM}$, especially at high redshift.
+However, we note that our simulations certainly do not contain a cosmologically realistic circumgalactic medium, nor do they include ongoing cosmological accretion of pristine gas; this will certainly lower the typical halo and outflow metallicities, possibly
+%mm more in 
+    resulting in better
+agreement with the findings of \citet{Muratov2017}.
 

### 2017-11-29 main.tex
up to 5.2.2

@@
 Observations of Local Group dwarf galaxies have shown that they retain very little of the total amount of metals they are expected to have produced, given their star formation histories (see Section~\ref{sec:observation}).
-In Figure~\ref{fig:species_fractions} we show the fraction of metals retained within the disk / expelled into the halo of our galaxy over time, along with a break down of the locations of each metal species by the end of the simulation time.
+In Figure~\ref{fig:species_fractions} we show the fraction of metals retained within the disk or expelled into the halo of our galaxy over time, along with a breakdown of the locations of each metal species by the end of the simulation.
 As shown in the top panel, a majority of each metal tracer species is found outside the disk of the galaxy, in the galaxy halo.
@@
 Interestingly, the exact fraction is not uniform across metal species.
-Most notably, Nitrogen, is preferentially retained by the galaxy over the other species.
-
-Roughly \textbf{35\%} of the N produced remains in the disk, as compared to \textbf{15\%} of O and \textbf{15\%} of Fe, for example.
-This difference is entirely feedback driven, but a coincidence of our particular galaxy conditions.
-At our galaxy's metallicity, the IMF weighted production of N rests entirely with the stellar winds of stars between 8 and 10 M$_{\odot}$; there is little to no N production in supernovae at this metallicity.
-The rest of the species either have very little stellar wind production, produced solely in supernovae, or have similar production levels between both supernovae and stellar winds (like O, for example).
-The typically lower injection energies of N into the galaxy than the SN injected elements means N is preferentially retained within the ISM, and not as effectively ejected through outflows.
+
+Most notably, N is preferentially retained by the galaxy over the other species. 
+Roughly \textbf{35\%} of N produced remains in the disk, as compared to \textbf{15\%} of O 
+%mm and \textbf{15\%} of 
+    or
+Fe, for example. This difference is entirely feedback driven, but 
+%mm a coincidence of our particular galaxy conditions. At our galaxy's metallicity, the IMF weighted production of N occurs entirely
+    determined by the chosen metallicity of our galaxy. At this metallicity, N is 
+    produced only 
+in the stellar winds of stars between 8 and 10 M$_{\odot}$, with little to no production in supernovae.
+The rest of the species either have very little stellar wind production, are produced solely in supernovae, or have similar production levels between both supernovae and stellar winds (like O, for example).
+The typically lower injection energies of N into the galaxy compared to the SN
+%mm injected 
+   produced
+elements means N is preferentially retained within the ISM, and not as effectively ejected through outflows.
 In truth, the stars that produce N do eventually explode as supernovae, sweeping up some fraction of the wind produced N into outflows.
-However, clearly some of this N is able to mix more effectively within the ISM than the other metal species.
-How abundance variations like this evolve over longer timescales and with varying feedback physics is the subject of ongoing work (Emerick et.
-al.
-in prep.).
+However, clearly some of this N mixes more effectively within the ISM than the other metal species.
+How abundance variations like this evolve over longer timescales and with varying feedback physics is the subject of ongoing work.
+%mm (Emerick et. al. in prep.).
 
@@
 \includegraphics[width=0.9\linewidth]{species_bar_disk.png}
-\caption{The fraction of each species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone each in phase of the ISM (bottom).}
+\caption{The fraction of each species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).}
 \label{fig:species_fractions}
@@
 The WIM contains only $\sim$ 10\% of each species, with the HIM containing very little.
-This may be counterintuitive to the fact that most metals are initially injected into the galaxy in either the WIM or HIM phases.
+This may be counterintuitive given
+that most metals are initially injected into the galaxy in either the WIM or HIM phases.
 However, the disk metals represent only a small fraction of the total metals produced.
 Much of the metals are effectively removed from the disk into the halo (see Section~\ref{sec:outflows}).
-It is apparently that the remaining metals quickly mix or cool into denser gas phases.
+It is apparent that the remaining metals quickly mix or cool into denser gas phases.
 
@@
 However, the sample of isolated dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) law (left) for low mass galaxies, and the extended Schmidt law (ESL) (right) which has been shown recently to be extend to low mass, low metallicity dwarf galaxies \citep{Roychowdhury2017}.
+In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) law (left) for low mass galaxies, and the extended Schmidt law (ESL) (right) which has been shown recently to extend to low mass, low metallicity dwarf galaxies \citep{Roychowdhury2017}.
 We plot our galaxy every 1 Myr in these diagrams, showing the significant temporal variation in both spaces.
 Although these quantities are conceptually simple, due to how these values are measured observationally it is challenging to make a direct comparison to simulations, particularly in defining the geometric region to measure the surface densities.
-We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs following what is described in \citet{Roychowdhury2014}.
+We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs following the procedure described in \citet{Roychowdhury2014}.
 We define $\Sigma_{\rm sfr} = \dot{M}_{*, \rm{10 Myr}} / A_{*, \rm{10 Myr}}$, where $\dot{M}_{*, \rm{10 Myr}}$ is the SFR measured over the preceding 10 Myr, and $A_{*, \rm{10 Myr}}$ is the disk defined out to the farthest star formed within the previous 10 Myr.
@@
 
-In both panels, we also include recent observational constraints from these relationships.
-We include the KS fits from \citet{Shi2011} with 1$\sigma$ errors (black), the fits from \citet{Roychowdhury2014} (blue), and the individual points from the recent SHIELD sample \citep{Teich2016}; we include only the fit and 1$\sigma$ errors from \citep{Shi2011} for the ESL (black), which have been shown to match well for dwarf galaxies at these surface densities \citep{Roychowdhury2017}.
+In both panels, we also include recent observational constraints from these relationships. We include the KS fits from \citet{Shi2011} with 1$\sigma$ errors (black), the fits 
+%mm
+   and errors 
+from \citet{Roychowdhury2014} (blue), and the individual points 
+%mm
+   (black squares) 
+from the recent SHIELD sample \citep{Teich2016}; we include only the fit and 1$\sigma$ errors from \citep{Shi2011} for the ESL (black), which have been shown to match well for dwarf galaxies at these surface densities \citep{Roychowdhury2017}.
 In both relationships our simulations fit well around the median observed fit, spanning the 1 $\sigma$ variations about the mean.
+
 This is a remarkable result.
@@
 This result is consistent with recent galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics (\textit{relevant citations})
+%mm 
+   but also with the demonstration by \citet{Li2005} that the KS law can be reproduced 
+   by gravitation acting on an isothermal disk, which was argued to demonstrate that 
+   this represents the basic physics at work.
 

### 2017-11-29 main.tex
up to 5.2.2

@@
 Instead, we use a log-linear fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
-%This is a compromise between adoption a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equillibrium chemistry \citet[e.x.][]{Hu2016}.
+%This is a compromise between adoption a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
 
@@
 
-The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equillibrium with a static, background dark matter potential.
+The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential.
 The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
@@
 
-In both panels, we also include recent observational constraints from these relationships. We include the KS fits from \citet{Shi2011} with 1$\sigma$ errors (black), the fits 
+In both panels, we also include recent observational constraints from these relationships. For the KS relationship we include the fits from \citet{Shi2011} with 1$\sigma$ errors (black), the fits 
 %mm
@@
    (black squares) 
-from the recent SHIELD sample \citep{Teich2016}; we include only the fit and 1$\sigma$ errors from \citep{Shi2011} for the ESL (black), which have been shown to match well for dwarf galaxies at these surface densities \citep{Roychowdhury2017}.
+from the recent SHIELD sample \citep{Teich2016}, while for the ESL relationship we include only the fit and 1$\sigma$ errors (black) from \citet{Shi2011}, which have been shown to match well for dwarf galaxies at these surface densities \citep{Roychowdhury2017}.
 In both relationships our simulations fit well around the median observed fit, spanning the 1 $\sigma$ variations about the mean.
@@
 
-The molecular gas content of low mass dwarf galaxies like this is generally considered to be small, (references).
+The molecular gas content of low mass dwarf galaxies like this is generally considered 
+to be small (references).
 Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas fractions anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
-Given As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ typically of 0.17 - 0.20, in between this range, but significantly above the few percent often found in models.
-This means ignoring the $H_2$ component of our galaxies leads to an average shift of 0.24 dex to the right in the KS relationship, and 0.24 dex right and down in the ESL.
+As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.17--0.20, within this range, but significantly exceeding the few percent often found in models.
+This means ignoring the H$_2$ component of our galaxies leads to an average shift of 0.24 dex to the right in the KS relationship, and 0.24 dex right and down in the ESL.
 This does not lead to a significant disagreement with the observed relationships, but would constitute a quantitative change to the observed fits if our $f_{\rm H_2}$ is robust for low mass, low metallicity dwarf galaxies.
-However, our non-equillibrium chemical model for $H_2$ formation and destruction is relatively simple, and does not account for C and O chemistry, a detailed dust model, or cosmic rays; all of which may significantly affect $f_{\rm H_2}$.
-Simulations in \citet{Hu2016} and \citet{Hu2017}, which contain a more detailed non-equillibrium chemistry model than included here, give very low $f_{\rm H_2}$, below $10^{-4}$ for their full feedback simulations; even their simulations without any radiation feedback only reach $f_{\rm H_2} \sim 2 \times 10^{-3}$.
+However,
+%mm
+    we do not fully resolve the turbulent density perturbations in which 
+    H$_2$ forms most efficiently \citep{Glover2007}, and
+our non-equilibrium chemical model for H$_2$ formation and destruction is relatively simple: it does not account for C and O chemistry, a detailed dust model, or cosmic rays, all of which may significantly affect $f_{\rm H_2}$.
+
+Simulations by \citet{Hu2016} and \citet{Hu2017}, which contain a more detailed non-equilibrium chemistry model than included here, give very low $f_{\rm H_2}$, below $10^{-4}$ for their full feedback simulations; even their simulations without any radiation feedback only reach $f_{\rm H_2} \sim 2 \times 10^{-3}$.
 However, their simulated dwarf galaxies are more massive ($M_{\rm vir} = 10^{10} M_{\odot}$) and higher metallicity ($Z = 0.1 Z_{\odot}$) than those examined here.
@@
 First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal line cooling and heating rates are used.
-The actual primordial heating and cooling rates are calculated self-consistently using the non-equillibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}.
+The actual primordial heating and cooling rates are calculated self-consistently using the non-equilibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}.
 However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations.

### 2017-11-29 main.tex
up to 5.3

@@
 
-Unfortunately, these high resolution simulations are not (yet) run for the $\sim$ Gyr timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at z = 0.
-However, we can compare to a key observable, the ejection / retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from stellar evolution models based on the galaxy's star formation history.
-This can be done readily with Milky Way dSph's, whose stars seem to retain very little of the expected metals produced, on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
+%mm Unfortunately, these high resolution simulations are not (yet) run
+    The simulations presented here have not yet been run
+for the 
+%mm $\sim$ Gyr 
+    gigayear
+timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$. However, we can compare to a key observable, the 
+%mm ejection / 
+retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from stellar evolution models based on the galaxy's star formation history.
+This can be done readily with Milky Way dSph's, whose stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
 However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
-Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low mass dwarf galaxy close enough to the Milky Way to conduct this experiment and with an observable \ion{H}{2} region, necessary for determining gas phase abundances.
+
+Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, and close enough to the Milky Way to conduct this experiment.
 Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, roughly \textbf{95\%} of the tracked metals produced throughout the simulation time no longer reside within the galaxy's disk.
+As discussed in Section~\ref{sec:chemical evolution}, roughly \textbf{95\%} of the tracked metals produced during the simulation no longer reside within the galaxy's disk.
 At the end of our simulation, we agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
-Although more than half of these metals are expected to be re-accreted \citep{Angles-Alcazar2017}, it is still possible that, at any moment, most of the metals that have been produced lie outside the galaxy disk.
-We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.
-
-It is interesting to consider where these metals lie outside of the galaxy's disk, in the CGM or ejected into the IGM, and their eventual fate.
-While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of a $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero $\sim$ 60\% of ejected gas is recycled over time, while 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
-In our case, no metals have been ejected outside the virial radius; this is possibly not surprising however given that metals ejected outside the halo would need to travel with an average velocity of 150 km s$^{-1}$ for the entirety of our simulation time.
-\textbf{32\%} of all metals lie within 1 kpc of the center of our galaxy, \textbf{75\%} within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and only \textbf{10\%} outside $R_{\rm vir}$.
+Although more than half of these metals are expected to
+%mm
+   eventually
+be re-accreted \citep{Angles-Alcazar2017}, it is still possible that, at %mm any moment, 
+   the early times we have simulated,
+most of the metals that have been produced 
+%mm lie 
+    remain
+outside the galaxy disk. We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.
+
+It is interesting to consider 
+%mm where these metals lie outside of the galaxy's disk, 
+    whether ejected metals in our model reside 
+in the CGM or have been ejected into the IGM, and their eventual fate.
+While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of a $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero $\sim$ 60\% of ejected gas is recycled, while 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
+In our case, no metals have been ejected beyond the virial radius; this is not surprising however, given that metals ejected beyond the halo would need to travel with an average velocity of 150 km s$^{-1}$ for the entirety of our simulation time.
+We find \textbf{32\%} of all metals lie within 1 kpc of the center of our galaxy, \textbf{75\%} within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and only \textbf{10\%} outside $R_{\rm vir}$.
 Over time, the re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
-Re-cycling of metal enriched gas, could be a significant source of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) returns.
+Recycling of metal enriched gas could be a significant
+%mm source 
+    driver
+of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) returns.
 Unfortunately, we cannot yet speak to how this gas evolves over time, but will investigate this in future work with our feedback model.

### 2017-11-29 main.tex
completed comments on main text

@@
 
-We note the ``knee'' like feature at very low [Fe/H] is not the characteristic knee seen in $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ space, corresponding to the period when iron enrichment from SNIa begins to make a significant contribution to the galactic chemical evolution.
+We note the ``knee'' like feature at very low [Fe/H] is not the characteristic knee seen in $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ space, corresponding to the period when iron enrichment from SN Type Ia begins to make a significant contribution to the galactic chemical evolution.
 This generally occurs after roughly 1 Gyr of stellar evolution, far longer than the \textbf{170} Myr simulated here.
@@
 \subsection{Missing Physics}
-Although we include detailed physics in our simulations, there remains additional physics that may be relevant.These are discussed below.
+Although we include detailed physics in our simulations, there remains additional physical processes that may be relevant.These are discussed below.
 
@@
 \label{sec:stellar winds discussion}
-As discussed previously, our stellar wind model significantly reduces the injected wind velocity from $\sim$1000 km s$^{-1}$ to 1 km s$^{-1}$.
+Our stellar wind model significantly reduces the injected wind velocity from $\sim$1000 km s$^{-1}$ to 1 km s$^{-1}$.
 Although our model is capable of generating realistic stellar winds with temperature profiles and radial evolution comparable to those expected from analytic calculations \citep{Weaver1977}, the hot, fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
 When considered in isolation, stellar winds are an important source of pre-SN feedback and do dramatically influence the dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
-However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or GMCs \citep{Dale2014}.
+However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or
+%mm GMCs
+   individual giant molecular clouds
+\citep{Dale2014}.
 They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
-Although they likely have minimal dynamical importance, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.
+Although they likely have minimal dynamical importance
+%mm 
+   at resolutions where peak densities are not anyway high enough to trap ionization 
+   fronts, 
+a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.
 
@@
 \subsubsection{Cosmic Rays and Magnetic Fields}
-Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017} and simulations of both isolated \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017} and cosmological galaxies \citep{SalemBryanHummels}.
-These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows with different phases and velocities than those driven through stellar feedback alone \citep{SalemBryanCorlies}.
+Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}.
+These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through
+%mm stellar [CRs are also stellar feedback...]
+     thermal 
+feedback alone \citep{SalemBryanCorlies}.
 Modeling cosmic rays is challenging, however, as they encompass a wide range of energies (give range), with significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.

### 2017-12-05 main.tex
Final revisions to appendix

@@
 This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
-To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic UV background.
+To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background.
 We
@@
 We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure.
-In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner (LW) dissociation of molecular hydrogen.
+In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
 We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both.
@@
 However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}.
-Generally, models for photoelectric heating and LW radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile.
+Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile.
 Only recently has the localization and time variation of these processes been considered.
@@
 \label{sec:LW}
-In addition to the LW radiation from the UV background, we account for localized LW flux from each of our stars to compute the total, local H$_2$ dissociation rates.
-Given the local LW flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
-We account for approximate H$_2$ self-shielding against these sources of LW flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.
+In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rates.
+Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
+We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.
 
@@
 We present a new method for simulating the evolution of low mass galaxies with detailed feedback and chemical enrichment as traced through individual star particles.
-This model follows multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia supernovae, ionizing radiation followed through radiative transfer, photoelectric heating, and LW radiation.
-This is in addition to the detailed cooling, heating, and chemistry followed through Grackle, including a self-consistent model for gas self-shielding from the metagalactic UVB.
+This model follows multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia supernovae, ionizing radiation followed through radiative transfer, photoelectric heating, and Lyman-Werner radiation.
+This is in addition to the detailed cooling, heating, and chemistry followed through Grackle, including a self-consistent model for gas self-shielding from the metagalactic UV background.
 
@@
 We detail the radiation properties of our model stars as a function of stellar mass and metallicity, both of which are assigned directly from an IMF and from the local gas properties respectively.
-The stellar radiation properties are a determined from the OSTAR2002 grid \citep{Lanz2003} (or as integrated from an adjusted black body curve for stars off of the OSTAR2002 grid) given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Figure~\ref{fig:stellar radiation properties} we plot the ionizing photon luminosities for \ion{H}{1} (top left) and \ion{He}{1} (top right) for each star, the FUV (middle left) and LW (middle right) luminosities, and finally the \ion{H}{1} ionizing radiation photon energy (bottom left) and \ion{He}{1} ionizing photon energy (bottom right).
+The stellar radiation properties are determined from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve
+%mm off of the OSTAR2002 grid) 
+    for other stars,
+given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
+In Figure~\ref{fig:stellar radiation properties} we plot these properties.
 We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
@@
 We use the following multiplicative factors to adjust the black body spectrum for \ion{H}{1} and \ion{He}{1} radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
-We do not find this adjustment to be necessary for the FUV and LW radiation bands.
+We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
 
 The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid.
-A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency dependent absorption cross section.
-We tested this approach using the frequency dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \texttt{http://www.pa.uky.edu/~verner/photo.html}} The black body approximation is accurate to within 5\%, yet substantially easier to compute on the fly as integrals over the black body spectrum can be expressed as infinite series that rapidly converge to high precision.
-Unlike the ionizing radiation, we assume constant FUV and LW band energies for each star, at 9.8 eV and 12.8 eV respectively.
+A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section.
+We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \texttt{http://www.pa.uky.edu/~verner/photo.html}} The black body approximation is accurate to within 5\%, yet substantially easier to compute on the fly as integrals over the black body spectrum can be expressed as infinite series that rapidly converge to high precision.
+Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.
 
@@
 \includegraphics[width=0.4\linewidth]{E1}
-\caption{Radiation properties for our model stars. Note, we only track radiation from stars above
-8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
+\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for \ion{H}{1} (top left) and \ion{He}{1} (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for \ion{H}{1} (bottom left) and \ion{He}{1} (bottom right).
+Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
 \label{fig:stellar radiation properties}
@@
 
-Modeling supernova feedback with the injection of thermal energy alone can lead to rapid over cooling of the injected energy, and a significant underestimate of the effects of supernova feedback.
+Modeling supernova feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of supernova feedback.
 Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time.
-However, physically consistent solutions have been employed \citep[e.g][]{Simpson2016} which inject a mixture of kinetic and thermal energy, whose ratio of kinetic to thermal energy injection depends on resolution and/or local gas density.
-This over cooling problem improves with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each supernova.
-We take advantage of our high ($\sim$ pc) scale resolution and employ a simple thermal energy injection model for our supernova feedback.
-Here we demonstrate how well this resolves our supernovae in the comparison simulation presented in this work.
-
-The left panel of Figure ~\ref{fig:supernova histogram} gives the distributions of the max (orange) and average (black) ISM number densities in the supernova injection regions for each supernovae in the simulations presented in this work.
+However, physically consistent solutions have been developed \citep[e.g][]{Simpson2016} that inject a mixture of kinetic and thermal energy with a ratio that depends on resolution and local gas density.
+%mm This overcooling problem improves 
+   Overcooling becomes less important 
+with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each supernova.
+We take advantage of our high (parsec scale) resolution and employ a simple thermal energy injection model for our supernova feedback.
+We demonstrate how well this resolves our supernovae in the comparison simulation presented in this work.
+
+The left panel of Figure ~\ref{fig:supernova histogram} gives the distributions of the peak and average ISM number densities in the supernova injection regions for each supernovae in the simulations presented in this work.
 As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
 For most supernovae, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-supernova feedback included in our simulations.
-The right panel of Figure ~\ref{fig:supernova histogram} gives the fractional distribution of the calculated radius of pressure driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}, given as
+The right panel of Figure ~\ref{fig:supernova histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
 \[
@@
 \includegraphics[width=0.4\linewidth]{sn_radius_hist}
-\caption{Distribution of peak and average gas densities (left) in the injection region of each of the supernovae from the simulation.
-On the right, we give the distribution of the radius of the pressure driven snowplow phase for each supernova assuming a uniform medium at either the peak or average density in the injection region.
-The vertical lines give one and 4.5 cell widths.
-As shown, a fraction of these SN are certainly under resolved, with R$_{\rm PDS}$ less than a single cell size, but a majority are resolved.}
+\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the supernovae from the simulation.
+{\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each supernova assuming a uniform medium at either the peak or average density in the injection region.
+The vertical lines show one and 4.5 cell widths.
+This shows that a fraction of these supernovae are certainly under resolved, with R$_{\rm PDS}$ less than a single cell size, but the majority are well resolved.}
 \label{fig:supernova histogram}
@@
 
-\section{Cooling Rates}
+\section{Cooling and Heating Rates}
 \label{appendix:cooling}
-Figure ~\ref{fig:cooling} shows the combined primordial and metal line cooling (dashed) and heating (dotted) rates at three characteristic densities for Z = 0.01 Z$_{\odot}$, closer to the metallicities of our fiducial set of dwarf galaxy simulations (Emerick et.
-al.
-in prep).
-The solid lines give the absolute value of the net cooling rate, which more clearly indicates the regime at low temperatures where heating dominates.
-The curve as shown includes the z = 0 \citet{HM2012} metagalactic UVB.
+
+%mm moved this paragraph to the start of the section and rewrote accordingly.
+To derive the diffuse cooling and heating rates used in the simulations, we make two approximations.
+First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal-line cooling and heating rates are used.
+The primordial heating and cooling rates are calculated self-consistently using the non-equilibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}.
+However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations.
+Second, this figure ignores the contributions to the heating rate from the variable interstellar radiation field, namely the stellar contribution to photoelectric heating, heating from Lyman-Werner dissociation, and ionization heating.
+We describe how we obtain the metal line cooling rates below and quantify the change in using these updated tables.
+%Therefore, the heating rates shown are approximate lower limits to the true heating experienced by any given cell in the simulation.
+
+Figure ~\ref{fig:cooling} shows the combined primordial and metal line cooling and heating rates at three characteristic densities for $Z = 0.01 $Z$_{\odot}$, closer to the metallicities of our fiducial set of dwarf galaxy simulations (Emerick et al.\ in prep).
+The
+%mm solid lines give the absolute value of the net cooling rate, which more clearly 
+    Figure 
+indicates the regime at low temperatures where heating dominates over cooling. The curve as shown includes 
+%mm [it neglects local FUV]
+   only
+the $z = 0$ \citet{HM2012} metagalactic UV background.
 
@@
 \includegraphics[width=0.95\linewidth]{cooling_curve}
-\caption{The total heating and cooling rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic background as modeled in \textsc{Cloudy}.
-The absolute value of the net cooling rate is shown with solid lines.}
+\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}.
+The absolute value of the net cooling
+%mm
+   or heating
+rate is shown with solid lines.}
 \label{fig:cooling}
@@
 
-We note that this cooling curve shows only an approximation of the local cooling and heating rates used in the simulations for two reasons.
-First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal line cooling and heating rates are used.
-The actual primordial heating and cooling rates are calculated self-consistently using the non-equilibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}.
-However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations.
-Second, this figure ignores the contributions to the heating rate from the variable interstellar radiation field, namely the stellar contribution to photoelectric heating, heating from LW dissociation, and ionization heating.
-We describe how we obtain the metal line cooling rates below and quantify the change in using these updated tables.
-%Therefore, the heating rates shown are approximate lower limits to the true heating experienced by any given cell in the simulation.
-
-The cooling curves used in this work corrects a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with self-shielding approximations.
-Previous work in \citet{Hu2017} details this inconsistency.
-In short, adopting tabulated metal cooling rates computed under the assumption of an optically thin UV background overestimates the electron fraction in regimes where self-shielding is important, about $-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$, leading to an overestimation of the metal cooling rates.
-We demonstrate this effect in Figure~\ref{fig:cooling comparison}, which gives |cooling - heating| for our full model at $Z = 0.1~Z_{\odot}$ (black) as compared to a model using the optically thin metal line cooling rates (orange) at a range of densities.
+The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with self-shielding approximations.
+\citet{Hu2017} detail this inconsistency: adopting tabulated metal cooling rates computed under the assumption of an optically thin UV background overestimates the electron fraction in regimes where self-shielding is important, about $-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$, leading to an overestimation of the metal cooling rates.
+We demonstrate this effect in Figure~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate
+%mm |cooling - heating| 
+for our full model at $Z = 0.1$Z$_{\odot}$ as compared to a model using the optically thin metal line cooling rates at a range of densities.
 The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
@@
 In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud.
-We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UVB.
+We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UV background.
 These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}.
-In computing these tables we had to include the CR ionization that dominates in optically thick clouds.
+In computing these tables we had to include the cosmic ray ionization that dominates in optically thick clouds.
 Without this effect, \texttt{Cloudy} becomes unstable in entirely neutral regions.
-We adopted a CR ionization rate of 10\% the MW value, though we note varying this from 1\% to 100\% the MW value did not have an effect on the extracted metal line cooling rates.
+We adopted a cosmic ray ionization rate of 10\% the Milky Way value, though we note that varying this from 1\% to 100\% the Milky Way value did not have an effect on the extracted metal line cooling rates.
 
@@
 \includegraphics[width=0.95\linewidth]{cooling_model_comparison}
-\caption{The absolute value of the net cooling rate (|cooling - heating|) in two models that account for self-shielding of primordial gas against a metagalactic UV background.
+\caption{The absolute value of the net cooling or heating rate 
+%mm (|cooling - heating|)
+ in two models that account for self-shielding of primordial gas against a metagalactic UV background.
 Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the un-corrected (i.e.

### 2017-12-14 main.tex
Project created

--- 2017-11-29 main.tex
@@
 \usepackage[figure,figure*]{hypcap}
-\usepackage{multirow}
-\usepackage{mathtools}
+
 \renewcommand*{\sectionautorefname}{Section} %for \autoref
@@
 
-\shorttitle{Feedback with Individual Stars}
-\shortauthors{Emerick, Bryan, Mac Low}
-\newcommand{\msun}{M$_{\odot}$}
-\newcommand{\ccunit}{cm$^{-3}$}
+\shorttitle{Dwarf Galaxy Feedback}
+\shortauthors{Emerick, Bryan, Mac-Low}
 
@@
 
-\title{REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case}
-%Unstable Star Formation for the Lowest Mass Dwarf Galaxies
+\title{(TBD): Feedback and Chemical Evolution in Low Mass Dwarf Galaxies III: Role of Feedback in Regulating Metal Enrichment of Stars and the ISM}
+
+%\title{Simulating Dwarf Galaxy Evolution with Individual Star Feedback II: Importance of Dark Matter Halo Depth to Prevent Self-Quenching in the Lowest Mass Dwarf Galaxies}
+
 \author{Andrew Emerick}
@@
 \affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-
-%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}
 
 \begin{abstract}
-\textbf{Saving this for after the first iteration}
+Abstract.
 \end{abstract}
 
-\keywords{Galaxy -- Hydrodynamics -- Simulation -- Feedback}
+\keywords{}
 
@@
 
-Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade.
-Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc.
-\citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses.
-On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM.
-This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}.
-See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.
-
-These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution.
-In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense.
-In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships.
-For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.
-
-Due to its complexity, the detailed interstellar medium (ISM) and chemical abundance properties, beyond total metallicity, are sensitive tests of the underlying physical processes that govern galaxy evolution.
-Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
-There is a considerable body of work examining the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
-These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017} and more detailed quantities such as metallicity distribution functions (MDFs) and abundance evolution of individual species \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
-However, there is a general lack of numerical diversity in these works, as a majority are implemented in some flavor of smoothed particle hydrodynamics (SPH) schemes.
-Given the known differences between hydrodynamics implementations \citep{Agertz2007,AGORA,AGORA2}, extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.
-Additionally, grid-based schemes are able to generally avoid issues with metal mixing, one of the largest model uncertainties in standard SPH codes.
-
-The native SPH scheme is incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
-This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017} which, while sophisticated, must still generally be fine-tuned.
-Even more, a given parameterization is not necessarily applicable generally \citep{Revaz2016}, though recent studies have shown great improvements to this end \citep{Escala2017}.
-Metal mixing efficiencies may also vary species-by-species (refs), as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
-In part, this is because mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources)
-%mm in which they are injected to
-    that injects metals into 
-the ISM.
-The variations in how one handles sub-grid metal injection and metal mixing schemes can lead to challenges in connecting models back to the fundamental physics that drives galactic evolution.
-We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mesh refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies.
-
-Although increasing physical resolution reduces 
-%mm one's 
-reliance on sub-grid physics, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations \citep[SSPs; as studied in detail in ][]{Revaz2016} do not make physical sense.
-Below 10$^4$ M$_{\odot}$, SSPs begin to no longer fully sample the IMF, and can no longer be considered average representations of stellar populations; this becomes conceptually problematic at SSP masses comparable to or below the mass of the most massive star ($\sim 100$ M$_{\odot}$).
-Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Rosdahl2015,Kroupa2013}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
-%mm Perhaps the most naive, 
-   The most straightforward
-solution, though untenable for large scale simulations, is to remove the SSP formalism entirely and simply track stars as individual particles. In this work, we 
-%mm follow stars as individual star particles, allowing us to place unprecedented detail on our
-     do this, allowing unprecedented detail in our
- accounting of stellar feedback processes and chemical enrichment.
-
-The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms.
-We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution.
-For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies.
-\citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
-Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
-
-Using star-by-star modeling, we are able to capture in more detail the stellar yields from individual stars released over their lifetime.
-In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
-This opens an exciting new channel for testing models of galaxy evolution by enabling us to leverage current and ongoing observations probing the detailed chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
-
-This paper is the first in a series of papers examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
-In this paper we introduce a new method of modeling for feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}.
-For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer.
-In addition, we couple to a self-consistent set of stellar yields
-%mm tables from the
-to track stellar yields from massive star stellar winds, AGB star winds, and supernovae. We describe each mode of our multi-channel feedback 
-%mm implementation 
-in detail below, and briefly discuss their implementation in an isolated dwarf galaxy simulation.
-
-Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.
-
 \section{Methods}
 \label{sec:methods}
-In 
-%mm brief, 
-     summary, 
-we produce high-resolution galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
-This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
-To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic UV background.
-We
-%mm 
-    assume collisional ionization equilibrium for all other elements in order to
-use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$).
-Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback.
-We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure.
-In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner (LW) dissociation of molecular hydrogen.
-We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both.
-We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors.
-We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star
-%mm
-   as it forms
-with the associated local gas abundances for each species. These methods are discussed in full detail below.
+We refer the reader to Paper I for a detailed description of our numerical methods and feedback models, briefly summarized below.
 
-\subsection{Hydrodynamics and Gravity}
-\label{sec:hydro}
-
-We use the adaptive mesh refinement (AMR) hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodyanamical evolution and detailed feedback physics in a set of high resolution, isolated, low mass dwarf galaxies.
+\subsection{Hydrodynamics}
+We use the adaptive mesh refinement (AMR) astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{http://www.enzo-project.org} \citep{Enzo2014} in this work.
 \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions.
 We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick.
-Specifically, simulations presented here were conducted at changeset 445de816fd99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
-We compute the total gravitational potential from gas self-gravity, stars, and static background dark matter potential.
-The collisionless star particles are evolved with a particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.
+Specifically, simulations presented here were conducted at changeset 445de816fd99.}.
+We solve the equations of hydrodynamics in our isolated galaxy simulations using a direct-Eulerian piecewise parabolic method (PPM) \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
+We include the contribution of gas self-gravity to the local potential, and evolve the collisionless star particles using a particle mesh N-body solver.
 
-The computational domain in an AMR simulation is adaptively refined up to a designated resolution limit for a given set of refinement criteria.
-We require that the Jeans length be resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution.
-Our maximum resolution in the simulations presented here is 1.8 pc.
-At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation.
-Studies have shown that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation \citep{Truelove1997}.
+Each galaxy is centered in a 128$^{3}$ zone computational domain with width equal to approximately 2 $R_{\rm vir}$ (see Section~\ref{sec:IC} and Table~\ref{table:IC}).
+We use 8 or 9 additional levels of refinement to reach a maximum resolution of $\sim$ 2 pc in each galaxy.
+A zone is refined 1) if the mass in a given cell exceeds $M_{\rm res} = 52 $~M$_{\odot}$, 2) such that the local Jeans length is always refined by 8 cells.
+In addition, regions within 4 cells of a star particle are refined to the maximum refinement level to ensure feedback is always deposited at maximum resolution.
+Our star formation density threshold corresponds roughly to densities where the Jeans length becomes unresolved at the maximum refinement level (discussed below).
+However, we use a pressure floor to prevent artificial fragmentation of this star forming gas.
 
-We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}).
-Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
-However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial collapse once its Jeans length becomes unresolved.
-This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
-The use of a pressure floor is common in galaxy scale simulations with limited dynamic range.
-(\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out.
-Leave it in?})
+\subsection{Star Formation and Stellar Feedback}
+We refer the reader to Paper I for the complete details of our star formation and feedback methods, summarized below.
 
-\subsection{Chemistry and Cooling Physics}
-\label{sec:chemistry}
+We allow star formation using a stochastic method \citep{Goldbaum2015,Goldbaum2016} that samples directly from an adopted IMF.
+In contrast to most other galaxy scale simulations to date, these star particles represent individual stars rather than populations of many stars.
+In each star forming region, defined as zones with $n > 200$~cm$^{-3}$, $T < 200$~K, and a convergent flow, we compute the probability that 100 M$_{\odot}$ of stars form in that region in that time step assuming the star formation rate depends on the local gas free-fall time and a star formation efficiency, which we take as $\epsilon_{\rm f} = 0.02$ (cite).
+Stars are sampled from a Salpeter IMF with $M_{*} \in [1,100]$~M$_{\odot}$.
 
-We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset 59adc76b3130.} \texttt{Grackle} is a freely available, open source multi-code library, designed to interface with a wide variety of astrophysical codes.
-We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.
-We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
-However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$) with the broken power law scalings from \citet{Remy-Ruyer2014}.
-For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
-% Since we assume a dust abundance that depends only on metallicity, we do not track dust destruction or creation, which may play an important role regulating detailed ISM properties.
-(Vogelsberger is working on this directly but no papers yet...
-will cite if it gets submitted by then)
+We follow yields from 12 individual metal species using yields tables from XXXX for all stars with $M_{*} < 25$~M$_{\odot}$, and XXX for the stellar winds from stars with $M_{*} > 25$M$_{\odot}$.
+We make the simplifying assumption that all stars with $M_{*} > 25$M~$_{\odot}$ do not explode as supernovae, given the significant uncertainties in the end-of-life behaviors for stars in this regime (citations).
+We include three distinct feedback channels for each of our stars: 1) supernovae, both core collapse and Type Ia, 2) stellar winds, both from massive and AGB stars, and 3) stellar radiation from massive stars.
+Here, we define massive stars as those with birth masses greater than 8 M$_{\odot}$.
+% Stellar attributes, used to set their lifetimes and feedback properties, are interpolated from the ZAMS values on the PARSEC stellar evolution tracks given the initial mass and metallicity of each star.
 
-Metal line cooling is modeled using pre-computed \texttt{Cloudy}\footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
-As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
-Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities.
-To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.
-We have made these new tables public in the main \texttt{Grackle} repository.
-These are both discussed in greater detail in Appendix ~\ref{appendix:cooling}.
+Supernovae are injected as thermal feedback alone with $E_{\rm SN} = 10^{51}$~erg in a 3-cell radius region around the given star particle.
+We have demonstrated in Paper I (see Appendix) that we have sufficient resolution to resolve these explosions with thermal energy injection alone.
+Low mass stars are tracked as white dwarfs at the end of their lives, using a delay-time-distribution model to determine when, if at all, a  given white dwarf will explode as a Type Ia supernovae.
+We assume the energy injection from stellar winds is negligible, given the computational expense of following fast (10$^{3}$ km s$^{-1}$), hot ($\sim 10^{6}$~K) gas while satisfying the Courant condition.
+Rather, winds are injected as thermal energy, with wind temperature equal to the stellar surface temperature, and at $v_{\rm wind} = 1$ km s$^{-1}$.
+Confirming the common assumption that wind energy is not a significant long-term source of feedback in the evolution of these galaxies is the subject of ongoing work.
 
-\subsection{Star Formation Algorithm}
-\label{sec:star formation}
-In order to resolve individual star formation on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
-Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
-Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively.
-We limit the fraction of a cell's gas mass that is converted into stars by requiring $M_{\rm gas} > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and $M_{\rm max,*}$ is the maximum star mass (100 M$_{\odot}$).
-No star formation occurs when $M_{\rm gas} < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode does not produce negative densities.
+We follow stellar radiation in four bands.
+Two, HI and HeI ionizing radiation, are followed through direct ray-tracing methods from (cite).
+The other two, FUV and LW radiation, are assumed to be everywhere optically thin in these small, low metallicity dwarf galaxies.
+The stellar FUV radiation contributes to the local photoelectric heating rate using a prescription described in Paper I, similar to previous works \cite{BakesTielens1994,Wolfire2003,Forbes2016,Hu2017}.
+The LW radiation contributes to the local H$_{2}$ dissociation rates.
+These radiation fields are included in addition to the metagalactic UV background, discussed below.
 
-We make the common ansatz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
-At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
-%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
-The gas mass converted to stars in a time step, $dt$, is
-\begin{equation}
-M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
-\end{equation}
-In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution.
-We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses.
-In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
-If it does, we random sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$.
-We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and maximum stellar mass of 100 M$_{\odot}$.
+% We follow the ionizing radiation from massive stars, $M_{*} > 8$~M$_{\odot}$, through direct radiative transfer (cite) using fluxes obtained from interpolation on the OSTAR2002 grid of stellar atmospheric properties.
+We also follow FUV and LW band radiation from these stars under the assumption that this non-ionizing radiation is optically thin.
+The FUV radiation is used to compute the local photoelectric heating rate using a model adopted from (bakes, wolfire, forbes).
 
-Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
-Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
-Stars evolve during the simulation, by losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation.
-For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.
+% We follow stellar winds from both massive stars, assumed to be constant throughout their lifetime, and the AGB phases of less massive stars.
+Due to the computational expense of following these fast ($\sim 10^{3}$~km~s$^{-1}$) and hot ($T \sim 10^{6}$~K) winds, we inject these winds with low velocities and with thermal energy equivalent to the stellar effective temperature.
+We therefore assume that energy injection to the ISM from these winds to be negligible compared to the stellar radiation and supernova feedback (cite).
+Confirming the effects of a detailed stellar wind implementation on long-term galaxy evolution is the subject of future work.
 
-Finally, each star is marked as a ``must refine" particle, requiring that each star be surrounded by a four-cell region at the highest level of refinement.
-This ensures that both stellar winds and supernovae feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.
+%We track both core collapse supernovae from massive stars and Type Ia supernovae from low mass stars.
+The Type Ia supernovae are included self-consistently, using a delay time distribution model to compute the probability that a white dwarf formed from the low mass stars will explode in the simulation time, deterministically setting their explosion times.
 
-\subsection{Stellar Properties}
-\label{sec:properties}
-Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}).
-We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$.
-Although $T_{\rm eff}$ and $g$ evolve over time for stars, modifying stellar radiative properties, following a stellar evolution track for each of our stars is beyond the scope of this work.
-We instead fix these properties at their zero age main sequence values.
+\subsection{Heating and Cooling Physics}
+\label{sec:heating and cooling}
+We use the chemistry and cooling package Grackle \citep{GrackleMethod} to follow 9 species non-equillibrium primordial chemistry and approximate metal line cooling in our simulations.
+Our primordial cooling and heating rates are computed self-consistently with the non-equillibrium chemistry under a metagalactic UV background \citep{HM2012}.
+We account for approximate self-shielding against the UV background following \citep{Rahmati2013} and include use metal line cooling rates tabulated from \textsc{Cloudy}, accounting self-consistently for the reduced ionizing background in self-shielded regimes (see Paper I for more details on these tables).
+We also include both the LW radiation and photoelectric heating from the UV background.
 
-\subsection{Stellar Feedback and Chemical Yields}
+\subsection{Initial Conditions}
+\label{sec:IC}
+Each galaxy in this work was initialized as a uniform distribution of gas set to be in hydrostatic equilibrium with a background, static dark matter potential.
+The gas properties in each galaxy remain fixed, modeled after the Local Group dwarf galaxy Leo P, as does the dynamical mass interior to 500 pc, set to $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$.
+In each of our four galaxies, we vary only the maximum circular velocity of the dark matter halo, and by extension $M_{\rm vir}$ and $R_{\rm vir}$, as described below.
 
-\subsubsection{Stellar Yields}
-\label{sec:yields}
-For the first time in galaxy scale simulations, we track galactic chemodynamical evolution using stellar yields as ejected from star particles that represent individual stars.
-We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}.
-This grid includes yields from the AGB phase of stars between 1 and 7 M$_{\odot}$, as well as yields from both stellar winds and core collapse supernova of massive stars over 12 to 25 M$_{\odot}$.
-We complement these tables with tables from Slemer et.
-al.
-(in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014} to track stellar winds for stars more massive than 25 M$_{\odot}$.
-We ignore supernova yields from these stars (see next paragraph).
-We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth.
-Although we can follow an arbitrary number of metal species, practical considerations
-%mm 
-   of memory use 
-prevent this in any given simulation.
-We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
+The gas properties in each galaxy are designed to be similar to that of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, but are not meant to be a matched model to this galaxy.
+Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4}$ adopting $Z_{\odot} = 0.018$ from \cite{Asplund2009}.
+We initialize our dwarf galaxy without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citep{McQuinn2015}.
+The gas density profile is set using an exponential disk (see Paper I) with scale radius and scale height of $250$~pc and $100$~pc respectively, with a total radial extent of 600~pc.
+The temperature and circular velocity profiles are set assuming hydrostatic equillibrium with the dark matter background, described below.
 
-Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse supernovae.
-Where this transition occurs is uncertain, but is commonly taken to be around 8--10~M$_{\odot}$.
-This is a free parameter in our model, but we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value.
-In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
-Stars above this mass
-%mm
-    are assumed to
-eject their stellar yields via 
-%mm ``massive" 
-   line-driven
-stellar winds at a constant mass loss rate throughout their lifetime
-%mm ,
-  (neglecting Wolf-Rayet and luminous blue variable phases),
-ending their lives as a core-collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics).
-Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
-\citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.
+As mentioned, we fix the dynamical mass interior to 500 pc in each galaxy to the measured value in Leo P.
+This is equivalent to fixing the circular velocity at 500 pc, or $v_{\rm c, 500 \rm{pc}} = 15$~km~s$^{-1}$ as is observed for Leo P \citep{Bernstein-Cooper2014}.
+We represent our dark matter halo using a static Burkert potential \citep{Burkert1995}, and vary the maximum circular velocity by changing the adopted scale radius, $r_{\rm s}$.
+We do this for four different values of $v_{\rm c, max}$.
+Table~\ref{table: IC} gives the dark matter halo properties for each galaxy, and we show the profiles for each in Figure~\ref{fig:dm profile}.
+Increasing $v_{\rm c,max}$ while keeping $v_{\rm c}$ fixed at 500 pc serves to reduce dark matter density profile interior to 500 pc, broadening the potential well.
 
-There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}.
-Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
-Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no
-%mm
-    further
-mass or energy ejection.
+As the initial gas profile in each galaxy is smooth, we use initial supernova driving to prevent uniform collapse and a spurious starburst.
+We randomly place supernovae in the disk of the galaxy at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}.
+We stop the artificial driving 25~Myr after the first star particle forms.
 
-Type Ia supernovae are an important additional source of galactic chemical enrichment.
-These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
-We use the Type Ia supernova yields given in \citet{Thielemann1986}, adopting a Type Ia supernova model as discussed in Section~\ref{sec:Type Ia}.
-%mm
-    We emphasize that we only track Type Ia supernovae occurring within the 
-    population of stars formed in this model, neglecting supernovae from any 
-    pre-existing population.
-
-\subsubsection{Stellar Winds}
-\label{sec:stellar winds}
-Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
-Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from supernovae and radiation, stellar winds are potentially important sources of pre-supernova feedback.
-%mm For both AGB winds and massive stellar winds
-    In models that include feedback energy from stellar winds from both AGB and 
-    massive stars, 
-we inject the feedback energy in a three-cell radius spherical region centered on the emitting star particle, assuming full thermalization of the wind kinetic energy.
-The total injected energy in timestep $\Delta t$ is therefore $E_{\rm wind} = \dot{M}\Delta t \times v^2_{\rm wind} + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass ($\dot{M}\Delta t$) given the star's interpolated $T_{\rm eff}$.
-We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells.
-We assume constant mass loss rates for all winds as set by the yields tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars). 
-%Properly modeling stellar winds requires sub-parsec resolution, which is problematic in galaxy-scale simulations.
-
-Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}.
-Satisfying the Courant time step becomes prohibitively expensive following this gas ($dt \sim$~100~yr), particularly as stellar wind bubbles have typical temperatures of 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
-For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
-In our case, we fix massive stellar winds to $v_{\rm wind} = 1$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies.
-Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work.
-These points are discussed in more detail in Section \ref{sec:stellar winds discussion}.
-
-% Injecting 10$^{3}$ km s$^{-1}$ gas onto the grid at these scales leads to super heated, shocked gas at unphysical temperatures of about 10$^{8-9}$ K, particularly when injecting into very low density media.
-This can lead to painfully short time step sizes and crashes in the hydrodynamics solver.
-We adopt the common solution of artifiially reducing the wind velocity from massive stars, choosing $v_{\rm wind} = 500$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-However, this can still be problematic once the star evacuates the local ISM and injects its energy to very low density ($n \lesssim 10^{-3}$ \ccunit) gas.
-We address this issue by mass loading our winds when injection would lead to wind bubble temperatures in the spherical source region above a maximum temperature typical of wind bubble.
-This is a free parameter that we take to be 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
-Mass loading in this manner is (in effect) a sub-grid model for the unresolved ISM mixing at the boundary layer of the wind bubble, which is in fact the source of a majority of the gas mass within the wind bubble \citep{Weaver1977}.
-We take the metal species abundances of the mass loaded ISM to be the average cold / warm ISM abundance on each grid to prevent artificially inflating/deflating the overall abundances.
-We discuss our ability to resolve typical single star wind bubble properties in Appendix ~\ref{appendix:stellar winds}.
-
-%parameterized in this work with the STARBURST99 wind model, \citep{Leitherer1992}:
-%\begin{multline}
-%{\rm log} \left[ v_{\rm wind} {\rm (km~s^{-1})} \right] = 1.23 - 0.30~{\rm log}~\left[L{\rm (L_{\odot})}\right] \\
-% + 0.55~{\rm log}\left[M({\rm M_{\odot}})\right] + 0.64~{\rm log}\left[T_{\rm eff}(K)\right] \\
-% + 0.13~{\rm log}\left[Z({\rm Z_{\odot}})\right].
-%\end{multline}
-
-Stars that only undergo an AGB phase deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks.
-AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$.
-For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars.
-
-\subsubsection{Core Collapse Supernovae}
-\label{sec: core collapse}
-Stars between  $M_{\rm thresh} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse supernovae, ejecting mass and yields as determined by the NuGrid stellar yield tables at 10$^{51}$ erg of thermal energy.
-Due to the high resolution (1.5--2.5 pc depending on galaxy size) of our simulations, we generally resolve the Sedov phase of each supernova explosion well (see Appendix~\ref{appendix:supernova}).
-We find injecting thermal energy alone in a three-cell radius spherical region around the star particle to be sufficient to resolve the supernova explosions.
-We continue to track any remaining stellar mass after the supernovae as a massive ``remnant" tracer particle.
-In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment through X-ray binaries and neutron-star-neutron-star merger events which, while rare, could be important in long term galaxy evolution.
-\textbf{Should I reference a few recent hydro sims that included these feedback sources? - AE  
-%mm
-Can't hurt if they are ready to hand. Not high priority, though. M-M}
-
-\subsubsection{Type Ia Supernova}
-\label{sec:Type Ia}
-We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors.
-At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
-%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
-%or, 
-%\[
-%M_{\rm WD} = 
-%\begin{cases}
-%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
-%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
-%\end{cases}
-%\]
-%where $M_{\rm *}$ is the initial mass of the WD progenitor.
-We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WD's that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.
-
-We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution (DTD) model. 
-%\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):} 
-The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope and normalization are observables, and $\eta$ the fraction of stars which can form SN Ia progenitors that \textit{will} explode as a SN Ia within a Hubble time.
-The value for $\eta$ depends on the normalization of the DTD (an observable), as well as one's choice of IMF and mass range of potential SN Ia progenitors (as given above).
-This fraction is given as
-\begin{equation}
-\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
-\end{equation}
-where $N_{\rm Ia}/M_{\rm SF}$ is the DTD normalization, which represents the fraction of stars that form SN Ia progenitors, $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF ($dN/dm$), and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
-The DTD slope, $\beta$, is of order unity, with typical values between 1.0 and 1.2 (see \citet{Maoz2014} for a recent review).
-$N_{\rm Ia}/M_{\rm SF}$ represents the number of SN Ia per mass of star formation; this can be derived by taking observed values of the SNIa rate and integrating over a Hubble time.
-Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
-We adopt 1.2 \citep{Maoz2010} and 0.8$\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013} for our fiducial values of $\beta$ and $N_{\rm Ia}/M_{\rm SF}$.
-Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.
-
-Finally, the probability a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor is taken as
-
-\begin{equation}
-P(t) = \dot{P}(t)dt = \eta \frac{ t^{-\beta}}{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau} dt,
-\end{equation}
-
-where $t_{\rm o}$ is the formation time of the WD and the denominator normalizes the total probability to $\eta$.
-This naturally accounts for both a prompt and delayed Type Ia supernova population in our simulations.
-In practice, we invert the cumulative probability distribution to assign an exact time at which a given WD will explode, rather than making a random number draw for every WD particle every time step as $\eta$ is small.
-
-\subsubsection{Ionizing Radiation}
-\label{sec:ionizing radiation}
-Radiation feedback (ionization, ionization heating, and radiation pressure) is an important source of pre-SN feedback in galaxies.
-\ion{H}{2} regions carved out by stellar radiation change the ISM structure where SNe eventually explode, generally increasing their dynamical importance.
-However, when accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily through channels carved through dense clouds.
-Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with limited application in full radiation hydrodynamics simulations \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
-As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through ray tracing methods described below.
-%mm In this particular work, we 
-  We here
-use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).
-
-Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer as coupled to the hydrodynamics of the simulation.
-We follow \ion{H}{1} and \ion{He}{1} ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
-Radiation pressure is expected to be an important source of feedback only in more massive galaxies; we explore this point further in this work.
-
-We adopt the \ion{H}{1} and \ion{He}{1} ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
-We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star.
-Stars less massive than about 15 M$_{\odot}$ are generally off of the OSTAR2002 grid, and massive stars with sub-solar metallicity generally have effective temperatures above the OSTAR2002 grid.
-In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).
-\citet{Dale2012} demonstrated that uncertainties on order of a few in the ionizing radiation rates are not significant in giant molecular cloud (GMC) scale simulations.
-%Generally, the ionizing fluxes from high temperature black bodies underestimate the OSTAR2002 flux, and lower temperature black bodies overestimate the flux by a factor of 2-5 and 10-1000 respectively.
-
-Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}).
-The average energy for \ion{H}{1} and \ion{He}{1} ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
-
-We also include the effects of radiation pressure on \ion{H}{1}.
-This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}.
-We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared.
-This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}.
-However, the importance of multiple scattering is still unclear.
-Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017}.
-Due to these uncertainties, and given that we focus on low-metallicity dwarf galaxies with low dust content, we ignore this effect.
-
-%mm \subsubsection{Diffusive Heating}
-         \subsubsection{Diffuse  Heating}
-\label{sec:diffusive heating}
-We include two forms of 
-%mm diffusive 
-   diffuse
-heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars.
-Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
-However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}.
-Generally, models for photoelectric heating and LW radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile.
-Only recently has the localization and time variation of these processes been considered.
-
-Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy.
-We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background (see \citep{GrackleMethod} for more details of this implementation).
-We assume \ion{He}{1} ionization generally follows \ion{H}{1}.
-This allows us to approximate \ion{He}{1} self-shielding using the same form (A.
-Rahmati, private communication).
-We ignore \ion{He}{2} photoionization from the UV background entirely.
-Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \citet{Hu2017}).
-As mentioned previously, we have re-computed metal line cooling tables using \texttt{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
-This is described in more detail in Appendix ~\ref{appendix:cooling}.
-
-%Ignoring this effect leads to an overestimation of the cooling rates when in the self-shielding regime.
-%We refer to \citet{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \citet{Gracklemethod} for its specific implementation, as used here.
-
-%mm We assume the FUV luminosity for each our stars is everywhere optically thin. The 
-     We assume the galaxy is mostly optically thin to stellar FUV.  Therefore, the stellar
-%
-FUV flux in each cell is summed over the contributions from each star
-%mm 
-   with a local approximation to the attenuation within dense cells applied. 
-We parameterize the local photoelectric heating rate \citep{BakesTielens1994,Wolfire2003,Bergin2004}
-\begin{equation}
-\label{eq:PE}
-\Gamma_{\rm pe} = (1.3 \times 10^{-24} \mbox{~erg~s~cm}^{-3}) \epsilon n_{\rm H} G_{\rm eff} D 
-\end{equation}
-where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\rm{exp}(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust to gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
-Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
-
-$D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
-The extremely low dust to gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a $D$ that scales linearly with metallicity at very low metallicity.
-At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit.
-Given that the ambient density of the ISM is generally 1--10~cm$^{-3}$, we can safely assume the FUV field to be optically thin.
-However, we do include a localized attenuation prescription that may influence high-density or metal-enriched regions of the galaxy.
-We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.
-
-Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
-This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; none of which are followed directly in these simulations.
-Instead, we use a log-linear fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
-%This is a compromise between adoption a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
-
-\subsubsection{Lyman-Werner Radiation}
-\label{sec:LW}
-In addition to the LW radiation from the UV background, we account for localized LW flux from each of our stars to compute the total, local H$_2$ dissociation rates.
-Given the local LW flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
-We account for approximate H$_2$ self-shielding against these sources of LW flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.
-
-%
-% CR section moved to missing physics
-%
-%\subsubsection{Cosmic Rays}
-%\label{sec:cosmic rays}
-%Cosmic rays may be a signficant source of feedback within star forming galaxies, capable of driving galactic outflows.
-Recent work has shown that CR's are capable of providing a significant additional pressure support within the ISM \citep{SalemBryan2014, SalemBryanHummels, GirichidisCR, Pakmor2016}, and are capable of producing more realistic galaxy gas halos \citep{SalemBryanCorlies}.
-We include cosmic rays coupled to the hydrodynamics of our simulation using a two-fluid model with adiabatic index $\gamma = 5/3$, as described in \citep{SalemBryan2014}.
-Cosmic ray energy is injected as some fraction, $f_{\rm CR}$, of the total supernova rate; we adopt $f_{\rm CR}$ with the fiducial value of 0.1.
-We include isotropic cosmic ray diffusion as described with the diffusion coefficient, $\kappa_{\rm CR} = 3.0\times10^{28}$.
-We refer the reader to \citep{SalemBryan2014} for a study of the effects different values for $f_{\rm CR}$, $\kappa_{\rm CR}$, and the CR adiabatic index has on galaxy evolution.
-
-%Recent work has examined the impact anisotropic diffusion of cosmic rays along magnetic fields has on galaxy evolution \citep{GirichidisCR, Pakmor2016} and galactic winds generated from cosmic ray feedback \citep{GirichidisCR, Simpson2016}.
-Including magnetic fields can substantially change the effect of cosmic ray feedback provided $\mu$G level, ordered magnetic fields develop within the galaxy, as is the case for more massive disk galaxies.
-However, the magnetic field properties of small, ultrafaint dwarf galaxies are poorly understood.
-These small, puffy galaxies may be completely unable to sustain ordered magnetic fields, damping the effects of anisotropic diffusion as cosmic ray diffusion through random, tangled magnetic fields is approximately isotropic.
-We do not expect anisotropic diffusion and magnetic fields to have a significant impact on the effectiveness of cosmic ray feedback for ultrafaint dwarf galaxies, but this stands to be an important area of future research.
-
-\section{Galaxy Initial Conditions}
-\label{sec:IC}
-The galaxy presented in this work is constructed to be similar to the observed properties of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
-Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4} Z_{\odot}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}.
-Our dwarf galaxy is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
-
-The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential.
-The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
-\begin{equation}
-\rho_{\rm gas} (R,z) = \frac{M_{\rm gas}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
-\end{equation}
-where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm gas}$ is approximately 70\% of the total gas mass.
-We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$.
-We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5\times 10^{8} \mbox{ M_{\odot}}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc.
-This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc.
-These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc, or $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012} (need more cite).
-We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in a future work.
-
-Following the initialization procedure of \citet{Hu2017}, we use artificial supernova driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
-This additionally prevents an otherwise uniform collapse of the gas disk
-%mm
-   at the beginning of the simulation.
-These supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
-We stop the artificial driving 25~Myr after the first star particle forms.
-These artificial supernovae do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
-%mm
-    We do not include any other effects from the stellar population that would have caused these   
-    supernovae.
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.8\linewidth]{dark_matter_mass_virial} \\
+%\vspace{0.1cm}
+%\includegraphics[width=0.8\linewidth]{circular_velocity_virial} \\
+%\includegraphics[width=0.8\linewidth]{initial_surface_density}
+%\caption{Dark matter cumulative mass (top) and circular velocity profiles (middle) for each of our galaxies, plotted as a fraction of the virial radius for each (see Table~\ref{table:IC} for details).
+The cumulative mass interior to 500 pc is held fixed in each galaxy, at $2.5\times 10^7$ M$_{\odot}$, with the variations in profile arising from changing the scale radius.
+The bottom panel gives the initial gas surface density profiles for each galaxy, which are essentially the same.}
+%\ref{fig:dm profile}
 
 \section{Results}
-\label{sec:results}
-We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:star formation}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first \textbf{200 Myr} after the first star forms.
-Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.\footnote{All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset \textbf{changeset number}.}
-
-\subsection{Morphological Structure and Evolution}
-\label{sec:structure}
-
-We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and O column density projections (fourth row), at four different times in the simulation \textit{(list times here)}.
-In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points.
-Towards the end of the simulation time, the half light radius is $389 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
-
-The increased gravitational potential towards the center of our dwarf galaxy leads to an inside-out star formation evolution, whereby star formation propagates from the inner regions outward during the galaxy's evolution.
-This is obvious in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
-This region quickly becomes volume-filled with both warm and hot gas generated from radiation feedback and supernovae respectively.
-Both the ISM and the halo gas is multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident by the temperature slices in both panels.
-The ISM properties are quantified further in Section~\ref{sec:phase}.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
-\caption{\textbf{Draft figure - need to pretty up and finalize fields and times.} Edge-on views of our dwarf galaxy at four different times in its evolution, beginning with the time at first star formation and ending at XXX Myr.
-Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and O column density (fourth row).
-Additionally, each individual main sequence star particle is shown in the number density projections as a single black dot.}
-\label{fig:panel_x}
-\end{figure*}
-
-The gas disk is thin outside the stellar radius of our galaxy, but is resolved at all radii.
-In Figure~\ref{fig:scale_height} we plot the scale height of our gas disk as a function of radius at the initial conditions (blue), just before first star formation (orange), and averaged over the last 20 Myr of simulation time (black).
-At the outer edges of the disk, beyond regions of ongoing star formation, the scale height is $\sim 15$ pc, comparable to the scale height in the inner 200 pc prior to first star formation.
-Though small, both of these scale heights are resolved at our maximum resolution, 1.8 pc; we note that without feedback, our gas disk would continue to cool and collapse to an uresolved, razor thin disk.
-For the majority of the galaxy, stellar feedback sets the scale height.
-Heating, from both stellar radiation and supernovae, lifts gas above the midplane and generating scale heights between 40 and 100 pc within the half light radius.
-Effective galactic winds have carved out most of the gas within the inner 40 pc, distributing it somewhat smoothly above/below the midplane, leading to the significantly larger scale heights.
-This is made clear in the density panels if Fig~\ref{fig:panel_x}, where regions of active star formation show a general lack of the dense, cool gas that creates the smaller scale heights at larger radii.
-%We additionally compute the mass weighted height of the disk, defined as $H = (\sum{Mz^2}/\sum{M})^{1/2}$, where the summation is over each gas cell, as a function of radius (not shown here).
-$H$ is generally larger than the scale height by a factor of 2, but is comparable to the scale height at radii with ongoing star formation, indicating a particularly uniform-then-truncated density distribution.
-At large radii, away from active star formation, $H$ is roughly 50 pc, or $\sim$ 3 times the scale height.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
-\caption{\textbf{Draft figure - need to pretty up and finalize fields}. Same as Figure~\ref{fig:panel_x}, but showing face-on projections/slices.}
-\label{fig:panel_z}
-\end{figure*}
-
-Interestingly, there is significant structure well above the gas disk in the form of dense clouds and filamentary features, as seen in the edge-on projections.
-These gas cold gas clumps appear to have typical sizes on order of $\sim$ 10 pc, but with lower density tails that can extend up to 100 pc.
-These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy.
-These clumps have typical velocities on order of a few to tens of kilometers per second, and appear to survive for 10--100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk.
-The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work.
-This is exciting given recent \citep[e.g.][]{Zheng2017} and ongoing \citep{Zheng2017HST} observational observational work examining the disk-halo interface in nearby galaxies.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.975\linewidth]{scale_height}
-\caption{The average gas disk scale height as a function of radius for the last 20 Myr of simulation time (black) as compared to the uniform initial conditions (blue) and the scale height profile immediately before the first star formed (orange).}
-\label{fig:scale_height}
-\end{figure}
-
-\subsection{Star Formation Rate and Mass Evolution}
-\label{sec:sfr}
-
-We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.
-(By the end of the simulation, there have been no Type Ia supernovae.) Within the first 40 Myr of evolution the SFR rises quickly to between $2-4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, and remains at this level with fluctuations of about a factor of 2 or less.
-Averaging over the entire simulation time since the first star was formed, we obtain  $<\rm{SFR}> = 2.34 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
-The star formation rate of our model galaxy as compared to observed galaxies is discussed further in Section~\ref{sec:observation}.
-
-%mm \footnote{  [This is rather too long for a footnote, I think.]
-The granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
-Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
-For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$.
-Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense.
-Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.
-
-At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about \textbf{$6 \times 10^5$ M$_{\odot}$, or roughly 17\%} of the total mass in the galaxy's disk.
-The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases to about \textbf{25\%} as the total amount of mass in the disk decreases through feedback driven winds.
-Small drops in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback.
-Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
-The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{sfr_snr}
-\includegraphics[width=0.475\linewidth]{mass_evolution}
-\caption{Left: The SFR and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left).
-Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy over time.
-Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.}
-\label{fig:sfr_mass_evolution}
-\end{figure*}
-
-\subsection{Phase Diagrams and ISM Properties}
-\label{sec:phase}
-
-Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy. 
-%mm \textbf{too strong of a claim?}. [No, it's quite true: you just need a cooling curve balanced against diffuse and SN heating.] 
-We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
-See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-Each of these exist in our simulations, and are regulated by the complex interplay between
-%mm
-   cooling, 
-turbulence, self-gravity, and 
-%mm 
-    diffuse and shock heating from 
-stellar feedback throughout the galaxy's evolution. Here we discuss the phase properties of the gas throughout the simulation box and within the ISM of our dwarf galaxy.
-
-Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas in the simulation domain, averaged over the final 50 Myr of simulation time.
-One can readily identify the two most massive regions of gas in the simulation, a low density, warm phase produced through ionization and supernovae heating, and a cold, high density phase which makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
-\textbf{not completely sure what to talk about here for the diagram}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{phase_diagram.png}
-\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation, averaged over the final 50 Myr of simulation time, and showing the whole simulation domain.}
-\label{fig:phase}
-\end{figure}
-
-The mass of the ISM in our dwarf galaxy is dominated by the CNM over the entire simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
-Together, the CNM and WNM comprise roughly 90\% of the galaxy's mass throughout most of its evolution.
-While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume each, though the two warm phases dominate.
-The volume fractions are subject to significantly more fluctuations over time, due to the low SFR and supernova rate of our galaxy.
-Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-These results are in some contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}.
-In short, they find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass.
-Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
-\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
-\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. This figure only includes gas present within the disk of the galaxy.}
-\label{fig:ISM_evolution}
-\end{figure*}
-
-\subsection{Interstellar Radiation Field}
-\label{sec:ISRF}
-
-The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields 
-%mm 
-   both as expected from stellar motions in our own galaxy \citep{Parravano2003},
-   and in models including radiation \citep[e.g.][]{Hu2017}. 
-This is particularly not surprising in our low SFR regime, where there can be large fluctuations over time 
-%mm in proximity to a massive, radiating star. 
-    as individual massive stars form, move about, and evolve.
-In Figure~\ref{fig:ISRF} we present 
-%mm 1D volume-
-    azimuthally averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time. The top panel shows 
-%mm the average value of 
-$G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sect.~\ref{sec:diffusive heating}).
-(The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.)
-%mm The shaded region gives the minimum and maximum value of $G_{\rm o}$ in the sampled time range. [redundant with caption] 
-%mm As shown, regions typically experience  
-    This shows that any given point experiences
-fluctuations in the ISRF of an order of magnitude.
-Interestingly, the central 200 pc does not contain the peak of the ISRF in the galaxy.
-This is likely a transient property, however, and is a by-product of the inside-out star formation of this dwarf galaxy.
-By the end of the simulation the feedback from stars produced in the central region has reduced the SFR compared to outer parts of the galaxy.
-The latter is thus host to more radiating young stars.
-
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{G_o_profile} \\
-\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
-\caption{
-%mm 1D radial
-    Azimuthally averaged radial 
-profiles of the ISRF in our galaxy in three different bands, time-averaged over the final 50 Myr of simulation time.
-The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
-The bottom panel gives the \ion{H}{1} and \ion{He}{1} ionizing stellar radiation flux, showing average and maximum values only.
-For these fields the minimum value reaches zero at some point during the examined period at all radii.}
-\label{fig:ISRF}
-\end{figure}
-
-The bottom panel gives the ionizing photon fluxes for \ion{H}{1} and \ion{He}{1} from %mm ionizing photons from the 
-stellar radiation 
-%mm \texttt{only}.
-   {\em only}. 
-Since these fields are tracked directly using ray-tracing radiative transfer, the profiles encode information about local attenuation of these photons from dense, neutral gas.
-This is the main driver of the differences between these fields and $G_{\rm o}$.
-%mm In addition, we only show the average line and shade to the maximum value at any given position, since the minimum value reaches zero at all radii at some point over the 50 Myr examined.
-As shown, this causes the profile to
-   The ionizing fields
-vary much more dramatically at all radii.
-However, the same general trend is preserved of less radiation in the inner 200 pc than in the region between 200 and 400 pc, and an order of magnitude or more fluctuation at all radii.
-The rapid drop off beyond 400 pc is due to the rapid attenuation of ionizing photons by the cold gas at large radii (see Figure~\ref{fig:panel_x}).
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
-\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
-\caption{Single-snapshot 2D radial profile plots of the ISRF in two flux bands, $G_{\rm o}$ and \ion{H}{1} ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
-Here, we include all gas within 25 pc of the midplane of our dwarf galaxy.
-We note the large difference in color scale between the two plots.
-Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to \ion{H}{1} ionizing radiation, it does not show up in the \ion{H}{1} ionizing radiation diagram.
-This gas readily appears in the $G_{\rm o}$ since we assume it to be optically thin, though do apply a localized shielding approximation.}
-\label{fig:ISRF_2D}
-\end{figure*}
-
-These plots are useful to understand the time-varying properties of the ISRF in a spatially averaged sense.
-However, the local variations for individual regions can be much larger than is illustrated in these profiles.
-In Figure~\ref{fig:ISRF_2D} we present %mm a 2D profile of $G_{\rm o}$ averaged
-    the full distribution of $G_{\rm o}$ over the final 50 Myr of the simulation time, which effectively captures the large spikes in local ISRF from recent star forming regions.
-The azimuthally averaged profiles accurately capture the averaged heating and ionizing effects of the ISRF in our galaxy, which helps reduce star formation by increasing the thermal pressure support and equilibrium temperature of the ISM, yet it is the spikes that act as important local feedback to shut off star formation in dense, collapsing regions that satisfy our star formation criteria.
-This point will be examined in more detail in future work with comparison simulations using different feedback processes.
-%mm (Emerick et. al. in prep).  [I'd only insert the reference when there is an actual astro-ph number to support it.]
-
-\subsection{Outflow Properties}
-\label{sec:outflows}
-
-Recent cosmological simulations of dwarf galaxies with 
-%mm detailed 
-feedback over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors on order of 100--1000 \citep{Muratov2015}.
-However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
-In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
-We follow \citet{Muratov2015} defining the mass outflow rate ($\dot{M}_{\rm outflow}$) at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
-\begin{equation} \label{eq:dotM}
-\dot{M}_{\rm outflow} = \sum M_{\rm gas} \times v_{\rm r} / dL.
-\end{equation} 
-We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.
-
-The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
-We use the 10 Myr averaged SFR to compute the mass loading rates.
-The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time.
-This quickly declines towards larger radii, however, with effectively zero outflow past the virial radius.
-\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift.
-Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below their typical values.
-
-Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
-Using a fit provided in \citet{Muratov2015} to extrapolate and compare at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
-These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
-We note, however, that our results are much closer to the \citep{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly much smaller mass loading factors at 0.25 $R_{\rm vir}$.
-
-% figure here of mass loading and mass outflow rates
-\begin{figure*}
-\centering
-\includegraphics[width=0.45\linewidth]{total_mass_outflow}
-\includegraphics[width=0.45\linewidth]{total_mass_loading}
-\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
-\label{fig:mass_outflow}
-\end{figure*}
-
-Detailed outflow properties, beyond outflow rates and mass loading factors, are important discriminators between the model dependent feedback physics included in galaxy simulations. 
-%mm \textbf{(do I need an example of this in recent work?)}. [maybe soften to "can help discriminate?"]
-In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
-Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{-1}$ or below.
-This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities.
-The distribution has a very long tail out to and beyond 500~km~s$^{-1}$.
-The dominant launching mechanism in this simulation are supernovae (Emerick et.
-al.
-in prep), generating a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
-However, as shown, the HIM comprises very little of the outflow by mass.
-Most of the outflowing gas comes from the warm phase, pushed out by the high pressure, fast moving HIM.
-Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
-The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{outflow_velocity_distribution}
-\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-The outflowing material is multiphase, broken into WNM, WIM, and HIM.
-See Section~\ref{sec:phase} for definitions of these regimes.
-We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$K.
-There is little to no outflowing mass in the CNM or molecular phases.}
-\label{fig:outflow_velocity}
-\end{figure}
-
-Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
-This has been better quantified recently both observationally \citep[e.g.][]{Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Angles-Alcazar2017,Muratov2017}.
-In Figure~\ref{fig:outflow_metallicity} we show the average ISM metallicity (black), halo metallicity (blue), and outflow metallicities (orange) at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
-The ISM metallicity evolves minimally from the initial conditions in this time, while the halo and outflow properties change significantly.
-It is apparent from this figure that the outflows are preferentially metal enriched, as the halo increases in metallicity by a factor of $\sim 2$ in the simulation time.
-Although most of the gas mass in the halo (outside the disk) remains within 0.2 $R_{\rm vir}$ (see Section~\ref{sec:obs_metals}), the mass that does make it
-%mm out far and out side the halo
-   to the outer reaches of the halo or beyond 
-is metal enriched by a factor of $\sim$5--6 compared to the ISM.
-This is in contrast with the results from \citet{Muratov2017}, which generally show $Z_{\rm outflow} \simeq Z_{\rm ISM}$ at $0.25~R_{\rm vir}$ and $Z_{\rm outflow} < Z_{\rm ISM}$ at $1.0~R_{\rm vir}$, though both with some scatter that reaches
-%mm above 
-$Z_{\rm outflow} > Z_{\rm ISM}$, especially at high redshift.
-However, we note that our simulations certainly do not contain a cosmologically realistic circumgalactic medium, nor do they include ongoing cosmological accretion of pristine gas; this will certainly lower the typical halo and outflow metallicities, possibly
-%mm more in 
-    resulting in better
-agreement with the findings of \citet{Muratov2017}.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{metallicity_evolution}
-\caption{The mass-weighted average metallicity of our dwarf galaxy's ISM, halo, and outflowing gas at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
-The halo is defined as the region outside of the disk, yet inside the virial radius.}
-\label{fig:outflow_metallicity}
-\end{figure}
-
-\subsection{Chemical Evolution} 
-\label{sec:chemical evolution}
-Observations of Local Group dwarf galaxies have shown that they retain very little of the total amount of metals they are expected to have produced, given their star formation histories (see Section~\ref{sec:observation}).
-In Figure~\ref{fig:species_fractions} we show the fraction of metals retained within the disk or expelled into the halo of our galaxy over time, along with a breakdown of the locations of each metal species by the end of the simulation.
-As shown in the top panel, a majority of each metal tracer species is found outside the disk of the galaxy, in the galaxy halo.
-In total, \textbf{85\%} of the tracer metal species produced lie outside of the disk of our galaxy.
-Interestingly, the exact fraction is not uniform across metal species.
-
-Most notably, N is preferentially retained by the galaxy over the other species. 
-Roughly \textbf{35\%} of N produced remains in the disk, as compared to \textbf{15\%} of O 
-%mm and \textbf{15\%} of 
-    or
-Fe, for example. This difference is entirely feedback driven, but 
-%mm a coincidence of our particular galaxy conditions. At our galaxy's metallicity, the IMF weighted production of N occurs entirely
-    determined by the chosen metallicity of our galaxy. At this metallicity, N is 
-    produced only 
-in the stellar winds of stars between 8 and 10 M$_{\odot}$, with little to no production in supernovae.
-The rest of the species either have very little stellar wind production, are produced solely in supernovae, or have similar production levels between both supernovae and stellar winds (like O, for example).
-The typically lower injection energies of N into the galaxy compared to the SN
-%mm injected 
-   produced
-elements means N is preferentially retained within the ISM, and not as effectively ejected through outflows.
-In truth, the stars that produce N do eventually explode as supernovae, sweeping up some fraction of the wind produced N into outflows.
-However, clearly some of this N mixes more effectively within the ISM than the other metal species.
-How abundance variations like this evolve over longer timescales and with varying feedback physics is the subject of ongoing work.
-%mm (Emerick et. al. in prep.).
-
-\begin{figure*}
-\includegraphics[width=0.9\linewidth]{species_bar.png}\\
-\includegraphics[width=0.9\linewidth]{species_bar_disk.png}
-\caption{The fraction of each species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).}
-\label{fig:species_fractions}
-\end{figure*}
-
-The bottom panel illustrates where these metals are partitioned within the ISM of the galaxy at the end of the simulation time.
-The CNM contains roughly 50-60\% of each species, with the CNM and WNM together accounting for most of the metals in the galaxy.
-The WIM contains only $\sim$ 10\% of each species, with the HIM containing very little.
-This may be counterintuitive given
-that most metals are initially injected into the galaxy in either the WIM or HIM phases.
-However, the disk metals represent only a small fraction of the total metals produced.
-Much of the metals are effectively removed from the disk into the halo (see Section~\ref{sec:outflows}).
-It is apparent that the remaining metals quickly mix or cool into denser gas phases.
-
-\subsection{Stellar Abundances}
-\label{sec:stellar properties}
-\textbf{This section needs work.
-As per discussion with Keith and Kathryn, displaying abundance evolution like this is confusing and misleading.
-Switch to discussion of mass / abundance fraction evolution of individual specie(s).}
-We plot the $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ ratio for all star particles in our simulation that are ``alive'' in Figure~\ref{fig:stellar_abundance}.
-This represents stars that have not gone supernovae or have otherwise formed a compact object.
-Here, $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$, and the notation [X/Y] denotes the ratio of the abundance of species X over Y, relative to the solar value, or log([X/Y]) = log(X/Y) - log(X$_{\odot}$/Y$_{\odot}$).
-All stars are colored by their age.
-
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{alpha_over_fe_hist}
-\caption{The $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$
-diagram for all stars in our simulation, colored by their age. Here, we define $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$. Each histogram shows counts, normalized to the peak in each distribution.}
-\label{fig:stellar_abundance}
-\end{figure}
-
-As expected, there is a noticeable trend of stellar age with [Fe/H]; especially in our case as the overall iron abundance is gradually increasing, yet we do not have any accretion of primordial material.
-Interestingly, the few stars with the highest [Fe/H], between -3 and -2, are not the most recently formed; the most recent star formation is clustered around [Fe/H] between -3 and -4.
-
-We note the ``knee'' like feature at very low [Fe/H] is not the characteristic knee seen in $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ space, corresponding to the period when iron enrichment from SNIa begins to make a significant contribution to the galactic chemical evolution.
-This generally occurs after roughly 1 Gyr of stellar evolution, far longer than the \textbf{170} Myr simulated here.
-% The origin of this feature and the longer term chemical evolution of this galaxy will be investigated in a future work.
 
 \section{Discussion}
-\label{sec:discussion}
-
-\subsection{Comparison to Previous Work}
-\textbf{At the moment, doing a lot of this throughout paper. Not certain if I need an explicit, separate discussion here.}
-
-\subsection{Comparison to Observed Low Mass Dwarf Galaxies}
-\label{sec:observation}
-
-\subsubsection{Gas and Star Formation}
-\label{sec:gas_sf}
-
-The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted \ion{H}{1} surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, Tollerud2015, Sand2015}.
-However, the sample of isolated dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) law (left) for low mass galaxies, and the extended Schmidt law (ESL) (right) which has been shown recently to extend to low mass, low metallicity dwarf galaxies \citep{Roychowdhury2017}.
-We plot our galaxy every 1 Myr in these diagrams, showing the significant temporal variation in both spaces.
-Although these quantities are conceptually simple, due to how these values are measured observationally it is challenging to make a direct comparison to simulations, particularly in defining the geometric region to measure the surface densities.
-We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs following the procedure described in \citet{Roychowdhury2014}.
-We define $\Sigma_{\rm sfr} = \dot{M}_{*, \rm{10 Myr}} / A_{*, \rm{10 Myr}}$, where $\dot{M}_{*, \rm{10 Myr}}$ is the SFR measured over the preceding 10 Myr, and $A_{*, \rm{10 Myr}}$ is the disk defined out to the farthest star formed within the previous 10 Myr.
-Likewise, $\Sigma_{\rm gas} = M_{\rm gas, 10 Myr} / A_{*, \rm{10 Myr}}$, where M$_{\rm gas, 10 Myr}$ is the total gas mass within this defined disk.
-However, the total gas content cannot be determined observationally, particularly for low mass dwarf galaxies with a virtually unmeasurable H$_2$ content.
-Therefore, we present $\Sigma_{\rm gas}$ as measured directly in the simulations (green/purple points) and the observational equivalent, or $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He, and where there is no correction for H$_2$ (plasma points).
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution}
-\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution}
-\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every 1 Myr for the total gas surface density computed from the simulations, and an observational analog derived using the \ion{H}{1} content (see text for details).}
-\label{fig:KS}
-\end{figure*}
-
-In both panels, we also include recent observational constraints from these relationships. For the KS relationship we include the fits from \citet{Shi2011} with 1$\sigma$ errors (black), the fits 
-%mm
-   and errors 
-from \citet{Roychowdhury2014} (blue), and the individual points 
-%mm
-   (black squares) 
-from the recent SHIELD sample \citep{Teich2016}, while for the ESL relationship we include only the fit and 1$\sigma$ errors (black) from \citet{Shi2011}, which have been shown to match well for dwarf galaxies at these surface densities \citep{Roychowdhury2017}.
-In both relationships our simulations fit well around the median observed fit, spanning the 1 $\sigma$ variations about the mean.
-
-This is a remarkable result.
-In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
-It is non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, but signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
-This result is consistent with recent galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics (\textit{relevant citations})
-%mm 
-   but also with the demonstration by \citet{Li2005} that the KS law can be reproduced 
-   by gravitation acting on an isothermal disk, which was argued to demonstrate that 
-   this represents the basic physics at work.
-
-The molecular gas content of low mass dwarf galaxies like this is generally considered 
-to be small (references).
-Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas fractions anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
-As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.17--0.20, within this range, but significantly exceeding the few percent often found in models.
-This means ignoring the H$_2$ component of our galaxies leads to an average shift of 0.24 dex to the right in the KS relationship, and 0.24 dex right and down in the ESL.
-This does not lead to a significant disagreement with the observed relationships, but would constitute a quantitative change to the observed fits if our $f_{\rm H_2}$ is robust for low mass, low metallicity dwarf galaxies.
-However,
-%mm
-    we do not fully resolve the turbulent density perturbations in which 
-    H$_2$ forms most efficiently \citep{Glover2007}, and
-our non-equilibrium chemical model for H$_2$ formation and destruction is relatively simple: it does not account for C and O chemistry, a detailed dust model, or cosmic rays, all of which may significantly affect $f_{\rm H_2}$.
-
-Simulations by \citet{Hu2016} and \citet{Hu2017}, which contain a more detailed non-equilibrium chemistry model than included here, give very low $f_{\rm H_2}$, below $10^{-4}$ for their full feedback simulations; even their simulations without any radiation feedback only reach $f_{\rm H_2} \sim 2 \times 10^{-3}$.
-However, their simulated dwarf galaxies are more massive ($M_{\rm vir} = 10^{10} M_{\odot}$) and higher metallicity ($Z = 0.1 Z_{\odot}$) than those examined here.
-This disagreement warrants additional investigation, particularly as making predictions for the H$_2$ content of low mass dwarf galaxies is valuable.
-We do note that there is some possible observational evidence for higher than expected ($\sim 15$ \%) molecular fractions \citep{Schruba2017}, though this still remains highly uncertain.
-
-\subsubsection{Metal Retention}
-\label{sec:obs_metals}
-
-%mm Unfortunately, these high resolution simulations are not (yet) run
-    The simulations presented here have not yet been run
-for the 
-%mm $\sim$ Gyr 
-    gigayear
-timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$. However, we can compare to a key observable, the 
-%mm ejection / 
-retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from stellar evolution models based on the galaxy's star formation history.
-This can be done readily with Milky Way dSph's, whose stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
-However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
-
-Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, and close enough to the Milky Way to conduct this experiment.
-Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, roughly \textbf{95\%} of the tracked metals produced during the simulation no longer reside within the galaxy's disk.
-At the end of our simulation, we agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
-Although more than half of these metals are expected to
-%mm
-   eventually
-be re-accreted \citep{Angles-Alcazar2017}, it is still possible that, at %mm any moment, 
-   the early times we have simulated,
-most of the metals that have been produced 
-%mm lie 
-    remain
-outside the galaxy disk. We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.
-
-It is interesting to consider 
-%mm where these metals lie outside of the galaxy's disk, 
-    whether ejected metals in our model reside 
-in the CGM or have been ejected into the IGM, and their eventual fate.
-While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of a $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero $\sim$ 60\% of ejected gas is recycled, while 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
-In our case, no metals have been ejected beyond the virial radius; this is not surprising however, given that metals ejected beyond the halo would need to travel with an average velocity of 150 km s$^{-1}$ for the entirety of our simulation time.
-We find \textbf{32\%} of all metals lie within 1 kpc of the center of our galaxy, \textbf{75\%} within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and only \textbf{10\%} outside $R_{\rm vir}$.
-Over time, the re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
-Recycling of metal enriched gas could be a significant
-%mm source 
-    driver
-of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) returns.
-Unfortunately, we cannot yet speak to how this gas evolves over time, but will investigate this in future work with our feedback model.
-
-\subsection{Missing Physics}
-Although we include detailed physics in our simulations, there remains additional physics that may be relevant.These are discussed below.
-
-\subsubsection{Full Stellar Wind Model}
-\label{sec:stellar winds discussion}
-As discussed previously, our stellar wind model significantly reduces the injected wind velocity from $\sim$1000 km s$^{-1}$ to 1 km s$^{-1}$.
-Although our model is capable of generating realistic stellar winds with temperature profiles and radial evolution comparable to those expected from analytic calculations \citep{Weaver1977}, the hot, fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
-When considered in isolation, stellar winds are an important source of pre-SN feedback and do dramatically influence the dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
-However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or GMCs \citep{Dale2014}.
-They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
-Although they likely have minimal dynamical importance, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.
-
-%old comment: (need to ref or back up this claim: see Dale et al.
-2014 for individual clouds, while the right panel of Fig 2 in Shull \& Saken 1995 shows that the integrated wind energy from a cluster is about 10\% that of the supernovae -M).
-
-\subsubsection{Cosmic Rays and Magnetic Fields}
-Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017} and simulations of both isolated \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017} and cosmological galaxies \citep{SalemBryanHummels}.
-These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows with different phases and velocities than those driven through stellar feedback alone \citep{SalemBryanCorlies}.
-Modeling cosmic rays is challenging, however, as they encompass a wide range of energies (give range), with significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
-Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy.
-In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM.
-Modeling cosmic ray feedback completely requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena.
-Finally, including MHD presents additional difficulties in untangling the effects each individual feedback mechanism on galaxy chemodynamics.
-
-We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested.
-Mechanically, including cosmic ray feedback in our model is trivial.
-However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to a later work.
-
-\subsection{Detailed Dust Model}
-\textbf{Should we discuss this? If so I definitely need more info and references - AE}.
-The dust content of our galaxy is modeled only approximately, scaling with the cell-to-cell variations in gas metallicity.
-Explicitly following the dust content in our galaxy, even crudely, could introduce significant variations in local cooling and heating rates.
-Accounting for metals trapped in a dust phase would produce additional variations in the cooling rates and potentially changes to the galactic chemodynamical evolution.
-
-\subsection{Detailed Stellar Evolution and Binary Stars}
-\textbf{Definitely a question that comes up a lot whenever I say our simulations are star-by-star and detailed (as in ``but what about binary stars''?).
-Do we need to discuss this here as a quick paragraph about how it would affect feedback properties (namely radiation and different stellar lifetimes)?} \citep{Ma2016-binary}
 
 \section{Conclusion}
-\textbf{You can ignore this for now, I'm saving it after the first iteration (AE)}
-We present a new method for simulating the evolution of low mass galaxies with detailed feedback and chemical enrichment as traced through individual star particles.
-This model follows multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia supernovae, ionizing radiation followed through radiative transfer, photoelectric heating, and LW radiation.
-This is in addition to the detailed cooling, heating, and chemistry followed through Grackle, including a self-consistent model for gas self-shielding from the metagalactic UVB.
 
-In this work, we presented the initial results of these methods applied to the evolution of an isolated, low mass dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
+\acknowledgments
+Acknowledgments.
 
-In future works we will investigate in detail the role each individual feedback process has in governing the chemodynamical evolution of isolated, low mass dwarf galaxies.
-These simulations will demonstrate how feedback affects metal mixing within the ISM and the enrichment of future stellar populations, in addition to how feedback influence metal ejection into, and possibly beyond, the galaxy's dark matter halo.
-\textbf{will finish at very end}
-
-%\bibliographystyle{apj}
-%\bibliography{msbib}
+\facilities{Yeti, CCA cluster, Stampede, Pleiades} 
+\software{Numpy, Enzo, yt, astropy}
 
@@
 \appendix
-
-\section{Gas Phases of the ISM}
-\label{appendix:phases}
-
-To aid in comparison to other works, we define our ISM phases here, as adopted from \citet{Draine2011} Table 1.3 and used consistently throughout this analysis.
-By construction, these phases are mutually exclusive.
-In the below, $f_{\rm H_2}$ is the molecular hydrogen fraction by abundance.
-
-\begin{enumerate}
-\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
-\item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
-\item Warm Neutral Medium (WNM): $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$
-\item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
-\item Molecular: \textbf{MAY CHANGE} $T < 10^2$, $f_{\rm H_2} > 0.5$
-\end{enumerate}
-
-\section{Stellar Radiation Properties}
-\label{appendix:radiation}
-We detail the radiation properties of our model stars as a function of stellar mass and metallicity, both of which are assigned directly from an IMF and from the local gas properties respectively.
-The stellar radiation properties are a determined from the OSTAR2002 grid \citep{Lanz2003} (or as integrated from an adjusted black body curve for stars off of the OSTAR2002 grid) given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Figure~\ref{fig:stellar radiation properties} we plot the ionizing photon luminosities for \ion{H}{1} (top left) and \ion{He}{1} (top right) for each star, the FUV (middle left) and LW (middle right) luminosities, and finally the \ion{H}{1} ionizing radiation photon energy (bottom left) and \ion{He}{1} ionizing photon energy (bottom right).
-We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
-This requires two factors for each radiation type, one for low mass and one for high mass stars.
-We use the following multiplicative factors to adjust the black body spectrum for \ion{H}{1} and \ion{He}{1} radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
-We do not find this adjustment to be necessary for the FUV and LW radiation bands.
-
-The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid.
-A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency dependent absorption cross section.
-We tested this approach using the frequency dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \texttt{http://www.pa.uky.edu/~verner/photo.html}} The black body approximation is accurate to within 5\%, yet substantially easier to compute on the fly as integrals over the black body spectrum can be expressed as infinite series that rapidly converge to high precision.
-Unlike the ionizing radiation, we assume constant FUV and LW band energies for each star, at 9.8 eV and 12.8 eV respectively.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.4\linewidth]{Q0}
-\includegraphics[width=0.4\linewidth]{Q1}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{L_FUV}
-\includegraphics[width=0.4\linewidth]{L_LW}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{E0}
-\includegraphics[width=0.4\linewidth]{E1}
-\caption{Radiation properties for our model stars. Note, we only track radiation from stars above
-8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
-\label{fig:stellar radiation properties}
-\end{figure}
-
-\section{Typical Gas Densities in Supernova Injection Regions}
-\label{appendix:supernova}
-
-Modeling supernova feedback with the injection of thermal energy alone can lead to rapid over cooling of the injected energy, and a significant underestimate of the effects of supernova feedback.
-Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time.
-However, physically consistent solutions have been employed \citep[e.g][]{Simpson2016} which inject a mixture of kinetic and thermal energy, whose ratio of kinetic to thermal energy injection depends on resolution and/or local gas density.
-This over cooling problem improves with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each supernova.
-We take advantage of our high ($\sim$ pc) scale resolution and employ a simple thermal energy injection model for our supernova feedback.
-Here we demonstrate how well this resolves our supernovae in the comparison simulation presented in this work.
-
-The left panel of Figure ~\ref{fig:supernova histogram} gives the distributions of the max (orange) and average (black) ISM number densities in the supernova injection regions for each supernovae in the simulations presented in this work.
-As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
-For most supernovae, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-supernova feedback included in our simulations.
-The right panel of Figure ~\ref{fig:supernova histogram} gives the fractional distribution of the calculated radius of pressure driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}, given as
-\[
-R_{\rm PDS} = 
-\begin{cases*}
-49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z $\le$ 0.01 \\
-18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z $\ge$ 0.01 \\
-\end{cases*}
-\]
-where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$.
-\citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the supernova explosion with thermal energy injection alone, assuming uniform density in the injection region.
-In practice, the injection region is never uniform.
-We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each supernova.
-As shown, a majority of supernovae are resolved (to the right of the 4.5$\Delta x$ line), but that up to 10\% are somewhat under-resolved.
-In general, these are supernova explosions from the most massive (i.e.
-most prompt) stars.
-We do not expect that resolving these supernovae will dramatically alter our results, but note that simulations presented in future work will examine lower mass galaxies at higher resolution than those presented here.
-In those, the supernovae are more resolved, but we note that using our feedback model at resolutions much less than 2 pc will require adopting a different injection mechanism.
-
-% We use a spherically symmetric thermal dump method of modelling supernova explosions.
-This is the simplest method possible, but can often result in rapid overcooling of the heated gas, effectively underestimating the effectiveness of supernova feedback.
-Solutions to this problem can often be ad hoc (e.g.
-briefly turning off cooling) in low resolution, large cosmological simulations.
-However, recent work has shown injecting some fraction of this thermal energy directly as kinetic energy or momentum alleviates this issue without sacrificing physical realism.
-However, it has been shown that simple thermal energy injection is sufficient for parsec scale (or better) resolutions, provided the supernova do not occur in very high density regions; if resolved, thermal injection converges with kinetic energy / momentum injection methods.
-Resolving these explosions with thermal energy injection alone depends ultimately on the grid resolution, background density and ISM structure, the background cooling/heating physics used, and the size and shape of the injection region.
-Here, we perform a resolution test of our thermal injection method over four uniform densities (0.1 \ccunit, 1.0 \ccunit, 10.0 \ccunit, and 100.0 \ccunit) for both a 8.0 \msun and 25.0 \msun star, comparing to both the analytic solution and results using kinetic energy injection from \citet{Simpson2015}.
-These results are presented in Figure~\ref{fig:supernova tests}.
-We note these are heavily idealized cases.
-In general in our simulations, pre-SN feedback from stellar winds and radiation will reduce the typical densities within which our supernova explosions occur.
-In addition, supernova will generally be clustered, meaning each SN will reducing the typical density for each subsequent SN in that region.
-In Figure~\ref{fig:supernova histogram} we plot a histogram of the typical peak and average gas densities in the 3 cell injection region of each supernova in the XXXX XXXXX simulation.
-As shown, some of the supernova explode in high density regions around 100 \ccunit and are likely under-resolved, but a majority will be resolved.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.4\linewidth]{sn_density_hist}
-\includegraphics[width=0.4\linewidth]{sn_radius_hist}
-\caption{Distribution of peak and average gas densities (left) in the injection region of each of the supernovae from the simulation.
-On the right, we give the distribution of the radius of the pressure driven snowplow phase for each supernova assuming a uniform medium at either the peak or average density in the injection region.
-The vertical lines give one and 4.5 cell widths.
-As shown, a fraction of these SN are certainly under resolved, with R$_{\rm PDS}$ less than a single cell size, but a majority are resolved.}
-\label{fig:supernova histogram}
-\end{figure}
-
-%\section{Stellar Wind Model}
-%\label{appendix:stellar winds}
-%
-% This is still probably a good idea to do at some point, but save for if/when
-% we have a paper using full stellar winds where this matters - AE (Jul. 19 2017)
-%
-%Discuss wind properties and evolution in a hand full of isolated star runs (don't need to do a resolution study...
-kinda) and compare to Weaver et.
-al.
-1977 analytic results.
-Really we won't resolve the winds at high densities, but that is OK...
-as long as the wind bubbles are > 3*dx (the injection size) we are generally going to be fine...
-aka as long as the SN explosion goes off in wind bubble gas and not dense ISM that shouldn't be there..
-
-\section{Cooling Rates}
-\label{appendix:cooling}
-Figure ~\ref{fig:cooling} shows the combined primordial and metal line cooling (dashed) and heating (dotted) rates at three characteristic densities for Z = 0.01 Z$_{\odot}$, closer to the metallicities of our fiducial set of dwarf galaxy simulations (Emerick et.
-al.
-in prep).
-The solid lines give the absolute value of the net cooling rate, which more clearly indicates the regime at low temperatures where heating dominates.
-The curve as shown includes the z = 0 \citet{HM2012} metagalactic UVB.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_curve}
-\caption{The total heating and cooling rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic background as modeled in \textsc{Cloudy}.
-The absolute value of the net cooling rate is shown with solid lines.}
-\label{fig:cooling}
-\end{figure}
-
-We note that this cooling curve shows only an approximation of the local cooling and heating rates used in the simulations for two reasons.
-First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal line cooling and heating rates are used.
-The actual primordial heating and cooling rates are calculated self-consistently using the non-equilibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}.
-However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations.
-Second, this figure ignores the contributions to the heating rate from the variable interstellar radiation field, namely the stellar contribution to photoelectric heating, heating from LW dissociation, and ionization heating.
-We describe how we obtain the metal line cooling rates below and quantify the change in using these updated tables.
-%Therefore, the heating rates shown are approximate lower limits to the true heating experienced by any given cell in the simulation.
-
-The cooling curves used in this work corrects a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with self-shielding approximations.
-Previous work in \citet{Hu2017} details this inconsistency.
-In short, adopting tabulated metal cooling rates computed under the assumption of an optically thin UV background overestimates the electron fraction in regimes where self-shielding is important, about $-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$, leading to an overestimation of the metal cooling rates.
-We demonstrate this effect in Figure~\ref{fig:cooling comparison}, which gives |cooling - heating| for our full model at $Z = 0.1~Z_{\odot}$ (black) as compared to a model using the optically thin metal line cooling rates (orange) at a range of densities.
-The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
-In low temperature regions, this can significantly shift the inferred equilibrium temperature.
-
-The cooling curve shown in Figure~\ref{fig:cooling} avoids this discrepancy using re-computed metal line cooling tables.
-We have made these tables publicly available in the main distribution of \texttt{Grackle}.
-For densities where self-shielding is important, we computed \texttt{Cloudy} models of 1D clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
-In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud.
-We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UVB.
-These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}.
-In computing these tables we had to include the CR ionization that dominates in optically thick clouds.
-Without this effect, \texttt{Cloudy} becomes unstable in entirely neutral regions.
-We adopted a CR ionization rate of 10\% the MW value, though we note varying this from 1\% to 100\% the MW value did not have an effect on the extracted metal line cooling rates.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
-\caption{The absolute value of the net cooling rate (|cooling - heating|) in two models that account for self-shielding of primordial gas against a metagalactic UV background.
-Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the un-corrected (i.e.
-optically thin) metal line cooling rates.
-The regimes where heating dominates are plotted with dashed lines for clarity.}
-\label{fig:cooling comparison}
-\end{figure}
-
-\section{Resolution Study}
-\label{appendix:resolution study}
-Insert some light resolution study details here.
-Ultimately this will be somewhat difficult as we need to go into how this is challenging since star formation criteria will change as resolution scales.
-%\section{Pre-SN Feedback with and without radiation}
-
-%\section{Code}
-%(likely just do this as a short blurb in acknowledgements)
-
-%A one-zone chemical evolution and feedback model was constructed to provide rapid testing and examination of the feedback and yield properties of each of our stars in our model.
-This code is publically available at https://github.com/aemerick/onez.
-In the simplest case, one can generate a series of star particles and examine their resulting properties, including wind and supernova yields, as a function of mass and metallicity.
-Included also are more complicated examples of running the full one-zone model.
-Support currently only exists for running in a non-cosmological mode with a constant star formation rate.
-In addition, this one-zone model uses star-by-star modelling and becomes extremely inefficient at large particle counts.
-Future develop will better optimize this code, allow for variable input or evolving star formation rates, cosmological evolution, and parallelism.
-
-%\appendix
-%\section{appendix section}
+\section{appendix section}
 

### 2017-12-20 main.tex
Update on Overleaf.

--- 2017-12-05 main.tex
@@
 Specifically, simulations presented here were conducted at changeset 445de816fd99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
-We compute the total gravitational potential from gas self-gravity, stars, and static background dark matter potential.
-The collisionless star particles are evolved with a particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.
+We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}.
+Self-gravity is computed with a multigrid Poisson solver.
+The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.
 
@@
 The use of a pressure floor is common in galaxy scale simulations with limited dynamic range.
-(\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out.
+%(\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out.
 Leave it in?})
@@
 
-Metal line cooling is modeled using pre-computed \texttt{Cloudy}\footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
+As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
 As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
@@
 \label{sec:star formation}
-In order to resolve individual star formation on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
+In order to resolve individual star formation events on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
 Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
-Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively.
+Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively \textbf{justify choices}.
 We limit the fraction of a cell's gas mass that is converted into stars by requiring $M_{\rm gas} > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and $M_{\rm max,*}$ is the maximum star mass (100 M$_{\odot}$).
@@
 In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
-If it does, we random sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$.
+If it does, we randomly sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$.
 We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and maximum stellar mass of 100 M$_{\odot}$.
-
-Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
+Our lower limit on stellar masses ensures that we are able to both directly track all particles that participate in some way to feedback and metal enrichment, and follow longer lived start particles, while reducing the computational expense of following many low mass stars that have no dynamical impact on the galaxy evolution.
+100 M$_{\odot}$ is a reasonable upper limit on the most massive star \textbf{sounds weak}.
+
+Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a \textbf{1~km~s$^{-1}$ velocity dispersion - justify!}.
 Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
@@
 We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth.
-Although we can follow an arbitrary number of metal species, practical considerations
-%mm 
-   of memory use 
-prevent this in any given simulation.
+Although we can follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation.
 We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
@@
 In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
-Stars above this mass
-%mm
-    are assumed to
-eject their stellar yields via 
-%mm ``massive" 
-   line-driven
-stellar winds at a constant mass loss rate throughout their lifetime
-%mm ,
-  (neglecting Wolf-Rayet and luminous blue variable phases),
-ending their lives as a core-collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics).
+Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics).
 Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
@@
 Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
-Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no
-%mm
-    further
-mass or energy ejection.
+Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass or energy ejection.
 
@@
 We use the Type Ia supernova yields given in \citet{Thielemann1986}, adopting a Type Ia supernova model as discussed in Section~\ref{sec:Type Ia}.
-%mm
-    We emphasize that we only track Type Ia supernovae occurring within the 
-    population of stars formed in this model, neglecting supernovae from any 
-    pre-existing population.
+We emphasize that we only track Type Ia supernovae occurring within the population of stars formed in this model, neglecting supernovae from any pre-existing population.
 
@@
 Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from supernovae and radiation, stellar winds are potentially important sources of pre-supernova feedback.
-%mm For both AGB winds and massive stellar winds
-    In models that include feedback energy from stellar winds from both AGB and 
-    massive stars, 
-we inject the feedback energy in a three-cell radius spherical region centered on the emitting star particle, assuming full thermalization of the wind kinetic energy.
+In models that include feedback energy from stellar winds from both AGB and  massive stars, we inject the feedback energy in a three-cell radius spherical region centered on the emitting star particle, assuming full thermalization of the wind kinetic energy.
 The total injected energy in timestep $\Delta t$ is therefore $E_{\rm wind} = \dot{M}\Delta t \times v^2_{\rm wind} + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass ($\dot{M}\Delta t$) given the star's interpolated $T_{\rm eff}$.
 We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells.
+
 We assume constant mass loss rates for all winds as set by the yields tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars). 
@@
 We continue to track any remaining stellar mass after the supernovae as a massive ``remnant" tracer particle.
-In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment through X-ray binaries and neutron-star-neutron-star merger events which, while rare, could be important in long term galaxy evolution.
-\textbf{Should I reference a few recent hydro sims that included these feedback sources? - AE  
-%mm
-Can't hurt if they are ready to hand. Not high priority, though. M-M}
+In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment through X-ray binaries and neutron-star-neutron-star merger events which, while rare, could be important in long term galaxy evolution \citep[e.x.][]{Artale2015}.
 
@@
 We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors.
+\textbf{This is the most self-consistent model for Type 1a supernovae in galaxy scale simulations.
+(worth mentioning?
+maybe softer version of this?)} We note however that for the low SFR's in our isolated dwarf galaxy simulations, the first SNIa only appears after a few hundred Myr of simulation time.
+For example, by the end of the simulation presented here (XXX Myr), only XXX have gone off.
 At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
@@
 %\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):} 
-The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope and normalization are observables, and $\eta$ the fraction of stars which can form SN Ia progenitors that \textit{will} explode as a SN Ia within a Hubble time.
-The value for $\eta$ depends on the normalization of the DTD (an observable), as well as one's choice of IMF and mass range of potential SN Ia progenitors (as given above).
-This fraction is given as
+The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope ($\beta$) and normalization ($N_{\rm 1a}/M_{\rm SF}$) are observables.
+The latter represents the number of Type 1a supernova per mass of star formation.
+By assuming an IMF, one can write down the fraction ($\eta$) of stars capable of forming a SNIa progenitor that \textit{will} explode within a Hubble time.
+This is given as
 \begin{equation}
@@
 \end{equation}
-where $N_{\rm Ia}/M_{\rm SF}$ is the DTD normalization, which represents the fraction of stars that form SN Ia progenitors, $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF ($dN/dm$), and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
+where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF ($dN/dm$), and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
 The DTD slope, $\beta$, is of order unity, with typical values between 1.0 and 1.2 (see \citet{Maoz2014} for a recent review).
-$N_{\rm Ia}/M_{\rm SF}$ represents the number of SN Ia per mass of star formation; this can be derived by taking observed values of the SNIa rate and integrating over a Hubble time.
+$N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the SNIa rate and integrating over a Hubble time.
 Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
@@
 
-Finally, the probability a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor is taken as
+Finally, we can normalize $\Psi(t)$ to give the probability per unit time ($\dot{P}(t)$) that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor.
+Integrating this gives the total probability at any given time as,
 
 \begin{equation}
-P(t) = \dot{P}(t)dt = \eta \frac{ t^{-\beta}}{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau} dt,
+P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
 \end{equation}
-
-where $t_{\rm o}$ is the formation time of the WD and the denominator normalizes the total probability to $\eta$.
+where $t_{\rm o}$ is the formation time of the WD and the leading term in the R.H.S properly normalizes the total probability over a Hubble time to $\eta$.
 This naturally accounts for both a prompt and delayed Type Ia supernova population in our simulations.
-In practice, we invert the cumulative probability distribution to assign an exact time at which a given WD will explode, rather than making a random number draw for every WD particle every time step as $\eta$ is small.
-
-\subsubsection{Ionizing Radiation}
+In practice, we invert the cumulative probability function to assign an exact time at which a given WD will explode using only a single random number draw, rather than sampling the probability distribution for each WD particle at every time step.
+
+\subsubsection{Ionizing Radiation from Discrete Sources}
 \label{sec:ionizing radiation}
-Radiation feedback (ionization, ionization heating, and radiation pressure) is an important source of pre-SN feedback in galaxies.
+Radiation feedback (ionization, ionization heating, and radiation pressure) is an important source of feedback in galaxies.
 \ion{H}{2} regions carved out by stellar radiation change the ISM structure where SNe eventually explode, generally increasing their dynamical importance.
 However, when accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily through channels carved through dense clouds.
-Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with limited application in full radiation hydrodynamics simulations \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
+Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
 As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through ray tracing methods described below.
-%mm In this particular work, we 
-  We here
-use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).
+% AE (no longer the case): We here use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).
 
@@
 We follow \ion{H}{1} and \ion{He}{1} ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
-Radiation pressure is expected to be an important source of feedback only in more massive galaxies; we explore this point further in this work.
+% AE: (removed) Radiation pressure is expected to be an important source of feedback only in more massive galaxies; we explore this point further in this work.
 
@@
 In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).
-\citet{Dale2012} demonstrated that uncertainties on order of a few in the ionizing radiation rates are not significant in giant molecular cloud (GMC) scale simulations.
+
+%AE (taking this out...
+looked into more detail in paper and they argue this, but frankly I do not see how they reach this conclusion from their Appendix plots): \citet{Dale2012} demonstrated that uncertainties on the order of a few in the ionizing radiation rates are not significant in giant molecular cloud (GMC) scale simulations.
 %Generally, the ionizing fluxes from high temperature black bodies underestimate the OSTAR2002 flux, and lower temperature black bodies overestimate the flux by a factor of 2-5 and 10-1000 respectively.
@@
 Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017}.
-Due to these uncertainties, and given that we focus on low-metallicity dwarf galaxies with low dust content, we ignore this effect.
-
-%mm \subsubsection{Diffusive Heating}
+Due to these uncertainties, and given that our dwarf galaxy has a low dust content (and therefore a low IR opacity), we ignore this effect.
+\textbf{Greg referenced Dong Zheng in comments but I could not find anything for this}
+
 \subsubsection{Diffuse  Heating}
 \label{sec:diffusive heating}
-We include two forms of 
-%mm diffusive 
-   diffuse
-heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars.
+We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars.
 Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
@@
 
-%mm We assume the FUV luminosity for each our stars is everywhere optically thin. The 
-     We assume the galaxy is mostly optically thin to stellar FUV.  Therefore, the stellar
-%
-FUV flux in each cell is summed over the contributions from each star
-%mm 
-   with a local approximation to the attenuation within dense cells applied. 
-We parameterize the local photoelectric heating rate \citep{BakesTielens1994,Wolfire2003,Bergin2004}
+We assume the galaxy is mostly optically thin to stellar FUV and use only local approximations for shielding.
+We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
 \begin{equation}
@@
 We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$.
-We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5\times 10^{8} \mbox{ M_{\odot}}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc.
+We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5\times 10^{8}~M_{\odot}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc.
 This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc.
@@
 Following the initialization procedure of \citet{Hu2017}, we use artificial supernova driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
-This additionally prevents an otherwise uniform collapse of the gas disk
-%mm
-   at the beginning of the simulation.
+This additionally prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
 These supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
@@
 These artificial supernovae do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
-%mm
-    We do not include any other effects from the stellar population that would have caused these   
-    supernovae.
+We note that this initial driving is somewhat ad hoc in that do not include any other effects from the stellar population that would have caused these supernovae.
 
@@
 \label{sec:results}
-We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:star formation}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first \textbf{200 Myr} after the first star forms.
+We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first \textbf{350 Myr} after the first star forms.
+This occurs 43 Myr after initialization.
 Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.\footnote{All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset \textbf{changeset number}.}
+
+Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle formed, and the galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy.
+ISM properties are calculated considering only the gas contained within the disk of the galaxy.
 
@@
 \includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
-\caption{\textbf{Draft figure - need to pretty up and finalize fields and times.} Edge-on views of our dwarf galaxy at four different times in its evolution, beginning with the time at first star formation and ending at XXX Myr.
+\caption{ \textbf{need to adjust overlapping labels} Edge-on views of our dwarf galaxy at four different times in its evolution, separated by 100~Myr, beginning with the time at first star formation and ending at 300 Myr.
 Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and O column density (fourth row).
-Additionally, each individual main sequence star particle is shown in the number density projections as a single black dot.}
+Each individual main sequence star particle is shown in the number density projections as a single black dot.
+\textbf{use H2 in bottom panel instead}}
 \label{fig:panel_x}
@@
 
-The gas disk is thin outside the stellar radius of our galaxy, but is resolved at all radii.
-In Figure~\ref{fig:scale_height} we plot the scale height of our gas disk as a function of radius at the initial conditions (blue), just before first star formation (orange), and averaged over the last 20 Myr of simulation time (black).
-At the outer edges of the disk, beyond regions of ongoing star formation, the scale height is $\sim 15$ pc, comparable to the scale height in the inner 200 pc prior to first star formation.
-Though small, both of these scale heights are resolved at our maximum resolution, 1.8 pc; we note that without feedback, our gas disk would continue to cool and collapse to an uresolved, razor thin disk.
-For the majority of the galaxy, stellar feedback sets the scale height.
-Heating, from both stellar radiation and supernovae, lifts gas above the midplane and generating scale heights between 40 and 100 pc within the half light radius.
-Effective galactic winds have carved out most of the gas within the inner 40 pc, distributing it somewhat smoothly above/below the midplane, leading to the significantly larger scale heights.
-This is made clear in the density panels if Fig~\ref{fig:panel_x}, where regions of active star formation show a general lack of the dense, cool gas that creates the smaller scale heights at larger radii.
+The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
+This figure shows the 30~Myr time averaged scale height of all gas in the disk throughout the simulated time.
+Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights between 50--200~pc.
+Although the disk remains thin beyond the stellar radius of our galaxy, it is resolved at all radii.
+The low central scale heights at 100 Myr (dashed, purple) compared to those at 200-300~pc are due to a general lack of gas in this central region from the initial burst of star formation.
+This is clear in the density panels of Fig~\ref{fig:panel_x}.
+Although the cold disk is thin, this property is currently unconstrained in galaxies of this mass due to low ($\sim$ 100 pc or worse) spatial resolution \citep[e.g.][]{Bernstein-Cooper2014}.
 %We additionally compute the mass weighted height of the disk, defined as $H = (\sum{Mz^2}/\sum{M})^{1/2}$, where the summation is over each gas cell, as a function of radius (not shown here).
@@
 \includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
-\caption{\textbf{Draft figure - need to pretty up and finalize fields}. Same as Figure~\ref{fig:panel_x}, but showing face-on projections/slices.}
+\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on projections/slices. \textbf{use H2 in bottom panel instead}}
 \label{fig:panel_z}
@@
 The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work.
-This is exciting given recent \citep[e.g.][]{Zheng2017} and ongoing \citep{Zheng2017HST} observational observational work examining the disk-halo interface in nearby galaxies.
+% AE (left out): This is exciting given recent \citep[e.g.][]{Zheng2017} and ongoing \citep{Zheng2017HST} observational observational work examining the disk-halo interface in nearby galaxies.
 
@@
 \includegraphics[width=0.975\linewidth]{scale_height}
-\caption{The average gas disk scale height as a function of radius for the last 20 Myr of simulation time (black) as compared to the uniform initial conditions (blue) and the scale height profile immediately before the first star formed (orange).}
+\caption{The 30~Myr time average gas disk scale height as a function of radius at various times throughout the simulation.}
 \label{fig:scale_height}
@@
 We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.
-(By the end of the simulation, there have been no Type Ia supernovae.) Within the first 40 Myr of evolution the SFR rises quickly to between $2-4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, and remains at this level with fluctuations of about a factor of 2 or less.
-Averaging over the entire simulation time since the first star was formed, we obtain  $<\rm{SFR}> = 2.34 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
-The star formation rate of our model galaxy as compared to observed galaxies is discussed further in Section~\ref{sec:observation}.
+(By the end of the simulation, there have \textbf{only been XX Type 1a supernovae}.) Within the first 40 Myr of evolution the SFR rises quickly to between $2--4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly this level for 100 Myr, and drops to an average of about $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ for the remainder of the simulation, with large fluctuations.
+The SNR tracks the SFR with a time delay, capturing the rough rule of thumb that there is one core collapse supernovae per 100 M$_{\odot}$ of star formation.
+Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.33 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
+We note the discontinuity in SFR near 340~Myr represents a 10~Myr period without any star formation.
+We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.
 
@@
 By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about \textbf{$6 \times 10^5$ M$_{\odot}$, or roughly 17\%} of the total mass in the galaxy's disk.
-The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases to about \textbf{25\%} as the total amount of mass in the disk decreases through feedback driven winds.
-Small drops in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback.
+The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction doubles over time to roughly 35\%.
+This is because the total amount of mass in the disk decreases through feedback driven winds, but the H$_2$ is preferentially retained.
+Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback.
 Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
 The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
+\textbf{Is it worth also plotting the non-luminous stellar masses here?
+The total mass in WD's and other SN remnants?
+This mass is roughly half of the mass of luminous stars at the end of the simulation.}
 
@@
 Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
-%mm \textbf{too strong of a claim?}. [No, it's quite true: you just need a cooling curve balanced against diffuse and SN heating.] 
 We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
+We emphasize that the molecular ISM phase is defined as all regions with f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content as decoupled from the rest of the gas.
 See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-Each of these exist in our simulations, and are regulated by the complex interplay between
-%mm
-   cooling, 
-turbulence, self-gravity, and 
-%mm 
-    diffuse and shock heating from 
-stellar feedback throughout the galaxy's evolution. Here we discuss the phase properties of the gas throughout the simulation box and within the ISM of our dwarf galaxy.
-
-Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas in the simulation domain, averaged over the final 50 Myr of simulation time.
+Each of these exist in our simulations, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and diffuse and shock heating from stellar feedback throughout the galaxy's evolution.
+Here we discuss the phase properties of the gas within the inner halo of our dwarf galaxy.
+
+Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the final 50 Myr of simulation time.
 One can readily identify the two most massive regions of gas in the simulation, a low density, warm phase produced through ionization and supernovae heating, and a cold, high density phase which makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
-\textbf{not completely sure what to talk about here for the diagram}
+Several notable features of the phase diagram include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
+We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
+The boxed regime in the lower right corner shows our star formation density and temperature threshold.
+Gas in this regime is rapidly consumed by star formation and subsequent feedback.
+Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does show up in this time average.
+We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work.
+\textbf{is last bit on CR heating and SF gas OK?}
 
@@
 Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few.
+\textbf{Note to look into this / discuss a little further since it is different than previous sims}
 
@@
 
-The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields 
-%mm 
-   both as expected from stellar motions in our own galaxy \citep{Parravano2003},
-   and in models including radiation \citep[e.g.][]{Hu2017}. 
-This is particularly not surprising in our low SFR regime, where there can be large fluctuations over time 
-%mm in proximity to a massive, radiating star. 
-    as individual massive stars form, move about, and evolve.
-In Figure~\ref{fig:ISRF} we present 
-%mm 1D volume-
-    azimuthally averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time. The top panel shows 
-%mm the average value of 
-$G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sect.~\ref{sec:diffusive heating}).
-(The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.)
-%mm The shaded region gives the minimum and maximum value of $G_{\rm o}$ in the sampled time range. [redundant with caption] 
-%mm As shown, regions typically experience  
-    This shows that any given point experiences
-fluctuations in the ISRF of an order of magnitude.
-Interestingly, the central 200 pc does not contain the peak of the ISRF in the galaxy.
-This is likely a transient property, however, and is a by-product of the inside-out star formation of this dwarf galaxy.
-By the end of the simulation the feedback from stars produced in the central region has reduced the SFR compared to outer parts of the galaxy.
-The latter is thus host to more radiating young stars.
+The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}.
+This is particularly not surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
+In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time.
+The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
+The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.
+Interestingly, the averaged profile appears nearly flat for most of the disk, with an increase at higher radii due to more recently formed stars.
+However, the ISRF varies significantly over time, fluctuating by an order of magnitude or more at any given radius.
+\textbf{Note to remember to discuss: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e.
+how does this compare to a uniform or 1D radial profile).
+G$_{eff}$ is convolved with local density and temperature variations, and is thus a bit harder to parse / interpret.
+Though possibly I should show both?}
 
@@
 \caption{
-%mm 1D radial
-    Azimuthally averaged radial 
-profiles of the ISRF in our galaxy in three different bands, time-averaged over the final 50 Myr of simulation time.
+Azimuthally averaged radial profiles of the ISRF in our galaxy in three different bands, time-averaged over the final 50 Myr of simulation time.
 The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
@@
 
-The bottom panel gives the ionizing photon fluxes for \ion{H}{1} and \ion{He}{1} from %mm ionizing photons from the 
-stellar radiation 
-%mm \texttt{only}.
-   {\em only}. 
+The bottom panel gives the ionizing photon fluxes for \ion{H}{1} and \ion{He}{1} from stellar radiation {\em only}.
 Since these fields are tracked directly using ray-tracing radiative transfer, the profiles encode information about local attenuation of these photons from dense, neutral gas.
 This is the main driver of the differences between these fields and $G_{\rm o}$.
-%mm In addition, we only show the average line and shade to the maximum value at any given position, since the minimum value reaches zero at all radii at some point over the 50 Myr examined.
-As shown, this causes the profile to
-   The ionizing fields
-vary much more dramatically at all radii.
-However, the same general trend is preserved of less radiation in the inner 200 pc than in the region between 200 and 400 pc, and an order of magnitude or more fluctuation at all radii.
-The rapid drop off beyond 400 pc is due to the rapid attenuation of ionizing photons by the cold gas at large radii (see Figure~\ref{fig:panel_x}).
+The ionizing fields vary much more dramatically at all radii, \textbf{need to figure out how to plot these.
+median / average mean very different things.}
 
@@
 However, the local variations for individual regions can be much larger than is illustrated in these profiles.
-In Figure~\ref{fig:ISRF_2D} we present %mm a 2D profile of $G_{\rm o}$ averaged
-    the full distribution of $G_{\rm o}$ over the final 50 Myr of the simulation time, which effectively captures the large spikes in local ISRF from recent star forming regions.
-The azimuthally averaged profiles accurately capture the averaged heating and ionizing effects of the ISRF in our galaxy, which helps reduce star formation by increasing the thermal pressure support and equilibrium temperature of the ISM, yet it is the spikes that act as important local feedback to shut off star formation in dense, collapsing regions that satisfy our star formation criteria.
-This point will be examined in more detail in future work with comparison simulations using different feedback processes.
+In Figure~\ref{fig:ISRF_2D} we present the full distribution of $G_{\rm o}$ at the end of the simulation time.
+This more effectively captures the large spikes in local ISRF from young, massive stars.
+The azimuthally averaged profiles capture the averaged heating and ionizing effects of the ISRF in our galaxy.
+This helps reduce star formation by increasing the thermal pressure support and equilibrium temperature of the ISM.
+However, it is the spikes that act as important local feedback to shut off star formation in dense, collapsing regions that satisfy our star formation criteria.
 %mm (Emerick et. al. in prep).  [I'd only insert the reference when there is an actual astro-ph number to support it.]
@@
 
-Recent cosmological simulations of dwarf galaxies with 
-%mm detailed 
-feedback over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors on order of 100--1000 \citep{Muratov2015}.
+The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors on order of 100--1000 \citep{Muratov2015}.
 However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
@@
 The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time.
-This quickly declines towards larger radii, however, with effectively zero outflow past the virial radius.
+This quickly declines towards larger radii, however, with \textbf{check this effectively zero outflow past the virial radius}.
 \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift.
@@
 
+Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
+This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Angles-Alcazar2017,Muratov2017}.
+The right hand panel of Figure~\ref{fig:mass_outflow} gives the metal mass loading factor over time for our dwarf galaxy, considering only the new metals produced by the star particles.
+Metal mass loading factor is defined as
+\begin{equation}
+\eta_{\rm metal} = \frac{\dot{M_{\rm metal}}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
+\end{equation}
+where $\dot{M_{\rm metal}}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
+\textbf{compare mass loading here and in other works...
+check back to Muratov for these.
+also cite miao and drummond.} \citep{Li2017}
+
 % figure here of mass loading and mass outflow rates
@@
 \centering
-\includegraphics[width=0.45\linewidth]{total_mass_outflow}
-\includegraphics[width=0.45\linewidth]{total_mass_loading}
+\includegraphics[width=0.33\linewidth]{total_mass_outflow}
+\includegraphics[width=0.33\linewidth]{total_mass_loading}
+\includegraphics[width=0.33\linewidth]{metal_mass_loading}
 \caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
@@
 
-Detailed outflow properties, beyond outflow rates and mass loading factors, are important discriminators between the model dependent feedback physics included in galaxy simulations. 
-%mm \textbf{(do I need an example of this in recent work?)}. [maybe soften to "can help discriminate?"]
+Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
 In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
@@
 However, as shown, the HIM comprises very little of the outflow by mass.
-Most of the outflowing gas comes from the warm phase, pushed out by the high pressure, fast moving HIM.
+Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM.
 Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
@@
 
-Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
-This has been better quantified recently both observationally \citep[e.g.][]{Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Angles-Alcazar2017,Muratov2017}.
-In Figure~\ref{fig:outflow_metallicity} we show the average ISM metallicity (black), halo metallicity (blue), and outflow metallicities (orange) at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
+\textbf{AE: Took plot and discussion of outflow metallicities out and replaced with metal mass loading factor (above)}
+%In Figure~\ref{fig:outflow_metallicity} we show the average ISM metallicity (black), halo metallicity (blue), and outflow metallicities (orange) at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
 The ISM metallicity evolves minimally from the initial conditions in this time, while the halo and outflow properties change significantly.
 It is apparent from this figure that the outflows are preferentially metal enriched, as the halo increases in metallicity by a factor of $\sim 2$ in the simulation time.
-Although most of the gas mass in the halo (outside the disk) remains within 0.2 $R_{\rm vir}$ (see Section~\ref{sec:obs_metals}), the mass that does make it
-%mm out far and out side the halo
-   to the outer reaches of the halo or beyond 
-is metal enriched by a factor of $\sim$5--6 compared to the ISM.
-This is in contrast with the results from \citet{Muratov2017}, which generally show $Z_{\rm outflow} \simeq Z_{\rm ISM}$ at $0.25~R_{\rm vir}$ and $Z_{\rm outflow} < Z_{\rm ISM}$ at $1.0~R_{\rm vir}$, though both with some scatter that reaches
-%mm above 
-$Z_{\rm outflow} > Z_{\rm ISM}$, especially at high redshift.
-However, we note that our simulations certainly do not contain a cosmologically realistic circumgalactic medium, nor do they include ongoing cosmological accretion of pristine gas; this will certainly lower the typical halo and outflow metallicities, possibly
-%mm more in 
-    resulting in better
-agreement with the findings of \citet{Muratov2017}.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{metallicity_evolution}
-\caption{The mass-weighted average metallicity of our dwarf galaxy's ISM, halo, and outflowing gas at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
+Although most of the gas mass in the halo (outside the disk) remains within 0.2 $R_{\rm vir}$ (see Section~\ref{sec:obs_metals}), the mass that does make it to the outer reaches of the halo or beyond is metal enriched by a factor of $\sim$5--6 compared to the ISM.
+This is in contrast with the results from \citet{Muratov2017}, which generally show $Z_{\rm outflow} \simeq Z_{\rm ISM}$ at $0.25~R_{\rm vir}$ and $Z_{\rm outflow} < Z_{\rm ISM}$ at $1.0~R_{\rm vir}$, though both with some scatter that reaches $Z_{\rm outflow} > Z_{\rm ISM}$, especially at high redshift.
+However, we note that our simulations certainly do not contain a cosmologically realistic circumgalactic medium, nor do they include ongoing cosmological accretion of pristine gas.
+Mixing of outflowing, metal enriched gas and pristine inflows will lower the typical halo and outflow metallicities, particularly at large radii.
+
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.95\linewidth]{metallicity_evolution}
+%\caption{The mass-weighted average metallicity of our dwarf galaxy's ISM, halo, and outflowing gas at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
 The halo is defined as the region outside of the disk, yet inside the virial radius.}
-\label{fig:outflow_metallicity}
-\end{figure}
+%\label{fig:outflow_metallicity}
+%\end{figure}
 
@@
 \label{sec:chemical evolution}
-Observations of Local Group dwarf galaxies have shown that they retain very little of the total amount of metals they are expected to have produced, given their star formation histories (see Section~\ref{sec:observation}).
+\textbf{Commented out all previous discussion of species abundance retention differences and stellar abundances to save for a future paper.
+Instead, here give a panel plot showing the column densities of the metals at various times?}
+
+%Observations of Local Group dwarf galaxies have shown that they retain very little of the total amount of metals they are expected to have produced, given their star formation histories (see Section~\ref{sec:observation}).
 In Figure~\ref{fig:species_fractions} we show the fraction of metals retained within the disk or expelled into the halo of our galaxy over time, along with a breakdown of the locations of each metal species by the end of the simulation.
@@
 
-Most notably, N is preferentially retained by the galaxy over the other species. 
-Roughly \textbf{35\%} of N produced remains in the disk, as compared to \textbf{15\%} of O 
-%mm and \textbf{15\%} of 
-    or
-Fe, for example. This difference is entirely feedback driven, but 
-%mm a coincidence of our particular galaxy conditions. At our galaxy's metallicity, the IMF weighted production of N occurs entirely
-    determined by the chosen metallicity of our galaxy. At this metallicity, N is 
-    produced only 
-in the stellar winds of stars between 8 and 10 M$_{\odot}$, with little to no production in supernovae.
+%\textbf{Use Ba here as example element, not N}
+%Most notably, N is preferentially retained by the galaxy over the other species.
+Roughly \textbf{35\%} of N produced remains in the disk, as compared to \textbf{15\%} of O or Fe, for example.
+This difference is entirely feedback driven.
+At this metallicity, N is produced only in the stellar winds of stars between 8 and 10 M$_{\odot}$, with little to no production in supernovae.
 The rest of the species either have very little stellar wind production, are produced solely in supernovae, or have similar production levels between both supernovae and stellar winds (like O, for example).
-The typically lower injection energies of N into the galaxy compared to the SN
-%mm injected 
-   produced
-elements means N is preferentially retained within the ISM, and not as effectively ejected through outflows.
+The typically lower injection energies of N into the galaxy compared to the SNe produced elements means N is preferentially retained within the ISM, and not as effectively ejected through outflows.
 In truth, the stars that produce N do eventually explode as supernovae, sweeping up some fraction of the wind produced N into outflows.
@@
 How abundance variations like this evolve over longer timescales and with varying feedback physics is the subject of ongoing work.
-%mm (Emerick et. al. in prep.).
-
-\begin{figure*}
-\includegraphics[width=0.9\linewidth]{species_bar.png}\\
-\includegraphics[width=0.9\linewidth]{species_bar_disk.png}
-\caption{The fraction of each species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).}
-\label{fig:species_fractions}
-\end{figure*}
-
-The bottom panel illustrates where these metals are partitioned within the ISM of the galaxy at the end of the simulation time.
+% AE: possibly cite letter here if we have it done
+
+%\begin{figure*}
+%\includegraphics[width=0.9\linewidth]{species_bar.png}\\
+%\includegraphics[width=0.9\linewidth]{species_bar_disk.png}
+%\caption{The fraction of each species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).}
+%\label{fig:species_fractions}
+%\end{figure*}
+
+%The bottom panel illustrates where these metals are partitioned within the ISM of the galaxy at the end of the simulation time.
 The CNM contains roughly 50-60\% of each species, with the CNM and WNM together accounting for most of the metals in the galaxy.
 The WIM contains only $\sim$ 10\% of each species, with the HIM containing very little.
-This may be counterintuitive given
-that most metals are initially injected into the galaxy in either the WIM or HIM phases.
+This may be counterintuitive given that most metals are initially injected into the galaxy in either the WIM or HIM phases.
 However, the disk metals represent only a small fraction of the total metals produced.
@@
 
-\subsection{Stellar Abundances}
-\label{sec:stellar properties}
-\textbf{This section needs work.
+%\subsection{Stellar Abundances}
+%\label{sec:stellar properties}
+
+% By initializing the metallicity of our galaxy to a non-zero value (XXX), yet setting each of the metal tracer species to initial mass fractions of 10$^{-20}$ (effectively zero abundance), the species abundances in our galaxy are somewhat contrived.
+However, this was done to be able to unambiguously follow how self-consistently produced chemical enrichment evolves over time.
+In effect, what each individual metal field traces is a ``delta'' abundance, or change in metal mass fraction relative to an arbitrary initial condition.
+
+%\textbf{This section needs work.
 As per discussion with Keith and Kathryn, displaying abundance evolution like this is confusing and misleading.
 Switch to discussion of mass / abundance fraction evolution of individual specie(s).}
-We plot the $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ ratio for all star particles in our simulation that are ``alive'' in Figure~\ref{fig:stellar_abundance}.
+%We plot the $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ ratio for all star particles in our simulation that are ``alive'' in Figure~\ref{fig:stellar_abundance}.
 This represents stars that have not gone supernovae or have otherwise formed a compact object.
@@
 
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{alpha_over_fe_hist}
-\caption{The $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$
-diagram for all stars in our simulation, colored by their age. Here, we define $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$. Each histogram shows counts, normalized to the peak in each distribution.}
-\label{fig:stellar_abundance}
-\end{figure}
-
-As expected, there is a noticeable trend of stellar age with [Fe/H]; especially in our case as the overall iron abundance is gradually increasing, yet we do not have any accretion of primordial material.
+%\begin{figure}
+%\includegraphics[width=0.95\linewidth]{alpha_over_fe_hist}
+%\caption{The $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$
+%diagram for all stars in our simulation, colored by their age. Here, we define $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$. Each histogram shows counts, normalized to the peak in each distribution.}
+%\label{fig:stellar_abundance}
+%\end{figure}
+
+%As expected, there is a noticeable trend of stellar age with [Fe/H]; especially in our case as the overall iron abundance is gradually increasing, yet we do not have any accretion of primordial material.
 Interestingly, the few stars with the highest [Fe/H], between -3 and -2, are not the most recently formed; the most recent star formation is clustered around [Fe/H] between -3 and -4.
 
-We note the ``knee'' like feature at very low [Fe/H] is not the characteristic knee seen in $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ space, corresponding to the period when iron enrichment from SN Type Ia begins to make a significant contribution to the galactic chemical evolution.
+%We note the ``knee'' like feature at very low [Fe/H] is not the characteristic knee seen in $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ space, corresponding to the period when iron enrichment from SN Type Ia begins to make a significant contribution to the galactic chemical evolution.
 This generally occurs after roughly 1 Gyr of stellar evolution, far longer than the \textbf{170} Myr simulated here.
@@
 
-\subsection{Comparison to Previous Work}
-\textbf{At the moment, doing a lot of this throughout paper. Not certain if I need an explicit, separate discussion here.}
-
 \subsection{Comparison to Observed Low Mass Dwarf Galaxies}
@@
 
-The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted \ion{H}{1} surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, Tollerud2015, Sand2015}.
-However, the sample of isolated dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) law (left) for low mass galaxies, and the extended Schmidt law (ESL) (right) which has been shown recently to extend to low mass, low metallicity dwarf galaxies \citep{Roychowdhury2017}.
-We plot our galaxy every 1 Myr in these diagrams, showing the significant temporal variation in both spaces.
-Although these quantities are conceptually simple, due to how these values are measured observationally it is challenging to make a direct comparison to simulations, particularly in defining the geometric region to measure the surface densities.
-We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs following the procedure described in \citet{Roychowdhury2014}.
+The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted \ion{H}{1} surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}.
+However, the sample of isolated, gaseous dwarf galaxies with and $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
+In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) law (left) for low mass galaxies, and the extended Schmidt law (ESL) (right).
+In both diagrams, our simulations are given by the colored points, sampled every 1 Myr throughout the entire simulation.
+Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
+We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs given the procedure described in \citet{Roychowdhury2014}.
 We define $\Sigma_{\rm sfr} = \dot{M}_{*, \rm{10 Myr}} / A_{*, \rm{10 Myr}}$, where $\dot{M}_{*, \rm{10 Myr}}$ is the SFR measured over the preceding 10 Myr, and $A_{*, \rm{10 Myr}}$ is the disk defined out to the farthest star formed within the previous 10 Myr.
 Likewise, $\Sigma_{\rm gas} = M_{\rm gas, 10 Myr} / A_{*, \rm{10 Myr}}$, where M$_{\rm gas, 10 Myr}$ is the total gas mass within this defined disk.
-However, the total gas content cannot be determined observationally, particularly for low mass dwarf galaxies with a virtually unmeasurable H$_2$ content.
-Therefore, we present $\Sigma_{\rm gas}$ as measured directly in the simulations (green/purple points) and the observational equivalent, or $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He, and where there is no correction for H$_2$ (plasma points).
+However, the total gas content cannot be determined observationally.
+To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He.
+There is generally no correction applied to account for any H$_{2}$ or HII content.
+The molecular component is discussed further in Section~\ref{sec:molecular gas content}.
 
@@
 \includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution}
-\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every 1 Myr for the total gas surface density computed from the simulations, and an observational analog derived using the \ion{H}{1} content (see text for details).}
+\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every 1 Myr.
+We take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$ in our simulations to make a fair comparison to the observational sample (see text for more details).
+Plotted as points on both plots are recent observations from the SHIELD sample \citep{Teich2016}.
+On the left, we also give the best fit line to galaxies from the FIGGS sample from \cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \cite{Shi2011}.}
 \label{fig:KS}
@@
 
-In both panels, we also include recent observational constraints from these relationships. For the KS relationship we include the fits from \citet{Shi2011} with 1$\sigma$ errors (black), the fits 
-%mm
-   and errors 
-from \citet{Roychowdhury2014} (blue), and the individual points 
-%mm
-   (black squares) 
-from the recent SHIELD sample \citep{Teich2016}, while for the ESL relationship we include only the fit and 1$\sigma$ errors (black) from \citet{Shi2011}, which have been shown to match well for dwarf galaxies at these surface densities \citep{Roychowdhury2017}.
-In both relationships our simulations fit well around the median observed fit, spanning the 1 $\sigma$ variations about the mean.
-
-This is a remarkable result.
+In both panels, we also include recent observational constraints from these relationships.
+For the KS relationship we include the best fit line from \citet{Roychowdhury2014} (black, dashed).
+In both we give recent measurements from the SHIELD galaxy sample \citep{Teich2016} (black, points).
+Recently, \cite{Roychowdhury2017} demonstrated that the best fit line in the ESL from \cite{Shi2011} extends to the low mass FIGGS sample of galaxies; we give this best fit line and 1$\sigma$ errors in the right hand panel (black lines).
+Our galaxy fluctuates significantly about both relationships with no clear trends in time.
+However, in both cases, it is consistent with the available observational sample.
+At times our galaxy exhibits gas surface densities below the observational constraints.
+The trend is still consistent with higher densities at this point, but with a larger scatter towards lower star formation rate densities and efficiencies.
+
+Fig.~\ref{fig:KS} represents a remarkable result.
 In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
@@
 %mm 
+%ae: but does this bit then contradict my statement that this is remarkable? if its 'just gravity' at play?
    but also with the demonstration by \citet{Li2005} that the KS law can be reproduced 
@@
 
-The molecular gas content of low mass dwarf galaxies like this is generally considered 
-to be small (references).
+\subsubsection{Molecular Gas Content}
+\label{sec:molecular gas content}
+
+The molecular gas content of low mass dwarf galaxies is generally assumed
+to be small, but is not well constrained by either theory or observations.
 Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas fractions anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
 As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.17--0.20, within this range, but significantly exceeding the few percent often found in models.
-This means ignoring the H$_2$ component of our galaxies leads to an average shift of 0.24 dex to the right in the KS relationship, and 0.24 dex right and down in the ESL.
-This does not lead to a significant disagreement with the observed relationships, but would constitute a quantitative change to the observed fits if our $f_{\rm H_2}$ is robust for low mass, low metallicity dwarf galaxies.
-However,
-%mm
-    we do not fully resolve the turbulent density perturbations in which 
-    H$_2$ forms most efficiently \citep{Glover2007}, and
-our non-equilibrium chemical model for H$_2$ formation and destruction is relatively simple: it does not account for C and O chemistry, a detailed dust model, or cosmic rays, all of which may significantly affect $f_{\rm H_2}$.
-
-Simulations by \citet{Hu2016} and \citet{Hu2017}, which contain a more detailed non-equilibrium chemistry model than included here, give very low $f_{\rm H_2}$, below $10^{-4}$ for their full feedback simulations; even their simulations without any radiation feedback only reach $f_{\rm H_2} \sim 2 \times 10^{-3}$.
-However, their simulated dwarf galaxies are more massive ($M_{\rm vir} = 10^{10} M_{\odot}$) and higher metallicity ($Z = 0.1 Z_{\odot}$) than those examined here.
-This disagreement warrants additional investigation, particularly as making predictions for the H$_2$ content of low mass dwarf galaxies is valuable.
-We do note that there is some possible observational evidence for higher than expected ($\sim 15$ \%) molecular fractions \citep{Schruba2017}, though this still remains highly uncertain.
+Ignoring the H$_2$ component of our galaxies would lead to an average shift of 0.24 dex to the right in the KS relationship, and 0.24 dex right and down in the ESL.
+This does not result in a significant disagreement with the observed relationships, but would constitute a quantitative change to the observed fits if our $f_{\rm H_2}$ is robust for observed low mass, low metallicity dwarf galaxies.
+
+Interestingly, in this low-dust regime, our H$_2$ formation is dominated by the gas-phase reactions H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
+In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
+Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionizations of H and He from the UVB.
+This has the seemingly counterintuitive effect that turning off the UVB actually decreases the formation rate of H$_2$, as confirmed in test simulations.
+In a test simulation ignoring H$^{-}$, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.
+
+This explains our contention with the simulations in \citet{Hu2016} and \citet{Hu2017}, which find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
+Although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
+Our model suggests that H$^{-}$ and a UVB (in the absence of a local radiation field) are critical components in H$_2$ formation in small dwarf galaxies.
+It is not surprising that the gas phase reactions dominates over grain XXX in this low metallicity regime \citep{Glover2003}, but the total amount of H$_2$ formed is perhaps surprising.
+However, the rate coefficients association with gas-phase H$_2$ formation are uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
+%In addition, \cite{Glover2006} demonstrated that the total amount of H$_2$ formed can be quite sensitive to the initial conditions.
+Finally, our model lacks additional chemistry which may be important in the formation and destruction of H$_2$, including $HD$ chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
+It is unclear how the combination of all of these effects with behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
+This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
+%ae rewrote above and took out this citation, need to see if need to put back in:
+%            there is some possible observational evidence for higher than expected ($\sim 15$ \%)   %            molecular fractions \citep{Schruba2017}, though this still remains highly uncertain.
 
@@
 
-%mm Unfortunately, these high resolution simulations are not (yet) run
-    The simulations presented here have not yet been run
-for the 
-%mm $\sim$ Gyr 
-    gigayear
-timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$. However, we can compare to a key observable, the 
-%mm ejection / 
-retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from stellar evolution models based on the galaxy's star formation history.
+The simulations presented here have not yet been run for the gigayear timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$.
+However, we can compare to a key observable, the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from stellar evolution models based on the galaxy's star formation history.
 This can be done readily with Milky Way dSph's, whose stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
@@
 At the end of our simulation, we agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
-Although more than half of these metals are expected to
-%mm
-   eventually
-be re-accreted \citep{Angles-Alcazar2017}, it is still possible that, at %mm any moment, 
-   the early times we have simulated,
-most of the metals that have been produced 
-%mm lie 
-    remain
-outside the galaxy disk. We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.
-
-It is interesting to consider 
-%mm where these metals lie outside of the galaxy's disk, 
-    whether ejected metals in our model reside 
-in the CGM or have been ejected into the IGM, and their eventual fate.
+Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that
+most of the metals that have been produced at these early times will remain outside the galaxy disk.
+We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.
+
+It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the IGM.
 While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of a $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero $\sim$ 60\% of ejected gas is recycled, while 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
@@
 Over time, the re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
-Recycling of metal enriched gas could be a significant
-%mm source 
-    driver
-of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) returns.
+Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) returns.
 Unfortunately, we cannot yet speak to how this gas evolves over time, but will investigate this in future work with our feedback model.
@@
 Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}.
-These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through
-%mm stellar [CRs are also stellar feedback...]
-     thermal 
-feedback alone \citep{SalemBryanCorlies}.
+These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}.
 Modeling cosmic rays is challenging, however, as they encompass a wide range of energies (give range), with significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
@@
 
-\subsection{Detailed Dust Model}
-\textbf{Should we discuss this? If so I definitely need more info and references - AE}.
-The dust content of our galaxy is modeled only approximately, scaling with the cell-to-cell variations in gas metallicity.
+%\subsection{Detailed Dust Model}
+%\textbf{Should we discuss this? If so I definitely need more info and references - AE}.
+%The dust content of our galaxy is modeled only approximately, scaling with the cell-to-cell variations in gas metallicity.
 Explicitly following the dust content in our galaxy, even crudely, could introduce significant variations in local cooling and heating rates.
@@
 \textbf{Definitely a question that comes up a lot whenever I say our simulations are star-by-star and detailed (as in ``but what about binary stars''?).
-Do we need to discuss this here as a quick paragraph about how it would affect feedback properties (namely radiation and different stellar lifetimes)?} \citep{Ma2016-binary}
+Do we need to discuss this here as a quick paragraph about how it would affect feedback properties (namely radiation and different stellar lifetimes)?} \citep{Ma2016-binary} go through this paper and check sources.
+discuss here briefly and include possible effects on yields
 

### 2017-12-21 main.tex
Update on Overleaf.

@@
    as it forms
-with the associated local gas abundances for each species. These methods are discussed in full detail below.
+with the associated local gas abundances for each species.
+In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked.
+This field is used to inform the heating/cooling physics and determines the metallicity of each star.
+These methods are discussed in full detail below.
 
@@
 
-Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
-This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Angles-Alcazar2017,Muratov2017}.
-The right hand panel of Figure~\ref{fig:mass_outflow} gives the metal mass loading factor over time for our dwarf galaxy, considering only the new metals produced by the star particles.
-Metal mass loading factor is defined as
-\begin{equation}
-\eta_{\rm metal} = \frac{\dot{M_{\rm metal}}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
-\end{equation}
-where $\dot{M_{\rm metal}}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-\textbf{compare mass loading here and in other works...
-check back to Muratov for these.
-also cite miao and drummond.} \citep{Li2017}
-
 % figure here of mass loading and mass outflow rates
@@
 \centering
-\includegraphics[width=0.33\linewidth]{total_mass_outflow}
-\includegraphics[width=0.33\linewidth]{total_mass_loading}
-\includegraphics[width=0.33\linewidth]{metal_mass_loading}
+\includegraphics[width=0.45\linewidth]{total_mass_outflow}
+\includegraphics[width=0.45\linewidth]{total_mass_loading}
+%\includegraphics[width=0.33\linewidth]{metal_mass_loading}
 \caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
@@
 
-\subsection{Chemical Evolution} 
+\subsection{Metal Evolution} 
 \label{sec:chemical evolution}
@@
 Instead, here give a panel plot showing the column densities of the metals at various times?}
+
+Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
+This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Angles-Alcazar2017,Muratov2017}.
+The right hand panel of Figure~\ref{fig:mass_outflow} gives the metal mass loading factor over time for our dwarf galaxy, considering only the new metals produced by the star particles.
+Metal mass loading factor is defined as
+\begin{equation}
+\eta_{\rm metal} = \frac{\dot{M_{\rm metal}}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
+\end{equation}
+where $\dot{M_{\rm metal}}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
+\textbf{compare mass loading here and in other works...
+check back to Muratov for these.
+also cite miao and drummond.} \citep{Li2017}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
+\includegraphics[width=0.9\linewidth]{metal_fraction_evolution}
+\caption{Top: Metal mass loading factor at four radii over time (see text for how this is defined).
+Bottom: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
+In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
+\label{fig:metal_evolution}
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.23\linewidth]{metal_mass_loading} 
+\includegraphics[width=0.23\linewidth]{metal_fraction_evolution}
+\includegraphics[width=0.23\linewidth]{metal_mass_loading} 
+\includegraphics[width=0.23\linewidth]{metal_fraction_evolution}
+\caption{Full-box projections of the entire computational domain showing the total column density in each of 4 different metal species at the end of the simulation time.
+For a more reasonable comparison across metal fields with significant differences total column density, the maximum of the color bar scales are each set to the peak column density for that field, and the minimum to a fixed fraction of this maximum.}
+\label{fig:metal_column_panels}
+\end{figure*}
 

### 2017-12-21 main.tex
scribbled some notes for binary section

--- 2017-12-20 main.tex
@@
 
+Most (word) models, including this work, of feedback and chemical evolution in galaxies ignore the effects of binary star evolution, generating feedback and yields from stellar populations that are comprised of many single stars.
+There are two effects that could significantly influence galaxy evolution: 1) radiation, and 2) runaway stars.
+The former could greatly increase the impact radiation feedback has on the galaxy, but its exact role is unclear since the photons emitted durign the extended lifetime are more likely to escape the galaxy (check this).
+The latter, however, could influence the typical regions where supernovae occur, as stars can travel appreciably far from their birth cloud (distance) before exploding, changing the effect of feedback and (yields).
+Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochasitcally assigning binary star properties to some subset of our individual stars.
+This is beyond the scope of this project, but will be investigated in future works.
+
 \section{Conclusion}

### 2018-01-11 main.tex
Update on Overleaf.

--- 2017-12-21 main.tex
@@
 
-\title{REDO Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution I: Methods and Test Case}
+\title{Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution}
 %Unstable Star Formation for the Lowest Mass Dwarf Galaxies
@@
 \begin{abstract}
-\textbf{Saving this for after the first iteration}
+We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement code \textsc{Enzo}.
+For the first time in galaxy scale simulations, we are capable of capturing detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae.
+%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
+In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species \textbf{list here?}.
+We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium.
+We present the first application of these methods on a \textbf{XX Myr} simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
+Our methods are capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
+Effective feedback drives significant metal enriched outflows, leading to a low metal retention fractions consistent with observations.
+Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions.
+We end with a discussion on how this work will impact our understanding of galactic chemical evolution on a species-by-species basis, with first results presented in a companion paper \textit{reference here?}.
 \end{abstract}
@@
 \section{Introduction}
-
-Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade.
+%
+% AE removed below.. MM suggested  skipping both pars.
+%
+%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade.
 Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc.
@@
 See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.
-
-These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution.
+%
+%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution.
 In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense.
@@
 
-Due to its complexity, the detailed interstellar medium (ISM) and chemical abundance properties, beyond total metallicity, are sensitive tests of the underlying physical processes that govern galaxy evolution.
+Due to its complexity, the detailed interstellar medium (ISM) and chemical abundance properties of galaxies
+%beyond total metallicity
+are sensitive tests of the underlying physical processes that govern galaxy evolution.
 Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
-There is a considerable body of work examining the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
-These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017} and more detailed quantities such as metallicity distribution functions (MDFs) and abundance evolution of individual species \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
-However, there is a general lack of numerical diversity in these works, as a majority are implemented in some flavor of smoothed particle hydrodynamics (SPH) schemes.
+There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
+These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and abundance evolution of individual species \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
+
+%\textbf{rework here to the end... focus less on numerics}
+% However, there is a general lack of numerical diversity in these works, as a majority are implemented in some flavor of smoothed particle hydrodynamics (SPH) schemes.
 Given the known differences between hydrodynamics implementations \citep{Agertz2007,AGORA,AGORA2}, extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.
-Additionally, grid-based schemes are able to generally avoid issues with metal mixing, one of the largest model uncertainties in standard SPH codes.
-
-The native SPH scheme is incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
-This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017} which, while sophisticated, must still generally be fine-tuned.
+% AE (incorrect statement): Additionally, grid-based schemes are able to generally avoid issues with metal mixing, one of the largest model uncertainties in standard SPH codes.
+
+The native smooth particle hydrodynamics (SPH) scheme is incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
+This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017a}.
 Even more, a given parameterization is not necessarily applicable generally \citep{Revaz2016}, though recent studies have shown great improvements to this end \citep{Escala2017}.
-Metal mixing efficiencies may also vary species-by-species (refs), as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
-In part, this is because mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources)
+Metal mixing efficiencies may also vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
+Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources)
 %mm in which they are injected to
-    that injects metals into 
-the ISM.
-The variations in how one handles sub-grid metal injection and metal mixing schemes can lead to challenges in connecting models back to the fundamental physics that drives galactic evolution.
-We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mesh refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies.
+    that inject metals into 
+the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
+The variations in how one handles sub-grid metal injection and metal mixing schemes can lead to challenges in connecting models to observations and the fundamental physics that drives galaxy evolution.
+\textbf{Still not sure about this sentence - but I do need a way to cite mentioned papers:} Extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.
 
@@
 %mm one's 
-reliance on sub-grid physics, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations \citep[SSPs; as studied in detail in ][]{Revaz2016} do not make physical sense.
-Below 10$^4$ M$_{\odot}$, SSPs begin to no longer fully sample the IMF, and can no longer be considered average representations of stellar populations; this becomes conceptually problematic at SSP masses comparable to or below the mass of the most massive star ($\sim 100$ M$_{\odot}$).
-Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Rosdahl2015,Kroupa2013}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
+reliance on sub-grid physics, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations (SSPs) are no longer valid \citep[as studied in detail in ][]{Revaz2016}.
+Below 10$^4$ M$_{\odot}$, SSPs do not fully sample the IMF, and cannot be considered average representations of stellar populations.
+This is acutely problematic at star particle masses comparable to or below the mass of the most massive individual star (or $\sim 100$ M$_{\odot}$).
+Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
 %mm Perhaps the most naive, 
    The most straightforward
-solution, though untenable for large scale simulations, is to remove the SSP formalism entirely and simply track stars as individual particles. In this work, we 
+solution is to remove the SSP formalism entirely and simply track stars as individual particles.
+However, the number of particles required to do so make this computationally prohibitive in all but the smallest of galaxies ($M_{*} \lesssim 10^{7} {\rm M_{\odot}})$, let alone in a cosmological simulation.
+%In this work, we 
 %mm follow stars as individual star particles, allowing us to place unprecedented detail on our
-     do this, allowing unprecedented detail in our
- accounting of stellar feedback processes and chemical enrichment.
-
+%     do this, allowing unprecedented detail in our
+% accounting of stellar feedback processes and chemical enrichment.
+
+We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mesh refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies.
 The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms.
-We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution.
-For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies.
+We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
+%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies.
 \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
-Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
+Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback of both massive stars and AGB stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
 
@@
 This paper is the first in a series of papers examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
-In this paper we introduce a new method of modeling for feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}.
+In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}.
 For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer.
-In addition, we couple to a self-consistent set of stellar yields
-%mm tables from the
-to track stellar yields from massive star stellar winds, AGB star winds, and supernovae. We describe each mode of our multi-channel feedback 
+In addition, we couple to a self-consistent set of stellar yields %mm tables from the
+to track yields from massive star stellar winds, AGB star winds, and supernovae. We describe each mode of our multi-channel feedback 
 %mm implementation 
@@
 We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and O column density projections (fourth row), at four different times in the simulation \textit{(list times here)}.
+Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation \textit{(list times here)}.
 In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points.
-Towards the end of the simulation time, the half light radius is $389 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
+Towards the end of the simulation time, the half light radius is \textbf{$389 \pm 21$ pc}, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
 
@@
 \caption{ \textbf{need to adjust overlapping labels} Edge-on views of our dwarf galaxy at four different times in its evolution, separated by 100~Myr, beginning with the time at first star formation and ending at 300 Myr.
-Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and O column density (fourth row).
-Each individual main sequence star particle is shown in the number density projections as a single black dot.
-\textbf{use H2 in bottom panel instead}}
+Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and H$_2$ column density (fourth row).
+Each individual main sequence star particle is shown in the number density projections as a single black dot.}
 \label{fig:panel_x}
@@
 \includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
-\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on projections/slices. \textbf{use H2 in bottom panel instead}}
+\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on projections/slices.}
 \label{fig:panel_z}
@@
 \includegraphics[width=0.975\linewidth]{scale_height}
-\caption{The 30~Myr time average gas disk scale height as a function of radius at various times throughout the simulation.}
+\caption{The total gas scale height at various times throughout the simulation.}
 \label{fig:scale_height}
@@
 The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
-\textbf{Is it worth also plotting the non-luminous stellar masses here?
-The total mass in WD's and other SN remnants?
-This mass is roughly half of the mass of luminous stars at the end of the simulation.}
 
@@
 \includegraphics[width=0.95\linewidth]{phase_diagram.png}
-\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation, averaged over the final 50 Myr of simulation time, and showing the whole simulation domain.}
+\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gass interior to 0.25~$R_{\rm vir}$, averaged over the final 50 Myr of simulation time.
+The two red dashed lines show lines of constant pressure for guidance.
+The region in the lower right corner indicates our density and temperature thresholds for star formation.}
 \label{fig:phase}
@@
 However, the ISRF varies significantly over time, fluctuating by an order of magnitude or more at any given radius.
+
 \textbf{Note to remember to discuss: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e.
@@
 \caption{
-Azimuthally averaged radial profiles of the ISRF in our galaxy in three different bands, time-averaged over the final 50 Myr of simulation time.
+Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over the final 50 Myr of simulation time.
+Here we define the midplace as within 2.5~$dx$ of z = 0, or 4.5~pc.
 The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
-The bottom panel gives the \ion{H}{1} and \ion{He}{1} ionizing stellar radiation flux, showing average and maximum values only.
-For these fields the minimum value reaches zero at some point during the examined period at all radii.}
+The bottom panel gives the \ion{H}{1} ionizing stellar radiation flux.
+Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point.
+For this reason we only shade between the first quartile and maximum values only.
+\ion{He}{1} is very similar to \ion{H}{1}, with a small vertical offset, and is not shown for clarity.}
 \label{fig:ISRF}
@@
 
-The bottom panel gives the ionizing photon fluxes for \ion{H}{1} and \ion{He}{1} from stellar radiation {\em only}.
-Since these fields are tracked directly using ray-tracing radiative transfer, the profiles encode information about local attenuation of these photons from dense, neutral gas.
-This is the main driver of the differences between these fields and $G_{\rm o}$.
-The ionizing fields vary much more dramatically at all radii, \textbf{need to figure out how to plot these.
-median / average mean very different things.}
+The bottom panel gives the ionizing photon fluxes for \ion{H}{1} from stellar radiation {\em only}.
+Since this field is tracked directly using ray-tracing radiative transfer, the profile encodes information about local attenuation of these photons from dense, neutral gas.
+This is the main driver of the differences between this field and $G_{\rm o}$.
+However, both profiles track each other well as a function of radius.
+The lack of dramatic trend with radius in both diagrams suggests that one could model the ISRF in low mass dwarf galaxies using a uniform heating / ionization rate; however, this would still fail to capture the fact that any given region of the galaxy will experience order of magnitude or more fluctuations in the incident flux.
+% These fluctuations are likely important in reducing star formation locally around young, massive stars.
+This effect would be challenging to capture with a simple model.
+(AE this bit is moved to the end of section)
 
@@
 \includegraphics[width=0.45\linewidth]{q_o_2D_phase}
-\caption{Single-snapshot 2D radial profile plots of the ISRF in two flux bands, $G_{\rm o}$ and \ion{H}{1} ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
-Here, we include all gas within 25 pc of the midplane of our dwarf galaxy.
-We note the large difference in color scale between the two plots.
+\caption{Single-snapshot 2D radial profile plots at 200~Myr of the ISRF in two flux bands, $G_{\rm o}$ and \ion{H}{1} ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
+Here, we include all gas within the mid-plane of our dwarf galaxy.
 Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to \ion{H}{1} ionizing radiation, it does not show up in the \ion{H}{1} ionizing radiation diagram.
@@
 
-These plots are useful to understand the time-varying properties of the ISRF in a spatially averaged sense.
-However, the local variations for individual regions can be much larger than is illustrated in these profiles.
-In Figure~\ref{fig:ISRF_2D} we present the full distribution of $G_{\rm o}$ at the end of the simulation time.
-This more effectively captures the large spikes in local ISRF from young, massive stars.
-The azimuthally averaged profiles capture the averaged heating and ionizing effects of the ISRF in our galaxy.
-This helps reduce star formation by increasing the thermal pressure support and equilibrium temperature of the ISM.
-However, it is the spikes that act as important local feedback to shut off star formation in dense, collapsing regions that satisfy our star formation criteria.
+To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the \ion{H}{1} ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr.
+This diagram shows how dramatic the increase in ISRF near young, massive stars (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
+The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
+From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy various greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
+Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation.
+In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency.
+It is unclear which of these two modes of feedback is more important in controlling star formation.
+
 %mm (Emerick et. al. in prep).  [I'd only insert the reference when there is an actual astro-ph number to support it.]
@@
 The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time.
-This quickly declines towards larger radii, however, with \textbf{check this effectively zero outflow past the virial radius}.
+This quickly declines towards larger radii, however, with minimal outflow past the virial radius.
 \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift.
@@
 
-\textbf{AE: Took plot and discussion of outflow metallicities out and replaced with metal mass loading factor (above)}
+\textbf{AE: Took plot and discussion of outflow metallicities out and replaced with metal mass loading factor (below)}
 %In Figure~\ref{fig:outflow_metallicity} we show the average ISM metallicity (black), halo metallicity (blue), and outflow metallicities (orange) at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
@@
 \label{sec:chemical evolution}
-\textbf{Commented out all previous discussion of species abundance retention differences and stellar abundances to save for a future paper.
-Instead, here give a panel plot showing the column densities of the metals at various times?}
-
+\textbf{Commented out all previous discussion of species abundance retention differences and stellar abundances to save for a future paper.}
+
+\subsubsection{Metal Enriched Outflows}
 Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
 This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Angles-Alcazar2017,Muratov2017}.
-The right hand panel of Figure~\ref{fig:mass_outflow} gives the metal mass loading factor over time for our dwarf galaxy, considering only the new metals produced by the star particles.
-Metal mass loading factor is defined as
+In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}.
+We define the metal mass loading factor as
 \begin{equation}
-\eta_{\rm metal} = \frac{\dot{M_{\rm metal}}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
+\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
 \end{equation}
-where $\dot{M_{\rm metal}}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-\textbf{compare mass loading here and in other works...
-check back to Muratov for these.
-also cite miao and drummond.} \citep{Li2017}
+where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
+The metal mass loading factor at radii interior to 0.5~$R_{\rm vir}$ are much more similar than the total gas mass loading factor in Figure~\ref{fig:mass_outflow}, indicating $\dot{M}_{\rm metal}$ varies less with radius than the total mass outflow rate.
+At these radii, $\eta_{\rm metal}$ is almost always above unity, reaching values of 7-8 for much of the evolution.
+These values are quite large, but perhaps not surprising for a low mass dwarf galaxy.
+Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ an order of magnitude below this, typically between 0.5 and 1 \citep{Li2017,Fielding2017}.
+\cite{Muratov2017} computes a normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$ for their galaxies, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
+Our galaxy is slightly broadly consistent but slightly above this finding, with an average $\eta_Z = 0.04$, fluctuating between 0.01 and 0.08.
 
@@
 
+These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
+This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, CGM, and outside the virial radius of our galaxy over time.
+After the first 20 Myr, supernova driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
+This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy.
+It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, or 20\% by the end of the simulation.
+The CGM metal content is falling at the end of the simulation, due mostly to ejection from the virial radius, but there is some re-accretion of metals from the CGM into the disk as suggested by the slight increase in disk metal fraction at the end of the simulation.
+It is reasonable to expect that the fraction of metals contained in the disk reaches a steady state, as possibly suggested by the diagram, but if the star formation of this galaxy is bursty over long timescales, this will certainly fluctuate over time depending on the relative significance of feedback driven outflows and re-accretion of ejected gas.
+%\textbf{closing sentence}
+
+\subsubsection{Metal Distribution within the ISM}
+
+It is important to understand how metals from each source of stellar yields (stellar winds, AGB star winds, and supernovae) enrich the ISM.
+It is unclear how uniform metal distributions are in ultrafaint dwarf galaxies, and over what timescales newly produced metals mix across the galaxy.
+We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, in addressing these questions with Fig~\ref{fig:metal_slices}.
+The top two panels give the slices of number density (top left) and temperature (top right) in the mid-plane of a portion of our dwarf galaxy.
+These serve to guide the eye in the lower panels, clearly indicating regions with dense, cold gas clouds ($n \sim 100 \rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
+The bottom panels give abundance ratios for oxygen and hydrogen (bottom left), nitrogen and hydrogen (bottom middle), and nitrogen and oxygen (bottom right).
+
 \begin{figure*}
 \centering
-\includegraphics[width=0.23\linewidth]{metal_mass_loading} 
-\includegraphics[width=0.23\linewidth]{metal_fraction_evolution}
-\includegraphics[width=0.23\linewidth]{metal_mass_loading} 
-\includegraphics[width=0.23\linewidth]{metal_fraction_evolution}
-\caption{Full-box projections of the entire computational domain showing the total column density in each of 4 different metal species at the end of the simulation time.
-For a more reasonable comparison across metal fields with significant differences total column density, the maximum of the color bar scales are each set to the peak column density for that field, and the minimum to a fixed fraction of this maximum.}
-\label{fig:metal_column_panels}
+\includegraphics[width=0.32\linewidth]{number_density} 
+\includegraphics[width=0.32\linewidth]{temperature}\\
+\includegraphics[width=0.32\linewidth]{log_OH} 
+\includegraphics[width=0.32\linewidth]{log_NH}
+\includegraphics[width=0.32\linewidth]{log_NO}
+\caption{Five slices in the mid-place of our dwarf galaxy at an arbitrary time (XXX Myr) demonstrating the power of our chemical evolution model.
+We show the number density and temperature in this region of the galaxy (top row), along with three different elemental abundance ratios, O/H (bottom left), N/H (bottom middle), and N/O (bottom right).
+We caution against making direct comparisons of these images to observed abundances of dwarf galaxies, as we do not capture a cosmologically realistic chemical evolution in these relatively short ($< 1$~Gyr) simulations.
+This will be addressed in future work.}
+\label{fig:metal_slices}
 \end{figure*}
+
+Beginning with $log(O/H)$, the gas from the recent SN explosion is abundantly clear, with a higher oxygen abundance by at least 1 dex from its surroundings.
+The oxygen abundance throughout the rest of the ISM does vary, with some dense regions showing slightly higher oxygen abundance than their less dense surroundings, but the variation is not dramatic.
+$log(N/H)$, however, shows slightly more significant variation throughout the ISM.
+Comparing the two diagrams, one can pick out regions with differing abundances between the two species.
+This is clear in the $log(N/O)$ slice, emphasizing regions that are over/under abundance in either species.
+The gas from the SN explosion, for example, has a low $log(N/O)$ due to the significant amount of oxygen released in the SN.
+Oxygen is generally more abundant than nitrogen throughout the ISM, particularly in the warm, diffuse gas.
+However, the dense, cold gas typically has a greater $log(N/O)$ than its surroundings, indicating that nitrogen may more easily pollute cold gas than oxygen.
+These differences are also evident with a few regions of warmer gas (small sliver at center of figure, horseshoe shaped feature in lower right, and the blob in the upper right) where $log(N/O) > 0$, indicating an overabundance of nitrogen as compared to oxygen.
+At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse supernovae and winds from more massive stars.
+Therefore, nitrogen is injected to the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in supernovae, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
+This suggests that the energetic differences between the injection sources can drive abundance variations within the ISM of our dwarf galaxy.
+It is possible, then, that metal mixing within the ISM (and also metal ejection from the ISM) is a process is species dependent.
+We will investigate this point, and any potential observational consequences in stellar abundances, in future projects.
+A more detailed analysis is beyond the scope of this work.
+% reference my other paper if it is ready-ish by the time I submit this one.
 
@@
 However, the sample of isolated, gaseous dwarf galaxies with and $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) law (left) for low mass galaxies, and the extended Schmidt law (ESL) (right).
+In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) relation (left) for low mass galaxies, and the extended Schmidt law (ESL) (right).
 In both diagrams, our simulations are given by the colored points, sampled every 1 Myr throughout the entire simulation.
@@
 \subsection{Detailed Stellar Evolution and Binary Stars}
-\textbf{Definitely a question that comes up a lot whenever I say our simulations are star-by-star and detailed (as in ``but what about binary stars''?).
-Do we need to discuss this here as a quick paragraph about how it would affect feedback properties (namely radiation and different stellar lifetimes)?} \citep{Ma2016-binary} go through this paper and check sources.
-discuss here briefly and include possible effects on yields
+
+% Although we track individual stars and assign properties to each based on stellar evolution models, these properties are fixed.
+A more detailed model could follow each star on an interpolated stellar evolution track, which would account for variations in radiation and stellar wind properties in each star over time.
+
+Roughly half of massive stars live in binary pairs.
+Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes.
+This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as supernovae.
+This effect is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g.
+STARBURST99), but could be significant.
+For example, \cite{Zapartas2017} finds that binarity extends the timescales over which core collapse supernovae occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
+Although they find only $\sim 15\%$ of core collapse supernovae explode after 50~Myr, this could still be an important effect.
+Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}.
+Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
+% does this affect yields??
+% runaway stars
+
+Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochasitcally assigning binary star properties to some subset of our individual stars.
+This is beyond the scope of this project, but will be investigated in future works.
 
 \section{Conclusion}
-\textbf{You can ignore this for now, I'm saving it after the first iteration (AE)}
-We present a new method for simulating the evolution of low mass galaxies with detailed feedback and chemical enrichment as traced through individual star particles.
-This model follows multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia supernovae, ionizing radiation followed through radiative transfer, photoelectric heating, and Lyman-Werner radiation.
-This is in addition to the detailed cooling, heating, and chemistry followed through Grackle, including a self-consistent model for gas self-shielding from the metagalactic UV background.
-
-In this work, we presented the initial results of these methods applied to the evolution of an isolated, low mass dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
-
-In future works we will investigate in detail the role each individual feedback process has in governing the chemodynamical evolution of isolated, low mass dwarf galaxies.
-These simulations will demonstrate how feedback affects metal mixing within the ISM and the enrichment of future stellar populations, in addition to how feedback influence metal ejection into, and possibly beyond, the galaxy's dark matter halo.
-\textbf{will finish at very end}
-
+\label{sec:conclusion}
+We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
+For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia supernovae, ionizing radiation followed through radiative transfer, photoelectric heating, and Lyman-Werner radiation using individual star particles.
+This, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
+In this work, we apply these methods to simulate the evolution of an isolated, low mass dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
+We present an overview of the properties of this galaxy in this work.
+% AE: mention companion paper here if publish at same time
+
+Most notably, our galaxy is characterized by (\textbf{figure out order... and spacing})
+\begin{enumerate}
+\item Multi-channel feedback is effective in this galaxy in regulating star formation consistent with the KS relationship and extended Schmidt law in observed galaxies. 
+\item A thin ($\sim$~50~pc), yet resolved, disk outside the stellar radius, with larger ($\sim 100 - 200$~pc) scale heights driven by feedback.
+This is comparable to the resolution limit of observed, gaseous UDG's.
+\item This feedback drives large outflows ($\eta > 100$) with metal mass loading factors greater than unity ($\eta_{\rm metal} \sim 5$).
+By mass, nearly all of this outflow is moving with velocities below 100 km~s$^{-1}$, but there is a significant tail towards velocities up to 1000 km s$^{-1}$.
+This galaxy is consistent with observed metal retention fractions of UDG's, loosing XX\% of produced metals to the halo.
+\item The ISRF of our galaxy is highly varying in time by orders of magnitude, though is surprisingly uniform in space at any given time. 
+\end{enumerate}
+
+In future works in this series, we will investigate in more detail how metal enrichment proceeds in this galaxy.
+We can directly study, on a species-by-species basis, how metals evolve through the phases of the ISM, from hot, ionized gas into star forming regions.
+This evolution is poorly understood, but has direct implications for chemical evolution models, and can inform the assumed time scales with which new metals enrich future stellar populations in galaxies.
+\textbf{how much detail should I go into on future work?}
+
+\section*{Acknowledgements:} A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. 
+We gratefully recognize computational
+resources provided by NSF XSEDE through grant number TGMCA99S024, \textbf{Pleiades alloc}, Columbia University, and the \textbf{Simons Foundation}. Analysis in this work
+made significant use of the publicly available yt (http://ytproject.org)
+toolkit. \textsc{Enzo}, \textsc{Grackle}, and yt are the products of a collaborative effort of many independent scientists from numerous institutions around
+the world. Their commitment to open science has helped make
+this work possible
+We would also like to thank for their advice and valuable conversations: John Wise, Brian O'Shea, Benoit Cote, Britton Smith, Simon Glover, Kathryn Johnston, Mary Putman, Keith Hawkins, Joshua Wall, and Chia-yu Hu.
+\textbf{is this too many people?
+I do think they all deserve acknowledgement.
+(list is in no particular order)}
+
+\textit{Software:} \textsc{Enzo} \citep{Enzo2014}, \textsc{yt} \citep{yt}, \textsc{Grackle} \citep{GrackleMethod}, \textsc{Cloudy} \citep{Cloudy2013}
 %\bibliographystyle{apj}

### 2018-01-12 main.tex
Update on Overleaf.

@@
 We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium.
-We present the first application of these methods on a \textbf{XX Myr} simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
+We present the first application of these methods on a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
 Our methods are capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
@@
 Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions.
-We end with a discussion on how this work will impact our understanding of galactic chemical evolution on a species-by-species basis, with first results presented in a companion paper \textit{reference here?}.
+We end with a discussion on how this work will impact our understanding of galactic chemical evolution on a species-by-species basis.
 \end{abstract}
@@
 We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors.
-\textbf{This is the most self-consistent model for Type 1a supernovae in galaxy scale simulations.
-(worth mentioning?
-maybe softer version of this?)} We note however that for the low SFR's in our isolated dwarf galaxy simulations, the first SNIa only appears after a few hundred Myr of simulation time.
-For example, by the end of the simulation presented here (XXX Myr), only XXX have gone off.
+This is the most self-consistent model for Type 1a supernovae in galaxy scale simulations.
+\textbf{(Is this worth mentioning like this?
+or too strong a statement?)} We note however that for the low SFR's in our isolated dwarf galaxy simulations, the first SNIa only appears after a few hundred Myr of simulation time.
+For example, by the end of the simulation presented here (500~Myr), only 18 have gone off.
 At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
@@
 This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc.
-These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc, or $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012} (need more cite).
+These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc, or $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012}.
 We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in a future work.
@@
 \label{sec:results}
-We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first \textbf{350 Myr} after the first star forms.
+We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first 500~Myr after the first star forms.
 This occurs 43 Myr after initialization.
-Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.\footnote{All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset \textbf{changeset number}.}
-
 Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle formed, and the galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy.
 ISM properties are calculated considering only the gas contained within the disk of the galaxy.
+
+Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.
+All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset \textbf{changeset number}.
 
@@
 In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points.
-Towards the end of the simulation time, the half light radius is \textbf{$389 \pm 21$ pc}, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
+Towards the end of the simulation time, the half light radius is $390 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
 
@@
 The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
-This figure shows the 30~Myr time averaged scale height of all gas in the disk throughout the simulated time.
+This figure shows the 40~Myr time averaged scale height of all gas in the disk centered on the given time.
 Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights between 50--200~pc.
-Although the disk remains thin beyond the stellar radius of our galaxy, it is resolved at all radii.
-The low central scale heights at 100 Myr (dashed, purple) compared to those at 200-300~pc are due to a general lack of gas in this central region from the initial burst of star formation.
-This is clear in the density panels of Fig~\ref{fig:panel_x}.
-Although the cold disk is thin, this property is currently unconstrained in galaxies of this mass due to low ($\sim$ 100 pc or worse) spatial resolution \citep[e.g.][]{Bernstein-Cooper2014}.
+Although the disk remains thin beyond the stellar radius of our galaxy (a scale height of around 40~--~60~pc), it is resolved at all radii.
+By the end of the simulation, the majority of the gas has a scale height of $\sim$100~pc.
+Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging.
+For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100 - 200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
 %We additionally compute the mass weighted height of the disk, defined as $H = (\sum{Mz^2}/\sum{M})^{1/2}$, where the summation is over each gas cell, as a function of radius (not shown here).
@@
 
-We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.
-(By the end of the simulation, there have \textbf{only been XX Type 1a supernovae}.) Within the first 40 Myr of evolution the SFR rises quickly to between $2--4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly this level for 100 Myr, and drops to an average of about $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ for the remainder of the simulation, with large fluctuations.
-The SNR tracks the SFR with a time delay, capturing the rough rule of thumb that there is one core collapse supernovae per 100 M$_{\odot}$ of star formation.
-Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.33 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
-We note the discontinuity in SFR near 340~Myr represents a 10~Myr period without any star formation.
+We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type 1a rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between $2--4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly this level for 100 Myr, and drops to an average of about $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations.
+By the end of the simulation, the SFR is very low and infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$.
+The SNR tracks the SFR with a time delay, with roughly one core collapse supernovae per 100 M$_{\odot}$ of star formation.
+Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 9.93 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$.
 We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.
@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about \textbf{$6 \times 10^5$ M$_{\odot}$, or roughly 17\%} of the total mass in the galaxy's disk.
-The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction doubles over time to roughly 35\%.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\%, of the total mass in the galaxy's disk.
+The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\% and is about equal with the HI gas.
 This is because the total amount of mass in the disk decreases through feedback driven winds, but the H$_2$ is preferentially retained.
@@
 \caption{Left: The SFR and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left).
-Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the galaxy over time.
+Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.
 Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.}
+% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
 \label{fig:sfr_mass_evolution}
@@
 See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-Each of these exist in our simulations, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and diffuse and shock heating from stellar feedback throughout the galaxy's evolution.
+Each of these phases exist throughout our simulation, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and diffuse and shock heating from stellar feedback throughout the galaxy's evolution.
 Here we discuss the phase properties of the gas within the inner halo of our dwarf galaxy.
 
-Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the final 50 Myr of simulation time.
+Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300 -- 350~Myr.
 One can readily identify the two most massive regions of gas in the simulation, a low density, warm phase produced through ionization and supernovae heating, and a cold, high density phase which makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
@@
 \includegraphics[width=0.95\linewidth]{phase_diagram.png}
-\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gass interior to 0.25~$R_{\rm vir}$, averaged over the final 50 Myr of simulation time.
+\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gass interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr.
 The two red dashed lines show lines of constant pressure for guidance.
 The region in the lower right corner indicates our density and temperature thresholds for star formation.}
+% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
 \label{fig:phase}
@@
 
-The mass of the ISM in our dwarf galaxy is dominated by the CNM over the entire simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
-Together, the CNM and WNM comprise roughly 90\% of the galaxy's mass throughout most of its evolution.
-While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume each, though the two warm phases dominate.
-The volume fractions are subject to significantly more fluctuations over time, due to the low SFR and supernova rate of our galaxy.
+The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
+At this point the molecular component dominates through the end of the simulation.
+
+Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining dominated by the WNM.
+While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume fraction.
+However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy.
 Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-These results are in some contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}.
+These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}.
 In short, they find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass.
 Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few.
-\textbf{Note to look into this / discuss a little further since it is different than previous sims}
+\textbf{Do I need to discuss a little further since it is different than previous sims?
+If so, where should I go with this?}
 
@@
 \includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
-\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. This figure only includes gas present within the disk of the galaxy.}
+\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM.}
+% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
 \label{fig:ISM_evolution}
@@
 This is particularly not surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
-In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over the last 50 Myr of simulation time.
+In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 50 Myr from 300--350~Myr.
 The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
@@
 
-\textbf{Note to remember to discuss: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e.
+\textbf{In response to MM's comment: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e.
 how does this compare to a uniform or 1D radial profile).
@@
 \caption{
-Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over the final 50 Myr of simulation time.
-Here we define the midplace as within 2.5~$dx$ of z = 0, or 4.5~pc.
+Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr.
+Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc.
 The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
@@
 The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
-We use the 10 Myr averaged SFR to compute the mass loading rates.
+Generally, other works use long timescale measurements of the SFR ($\sim$~Gyr) to compute the mass loading factor.
+For consistency in these works, we use the 500~Myr average SFR for computing the mass loading factor.
 The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time.
@@
 \label{sec:chemical evolution}
-\textbf{Commented out all previous discussion of species abundance retention differences and stellar abundances to save for a future paper.}
+\textbf{This section saw significant change. Removed previous mention of stellar abundances and species retention fractions. Much of below is new(ish)}
 
@@
 where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-The metal mass loading factor at radii interior to 0.5~$R_{\rm vir}$ are much more similar than the total gas mass loading factor in Figure~\ref{fig:mass_outflow}, indicating $\dot{M}_{\rm metal}$ varies less with radius than the total mass outflow rate.
-At these radii, $\eta_{\rm metal}$ is almost always above unity, reaching values of 7-8 for much of the evolution.
-These values are quite large, but perhaps not surprising for a low mass dwarf galaxy.
-Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ an order of magnitude below this, typically between 0.5 and 1 \citep{Li2017,Fielding2017}.
-\cite{Muratov2017} computes a normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$ for their galaxies, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
-Our galaxy is slightly broadly consistent but slightly above this finding, with an average $\eta_Z = 0.04$, fluctuating between 0.01 and 0.08.
+We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions.
+For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but each increases, fluctuating around unity for the second half of the simulation.
+Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}.
+\cite{Muratov2017} computes a slightly different value for their galaxies, a normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
+Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.
 
@@
 This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy.
-It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, or 20\% by the end of the simulation.
-The CGM metal content is falling at the end of the simulation, due mostly to ejection from the virial radius, but there is some re-accretion of metals from the CGM into the disk as suggested by the slight increase in disk metal fraction at the end of the simulation.
-It is reasonable to expect that the fraction of metals contained in the disk reaches a steady state, as possibly suggested by the diagram, but if the star formation of this galaxy is bursty over long timescales, this will certainly fluctuate over time depending on the relative significance of feedback driven outflows and re-accretion of ejected gas.
+It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, or 40\% by the end of the simulation.
+Likewise, the CGM metal content is continually decreasing until the end of the simulation time, from loss through the virial radius of the halo.
+Although the metal content of the ISM is gradually decreasing throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution.
 %\textbf{closing sentence}
@@
 It is important to understand how metals from each source of stellar yields (stellar winds, AGB star winds, and supernovae) enrich the ISM.
-It is unclear how uniform metal distributions are in ultrafaint dwarf galaxies, and over what timescales newly produced metals mix across the galaxy.
+Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}.
+This requires that metal mixing and transport must occur much more rapidly ($\sim 10^2$~Myr) than what is possible assuming transport at the cold gas sound speed ($\sim 1$~Gyr).
+This suggests either that metals are transported first through a hot phase or are driven through efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}.
+How metal abundances vary in detail within these galaxies, beyond 1D radial profiles, and whether or not abundance distributions depend on the metal species is uncertain.
+It is even more unclear as to how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few HII regions for a detailed examination.
+
 We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, in addressing these questions with Fig~\ref{fig:metal_slices}.
 The top two panels give the slices of number density (top left) and temperature (top right) in the mid-plane of a portion of our dwarf galaxy.
-These serve to guide the eye in the lower panels, clearly indicating regions with dense, cold gas clouds ($n \sim 100 \rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
+These serve to guide the eye in the lower panels, clearly indicating regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
 The bottom panels give abundance ratios for oxygen and hydrogen (bottom left), nitrogen and hydrogen (bottom middle), and nitrogen and oxygen (bottom right).
@@
 We caution against making direct comparisons of these images to observed abundances of dwarf galaxies, as we do not capture a cosmologically realistic chemical evolution in these relatively short ($< 1$~Gyr) simulations.
-This will be addressed in future work.}
+This will be addressed in future work.
+\textbf{I need to adjust axis label size}}
 \label{fig:metal_slices}
@@
 
-Beginning with $log(O/H)$, the gas from the recent SN explosion is abundantly clear, with a higher oxygen abundance by at least 1 dex from its surroundings.
+Beginning with log(O/H), the gas from the recent SN explosion is abundantly clear, with a higher oxygen abundance by at least 1 dex from its surroundings.
 The oxygen abundance throughout the rest of the ISM does vary, with some dense regions showing slightly higher oxygen abundance than their less dense surroundings, but the variation is not dramatic.
-$log(N/H)$, however, shows slightly more significant variation throughout the ISM.
+log(N/H), however, shows slightly more significant variation throughout the ISM.
 Comparing the two diagrams, one can pick out regions with differing abundances between the two species.
-This is clear in the $log(N/O)$ slice, emphasizing regions that are over/under abundance in either species.
-The gas from the SN explosion, for example, has a low $log(N/O)$ due to the significant amount of oxygen released in the SN.
+This is clear in the log(N/O) slice, emphasizing regions that are over/under abundance in either species.
+The gas from the SN explosion, for example, has a low log(N/O) due to the significant amount of oxygen released in the SN.
 Oxygen is generally more abundant than nitrogen throughout the ISM, particularly in the warm, diffuse gas.
-However, the dense, cold gas typically has a greater $log(N/O)$ than its surroundings, indicating that nitrogen may more easily pollute cold gas than oxygen.
-These differences are also evident with a few regions of warmer gas (small sliver at center of figure, horseshoe shaped feature in lower right, and the blob in the upper right) where $log(N/O) > 0$, indicating an overabundance of nitrogen as compared to oxygen.
+However, the dense, cold gas typically has a greater log(N/O) than its surroundings, indicating that nitrogen may more easily pollute cold gas than oxygen.
+These differences are also evident with a few regions of warmer gas (small sliver at center of figure, horseshoe shaped feature in lower right, and the blob in the upper right) where log(N/O) > 0, indicating an overabundance of nitrogen as compared to oxygen.
 At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse supernovae and winds from more massive stars.

### 2018-02-08 main.tex
Update on Overleaf.

@@
 \begin{abstract}
-We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we are capable of capturing detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae.
+We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
+For the first time in galaxy scale simulations, we are capable of capturing detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
 %This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
-In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species \textbf{list here?}.
+In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, St, Y, and Ba.
 We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium.
 We present the first application of these methods on a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
-Our methods are capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
+We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
 Effective feedback drives significant metal enriched outflows, leading to a low metal retention fractions consistent with observations.
@@
 Specifically, simulations presented here were conducted at changeset 445de816fd99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
-We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}.
+We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}).
 Self-gravity is computed with a multigrid Poisson solver.
@@
 We require that the Jeans length be resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution.
-Our maximum resolution in the simulations presented here is 1.8 pc.
+Our maximum resolution in the simulations presented here is 1.8~pc.
 At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation.
@@
 This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
-The use of a pressure floor is common in galaxy scale simulations with limited dynamic range.
-%(\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out.
-Leave it in?})
+The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, RobertsonKravtsov2008}.
+
+%(\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out. Leave it in?})
 
@@
 As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
-Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities.
+Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}.
 To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.
 We have made these new tables public in the main \texttt{Grackle} repository.
-These are both discussed in greater detail in Appendix ~\ref{appendix:cooling}.
+These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
 
@@
 Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
-Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively \textbf{justify choices}.
+Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively.
 We limit the fraction of a cell's gas mass that is converted into stars by requiring $M_{\rm gas} > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and $M_{\rm max,*}$ is the maximum star mass (100 M$_{\odot}$).
@@
 If it does, we randomly sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$.
-We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and maximum stellar mass of 100 M$_{\odot}$.
+We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
 Our lower limit on stellar masses ensures that we are able to both directly track all particles that participate in some way to feedback and metal enrichment, and follow longer lived start particles, while reducing the computational expense of following many low mass stars that have no dynamical impact on the galaxy evolution.
-100 M$_{\odot}$ is a reasonable upper limit on the most massive star \textbf{sounds weak}.
-
-Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a \textbf{1~km~s$^{-1}$ velocity dispersion - justify!}.
+
+Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
+This dispersion captures some of the unresolved gas motions below the resolution limit and smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations.
 Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
@@
 \citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.
+We neglect the effects of binary star evolution on stellar feedback, but discuss the significance of this in Section~\ref{sec:binary stars}.
 
@@
 We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors.
-This is the most self-consistent model for Type 1a supernovae in galaxy scale simulations.
-\textbf{(Is this worth mentioning like this?
-or too strong a statement?)} We note however that for the low SFR's in our isolated dwarf galaxy simulations, the first SNIa only appears after a few hundred Myr of simulation time.
+This is the most self-consistent model for Type Ia supernovae in galaxy scale simulations.
+We note however that for the low SFR's in our isolated dwarf galaxy simulations, the first SNIa only appears after a few hundred Myr of simulation time.
 For example, by the end of the simulation presented here (500~Myr), only 18 have gone off.
@@
 %\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):} 
-The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope ($\beta$) and normalization ($N_{\rm 1a}/M_{\rm SF}$) are observables.
-The latter represents the number of Type 1a supernova per mass of star formation.
+The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope ($\beta$) and normalization ($N_{\rm Ia}/M_{\rm SF}$) are observables.
+The latter represents the number of Type Ia supernova per mass of star formation.
 By assuming an IMF, one can write down the fraction ($\eta$) of stars capable of forming a SNIa progenitor that \textit{will} explode within a Hubble time.
@@
 Due to these uncertainties, and given that our dwarf galaxy has a low dust content (and therefore a low IR opacity), we ignore this effect.
-\textbf{Greg referenced Dong Zheng in comments but I could not find anything for this}
+\textbf{cite davis and stone, Zhang and davis?}
 
@@
 \label{sec:diffusive heating}
-We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from our stars.
+We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from each of our star particles.
 Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
@@
 Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.
-All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset \textbf{changeset number}.
+All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset 66452ba.
 
@@
 
-We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type 1a rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between $2--4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly this level for 100 Myr, and drops to an average of about $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations.
+We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between $2---4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly this level for 100 Myr, and drops to an average of about $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations.
 By the end of the simulation, the SFR is very low and infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$.
@@
 \centering
-\includegraphics[width=0.475\linewidth]{sfr_snr}
+\includegraphics[width=0.475\linewidth]{sfr_snrx100}
 \includegraphics[width=0.475\linewidth]{mass_evolution}
@@
 The distribution has a very long tail out to and beyond 500~km~s$^{-1}$.
-The dominant launching mechanism in this simulation are supernovae (Emerick et.
-al.
-in prep), generating a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
+The dominant launching mechanism in this simulation are supernovae, generating a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
 However, as shown, the HIM comprises very little of the outflow by mass.
@@
 
-\textbf{AE: Took plot and discussion of outflow metallicities out and replaced with metal mass loading factor (below)}
+%\textbf{AE: Took plot and discussion of outflow metallicities out and replaced with metal mass loading factor (below)}
 %In Figure~\ref{fig:outflow_metallicity} we show the average ISM metallicity (black), halo metallicity (blue), and outflow metallicities (orange) at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
@@
 \includegraphics[width=0.32\linewidth]{log_NO}
-\caption{Five slices in the mid-place of our dwarf galaxy at an arbitrary time (XXX Myr) demonstrating the power of our chemical evolution model.
+\caption{Five slices in the mid-place of our dwarf galaxy at an arbitrary time demonstrating the power of our chemical evolution model.
 We show the number density and temperature in this region of the galaxy (top row), along with three different elemental abundance ratios, O/H (bottom left), N/H (bottom middle), and N/O (bottom right).
@@
 This will be addressed in future work.
-\textbf{I need to adjust axis label size}}
+\textbf{(AE: need to adjust axis label size)}}
 \label{fig:metal_slices}
@@
 Our model suggests that H$^{-}$ and a UVB (in the absence of a local radiation field) are critical components in H$_2$ formation in small dwarf galaxies.
-It is not surprising that the gas phase reactions dominates over grain XXX in this low metallicity regime \citep{Glover2003}, but the total amount of H$_2$ formed is perhaps surprising.
+It is not surprising that the gas phase reactions dominate over grain catalysis in this low metallicity regime \citep{Glover2003}, but the total amount of H$_2$ formed is perhaps surprising.
 However, the rate coefficients association with gas-phase H$_2$ formation are uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
 %In addition, \cite{Glover2006} demonstrated that the total amount of H$_2$ formed can be quite sensitive to the initial conditions.
-Finally, our model lacks additional chemistry which may be important in the formation and destruction of H$_2$, including $HD$ chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
+Finally, our model lacks additional chemistry which may be important in the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
 It is unclear how the combination of all of these effects with behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
@@
 Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, roughly \textbf{95\%} of the tracked metals produced during the simulation no longer reside within the galaxy's disk.
+As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during the simulation no longer reside within the galaxy's disk.
 At the end of our simulation, we agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
@@
 In our case, no metals have been ejected beyond the virial radius; this is not surprising however, given that metals ejected beyond the halo would need to travel with an average velocity of 150 km s$^{-1}$ for the entirety of our simulation time.
-We find \textbf{32\%} of all metals lie within 1 kpc of the center of our galaxy, \textbf{75\%} within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and only \textbf{10\%} outside $R_{\rm vir}$.
-Over time, the re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
-Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) returns.
-Unfortunately, we cannot yet speak to how this gas evolves over time, but will investigate this in future work with our feedback model.
+We find 13.7\% of all metals lie within 1 kpc of the center of our galaxy, 26.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 38.6\% outside $R_{\rm vir}$.
+The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
+Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return.
+Our model seems to suggest that many of the metals ejected into the halo will not be recycled back into the galaxy, but this is difficult to determine with only 500~Myr of evolution.
+In addition, the accretion of pristine gas from the IGM could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals.
+This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.
 
@@
 \subsection{Detailed Stellar Evolution and Binary Stars}
-
+\section{sec:binary stars}
 % Although we track individual stars and assign properties to each based on stellar evolution models, these properties are fixed.
@@
 
-Most notably, our galaxy is characterized by (\textbf{figure out order... and spacing})
+For our simulated dwarf galaxy, we find:
 \begin{enumerate}
 \item Multi-channel feedback is effective in this galaxy in regulating star formation consistent with the KS relationship and extended Schmidt law in observed galaxies. 
-\item A thin ($\sim$~50~pc), yet resolved, disk outside the stellar radius, with larger ($\sim 100 - 200$~pc) scale heights driven by feedback.
-This is comparable to the resolution limit of observed, gaseous UDG's.
 \item This feedback drives large outflows ($\eta > 100$) with metal mass loading factors greater than unity ($\eta_{\rm metal} \sim 5$).
 By mass, nearly all of this outflow is moving with velocities below 100 km~s$^{-1}$, but there is a significant tail towards velocities up to 1000 km s$^{-1}$.
-This galaxy is consistent with observed metal retention fractions of UDG's, loosing XX\% of produced metals to the halo.
-\item The ISRF of our galaxy is highly varying in time by orders of magnitude, though is surprisingly uniform in space at any given time. 
+This galaxy is consistent with observed metal retention fractions of UDG's, loosing 89\% of produced metals to the halo.
+\item A thin scale height ($\sim$~50~pc), yet resolved, in the gaseous disk outside the stellar radius, with larger scale heights ($\sim 100 - 200$~pc) driven by feedback.
+This is comparable to the resolution limit of the diffuse HI in observed, gaseous ultrafaint dwarf galaxies.
+\item The ISRF of our galaxy is highly varying in time by orders of magnitude, though is relatively uniform in space at any given time.
+It is unclear how important these fluctuations are as a source of feedback, or if the affect can simply be approximated with a time averaged radial profile.
+\item Our galaxy forms a significant amount of H$_2$ through gas ($H^-$) reactions.
+This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy.
+This leads to high molecular gas fractions, with a H$_2$ mass comparable to the HI content by the end of the simulation.
+This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies.
 \end{enumerate}
 
-In future works in this series, we will investigate in more detail how metal enrichment proceeds in this galaxy.
-We can directly study, on a species-by-species basis, how metals evolve through the phases of the ISM, from hot, ionized gas into star forming regions.
-This evolution is poorly understood, but has direct implications for chemical evolution models, and can inform the assumed time scales with which new metals enrich future stellar populations in galaxies.
-\textbf{how much detail should I go into on future work?}
+Finally, we used O and N as examples to briefly demonstrate that there are discernible differences in how individual metal species are distributed within the ISM of our galaxy.
+In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and the gas flows of individual metals through the halos of low mass dwarf galaxies.
+In addition, we will investigate the role of each of our sources of feedback plays in driving dwarf galaxy chemodynamics.
+\textbf{Do I need more detail on future work?}
 
@@
 We gratefully recognize computational
-resources provided by NSF XSEDE through grant number TGMCA99S024, \textbf{Pleiades alloc}, Columbia University, and the \textbf{Simons Foundation}. Analysis in this work
+resources provided by NSF XSEDE through grant number TGMCA99S024, \textbf{need Pleiades alloc}, Columbia University, and the \textbf{(need proper ack.
+for Simons computing resources)}.
+Analysis in this work
 made significant use of the publicly available yt (http://ytproject.org)
@@
 \appendix
+\renewcommand\thefigure{\thesection.\arabic{figure}}    
+\setcounter{figure}{0}
 
@@
 \item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
-\item Molecular: \textbf{MAY CHANGE} $T < 10^2$, $f_{\rm H_2} > 0.5$
+\item Molecular: $T < 10^2$, $f_{\rm H_2} > 0.5$
 \end{enumerate}
@@
 \label{appendix:resolution study}
-Insert some light resolution study details here.
-Ultimately this will be somewhat difficult as we need to go into how this is challenging since star formation criteria will change as resolution scales.
+We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate (left), mass evolution (middle), and metal ejection/retention fractions (right) for our high resolution simulations (solid) as compared to two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc.
+The physics in each of these simulations remains the same.
+However, our star formation algorithm is tied to resolution, since star formation proceeds in gas at densities where the Jeans mass becomes unresolved at the maximum resolution.
+A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.33\linewidth]{sfr_resolution_study.png}
+\includegraphics[width=0.33\linewidth]{mass_evolution_resolution.png}
+\includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
+\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), and 7.2~pc run (dash-dotted).
+We also include a 3.6~pc run with an initial SN driving rate increased by a factor of 2 (dashed).
+The line colors in the middle panel are the same as in Figure~\ref{fig:sfr_mass_evolution}, where the total disk mass is shown in black, cold gas mass in blue, H$_2$ mass in orange, and stellar mass in red.}
+\label{fig:resolution}
+\end{figure*}
+
+As shown in these diagrams, resolution certainly changes the evolution, but not dramatically.
+We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation, but point has not been confirmed.
+Clearly, the initial SFR over the first 100~Myr is different in each simulation; it is larger in each of the lower resolution runs.
+This is because the initial SN driving is less resolved, leading to over cooling and an increase in the initial star formation rate.
+This is much less an issue for the SN from real star particles as the pre-SN feedback (winds and radiation) are capable of decreasing the local density enough to resolve the Sedov radius.
+To test this, we re-ran the 3.6~pc run with an increase in the initial SN driving rate by a factor of 2, which subsequently lowers the initial SFR.
+
+The largest qualitative difference between these runs is the H$_2$ mass.
+As discussed in this work, the H$_2$ mass fraction of our fiducial run is quite high, driven by significant H$_2$ production from gas-phase reactions and the preferential retention of cold, dense H$_2$ gas in feedback driven outflows.
+However, each of the lower resolution runs produce much less H$_2$ (by a factor of XX) than our fiducial run.
+This is certainly an issue in interpreting the generality of our H$_2$ mass fractions in our fiducial run, and requires more tests to confirm.
+However, it is not unreasonable to expect that the H$_2$ production occurs most effectively at densities not captured in the 3.6~pc and 7.2~pc runs.
+This suggests that most of our H$_2$ production in the fiducial run occurs in gas with densities above 50~cm$^{-3}$.
+To clarify the gas phase differences between these simulations, we present the temperature-density phase diagrams for our 3.6~pc (left) and 7.2~pc (right) simulations in Figure~\ref{fig:phase_resolution} over the same time interval as that presented for our fiducial run in Figure~\ref{fig:phase}.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.475\linewidth]{3pc_phase.png}
+\includegraphics[width=0.475\linewidth]{6pc_phase.png}
+\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Figure~\ref{fig:phase}.}
+\label{fig:phase_resolution}
+\end{figure*}
+
+Finally, each of the lower resolution runs retain a surprisingly similar fractions of their produced metals in their disks (black curves in right panel of Figure~\ref{fig:resolution}), but this is about a factor of 2 below what is found in the fiducial run (5\% vs.
+10\%).
+The amount that escapes the halo is significantly more, however.
+This is an interesting difference, as the resolution decrease primarily affects the disk of the galaxy; little to none of the halo volume is refined to the highest resolution, and so should be unaffected by this change.
+\textbf{I'm a bit puzzled by this difference...}
+
 %\section{Pre-SN Feedback with and without radiation}

### 2018-02-09 main.tex
Update on Overleaf.

@@
 %This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
-In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, St, Y, and Ba.
+In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
 We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium.
@@
 We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
-Effective feedback drives significant metal enriched outflows, leading to a low metal retention fractions consistent with observations.
+Effective feedback drives significant metal enriched outflows, leading to low metal retention fractions consistent with observations.
 Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions.
@@
 
-The native smooth particle hydrodynamics (SPH) scheme is incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
+Fully Lagrangian schemes, like native smooth particle hydrodynamics (SPH), are incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
 This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017a}.
-Even more, a given parameterization is not necessarily applicable generally \citep{Revaz2016}, though recent studies have shown great improvements to this end \citep{Escala2017}.
-Metal mixing efficiencies may also vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
+Even more, there are many possible sub-grid models that are not applicable in every regime \citep[see ][]{Revaz2016}, though recent studies have shown great improvements in characterizing various methods \citep{Escala2017}.
+While mixing occurs in Eulerian codes without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution or additional viscosity to reduce.
+Molecular diffusion is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
+Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
 Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources)
@@
 the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
-The variations in how one handles sub-grid metal injection and metal mixing schemes can lead to challenges in connecting models to observations and the fundamental physics that drives galaxy evolution.
+The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
 \textbf{Still not sure about this sentence - but I do need a way to cite mentioned papers:} Extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.
@@
 
-We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mesh refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies.
+We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies.
 The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms.
@@
 In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
-This opens an exciting new channel for testing models of galaxy evolution by enabling us to leverage current and ongoing observations probing the detailed chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
-
-This paper is the first in a series of papers examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
+This opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
+
+This paper is the first in a series examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
 In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}.
@@
 We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from each of our star particles.
+The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the SEDs for each gridded star.
+Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Section~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
 Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
@@
 In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rates.
+We compute the stellar LW flux again from the OSTAR2002 grid by integrating the SEDs over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}).
 Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
@@
 The galaxy presented in this work is constructed to be similar to the observed properties of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
-Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4} Z_{\odot}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}.
+Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity fraction of $Z \sim 5.4\times10^{-4}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}.
 Our dwarf galaxy is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
@@
 We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first 500~Myr after the first star forms.
-This occurs 43 Myr after initialization.
-Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle formed, and the galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy.
+Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle forms, which is 43~Myr after the actual initialization of the simulation.
+The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy.
 ISM properties are calculated considering only the gas contained within the disk of the galaxy.
@@
 We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation \textit{(list times here)}.
+Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation (0, 150, 300, and 500 Myr).
 In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points.
@@
 \includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
-\caption{ \textbf{need to adjust overlapping labels} Edge-on views of our dwarf galaxy at four different times in its evolution, separated by 100~Myr, beginning with the time at first star formation and ending at 300 Myr.
+\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0 Myr, 150 Myr, 300 Myr, and 500 Myr.
 Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and H$_2$ column density (fourth row).
@@
 Interestingly, there is significant structure well above the gas disk in the form of dense clouds and filamentary features, as seen in the edge-on projections.
-These gas cold gas clumps appear to have typical sizes on order of $\sim$ 10 pc, but with lower density tails that can extend up to 100 pc.
+These cold gas clumps appear to have typical sizes on order of $\sim$ 10 pc, but with lower density tails that can extend up to 100 pc.
 These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy.
@@
 \includegraphics[width=0.975\linewidth]{scale_height}
-\caption{The total gas scale height at various times throughout the simulation.}
+\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figures~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
 \label{fig:scale_height}
@@
 We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work.
-\textbf{is last bit on CR heating and SF gas OK?}
 
@@
 Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few.
-\textbf{Do I need to discuss a little further since it is different than previous sims?
-If so, where should I go with this?}
+The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future works.
 
@@
 The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}.
-This is particularly not surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
+This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
 In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 50 Myr from 300--350~Myr.
@@
 It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, or 40\% by the end of the simulation.
-Likewise, the CGM metal content is continually decreasing until the end of the simulation time, from loss through the virial radius of the halo.
+Likewise, the CGM metal content is continually decreasing until the end of the simulation, from loss through the virial radius of the halo.
 Although the metal content of the ISM is gradually decreasing throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution.
+See Section~\ref{sec:obs_metals} for further discussion.
 %\textbf{closing sentence}
@@
 How metal abundances vary in detail within these galaxies, beyond 1D radial profiles, and whether or not abundance distributions depend on the metal species is uncertain.
-It is even more unclear as to how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few HII regions for a detailed examination.
+It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few HII regions for a detailed examination.
 
@@
 
-Beginning with log(O/H), the gas from the recent SN explosion is abundantly clear, with a higher oxygen abundance by at least 1 dex from its surroundings.
+Beginning with log(O/H), the gas from the recent SN explosion is abundantly clear, with a higher oxygen abundance by at least 1 dex than its surroundings.
 The oxygen abundance throughout the rest of the ISM does vary, with some dense regions showing slightly higher oxygen abundance than their less dense surroundings, but the variation is not dramatic.
@@
 It is possible, then, that metal mixing within the ISM (and also metal ejection from the ISM) is a process is species dependent.
-We will investigate this point, and any potential observational consequences in stellar abundances, in future projects.
-A more detailed analysis is beyond the scope of this work.
+A more detailed analysis is beyond the scope of this work, but we plan to investigate this point, and potential observational consequences in stellar abundances, in future work.
 % reference my other paper if it is ready-ish by the time I submit this one.
@@
 The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted \ion{H}{1} surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}.
-However, the sample of isolated, gaseous dwarf galaxies with and $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
+However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
 In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) relation (left) for low mass galaxies, and the extended Schmidt law (ESL) (right).
@@
 Plotted as points on both plots are recent observations from the SHIELD sample \citep{Teich2016}.
-On the left, we also give the best fit line to galaxies from the FIGGS sample from \cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \cite{Shi2011}.}
+On the left, we also give the best fit line to galaxies from the FIGGS sample from \cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \cite{Shi2011}.
+The simulations points are colored by time, with dark / purple early and light / green late.
+This is simply to indicate there is no obvious correlation with time in this diagram.}
 \label{fig:KS}
@@
 
-In both panels, we also include recent observational constraints from these relationships.
+In both panels, we also include recent observational constraints on these relationships.
 For the KS relationship we include the best fit line from \citet{Roychowdhury2014} (black, dashed).
@@
 Finally, our model lacks additional chemistry which may be important in the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
-It is unclear how the combination of all of these effects with behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
+It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
 This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
@@
 Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, and close enough to the Milky Way to conduct this experiment.
-Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
+Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the remaining in ISM gas \citep{McQuinn2015}.
 As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during the simulation no longer reside within the galaxy's disk.
@@
 \subsection{Missing Physics}
-Although we include detailed physics in our simulations, there remains additional physical processes that may be relevant.These are discussed below.
+Although we include detailed physics in our simulations, there remains additional physical processes that may be relevant, these are discussed below.
 
@@
 \subsection{Detailed Stellar Evolution and Binary Stars}
-\section{sec:binary stars}
+\label{sec:binary stars}
 % Although we track individual stars and assign properties to each based on stellar evolution models, these properties are fixed.
@@
 Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}.
-Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
+Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
 % does this affect yields??
@@
 
-Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochasitcally assigning binary star properties to some subset of our individual stars.
+Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars.
 This is beyond the scope of this project, but will be investigated in future works.
@@
 \item Multi-channel feedback is effective in this galaxy in regulating star formation consistent with the KS relationship and extended Schmidt law in observed galaxies.
-\item This feedback drives large outflows ($\eta > 100$) with metal mass loading factors greater than unity ($\eta_{\rm metal} \sim 5$).
-By mass, nearly all of this outflow is moving with velocities below 100 km~s$^{-1}$, but there is a significant tail towards velocities up to 1000 km s$^{-1}$.
-This galaxy is consistent with observed metal retention fractions of UDG's, loosing 89\% of produced metals to the halo.
-\item A thin scale height ($\sim$~50~pc), yet resolved, in the gaseous disk outside the stellar radius, with larger scale heights ($\sim 100 - 200$~pc) driven by feedback.
-This is comparable to the resolution limit of the diffuse HI in observed, gaseous ultrafaint dwarf galaxies.
+See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}.
+
+\item This feedback drives large outflows ($\eta \sim 50$ at 0.25~R$_{\rm vir}$) with metal mass loading factors near unity.
+By mass, nearly all of this outflow is moving with velocities below 100 km~s$^{-1}$, but there is a significant tail towards velocities up to 1000 km s$^{-1}$ (Figure~\ref{fig:outflow_velocity}).
+This galaxy is consistent with observed metal retention fractions of UFD's, retaining only $\sim$10\% of metals in the disk.
+By the end of the simulation the remaining metals reside within the virial radius ($\sim$50\%) and $\sim$40\% are ejected outside the virial radius.
+The fraction in the disk remains fairly constant towards the end of the simulation, but the metals in the halo are still evolving.
+See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.
+
+\item A thin, yet resolved, gas scale height ($\sim$~50~pc) beyond our stellar radius, with larger scale heights ($\sim 100 - 200$~pc) driven by feedback interior to the stellar radius.
+This is comparable to the resolution limit of the diffuse HI in observed, gaseous UFDs.
+See Figure~\ref{fig:scale_height}.
+
 \item The ISRF of our galaxy is highly varying in time by orders of magnitude, though is relatively uniform in space at any given time.
 It is unclear how important these fluctuations are as a source of feedback, or if the affect can simply be approximated with a time averaged radial profile.
+See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.
+
 \item Our galaxy forms a significant amount of H$_2$ through gas ($H^-$) reactions.
@@
 This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies.
+See Figure~\ref{fig:ISM_evolution}.
 \end{enumerate}
@@
 In addition, we will investigate the role of each of our sources of feedback plays in driving dwarf galaxy chemodynamics.
-\textbf{Do I need more detail on future work?}
 
@@
 As discussed in this work, the H$_2$ mass fraction of our fiducial run is quite high, driven by significant H$_2$ production from gas-phase reactions and the preferential retention of cold, dense H$_2$ gas in feedback driven outflows.
-However, each of the lower resolution runs produce much less H$_2$ (by a factor of XX) than our fiducial run.
+However, each of the lower resolution runs produce less H$_2$ (about 40\% less) than our fiducial run.
 This is certainly an issue in interpreting the generality of our H$_2$ mass fractions in our fiducial run, and requires more tests to confirm.

### 2018-02-13 main.tex
edits to introduction

@@
+%mm2 substantive changes marked with this comment tag, minor changes and wordsmithing done silently.  12-15 Feb
 \documentclass[twocolumn]{aastex61}
@@
 We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we are capable of capturing detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
 %This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
-In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
+We furthermore follow the star-by-star stellar yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
 We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium.
-We present the first application of these methods on a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
+We present the first application of these methods in a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
 We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
-Effective feedback drives significant metal enriched outflows, leading to low metal retention fractions consistent with observations.
+Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations.
 Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions.
-We end with a discussion on how this work will impact our understanding of galactic chemical evolution on a species-by-species basis.
+We end with a discussion on how this work impacts our understanding of galactic chemical evolution on a species-by-species basis.
 \end{abstract}
@@
 
-Due to its complexity, the detailed interstellar medium (ISM) and chemical abundance properties of galaxies
+%mm2 Due to its complexity, the 
+Detailed interstellar medium (ISM) and chemical abundance properties of galaxies
 %beyond total metallicity
@@
 
-Fully Lagrangian schemes, like native smooth particle hydrodynamics (SPH), are incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
+%mm2 I think there does need to be some introduction to this discussion:
+   However, the bulk of this work has been done with fully Lagrangian
+%mm2 Fully Lagrangian schemes, like native 
+smoothed particle hydrodynamics (SPH), 
+%mm2 are incapable of capturing
+    with a few recent exceptions  \citep{Few2012,Few2014,Vorobyov2015}. In its original form, 
+    SPH cannot model
+mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
 This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017a}.
 Even more, there are many possible sub-grid models that are not applicable in every regime \citep[see ][]{Revaz2016}, though recent studies have shown great improvements in characterizing various methods \citep{Escala2017}.
-While mixing occurs in Eulerian codes without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution or additional viscosity to reduce.
-Molecular diffusion is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
+While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution or additional viscosity to reduce.
+Molecular diffusion %mm2
+    or even turbulent mixing
+is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
 Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
@@
     that inject metals into 
+%mm2
+    different phases of 
 the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
 The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
-\textbf{Still not sure about this sentence - but I do need a way to cite mentioned papers:} Extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.
-
-Although increasing physical resolution reduces 
-%mm one's 
-reliance on sub-grid physics, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations (SSPs) are no longer valid \citep[as studied in detail in ][]{Revaz2016}.
-Below 10$^4$ M$_{\odot}$, SSPs do not fully sample the IMF, and cannot be considered average representations of stellar populations.
-This is acutely problematic at star particle masses comparable to or below the mass of the most massive individual star (or $\sim 100$ M$_{\odot}$).
+%mm2 [cited above] \textbf{Still not sure about this sentence - but I do need a way to cite mentioned papers:} Extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.
+
+%mm2 [broke up sentence]
+Increasing physical resolution reduces reliance on sub-grid physics for mixing.
+However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations (SSPs) then lose validity  \citep[as studied in detail by][]{Revaz2016}.
+Below 10$^4$ M$_{\odot}$, SSPs do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
+This is acutely problematic at star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
 Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
-%mm Perhaps the most naive, 
 The most straightforward
-solution is to remove the SSP formalism entirely and simply track stars as individual particles.
-However, the number of particles required to do so make this computationally prohibitive in all but the smallest of galaxies ($M_{*} \lesssim 10^{7} {\rm M_{\odot}})$, let alone in a cosmological simulation.
-%In this work, we 
-%mm follow stars as individual star particles, allowing us to place unprecedented detail on our
-%     do this, allowing unprecedented detail in our
-% accounting of stellar feedback processes and chemical enrichment.
-
+solution is to remove the SSP formalism entirely and simply track stars as individual particles,
+%mm2 [maybe it would be best to just remove this.] However, the number of particles required to do so make this computationally prohibitive in all but the smallest of galaxies ($M_{*} \lesssim 10^{7} {\rm M_{\odot}})$, let alone in a cosmological simulation.
+    which we do here.
+
+%mm2 [if we were to keep the previous sentence, we'd need to segue like this.]
+%   Nevertheless, we 
 We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies.
@@
 \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
-Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback of both massive stars and AGB stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
-
-Using star-by-star modeling, we are able to capture in more detail the stellar yields from individual stars released over their lifetime.
+Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar wind feedback from both massive stars and AGB stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
+%mm2
+  We include stellar feedback from stellar winds, core collapse and Type Ia supernovae,    
+  photoelectric heating, and ionizing radiation.
+
+Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. self-consistent set of stellar yields. 
+%mm2 
+    We track yields from massive star stellar winds, AGB star winds, and supernovae. 
 In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
-This opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
-
+This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed
+%mm2
+   distributions of
+chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
+%mm2 
 This paper is the first in a series examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. 
-In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}.
+%mm2 [this is somehow redundant with the previous paragraph.  I have moved a few things up.]
+% In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}.
 For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer.
-In addition, we couple to a self-consistent set of stellar yields %mm tables from the
-to track yields from massive star stellar winds, AGB star winds, and supernovae. We describe each mode of our multi-channel feedback 
-%mm implementation 
+In addition, we couple to a self-consistent set of stellar yields
+%to track yields from massive star stellar winds, AGB star winds, and supernovae. 
+We describe each mode of our multi-channel feedback 
 in detail below, and briefly discuss their implementation in an isolated dwarf galaxy simulation.
@@
 \label{sec:methods}
-In 
-%mm brief, 
-     summary, 
-we produce high-resolution galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
+%mm2 In      summary, 
+We produce high-resolution galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
 This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
-To properly model the ISM, we track non-equilibrium primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background.
+To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background.
 We
@@
     assume collisional ionization equilibrium for all other elements in order to
-use updated \texttt{Cloudy} metal line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$).
+use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$).
 Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback.

### 2018-02-14 main.tex
added a description of the sections to the end of the introduction

@@
 We describe each mode of our multi-channel feedback 
-in detail below, and briefly discuss their implementation in an isolated dwarf galaxy simulation.
+in detail in Sect.~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation
+%mm2 
+   in Sect.~\ref{sec:IC}, show results from this simulation in Sect.~\ref{sec:results}, discuss the 
+   results in Sect.~\ref{sec:discussion}, and conclude in Sect.~\ref{sec:conclusion}.
 
@@
 %mm2 In  summary, 
-We produce high-resolution galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
+We produce high-resolution, galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
 This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
@@
 use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$).
-Each star is assigned basic properties (surface gravity, effective temperature, radius, lifetime) from tabulated stellar evolution models, which inform how the stars deposit their feedback.
+Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
 We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure.
-In addition, we follow the optically thin non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
+In addition, we follow the optically thin, non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
 We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both.
@@
 \label{sec:results}
-We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first 500~Myr after the first star forms.
+We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first 500~Myr after the first star forms.
 Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle forms, which is 43~Myr after the actual initialization of the simulation.
@@
 
-\section{Discussion}
+\secton{Discussion}
 \label{sec:discussion}

### 2018-02-14 main.tex
small changes up to 2.2

@@
 We end with a discussion on how this work impacts our understanding of galactic chemical evolution on a species-by-species basis.
+{\bf the conclusion of this discussion should perhaps be mentioned.}
 \end{abstract}
@@
     assume collisional ionization equilibrium for all other elements in order to
-use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here (Z $\lesssim 0.1$ Z$_{\odot}$).
+use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
 Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
@@
 We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both.
-We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernovae progenitors.
+We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernova progenitors.
 We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star
@@
 In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked.
-This field is used to inform the heating/cooling physics and determines the metallicity of each star.
+This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth.
 These methods are discussed in full detail below.
@@
 
-We use the adaptive mesh refinement (AMR) hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodyanamical evolution and detailed feedback physics in a set of high resolution, isolated, low mass dwarf galaxies.
+We use the adaptive mesh refinement (AMR) hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies.
 \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions.
@@
 This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
-The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, RobertsonKravtsov2008}.
+The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001,RobertsonKravtsov2008}.
 
@@
 
-We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset 59adc76b3130.} \texttt{Grackle} is a freely available, open source multi-code library, designed to interface with a wide variety of astrophysical codes.
+We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset 59adc76b3130.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes.
 We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.

### 2018-02-14 main.tex
now compiles again
revisions to section 4

@@
 Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy.
-We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background (see \citep{GrackleMethod} for more details of this implementation).
+We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
 We assume \ion{He}{1} ionization generally follows \ion{H}{1}.
@@
 We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
+%mm2
+    {\bf Shouldn't the units here include s$^{-1}$ rather than s?}
 \begin{equation}
 \label{eq:PE}
-\Gamma_{\rm pe} = (1.3 \times 10^{-24} \mbox{~erg~s~cm}^{-3}) \epsilon n_{\rm H} G_{\rm eff} D 
+\Gamma_{\rm pe} = (1.3 \times 10^{-24} \mbox{~erg~s~cm}^{-3})\, \epsilon n_{\rm H} G_{\rm eff} D 
 \end{equation}
-where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\rm{exp}(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust to gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
+where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust to gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
 Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
@@
 \label{sec:results}
-We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first 500~Myr after the first star forms.
+We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first star forms.
 Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle forms, which is 43~Myr after the actual initialization of the simulation.
@@
 We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation (0, 150, 300, and 500 Myr).
+%mm2 [redundant with caption] Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation (0, 150, 300, and 500 Myr).
 In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points.
-Towards the end of the simulation time, the half light radius is $390 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
-
-The increased gravitational potential towards the center of our dwarf galaxy leads to an inside-out star formation evolution, whereby star formation propagates from the inner regions outward during the galaxy's evolution.
-This is obvious in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
-This region quickly becomes volume-filled with both warm and hot gas generated from radiation feedback and supernovae respectively.
-Both the ISM and the halo gas is multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident by the temperature slices in both panels.
+%
+These Figures show 
+%mm2 increased gravitational potential towards the center of our dwarf galaxy leads to [can we demonstrate this?
+Otherwise it seems like an unsupported claim, since it could have to do with other things like the surface density profile, the rotational velocity profile, etc.]
+inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
+This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
+%mm2 This region quickly becomes volume-filled with both 
+    This central region quickly fills with
+warm and hot gas generated from radiation feedback and supernovae respectively.
+Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels.
 The ISM properties are quantified further in Section~\ref{sec:phase}.
@@
 \includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
-\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0 Myr, 150 Myr, 300 Myr, and 500 Myr.
-Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and H$_2$ column density (fourth row).
-Each individual main sequence star particle is shown in the number density projections as a single black dot.}
+\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation.
+Shown are the density weighted projection of number density (top row), temperature slices (second row),
+%mm2 and integrated projections giving 
+\ion{H}{1} column density (third row), and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single black dot.}
 \label{fig:panel_x}
@@
 The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
-This figure shows the 40~Myr time averaged scale height of all gas in the disk centered on the given time.
-Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights between 50--200~pc.
-Although the disk remains thin beyond the stellar radius of our galaxy (a scale height of around 40~--~60~pc), it is resolved at all radii.
+This figure shows the scale height of all gas in the disk, averaged over 40~Myr periods centered on each given time.
+Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--200~pc.
+%mm2 [moved from above]
+  Towards the end of the simulation time, the half-light radius is $390 \pm 21$ pc, where the 
+  uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
+Although the disk remains thin beyond the half-light radius, with a scale height of around 40--60~pc, it is fully resolved at all radii.
 By the end of the simulation, the majority of the gas has a scale height of $\sim$100~pc.
+
 Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging.
-For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100 - 200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
+For Leo P, located at 1.7~Mpc, \ion{H}{1} observations that are capable of detecting the diffuse \ion{H}{1} throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest \ion{H}{1} clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
 %We additionally compute the mass weighted height of the disk, defined as $H = (\sum{Mz^2}/\sum{M})^{1/2}$, where the summation is over each gas cell, as a function of radius (not shown here).
@@
 \includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
-\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on projections/slices.}
+\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on views.}
 \label{fig:panel_z}
@@
 
-Interestingly, there is significant structure well above the gas disk in the form of dense clouds and filamentary features, as seen in the edge-on projections.
-These cold gas clumps appear to have typical sizes on order of $\sim$ 10 pc, but with lower density tails that can extend up to 100 pc.
+Interestingly, there is significant structure well above the gas disk in our model, in the form of dense clouds and filamentary features, as seen in the edge-on projections.
+These cold gas clumps appear to have typical sizes on order of $\sim 10$~pc, but with lower density tails that can extend up to 100 pc.
 These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy.
@@
 
-We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between $2---4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly this level for 100 Myr, and drops to an average of about $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations.
-By the end of the simulation, the SFR is very low and infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$.
+We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between 2--4$ \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly at this level for 100 Myr, and then drops to an average of about
+%mm2
+  {\bf [Shouldn't this be $4 \times 10^{-5}$?]}
+ $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations. By the end of the simulation, the SFR is very low and 
+%mm2
+   star formation events are
+infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$.
 The SNR tracks the SFR with a time delay, with roughly one core collapse supernovae per 100 M$_{\odot}$ of star formation.
@@
 %mm \footnote{  [This is rather too long for a footnote, I think.]
-The granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
+We note that the granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
 Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
@@
 By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\%, of the total mass in the galaxy's disk.
-The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\% and is about equal with the HI gas.
-This is because the total amount of mass in the disk decreases through feedback driven winds, but the H$_2$ is preferentially retained.
+The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\% and is about equal with the \ion{H}{1} gas.
+This is because the total amount of mass in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained.
 Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback.
@@
 Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.
-Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.}
+%mm2 Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.
+   Note that the supernova rate has been scaled by a factor of 100 to fit on the same vertical 
+   axis as the SFR.}
 % This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
@@
 
-\subsection{Phase Diagrams and ISM Properties}
+%mm2 \subsection{Phase Diagrams and ISM Properties}
+\subsection{ISM Properties}
+
 \label{sec:phase}
 
-Our simulations contain both ample resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
+Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
 We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
@@
 See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-Each of these phases exist throughout our simulation, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and diffuse and shock heating from stellar feedback throughout the galaxy's evolution.
-Here we discuss the phase properties of the gas within the inner halo of our dwarf galaxy.
-
-Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300 -- 350~Myr.
-One can readily identify the two most massive regions of gas in the simulation, a low density, warm phase produced through ionization and supernovae heating, and a cold, high density phase which makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
-Several notable features of the phase diagram include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
+Each of these phases exist throughout our simulation, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and
+%mm2 diffuse 
+  radiative
+and shock heating from stellar feedback throughout the galaxy's evolution. Here we discuss the %mm phase
+   thermodynamic 
+properties of the gas within the inner halo of our dwarf galaxy.
+
+Figure~\ref{fig:phase} shows the temperature-density 
+%mm2 phase diagram 
+    distribution
+of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr. One can readily identify the two
+%mm2  most massive regions of gas [eliminated phase language below for consistency with your claim a bit further down the para that there are not well-defined phases.]
+    regimes containing most of the mass 
+in the simulation: low density, warm gas produced through ionization and supernova heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
+Several notable features of the
+%mm2 phase diagram 
+     distribution
+include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
 We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
@@
 The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
-At this point the molecular component dominates through the end of the simulation.
+After this point, the molecular component dominates through the end of the simulation.
 
@@
 These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}.
-In short, they find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass.
+They find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass.
 Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few.
@@
 This diagram shows how dramatic the increase in ISRF near young, massive stars (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
-The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
+The striking contrast between the two diagrams is due to the shielding of the \ion{H}{1} ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
 From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy various greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
@@
 
-\secton{Discussion}
+\section{Discussion}
 \label{sec:discussion}
@@
 \item A thin, yet resolved, gas scale height ($\sim$~50~pc) beyond our stellar radius, with larger scale heights ($\sim 100 - 200$~pc) driven by feedback interior to the stellar radius.
-This is comparable to the resolution limit of the diffuse HI in observed, gaseous UFDs.
+This is comparable to the resolution limit of the diffuse \ion{H}{1} in observed, gaseous UFDs.
 See Figure~\ref{fig:scale_height}.
@@
 This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy.
-This leads to high molecular gas fractions, with a H$_2$ mass comparable to the HI content by the end of the simulation.
+This leads to high molecular gas fractions, with a H$_2$ mass comparable to the \ion{H}{1} content by the end of the simulation.
 This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies.

### 2018-02-15 main.tex
completed revisions to Sect 4.  Fixed up a couple of acronyms

@@
 We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including stellar winds from massive and asymptotic giant branch stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
 %This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
@@
 \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
-Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar wind feedback from both massive stars and AGB stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
+Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar wind feedback from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
 %mm2
@@
 %mm2 
-    We track yields from massive star stellar winds, AGB star winds, and supernovae. 
+    We track yields from massive and AGB star winds, and supernovae. 
 In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
@@
 After this point, the molecular component dominates through the end of the simulation.
-
-Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining dominated by the WNM.
-While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume fraction.
+%mm2 [remove para break]
+Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining mass dominated by the WNM.
+While the CNM has a negligible volume fraction, the WNM, WIM, and HIM each occupy roughly the same volume fraction.
 However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy.
 Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
+
+%mm[new para]
 These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}.
-They find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass.
+They find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas having $\sim$ 10\% of the mass, and occupying negligible volume, and hot gas occupying $\sim$ 10\% of the volume, but having negligible mass.
 Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few.
-The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future works.
+The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
 
@@
 Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point.
-For this reason we only shade between the first quartile and maximum values only.
+For this reason we only shade between the first quartile and maximum values.
 \ion{He}{1} is very similar to \ion{H}{1}, with a small vertical offset, and is not shown for clarity.}
@@
 Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to \ion{H}{1} ionizing radiation, it does not show up in the \ion{H}{1} ionizing radiation diagram.
-This gas readily appears in the $G_{\rm o}$ since we assume it to be optically thin, though do apply a localized shielding approximation.}
+This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
 \label{fig:ISRF_2D}
@@
 To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the \ion{H}{1} ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr.
-This diagram shows how dramatic the increase in ISRF near young, massive stars (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
+This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
 The striking contrast between the two diagrams is due to the shielding of the \ion{H}{1} ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
@@
 In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency.
-It is unclear which of these two modes of feedback is more important in controlling star formation.
+It
+%mm2 is unclear 
+   remains to be seen
+which of these two modes of feedback is more important in controlling star formation.
 
@@
 In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
-We follow \citet{Muratov2015} defining the mass outflow rate ($\dot{M}_{\rm outflow}$) at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
+We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
 \begin{equation} \label{eq:dotM}
-\dot{M}_{\rm outflow} = \sum M_{\rm gas} \times v_{\rm r} / dL.
+\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
 \end{equation} 
@@
 The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
-Generally, other works use long timescale measurements of the SFR ($\sim$~Gyr) to compute the mass loading factor.
-For consistency in these works, we use the 500~Myr average SFR for computing the mass loading factor.
+Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
+For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor.
 The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time.
@@
 These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
-We note, however, that our results are much closer to the \citep{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly much smaller mass loading factors at 0.25 $R_{\rm vir}$.
+We note, however, that our results are much closer to the \citep{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly have much smaller mass loading factors at 0.25 $R_{\rm vir}$.
 
@@
 \label{sec:chemical evolution}
-\textbf{This section saw significant change. Removed previous mention of stellar abundances and species retention fractions. Much of below is new(ish)}
+%mm2 \textbf{This section saw significant change. Removed previous mention of stellar abundances and species retention fractions. Much of below is new(ish)}
 
@@
 We define the metal mass loading factor as
-\begin{equation}
+\begin{equation} \label{eq:eta-metal}
 \eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
@@
 We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions.
-For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but each increases, fluctuating around unity for the second half of the simulation.
+For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but it increases at each radius, fluctuating around unity for the second half of the simulation.
 Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}.
-\cite{Muratov2017} computes a slightly different value for their galaxies, a normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
+\cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
 Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.
@@
 \includegraphics[width=0.9\linewidth]{metal_fraction_evolution}
-\caption{Top: Metal mass loading factor at four radii over time (see text for how this is defined).
+\caption{Top: Metal mass loading factor (see Eq.~\ref{eq:eta-metal}) at radii of 0.1 ({\em black}), 0.2 ({\em purple}), 0.5 ({\em salmon pink}), and 1.0 $R_{\rm vir}$ ({\em yellow}) over time.
 Bottom: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
@@
 This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, CGM, and outside the virial radius of our galaxy over time.
-After the first 20 Myr, supernova driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
+After the first 20 Myr, supernova-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
 This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy.
-It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, or 40\% by the end of the simulation.
-Likewise, the CGM metal content is continually decreasing until the end of the simulation, from loss through the virial radius of the halo.
-Although the metal content of the ISM is gradually decreasing throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution.
+It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, reaching 40\% by the end of the simulation.
+Likewise, the CGM metal content continually decreases until the end of the simulation, from loss through the virial radius of the halo.
+Although the metal content of the ISM gradually decreases throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution.
 See Section~\ref{sec:obs_metals} for further discussion.
@@
 
-It is important to understand how metals from each source of stellar yields (stellar winds, AGB star winds, and supernovae) enrich the ISM.
+It is important to understand how metals from each source of stellar yields (massive and AGB stellar winds and supernovae) enrich the ISM.
 Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}.
-This requires that metal mixing and transport must occur much more rapidly ($\sim 10^2$~Myr) than what is possible assuming transport at the cold gas sound speed ($\sim 1$~Gyr).
-This suggests either that metals are transported first through a hot phase or are driven through efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}.
-How metal abundances vary in detail within these galaxies, beyond 1D radial profiles, and whether or not abundance distributions depend on the metal species is uncertain.
+This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed.
+This suggests either that metals are transported first through a hot phase
+%mm2 
+   with high sound speed, 
+or by efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}.
+It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
 It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few HII regions for a detailed examination.
 
-We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, in addressing these questions with Fig~\ref{fig:metal_slices}.
+We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
 The top two panels give the slices of number density (top left) and temperature (top right) in the mid-plane of a portion of our dwarf galaxy.
@@
 \includegraphics[width=0.32\linewidth]{log_NO}
-\caption{Five slices in the mid-place of our dwarf galaxy at an arbitrary time demonstrating the power of our chemical evolution model.
+\caption{Five slices in the mid-plane of our dwarf galaxy at an arbitrary time 
+%mm2 [give the time]
+  of {\bf XXX}~Myr after the start of star formation,
+demonstrating the power of our chemical evolution model.
 We show the number density and temperature in this region of the galaxy (top row), along with three different elemental abundance ratios, O/H (bottom left), N/H (bottom middle), and N/O (bottom right).
@@
 Beginning with log(O/H), the gas from the recent SN explosion is abundantly clear, with a higher oxygen abundance by at least 1 dex than its surroundings.
-The oxygen abundance throughout the rest of the ISM does vary, with some dense regions showing slightly higher oxygen abundance than their less dense surroundings, but the variation is not dramatic.
-log(N/H), however, shows slightly more significant variation throughout the ISM.
+The oxygen abundance throughout the rest of the ISM does vary, with
+%mm2 some 
+   almost all 
+dense regions showing 
+%mm2 slightly higher 
+   modest enhancements in oxygen abundance compared to their less dense surroundings.
+%mm2 , but the variation is not dramatic. 
+The ratio log(N/H), however, shows slightly more significant variation throughout the ISM.
 Comparing the two diagrams, one can pick out regions with differing abundances between the two species.
-This is clear in the log(N/O) slice, emphasizing regions that are over/under abundance in either species.
+This is clear in the log(N/O) slice, which emphasizes regions with strongly varying abundance in either species.
 The gas from the SN explosion, for example, has a low log(N/O) due to the significant amount of oxygen released in the SN.
@@
 These differences are also evident with a few regions of warmer gas (small sliver at center of figure, horseshoe shaped feature in lower right, and the blob in the upper right) where log(N/O) > 0, indicating an overabundance of nitrogen as compared to oxygen.
+
+%mm2 [new para for the explanation]
 At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse supernovae and winds from more massive stars.
-Therefore, nitrogen is injected to the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in supernovae, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
+Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in supernovae, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
 This suggests that the energetic differences between the injection sources can drive abundance variations within the ISM of our dwarf galaxy.
-It is possible, then, that metal mixing within the ISM (and also metal ejection from the ISM) is a process is species dependent.
-A more detailed analysis is beyond the scope of this work, but we plan to investigate this point, and potential observational consequences in stellar abundances, in future work.
+%mm2 It is possible, then, 
+   This suggests
+that metal mixing within the ISM (and also metal ejection from the ISM) 
+%mm2 is a process 
+is species dependent.
+A more detailed analysis is beyond the scope of this work, but we plan to investigate this point, and potential observational consequences for stellar abundances, in future work.
 % reference my other paper if it is ready-ish by the time I submit this one.
@@
 We have made these tables publicly available in the main distribution of \texttt{Grackle}.
-For densities where self-shielding is important, we computed \texttt{Cloudy} models of 1D clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
+For densities where self-shielding is important, we computed \texttt{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
 In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud.

### 2018-02-15 main.tex
completed revisions of sections 4 and 5.

@@
 These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
-This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, CGM, and outside the virial radius of our galaxy over time.
+This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
 After the first 20 Myr, supernova-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
@@
 However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) relation (left) for low mass galaxies, and the extended Schmidt law (ESL) (right).
+In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) relation and extended Schmidt law (ESL)  for low mass galaxies.
 In both diagrams, our simulations are given by the colored points, sampled every 1 Myr throughout the entire simulation.
 Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
-We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs given the procedure described in \citet{Roychowdhury2014}.
-We define $\Sigma_{\rm sfr} = \dot{M}_{*, \rm{10 Myr}} / A_{*, \rm{10 Myr}}$, where $\dot{M}_{*, \rm{10 Myr}}$ is the SFR measured over the preceding 10 Myr, and $A_{*, \rm{10 Myr}}$ is the disk defined out to the farthest star formed within the previous 10 Myr.
-Likewise, $\Sigma_{\rm gas} = M_{\rm gas, 10 Myr} / A_{*, \rm{10 Myr}}$, where M$_{\rm gas, 10 Myr}$ is the total gas mass within this defined disk.
+
+%mm [new para]
+We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs using the procedure described in \citet{Roychowdhury2014}.
+We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the
+%mm2 disk defined out to the farthest
+   area of the disk within the radius of the outermost 
+star formed within the previous 10 Myr.
+Likewise, $\Sigma_{\rm gas} = M_{\rm gas,10} / A_{*,10}$, where M$_{\rm gas,10}$ is the total gas mass within this defined disk.
 However, the total gas content cannot be determined observationally.
 To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He.
-There is generally no correction applied to account for any H$_{2}$ or HII content.
+There is generally no correction applied to account for any H$_{2}$ or \ion{H}{2} content.
 The molecular component is discussed further in Section~\ref{sec:molecular gas content}.
@@
 \includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution}
-\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every 1 Myr.
-We take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$ in our simulations to make a fair comparison to the observational sample (see text for more details).
-Plotted as points on both plots are recent observations from the SHIELD sample \citep{Teich2016}.
+\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late. 
+%mm2 We take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$ in our simulations to make a fair comparison to the observational sample (see text for more details)
+    See text for details of the calculation.
+Recent observations from the SHIELD sample \citep{Teich2016} are plotted as 
+%mm2 points
+    black points with error bars.
 On the left, we also give the best fit line to galaxies from the FIGGS sample from \cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \cite{Shi2011}.
-The simulations points are colored by time, with dark / purple early and light / green late.
-This is simply to indicate there is no obvious correlation with time in this diagram.}
+%mm2  This  is simply to indicate there 
+   There
+is no clear correlation with time in this diagram.}
 \label{fig:KS}
@@
 
-In both panels, we also include recent observational constraints on these relationships.
-For the KS relationship we include the best fit line from \citet{Roychowdhury2014} (black, dashed).
-In both we give recent measurements from the SHIELD galaxy sample \citep{Teich2016} (black, points).
+%mm2 In both panels, we also 
+   We
+include recent observational constraints on these relationships
+%mm2
+    in Figure ~\ref{fig:KS}. 
+%mm2 For the KS relationship we 
+   These 
+include the best-fit line from \citet{Roychowdhury2014}, 
+%mm2 (black, dashed). In both we give recent measurements from
+the SHIELD galaxy sample \citep{Teich2016}, 
+%mm2 (black, points).
 Recently, \cite{Roychowdhury2017} demonstrated that the best fit line in the ESL from \cite{Shi2011} extends to the low mass FIGGS sample of galaxies; we give this best fit line and 1$\sigma$ errors in the right hand panel (black lines).
+  and the best-fit line with 1$\sigma$ errors from \citet{Shi2011}, which 
+  \citet{Roychowdhury2017} demonstrated extends to the low mass FIGGS sample of galaxies.
 Our galaxy fluctuates significantly about both relationships with no clear trends in time.
@@
 
-Fig.~\ref{fig:KS} represents a remarkable result.
+%mm2 Fig.~\ref{fig:KS} represents a remarkable result. 
 In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
-It is non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, but signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
-This result is consistent with recent galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics (\textit{relevant citations})
+It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
+This result is consistent with
+%mm2 recent 
+galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics (\textit{relevant citations}
+%mm2
+   starting with A. Kravtsov 2003, ApJ L.)
 %mm 
 %ae: but does this bit then contradict my statement that this is remarkable? if its 'just gravity' at play?  
-   but also with the demonstration by \citet{Li2005} that the KS law can be reproduced 
+%mm2: that's the question, isn't it?  maybe keep the description of the result, but remove the claim of remarkability, as I have edited to do?
+   but also with the demonstration by \citet{Li2006} that the KS law can be reproduced 
    by gravitation acting on an isothermal disk, which was argued to demonstrate that 
@@
 
-Interestingly, in this low-dust regime, our H$_2$ formation is dominated by the gas-phase reactions H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
+Interestingly, in this low-dust regime, our H$_2$ formation is dominated by the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
 In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
-Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionizations of H and He from the UVB.
-This has the seemingly counterintuitive effect that turning off the UVB actually decreases the formation rate of H$_2$, as confirmed in test simulations.
+Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionization of H and He from the ultraviolet background.
+This has the seemingly counterintuitive effect that turning off the ultraviolet background actually decreases the formation rate of H$_2$, as confirmed in test simulations.
 In a test simulation ignoring H$^{-}$, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.
 
-This explains our contention with the simulations in \citet{Hu2016} and \citet{Hu2017}, which find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
+This explains our 
+%mm2 contention 
+    disagreement
+with the simulations in \citet{Hu2016} and \citet{Hu2017}, which find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
 Although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
-Our model suggests that H$^{-}$ and a UVB (in the absence of a local radiation field) are critical components in H$_2$ formation in small dwarf galaxies.
+Our model suggests that H$^{-}$ and the ultraviolet background (in the absence of a local radiation field) are critical components in H$_2$ formation in small dwarf galaxies.
 It is not surprising that the gas phase reactions dominate over grain catalysis in this low metallicity regime \citep{Glover2003}, but the total amount of H$_2$ formed is perhaps surprising.
-However, the rate coefficients association with gas-phase H$_2$ formation are uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
+However, the rate coefficients associated with gas-phase H$_2$ formation are uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
 %In addition, \cite{Glover2006} demonstrated that the total amount of H$_2$ formed can be quite sensitive to the initial conditions.
-Finally, our model lacks additional chemistry which may be important in the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
+%mm2 Finally, our model lacks additional chemistry which 
+    Our model does lack additional chemistry that
+may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
 It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
@@
 The simulations presented here have not yet been run for the gigayear timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$.
-However, we can compare to a key observable, the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from stellar evolution models based on the galaxy's star formation history.
-This can be done readily with Milky Way dSph's, whose stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
+However, we can compare to a key observable, the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from
+%mm2
+  closed box
+stellar evolution models based on the galaxy's star formation history.
+This can be done readily with Milky Way dSph's.
+Their stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
 However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
 
-Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, and close enough to the Milky Way to conduct this experiment.
-Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the remaining in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during the simulation no longer reside within the galaxy's disk.
-At the end of our simulation, we agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
+Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a %mm2 gaseous, 
+   gas-containing,
+star forming, low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
+Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
+As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk.
+At the end of our simulation, we
+%mm2
+   thus
+agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
 Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that
@@
 
-It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the IGM.
+It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium.
 While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of a $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero $\sim$ 60\% of ejected gas is recycled, while 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
@@
 We find 13.7\% of all metals lie within 1 kpc of the center of our galaxy, 26.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 38.6\% outside $R_{\rm vir}$.
+
+%mm2 [new para]
 The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
@@
 Our model seems to suggest that many of the metals ejected into the halo will not be recycled back into the galaxy, but this is difficult to determine with only 500~Myr of evolution.
-In addition, the accretion of pristine gas from the IGM could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals.
+In addition, the accretion of pristine gas from the intergalactic medium could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals.
 This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.
@@
 \subsection{Missing Physics}
-Although we include detailed physics in our simulations, there remains additional physical processes that may be relevant, these are discussed below.
+Although we include many detailed physical models in our simulations, there remain additional physical processes that may be relevant, which we now discuss.
 
@@
 a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.
-
+%mm2: should we recover the reference to Shull \& Saken?
 %old comment: (need to ref or back up this claim: see Dale et al.
@@
 
-\subsubsection{Cosmic Rays and Magnetic Fields}
+\subsubsection{Cosmic Rays} 
+%mm2 and Magnetic Fields}  One could make the case that we should have a separate discussion of magnetic fields.  However, this section is only about CRs.
+
 Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}.
 These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}.
-Modeling cosmic rays is challenging, however, as they encompass a wide range of energies (give range), with significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
+Modeling cosmic rays is challenging, however, as they encompass a wide range of energies,
+%mm2 (give range), with 
+   and there are
+significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
 Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy.
 In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM.
-Modeling cosmic ray feedback completely requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena.
-Finally, including MHD presents additional difficulties in untangling the effects each individual feedback mechanism on galaxy chemodynamics.
+Modeling cosmic ray feedback completely thus requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena.
+Finally, including MHD presents additional difficulties in untangling the effects of each individual feedback mechanism on galaxy chemodynamics.
 
@@
 
-Roughly half of massive stars live in binary pairs.
+Roughly half of massive stars live in binary pairs 
+%mm2 doi:10.1051/0004-6361/201219621
+   \citep{Sana2012}. 
 Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes.
@@
 STARBURST99), but could be significant.
-For example, \cite{Zapartas2017} finds that binarity extends the timescales over which core collapse supernovae occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
+For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse supernovae occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
 Although they find only $\sim 15\%$ of core collapse supernovae explode after 50~Myr, this could still be an important effect.
@@
 Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars.
-This is beyond the scope of this project, but will be investigated in future works.
+This is beyond the scope of this project, but will be investigated in future work.
 
@@
 This, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
-In this work, we apply these methods to simulate the evolution of an isolated, low mass dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
-We present an overview of the properties of this galaxy in this work.
+In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
+We present an overview of the properties of this
+%mm2 galaxy
+    simulation 
+in this work.
 % AE: mention companion paper here if publish at same time
@@
 \begin{enumerate}
-\item Multi-channel feedback is effective in this galaxy in regulating star formation consistent with the KS relationship and extended Schmidt law in observed galaxies.
-See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}.
-
-\item This feedback drives large outflows ($\eta \sim 50$ at 0.25~R$_{\rm vir}$) with metal mass loading factors near unity.
+\item Multi-channel feedback is effective in this galaxy in regulating star formation 
+%mm2 
+   to occur at a rate 
+consistent with the KS relationship and extended Schmidt law in observed galaxies. See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}.
+
+\item This feedback drives large outflows 
+%mm2 ($\eta \sim 50$ at 0.25~R$_{\rm vir}$) with
+   having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, and
+metal mass loading factors near unity.
 By mass, nearly all of this outflow is moving with velocities below 100 km~s$^{-1}$, but there is a significant tail towards velocities up to 1000 km s$^{-1}$ (Figure~\ref{fig:outflow_velocity}).
-This galaxy is consistent with observed metal retention fractions of UFD's, retaining only $\sim$10\% of metals in the disk.
-By the end of the simulation the remaining metals reside within the virial radius ($\sim$50\%) and $\sim$40\% are ejected outside the virial radius.
+
+%mm2 [made this a separate item]
+\item 
+%mm2 This galaxy result is consistent with the observed metal retention fractions of ultrafaint dwarfs, retaining only $\sim$10\% of metals in the disk. 
+    Only $\sim$10\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of ultrafaint dwarfs.
+By the end of the simulation $\sim$50\% of the remaining metals remain within the virial radius and $\sim$40\%
+have been ejected beyond the virial radius.
 The fraction in the disk remains fairly constant towards the end of the simulation, but the metals in the halo are still evolving.
@@
 
-\item A thin, yet resolved, gas scale height ($\sim$~50~pc) beyond our stellar radius, with larger scale heights ($\sim 100 - 200$~pc) driven by feedback interior to the stellar radius.
-This is comparable to the resolution limit of the diffuse \ion{H}{1} in observed, gaseous UFDs.
+\item A thin, yet resolved, gas scale height ($\sim 50$~pc) beyond our stellar radius, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
+This is comparable to the resolution limit of the diffuse \ion{H}{1} in observed, gaseous ultrafaint dwarfs.
 See Figure~\ref{fig:scale_height}.
 
-\item The ISRF of our galaxy is highly varying in time by orders of magnitude, though is relatively uniform in space at any given time.
-It is unclear how important these fluctuations are as a source of feedback, or if the affect can simply be approximated with a time averaged radial profile.
-See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.
-
-\item Our galaxy forms a significant amount of H$_2$ through gas ($H^-$) reactions.
+\item The ISRF of our galaxy is highly varying in time, by orders of magnitude, though it is relatively uniform in space at any given time.
+It is unclear how important these fluctuations are as a source of feedback, or if the affect can
+%mm2 simply 
+be approximated with a time averaged radial profile. See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.
+
+\item Formation of a significant amount of H$_2$ through gas phase reactions with H$^_$.
 This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy.
-This leads to high molecular gas fractions, with a H$_2$ mass comparable to the \ion{H}{1} content by the end of the simulation.
+This leads to high molecular gas fractions, with an H$_2$ mass comparable to that of \ion{H}{1} by the end of the simulation.
 This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies.
@@
 Finally, we used O and N as examples to briefly demonstrate that there are discernible differences in how individual metal species are distributed within the ISM of our galaxy.
-In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and the gas flows of individual metals through the halos of low mass dwarf galaxies.
-In addition, we will investigate the role of each of our sources of feedback plays in driving dwarf galaxy chemodynamics.
+In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and how individual metals move
+%mm2 through the halos of low mass dwarf galaxies.
+  into halos. 
+% In addition, we will investigate 
+   This will allow us to examine
+the role each of our sources of feedback plays in driving dwarf galaxy chemodynamics.
 
@@
 Analysis in this work
-made significant use of the publicly available yt (http://ytproject.org)
-toolkit. \textsc{Enzo}, \textsc{Grackle}, and yt are the products of a collaborative effort of many independent scientists from numerous institutions around
+made significant use of the publicly available \textsc{yt} (http://ytproject.org)
+toolkit. \textsc{Enzo}, \textsc{Grackle}, and \textsc{yt} are the products of a collaborative effort of many independent scientists from numerous institutions around
 the world. Their commitment to open science has helped make
@@
 We would also like to thank for their advice and valuable conversations: John Wise, Brian O'Shea, Benoit Cote, Britton Smith, Simon Glover, Kathryn Johnston, Mary Putman, Keith Hawkins, Joshua Wall, and Chia-yu Hu.
-\textbf{is this too many people?
+\textbf{AE: is this too many people?
 I do think they all deserve acknowledgement.
-(list is in no particular order)}
+(list is in no particular order).
+MM: I'd alphabetize and use first initials following ApJ style, but fine by me to keep everyone on.}
 

### 2018-02-15 main.tex
compiles now

@@
 We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including stellar winds from massive and asymptotic giant branch stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including
+%mm2 
+     {\bf [should we somehow make clear that we are ignoring energetic feedback from stellar winds?]}
+stellar winds from massive and asymptotic giant branch stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
 %This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
@@
 We
-%mm 
 assume collisional ionization equilibrium for all other elements in order to
@@
 We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernova progenitors.
-We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star
-%mm
-   as it forms
+We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms
 with the associated local gas abundances for each species.
@@
 
-We use the adaptive mesh refinement (AMR) hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies.
+We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies.
 \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions.
@@
 
-The computational domain in an AMR simulation is adaptively refined up to a designated resolution limit for a given set of refinement criteria.
-We require that the Jeans length be resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution.
+%mm2 The computational domain in an adaptive mesh refinement simulation is adaptively refined up to a designated resolution limit for a given set of refinement criteria. We require that
+     We refine the mesh whenever 
+the Jeans length 
+%mm2 be
+    is no longer
+resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution.
 Our maximum resolution in the simulations presented here is 1.8~pc.
 At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation.
-Studies have shown that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation \citep{Truelove1997}.
+\citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.
 
@@
 These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
+
+%mm2 
+   {\bf [I'm a bit confused here: how does the ISRF interact with the cooling?  Shouldn't that move you around in the Cloudy tables, possibly quite substantially?]}
 
@@
 
-\item Formation of a significant amount of H$_2$ through gas phase reactions with H$^_$.
+\item Formation of a significant amount of H$_2$ through gas phase reactions with H$^-$.
 This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy.

### 2018-02-16 main.tex
completed revision of sections 2 and 3.

@@
 Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
-Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources)
+Mixing behavior is tied critically to the feedback source (stellar winds, supernovae (SNe), and possibly more exotic sources)
 %mm in which they are injected to
@@
 %mm2
-  We include stellar feedback from stellar winds, core collapse and Type Ia supernovae,    
+  We include stellar feedback from stellar winds, core collapse and Type Ia SNe,    
   photoelectric heating, and ionizing radiation.
@@
 %mm2 
-    We track yields from massive and AGB star winds, and supernovae. 
+    We track yields from massive and AGB star winds, and SNe. 
 In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
@@
 % In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}.
-For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer.
+For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia SNe, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer.
 In addition, we couple to a self-consistent set of stellar yields
-%to track yields from massive star stellar winds, AGB star winds, and supernovae. 
+%to track yields from massive star stellar winds, AGB star winds, and SNe. 
 We describe each mode of our multi-channel feedback 
@@
 %mm2 In  summary, 
-We produce high-resolution, galaxy-scale simulations tracking stars not as SSP's, but as individual stars sampled from an assumed IMF.
+We produce high-resolution, galaxy-scale simulations tracking stars not as SSPs, but as individual stars sampled from an assumed IMF.
 This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
@@
 In addition, we follow the optically thin, non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
-We track the stellar wind feedback and supernovae from these stars, depositing individual metal yields from both.
-We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia supernova progenitors.
+We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both.
+We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors.
 We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms
@@
 In order to resolve individual star formation events on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
-Each cell at the maximum refinement level is capable of forming stars if it meets the following local criteria: 1) $n_{\rm cell} > n_{\rm thresh}$, 2) $T_{\rm gas} < T_{\rm thresh}$, 3) $M_{\rm gas} > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
-Our fiducial values for $n_{\rm thresh}$ and $T_{\rm thresh}$ are 200~cm$^{-3}$ and 200~K respectively.
-We limit the fraction of a cell's gas mass that is converted into stars by requiring $M_{\rm gas} > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and $M_{\rm max,*}$ is the maximum star mass (100 M$_{\odot}$).
-No star formation occurs when $M_{\rm gas} < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode does not produce negative densities.
+Each cell at the maximum refinement level is capable of forming stars if it
+%mm2 
+   contains gas that 
+meets the following local criteria
+%mm2 [removed extraneous subscripts and simplified a bit]
+     on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$:
+1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
+Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K.
+We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$.
+No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.
 
@@
 %but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
-The gas mass converted to stars in a time step, $dt$, is
+
+%mm2 The gas mass converted to stars in a time step, $dt$, is
+   The stellar mass formed during a timestep $\Delta t$ is
 \begin{equation}
-M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
+%mm2 M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
+         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
 \end{equation}
-In practice, $dt/\tau_{\rm ff} \ll 1$, and $M_{ {\rm gas} \to *}$ is smaller than the minimum star particle mass at parsec scale resolution.
+In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution.
 We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses.
 In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
-If it does, we randomly sample over the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle if the total stellar mass formed exceeds 100 M$_{\odot}$.
-We make the simple assumption of a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
-Our lower limit on stellar masses ensures that we are able to both directly track all particles that participate in some way to feedback and metal enrichment, and follow longer lived start particles, while reducing the computational expense of following many low mass stars that have no dynamical impact on the galaxy evolution.
+If it does, we randomly sample
+%mm2 over 
+   from
+the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle 
+%mm2 if 
+   when 
+the total stellar mass formed exceeds 100 M$_{\odot}$. We 
+%mm2 make the simple assumption of 
+     assume 
+a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over
+%mm2
+   the range between  
+a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
+Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
 
 Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
-This dispersion captures some of the unresolved gas motions below the resolution limit and smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations.
+This dispersion captures some of the unresolved gas motions below the resolution limit that are smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations.
 Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
-Stars evolve during the simulation, by losing mass from stellar winds and supernovae as described below, and by changing types, but persist throughout the entire simulation.
-For example, low mass stars are tagged as white dwarfs at the end of their life, which may eventually explode as a Type Ia supernova (discussed below), after which they persist as massless tracer particle ``remnants''.
-
-Finally, each star is marked as a ``must refine" particle, requiring that each star be surrounded by a four-cell region at the highest level of refinement.
-This ensures that both stellar winds and supernovae feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.
+
+%mm2 [moved para break up]
+Stars evolve during the simulation, by losing mass from stellar winds and SNe as described below, and by changing types, but persist throughout the entire simulation.
+For example, low mass stars are tagged as white dwarfs (WDs) at the end of their life, which may eventually explode as a Type Ia SN (discussed below), after which they persist as massless tracer particle remnants.
+Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a four-cell region at the highest level of refinement.
+This ensures that both stellar winds and SNe feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.
 
@@
 We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}.
-This grid includes yields from the AGB phase of stars between 1 and 7 M$_{\odot}$, as well as yields from both stellar winds and core collapse supernova of massive stars over 12 to 25 M$_{\odot}$.
+This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$.
 We complement these tables with tables from Slemer et.
@@
 (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014} to track stellar winds for stars more massive than 25 M$_{\odot}$.
-We ignore supernova yields from these stars (see next paragraph).
+We ignore SN yields from these stars (see next paragraph).
 We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth.
-Although we can follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation.
+Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation.
 We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
 
-Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse supernovae.
+Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse SNe.
 Where this transition occurs is uncertain, but is commonly taken to be around 8--10~M$_{\odot}$.
@@
 In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
-Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse supernova (see Section \ref{sec:stellar winds} for details on the wind energetics).
-Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of a 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
+Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics).
+Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
 \citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.
-We neglect the effects of binary star evolution on stellar feedback, but discuss the significance of this in Section~\ref{sec:binary stars}.
+We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
 
@@
 Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
-Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass or energy ejection.
-
-Type Ia supernovae are an important additional source of galactic chemical enrichment.
+Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass,
+%mm2 
+   metal, 
+or energy ejection.
+
+Type Ia SNe are an important additional source of galactic chemical enrichment.
 These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
-We use the Type Ia supernova yields given in \citet{Thielemann1986}, adopting a Type Ia supernova model as discussed in Section~\ref{sec:Type Ia}.
-We emphasize that we only track Type Ia supernovae occurring within the population of stars formed in this model, neglecting supernovae from any pre-existing population.
+We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
+We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any pre-existing population.
 
@@
 Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
-Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from supernovae and radiation, stellar winds are potentially important sources of pre-supernova feedback.
+Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{shull1995}, stellar winds are potentially important sources of pre-SN feedback.
 In models that include feedback energy from stellar winds from both AGB and massive stars, we inject the feedback energy in a three-cell radius spherical region centered on the emitting star particle, assuming full thermalization of the wind kinetic energy.
-The total injected energy in timestep $\Delta t$ is therefore $E_{\rm wind} = \dot{M}\Delta t \times v^2_{\rm wind} + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass ($\dot{M}\Delta t$) given the star's interpolated $T_{\rm eff}$.
+The total injected energy in timestep $\Delta t$ is therefore $E_w = \dot{M}\Delta t \times v^2_w + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
 We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells.
-
-We assume constant mass loss rates for all winds as set by the yields tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars). 
+We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
 %Properly modeling stellar winds requires sub-parsec resolution, which is problematic in galaxy-scale simulations.
@@
 Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}.
-Satisfying the Courant time step becomes prohibitively expensive following this gas ($dt \sim$~100~yr), particularly as stellar wind bubbles have typical temperatures of 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
+Satisfying the Courant time step becomes prohibitively expensive following this gas, with time steps dropping to $\Delta t \sim$~100~yr.
+%mm2 , particularly as stellar wind bubbles have typical temperatures of 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
+[This yields a sound speed on the same order as the flow velocity, more or less by energy conservation, so doesn't change the timestep.]
 For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
-In our case, we fix massive stellar winds to $v_{\rm wind} = 1$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
+In our case, we fix massive stellar wind velocities to $v_w = 1$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
 Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies.
 Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work.
-These points are discussed in more detail in Section \ref{sec:stellar winds discussion}.
+These points are discussed in more detail in Sect.~\ref{sec:stellar winds discussion}.
 
@@
 
-\subsubsection{Core Collapse Supernovae}
+\subsubsection{Core Collapse SNe}
 \label{sec: core collapse}
-Stars between  $M_{\rm thresh} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse supernovae, ejecting mass and yields as determined by the NuGrid stellar yield tables at 10$^{51}$ erg of thermal energy.
-Due to the high resolution (1.5--2.5 pc depending on galaxy size) of our simulations, we generally resolve the Sedov phase of each supernova explosion well (see Appendix~\ref{appendix:supernova}).
-We find injecting thermal energy alone in a three-cell radius spherical region around the star particle to be sufficient to resolve the supernova explosions.
-We continue to track any remaining stellar mass after the supernovae as a massive ``remnant" tracer particle.
-In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment through X-ray binaries and neutron-star-neutron-star merger events which, while rare, could be important in long term galaxy evolution \citep[e.x.][]{Artale2015}.
-
-\subsubsection{Type Ia Supernova}
+Stars between  $M_{\rm thresh} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
+Due to the high resolution
+%mm2
+    {\bf [is this resolution variation from an earlier version of the paper?]}
+(1.5--2.5 pc depending on galaxy size) of our simulations, we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}). We 
+%mm2 find injecting 
+   inject
+thermal energy alone in a three-cell radius spherical region around the star particle,
+%mm2
+   which we find to be sufficient to resolve the SN explosions.
+We continue to track any remaining stellar mass after the SNe as a massive remnant tracer particle.
+In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.
+
+\subsubsection{Type Ia SNe}
 \label{sec:Type Ia}
-We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as white dwarf (WD) particles, marking a subset as Type Ia supernova progenitors.
-This is the most self-consistent model for Type Ia supernovae in galaxy scale simulations.
-We note however that for the low SFR's in our isolated dwarf galaxy simulations, the first SNIa only appears after a few hundred Myr of simulation time.
-For example, by the end of the simulation presented here (500~Myr), only 18 have gone off.
+We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as WD particles, marking a subset as Type Ia SN progenitors.
+This is the most self-consistent model for Type Ia SNe in galaxy scale simulations.
+We note however that for the low SFRs in our isolated dwarf galaxy simulation, the first Type Ia SN only appears after a few hundred megayears of simulation time.
+%mm2 For example, by 
+    By
+the end of the simulation presented here (500~Myr), only 18 have gone off.
 At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
@@
 %where $M_{\rm *}$ is the initial mass of the WD progenitor.
-We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WD's that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.
-
-We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution (DTD) model. 
-%\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):} 
-The SNIa rate is taken as a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope ($\beta$) and normalization ($N_{\rm Ia}/M_{\rm SF}$) are observables.
-The latter represents the number of Type Ia supernova per mass of star formation.
-By assuming an IMF, one can write down the fraction ($\eta$) of stars capable of forming a SNIa progenitor that \textit{will} explode within a Hubble time.
+We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.
+
+We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution model. 
+%\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):  %mm2 At this point, the paper is large anyway, so I'd not worry about it.
+I have cleaned up the text a bit in this paragraph, using ApJ style apposition rather than parentheses and such.}
+The Type Ia SN rate is taken to be a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope $\beta$ and normalization $N_{\rm Ia}/M_{\rm SF}$ are observables.
+The latter represents the number of Type Ia SNe per mass of star formation.
+By assuming an IMF  $dN/dm$, one can write down the fraction $\eta$ of stars capable of forming a Type Ia SN progenitor that \textit{will} explode within a Hubble time.
 This is given as
@@
 \end{equation}
-where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF ($dN/dm$), and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
-The DTD slope, $\beta$, is of order unity, with typical values between 1.0 and 1.2 (see \citet{Maoz2014} for a recent review).
-$N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the SNIa rate and integrating over a Hubble time.
+where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF, and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
+The distribution slope $\beta$ is of order unity, with typical values between 1.0 and 1.2 \citep[see][for a recent review]{Maoz2014}.
+$N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the Type Ia SN rate and integrating over a Hubble time.
 Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
-We adopt 1.2 \citep{Maoz2010} and 0.8$\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013} for our fiducial values of $\beta$ and $N_{\rm Ia}/M_{\rm SF}$.
+For our fiducial values, we adopt $\beta = 1.2$ \citep{Maoz2010} and $N_{\rm Ia}/M_{\rm SF} = 0.8\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013}.
 Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.
 
-Finally, we can normalize $\Psi(t)$ to give the probability per unit time ($\dot{P}(t)$) that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor.
-Integrating this gives the total probability at any given time as,
-
+Finally, we can normalize $\Psi(t)$ to give the probability per unit time $\dot{P}(t)$ that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor.
+Integrating this gives the total probability at any given time as
 \begin{equation}
@@
 \end{equation}
-where $t_{\rm o}$ is the formation time of the WD and the leading term in the R.H.S properly normalizes the total probability over a Hubble time to $\eta$.
-This naturally accounts for both a prompt and delayed Type Ia supernova population in our simulations.
+where $t_{\rm o}$ is the formation time of the WD and the leading term on the right hand side properly normalizes the total probability over a Hubble time to $\eta$.
+This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
 In practice, we invert the cumulative probability function to assign an exact time at which a given WD will explode using only a single random number draw, rather than sampling the probability distribution for each WD particle at every time step.
@@
 \label{sec:ionizing radiation}
-Radiation feedback (ionization, ionization heating, and radiation pressure) is an important source of feedback in galaxies.
-\ion{H}{2} regions carved out by stellar radiation change the ISM structure where SNe eventually explode, generally increasing their dynamical importance.
-However, when accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily through channels carved through dense clouds.
+Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies.
+\ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance.
+However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds.
 Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
-As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through ray tracing methods described below.
+As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through the ray tracing methods described below.
 % AE (no longer the case): We here use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).
 
-Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer as coupled to the hydrodynamics of the simulation.
+Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation.
 We follow \ion{H}{1} and \ion{He}{1} ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
@@
 
-We adopt the \ion{H}{1} and \ion{He}{1} ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
+We determine the \ion{H}{1} and \ion{He}{1} ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
 We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star.
@@
 Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017}.
-Due to these uncertainties, and given that our dwarf galaxy has a low dust content (and therefore a low IR opacity), we ignore this effect.
-\textbf{cite davis and stone, Zhang and davis?}
+Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low IR opacity, we ignore this effect.
+%mm2 [seems to have been done] \textbf{cite davis and stone, Zhang and davis?}
 
@@
 \label{sec:diffusive heating}
-We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from each of our star particles.
+We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles.
 The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the SEDs for each gridded star.
-Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Section~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
+Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
 Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
@@
 
-Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy.
+Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy.
 We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
@@
 \end{equation}
-where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust to gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
+where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust-to-gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
 Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
 
-$D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
-The extremely low dust to gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a $D$ that scales linearly with metallicity at very low metallicity.
+The value of $D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
+The extremely low dust-to-gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a ratio $D$ that scales linearly with metallicity at very low metallicity.
 At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit.
@@
 We include cosmic rays coupled to the hydrodynamics of our simulation using a two-fluid model with adiabatic index $\gamma = 5/3$, as described in \citep{SalemBryan2014}.
-Cosmic ray energy is injected as some fraction, $f_{\rm CR}$, of the total supernova rate; we adopt $f_{\rm CR}$ with the fiducial value of 0.1.
+Cosmic ray energy is injected as some fraction, $f_{\rm CR}$, of the total SN rate; we adopt $f_{\rm CR}$ with the fiducial value of 0.1.
 We include isotropic cosmic ray diffusion as described with the diffusion coefficient, $\kappa_{\rm CR} = 3.0\times10^{28}$.
@@
 \label{sec:IC}
-The galaxy presented in this work is constructed to be similar to the observed properties of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
-Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity fraction of $Z \sim 5.4\times10^{-4}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}.
-Our dwarf galaxy is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
+The galaxy 
+%mm2 presented in this work 
+   simulated as an example here
+is constructed to have properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
+Leo P is gas rich,
+%mm2 with $M_{\rm gas} > M_{*}$ and low metallicity, 
+with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and
+%mm2
+   low metallicity,
+with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity fraction of $Z/Z_{\odot} \sim 5.4\times10^{-4}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}.
+Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z/Z_{\odot} = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
 
@@
 This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc.
-These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc, or $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012}.
-We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in a future work.
-
-Following the initialization procedure of \citet{Hu2017}, we use artificial supernova driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
+These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012}.
+We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in future work.
+
+Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
 This additionally prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
-These supernovae explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
+These SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
 We stop the artificial driving 25~Myr after the first star particle forms.
-These artificial supernovae do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
-We note that this initial driving is somewhat ad hoc in that do not include any other effects from the stellar population that would have caused these supernovae.
+These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
+We note that this initial driving is somewhat ad hoc in that do not include any other effects from the stellar population that would have caused these SNe.
 
@@
     This central region quickly fills with
-warm and hot gas generated from radiation feedback and supernovae respectively.
+warm and hot gas generated from radiation feedback and SNe respectively.
 Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels.
@@
 
-We present the star formation rate (SFR) and core collapse supernova rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between 2--4$ \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly at this level for 100 Myr, and then drops to an average of about
+We present the star formation rate (SFR) and core collapse SN rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between 2--4$ \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly at this level for 100 Myr, and then drops to an average of about
 %mm2
@@
 infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$.
-The SNR tracks the SFR with a time delay, with roughly one core collapse supernovae per 100 M$_{\odot}$ of star formation.
+The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation.
 Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 9.93 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$.
@@
 \includegraphics[width=0.475\linewidth]{mass_evolution}
-\caption{Left: The SFR and core collapse supernova rate in our dwarf galaxy in 10 Myr bins (left).
+\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins (left).
 Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.
-%mm2 Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and supernova rate.
-   Note that the supernova rate has been scaled by a factor of 100 to fit on the same vertical 
+%mm2 Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and SN rate.
+   Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical 
    axis as the SFR.}
@@
     regimes containing most of the mass 
-in the simulation: low density, warm gas produced through ionization and supernova heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
+in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
 Several notable features of the
@@
 
-\textbf{In response to MM's comment: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e.
+%mm2 \textbf{In response to MM's comment: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e.
 how does this compare to a uniform or 1D radial profile).
 G$_{eff}$ is convolved with local density and temperature variations, and is thus a bit harder to parse / interpret.
-Though possibly I should show both?}
+Though possibly I should show both?
+%MM: given how low the optical depth is, it probably doesn't matter.}
 
@@
 The distribution has a very long tail out to and beyond 500~km~s$^{-1}$.
-The dominant launching mechanism in this simulation are supernovae, generating a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
+The dominant launching mechanism in this simulation are SNe, generating a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
 However, as shown, the HIM comprises very little of the outflow by mass.
@@
 This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
-After the first 20 Myr, supernova-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
+After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
 This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy.
@@
 
-It is important to understand how metals from each source of stellar yields (massive and AGB stellar winds and supernovae) enrich the ISM.
+It is important to understand how metals from each source of stellar yields (massive and AGB stellar winds and SNe) enrich the ISM.
 Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}.
@@
 %mm2 [new para for the explanation]
-At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse supernovae and winds from more massive stars.
-Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in supernovae, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
+At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars.
+Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
 This suggests that the energetic differences between the injection sources can drive abundance variations within the ISM of our dwarf galaxy.
@@
 This difference is entirely feedback driven.
-At this metallicity, N is produced only in the stellar winds of stars between 8 and 10 M$_{\odot}$, with little to no production in supernovae.
-The rest of the species either have very little stellar wind production, are produced solely in supernovae, or have similar production levels between both supernovae and stellar winds (like O, for example).
+At this metallicity, N is produced only in the stellar winds of stars between 8 and 10 M$_{\odot}$, with little to no production in SNe.
+The rest of the species either have very little stellar wind production, are produced solely in SNe, or have similar production levels between both SNe and stellar winds (like O, for example).
 The typically lower injection energies of N into the galaxy compared to the SNe produced elements means N is preferentially retained within the ISM, and not as effectively ejected through outflows.
-In truth, the stars that produce N do eventually explode as supernovae, sweeping up some fraction of the wind produced N into outflows.
+In truth, the stars that produce N do eventually explode as SNe, sweeping up some fraction of the wind produced N into outflows.
 However, clearly some of this N mixes more effectively within the ISM than the other metal species.
@@
 %We plot the $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ ratio for all star particles in our simulation that are ``alive'' in Figure~\ref{fig:stellar_abundance}.
-This represents stars that have not gone supernovae or have otherwise formed a compact object.
+This represents stars that have not gone SNe or have otherwise formed a compact object.
 Here, $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$, and the notation [X/Y] denotes the ratio of the abundance of species X over Y, relative to the solar value, or log([X/Y]) = log(X/Y) - log(X$_{\odot}$/Y$_{\odot}$).
@@
 In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
-Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionization of H and He from the ultraviolet background.
-This has the seemingly counterintuitive effect that turning off the ultraviolet background actually decreases the formation rate of H$_2$, as confirmed in test simulations.
+Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionization of H and He from the UV background.
+This has the seemingly counterintuitive effect that turning off the UV background actually decreases the formation rate of H$_2$, as confirmed in test simulations.
 In a test simulation ignoring H$^{-}$, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.
@@
 Although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
-Our model suggests that H$^{-}$ and the ultraviolet background (in the absence of a local radiation field) are critical components in H$_2$ formation in small dwarf galaxies.
+Our model suggests that H$^{-}$ and the UV background (in the absence of a local radiation field) are critical components in H$_2$ formation in small dwarf galaxies.
 It is not surprising that the gas phase reactions dominate over grain catalysis in this low metallicity regime \citep{Glover2003}, but the total amount of H$_2$ formed is perhaps surprising.
@@
 Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a %mm2 gaseous, 
-   gas-containing,
+   gas-rich,
 star forming, low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
@@
 a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.
-%mm2: should we recover the reference to Shull \& Saken?
 %old comment: (need to ref or back up this claim: see Dale et al.
-2014 for individual clouds, while the right panel of Fig 2 in Shull \& Saken 1995 shows that the integrated wind energy from a cluster is about 10\% that of the supernovae -M).
+2014 for individual clouds, while the right panel of Fig 2 in Shull \& Saken 1995 shows that the integrated wind energy from a cluster is about 10\% that of the SNe -M).
 
@@
 Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes.
-This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as supernovae.
+This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as SNe.
 This effect is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g.
 STARBURST99), but could be significant.
-For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse supernovae occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
-Although they find only $\sim 15\%$ of core collapse supernovae explode after 50~Myr, this could still be an important effect.
+For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse SNe occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
+Although they find only $\sim 15\%$ of core collapse SNe explode after 50~Myr, this could still be an important effect.
 Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}.
@@
 We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
-For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia supernovae, ionizing radiation followed through radiative transfer, photoelectric heating, and Lyman-Werner radiation using individual star particles.
+For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, and Lyman-Werner radiation using individual star particles.
 This, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
@@
 
-\section{Typical Gas Densities in Supernova Injection Regions}
-\label{appendix:supernova}
-
-Modeling supernova feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of supernova feedback.
+\section{Typical Gas Densities in SN Injection Regions}
+\label{appendix:SN}
+
+Modeling SN feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of SN feedback.
 Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time.
@@
    Overcooling becomes less important 
-with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each supernova.
-We take advantage of our high (parsec scale) resolution and employ a simple thermal energy injection model for our supernova feedback.
-We demonstrate how well this resolves our supernovae in the comparison simulation presented in this work.
-
-The left panel of Figure ~\ref{fig:supernova histogram} gives the distributions of the peak and average ISM number densities in the supernova injection regions for each supernovae in the simulations presented in this work.
+with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each SN.
+We take advantage of our high (parsec scale) resolution and employ a simple thermal energy injection model for our SN feedback.
+We demonstrate how well this resolves our SNe in the comparison simulation presented in this work.
+
+The left panel of Figure ~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SNe in the simulations presented in this work.
 As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
-For most supernovae, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-supernova feedback included in our simulations.
-The right panel of Figure ~\ref{fig:supernova histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
+For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations.
+The right panel of Figure ~\ref{fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
 \[
@@
 where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$.
-\citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the supernova explosion with thermal energy injection alone, assuming uniform density in the injection region.
+\citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the SN explosion with thermal energy injection alone, assuming uniform density in the injection region.
 In practice, the injection region is never uniform.
-We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each supernova.
-As shown, a majority of supernovae are resolved (to the right of the 4.5$\Delta x$ line), but that up to 10\% are somewhat under-resolved.
-In general, these are supernova explosions from the most massive (i.e.
+We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each SN.
+As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but that up to 10\% are somewhat under-resolved.
+In general, these are SN explosions from the most massive (i.e.
 most prompt) stars.
-We do not expect that resolving these supernovae will dramatically alter our results, but note that simulations presented in future work will examine lower mass galaxies at higher resolution than those presented here.
-In those, the supernovae are more resolved, but we note that using our feedback model at resolutions much less than 2 pc will require adopting a different injection mechanism.
-
-% We use a spherically symmetric thermal dump method of modelling supernova explosions.
-This is the simplest method possible, but can often result in rapid overcooling of the heated gas, effectively underestimating the effectiveness of supernova feedback.
+We do not expect that resolving these SNe will dramatically alter our results, but note that simulations presented in future work will examine lower mass galaxies at higher resolution than those presented here.
+In those, the SNe are more resolved, but we note that using our feedback model at resolutions much less than 2 pc will require adopting a different injection mechanism.
+
+% We use a spherically symmetric thermal dump method of modelling SN explosions.
+This is the simplest method possible, but can often result in rapid overcooling of the heated gas, effectively underestimating the effectiveness of SN feedback.
 Solutions to this problem can often be ad hoc (e.g.
@@
 However, recent work has shown injecting some fraction of this thermal energy directly as kinetic energy or momentum alleviates this issue without sacrificing physical realism.
-However, it has been shown that simple thermal energy injection is sufficient for parsec scale (or better) resolutions, provided the supernova do not occur in very high density regions; if resolved, thermal injection converges with kinetic energy / momentum injection methods.
+However, it has been shown that simple thermal energy injection is sufficient for parsec scale (or better) resolutions, provided the SN do not occur in very high density regions; if resolved, thermal injection converges with kinetic energy / momentum injection methods.
 Resolving these explosions with thermal energy injection alone depends ultimately on the grid resolution, background density and ISM structure, the background cooling/heating physics used, and the size and shape of the injection region.
 Here, we perform a resolution test of our thermal injection method over four uniform densities (0.1 \ccunit, 1.0 \ccunit, 10.0 \ccunit, and 100.0 \ccunit) for both a 8.0 \msun and 25.0 \msun star, comparing to both the analytic solution and results using kinetic energy injection from \citet{Simpson2015}.
-These results are presented in Figure~\ref{fig:supernova tests}.
+These results are presented in Figure~\ref{fig:SN tests}.
 We note these are heavily idealized cases.
-In general in our simulations, pre-SN feedback from stellar winds and radiation will reduce the typical densities within which our supernova explosions occur.
-In addition, supernova will generally be clustered, meaning each SN will reducing the typical density for each subsequent SN in that region.
-In Figure~\ref{fig:supernova histogram} we plot a histogram of the typical peak and average gas densities in the 3 cell injection region of each supernova in the XXXX XXXXX simulation.
-As shown, some of the supernova explode in high density regions around 100 \ccunit and are likely under-resolved, but a majority will be resolved.
+In general in our simulations, pre-SN feedback from stellar winds and radiation will reduce the typical densities within which our SN explosions occur.
+In addition, SN will generally be clustered, meaning each SN will reducing the typical density for each subsequent SN in that region.
+In Figure~\ref{fig:SN histogram} we plot a histogram of the typical peak and average gas densities in the 3 cell injection region of each SN in the XXXX XXXXX simulation.
+As shown, some of the SN explode in high density regions around 100 \ccunit and are likely under-resolved, but a majority will be resolved.
 
@@
 \includegraphics[width=0.4\linewidth]{sn_radius_hist}
-\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the supernovae from the simulation.
-{\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each supernova assuming a uniform medium at either the peak or average density in the injection region.
+\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation.
+{\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each SN assuming a uniform medium at either the peak or average density in the injection region.
 The vertical lines show one and 4.5 cell widths.
-This shows that a fraction of these supernovae are certainly under resolved, with R$_{\rm PDS}$ less than a single cell size, but the majority are well resolved.}
-\label{fig:supernova histogram}
+This shows that a fraction of these SNe are certainly under resolved, with R$_{\rm PDS}$ less than a single cell size, but the majority are well resolved.}
+\label{fig:SN histogram}
 \end{figure}
@@
 This code is publically available at https://github.com/aemerick/onez.
-In the simplest case, one can generate a series of star particles and examine their resulting properties, including wind and supernova yields, as a function of mass and metallicity.
+In the simplest case, one can generate a series of star particles and examine their resulting properties, including wind and SN yields, as a function of mass and metallicity.
 Included also are more complicated examples of running the full one-zone model.

### 2018-02-16 main.tex
edited all of appendix but still thinking about last comment

@@
 By construction, these phases are mutually exclusive.
-In the below, $f_{\rm H_2}$ is the molecular hydrogen fraction by abundance.
+In the below, $f_{\rm H_2}$ is the molecular hydrogen fraction
+%mm2 by abundance, [to avoid the ambiguity of fraction by proton number or total mass]
+   of the total gas mass.
 
@@
 \item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
-\item Molecular: $T < 10^2$, $f_{\rm H_2} > 0.5$
+\item Molecular: $T < 10^2$~K, $f_{\rm H_2} > 0.5$
 \end{enumerate}
@@
 A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section.
-We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \texttt{http://www.pa.uky.edu/~verner/photo.html}} The black body approximation is accurate to within 5\%, yet substantially easier to compute on the fly as integrals over the black body spectrum can be expressed as infinite series that rapidly converge to high precision.
+We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \texttt{http://www.pa.uky.edu/~verner/photo.html}} The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision.
 Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.
@@
 
-The left panel of Figure ~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SNe in the simulations presented in this work.
+The left panel of Figure ~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in the simulations presented in this work.
 As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
@@
 The right panel of Figure ~\ref{fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
-\[
+\begin{equation}
 R_{\rm PDS} = 
@@
 \end{cases*}
-\]
+\end{equation}
 where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$.
@@
 We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each SN.
-As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but that up to 10\% are somewhat under-resolved.
+As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but up to 10\% are somewhat under-resolved.
 In general, these are SN explosions from the most massive (i.e.
@@
 \section{Resolution Study}
-\label{appendix:resolution study}
-We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate (left), mass evolution (middle), and metal ejection/retention fractions (right) for our high resolution simulations (solid) as compared to two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc.
+\label{appendix:resolution_study}
+
+%mm2
+    {\bf [This appendix should be cited in the main paper]}
+We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions for our high resolution simulations as compared to two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc.
 The physics in each of these simulations remains the same.
@@
 The line colors in the middle panel are the same as in Figure~\ref{fig:sfr_mass_evolution}, where the total disk mass is shown in black, cold gas mass in blue, H$_2$ mass in orange, and stellar mass in red.}
-\label{fig:resolution}
+\label{fig:resolution_study}
 \end{figure*}
 
-As shown in these diagrams, resolution certainly changes the evolution, but not dramatically.
-We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation, but point has not been confirmed.
-Clearly, the initial SFR over the first 100~Myr is different in each simulation; it is larger in each of the lower resolution runs.
-This is because the initial SN driving is less resolved, leading to over cooling and an increase in the initial star formation rate.
+Figure~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, it does not do so dramatically.
+We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
+%mm2, but point has not been confirmed. 
+Clearly, the initial SFR over the first 100~Myr is different in each simulation: it is larger in each of the lower resolution runs.
+This is because the initial SN driving is less resolved, leading to overcooling and an increase in the initial star formation rate.
 This is much less an issue for the SN from real star particles as the pre-SN feedback (winds and radiation) are capable of decreasing the local density enough to resolve the Sedov radius.
@@
 This is an interesting difference, as the resolution decrease primarily affects the disk of the galaxy; little to none of the halo volume is refined to the highest resolution, and so should be unaffected by this change.
-\textbf{I'm a bit puzzled by this difference...}
+\textbf{I'm a bit puzzled by this difference...
+}
 

### 2018-02-16 main.tex
added final comment on puzzles in resolution study. This is the end of this revision

@@
 %mm2
-    {\bf [This appendix should be cited in the main paper]}
+    {\bf [This important appendix should be cited in the main paper, probably at least
+once in the body and once in the conclusions.]}
 We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions for our high resolution simulations as compared to two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc.
@@
 \textbf{I'm a bit puzzled by this difference...
-}
+MM: Staring at Figure~\ref{fig:phase_resolution}, the key differences seem to be that at low resolution the locus of warm, presumably ionized gas at densities of $10^{-2}$ appears cooler, there's substantially less mass at $10^4$~K and extremely low densities, and substantially {\em more} mass at $10^6$~K, which is presumably what's carrying the metals out of the halo the low resolution runs.
+Perhaps we are somehow not properly resolving adiabatic expansion in the plane or something like that??}
 

### 2018-02-20 main.tex
Update on Overleaf.

--- 2018-02-16 main.tex
@@
 
-%mm2 Due to its complexity, the 
-Detailed interstellar medium (ISM) and chemical abundance properties of galaxies
-%beyond total metallicity
-are sensitive tests of the underlying physical processes that govern galaxy evolution.
+Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution.
 Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
@@
 %mm2 I think there does need to be some introduction to this discussion:
-   However, the bulk of this work has been done with fully Lagrangian
-%mm2 Fully Lagrangian schemes, like native 
-smoothed particle hydrodynamics (SPH), 
-%mm2 are incapable of capturing
-    with a few recent exceptions  \citep{Few2012,Few2014,Vorobyov2015}. In its original form, 
-    SPH cannot model
-mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
+However, the bulk of this work has been done with fully Lagrangian smoothed particle hydrodynamics (SPH), with a few recent exceptions  \citep{Few2012,Few2014,Vorobyov2015}.
+In its original form, SPH cannot model mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
 This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017a}.
@@
 While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution or additional viscosity to reduce.
-Molecular diffusion %mm2
-    or even turbulent mixing
-is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
+Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
 Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
-Mixing behavior is tied critically to the feedback source (stellar winds, supernovae (SNe), and possibly more exotic sources)
-%mm in which they are injected to
-    that inject metals into 
-%mm2
-    different phases of 
+Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
 the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
 The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
-%mm2 [cited above] \textbf{Still not sure about this sentence - but I do need a way to cite mentioned papers:} Extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.
-
-%mm2 [broke up sentence]
+
 Increasing physical resolution reduces reliance on sub-grid physics for mixing.
@@
 The most straightforward
-solution is to remove the SSP formalism entirely and simply track stars as individual particles,
-%mm2 [maybe it would be best to just remove this.] However, the number of particles required to do so make this computationally prohibitive in all but the smallest of galaxies ($M_{*} \lesssim 10^{7} {\rm M_{\odot}})$, let alone in a cosmological simulation.
-    which we do here.
-
-%mm2 [if we were to keep the previous sentence, we'd need to segue like this.]
-%   Nevertheless, we 
+solution is to remove the SSP formalism entirely and simply track stars as individual particles, which we do here.
+
 We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies.
@@
 Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar wind feedback from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
-%mm2
-  We include stellar feedback from stellar winds, core collapse and Type Ia SNe,    
-  photoelectric heating, and ionizing radiation.
-
-Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. self-consistent set of stellar yields. 
-%mm2 
+We include stellar feedback from stellar winds, core collapse and Type Ia SNe, photoelectric heating, and ionizing radiation.
+
+Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime.
+self-consistent set of stellar yields.
 We track yields from massive and AGB star winds, and SNe.
 In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
-This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed
-%mm2
-   distributions of
-chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
-%mm2 
+This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
 This paper is the first in a series examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
-%mm2 [this is somehow redundant with the previous paragraph.  I have moved a few things up.]
-% In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}.
-For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia SNe, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer.
-In addition, we couple to a self-consistent set of stellar yields
-%to track yields from massive star stellar winds, AGB star winds, and SNe. 
 We describe each mode of our multi-channel feedback
-in detail in Sect.~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation
-%mm2 
-   in Sect.~\ref{sec:IC}, show results from this simulation in Sect.~\ref{sec:results}, discuss the 
-   results in Sect.~\ref{sec:discussion}, and conclude in Sect.~\ref{sec:conclusion}.
+in detail in Sect.~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Sect.~\ref{sec:IC}, show results from this simulation in Sect.~\ref{sec:results}, discuss the results in Sect.~\ref{sec:discussion}, and conclude in Sect.~\ref{sec:conclusion}.
 
@@
 \label{sec:methods}
-%mm2 In  summary, 
 We produce high-resolution, galaxy-scale simulations tracking stars not as SSPs, but as individual stars sampled from an assumed IMF.
@@
 We
-assume collisional ionization equilibrium for all other elements in order to
-use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
+assume collisional ionization equilibrium for all other elements in order to use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
 Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
@@
 We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors.
-We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms
-with the associated local gas abundances for each species.
+We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species.
 In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked.
@@
 
-%mm2 The computational domain in an adaptive mesh refinement simulation is adaptively refined up to a designated resolution limit for a given set of refinement criteria. We require that
-     We refine the mesh whenever 
-the Jeans length 
-%mm2 be
-    is no longer
-resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution.
+We refine the mesh whenever the Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution.
 Our maximum resolution in the simulations presented here is 1.8~pc.
@@
 The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001,RobertsonKravtsov2008}.
-
-%(\textbf{I contrasted this to Hu's work which allows arbitrarily high densities, hoping feedback mitigates how high the densities actually get, but took it out. Leave it in?})
 
@@
 In order to resolve individual star formation events on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
-Each cell at the maximum refinement level is capable of forming stars if it
-%mm2 
-   contains gas that 
-meets the following local criteria
-%mm2 [removed extraneous subscripts and simplified a bit]
-     on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$:
-1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
+Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
 Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K.
@@
 
-%mm2 The gas mass converted to stars in a time step, $dt$, is
 The stellar mass formed during a timestep $\Delta t$ is
@@
 In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
-If it does, we randomly sample
-%mm2 over 
-   from
-the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle 
-%mm2 if 
-   when 
-the total stellar mass formed exceeds 100 M$_{\odot}$. We 
-%mm2 make the simple assumption of 
-     assume 
-a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over
-%mm2
-   the range between  
-a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
+If it does, we randomly sample from
+the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
+We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
 Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
@@
 
-%mm2 [moved para break up]
 Stars evolve during the simulation, by losing mass from stellar winds and SNe as described below, and by changing types, but persist throughout the entire simulation.
@@
 Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
-Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass,
-%mm2 
-   metal, 
-or energy ejection.
+Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass, metal, or energy ejection.
 
@@
 Satisfying the Courant time step becomes prohibitively expensive following this gas, with time steps dropping to $\Delta t \sim$~100~yr.
-%mm2 , particularly as stellar wind bubbles have typical temperatures of 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
-[This yields a sound speed on the same order as the flow velocity, more or less by energy conservation, so doesn't change the timestep.]
 For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
@@
 Stars between  $M_{\rm thresh} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
-Due to the high resolution
-%mm2
-    {\bf [is this resolution variation from an earlier version of the paper?]}
-(1.5--2.5 pc depending on galaxy size) of our simulations, we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}). We 
-%mm2 find injecting 
-   inject
-thermal energy alone in a three-cell radius spherical region around the star particle,
-%mm2
-   which we find to be sufficient to resolve the SN explosions.
+Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}).
+We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
 We continue to track any remaining stellar mass after the SNe as a massive remnant tracer particle.
@@
 We note however that for the low SFRs in our isolated dwarf galaxy simulation, the first Type Ia SN only appears after a few hundred megayears of simulation time.
-%mm2 For example, by 
-    By
-the end of the simulation presented here (500~Myr), only 18 have gone off.
+By the end of the simulation presented here (500~Myr), only 18 have gone off.
 At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
@@
 We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution model.
-%\textbf{I went in detail on the DTD model here out of frustration of the lack of detail in other works, but I can trim this if needed (AE):  %mm2 At this point, the paper is large anyway, so I'd not worry about it.
-I have cleaned up the text a bit in this paragraph, using ApJ style apposition rather than parentheses and such.}
 The Type Ia SN rate is taken to be a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope $\beta$ and normalization $N_{\rm Ia}/M_{\rm SF}$ are observables.
@@
 As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through the ray tracing methods described below.
-% AE (no longer the case): We here use two different simulations of the same galaxy to demonstrate the importance of following radiation feedback with full radiative transfer methods (see Section~\ref{sec:IC}).
 
@@
 We follow \ion{H}{1} and \ion{He}{1} ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
-% AE: (removed) Radiation pressure is expected to be an important source of feedback only in more massive galaxies; we explore this point further in this work.
 
@@
 Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low IR opacity, we ignore this effect.
-%mm2 [seems to have been done] \textbf{cite davis and stone, Zhang and davis?}
 
@@
 We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
-%mm2
-    {\bf Shouldn't the units here include s$^{-1}$ rather than s?}
 \begin{equation}
 \label{eq:PE}
-\Gamma_{\rm pe} = (1.3 \times 10^{-24} \mbox{~erg~s~cm}^{-3})\, \epsilon n_{\rm H} G_{\rm eff} D 
+\Gamma_{\rm pe} = (1.3 \times 10^{-24} \rm{erg~s^{-1}~cm^{-3}})\, \epsilon n_{\rm H} G_{\rm eff} D 
 \end{equation}
@@
 \label{sec:IC}
-The galaxy 
-%mm2 presented in this work 
-   simulated as an example here
-is constructed to have properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
-Leo P is gas rich,
-%mm2 with $M_{\rm gas} > M_{*}$ and low metallicity, 
-with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and
-%mm2
-   low metallicity,
+The galaxy simulated as an example here is constructed to have properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
+Leo P is gas rich, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and low metallicity,
 with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity fraction of $Z/Z_{\odot} \sim 5.4\times10^{-4}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}.
@@
 We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-%mm2 [redundant with caption] Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation (0, 150, 300, and 500 Myr).
-In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points.
-%
-These Figures show 
-%mm2 increased gravitational potential towards the center of our dwarf galaxy leads to [can we demonstrate this?
-Otherwise it seems like an unsupported claim, since it could have to do with other things like the surface density profile, the rotational velocity profile, etc.]
-inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
+These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
 This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
-%mm2 This region quickly becomes volume-filled with both 
-    This central region quickly fills with
-warm and hot gas generated from radiation feedback and SNe respectively.
+This central region quickly fills with warm and hot gas generated from radiation feedback and SNe respectively.
 Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels.
@@
 \caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation.
-Shown are the density weighted projection of number density (top row), temperature slices (second row),
-%mm2 and integrated projections giving 
-\ion{H}{1} column density (third row), and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single black dot.}
+Shown are the density weighted projection of number density (top row), temperature slices (second row), \ion{H}{1} column density (third row), and H$_2$ column density (fourth row).
+Each individual main sequence star particle is shown in the number density projections as a single black dot.}
 \label{fig:panel_x}
@@
 Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--200~pc.
-%mm2 [moved from above]
-  Towards the end of the simulation time, the half-light radius is $390 \pm 21$ pc, where the 
-  uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
+Towards the end of the simulation time, the half-light radius is $390 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
 Although the disk remains thin beyond the half-light radius, with a scale height of around 40--60~pc, it is fully resolved at all radii.
@@
 For Leo P, located at 1.7~Mpc, \ion{H}{1} observations that are capable of detecting the diffuse \ion{H}{1} throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest \ion{H}{1} clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
-%We additionally compute the mass weighted height of the disk, defined as $H = (\sum{Mz^2}/\sum{M})^{1/2}$, where the summation is over each gas cell, as a function of radius (not shown here).
-$H$ is generally larger than the scale height by a factor of 2, but is comparable to the scale height at radii with ongoing star formation, indicating a particularly uniform-then-truncated density distribution.
-At large radii, away from active star formation, $H$ is roughly 50 pc, or $\sim$ 3 times the scale height.
 
@@
 
-We present the star formation rate (SFR) and core collapse SN rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between 2--4$ \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly at this level for 100 Myr, and then drops to an average of about
-%mm2
-  {\bf [Shouldn't this be $4 \times 10^{-5}$?]}
- $4 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations. By the end of the simulation, the SFR is very low and 
-%mm2
-   star formation events are
-infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$.
+We present the star formation rate (SFR) and core collapse SN rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between 2--4$ \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly at this level for 100 Myr, and then drops to an average of about $4 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations.
+By the end of the simulation, the SFR is very low and star formation events are infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$.
 The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation.
@@
 
-%mm \footnote{  [This is rather too long for a footnote, I think.]
 We note that the granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
@@
 Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.
-%mm2 Note that the vertical axis limits in the left panel have been scaled to the same numerical values, yet with different units for the SFR and SN rate.
-   Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical 
-   axis as the SFR.}
-% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
+Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.}
 \label{fig:sfr_mass_evolution}
@@
 
-%mm2 \subsection{Phase Diagrams and ISM Properties}
 \subsection{ISM Properties}
-
 \label{sec:phase}
@@
 See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-Each of these phases exist throughout our simulation, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and
-%mm2 diffuse 
-  radiative
-and shock heating from stellar feedback throughout the galaxy's evolution. Here we discuss the %mm phase
-   thermodynamic 
-properties of the gas within the inner halo of our dwarf galaxy.
-
-Figure~\ref{fig:phase} shows the temperature-density 
-%mm2 phase diagram 
-    distribution
-of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr. One can readily identify the two
-%mm2  most massive regions of gas [eliminated phase language below for consistency with your claim a bit further down the para that there are not well-defined phases.]
-    regimes containing most of the mass 
-in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
-Several notable features of the
-%mm2 phase diagram 
-     distribution
-include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
+Each of these phases exist throughout our simulation, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
+Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.
+
+Figure~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
+One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
+Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
 We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
@@
 The region in the lower right corner indicates our density and temperature thresholds for star formation.}
-% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
 \label{fig:phase}
@@
 After this point, the molecular component dominates through the end of the simulation.
-%mm2 [remove para break]
 Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining mass dominated by the WNM.
@@
 
-%mm[new para]
 These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}.
@@
 \caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM.}
-% This figure only includes gas present within the disk of the galaxy, as defined in the beginning of ~\Section{sec:results}.
 \label{fig:ISM_evolution}
@@
 However, the ISRF varies significantly over time, fluctuating by an order of magnitude or more at any given radius.
-
-%mm2 \textbf{In response to MM's comment: I focus on G$_o$ here because I found it to be the more general quantity, getting at how one should think of / model the time-and-space-varying ISFR in a tiny dwarf galaxy (i.e.
-how does this compare to a uniform or 1D radial profile).
-G$_{eff}$ is convolved with local density and temperature variations, and is thus a bit harder to parse / interpret.
-Though possibly I should show both?
-%MM: given how low the optical depth is, it probably doesn't matter.}
 
@@
 The lack of dramatic trend with radius in both diagrams suggests that one could model the ISRF in low mass dwarf galaxies using a uniform heating / ionization rate; however, this would still fail to capture the fact that any given region of the galaxy will experience order of magnitude or more fluctuations in the incident flux.
-% These fluctuations are likely important in reducing star formation locally around young, massive stars.
-This effect would be challenging to capture with a simple model.
-(AE this bit is moved to the end of section)
 
@@
 In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency.
-It
-%mm2 is unclear 
-   remains to be seen
-which of these two modes of feedback is more important in controlling star formation.
-
-%mm (Emerick et. al. in prep).  [I'd only insert the reference when there is an actual astro-ph number to support it.]
+It remains to be seen which of these two modes of feedback is more important in controlling star formation.
 
@@
 \label{sec:chemical evolution}
-%mm2 \textbf{This section saw significant change. Removed previous mention of stellar abundances and species retention fractions. Much of below is new(ish)}
 
@@
 This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed.
-This suggests either that metals are transported first through a hot phase
-%mm2 
-   with high sound speed, 
-or by efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}.
+This suggests either that metals are transported first through a hot phase with high sound speed, or by efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}.
 It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
@@
 \includegraphics[width=0.32\linewidth]{temperature}\\
-\includegraphics[width=0.32\linewidth]{log_OH} 
-\includegraphics[width=0.32\linewidth]{log_NH}
+%\includegraphics[width=0.32\linewidth]{log_OH} 
+%\includegraphics[width=0.32\linewidth]{log_NH}
 \includegraphics[width=0.32\linewidth]{log_NO}
-\caption{Five slices in the mid-plane of our dwarf galaxy at an arbitrary time 
-%mm2 [give the time]
-  of {\bf XXX}~Myr after the start of star formation,
-demonstrating the power of our chemical evolution model.
+\caption{Five slices in the mid-plane of our dwarf galaxy at an arbitrary time of 350~Myr after the start of star formation, demonstrating the power of our chemical evolution model.
 We show the number density and temperature in this region of the galaxy (top row), along with three different elemental abundance ratios, O/H (bottom left), N/H (bottom middle), and N/O (bottom right).

### 2018-02-27 main.tex
Update on Overleaf.

@@
 \renewcommand*{\subsectionautorefname}{Section} %for \autoref
+%\usepackage{graphicx}
+
+%\usepackage[active,floats,tightpage]{preview}
+%    \setlength\PreviewBorder{1em}
 
@@
 \begin{abstract}
-We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including
-%mm2 
-     {\bf [should we somehow make clear that we are ignoring energetic feedback from stellar winds?]}
-stellar winds from massive and asymptotic giant branch stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+Galactic chemical evolution is driven through stellar feedback and its ability to drive metal mixing within the interstellar medium (ISM) and beyond the galaxy in outflows.
+However, we are far from a complete understanding of feedback along and galactic chemodynamics in general.
+In order to better understand this relationship, we have developed a new model for stellar feedback and galactic chemical evolution at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
+For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including stellar winds from massive and asymptotic giant branch stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
 %This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
 We furthermore follow the star-by-star stellar yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
-We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium.
-We present the first application of these methods in a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
+We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
 We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
 Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations.
-Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions.
-We end with a discussion on how this work impacts our understanding of galactic chemical evolution on a species-by-species basis.
-{\bf the conclusion of this discussion should perhaps be mentioned.}
+Finally, we demonstrate that these simulations yield valuable information on the differences with which individual metal species mix and evolve within the ISM.
+
+\textbf{CHANGE: Cleaned up a few sentences. better intro + last sentence. removed large H2 content mention (should I put this last one back?).}
+%Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions.
+
+% mm: conclusion of this discussion should perhaps be mentioned
+%% AE (reply): reworded slightly but still have no detailed mention of this.
 \end{abstract}
@@
 %mm2 I think there does need to be some introduction to this discussion:
-However, the bulk of this work has been done with fully Lagrangian smoothed particle hydrodynamics (SPH), with a few recent exceptions  \citep{Few2012,Few2014,Vorobyov2015}.
-In its original form, SPH cannot model mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
-This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017a}.
-Even more, there are many possible sub-grid models that are not applicable in every regime \citep[see ][]{Revaz2016}, though recent studies have shown great improvements in characterizing various methods \citep{Escala2017}.
+However, much of this work has been done with Lagrangian smoothed particle hydrodynamics (SPH) schemes, with a few recent exceptions  \citep{Few2012,Few2014,Vorobyov2015}.
+In its original form, SPH does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
+This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possibly models that are not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
 While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution or additional viscosity to reduce.
@@
 The most straightforward
-solution is to remove the SSP formalism entirely and simply track stars as individual particles, which we do here.
+solution is to remove the SSP formalism entirely and simply track stars as individual particles. %which we do here
 
@@
 Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar wind feedback from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
-We include stellar feedback from stellar winds, core collapse and Type Ia SNe, photoelectric heating, and ionizing radiation.
+We also include core collapse and Type Ia supernova feedback, photoelectric heating, and Lyman-Werner dissociation.
 
 Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime.
-self-consistent set of stellar yields.
-We track yields from massive and AGB star winds, and SNe.
+This includes yields from massive and AGB stellar winds, and SNe.
 In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
@@
 We describe each mode of our multi-channel feedback
-in detail in Sect.~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Sect.~\ref{sec:IC}, show results from this simulation in Sect.~\ref{sec:results}, discuss the results in Sect.~\ref{sec:discussion}, and conclude in Sect.~\ref{sec:conclusion}.
+in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.
 
@@
 To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background.
-We
-assume collisional ionization equilibrium for all other elements in order to use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix ~\ref{appendix:cooling}), and an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
+We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}).
+We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
 Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
-We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure.
-In addition, we follow the optically thin, non-ionizing UV radiation from these stars leading to photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
+We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on \ion{H}{1}.
+In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
 We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both.
@@
 We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick.
-Specifically, simulations presented here were conducted at changeset 445de816fd99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
+Specifically, simulations presented here were conducted at changeset 5cc7cea.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
 We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}).
@@
 
-We refine the mesh whenever the Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or the region reaches the maximum resolution.
-Our maximum resolution in the simulations presented here is 1.8~pc.
+We refine the mesh whenever the Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or until the region reaches the maximum resolution (1.8~pc).
 At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation.
@@
 This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
-The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001,RobertsonKravtsov2008}.
+The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.
 
@@
 These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
+{\bf {\it (addressing MM's comment below (I was unable to find a ref.
+where this was accounted for)}: Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.
+}
 
 %mm2 
-   {\bf [I'm a bit confused here: how does the ISRF interact with the cooling?  Shouldn't that move you around in the Cloudy tables, possibly quite substantially?]}
+   {\bf [MM: I'm a bit confused here: how does the ISRF interact with the cooling?  Shouldn't that move you around in the Cloudy tables, possibly quite substantially?]}
 
@@
 \begin{equation}
-%mm2 M_{ {\rm gas} \to *} = \epsilon_{\rm f} M_{\rm gas} \frac{dt}{\tau_{\rm ff}}.
          M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
@@
 We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
-We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any pre-existing population.
+We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population.
 
@@
 Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
-Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{shull1995}, stellar winds are potentially important sources of pre-SN feedback.
-In models that include feedback energy from stellar winds from both AGB and massive stars, we inject the feedback energy in a three-cell radius spherical region centered on the emitting star particle, assuming full thermalization of the wind kinetic energy.
+Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback.
+We inject the feedback energy in a spherical region with a three-cell radius centered on the emitting star particle, assuming full thermalization of the wind kinetic energy.
 The total injected energy in timestep $\Delta t$ is therefore $E_w = \dot{M}\Delta t \times v^2_w + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
@@
 For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
-In our case, we fix massive stellar wind velocities to $v_w = 1$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
+In our case, we fix massive stellar wind velocities to $v_w = 20$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
 Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies.
@@
 %where $M_{\rm *}$ is the initial mass of the WD progenitor.
-We follow the common assumption that progenitor stars with masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.
+We follow the common assumption that progenitor stars with initial masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.
 
@@
 We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star.
-Stars less massive than about 15 M$_{\odot}$ are generally off of the OSTAR2002 grid, and massive stars with sub-solar metallicity generally have effective temperatures above the OSTAR2002 grid.
+Stars less massive than about 15 M$_{\odot}$ and very massive stars with sub-solar metallicity are generally not well sampled by the OSTAR2002 grid.
 In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).
@@
 Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017}.
-Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low IR opacity, we ignore this effect.
+Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.
 
@@
 \label{sec:IC}
-The galaxy simulated as an example here is constructed to have properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
+We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy.
+The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
 Leo P is gas rich, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and low metallicity,
@@
 We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$.
-We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 3.5\times 10^{8}~M_{\odot}$, $R_{\rm vir}~=~14.3$~kpc and r$_{\rm s} = 370$~pc.
-This gives a maximum circular velocity $V_{\rm max} = 17.4$~km~s$^{-1}$ at $R_{\rm vmax}~=~1.2$~kpc.
-These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties near the minimum halo mass expected for galaxies of this size \citep{Ferrero2012}.
+We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$, $R_{\rm vir}~=~27.4$~kpc and r$_{\rm s} = 990$~pc.
+This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc.
+These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012}.
 We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in future work.
@@
 These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
-We note that this initial driving is somewhat ad hoc in that do not include any other effects from the stellar population that would have caused these SNe.
+We note that this initial driving is somewhat ad hoc in that we do not include any other effects from the stellar population that would have caused these SNe.
 
@@
 ISM properties are calculated considering only the gas contained within the disk of the galaxy.
+We include a resolution study in Appendix \ref{appendix:resolution_study},
 
@@
 
-We present the star formation rate (SFR) and core collapse SN rate evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between 2--4$ \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly at this level for 100 Myr, and then drops to an average of about $4 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations.
+We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between 2--4$ \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly at this level for 100 Myr, and then drops to an average of about $4 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations.
 By the end of the simulation, the SFR is very low and star formation events are infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$.
@@
 By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\%, of the total mass in the galaxy's disk.
-The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\% and is about equal with the \ion{H}{1} gas.
+The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\%; at this point, it is about equal with the \ion{H}{1} gas.
 This is because the total amount of mass in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained.
@@
 Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
-We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
-We emphasize that the molecular ISM phase is defined as all regions with f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content as decoupled from the rest of the gas.
+We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (\ion{H}{1}M).
+We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content as decoupled from the rest of the gas.
 See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
@@
 Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining mass dominated by the WNM.
-While the CNM has a negligible volume fraction, the WNM, WIM, and HIM each occupy roughly the same volume fraction.
-However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy.
+While the CNM has a negligible volume fraction, the WNM, WIM, and \ion{H}{1}M each occupy roughly the same volume fraction.
+However, the frequent fluctuations in the \ion{H}{1}M volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy.
 Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
@@
 These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}.
-They find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas having $\sim$ 10\% of the mass, and occupying negligible volume, and hot gas occupying $\sim$ 10\% of the volume, but having negligible mass.
+They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (ionized and neutral), with cold gas having $\sim$ 10\% of the mass, and occupying negligible volume, and hot gas occupying $\sim$ 10\% of the volume, but having negligible mass.
 Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few.
 The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
+\textbf{AS: Should I note here that we compared cooling curves to Hu et. al. and did not find anything unusual?}
 
@@
 For this reason we only shade between the first quartile and maximum values.
-\ion{He}{1} is very similar to \ion{H}{1}, with a small vertical offset, and is not shown for clarity.}
+\ion{He}{1} ionizing radiation is very similar to \ion{H}{1} ionizing radiation, with a small vertical offset, and is not shown for clarity.}
 \label{fig:ISRF}
@@
 The striking contrast between the two diagrams is due to the shielding of the \ion{H}{1} ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
-From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy various greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
+From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
 Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation.
 In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency.
-It remains to be seen which of these two modes of feedback is more important in controlling star formation.
+It remains to be seen which of these two modes of feedback is more important in regulating star formation.
 
@@
 Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
-Using a fit provided in \citet{Muratov2015} to extrapolate and compare at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
+Using a fit provided in \citet{Muratov2015} to extrapolate and compare $\eta$ at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
 These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
-We note, however, that our results are much closer to the \citep{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly have much smaller mass loading factors at 0.25 $R_{\rm vir}$.
+We note, however, that our results are closer to the \citep{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly have much smaller mass loading factors at 0.25 $R_{\rm vir}$.
 
@@
 The distribution has a very long tail out to and beyond 500~km~s$^{-1}$.
-The dominant launching mechanism in this simulation are SNe, generating a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
-However, as shown, the HIM comprises very little of the outflow by mass.
-Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM.
-Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
+The dominant launching mechanism in this simulation are SNe, generating a rapidly moving and volume-filling \ion{H}{1}M, consistent with the results in \citet{Hu2016,Hu2017}.
+However, as shown, the \ion{H}{1}M comprises very little of the outflow by mass.
+Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving \ion{H}{1}M.
+Some of this warm gas certainly originates from adiabatically and radiatively cooled \ion{H}{1}M, however.
 The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
@@
 \caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-The outflowing material is multiphase, broken into WNM, WIM, and HIM.
+The outflowing material is multiphase, broken into WNM, WIM, and \ion{H}{1}M.
 See Section~\ref{sec:phase} for definitions of these regimes.
@@
 In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}.
-We define the metal mass loading factor as
+The parameter used to quantify metal outflow efficiencies varies among works.
+Here, we define the metal mass loading factor as
 \begin{equation} \label{eq:eta-metal}
@@
 \subsubsection{Metal Distribution within the ISM}
-
-It is important to understand how metals from each source of stellar yields (massive and AGB stellar winds and SNe) enrich the ISM.
+\textbf{CHANGE: Simplified plot to just log(N/O) to make this less confusing and easier to interpret. Cleaned up text accordingly.}
+It is important to understand how metals from each source of stellar yields enrich the ISM.
 Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}.
 This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed.
-This suggests either that metals are transported first through a hot phase with high sound speed, or by efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}.
+Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}.
 It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
-It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few HII regions for a detailed examination.
-
-We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
+It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few \ion{H}{1}I regions for a detailed examination.
+
+%We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
 The top two panels give the slices of number density (top left) and temperature (top right) in the mid-plane of a portion of our dwarf galaxy.
@@
 
+We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
+The left two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy.
+These serve to guide the eye in the right panel, clearly indicating regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
+The left panel gives the abundance ratio of N to O throughout the ISM.
+
 \begin{figure*}
-\centering
-\includegraphics[width=0.32\linewidth]{number_density} 
-\includegraphics[width=0.32\linewidth]{temperature}\\
-%\includegraphics[width=0.32\linewidth]{log_OH} 
-%\includegraphics[width=0.32\linewidth]{log_NH}
-\includegraphics[width=0.32\linewidth]{log_NO}
-\caption{Five slices in the mid-plane of our dwarf galaxy at an arbitrary time of 350~Myr after the start of star formation, demonstrating the power of our chemical evolution model.
+%\gridline{\fig{DD0557_Slice_z_logN_O}{0.8\textwidth}{}}
+%\gridline{\fig{DD0557_Slice_z_number_density}{0.4\textwidth}{}
+%          \fig{DD0557_Slice_z_Temperature}{0.4\textwidth}{}}
+\includegraphics[width=0.98\linewidth]{log_NO_panel}
+            \caption{Three slices in the mid-plane of our dwarf galaxy at an arbitrary time of 350~Myr after the start of star formation showing the variation in gas phase metal abundances.
+The left slice gives the ratio of the abundance between N and O, while the number density and temperature are shown on the right.
+}
+\label{fig:metal_slices}
+\end{figure*}
+
+  % \caption{Three slices in the mid-plane of our dwarf galaxy at an arbitrary time of 350~Myr after the start of star formation, demonstrating the power of our chemical evolution model.
 We show the number density and temperature in this region of the galaxy (top row), along with three different elemental abundance ratios, O/H (bottom left), N/H (bottom middle), and N/O (bottom right).
@@
 \textbf{(AE: need to adjust axis label size)}}
-\label{fig:metal_slices}
-\end{figure*}
-
-Beginning with log(O/H), the gas from the recent SN explosion is abundantly clear, with a higher oxygen abundance by at least 1 dex than its surroundings.
-The oxygen abundance throughout the rest of the ISM does vary, with
-%mm2 some 
-   almost all 
-dense regions showing 
-%mm2 slightly higher 
-   modest enhancements in oxygen abundance compared to their less dense surroundings.
-%mm2 , but the variation is not dramatic. 
+
+%\begin{figure*}
+%\centering
+%\includegraphics[width=0.5\linewidth]{test}\\
+%\includegraphics[width=0.32\linewidth]{y} 
+%\includegraphics[width=0.32\linewidth]{DD0557_Slice_z_Temperature}\\
+%\includegraphics[width=0.32\linewidth]{log_OH} 
+%\includegraphics[width=0.32\linewidth]{log_NH}
+%
+%\end{figure*}
+
+The number density and temperature panels clearly show a multi-phase ISM: the CNM consists of cold filaments that connect dense clumps of molecular gas which are readily visible in both diagrams.
+Distinguishing the WNM and WIM is difficult, but the lower density regions between the cold filaments is dominated by these phases.
+Gas from a recent SN explosion is clearly visible as the hot (T~$\gtrsim 10^{6}$~K) and diffuse region in the top left corner.
+As shown in the left panel, log(N/O) varies significantly over this section of the ISM with notable differences across the various phases and ISM structures.
+As expected, O is overabundant throughout the ISM, most strongly in the region of recent SN enrichment (top left, dark purple region in log(N/O) / dark red in temperature).
+However, the relative abundance of N increases significantly in the warmer phases, reaching equipartition (white color in log(N/O)) in many patches throughout the ISM.
+There are three regions in particular that are overabundant in N (green color).
+These are sites of recent AGB winds that have yet to mix with the rest of the ISM.
+
+% Beginning with log(O/H), the gas from the recent SN explosion is abundantly clear, with a higher oxygen abundance by at least 1 dex than its surroundings.
+The oxygen abundance throughout the rest of the ISM does vary, with almost all dense regions showing modest enhancements in oxygen abundance compared to their less dense surroundings.
 The ratio log(N/H), however, shows slightly more significant variation throughout the ISM.
@@
 
-%mm2 [new para for the explanation]
 At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars.
 Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
-This suggests that the energetic differences between the injection sources can drive abundance variations within the ISM of our dwarf galaxy.
-%mm2 It is possible, then, 
-   This suggests
-that metal mixing within the ISM (and also metal ejection from the ISM) 
-%mm2 is a process 
-is species dependent.
+Given the variations in Figure~\ref{fig:stellar_abundance}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
+This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
 A more detailed analysis is beyond the scope of this work, but we plan to investigate this point, and potential observational consequences for stellar abundances, in future work.
@@
 The CNM contains roughly 50-60\% of each species, with the CNM and WNM together accounting for most of the metals in the galaxy.
-The WIM contains only $\sim$ 10\% of each species, with the HIM containing very little.
-This may be counterintuitive given that most metals are initially injected into the galaxy in either the WIM or HIM phases.
+The WIM contains only $\sim$ 10\% of each species, with the \ion{H}{1}M containing very little.
+This may be counterintuitive given that most metals are initially injected into the galaxy in either the WIM or \ion{H}{1}M phases.
 However, the disk metals represent only a small fraction of the total metals produced.
@@
 In both diagrams, our simulations are given by the colored points, sampled every 1 Myr throughout the entire simulation.
+
 Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
-
-%mm [new para]
-We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs using the procedure described in \citet{Roychowdhury2014}.
-We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the
-%mm2 disk defined out to the farthest
-   area of the disk within the radius of the outermost 
-star formed within the previous 10 Myr.
+sWe have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}.
+We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the area of the disk within the radius of the outermost star formed within the previous 10 Myr.
 Likewise, $\Sigma_{\rm gas} = M_{\rm gas,10} / A_{*,10}$, where M$_{\rm gas,10}$ is the total gas mass within this defined disk.
@@
 To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He.
-There is generally no correction applied to account for any H$_{2}$ or \ion{H}{2} content.
-The molecular component is discussed further in Section~\ref{sec:molecular gas content}.
+We note that there is generally no correction made for any possible H$_{\rm 2}$ or \ion{H}{2} content.
+As shown in Section~\ref{sec:molecular gas content}, these components may be significant.
 
@@
 \caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
-%mm2 We take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$ in our simulations to make a fair comparison to the observational sample (see text for more details)
 See text for details of the calculation.
-Recent observations from the SHIELD sample \citep{Teich2016} are plotted as 
-%mm2 points
-    black points with error bars.
+Recent observations from the S\ion{H}{1}ELD sample \citep{Teich2016} are plotted as black points with error bars.
 On the left, we also give the best fit line to galaxies from the FIGGS sample from \cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \cite{Shi2011}.
-%mm2  This  is simply to indicate there 
-   There
-is no clear correlation with time in this diagram.}
+There is no clear correlation with time in this diagram.}
 \label{fig:KS}
@@
 
-%mm2 In both panels, we also 
-   We
-include recent observational constraints on these relationships
-%mm2
-    in Figure ~\ref{fig:KS}. 
-%mm2 For the KS relationship we 
-   These 
-include the best-fit line from \citet{Roychowdhury2014}, 
-%mm2 (black, dashed). In both we give recent measurements from
-the SHIELD galaxy sample \citep{Teich2016}, 
-%mm2 (black, points).
-Recently, \cite{Roychowdhury2017} demonstrated that the best fit line in the ESL from \cite{Shi2011} extends to the low mass FIGGS sample of galaxies; we give this best fit line and 1$\sigma$ errors in the right hand panel (black lines).
-  and the best-fit line with 1$\sigma$ errors from \citet{Shi2011}, which 
-  \citet{Roychowdhury2017} demonstrated extends to the low mass FIGGS sample of galaxies.
+We include recent observational constraints on these relationships in Figure ~\ref{fig:KS}.
 Our galaxy fluctuates significantly about both relationships with no clear trends in time.
@@
 
-%mm2 Fig.~\ref{fig:KS} represents a remarkable result. 
 In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
 It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
-This result is consistent with
-%mm2 recent 
-galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics (\textit{relevant citations}
-%mm2
-   starting with A. Kravtsov 2003, ApJ L.)
-%mm 
-%ae: but does this bit then contradict my statement that this is remarkable? if its 'just gravity' at play?  
-%mm2: that's the question, isn't it?  maybe keep the description of the result, but remove the claim of remarkability, as I have edited to do?
-   but also with the demonstration by \citet{Li2006} that the KS law can be reproduced 
-   by gravitation acting on an isothermal disk, which was argued to demonstrate that 
-   this represents the basic physics at work.
+This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the KS law can be reproduced by gravitation acting on an isothermal disk.
+%AE, which was argued to demonstrate that this represents the basic physics at work.
 
@@
 to be small, but is not well constrained by either theory or observations.
-Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas fractions anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
+Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
 As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.17--0.20, within this range, but significantly exceeding the few percent often found in models.
@@
 This has the seemingly counterintuitive effect that turning off the UV background actually decreases the formation rate of H$_2$, as confirmed in test simulations.
-In a test simulation ignoring H$^{-}$, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.
-
-This explains our 
-%mm2 contention 
-    disagreement
-with the simulations in \citet{Hu2016} and \citet{Hu2017}, which find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
+In a test simulation ignoring all H$^{-}$ reactions, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.
+
+This explains our disagreement with the simulations in \citet{Hu2016} and \citet{Hu2017}, which find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
 Although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
-Our model suggests that H$^{-}$ and the UV background (in the absence of a local radiation field) are critical components in H$_2$ formation in small dwarf galaxies.
-It is not surprising that the gas phase reactions dominate over grain catalysis in this low metallicity regime \citep{Glover2003}, but the total amount of H$_2$ formed is perhaps surprising.
+Our model suggests that H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies.
+It is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, but the total amount of H$_2$ formed is perhaps surprising.
 However, the rate coefficients associated with gas-phase H$_2$ formation are uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
-%In addition, \cite{Glover2006} demonstrated that the total amount of H$_2$ formed can be quite sensitive to the initial conditions.
-%mm2 Finally, our model lacks additional chemistry which 
-    Our model does lack additional chemistry that
-may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
+Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
 It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
 This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
-%ae rewrote above and took out this citation, need to see if need to put back in:
-%            there is some possible observational evidence for higher than expected ($\sim 15$ \%)   %            molecular fractions \citep{Schruba2017}, though this still remains highly uncertain.
 
@@
 
-The simulations presented here have not yet been run for the gigayear timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$.
-However, we can compare to a key observable, the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from
-%mm2
-  closed box
-stellar evolution models based on the galaxy's star formation history.
+The simulations presented here have not yet been run for the gigayear timescales required to begin to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$.
+However, we can compare to a key observable: the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from closed box stellar evolution models given the galaxy's star formation history.
 This can be done readily with Milky Way dSph's.
@@
 
-Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a %mm2 gaseous, 
-   gas-rich,
+Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich,
 star forming, low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
 Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk.
-At the end of our simulation, we
-%mm2
-   thus
-agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
-Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that
-most of the metals that have been produced at these early times will remain outside the galaxy disk.
-We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.
+As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
+However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
+Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
+%We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.
 
 It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium.
-While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of a $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero $\sim$ 60\% of ejected gas is recycled, while 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
-In our case, no metals have been ejected beyond the virial radius; this is not surprising however, given that metals ejected beyond the halo would need to travel with an average velocity of 150 km s$^{-1}$ for the entirety of our simulation time.
+While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of a $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
 We find 13.7\% of all metals lie within 1 kpc of the center of our galaxy, 26.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 38.6\% outside $R_{\rm vir}$.
-
-%mm2 [new para]
+This is consistent with previous works, but this is again an evolving quantity.
+In addition, the amount of gas that escapes the virial radius is certainly sensitive to the details of gas accretion from the IGM on this galaxy, which we cannot capture in this model.
+
 The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
 Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return.
-Our model seems to suggest that many of the metals ejected into the halo will not be recycled back into the galaxy, but this is difficult to determine with only 500~Myr of evolution.
 In addition, the accretion of pristine gas from the intergalactic medium could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals.
@@
 \label{sec:stellar winds discussion}
-Our stellar wind model significantly reduces the injected wind velocity from $\sim$1000 km s$^{-1}$ to 1 km s$^{-1}$.
+Our stellar wind model significantly reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$.
 Although our model is capable of generating realistic stellar winds with temperature profiles and radial evolution comparable to those expected from analytic calculations \citep{Weaver1977}, the hot, fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
 When considered in isolation, stellar winds are an important source of pre-SN feedback and do dramatically influence the dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
-However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or
-%mm GMCs
-   individual giant molecular clouds
-\citep{Dale2014}.
+However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}.
 They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
-Although they likely have minimal dynamical importance
-%mm 
-   at resolutions where peak densities are not anyway high enough to trap ionization 
-   fronts, 
-a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.
-%old comment: (need to ref or back up this claim: see Dale et al.
-2014 for individual clouds, while the right panel of Fig 2 in Shull \& Saken 1995 shows that the integrated wind energy from a cluster is about 10\% that of the SNe -M).
+Although they likely have minimal dynamical importance at resolutions where peak densities are not anyway high enough to trap ionization fronts, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.
+
+%\subsubsection{Magnetic Fields}
+%\label{sec:magnetic fields}
 
@@
 These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}.
-Modeling cosmic rays is challenging, however, as they encompass a wide range of energies,
-%mm2 (give range), with 
-   and there are
-significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
+Modeling cosmic rays is challenging, however, as they encompass a wide range of energies, and there are significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
 Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy.
@@
 \label{sec:binary stars}
-% Although we track individual stars and assign properties to each based on stellar evolution models, these properties are fixed.
-A more detailed model could follow each star on an interpolated stellar evolution track, which would account for variations in radiation and stellar wind properties in each star over time.
-
-Roughly half of massive stars live in binary pairs 
-%mm2 doi:10.1051/0004-6361/201219621
-   \citep{Sana2012}. 
+
+Roughly half of massive stars live in binary pairs \citep{Sana2013}.
 Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes.
@@
 Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
-% does this affect yields??
-% runaway stars
 
@@
 In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
-We present an overview of the properties of this
-%mm2 galaxy
-    simulation 
+We present an overview of the properties of this simulation
 in this work.
@@
 \begin{enumerate}
-\item Multi-channel feedback is effective in this galaxy in regulating star formation 
-%mm2 
-   to occur at a rate 
-consistent with the KS relationship and extended Schmidt law in observed galaxies. See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}.
-
-\item This feedback drives large outflows 
-%mm2 ($\eta \sim 50$ at 0.25~R$_{\rm vir}$) with
-   having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, and
+\item Multi-channel feedback is effective in this galaxy in regulating star formation to occur at a rate consistent with the KS relationship and extended Schmidt law in observed galaxies.
+See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}.
+
+\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, and
 metal mass loading factors near unity.
-By mass, nearly all of this outflow is moving with velocities below 100 km~s$^{-1}$, but there is a significant tail towards velocities up to 1000 km s$^{-1}$ (Figure~\ref{fig:outflow_velocity}).
-
-%mm2 [made this a separate item]
+By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Figure~\ref{fig:outflow_velocity}).
+
 \item 
-%mm2 This galaxy result is consistent with the observed metal retention fractions of ultrafaint dwarfs, retaining only $\sim$10\% of metals in the disk. 
 Only $\sim$10\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of ultrafaint dwarfs.
-By the end of the simulation $\sim$50\% of the remaining metals remain within the virial radius and $\sim$40\%
+By the end of the simulation $\sim$50\% of the remaining metals remain within the virial radius (but outside the galaxy) and $\sim$40\%
 have been ejected beyond the virial radius.
 The fraction in the disk remains fairly constant towards the end of the simulation, but the metals in the halo are still evolving.
-See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.
+(See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
 
@@
 \item The ISRF of our galaxy is highly varying in time, by orders of magnitude, though it is relatively uniform in space at any given time.
-It is unclear how important these fluctuations are as a source of feedback, or if the affect can
-%mm2 simply 
-be approximated with a time averaged radial profile. See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.
+It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time averaged radial profile.
+See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.
 
@@
 Finally, we used O and N as examples to briefly demonstrate that there are discernible differences in how individual metal species are distributed within the ISM of our galaxy.
-In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and how individual metals move
-%mm2 through the halos of low mass dwarf galaxies.
-  into halos. 
-% In addition, we will investigate 
+In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and how individual metals move into halos.
 This will allow us to examine
-the role each of our sources of feedback plays in driving dwarf galaxy chemodynamics.
+the role that each source of feedback plays in driving dwarf galaxy chemodynamics.
 
@@
 We gratefully recognize computational
-resources provided by NSF XSEDE through grant number TGMCA99S024, \textbf{need Pleiades alloc}, Columbia University, and the \textbf{(need proper ack.
-for Simons computing resources)}.
+resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute.
 Analysis in this work
@@
 the world. Their commitment to open science has helped make
-this work possible
-We would also like to thank for their advice and valuable conversations: John Wise, Brian O'Shea, Benoit Cote, Britton Smith, Simon Glover, Kathryn Johnston, Mary Putman, Keith Hawkins, Joshua Wall, and Chia-yu Hu.
-\textbf{AE: is this too many people?
-I do think they all deserve acknowledgement.
-(list is in no particular order).
-MM: I'd alphabetize and use first initials following ApJ style, but fine by me to keep everyone on.}
+this work possible.
+We would also like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
+Cote, S.
+Glover, K.
+Hawkins, C.
+Hu, K.
+Johnston, B.
+O'Shea, M.
+Putman, B.
+Smith, J.
+Wall, and J.
+Wise.
 
@@
 
-To aid in comparison to other works, we define our ISM phases here, as adopted from \citet{Draine2011} Table 1.3 and used consistently throughout this analysis.
+To aid in comparison to other works, we define our ISM phases here, as adopted and modified from \citet{Draine2011} Table 1.3 and used consistently throughout this analysis.
 By construction, these phases are mutually exclusive.
-In the below, $f_{\rm H_2}$ is the molecular hydrogen fraction
-%mm2 by abundance, [to avoid the ambiguity of fraction by proton number or total mass]
-   of the total gas mass.
+In the below, $f_{\rm H_2}$ is the molecular hydrogen fraction of the total gas mass.
 
 \begin{enumerate}
-\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
+\item Hot Ionized Medium (\ion{H}{1}M): $T \geq 10^{5.5}$ K
 \item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
@@
 \label{appendix:radiation}
-We detail the radiation properties of our model stars as a function of stellar mass and metallicity, both of which are assigned directly from an IMF and from the local gas properties respectively.
-The stellar radiation properties are determined from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve
-%mm off of the OSTAR2002 grid) 
-    for other stars,
-given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
+We detail the radiation properties of our model stars as a function of stellar mass and metallicity.
+The stellar radiation properties are determined from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
 In Figure~\ref{fig:stellar radiation properties} we plot these properties.
@@
 
-\section{Typical Gas Densities in SN Injection Regions}
+\setcounter{figure}{0}
+\section{Typical Gas Densities in Supernova Injection Regions}
 \label{appendix:SN}
@@
 However, physically consistent solutions have been developed \citep[e.g][]{Simpson2016} that inject a mixture of kinetic and thermal energy with a ratio that depends on resolution and local gas density.
-%mm This overcooling problem improves 
-   Overcooling becomes less important 
-with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each SN.
-We take advantage of our high (parsec scale) resolution and employ a simple thermal energy injection model for our SN feedback.
+Overcooling becomes less important with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each SN.
+We take advantage of our high resolution and employ a simple thermal energy injection model for our SN feedback.
 We demonstrate how well this resolves our SNe in the comparison simulation presented in this work.
@@
 most prompt) stars.
-We do not expect that resolving these SNe will dramatically alter our results, but note that simulations presented in future work will examine lower mass galaxies at higher resolution than those presented here.
-In those, the SNe are more resolved, but we note that using our feedback model at resolutions much less than 2 pc will require adopting a different injection mechanism.
+We do not expect that resolving these SNe will dramatically alter our results.
+However, we note that using our feedback model at resolutions much less than a few pc will require adopting a different injection mechanism.
 
@@
 
+\setcounter{figure}{0}
 \section{Cooling and Heating Rates}
 \label{appendix:cooling}
-
-%mm moved this paragraph to the start of the section and rewrote accordingly.
-To derive the diffuse cooling and heating rates used in the simulations, we make two approximations.
+\textbf{CHANGE: Section was somewhat confusing in original form. Re-arranged order and re-worded}
+
+%AE: 2/23 Old version of text... keeping around for now:
+% For comparisons to other works, we present the cooling curve used in our simulations here.
+This cannot be done exactly, however, as primordial cooling and heating is computed cell-by-cell using the non-equillibrium chemistry solver in \textsc{Grackle}.
+These rates are not interpolated from the generated \textsc{CLOUDY} tables as is done for the metal line cooling rates.
+In addition, although these tables do include the effect of the UVB, they do not account for local variations in the ISRF from stellar radiation.
+However, we present the combined primordial and metal line cooling rates from the generated \textit{CLOUDY} tables in Figure~\ref{fig:cooling} at three characteristic densities for $Z = 0.01$Z$_{\odot}$.
+As discussed in Section~\ref{sec:methods}, we account for self-shielding against the UVB in both our simulations and the computed \textsc{CLOUDY} models shown in this figure.
+
+%AE: 2/23 Old version of text... keeping around for now:
+%To derive the diffuse cooling and heating rates used in the simulations, we make two approximations.
 First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal-line cooling and heating rates are used.
@@
 
-Figure ~\ref{fig:cooling} shows the combined primordial and metal line cooling and heating rates at three characteristic densities for $Z = 0.01 $Z$_{\odot}$, closer to the metallicities of our fiducial set of dwarf galaxy simulations (Emerick et al.\ in prep).
-The
-%mm solid lines give the absolute value of the net cooling rate, which more clearly 
-    Figure 
-indicates the regime at low temperatures where heating dominates over cooling. The curve as shown includes 
-%mm [it neglects local FUV]
-   only
-the $z = 0$ \citet{HM2012} metagalactic UV background.
+%AE: 2/23 Old version of text... keeping around for now:
+%Figure ~\ref{fig:cooling} shows the combined primordial and metal line cooling and heating rates at three characteristic densities for $Z = 0.01 $Z$_{\odot}$.
+The Figure indicates the regime at low temperatures where heating dominates over cooling.
+The curve as shown includes only the $z = 0$ \citet{HM2012} metagalactic UV background.
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{cooling_curve}
-\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}.
-The absolute value of the net cooling
-%mm
-   or heating
-rate is shown with solid lines.}
-\label{fig:cooling}
+\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
+\caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background.
+Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the un-corrected (i.e.
+optically thin) metal line cooling rates.
+The regimes where heating dominates are plotted with dashed lines for clarity.}
+\label{fig:cooling comparison}
 \end{figure}
 
-The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with self-shielding approximations.
-\citet{Hu2017} detail this inconsistency: adopting tabulated metal cooling rates computed under the assumption of an optically thin UV background overestimates the electron fraction in regimes where self-shielding is important, about $-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$, leading to an overestimation of the metal cooling rates.
-We demonstrate this effect in Figure~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate
-%mm |cooling - heating| 
-for our full model at $Z = 0.1$Z$_{\odot}$ as compared to a model using the optically thin metal line cooling rates at a range of densities.
+The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with a self-shielding approximations.
+\citet{Hu2017} details this inconsistency: metal cooling rates computed under the assumption of an optically thin UV background overestimate the electron fraction in regimes where self-shielding is important ($-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$).
+This results in an artificially enhanced metal line cooling rate in regions of self-shielding.
+This can be a significant effect, particularly at higher metallicities.
+We demonstrate this in Figure~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
 The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
-In low temperature regions, this can significantly shift the inferred equilibrium temperature.
-
-The cooling curve shown in Figure~\ref{fig:cooling} avoids this discrepancy using re-computed metal line cooling tables.
-We have made these tables publicly available in the main distribution of \texttt{Grackle}.
+In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
+Figure~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
+We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
+
 For densities where self-shielding is important, we computed \texttt{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
@@
 
+Finally, we note that the cooling and heating rates in our simulation depend will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
+The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which are not included in these diagrams.
+
 \begin{figure}
 \centering
-\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
-\caption{The absolute value of the net cooling or heating rate 
-%mm (|cooling - heating|)
- in two models that account for self-shielding of primordial gas against a metagalactic UV background.
-Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the un-corrected (i.e.
-optically thin) metal line cooling rates.
-The regimes where heating dominates are plotted with dashed lines for clarity.}
-\label{fig:cooling comparison}
+\includegraphics[width=0.95\linewidth]{cooling_curve}
+\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}.
+The absolute value of the net cooling or heating
+rate is shown with solid lines.}
+\label{fig:cooling}
 \end{figure}
 
+\setcounter{figure}{0}
 \section{Resolution Study}
 \label{appendix:resolution_study}
-
-%mm2
-    {\bf [This appendix should be cited in the main paper]}
-We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions for our high resolution simulations as compared to two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc.
-The physics in each of these simulations remains the same.
-However, our star formation algorithm is tied to resolution, since star formation proceeds in gas at densities where the Jeans mass becomes unresolved at the maximum resolution.
+\textbf{CHANGE: Updated plots with full runs. No significant change to text.}
+We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions between high resolution simulations, two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc.
+The physics in each of these simulations remains the same with the exception of our star formation threshold.
+Since star formation is set to occur at gas densities where the Jeans mass is unresolved at the maximum resolution, our star formation algorithm is tied to resolution.
 A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.
@@
 \includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
-\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), and 7.2~pc run (dash-dotted).
-We also include a 3.6~pc run with an initial SN driving rate increased by a factor of 2 (dashed).
-The line colors in the middle panel are the same as in Figure~\ref{fig:sfr_mass_evolution}, where the total disk mass is shown in black, cold gas mass in blue, H$_2$ mass in orange, and stellar mass in red.}
+\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted).
+The line colors in the left panel are for better clarity between the SFRs.}
 \label{fig:resolution_study}
@@
 Figure~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, it does not do so dramatically.
-We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
-%mm2, but point has not been confirmed. 
-Clearly, the initial SFR over the first 100~Myr is different in each simulation: it is larger in each of the lower resolution runs.
-This is because the initial SN driving is less resolved, leading to overcooling and an increase in the initial star formation rate.
-This is much less an issue for the SN from real star particles as the pre-SN feedback (winds and radiation) are capable of decreasing the local density enough to resolve the Sedov radius.
-To test this, we re-ran the 3.6~pc run with an increase in the initial SN driving rate by a factor of 2, which subsequently lowers the initial SFR.
+We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation and driven mostly by variation in the initial star formation rate of the galaxy.
+In each of the lower resolution runs, the SFR is larger within the first 100~Myr.
+This is because, at lower resolution, the initial driving SN are less resolved and less effective at preventing uniform collapse of the gas disk.
+The 3.6~pc run with a factor of 2 higher initial SN driving rate demonstrates that an increase in the effectiveness of the supernova at lower resolution brings the evolution much closer to that seen at our highest resolution run.
+We note that the self-consistent SN are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Figure~\ref{fig:SN histogram}.
+However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
+This is shown more clearly comparing the left and right panels of Figure~\ref{fig:phase_resolution}, the temperature-density phase diagrams for the 3.6 and 7.2 pc.
+There is clearly much less hot gas (T $> 10^6$~K) in our lowest resolution run.
 
@@
 However, each of the lower resolution runs produce less H$_2$ (about 40\% less) than our fiducial run.
-This is certainly an issue in interpreting the generality of our H$_2$ mass fractions in our fiducial run, and requires more tests to confirm.
+This is certainly an issue in interpreting the generality of our large H$_2$ mass fractions, and requires more tests to confirm.
 However, it is not unreasonable to expect that the H$_2$ production occurs most effectively at densities not captured in the 3.6~pc and 7.2~pc runs.
 This suggests that most of our H$_2$ production in the fiducial run occurs in gas with densities above 50~cm$^{-3}$.
-To clarify the gas phase differences between these simulations, we present the temperature-density phase diagrams for our 3.6~pc (left) and 7.2~pc (right) simulations in Figure~\ref{fig:phase_resolution} over the same time interval as that presented for our fiducial run in Figure~\ref{fig:phase}.
+As shown in Figure~\ref{fig:phase_resolution}, the maximum density is clearly lower in each of the two lower resolution runs,
 
@@
 
-Finally, each of the lower resolution runs retain a surprisingly similar fractions of their produced metals in their disks (black curves in right panel of Figure~\ref{fig:resolution}), but this is about a factor of 2 below what is found in the fiducial run (5\% vs.
-10\%).
-The amount that escapes the halo is significantly more, however.
+Finally, each of the lower resolution runs retain a similar fraction of their produced metals in their disks (black curves in right panel of Figure~\ref{fig:resolution_study}), but all of the lower resolution runs contain about a factor of two less than our fiducial simulation.
+The fraction leaving the virial radius of the galaxy is higher in the lower resolution runs, again within a factor of two of our fiducial resolution.
 This is an interesting difference, as the resolution decrease primarily affects the disk of the galaxy; little to none of the halo volume is refined to the highest resolution, and so should be unaffected by this change.
-\textbf{I'm a bit puzzled by this difference...
-}
+This suggests that this difference is a secondary effect, driven by changes to the particular SFH and disk structure between the various resolutions.
 

### 2018-03-12 main.tex
Update on Overleaf.

@@
 
-\title{Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution}
+\title{Simulating an Isolated Dwarf Galaxy with Individual Star Feedback and Chemistry}
+%\title{Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution}
 %Unstable Star Formation for the Lowest Mass Dwarf Galaxies
@@
 \affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-\author{Greg Bryan}
+\author{Greg L. Bryan}
 \affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
@@
 \begin{abstract}
-Galactic chemical evolution is driven through stellar feedback and its ability to drive metal mixing within the interstellar medium (ISM) and beyond the galaxy in outflows.
-However, we are far from a complete understanding of feedback along and galactic chemodynamics in general.
-In order to better understand this relationship, we have developed a new model for stellar feedback and galactic chemical evolution at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including stellar winds from massive and asymptotic giant branch stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+\textbf{CHANGE: Cleaned up a few sentences. better intro + last sentence. added wind caveat. removed large H2 content mention (should I put this last one back?).}
+%Galactic chemical evolution is driven through stellar feedback and its ability to drive metal mixing within the interstellar medium (ISM) and beyond the galaxy in outflows.
+However, we are far from a complete understanding of feedback and galactic chemodynamics in general.
+In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at high resolution ($\sim$ few pc) in global disk simulations using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
+For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including %stellar winds from massive and asymptotic giant branch stars,
+AGB winds, 
+photoelectric heating, Lyman-Werner dissociation radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+{\bf We additionally include stellar winds from massive stars, but reduce their velocity due to computational constraints.}
 %This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
@@
 
-\textbf{CHANGE: Cleaned up a few sentences. better intro + last sentence. removed large H2 content mention (should I put this last one back?).}
 %Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions.
@@
 There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
-These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and abundance evolution of individual species \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
+These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
 
@@
 Increasing physical resolution reduces reliance on sub-grid physics for mixing.
-However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations (SSPs) then lose validity  \citep[as studied in detail by][]{Revaz2016}.
+However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations (SSPs) lose validity  \citep[as studied in detail by][]{Revaz2016}.
 Below 10$^4$ M$_{\odot}$, SSPs do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
@@
 \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
-Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar wind feedback from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
-We also include core collapse and Type Ia supernova feedback, photoelectric heating, and Lyman-Werner dissociation.
+Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar winds from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
+We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar FUV radiation, and Lyman-Werner dissociation from stellar radiation.
 
@@
 Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
-We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (\ion{H}{1}M).
+We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
 We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content as decoupled from the rest of the gas.
@@
 Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining mass dominated by the WNM.
-While the CNM has a negligible volume fraction, the WNM, WIM, and \ion{H}{1}M each occupy roughly the same volume fraction.
-However, the frequent fluctuations in the \ion{H}{1}M volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy.
+While the CNM has a negligible volume fraction, the WNM, WIM, and HIM each occupy roughly the same volume fraction.
+However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy.
 Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
@@
 The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
-\textbf{AS: Should I note here that we compared cooling curves to Hu et. al. and did not find anything unusual?}
+{\bf We have compared our cooling curves to those used in \citep{Hu2017} (C.
+Hu, private communication) and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.}
 
@@
 The distribution has a very long tail out to and beyond 500~km~s$^{-1}$.
-The dominant launching mechanism in this simulation are SNe, generating a rapidly moving and volume-filling \ion{H}{1}M, consistent with the results in \citet{Hu2016,Hu2017}.
-However, as shown, the \ion{H}{1}M comprises very little of the outflow by mass.
-Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving \ion{H}{1}M.
-Some of this warm gas certainly originates from adiabatically and radiatively cooled \ion{H}{1}M, however.
+The dominant launching mechanism in this simulation are SNe, generating a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
+However, as shown, the HIM comprises very little of the outflow by mass.
+Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM.
+Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
 The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
@@
 \caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-The outflowing material is multiphase, broken into WNM, WIM, and \ion{H}{1}M.
+The outflowing material is multiphase, broken into WNM, WIM, and HIM.
 See Section~\ref{sec:phase} for definitions of these regimes.
@@
 Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
-Given the variations in Figure~\ref{fig:stellar_abundance}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
+Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
 This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
@@
 The CNM contains roughly 50-60\% of each species, with the CNM and WNM together accounting for most of the metals in the galaxy.
-The WIM contains only $\sim$ 10\% of each species, with the \ion{H}{1}M containing very little.
-This may be counterintuitive given that most metals are initially injected into the galaxy in either the WIM or \ion{H}{1}M phases.
+The WIM contains only $\sim$ 10\% of each species, with the HIM containing very little.
+This may be counterintuitive given that most metals are initially injected into the galaxy in either the WIM or HIM phases.
 However, the disk metals represent only a small fraction of the total metals produced.
@@
 \begin{enumerate}
-\item Multi-channel feedback is effective in this galaxy in regulating star formation to occur at a rate consistent with the KS relationship and extended Schmidt law in observed galaxies.
+\item Multi-channel feedback is effective in this galaxy in regulating star formation to occur at a rate consistent with the KS relationship and the extended Schmidt law in observed galaxies.
 See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}.
 
-\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, and
+\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, falling to $\eta \sim 10$ at R$_{\rm vir}$,  and
 metal mass loading factors near unity.
@@
 
-\section*{Acknowledgements:} A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. 
+\section*{Acknowledgements:} A.E.
+is funded by the NSF Graduate Research Fellowship DGE 16-44869.
+G.L.B.
+is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
 We gratefully recognize computational
@@
 
-\textit{Software:} \textsc{Enzo} \citep{Enzo2014}, \textsc{yt} \citep{yt}, \textsc{Grackle} \citep{GrackleMethod}, \textsc{Cloudy} \citep{Cloudy2013}
+\textit{Software:} \textsc{Enzo} \citep{Enzo2014}, \textsc{yt} \citep{yt}, \textsc{Grackle} \citep{GrackleMethod}, \textsc{Cloudy} \citep{Cloudy2013}, matplotlib, astropy
 %\bibliographystyle{apj}
@@
 \begin{enumerate}
-\item Hot Ionized Medium (\ion{H}{1}M): $T \geq 10^{5.5}$ K
+\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
 \item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $

### 2018-03-13 main.tex
Update on Overleaf.

@@
 Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
-There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
+There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
 These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
@@
 %mm2 I think there does need to be some introduction to this discussion:
-However, much of this work has been done with Lagrangian smoothed particle hydrodynamics (SPH) schemes, with a few recent exceptions  \citep{Few2012,Few2014,Vorobyov2015}.
+However, much of this work has been done with Lagrangian smoothed particle hydrodynamics (SPH) schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}.
 In its original form, SPH does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
@@
 We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
+
+%
+% KVJ: Possibly include a discussion on uncertainties in stellar yields
+%
 
@@
 
-Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy.
+Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}.
 We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
@@
 \begin{equation}
-\rho_{\rm gas} (R,z) = \frac{M_{\rm gas}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
+\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
 \end{equation}
-where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm gas}$ is approximately 70\% of the total gas mass.
-We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and a total gas mass of $M_{\rm T,gas} = 2.0\times 10^6$~M$_{\odot}$.
+where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass.
+We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$.
 We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$, $R_{\rm vir}~=~27.4$~kpc and r$_{\rm s} = 990$~pc.
 This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc.
-These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012}.
+These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}.
 We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in future work.
@@
 We note that this initial driving is somewhat ad hoc in that we do not include any other effects from the stellar population that would have caused these SNe.
+
+{\bf New (addressing KVJ's comment to clarify how to interpret / what is target comparison point for our galaxy model:} We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
+In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations.
+Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances.
+In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution.
+Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe.
+The subsequent metal enrichment from the stars in our simulation can be thought of as a change in abundances, or delta abundances, from arbitrary initial conditions.
+We discuss how to make proper comparison to observed stellar and gas abundance properties of dwarf galaxies in future work, where we investigate the abundance evolution of our simulations in more detail.
 
@@
 
-Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging.
+Constraining the gas scale height in ultra-faint dwarf galaxies observationally, to compare to our simulations, is challenging.
 For Leo P, located at 1.7~Mpc, \ion{H}{1} observations that are capable of detecting the diffuse \ion{H}{1} throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest \ion{H}{1} clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
@@
 
-The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors on order of 100--1000 \citep{Muratov2015}.
+The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}.
 However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
@@
 Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
-This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Angles-Alcazar2017,Muratov2017}.
+This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
 In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}.
 The parameter used to quantify metal outflow efficiencies varies among works.
-Here, we define the metal mass loading factor as
+Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
 \begin{equation} \label{eq:eta-metal}
@@
 \includegraphics[width=0.9\linewidth]{metal_fraction_evolution}
-\caption{Top: Metal mass loading factor (see Eq.~\ref{eq:eta-metal}) at radii of 0.1 ({\em black}), 0.2 ({\em purple}), 0.5 ({\em salmon pink}), and 1.0 $R_{\rm vir}$ ({\em yellow}) over time.
-Bottom: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
+\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Figure~\ref{fig:mass_outflow}.
+This is the ratio between the metal outflow rate and the metal production rate.
+{\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
 In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
@@
 
-\subsubsection{Metal Distribution within the ISM}
+\subsubsection{Differential Mixing of Elements Within the ISM}
 \textbf{CHANGE: Simplified plot to just log(N/O) to make this less confusing and easier to interpret. Cleaned up text accordingly.}
@@
 
+{\bf New (response to KVJ comment on comparability):} As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group UFD's.
+Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of z = 0 dwarf galaxies.
+However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies.
+We show that these properties are broadly consistent with observations.
+
 \subsubsection{Gas and Star Formation}
@@
 
-\item Formation of a significant amount of H$_2$ through gas phase reactions with H$^-$.
+\item (\textbf{Possibly remove depending on follow up}) Formation of a significant amount of H$_2$ through gas phase reactions with H$^-$.
 This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy.
@@
 See Figure~\ref{fig:ISM_evolution}.
+
+\item Finally, we used O and N as examples to briefly demonstrate that there are discernible differences in how individual metal species are distributed within the ISM of our galaxy.
+These variations could be tied to differences in yield sources among elements (for example, AGB winds vs.
+SNe), as suggested by \cite{KrumholzTing2018}.
+This will be explored in more detail in future work (Emerick et.
+al.
+\textit{in prep.}).
 \end{enumerate}
 
-Finally, we used O and N as examples to briefly demonstrate that there are discernible differences in how individual metal species are distributed within the ISM of our galaxy.
-In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and how individual metals move into halos.
-This will allow us to examine
-the role that each source of feedback plays in driving dwarf galaxy chemodynamics.
+%In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and how individual metals move into halos.
+This will allow us to examine the role that each source of feedback plays in driving dwarf galaxy chemodynamics.
 
@@
 resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute.
-Analysis in this work
-made significant use of the publicly available \textsc{yt} (http://ytproject.org)
-toolkit. \textsc{Enzo}, \textsc{Grackle}, and \textsc{yt} are the products of a collaborative effort of many independent scientists from numerous institutions around
-the world. Their commitment to open science has helped make
-this work possible.
+This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{matplotlib}, \textsc{hdf5}, \textsc{h5py}, \textsc{astropy}, \textsc{Cloudy} and \textsc{deepdish}.
+These are the products products of a collaborative effort of many independent developers from numerous institutions around the world.
+Their commitment to open science has helped make this work possible.
 We would also like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
@@
 
-\textit{Software:} \textsc{Enzo} \citep{Enzo2014}, \textsc{yt} \citep{yt}, \textsc{Grackle} \citep{GrackleMethod}, \textsc{Cloudy} \citep{Cloudy2013}, matplotlib, astropy
+%\textit{Software:} \textsc{Enzo} \citep{Enzo2014}, \textsc{yt} \citep{yt}, \textsc{Grackle} \citep{GrackleMethod}, \textsc{Cloudy} \citep{Cloudy2013}
 %\bibliographystyle{apj}
@@
 \label{appendix:resolution_study}
+
 \textbf{CHANGE: Updated plots with full runs. No significant change to text.}

### 2018-03-13 main.tex
abstract revision

--- 2018-03-12 main.tex
@@
 %mm2 substantive changes marked with this comment tag, minor changes and wordsmithing done silently.  12-15 Feb
+%mm3 since Greg has already read this, I have removed commentary as I go.  substantive changes now marked with %mm3 13 Mar 18
 \documentclass[twocolumn]{aastex61}
@@
 
-\title{Simulating an Isolated Dwarf Galaxy with Individual Star Feedback and Chemistry}
+%mm3 [Proposed new title]
+\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
+%mm3 \title{Simulating an Isolated Dwarf Galaxy with Individual Star Feedback and Chemistry}
 %\title{Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution}
@@
 \begin{abstract}
-\textbf{CHANGE: Cleaned up a few sentences. better intro + last sentence. added wind caveat. removed large H2 content mention (should I put this last one back?).}
+%\textbf{CHANGE: Cleaned up a few sentences. better intro + last sentence. added wind caveat. removed large H2 content mention (should I put this last one back?).}
 %Galactic chemical evolution is driven through stellar feedback and its ability to drive metal mixing within the interstellar medium (ISM) and beyond the galaxy in outflows.
 However, we are far from a complete understanding of feedback and galactic chemodynamics in general.
-In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at high resolution ($\sim$ few pc) in global disk simulations using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
+In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at 
+%mm3 high resolution ($\sim$ few pc) 
+   grid resolutions of only a few parsecs 
+in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
 For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including %stellar winds from massive and asymptotic giant branch stars,
-AGB winds, 
-photoelectric heating, Lyman-Werner dissociation radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
-{\bf We additionally include stellar winds from massive stars, but reduce their velocity due to computational constraints.}
+%mm3 AGB
+    asymptotic giant branch 
+winds, 
+photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. 
+%mm3 [moved below] {\bf We additionally include stellar winds from massive stars, but reduce their velocity due to computational constraints.}
 %This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
-We furthermore follow the star-by-star stellar yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
+We furthermore follow the star-by-star 
+%mm3 stellar 
+      chemical
+yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
+%mm3 
+    We include the yields ejected in massive stellar winds, but neglect the winds' energetic contribution due to computational 
+    constraints.
  We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
@@
 Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations.
-Finally, we demonstrate that these simulations yield valuable information on the differences with which individual metal species mix and evolve within the ISM.
+Finally, we demonstrate that these simulations yield valuable information on the
+%mm3 differences with which individual metal species mix and evolve 
+    variation in mixing behavior of individual metal species
+within the 
+%mm3 ISM.
+     multi-phase interstellar medium.
 

### 2018-03-14 main.tex
changes through 2.5.1

@@
 This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possibly models that are not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
-While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution or additional viscosity to reduce.
+While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution
+%mm3 or additional viscosity [I'm not sure I understand this.
+Adding explicit viscosity will increase mixing, although it at least places it on a physical basis, rather than relying on error terms with unphysical scale dependences.]
+to reduce.
 Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
@@
 Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
-the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
+the ISM with different energies and on different timescales; the observational effect of this remains poorly understood, however.
 The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
@@
 
-We refine the mesh whenever the Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criteria is met or until the region reaches the maximum resolution (1.8~pc).
-At maximum resolution, the Jeans length can become under resolved, leading to artificial numerical fragmentation.
+We refine the mesh whenever the Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
+At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation.
 \citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.
@@
 We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
-However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$) with the broken power law scalings from \citet{Remy-Ruyer2014}.
-For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
+However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}.
+For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
 % Since we assume a dust abundance that depends only on metallicity, we do not track dust destruction or creation, which may play an important role regulating detailed ISM properties.
@@
 These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
-{\bf {\it (addressing MM's comment below (I was unable to find a ref.
-where this was accounted for)}: Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.
-}
-
-%mm2 
-   {\bf [MM: I'm a bit confused here: how does the ISRF interact with the cooling?  Shouldn't that move you around in the Cloudy tables, possibly quite substantially?]}
+%mm3 {\bf {\it (addressing MM's comment below (I was unable to find a ref. where this was accounted for)}: 
+Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates. 
+%}
+%%mm2 
+%   {\bf [MM: I'm a bit confused here: how does the ISRF interact with the cooling?  Shouldn't that move you around in the Cloudy tables, possibly quite substantially?]}
 
@@
 \label{sec:star formation}
-In order to resolve individual star formation events on galaxy scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
+In order to resolve individual star formation events on 
+%mm3 galaxy 
+    galacitc
+scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
 Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
@@
 
-We make the common ansatz that star formation occurs by converting some fraction of gas into stars in a free fall time ($\tau_{\rm ff}$) as characterized by a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
-At high resolution, one's choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
+We make the common ansatz that star formation occurs by converting 
+%mm3 some fraction of 
+gas into stars in a free fall time $\tau_{\rm ff}$ 
+%mm3 characterized by 
+   with 
+a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, 
+the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
 %but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
@@
 \label{sec:yields}
-For the first time in galaxy scale simulations, we track galactic chemodynamical evolution using stellar yields as ejected from star particles that represent individual stars.
-We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}.
+For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars.
+We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z
+%mm3 [confirm]
+       / Z_{\odot} 
+=$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}.
 This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$.
-We complement these tables with tables from Slemer et.
-al.
-(in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014} to track stellar winds for stars more massive than 25 M$_{\odot}$.
+We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$.
 We ignore SN yields from these stars (see next paragraph).
@@
 
-Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars do not undergo AGB wind phases and end their lives as core collapse SNe.
-Where this transition occurs is uncertain, but is commonly taken to be around 8--10~M$_{\odot}$.
-This is a free parameter in our model, but we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value.
+Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe.
+Where this transition occurs is uncertain, but is commonly taken to be
+%mm3
+     at a mass $M_{\rm trans} \sim 
+8$--10~M$_{\odot}$.
+This is a free parameter in our model; we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value.
 In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
 Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics).
-Varying $M_{\rm thresh}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
-\citet{Cote2017} explores how the choice of $M_{\rm thresh}$ affects galaxy abundances in a one-zone model.
+Varying
+%mm3 $M_{\rm thresh}$ 
+           $M_{\rm trans}$
+changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
+\citet{Cote2017} explores how the choice of
+%mm3 $M_{\rm thresh}$
+           $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
 We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
@@
 We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
-We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population.
+We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population,
+%mm3
+     substantially limiting the number of Type Ia SNe occurring during the initial gigayear in 
+     our models.
 

### 2018-03-14 main.tex

@@
 %mm2 I think there does need to be some introduction to this discussion:
-However, much of this work has been done with Lagrangian smoothed particle hydrodynamics (SPH) schemes, with a few recent exceptions  \citep{Few2012,Few2014,Vorobyov2015}.
+
+However, much of this work has been done with Lagrangian smoothed particle hydrodynamics (SPH) schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}.
 In its original form, SPH does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
@@
 Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
-the ISM with different energies and on different timescales; the observational effect of this remains poorly understood, however.
+the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
 The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.

### 2018-03-15 main.tex
updated ArXiv references to include journal and status where available.

@@
 We inject the feedback energy in a spherical region with a three-cell radius centered on the emitting star particle, assuming full thermalization of the wind kinetic energy.
-The total injected energy in timestep $\Delta t$ is therefore $E_w = \dot{M}\Delta t \times v^2_w + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
+The total injected energy in timestep $\Delta t$ is therefore $E_w = \dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
 We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells.
@@
 AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$.
-For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars.
+For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars as well.
 
@@
 \label{sec: core collapse}
-Stars between  $M_{\rm thresh} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
+Stars between  $
+%mm3 M_{\rm thresh}
+           M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
 Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}).
 We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
-We continue to track any remaining stellar mass after the SNe as a massive remnant tracer particle.
+%mm3 [How do you antialias the energy?  Something like Simpson's cloud-in-cell method, or something else?]
+We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle.
 In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.
@@
 We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as WD particles, marking a subset as Type Ia SN progenitors.
-This is the most self-consistent model for Type Ia SNe in galaxy scale simulations.
+This is the most self-consistent model for Type Ia SNe in galaxy-scale simulations.
 We note however that for the low SFRs in our isolated dwarf galaxy simulation, the first Type Ia SN only appears after a few hundred megayears of simulation time.
@@
 However, the importance of multiple scattering is still unclear.
-Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017}.
+Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017,Wibking2018}.
 Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.

### 2018-03-15 main.tex
revisions to section 3

@@
 
-However, much of this work has been done with Lagrangian smoothed particle hydrodynamics (SPH) schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}.
-In its original form, SPH does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
+However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}.
+In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
 This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possibly models that are not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
@@
 Increasing physical resolution reduces reliance on sub-grid physics for mixing.
-However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations (SSPs) lose validity  \citep[as studied in detail by][]{Revaz2016}.
-Below 10$^4$ M$_{\odot}$, SSPs do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
+However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}.
+Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
 This is acutely problematic at star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
@@
 The most straightforward
-solution is to remove the SSP formalism entirely and simply track stars as individual particles. %which we do here
+solution is to remove the single stellar population formalism entirely and simply track stars as individual particles. %which we do here
 
@@
 Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar winds from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
-We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar FUV radiation, and Lyman-Werner dissociation from stellar radiation.
+We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar far ultra-violet (FUV) radiation, and Lyman-Werner dissociation from stellar radiation.
 
 Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime.
-This includes yields from massive and AGB stellar winds, and SNe.
+This includes yields from massive and AGB stellar winds, and supernovae (SNe).
 In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
@@
 \label{sec:methods}
-We produce high-resolution, galaxy-scale simulations tracking stars not as SSPs, but as individual stars sampled from an assumed IMF.
+We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
 This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
@@
 \label{sec:diffusive heating}
-We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles.
-The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the SEDs for each gridded star.
+We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the FUV (6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles.
+The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the spectral energy distributions for each gridded star.
 Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
@@
 This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; none of which are followed directly in these simulations.
-Instead, we use a log-linear fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
-%This is a compromise between adoption a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
+Instead, we use a
+%mm3 log-linear 
+    power-law 
+fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
+%This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
 
@@
 \label{sec:LW}
-In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rates.
-We compute the stellar LW flux again from the OSTAR2002 grid by integrating the SEDs over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}).
+In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rate.
+We compute the stellar Lyman-Werner flux again from the OSTAR2002 grid by integrating the spectral energy distributions over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}).
 Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
@@
 
-Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
-This additionally prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
-These SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
+Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM. This 
+%mm3 additionally 
+prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation. 
+%mm3 These 
+    During this period, 
+SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
 We stop the artificial driving 25~Myr after the first star particle forms.
@@
 
-{\bf New (addressing KVJ's comment to clarify how to interpret / what is target comparison point for our galaxy model:} We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
+%mm3 {\bf New (addressing KVJ's comment to clarify how to interpret / what is target comparison point for our galaxy model:} 
+We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
 In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations.
@@
 Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe.
-The subsequent metal enrichment from the stars in our simulation can be thought of as a change in abundances, or delta abundances, from arbitrary initial conditions.
-We discuss how to make proper comparison to observed stellar and gas abundance properties of dwarf galaxies in future work, where we investigate the abundance evolution of our simulations in more detail.
+The subsequent metal enrichment from the stars in our simulation can be thought of as
+%mm3
+    tracking 
+a change in abundances
+%mm3 , or delta abundances, 
+from arbitrary initial conditions. We 
+%mm3
+   will 
+discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we investigate the abundance evolution of our simulations in more detail.
 

### 2018-03-16 main.tex
revisions through end of section 4, and added a reference

@@
    will 
-discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we investigate the abundance evolution of our simulations in more detail.
+discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.
 
@@
 \label{sec:results}
-We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first star forms.
-Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle forms, which is 43~Myr after the actual initialization of the simulation.
-The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy.
+We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first
+%mm3
+   new
+star forms. Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual 
+%mm3 initialization of the simulation
+   beginning of the simulation run. 
+The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical heigh $|z| < 200$~pc relative to the center of the galaxy.
 ISM properties are calculated considering only the gas contained within the disk of the galaxy.
-We include a resolution study in Appendix \ref{appendix:resolution_study},
+We include a resolution study in Appendix \ref{appendix:resolution_study}.
 
@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\%, of the total mass in the galaxy's disk.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\%, of the total
+%mm3 [confirm]
+    gas 
+mass in the galaxy's disk.
 The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\%; at this point, it is about equal with the \ion{H}{1} gas.
-This is because the total amount of mass in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained.
+This is because the total amount of
+%mm3 mass 
+    gas
+in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained.
 Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback.
@@
 The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
-After this point, the molecular component dominates through the end of the simulation.
+After this point, the molecular component
+%mm3 dominates
+   becomes equally or even somewhat more important 
+through the end of the simulation.
 Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining mass dominated by the WNM.
@@
 
-These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}.
+These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
 They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (ionized and neutral), with cold gas having $\sim$ 10\% of the mass, and occupying negligible volume, and hot gas occupying $\sim$ 10\% of the volume, but having negligible mass.
@@
 These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
-We note, however, that our results are closer to the \citep{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly have much smaller mass loading factors at 0.25 $R_{\rm vir}$.
+We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly have much smaller mass loading factors at 0.25 $R_{\rm vir}$.
 
@@
 The distribution has a very long tail out to and beyond 500~km~s$^{-1}$.
-The dominant launching mechanism in this simulation are SNe, generating a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
+The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
 However, as shown, the HIM comprises very little of the outflow by mass.
@@
 See Section~\ref{sec:phase} for definitions of these regimes.
-We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$K.
+We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K.
 There is little to no outflowing mass in the CNM or molecular phases.}
@@
 \begin{equation} \label{eq:eta-metal}
-\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times \frac{M_{\rm metal}}{M_{*}}},
+\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
 \end{equation}
@@
 \subsubsection{Differential Mixing of Elements Within the ISM}
-\textbf{CHANGE: Simplified plot to just log(N/O) to make this less confusing and easier to interpret. Cleaned up text accordingly.}
+%mm3 \textbf{CHANGE: Simplified plot to just log(N/O) to make this less confusing and easier to interpret. Cleaned up text accordingly.}
 It is important to understand how metals from each source of stellar yields enrich the ISM.
@@
 This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed.
-Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}.
+Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Avillez2002,Tassis2008,YangKrumholz2012}.
 It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
-It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few \ion{H}{1}I regions for a detailed examination.
+It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.
 
@@
 We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
-The left two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy.
-These serve to guide the eye in the right panel, clearly indicating regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
 The left panel gives the abundance ratio of N to O throughout the ISM.
+The
+%mm3 left 
+   right 
+two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy. These 
+%mm3 serve to guide the eye in the right panel, clearly indicating 
+    show
+regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
 
@@
 
-The number density and temperature panels clearly show a multi-phase ISM: the CNM consists of cold filaments that connect dense clumps of molecular gas which are readily visible in both diagrams.
-Distinguishing the WNM and WIM is difficult, but the lower density regions between the cold filaments is dominated by these phases.
-Gas from a recent SN explosion is clearly visible as the hot (T~$\gtrsim 10^{6}$~K) and diffuse region in the top left corner.
+The 
+%mm3 [redundant with end of previous para?] number density and temperature panels clearly show a multi-phase ISM: the 
+CNM consists of cold filaments that connect dense clumps of molecular gas that are readily visible in both diagrams.
+Distinguishing the WNM and WIM is difficult, but the lower density regions between the cold filaments are dominated by these phases.
+Gas from a recent SN explosion is clearly visible as the hot (T~$\gtrsim 10^{6}$~K), diffuse region in the top left corner.
 As shown in the left panel, log(N/O) varies significantly over this section of the ISM with notable differences across the various phases and ISM structures.
@@
 There are three regions in particular that are overabundant in N (green color).
-These are sites of recent AGB winds that have yet to mix with the rest of the ISM.
+%mm3 [moved to next para] These are sites of recent AGB winds that have yet to mix with the rest of the ISM.
 
@@
 Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
+%mm3
+    The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.  
 This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.

### 2018-03-16 main.tex
most of 6 finished

@@
 
-{\bf New (response to KVJ comment on comparability):} As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group UFD's.
-Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of z = 0 dwarf galaxies.
+%mm3 {\bf New (response to KVJ comment on comparability):} 
+As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs.
+Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of $z = 0$ dwarf galaxies.
 However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies.
@@
 However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) relation and extended Schmidt law (ESL)  for low mass galaxies.
-In both diagrams, our simulations are given by the colored points, sampled every 1 Myr throughout the entire simulation.
+In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
+In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.
 
 Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
-sWe have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}.
+We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}.
 We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the area of the disk within the radius of the outermost star formed within the previous 10 Myr.
@@
 \includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution}
-\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
+\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
 See text for details of the calculation.
@@
 It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
-This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the KS law can be reproduced by gravitation acting on an isothermal disk.
+This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
 %AE, which was argued to demonstrate that this represents the basic physics at work.
@@
 
-The molecular gas content of low mass dwarf galaxies is generally assumed
+The molecular gas content of low-mass dwarf galaxies is generally assumed
 to be small, but is not well constrained by either theory or observations.
@@
 As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.17--0.20, within this range, but significantly exceeding the few percent often found in models.
-Ignoring the H$_2$ component of our galaxies would lead to an average shift of 0.24 dex to the right in the KS relationship, and 0.24 dex right and down in the ESL.
-This does not result in a significant disagreement with the observed relationships, but would constitute a quantitative change to the observed fits if our $f_{\rm H_2}$ is robust for observed low mass, low metallicity dwarf galaxies.
+Ignoring the H$_2$ component of our galaxies would lead to an average shift of 0.24 dex to the right in the Kennicutt-Schmidt law, and 0.24 dex right and down in the extended Schmidt law.
+This does not result in a significant disagreement with the observed relationships, but would constitute a quantitative change to the observed fits if our $f_{\rm H_2}$ is robust for observed low-mass, low-metallicity dwarf galaxies.
 
@@
 In a test simulation ignoring all H$^{-}$ reactions, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.
+%mm3 
+    {\bf [Is there any treatment in the model of the visible light radiation field, which is sufficient to destroy H$^-$?]}
 
@@
 It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium.
-While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of a $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
+While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
 We find 13.7\% of all metals lie within 1 kpc of the center of our galaxy, 26.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 38.6\% outside $R_{\rm vir}$.
@@
 
-\subsubsection{Full Stellar Wind Model}
+%mm3 \subsubsection{Full Stellar Wind Model}
+    \subsubsection{Massive Stellar Wind Energy}
 \label{sec:stellar winds discussion}
-Our stellar wind model significantly reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$.
-Although our model is capable of generating realistic stellar winds with temperature profiles and radial evolution comparable to those expected from analytic calculations \citep{Weaver1977}, the hot, fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
-When considered in isolation, stellar winds are an important source of pre-SN feedback and do dramatically influence the dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
-However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}.
+Our 
+%mm3
+   massive
+stellar wind model 
+%mm3 significantly 
+     drastically 
+reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$. Although our 
+%mm3 model is 
+   algorithm is entirely 
+capable of generating realistic stellar winds with
+%mm3 temperature profiles and radial evolution comparable to those expected from analytic calculations \citep{Weaver1977}, the hot, [the winds are not hot, only the post-shock gas; Weaver et al.
+calculated the bubble structure resulting from winds moving at observed speeds]
+     velocities comparable to those observed, such
+fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
+When considered in isolation, stellar winds are an important source of pre-SN feedback and
+%mm3 do 
+   can
+dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
+However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014},
+%mm3 [insert text]
+    unless densities near the ionizing source are high enough to trap the  \ion{H}{2} region in the source cell.
+In that case, they can clear out a cavity to allow initial establishment of the \ion{H}{2} region.
+
+% [end of insertion]
 They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
-Although they likely have minimal dynamical importance at resolutions where peak densities are not anyway high enough to trap ionization fronts, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.
+Although they likely have minimal dynamical importance at resolutions where peak densities are not anyway high enough to trap ionization fronts, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting closer examination in future work.
 
@@
 
-We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested.
-Mechanically, including cosmic ray feedback in our model is trivial.
-However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to a later work.
+We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested. Mechanically, including
+%mm3 
+   this relatively simple treatment of 
+cosmic ray feedback in our model is trivial.
+However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to later work.
 
@@
 This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as SNe.
-This effect is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g.
-STARBURST99), but could be significant.
+This effect could be significant, but is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g.
+STARBURST99).
 For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse SNe occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
@@
 We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
-For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, and Lyman-Werner radiation using individual star particles.
-This, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
+For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail,
+%mm3 accounting for stellar winds, 
+     using individual star particles to model
+core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, Lyman-Werner radiation
+%mm3 using individual star particles
+    and pollution from AGB and massive stellar winds. This
+%mm3
+    treatment of feedback, 
+coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
 In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
@@
 \begin{enumerate}
-\item Multi-channel feedback is effective in this galaxy in regulating star formation to occur at a rate consistent with the KS relationship and the extended Schmidt law in observed galaxies.
+\item Multi-channel feedback is effective in this galaxy in regulating star formation to occur at a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
 See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}.
@@
 
-\item A thin, yet resolved, gas scale height ($\sim 50$~pc) beyond our stellar radius, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
+\item 
+%mm3 A thin, yet resolved, gas scale height ($\sim 50$~pc)
+   The gas scale height is thin ($\sim 50$~pc), yet resolved, 
+beyond our stellar radius, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
 This is comparable to the resolution limit of the diffuse \ion{H}{1} in observed, gaseous ultrafaint dwarfs.
-See Figure~\ref{fig:scale_height}.
-
-\item The ISRF of our galaxy is highly varying in time, by orders of magnitude, though it is relatively uniform in space at any given time.
-It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time averaged radial profile.
-See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.
-
-\item (\textbf{Possibly remove depending on follow up}) Formation of a significant amount of H$_2$ through gas phase reactions with H$^-$.
+(See Figure~\ref{fig:scale_height}).
+
+\item The ISRF of our galaxy varies strongly in time, by orders of magnitude, though
+%mm3 it is relatively uniform in space at any given time. [this is contradicted by Figure \ref{fig:ISRF_2D}]
+    it has a relatively uniform radial profile averaged over tens of megayears.
+It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
+(See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
+
+\item 
+%mm3 (\textbf{Possibly remove depending on follow up}) Formation of a significant amount of H$_2$ 
+     A significant amount of H$_2$ forms
+through gas phase reactions with H$^-$.
 This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy.

### 2018-03-17 main.tex
completed revisions to main text and acknowledgments

@@
 This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies.
-See Figure~\ref{fig:ISM_evolution}.
-
-\item Finally, we used O and N as examples to briefly demonstrate that there are discernible differences in how individual metal species are distributed within the ISM of our galaxy.
-These variations could be tied to differences in yield sources among elements (for example, AGB winds vs.
-SNe), as suggested by \cite{KrumholzTing2018}.
-This will be explored in more detail in future work (Emerick et.
-al.
-\textit{in prep.}).
+(See Figure~\ref{fig:ISM_evolution}.)
+
+\item Finally, we used O and N as examples to briefly demonstrate that there are 
+%mm3 discernible 
+    marked
+differences in how individual metal species are distributed within the ISM of our galaxy. These variations could be tied to differences in 
+%mm3 yield sources among elements
+    elemental yields among different sources 
+(for example, AGB winds vs. SNe), as suggested by \cite{KrumholzTing2018}. This will be explored in more detail in future work.
+%mm3 (Emerick et. al. \textit{in prep.}). [only cite after submission]
 \end{enumerate}
@@
 
-\section*{Acknowledgements:} A.E.
-is funded by the NSF Graduate Research Fellowship DGE 16-44869.
-G.L.B.
-is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
-We gratefully recognize computational
-resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute.
-This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{matplotlib}, \textsc{hdf5}, \textsc{h5py}, \textsc{astropy}, \textsc{Cloudy} and \textsc{deepdish}.
-These are the products products of a collaborative effort of many independent developers from numerous institutions around the world.
-Their commitment to open science has helped make this work possible.
-We would also like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
-Cote, S.
+\section*{Acknowledgments:} 
+%mm3 [moved personal acknowledgments to the front}
+We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
+C\^ot\'e, S.
 Glover, K.
@@
 Wise.
+A.E.
+is funded by the NSF Graduate Research Fellowship DGE 16-44869.
+G.L.B.
+is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
+M.-M.M.L.
+was funded by NASA
+%mm3 [have to scare up the number still]
+We gratefully recognize computational
+resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute.
+This work made significant use of many open source software packages, including
+%mm3 [updated capitalization to that used in relevant websites]
+\textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.
+These are products of collaborative effort by many independent developers from numerous institutions around the world.
+Their commitment to open science has helped make this work possible.
 

### 2018-03-17 main.tex
final revisions

@@
 We ignore \ion{He}{2} photoionization from the UV background entirely.
-Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from Cloudy (see Section 4.1.1 of \citet{Hu2017}).
-As mentioned previously, we have re-computed metal line cooling tables using \texttt{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
+Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
+As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
 This is described in more detail in Appendix ~\ref{appendix:cooling}.
@@
 
-To aid in comparison to other works, we define our ISM phases here, as adopted and modified from \citet{Draine2011} Table 1.3 and used consistently throughout this analysis.
+To aid in comparison to other works, we define our ISM phases here, as adopted and modified from \citet{Draine2011}, Table 1.3, and used consistently throughout this analysis.
 By construction, these phases are mutually exclusive.
-In the below, $f_{\rm H_2}$ is the molecular hydrogen fraction of the total gas mass.
+We take $f_{\rm H_2}$ to be the molecular hydrogen fraction of the total gas mass.
 
@@
 \label{appendix:radiation}
-We detail the radiation properties of our model stars as a function of stellar mass and metallicity.
-The stellar radiation properties are determined from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
+We 
+%mm3 detail 
+  determine 
+the radiation properties of our model stars as a function of stellar mass and metallicity
+%mm3 . The stellar radiation properties are determined 
+from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
 In Figure~\ref{fig:stellar radiation properties} we plot these properties.
@@
 This requires two factors for each radiation type, one for low mass and one for high mass stars.
-We use the following multiplicative factors to adjust the black body spectrum for \ion{H}{1} and \ion{He}{1} radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
-We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
+We use the following multiplicative factors to adjust the black body spectrum for \ion{H}{1} and \ion{He}{1}
+%mm3
+   ionizing 
+radiation respectively: [0.1, 3.2] and [0.0001, 4.0]. We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
 
@@
 A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section.
-We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \texttt{http://www.pa.uky.edu/~verner/photo.html}} The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision.
+We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from
+%mm3 [changed to \url because \texttt translates the tilde into a space]
+\url{http://www.pa.uky.edu/~verner/photo.html}} 
+The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision.
 Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.
@@
 
-The left panel of Figure ~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in the simulations presented in this work.
+The left panel of Figure~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our simulations.
 As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
@@
 We do not expect that resolving these SNe will dramatically alter our results.
-However, we note that using our feedback model at resolutions much less than a few pc will require adopting a different injection mechanism.
+However, we note that using our feedback model at resolutions much less than a few parsecs will require adopting a different injection mechanism.
 
@@
 The vertical lines show one and 4.5 cell widths.
-This shows that a fraction of these SNe are certainly under resolved, with R$_{\rm PDS}$ less than a single cell size, but the majority are well resolved.}
+This shows that a fraction of these SNe are certainly underresolved, with R$_{\rm PDS}$ less than a single cell size,
+%mm3
+   and somewhat more don't satisfy the 4.5 cell criterion, 
+but the majority are well resolved.}
 \label{fig:SN histogram}
@@
 \label{appendix:cooling}
-\textbf{CHANGE: Section was somewhat confusing in original form. Re-arranged order and re-worded}
+%mm3 \textbf{CHANGE: Section was somewhat confusing in original form. Re-arranged order and re-worded}
 
@@
 
-For densities where self-shielding is important, we computed \texttt{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
+For densities where self-shielding is important, we computed \textsc{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
 In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud.
@@
 In computing these tables we had to include the cosmic ray ionization that dominates in optically thick clouds.
-Without this effect, \texttt{Cloudy} becomes unstable in entirely neutral regions.
+Without this effect, \textsc{Cloudy} becomes unstable in entirely neutral regions.
 We adopted a cosmic ray ionization rate of 10\% the Milky Way value, though we note that varying this from 1\% to 100\% the Milky Way value did not have an effect on the extracted metal line cooling rates.
 
-Finally, we note that the cooling and heating rates in our simulation depend will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
-The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which are not included in these diagrams.
+Finally, we note that the cooling and heating rates in our simulation 
+%mm3 depend 
+will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
+The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which is not included in these diagrams.
 
@@
 
-\textbf{CHANGE: Updated plots with full runs. No significant change to text.}
-We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions between high resolution simulations, two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc.
+%mm3 \textbf{CHANGE: Updated plots with full runs. No significant change to text.}
+We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions between our fiducial high-resolution simulation, two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc.
 The physics in each of these simulations remains the same with the exception of our star formation threshold.
@@
 This is because, at lower resolution, the initial driving SN are less resolved and less effective at preventing uniform collapse of the gas disk.
-The 3.6~pc run with a factor of 2 higher initial SN driving rate demonstrates that an increase in the effectiveness of the supernova at lower resolution brings the evolution much closer to that seen at our highest resolution run.
-We note that the self-consistent SN are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Figure~\ref{fig:SN histogram}.
+The 3.6~pc run with a factor of two higher initial SN driving rate demonstrates that an increase in the effectiveness of the supernova at lower resolution brings the evolution much closer to that seen at our highest resolution run.
+We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Figure~\ref{fig:SN histogram}.
 However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
@@
 This suggests that most of our H$_2$ production in the fiducial run occurs in gas with densities above 50~cm$^{-3}$.
-As shown in Figure~\ref{fig:phase_resolution}, the maximum density is clearly lower in each of the two lower resolution runs,
+As shown in Figure~\ref{fig:phase_resolution}, the maximum density is clearly lower in each of the two lower resolution runs.
 

### 2018-03-18 main.tex
Update on Overleaf.

@@
 
-%mm3 [Proposed new title]
 \title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
-%mm3 \title{Simulating an Isolated Dwarf Galaxy with Individual Star Feedback and Chemistry}
-%\title{Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution}
-%Unstable Star Formation for the Lowest Mass Dwarf Galaxies
+
 \author{Andrew Emerick}
@@
 However, we are far from a complete understanding of feedback and galactic chemodynamics in general.
-In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at 
-%mm3 high resolution ($\sim$ few pc) 
-   grid resolutions of only a few parsecs 
-in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including %stellar winds from massive and asymptotic giant branch stars,
-%mm3 AGB
-    asymptotic giant branch 
-winds, 
-photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. 
-%mm3 [moved below] {\bf We additionally include stellar winds from massive stars, but reduce their velocity due to computational constraints.}
-%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
-We furthermore follow the star-by-star 
-%mm3 stellar 
-      chemical
-yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
-%mm3 
-    We include the yields ejected in massive stellar winds, but neglect the winds' energetic contribution due to computational 
-    constraints.
+In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
+For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
+We include the yields ejected in massive stellar winds, but neglect the winds' energetic contribution due to computational constraints.
 We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
@@
 Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations.
-Finally, we demonstrate that these simulations yield valuable information on the
-%mm3 differences with which individual metal species mix and evolve 
-    variation in mixing behavior of individual metal species
-within the 
-%mm3 ISM.
-     multi-phase interstellar medium.
-
-%Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions.
-
-% mm: conclusion of this discussion should perhaps be mentioned
-%% AE (reply): reworded slightly but still have no detailed mention of this.
+Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
 \end{abstract}
@@
 This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possibly models that are not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
-While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution
-%mm3 or additional viscosity [I'm not sure I understand this.
-Adding explicit viscosity will increase mixing, although it at least places it on a physical basis, rather than relying on error terms with unphysical scale dependences.]
-to reduce.
+While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution to reduce.
 Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
@@
 Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
-The most straightforward
-solution is to remove the single stellar population formalism entirely and simply track stars as individual particles. %which we do here
+The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
 
@@
 These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
-%mm3 {\bf {\it (addressing MM's comment below (I was unable to find a ref. where this was accounted for)}: 
 Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.
-%}
-%%mm2 
-%   {\bf [MM: I'm a bit confused here: how does the ISRF interact with the cooling?  Shouldn't that move you around in the Cloudy tables, possibly quite substantially?]}
 
@@
 \label{sec:star formation}
-In order to resolve individual star formation events on 
-%mm3 galaxy 
-    galacitc
-scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
+In order to resolve individual star formation events on galacitc scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
 Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
@@
 
-We make the common ansatz that star formation occurs by converting 
-%mm3 some fraction of 
-gas into stars in a free fall time $\tau_{\rm ff}$ 
-%mm3 characterized by 
-   with 
-a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, 
-the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
-%but we find that $\epsilon_{\rm f}$ may impact star formation in the lowest mass halos, which are unusually sensitive to stellar ionization feedback (see Emerick et. al. in prep).
+We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
+At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
 
@@
 For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars.
-We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at $Z
-%mm3 [confirm]
-       / Z_{\odot} 
-=$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}.
+We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}.
 This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$.
@@
 Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe.
-Where this transition occurs is uncertain, but is commonly taken to be
-%mm3
-     at a mass $M_{\rm trans} \sim 
-8$--10~M$_{\odot}$.
+Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$.
 This is a free parameter in our model; we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value.
@@
 Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics).
-Varying
-%mm3 $M_{\rm thresh}$ 
-           $M_{\rm trans}$
-changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
-\citet{Cote2017} explores how the choice of
-%mm3 $M_{\rm thresh}$
-           $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
+Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
+\citet{Cote2017} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
 We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
@@
 We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
-We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population,
-%mm3
-     substantially limiting the number of Type Ia SNe occurring during the initial gigayear in 
-     our models.
+We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, substantially limiting the number of Type Ia SNe occurring during the initial gigayear in our models.
 
@@
 We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
-%Properly modeling stellar winds requires sub-parsec resolution, which is problematic in galaxy-scale simulations.
 
@@
 \label{sec: core collapse}
-Stars between  $
-%mm3 M_{\rm thresh}
-           M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
+Stars between  $M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
 Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}).
 We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
-%mm3 [How do you antialias the energy?  Something like Simpson's cloud-in-cell method, or something else?]
+% AE: responding to mm3, this avoids aliasing:
+We use the same Monte Carlo sampling method as used in our stellar winds to map the spherical injection region to the grid.
 We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle.
@@
 This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; none of which are followed directly in these simulations.
-Instead, we use a
-%mm3 log-linear 
-    power-law 
-fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
+Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
 %This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
@@
 
-Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM. This 
-%mm3 additionally 
-prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation. 
-%mm3 These 
-    During this period, 
-SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
+Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
+This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
+During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
 We stop the artificial driving 25~Myr after the first star particle forms.
@@
 
-%mm3 {\bf New (addressing KVJ's comment to clarify how to interpret / what is target comparison point for our galaxy model:} 
 We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
@@
 Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe.
-The subsequent metal enrichment from the stars in our simulation can be thought of as
-%mm3
-    tracking 
-a change in abundances
-%mm3 , or delta abundances, 
-from arbitrary initial conditions. We 
-%mm3
-   will 
-discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.
+The subsequent metal enrichment from the stars in our simulation can be thought of as tracking
+a change in abundances from arbitrary initial conditions.
+We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.
 
@@
 \label{sec:results}
-We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first
-%mm3
-   new
-star forms. Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual 
-%mm3 initialization of the simulation
-   beginning of the simulation run. 
+We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms.
+Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run.
 The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical heigh $|z| < 200$~pc relative to the center of the galaxy.
@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $6 \times 10^5$ M$_{\odot}$, or roughly 17\%, of the total
-%mm3 [confirm]
-    gas 
-mass in the galaxy's disk.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $5.8 \times 10^5$ M$_{\odot}$, or roughly 16\%, of the total gas mass in the galaxy's disk.
 The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\%; at this point, it is about equal with the \ion{H}{1} gas.
-This is because the total amount of
-%mm3 mass 
-    gas
-in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained.
+This is because the total amount of gas in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained.
 Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback.
@@
 The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
-After this point, the molecular component
-%mm3 dominates
-   becomes equally or even somewhat more important 
-through the end of the simulation.
+After this point, the molecular component becomes equally or even somewhat more important through the end of the simulation.
 Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining mass dominated by the WNM.
@@
 
-% figure here of mass loading and mass outflow rates
 \begin{figure*}
@@
 See Section~\ref{sec:obs_metals} for further discussion.
-%\textbf{closing sentence}
 
 \subsubsection{Differential Mixing of Elements Within the ISM}
-%mm3 \textbf{CHANGE: Simplified plot to just log(N/O) to make this less confusing and easier to interpret. Cleaned up text accordingly.}
 It is important to understand how metals from each source of stellar yields enrich the ISM.
@@
 The left panel gives the abundance ratio of N to O throughout the ISM.
-The
-%mm3 left 
-   right 
-two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy. These 
-%mm3 serve to guide the eye in the right panel, clearly indicating 
-    show
-regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
+The right
+two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy.
+These show regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K) connected by cold filaments, warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
 
 \begin{figure*}
-%\gridline{\fig{DD0557_Slice_z_logN_O}{0.8\textwidth}{}}
-%\gridline{\fig{DD0557_Slice_z_number_density}{0.4\textwidth}{}
-%          \fig{DD0557_Slice_z_Temperature}{0.4\textwidth}{}}
 \includegraphics[width=0.98\linewidth]{log_NO_panel}
@@
 
-  % \caption{Three slices in the mid-plane of our dwarf galaxy at an arbitrary time of 350~Myr after the start of star formation, demonstrating the power of our chemical evolution model.
-We show the number density and temperature in this region of the galaxy (top row), along with three different elemental abundance ratios, O/H (bottom left), N/H (bottom middle), and N/O (bottom right).
-We caution against making direct comparisons of these images to observed abundances of dwarf galaxies, as we do not capture a cosmologically realistic chemical evolution in these relatively short ($< 1$~Gyr) simulations.
-This will be addressed in future work.
-\textbf{(AE: need to adjust axis label size)}}
-
-%\begin{figure*}
-%\centering
-%\includegraphics[width=0.5\linewidth]{test}\\
-%\includegraphics[width=0.32\linewidth]{y} 
-%\includegraphics[width=0.32\linewidth]{DD0557_Slice_z_Temperature}\\
-%\includegraphics[width=0.32\linewidth]{log_OH} 
-%\includegraphics[width=0.32\linewidth]{log_NH}
-%
-%\end{figure*}
-
-The 
-%mm3 [redundant with end of previous para?] number density and temperature panels clearly show a multi-phase ISM: the 
-CNM consists of cold filaments that connect dense clumps of molecular gas that are readily visible in both diagrams.
+%The CNM consists of cold filaments that connect dense clumps of molecular gas that are readily visible in both diagrams.
 Distinguishing the WNM and WIM is difficult, but the lower density regions between the cold filaments are dominated by these phases.
@@
 There are three regions in particular that are overabundant in N (green color).
-%mm3 [moved to next para] These are sites of recent AGB winds that have yet to mix with the rest of the ISM.
-
-% Beginning with log(O/H), the gas from the recent SN explosion is abundantly clear, with a higher oxygen abundance by at least 1 dex than its surroundings.
-The oxygen abundance throughout the rest of the ISM does vary, with almost all dense regions showing modest enhancements in oxygen abundance compared to their less dense surroundings.
-The ratio log(N/H), however, shows slightly more significant variation throughout the ISM.
-Comparing the two diagrams, one can pick out regions with differing abundances between the two species.
-This is clear in the log(N/O) slice, which emphasizes regions with strongly varying abundance in either species.
-The gas from the SN explosion, for example, has a low log(N/O) due to the significant amount of oxygen released in the SN.
-Oxygen is generally more abundant than nitrogen throughout the ISM, particularly in the warm, diffuse gas.
-However, the dense, cold gas typically has a greater log(N/O) than its surroundings, indicating that nitrogen may more easily pollute cold gas than oxygen.
-These differences are also evident with a few regions of warmer gas (small sliver at center of figure, horseshoe shaped feature in lower right, and the blob in the upper right) where log(N/O) > 0, indicating an overabundance of nitrogen as compared to oxygen.
 
@@
 Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
-%mm3
 The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
@@
 
-%mm3 {\bf New (response to KVJ comment on comparability):} 
 As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs.
@@
 This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
-%AE, which was argued to demonstrate that this represents the basic physics at work.
 
@@
 
-%mm3 \subsubsection{Full Stellar Wind Model}
 \subsubsection{Massive Stellar Wind Energy}
 \label{sec:stellar winds discussion}
-Our 
-%mm3
-   massive
-stellar wind model 
-%mm3 significantly 
-     drastically 
-reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$. Although our 
-%mm3 model is 
-   algorithm is entirely 
-capable of generating realistic stellar winds with
-%mm3 temperature profiles and radial evolution comparable to those expected from analytic calculations \citep{Weaver1977}, the hot, [the winds are not hot, only the post-shock gas; Weaver et al.
-calculated the bubble structure resulting from winds moving at observed speeds]
-     velocities comparable to those observed, such
-fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
-When considered in isolation, stellar winds are an important source of pre-SN feedback and
-%mm3 do 
-   can
-dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
-However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014},
-%mm3 [insert text]
-    unless densities near the ionizing source are high enough to trap the  \ion{H}{2} region in the source cell.
+Our massive stellar wind model drastically reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$.
+Although our algorithm is entirely capable of generating realistic stellar winds with velocities comparable to those observed, such fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
+When considered in isolation, stellar winds are an important source of pre-SN feedback and can dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
+However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}, unless densities near the ionizing source are high enough to trap the  \ion{H}{2} region in the source cell.
 In that case, they can clear out a cavity to allow initial establishment of the \ion{H}{2} region.
 
-% [end of insertion]
 They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
@@
 
-We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested. Mechanically, including
-%mm3 
-   this relatively simple treatment of 
+We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested.
+Mechanically, including this relatively simple treatment of
 cosmic ray feedback in our model is trivial.
@@
 We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
-For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail,
-%mm3 accounting for stellar winds, 
-     using individual star particles to model
-core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, Lyman-Werner radiation
-%mm3 using individual star particles
-    and pollution from AGB and massive stellar winds. This
-%mm3
-    treatment of feedback, 
-coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
+For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, using individual star particles to model core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, Lyman-Werner radiation and pollution from AGB and massive stellar winds.
+This treatment of feedback, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
 In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
@@
 \item 
-%mm3 A thin, yet resolved, gas scale height ($\sim 50$~pc)
 The gas scale height is thin ($\sim 50$~pc), yet resolved, 
@@
 
-\item The ISRF of our galaxy varies strongly in time, by orders of magnitude, though
-%mm3 it is relatively uniform in space at any given time. [this is contradicted by Figure \ref{fig:ISRF_2D}]
-    it has a relatively uniform radial profile averaged over tens of megayears.
+\item The ISRF of our galaxy varies strongly in time, by orders of magnitude, though it has a relatively uniform radial profile averaged over tens of megayears.
 It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
@@
 
-\item Finally, we used O and N as examples to briefly demonstrate that there are 
-%mm3 discernible 
-    marked
-differences in how individual metal species are distributed within the ISM of our galaxy. These variations could be tied to differences in 
-%mm3 yield sources among elements
-    elemental yields among different sources 
-(for example, AGB winds vs. SNe), as suggested by \cite{KrumholzTing2018}. This will be explored in more detail in future work.
+\item Finally, we used O and N as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy.
+These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs.
+SNe), as suggested by \cite{KrumholzTing2018}.
+This will be explored in more detail in future work.
 %mm3 (Emerick et. al. \textit{in prep.}). [only cite after submission]
@@
 \section*{Acknowledgments:} 
-%mm3 [moved personal acknowledgments to the front}
 We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
@@
 resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute.
-This work made significant use of many open source software packages, including
-%mm3 [updated capitalization to that used in relevant websites]
-\textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.
+This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.
 These are products of collaborative effort by many independent developers from numerous institutions around the world.
 Their commitment to open science has helped make this work possible.
-
-%\textit{Software:} \textsc{Enzo} \citep{Enzo2014}, \textsc{yt} \citep{yt}, \textsc{Grackle} \citep{GrackleMethod}, \textsc{Cloudy} \citep{Cloudy2013}
-%\bibliographystyle{apj}
-%\bibliography{msbib}
 
@@
 \label{appendix:radiation}
-We 
-%mm3 detail 
-  determine 
-the radiation properties of our model stars as a function of stellar mass and metallicity
-%mm3 . The stellar radiation properties are determined 
-from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
+We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
 In Figure~\ref{fig:stellar radiation properties} we plot these properties.
@@
 This requires two factors for each radiation type, one for low mass and one for high mass stars.
-We use the following multiplicative factors to adjust the black body spectrum for \ion{H}{1} and \ion{He}{1}
-%mm3
-   ionizing 
-radiation respectively: [0.1, 3.2] and [0.0001, 4.0]. We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
+We use the following multiplicative factors to adjust the black body spectrum for \ion{H}{1} and \ion{He}{1} ionizing radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
+We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
 
@@
 A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section.
-We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from
-%mm3 [changed to \url because \texttt translates the tilde into a space]
-\url{http://www.pa.uky.edu/~verner/photo.html}} 
+We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \url{http://www.pa.uky.edu/~verner/photo.html}}
 The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision.
@@
 The vertical lines show one and 4.5 cell widths.
-This shows that a fraction of these SNe are certainly underresolved, with R$_{\rm PDS}$ less than a single cell size,
-%mm3
-   and somewhat more don't satisfy the 4.5 cell criterion, 
-but the majority are well resolved.}
+This shows that a fraction of these SNe are certainly underresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
 \label{fig:SN histogram}
@@
 \label{appendix:cooling}
-%mm3 \textbf{CHANGE: Section was somewhat confusing in original form. Re-arranged order and re-worded}
-
 %AE: 2/23 Old version of text... keeping around for now:
@@
 
-Finally, we note that the cooling and heating rates in our simulation 
-%mm3 depend 
-will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
+Finally, we note that the cooling and heating rates in our simulation will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
 The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which is not included in these diagrams.
@@
 
-%mm3 \textbf{CHANGE: Updated plots with full runs. No significant change to text.}
 We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions between our fiducial high-resolution simulation, two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc.

### 2018-03-22 main.tex
added M-M NASA grant number
Update on Overleaf.

@@
 The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
-{\bf We have compared our cooling curves to those used in \citep{Hu2017} (C.
-Hu, private communication) and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.}
+We have compared our cooling curves to those used in \citep{Hu2017} (C.
+Hu, private communication) and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.
 
@@
 In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
-Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionization of H and He from the UV background.
+Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionization of H and H from the UV background.
 This has the seemingly counterintuitive effect that turning off the UV background actually decreases the formation rate of H$_2$, as confirmed in test simulations.
 In a test simulation ignoring all H$^{-}$ reactions, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.
-%mm3 
-    {\bf [Is there any treatment in the model of the visible light radiation field, which is sufficient to destroy H$^-$?]}
+Although we ignore the visible component of our ISRF, capable of destroying H$^{-}$, this is included from the UV background.
 
@@
 M.-M.M.L.
-was funded by NASA
-%mm3 [have to scare up the number still]
-We gratefully recognize computational
-resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute.
+was partly funded by NASA  grant NNX14AP27G.
+We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute.
 This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.

### 2018-04-19 main.tex
Update on Overleaf.
MNRAS style updates

@@
 %mm3 since Greg has already read this, I have removed commentary as I go.  substantive changes now marked with %mm3 13 Mar 18
-\documentclass[twocolumn]{aastex61}
-\pdfoutput=1 %for arXiv submission
-\usepackage{amsmath,amstext}
+%\documentclass[twocolumn]{aastex61}
+%\pdfoutput=1 %for arXiv submission
+\documentclass[a4paper,fleqn,usenatbib,useAMS]{mnras}
+\usepackage{graphicx}	% Including figure files
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+\usepackage{multicol}        % Multi-column entries in tables
+\usepackage{bm}		% Bold maths symbols, including upright Greek
+%\usepackage{pdflscape}	% Landscape pages
+
 \usepackage[T1]{fontenc}
-\usepackage{apjfonts} 
+\usepackage{ae,aecompl}
+\usepackage{newtxtext,newtxmath}
+
+%\usepackage{amsmath,amstext}
+%\usepackage[T1]{fontenc}
 \usepackage[figure,figure*]{hypcap}
-\usepackage{multirow}
-\usepackage{mathtools}
-\renewcommand*{\sectionautorefname}{Section} %for \autoref
-\renewcommand*{\subsectionautorefname}{Section} %for \autoref
+%\usepackage{multirow}
+%\usepackage{mathtools}
+%\renewcommand*{\sectionautorefname}{Section} %for \autoref
+%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
 %\usepackage{graphicx}
+
+%\usepackage{apjfonts} 
+%\usepackage{natbib} % bibliography
 
@@
 
-\shorttitle{Feedback with Individual Stars}
-\shortauthors{Emerick, Bryan, Mac Low}
+%\shorttitle{Feedback with Individual Stars}
+%\shortauthors{Emerick, Bryan, Mac Low}
 \newcommand{\msun}{M$_{\odot}$}
@@
 
+% For bibtex
+
+\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
+
+\author[A. Eemerick et. al.]{
+Andrew Emerick,$^{1,2}$
+Greg L. Bryan,$^{1,3}$
+and Mordecai-Mark Mac Low$^{2,1}$
+\\
+$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
+$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
+$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+
 \begin{document}
 
-\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
-
-\author{Andrew Emerick}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-\author{Greg L. Bryan}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-\author{Mordecai-Mark Mac Low}
-\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\label{firstpage}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
+%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
+
+%\author{Andrew Emerick}
+%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+%\author{Greg L. Bryan}
+%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+%\author{Mordecai-Mark Mac Low}
+%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
 
@@
 
-\keywords{Galaxy -- Hydrodynamics -- Simulation -- Feedback}
+\begin{keywords}
+Galaxy -- Hydrodynamics -- Simulation -- Feedback
+\end{keywords}
 
@@
 Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
-We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on \ion{H}{1}.
+We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on HI.
 In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
@@
 Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
-As we seek a complete accounting of stellar feedback physics, we follow \ion{H}{1} and \ion{He}{1} ionizing radiation from our stars through the ray tracing methods described below.
+As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.
 
 Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation.
-We follow \ion{H}{1} and \ion{He}{1} ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
-
-We determine the \ion{H}{1} and \ion{He}{1} ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
+We follow HI and HeI ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
+
+We determine the HI and HeI ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
 We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star.
@@
 Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}).
-The average energy for \ion{H}{1} and \ion{He}{1} ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
-
-We also include the effects of radiation pressure on \ion{H}{1}.
+The average energy for HI and HeI ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
+
+We also include the effects of radiation pressure on HI.
 This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}.
@@
 Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}.
-We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for \ion{H}{1} self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
-We assume \ion{He}{1} ionization generally follows \ion{H}{1}.
-This allows us to approximate \ion{He}{1} self-shielding using the same form (A.
+We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
+We assume HeI ionization generally follows HI.
+This allows us to approximate HeI self-shielding using the same form (A.
 Rahmati, private communication).
-We ignore \ion{He}{2} photoionization from the UV background entirely.
+We ignore HeII photoionization from the UV background entirely.
 Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
@@
 Leo P is gas rich, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and low metallicity,
-with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity fraction of $Z/Z_{\odot} \sim 5.4\times10^{-4}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}.
-Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z/Z_{\odot} = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
+with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
+Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
 
@@
 This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
-During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central \ion{H}{1} surface density and the relation presented in \citep{Roychowdhury2009}.
+During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}.
 We stop the artificial driving 25~Myr after the first star particle forms.
@@
 \caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation.
-Shown are the density weighted projection of number density (top row), temperature slices (second row), \ion{H}{1} column density (third row), and H$_2$ column density (fourth row).
+Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row).
 Each individual main sequence star particle is shown in the number density projections as a single black dot.}
@@
 Constraining the gas scale height in ultra-faint dwarf galaxies observationally, to compare to our simulations, is challenging.
-For Leo P, located at 1.7~Mpc, \ion{H}{1} observations that are capable of detecting the diffuse \ion{H}{1} throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest \ion{H}{1} clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
+For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
 
@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), \ion{H}{1} still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $5.8 \times 10^5$ M$_{\odot}$, or roughly 16\%, of the total gas mass in the galaxy's disk.
-The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\%; at this point, it is about equal with the \ion{H}{1} gas.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $5.8 \times 10^5$ M$_{\odot}$, or roughly 16\%, of the total gas mass in the galaxy's disk.
+The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\%; at this point, it is about equal with the HI gas.
 This is because the total amount of gas in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained.
@@
 \caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins (left).
-Right: The evolution of the total gas mass (black), \ion{H}{1} mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.
+Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.
 Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.}
@@
 \begin{figure}
-\centering
+%\centering
 \includegraphics[width=0.95\linewidth]{phase_diagram.png}
@@
 \begin{figure*}
-\centering
+%\centering
 \includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
@@
 The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
-The bottom panel gives the \ion{H}{1} ionizing stellar radiation flux.
+The bottom panel gives the HI ionizing stellar radiation flux.
 Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point.
 For this reason we only shade between the first quartile and maximum values.
-\ion{He}{1} ionizing radiation is very similar to \ion{H}{1} ionizing radiation, with a small vertical offset, and is not shown for clarity.}
+HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.}
 \label{fig:ISRF}
@@
 
-The bottom panel gives the ionizing photon fluxes for \ion{H}{1} from stellar radiation {\em only}.
+The bottom panel gives the ionizing photon fluxes for HI from stellar radiation {\em only}.
 Since this field is tracked directly using ray-tracing radiative transfer, the profile encodes information about local attenuation of these photons from dense, neutral gas.
@@
 \begin{figure*}
-\centering
+%\centering
 \includegraphics[width=0.45\linewidth]{g_o_2D_phase}
 \includegraphics[width=0.45\linewidth]{q_o_2D_phase}
-\caption{Single-snapshot 2D radial profile plots at 200~Myr of the ISRF in two flux bands, $G_{\rm o}$ and \ion{H}{1} ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
+\caption{Single-snapshot 2D radial profile plots at 200~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
 Here, we include all gas within the mid-plane of our dwarf galaxy.
-Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to \ion{H}{1} ionizing radiation, it does not show up in the \ion{H}{1} ionizing radiation diagram.
+Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
 This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
@@
 
-To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the \ion{H}{1} ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr.
+To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr.
 This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
-The striking contrast between the two diagrams is due to the shielding of the \ion{H}{1} ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
+The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
 From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
@@
 \begin{figure*}
-\centering
+%\centering
 \includegraphics[width=0.45\linewidth]{total_mass_outflow}
@@
 \begin{figure}
-\centering
+%\centering
 \includegraphics[width=0.95\linewidth]{outflow_velocity_distribution}
@@
 \begin{figure}
-\centering
+%\centering
 \includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
@@
 
-The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted \ion{H}{1} surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}.
+The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}.
 However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
@@
 \centering
-\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution}
-\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution}
+\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
+\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution.png}
 \caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
 See text for details of the calculation.
-Recent observations from the S\ion{H}{1}ELD sample \citep{Teich2016} are plotted as black points with error bars.
+Recent observations from the SHIELD sample \citep{Teich2016} are plotted as black points with error bars.
 On the left, we also give the best fit line to galaxies from the FIGGS sample from \cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \cite{Shi2011}.
@@
 beyond our stellar radius, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
-This is comparable to the resolution limit of the diffuse \ion{H}{1} in observed, gaseous ultrafaint dwarfs.
+This is comparable to the resolution limit of the diffuse HI in observed, gaseous ultrafaint dwarfs.
 (See Figure~\ref{fig:scale_height}).
@@
 This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy.
-This leads to high molecular gas fractions, with an H$_2$ mass comparable to that of \ion{H}{1} by the end of the simulation.
+This leads to high molecular gas fractions, with an H$_2$ mass comparable to that of HI by the end of the simulation.
 This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies.
@@
 
-\bibliographystyle{yahapj}
+%\bibliographystyle{yahapj}
+\bibliographystyle{mnras}
 \bibliography{msbib}
@@
 This requires two factors for each radiation type, one for low mass and one for high mass stars.
-We use the following multiplicative factors to adjust the black body spectrum for \ion{H}{1} and \ion{He}{1} ionizing radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
+We use the following multiplicative factors to adjust the black body spectrum for HI and HeI ionizing radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
 We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
@@
 \includegraphics[width=0.4\linewidth]{E1}
-\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for \ion{H}{1} (top left) and \ion{He}{1} (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for \ion{H}{1} (bottom left) and \ion{He}{1} (bottom right).
+\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right).
 Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
@@
 R_{\rm PDS} = 
-\begin{cases*}
-49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z $\le$ 0.01 \\
-18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z $\ge$ 0.01 \\
-\end{cases*}
+\begin{cases}
+49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z \le 0.01 \\
+18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z \ge 0.01 \\
+\end{cases}
 \end{equation}

### 2018-04-19 main.tex
Update on Overleaf.

@@
 We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
-We include the yields ejected in massive stellar winds, but neglect the winds' energetic contribution due to computational constraints.
+We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints.
 We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
@@
 See text for details of the calculation.
-Recent observations from the SHIELD sample \citep{Teich2016} are plotted as black points with error bars.
-On the left, we also give the best fit line to galaxies from the FIGGS sample from \cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \cite{Shi2011}.
-There is no clear correlation with time in this diagram.}
+Recent observations from the SHIELD sample Teich2016 are plotted as black points with error bars.
+On the left, we also give the best fit line to galaxies from the FIGGS sample from Roychowdhury2014, and on the right we also show the best fit line and 1 $\sigma$ errors from Shi2011.
+There is no clear correlation with time in this diagram.} %something is breaking here in compiling
 \label{fig:KS}

### 2018-04-19 main.tex
Update on Overleaf.
fixed issues with hyperref and compiling

@@
 %\pdfoutput=1 %for arXiv submission
-\documentclass[a4paper,fleqn,usenatbib,useAMS]{mnras}
+\documentclass[fleqn,usenatbib,useAMS]{mnras}
 \usepackage{graphicx}	% Including figure files
@@
 
+%%%%%%%%%%%%%%%%%%\hypersetup{draft}
 % For bibtex
@@
 Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
-Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
+Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
 Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
@@
 See text for details of the calculation.
-Recent observations from the SHIELD sample Teich2016 are plotted as black points with error bars.
-On the left, we also give the best fit line to galaxies from the FIGGS sample from Roychowdhury2014, and on the right we also show the best fit line and 1 $\sigma$ errors from Shi2011.
+Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars.
+On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}.
 There is no clear correlation with time in this diagram.} %something is breaking here in compiling
@@
 %\section{appendix section}
+\label{lastpage}
 

### 2018-04-30 main.tex
adressing first half of referees comments. Primarily those in methods / intro that do not go into results. updating some references

@@
 \label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
 \maketitle
@@
 Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
-Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
+Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b}.
 Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
@@
 Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
-This is acutely problematic at star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
-Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
+\textbf{This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
+At high star formation rate densities, an undersampled IMF in a single low mass star particle can be ompensated for by having many adjacent star particles.} Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
 The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
@@
 
-We refine the mesh whenever the Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
+We refine the mesh whenever the \textbf{thermal} Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
 At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation.
@@
 Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
-However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial collapse once its Jeans length becomes unresolved.
+However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse.
+\textbf{A non-thermal pressure term is added} to cells once their \textbf{thermal} Jeans length becomes unresolved.
 This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
@@
 In order to resolve individual star formation events on galacitc scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
-Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
+Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local \textbf{thermal} Jeans mass.
 Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K.
@@
 
-The stellar mass formed during a timestep $\Delta t$ is
+The stellar mass formed during a timestep $\Delta t$ \textbf{from a region with a total gas mass $M_{\rm gas}$} is
 \begin{equation}
@@
 If it does, we randomly sample from
-the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
-We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
+the adopted IMF until \textbf{approximately} 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
+\textbf{The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.} We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
 Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
@@
 Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation.
-We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
+We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017a} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
 
@@
 Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
-\citet{Cote2017} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
+\citet{Cote2017a} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
 We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
@@
 Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback.
-We inject the feedback energy in a spherical region with a three-cell radius centered on the emitting star particle, assuming full thermalization of the wind kinetic energy.
-The total injected energy in timestep $\Delta t$ is therefore $E_w = \dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
-We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells.
-We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
+We assume complete thermalization of the wind kinetic energy, taking the total injected energy injected in timestep $\Delta t$ as $E_w = \frac{1}{2}\dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
+\textbf{This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle.
+The edges of this spherical region will only partially overlap grid cells.
+We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately.} We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
 
@@
 %where $M_{\rm *}$ is the initial mass of the WD progenitor.
-We follow the common assumption that progenitor stars with initial masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.
+We follow the common assumption that progenitor stars with initial masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017a}.
 
@@
 This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
-In practice, we invert the cumulative probability function to assign an exact time at which a given WD will explode using only a single random number draw, rather than sampling the probability distribution for each WD particle at every time step.
+\textbf{In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle.
+For $u \in [0,1]$, we interpolate its position on a pre-tabulated and inverted cumulative probability distribution function to assign a single time at which the WD particle will explode as a Type 1a supernova.
+We institute a minium delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.}
 
@@
 However, the importance of multiple scattering is still unclear.
-Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017,Wibking2018}.
+Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013a,Reissl2017,Wibking2018}.
 Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.
@@
 Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
-This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; none of which are followed directly in these simulations.
-Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
+This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations.
+\textbf{Our chemical work only includes contributions from H, He, and H$_2$ to n$_e$.} Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
 %This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
@@
 The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
-Leo P is gas rich, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and low metallicity,
-with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
+Leo P is gas rich, with a \textbf{neutral hydrogen mass} $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and \textbf{stellar mass} $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to an \textbf{observed neutral hydrogen radius} $r_{\rm HI} = 500$~pc.
+LeoP has a low metallicity, with \textbf{an oxygen to hydrogen abundance ratio} of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
 Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
@@
 We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$.
-We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$, $R_{\rm vir}~=~27.4$~kpc and r$_{\rm s} = 990$~pc.
+We adopt a \citet{Burkert1995} dark matter potential with \textbf{virial mass and radius} $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and \textbf{scale radius} r$_{\rm s} = 990$~pc.
 This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc.
@@
 
-\subsubsection{Differential Mixing of Elements Within the ISM}
+\subsubsection{Differential Evolution of Elements Within the ISM}
 It is important to understand how metals from each source of stellar yields enrich the ISM.
@@
 To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He.
-We note that there is generally no correction made for any possible H$_{\rm 2}$ or \ion{H}{2} content.
+We note that there is generally no correction made for any possible H$_{\rm 2}$ or HII content.
 As shown in Section~\ref{sec:molecular gas content}, these components may be significant.

### 2018-06-03 main.tex
Update on Overleaf.

@@
 We ignore HeII photoionization from the UV background entirely.
-Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
+{\bf For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (, eV) and H$_2^+$ destruction (,eV) by the same shielding factors computed for HI and HeI shielding.}\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
 As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.

### 2018-06-21 main.tex
filename typo fix
Update on Overleaf.

--- 2018-04-19 main.tex
@@
-%mm2 substantive changes marked with this comment tag, minor changes and wordsmithing done silently.  12-15 Feb
-%mm3 since Greg has already read this, I have removed commentary as I go.  substantive changes now marked with %mm3 13 Mar 18
-%\documentclass[twocolumn]{aastex61}
-%\pdfoutput=1 %for arXiv submission
-\documentclass[fleqn,usenatbib,useAMS]{mnras}
-\usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{multicol}        % Multi-column entries in tables
-\usepackage{bm}		% Bold maths symbols, including upright Greek
-%\usepackage{pdflscape}	% Landscape pages
-
+\documentclass[twocolumn]{aastex61}
+\pdfoutput=1 %for arXiv submission
+\usepackage{amsmath,amstext}
 \usepackage[T1]{fontenc}
-\usepackage{ae,aecompl}
-\usepackage{newtxtext,newtxmath}
-
-%\usepackage{amsmath,amstext}
-%\usepackage[T1]{fontenc}
+\usepackage{apjfonts} 
 \usepackage[figure,figure*]{hypcap}
-%\usepackage{multirow}
-%\usepackage{mathtools}
-%\renewcommand*{\sectionautorefname}{Section} %for \autoref
-%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
-%\usepackage{graphicx}
-
-%\usepackage{apjfonts} 
-%\usepackage{natbib} % bibliography
-
-%\usepackage[active,floats,tightpage]{preview}
-%    \setlength\PreviewBorder{1em}
-
-%\shorttitle{Feedback with Individual Stars}
-%\shortauthors{Emerick, Bryan, Mac Low}
-\newcommand{\msun}{M$_{\odot}$}
-\newcommand{\ccunit}{cm$^{-3}$}
-
-%%%%%%%%%%%%%%%%%%\hypersetup{draft}
-% For bibtex
-
-\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
-
-\author[A. Eemerick et. al.]{
-Andrew Emerick,$^{1,2}$
-Greg L. Bryan,$^{1,3}$
-and Mordecai-Mark Mac Low$^{2,1}$
-\\
-$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
-$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
-$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+
+\renewcommand*{\sectionautorefname}{Section} %for \autoref
+\renewcommand*{\subsectionautorefname}{Section} %for \autoref
+
+\shorttitle{Differential Metal Mixing}
 
@@
 
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
-
-%\author{Andrew Emerick}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\author{Greg L. Bryan}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-%\author{Mordecai-Mark Mac Low}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-
-%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}
+%\title{Evolution of Individual Metals in Galactic Winds and the ISM}
+
+% GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
+\title{Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies}
+
+\author{Andrew Emerick}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\author{{\it more...}}
 
 \begin{abstract}
-%\textbf{CHANGE: Cleaned up a few sentences. better intro + last sentence. added wind caveat. removed large H2 content mention (should I put this last one back?).}
-%Galactic chemical evolution is driven through stellar feedback and its ability to drive metal mixing within the interstellar medium (ISM) and beyond the galaxy in outflows.
-However, we are far from a complete understanding of feedback and galactic chemodynamics in general.
-In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
-We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
-We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints.
-We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
-We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
-Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations.
-Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
+Using a high resolution simulation of an isolated dwarf galaxy, accounting for stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy through galactic winds.
+For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal + power-law distribution.
+The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail.
+The PDF properties, and relative significance of these two components, vary within each ISM phase.
+Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component.
+In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe).
+This difference is driven by the differences in energetics between each source, particularly the poor coupling of AGB winds.
+Only 60\% of metals dominated by AGB enrichment are ejected through winds, even though 90\% of all metals leave the galaxy.
+In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae.
+We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
 \end{abstract}
 
-\begin{keywords}
-Galaxy -- Hydrodynamics -- Simulation -- Feedback
-\end{keywords}
+\keywords{}
 
 \section{Introduction}
-%
-% AE removed below.. MM suggested  skipping both pars.
-%
-%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade.
-Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc.
-\citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses.
-On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM.
-This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}.
-See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.
-%
-%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution.
-In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense.
-In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships.
-For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.
-
-Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution.
-Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
-There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
-These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
-
-%\textbf{rework here to the end... focus less on numerics}
-% However, there is a general lack of numerical diversity in these works, as a majority are implemented in some flavor of smoothed particle hydrodynamics (SPH) schemes.
-Given the known differences between hydrodynamics implementations \citep{Agertz2007,AGORA,AGORA2}, extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.
-% AE (incorrect statement): Additionally, grid-based schemes are able to generally avoid issues with metal mixing, one of the largest model uncertainties in standard SPH codes.
-
-%mm2 I think there does need to be some introduction to this discussion:
-
-However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}.
-In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
-This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possibly models that are not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
-While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution to reduce.
-Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
-Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}.
-Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
-the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
-The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
-
-Increasing physical resolution reduces reliance on sub-grid physics for mixing.
-However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}.
-Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
-This is acutely problematic at star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
-Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
-The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
-
-We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies.
-The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms.
-We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
-%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies.
-\citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
-Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar winds from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
-We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar far ultra-violet (FUV) radiation, and Lyman-Werner dissociation from stellar radiation.
-
-Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime.
-This includes yields from massive and AGB stellar winds, and supernovae (SNe).
-In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
-This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
-This paper is the first in a series examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
-We describe each mode of our multi-channel feedback
-in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.
-
-Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.
+% can I work "Currents of Space" into this paper somehow (Asimov)?
+Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (review refs for obs and theory).
+One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (e.x.
+stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas.
+(\textit{...
+more...})
+% Discuss common modeling assumptions in CE models that
+%    can be addressed here:
+%        1) instantaneous recycling approximation
+%        2) No metal mass loading of winds, or uniform 
+%           loading across species
+%        3) Uniform metal abundances across the ISM (one zone)
+%
+%  To some degree, cosmological simulations with comparably
+%     low spatial resolution face the same problems, where
+%     variations and spreads in abundances (esp. across 
+%     species) can be smoothed over due to the low res. or
+%     the particular details of the feedback methods and
+%     yield injection methods.
+
+One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references).
+While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood.
+This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
+Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (references), which plays an important role in determining the chemical properties of galaxies (references).
+% more on mixing
+Consequently, following metal mixing, if treated in these models, requires assumptions in how metals mix within the ISM and how metals couple to galactic outflows.
+When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly.
+However, these processes are critical components in understanding galactic chemical evolution.
+Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows.
+In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.
+
+The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
+(\textit{...
+more...}) That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1968,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucelosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
+Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in semi-analytic models and lower resolution cosmological simulations.
+However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
+
+% Paragraphs
+It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group.
+(APOGEE, GAIA, GALAH, RAVE?
+TGAS?).
+Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
+The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM.
+However, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.
+
+% Can shorten if this is actually going to be a letter
+In this paper we present the first detailed chemical evolution results from a set of high resolution hydrodynamics simulations in the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014} of an isolated, low mass dwarf galaxy.
+The simulation discussed here was first introduced in detail in Emerick et.
+al.
+2018 (hereafter Paper I).
+To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae.
+This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below.
+We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species.
+We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.
+
+The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity.
+Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging.
+[list examples of modelling problems].
+These uncertainties combined with the difficultly in simulating a fully self-consistent galaxy in detail motivates this current study.
+By focusing on a low mass dwarf galaxy, we are capable of capturing detailed feedback and ISM physics at high resolution, while following individual stars, due to their small physical scales and low star formation rates.
+In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios for two reasons.
+First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
+Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies with observational analogs in as much detail as we provide here.
+This work will be the first in several in attempting to bridge this gap.
+With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and low resolution simulations of more massive galaxies with physically motivated sub-grid physics models.
+
+We summarize of our methods and physics models in Section~\ref{sec:methods}.
+We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}.
+In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
 
@@
 \label{sec:methods}
-We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
-This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
-To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background.
-We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}).
-We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
-Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
-We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on HI.
-In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
-We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both.
-We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors.
-We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species.
-In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked.
-This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth.
-These methods are discussed in full detail below.
-
-\subsection{Hydrodynamics and Gravity}
-\label{sec:hydro}
-
-We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies.
-\texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions.
-We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick.
-Specifically, simulations presented here were conducted at changeset 5cc7cea.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
-We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}).
-Self-gravity is computed with a multigrid Poisson solver.
-The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.
-
-We refine the mesh whenever the Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
-At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation.
-\citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.
-
-We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}).
-Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
-However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial collapse once its Jeans length becomes unresolved.
-This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
-The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.
-
-\subsection{Chemistry and Cooling Physics}
-\label{sec:chemistry}
-
-We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset 59adc76b3130.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes.
-We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.
-We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
-However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}.
-For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
-% Since we assume a dust abundance that depends only on metallicity, we do not track dust destruction or creation, which may play an important role regulating detailed ISM properties.
-(Vogelsberger is working on this directly but no papers yet...
-will cite if it gets submitted by then)
-
-As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
-As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
-Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}.
-To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.
-We have made these new tables public in the main \texttt{Grackle} repository.
-These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
-Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.
-
-\subsection{Star Formation Algorithm}
-\label{sec:star formation}
-In order to resolve individual star formation events on galacitc scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
-Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local Jeans mass.
-Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K.
-We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$.
-No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.
-
-We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
-At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
-
-The stellar mass formed during a timestep $\Delta t$ is
+We refer the reader to Paper I for a detailed description of our numerical methods and feedback models. We briefly summarize the relevant details here.
+
+\textit{Hydrodynamics ---} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}.
+Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
+We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver.
+We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
+Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas and 2) a cell's local Jeans length becomes resolved by less than 8 cells.
+If the cell is within 4 zones of a star particle with active feedback, it is refined to the maximum resolution.
+At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.
+
+\textit{Chemistry, Heating, and Cooling Physics ---} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
+We account for approximate self-shielding of HI against the UV background following \cite{Rahmati2013}.
+We assume HeI self-shields in the same fashion as HI, and ignore HeII heating from the UVB entirely.
+Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}.
+Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.
+
+\textit{Star Formation ---} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
+Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$.
+Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$).
+We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\%.
+Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment.
+We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
+
+\textit{Stellar Feedback and Stellar Yields ---} We track the feedback and yields of 15 metal species for each star individually.
+Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
+Stars above this mass are assumed to direct collapse with no mass or energy injection.
+For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their HI and HeI ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
+We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars.
+Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind.
+Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
+Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et.
+al.
+in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.
+
+\textit{Initial Conditions ---} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
+We initialize a M$_{\rm gas} = 1.8 \times 10^{6} M_{\odot}$ disk with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$ using an exponential gas profile.
+The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
+Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium.
+The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
+Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
+Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.
+
+\section{Results}
+For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
+\textbf{UPDATE VALS:  In general, this galaxy has an average star formation rate of $4~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
+The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy.
+The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$.
+These winds eject 90\% of the metals produced in the galaxy, with 40\% of all metals leaving the virial radius by the end of the simulation time.
+}
+
+In this work we focus in detail on how each of the 15 individual metal species evolve in this galaxy.
+We address differences between the ejection fractions of each metal in Section~\ref{sec:ejection} and analyze for the first time the mass-fraction PDFs of the metals retained by the ISM in Section~\ref{sec:mixing}.
+
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.95\linewidth]{sfr_snrx100_agb.png}\\
+%\caption{}
+%\label{fig:sfr}
+%\end{figure}
+
+\subsection{Preferential Ejection of Metals from the ISM}
+\label{sec:ejection}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{species_bar.png}\\
+\includegraphics[width=0.95\linewidth]{species_bar_ISM.png}
+\caption{The fraction of each metal species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).
+The leftmost bar in each plot shows the sum of all metals.
+\textbf{font sizes}}
+\label{fig:species_fractions}
+% GB(AE): Why are H and He different? Either discuss or remove from plot.
+%  ------ AE removed from plot
+%
+\end{figure}
+
+The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (orange), and outside the virial radius (green).
+Gas that has left the simulation domain is included in this final category.
+We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in molecular gas ($f_{\rm H_2} > 0.5$, $T < 100 K$), the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
+Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+
+We find two major results.
+First, most of the metals in the ISM reside in cold gas, either the CNM or molecular gas, with only a few percent in the hot phases.
+The exact fraction varies with each species, but only on the level of a few percent.
+This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have higher metal mass fractions.
+Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however,the retention factor varies.
+The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 40\% for each) as compared to the rest of the metals ($\sim$ 10\%).
+This suggests that individual metals \textit{do not} share the same dynamical evolution.
+Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field.
+In this particular case, assuming that all metals behave the same would underestimate the galactic N and Ba enrichment by a factor of four.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{species_bar_sources.png}\\
+\caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
+These channels differ in both when metals are ejected, as determined by stellar evolution, and the energy with which they are ejected into the ISM.
+We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because only XX of them have exploded by the end of our 500~Myr simulation.}
+% GB(AE): Why are H and He different? Either discuss or remove from plot.
+%  ------ AE removed from plot
+%
+\label{fig:species_sources}
+\end{figure}
+
+The only physics that separates the dynamical evolution of these elements in our simulations is the individual sources of enrichment: AGB winds, stellar winds (from stars above 8~M$_{\odot}$), core collapse supernovae, and Type Ia supernovae.
+These channels differ in how long after a given star formation event they occur, and by consequence the typical ISM properties in which they occur, and how much energy is associated with each event, which determines the temperature of the gas carrying each element.
+To understand where each of the elements in Figure~\ref{fig:species_fractions} originated, we show the mass fraction of metals produced through each channel in Figure~\ref{fig:species_sources}.
+Core collapse supernovae are responsible for over 90\% of the total metal enrichment in our galaxy, but this is clearly not true for all elements.
+In particular, a majority of N (76\%) and Ba (65\%) are ejected by AGB winds, and both are retained at a higher rate than the rest of the metals.
+That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yields tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through supernovae.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and supernovae.
+However, this cannot be determined as we lack Lagrangian information about individual gas elements.} We discuss how this result may extend towards other metal yields that are not well sampled on our relatively short (500 Myr) simulation timescales in Section~\ref{sec:discussion:metal yields}.
+
+AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of supernovae ($\sim$1000~km~s$^{-1}$).
+In addition, their longer timescales (40-100~Myr as compared to $\sim$10~Myr) means that AGB stars are typically removed from their birth regions.
+The changes in typical ISM density and height of these events contributes to these variations.
+We show histograms of the average number density within 20~pc of the source (top) and height above/below the disk (bottom) within 1~Myr of the event (as limited by our output cadence) in Figure~\ref{fig:spatial distribution}.
+As shown, SN have a bi-modal distribution in density as they explode either close to their dense formation region or within superbubbles, while AGB stars are singly peaked between this distribution at close to the average ISM density.
+We do not expect these differences to be the dominant effect in driving the differential evolution of elements ejected by AGB winds vs.
+supernovae, compared to the energetics.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{SE_density.png}\\
+\includegraphics[width=0.95\linewidth]{SE_z.png}
+\caption{The average gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event. {\bf ignore SNIa line in plot}}
+\label{fig:spatial distribution}
+\end{figure}
+
+\subsection{Mixing and Distribution of Metals in the ISM}
+\label{sec:mixing}
+
+Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
+In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textbf{refs to canonical models}).
+Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances.
+In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
+However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
+To build towards this, we characterize the metal evolution and distributions in our galaxy below.
+
+% Classic chemical evolution models often adopt the simplifying assumption that metals from newly formed stars are instantly deposited back into the ISM \textbf{(examples)}.
+With added complication, this instantaneous recycling approximation (IRA) can be expanded upon by taking into account individual stellar lifetimes (references) which have been shown to produce significant variations in stellar abundances (references) as compared to IRA models.
+However, even in this new model it is unlikely that whatever fraction of a star's yields that remains in the ISM instantaneously enriches star forming gas.
+Rather, these yields are first injected through a hot phase (stellar winds, HII regions, supernovae), cooling over time into star forming gas.
+(refs for models accounting for this).
+We investigate this process in our simulations below, first by outlining a new analytic description of metal distributions in the ISM.
+
+\subsubsection{A Functional Form for Metal PDFs}
+\label{sec:log-normal}
+
+The log-normal distribution is found often in nature, generally describing processes with non-negative values that grow with time.
+In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}.
+In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}.
+Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}.
+It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape.
+This includes a log-normal component, generated by multiplicative processes (shocks and the turbulent cascade in the ISM) and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2017}.
+
+The physics that drives the density PDF is directly related to the process of metal mixing and diffusion.
+However, there is no a priori reason why gas density and metallicity PDFs should have similar functional forms.
+We demonstrate here for the first time that the mass fraction PDFs for each metal species in our simulation can indeed be well fit using a piecewise log-normal + power-law PDF.
+We use a simple conceptual model in Section~\ref{sec:interpretation} to motivate the emergence of this distribution.
+
+We follow \cite{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF.
+We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element.
+This PDF is given as
+\begin{align*}
+  p(Z) = 
+  \begin{cases}
+    \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right], 
+    & Z < Z_{\rm{trans}} \\
+    % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
+    N p_o Z^{-\alpha},
+    & Z > Z_{\rm{trans}}
+\end{cases}
+\end{align*}
+where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm trans}$ is the metal fraction at the transition between the log-normal and power-law components.
+When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm trans}$ as free parameters.
+These conditions set $N$ and $p_o$ to
 \begin{equation}
-         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
+N = 
 \end{equation}
-In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution.
-We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses.
-In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
-If it does, we randomly sample from
-the adopted IMF until 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
-We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
-Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
-
-Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
-This dispersion captures some of the unresolved gas motions below the resolution limit that are smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations.
-Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
-
-Stars evolve during the simulation, by losing mass from stellar winds and SNe as described below, and by changing types, but persist throughout the entire simulation.
-For example, low mass stars are tagged as white dwarfs (WDs) at the end of their life, which may eventually explode as a Type Ia SN (discussed below), after which they persist as massless tracer particle remnants.
-Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a four-cell region at the highest level of refinement.
-This ensures that both stellar winds and SNe feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.
-
-\subsection{Stellar Properties}
-\label{sec:properties}
-Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}).
-We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$.
-Although $T_{\rm eff}$ and $g$ evolve over time for stars, modifying stellar radiative properties, following a stellar evolution track for each of our stars is beyond the scope of this work.
-We instead fix these properties at their zero age main sequence values.
-
-\subsection{Stellar Feedback and Chemical Yields}
-
-\subsubsection{Stellar Yields}
-\label{sec:yields}
-For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars.
-We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}.
-This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$.
-We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$.
-We ignore SN yields from these stars (see next paragraph).
-We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth.
-Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation.
-We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
-
-%
-% KVJ: Possibly include a discussion on uncertainties in stellar yields
-%
-
-Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe.
-Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$.
-This is a free parameter in our model; we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value.
-In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
-Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics).
-Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
-\citet{Cote2017} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
-We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
-
-There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}.
-Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
-Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass, metal, or energy ejection.
-
-Type Ia SNe are an important additional source of galactic chemical enrichment.
-These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
-We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
-We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, substantially limiting the number of Type Ia SNe occurring during the initial gigayear in our models.
-
-\subsubsection{Stellar Winds}
-\label{sec:stellar winds}
-Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
-Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback.
-We inject the feedback energy in a spherical region with a three-cell radius centered on the emitting star particle, assuming full thermalization of the wind kinetic energy.
-The total injected energy in timestep $\Delta t$ is therefore $E_w = \dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
-We use a Monte Carlo sampling method to inject mass and energy into the surrounding cells to account for partial cell overlap at the edge of the injection region that is a result of mapping a spherical injection region to cubic grid cells.
-We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
-
-Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}.
-Satisfying the Courant time step becomes prohibitively expensive following this gas, with time steps dropping to $\Delta t \sim$~100~yr.
-For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
-In our case, we fix massive stellar wind velocities to $v_w = 20$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies.
-Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work.
-These points are discussed in more detail in Sect.~\ref{sec:stellar winds discussion}.
-
-% Injecting 10$^{3}$ km s$^{-1}$ gas onto the grid at these scales leads to super heated, shocked gas at unphysical temperatures of about 10$^{8-9}$ K, particularly when injecting into very low density media.
-This can lead to painfully short time step sizes and crashes in the hydrodynamics solver.
-We adopt the common solution of artifiially reducing the wind velocity from massive stars, choosing $v_{\rm wind} = 500$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-However, this can still be problematic once the star evacuates the local ISM and injects its energy to very low density ($n \lesssim 10^{-3}$ \ccunit) gas.
-We address this issue by mass loading our winds when injection would lead to wind bubble temperatures in the spherical source region above a maximum temperature typical of wind bubble.
-This is a free parameter that we take to be 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
-Mass loading in this manner is (in effect) a sub-grid model for the unresolved ISM mixing at the boundary layer of the wind bubble, which is in fact the source of a majority of the gas mass within the wind bubble \citep{Weaver1977}.
-We take the metal species abundances of the mass loaded ISM to be the average cold / warm ISM abundance on each grid to prevent artificially inflating/deflating the overall abundances.
-We discuss our ability to resolve typical single star wind bubble properties in Appendix ~\ref{appendix:stellar winds}.
-
-%parameterized in this work with the STARBURST99 wind model, \citep{Leitherer1992}:
-%\begin{multline}
-%{\rm log} \left[ v_{\rm wind} {\rm (km~s^{-1})} \right] = 1.23 - 0.30~{\rm log}~\left[L{\rm (L_{\odot})}\right] \\
-% + 0.55~{\rm log}\left[M({\rm M_{\odot}})\right] + 0.64~{\rm log}\left[T_{\rm eff}(K)\right] \\
-% + 0.13~{\rm log}\left[Z({\rm Z_{\odot}})\right].
-%\end{multline}
-
-Stars that only undergo an AGB phase deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks.
-AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$.
-For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars as well.
-
-\subsubsection{Core Collapse SNe}
-\label{sec: core collapse}
-Stars between  $M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
-Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}).
-We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
-% AE: responding to mm3, this avoids aliasing:
-We use the same Monte Carlo sampling method as used in our stellar winds to map the spherical injection region to the grid.
-We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle.
-In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.
-
-\subsubsection{Type Ia SNe}
-\label{sec:Type Ia}
-We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as WD particles, marking a subset as Type Ia SN progenitors.
-This is the most self-consistent model for Type Ia SNe in galaxy-scale simulations.
-We note however that for the low SFRs in our isolated dwarf galaxy simulation, the first Type Ia SN only appears after a few hundred megayears of simulation time.
-By the end of the simulation presented here (500~Myr), only 18 have gone off.
-At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
-%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
-%or, 
-%\[
-%M_{\rm WD} = 
-%\begin{cases}
-%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
-%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
-%\end{cases}
-%\]
-%where $M_{\rm *}$ is the initial mass of the WD progenitor.
-We follow the common assumption that progenitor stars with initial masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017}.
-
-We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution model.
-The Type Ia SN rate is taken to be a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope $\beta$ and normalization $N_{\rm Ia}/M_{\rm SF}$ are observables.
-The latter represents the number of Type Ia SNe per mass of star formation.
-By assuming an IMF  $dN/dm$, one can write down the fraction $\eta$ of stars capable of forming a Type Ia SN progenitor that \textit{will} explode within a Hubble time.
-This is given as
+and
 \begin{equation}
-\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
-\end{equation}
-where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF, and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
-The distribution slope $\beta$ is of order unity, with typical values between 1.0 and 1.2 \citep[see][for a recent review]{Maoz2014}.
-$N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the Type Ia SN rate and integrating over a Hubble time.
-Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
-For our fiducial values, we adopt $\beta = 1.2$ \citep{Maoz2010} and $N_{\rm Ia}/M_{\rm SF} = 0.8\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013}.
-Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.
-
-Finally, we can normalize $\Psi(t)$ to give the probability per unit time $\dot{P}(t)$ that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor.
-Integrating this gives the total probability at any given time as
-\begin{equation}
-P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
-\end{equation}
-where $t_{\rm o}$ is the formation time of the WD and the leading term on the right hand side properly normalizes the total probability over a Hubble time to $\eta$.
-This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
-In practice, we invert the cumulative probability function to assign an exact time at which a given WD will explode using only a single random number draw, rather than sampling the probability distribution for each WD particle at every time step.
-
-\subsubsection{Ionizing Radiation from Discrete Sources}
-\label{sec:ionizing radiation}
-Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies.
-\ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance.
-However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds.
-Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
-As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.
-
-Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation.
-We follow HI and HeI ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
-
-We determine the HI and HeI ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
-We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star.
-Stars less massive than about 15 M$_{\odot}$ and very massive stars with sub-solar metallicity are generally not well sampled by the OSTAR2002 grid.
-In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).
-
-%AE (taking this out...
-looked into more detail in paper and they argue this, but frankly I do not see how they reach this conclusion from their Appendix plots): \citet{Dale2012} demonstrated that uncertainties on the order of a few in the ionizing radiation rates are not significant in giant molecular cloud (GMC) scale simulations.
-%Generally, the ionizing fluxes from high temperature black bodies underestimate the OSTAR2002 flux, and lower temperature black bodies overestimate the flux by a factor of 2-5 and 10-1000 respectively.
-
-Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}).
-The average energy for HI and HeI ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
-
-We also include the effects of radiation pressure on HI.
-This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}.
-We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared.
-This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}.
-However, the importance of multiple scattering is still unclear.
-Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013,Reissl2017,Wibking2018}.
-Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.
-
-\subsubsection{Diffuse  Heating}
-\label{sec:diffusive heating}
-We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the FUV (6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles.
-The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the spectral energy distributions for each gridded star.
-Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
-Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
-However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}.
-Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile.
-Only recently has the localization and time variation of these processes been considered.
-
-Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}.
-We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
-We assume HeI ionization generally follows HI.
-This allows us to approximate HeI self-shielding using the same form (A.
-Rahmati, private communication).
-We ignore HeII photoionization from the UV background entirely.
-Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
-As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
-This is described in more detail in Appendix ~\ref{appendix:cooling}.
-
-%Ignoring this effect leads to an overestimation of the cooling rates when in the self-shielding regime.
-%We refer to \citet{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \citet{Gracklemethod} for its specific implementation, as used here.
-
-We assume the galaxy is mostly optically thin to stellar FUV and use only local approximations for shielding.
-We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
-\begin{equation}
-\label{eq:PE}
-\Gamma_{\rm pe} = (1.3 \times 10^{-24} \rm{erg~s^{-1}~cm^{-3}})\, \epsilon n_{\rm H} G_{\rm eff} D 
-\end{equation}
-where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust-to-gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
-Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
-
-The value of $D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
-The extremely low dust-to-gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a ratio $D$ that scales linearly with metallicity at very low metallicity.
-At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit.
-Given that the ambient density of the ISM is generally 1--10~cm$^{-3}$, we can safely assume the FUV field to be optically thin.
-However, we do include a localized attenuation prescription that may influence high-density or metal-enriched regions of the galaxy.
-We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.
-
-Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
-This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations; none of which are followed directly in these simulations.
-Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
-%This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
-
-\subsubsection{Lyman-Werner Radiation}
-\label{sec:LW}
-In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rate.
-We compute the stellar Lyman-Werner flux again from the OSTAR2002 grid by integrating the spectral energy distributions over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}).
-Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
-We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.
-
-%
-% CR section moved to missing physics
-%
-%\subsubsection{Cosmic Rays}
-%\label{sec:cosmic rays}
-%Cosmic rays may be a signficant source of feedback within star forming galaxies, capable of driving galactic outflows.
-Recent work has shown that CR's are capable of providing a significant additional pressure support within the ISM \citep{SalemBryan2014, SalemBryanHummels, GirichidisCR, Pakmor2016}, and are capable of producing more realistic galaxy gas halos \citep{SalemBryanCorlies}.
-We include cosmic rays coupled to the hydrodynamics of our simulation using a two-fluid model with adiabatic index $\gamma = 5/3$, as described in \citep{SalemBryan2014}.
-Cosmic ray energy is injected as some fraction, $f_{\rm CR}$, of the total SN rate; we adopt $f_{\rm CR}$ with the fiducial value of 0.1.
-We include isotropic cosmic ray diffusion as described with the diffusion coefficient, $\kappa_{\rm CR} = 3.0\times10^{28}$.
-We refer the reader to \citep{SalemBryan2014} for a study of the effects different values for $f_{\rm CR}$, $\kappa_{\rm CR}$, and the CR adiabatic index has on galaxy evolution.
-
-%Recent work has examined the impact anisotropic diffusion of cosmic rays along magnetic fields has on galaxy evolution \citep{GirichidisCR, Pakmor2016} and galactic winds generated from cosmic ray feedback \citep{GirichidisCR, Simpson2016}.
-Including magnetic fields can substantially change the effect of cosmic ray feedback provided $\mu$G level, ordered magnetic fields develop within the galaxy, as is the case for more massive disk galaxies.
-However, the magnetic field properties of small, ultrafaint dwarf galaxies are poorly understood.
-These small, puffy galaxies may be completely unable to sustain ordered magnetic fields, damping the effects of anisotropic diffusion as cosmic ray diffusion through random, tangled magnetic fields is approximately isotropic.
-We do not expect anisotropic diffusion and magnetic fields to have a significant impact on the effectiveness of cosmic ray feedback for ultrafaint dwarf galaxies, but this stands to be an important area of future research.
-
-\section{Galaxy Initial Conditions}
-\label{sec:IC}
-We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy.
-The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
-Leo P is gas rich, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and low metallicity,
-with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
-Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
-
-The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential.
-The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
-\begin{equation}
-\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
-\end{equation}
-where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass.
-We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$.
-We adopt a \citet{Burkert1995} dark matter potential with $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$, $R_{\rm vir}~=~27.4$~kpc and r$_{\rm s} = 990$~pc.
-This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc.
-These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}.
-We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in future work.
-
-Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
-This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
-During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}.
-We stop the artificial driving 25~Myr after the first star particle forms.
-These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
-We note that this initial driving is somewhat ad hoc in that we do not include any other effects from the stellar population that would have caused these SNe.
-
-We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
-In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations.
-Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances.
-In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution.
-Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe.
-The subsequent metal enrichment from the stars in our simulation can be thought of as tracking
-a change in abundances from arbitrary initial conditions.
-We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.
-
-\section{Results}
-\label{sec:results}
-We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms.
-Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run.
-The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical heigh $|z| < 200$~pc relative to the center of the galaxy.
-ISM properties are calculated considering only the gas contained within the disk of the galaxy.
-We include a resolution study in Appendix \ref{appendix:resolution_study}.
-
-Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.
-All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset 66452ba.
-
-\subsection{Morphological Structure and Evolution}
-\label{sec:structure}
-
-We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
-This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
-This central region quickly fills with warm and hot gas generated from radiation feedback and SNe respectively.
-Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels.
-The ISM properties are quantified further in Section~\ref{sec:phase}.
+p_o = \frac{1}{\sigma Z_{\rm trans} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm trans}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm trans}) \right]
+\end{equation}.
+
+We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin with of 0.05 dex.
+We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{Scipy} \cite{Scipy}, stepping through possible values for $Z_{\rm trans}$, set to the centers of each of these bins.
+The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted.
+We note that the log-normal + power-law PDF produced the best fit in nearly all cases.
+
+We show in \ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
+These PDFs have been computed at an arbitrary single point in time, at 380 Myr.
+For clarity, we only show a subset of the 15 elements we follow.
+As shown, there are clear differences in the PDFs across elements of different nucleosynthetic origins and between each phases.
+However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions.
+We discuss the differences among each phase in more detail in the next section, but note here that the significance of each of these components varies notably across phases.
+In many of these cases, the piecewise log-normal + power-law distribution fits the numerical PDF quite well.
+However, there are often deviations, particularly at low metal fractions, from pure log-normal behavior.
+This manifests as either a very broad, flat PDF at low metal fraction (see N and Ba, for example), or large peaks not well described by $p(Z)$ at low metal fraction.
+In these situations, it is unclear what, if any, portion should be considered as a log-normal, or if there are multiple components within this region.
+
+We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the the metal fraction  PDFs of individual elements in galaxy models.
+The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM.
+In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions.
+Most importantly, however, the PDFs of the coldest gas phases, the CNM and molecular gas, are indeed well fit by the adopted $p(Z)$.
+As this is the source of star forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.
+%Developing a complete physical model for what drives the formation and properties of $p(Z)$ is beyond the scope of this paper, but these prospects are discussed in Section~\ref{sec:discussion}.
+
+%The log-normal distribution is a two parameter model defined by the log mean $M$ and the log standard deviation $S$.
+These values are related to the linear mean, $\mu$, and standard deviation, $\sigma$, as $\mu = e^{M+S^2/2}$ and $\sigma = e^{S^2 + 2M}(e^{S^2}-1)$.
+We define the log-normal distribution of metals in the ISM as a function of either the total metallicity $Z$ or the mass fraction of an individual metal species, $Z_i$, where $i$ denotes an individual element.
+For clarity in this section, we refer most often to total metallicity as the variable of interest.
+However, we note that any statement that applies to metallicity also applies to the mass fraction an individual metal species ($Z_i$).
+With these definitions, the log-normal metallicity PDF is given as
+%\begin{equation}
+%f(Z_i, M_i, S_i) = \frac{1}{\sqrt{2 \pi} S_i} \rm{exp}\left(\frac{-(ln(Z_i) - M_i)^2}{2S_i^2}\right).
+%\end{equation}
+%We can also specify the CDF of this distribution as 
+%\begin{equation}
+%F(Z_i, M_i, S_i) = \frac{1}{2} \left[1 + \rm{erf} \left(\frac{ln(Z_i) - M_i}{S_i \sqrt{2}} \right). \right].
+%\end{equation}
+%Thus, $F(Z_i, M_i, S_i)$ gives the fraction of mass in the ISM with metallicity $Z < Z_i$.
+For each of the 15 metal species in our simulations, and for each phase of the ISM, we compute the mass-weighted metal fraction PDFs and fit $f(Z_i,M_i,S_i)$ to each.
+In fitting, we find the parameters $M_i$ and $S_i$ for each distribution that minimizes the distance between the CDF from the simulations and the CDF from the log-normal fit, or $D_{\rm CDF}$.
+For consistency, we use equally spaced bins in log of 0.05 dex in every case.
+
+%
+% OLD TEXT - pre powerlaw
+% We give the results of this fit in Figure~\ref{fig:log-normal} for the metal fraction PDFs of each element in the ISM as a whole.
+The PDFs computed directly from the simulation are shown in the top pane.
+Their log-normal best fits, and corresponding $D_{\rm CDF}$, are shown in the bottom panel.
+For clarity, we normalize each distribution by the peak (mode).
+In all cases, the metal mass fraction PDFs can be described with a log-normal distribution.
+This is a remarkable result.
+That the complex interplay between the dominant physical processes in the ISM, namely stellar feedback, turbulence, self-gravity, heating/cooling, and chemistry, produces metal distributions that are analytically tractable is surprising.
+Linking these instantaneous PDFs to a time evolution of the distributions parameters, $M_i$ and $S_i$, in a general way would create a powerful tool for modelling galactic chemical enrichment in semi-analytic models.
+This is beyond the scope of this work, but we discuss this further in Section~\ref{sec:discussion}.
+
+% OLD TEXT ---- PRE powerlaw
+%Upon closer inspection, we note that there are distinct differences with each metal and some noticeable deviations from true log-normality.
+Most elements have higher positive skew, tails towards higher metal fractions, than can be reasonable captured by a log-normal fit.
+Two elements in particular show quite broad distributions, N and Ba, which are less well fit by a log-normal as the other elements.
+As discussed earlier, these two elements have a distinct nucleosynthetic source, AGB winds, than the rest of the elements.
+Lower energy AGB winds generate broader enrichment distributions that are less well mixed than metals from core collapse and Type Ia supernovae.
+If this behavior is similar in star forming gas, we would expect elements from AGB winds to exhibit larger scatter in observed abundances.
+However, we note again that this figure represents all gas in the ISM.
+These deviations from log-normality and the high metallicity tails could be driven simply by grouping together qualitatively distinct phases of gas in the ISM, each with their own enrichment history.
+We investigate the metal fraction PDFs of individual gas phases below.
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
-\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation.
-Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row).
-Each individual main sequence star particle is shown in the number density projections as a single black dot.}
-\label{fig:panel_x}
+\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
+\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}.
+For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
+We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.}
+\label{fig:log-normal}
 \end{figure*}
 
-The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
-This figure shows the scale height of all gas in the disk, averaged over 40~Myr periods centered on each given time.
-Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--200~pc.
-Towards the end of the simulation time, the half-light radius is $390 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
-Although the disk remains thin beyond the half-light radius, with a scale height of around 40--60~pc, it is fully resolved at all radii.
-By the end of the simulation, the majority of the gas has a scale height of $\sim$100~pc.
-
-Constraining the gas scale height in ultra-faint dwarf galaxies observationally, to compare to our simulations, is challenging.
-For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
+%\begin{figure*}
+%\centering
+%\includegraphics[width=0.95\linewidth]{lognorm_elements.png}
+%\caption{The metal mass fraction PDF's binned directly from the simulation (top) for all 15 elements tracked in the simulation and the associated log-normal fits (bottom) along with the minimized CDF distance for each.
+Given the wide range in mass fractions among species, we normalize the PDFs by their peak for clarity.
+These PDFs are shown at 350~Myr into the 500~Myr simulation; the choice of time was arbitrary.}
+%\label{fig:log-normal}
+%\end{figure*}
+
+% NOTES:
+%    Discuss how generally good of fits these are but how some are less good.
+Mention how N and Ba are less well mixed (reference above) and how this should really be examined in sub-groups of the ISM, motivating the next section.
+Next section will plot mean and std of fits and distributions as function of time for each phase, along with chi-squared good-ness of fits values.
+Need to find a way to estimate / compute the uncertainty for this!!
+Poisson in each bin?
+shift bins a little and estimate variance this way?
+
+%   Give the distributions of metals at ONE point in time in each phase for two elements, O and Ba.
+Show the log fit and the histogram on each (maybe use orange and blue?).
+Discuss how the distributions are well fit by lognormals and the evolution of each, giving values for the fits and using dashed lines showing mean/std of full distribution when not well fit by a lognormal.
+
+\subsubsection{PDF Variation Across Gas Phase}
+\label{sec:phase-pdfs}
+
+%\subsubsection{Log-normality in each Phase of the ISM}
+%\label{sec:phase-pdfs}
+The various phases represented in Figure~\ref{fig:log-normal} involve variations in density and temperature of more than six orders of magnitude.
+The evolution of each phase is qualitatively different, and the metal mixing behavior of each should vary.
+Mixing timescales over a given length scale should be related to the local sound speed; hot gas, with higher sound speeds should mix more rapidly than the dense, disconnected clumps of cold gas in the ISM.
+In addition, one would expect a metallicity gradient with gas temperature as enrichment occurs first in the hot phases, cooling and enriching denser gas over time.
+We examine the PDF variations among elements in each phase, as shown in Figure~\ref{fig:log-normal}, in more detail here.
+
+Unsurprisingly the diffuse HIM contains the most metal enriched gas, as it is comprised predominately of metal enriched supernova ejecta.
+Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
+Broadly, in colder gas the metal PDFs become less enriched with broader low metal fraction components and steeper, power-law tails.
+Although the extended power-law tail of the HIM leads to a large range of metal fractions, the HIM represents very little mass, and this tail represents recent, un-mixed enrichment.
+The comparatively narrow width in the log-normal regimes of the molecular phase and CNM is perhaps surprising.
+Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is more well mixed.
+This runs counter to the idea that mixing times should be long in colder gas unless mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.
+
+Although these trends across phases hold for all elements, there are qualitative differences between elements, particularly between those ejected predominantly by AGB winds (e.g.
+Ba and N) and those ejected by supernovae (e.g.
+O and Mg).
+In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by supernova enrichment.
+The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the molecular phase and the CNM.
+Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N produced in supernovae yields.
+Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and supernovae.
+AGB wind elements enrich the WNM and WIM directly, rather than the HIM, which would increase their mixing timescales and broaden their PDFs.
+
+%\textit{ It is unlikely that metals evolve uniformly across the large variations in density (10$^{-3}$ cm$^{-3}$ $<~n~<$ 10$^{3}$~cm$^{-3}$) and temperatures (10~K~$<~T~<$ 10$^{7}$~K) in our galaxy's ISM.
+Higher temperature gas has a higher sound speed and shorter mixing timescales than cold, dense star forming gas.
+From this, one would expect that high temperature gas is more well mixed than the disconnected dense clouds that comprise the galaxy's cold ISM.
+In addition, gas in the hot phase is generated almost entirely from HII regions and supernovae remnants and should therefore be more metal rich on average than cold gas.
+We investigate both of these expectations below.
+To simplify this discussion, we focus only on O and Ba as representative examples of elements produced predominately through supernovae explosions (core collapse or Type Ia) and elements produced in lower energy AGB winds respectively.}
+
+%The previous section demonstrated that metals are log-normally distributed within the ISM of our dwarf galaxy as a whole, but given the significant variation in densities (10$^{-3}$cm$^{-3}$~$<~n~<~10^{3}$~cm$^{-3}$) and temperatures (10~K~$<~T~<$ 10$^{7}$~K) within the ISM, we investigate how this may vary across regimes in the ISM.
+(give reference to sources which show log-normal within different temperature regimes).
+In particular, turbulent mixing and log-normal density distributions seen in local ISM simulations do depend on the temperature of the examined gas.
+Higher temperature gas has a higher sound speed and shorter mixing timescales than cold, dense star forming gas.
+This should impact the variance of each distribution.
+To simplify this discussion, we focus on two elements only, O and N, as representative examples of elements whose injection is dominated by supernovae or stellar winds, respectively.
+Conclusions reached as to the general trends for these two elements can be generalized to other elements of similar injection source.
+
+%\textit{In Figure~\ref{fig:log-normal phases} we present the numerical PDFs (top, histograms) along with their log-normal fits (bottom, curves) for O (left) and Ba (right) in each of the five phases of our dwarf galaxy's ISM.
+It is clear that each phase can be described with a different log-normal distribution, and it is the sum of these distributions that drives the deviations from log-normality in the PDFs of the galaxy's ISM as a whole in Figure~\ref{fig:log-normal}.
+In both cases, the HIM deviates the most from a log-normal, with large tails towards higher metallicities.
+In O, these tails become progressively less extreme in the colder phases, with both the CNM and molecular gas conforming well to a log-normal distribution with the least amount of variance.
+Although it is expected that the hot phases are more metal enriched than the cooler phases, it is surprising that the cold, dense gas is more well-mixed than the hot phases.
+We discuss the implications of this result further in Section~\ref{sec:statistics}.
+In contrast with O, the PDFs in Ba appear to universally be less well described by a log-normal in all phases, with less distinct enrichment between the phases.
+Although the cold phases here are still less enriched than the hot phases, each still exhibits longer tails towards high metal fractions that are the source of the deviations from log-normal.
+The differences in the PDFs across elements from supernovae explosions and AGB winds indicates that these species diffuse and mix differently throughout the ISM.
+Again, AGB produced metals should show larger abundance variations observationally than those produced in supernovae.
+}
+
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.95\linewidth]{lognorm_O_Ba_phases}
+%\caption{The metal mass fraction PDFs computed directly from the simulation (top) for O (left) and Ba (right) in each of the five phases of our galaxy's ISM at the same time as shown in Figure~\ref{fig:log-normal}.
+The log-normal best fits to each of these phases are given in the bottom row.}
+%\label{fig:log-normal phases}
+%\end{figure}
+
+\subsubsection{The Time Evolution of Metal PDFs}
+\label{sec:statistics}
+We focus on the time evolution of the full numerical PDFs in this section so that our results here do not depend upon the choice of functional form for $p(Z)$.
+Figure~\ref{fig:phase-statistics} shows the evolution of three different statistics for the O (top) and Ba (bottom) PDFs.
+These two elements are treated as representative elements for supernova and AGB wind production respectively.
+The difference between the mean and median masses of the PDF is a measure of the skew of the PDF.
+Higher values indicate that metals are preferentially sequestered in metal-rich gas, and are less well mixed throughout the given phase.
+The skew is always positive in these distributions.
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
-\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on views.}
-\label{fig:panel_z}
+\includegraphics[width=0.95\linewidth]{oxygen_barium_phases_CDF_evolution.png}
+\caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation.
+The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
+\label{fig:phase-statistics}
 \end{figure*}
 
-Interestingly, there is significant structure well above the gas disk in our model, in the form of dense clouds and filamentary features, as seen in the edge-on projections.
-These cold gas clumps appear to have typical sizes on order of $\sim 10$~pc, but with lower density tails that can extend up to 100 pc.
-These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy.
-These clumps have typical velocities on order of a few to tens of kilometers per second, and appear to survive for 10--100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk.
-The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work.
-% AE (left out): This is exciting given recent \citep[e.g.][]{Zheng2017} and ongoing \citep{Zheng2017HST} observational observational work examining the disk-halo interface in nearby galaxies.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.975\linewidth]{scale_height}
-\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figures~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
-\label{fig:scale_height}
-\end{figure}
-
-\subsection{Star Formation Rate and Mass Evolution}
-\label{sec:sfr}
-
-We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between 2--4$ \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly at this level for 100 Myr, and then drops to an average of about $4 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations.
-By the end of the simulation, the SFR is very low and star formation events are infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$.
-The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation.
-Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 9.93 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$.
-We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.
-
-We note that the granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
-Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
-For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$.
-Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense.
-Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.
-
-At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $5.8 \times 10^5$ M$_{\odot}$, or roughly 16\%, of the total gas mass in the galaxy's disk.
-The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\%; at this point, it is about equal with the HI gas.
-This is because the total amount of gas in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained.
-Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback.
-Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
-The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
+For O, the median mass fraction is ordered by phase temperature.
+The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 2.5 dex, fluctuating by $\sim$ 1 dex over the simulation time.
+The frequent large skew in the HIM (see middle panel) and spread in the HIM (right panel), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
+%This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events. 
+Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread; the two coldest phases, the CNM and molecular gas, have similar spread throughout the evolution, but a continuous $\sim$0.2 dex offset in median metal fraction.
+The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star forming gas.
+This is the only explanation for how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (middle and right panels).
+Individual enrichment events will have significantly higher metallicities than the ambient ISM in any phase, and will drive an increase in the difference between the mean and median of the PDF.
+These can be seen as the obvious spikes in the HIM and WIM.
+For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.
+
+% In each phase, enrichment events will tend to drive larger differences between mean and median mass fraction,
+
+Although these trends are generally true for Ba, its evolution is much more complicated.
+%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability. 
+Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of over 1 dex in the CNM and over 2 dex in the WNM and WIM.
+The HIM is seemingly unaffected by this trend, and generally decreases in spread and skew over time.
+Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in supernovae.
+The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
+These tails represent the most recently enriched gas, and is clearly much more locally confined than O.
+
+%{\bf (move to discussion?)}: 
+The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e.
+the ratio between the total mass of metals and the total mass).
+Assuming star forming gas follows the same properties as the molecular gas, this distinction is small ($\sim$ 0.2 dex), but significant, for elements released during SNe explosions, and can be very significant, up to $\sim$ 0.8 dex, for elements released in AGB winds.
+Chemical evolution models, especially one-zone models, follow the mean metal fraction, not median.
+These results indicate that these models are biased to overestimate gas and stellar elemental abundances.
+. % However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.
+
+To summarize, this figure demonstrates: 1) there are qualitative differences in how supernova injected elements (e.g.
+O, Mg) and AGB wind injected elements (e.g.
+N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value.
+In the case of supernova injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
+For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.
+
+\section{Discussion}
+\label{sec:discussion}
+We begin with a simple toy model that motivates the power-law tail at high metal fractions of the metal fraction PDFs and a subsequent turnover at low metal fractions in Section~\ref{sec:interpretation}.
+This work is placed in context with previous works focusing on metal mixing in the ISM in Section~\ref{sec:context}.
+Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impact of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
+
+\subsection{Physical Interpretation of the PDF}
+\label{sec:interpretation}
+Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_o = 0$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$.
+Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas.
+In this case, $p(Z)$ takes the form of a double-delta function
+\begin{equation}
+p(Z) = \delta(Z) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
+\end{equation}
+If the enriched material mixes continually with the primordial gas at a constant rate, after some time this gas will have mixed with an equal amount of primordial gas.
+At this point, the high metal fraction delta term becomes $\frac{2M_{\rm ej}}{M_o} \delta(Z - \frac{1}{2}Z_{\rm ej})$.
+This implies an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas, and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$.
+If the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, $p(Z)$ will become a power-law in $Z$, truncated at some time dependent minimum $Z$.
+The slope of the power-law is determined by the rate of injection versus mixing with the ambient medium.
+A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium.
+Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than enrichment.
+If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.
+
+In reality, however, $M_o$ is not an inexhaustible reservoir of primordial gas.
+Eventually the entire ambient medium will become enriched to some $Z > Z_o$, and $p(Z)$ will consist entirely of a continuous, truncated power-law.
+As enrichment proceeds, gas near the low metallicity truncation of $p(Z)$, which still comprises much of the mass of the system, enriches towards higher metallicities in the power-law tail.
+This will produce a turnover at the low $Z$ limit of $p(Z)$.
+The low-turnover limit is produced by diffusion from many different sources, and is thus an additive process, which, as we noted above, tends to produce log-normal distributions.
+The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.
+
+This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases.
+The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions.
+Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low-metallicities.
+Molecular gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.
+
+%
+%
+%
+%Although this model is useful to explain these very general features, it is certainly incomplete in practice.
+Enrichment proceeds irregularly through the mulit-phase ISM with a variety of ejection masses and metallicities.
+Phases are not independent, and the hot phase cools and enriches cooler phases in the ISM, distorting $p(Z)$ within each phase.
+Cold gas is heated up and destroyed through feedback, changing the content of the low-metallicity end of the warm and hot phases.
+Finally, gas is removed from the galaxy through feedback driven winds that preferentially remove metal enriched gas.
+Each of these processes has a non-trivial effect on the evolution of the PDF that will cause deviations from the simple toy model outlined here.
+Determining the exact physical processes that drive and set the properties of each PDF is the subject of ongoing work.
+
+%
+% A.E. paragraph may need work
+%
+Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}.
+Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
+This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in molecular gas ($\sim$ 1 km s$^{-1}$).
+Our results show, however, that in general the WIM and HIM are the least well mixed, while molecular and CNM gas is the most well mixed across the galaxy.
+This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
+It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing supernovae.
+Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into molecular gas.
+Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy.
+The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.
+
+\subsection{Context}
+\label{sec:context}
+That metal fraction distributions can be described using a simple analytic log-normal + power-law PDFs, even in a complex, multi-phase ISM, has not been demonstrated prior to this work.
+In addition, this is the first work to demonstrate differential mixing behavior of individual metal species using 3D hydrodynamics simulations.
+However, there does exist a significant body of work investigating the mixing behavior of passive scalars in a variety of contexts, as discussed below.
+\cite{KrumholzTing2018} predict differential behavior for AGB wind and core collapse supernova synthesized elements as a direct consequence of the differences in size of typical planetary nebulae ($\sim$ 0.1~pc) and supernova remnants ($\sim$ 100~pc).
+%We discuss our results further in the context of previous research on metal mixing in the ISM and speculate on the physical processes that drive the evolution of these PDFs across phases.
+
+Previous work on the evolution of metals in the ISM varies from studies concerning the advection of passive scalars in idealized turbulent boxes \citep[e.g.][]{Pope1991, PanScannapieco2010, PanScannapiecoScalo2012, PanScannapiecoScalo2013, YangKrumholz2012, SurPanScannapieco2014, Colbrook2017}
+% cite passive scalar reviews by Warhaft 2000 in fluid mech and scalo + Elmegreen 2004?
+to global galaxy models studying generalized advection and mixing of passive scalars \citep[e.g.][]{deAvillez2002,Petit2015,Goldbaum2016} to models with more detailed self-consistent metal enrichment \citep[e.g.][]{Revaz2009,Escala2018}.
+% summarize conclusions from these works:
+
+The evolution of metallicity PDFs has been investigated previously in some of these works \citep[see ][ and references therein]{PanScannapiecoScalo2012,PanScannapiecoScalo2013}, with effort towards developing closure models to describe the evolution of the PDFs of passive scalars in turbulent media \citep[e.g.][]{EswaranPope1988,Chen1989,Pope1991}.
+The astrophysical context in much of this work was enrichment from the first stars, so the focus was on the low-metallicity tail of the PDF and the timescales over which gas is polluted \citep[e.g.][]{PanScannapiecoScalo2013,Sarmento2017}.
+These works often use isothermal turbulent-box simulations initialized with a double-delta function PDF of pristine gas and enriched gas in some varying spatial distribution, ignoring ongoing enrichment.
+Initial PDFs of this form were demonstrated some time ago to evolve into a Gaussian distribution at late times \citep{EswaranPope1988}, but it is unclear if these could also be described with a log-normal distribution.
+However, these works uniformly do not contain the high metallicity power-law tails shown in our work.
+As suggested by our toy model in Section~\ref{sec:interpretation}, this is due to the lack of ongoing enrichment in these studies.
+More detailed models of global galaxy evolution have generally focused on spatial correlations and mixing timescales of initially asymmetric fields, without concern for ongoing enrichment \citep[e.g.][]{deAvillez2002,Petit2015} or focused primarily on the evolution of stellar abundance patterns and metallicity distribution functions \citep[e.g][need more]{Jeon2017,Hirai2017,Escala2018}, without directly examining the evolution of gas-phase metallicity PDFs.
+
+%
+% MM: remove from this section:
+%This is the first work examining the gas-phase properties of metallicity PDFs in a global galaxy simulation with a detailed model for stellar feedback, chemical enrichment, and a multi-phase ISM.
+Since we are far from a complete understanding of galactic chemical evolution, investigating the physics behind what sets the statistical properties of these PDFs, particularly what drives the differences across metal species and phases, is important.
+Although this is beyond the scope of this current work, we use scaling arguments to speculate on the meaning of these results.
+%Metal mixing in the ISM is a diffusive process driven by turbulence.
+
+% Recent works investigating dwarf galaxy chemical enrichment with Lagrangian simulations have shown that the sub-grid diffusion models required to reproduce observed dwarf galaxy abundance properties imply fairly rapid mixing timescales \citep{Escala2018,Hirai2017}.
+In contrast to this work, \cite{Escala2018} finds dwarf galaxy
+%The sub-grid diffusion models in Langrangian simulations of dwarf galaxy chemical enrichment that match the abundance properties of observed dwarf galaxies imply rapid mixing timescales
+
+%
+%
+%  Recent works specifically examining metal mixing in dwarf galaxies. Saving for potential future discussion:
+% \cite{Hirai2017} uses constrains the diffusion parameter in their SPH simulations comparing their simulated dwarf galaxies to observations in [Mg/Fe] vs.
+[Fe/H] and [Ba/Fe] vs.
+[Fe/H] space.
+Suggests Ba/Fe is more powerful constraint and briefly discusses potential differences in mixing between elements but does not do work with this
+% \cite{Jeon2017} 
+% \cite{Escala2018} tests of role of metal diffusion models in producing realistic MDFs in dwarf galaxies. Able to reproduce things like MDF width and [alpha/Fe]vs[Fe/H] scatter.
+
+% The properties of log-normal density PDFs in isothermal simulations are governed by the statistical properties of turbulence (refs) and the relative importance of compressive and solenoidal driving.
+However, the density PDFs in simulations of global galaxies with a resolved, multiphase ISM show significant departures from log-normallity \citep[see][]{Hopkins2013} but are still approximately log-normal within individual phases of the ISM \citep{HopkinsQuataertMurray2012}.
+The properties of the density PDF in multiphase simulations have not been well studied which offers little insight into what sets the mass fraction PDFs for each element.
+We speculate on this here to motivate future study, but note that a detailed characterization is beyond the scope of this work.
+
+% The log-normal density PDFs found in ISM simulations have a variance that is proportional to the mach number \citep[e.g.][(maybe more)]{PNJ1997, Passot1998, Fedderath2008, LemasterStone2009}.
+In our simulations, however,
+
+%We discuss possible caveats to this in Section~\ref{sec:caveats}.
+Does this extend to more massive?
+how does DM potential affect this?
+Are general trends still true in much larger galaxies?
+or are things very different once HIM crossing times are more like 100 Myr (aka MW size galaxies).
+
+\subsection{Timescale Dependence of AGB Ejecta}
+\label{sec:discussion:metal yields}
+We can generally say that metals produced in AGB winds evolve qualitatively differently in dwarf galaxies than metals produced through supernovae.
+However, exactly which metals exhibit these differences, and to what degree, is timescale and metallicity dependent.
+Short-timescales ($\lesssim 100$~Myr) only samples enrichment from the most massive AGB stars, which stars on order of a few solar masses enrich on 1 Gyr timescales or longer.
+In our simulations, which only sample 500 Myr of evolution, N and Ba are dominated from AGB wind ejecta.
+C is commonly used to track AGB wind enrichment, but as it originates from lower mass AGB stars, C enrichment operates on $\sim$ Gyr timescales, longer than we follow in this work.
+This additionally varies with metallicity.
+Sr, for example, is only significantly ejected through AGB winds at our metallicity on $\sim$~Gyr timescales; stellar winds from more massive stars dominate the production of Sr on shorter timescales.
+At higher metallicity, much more Sr is produced through massive AGB stars, decreasing the timescale over which Sr should exhibit a differential chemical evolution as compared to supernovae ejected elements.
+
+To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected through AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times.
+This model was run using \textsc{SYGMA} \citep{Ritter2017}.
+As shown, metal enrichment from AGB winds only begins to dominate for a given species at $\sim$ 100 Myr.
+This includes N and Ba, as followed in our simulations, but this plot indicates that Li should show the strongest differences with respect to metal ejected through supernovae, even on relatively short ($< 100~$~Myr) timescales.
+It takes over a Gyr for C to be dominated from AGB wind ejecta, which is the case for many of the elements shown.
+F, which shows very little contribution from AGB winds at short timescales is dominated by enrichment on longer timescales.
+These dependences on metallicity and timescales certainly adds complications in generalizing our work and in interpreting observations in the context of the results presented here, but these difference could be leveraged to better understand galactic chemical evolution on multiple, distinct timescales.
+Clearly this motivates future work covering Gyr timescales to fully understand how metal mass fraction PDFs evolve with time.
 
@@
 \centering
-\includegraphics[width=0.475\linewidth]{sfr_snrx100}
-\includegraphics[width=0.475\linewidth]{mass_evolution}
-\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins (left).
-Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.
-Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.}
-\label{fig:sfr_mass_evolution}
+\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0.png}
+\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, with no continual star formation.
+We only show a sample of some of the elements dominated most by AGB enrichment.
+The horizontal line marks 50\% contribution.}
+\label{fig:agb evolution}
 \end{figure*}
 
-\subsection{ISM Properties}
-\label{sec:phase}
-
-Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
-We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
-We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content as decoupled from the rest of the gas.
-See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-Each of these phases exist throughout our simulation, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
-Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.
-
-Figure~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
-One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
-Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
-We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
-The boxed regime in the lower right corner shows our star formation density and temperature threshold.
-Gas in this regime is rapidly consumed by star formation and subsequent feedback.
-Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does show up in this time average.
-We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work.
-
-\begin{figure}
+%\begin{figure*}
 %\centering
-\includegraphics[width=0.95\linewidth]{phase_diagram.png}
-\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gass interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr.
-The two red dashed lines show lines of constant pressure for guidance.
-The region in the lower right corner indicates our density and temperature thresholds for star formation.}
-\label{fig:phase}
-\end{figure}
-
-The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
-After this point, the molecular component becomes equally or even somewhat more important through the end of the simulation.
-Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining mass dominated by the WNM.
-While the CNM has a negligible volume fraction, the WNM, WIM, and HIM each occupy roughly the same volume fraction.
-However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy.
-Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-
-These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
-They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (ionized and neutral), with cold gas having $\sim$ 10\% of the mass, and occupying negligible volume, and hot gas occupying $\sim$ 10\% of the volume, but having negligible mass.
-Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few.
-The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
-We have compared our cooling curves to those used in \citep{Hu2017} (C.
-Hu, private communication) and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.
-
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
-\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
-\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM.}
-\label{fig:ISM_evolution}
-\end{figure*}
-
-\subsection{Interstellar Radiation Field}
-\label{sec:ISRF}
-
-The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}.
-This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
-In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 50 Myr from 300--350~Myr.
-The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
-The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.
-Interestingly, the averaged profile appears nearly flat for most of the disk, with an increase at higher radii due to more recently formed stars.
-However, the ISRF varies significantly over time, fluctuating by an order of magnitude or more at any given radius.
-
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{G_o_profile} \\
-\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
-\caption{
-Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr.
-Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc.
-The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
-The bottom panel gives the HI ionizing stellar radiation flux.
-Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point.
-For this reason we only shade between the first quartile and maximum values.
-HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.}
-\label{fig:ISRF}
-\end{figure}
-
-The bottom panel gives the ionizing photon fluxes for HI from stellar radiation {\em only}.
-Since this field is tracked directly using ray-tracing radiative transfer, the profile encodes information about local attenuation of these photons from dense, neutral gas.
-This is the main driver of the differences between this field and $G_{\rm o}$.
-However, both profiles track each other well as a function of radius.
-The lack of dramatic trend with radius in both diagrams suggests that one could model the ISRF in low mass dwarf galaxies using a uniform heating / ionization rate; however, this would still fail to capture the fact that any given region of the galaxy will experience order of magnitude or more fluctuations in the incident flux.
-
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
-\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
-\caption{Single-snapshot 2D radial profile plots at 200~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
-Here, we include all gas within the mid-plane of our dwarf galaxy.
-Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
-This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
-\label{fig:ISRF_2D}
-\end{figure*}
-
-To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr.
-This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
-The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
-From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
-Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation.
-In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency.
-It remains to be seen which of these two modes of feedback is more important in regulating star formation.
-
-\subsection{Outflow Properties}
-\label{sec:outflows}
-
-The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}.
-However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
-In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
-We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
-\begin{equation} \label{eq:dotM}
-\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
-\end{equation} 
-We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.
-
-The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
-Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
-For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor.
-The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time.
-This quickly declines towards larger radii, however, with minimal outflow past the virial radius.
-\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift.
-Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below their typical values.
-
-Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
-Using a fit provided in \citet{Muratov2015} to extrapolate and compare $\eta$ at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
-These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
-We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly have much smaller mass loading factors at 0.25 $R_{\rm vir}$.
-
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{total_mass_outflow}
-\includegraphics[width=0.45\linewidth]{total_mass_loading}
-%\includegraphics[width=0.33\linewidth]{metal_mass_loading}
-\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
-\label{fig:mass_outflow}
-\end{figure*}
-
-Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
-In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
-Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{-1}$ or below.
-This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities.
-The distribution has a very long tail out to and beyond 500~km~s$^{-1}$.
-The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
-However, as shown, the HIM comprises very little of the outflow by mass.
-Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM.
-Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
-The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
-
-\begin{figure}
-%\centering
-\includegraphics[width=0.95\linewidth]{outflow_velocity_distribution}
-\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-The outflowing material is multiphase, broken into WNM, WIM, and HIM.
-See Section~\ref{sec:phase} for definitions of these regimes.
-We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K.
-There is little to no outflowing mass in the CNM or molecular phases.}
-\label{fig:outflow_velocity}
-\end{figure}
-
-%\textbf{AE: Took plot and discussion of outflow metallicities out and replaced with metal mass loading factor (below)}
-%In Figure~\ref{fig:outflow_metallicity} we show the average ISM metallicity (black), halo metallicity (blue), and outflow metallicities (orange) at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
-The ISM metallicity evolves minimally from the initial conditions in this time, while the halo and outflow properties change significantly.
-It is apparent from this figure that the outflows are preferentially metal enriched, as the halo increases in metallicity by a factor of $\sim 2$ in the simulation time.
-Although most of the gas mass in the halo (outside the disk) remains within 0.2 $R_{\rm vir}$ (see Section~\ref{sec:obs_metals}), the mass that does make it to the outer reaches of the halo or beyond is metal enriched by a factor of $\sim$5--6 compared to the ISM.
-This is in contrast with the results from \citet{Muratov2017}, which generally show $Z_{\rm outflow} \simeq Z_{\rm ISM}$ at $0.25~R_{\rm vir}$ and $Z_{\rm outflow} < Z_{\rm ISM}$ at $1.0~R_{\rm vir}$, though both with some scatter that reaches $Z_{\rm outflow} > Z_{\rm ISM}$, especially at high redshift.
-However, we note that our simulations certainly do not contain a cosmologically realistic circumgalactic medium, nor do they include ongoing cosmological accretion of pristine gas.
-Mixing of outflowing, metal enriched gas and pristine inflows will lower the typical halo and outflow metallicities, particularly at large radii.
-
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.95\linewidth]{metallicity_evolution}
-%\caption{The mass-weighted average metallicity of our dwarf galaxy's ISM, halo, and outflowing gas at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
-The halo is defined as the region outside of the disk, yet inside the virial radius.}
-%\label{fig:outflow_metallicity}
-%\end{figure}
-
-\subsection{Metal Evolution} 
-\label{sec:chemical evolution}
-
-\subsubsection{Metal Enriched Outflows}
-Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
-This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
-In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}.
-The parameter used to quantify metal outflow efficiencies varies among works.
-Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
-\begin{equation} \label{eq:eta-metal}
-\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
-\end{equation}
-where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions.
-For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but it increases at each radius, fluctuating around unity for the second half of the simulation.
-Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}.
-\cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
-Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.
-
-\begin{figure}
-%\centering
-\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
-\includegraphics[width=0.9\linewidth]{metal_fraction_evolution}
-\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Figure~\ref{fig:mass_outflow}.
-This is the ratio between the metal outflow rate and the metal production rate.
-{\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
-In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
-\label{fig:metal_evolution}
-\end{figure}
-
-These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
-This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
-After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
-This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy.
-It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, reaching 40\% by the end of the simulation.
-Likewise, the CGM metal content continually decreases until the end of the simulation, from loss through the virial radius of the halo.
-Although the metal content of the ISM gradually decreases throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution.
-See Section~\ref{sec:obs_metals} for further discussion.
-
-\subsubsection{Differential Mixing of Elements Within the ISM}
-It is important to understand how metals from each source of stellar yields enrich the ISM.
-Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}.
-This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed.
-Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Avillez2002,Tassis2008,YangKrumholz2012}.
-It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
-It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.
-
-%We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
-The top two panels give the slices of number density (top left) and temperature (top right) in the mid-plane of a portion of our dwarf galaxy.
-These serve to guide the eye in the lower panels, clearly indicating regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
-The bottom panels give abundance ratios for oxygen and hydrogen (bottom left), nitrogen and hydrogen (bottom middle), and nitrogen and oxygen (bottom right).
-
-We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
-The left panel gives the abundance ratio of N to O throughout the ISM.
-The right
-two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy.
-These show regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K) connected by cold filaments, warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
-
-\begin{figure*}
-\includegraphics[width=0.98\linewidth]{log_NO_panel}
-            \caption{Three slices in the mid-plane of our dwarf galaxy at an arbitrary time of 350~Myr after the start of star formation showing the variation in gas phase metal abundances.
-The left slice gives the ratio of the abundance between N and O, while the number density and temperature are shown on the right.
-}
-\label{fig:metal_slices}
-\end{figure*}
-
-%The CNM consists of cold filaments that connect dense clumps of molecular gas that are readily visible in both diagrams.
-Distinguishing the WNM and WIM is difficult, but the lower density regions between the cold filaments are dominated by these phases.
-Gas from a recent SN explosion is clearly visible as the hot (T~$\gtrsim 10^{6}$~K), diffuse region in the top left corner.
-As shown in the left panel, log(N/O) varies significantly over this section of the ISM with notable differences across the various phases and ISM structures.
-As expected, O is overabundant throughout the ISM, most strongly in the region of recent SN enrichment (top left, dark purple region in log(N/O) / dark red in temperature).
-However, the relative abundance of N increases significantly in the warmer phases, reaching equipartition (white color in log(N/O)) in many patches throughout the ISM.
-There are three regions in particular that are overabundant in N (green color).
-
-At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars.
-Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
-Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
-The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
-This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
-A more detailed analysis is beyond the scope of this work, but we plan to investigate this point, and potential observational consequences for stellar abundances, in future work.
-% reference my other paper if it is ready-ish by the time I submit this one.
-
-%Observations of Local Group dwarf galaxies have shown that they retain very little of the total amount of metals they are expected to have produced, given their star formation histories (see Section~\ref{sec:observation}).
-In Figure~\ref{fig:species_fractions} we show the fraction of metals retained within the disk or expelled into the halo of our galaxy over time, along with a breakdown of the locations of each metal species by the end of the simulation.
-As shown in the top panel, a majority of each metal tracer species is found outside the disk of the galaxy, in the galaxy halo.
-In total, \textbf{85\%} of the tracer metal species produced lie outside of the disk of our galaxy.
-Interestingly, the exact fraction is not uniform across metal species.
-
-%\textbf{Use Ba here as example element, not N}
-%Most notably, N is preferentially retained by the galaxy over the other species.
-Roughly \textbf{35\%} of N produced remains in the disk, as compared to \textbf{15\%} of O or Fe, for example.
-This difference is entirely feedback driven.
-At this metallicity, N is produced only in the stellar winds of stars between 8 and 10 M$_{\odot}$, with little to no production in SNe.
-The rest of the species either have very little stellar wind production, are produced solely in SNe, or have similar production levels between both SNe and stellar winds (like O, for example).
-The typically lower injection energies of N into the galaxy compared to the SNe produced elements means N is preferentially retained within the ISM, and not as effectively ejected through outflows.
-In truth, the stars that produce N do eventually explode as SNe, sweeping up some fraction of the wind produced N into outflows.
-However, clearly some of this N mixes more effectively within the ISM than the other metal species.
-How abundance variations like this evolve over longer timescales and with varying feedback physics is the subject of ongoing work.
-% AE: possibly cite letter here if we have it done
-
-%\begin{figure*}
-%\includegraphics[width=0.9\linewidth]{species_bar.png}\\
-%\includegraphics[width=0.9\linewidth]{species_bar_disk.png}
-%\caption{The fraction of each species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).}
-%\label{fig:species_fractions}
+%\includegraphics[width=0.95\linewidth]{C_N_evolution.png}
+%\caption{The fractional contribution of AGB winds to the total yields of C and N as a function of time for a simple stellar population at three different metallicities.
+Since the nucleosynthetic source governs the mixing dynamics of a given metal, this plot illustrates how this can change with both time and metallicity for a given species.
+These models were generated using \textsc{SYGMA} \citep{Ritter2017-sygma}}
+%\label{fig:agb evolution}
 %\end{figure*}
 
-%The bottom panel illustrates where these metals are partitioned within the ISM of the galaxy at the end of the simulation time.
-The CNM contains roughly 50-60\% of each species, with the CNM and WNM together accounting for most of the metals in the galaxy.
-The WIM contains only $\sim$ 10\% of each species, with the HIM containing very little.
-This may be counterintuitive given that most metals are initially injected into the galaxy in either the WIM or HIM phases.
-However, the disk metals represent only a small fraction of the total metals produced.
-Much of the metals are effectively removed from the disk into the halo (see Section~\ref{sec:outflows}).
-It is apparent that the remaining metals quickly mix or cool into denser gas phases.
-
-%\subsection{Stellar Abundances}
-%\label{sec:stellar properties}
-
-% By initializing the metallicity of our galaxy to a non-zero value (XXX), yet setting each of the metal tracer species to initial mass fractions of 10$^{-20}$ (effectively zero abundance), the species abundances in our galaxy are somewhat contrived.
-However, this was done to be able to unambiguously follow how self-consistently produced chemical enrichment evolves over time.
-In effect, what each individual metal field traces is a ``delta'' abundance, or change in metal mass fraction relative to an arbitrary initial condition.
-
-%\textbf{This section needs work.
-As per discussion with Keith and Kathryn, displaying abundance evolution like this is confusing and misleading.
-Switch to discussion of mass / abundance fraction evolution of individual specie(s).}
-%We plot the $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ ratio for all star particles in our simulation that are ``alive'' in Figure~\ref{fig:stellar_abundance}.
-This represents stars that have not gone SNe or have otherwise formed a compact object.
-Here, $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$, and the notation [X/Y] denotes the ratio of the abundance of species X over Y, relative to the solar value, or log([X/Y]) = log(X/Y) - log(X$_{\odot}$/Y$_{\odot}$).
-All stars are colored by their age.
-
-%\begin{figure}
-%\includegraphics[width=0.95\linewidth]{alpha_over_fe_hist}
-%\caption{The $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$
-%diagram for all stars in our simulation, colored by their age. Here, we define $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$. Each histogram shows counts, normalized to the peak in each distribution.}
-%\label{fig:stellar_abundance}
-%\end{figure}
-
-%As expected, there is a noticeable trend of stellar age with [Fe/H]; especially in our case as the overall iron abundance is gradually increasing, yet we do not have any accretion of primordial material.
-Interestingly, the few stars with the highest [Fe/H], between -3 and -2, are not the most recently formed; the most recent star formation is clustered around [Fe/H] between -3 and -4.
-
-%We note the ``knee'' like feature at very low [Fe/H] is not the characteristic knee seen in $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ space, corresponding to the period when iron enrichment from SN Type Ia begins to make a significant contribution to the galactic chemical evolution.
-This generally occurs after roughly 1 Gyr of stellar evolution, far longer than the \textbf{170} Myr simulated here.
-% The origin of this feature and the longer term chemical evolution of this galaxy will be investigated in a future work.
-
-\section{Discussion}
-\label{sec:discussion}
-
-\subsection{Comparison to Observed Low Mass Dwarf Galaxies}
-\label{sec:observation}
-
-As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs.
-Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of $z = 0$ dwarf galaxies.
-However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies.
-We show that these properties are broadly consistent with observations.
-
-\subsubsection{Gas and Star Formation}
-\label{sec:gas_sf}
-
-The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}.
-However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
-In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.
-
-Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
-We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}.
-We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the area of the disk within the radius of the outermost star formed within the previous 10 Myr.
-Likewise, $\Sigma_{\rm gas} = M_{\rm gas,10} / A_{*,10}$, where M$_{\rm gas,10}$ is the total gas mass within this defined disk.
-However, the total gas content cannot be determined observationally.
-To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He.
-We note that there is generally no correction made for any possible H$_{\rm 2}$ or \ion{H}{2} content.
-As shown in Section~\ref{sec:molecular gas content}, these components may be significant.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
-\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution.png}
-\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
-See text for details of the calculation.
-Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars.
-On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}.
-There is no clear correlation with time in this diagram.} %something is breaking here in compiling
-\label{fig:KS}
-\end{figure*}
-
-We include recent observational constraints on these relationships in Figure ~\ref{fig:KS}.
-Our galaxy fluctuates significantly about both relationships with no clear trends in time.
-However, in both cases, it is consistent with the available observational sample.
-At times our galaxy exhibits gas surface densities below the observational constraints.
-The trend is still consistent with higher densities at this point, but with a larger scatter towards lower star formation rate densities and efficiencies.
-
-In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
-It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
-This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
-
-\subsubsection{Molecular Gas Content}
-\label{sec:molecular gas content}
-
-The molecular gas content of low-mass dwarf galaxies is generally assumed
-to be small, but is not well constrained by either theory or observations.
-Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
-As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.17--0.20, within this range, but significantly exceeding the few percent often found in models.
-Ignoring the H$_2$ component of our galaxies would lead to an average shift of 0.24 dex to the right in the Kennicutt-Schmidt law, and 0.24 dex right and down in the extended Schmidt law.
-This does not result in a significant disagreement with the observed relationships, but would constitute a quantitative change to the observed fits if our $f_{\rm H_2}$ is robust for observed low-mass, low-metallicity dwarf galaxies.
-
-Interestingly, in this low-dust regime, our H$_2$ formation is dominated by the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
-In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
-Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionization of H and H from the UV background.
-This has the seemingly counterintuitive effect that turning off the UV background actually decreases the formation rate of H$_2$, as confirmed in test simulations.
-In a test simulation ignoring all H$^{-}$ reactions, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.
-Although we ignore the visible component of our ISRF, capable of destroying H$^{-}$, this is included from the UV background.
-
-This explains our disagreement with the simulations in \citet{Hu2016} and \citet{Hu2017}, which find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
-Although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
-Our model suggests that H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies.
-It is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, but the total amount of H$_2$ formed is perhaps surprising.
-However, the rate coefficients associated with gas-phase H$_2$ formation are uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
-Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
-It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
-This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
-
-\subsubsection{Metal Retention}
-\label{sec:obs_metals}
-
-The simulations presented here have not yet been run for the gigayear timescales required to begin to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$.
-However, we can compare to a key observable: the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from closed box stellar evolution models given the galaxy's star formation history.
-This can be done readily with Milky Way dSph's.
-Their stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
-However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
-
-Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich,
-star forming, low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
-Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
-However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
-Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
-%We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.
-
-It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium.
-While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
-We find 13.7\% of all metals lie within 1 kpc of the center of our galaxy, 26.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 38.6\% outside $R_{\rm vir}$.
-This is consistent with previous works, but this is again an evolving quantity.
-In addition, the amount of gas that escapes the virial radius is certainly sensitive to the details of gas accretion from the IGM on this galaxy, which we cannot capture in this model.
-
-The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
-Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return.
-In addition, the accretion of pristine gas from the intergalactic medium could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals.
-This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.
-
-\subsection{Missing Physics}
-Although we include many detailed physical models in our simulations, there remain additional physical processes that may be relevant, which we now discuss.
-
-\subsubsection{Massive Stellar Wind Energy}
-\label{sec:stellar winds discussion}
-Our massive stellar wind model drastically reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$.
-Although our algorithm is entirely capable of generating realistic stellar winds with velocities comparable to those observed, such fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
-When considered in isolation, stellar winds are an important source of pre-SN feedback and can dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
-However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}, unless densities near the ionizing source are high enough to trap the  \ion{H}{2} region in the source cell.
-In that case, they can clear out a cavity to allow initial establishment of the \ion{H}{2} region.
-
-They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
-Although they likely have minimal dynamical importance at resolutions where peak densities are not anyway high enough to trap ionization fronts, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting closer examination in future work.
-
-%\subsubsection{Magnetic Fields}
-%\label{sec:magnetic fields}
-
-\subsubsection{Cosmic Rays} 
-%mm2 and Magnetic Fields}  One could make the case that we should have a separate discussion of magnetic fields.  However, this section is only about CRs.
-
-Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}.
-These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}.
-Modeling cosmic rays is challenging, however, as they encompass a wide range of energies, and there are significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
-Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy.
-In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM.
-Modeling cosmic ray feedback completely thus requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena.
-Finally, including MHD presents additional difficulties in untangling the effects of each individual feedback mechanism on galaxy chemodynamics.
-
-We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested.
-Mechanically, including this relatively simple treatment of
-cosmic ray feedback in our model is trivial.
-However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to later work.
-
-%\subsection{Detailed Dust Model}
-%\textbf{Should we discuss this? If so I definitely need more info and references - AE}.
-%The dust content of our galaxy is modeled only approximately, scaling with the cell-to-cell variations in gas metallicity.
-Explicitly following the dust content in our galaxy, even crudely, could introduce significant variations in local cooling and heating rates.
-Accounting for metals trapped in a dust phase would produce additional variations in the cooling rates and potentially changes to the galactic chemodynamical evolution.
-
-\subsection{Detailed Stellar Evolution and Binary Stars}
-\label{sec:binary stars}
-
-Roughly half of massive stars live in binary pairs \citep{Sana2013}.
-Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes.
-This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as SNe.
-This effect could be significant, but is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g.
-STARBURST99).
-For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse SNe occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
-Although they find only $\sim 15\%$ of core collapse SNe explode after 50~Myr, this could still be an important effect.
-Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}.
-Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
-
-Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars.
-This is beyond the scope of this project, but will be investigated in future work.
-
-\section{Conclusion}
-\label{sec:conclusion}
-We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
-For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, using individual star particles to model core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, Lyman-Werner radiation and pollution from AGB and massive stellar winds.
-This treatment of feedback, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
-In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
-We present an overview of the properties of this simulation
-in this work.
-% AE: mention companion paper here if publish at same time
-
-For our simulated dwarf galaxy, we find:
-\begin{enumerate}
-\item Multi-channel feedback is effective in this galaxy in regulating star formation to occur at a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
-See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}.
-
-\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, falling to $\eta \sim 10$ at R$_{\rm vir}$,  and
-metal mass loading factors near unity.
-By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Figure~\ref{fig:outflow_velocity}).
-
-\item 
-Only $\sim$10\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of ultrafaint dwarfs.
-By the end of the simulation $\sim$50\% of the remaining metals remain within the virial radius (but outside the galaxy) and $\sim$40\%
-have been ejected beyond the virial radius.
-The fraction in the disk remains fairly constant towards the end of the simulation, but the metals in the halo are still evolving.
-(See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
-
-\item 
-The gas scale height is thin ($\sim 50$~pc), yet resolved, 
-beyond our stellar radius, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
-This is comparable to the resolution limit of the diffuse HI in observed, gaseous ultrafaint dwarfs.
-(See Figure~\ref{fig:scale_height}).
-
-\item The ISRF of our galaxy varies strongly in time, by orders of magnitude, though it has a relatively uniform radial profile averaged over tens of megayears.
-It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
-(See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
-
-\item 
-%mm3 (\textbf{Possibly remove depending on follow up}) Formation of a significant amount of H$_2$ 
-     A significant amount of H$_2$ forms
-through gas phase reactions with H$^-$.
-This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy.
-This leads to high molecular gas fractions, with an H$_2$ mass comparable to that of HI by the end of the simulation.
-This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies.
-(See Figure~\ref{fig:ISM_evolution}.)
-
-\item Finally, we used O and N as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy.
-These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs.
-SNe), as suggested by \cite{KrumholzTing2018}.
-This will be explored in more detail in future work.
-%mm3 (Emerick et. al. \textit{in prep.}). [only cite after submission]
-\end{enumerate}
-
-%In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and how individual metals move into halos.
-This will allow us to examine the role that each source of feedback plays in driving dwarf galaxy chemodynamics.
-
-\section*{Acknowledgments:} 
-We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
-C\^ot\'e, S.
-Glover, K.
-Hawkins, C.
-Hu, K.
-Johnston, B.
-O'Shea, M.
-Putman, B.
-Smith, J.
-Wall, and J.
-Wise.
-A.E.
-is funded by the NSF Graduate Research Fellowship DGE 16-44869.
-G.L.B.
-is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
-M.-M.M.L.
-was partly funded by NASA  grant NNX14AP27G.
-We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute.
-This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.
-These are products of collaborative effort by many independent developers from numerous institutions around the world.
-Their commitment to open science has helped make this work possible.
-
-%\bibliographystyle{yahapj}
-\bibliographystyle{mnras}
+\subsection{Impact on Stellar Abundance Patterns}
+\label{sec:stellar abundances}
+% AE: Possibly need better general introduction to CE models / sims and importance of understanding stellar abundances (obs+theory)
+In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star forming gas in our simulations.
+This could be used to help disentangle sources of scatter in observed stellar abundance, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
+If the star forming gas in our simulations can also be well-fit by a log-normal + power-law PDF, and if we can parameterize their evolution as functions of global galaxy properties, this can be used as a powerful and analytic tool for modeling stellar abundance patterns in semi-analytic models.
+This would be a physically motivated way to account for both the intrinsic spread in stellar abundances due to inhomogeneities in the ISM and variations in mixing for different metal species.
+We reserve an analysis of these distributions in abundance space in both the gas and stars for a future work.
+However, we briefly discuss the connection to star forming gas and stellar enrichment below.
+
+Unfortunately, there is insufficient star forming gas at any one time in these simulations to construct a PDF of metal distributions.
+However, star forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, follow a similar PDF to the CNM.
+To very this, Figure ~\ref{fig:stars} shows the difference between the mass fraction of a given element in stars and the median mass fraction from the CNM PDF at the time that particle formed.
+Stars seem to be sampled evenly around the median of the CNM distribution (i.e.
+there is no obvious bias towards high metal fractions).
+Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
+High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
+
+\subsection{Do these results apply to more massive galaxies?}
+\label{sec:massive galaxies}
+One important caveat about our work is that these results are derived from simulations of an isolated, low mass dwarf galaxy whose properties vary dramatically from a more massive galaxy like the Milky Way.
+It is unclear how much of these results apply to more massive galaxies given their deeper potential wells and higher star formation rates.
+Feedback driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
+We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy.
+With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
+If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
+If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+This difference would be greater at later times (higher metallicity) once AGB enrichment becomes significant.
+For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
+At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way.
+Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way.
+However, there has been no definitive explanation for these observations.
+Generalizing our results and detailing their observational consequences is the topic of ongoing work.
+
+In contrast, we expect the properties of the enrichment PDFs, and the variations between AGB enriched elements and supernova enriched elements (as presented in Figures~\ref{fig:log-normal} and ~\ref{fig:phase-statistics}), to be general.
+We expect metals to exhibit log-normal + power-law distributions in the ISM of all galaxies, with similar trends with enrichment source and gas phase as outlined here.
+However, the detailed properties of the PDFs (e.g, log-normal width, power-law slope) likely depend non-trivially on global galaxy properties.
+How these results vary as a function of galaxy properties will be investigated in future work.
+
+% Talk about CGM at all???
+
+%\textit{In addition, hot gas in a galaxy with a deeper potential well is less likely to be ejected from the galaxy, allowing more time for homogenization and possibly smaller metal fraction variation than seen here.}.
+
+%
+% moved to possible to-do list below,
+%
+\subsection{Implications for Exotic Enrichment Sources}
+\label{sec:exotic enrichment}
+We have shown that the dynamical evolution of metals depends upon their nucleosynthetic source, focusing here on AGB synthesized elements and supernova synthesized elements.
+However, these differences should also apply to exotic enrichment sources, such as hypernovae, neutron-star neutron-star mergers, and neutron star - black hole mergers.
+These sources have energies that differ significantly from typical supernova (10$^{51}$ erg), reaching $> 10^{52}$ for HNe \citep{Nomoto2004} and $\sim$10$^{49}$~erg for NSMs \citep{Goriely2011}.
+We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to supernovae.
+Based on our results here, we would expect elements from HNe to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe.
+Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies.
+These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
+In particular, low mass dwarf galaxies with unusual r-process enrichment \citep[e.g.][]{Ji2015}, are valuable for constraining the source of these elements, their frequency, and typical yields.
+The differential metal evolution presented in our work both opens up an additional avenue by which elements from distinct nucleosynthetic sources may be distinguished in observations and challenges current assumptions used in interpreting these observations.
+
+%\subsection{Extra things I could discuss:}
+%\textit{Things I can / will additionally discuss}
+%\begin{itemize}
+%\item Observed N/O in stellar abundances exhibits large spreads at low metallicity.
+Argument has been that this is driven by timescale differences in AGB vs.
+massive star nucleosynthesis.
+However, our results would predict that N/O have a large spread due to mixing efficiency diffein rences between AGB winds and SNe.
+%\end{itemize}
+
+\section{Conclusions}
+\label{sec:conclusions}
+For the first time we present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
+This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze how individual metal species couple to the galactic winds and ISM of this galaxy.
+We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, core collapse supernovae, and Type Ia supernovae).
+This difference is most significant in our model between elements ejected predominately through AGB winds and those ejected predominantly by core-collapse supernovae.
+In addition, we find for the first time that the metal mass fraction PDFs of each metal in the ISM can be described using an analytic piece-wise log-normal + power-law PDF.
+The properties of these PDFs vary with both ISM phase and metal species, again driven mostly by differences in enrichment sources.
+
+We summarize our results as follows:
+\begin{itemize}
+
+%\item Elements from lower energy enrichment sources (i.e.
+AGB winds) are preferentially retained in the ISM of low mass dwarf galaxies as compared to those from higher energy sources (supernovae), which are more readily launched in galactic winds.
+This result is likely sensitive to global galaxy properties, becoming less significant with increasing halo mass.
+We predict the abundance ratios between AGB wind dominated metals (s-process elements) and SN dominated metals ($\alpha$ elements) to be higher at fixed metallicity in low mass dwarf galaxies than in more massive galaxies, like the Milky Way.
+
+\item Power-law tails in metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
+
+\item Hotter phases have metal fraction PDFs that are more enriched with significant power-law tails as compared to cold phases, which have a more dominant log-normal structure.
+The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling into dense gas.
+% missing text???????????
+
+\item Metal outflow in low mass dwarf galaxies depends upon nucleosynthetic origin.
+Metals from lower energy enrichment events (e.g.
+AGB winds) are preferentially retained in the ISM as compared to those from higher energy events (e.g.
+SNe).
+The degree to which this is true likely depends upon global galaxy properties such as star formation rate, dark matter potential well, and gas geometry.
+
+\item Likewise, metals originating in AGB winds are less well mixed in the ISM compared to metals injected through SNe, with spreads of over 1 dex in cold gas, as compared to
+
+\item Metal distributions exhibit positive skew, such that the median metal fraction can be anywhere from 0.1 to 1.0 dex above the mean metal fraction.
+One-zone chemical evolution models which follow the mean abundance are likely biased to higher enrichment values.
+
+\end{itemize}
+
+We expect these results to be general for more massive galaxies and galaxy properties.
+However, it may be the case that metals couple more uniformly to galactic winds in more massive galaxies as wind driving occurs increasingly through entrainment of the ambient ISM rather than the ejection of individual enrichment events.
+This warrants further examination.
+But interpreting these results for low mass dwarf galaxies, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements, particularly at lower metallicities, 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way, and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements.
+
+%\section{Things to cite}
+%Hou, Yu, Lu 2014: Need to read closer, but CE model playing around with SN energy feedback effectiveness finds that weaker feedback leads to more metal enrichment, higher FB, lower metallicities.
+Suggestion of importance of FB driving CE.
+
+\acknowledgments
+Acknowledgments.
+
+\facilities{Yeti, CCA cluster, Stampede, Pleiades} 
+\software{Numpy, Enzo, yt, astropy}
+
+\bibliographystyle{yahapj}
 \bibliography{msbib}
@@
 
-\section{Gas Phases of the ISM}
-\label{appendix:phases}
-
-To aid in comparison to other works, we define our ISM phases here, as adopted and modified from \citet{Draine2011}, Table 1.3, and used consistently throughout this analysis.
-By construction, these phases are mutually exclusive.
-We take $f_{\rm H_2}$ to be the molecular hydrogen fraction of the total gas mass.
-
-\begin{enumerate}
-\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
-\item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
-\item Warm Neutral Medium (WNM): $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$
-\item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
-\item Molecular: $T < 10^2$~K, $f_{\rm H_2} > 0.5$
-\end{enumerate}
-
-\section{Stellar Radiation Properties}
-\label{appendix:radiation}
-We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Figure~\ref{fig:stellar radiation properties} we plot these properties.
-We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
-This requires two factors for each radiation type, one for low mass and one for high mass stars.
-We use the following multiplicative factors to adjust the black body spectrum for HI and HeI ionizing radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
-We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
-
-The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid.
-A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section.
-We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \url{http://www.pa.uky.edu/~verner/photo.html}}
-The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision.
-Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.
+\section{Density PDF}
+\label{appendix:density PDF}
+We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}.
+We show the mass-weighted PDF ($dm/Md\rm{log}n$) on the left, and the volume-weighted PDF ($dv/Vd\rm{log}n$) on the right.
+As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution.
+The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.
+The volume weighted PDF is much better described as a multi-component power law.
+However, in both cases the molecular gas distributions are in fact log-normal.
+The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities.
+These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.
+Finally, \cite{Hopkins2013} suggests a different functional form for describing these PDFs across a range of idealized simulations, but it still may be insufficient to fully describe the density PDF in realistic galaxy simulations.
+Clearly, we are far from a general understanding of mass-weighted and volume-weighted density PDFs in the case of a turbulent, self-gravitating, multi-phase ISM.
 
@@
 \centering
-\includegraphics[width=0.4\linewidth]{Q0}
-\includegraphics[width=0.4\linewidth]{Q1}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{L_FUV}
-\includegraphics[width=0.4\linewidth]{L_LW}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{E0}
-\includegraphics[width=0.4\linewidth]{E1}
-\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right).
-Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
-\label{fig:stellar radiation properties}
+\includegraphics[width=0.475\linewidth]{density_PDF.png} 
+\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted.png}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr.
+The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
+\label{fig:density_pdf}
 \end{figure}
 
-\setcounter{figure}{0}
-\section{Typical Gas Densities in Supernova Injection Regions}
-\label{appendix:SN}
-
-Modeling SN feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of SN feedback.
-Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time.
-However, physically consistent solutions have been developed \citep[e.g][]{Simpson2016} that inject a mixture of kinetic and thermal energy with a ratio that depends on resolution and local gas density.
-Overcooling becomes less important with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each SN.
-We take advantage of our high resolution and employ a simple thermal energy injection model for our SN feedback.
-We demonstrate how well this resolves our SNe in the comparison simulation presented in this work.
-
-The left panel of Figure~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our simulations.
-As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
-For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations.
-The right panel of Figure ~\ref{fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
-\begin{equation}
-R_{\rm PDS} = 
-\begin{cases}
-49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z \le 0.01 \\
-18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z \ge 0.01 \\
-\end{cases}
-\end{equation}
-where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$.
-\citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the SN explosion with thermal energy injection alone, assuming uniform density in the injection region.
-In practice, the injection region is never uniform.
-We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each SN.
-As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but up to 10\% are somewhat under-resolved.
-In general, these are SN explosions from the most massive (i.e.
-most prompt) stars.
-We do not expect that resolving these SNe will dramatically alter our results.
-However, we note that using our feedback model at resolutions much less than a few parsecs will require adopting a different injection mechanism.
-
-% We use a spherically symmetric thermal dump method of modelling SN explosions.
-This is the simplest method possible, but can often result in rapid overcooling of the heated gas, effectively underestimating the effectiveness of SN feedback.
-Solutions to this problem can often be ad hoc (e.g.
-briefly turning off cooling) in low resolution, large cosmological simulations.
-However, recent work has shown injecting some fraction of this thermal energy directly as kinetic energy or momentum alleviates this issue without sacrificing physical realism.
-However, it has been shown that simple thermal energy injection is sufficient for parsec scale (or better) resolutions, provided the SN do not occur in very high density regions; if resolved, thermal injection converges with kinetic energy / momentum injection methods.
-Resolving these explosions with thermal energy injection alone depends ultimately on the grid resolution, background density and ISM structure, the background cooling/heating physics used, and the size and shape of the injection region.
-Here, we perform a resolution test of our thermal injection method over four uniform densities (0.1 \ccunit, 1.0 \ccunit, 10.0 \ccunit, and 100.0 \ccunit) for both a 8.0 \msun and 25.0 \msun star, comparing to both the analytic solution and results using kinetic energy injection from \citet{Simpson2015}.
-These results are presented in Figure~\ref{fig:SN tests}.
-We note these are heavily idealized cases.
-In general in our simulations, pre-SN feedback from stellar winds and radiation will reduce the typical densities within which our SN explosions occur.
-In addition, SN will generally be clustered, meaning each SN will reducing the typical density for each subsequent SN in that region.
-In Figure~\ref{fig:SN histogram} we plot a histogram of the typical peak and average gas densities in the 3 cell injection region of each SN in the XXXX XXXXX simulation.
-As shown, some of the SN explode in high density regions around 100 \ccunit and are likely under-resolved, but a majority will be resolved.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.4\linewidth]{sn_density_hist}
-\includegraphics[width=0.4\linewidth]{sn_radius_hist}
-\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation.
-{\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each SN assuming a uniform medium at either the peak or average density in the injection region.
-The vertical lines show one and 4.5 cell widths.
-This shows that a fraction of these SNe are certainly underresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
-\label{fig:SN histogram}
-\end{figure}
-
-%\section{Stellar Wind Model}
-%\label{appendix:stellar winds}
-%
-% This is still probably a good idea to do at some point, but save for if/when
-% we have a paper using full stellar winds where this matters - AE (Jul. 19 2017)
-%
-%Discuss wind properties and evolution in a hand full of isolated star runs (don't need to do a resolution study...
-kinda) and compare to Weaver et.
-al.
-1977 analytic results.
-Really we won't resolve the winds at high densities, but that is OK...
-as long as the wind bubbles are > 3*dx (the injection size) we are generally going to be fine...
-aka as long as the SN explosion goes off in wind bubble gas and not dense ISM that shouldn't be there..
-
-\setcounter{figure}{0}
-\section{Cooling and Heating Rates}
-\label{appendix:cooling}
-%AE: 2/23 Old version of text... keeping around for now:
-% For comparisons to other works, we present the cooling curve used in our simulations here.
-This cannot be done exactly, however, as primordial cooling and heating is computed cell-by-cell using the non-equillibrium chemistry solver in \textsc{Grackle}.
-These rates are not interpolated from the generated \textsc{CLOUDY} tables as is done for the metal line cooling rates.
-In addition, although these tables do include the effect of the UVB, they do not account for local variations in the ISRF from stellar radiation.
-However, we present the combined primordial and metal line cooling rates from the generated \textit{CLOUDY} tables in Figure~\ref{fig:cooling} at three characteristic densities for $Z = 0.01$Z$_{\odot}$.
-As discussed in Section~\ref{sec:methods}, we account for self-shielding against the UVB in both our simulations and the computed \textsc{CLOUDY} models shown in this figure.
-
-%AE: 2/23 Old version of text... keeping around for now:
-%To derive the diffuse cooling and heating rates used in the simulations, we make two approximations.
-First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal-line cooling and heating rates are used.
-The primordial heating and cooling rates are calculated self-consistently using the non-equilibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}.
-However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations.
-Second, this figure ignores the contributions to the heating rate from the variable interstellar radiation field, namely the stellar contribution to photoelectric heating, heating from Lyman-Werner dissociation, and ionization heating.
-We describe how we obtain the metal line cooling rates below and quantify the change in using these updated tables.
-%Therefore, the heating rates shown are approximate lower limits to the true heating experienced by any given cell in the simulation.
-
-%AE: 2/23 Old version of text... keeping around for now:
-%Figure ~\ref{fig:cooling} shows the combined primordial and metal line cooling and heating rates at three characteristic densities for $Z = 0.01 $Z$_{\odot}$.
-The Figure indicates the regime at low temperatures where heating dominates over cooling.
-The curve as shown includes only the $z = 0$ \citet{HM2012} metagalactic UV background.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
-\caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background.
-Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the un-corrected (i.e.
-optically thin) metal line cooling rates.
-The regimes where heating dominates are plotted with dashed lines for clarity.}
-\label{fig:cooling comparison}
-\end{figure}
-
-The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with a self-shielding approximations.
-\citet{Hu2017} details this inconsistency: metal cooling rates computed under the assumption of an optically thin UV background overestimate the electron fraction in regimes where self-shielding is important ($-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$).
-This results in an artificially enhanced metal line cooling rate in regions of self-shielding.
-This can be a significant effect, particularly at higher metallicities.
-We demonstrate this in Figure~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
-The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
-In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
-Figure~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
-We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
-
-For densities where self-shielding is important, we computed \textsc{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
-In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud.
-We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UV background.
-These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}.
-In computing these tables we had to include the cosmic ray ionization that dominates in optically thick clouds.
-Without this effect, \textsc{Cloudy} becomes unstable in entirely neutral regions.
-We adopted a cosmic ray ionization rate of 10\% the Milky Way value, though we note that varying this from 1\% to 100\% the Milky Way value did not have an effect on the extracted metal line cooling rates.
-
-Finally, we note that the cooling and heating rates in our simulation will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
-The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which is not included in these diagrams.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_curve}
-\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}.
-The absolute value of the net cooling or heating
-rate is shown with solid lines.}
-\label{fig:cooling}
-\end{figure}
-
-\setcounter{figure}{0}
-\section{Resolution Study}
-\label{appendix:resolution_study}
-
-We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions between our fiducial high-resolution simulation, two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc.
-The physics in each of these simulations remains the same with the exception of our star formation threshold.
-Since star formation is set to occur at gas densities where the Jeans mass is unresolved at the maximum resolution, our star formation algorithm is tied to resolution.
-A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.
+\section{Resolution Comparison}
+\textbf{Still a to-do:}
+We perform a resolution test to confirm that the key results of this study are convergent, at least qualitatively.
+Given the variations in star formation rate, feedback effectiveness, and stochasticisty in our model, we do not expect exact numerical convergence in any one quantity.
+We conduct two lower resolution simulations with a maximum physical resolution of 3.6 pc and 7.2 pc.
+We refer the reader to Paper I for a previous comparison of these simulations to our fiducial run.
+In Figure~\ref{fig:resolution-phase} we demonstrate that O and Ba abundances behave qualitatively similar in our lower resolution runs as in our fiducial model.
+In both lower resolution runs O has a generally tighter distribution that narrows over time, while Ba is much less well mixed, in agreement with our fiducial simulation.
+The exact numerical values for these spreads are not convergent across simulations, but we do note significant variations in the exact SFH of these lower resolution runs could be driving these differences.
 
@@
 \centering
-\includegraphics[width=0.33\linewidth]{sfr_resolution_study.png}
-\includegraphics[width=0.33\linewidth]{mass_evolution_resolution.png}
-\includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
-\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted).
-The line colors in the left panel are for better clarity between the SFRs.}
-\label{fig:resolution_study}
+\includegraphics[width=0.95\linewidth]{O_Ba_spread_resolution-comparison.png}
+\caption{Resolution comparison at two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.
+Compare to Figure~\ref{fig:phase-statistics}.}
+\label{fig:resolution-phase}
 \end{figure*}
 
-Figure~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, it does not do so dramatically.
-We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation and driven mostly by variation in the initial star formation rate of the galaxy.
-In each of the lower resolution runs, the SFR is larger within the first 100~Myr.
-This is because, at lower resolution, the initial driving SN are less resolved and less effective at preventing uniform collapse of the gas disk.
-The 3.6~pc run with a factor of two higher initial SN driving rate demonstrates that an increase in the effectiveness of the supernova at lower resolution brings the evolution much closer to that seen at our highest resolution run.
-We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Figure~\ref{fig:SN histogram}.
-However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
-This is shown more clearly comparing the left and right panels of Figure~\ref{fig:phase_resolution}, the temperature-density phase diagrams for the 3.6 and 7.2 pc.
-There is clearly much less hot gas (T $> 10^6$~K) in our lowest resolution run.
-
-The largest qualitative difference between these runs is the H$_2$ mass.
-As discussed in this work, the H$_2$ mass fraction of our fiducial run is quite high, driven by significant H$_2$ production from gas-phase reactions and the preferential retention of cold, dense H$_2$ gas in feedback driven outflows.
-However, each of the lower resolution runs produce less H$_2$ (about 40\% less) than our fiducial run.
-This is certainly an issue in interpreting the generality of our large H$_2$ mass fractions, and requires more tests to confirm.
-However, it is not unreasonable to expect that the H$_2$ production occurs most effectively at densities not captured in the 3.6~pc and 7.2~pc runs.
-This suggests that most of our H$_2$ production in the fiducial run occurs in gas with densities above 50~cm$^{-3}$.
-As shown in Figure~\ref{fig:phase_resolution}, the maximum density is clearly lower in each of the two lower resolution runs.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{3pc_phase.png}
-\includegraphics[width=0.475\linewidth]{6pc_phase.png}
-\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Figure~\ref{fig:phase}.}
-\label{fig:phase_resolution}
-\end{figure*}
-
-Finally, each of the lower resolution runs retain a similar fraction of their produced metals in their disks (black curves in right panel of Figure~\ref{fig:resolution_study}), but all of the lower resolution runs contain about a factor of two less than our fiducial simulation.
-The fraction leaving the virial radius of the galaxy is higher in the lower resolution runs, again within a factor of two of our fiducial resolution.
-This is an interesting difference, as the resolution decrease primarily affects the disk of the galaxy; little to none of the halo volume is refined to the highest resolution, and so should be unaffected by this change.
-This suggests that this difference is a secondary effect, driven by changes to the particular SFH and disk structure between the various resolutions.
-
-%\section{Pre-SN Feedback with and without radiation}
-
-%\section{Code}
-%(likely just do this as a short blurb in acknowledgements)
-
-%A one-zone chemical evolution and feedback model was constructed to provide rapid testing and examination of the feedback and yield properties of each of our stars in our model.
-This code is publically available at https://github.com/aemerick/onez.
-In the simplest case, one can generate a series of star particles and examine their resulting properties, including wind and SN yields, as a function of mass and metallicity.
-Included also are more complicated examples of running the full one-zone model.
-Support currently only exists for running in a non-cosmological mode with a constant star formation rate.
-In addition, this one-zone model uses star-by-star modelling and becomes extremely inefficient at large particle counts.
-Future develop will better optimize this code, allow for variable input or evolving star formation rates, cosmological evolution, and parallelism.
-
-%\appendix
-%\section{appendix section}
-\label{lastpage}
-
 \end{document}

### 2018-07-06 main.tex
updating plots
Update on Overleaf.

--- 2018-06-03 main.tex
@@
 \usepackage[figure,figure*]{hypcap}
+
+\hypersetup{draft}
 %\usepackage{multirow}
@@
 %\centering
-\includegraphics[width=0.95\linewidth]{outflow_velocity_distribution}
+\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
 \caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
@@
 \includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
-\includegraphics[width=0.9\linewidth]{metal_fraction_evolution}
+\includegraphics[width=0.9\linewidth]{metal_retention}
 \caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Figure~\ref{fig:mass_outflow}.
@@
 
+\subsection{Importance of Ionizing Radiation}
+\label{sec:ionizing radiation}
+
+We investigate the relative importance of stellar ionizing radiation as a source of feedback in our galaxy with two comparison simulations.
+We ran one simulation with no stellar ionizing radition (NAME) and a second including only the local effects of stellar ionizing radiation, deleting all photons that travel more than 25~pc from their source star.
+Although radiative transfer is itself expensive, our simulation without ionizing radiation rapidly formed a significant amount of stars and ended up being more expensive than our fiducial run.
+We were only able to run this simulation for XXX Myr.
+We compare the star formation rate
+
+In the first case, we were unable to run the simulation for more than
+
+We compare our fiducial simulation, which includes stellar ionizing radiation traced with radiative transfer, and a simulati
+
 \section{Discussion}
@@
 \includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
-\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution.png}
+\includegraphics[width=0.475\linewidth]{all_gas_efficiency_evolution.png}
 \caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.

### 2018-07-10 mnras_template.tex
Update on Overleaf.

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title{Gas Fractions of Galaxies Across Simulations}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[Emerick]{ Andrew Emerick$^{1,2}$\thanks{E-mail: emerick@astro.columbia.edu} + more + IQ Collaboratory (alphabetical order)
\\
% List of institutions
$^{1}$Department of Astronomy, Columbia University, New York, NY 10027 \\
$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
{\bf NOTE: all plots should be considered preliminary for both style and content}
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

Modern large cosmological hydrodynamics simulations have made tremendous progress in being able to reproduce observed properties of galaxies. This progress is fueled both by better computational resources, allowing for increased dynamic range in these simulations, and more careful attention to models of feedback. Updated sub-grid methods for stellar feedback physics better describe how feedback regulates star formation and drives outflows in galaxies. To obtain these improvements, however, the free many parameters associated with these models are generally calibrated specifically to reproduce observed relationships of the stellar properties galaxies, such as the galaxy stellar mass function (GSFMS), the stellar mass halo mass (SMHM) relationship, galaxy sizes, and/or the redshift evolution of these relations. Understanding how well, if at all, a given simulation that reproduces galaxy stellar properties matches galaxy gas properties is an important tool to better understand the physics that drives galaxy evolution. The differences among these models are significant enough that, even with similar galaxy stellar mass properties, galaxy gas properties are not necessarily comparable. Although this study has been done individually for EAGLE \citep{Bahe2016,Marasco2016,Crain2017}, MUFASA \citep{Dave2017}, (and {\it Illustris + SAM?}), these works have never been compared with each other simultaneously. In this work we examine the gas properties of galaxies between Illustris \citep{Vogelsberger2014,Genel2014}, EAGLE \citep{Schaye2015,Crain2015}, MUFASA \citep{Dave2016}, and the ``Santa Cruz'' SAM \citep{Somerville2012,Porter2014} {\it check these refs.}.

% Illustris TNG??

\section{Simulations and Data Selection}
\begin{table*}
\centering
\caption{Caption}
\label{table:simulations}
  \begin{tabular}{l c c c c c c c}
  \hline
  Simulation & Baryon Res. (10$^6$ M$_{\odot}$) & DM Res. (10$^6$ M$_{\odot}$) & Vol. (x cMpc)$^3$ & $\epsilon$ (ckpc) & Gas Def. & Pressure Floor & Ref. \\
  \hline 
  Illustris  & 1.26 ($\Delta x$ = 48 cpc) & 6.26 & 106.5 & 0.71 / 1.42 & &  & \citep{Vogelsberger2014} \\
  %Illustris-TNG & & & \\
  MUFASA & 18.2 & 96 & 50 & 0.5 & & & \citep{Dave2016} \\
  EAGLE  & 1.81 &  9.70  & 100 & 0.70 (pkpc) & &  & \citep{Schaye2015,Crain2015} \\
  Brooks & & &  & & & & \\
  SC-SAM & -  & - & & - & - & & \citep{Somerville2012,Porter2014}\\
  \hline
  \end{tabular}

\end{table*}

For each data source we utilize all central galaxies, as determined by a halo finder, without consideration of nearest-neighbor distance to a comparably massive or more massive galaxy. {\it (list halo finders used across simulations for clarity? Likely not the same)}. We consider all gas, stellar, and dark matter mass assigned as belonging to the central galaxy by the halo finder, ignoring mass assigned to sub-halos. In truth, this selection can include a large amount of gas in the circumgalactic medium (CGM), far from the central galaxy. However, we focus our attention solely on the cold gas content of these galaxies, which should be be contained predominately in the disk of the galaxy. SFR's and sSFR's are computed as averaged over 100~Myr and 1~Gyr.

The works considered here treat the sub-grid physics required to model individual gas components (e.g. H, He, H$_2$) and their ionization states somewhat differently. Each of the big-box simulations lack the resolution and physics needed to self-consistently model each ionization state. Rather, these are computed through some approximation either live during the simulation (EAGLE) or via post-processing (MUFASA). Though each of these methods are similar, they likely do not produce identical results; characterizing the variation in galaxy gas properties caused by different ionization models is beyond the scope of this work. If H$_2$ is followed, we compute the gas mass of each galaxy as the total neutral hydrogen mass, or M$_{\rm gas}$ = M$_{\rm H_2}$ + M$_{\rm \ion{H}{i}}$ (EAGLE, MUFASA,Brooks), otherwise we take M$_{\rm gas}$ = M$_{\rm \ion{H}{i}}$ if H$_2$ is not tracked (Illustris, SC-SAM). This is a more faithful comparison than taking M$_{\rm \ion{H}{i}}$ alone, as the H$_2$ content in these works is derived directly from the \ion{H}{i} content. We define gas fraction here as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm HI}}{M_{\rm HI} + M_{*}},
\end{equation}
though we note some authors consider instead the the ratio $M_{\ion{H}{i}} / M_{*}$.

We briefly describe each data source below including how gas phases are computed for each work. We refer the reader to the individual method papers associated with these works for detailed descriptions. The properties of these simulations are summarized in Table~\ref{table:simulations}.

{\bf For each of the below need: 1) code + hydro (SPH, moving mesh, etc.), 2) included feedback physics and briefly how they are modeled (thermal? mechanical? any hydro or cooling decoupling? AGN threshold / methods if they exist, etc.), 3) brief characterization of the feedback physics (bursty, strong, weak, etc.), 4) how is neutral gas followed / computed in each work, and 5) resolution and box size.}
\subsection{Illustris}
\label{sec:illustris method}
{\it ask Shy for text}

\subsection{EAGLE}
\label{sec:EAGLE method}
{\it ask ?? for text}

\subsection{MUFASA}
\label{sec:MUFASA method}
{\it ask Romeel for text}

\subsection{SC SAM}
\label{sec:SC-SAM method}
{\it ask Rachel and/or Viraj for text}

\subsection{Brooks zooms}
\label{sec:Brooks method}
{\it ask Alyson for text}

\subsection{Observational datasets}
\label{sec:observational data}
{\bf decide if we are making observational comparisons.} describe datasets here ({\it Marla for text?}).. likely both Bradford et. al. 2015 and recent xGASS data release.

\section{Results}
\label{sec:results}
%\subsection{Gas mass vs stellar mass}
%Maybe just ignore this for simplicity in favor of gas fraction plots

\subsection{Stellar Mass Halo Mass Relationship}
\label{sec:results:SMHM}
{\bf missing data at the moment}
{\it Discuss SMHM relationship across the works. Discuss how their similarities / differences may affect how to interpret rest of paper (though they should probably be similar?).  Possibly also shade with median gas fraction... this should be similar (maybe) across works}

\begin{figure*}
\includegraphics[width = 0.975\textwidth]{halo_stellar_2D_fraction.png}
\caption{The stellar mass halo mass relationship for the full population of galaxies across datasets. Shading indicates the fraction of galaxies within a given bin.}
\label{fig:fgas mstar 2D}
\end{figure*}

\subsection{Gas fraction vs stellar mass}
\label{sec:results:fg Mstar}

\begin{figure*}
\includegraphics[width = 0.99\textwidth]{fgas_mstar_2D_log_fgas.png}
\caption{Galaxy gas fraction (f$_{\rm gas}$) as a function of stellar mass for the full population of galaxies in each of the four data sets with large galaxy counts. Shading indicates the fraction of galaxies in a given bin. This diagram explicitly does not include galaxies with f$_{\rm gas}$ = 0 (see Figure~\ref{fig:linear fgas mstar}).}
\label{fig:fgas mstar 2D}
\end{figure*}

In Figure~\ref{fig:fgas mstar 2D} we present the gas fraction as a function of stellar mass for the entire population of galaxies in each of the large sample-size datasets. To zeroth order, each data set has the same trend of decreasing gas fraction with increasing stellar mass, but the distribution of gas fractions at fixed stellar mass varies significantly across each data source. In particular, Illustris is more tightly distributed around high gas fractions than the other datasets, while the remaining have wider distributions and lower typical gas fractions. EAGLE exhibits the largest spread in gas fraction at fixed stellar mass.

By nature of plotting gas fraction in logsapce, these diagrams exclude any galaxies with no gas content. To help clarify these populations across datasets we plot the median gas fraction (including galaxies with f$_{\rm gas}$ = 0) as a function of stellar mass in the top panel of Figure~\ref{fig:linear fgas mstar}, including the Brooks zoom-in simulations. The shaded regions in each encompass the innerquartile range of each distribution; in stellar mass bins with less than 10 galaxies we plot points instead of the median curve. In the bottom panel, we show the fraction of galaxies in stellar mass bins that are devoid of gas for each data source. The same trends observed in Figure~\ref{fig:fgas mstar 2D} are clear here as well: Illustris galaxies are tightly distributed with high gas fractions at fixed stellar mass, as compared to EAGLE, MUFASA, and the SC-SAM which have comparable gas fractions and wider distributions. At low stellar mass, the SC-SAM approaches unity, unlike MUFASA and EAGLE.

The bottom panel of Figure~\ref{fig:linear fgas mstar} is striking. This shows the fraction of galaxies in each stellar mass bin that contain no cold gas (defined again as either \ion{H}{i} or \ion{H}{i} and H$_2$), with the total percentage of gasless galaxies in each sample given in the legend. Both EAGLE and MUFASA uniformly have large populations of gasless galaxies across all stellar masses, with particularly high fractions at low stellar masses. In contrast, Illustris uniformly has very few galaxies devoid of cold gas at all stellar masses. The SC-SAM is the only model that evolves with stellar mass in this space.

\begin{figure}
\includegraphics[width = 0.99\linewidth]{fgas_mstar_binned_IQR_logged.png}\\
\includegraphics[width = 0.99\linewidth]{gasless_fraction_mstar.png}
\caption{{\bf Top:} The running median of f$_{\rm gas}$ as a function of stellar mass for each dataset with shading denoting the inner quartile range of each. Unlike in Figure~\ref{fig:fgas mstar 2D}, this includes galaxies with zero neutral gas mass. {\bf Bottom:} The fraction of galaxies per stellar mass bin for each dataset that do not contain any neutral gas. The percent of all galaxies without gas in each dataset is shown in the legend.}
\label{fig:linear fgas mstar}
\end{figure}

\subsection{SFR vs. stellar mass}
\label{sec:results:SFMS fgas}

\begin{figure*}
\includegraphics[width = 0.99\linewidth]{SFMS_fits_2dhist_median.png}\\
\caption{2D Histograms of the SFMS, colored by median gas fraction. }
\label{fig:SFMS fgas}
\end{figure*}

\begin{figure*}
\includegraphics[width = 0.99\linewidth]{fgas_DSFMS_binned_IQR_logged.png}\\
\caption{Running median and IQR of the gas fraction of galaxies as a function of their distance (in dex) from the SFMS, as defined in Figure~\ref{fig:SFMS fgas}.}
\label{fig:fgas DSFMS}
\end{figure*}

\begin{figure*}
\includegraphics[width = 0.99\linewidth]{fgas_DSFMS_panel_plot_IQR_logged.png}\\
\caption{Same as Figure~\ref{fig:fgas DSFMS}, but separated into stellar mass bins.}
\label{fig:fgas DSFMS panel}
\end{figure*}

\section{Discussion}

\subsection{Comparison to Observations}
\label{sec:observations}
{\it Possibly should not be the focal point of this paper, but could be nice to include. }

\begin{figure*}
\includegraphics[width = 0.99\textwidth]{fgas_mstar_2D_log_fgas_obs.png}
\caption{Same as Figure~\ref{fig:fgas mstar 2D}, but for the observational data from Bradford2015 and Cantinella2018.}
\label{fig:fgas mstar 2D obs}
\end{figure*}

\begin{figure*}
\includegraphics[width = 0.99\textwidth]{SFMS_fits_2dhist_median_obs.png}
\caption{Same as Figure~\ref{fig:SFMS fgas}, but for the observational data from Bradford2015 and Cantinella2018.}
\label{fig:SFMS mstar 2D obs}
\end{figure*}

\section{Conclusion}

\section*{Acknowledgements}
IQ collab and funding

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{msbib.bib} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2018-07-10 main.tex
updates

@@
 We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
-Effective feedback drives significantly metal-enriched outflows, leading to low metal retention fractions consistent with observations.
+Effective feedback \textbf{drives outflows with a greater metallicity than the ISM}, leading to low metal retention fractions consistent with observations.
 Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
@@
 Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
-There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
+There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
+%{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
 These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
@@
 Leo P is gas rich, with a \textbf{neutral hydrogen mass} $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and \textbf{stellar mass} $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to an \textbf{observed neutral hydrogen radius} $r_{\rm HI} = 500$~pc.
-LeoP has a low metallicity, with \textbf{an oxygen to hydrogen abundance ratio} of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
+LeoP has a low metallicity, with \textbf{an oxygen to hydrogen abundance ratio (O/H)} of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
 Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
@@
 
-We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 18 by the end of the simulation.} Within the first 40 Myr of evolution the SFR rises quickly to between 2--4$ \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$, remains roughly at this level for 100 Myr, and then drops to an average of about $4 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$, with large fluctuations.
-By the end of the simulation, the SFR is very low and star formation events are infrequent, with an average SFR over the final 200~Myr of 2.58$\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$.
+We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
+The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$.
 The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation.
-Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 9.93 \times 10^{-5}$ M$_{\odot}$ yr$^{-1}$.
+Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.19 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
 We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.
@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, but a fairly significant component of molecular hydrogen has formed, with a mass of about $5.8 \times 10^5$ M$_{\odot}$, or roughly 16\%, of the total gas mass in the galaxy's disk.
-The total amount of molecular hydrogen mass in the system remains fairly consistent throughout the evolution, yet its fraction increases over time to roughly 35-40\%; at this point, it is about equal with the HI gas.
-This is because the total amount of gas in the disk decreases through feedback-driven winds, but the H$_2$ is preferentially retained.
-Small fluctuations in the H$_2$ mass correspond with small increases in the total stellar mass, as some small fraction of H$_2$ is converted into stars, and more is destroyed from the subsequent feedback.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, \textbf{ with a molecular hydrogen mass fraction of only $\sim$ 0.3 \%.
+The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
+For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% by the end of the simulation.
+The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy due to feedback-driven galactic winds.
+During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM.
 Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
-The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
+The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.}
 
@@
 We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
-We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content as decoupled from the rest of the gas.
+We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content.
+\textbf{We further note that no region in our galaxy is more than 0.5\% molecular}.
 See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-Each of these phases exist throughout our simulation, and are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
+These presence of phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
 Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.
@@
 We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
-The boxed regime in the lower right corner shows our star formation density and temperature threshold.
+\textbf{Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:methods}) is seen clearly by the slight horizontal feature at high temperatures.}  The boxed regime in the lower right corner shows our star formation density and temperature threshold.
 Gas in this regime is rapidly consumed by star formation and subsequent feedback.
@@
 
-The mass of the ISM in our dwarf galaxy is dominated by the CNM for the first 200~Myr of simulation time, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
-After this point, the molecular component becomes equally or even somewhat more important through the end of the simulation.
-Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining mass dominated by the WNM.
-While the CNM has a negligible volume fraction, the WNM, WIM, and HIM each occupy roughly the same volume fraction.
-However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy.
+\textbf{H2 changes:} The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
+The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
+The WNM is initially comparable to the CNM, only comprises a mass fraction of about 0.1 by the end of the run.
+The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation.
+During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1.
+Although the CNM dominates the mass fraction, it is a negligable component of the ISM volume.
+The volume is generally dominated by the WIM, but the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
 Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
 
-These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
-They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (ionized and neutral), with cold gas having $\sim$ 10\% of the mass, and occupying negligible volume, and hot gas occupying $\sim$ 10\% of the volume, but having negligible mass.
-Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few.
+\textbf{H2 Changes:} These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
+They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (defined in those works as gas with 100~K$<$T$< 3\times 10^{4}$), with cold gas having between 1 and 10\% of the mass, and occupying negligible volume.
+Hot gas (defined as gas with $T > 3\times 10^{4}$~K) occupies 10\% of the volume, with negligable mass, in their galaxy, while our WIM alone occupies $>$ 50\% of the volume.
+Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) and hot gas (by volume fraction) that seen in the more massive dwarf galaxy in these works.
 The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
@@
 This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
-In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 50 Myr from 300--350~Myr.
+In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
 The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
 The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.
-Interestingly, the averaged profile appears nearly flat for most of the disk, with an increase at higher radii due to more recently formed stars.
-However, the ISRF varies significantly over time, fluctuating by an order of magnitude or more at any given radius.
+\textbf{The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
+At any given radii, there is over a two order magnitude variation in the ISRF during this period of time.}
+
+\textbf{ The bottom panel gives the HI ionizing photon flux from stellar radiation.
+The ionizing radiation profile follows a similar trend, yet with significantly more variation, anywhere from two to four orders of magnitude.
+As this radiation is followed through radiative transfer, the profile encodes information about local attentuation by dense, neutral gas.
+This is the main driver of the differences between the two panels.
+The total fluctuation in both panels is due in part to the low-level, stochastic star formation in our galaxy.
+A higher star formation rate would produce a more regular population of massive stars and more uniform (in time) ISRF.}
 
@@
 
-The bottom panel gives the ionizing photon fluxes for HI from stellar radiation {\em only}.
-Since this field is tracked directly using ray-tracing radiative transfer, the profile encodes information about local attenuation of these photons from dense, neutral gas.
-This is the main driver of the differences between this field and $G_{\rm o}$.
-However, both profiles track each other well as a function of radius.
-The lack of dramatic trend with radius in both diagrams suggests that one could model the ISRF in low mass dwarf galaxies using a uniform heating / ionization rate; however, this would still fail to capture the fact that any given region of the galaxy will experience order of magnitude or more fluctuations in the incident flux.
-
 \begin{figure*}
@@
 \includegraphics[width=0.45\linewidth]{q_o_2D_phase}
-\caption{Single-snapshot 2D radial profile plots at 200~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
+\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
 Here, we include all gas within the mid-plane of our dwarf galaxy.
@@
 
-To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 200~Myr.
+To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr.
 This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
@@
 For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor.
-The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors on order of 50--100 throughout the simulation time.
-This quickly declines towards larger radii, however, with minimal outflow past the virial radius.
-\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift.
-Our dwarf galaxy exhibits mass loading factors between 4 and 40 at this radius; this is consistent with the results from \citet{Muratov2015}, but perhaps slightly below their typical values.
+The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors between 20--100 throughout the simulation time.
+This declines towards larger radii, however, with substantially less outflow past the virial radius.
+\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift, consistent with our results.
 
@@
 These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
-We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find mass loading factors at 0.05 $R_{\rm vir}$ between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$, and therefore certainly have much smaller mass loading factors at 0.25 $R_{\rm vir}$.
+We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find lower mass loading factors even closer to the disk, at 0.05 $R_{\rm vir}$, between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$; certainly this implies even smaller mass loading factors at 0.25 $R_{\rm vir}$.
 
@@
 
-Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
+\textbf{H2 Changes:} Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
 In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
-Half of the outflow, by mass, is at velocities below 40 km s$^{-1}$, with 75\% at velocities of 70 km s$^{-1}$ or below.
-This gas is dominated by the two warm gas phases, with the WNM dominating at lower velocities, and the WIM at higher velocities.
-The distribution has a very long tail out to and beyond 500~km~s$^{-1}$.
-The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling HIM, consistent with the results in \citet{Hu2016,Hu2017}.
-However, as shown, the HIM comprises very little of the outflow by mass.
+Gas with a negative velocity is moving towards the center of the halo.
+Roughly 25\% of this mass is inflowing, mostly with modest negative velocities, and corresponds to previously ejected gas mixing and recycling throughout the halo.
+Half of the outflowing gas (positive velocities) is moving at velocities below 30 km s$^{-1}$, 75\% at velocities below 70 km s$^{-1}$, and 95\% at velocities below 100 km s$^{-1}$.
+Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-neglibable amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$.
+The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominated at velocities above 200 km s$^{-1}$.
+The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling WIM and HIM, consistent with the results in \citet{Hu2016,Hu2017}.
+However, as shown, the HIM, which is mostly the SN ejecta itself, comprises very little of the outflow by mass.
 Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM.
@@
 \caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
+This is averaged over the same time interval as Figure~\ref{fig:ISRF}.
 The outflowing material is multiphase, broken into WNM, WIM, and HIM.
@@
 We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K.
-There is little to no outflowing mass in the CNM or molecular phases.}
+There is little to no outflowing mass in the CNM.}
 \label{fig:outflow_velocity}
@@
 After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
-This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy.
-It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, reaching 40\% by the end of the simulation.
-Likewise, the CGM metal content continually decreases until the end of the simulation, from loss through the virial radius of the halo.
-Although the metal content of the ISM gradually decreases throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution.
+This continues throughout the simulation, with only $\sim$4\% of produced metals residing in the disk of the galaxy.
+It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius until about 350 Myr where the fraction levels off to just above 50\%.
+Likewise, the CGM metal content continually decreases until the end of the simulation from loss through the virial radius of the halo.
 See Section~\ref{sec:obs_metals} for further discussion.
@@
 \includegraphics[width=0.98\linewidth]{log_NO_panel}
-            \caption{Three slices in the mid-plane of our dwarf galaxy at an arbitrary time of 350~Myr after the start of star formation showing the variation in gas phase metal abundances.
+            \caption{\textbf{NEED TO UPDATE:} Three slices in the mid-plane of our dwarf galaxy at an arbitrary time of 350~Myr after the start of star formation showing the variation in gas phase metal abundances.
 The left slice gives the ratio of the abundance between N and O, while the number density and temperature are shown on the right.
@@
 \label{sec:molecular gas content}
-
+\textbf{AE: rewording - changed numbers and text to reflect lower H2 fractions. left discusion of uncertainties in H2 formation in low mass dwarfs and need for further study:}
 The molecular gas content of low-mass dwarf galaxies is generally assumed
@@
 Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
-As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.17--0.20, within this range, but significantly exceeding the few percent often found in models.
-Ignoring the H$_2$ component of our galaxies would lead to an average shift of 0.24 dex to the right in the Kennicutt-Schmidt law, and 0.24 dex right and down in the extended Schmidt law.
-This does not result in a significant disagreement with the observed relationships, but would constitute a quantitative change to the observed fits if our $f_{\rm H_2}$ is robust for observed low-mass, low-metallicity dwarf galaxies.
-
-Interestingly, in this low-dust regime, our H$_2$ formation is dominated by the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
+As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, within this range.
+H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
+The gas-phase reaction dominates in our low-metallicity galaxy over the other two channels by several orders of magnitude.
 In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
-Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionization of H and H from the UV background.
-This has the seemingly counterintuitive effect that turning off the UV background actually decreases the formation rate of H$_2$, as confirmed in test simulations.
-In a test simulation ignoring all H$^{-}$ reactions, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.
-Although we ignore the visible component of our ISRF, capable of destroying H$^{-}$, this is included from the UV background.
-
-This explains our disagreement with the simulations in \citet{Hu2016} and \citet{Hu2017}, which find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
-Although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
-Our model suggests that H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies.
-It is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, but the total amount of H$_2$ formed is perhaps surprising.
-However, the rate coefficients associated with gas-phase H$_2$ formation are uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
+Thus the presence of some ionizing background is required to generate the molecular fractions we find in our simulations, as confirmed in test simulations run only to the onset of first star formation.
+
+In contrast, \citet{Hu2016} and \citet{Hu2017} find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
+However, although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
+Our model suggests that both H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies.
+Indeed it is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, though it is worth noting that the rate coefficients associated with gas-phase H$_2$ formation are still uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
 Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
@@
 Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
+As discussed in Section~\ref{sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
 However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
@@
 While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
-We find 13.7\% of all metals lie within 1 kpc of the center of our galaxy, 26.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 38.6\% outside $R_{\rm vir}$.
+We find 5.3\% of all metals lie within 1 kpc of the center of our galaxy, 24.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 51\% outside $R_{\rm vir}$.
 This is consistent with previous works, but this is again an evolving quantity.
@@
 
-We demonstrate the effect of varying resolution on three different results in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}, comparing the star formation rate, mass evolution, and metal ejection/retention fractions between our fiducial high-resolution simulation, two runs at 3.6 pc with different initial SN driving rates, and a final run at 7.2 pc.
-The physics in each of these simulations remains the same with the exception of our star formation threshold.
-Since star formation is set to occur at gas densities where the Jeans mass is unresolved at the maximum resolution, our star formation algorithm is tied to resolution.
+\textbf{Significant changes to the lower resolution runs and the comparison to our fiducial simulation with the change to the H$_2$ production:}
+
+We demonstrate the effect of varying resolution in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}.
+We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines).
+The physics in each simulation remains the same with the exception of star formation, which employs a resolution-dependent density threshold.
 A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.
+As a result, the time at which star formation first occurs varies between the simulations, but we again define t = 0 as the time of first star formation in each simulation.
 
@@
 
-Figure~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, it does not do so dramatically.
-We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation and driven mostly by variation in the initial star formation rate of the galaxy.
-In each of the lower resolution runs, the SFR is larger within the first 100~Myr.
-This is because, at lower resolution, the initial driving SN are less resolved and less effective at preventing uniform collapse of the gas disk.
-The 3.6~pc run with a factor of two higher initial SN driving rate demonstrates that an increase in the effectiveness of the supernova at lower resolution brings the evolution much closer to that seen at our highest resolution run.
+Figure~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
+We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
+The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs.
 We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Figure~\ref{fig:SN histogram}.
 However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
-This is shown more clearly comparing the left and right panels of Figure~\ref{fig:phase_resolution}, the temperature-density phase diagrams for the 3.6 and 7.2 pc.
-There is clearly much less hot gas (T $> 10^6$~K) in our lowest resolution run.
-
-The largest qualitative difference between these runs is the H$_2$ mass.
-As discussed in this work, the H$_2$ mass fraction of our fiducial run is quite high, driven by significant H$_2$ production from gas-phase reactions and the preferential retention of cold, dense H$_2$ gas in feedback driven outflows.
-However, each of the lower resolution runs produce less H$_2$ (about 40\% less) than our fiducial run.
-This is certainly an issue in interpreting the generality of our large H$_2$ mass fractions, and requires more tests to confirm.
-However, it is not unreasonable to expect that the H$_2$ production occurs most effectively at densities not captured in the 3.6~pc and 7.2~pc runs.
-This suggests that most of our H$_2$ production in the fiducial run occurs in gas with densities above 50~cm$^{-3}$.
-As shown in Figure~\ref{fig:phase_resolution}, the maximum density is clearly lower in each of the two lower resolution runs.
+
+Generally ineffective feedback leads to increased, not decreased, star formation rates.
+However, the lower resolution run has the lowest SFR.
+The source of this difference is likely related to the ability to resolve dense, cold gas in the lower resolution simulations.
+In particular, the low resolution simulation clearly is unable to resolve the densities at which gas-phase H$_2$ formation becomes efficient, leading to significantly lower H$_2$ fractions (middle panel) and lower cooling rates.
+In addition, whatever H$_2$ does form at these lower resolutions exists at lower gas densities than in our fiducial run, and is less well protected by self-shielding effects.
+This is shown clearly in the significant plummet in the H$_2$ mass during the phase of first star formation that is less severe in our fiducial run.
+In this low metallicity regime, where H$_2$ is an important coolant, the ability to resolve the densities responsible for H$_2$ formation and self-shielding is important.
+
+Theses differences in densities are shown clearly by comparing Figure~\ref{fig:phase_diagram} with Figure~\ref{fig:phase_resolution}.
+Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.
+In the 7.2~pc run, the gas phases are notably less distinct, with gas more evenly smoothed out in the mulit-phase region between cold, dense gas and warm, ionized gas.
+We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature cieling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.
 
@@
 
-Finally, each of the lower resolution runs retain a similar fraction of their produced metals in their disks (black curves in right panel of Figure~\ref{fig:resolution_study}), but all of the lower resolution runs contain about a factor of two less than our fiducial simulation.
-The fraction leaving the virial radius of the galaxy is higher in the lower resolution runs, again within a factor of two of our fiducial resolution.
-This is an interesting difference, as the resolution decrease primarily affects the disk of the galaxy; little to none of the halo volume is refined to the highest resolution, and so should be unaffected by this change.
-This suggests that this difference is a secondary effect, driven by changes to the particular SFH and disk structure between the various resolutions.
+Finally, the metal retention fraction (right panel) between the fiducial and 3.6~pc runs are quite similar, but is significantly higher for the lowest resolution simulation.
+It is likely, however, that this is a result of the lower SFR in the 7.2~pc run and is not directly a resolution effect.
+This also affects the fraction of metals ejected outside the virial radius, with less metals being ejected in the lower resolution runs.
 

### 2018-07-11 main.tex
Final changes to paper and figures EXCEPT the radiation comparison section

@@
 In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
-This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possibly models that are not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
-While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution to reduce.
+This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
+While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficienty high spatial resolution.
 Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
-Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b}.
+Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b, KrumholzTing2018}.
 Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
@@
 \textbf{This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
-At high star formation rate densities, an undersampled IMF in a single low mass star particle can be ompensated for by having many adjacent star particles.} Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
+At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.} Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
 The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
@@
 This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
-This paper is the first in a series examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
+This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
 We describe each mode of our multi-channel feedback
@@
 We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick.
-Specifically, simulations presented here were conducted at changeset 5cc7cea.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
+Specifically, simulations presented here were conducted at changeset 7001d99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
 We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}).
@@
 
+\textbf{Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas.
+These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution.
+At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr.
+We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$.
+These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions.
+This threshold decreases the required run-time by factors of a few.
+The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)}
+
 \subsection{Chemistry and Cooling Physics}
@@
 
-We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset 59adc76b3130.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes.
+We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset c2c0faf.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes.
 We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.
@@
 We ignore HeII photoionization from the UV background entirely.
-{\bf For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (, eV) and H$_2^+$ destruction (,eV) by the same shielding factors computed for HI and HeI shielding.}\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
+{\bf For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.}\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
 As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
@@
 These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}.
-We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in future work.
+
+% AE: removing this as it may no longer be the case
+%We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in future work.
 
@@
 These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
-We note that this initial driving is somewhat ad hoc in that we do not include any other effects from the stellar population that would have caused these SNe.
-
-We emphasize here that our model, with no initial stellar distribution, is not intended to reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
+We note this initial driving is ad hoc in that we do not include other effects from the stellar population that would have caused these SNe.
+
+We emphasize here that our model, with no initial stellar distribution, is not intended to identically reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
 In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations.
@@
 Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run.
-The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical heigh $|z| < 200$~pc relative to the center of the galaxy.
+The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical height $|z| < 200$~pc relative to the center of the galaxy.
 ISM properties are calculated considering only the gas contained within the disk of the galaxy.
@@
 Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.
-All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset 66452ba.
+All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset dd76ad10.
 
@@
 The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
-This figure shows the scale height of all gas in the disk, averaged over 40~Myr periods centered on each given time.
-Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--200~pc.
-Towards the end of the simulation time, the half-light radius is $390 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
-Although the disk remains thin beyond the half-light radius, with a scale height of around 40--60~pc, it is fully resolved at all radii.
-By the end of the simulation, the majority of the gas has a scale height of $\sim$100~pc.
-
-Constraining the gas scale height in ultra-faint dwarf galaxies observationally, to compare to our simulations, is challenging.
+This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time.
+Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--120~pc.
+Towards the end of the simulation time, the half-light radius is $391 \pm 19$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
+Although the disk remains thin beyond the half-light radius, with a scale height of around 50~pc, it is fully resolved at all radii.
+By the end of the simulation, the majority of the disk has a scale height of $\sim$100~pc.
+
+Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging.
 For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
+\textbf{In the final column of Figure~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
+With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
+At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$.
+These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.}
 
@@
 
-Interestingly, there is significant structure well above the gas disk in our model, in the form of dense clouds and filamentary features, as seen in the edge-on projections.
-These cold gas clumps appear to have typical sizes on order of $\sim 10$~pc, but with lower density tails that can extend up to 100 pc.
-These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy.
-These clumps have typical velocities on order of a few to tens of kilometers per second, and appear to survive for 10--100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk.
-The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work.
-% AE (left out): This is exciting given recent \citep[e.g.][]{Zheng2017} and ongoing \citep{Zheng2017HST} observational observational work examining the disk-halo interface in nearby galaxies.
-
 \begin{figure}
@@
 The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
-For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% by the end of the simulation.
-The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy due to feedback-driven galactic winds.
+For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% at 500~Myr.
+The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy from feedback-driven galactic winds.
 During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM.
@@
 We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content.
-\textbf{We further note that no region in our galaxy is more than 0.5\% molecular}.
+\textbf{We further note that no region in our galaxy is more than 50.0\% molecular}.
 See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-These presence of phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
+The properties of these phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
 Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.
@@
 We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
-\textbf{Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:methods}) is seen clearly by the slight horizontal feature at high temperatures.}  The boxed regime in the lower right corner shows our star formation density and temperature threshold.
+\textbf{Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left.}  The boxed regime in the lower right corner shows our star formation density and temperature threshold.
 Gas in this regime is rapidly consumed by star formation and subsequent feedback.
-Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does show up in this time average.
+Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average.
 We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work.
@@
 The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
-The WNM is initially comparable to the CNM, only comprises a mass fraction of about 0.1 by the end of the run.
+The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run.
 The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation.
 During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1.
-Although the CNM dominates the mass fraction, it is a negligable component of the ISM volume.
-The volume is generally dominated by the WIM, but the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
+Although the CNM dominates the mass fraction, it is a negligable component of the ISM volume, which is WIM dominated.
+However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
 Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
@@
 \includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
-\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM.}
+\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
 \label{fig:ISM_evolution}
@@
 Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-neglibable amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$.
-The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominated at velocities above 200 km s$^{-1}$.
+The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominating at velocities above 200 km s$^{-1}$.
 The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling WIM and HIM, consistent with the results in \citet{Hu2016,Hu2017}.
@@
 Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich,
-star forming, low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
+star forming, low-mass dwarf galaxy, with an observable HII region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
 Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
@@
 When considered in isolation, stellar winds are an important source of pre-SN feedback and can dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
-However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}, unless densities near the ionizing source are high enough to trap the  \ion{H}{2} region in the source cell.
-In that case, they can clear out a cavity to allow initial establishment of the \ion{H}{2} region.
+However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}, unless densities near the ionizing source are high enough to trap the  HII region in the source cell.
+In that case, they can clear out a cavity to allow initial establishment of the HII region.
 
@@
 \item Multi-channel feedback is effective in this galaxy in regulating star formation to occur at a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
-See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}.
+(See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).
 
@@
 \item 
-Only $\sim$10\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of ultrafaint dwarfs.
-By the end of the simulation $\sim$50\% of the remaining metals remain within the virial radius (but outside the galaxy) and $\sim$40\%
+Only $\sim$4\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of ultrafaint dwarfs.
+By the end of the simulation $\sim$45\% of the remaining metals remain within the virial radius (but outside the galaxy) and $\sim$50\%
 have been ejected beyond the virial radius. 
-The fraction in the disk remains fairly constant towards the end of the simulation, but the metals in the halo are still evolving.
+%The fraction in the disk remains fairly constant towards the end of the simulation, but the metals in the halo are still evolving.
 (See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
@@
 This is comparable to the resolution limit of the diffuse HI in observed, gaseous ultrafaint dwarfs.
-(See Figure~\ref{fig:scale_height}).
-
-\item The ISRF of our galaxy varies strongly in time, by orders of magnitude, though it has a relatively uniform radial profile averaged over tens of megayears.
+At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8--4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Figure~\ref{fig:scale_height}).
+
+\item The ISRF of our galaxy varies strongly in both space and time by orders of magnitude.
 It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
@@
 \item 
-%mm3 (\textbf{Possibly remove depending on follow up}) Formation of a significant amount of H$_2$ 
-     A significant amount of H$_2$ forms
-through gas phase reactions with H$^-$.
-This dense gas is more resistive to feedback driven outflows than the less dense gas in the galaxy.
-This leads to high molecular gas fractions, with an H$_2$ mass comparable to that of HI by the end of the simulation.
-This result requires further investigation to determine if this behavior is universally true of ultrafaint dwarf galaxies.
-(See Figure~\ref{fig:ISM_evolution}.)
+We find H$_2$ fractions below 5\% in our dwarf galaxy, consistent with the poor constraints on molecular gas formation in low metallicity dwarf galaxies.
+This H$_2$ forms entirely through gas-phase reactions facilitated by H$^{-}$ in self-shielding regions; H$_2$ formation on dust grains and in the three body reaction are both insignificant.
+Cold, neutral hydrogen dominates the mass of our galaxy.
+While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Figure~\ref{fig:sfr_mass_evolution} and Figure~\ref{fig:ISM_evolution}.)
 
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \label{fig:stellar radiation properties}
-\end{figure}
+\end{figure*}
 
@@
 
-The left panel of Figure~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our simulations.
+The left panel of Figure~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
 As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
@@
 We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each SN.
-As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but up to 10\% are somewhat under-resolved.
+As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but up to 8.3\% are not well resolved and 2.0\% are completely unresolved (below a single cell width).
 In general, these are SN explosions from the most massive (i.e.
@@
 We do not expect that resolving these SNe will dramatically alter our results.
-However, we note that using our feedback model at resolutions much less than a few parsecs will require adopting a different injection mechanism.
+However, we note that using our feedback model at resolutions much less than a few parsecs will require implementing an different injection mechanism.
 
@@
 \label{fig:SN histogram}
-\end{figure}
+\end{figure*}
 
@@
 \label{fig:cooling comparison}
-\end{figure}
+\end{figure*}
 
@@
 \label{fig:cooling}
-\end{figure}
+\end{figure*}
 
@@
 In the 7.2~pc run, the gas phases are notably less distinct, with gas more evenly smoothed out in the mulit-phase region between cold, dense gas and warm, ionized gas.
-We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature cieling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.
+We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature ceiling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.
 

### 2018-07-11 main.tex
fiddling with acknowledgement acronyms

@@
 was partly funded by NASA  grant NNX14AP27G.
-We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, by the NASA High-End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center, Columbia University, and the Flatiron Institute.
+We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing
+%mm4 (HEC) 
+Program through the NASA Advanced Supercomputing 
+%mm4 (NAS) 
+Division at Ames Research Center, Columbia University, and the Flatiron Institute.
 This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.

### 2018-07-11 main.tex
Removing old commented out blocks of text. leaving a few that may still be somewhat relevant as a note

@@
-%mm2 substantive changes marked with this comment tag, minor changes and wordsmithing done silently.  12-15 Feb
-%mm3 since Greg has already read this, I have removed commentary as I go.  substantive changes now marked with %mm3 13 Mar 18
 %\documentclass[twocolumn]{aastex61}
@@
 These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
-
-%\textbf{rework here to the end... focus less on numerics}
-% However, there is a general lack of numerical diversity in these works, as a majority are implemented in some flavor of smoothed particle hydrodynamics (SPH) schemes.
-Given the known differences between hydrodynamics implementations \citep{Agertz2007,AGORA,AGORA2}, extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.
-% AE (incorrect statement): Additionally, grid-based schemes are able to generally avoid issues with metal mixing, one of the largest model uncertainties in standard SPH codes.
-
-%mm2 I think there does need to be some introduction to this discussion:
 
@@
 For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
-% Since we assume a dust abundance that depends only on metallicity, we do not track dust destruction or creation, which may play an important role regulating detailed ISM properties.
-(Vogelsberger is working on this directly but no papers yet...
-will cite if it gets submitted by then)
 
@@
 We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
-% AE: responding to mm3, this avoids aliasing:
 We use the same Monte Carlo sampling method as used in our stellar winds to map the spherical injection region to the grid.
@@
 
-%AE (taking this out...
-looked into more detail in paper and they argue this, but frankly I do not see how they reach this conclusion from their Appendix plots): \citet{Dale2012} demonstrated that uncertainties on the order of a few in the ionizing radiation rates are not significant in giant molecular cloud (GMC) scale simulations.
-%Generally, the ionizing fluxes from high temperature black bodies underestimate the OSTAR2002 flux, and lower temperature black bodies overestimate the flux by a factor of 2-5 and 10-1000 respectively.
-
 Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}).
@@
 
-% AE: removing this as it may no longer be the case
-%We will explore the effect of adopting different dark matter potentials within the large range of possible profiles in future work.
-
 Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
@@
 \includegraphics[width=0.475\linewidth]{mass_evolution}
-\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins (left).
-Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.
-Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.}
+\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins.
+Broken portions of this histogram are time periods with no star formation or supernovae.
+Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.
+Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
 \label{fig:sfr_mass_evolution}
@@
 \end{figure}
-
-%\textbf{AE: Took plot and discussion of outflow metallicities out and replaced with metal mass loading factor (below)}
-%In Figure~\ref{fig:outflow_metallicity} we show the average ISM metallicity (black), halo metallicity (blue), and outflow metallicities (orange) at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
-The ISM metallicity evolves minimally from the initial conditions in this time, while the halo and outflow properties change significantly.
-It is apparent from this figure that the outflows are preferentially metal enriched, as the halo increases in metallicity by a factor of $\sim 2$ in the simulation time.
-Although most of the gas mass in the halo (outside the disk) remains within 0.2 $R_{\rm vir}$ (see Section~\ref{sec:obs_metals}), the mass that does make it to the outer reaches of the halo or beyond is metal enriched by a factor of $\sim$5--6 compared to the ISM.
-This is in contrast with the results from \citet{Muratov2017}, which generally show $Z_{\rm outflow} \simeq Z_{\rm ISM}$ at $0.25~R_{\rm vir}$ and $Z_{\rm outflow} < Z_{\rm ISM}$ at $1.0~R_{\rm vir}$, though both with some scatter that reaches $Z_{\rm outflow} > Z_{\rm ISM}$, especially at high redshift.
-However, we note that our simulations certainly do not contain a cosmologically realistic circumgalactic medium, nor do they include ongoing cosmological accretion of pristine gas.
-Mixing of outflowing, metal enriched gas and pristine inflows will lower the typical halo and outflow metallicities, particularly at large radii.
-
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.95\linewidth]{metallicity_evolution}
-%\caption{The mass-weighted average metallicity of our dwarf galaxy's ISM, halo, and outflowing gas at 0.1 (solid), 0.25 (dashed), and 1.0 (dotted) $R_{\rm vir}$ over the simulation time.
-The halo is defined as the region outside of the disk, yet inside the virial radius.}
-%\label{fig:outflow_metallicity}
-%\end{figure}
 
@@
 A more detailed analysis is beyond the scope of this work, but we plan to investigate this point, and potential observational consequences for stellar abundances, in future work.
-% reference my other paper if it is ready-ish by the time I submit this one.
-
-%Observations of Local Group dwarf galaxies have shown that they retain very little of the total amount of metals they are expected to have produced, given their star formation histories (see Section~\ref{sec:observation}).
-In Figure~\ref{fig:species_fractions} we show the fraction of metals retained within the disk or expelled into the halo of our galaxy over time, along with a breakdown of the locations of each metal species by the end of the simulation.
-As shown in the top panel, a majority of each metal tracer species is found outside the disk of the galaxy, in the galaxy halo.
-In total, \textbf{85\%} of the tracer metal species produced lie outside of the disk of our galaxy.
-Interestingly, the exact fraction is not uniform across metal species.
-
-%\textbf{Use Ba here as example element, not N}
-%Most notably, N is preferentially retained by the galaxy over the other species.
-Roughly \textbf{35\%} of N produced remains in the disk, as compared to \textbf{15\%} of O or Fe, for example.
-This difference is entirely feedback driven.
-At this metallicity, N is produced only in the stellar winds of stars between 8 and 10 M$_{\odot}$, with little to no production in SNe.
-The rest of the species either have very little stellar wind production, are produced solely in SNe, or have similar production levels between both SNe and stellar winds (like O, for example).
-The typically lower injection energies of N into the galaxy compared to the SNe produced elements means N is preferentially retained within the ISM, and not as effectively ejected through outflows.
-In truth, the stars that produce N do eventually explode as SNe, sweeping up some fraction of the wind produced N into outflows.
-However, clearly some of this N mixes more effectively within the ISM than the other metal species.
-How abundance variations like this evolve over longer timescales and with varying feedback physics is the subject of ongoing work.
-% AE: possibly cite letter here if we have it done
-
-%\begin{figure*}
-%\includegraphics[width=0.9\linewidth]{species_bar.png}\\
-%\includegraphics[width=0.9\linewidth]{species_bar_disk.png}
-%\caption{The fraction of each species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).}
-%\label{fig:species_fractions}
-%\end{figure*}
-
-%The bottom panel illustrates where these metals are partitioned within the ISM of the galaxy at the end of the simulation time.
-The CNM contains roughly 50-60\% of each species, with the CNM and WNM together accounting for most of the metals in the galaxy.
-The WIM contains only $\sim$ 10\% of each species, with the HIM containing very little.
-This may be counterintuitive given that most metals are initially injected into the galaxy in either the WIM or HIM phases.
-However, the disk metals represent only a small fraction of the total metals produced.
-Much of the metals are effectively removed from the disk into the halo (see Section~\ref{sec:outflows}).
-It is apparent that the remaining metals quickly mix or cool into denser gas phases.
-
-%\subsection{Stellar Abundances}
-%\label{sec:stellar properties}
-
-% By initializing the metallicity of our galaxy to a non-zero value (XXX), yet setting each of the metal tracer species to initial mass fractions of 10$^{-20}$ (effectively zero abundance), the species abundances in our galaxy are somewhat contrived.
-However, this was done to be able to unambiguously follow how self-consistently produced chemical enrichment evolves over time.
-In effect, what each individual metal field traces is a ``delta'' abundance, or change in metal mass fraction relative to an arbitrary initial condition.
-
-%\textbf{This section needs work.
-As per discussion with Keith and Kathryn, displaying abundance evolution like this is confusing and misleading.
-Switch to discussion of mass / abundance fraction evolution of individual specie(s).}
-%We plot the $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ ratio for all star particles in our simulation that are ``alive'' in Figure~\ref{fig:stellar_abundance}.
-This represents stars that have not gone SNe or have otherwise formed a compact object.
-Here, $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$, and the notation [X/Y] denotes the ratio of the abundance of species X over Y, relative to the solar value, or log([X/Y]) = log(X/Y) - log(X$_{\odot}$/Y$_{\odot}$).
-All stars are colored by their age.
-
-%\begin{figure}
-%\includegraphics[width=0.95\linewidth]{alpha_over_fe_hist}
-%\caption{The $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$
-%diagram for all stars in our simulation, colored by their age. Here, we define $\alpha = (\rm{O} + \rm{Mg} + \rm{Si})/3.0$. Each histogram shows counts, normalized to the peak in each distribution.}
-%\label{fig:stellar_abundance}
-%\end{figure}
-
-%As expected, there is a noticeable trend of stellar age with [Fe/H]; especially in our case as the overall iron abundance is gradually increasing, yet we do not have any accretion of primordial material.
-Interestingly, the few stars with the highest [Fe/H], between -3 and -2, are not the most recently formed; the most recent star formation is clustered around [Fe/H] between -3 and -4.
-
-%We note the ``knee'' like feature at very low [Fe/H] is not the characteristic knee seen in $[\alpha / {\rm Fe}]-[\rm{Fe}/\rm{H}]$ space, corresponding to the period when iron enrichment from SN Type Ia begins to make a significant contribution to the galactic chemical evolution.
-This generally occurs after roughly 1 Gyr of stellar evolution, far longer than the \textbf{170} Myr simulated here.
-% The origin of this feature and the longer term chemical evolution of this galaxy will be investigated in a future work.
 
@@
 
-%\subsection{Detailed Dust Model}
-%\textbf{Should we discuss this? If so I definitely need more info and references - AE}.
-%The dust content of our galaxy is modeled only approximately, scaling with the cell-to-cell variations in gas metallicity.
-Explicitly following the dust content in our galaxy, even crudely, could introduce significant variations in local cooling and heating rates.
-Accounting for metals trapped in a dust phase would produce additional variations in the cooling rates and potentially changes to the galactic chemodynamical evolution.
-
 \subsection{Detailed Stellar Evolution and Binary Stars}
@@
 By the end of the simulation $\sim$45\% of the remaining metals remain within the virial radius (but outside the galaxy) and $\sim$50\%
-have been ejected beyond the virial radius. 
-%The fraction in the disk remains fairly constant towards the end of the simulation, but the metals in the halo are still evolving.
-(See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
+have been ejected beyond the virial radius. (See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
 
@@
 
-% We use a spherically symmetric thermal dump method of modelling SN explosions.
-This is the simplest method possible, but can often result in rapid overcooling of the heated gas, effectively underestimating the effectiveness of SN feedback.
-Solutions to this problem can often be ad hoc (e.g.
-briefly turning off cooling) in low resolution, large cosmological simulations.
-However, recent work has shown injecting some fraction of this thermal energy directly as kinetic energy or momentum alleviates this issue without sacrificing physical realism.
-However, it has been shown that simple thermal energy injection is sufficient for parsec scale (or better) resolutions, provided the SN do not occur in very high density regions; if resolved, thermal injection converges with kinetic energy / momentum injection methods.
-Resolving these explosions with thermal energy injection alone depends ultimately on the grid resolution, background density and ISM structure, the background cooling/heating physics used, and the size and shape of the injection region.
-Here, we perform a resolution test of our thermal injection method over four uniform densities (0.1 \ccunit, 1.0 \ccunit, 10.0 \ccunit, and 100.0 \ccunit) for both a 8.0 \msun and 25.0 \msun star, comparing to both the analytic solution and results using kinetic energy injection from \citet{Simpson2015}.
-These results are presented in Figure~\ref{fig:SN tests}.
-We note these are heavily idealized cases.
-In general in our simulations, pre-SN feedback from stellar winds and radiation will reduce the typical densities within which our SN explosions occur.
-In addition, SN will generally be clustered, meaning each SN will reducing the typical density for each subsequent SN in that region.
-In Figure~\ref{fig:SN histogram} we plot a histogram of the typical peak and average gas densities in the 3 cell injection region of each SN in the XXXX XXXXX simulation.
-As shown, some of the SN explode in high density regions around 100 \ccunit and are likely under-resolved, but a majority will be resolved.
-
 \begin{figure*}
@@
 
-%\section{Stellar Wind Model}
-%\label{appendix:stellar winds}
-%
-% This is still probably a good idea to do at some point, but save for if/when
-% we have a paper using full stellar winds where this matters - AE (Jul. 19 2017)
-%
-%Discuss wind properties and evolution in a hand full of isolated star runs (don't need to do a resolution study...
-kinda) and compare to Weaver et.
-al.
-1977 analytic results.
-Really we won't resolve the winds at high densities, but that is OK...
-as long as the wind bubbles are > 3*dx (the injection size) we are generally going to be fine...
-aka as long as the SN explosion goes off in wind bubble gas and not dense ISM that shouldn't be there..
-
 \setcounter{figure}{0}
@@
 \label{appendix:cooling}
-%AE: 2/23 Old version of text... keeping around for now:
-% For comparisons to other works, we present the cooling curve used in our simulations here.
-This cannot be done exactly, however, as primordial cooling and heating is computed cell-by-cell using the non-equillibrium chemistry solver in \textsc{Grackle}.
-These rates are not interpolated from the generated \textsc{CLOUDY} tables as is done for the metal line cooling rates.
-In addition, although these tables do include the effect of the UVB, they do not account for local variations in the ISRF from stellar radiation.
-However, we present the combined primordial and metal line cooling rates from the generated \textit{CLOUDY} tables in Figure~\ref{fig:cooling} at three characteristic densities for $Z = 0.01$Z$_{\odot}$.
-As discussed in Section~\ref{sec:methods}, we account for self-shielding against the UVB in both our simulations and the computed \textsc{CLOUDY} models shown in this figure.
-
-%AE: 2/23 Old version of text... keeping around for now:
-%To derive the diffuse cooling and heating rates used in the simulations, we make two approximations.
-First, the primordial cooling and heating rates shown here are those returned by \textsc{Cloudy}, but only the tabulated \textsc{Cloudy} metal-line cooling and heating rates are used.
-The primordial heating and cooling rates are calculated self-consistently using the non-equilibrium chemistry solver and the self-shielding approximation from radiative transfer simulations given in \citet{Rahmati2013}.
-However, given that we remove the optically thin assumption when computing the \textsc{Cloudy} tables, the rates shown should be comparable to the locally varying cooling curve in the simulations.
-Second, this figure ignores the contributions to the heating rate from the variable interstellar radiation field, namely the stellar contribution to photoelectric heating, heating from Lyman-Werner dissociation, and ionization heating.
-We describe how we obtain the metal line cooling rates below and quantify the change in using these updated tables.
-%Therefore, the heating rates shown are approximate lower limits to the true heating experienced by any given cell in the simulation.
-
-%AE: 2/23 Old version of text... keeping around for now:
-%Figure ~\ref{fig:cooling} shows the combined primordial and metal line cooling and heating rates at three characteristic densities for $Z = 0.01 $Z$_{\odot}$.
-The Figure indicates the regime at low temperatures where heating dominates over cooling.
-The curve as shown includes only the $z = 0$ \citet{HM2012} metagalactic UV background.
 
@@
 
-%\section{Pre-SN Feedback with and without radiation}
-
 %\section{Code}
@@
 
-%\appendix
-%\section{appendix section}
 \label{lastpage}

### 2018-07-11 main.tex
One more comment removed

@@
 \begin{abstract}
-%\textbf{CHANGE: Cleaned up a few sentences. better intro + last sentence. added wind caveat. removed large H2 content mention (should I put this last one back?).}
-%Galactic chemical evolution is driven through stellar feedback and its ability to drive metal mixing within the interstellar medium (ISM) and beyond the galaxy in outflows.
-However, we are far from a complete understanding of feedback and galactic chemodynamics in general.
 In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.

### 2018-07-11 main.tex
Fixing comments from Mordecai's quick look through on 7-11. Still need to edit / fix the column density

@@
 We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content.
-\textbf{We further note that no region in our galaxy is more than 50.0\% molecular}.
-See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
+\textbf{By this definition, although our galaxy certainly contains molecular hydrogen, molecular gas as a phase does not exist; the peak f$_{\rm H_2}$ in any single cell remains below 30\%.} See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
 The properties of these phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
@@
 The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
-We have compared our cooling curves to those used in \citep{Hu2017} (C.
-Hu, private communication) and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.
+We have compared our cooling curves to those used in \citep{Hu2017} and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.
 
@@
 \textbf{The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
-At any given radii, there is over a two order magnitude variation in the ISRF during this period of time.}
+At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.}
 
@@
 Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
-As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, within this range.
+As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range.
 H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.

### 2018-07-12 mnras_template.tex

@@
 
-\begin{figure}
-\includegraphics[width = 0.99\linewidth]{fgas_mstar_binned_IQR_logged.png}\\
-\includegraphics[width = 0.99\linewidth]{gasless_fraction_mstar.png}
-\caption{{\bf Top:} The running median of f$_{\rm gas}$ as a function of stellar mass for each dataset with shading denoting the inner quartile range of each.
+\begin{figure*}
+\includegraphics[width = 0.33\linewidth]{fgas_mstar_binned_IQR_logged.png}\\
+\includegraphics[width = 0.33\linewidth]{MHI_Mstar_binned_IQR.png}
+\includegraphics[width = 0.33\linewidth]{gasless_fraction_mstar.png}
+\caption{{\bf Left:} The running median of f$_{\rm gas}$ as a function of stellar mass for each dataset with shading denoting the inner quartile range of each.
 Unlike in Figure~\ref{fig:fgas mstar 2D}, this includes galaxies with zero neutral gas mass.
-{\bf Bottom:} The fraction of galaxies per stellar mass bin for each dataset that do not contain any neutral gas.
+{\bf Middle} The running median of gas mass as a function of stellar mass for each dataset with shading denoting the IQR.
+{\bf Right:} The fraction of galaxies per stellar mass bin for each dataset that do not contain any neutral gas.
 The percent of all galaxies without gas in each dataset is shown in the legend.}
 \label{fig:linear fgas mstar}
-\end{figure}
+\end{figure*}
 
@@
 \caption{Same as Figure~\ref{fig:fgas DSFMS}, but separated into stellar mass bins.}
+\label{fig:fgas DSFMS panel}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width = 0.99\linewidth]{fgas_DSFMS_2dhist_count_log_fgas.png}\\
+\caption{2D histogram of fraction of galaxies in a given gas fraction and distance from SFMS bin.}
 \label{fig:fgas DSFMS panel}

### 2018-07-12 mnras_template.tex
Update on Overleaf.

@@
 \begin{figure*}
-\includegraphics[width = 0.33\linewidth]{fgas_mstar_binned_IQR_logged.png}\\
-\includegraphics[width = 0.33\linewidth]{MHI_Mstar_binned_IQR.png}
-\includegraphics[width = 0.33\linewidth]{gasless_fraction_mstar.png}
+\includegraphics[width = 0.3\linewidth]{fgas_mstar_binned_IQR_logged.png}
+\includegraphics[width = 0.3\linewidth]{MHI_Mstar_binned_IQR.png}
+\includegraphics[width = 0.3\linewidth]{gasless_fraction_mstar.png}
 \caption{{\bf Left:} The running median of f$_{\rm gas}$ as a function of stellar mass for each dataset with shading denoting the inner quartile range of each.
@@
 \begin{figure*}
+\includegraphics[width = 0.99\linewidth]{fgas_DSFMS_2dhist_count_log_fgas.png}\\
+\caption{2D histogram of fraction of galaxies in a given gas fraction and distance from SFMS bin.}
+\label{fig:fgas DSFMS panel}
+\end{figure*}
+
+\begin{figure*}
 \includegraphics[width = 0.99\linewidth]{fgas_DSFMS_binned_IQR_logged.png}\\
@@
 \begin{figure*}
-\includegraphics[width = 0.99\linewidth]{fgas_DSFMS_2dhist_count_log_fgas.png}\\
-\caption{2D histogram of fraction of galaxies in a given gas fraction and distance from SFMS bin.}
+\includegraphics[width = 0.49\linewidth]{MHI_Mstar_binned_IQR_bradford_fgas_cut}
+\includegraphics[width=0.49\linewidth]{fgas_mstar_binned_IQR_logged_bradford_fgas_cut.png}
+\caption{Running medians of simulated galaxies in comparison to isolated galaxies from Bradford et.
+al.
+2015 and the xGASS survey.
+The same Bradford et.
+al.
+2015 limiting gas fraction thresholds were applied to all plotted data.}
 \label{fig:fgas DSFMS panel}

### 2018-07-12 mnras_template.tex
Update on Overleaf.

@@
   EAGLE  & 1.81 &  9.70  & 100 & 0.70 (pkpc) & &  & \citep{Schaye2015,Crain2015} \\
-  Brooks & & &  & & & & \\
   SC-SAM & -  & - & & - & - & & \citep{Somerville2012,Porter2014}\\
@@
 Though each of these methods are similar, they likely do not produce identical results; characterizing the variation in galaxy gas properties caused by different ionization models is beyond the scope of this work.
-If H$_2$ is followed, we compute the gas mass of each galaxy as the total neutral hydrogen mass, or M$_{\rm gas}$ = M$_{\rm H_2}$ + M$_{\rm \ion{H}{i}}$ (EAGLE, MUFASA,Brooks), otherwise we take M$_{\rm gas}$ = M$_{\rm \ion{H}{i}}$ if H$_2$ is not tracked (Illustris, SC-SAM).
+If H$_2$ is followed, we compute the gas mass of each galaxy as the total neutral hydrogen mass, or M$_{\rm gas}$ = M$_{\rm H_2}$ + M$_{\rm \ion{H}{i}}$ (EAGLE, MUFASA), otherwise we take M$_{\rm gas}$ = M$_{\rm \ion{H}{i}}$ if H$_2$ is not tracked (Illustris, SC-SAM).
 This is a more faithful comparison than taking M$_{\rm \ion{H}{i}}$ alone, as the H$_2$ content in these works is derived directly from the \ion{H}{i} content.
@@
 
-\subsection{Brooks zooms}
-\label{sec:Brooks method}
-{\it ask Alyson for text}
-
 \subsection{Observational datasets}
@@
 \label{sec:results:SMHM}
-{\bf missing data at the moment}
-{\it Discuss SMHM relationship across the works.
-Discuss how their similarities / differences may affect how to interpret rest of paper (though they should probably be similar?).
-Possibly also shade with median gas fraction...
-this should be similar (maybe) across works}
+{\it Discuss SMHM relationship across data with references to original publications.
+Main story: Stellar properties of galaxies are similar (this is one example).
+Physics that generates these similar properties is very different.
+Leads into how this may affect related but un-tuned properties (i.e.
+gas).}
 
@@
 
-\subsection{Gas fraction vs stellar mass}
+\subsection{Gas Fraction and Gas Mass vs stellar mass}
 \label{sec:results:fg Mstar}
@@
 By nature of plotting gas fraction in logsapce, these diagrams exclude any galaxies with no gas content.
-To help clarify these populations across datasets we plot the median gas fraction (including galaxies with f$_{\rm gas}$ = 0) as a function of stellar mass in the top panel of Figure~\ref{fig:linear fgas mstar}, including the Brooks zoom-in simulations.
+To help clarify these populations across datasets we plot the median gas fraction (including galaxies with f$_{\rm gas}$ = 0) as a function of stellar mass in the top panel of Figure~\ref{fig:linear fgas mstar}.
 The shaded regions in each encompass the innerquartile range of each distribution; in stellar mass bins with less than 10 galaxies we plot points instead of the median curve.
@@
 \label{sec:results:SFMS fgas}
+
+\textit{ Establish definition of SFMS from Paper I. Discuss Figure~\ref{fig:SFMS fgas}. 
+\begin{enumerate}
+\item Significant variation among simulations as to where (relative to SFMS) galaxies are gas-rich and gas-poor.
+\item SFMS slope is somewhat correlated with EAGLE f$_{\rm gas}$ = 0.5 line. Is this significant? Should they be related?
+\item SCSAM galaxies at low stellar masses are gas rich above and below SFMS.
+\end{enumerate}
+}
+
+\subsubsection{Distance from the main sequence and gas properties}
+\label{sec:distance SFMS}
 

### 2018-07-12 main.tex
placeholder in conclusions
Update on Overleaf.

@@
 
-\author[A. Eemerick et. al.]{
+\author[A. Emerick et. al.]{
 Andrew Emerick,$^{1,2}$
@@
 Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
+\textbf{By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.}
 
@@
 
-\subsection{Importance of Ionizing Radiation}
-\label{sec:ionizing radiation}
-
-We investigate the relative importance of stellar ionizing radiation as a source of feedback in our galaxy with two comparison simulations.
-We ran one simulation with no stellar ionizing radition (NAME) and a second including only the local effects of stellar ionizing radiation, deleting all photons that travel more than 25~pc from their source star.
-Although radiative transfer is itself expensive, our simulation without ionizing radiation rapidly formed a significant amount of stars and ended up being more expensive than our fiducial run.
-We were only able to run this simulation for XXX Myr.
-We compare the star formation rate
-
-In the first case, we were unable to run the simulation for more than
-
-We compare our fiducial simulation, which includes stellar ionizing radiation traced with radiative transfer, and a simulati
-
 \section{Discussion}
@@
 This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
+\textbf{The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.} % AE: Mordecai, is this an appropriate clarification of this poitn?
 
@@
 SNe), as suggested by \cite{KrumholzTing2018}.
-This will be explored in more detail in future work.
-%mm3 (Emerick et. al. \textit{in prep.}). [only cite after submission]
+This will be explored in more detail in future work (Emerick et.
+al.
+\textit{in prep.}).
 \end{enumerate}
-
-%In future work we will investigate in detail how metal enrichment proceeds in low mass dwarf galaxies, including how metals move through the various phases of the ISM into star forming gas, and how individual metals move into halos.
-This will allow us to examine the role that each source of feedback plays in driving dwarf galaxy chemodynamics.
 

### 2018-07-12 main.tex
final updates for now

@@
 \includegraphics[width=0.98\linewidth]{log_NO_panel}
-            \caption{\textbf{NEED TO UPDATE:} Three slices in the mid-plane of our dwarf galaxy at an arbitrary time of 350~Myr after the start of star formation showing the variation in gas phase metal abundances.
-The left slice gives the ratio of the abundance between N and O, while the number density and temperature are shown on the right.
-}
+            \caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances.
+The left slice gives the ratio of the abundance between N and O, normalized to the solar abundance, while the number density and temperature are shown on the right.
+In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occured in the preceeding 5 Myr as black stars and orange diamonds respectively.}
 \label{fig:metal_slices}
@@
 As shown in the left panel, log(N/O) varies significantly over this section of the ISM with notable differences across the various phases and ISM structures.
-As expected, O is overabundant throughout the ISM, most strongly in the region of recent SN enrichment (top left, dark purple region in log(N/O) / dark red in temperature).
-However, the relative abundance of N increases significantly in the warmer phases, reaching equipartition (white color in log(N/O)) in many patches throughout the ISM.
-There are three regions in particular that are overabundant in N (green color).
+The hottest gas, dominated by recent supernova explosions is overabundant in oxygen, relative to solar (purple).
+However, the relative abundance of nitrogen increases in the WIM and WNM, being overabundant relative to solar (green).
 
@@
 This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
-A more detailed analysis is beyond the scope of this work, but we plan to investigate this point, and potential observational consequences for stellar abundances, in future work.
+A more detailed analysis is beyond the scope of this work, but we \textbf{investigate this in detail in Emerick et.
+al.
+(in prep.).}
 

### 2018-07-12 main.tex
typos

@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, \textbf{ with a molecular hydrogen mass fraction of only $\sim$ 0.3 \%.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, \textbf{ with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
 The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
@@
 Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average.
-We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work.
+% AE: Left this out since I don't have major plans to address this...... We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work.
 
@@
 \includegraphics[width=0.95\linewidth]{phase_diagram.png}
-\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gass interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr.
-The two red dashed lines show lines of constant pressure for guidance.
+\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gas interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr.
+The dashed lines are lines of constant pressure, separated by factors of 10.
 The region in the lower right corner indicates our density and temperature thresholds for star formation.}

### 2018-07-13 main.tex
updates

--- 2018-07-12 main.tex
@@
-%\documentclass[twocolumn]{aastex61}
-%\pdfoutput=1 %for arXiv submission
-\documentclass[fleqn,usenatbib,useAMS]{mnras}
-\usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{multicol}        % Multi-column entries in tables
-\usepackage{bm}		% Bold maths symbols, including upright Greek
-%\usepackage{pdflscape}	% Landscape pages
-
+\documentclass[twocolumn]{aastex61}
+\pdfoutput=1 %for arXiv submission
+\usepackage{amsmath,amstext}
 \usepackage[T1]{fontenc}
-\usepackage{ae,aecompl}
-\usepackage{newtxtext,newtxmath}
-
-%\usepackage{amsmath,amstext}
-%\usepackage[T1]{fontenc}
+\usepackage{apjfonts} 
 \usepackage[figure,figure*]{hypcap}
 
-\hypersetup{draft}
-%\usepackage{multirow}
-%\usepackage{mathtools}
-%\renewcommand*{\sectionautorefname}{Section} %for \autoref
-%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
-%\usepackage{graphicx}
-
-%\usepackage{apjfonts} 
-%\usepackage{natbib} % bibliography
-
-%\usepackage[active,floats,tightpage]{preview}
-%    \setlength\PreviewBorder{1em}
-
-%\shorttitle{Feedback with Individual Stars}
-%\shortauthors{Emerick, Bryan, Mac Low}
-\newcommand{\msun}{M$_{\odot}$}
-\newcommand{\ccunit}{cm$^{-3}$}
-
-%%%%%%%%%%%%%%%%%%\hypersetup{draft}
-% For bibtex
-
-\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
-
-\author[A. Emerick et. al.]{
-Andrew Emerick,$^{1,2}$
-Greg L. Bryan,$^{1,3}$
-and Mordecai-Mark Mac Low$^{2,1}$
-\\
-$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
-$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
-$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+\renewcommand*{\sectionautorefname}{Section} %for \autoref
+\renewcommand*{\subsectionautorefname}{Section} %for \autoref
+
+\shorttitle{Differential Metal Mixing}
 
@@
 
-\label{firstpage}
-%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
-
-%\author{Andrew Emerick}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\author{Greg L. Bryan}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-%\author{Mordecai-Mark Mac Low}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-
-%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}
+%\title{Evolution of Individual Metals in Galactic Winds and the ISM}
+
+% GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
+\title{Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies}
+
+\author{Andrew Emerick}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\author{{\it more...}}
 
 \begin{abstract}
-In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
-We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
-We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints.
-We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
-We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
-Effective feedback \textbf{drives outflows with a greater metallicity than the ISM}, leading to low metal retention fractions consistent with observations.
-Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
+Using a high resolution simulation of an isolated dwarf galaxy, accounting for stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy through galactic winds.
+For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal + power-law distribution.
+The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail.
+The PDF properties, and relative significance of these two components, vary within each ISM phase.
+Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component.
+In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe).
+This difference is driven by the differences in energetics between each source, particularly the poor coupling of AGB winds.
+Only 80\% of metals dominated by AGB enrichment are ejected through winds, even though 95\% of all metals leave the galaxy.
+In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae.
+We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
 \end{abstract}
 
-\begin{keywords}
-Galaxy -- Hydrodynamics -- Simulation -- Feedback
-\end{keywords}
+\keywords{}
 
 \section{Introduction}
-%
-% AE removed below.. MM suggested  skipping both pars.
-%
-%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade.
-Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc.
-\citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses.
-On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM.
-This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}.
-See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.
-%
-%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution.
-In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense.
-In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships.
-For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.
-
-Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution.
-Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
-There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
-%{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
-These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
-
-However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}.
-In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
-This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
-While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficienty high spatial resolution.
-Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
-Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b, KrumholzTing2018}.
-Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
-the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
-The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
-
-Increasing physical resolution reduces reliance on sub-grid physics for mixing.
-However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}.
-Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
-\textbf{This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
-At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.} Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
-The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
-
-We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies.
-The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms.
-We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
-%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies.
-\citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
-Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar winds from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
-We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar far ultra-violet (FUV) radiation, and Lyman-Werner dissociation from stellar radiation.
-
-Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime.
-This includes yields from massive and AGB stellar winds, and supernovae (SNe).
-In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
-This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
-This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
-We describe each mode of our multi-channel feedback
-in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.
-
-Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.
+% can I work "Currents of Space" into this paper somehow (Asimov)?
+Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (review refs for obs and theory).
+One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (e.x.
+stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas.
+(\textit{...
+more...})
+% Discuss common modeling assumptions in CE models that
+%    can be addressed here:
+%        1) instantaneous recycling approximation
+%        2) No metal mass loading of winds, or uniform 
+%           loading across species
+%        3) Uniform metal abundances across the ISM (one zone)
+%
+%  To some degree, cosmological simulations with comparably
+%     low spatial resolution face the same problems, where
+%     variations and spreads in abundances (esp. across 
+%     species) can be smoothed over due to the low res. or
+%     the particular details of the feedback methods and
+%     yield injection methods.
+
+One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references).
+While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood.
+This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
+Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (references), which plays an important role in determining the chemical properties of galaxies (references).
+% more on mixing
+Consequently, following metal mixing, if treated in these models, requires assumptions in how metals mix within the ISM and how metals couple to galactic outflows.
+When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly.
+However, these processes are critical components in understanding galactic chemical evolution.
+Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows.
+In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.
+
+The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
+(\textit{...
+more...}) That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1968,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucelosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
+Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in semi-analytic models and lower resolution cosmological simulations.
+However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
+
+% Paragraphs
+It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group.
+(APOGEE, GAIA, GALAH, RAVE?
+TGAS?).
+Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
+The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM.
+However, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.
+
+% Can shorten if this is actually going to be a letter
+In this paper we present the first detailed chemical evolution results from a set of high resolution hydrodynamics simulations in the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014} of an isolated, low mass dwarf galaxy.
+The simulation discussed here was first introduced in detail in Emerick et.
+al.
+2018 (hereafter Paper I).
+To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae.
+This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below.
+We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species.
+We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.
+
+The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity.
+Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging.
+[list examples of modelling problems].
+These uncertainties combined with the difficultly in simulating a fully self-consistent galaxy in detail motivates this current study.
+By focusing on a low mass dwarf galaxy, we are capable of capturing detailed feedback and ISM physics at high resolution, while following individual stars, due to their small physical scales and low star formation rates.
+In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios for two reasons.
+First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
+Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies with observational analogs in as much detail as we provide here.
+This work will be the first in several in attempting to bridge this gap.
+With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and low resolution simulations of more massive galaxies with physically motivated sub-grid physics models.
+
+We summarize of our methods and physics models in Section~\ref{sec:methods}.
+We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}.
+In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
 
@@
 \label{sec:methods}
-We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
-This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
-To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background.
-We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}).
-We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
-Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
-We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on HI.
-In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
-We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both.
-We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors.
-We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species.
-In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked.
-This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth.
-These methods are discussed in full detail below.
-
-\subsection{Hydrodynamics and Gravity}
-\label{sec:hydro}
-
-We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies.
-\texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions.
-We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick.
-Specifically, simulations presented here were conducted at changeset 7001d99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
-We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}).
-Self-gravity is computed with a multigrid Poisson solver.
-The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.
-
-We refine the mesh whenever the \textbf{thermal} Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
-At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation.
-\citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.
-
-We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}).
-Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
-However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse.
-\textbf{A non-thermal pressure term is added} to cells once their \textbf{thermal} Jeans length becomes unresolved.
-This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
-The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.
-
-\textbf{Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas.
-These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution.
-At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr.
-We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$.
-These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions.
-This threshold decreases the required run-time by factors of a few.
-The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)}
-
-\subsection{Chemistry and Cooling Physics}
-\label{sec:chemistry}
-
-We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset c2c0faf.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes.
-We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.
-We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
-However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}.
-For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
-
-As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
-As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
-Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}.
-To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.
-We have made these new tables public in the main \texttt{Grackle} repository.
-These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
-Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.
-
-\subsection{Star Formation Algorithm}
-\label{sec:star formation}
-In order to resolve individual star formation events on galacitc scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
-Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local \textbf{thermal} Jeans mass.
-Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K.
-We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$.
-No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.
-
-We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
-At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
-
-The stellar mass formed during a timestep $\Delta t$ \textbf{from a region with a total gas mass $M_{\rm gas}$} is
+We refer the reader to Paper I for a detailed description of our numerical methods and feedback models. We briefly summarize the relevant details here.
+
+\textit{Hydrodynamics ---} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}.
+Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
+We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver.
+We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
+Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas and 2) a cell's local Jeans length becomes resolved by less than 8 cells.
+If the cell is within 4 zones of a star particle with active feedback, it is refined to the maximum resolution.
+At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.
+
+\textit{Chemistry, Heating, and Cooling Physics ---} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
+We account for approximate self-shielding of HI against the UV background following \cite{Rahmati2013}.
+We assume HeI self-shields in the same fashion as HI, and ignore HeII heating from the UVB entirely.
+Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}.
+Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.
+
+\textit{Star Formation ---} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
+Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$.
+Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$).
+We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\%.
+Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment.
+We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
+
+\textit{Stellar Feedback and Stellar Yields ---} We track the feedback and yields of 15 metal species for each star individually.
+Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
+Stars above this mass are assumed to direct collapse with no mass or energy injection.
+For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their HI and HeI ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
+We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars.
+Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind.
+Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
+Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et.
+al.
+in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.
+
+\textit{Initial Conditions ---} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
+We initialize a M$_{\rm gas} = 1.8 \times 10^{6} M_{\odot}$ disk with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$ using an exponential gas profile.
+The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
+Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium.
+The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
+Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
+Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.
+
+\section{Results}
+For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
+\textbf{UPDATE VALS:  In general, this galaxy has an average star formation rate of $4~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
+The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy.
+The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$.
+These winds eject 90\% of the metals produced in the galaxy, with 40\% of all metals leaving the virial radius by the end of the simulation time.
+}
+
+In this work we focus in detail on how each of the 15 individual metal species evolve in this galaxy.
+We address differences between the ejection fractions of each metal in Section~\ref{sec:ejection} and analyze for the first time the mass-fraction PDFs of the metals retained by the ISM in Section~\ref{sec:mixing}.
+
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.95\linewidth]{sfr_snrx100_agb.png}\\
+%\caption{}
+%\label{fig:sfr}
+%\end{figure}
+
+\subsection{Preferential Ejection of Metals from the ISM}
+\label{sec:ejection}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.99\linewidth]{species_bar.png}\\
+\includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
+\caption{The fraction of each metal species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).
+The leftmost bar in each plot shows the sum of all metals.
+\textbf{Need to font sizes and mass labels}}
+\label{fig:species_fractions}
+% GB(AE): Why are H and He different? Either discuss or remove from plot.
+%  ------ AE removed from plot
+%
+\end{figure}
+
+The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
+We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
+Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+
+We find two major results.
+First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases.
+The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
+This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
+Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however,the retention factor varies.
+The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
+This suggests that individual metals \textit{do not} share the same dynamical evolution.
+Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field.
+In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{species_bar_sources.png}\\
+\caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
+These channels differ in both when metals are ejected, as determined by stellar evolution, and the energy with which they are ejected into the ISM.
+We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because only XX of them have exploded by the end of our 500~Myr simulation.}
+% GB(AE): Why are H and He different? Either discuss or remove from plot.
+%  ------ AE removed from plot
+%
+\label{fig:species_sources}
+\end{figure}
+
+The only physics that separates the dynamical evolution of these elements in our simulations is the individual sources of enrichment: AGB winds (stars less than 8~M$_{\odot}$), stellar winds (stars above 8~M$_{\odot}$), core collapse supernovae, and Type Ia supernovae.
+These channels differ in: 1) how long after a given star formation event they occur, 2), by consequence, the typical ISM properties in which they occur, 3) how much energy is associated with each event, which determines ejecta temperature and velocity.
+To understand where each of the elements in Figure~\ref{fig:species_fractions} originated, we show the mass fraction of metals produced through each channel in Figure~\ref{fig:species_sources}.
+Core collapse supernovae are responsible for over 90\% of the total metal enrichment in our galaxy, but this is clearly not true for all elements.
+In particular, a majority of N (74\%) and Ba (65\%) are ejected by AGB winds; both are retained at a higher rate than the rest of the metals.
+That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yields tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through supernovae.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and supernovae.
+However, this cannot be determined as we lack Lagrangian information about individual gas elements.}
+% AE: Actually if there are significant isotope variations between nucleosynthetic sources (i.e.
+N produced in AGB winds is a different isotope than the trace N produced in SNe) then that could be a very cool thing to distinguish if we had good gas-phase abundance measures of various isotopes...
+but maybe not if they aren't very stable....
+ We discuss how this result may extend towards other metal yields that are not well sampled on our relatively short (500 Myr) simulation timescales in Section~\ref{sec:discussion:metal yields}.
+
+AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of supernovae ($\sim$1000~km~s$^{-1}$).
+In addition, their longer timescales (40-100~Myr as compared to $\sim$10~Myr) means that AGB stars are typically removed from their birth regions.
+The changes in typical ISM density and height of these events contributes to these variations.
+We show histograms of the average number density within 20~pc of any given enrichment source (top) and height above/below the disk (bottom) within 1~Myr of each event (as limited by our output cadence) in Figure~\ref{fig:spatial distribution}.
+As shown, SN have a bi-modal distribution in density as they explode either close to their dense formation region or within superbubbles, while AGB stars are singly peaked between this distribution at close to the average ISM density.
+We do not expect these differences to be the dominant effect in driving the differential evolution of elements ejected by AGB winds vs.
+supernovae, compared to the energetics, but can certainly play a significant role in determining the mixing behavior of individual enrichment events.
+The changes to mixing behavior as a function of ISM properties will be investigated in more detail in a future work.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{SE_density.png}\\
+\includegraphics[width=0.95\linewidth]{SE_z.png}
+\caption{The average gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.
+{\bf ignore SNIa line in plot -- need to remove}}
+\label{fig:spatial distribution}
+\end{figure}
+
+\subsection{Mixing and Distribution of Metals in the ISM}
+\label{sec:mixing}
+
+Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
+In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textbf{refs to canonical models}).
+Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances.
+In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
+However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
+To build towards this, we characterize the metal evolution and distributions in our galaxy below.
+
+% Classic chemical evolution models often adopt the simplifying assumption that metals from newly formed stars are instantly deposited back into the ISM \textbf{(examples)}.
+With added complication, this instantaneous recycling approximation (IRA) can be expanded upon by taking into account individual stellar lifetimes (references) which have been shown to produce significant variations in stellar abundances (references) as compared to IRA models.
+However, even in this new model it is unlikely that whatever fraction of a star's yields that remains in the ISM instantaneously enriches star forming gas.
+Rather, these yields are first injected through a hot phase (stellar winds, HII regions, supernovae), cooling over time into star forming gas.
+(refs for models accounting for this).
+We investigate this process in our simulations below, first by outlining a new analytic description of metal distributions in the ISM.
+
+\subsubsection{A Functional Form for Metal PDFs}
+\label{sec:log-normal}
+
+The log-normal distribution is found often in nature, generally describing processes with non-negative values that grow with time.
+In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}.
+In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}.
+Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}.
+It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape.
+This includes a log-normal component, generated by multiplicative processes (shocks and the turbulent cascade in the ISM) and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2017}.
+
+The physics that drives the density PDF is directly related to the process of metal mixing and diffusion.
+However, there is no a priori reason why gas density and metallicity PDFs should have similar functional forms.
+We demonstrate here for the first time that the mass fraction PDFs for each metal species in our simulation can indeed be well fit using a piecewise log-normal + power-law PDF.
+We use a simple conceptual model in Section~\ref{sec:interpretation} to motivate the emergence of this distribution.
+
+We follow \cite{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF.
+We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element.
+This PDF is given as
+\begin{align*}
+  p(Z) = 
+  \begin{cases}
+    \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right], 
+    & Z < Z_{\rm{trans}} \\
+    % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
+    N p_o Z^{-\alpha},
+    & Z > Z_{\rm{trans}}
+\end{cases}
+\end{align*}
+where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm trans}$ is the metal fraction at the transition between the log-normal and power-law components.
+When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm trans}$ as free parameters.
+These conditions set $N$ and $p_o$ to
 \begin{equation}
-         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
+N = 
 \end{equation}
-In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution.
-We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses.
-In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
-If it does, we randomly sample from
-the adopted IMF until \textbf{approximately} 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
-\textbf{The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.} We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
-Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
-\textbf{By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.}
-
-Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
-This dispersion captures some of the unresolved gas motions below the resolution limit that are smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations.
-Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
-
-Stars evolve during the simulation, by losing mass from stellar winds and SNe as described below, and by changing types, but persist throughout the entire simulation.
-For example, low mass stars are tagged as white dwarfs (WDs) at the end of their life, which may eventually explode as a Type Ia SN (discussed below), after which they persist as massless tracer particle remnants.
-Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a four-cell region at the highest level of refinement.
-This ensures that both stellar winds and SNe feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.
-
-\subsection{Stellar Properties}
-\label{sec:properties}
-Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}).
-We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$.
-Although $T_{\rm eff}$ and $g$ evolve over time for stars, modifying stellar radiative properties, following a stellar evolution track for each of our stars is beyond the scope of this work.
-We instead fix these properties at their zero age main sequence values.
-
-\subsection{Stellar Feedback and Chemical Yields}
-
-\subsubsection{Stellar Yields}
-\label{sec:yields}
-For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars.
-We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}.
-This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$.
-We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$.
-We ignore SN yields from these stars (see next paragraph).
-We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth.
-Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation.
-We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017a} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
-
-%
-% KVJ: Possibly include a discussion on uncertainties in stellar yields
-%
-
-Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe.
-Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$.
-This is a free parameter in our model; we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value.
-In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
-Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics).
-Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
-\citet{Cote2017a} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
-We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
-
-There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}.
-Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
-Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass, metal, or energy ejection.
-
-Type Ia SNe are an important additional source of galactic chemical enrichment.
-These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
-We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
-We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, substantially limiting the number of Type Ia SNe occurring during the initial gigayear in our models.
-
-\subsubsection{Stellar Winds}
-\label{sec:stellar winds}
-Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
-Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback.
-We assume complete thermalization of the wind kinetic energy, taking the total injected energy injected in timestep $\Delta t$ as $E_w = \frac{1}{2}\dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
-\textbf{This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle.
-The edges of this spherical region will only partially overlap grid cells.
-We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately.} We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
-
-Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}.
-Satisfying the Courant time step becomes prohibitively expensive following this gas, with time steps dropping to $\Delta t \sim$~100~yr.
-For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
-In our case, we fix massive stellar wind velocities to $v_w = 20$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies.
-Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work.
-These points are discussed in more detail in Sect.~\ref{sec:stellar winds discussion}.
-
-% Injecting 10$^{3}$ km s$^{-1}$ gas onto the grid at these scales leads to super heated, shocked gas at unphysical temperatures of about 10$^{8-9}$ K, particularly when injecting into very low density media.
-This can lead to painfully short time step sizes and crashes in the hydrodynamics solver.
-We adopt the common solution of artifiially reducing the wind velocity from massive stars, choosing $v_{\rm wind} = 500$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-However, this can still be problematic once the star evacuates the local ISM and injects its energy to very low density ($n \lesssim 10^{-3}$ \ccunit) gas.
-We address this issue by mass loading our winds when injection would lead to wind bubble temperatures in the spherical source region above a maximum temperature typical of wind bubble.
-This is a free parameter that we take to be 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
-Mass loading in this manner is (in effect) a sub-grid model for the unresolved ISM mixing at the boundary layer of the wind bubble, which is in fact the source of a majority of the gas mass within the wind bubble \citep{Weaver1977}.
-We take the metal species abundances of the mass loaded ISM to be the average cold / warm ISM abundance on each grid to prevent artificially inflating/deflating the overall abundances.
-We discuss our ability to resolve typical single star wind bubble properties in Appendix ~\ref{appendix:stellar winds}.
-
-%parameterized in this work with the STARBURST99 wind model, \citep{Leitherer1992}:
-%\begin{multline}
-%{\rm log} \left[ v_{\rm wind} {\rm (km~s^{-1})} \right] = 1.23 - 0.30~{\rm log}~\left[L{\rm (L_{\odot})}\right] \\
-% + 0.55~{\rm log}\left[M({\rm M_{\odot}})\right] + 0.64~{\rm log}\left[T_{\rm eff}(K)\right] \\
-% + 0.13~{\rm log}\left[Z({\rm Z_{\odot}})\right].
-%\end{multline}
-
-Stars that only undergo an AGB phase deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks.
-AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$.
-For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars as well.
-
-\subsubsection{Core Collapse SNe}
-\label{sec: core collapse}
-Stars between  $M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
-Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}).
-We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
-We use the same Monte Carlo sampling method as used in our stellar winds to map the spherical injection region to the grid.
-We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle.
-In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.
-
-\subsubsection{Type Ia SNe}
-\label{sec:Type Ia}
-We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as WD particles, marking a subset as Type Ia SN progenitors.
-This is the most self-consistent model for Type Ia SNe in galaxy-scale simulations.
-We note however that for the low SFRs in our isolated dwarf galaxy simulation, the first Type Ia SN only appears after a few hundred megayears of simulation time.
-By the end of the simulation presented here (500~Myr), only 18 have gone off.
-At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
-%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
-%or, 
-%\[
-%M_{\rm WD} = 
-%\begin{cases}
-%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
-%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
-%\end{cases}
-%\]
-%where $M_{\rm *}$ is the initial mass of the WD progenitor.
-We follow the common assumption that progenitor stars with initial masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017a}.
-
-We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution model.
-The Type Ia SN rate is taken to be a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope $\beta$ and normalization $N_{\rm Ia}/M_{\rm SF}$ are observables.
-The latter represents the number of Type Ia SNe per mass of star formation.
-By assuming an IMF  $dN/dm$, one can write down the fraction $\eta$ of stars capable of forming a Type Ia SN progenitor that \textit{will} explode within a Hubble time.
-This is given as
+and
 \begin{equation}
-\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
-\end{equation}
-where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF, and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
-The distribution slope $\beta$ is of order unity, with typical values between 1.0 and 1.2 \citep[see][for a recent review]{Maoz2014}.
-$N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the Type Ia SN rate and integrating over a Hubble time.
-Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
-For our fiducial values, we adopt $\beta = 1.2$ \citep{Maoz2010} and $N_{\rm Ia}/M_{\rm SF} = 0.8\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013}.
-Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.
-
-Finally, we can normalize $\Psi(t)$ to give the probability per unit time $\dot{P}(t)$ that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor.
-Integrating this gives the total probability at any given time as
-\begin{equation}
-P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
-\end{equation}
-where $t_{\rm o}$ is the formation time of the WD and the leading term on the right hand side properly normalizes the total probability over a Hubble time to $\eta$.
-This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
-\textbf{In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle.
-For $u \in [0,1]$, we interpolate its position on a pre-tabulated and inverted cumulative probability distribution function to assign a single time at which the WD particle will explode as a Type 1a supernova.
-We institute a minium delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.}
-
-\subsubsection{Ionizing Radiation from Discrete Sources}
-\label{sec:ionizing radiation}
-Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies.
-\ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance.
-However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds.
-Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
-As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.
-
-Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation.
-We follow HI and HeI ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
-
-We determine the HI and HeI ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
-We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star.
-Stars less massive than about 15 M$_{\odot}$ and very massive stars with sub-solar metallicity are generally not well sampled by the OSTAR2002 grid.
-In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).
-
-Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}).
-The average energy for HI and HeI ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
-
-We also include the effects of radiation pressure on HI.
-This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}.
-We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared.
-This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}.
-However, the importance of multiple scattering is still unclear.
-Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013a,Reissl2017,Wibking2018}.
-Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.
-
-\subsubsection{Diffuse  Heating}
-\label{sec:diffusive heating}
-We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the FUV (6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles.
-The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the spectral energy distributions for each gridded star.
-Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
-Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
-However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}.
-Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile.
-Only recently has the localization and time variation of these processes been considered.
-
-Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}.
-We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
-We assume HeI ionization generally follows HI.
-This allows us to approximate HeI self-shielding using the same form (A.
-Rahmati, private communication).
-We ignore HeII photoionization from the UV background entirely.
-{\bf For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.}\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
-As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
-This is described in more detail in Appendix ~\ref{appendix:cooling}.
-
-%Ignoring this effect leads to an overestimation of the cooling rates when in the self-shielding regime.
-%We refer to \citet{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \citet{Gracklemethod} for its specific implementation, as used here.
-
-We assume the galaxy is mostly optically thin to stellar FUV and use only local approximations for shielding.
-We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
-\begin{equation}
-\label{eq:PE}
-\Gamma_{\rm pe} = (1.3 \times 10^{-24} \rm{erg~s^{-1}~cm^{-3}})\, \epsilon n_{\rm H} G_{\rm eff} D 
-\end{equation}
-where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust-to-gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
-Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
-
-The value of $D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
-The extremely low dust-to-gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a ratio $D$ that scales linearly with metallicity at very low metallicity.
-At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit.
-Given that the ambient density of the ISM is generally 1--10~cm$^{-3}$, we can safely assume the FUV field to be optically thin.
-However, we do include a localized attenuation prescription that may influence high-density or metal-enriched regions of the galaxy.
-We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.
-
-Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
-This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations.
-\textbf{Our chemical work only includes contributions from H, He, and H$_2$ to n$_e$.} Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
-%This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
-
-\subsubsection{Lyman-Werner Radiation}
-\label{sec:LW}
-In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rate.
-We compute the stellar Lyman-Werner flux again from the OSTAR2002 grid by integrating the spectral energy distributions over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}).
-Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
-We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.
-
-%
-% CR section moved to missing physics
-%
-%\subsubsection{Cosmic Rays}
-%\label{sec:cosmic rays}
-%Cosmic rays may be a signficant source of feedback within star forming galaxies, capable of driving galactic outflows.
-Recent work has shown that CR's are capable of providing a significant additional pressure support within the ISM \citep{SalemBryan2014, SalemBryanHummels, GirichidisCR, Pakmor2016}, and are capable of producing more realistic galaxy gas halos \citep{SalemBryanCorlies}.
-We include cosmic rays coupled to the hydrodynamics of our simulation using a two-fluid model with adiabatic index $\gamma = 5/3$, as described in \citep{SalemBryan2014}.
-Cosmic ray energy is injected as some fraction, $f_{\rm CR}$, of the total SN rate; we adopt $f_{\rm CR}$ with the fiducial value of 0.1.
-We include isotropic cosmic ray diffusion as described with the diffusion coefficient, $\kappa_{\rm CR} = 3.0\times10^{28}$.
-We refer the reader to \citep{SalemBryan2014} for a study of the effects different values for $f_{\rm CR}$, $\kappa_{\rm CR}$, and the CR adiabatic index has on galaxy evolution.
-
-%Recent work has examined the impact anisotropic diffusion of cosmic rays along magnetic fields has on galaxy evolution \citep{GirichidisCR, Pakmor2016} and galactic winds generated from cosmic ray feedback \citep{GirichidisCR, Simpson2016}.
-Including magnetic fields can substantially change the effect of cosmic ray feedback provided $\mu$G level, ordered magnetic fields develop within the galaxy, as is the case for more massive disk galaxies.
-However, the magnetic field properties of small, ultrafaint dwarf galaxies are poorly understood.
-These small, puffy galaxies may be completely unable to sustain ordered magnetic fields, damping the effects of anisotropic diffusion as cosmic ray diffusion through random, tangled magnetic fields is approximately isotropic.
-We do not expect anisotropic diffusion and magnetic fields to have a significant impact on the effectiveness of cosmic ray feedback for ultrafaint dwarf galaxies, but this stands to be an important area of future research.
-
-\section{Galaxy Initial Conditions}
-\label{sec:IC}
-We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy.
-The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
-Leo P is gas rich, with a \textbf{neutral hydrogen mass} $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and \textbf{stellar mass} $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to an \textbf{observed neutral hydrogen radius} $r_{\rm HI} = 500$~pc.
-LeoP has a low metallicity, with \textbf{an oxygen to hydrogen abundance ratio (O/H)} of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
-Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
-
-The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential.
-The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
-\begin{equation}
-\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
-\end{equation}
-where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass.
-We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$.
-We adopt a \citet{Burkert1995} dark matter potential with \textbf{virial mass and radius} $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and \textbf{scale radius} r$_{\rm s} = 990$~pc.
-This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc.
-These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}.
-
-Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
-This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
-During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}.
-We stop the artificial driving 25~Myr after the first star particle forms.
-These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
-We note this initial driving is ad hoc in that we do not include other effects from the stellar population that would have caused these SNe.
-
-We emphasize here that our model, with no initial stellar distribution, is not intended to identically reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
-In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations.
-Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances.
-In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution.
-Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe.
-The subsequent metal enrichment from the stars in our simulation can be thought of as tracking
-a change in abundances from arbitrary initial conditions.
-We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.
-
-\section{Results}
-\label{sec:results}
-We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms.
-Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run.
-The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical height $|z| < 200$~pc relative to the center of the galaxy.
-ISM properties are calculated considering only the gas contained within the disk of the galaxy.
-We include a resolution study in Appendix \ref{appendix:resolution_study}.
-
-Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.
-All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset dd76ad10.
-
-\subsection{Morphological Structure and Evolution}
-\label{sec:structure}
-
-We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
-This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
-This central region quickly fills with warm and hot gas generated from radiation feedback and SNe respectively.
-Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels.
-The ISM properties are quantified further in Section~\ref{sec:phase}.
+p_o = \frac{1}{\sigma Z_{\rm trans} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm trans}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm trans}) \right]
+\end{equation}.
+
+We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin with of 0.05 dex.
+We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{Scipy} \cite{Scipy}, stepping through possible values for $Z_{\rm trans}$, set to the centers of each of these bins.
+The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted.
+The log-normal + power-law PDF produces the best fit in nearly all cases.
+
+We show in \ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
+These PDFs have been computed at an arbitrary single point in time, at 380 Myr.
+For clarity, we only show a subset of the 15 elements we follow.
+As shown, there are clear differences in the PDFs across elements of different nucleosynthetic origins and between each phase.
+However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions.
+We discuss the differences among each phase in more detail in the next section, but note here that the significance of each of these components varies notably across phases.
+In many of these cases, the piecewise log-normal + power-law distribution fits the numerical PDF quite well.
+However, there are often deviations, particularly at low metal fractions, from pure log-normal behavior.
+This manifests as either a very broad, flat PDF at low metal fraction (see N and Ba, for example), or large peaks not well described by $p(Z)$ at low metal fraction.
+In these situations, it is unclear what, if any, portion should be considered as a log-normal, or if there are multiple components within this region.
+
+We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the the metal fraction  PDFs of individual elements in galaxy models.
+The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM.
+In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions.
+Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$.
+As this is the source of star forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.
+%Developing a complete physical model for what drives the formation and properties of $p(Z)$ is beyond the scope of this paper, but these prospects are discussed in Section~\ref{sec:discussion}.
+
+%The log-normal distribution is a two parameter model defined by the log mean $M$ and the log standard deviation $S$.
+These values are related to the linear mean, $\mu$, and standard deviation, $\sigma$, as $\mu = e^{M+S^2/2}$ and $\sigma = e^{S^2 + 2M}(e^{S^2}-1)$.
+We define the log-normal distribution of metals in the ISM as a function of either the total metallicity $Z$ or the mass fraction of an individual metal species, $Z_i$, where $i$ denotes an individual element.
+For clarity in this section, we refer most often to total metallicity as the variable of interest.
+However, we note that any statement that applies to metallicity also applies to the mass fraction an individual metal species ($Z_i$).
+With these definitions, the log-normal metallicity PDF is given as
+%\begin{equation}
+%f(Z_i, M_i, S_i) = \frac{1}{\sqrt{2 \pi} S_i} \rm{exp}\left(\frac{-(ln(Z_i) - M_i)^2}{2S_i^2}\right).
+%\end{equation}
+%We can also specify the CDF of this distribution as 
+%\begin{equation}
+%F(Z_i, M_i, S_i) = \frac{1}{2} \left[1 + \rm{erf} \left(\frac{ln(Z_i) - M_i}{S_i \sqrt{2}} \right). \right].
+%\end{equation}
+%Thus, $F(Z_i, M_i, S_i)$ gives the fraction of mass in the ISM with metallicity $Z < Z_i$.
+For each of the 15 metal species in our simulations, and for each phase of the ISM, we compute the mass-weighted metal fraction PDFs and fit $f(Z_i,M_i,S_i)$ to each.
+In fitting, we find the parameters $M_i$ and $S_i$ for each distribution that minimizes the distance between the CDF from the simulations and the CDF from the log-normal fit, or $D_{\rm CDF}$.
+For consistency, we use equally spaced bins in log of 0.05 dex in every case.
+
+%
+% OLD TEXT - pre powerlaw
+% We give the results of this fit in Figure~\ref{fig:log-normal} for the metal fraction PDFs of each element in the ISM as a whole.
+The PDFs computed directly from the simulation are shown in the top pane.
+Their log-normal best fits, and corresponding $D_{\rm CDF}$, are shown in the bottom panel.
+For clarity, we normalize each distribution by the peak (mode).
+In all cases, the metal mass fraction PDFs can be described with a log-normal distribution.
+This is a remarkable result.
+That the complex interplay between the dominant physical processes in the ISM, namely stellar feedback, turbulence, self-gravity, heating/cooling, and chemistry, produces metal distributions that are analytically tractable is surprising.
+Linking these instantaneous PDFs to a time evolution of the distributions parameters, $M_i$ and $S_i$, in a general way would create a powerful tool for modelling galactic chemical enrichment in semi-analytic models.
+This is beyond the scope of this work, but we discuss this further in Section~\ref{sec:discussion}.
+
+% OLD TEXT ---- PRE powerlaw
+%Upon closer inspection, we note that there are distinct differences with each metal and some noticeable deviations from true log-normality.
+Most elements have higher positive skew, tails towards higher metal fractions, than can be reasonable captured by a log-normal fit.
+Two elements in particular show quite broad distributions, N and Ba, which are less well fit by a log-normal as the other elements.
+As discussed earlier, these two elements have a distinct nucleosynthetic source, AGB winds, than the rest of the elements.
+Lower energy AGB winds generate broader enrichment distributions that are less well mixed than metals from core collapse and Type Ia supernovae.
+If this behavior is similar in star forming gas, we would expect elements from AGB winds to exhibit larger scatter in observed abundances.
+However, we note again that this figure represents all gas in the ISM.
+These deviations from log-normality and the high metallicity tails could be driven simply by grouping together qualitatively distinct phases of gas in the ISM, each with their own enrichment history.
+We investigate the metal fraction PDFs of individual gas phases below.
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
-\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation.
-Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row).
-Each individual main sequence star particle is shown in the number density projections as a single black dot.}
-\label{fig:panel_x}
+\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
+\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}.
+For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
+We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.}
+\label{fig:log-normal}
 \end{figure*}
 
-The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
-This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time.
-Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--120~pc.
-Towards the end of the simulation time, the half-light radius is $391 \pm 19$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
-Although the disk remains thin beyond the half-light radius, with a scale height of around 50~pc, it is fully resolved at all radii.
-By the end of the simulation, the majority of the disk has a scale height of $\sim$100~pc.
-
-Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging.
-For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
-\textbf{In the final column of Figure~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
-With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
-At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$.
-These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.}
+%\begin{figure*}
+%\centering
+%\includegraphics[width=0.95\linewidth]{lognorm_elements.png}
+%\caption{The metal mass fraction PDF's binned directly from the simulation (top) for all 15 elements tracked in the simulation and the associated log-normal fits (bottom) along with the minimized CDF distance for each.
+Given the wide range in mass fractions among species, we normalize the PDFs by their peak for clarity.
+These PDFs are shown at 350~Myr into the 500~Myr simulation; the choice of time was arbitrary.}
+%\label{fig:log-normal}
+%\end{figure*}
+
+% NOTES:
+%    Discuss how generally good of fits these are but how some are less good.
+Mention how N and Ba are less well mixed (reference above) and how this should really be examined in sub-groups of the ISM, motivating the next section.
+Next section will plot mean and std of fits and distributions as function of time for each phase, along with chi-squared good-ness of fits values.
+Need to find a way to estimate / compute the uncertainty for this!!
+Poisson in each bin?
+shift bins a little and estimate variance this way?
+
+%   Give the distributions of metals at ONE point in time in each phase for two elements, O and Ba.
+Show the log fit and the histogram on each (maybe use orange and blue?).
+Discuss how the distributions are well fit by lognormals and the evolution of each, giving values for the fits and using dashed lines showing mean/std of full distribution when not well fit by a lognormal.
+
+\subsubsection{PDF Variation Across Gas Phase}
+\label{sec:phase-pdfs}
+
+%\subsubsection{Log-normality in each Phase of the ISM}
+%\label{sec:phase-pdfs}
+The various phases represented in Figure~\ref{fig:log-normal} involve variations in density and temperature of more than six orders of magnitude.
+The evolution of each phase is qualitatively different, and the metal mixing behavior of each should vary.
+Mixing timescales over a given length scale should be related to the local sound speed; hot gas, with higher sound speeds, should mix more rapidly than the dense, disconnected clumps of cold gas in the ISM.
+In addition, one would expect a metallicity gradient with gas temperature as enrichment occurs first in the hot phases, cooling and enriching denser gas over time.
+We examine the PDF variations among elements in each phase, as shown in Figure~\ref{fig:log-normal}, in more detail here.
+
+Unsurprisingly the diffuse HIM contains the most metal enriched gas, as it is comprised predominately of metal enriched supernova ejecta.
+Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
+Generally, in colder gas the metal PDFs become less enriched with broader low metal fraction components and steeper, power-law tails.
+Although the extended power-law tail of the HIM leads to a large range of metal fractions, the HIM represents very little mass, and this tail represents recent, un-mixed enrichment.
+The comparatively narrow width in the log-normal regimes of CNM is perhaps surprising.
+Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is more well mixed.
+This runs counter to the idea that mixing times should be long in colder gas unless mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.
+
+Although these trends across phases hold for all elements, there are qualitative differences between elements, particularly between those ejected predominantly by AGB winds (e.g.
+Ba and N) and those ejected by supernovae (e.g.
+O and Mg).
+In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by supernova enrichment.
+The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the CNM.
+Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N produced in supernovae yields.
+Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and supernovae.
+AGB wind elements enrich the WNM and WIM directly, rather than the HIM, which would increase their mixing timescales and broaden their PDFs.
+
+%\textit{ It is unlikely that metals evolve uniformly across the large variations in density (10$^{-3}$ cm$^{-3}$ $<~n~<$ 10$^{3}$~cm$^{-3}$) and temperatures (10~K~$<~T~<$ 10$^{7}$~K) in our galaxy's ISM.
+Higher temperature gas has a higher sound speed and shorter mixing timescales than cold, dense star forming gas.
+From this, one would expect that high temperature gas is more well mixed than the disconnected dense clouds that comprise the galaxy's cold ISM.
+In addition, gas in the hot phase is generated almost entirely from HII regions and supernovae remnants and should therefore be more metal rich on average than cold gas.
+We investigate both of these expectations below.
+To simplify this discussion, we focus only on O and Ba as representative examples of elements produced predominately through supernovae explosions (core collapse or Type Ia) and elements produced in lower energy AGB winds respectively.}
+
+%The previous section demonstrated that metals are log-normally distributed within the ISM of our dwarf galaxy as a whole, but given the significant variation in densities (10$^{-3}$cm$^{-3}$~$<~n~<~10^{3}$~cm$^{-3}$) and temperatures (10~K~$<~T~<$ 10$^{7}$~K) within the ISM, we investigate how this may vary across regimes in the ISM.
+(give reference to sources which show log-normal within different temperature regimes).
+In particular, turbulent mixing and log-normal density distributions seen in local ISM simulations do depend on the temperature of the examined gas.
+Higher temperature gas has a higher sound speed and shorter mixing timescales than cold, dense star forming gas.
+This should impact the variance of each distribution.
+To simplify this discussion, we focus on two elements only, O and N, as representative examples of elements whose injection is dominated by supernovae or stellar winds, respectively.
+Conclusions reached as to the general trends for these two elements can be generalized to other elements of similar injection source.
+
+%\textit{In Figure~\ref{fig:log-normal phases} we present the numerical PDFs (top, histograms) along with their log-normal fits (bottom, curves) for O (left) and Ba (right) in each of the five phases of our dwarf galaxy's ISM.
+It is clear that each phase can be described with a different log-normal distribution, and it is the sum of these distributions that drives the deviations from log-normality in the PDFs of the galaxy's ISM as a whole in Figure~\ref{fig:log-normal}.
+In both cases, the HIM deviates the most from a log-normal, with large tails towards higher metallicities.
+In O, these tails become progressively less extreme in the colder phases, with both the CNM and molecular gas conforming well to a log-normal distribution with the least amount of variance.
+Although it is expected that the hot phases are more metal enriched than the cooler phases, it is surprising that the cold, dense gas is more well-mixed than the hot phases.
+We discuss the implications of this result further in Section~\ref{sec:statistics}.
+In contrast with O, the PDFs in Ba appear to universally be less well described by a log-normal in all phases, with less distinct enrichment between the phases.
+Although the cold phases here are still less enriched than the hot phases, each still exhibits longer tails towards high metal fractions that are the source of the deviations from log-normal.
+The differences in the PDFs across elements from supernovae explosions and AGB winds indicates that these species diffuse and mix differently throughout the ISM.
+Again, AGB produced metals should show larger abundance variations observationally than those produced in supernovae.
+}
+
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.95\linewidth]{lognorm_O_Ba_phases}
+%\caption{The metal mass fraction PDFs computed directly from the simulation (top) for O (left) and Ba (right) in each of the five phases of our galaxy's ISM at the same time as shown in Figure~\ref{fig:log-normal}.
+The log-normal best fits to each of these phases are given in the bottom row.}
+%\label{fig:log-normal phases}
+%\end{figure}
+
+\subsubsection{The Time Evolution of Metal PDFs}
+\label{sec:statistics}
+We focus on the time evolution of the full numerical PDFs in this section.
+Our results here do not depend upon the choice of functional form for $p(Z)$.
+Figure~\ref{fig:phase-statistics} shows the evolution of four different statistics for the O (top) and Ba (bottom) PDFs.
+These two elements are treated as representative elements for supernova and AGB wind production respectively.
+The difference between the mean and median masses of the PDF (second column) is a measure of the skew of the PDF.
+Positive values indicate that metals are preferentially sequestered in metal-rich gas, and are less well mixed throughout the given phase.
+The skew is always positive in these distributions.
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
-\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on views.}
-\label{fig:panel_z}
+\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution.png}
+\caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation.
+The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
+\label{fig:phase-statistics}
 \end{figure*}
 
-\begin{figure}
-\centering
-\includegraphics[width=0.975\linewidth]{scale_height}
-\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figures~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
-\label{fig:scale_height}
-\end{figure}
-
-\subsection{Star Formation Rate and Mass Evolution}
-\label{sec:sfr}
-
-We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
-The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$.
-The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation.
-Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.19 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
-We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.
-
-We note that the granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
-Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
-For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$.
-Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense.
-Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.
-
-At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, \textbf{ with a molecular hydrogen mass fraction of only $\sim$ 0.3 \%.
-The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
-For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% at 500~Myr.
-The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy from feedback-driven galactic winds.
-During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM.
-Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
-The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.}
+For O, the median mass fraction is ordered by phase temperature.
+The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm$ 1 dex over the simulation time.
+The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
+%This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events. 
+Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread.
+The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star forming gas.
+This is the only explanation for how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels).
+Individual enrichment events will have significantly higher metallicities than the ambient ISM in any phase, and will drive an increase in the difference between the mean and median of the PDF.
+These can be seen as the obvious spikes in the HIM and WIM.
+For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.
+
+% In each phase, enrichment events will tend to drive larger differences between mean and median mass fraction,
+
+Although these trends are generally true for Ba, its evolution is much more complicated.
+%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability. 
+Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM.
+The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
+Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in supernovae.
+The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
+These tails represent the most recently enriched gas, and is clearly much more locally confined than O.
+
+%{\bf (move to discussion?)}: 
+The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e.
+the ratio between the total mass of metals and the total mass).
+Assuming star forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex), but significant, for elements released during SNe explosions, but can be very significant, up to $\sim$ 0.8 dex, for elements released in AGB winds.
+Chemical evolution models, especially one-zone models, follow the mean metal fraction, not median.
+These results indicate that these models are biased to overestimate gas and stellar elemental abundances.
+. % However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.
+
+To summarize, this figure demonstrates: 1) there are qualitative differences in how supernova injected elements (e.g.
+O, Mg) and AGB wind injected elements (e.g.
+N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value.
+In the case of supernova injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
+For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.
+
+\section{Discussion}
+\label{sec:discussion}
+We begin with a simple toy model that motivates the power-law tail at high metal fractions of the metal fraction PDFs and a subsequent turnover at low metal fractions in Section~\ref{sec:interpretation}.
+This work is placed in context with previous works focusing on metal mixing in the ISM in Section~\ref{sec:context}.
+Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impact of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
+
+\subsection{Physical Interpretation of the PDF}
+\label{sec:interpretation}
+Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_o = 0$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$.
+Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas.
+In this case, $p(Z)$ takes the form of a double-delta function
+\begin{equation}
+p(Z) = \delta(Z) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
+\end{equation}
+If the enriched material mixes continually with the primordial gas at a constant rate, after some time this gas will have mixed with an equal amount of primordial gas.
+At this point, the high metal fraction delta term becomes $\frac{2M_{\rm ej}}{M_o} \delta(Z - \frac{1}{2}Z_{\rm ej})$.
+This implies an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas, and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$.
+If the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, $p(Z)$ will become a power-law in $Z$, truncated at some time dependent minimum $Z$.
+The slope of the power-law is determined by the rate of injection versus mixing with the ambient medium.
+A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium.
+Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than enrichment.
+If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.
+
+In reality, however, $M_o$ is not an inexhaustible reservoir of primordial gas.
+Eventually the entire ambient medium will become enriched to some $Z > Z_o$, and $p(Z)$ will consist entirely of a continuous, truncated power-law.
+As enrichment proceeds, gas near the low metallicity truncation of $p(Z)$, which still comprises much of the mass of the system, enriches towards higher metallicities in the power-law tail.
+This will produce a turnover at the low $Z$ limit of $p(Z)$.
+The low-turnover limit is produced by diffusion from many different sources, and is thus an additive process, which, as we noted above, tends to produce log-normal distributions.
+The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.
+
+This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases.
+The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions.
+Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low-metallicities.
+Cold, dense gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.
+
+%
+%
+%
+%Although this model is useful to explain these very general features, it is certainly incomplete in practice.
+Enrichment proceeds irregularly through the mulit-phase ISM with a variety of ejection masses and metallicities.
+Phases are not independent, and the hot phase cools and enriches cooler phases in the ISM, distorting $p(Z)$ within each phase.
+Cold gas is heated up and destroyed through feedback, changing the content of the low-metallicity end of the warm and hot phases.
+Finally, gas is removed from the galaxy through feedback driven winds that preferentially remove metal enriched gas.
+Each of these processes has a non-trivial effect on the evolution of the PDF that will cause deviations from the simple toy model outlined here.
+Determining the exact physical processes that drive and set the properties of each PDF is the subject of ongoing work.
+
+%
+% A.E. paragraph may need work
+%
+Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}.
+Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
+This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dnese gas ($\sim$ 1 km s$^{-1}$).
+Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy.
+This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
+It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing supernovae.
+Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star forming gas.
+Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy.
+The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.
+
+\subsection{Context}
+\label{sec:context}
+That metal fraction distributions can be described using a simple analytic log-normal + power-law PDFs, even in a complex, multi-phase ISM, has not been demonstrated prior to this work.
+In addition, this is the first work to demonstrate differential mixing behavior of individual metal species using 3D hydrodynamics simulations.
+However, there does exist a significant body of work investigating the mixing behavior of passive scalars in a variety of contexts, as discussed below.
+\cite{KrumholzTing2018} predict differential behavior for AGB wind and core collapse supernova synthesized elements as a direct consequence of the differences in size of typical planetary nebulae ($\sim$ 0.1~pc) and supernova remnants ($\sim$ 100~pc).
+%We discuss our results further in the context of previous research on metal mixing in the ISM and speculate on the physical processes that drive the evolution of these PDFs across phases.
+
+Previous work on the evolution of metals in the ISM varies from studies concerning the advection of passive scalars in idealized turbulent boxes \citep[e.g.][]{Pope1991, PanScannapieco2010, PanScannapiecoScalo2012, PanScannapiecoScalo2013, YangKrumholz2012, SurPanScannapieco2014, Colbrook2017}
+% cite passive scalar reviews by Warhaft 2000 in fluid mech and scalo + Elmegreen 2004?
+to global galaxy models studying generalized advection and mixing of passive scalars \citep[e.g.][]{deAvillez2002,Petit2015,Goldbaum2016} to models with more detailed self-consistent metal enrichment \citep[e.g.][]{Revaz2009,Escala2018}.
+% summarize conclusions from these works:
+
+The evolution of metallicity PDFs has been investigated previously in some of these works \citep[see ][ and references therein]{PanScannapiecoScalo2012,PanScannapiecoScalo2013}, with effort towards developing closure models to describe the evolution of the PDFs of passive scalars in turbulent media \citep[e.g.][]{EswaranPope1988,Chen1989,Pope1991}.
+The astrophysical context in much of this work was enrichment from the first stars, so the focus was on the low-metallicity tail of the PDF and the timescales over which gas is polluted \citep[e.g.][]{PanScannapiecoScalo2013,Sarmento2017}.
+These works often use isothermal turbulent-box simulations initialized with a double-delta function PDF of pristine gas and enriched gas in some varying spatial distribution, ignoring ongoing enrichment.
+Initial PDFs of this form were demonstrated some time ago to evolve into a Gaussian distribution at late times \citep{EswaranPope1988}, but it is unclear if these could also be described with a log-normal distribution.
+However, these works uniformly do not contain the high metallicity power-law tails shown in our work.
+As suggested by our toy model in Section~\ref{sec:interpretation}, this is due to the lack of ongoing enrichment in these studies.
+
+More detailed models of global galaxy evolution have generally focused on spatial correlations and mixing timescales of initially asymmetric fields, without concern for ongoing enrichment \citep[e.g.][]{deAvillez2002,Petit2015} or focused primarily on the evolution of stellar abundance patterns and metallicity distribution functions \citep[e.g][need more]{Jeon2017,Hirai2017,Escala2018}, without directly examining the evolution of gas-phase metallicity PDFs.
+
+%
+% MM: remove from this section:
+%This is the first work examining the gas-phase properties of metallicity PDFs in a global galaxy simulation with a detailed model for stellar feedback, chemical enrichment, and a multi-phase ISM.
+Since we are far from a complete understanding of galactic chemical evolution, investigating the physics behind what sets the statistical properties of these PDFs, particularly what drives the differences across metal species and phases, is important.
+Although this is beyond the scope of this current work, we use scaling arguments to speculate on the meaning of these results.
+%Metal mixing in the ISM is a diffusive process driven by turbulence.
+
+% Recent works investigating dwarf galaxy chemical enrichment with Lagrangian simulations have shown that the sub-grid diffusion models required to reproduce observed dwarf galaxy abundance properties imply fairly rapid mixing timescales \citep{Escala2018,Hirai2017}.
+In contrast to this work, \cite{Escala2018} finds dwarf galaxy
+%The sub-grid diffusion models in Langrangian simulations of dwarf galaxy chemical enrichment that match the abundance properties of observed dwarf galaxies imply rapid mixing timescales
+
+%
+%
+%  Recent works specifically examining metal mixing in dwarf galaxies. Saving for potential future discussion:
+% \cite{Hirai2017} uses constrains the diffusion parameter in their SPH simulations comparing their simulated dwarf galaxies to observations in [Mg/Fe] vs.
+[Fe/H] and [Ba/Fe] vs.
+[Fe/H] space.
+Suggests Ba/Fe is more powerful constraint and briefly discusses potential differences in mixing between elements but does not do work with this
+% \cite{Jeon2017} 
+% \cite{Escala2018} tests of role of metal diffusion models in producing realistic MDFs in dwarf galaxies. Able to reproduce things like MDF width and [alpha/Fe]vs[Fe/H] scatter.
+
+% The properties of log-normal density PDFs in isothermal simulations are governed by the statistical properties of turbulence (refs) and the relative importance of compressive and solenoidal driving.
+However, the density PDFs in simulations of global galaxies with a resolved, multiphase ISM show significant departures from log-normallity \citep[see][]{Hopkins2013} but are still approximately log-normal within individual phases of the ISM \citep{HopkinsQuataertMurray2012}.
+The properties of the density PDF in multiphase simulations have not been well studied which offers little insight into what sets the mass fraction PDFs for each element.
+We speculate on this here to motivate future study, but note that a detailed characterization is beyond the scope of this work.
+
+% The log-normal density PDFs found in ISM simulations have a variance that is proportional to the mach number \citep[e.g.][(maybe more)]{PNJ1997, Passot1998, Fedderath2008, LemasterStone2009}.
+In our simulations, however,
+
+%We discuss possible caveats to this in Section~\ref{sec:caveats}.
+Does this extend to more massive?
+how does DM potential affect this?
+Are general trends still true in much larger galaxies?
+or are things very different once HIM crossing times are more like 100 Myr (aka MW size galaxies).
+
+\subsection{Timescale Dependence of AGB Ejecta}
+\label{sec:discussion:metal yields}
+We can generally say that metals produced in AGB winds evolve qualitatively differently in dwarf galaxies than metals produced through supernovae.
+However, exactly which metals exhibit these differences, and to what degree, is timescale and metallicity dependent.
+Short-timescales ($\lesssim 100$~Myr) only samples enrichment from the most massive AGB stars, which stars on order of a few solar masses enrich on 1 Gyr timescales or longer.
+In our simulations, which only sample 500 Myr of evolution, N and Ba are dominated from AGB wind ejecta.
+C is commonly used to track AGB wind enrichment, but as it originates from lower mass AGB stars, C enrichment operates on $\sim$ Gyr timescales, longer than we follow in this work.
+This additionally varies with metallicity.
+Sr, for example, is only significantly ejected through AGB winds at our metallicity on $\sim$~Gyr timescales; stellar winds from more massive stars dominate the production of Sr on shorter timescales.
+At higher metallicity, much more Sr is produced through massive AGB stars, decreasing the timescale over which Sr should exhibit a differential chemical evolution as compared to supernovae ejected elements.
+
+To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected through AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times.
+This model was run using \textsc{SYGMA} \citep{Ritter2017}.
+As shown, metal enrichment from AGB winds only begins to dominate for a given species at $\sim$ 100 Myr.
+This includes N and Ba, as followed in our simulations, but this plot indicates that Li should show the strongest differences with respect to metal ejected through supernovae, even on relatively short ($< 100~$~Myr) timescales.
+It takes over a Gyr for C to be dominated from AGB wind ejecta, which is the case for many of the elements shown.
+F, which shows very little contribution from AGB winds at short timescales is dominated by enrichment on longer timescales.
+These dependences on metallicity and timescales certainly adds complications in generalizing our work and in interpreting observations in the context of the results presented here, but these difference could be leveraged to better understand galactic chemical evolution on multiple, distinct timescales.
+Clearly this motivates future work covering Gyr timescales to fully understand how metal mass fraction PDFs evolve with time.
 
@@
 \centering
-\includegraphics[width=0.475\linewidth]{sfr_snrx100}
-\includegraphics[width=0.475\linewidth]{mass_evolution}
-\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins.
-Broken portions of this histogram are time periods with no star formation or supernovae.
-Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.
-Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
-\label{fig:sfr_mass_evolution}
+\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0.png}
+\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, with no continual star formation.
+We only show a sample of some of the elements dominated most by AGB enrichment.
+The horizontal line marks 50\% contribution.}
+\label{fig:agb evolution}
 \end{figure*}
 
-\subsection{ISM Properties}
-\label{sec:phase}
-
-Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
-We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
-We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content.
-\textbf{By this definition, although our galaxy certainly contains molecular hydrogen, molecular gas as a phase does not exist; the peak f$_{\rm H_2}$ in any single cell remains below 30\%.} See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-The properties of these phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
-Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.
-
-Figure~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
-One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
-Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
-We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
-\textbf{Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left.}  The boxed regime in the lower right corner shows our star formation density and temperature threshold.
-Gas in this regime is rapidly consumed by star formation and subsequent feedback.
-Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average.
-We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work.
-
-\begin{figure}
+%\begin{figure*}
 %\centering
-\includegraphics[width=0.95\linewidth]{phase_diagram.png}
-\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gass interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr.
-The two red dashed lines show lines of constant pressure for guidance.
-The region in the lower right corner indicates our density and temperature thresholds for star formation.}
-\label{fig:phase}
-\end{figure}
-
-\textbf{H2 changes:} The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
-The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
-The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run.
-The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation.
-During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1.
-Although the CNM dominates the mass fraction, it is a negligable component of the ISM volume, which is WIM dominated.
-However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
-Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-
-\textbf{H2 Changes:} These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
-They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (defined in those works as gas with 100~K$<$T$< 3\times 10^{4}$), with cold gas having between 1 and 10\% of the mass, and occupying negligible volume.
-Hot gas (defined as gas with $T > 3\times 10^{4}$~K) occupies 10\% of the volume, with negligable mass, in their galaxy, while our WIM alone occupies $>$ 50\% of the volume.
-Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) and hot gas (by volume fraction) that seen in the more massive dwarf galaxy in these works.
-The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
-We have compared our cooling curves to those used in \citep{Hu2017} and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.
-
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
-\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
-\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
-\label{fig:ISM_evolution}
-\end{figure*}
-
-\subsection{Interstellar Radiation Field}
-\label{sec:ISRF}
-
-The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}.
-This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
-In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
-The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
-The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.
-\textbf{The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
-At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.}
-
-\textbf{ The bottom panel gives the HI ionizing photon flux from stellar radiation.
-The ionizing radiation profile follows a similar trend, yet with significantly more variation, anywhere from two to four orders of magnitude.
-As this radiation is followed through radiative transfer, the profile encodes information about local attentuation by dense, neutral gas.
-This is the main driver of the differences between the two panels.
-The total fluctuation in both panels is due in part to the low-level, stochastic star formation in our galaxy.
-A higher star formation rate would produce a more regular population of massive stars and more uniform (in time) ISRF.}
-
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{G_o_profile} \\
-\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
-\caption{
-Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr.
-Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc.
-The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
-The bottom panel gives the HI ionizing stellar radiation flux.
-Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point.
-For this reason we only shade between the first quartile and maximum values.
-HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.}
-\label{fig:ISRF}
-\end{figure}
-
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
-\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
-\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
-Here, we include all gas within the mid-plane of our dwarf galaxy.
-Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
-This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
-\label{fig:ISRF_2D}
-\end{figure*}
-
-To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr.
-This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
-The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
-From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
-Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation.
-In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency.
-It remains to be seen which of these two modes of feedback is more important in regulating star formation.
-
-\subsection{Outflow Properties}
-\label{sec:outflows}
-
-The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}.
-However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
-In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
-We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
-\begin{equation} \label{eq:dotM}
-\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
-\end{equation} 
-We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.
-
-The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
-Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
-For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor.
-The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors between 20--100 throughout the simulation time.
-This declines towards larger radii, however, with substantially less outflow past the virial radius.
-\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift, consistent with our results.
-
-Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
-Using a fit provided in \citet{Muratov2015} to extrapolate and compare $\eta$ at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
-These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
-We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find lower mass loading factors even closer to the disk, at 0.05 $R_{\rm vir}$, between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$; certainly this implies even smaller mass loading factors at 0.25 $R_{\rm vir}$.
-
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{total_mass_outflow}
-\includegraphics[width=0.45\linewidth]{total_mass_loading}
-%\includegraphics[width=0.33\linewidth]{metal_mass_loading}
-\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
-\label{fig:mass_outflow}
-\end{figure*}
-
-\textbf{H2 Changes:} Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
-In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
-Gas with a negative velocity is moving towards the center of the halo.
-Roughly 25\% of this mass is inflowing, mostly with modest negative velocities, and corresponds to previously ejected gas mixing and recycling throughout the halo.
-Half of the outflowing gas (positive velocities) is moving at velocities below 30 km s$^{-1}$, 75\% at velocities below 70 km s$^{-1}$, and 95\% at velocities below 100 km s$^{-1}$.
-Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-neglibable amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$.
-The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominating at velocities above 200 km s$^{-1}$.
-The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling WIM and HIM, consistent with the results in \citet{Hu2016,Hu2017}.
-However, as shown, the HIM, which is mostly the SN ejecta itself, comprises very little of the outflow by mass.
-Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM.
-Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
-The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
-
-\begin{figure}
-%\centering
-\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
-\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-This is averaged over the same time interval as Figure~\ref{fig:ISRF}.
-The outflowing material is multiphase, broken into WNM, WIM, and HIM.
-See Section~\ref{sec:phase} for definitions of these regimes.
-We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K.
-There is little to no outflowing mass in the CNM.}
-\label{fig:outflow_velocity}
-\end{figure}
-
-\subsection{Metal Evolution} 
-\label{sec:chemical evolution}
-
-\subsubsection{Metal Enriched Outflows}
-Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
-This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
-In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}.
-The parameter used to quantify metal outflow efficiencies varies among works.
-Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
-\begin{equation} \label{eq:eta-metal}
-\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
-\end{equation}
-where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions.
-For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but it increases at each radius, fluctuating around unity for the second half of the simulation.
-Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}.
-\cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
-Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.
-
-\begin{figure}
-%\centering
-\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
-\includegraphics[width=0.9\linewidth]{metal_retention}
-\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Figure~\ref{fig:mass_outflow}.
-This is the ratio between the metal outflow rate and the metal production rate.
-{\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
-In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
-\label{fig:metal_evolution}
-\end{figure}
-
-These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
-This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
-After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
-This continues throughout the simulation, with only $\sim$4\% of produced metals residing in the disk of the galaxy.
-It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius until about 350 Myr where the fraction levels off to just above 50\%.
-Likewise, the CGM metal content continually decreases until the end of the simulation from loss through the virial radius of the halo.
-See Section~\ref{sec:obs_metals} for further discussion.
-
-\subsubsection{Differential Evolution of Elements Within the ISM}
-It is important to understand how metals from each source of stellar yields enrich the ISM.
-Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}.
-This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed.
-Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Avillez2002,Tassis2008,YangKrumholz2012}.
-It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
-It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.
-
-%We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
-The top two panels give the slices of number density (top left) and temperature (top right) in the mid-plane of a portion of our dwarf galaxy.
-These serve to guide the eye in the lower panels, clearly indicating regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K), warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
-The bottom panels give abundance ratios for oxygen and hydrogen (bottom left), nitrogen and hydrogen (bottom middle), and nitrogen and oxygen (bottom right).
-
-We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
-The left panel gives the abundance ratio of N to O throughout the ISM.
-The right
-two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy.
-These show regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K) connected by cold filaments, warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
-
-\begin{figure*}
-\includegraphics[width=0.98\linewidth]{log_NO_panel}
-            \caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances.
-The left slice gives the ratio of the abundance between N and O, normalized to the solar abundance, while the number density and temperature are shown on the right.
-In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occured in the preceeding 5 Myr as black stars and orange diamonds respectively.}
-\label{fig:metal_slices}
-\end{figure*}
-
-%The CNM consists of cold filaments that connect dense clumps of molecular gas that are readily visible in both diagrams.
-Distinguishing the WNM and WIM is difficult, but the lower density regions between the cold filaments are dominated by these phases.
-Gas from a recent SN explosion is clearly visible as the hot (T~$\gtrsim 10^{6}$~K), diffuse region in the top left corner.
-As shown in the left panel, log(N/O) varies significantly over this section of the ISM with notable differences across the various phases and ISM structures.
-The hottest gas, dominated by recent supernova explosions is overabundant in oxygen, relative to solar (purple).
-However, the relative abundance of nitrogen increases in the WIM and WNM, being overabundant relative to solar (green).
-
-At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars.
-Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
-Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
-The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
-This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
-A more detailed analysis is beyond the scope of this work, but we \textbf{investigate this in detail in Emerick et.
-al.
-(in prep.).}
-
-\section{Discussion}
-\label{sec:discussion}
-
-\subsection{Comparison to Observed Low Mass Dwarf Galaxies}
-\label{sec:observation}
-
-As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs.
-Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of $z = 0$ dwarf galaxies.
-However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies.
-We show that these properties are broadly consistent with observations.
-
-\subsubsection{Gas and Star Formation}
-\label{sec:gas_sf}
-
-The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}.
-However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
-In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.
-
-Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
-We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}.
-We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the area of the disk within the radius of the outermost star formed within the previous 10 Myr.
-Likewise, $\Sigma_{\rm gas} = M_{\rm gas,10} / A_{*,10}$, where M$_{\rm gas,10}$ is the total gas mass within this defined disk.
-However, the total gas content cannot be determined observationally.
-To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He.
-We note that there is generally no correction made for any possible H$_{\rm 2}$ or HII content.
-As shown in Section~\ref{sec:molecular gas content}, these components may be significant.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
-\includegraphics[width=0.475\linewidth]{all_gas_efficiency_evolution.png}
-\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
-See text for details of the calculation.
-Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars.
-On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}.
-There is no clear correlation with time in this diagram.} %something is breaking here in compiling
-\label{fig:KS}
-\end{figure*}
-
-We include recent observational constraints on these relationships in Figure ~\ref{fig:KS}.
-Our galaxy fluctuates significantly about both relationships with no clear trends in time.
-However, in both cases, it is consistent with the available observational sample.
-At times our galaxy exhibits gas surface densities below the observational constraints.
-The trend is still consistent with higher densities at this point, but with a larger scatter towards lower star formation rate densities and efficiencies.
-
-In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
-It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
-This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
-\textbf{The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.} % AE: Mordecai, is this an appropriate clarification of this poitn?
-
-\subsubsection{Molecular Gas Content}
-\label{sec:molecular gas content}
-\textbf{AE: rewording - changed numbers and text to reflect lower H2 fractions. left discusion of uncertainties in H2 formation in low mass dwarfs and need for further study:}
-The molecular gas content of low-mass dwarf galaxies is generally assumed
-to be small, but is not well constrained by either theory or observations.
-Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
-As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range.
-H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
-The gas-phase reaction dominates in our low-metallicity galaxy over the other two channels by several orders of magnitude.
-In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
-Thus the presence of some ionizing background is required to generate the molecular fractions we find in our simulations, as confirmed in test simulations run only to the onset of first star formation.
-
-In contrast, \citet{Hu2016} and \citet{Hu2017} find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
-However, although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
-Our model suggests that both H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies.
-Indeed it is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, though it is worth noting that the rate coefficients associated with gas-phase H$_2$ formation are still uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
-Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
-It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
-This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
-
-\subsubsection{Metal Retention}
-\label{sec:obs_metals}
-
-The simulations presented here have not yet been run for the gigayear timescales required to begin to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$.
-However, we can compare to a key observable: the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from closed box stellar evolution models given the galaxy's star formation history.
-This can be done readily with Milky Way dSph's.
-Their stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
-However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
-
-Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich,
-star forming, low-mass dwarf galaxy, with an observable HII region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
-Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
-However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
-Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
-%We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.
-
-It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium.
-While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
-We find 5.3\% of all metals lie within 1 kpc of the center of our galaxy, 24.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 51\% outside $R_{\rm vir}$.
-This is consistent with previous works, but this is again an evolving quantity.
-In addition, the amount of gas that escapes the virial radius is certainly sensitive to the details of gas accretion from the IGM on this galaxy, which we cannot capture in this model.
-
-The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
-Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return.
-In addition, the accretion of pristine gas from the intergalactic medium could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals.
-This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.
-
-\subsection{Missing Physics}
-Although we include many detailed physical models in our simulations, there remain additional physical processes that may be relevant, which we now discuss.
-
-\subsubsection{Massive Stellar Wind Energy}
-\label{sec:stellar winds discussion}
-Our massive stellar wind model drastically reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$.
-Although our algorithm is entirely capable of generating realistic stellar winds with velocities comparable to those observed, such fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
-When considered in isolation, stellar winds are an important source of pre-SN feedback and can dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
-However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}, unless densities near the ionizing source are high enough to trap the  HII region in the source cell.
-In that case, they can clear out a cavity to allow initial establishment of the HII region.
-
-They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
-Although they likely have minimal dynamical importance at resolutions where peak densities are not anyway high enough to trap ionization fronts, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting closer examination in future work.
-
-%\subsubsection{Magnetic Fields}
-%\label{sec:magnetic fields}
-
-\subsubsection{Cosmic Rays} 
-%mm2 and Magnetic Fields}  One could make the case that we should have a separate discussion of magnetic fields.  However, this section is only about CRs.
-
-Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}.
-These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}.
-Modeling cosmic rays is challenging, however, as they encompass a wide range of energies, and there are significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
-Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy.
-In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM.
-Modeling cosmic ray feedback completely thus requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena.
-Finally, including MHD presents additional difficulties in untangling the effects of each individual feedback mechanism on galaxy chemodynamics.
-
-We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested.
-Mechanically, including this relatively simple treatment of
-cosmic ray feedback in our model is trivial.
-However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to later work.
-
-\subsection{Detailed Stellar Evolution and Binary Stars}
-\label{sec:binary stars}
-
-Roughly half of massive stars live in binary pairs \citep{Sana2013}.
-Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes.
-This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as SNe.
-This effect could be significant, but is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g.
-STARBURST99).
-For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse SNe occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
-Although they find only $\sim 15\%$ of core collapse SNe explode after 50~Myr, this could still be an important effect.
-Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}.
-Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
-
-Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars.
-This is beyond the scope of this project, but will be investigated in future work.
-
-\section{Conclusion}
-\label{sec:conclusion}
-We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
-For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, using individual star particles to model core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, Lyman-Werner radiation and pollution from AGB and massive stellar winds.
-This treatment of feedback, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
-In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
-We present an overview of the properties of this simulation
-in this work.
-% AE: mention companion paper here if publish at same time
-
-For our simulated dwarf galaxy, we find:
-\begin{enumerate}
-\item Multi-channel feedback is effective in this galaxy in regulating star formation to occur at a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
-(See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).
-
-\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, falling to $\eta \sim 10$ at R$_{\rm vir}$,  and
-metal mass loading factors near unity.
-By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Figure~\ref{fig:outflow_velocity}).
-
-\item 
-Only $\sim$4\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of ultrafaint dwarfs.
-By the end of the simulation $\sim$45\% of the remaining metals remain within the virial radius (but outside the galaxy) and $\sim$50\%
-have been ejected beyond the virial radius. (See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
-
-\item 
-The gas scale height is thin ($\sim 50$~pc), yet resolved, 
-beyond our stellar radius, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
-This is comparable to the resolution limit of the diffuse HI in observed, gaseous ultrafaint dwarfs.
-At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8--4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Figure~\ref{fig:scale_height}).
-
-\item The ISRF of our galaxy varies strongly in both space and time by orders of magnitude.
-It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
-(See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
-
-\item 
-We find H$_2$ fractions below 5\% in our dwarf galaxy, consistent with the poor constraints on molecular gas formation in low metallicity dwarf galaxies.
-This H$_2$ forms entirely through gas-phase reactions facilitated by H$^{-}$ in self-shielding regions; H$_2$ formation on dust grains and in the three body reaction are both insignificant.
-Cold, neutral hydrogen dominates the mass of our galaxy.
-While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Figure~\ref{fig:sfr_mass_evolution} and Figure~\ref{fig:ISM_evolution}.)
-
-\item Finally, we used O and N as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy.
-These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs.
-SNe), as suggested by \cite{KrumholzTing2018}.
-This will be explored in more detail in future work (Emerick et.
-al.
-\textit{in prep.}).
-\end{enumerate}
-
-\section*{Acknowledgments:} 
-We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
-C\^ot\'e, S.
-Glover, K.
-Hawkins, C.
-Hu, K.
-Johnston, B.
-O'Shea, M.
-Putman, B.
-Smith, J.
-Wall, and J.
-Wise.
-A.E.
-is funded by the NSF Graduate Research Fellowship DGE 16-44869.
-G.L.B.
-is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
-M.-M.M.L.
-was partly funded by NASA  grant NNX14AP27G.
-We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing
-%mm4 (HEC) 
-Program through the NASA Advanced Supercomputing 
-%mm4 (NAS) 
-Division at Ames Research Center, Columbia University, and the Flatiron Institute.
-This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.
-These are products of collaborative effort by many independent developers from numerous institutions around the world.
-Their commitment to open science has helped make this work possible.
-
-%\bibliographystyle{yahapj}
-\bibliographystyle{mnras}
+%\includegraphics[width=0.95\linewidth]{C_N_evolution.png}
+%\caption{The fractional contribution of AGB winds to the total yields of C and N as a function of time for a simple stellar population at three different metallicities.
+Since the nucleosynthetic source governs the mixing dynamics of a given metal, this plot illustrates how this can change with both time and metallicity for a given species.
+These models were generated using \textsc{SYGMA} \citep{Ritter2017-sygma}}
+%\label{fig:agb evolution}
+%\end{figure*}
+
+\subsection{Impact on Stellar Abundance Patterns}
+\label{sec:stellar abundances}
+% AE: Possibly need better general introduction to CE models / sims and importance of understanding stellar abundances (obs+theory)
+In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star forming gas in our simulations.
+This could be used to help disentangle sources of scatter in observed stellar abundance, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
+If the star forming gas in our simulations can also be well-fit by a log-normal + power-law PDF, and if we can parameterize their evolution as functions of global galaxy properties, this can be used as a powerful and analytic tool for modeling stellar abundance patterns in semi-analytic models.
+This would be a physically motivated way to account for both the intrinsic spread in stellar abundances due to inhomogeneities in the ISM and variations in mixing for different metal species.
+We reserve an analysis of these distributions in abundance space in both the gas and stars for a future work.
+However, we briefly discuss the connection to star forming gas and stellar enrichment below.
+
+Unfortunately, there is insufficient star forming gas at any one time in these simulations to construct a PDF of metal distributions.
+However, star forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, follow a similar PDF to the CNM.
+To very this, Figure ~\ref{fig:stars} shows the difference between the mass fraction of a given element in stars and the median mass fraction from the CNM PDF at the time that particle formed.
+Stars seem to be sampled evenly around the median of the CNM distribution (i.e.
+there is no obvious bias towards high metal fractions).
+Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
+High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
+
+\subsection{Do these results apply to more massive galaxies?}
+\label{sec:massive galaxies}
+One important caveat about our work is that these results are derived from simulations of an isolated, low mass dwarf galaxy whose properties vary dramatically from a more massive galaxy like the Milky Way.
+It is unclear how much of these results apply to more massive galaxies given their deeper potential wells and higher star formation rates.
+Feedback driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
+We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy.
+With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
+If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
+If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+This difference would be greater at later times (higher metallicity) once AGB enrichment becomes significant.
+For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
+At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way.
+Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way.
+However, there has been no definitive explanation for these observations.
+Generalizing our results and detailing their observational consequences is the topic of ongoing work.
+
+In contrast, we expect the properties of the enrichment PDFs, and the variations between AGB enriched elements and supernova enriched elements (as presented in Figures~\ref{fig:log-normal} and ~\ref{fig:phase-statistics}), to be general.
+We expect metals to exhibit log-normal + power-law distributions in the ISM of all galaxies, with similar trends with enrichment source and gas phase as outlined here.
+However, the detailed properties of the PDFs (e.g, log-normal width, power-law slope) likely depend non-trivially on global galaxy properties.
+How these results vary as a function of galaxy properties will be investigated in future work.
+
+% Talk about CGM at all???
+
+%\textit{In addition, hot gas in a galaxy with a deeper potential well is less likely to be ejected from the galaxy, allowing more time for homogenization and possibly smaller metal fraction variation than seen here.}.
+
+%
+% moved to possible to-do list below,
+%
+\subsection{Implications for Exotic Enrichment Sources}
+\label{sec:exotic enrichment}
+We have shown that the dynamical evolution of metals depends upon their nucleosynthetic source, focusing here on AGB synthesized elements and supernova synthesized elements.
+However, these differences should also apply to exotic enrichment sources, such as hypernovae (HNe), neutron-star neutron-star mergers (NSM), and neutron star - black hole mergers.
+These sources have energies that differ significantly from typical supernova (10$^{51}$ erg), reaching $> 10^{52}$ for HNe \citep{Nomoto2004} and $\sim$10$^{49}$~erg for NSMs \citep{Goriely2011}.
+We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to supernovae.
+Based on our results here, we would expect elements from HNe to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe.
+Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies.
+These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
+In particular, low mass dwarf galaxies with unusual r-process enrichment \citep[e.g.][]{Ji2015}, are valuable for constraining the source of these elements, their frequency, and typical yields.
+The differential metal evolution presented in our work both opens up an additional avenue by which elements from distinct nucleosynthetic sources may be distinguished in observations and challenges current assumptions used in interpreting these observations.
+
+%\subsection{Extra things I could discuss:}
+%\textit{Things I can / will additionally discuss}
+%\begin{itemize}
+%\item Observed N/O in stellar abundances exhibits large spreads at low metallicity.
+Argument has been that this is driven by timescale differences in AGB vs.
+massive star nucleosynthesis.
+However, our results would predict that N/O have a large spread due to mixing efficiency diffein rences between AGB winds and SNe.
+%\end{itemize}
+
+\section{Conclusions}
+\label{sec:conclusions}
+For the first time we present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
+This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze how individual metal species couple to the galactic winds and ISM of this galaxy.
+We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, core collapse supernovae, and Type Ia supernovae).
+This difference is most significant in our model between elements ejected predominately through AGB winds and those ejected predominantly by core-collapse supernovae.
+In addition, we find for the first time that the metal mass fraction PDFs of each metal in the ISM can be described using an analytic piece-wise log-normal + power-law PDF.
+The properties of these PDFs vary with both ISM phase and metal species, again driven mostly by differences in enrichment sources.
+
+We summarize our results as follows:
+\begin{itemize}
+
+%\item Elements from lower energy enrichment sources (i.e.
+AGB winds) are preferentially retained in the ISM of low mass dwarf galaxies as compared to those from higher energy sources (supernovae), which are more readily launched in galactic winds.
+This result is likely sensitive to global galaxy properties, becoming less significant with increasing halo mass.
+We predict the abundance ratios between AGB wind dominated metals (s-process elements) and SN dominated metals ($\alpha$ elements) to be higher at fixed metallicity in low mass dwarf galaxies than in more massive galaxies, like the Milky Way.
+
+\item Power-law tails in metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
+
+\item Hotter phases have metal fraction PDFs that are more enriched with significant power-law tails as compared to cold phases, which have a more dominant log-normal structure.
+The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling into dense gas.
+% missing text???????????
+
+\item Metal outflow in low mass dwarf galaxies depends upon nucleosynthetic origin.
+Metals from lower energy enrichment events (e.g.
+AGB winds) are preferentially retained in the ISM as compared to those from higher energy events (e.g.
+SNe).
+The degree to which this is true likely depends upon global galaxy properties such as star formation rate, dark matter potential well, and gas geometry.
+
+\item Likewise, metals originating in AGB winds are less well mixed in the ISM compared to metals injected through SNe, with spreads of over 1 dex in cold gas, as compared to
+
+\item Metal distributions exhibit positive skew, such that the median metal fraction can be anywhere from 0.1 to 1.0 dex above the mean metal fraction.
+Simple chemical evolution models, which generally follow the mean abundance, that are unable to account for complex metal mixing physics are likely biased towards higher enrichment values.
+
+\end{itemize}
+
+We expect these results to be general for more massive galaxies and galaxy properties.
+However, it may be the case that metals couple more uniformly to galactic winds in more massive galaxies as wind driving occurs increasingly through entrainment of the ambient ISM rather than the ejection of individual enrichment events.
+This warrants further examination.
+But interpreting these results for low mass dwarf galaxies, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements, particularly at lower metallicities, 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way, and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements.
+
+%\section{Things to cite}
+%Hou, Yu, Lu 2014: Need to read closer, but CE model playing around with SN energy feedback effectiveness finds that weaker feedback leads to more metal enrichment, higher FB, lower metallicities.
+Suggestion of importance of FB driving CE.
+
+\acknowledgments
+Acknowledgments.
+
+\facilities{Yeti, CCA cluster, Stampede, Pleiades} 
+\software{Numpy, Enzo, yt, astropy}
+
+\bibliographystyle{yahapj}
 \bibliography{msbib}
@@
 
-\section{Gas Phases of the ISM}
-\label{appendix:phases}
-
-To aid in comparison to other works, we define our ISM phases here, as adopted and modified from \citet{Draine2011}, Table 1.3, and used consistently throughout this analysis.
-By construction, these phases are mutually exclusive.
-We take $f_{\rm H_2}$ to be the molecular hydrogen fraction of the total gas mass.
-
-\begin{enumerate}
-\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
-\item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
-\item Warm Neutral Medium (WNM): $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$
-\item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
-\item Molecular: $T < 10^2$~K, $f_{\rm H_2} > 0.5$
-\end{enumerate}
-
-\section{Stellar Radiation Properties}
-\label{appendix:radiation}
-We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Figure~\ref{fig:stellar radiation properties} we plot these properties.
-We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
-This requires two factors for each radiation type, one for low mass and one for high mass stars.
-We use the following multiplicative factors to adjust the black body spectrum for HI and HeI ionizing radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
-We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
-
-The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid.
-A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section.
-We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \url{http://www.pa.uky.edu/~verner/photo.html}}
-The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision.
-Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.
+\section{Density PDF}
+\label{appendix:density PDF}
+We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}.
+We show the mass-weighted PDF ($dm/Md\rm{log}n$) on the left, and the volume-weighted PDF ($dv/Vd\rm{log}n$) on the right.
+As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution.
+The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.
+The volume weighted PDF is much better described as a multi-component power law.
+The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities.
+These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.
+Finally, \cite{Hopkins2013} suggests a different functional form for describing these PDFs across a range of idealized simulations, but it still may be insufficient to fully describe the density PDF in realistic galaxy simulations.
+Clearly, we are far from a general understanding of mass-weighted and volume-weighted density PDFs in the case of a turbulent, self-gravitating, multi-phase ISM.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.475\linewidth]{density_PDF.png} 
+\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted.png}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr.
+The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
+\label{fig:density_pdf}
+\end{figure}
+
+\section{Resolution Comparison}
+\textbf{Still a to-do:}
+We perform a resolution test to confirm that the key results of this study are convergent, at least qualitatively.
+Given the variations in star formation rate, feedback effectiveness, and stochasticisty in our model, we do not expect exact numerical convergence in any one quantity.
+We conduct two lower resolution simulations with a maximum physical resolution of 3.6 pc and 7.2 pc.
+We refer the reader to Paper I for a previous comparison of these simulations to our fiducial run.
+In Figure~\ref{fig:resolution-phase} we demonstrate that O and Ba abundances behave qualitatively similar in our lower resolution runs as in our fiducial model.
+In both lower resolution runs O has a generally tighter distribution that narrows over time, while Ba is much less well mixed, in agreement with our fiducial simulation.
+The exact numerical values for these spreads are not convergent across simulations, but we do note significant variations in the exact SFH of these lower resolution runs could be driving these differences.
 
@@
 \centering
-\includegraphics[width=0.4\linewidth]{Q0}
-\includegraphics[width=0.4\linewidth]{Q1}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{L_FUV}
-\includegraphics[width=0.4\linewidth]{L_LW}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{E0}
-\includegraphics[width=0.4\linewidth]{E1}
-\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right).
-Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
-\label{fig:stellar radiation properties}
+\includegraphics[width=0.95\linewidth]{O_Ba_spread_resolution-comparison.png}
+\caption{Resolution comparison at two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.
+Compare to Figure~\ref{fig:phase-statistics}.}
+\label{fig:resolution-phase}
 \end{figure*}
 
-\setcounter{figure}{0}
-\section{Typical Gas Densities in Supernova Injection Regions}
-\label{appendix:SN}
-
-Modeling SN feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of SN feedback.
-Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time.
-However, physically consistent solutions have been developed \citep[e.g][]{Simpson2016} that inject a mixture of kinetic and thermal energy with a ratio that depends on resolution and local gas density.
-Overcooling becomes less important with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each SN.
-We take advantage of our high resolution and employ a simple thermal energy injection model for our SN feedback.
-We demonstrate how well this resolves our SNe in the comparison simulation presented in this work.
-
-The left panel of Figure~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
-As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
-For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations.
-The right panel of Figure ~\ref{fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
-\begin{equation}
-R_{\rm PDS} = 
-\begin{cases}
-49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z \le 0.01 \\
-18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z \ge 0.01 \\
-\end{cases}
-\end{equation}
-where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$.
-\citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the SN explosion with thermal energy injection alone, assuming uniform density in the injection region.
-In practice, the injection region is never uniform.
-We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each SN.
-As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but up to 8.3\% are not well resolved and 2.0\% are completely unresolved (below a single cell width).
-In general, these are SN explosions from the most massive (i.e.
-most prompt) stars.
-We do not expect that resolving these SNe will dramatically alter our results.
-However, we note that using our feedback model at resolutions much less than a few parsecs will require implementing an different injection mechanism.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.4\linewidth]{sn_density_hist}
-\includegraphics[width=0.4\linewidth]{sn_radius_hist}
-\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation.
-{\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each SN assuming a uniform medium at either the peak or average density in the injection region.
-The vertical lines show one and 4.5 cell widths.
-This shows that a fraction of these SNe are certainly underresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
-\label{fig:SN histogram}
-\end{figure*}
-
-\setcounter{figure}{0}
-\section{Cooling and Heating Rates}
-\label{appendix:cooling}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
-\caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background.
-Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the un-corrected (i.e.
-optically thin) metal line cooling rates.
-The regimes where heating dominates are plotted with dashed lines for clarity.}
-\label{fig:cooling comparison}
-\end{figure*}
-
-The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with a self-shielding approximations.
-\citet{Hu2017} details this inconsistency: metal cooling rates computed under the assumption of an optically thin UV background overestimate the electron fraction in regimes where self-shielding is important ($-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$).
-This results in an artificially enhanced metal line cooling rate in regions of self-shielding.
-This can be a significant effect, particularly at higher metallicities.
-We demonstrate this in Figure~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
-The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
-In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
-Figure~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
-We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
-
-For densities where self-shielding is important, we computed \textsc{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
-In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud.
-We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UV background.
-These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}.
-In computing these tables we had to include the cosmic ray ionization that dominates in optically thick clouds.
-Without this effect, \textsc{Cloudy} becomes unstable in entirely neutral regions.
-We adopted a cosmic ray ionization rate of 10\% the Milky Way value, though we note that varying this from 1\% to 100\% the Milky Way value did not have an effect on the extracted metal line cooling rates.
-
-Finally, we note that the cooling and heating rates in our simulation will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
-The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which is not included in these diagrams.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_curve}
-\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}.
-The absolute value of the net cooling or heating
-rate is shown with solid lines.}
-\label{fig:cooling}
-\end{figure*}
-
-\setcounter{figure}{0}
-\section{Resolution Study}
-\label{appendix:resolution_study}
-
-\textbf{Significant changes to the lower resolution runs and the comparison to our fiducial simulation with the change to the H$_2$ production:}
-
-We demonstrate the effect of varying resolution in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}.
-We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines).
-The physics in each simulation remains the same with the exception of star formation, which employs a resolution-dependent density threshold.
-A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.
-As a result, the time at which star formation first occurs varies between the simulations, but we again define t = 0 as the time of first star formation in each simulation.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.33\linewidth]{sfr_resolution_study.png}
-\includegraphics[width=0.33\linewidth]{mass_evolution_resolution.png}
-\includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
-\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted).
-The line colors in the left panel are for better clarity between the SFRs.}
-\label{fig:resolution_study}
-\end{figure*}
-
-Figure~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
-We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
-The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs.
-We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Figure~\ref{fig:SN histogram}.
-However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
-
-Generally ineffective feedback leads to increased, not decreased, star formation rates.
-However, the lower resolution run has the lowest SFR.
-The source of this difference is likely related to the ability to resolve dense, cold gas in the lower resolution simulations.
-In particular, the low resolution simulation clearly is unable to resolve the densities at which gas-phase H$_2$ formation becomes efficient, leading to significantly lower H$_2$ fractions (middle panel) and lower cooling rates.
-In addition, whatever H$_2$ does form at these lower resolutions exists at lower gas densities than in our fiducial run, and is less well protected by self-shielding effects.
-This is shown clearly in the significant plummet in the H$_2$ mass during the phase of first star formation that is less severe in our fiducial run.
-In this low metallicity regime, where H$_2$ is an important coolant, the ability to resolve the densities responsible for H$_2$ formation and self-shielding is important.
-
-Theses differences in densities are shown clearly by comparing Figure~\ref{fig:phase_diagram} with Figure~\ref{fig:phase_resolution}.
-Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.
-In the 7.2~pc run, the gas phases are notably less distinct, with gas more evenly smoothed out in the mulit-phase region between cold, dense gas and warm, ionized gas.
-We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature ceiling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{3pc_phase.png}
-\includegraphics[width=0.475\linewidth]{6pc_phase.png}
-\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Figure~\ref{fig:phase}.}
-\label{fig:phase_resolution}
-\end{figure*}
-
-Finally, the metal retention fraction (right panel) between the fiducial and 3.6~pc runs are quite similar, but is significantly higher for the lowest resolution simulation.
-It is likely, however, that this is a result of the lower SFR in the 7.2~pc run and is not directly a resolution effect.
-This also affects the fraction of metals ejected outside the virial radius, with less metals being ejected in the lower resolution runs.
-
-%\section{Code}
-%(likely just do this as a short blurb in acknowledgements)
-
-%A one-zone chemical evolution and feedback model was constructed to provide rapid testing and examination of the feedback and yield properties of each of our stars in our model.
-This code is publically available at https://github.com/aemerick/onez.
-In the simplest case, one can generate a series of star particles and examine their resulting properties, including wind and SN yields, as a function of mass and metallicity.
-Included also are more complicated examples of running the full one-zone model.
-Support currently only exists for running in a non-cosmological mode with a constant star formation rate.
-In addition, this one-zone model uses star-by-star modelling and becomes extremely inefficient at large particle counts.
-Future develop will better optimize this code, allow for variable input or evolving star formation rates, cosmological evolution, and parallelism.
-
-\label{lastpage}
-
 \end{document}

### 2018-07-14 main.tex
removing old resolution study plot. new is complete
text updates (fixes) comment removal and updated plots

@@
 In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe).
-This difference is driven by the differences in energetics between each source, particularly the poor coupling of AGB winds.
-Only 80\% of metals dominated by AGB enrichment are ejected through winds, even though 95\% of all metals leave the galaxy.
+This difference is driven by the differences in energetics between each source, particularly the poor coupling of AGB winds to the ISM.
+Nearly all of the produced metals are ejected from the galaxy (only 5\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
 In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae.
@@
 % can I work "Currents of Space" into this paper somehow (Asimov)?
-Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (review refs for obs and theory).
+Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}).
 One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (e.x.
@@
 This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
-Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (references), which plays an important role in determining the chemical properties of galaxies (references).
+Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}).
 % more on mixing
@@
 However, these processes are critical components in understanding galactic chemical evolution.
-Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows.
+Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillota2018}.
 In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.
@@
 The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-(\textit{...
-more...}) That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1968,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1968,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
 It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucelosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
-Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in semi-analytic models and lower resolution cosmological simulations.
+Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
 However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
 
-% Paragraphs
 It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group.
-(APOGEE, GAIA, GALAH, RAVE?
-TGAS?).
+(\textit{ references to APOGEE, GAIA, GALAH, RAVE, TGAS}).
 Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
@@
 
-% Can shorten if this is actually going to be a letter
 In this paper we present the first detailed chemical evolution results from a set of high resolution hydrodynamics simulations in the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014} of an isolated, low mass dwarf galaxy.
@@
 Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment.
-We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
+We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
 
@@
 \textit{Initial Conditions ---} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
-We initialize a M$_{\rm gas} = 1.8 \times 10^{6} M_{\odot}$ disk with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$ using an exponential gas profile.
+We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$.
 The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
@@
 For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
-\textbf{UPDATE VALS:  In general, this galaxy has an average star formation rate of $4~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
+This galaxy has an average star formation rate of $1.2~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
 The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy.
 The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$.
-These winds eject 90\% of the metals produced in the galaxy, with 40\% of all metals leaving the virial radius by the end of the simulation time.
-}
+These winds eject 95\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.
 
@@
 \includegraphics[width=0.95\linewidth]{SE_z.png}
-\caption{The average gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.
-{\bf ignore SNIa line in plot -- need to remove}}
+\caption{The average gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
 \label{fig:spatial distribution}
@@
 Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
-In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textbf{refs to canonical models}).
+In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}).
 Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances.
@@
     \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right], 
-    & Z < Z_{\rm{trans}} \\
+    & Z < Z_{\rm{t}} \\
     % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
     N p_o Z^{-\alpha},
-    & Z > Z_{\rm{trans}}
+    & Z > Z_{\rm{t}}
 \end{cases}
 \end{align*}
-where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm trans}$ is the metal fraction at the transition between the log-normal and power-law components.
-When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm trans}$ as free parameters.
+where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm t}$ is the metal fraction at the transition between the log-normal and power-law components.
+When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm t}$ as free parameters.
 These conditions set $N$ and $p_o$ to
 \begin{equation}
-N = 
+N = \frac{1}{2} \left[ 1 + \rm{erf}\left( \frac{ln\left(Z_{\rm t}\right) - \mu}{\sigma\sqrt{2}}\right)\right] + \frac{p_o}{\alpha-1}Z_{\rm t}^{-\alpha + 1}
 \end{equation}
@@
 \begin{equation}
-p_o = \frac{1}{\sigma Z_{\rm trans} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm trans}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm trans}) \right]
+p_o = \frac{1}{\sigma Z_{\rm t} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm t}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm t}) \right]
 \end{equation}.
@@
 We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin with of 0.05 dex.
-We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{Scipy} \cite{Scipy}, stepping through possible values for $Z_{\rm trans}$, set to the centers of each of these bins.
+We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \cite{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins.
 The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted.
@@
 
-We show in \ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
+We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
 These PDFs have been computed at an arbitrary single point in time, at 380 Myr.
@@
 As this is the source of star forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.
-%Developing a complete physical model for what drives the formation and properties of $p(Z)$ is beyond the scope of this paper, but these prospects are discussed in Section~\ref{sec:discussion}.
-
-%The log-normal distribution is a two parameter model defined by the log mean $M$ and the log standard deviation $S$.
-These values are related to the linear mean, $\mu$, and standard deviation, $\sigma$, as $\mu = e^{M+S^2/2}$ and $\sigma = e^{S^2 + 2M}(e^{S^2}-1)$.
-We define the log-normal distribution of metals in the ISM as a function of either the total metallicity $Z$ or the mass fraction of an individual metal species, $Z_i$, where $i$ denotes an individual element.
-For clarity in this section, we refer most often to total metallicity as the variable of interest.
-However, we note that any statement that applies to metallicity also applies to the mass fraction an individual metal species ($Z_i$).
-With these definitions, the log-normal metallicity PDF is given as
-%\begin{equation}
-%f(Z_i, M_i, S_i) = \frac{1}{\sqrt{2 \pi} S_i} \rm{exp}\left(\frac{-(ln(Z_i) - M_i)^2}{2S_i^2}\right).
-%\end{equation}
-%We can also specify the CDF of this distribution as 
-%\begin{equation}
-%F(Z_i, M_i, S_i) = \frac{1}{2} \left[1 + \rm{erf} \left(\frac{ln(Z_i) - M_i}{S_i \sqrt{2}} \right). \right].
-%\end{equation}
-%Thus, $F(Z_i, M_i, S_i)$ gives the fraction of mass in the ISM with metallicity $Z < Z_i$.
-For each of the 15 metal species in our simulations, and for each phase of the ISM, we compute the mass-weighted metal fraction PDFs and fit $f(Z_i,M_i,S_i)$ to each.
-In fitting, we find the parameters $M_i$ and $S_i$ for each distribution that minimizes the distance between the CDF from the simulations and the CDF from the log-normal fit, or $D_{\rm CDF}$.
-For consistency, we use equally spaced bins in log of 0.05 dex in every case.
-
-%
-% OLD TEXT - pre powerlaw
-% We give the results of this fit in Figure~\ref{fig:log-normal} for the metal fraction PDFs of each element in the ISM as a whole.
-The PDFs computed directly from the simulation are shown in the top pane.
-Their log-normal best fits, and corresponding $D_{\rm CDF}$, are shown in the bottom panel.
-For clarity, we normalize each distribution by the peak (mode).
-In all cases, the metal mass fraction PDFs can be described with a log-normal distribution.
-This is a remarkable result.
-That the complex interplay between the dominant physical processes in the ISM, namely stellar feedback, turbulence, self-gravity, heating/cooling, and chemistry, produces metal distributions that are analytically tractable is surprising.
-Linking these instantaneous PDFs to a time evolution of the distributions parameters, $M_i$ and $S_i$, in a general way would create a powerful tool for modelling galactic chemical enrichment in semi-analytic models.
-This is beyond the scope of this work, but we discuss this further in Section~\ref{sec:discussion}.
-
-% OLD TEXT ---- PRE powerlaw
-%Upon closer inspection, we note that there are distinct differences with each metal and some noticeable deviations from true log-normality.
-Most elements have higher positive skew, tails towards higher metal fractions, than can be reasonable captured by a log-normal fit.
-Two elements in particular show quite broad distributions, N and Ba, which are less well fit by a log-normal as the other elements.
-As discussed earlier, these two elements have a distinct nucleosynthetic source, AGB winds, than the rest of the elements.
-Lower energy AGB winds generate broader enrichment distributions that are less well mixed than metals from core collapse and Type Ia supernovae.
-If this behavior is similar in star forming gas, we would expect elements from AGB winds to exhibit larger scatter in observed abundances.
-However, we note again that this figure represents all gas in the ISM.
-These deviations from log-normality and the high metallicity tails could be driven simply by grouping together qualitatively distinct phases of gas in the ISM, each with their own enrichment history.
-We investigate the metal fraction PDFs of individual gas phases below.
 
@@
 \includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
-\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}.
+\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), HIM (red), and all the gas in the ISM (black).
 For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
-We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.}
+We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.
+Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
 \label{fig:log-normal}
 \end{figure*}
-
-%\begin{figure*}
-%\centering
-%\includegraphics[width=0.95\linewidth]{lognorm_elements.png}
-%\caption{The metal mass fraction PDF's binned directly from the simulation (top) for all 15 elements tracked in the simulation and the associated log-normal fits (bottom) along with the minimized CDF distance for each.
-Given the wide range in mass fractions among species, we normalize the PDFs by their peak for clarity.
-These PDFs are shown at 350~Myr into the 500~Myr simulation; the choice of time was arbitrary.}
-%\label{fig:log-normal}
-%\end{figure*}
-
-% NOTES:
-%    Discuss how generally good of fits these are but how some are less good.
-Mention how N and Ba are less well mixed (reference above) and how this should really be examined in sub-groups of the ISM, motivating the next section.
-Next section will plot mean and std of fits and distributions as function of time for each phase, along with chi-squared good-ness of fits values.
-Need to find a way to estimate / compute the uncertainty for this!!
-Poisson in each bin?
-shift bins a little and estimate variance this way?
-
-%   Give the distributions of metals at ONE point in time in each phase for two elements, O and Ba.
-Show the log fit and the histogram on each (maybe use orange and blue?).
-Discuss how the distributions are well fit by lognormals and the evolution of each, giving values for the fits and using dashed lines showing mean/std of full distribution when not well fit by a lognormal.
 
@@
 
-%\subsubsection{Log-normality in each Phase of the ISM}
-%\label{sec:phase-pdfs}
 The various phases represented in Figure~\ref{fig:log-normal} involve variations in density and temperature of more than six orders of magnitude.
@@
 AGB wind elements enrich the WNM and WIM directly, rather than the HIM, which would increase their mixing timescales and broaden their PDFs.
-
-%\textit{ It is unlikely that metals evolve uniformly across the large variations in density (10$^{-3}$ cm$^{-3}$ $<~n~<$ 10$^{3}$~cm$^{-3}$) and temperatures (10~K~$<~T~<$ 10$^{7}$~K) in our galaxy's ISM.
-Higher temperature gas has a higher sound speed and shorter mixing timescales than cold, dense star forming gas.
-From this, one would expect that high temperature gas is more well mixed than the disconnected dense clouds that comprise the galaxy's cold ISM.
-In addition, gas in the hot phase is generated almost entirely from HII regions and supernovae remnants and should therefore be more metal rich on average than cold gas.
-We investigate both of these expectations below.
-To simplify this discussion, we focus only on O and Ba as representative examples of elements produced predominately through supernovae explosions (core collapse or Type Ia) and elements produced in lower energy AGB winds respectively.}
-
-%The previous section demonstrated that metals are log-normally distributed within the ISM of our dwarf galaxy as a whole, but given the significant variation in densities (10$^{-3}$cm$^{-3}$~$<~n~<~10^{3}$~cm$^{-3}$) and temperatures (10~K~$<~T~<$ 10$^{7}$~K) within the ISM, we investigate how this may vary across regimes in the ISM.
-(give reference to sources which show log-normal within different temperature regimes).
-In particular, turbulent mixing and log-normal density distributions seen in local ISM simulations do depend on the temperature of the examined gas.
-Higher temperature gas has a higher sound speed and shorter mixing timescales than cold, dense star forming gas.
-This should impact the variance of each distribution.
-To simplify this discussion, we focus on two elements only, O and N, as representative examples of elements whose injection is dominated by supernovae or stellar winds, respectively.
-Conclusions reached as to the general trends for these two elements can be generalized to other elements of similar injection source.
-
-%\textit{In Figure~\ref{fig:log-normal phases} we present the numerical PDFs (top, histograms) along with their log-normal fits (bottom, curves) for O (left) and Ba (right) in each of the five phases of our dwarf galaxy's ISM.
-It is clear that each phase can be described with a different log-normal distribution, and it is the sum of these distributions that drives the deviations from log-normality in the PDFs of the galaxy's ISM as a whole in Figure~\ref{fig:log-normal}.
-In both cases, the HIM deviates the most from a log-normal, with large tails towards higher metallicities.
-In O, these tails become progressively less extreme in the colder phases, with both the CNM and molecular gas conforming well to a log-normal distribution with the least amount of variance.
-Although it is expected that the hot phases are more metal enriched than the cooler phases, it is surprising that the cold, dense gas is more well-mixed than the hot phases.
-We discuss the implications of this result further in Section~\ref{sec:statistics}.
-In contrast with O, the PDFs in Ba appear to universally be less well described by a log-normal in all phases, with less distinct enrichment between the phases.
-Although the cold phases here are still less enriched than the hot phases, each still exhibits longer tails towards high metal fractions that are the source of the deviations from log-normal.
-The differences in the PDFs across elements from supernovae explosions and AGB winds indicates that these species diffuse and mix differently throughout the ISM.
-Again, AGB produced metals should show larger abundance variations observationally than those produced in supernovae.
-}
-
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.95\linewidth]{lognorm_O_Ba_phases}
-%\caption{The metal mass fraction PDFs computed directly from the simulation (top) for O (left) and Ba (right) in each of the five phases of our galaxy's ISM at the same time as shown in Figure~\ref{fig:log-normal}.
-The log-normal best fits to each of these phases are given in the bottom row.}
-%\label{fig:log-normal phases}
-%\end{figure}
 
@@
 However, star forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, follow a similar PDF to the CNM.
-To very this, Figure ~\ref{fig:stars} shows the difference between the mass fraction of a given element in stars and the median mass fraction from the CNM PDF at the time that particle formed.
+To verify this, Figure ~\ref{fig:stars} shows the difference between the mass fraction of a given element in stars and the median mass fraction from the CNM PDF at the time that particle formed.
 Stars seem to be sampled evenly around the median of the CNM distribution (i.e.
@@
 \section{Resolution Comparison}
-\textbf{Still a to-do:}
 We perform a resolution test to confirm that the key results of this study are convergent, at least qualitatively.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{O_Ba_spread_resolution-comparison.png}
+\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study.png}
 \caption{Resolution comparison at two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.

### 2018-07-14 main.tex
Update on Overleaf.

@@
 % GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
-\title{Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies}
+% AE: Had a hard time coming up with a succinct and interesting sounding title that
+%     fit both of the interesting results: 
+%          1) analytic PDF fits and 2) variations in metal mixing...
+\title{Metal Mixing in Dwarf Galaxies is Dependent on Nucleosynthetic Source}
+
+%Non-Uniform Metal Distributions in a Dwarf Galaxy Simulation}
+%Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies}
 
@@
 Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}).
-One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (e.x.
-stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas.
-(\textit{...
-more...})
-% Discuss common modeling assumptions in CE models that
-%    can be addressed here:
-%        1) instantaneous recycling approximation
-%        2) No metal mass loading of winds, or uniform 
-%           loading across species
-%        3) Uniform metal abundances across the ISM (one zone)
+One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (from stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas.
 %
-%  To some degree, cosmological simulations with comparably
-%     low spatial resolution face the same problems, where
-%     variations and spreads in abundances (esp. across 
-%     species) can be smoothed over due to the low res. or
-%     the particular details of the feedback methods and
-%     yield injection methods.
+% get a sentence with a better punch at the end
+%
 
@@
 Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}).
-% more on mixing
 Consequently, following metal mixing, if treated in these models, requires assumptions in how metals mix within the ISM and how metals couple to galactic outflows.
@@
 However, these processes are critical components in understanding galactic chemical evolution.
-Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillota2018}.
+Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillotta2018}.
 In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.
@@
 The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1968,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
-It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucelosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
+That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
 Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
@@
 
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.95\linewidth]{sfr_snrx100_agb.png}\\
-%\caption{}
-%\label{fig:sfr}
-%\end{figure}
-
 \subsection{Preferential Ejection of Metals from the ISM}
@@
 \caption{The fraction of each metal species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).
-The leftmost bar in each plot shows the sum of all metals.
-\textbf{Need to font sizes and mass labels}}
+The leftmost bar in each plot shows the sum of all metals.}
 \label{fig:species_fractions}
-% GB(AE): Why are H and He different? Either discuss or remove from plot.
-%  ------ AE removed from plot
-%
 \end{figure}

### 2018-07-14 main.tex
Update on Overleaf.

@@
 We show histograms of the average number density within 20~pc of any given enrichment source (top) and height above/below the disk (bottom) within 1~Myr of each event (as limited by our output cadence) in Figure~\ref{fig:spatial distribution}.
-As shown, SN have a bi-modal distribution in density as they explode either close to their dense formation region or within superbubbles, while AGB stars are singly peaked between this distribution at close to the average ISM density.
+As shown, SN peak at very low densities, indicating that most explode in superbubbles, regions carved out by previous SNe.
+AGB stars predominately release their metals close to the average ISM density.
+The scale height distributions for both events show no significant differences.
 We do not expect these differences to be the dominant effect in driving the differential evolution of elements ejected by AGB winds vs.

### 2018-07-15 main.tex
Update on Overleaf.

@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
+\caption{The separation (in dex) of each star's oxygen fraction from the median value of the gas phase oxygen mass fraction PDF for the CNM at within 1~Myr (our time resolution) of each star's formation time.
+The median deviation is given in the plot for stars formed after the initial enrichment period, or 100~Myr.}
+\label{fig:stars}
+\end{figure}
+
 \subsection{Do these results apply to more massive galaxies?}

### 2018-07-15 main.tex
Update on Overleaf.

--- 2018-07-14 main.tex
@@
 We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
-These PDFs have been computed at an arbitrary single point in time, at 380 Myr.
+These PDFs have been computed at an arbitrary single point in time, at 270 Myr.
 For clarity, we only show a subset of the 15 elements we follow.
@@
 However, star forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, follow a similar PDF to the CNM.
-To verify this, Figure ~\ref{fig:stars} shows the difference between the mass fraction of a given element in stars and the median mass fraction from the CNM PDF at the time that particle formed.
-Stars seem to be sampled evenly around the median of the CNM distribution (i.e.
-there is no obvious bias towards high metal fractions).
+To verify this, Figure ~\ref{fig:stars} shows the difference between the oxygen mass fraction of stars and the median mass fraction from the CNM PDF at the time that particle formed.
+The large scatter at early times ($<$ 120~Myr) is a result of the early enrichment phase, when the initial gas oxygen mass fraction was zero.
+Stars seem to be sampled evenly around the median of the CNM distribution, with only a slight bias (52\% of stars) towards values below the median.
+However, for stars formed after the initial phase, the median separation from the CNM median is 0.31~dex, and can reach up to $\sim$~0.5~dex.
+Though a significant deviation, this is smaller than the typical IQR of the CNM (see Figure~\ref{fig:phase-statistics}).
 Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
 High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
+
+The first core collapse supernova occurs at 12~Myr,
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
+\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the within 1~Myr (our time resolution) of each star's formation time.
+The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
+\label{fig:stars}
+\end{figure}
 

### 2018-07-15 main.tex
removing uneeded comments and fixing spelling mistakes

--- 2018-07-14 main.tex
@@
-\documentclass[twocolumn]{aastex61}
-\pdfoutput=1 %for arXiv submission
-\usepackage{amsmath,amstext}
+%\documentclass[twocolumn]{aastex61}
+%\pdfoutput=1 %for arXiv submission
+\documentclass[fleqn,usenatbib,useAMS]{mnras}
+\usepackage{graphicx}	% Including figure files
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+\usepackage{multicol}        % Multi-column entries in tables
+\usepackage{bm}		% Bold maths symbols, including upright Greek
+%\usepackage{pdflscape}	% Landscape pages
+
 \usepackage[T1]{fontenc}
-\usepackage{apjfonts} 
+\usepackage{ae,aecompl}
+\usepackage{newtxtext,newtxmath}
+
+%\usepackage{amsmath,amstext}
+%\usepackage[T1]{fontenc}
 \usepackage[figure,figure*]{hypcap}
 
-\renewcommand*{\sectionautorefname}{Section} %for \autoref
-\renewcommand*{\subsectionautorefname}{Section} %for \autoref
+\hypersetup{draft}
+%\usepackage{multirow}
+%\usepackage{mathtools}
+%\renewcommand*{\sectionautorefname}{Section} %for \autoref
+%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
+%\usepackage{graphicx}
 
-\shorttitle{Differential Metal Mixing}
+%\usepackage{apjfonts} 
+%\usepackage{natbib} % bibliography
+
+%\usepackage[active,floats,tightpage]{preview}
+%    \setlength\PreviewBorder{1em}
+
+%\shorttitle{Feedback with Individual Stars}
+%\shortauthors{Emerick, Bryan, Mac Low}
+\newcommand{\msun}{M$_{\odot}$}
+\newcommand{\ccunit}{cm$^{-3}$}
+
+%%%%%%%%%%%%%%%%%%\hypersetup{draft}
+% For bibtex
+
+\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
+
+\author[A. Emerick et. al.]{
+Andrew Emerick,$^{1,2}$
+Greg L. Bryan,$^{1,3}$
+and Mordecai-Mark Mac Low$^{2,1}$
+\\
+$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
+$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
+$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
 
@@
 
-%\title{Evolution of Individual Metals in Galactic Winds and the ISM}
+\label{firstpage}
+%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
+%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
 
-% GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
-% AE: Had a hard time coming up with a succinct and interesting sounding title that
-%     fit both of the interesting results: 
-%          1) analytic PDF fits and 2) variations in metal mixing...
-\title{Metal Mixing in Dwarf Galaxies is Dependent on Nucleosynthetic Source}
+%\author{Andrew Emerick}
+%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+%\author{Greg L. Bryan}
+%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+%\author{Mordecai-Mark Mac Low}
+%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
 
-%Non-Uniform Metal Distributions in a Dwarf Galaxy Simulation}
-%Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies}
-
-\author{Andrew Emerick}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\author{{\it more...}}
+%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}
 
 \begin{abstract}
-Using a high resolution simulation of an isolated dwarf galaxy, accounting for stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy through galactic winds.
-For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal + power-law distribution.
-The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail.
-The PDF properties, and relative significance of these two components, vary within each ISM phase.
-Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component.
-In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe).
-This difference is driven by the differences in energetics between each source, particularly the poor coupling of AGB winds to the ISM.
-Nearly all of the produced metals are ejected from the galaxy (only 5\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
-In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae.
-We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
+In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
+For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
+We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints.
+We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
+We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
+Effective feedback \textbf{drives outflows with a greater metallicity than the ISM}, leading to low metal retention fractions consistent with observations.
+Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
 \end{abstract}
 
-\keywords{}
+\begin{keywords}
+Galaxy -- Hydrodynamics -- Simulation -- Feedback
+\end{keywords}
 
 \section{Introduction}
-% can I work "Currents of Space" into this paper somehow (Asimov)?
-Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}).
-One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (from stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas.
 %
-% get a sentence with a better punch at the end
+% AE removed below.. MM suggested  skipping both pars.
 %
+%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade.
+Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc.
+\citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses.
+On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM.
+This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}.
+See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.
+%
+%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution.
+In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense.
+In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships.
+For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.
 
-One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references).
-While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood.
-This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
-Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}).
-Consequently, following metal mixing, if treated in these models, requires assumptions in how metals mix within the ISM and how metals couple to galactic outflows.
-When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly.
-However, these processes are critical components in understanding galactic chemical evolution.
-Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillotta2018}.
-In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.
+Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution.
+Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
+There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
+%{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
+These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
 
-The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
-It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
-Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
-However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
+However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}.
+In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
+This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
+While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficienty high spatial resolution.
+Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
+Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b, KrumholzTing2018}.
+Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
+the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
+The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
 
-It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group.
-(\textit{ references to APOGEE, GAIA, GALAH, RAVE, TGAS}).
-Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
-The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM.
-However, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.
+Increasing physical resolution reduces reliance on sub-grid physics for mixing.
+However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}.
+Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
+\textbf{This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
+At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.} Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
+The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
 
-In this paper we present the first detailed chemical evolution results from a set of high resolution hydrodynamics simulations in the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014} of an isolated, low mass dwarf galaxy.
-The simulation discussed here was first introduced in detail in Emerick et.
-al.
-2018 (hereafter Paper I).
-To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae.
-This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below.
-We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species.
-We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.
+We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies.
+The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms.
+We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
+%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies.
+\citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
+Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar winds from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
+We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar far ultra-violet (FUV) radiation, and Lyman-Werner dissociation from stellar radiation.
 
-The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity.
-Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging.
-[list examples of modelling problems].
-These uncertainties combined with the difficultly in simulating a fully self-consistent galaxy in detail motivates this current study.
-By focusing on a low mass dwarf galaxy, we are capable of capturing detailed feedback and ISM physics at high resolution, while following individual stars, due to their small physical scales and low star formation rates.
-In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios for two reasons.
-First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
-Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies with observational analogs in as much detail as we provide here.
-This work will be the first in several in attempting to bridge this gap.
-With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and low resolution simulations of more massive galaxies with physically motivated sub-grid physics models.
+Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime.
+This includes yields from massive and AGB stellar winds, and supernovae (SNe).
+In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
+This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
+This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
+We describe each mode of our multi-channel feedback
+in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.
 
-We summarize of our methods and physics models in Section~\ref{sec:methods}.
-We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}.
-In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
+Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.
 
@@
 \label{sec:methods}
-We refer the reader to Paper I for a detailed description of our numerical methods and feedback models. We briefly summarize the relevant details here.
+We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
+This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
+To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background.
+We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}).
+We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
+Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
+We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on HI.
+In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
+We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both.
+We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors.
+We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species.
+In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked.
+This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth.
+These methods are discussed in full detail below.
 
-\textit{Hydrodynamics ---} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}.
-Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
-We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver.
-We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
-Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas and 2) a cell's local Jeans length becomes resolved by less than 8 cells.
-If the cell is within 4 zones of a star particle with active feedback, it is refined to the maximum resolution.
-At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.
+\subsection{Hydrodynamics and Gravity}
+\label{sec:hydro}
 
-\textit{Chemistry, Heating, and Cooling Physics ---} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
-We account for approximate self-shielding of HI against the UV background following \cite{Rahmati2013}.
-We assume HeI self-shields in the same fashion as HI, and ignore HeII heating from the UVB entirely.
-Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}.
-Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.
+We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies.
+\texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions.
+We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick.
+Specifically, simulations presented here were conducted at changeset 7001d99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
+We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}).
+Self-gravity is computed with a multigrid Poisson solver.
+The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.
 
-\textit{Star Formation ---} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
-Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$.
-Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$).
-We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\%.
-Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment.
-We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
+We refine the mesh whenever the \textbf{thermal} Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
+At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation.
+\citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.
 
-\textit{Stellar Feedback and Stellar Yields ---} We track the feedback and yields of 15 metal species for each star individually.
-Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
-Stars above this mass are assumed to direct collapse with no mass or energy injection.
-For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their HI and HeI ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
-We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars.
-Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind.
-Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
-Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et.
-al.
-in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.
+We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}).
+Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
+However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse.
+\textbf{A non-thermal pressure term is added} to cells once their \textbf{thermal} Jeans length becomes unresolved.
+This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
+The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.
 
-\textit{Initial Conditions ---} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
-We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$.
-The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
-Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium.
-The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
-Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
-Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.
+\textbf{Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas.
+These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution.
+At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr.
+We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$.
+These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions.
+This threshold decreases the required run-time by factors of a few.
+The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)}
+
+\subsection{Chemistry and Cooling Physics}
+\label{sec:chemistry}
+
+We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset c2c0faf.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes.
+We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.
+We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
+However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}.
+For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
+
+As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
+As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
+Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}.
+To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.
+We have made these new tables public in the main \texttt{Grackle} repository.
+These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
+Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.
+
+\subsection{Star Formation Algorithm}
+\label{sec:star formation}
+In order to resolve individual star formation events on galactic scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
+Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local \textbf{thermal} Jeans mass.
+Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K.
+We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$.
+No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.
+
+We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
+At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
+
+The stellar mass formed during a timestep $\Delta t$ \textbf{from a region with a total gas mass $M_{\rm gas}$} is
+\begin{equation}
+         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
+\end{equation}
+In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution.
+We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses.
+In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
+If it does, we randomly sample from
+the adopted IMF until \textbf{approximately} 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
+\textbf{The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.} We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
+Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
+\textbf{By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.}
+
+Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
+This dispersion captures some of the unresolved gas motions below the resolution limit that are smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations.
+Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
+
+Stars evolve during the simulation, by losing mass from stellar winds and SNe as described below, and by changing types, but persist throughout the entire simulation.
+For example, low mass stars are tagged as white dwarfs (WDs) at the end of their life, which may eventually explode as a Type Ia SN (discussed below), after which they persist as massless tracer particle remnants.
+Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a four-cell region at the highest level of refinement.
+This ensures that both stellar winds and SNe feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.
+
+\subsection{Stellar Properties}
+\label{sec:properties}
+Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}).
+We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$.
+Although $T_{\rm eff}$ and $g$ evolve over time for stars, modifying stellar radiative properties, following a stellar evolution track for each of our stars is beyond the scope of this work.
+We instead fix these properties at their zero age main sequence values.
+
+\subsection{Stellar Feedback and Chemical Yields}
+
+\subsubsection{Stellar Yields}
+\label{sec:yields}
+For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars.
+We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}.
+This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$.
+We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$.
+We ignore SN yields from these stars (see next paragraph).
+We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth.
+Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation.
+We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017a} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
+
+%
+% KVJ: Possibly include a discussion on uncertainties in stellar yields
+%
+
+Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe.
+Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$.
+This is a free parameter in our model; we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value.
+In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
+Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics).
+Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
+\citet{Cote2017a} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
+We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
+
+There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}.
+Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
+Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass, metal, or energy ejection.
+
+Type Ia SNe are an important additional source of galactic chemical enrichment.
+These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
+We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
+We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, substantially limiting the number of Type Ia SNe occurring during the initial gigayear in our models.
+
+\subsubsection{Stellar Winds}
+\label{sec:stellar winds}
+Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
+Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback.
+We assume complete thermalization of the wind kinetic energy, taking the total injected energy injected in timestep $\Delta t$ as $E_w = \frac{1}{2}\dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
+\textbf{This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle.
+The edges of this spherical region will only partially overlap grid cells.
+We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately.} We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
+
+Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}.
+Satisfying the Courant time step becomes prohibitively expensive following this gas, with time steps dropping to $\Delta t \sim$~100~yr.
+For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
+In our case, we fix massive stellar wind velocities to $v_w = 20$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
+Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies.
+Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work.
+These points are discussed in more detail in Sect.~\ref{sec:stellar winds discussion}.
+
+% Injecting 10$^{3}$ km s$^{-1}$ gas onto the grid at these scales leads to super heated, shocked gas at unphysical temperatures of about 10$^{8-9}$ K, particularly when injecting into very low density media.
+This can lead to painfully short time step sizes and crashes in the hydrodynamics solver.
+We adopt the common solution of artifiially reducing the wind velocity from massive stars, choosing $v_{\rm wind} = 500$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
+However, this can still be problematic once the star evacuates the local ISM and injects its energy to very low density ($n \lesssim 10^{-3}$ \ccunit) gas.
+We address this issue by mass loading our winds when injection would lead to wind bubble temperatures in the spherical source region above a maximum temperature typical of wind bubble.
+This is a free parameter that we take to be 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
+Mass loading in this manner is (in effect) a sub-grid model for the unresolved ISM mixing at the boundary layer of the wind bubble, which is in fact the source of a majority of the gas mass within the wind bubble \citep{Weaver1977}.
+We take the metal species abundances of the mass loaded ISM to be the average cold / warm ISM abundance on each grid to prevent artificially inflating/deflating the overall abundances.
+We discuss our ability to resolve typical single star wind bubble properties in Appendix ~\ref{appendix:stellar winds}.
+
+%parameterized in this work with the STARBURST99 wind model, \citep{Leitherer1992}:
+%\begin{multline}
+%{\rm log} \left[ v_{\rm wind} {\rm (km~s^{-1})} \right] = 1.23 - 0.30~{\rm log}~\left[L{\rm (L_{\odot})}\right] \\
+% + 0.55~{\rm log}\left[M({\rm M_{\odot}})\right] + 0.64~{\rm log}\left[T_{\rm eff}(K)\right] \\
+% + 0.13~{\rm log}\left[Z({\rm Z_{\odot}})\right].
+%\end{multline}
+
+Stars that only undergo an AGB phase deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks.
+AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$.
+For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars as well.
+
+\subsubsection{Core Collapse SNe}
+\label{sec: core collapse}
+Stars between  $M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
+Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}).
+We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
+We use the same Monte Carlo sampling method as used in our stellar winds to map the spherical injection region to the grid.
+We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle.
+In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.
+
+\subsubsection{Type Ia SNe}
+\label{sec:Type Ia}
+We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as WD particles, marking a subset as Type Ia SN progenitors.
+This is the most self-consistent model for Type Ia SNe in galaxy-scale simulations.
+We note however that for the low SFRs in our isolated dwarf galaxy simulation, the first Type Ia SN only appears after a few hundred megayears of simulation time.
+By the end of the simulation presented here (500~Myr), only 18 have gone off.
+At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
+%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
+%or, 
+%\[
+%M_{\rm WD} = 
+%\begin{cases}
+%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
+%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
+%\end{cases}
+%\]
+%where $M_{\rm *}$ is the initial mass of the WD progenitor.
+We follow the common assumption that progenitor stars with initial masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017a}.
+
+We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution model.
+The Type Ia SN rate is taken to be a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope $\beta$ and normalization $N_{\rm Ia}/M_{\rm SF}$ are observables.
+The latter represents the number of Type Ia SNe per mass of star formation.
+By assuming an IMF  $dN/dm$, one can write down the fraction $\eta$ of stars capable of forming a Type Ia SN progenitor that \textit{will} explode within a Hubble time.
+This is given as
+\begin{equation}
+\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
+\end{equation}
+where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF, and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
+The distribution slope $\beta$ is of order unity, with typical values between 1.0 and 1.2 \citep[see][for a recent review]{Maoz2014}.
+$N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the Type Ia SN rate and integrating over a Hubble time.
+Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
+For our fiducial values, we adopt $\beta = 1.2$ \citep{Maoz2010} and $N_{\rm Ia}/M_{\rm SF} = 0.8\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013}.
+Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.
+
+Finally, we can normalize $\Psi(t)$ to give the probability per unit time $\dot{P}(t)$ that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor.
+Integrating this gives the total probability at any given time as
+\begin{equation}
+P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
+\end{equation}
+where $t_{\rm o}$ is the formation time of the WD and the leading term on the right hand side properly normalizes the total probability over a Hubble time to $\eta$.
+This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
+\textbf{In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle.
+For $u \in [0,1]$, we interpolate its position on a pre-tabulated and inverted cumulative probability distribution function to assign a single time at which the WD particle will explode as a Type 1a supernova.
+We institute a minimum delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.}
+
+\subsubsection{Ionizing Radiation from Discrete Sources}
+\label{sec:ionizing radiation}
+Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies.
+\ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance.
+However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds.
+Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
+As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.
+
+Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation.
+We follow HI and HeI ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
+
+We determine the HI and HeI ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
+We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star.
+Stars less massive than about 15 M$_{\odot}$ and very massive stars with sub-solar metallicity are generally not well sampled by the OSTAR2002 grid.
+In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).
+
+Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}).
+The average energy for HI and HeI ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
+
+We also include the effects of radiation pressure on HI.
+This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}.
+We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared.
+This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}.
+However, the importance of multiple scattering is still unclear.
+Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013a,Reissl2017,Wibking2018}.
+Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.
+
+\subsubsection{Diffuse  Heating}
+\label{sec:diffusive heating}
+We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the FUV (6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles.
+The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the spectral energy distributions for each gridded star.
+Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
+Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
+However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}.
+Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile.
+Only recently has the localization and time variation of these processes been considered.
+
+Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}.
+We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
+We assume HeI ionization generally follows HI.
+This allows us to approximate HeI self-shielding using the same form (A.
+Rahmati, private communication).
+We ignore HeII photoionization from the UV background entirely.
+{\bf For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.}\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
+As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
+This is described in more detail in Appendix ~\ref{appendix:cooling}.
+
+%Ignoring this effect leads to an overestimation of the cooling rates when in the self-shielding regime.
+%We refer to \citet{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \citet{Gracklemethod} for its specific implementation, as used here.
+
+We assume the galaxy is mostly optically thin to stellar FUV and use only local approximations for shielding.
+We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
+\begin{equation}
+\label{eq:PE}
+\Gamma_{\rm pe} = (1.3 \times 10^{-24} \rm{erg~s^{-1}~cm^{-3}})\, \epsilon n_{\rm H} G_{\rm eff} D 
+\end{equation}
+where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust-to-gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
+Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
+
+The value of $D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
+The extremely low dust-to-gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a ratio $D$ that scales linearly with metallicity at very low metallicity.
+At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit.
+Given that the ambient density of the ISM is generally 1--10~cm$^{-3}$, we can safely assume the FUV field to be optically thin.
+However, we do include a localized attenuation prescription that may influence high-density or metal-enriched regions of the galaxy.
+We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.
+
+Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
+This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations.
+\textbf{Our chemical work only includes contributions from H, He, and H$_2$ to n$_e$.} Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
+%This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
+
+\subsubsection{Lyman-Werner Radiation}
+\label{sec:LW}
+In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rate.
+We compute the stellar Lyman-Werner flux again from the OSTAR2002 grid by integrating the spectral energy distributions over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}).
+Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
+We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.
+
+\section{Galaxy Initial Conditions}
+\label{sec:IC}
+We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy.
+The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
+Leo P is gas rich, with a \textbf{neutral hydrogen mass} $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and \textbf{stellar mass} $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to an \textbf{observed neutral hydrogen radius} $r_{\rm HI} = 500$~pc.
+LeoP has a low metallicity, with \textbf{an oxygen to hydrogen abundance ratio (O/H)} of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
+Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
+
+The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential.
+The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
+\begin{equation}
+\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
+\end{equation}
+where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass.
+We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$.
+We adopt a \citet{Burkert1995} dark matter potential with \textbf{virial mass and radius} $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and \textbf{scale radius} r$_{\rm s} = 990$~pc.
+This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc.
+These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}.
+
+Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
+This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
+During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}.
+We stop the artificial driving 25~Myr after the first star particle forms.
+These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
+We note this initial driving is ad hoc in that we do not include other effects from the stellar population that would have caused these SNe.
+
+We emphasize here that our model, with no initial stellar distribution, is not intended to identically reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
+In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations.
+Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances.
+In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution.
+Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe.
+The subsequent metal enrichment from the stars in our simulation can be thought of as tracking a change in abundances from arbitrary initial conditions.
+We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.
 
 \section{Results}
-For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
-This galaxy has an average star formation rate of $1.2~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
-The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy.
-The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$.
-These winds eject 95\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.
+\label{sec:results}
+We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms.
+Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run.
+The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical height $|z| < 200$~pc relative to the center of the galaxy.
+ISM properties are calculated considering only the gas contained within the disk of the galaxy.
+We include a resolution study in Appendix \ref{appendix:resolution_study}.
 
-In this work we focus in detail on how each of the 15 individual metal species evolve in this galaxy.
-We address differences between the ejection fractions of each metal in Section~\ref{sec:ejection} and analyze for the first time the mass-fraction PDFs of the metals retained by the ISM in Section~\ref{sec:mixing}.
+Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.
+All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset dd76ad10.
 
-\subsection{Preferential Ejection of Metals from the ISM}
-\label{sec:ejection}
+\subsection{Morphological Structure and Evolution}
+\label{sec:structure}
+
+We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
+These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
+This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
+This central region quickly fills with warm and hot gas generated from radiation feedback and SNe respectively.
+Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels.
+The ISM properties are quantified further in Section~\ref{sec:phase}.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
+\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation.
+Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row).
+Each individual main sequence star particle is shown in the number density projections as a single black dot.}
+\label{fig:panel_x}
+\end{figure*}
+
+The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
+This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time.
+Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--120~pc.
+Towards the end of the simulation time, the half-light radius is $391 \pm 19$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
+Although the disk remains thin beyond the half-light radius, with a scale height of around 50~pc, it is fully resolved at all radii.
+By the end of the simulation, the majority of the disk has a scale height of $\sim$100~pc.
+
+Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging.
+For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
+\textbf{In the final column of Figure~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
+With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
+At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$.
+These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
+\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on views.}
+\label{fig:panel_z}
+\end{figure*}
 
@@
 \centering
-\includegraphics[width=0.99\linewidth]{species_bar.png}\\
-\includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
-\caption{The fraction of each metal species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).
-The leftmost bar in each plot shows the sum of all metals.}
-\label{fig:species_fractions}
+\includegraphics[width=0.975\linewidth]{scale_height}
+\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figures~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
+\label{fig:scale_height}
 \end{figure}
 
-The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
-We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
-Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+\subsection{Star Formation Rate and Mass Evolution}
+\label{sec:sfr}
 
-We find two major results.
-First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases.
-The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
-This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
-Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however,the retention factor varies.
-The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
-This suggests that individual metals \textit{do not} share the same dynamical evolution.
-Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field.
-In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
+We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
+The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$.
+The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation.
+Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.19 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
+We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.
 
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{species_bar_sources.png}\\
-\caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
-These channels differ in both when metals are ejected, as determined by stellar evolution, and the energy with which they are ejected into the ISM.
-We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because only XX of them have exploded by the end of our 500~Myr simulation.}
-% GB(AE): Why are H and He different? Either discuss or remove from plot.
-%  ------ AE removed from plot
-%
-\label{fig:species_sources}
-\end{figure}
+We note that the granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
+Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
+For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$.
+Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense.
+Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.
 
-The only physics that separates the dynamical evolution of these elements in our simulations is the individual sources of enrichment: AGB winds (stars less than 8~M$_{\odot}$), stellar winds (stars above 8~M$_{\odot}$), core collapse supernovae, and Type Ia supernovae.
-These channels differ in: 1) how long after a given star formation event they occur, 2), by consequence, the typical ISM properties in which they occur, 3) how much energy is associated with each event, which determines ejecta temperature and velocity.
-To understand where each of the elements in Figure~\ref{fig:species_fractions} originated, we show the mass fraction of metals produced through each channel in Figure~\ref{fig:species_sources}.
-Core collapse supernovae are responsible for over 90\% of the total metal enrichment in our galaxy, but this is clearly not true for all elements.
-In particular, a majority of N (74\%) and Ba (65\%) are ejected by AGB winds; both are retained at a higher rate than the rest of the metals.
-That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yields tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through supernovae.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and supernovae.
-However, this cannot be determined as we lack Lagrangian information about individual gas elements.}
-% AE: Actually if there are significant isotope variations between nucleosynthetic sources (i.e.
-N produced in AGB winds is a different isotope than the trace N produced in SNe) then that could be a very cool thing to distinguish if we had good gas-phase abundance measures of various isotopes...
-but maybe not if they aren't very stable....
- We discuss how this result may extend towards other metal yields that are not well sampled on our relatively short (500 Myr) simulation timescales in Section~\ref{sec:discussion:metal yields}.
-
-AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of supernovae ($\sim$1000~km~s$^{-1}$).
-In addition, their longer timescales (40-100~Myr as compared to $\sim$10~Myr) means that AGB stars are typically removed from their birth regions.
-The changes in typical ISM density and height of these events contributes to these variations.
-We show histograms of the average number density within 20~pc of any given enrichment source (top) and height above/below the disk (bottom) within 1~Myr of each event (as limited by our output cadence) in Figure~\ref{fig:spatial distribution}.
-As shown, SN peak at very low densities, indicating that most explode in superbubbles, regions carved out by previous SNe.
-AGB stars predominately release their metals close to the average ISM density.
-The scale height distributions for both events show no significant differences.
-We do not expect these differences to be the dominant effect in driving the differential evolution of elements ejected by AGB winds vs.
-supernovae, compared to the energetics, but can certainly play a significant role in determining the mixing behavior of individual enrichment events.
-The changes to mixing behavior as a function of ISM properties will be investigated in more detail in a future work.
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{SE_density.png}\\
-\includegraphics[width=0.95\linewidth]{SE_z.png}
-\caption{The average gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
-\label{fig:spatial distribution}
-\end{figure}
-
-\subsection{Mixing and Distribution of Metals in the ISM}
-\label{sec:mixing}
-
-Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
-In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}).
-Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances.
-In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
-However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
-To build towards this, we characterize the metal evolution and distributions in our galaxy below.
-
-% Classic chemical evolution models often adopt the simplifying assumption that metals from newly formed stars are instantly deposited back into the ISM \textbf{(examples)}.
-With added complication, this instantaneous recycling approximation (IRA) can be expanded upon by taking into account individual stellar lifetimes (references) which have been shown to produce significant variations in stellar abundances (references) as compared to IRA models.
-However, even in this new model it is unlikely that whatever fraction of a star's yields that remains in the ISM instantaneously enriches star forming gas.
-Rather, these yields are first injected through a hot phase (stellar winds, HII regions, supernovae), cooling over time into star forming gas.
-(refs for models accounting for this).
-We investigate this process in our simulations below, first by outlining a new analytic description of metal distributions in the ISM.
-
-\subsubsection{A Functional Form for Metal PDFs}
-\label{sec:log-normal}
-
-The log-normal distribution is found often in nature, generally describing processes with non-negative values that grow with time.
-In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}.
-In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}.
-Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}.
-It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape.
-This includes a log-normal component, generated by multiplicative processes (shocks and the turbulent cascade in the ISM) and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2017}.
-
-The physics that drives the density PDF is directly related to the process of metal mixing and diffusion.
-However, there is no a priori reason why gas density and metallicity PDFs should have similar functional forms.
-We demonstrate here for the first time that the mass fraction PDFs for each metal species in our simulation can indeed be well fit using a piecewise log-normal + power-law PDF.
-We use a simple conceptual model in Section~\ref{sec:interpretation} to motivate the emergence of this distribution.
-
-We follow \cite{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF.
-We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element.
-This PDF is given as
-\begin{align*}
-  p(Z) = 
-  \begin{cases}
-    \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right], 
-    & Z < Z_{\rm{t}} \\
-    % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
-    N p_o Z^{-\alpha},
-    & Z > Z_{\rm{t}}
-\end{cases}
-\end{align*}
-where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm t}$ is the metal fraction at the transition between the log-normal and power-law components.
-When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm t}$ as free parameters.
-These conditions set $N$ and $p_o$ to
-\begin{equation}
-N = \frac{1}{2} \left[ 1 + \rm{erf}\left( \frac{ln\left(Z_{\rm t}\right) - \mu}{\sigma\sqrt{2}}\right)\right] + \frac{p_o}{\alpha-1}Z_{\rm t}^{-\alpha + 1}
-\end{equation}
-and
-\begin{equation}
-p_o = \frac{1}{\sigma Z_{\rm t} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm t}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm t}) \right]
-\end{equation}.
-
-We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin with of 0.05 dex.
-We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \cite{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins.
-The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted.
-The log-normal + power-law PDF produces the best fit in nearly all cases.
-
-We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
-These PDFs have been computed at an arbitrary single point in time, at 380 Myr.
-For clarity, we only show a subset of the 15 elements we follow.
-As shown, there are clear differences in the PDFs across elements of different nucleosynthetic origins and between each phase.
-However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions.
-We discuss the differences among each phase in more detail in the next section, but note here that the significance of each of these components varies notably across phases.
-In many of these cases, the piecewise log-normal + power-law distribution fits the numerical PDF quite well.
-However, there are often deviations, particularly at low metal fractions, from pure log-normal behavior.
-This manifests as either a very broad, flat PDF at low metal fraction (see N and Ba, for example), or large peaks not well described by $p(Z)$ at low metal fraction.
-In these situations, it is unclear what, if any, portion should be considered as a log-normal, or if there are multiple components within this region.
-
-We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the the metal fraction  PDFs of individual elements in galaxy models.
-The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM.
-In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions.
-Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$.
-As this is the source of star forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.
+At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, \textbf{ with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
+The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
+For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% at 500~Myr.
+The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy from feedback-driven galactic winds.
+During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM.
+Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
+The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.}
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
-\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), HIM (red), and all the gas in the ISM (black).
-For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
-We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.
-Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
-\label{fig:log-normal}
+\includegraphics[width=0.475\linewidth]{sfr_snrx100}
+\includegraphics[width=0.475\linewidth]{mass_evolution}
+\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins.
+Broken portions of this histogram are time periods with no star formation or supernovae.
+Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.
+Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
+\label{fig:sfr_mass_evolution}
 \end{figure*}
 
-\subsubsection{PDF Variation Across Gas Phase}
-\label{sec:phase-pdfs}
+\subsection{ISM Properties}
+\label{sec:phase}
 
-The various phases represented in Figure~\ref{fig:log-normal} involve variations in density and temperature of more than six orders of magnitude.
-The evolution of each phase is qualitatively different, and the metal mixing behavior of each should vary.
-Mixing timescales over a given length scale should be related to the local sound speed; hot gas, with higher sound speeds, should mix more rapidly than the dense, disconnected clumps of cold gas in the ISM.
-In addition, one would expect a metallicity gradient with gas temperature as enrichment occurs first in the hot phases, cooling and enriching denser gas over time.
-We examine the PDF variations among elements in each phase, as shown in Figure~\ref{fig:log-normal}, in more detail here.
+Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
+We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
+We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content.
+\textbf{By this definition, although our galaxy certainly contains molecular hydrogen, molecular gas as a phase does not exist; the peak f$_{\rm H_2}$ in any single cell remains below 30\%.} See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
+The properties of these phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
+Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.
 
-Unsurprisingly the diffuse HIM contains the most metal enriched gas, as it is comprised predominately of metal enriched supernova ejecta.
-Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
-Generally, in colder gas the metal PDFs become less enriched with broader low metal fraction components and steeper, power-law tails.
-Although the extended power-law tail of the HIM leads to a large range of metal fractions, the HIM represents very little mass, and this tail represents recent, un-mixed enrichment.
-The comparatively narrow width in the log-normal regimes of CNM is perhaps surprising.
-Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is more well mixed.
-This runs counter to the idea that mixing times should be long in colder gas unless mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.
+Figure~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
+One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
+Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
+We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
+\textbf{Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left.}  The boxed regime in the lower right corner shows our star formation density and temperature threshold.
+Gas in this regime is rapidly consumed by star formation and subsequent feedback.
+Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average.
 
-Although these trends across phases hold for all elements, there are qualitative differences between elements, particularly between those ejected predominantly by AGB winds (e.g.
-Ba and N) and those ejected by supernovae (e.g.
-O and Mg).
-In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by supernova enrichment.
-The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the CNM.
-Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N produced in supernovae yields.
-Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and supernovae.
-AGB wind elements enrich the WNM and WIM directly, rather than the HIM, which would increase their mixing timescales and broaden their PDFs.
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{phase_diagram.png}
+\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gas interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr.
+The dashed lines are lines of constant pressure, separated by factors of 10.
+The region in the lower right corner indicates our density and temperature thresholds for star formation.}
+\label{fig:phase}
+\end{figure}
 
-\subsubsection{The Time Evolution of Metal PDFs}
-\label{sec:statistics}
-We focus on the time evolution of the full numerical PDFs in this section.
-Our results here do not depend upon the choice of functional form for $p(Z)$.
-Figure~\ref{fig:phase-statistics} shows the evolution of four different statistics for the O (top) and Ba (bottom) PDFs.
-These two elements are treated as representative elements for supernova and AGB wind production respectively.
-The difference between the mean and median masses of the PDF (second column) is a measure of the skew of the PDF.
-Positive values indicate that metals are preferentially sequestered in metal-rich gas, and are less well mixed throughout the given phase.
-The skew is always positive in these distributions.
+\textbf{H2 changes:} The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
+The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
+The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run.
+The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation.
+During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1.
+Although the CNM dominates the mass fraction, it is a negligible component of the ISM volume, which is WIM dominated.
+However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
+Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
+
+\textbf{H2 Changes:} These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
+They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (defined in those works as gas with 100~K$<$T$< 3\times 10^{4}$), with cold gas having between 1 and 10\% of the mass, and occupying negligible volume.
+Hot gas (defined as gas with $T > 3\times 10^{4}$~K) occupies 10\% of the volume, with negligible mass, in their galaxy, while our WIM alone occupies $>$ 50\% of the volume.
+Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) and hot gas (by volume fraction) that seen in the more massive dwarf galaxy in these works.
+The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
+We have compared our cooling curves to those used in \citep{Hu2017} and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.
+
+\begin{figure*}
+%\centering
+\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
+\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
+\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
+\label{fig:ISM_evolution}
+\end{figure*}
+
+\subsection{Interstellar Radiation Field}
+\label{sec:ISRF}
+
+The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}.
+This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
+In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
+The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
+The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.
+\textbf{The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
+At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.}
+
+\textbf{ The bottom panel gives the HI ionizing photon flux from stellar radiation.
+The ionizing radiation profile follows a similar trend, yet with significantly more variation, anywhere from two to four orders of magnitude.
+As this radiation is followed through radiative transfer, the profile encodes information about local attenuation by dense, neutral gas.
+This is the main driver of the differences between the two panels.
+The total fluctuation in both panels is due in part to the low-level, stochastic star formation in our galaxy.
+A higher star formation rate would produce a more regular population of massive stars and more uniform (in time) ISRF.}
+
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{G_o_profile} \\
+\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
+\caption{
+Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr.
+Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc.
+The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
+The bottom panel gives the HI ionizing stellar radiation flux.
+Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point.
+For this reason we only shade between the first quartile and maximum values.
+HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.}
+\label{fig:ISRF}
+\end{figure}
+
+\begin{figure*}
+%\centering
+\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
+\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
+\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
+Here, we include all gas within the mid-plane of our dwarf galaxy.
+Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
+This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
+\label{fig:ISRF_2D}
+\end{figure*}
+
+To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr.
+This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
+The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
+From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
+Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation.
+In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency.
+It remains to be seen which of these two modes of feedback is more important in regulating star formation.
+
+\subsection{Outflow Properties}
+\label{sec:outflows}
+
+The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}.
+However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
+In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
+We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
+\begin{equation} \label{eq:dotM}
+\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
+\end{equation} 
+We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.
+
+The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
+Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
+For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor.
+The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors between 20--100 throughout the simulation time.
+This declines towards larger radii, however, with substantially less outflow past the virial radius.
+\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift, consistent with our results.
+
+Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
+Using a fit provided in \citet{Muratov2015} to extrapolate and compare $\eta$ at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
+These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
+We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find lower mass loading factors even closer to the disk, at 0.05 $R_{\rm vir}$, between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$; certainly this implies even smaller mass loading factors at 0.25 $R_{\rm vir}$.
+
+\begin{figure*}
+\includegraphics[width=0.45\linewidth]{total_mass_outflow}
+\includegraphics[width=0.45\linewidth]{total_mass_loading}
+\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
+\label{fig:mass_outflow}
+\end{figure*}
+
+\textbf{H2 Changes:} Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
+In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
+Gas with a negative velocity is moving towards the center of the halo.
+Roughly 25\% of this mass is inflowing, mostly with modest negative velocities, and corresponds to previously ejected gas mixing and recycling throughout the halo.
+Half of the outflowing gas (positive velocities) is moving at velocities below 30 km s$^{-1}$, 75\% at velocities below 70 km s$^{-1}$, and 95\% at velocities below 100 km s$^{-1}$.
+Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-neglibable amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$.
+The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominating at velocities above 200 km s$^{-1}$.
+The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling WIM and HIM, consistent with the results in \citet{Hu2016,Hu2017}.
+However, as shown, the HIM, which is mostly the SN ejecta itself, comprises very little of the outflow by mass.
+Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM.
+Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
+The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
+
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
+\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
+This is averaged over the same time interval as Figure~\ref{fig:ISRF}.
+The outflowing material is multiphase, broken into WNM, WIM, and HIM.
+See Section~\ref{sec:phase} for definitions of these regimes.
+We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K.
+There is little to no outflowing mass in the CNM.}
+\label{fig:outflow_velocity}
+\end{figure}
+
+\subsection{Metal Evolution} 
+\label{sec:chemical evolution}
+
+\subsubsection{Metal Enriched Outflows}
+Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
+This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
+In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}.
+The parameter used to quantify metal outflow efficiencies varies among works.
+Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
+\begin{equation} \label{eq:eta-metal}
+\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
+\end{equation}
+where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
+We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions.
+For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but it increases at each radius, fluctuating around unity for the second half of the simulation.
+Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}.
+\cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
+Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.
+
+\begin{figure}
+\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
+\includegraphics[width=0.9\linewidth]{metal_retention}
+\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Figure~\ref{fig:mass_outflow}.
+This is the ratio between the metal outflow rate and the metal production rate.
+{\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
+In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
+\label{fig:metal_evolution}
+\end{figure}
+
+These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
+This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
+After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
+This continues throughout the simulation, with only $\sim$4\% of produced metals residing in the disk of the galaxy.
+It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius until about 350 Myr where the fraction levels off to just above 50\%.
+Likewise, the CGM metal content continually decreases until the end of the simulation from loss through the virial radius of the halo.
+See Section~\ref{sec:obs_metals} for further discussion.
+
+\subsubsection{Differential Evolution of Elements Within the ISM}
+It is important to understand how metals from each source of stellar yields enrich the ISM.
+Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}.
+This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed.
+Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Avillez2002,Tassis2008,YangKrumholz2012}.
+It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
+It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.
+
+We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
+The left panel gives the abundance ratio of N to O throughout the ISM.
+The right
+two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy.
+These show regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K) connected by cold filaments, warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
+
+\begin{figure*}
+\includegraphics[width=0.98\linewidth]{log_NO_panel}
+\caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances.
+The left slice gives the ratio of the abundance between N and O, normalized to the solar abundance, while the number density and temperature are shown on the right.
+In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occurred in the preceding 5 Myr as black stars and orange diamonds respectively.}
+\label{fig:metal_slices}
+\end{figure*}
+
+As shown in the left panel, [N/O] varies significantly over this section of the ISM with notable differences across the various phases and ISM structures.
+The hottest gas, dominated by recent supernova explosions is overabundant in oxygen, relative to solar (purple).
+However, the relative abundance of nitrogen increases in the WIM and WNM, being overabundant relative to solar (green).
+
+At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars.
+Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
+Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
+The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
+This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
+A more detailed analysis is beyond the scope of this work, but we \textbf{investigate this in detail in Emerick et.
+al.
+(in prep.).}
+
+\section{Discussion}
+\label{sec:discussion}
+
+\subsection{Comparison to Observed Low Mass Dwarf Galaxies}
+\label{sec:observation}
+
+As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs.
+Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of $z = 0$ dwarf galaxies.
+However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies.
+We show that these properties are broadly consistent with observations.
+
+\subsubsection{Gas and Star Formation}
+\label{sec:gas_sf}
+
+The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}.
+However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
+In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
+In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.
+
+Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
+We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}.
+We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the area of the disk within the radius of the outermost star formed within the previous 10 Myr.
+Likewise, $\Sigma_{\rm gas} = M_{\rm gas,10} / A_{*,10}$, where M$_{\rm gas,10}$ is the total gas mass within this defined disk.
+However, the total gas content cannot be determined observationally.
+To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He.
+We note that there is generally no correction made for any possible H$_{\rm 2}$ or HII content.
+As shown in Section~\ref{sec:molecular gas content}, these components may be significant.
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution.png}
-\caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation.
-The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
-\label{fig:phase-statistics}
+\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
+\includegraphics[width=0.475\linewidth]{all_gas_efficiency_evolution.png}
+\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
+See text for details of the calculation.
+Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars.
+On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}.
+There is no clear correlation with time in this diagram.} %something is breaking here in compiling
+\label{fig:KS}
 \end{figure*}
 
-For O, the median mass fraction is ordered by phase temperature.
-The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm$ 1 dex over the simulation time.
-The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
-%This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events. 
-Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread.
-The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star forming gas.
-This is the only explanation for how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels).
-Individual enrichment events will have significantly higher metallicities than the ambient ISM in any phase, and will drive an increase in the difference between the mean and median of the PDF.
-These can be seen as the obvious spikes in the HIM and WIM.
-For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.
+We include recent observational constraints on these relationships in Figure ~\ref{fig:KS}.
+Our galaxy fluctuates significantly about both relationships with no clear trends in time.
+However, in both cases, it is consistent with the available observational sample.
+At times our galaxy exhibits gas surface densities below the observational constraints.
+The trend is still consistent with higher densities at this point, but with a larger scatter towards lower star formation rate densities and efficiencies.
 
-% In each phase, enrichment events will tend to drive larger differences between mean and median mass fraction,
+In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
+It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
+This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
+\textbf{The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.}
 
-Although these trends are generally true for Ba, its evolution is much more complicated.
-%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability. 
-Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM.
-The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
-Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in supernovae.
-The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
-These tails represent the most recently enriched gas, and is clearly much more locally confined than O.
+\subsubsection{Molecular Gas Content}
+\label{sec:molecular gas content}
+\textbf{AE: rewording - changed numbers and text to reflect lower H2 fractions. left discussion of uncertainties in H2 formation in low mass dwarfs and need for further study:}
+The molecular gas content of low-mass dwarf galaxies is generally assumed
+to be small, but is not well constrained by either theory or observations.
+Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
+As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range.
+H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
+The gas-phase reaction dominates in our low-metallicity galaxy over the other two channels by several orders of magnitude.
+In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
+Thus the presence of some ionizing background is required to generate the molecular fractions we find in our simulations, as confirmed in test simulations run only to the onset of first star formation.
 
-%{\bf (move to discussion?)}: 
-The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e.
-the ratio between the total mass of metals and the total mass).
-Assuming star forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex), but significant, for elements released during SNe explosions, but can be very significant, up to $\sim$ 0.8 dex, for elements released in AGB winds.
-Chemical evolution models, especially one-zone models, follow the mean metal fraction, not median.
-These results indicate that these models are biased to overestimate gas and stellar elemental abundances.
-. % However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.
+In contrast, \citet{Hu2016} and \citet{Hu2017} find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
+However, although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
+Our model suggests that both H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies.
+Indeed it is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, though it is worth noting that the rate coefficients associated with gas-phase H$_2$ formation are still uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
+Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
+It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
+This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
 
-To summarize, this figure demonstrates: 1) there are qualitative differences in how supernova injected elements (e.g.
-O, Mg) and AGB wind injected elements (e.g.
-N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value.
-In the case of supernova injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
-For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.
+\subsubsection{Metal Retention}
+\label{sec:obs_metals}
 
-\section{Discussion}
-\label{sec:discussion}
-We begin with a simple toy model that motivates the power-law tail at high metal fractions of the metal fraction PDFs and a subsequent turnover at low metal fractions in Section~\ref{sec:interpretation}.
-This work is placed in context with previous works focusing on metal mixing in the ISM in Section~\ref{sec:context}.
-Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impact of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
+The simulations presented here have not yet been run for the gigayear timescales required to begin to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$.
+However, we can compare to a key observable: the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from closed box stellar evolution models given the galaxy's star formation history.
+This can be done readily with Milky Way dSph's.
+Their stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
+However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
 
-\subsection{Physical Interpretation of the PDF}
-\label{sec:interpretation}
-Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_o = 0$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$.
-Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas.
-In this case, $p(Z)$ takes the form of a double-delta function
-\begin{equation}
-p(Z) = \delta(Z) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
-\end{equation}
-If the enriched material mixes continually with the primordial gas at a constant rate, after some time this gas will have mixed with an equal amount of primordial gas.
-At this point, the high metal fraction delta term becomes $\frac{2M_{\rm ej}}{M_o} \delta(Z - \frac{1}{2}Z_{\rm ej})$.
-This implies an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas, and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$.
-If the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, $p(Z)$ will become a power-law in $Z$, truncated at some time dependent minimum $Z$.
-The slope of the power-law is determined by the rate of injection versus mixing with the ambient medium.
-A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium.
-Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than enrichment.
-If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.
+Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich, star forming, low-mass dwarf galaxy, with an observable HII region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
+Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
+As discussed in Section~\ref{sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
+However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
+Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
 
-In reality, however, $M_o$ is not an inexhaustible reservoir of primordial gas.
-Eventually the entire ambient medium will become enriched to some $Z > Z_o$, and $p(Z)$ will consist entirely of a continuous, truncated power-law.
-As enrichment proceeds, gas near the low metallicity truncation of $p(Z)$, which still comprises much of the mass of the system, enriches towards higher metallicities in the power-law tail.
-This will produce a turnover at the low $Z$ limit of $p(Z)$.
-The low-turnover limit is produced by diffusion from many different sources, and is thus an additive process, which, as we noted above, tends to produce log-normal distributions.
-The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.
+It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium.
+While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
+We find 5.3\% of all metals lie within 1 kpc of the center of our galaxy, 24.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 51\% outside $R_{\rm vir}$.
+This is consistent with previous works, but this is again an evolving quantity.
+In addition, the amount of gas that escapes the virial radius is certainly sensitive to the details of gas accretion from the IGM on this galaxy, which we cannot capture in this model.
 
-This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases.
-The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions.
-Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low-metallicities.
-Cold, dense gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.
+The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
+Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return.
+In addition, the accretion of pristine gas from the intergalactic medium could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals.
+This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.
 
-%
-%
-%
-%Although this model is useful to explain these very general features, it is certainly incomplete in practice.
-Enrichment proceeds irregularly through the mulit-phase ISM with a variety of ejection masses and metallicities.
-Phases are not independent, and the hot phase cools and enriches cooler phases in the ISM, distorting $p(Z)$ within each phase.
-Cold gas is heated up and destroyed through feedback, changing the content of the low-metallicity end of the warm and hot phases.
-Finally, gas is removed from the galaxy through feedback driven winds that preferentially remove metal enriched gas.
-Each of these processes has a non-trivial effect on the evolution of the PDF that will cause deviations from the simple toy model outlined here.
-Determining the exact physical processes that drive and set the properties of each PDF is the subject of ongoing work.
+\subsection{Missing Physics}
+Although we include many detailed physical models in our simulations, there remain additional physical processes that may be relevant, which we now discuss.
 
-%
-% A.E. paragraph may need work
-%
-Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}.
-Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
-This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dnese gas ($\sim$ 1 km s$^{-1}$).
-Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy.
-This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
-It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing supernovae.
-Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star forming gas.
-Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy.
-The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.
+\subsubsection{Massive Stellar Wind Energy}
+\label{sec:stellar winds discussion}
+Our massive stellar wind model drastically reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$.
+Although our algorithm is entirely capable of generating realistic stellar winds with velocities comparable to those observed, such fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
+When considered in isolation, stellar winds are an important source of pre-SN feedback and can dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
+However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}, unless densities near the ionizing source are high enough to trap the  HII region in the source cell.
+In that case, they can clear out a cavity to allow initial establishment of the HII region.
 
-\subsection{Context}
-\label{sec:context}
-That metal fraction distributions can be described using a simple analytic log-normal + power-law PDFs, even in a complex, multi-phase ISM, has not been demonstrated prior to this work.
-In addition, this is the first work to demonstrate differential mixing behavior of individual metal species using 3D hydrodynamics simulations.
-However, there does exist a significant body of work investigating the mixing behavior of passive scalars in a variety of contexts, as discussed below.
-\cite{KrumholzTing2018} predict differential behavior for AGB wind and core collapse supernova synthesized elements as a direct consequence of the differences in size of typical planetary nebulae ($\sim$ 0.1~pc) and supernova remnants ($\sim$ 100~pc).
-%We discuss our results further in the context of previous research on metal mixing in the ISM and speculate on the physical processes that drive the evolution of these PDFs across phases.
+They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
+Although they likely have minimal dynamical importance at resolutions where peak densities are not anyway high enough to trap ionization fronts, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting closer examination in future work.
 
-Previous work on the evolution of metals in the ISM varies from studies concerning the advection of passive scalars in idealized turbulent boxes \citep[e.g.][]{Pope1991, PanScannapieco2010, PanScannapiecoScalo2012, PanScannapiecoScalo2013, YangKrumholz2012, SurPanScannapieco2014, Colbrook2017}
-% cite passive scalar reviews by Warhaft 2000 in fluid mech and scalo + Elmegreen 2004?
-to global galaxy models studying generalized advection and mixing of passive scalars \citep[e.g.][]{deAvillez2002,Petit2015,Goldbaum2016} to models with more detailed self-consistent metal enrichment \citep[e.g.][]{Revaz2009,Escala2018}.
-% summarize conclusions from these works:
+\subsubsection{Cosmic Rays} 
+\label{sec:CRs}
 
-The evolution of metallicity PDFs has been investigated previously in some of these works \citep[see ][ and references therein]{PanScannapiecoScalo2012,PanScannapiecoScalo2013}, with effort towards developing closure models to describe the evolution of the PDFs of passive scalars in turbulent media \citep[e.g.][]{EswaranPope1988,Chen1989,Pope1991}.
-The astrophysical context in much of this work was enrichment from the first stars, so the focus was on the low-metallicity tail of the PDF and the timescales over which gas is polluted \citep[e.g.][]{PanScannapiecoScalo2013,Sarmento2017}.
-These works often use isothermal turbulent-box simulations initialized with a double-delta function PDF of pristine gas and enriched gas in some varying spatial distribution, ignoring ongoing enrichment.
-Initial PDFs of this form were demonstrated some time ago to evolve into a Gaussian distribution at late times \citep{EswaranPope1988}, but it is unclear if these could also be described with a log-normal distribution.
-However, these works uniformly do not contain the high metallicity power-law tails shown in our work.
-As suggested by our toy model in Section~\ref{sec:interpretation}, this is due to the lack of ongoing enrichment in these studies.
+Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}.
+These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}.
+Modeling cosmic rays is challenging, however, as they encompass a wide range of energies, and there are significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
+Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy.
+In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM.
+Modeling cosmic ray feedback completely thus requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena.
+Finally, including MHD presents additional difficulties in untangling the effects of each individual feedback mechanism on galaxy chemodynamics.
 
-More detailed models of global galaxy evolution have generally focused on spatial correlations and mixing timescales of initially asymmetric fields, without concern for ongoing enrichment \citep[e.g.][]{deAvillez2002,Petit2015} or focused primarily on the evolution of stellar abundance patterns and metallicity distribution functions \citep[e.g][need more]{Jeon2017,Hirai2017,Escala2018}, without directly examining the evolution of gas-phase metallicity PDFs.
+We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested.
+Mechanically, including this relatively simple treatment of cosmic ray feedback in our model is trivial.
+However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to later work.
 
-%
-% MM: remove from this section:
-%This is the first work examining the gas-phase properties of metallicity PDFs in a global galaxy simulation with a detailed model for stellar feedback, chemical enrichment, and a multi-phase ISM.
-Since we are far from a complete understanding of galactic chemical evolution, investigating the physics behind what sets the statistical properties of these PDFs, particularly what drives the differences across metal species and phases, is important.
-Although this is beyond the scope of this current work, we use scaling arguments to speculate on the meaning of these results.
-%Metal mixing in the ISM is a diffusive process driven by turbulence.
+\subsection{Detailed Stellar Evolution and Binary Stars}
+\label{sec:binary stars}
 
-% Recent works investigating dwarf galaxy chemical enrichment with Lagrangian simulations have shown that the sub-grid diffusion models required to reproduce observed dwarf galaxy abundance properties imply fairly rapid mixing timescales \citep{Escala2018,Hirai2017}.
-In contrast to this work, \cite{Escala2018} finds dwarf galaxy
-%The sub-grid diffusion models in Langrangian simulations of dwarf galaxy chemical enrichment that match the abundance properties of observed dwarf galaxies imply rapid mixing timescales
+Roughly half of massive stars live in binary pairs \citep{Sana2013}.
+Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes.
+This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as SNe.
+This effect could be significant, but is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g.
+STARBURST99).
+For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse SNe occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
+Although they find only $\sim 15\%$ of core collapse SNe explode after 50~Myr, this could still be an important effect.
+Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}.
+Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
 
-%
-%
-%  Recent works specifically examining metal mixing in dwarf galaxies. Saving for potential future discussion:
-% \cite{Hirai2017} uses constrains the diffusion parameter in their SPH simulations comparing their simulated dwarf galaxies to observations in [Mg/Fe] vs.
-[Fe/H] and [Ba/Fe] vs.
-[Fe/H] space.
-Suggests Ba/Fe is more powerful constraint and briefly discusses potential differences in mixing between elements but does not do work with this
-% \cite{Jeon2017} 
-% \cite{Escala2018} tests of role of metal diffusion models in producing realistic MDFs in dwarf galaxies. Able to reproduce things like MDF width and [alpha/Fe]vs[Fe/H] scatter.
+Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars.
+This is beyond the scope of this project, but will be investigated in future work.
 
-% The properties of log-normal density PDFs in isothermal simulations are governed by the statistical properties of turbulence (refs) and the relative importance of compressive and solenoidal driving.
-However, the density PDFs in simulations of global galaxies with a resolved, multiphase ISM show significant departures from log-normallity \citep[see][]{Hopkins2013} but are still approximately log-normal within individual phases of the ISM \citep{HopkinsQuataertMurray2012}.
-The properties of the density PDF in multiphase simulations have not been well studied which offers little insight into what sets the mass fraction PDFs for each element.
-We speculate on this here to motivate future study, but note that a detailed characterization is beyond the scope of this work.
+\section{Conclusion}
+\label{sec:conclusion}
+We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
+For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, using individual star particles to model core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, Lyman-Werner radiation and pollution from AGB and massive stellar winds.
+This treatment of feedback, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
+In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
+We present an overview of the properties of this simulation in this work.
 
-% The log-normal density PDFs found in ISM simulations have a variance that is proportional to the mach number \citep[e.g.][(maybe more)]{PNJ1997, Passot1998, Fedderath2008, LemasterStone2009}.
-In our simulations, however,
+For our simulated dwarf galaxy, we find:
+\begin{enumerate}
+\item Multi-channel feedback is effective in this galaxy in regulating star formation to occur at a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
+(See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).
 
-%We discuss possible caveats to this in Section~\ref{sec:caveats}.
-Does this extend to more massive?
-how does DM potential affect this?
-Are general trends still true in much larger galaxies?
-or are things very different once HIM crossing times are more like 100 Myr (aka MW size galaxies).
+\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, falling to $\eta \sim 10$ at R$_{\rm vir}$,  and
+metal mass loading factors near unity.
+By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Figure~\ref{fig:outflow_velocity}).
 
-\subsection{Timescale Dependence of AGB Ejecta}
-\label{sec:discussion:metal yields}
-We can generally say that metals produced in AGB winds evolve qualitatively differently in dwarf galaxies than metals produced through supernovae.
-However, exactly which metals exhibit these differences, and to what degree, is timescale and metallicity dependent.
-Short-timescales ($\lesssim 100$~Myr) only samples enrichment from the most massive AGB stars, which stars on order of a few solar masses enrich on 1 Gyr timescales or longer.
-In our simulations, which only sample 500 Myr of evolution, N and Ba are dominated from AGB wind ejecta.
-C is commonly used to track AGB wind enrichment, but as it originates from lower mass AGB stars, C enrichment operates on $\sim$ Gyr timescales, longer than we follow in this work.
-This additionally varies with metallicity.
-Sr, for example, is only significantly ejected through AGB winds at our metallicity on $\sim$~Gyr timescales; stellar winds from more massive stars dominate the production of Sr on shorter timescales.
-At higher metallicity, much more Sr is produced through massive AGB stars, decreasing the timescale over which Sr should exhibit a differential chemical evolution as compared to supernovae ejected elements.
+\item 
+Only $\sim$4\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of ultrafaint dwarfs.
+By the end of the simulation $\sim$45\% of the remaining metals remain within the virial radius (but outside the galaxy) and $\sim$50\%
+have been ejected beyond the virial radius. (See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
 
-To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected through AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times.
-This model was run using \textsc{SYGMA} \citep{Ritter2017}.
-As shown, metal enrichment from AGB winds only begins to dominate for a given species at $\sim$ 100 Myr.
-This includes N and Ba, as followed in our simulations, but this plot indicates that Li should show the strongest differences with respect to metal ejected through supernovae, even on relatively short ($< 100~$~Myr) timescales.
-It takes over a Gyr for C to be dominated from AGB wind ejecta, which is the case for many of the elements shown.
-F, which shows very little contribution from AGB winds at short timescales is dominated by enrichment on longer timescales.
-These dependences on metallicity and timescales certainly adds complications in generalizing our work and in interpreting observations in the context of the results presented here, but these difference could be leveraged to better understand galactic chemical evolution on multiple, distinct timescales.
-Clearly this motivates future work covering Gyr timescales to fully understand how metal mass fraction PDFs evolve with time.
+\item 
+The gas scale height is thin ($\sim 50$~pc), yet resolved, 
+beyond our stellar radius, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
+This is comparable to the resolution limit of the diffuse HI in observed, gaseous ultrafaint dwarfs.
+At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8--4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Figure~\ref{fig:scale_height}).
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0.png}
-\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, with no continual star formation.
-We only show a sample of some of the elements dominated most by AGB enrichment.
-The horizontal line marks 50\% contribution.}
-\label{fig:agb evolution}
-\end{figure*}
+\item The ISRF of our galaxy varies strongly in both space and time by orders of magnitude.
+It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
+(See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
 
-%\begin{figure*}
-%\centering
-%\includegraphics[width=0.95\linewidth]{C_N_evolution.png}
-%\caption{The fractional contribution of AGB winds to the total yields of C and N as a function of time for a simple stellar population at three different metallicities.
-Since the nucleosynthetic source governs the mixing dynamics of a given metal, this plot illustrates how this can change with both time and metallicity for a given species.
-These models were generated using \textsc{SYGMA} \citep{Ritter2017-sygma}}
-%\label{fig:agb evolution}
-%\end{figure*}
+\item 
+We find H$_2$ fractions below 5\% in our dwarf galaxy, consistent with the poor constraints on molecular gas formation in low metallicity dwarf galaxies.
+This H$_2$ forms entirely through gas-phase reactions facilitated by H$^{-}$ in self-shielding regions; H$_2$ formation on dust grains and in the three body reaction are both insignificant.
+Cold, neutral hydrogen dominates the mass of our galaxy.
+While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Figure~\ref{fig:sfr_mass_evolution} and Figure~\ref{fig:ISM_evolution}.)
 
-\subsection{Impact on Stellar Abundance Patterns}
-\label{sec:stellar abundances}
-% AE: Possibly need better general introduction to CE models / sims and importance of understanding stellar abundances (obs+theory)
-In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star forming gas in our simulations.
-This could be used to help disentangle sources of scatter in observed stellar abundance, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
-If the star forming gas in our simulations can also be well-fit by a log-normal + power-law PDF, and if we can parameterize their evolution as functions of global galaxy properties, this can be used as a powerful and analytic tool for modeling stellar abundance patterns in semi-analytic models.
-This would be a physically motivated way to account for both the intrinsic spread in stellar abundances due to inhomogeneities in the ISM and variations in mixing for different metal species.
-We reserve an analysis of these distributions in abundance space in both the gas and stars for a future work.
-However, we briefly discuss the connection to star forming gas and stellar enrichment below.
+\item Finally, we used O and N as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy.
+These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs.
+SNe), as suggested by \cite{KrumholzTing2018}.
+This will be explored in more detail in future work (Emerick et.
+al.
+\textit{in prep.}).
+\end{enumerate}
 
-Unfortunately, there is insufficient star forming gas at any one time in these simulations to construct a PDF of metal distributions.
-However, star forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, follow a similar PDF to the CNM.
-To verify this, Figure ~\ref{fig:stars} shows the difference between the mass fraction of a given element in stars and the median mass fraction from the CNM PDF at the time that particle formed.
-Stars seem to be sampled evenly around the median of the CNM distribution (i.e.
-there is no obvious bias towards high metal fractions).
-Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
-High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
+\section*{Acknowledgments:} 
+We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
+C\^ot\'e, S.
+Glover, K.
+Hawkins, C.
+Hu, K.
+Johnston, B.
+O'Shea, M.
+Putman, B.
+Smith, J.
+Wall, and J.
+Wise.
+A.E.
+is funded by the NSF Graduate Research Fellowship DGE 16-44869.
+G.L.B.
+is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
+M.-M.M.L.
+was partly funded by NASA  grant NNX14AP27G.
+We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute.
+This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.
+These are products of collaborative effort by many independent developers from numerous institutions around the world.
+Their commitment to open science has helped make this work possible.
 
-\subsection{Do these results apply to more massive galaxies?}
-\label{sec:massive galaxies}
-One important caveat about our work is that these results are derived from simulations of an isolated, low mass dwarf galaxy whose properties vary dramatically from a more massive galaxy like the Milky Way.
-It is unclear how much of these results apply to more massive galaxies given their deeper potential wells and higher star formation rates.
-Feedback driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
-We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy.
-With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
-If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
-If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
-This difference would be greater at later times (higher metallicity) once AGB enrichment becomes significant.
-For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
-At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way.
-Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way.
-However, there has been no definitive explanation for these observations.
-Generalizing our results and detailing their observational consequences is the topic of ongoing work.
-
-In contrast, we expect the properties of the enrichment PDFs, and the variations between AGB enriched elements and supernova enriched elements (as presented in Figures~\ref{fig:log-normal} and ~\ref{fig:phase-statistics}), to be general.
-We expect metals to exhibit log-normal + power-law distributions in the ISM of all galaxies, with similar trends with enrichment source and gas phase as outlined here.
-However, the detailed properties of the PDFs (e.g, log-normal width, power-law slope) likely depend non-trivially on global galaxy properties.
-How these results vary as a function of galaxy properties will be investigated in future work.
-
-% Talk about CGM at all???
-
-%\textit{In addition, hot gas in a galaxy with a deeper potential well is less likely to be ejected from the galaxy, allowing more time for homogenization and possibly smaller metal fraction variation than seen here.}.
-
-%
-% moved to possible to-do list below,
-%
-\subsection{Implications for Exotic Enrichment Sources}
-\label{sec:exotic enrichment}
-We have shown that the dynamical evolution of metals depends upon their nucleosynthetic source, focusing here on AGB synthesized elements and supernova synthesized elements.
-However, these differences should also apply to exotic enrichment sources, such as hypernovae (HNe), neutron-star neutron-star mergers (NSM), and neutron star - black hole mergers.
-These sources have energies that differ significantly from typical supernova (10$^{51}$ erg), reaching $> 10^{52}$ for HNe \citep{Nomoto2004} and $\sim$10$^{49}$~erg for NSMs \citep{Goriely2011}.
-We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to supernovae.
-Based on our results here, we would expect elements from HNe to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe.
-Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies.
-These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
-In particular, low mass dwarf galaxies with unusual r-process enrichment \citep[e.g.][]{Ji2015}, are valuable for constraining the source of these elements, their frequency, and typical yields.
-The differential metal evolution presented in our work both opens up an additional avenue by which elements from distinct nucleosynthetic sources may be distinguished in observations and challenges current assumptions used in interpreting these observations.
-
-%\subsection{Extra things I could discuss:}
-%\textit{Things I can / will additionally discuss}
-%\begin{itemize}
-%\item Observed N/O in stellar abundances exhibits large spreads at low metallicity.
-Argument has been that this is driven by timescale differences in AGB vs.
-massive star nucleosynthesis.
-However, our results would predict that N/O have a large spread due to mixing efficiency diffein rences between AGB winds and SNe.
-%\end{itemize}
-
-\section{Conclusions}
-\label{sec:conclusions}
-For the first time we present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
-This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze how individual metal species couple to the galactic winds and ISM of this galaxy.
-We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, core collapse supernovae, and Type Ia supernovae).
-This difference is most significant in our model between elements ejected predominately through AGB winds and those ejected predominantly by core-collapse supernovae.
-In addition, we find for the first time that the metal mass fraction PDFs of each metal in the ISM can be described using an analytic piece-wise log-normal + power-law PDF.
-The properties of these PDFs vary with both ISM phase and metal species, again driven mostly by differences in enrichment sources.
-
-We summarize our results as follows:
-\begin{itemize}
-
-%\item Elements from lower energy enrichment sources (i.e.
-AGB winds) are preferentially retained in the ISM of low mass dwarf galaxies as compared to those from higher energy sources (supernovae), which are more readily launched in galactic winds.
-This result is likely sensitive to global galaxy properties, becoming less significant with increasing halo mass.
-We predict the abundance ratios between AGB wind dominated metals (s-process elements) and SN dominated metals ($\alpha$ elements) to be higher at fixed metallicity in low mass dwarf galaxies than in more massive galaxies, like the Milky Way.
-
-\item Power-law tails in metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
-
-\item Hotter phases have metal fraction PDFs that are more enriched with significant power-law tails as compared to cold phases, which have a more dominant log-normal structure.
-The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling into dense gas.
-% missing text???????????
-
-\item Metal outflow in low mass dwarf galaxies depends upon nucleosynthetic origin.
-Metals from lower energy enrichment events (e.g.
-AGB winds) are preferentially retained in the ISM as compared to those from higher energy events (e.g.
-SNe).
-The degree to which this is true likely depends upon global galaxy properties such as star formation rate, dark matter potential well, and gas geometry.
-
-\item Likewise, metals originating in AGB winds are less well mixed in the ISM compared to metals injected through SNe, with spreads of over 1 dex in cold gas, as compared to
-
-\item Metal distributions exhibit positive skew, such that the median metal fraction can be anywhere from 0.1 to 1.0 dex above the mean metal fraction.
-Simple chemical evolution models, which generally follow the mean abundance, that are unable to account for complex metal mixing physics are likely biased towards higher enrichment values.
-
-\end{itemize}
-
-We expect these results to be general for more massive galaxies and galaxy properties.
-However, it may be the case that metals couple more uniformly to galactic winds in more massive galaxies as wind driving occurs increasingly through entrainment of the ambient ISM rather than the ejection of individual enrichment events.
-This warrants further examination.
-But interpreting these results for low mass dwarf galaxies, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements, particularly at lower metallicities, 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way, and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements.
-
-%\section{Things to cite}
-%Hou, Yu, Lu 2014: Need to read closer, but CE model playing around with SN energy feedback effectiveness finds that weaker feedback leads to more metal enrichment, higher FB, lower metallicities.
-Suggestion of importance of FB driving CE.
-
-\acknowledgments
-Acknowledgments.
-
-\facilities{Yeti, CCA cluster, Stampede, Pleiades} 
-\software{Numpy, Enzo, yt, astropy}
-
-\bibliographystyle{yahapj}
+%\bibliographystyle{yahapj}
+\bibliographystyle{mnras}
 \bibliography{msbib}
@@
 
-\section{Density PDF}
-\label{appendix:density PDF}
-We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}.
-We show the mass-weighted PDF ($dm/Md\rm{log}n$) on the left, and the volume-weighted PDF ($dv/Vd\rm{log}n$) on the right.
-As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution.
-The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.
-The volume weighted PDF is much better described as a multi-component power law.
-The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities.
-These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.
-Finally, \cite{Hopkins2013} suggests a different functional form for describing these PDFs across a range of idealized simulations, but it still may be insufficient to fully describe the density PDF in realistic galaxy simulations.
-Clearly, we are far from a general understanding of mass-weighted and volume-weighted density PDFs in the case of a turbulent, self-gravitating, multi-phase ISM.
+\section{Gas Phases of the ISM}
+\label{appendix:phases}
 
-\begin{figure}
-\centering
-\includegraphics[width=0.475\linewidth]{density_PDF.png} 
-\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted.png}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr.
-The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
-\label{fig:density_pdf}
-\end{figure}
+To aid in comparison to other works, we define our ISM phases here, as adopted and modified from \citet{Draine2011}, Table 1.3, and used consistently throughout this analysis.
+By construction, these phases are mutually exclusive.
+We take $f_{\rm H_2}$ to be the molecular hydrogen fraction of the total gas mass.
 
-\section{Resolution Comparison}
-We perform a resolution test to confirm that the key results of this study are convergent, at least qualitatively.
-Given the variations in star formation rate, feedback effectiveness, and stochasticisty in our model, we do not expect exact numerical convergence in any one quantity.
-We conduct two lower resolution simulations with a maximum physical resolution of 3.6 pc and 7.2 pc.
-We refer the reader to Paper I for a previous comparison of these simulations to our fiducial run.
-In Figure~\ref{fig:resolution-phase} we demonstrate that O and Ba abundances behave qualitatively similar in our lower resolution runs as in our fiducial model.
-In both lower resolution runs O has a generally tighter distribution that narrows over time, while Ba is much less well mixed, in agreement with our fiducial simulation.
-The exact numerical values for these spreads are not convergent across simulations, but we do note significant variations in the exact SFH of these lower resolution runs could be driving these differences.
+\begin{enumerate}
+\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
+\item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
+\item Warm Neutral Medium (WNM): $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$
+\item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
+\item Molecular: $T < 10^2$~K, $f_{\rm H_2} > 0.5$
+\end{enumerate}
+
+\section{Stellar Radiation Properties}
+\label{appendix:radiation}
+We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
+In Figure~\ref{fig:stellar radiation properties} we plot these properties.
+We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
+This requires two factors for each radiation type, one for low mass and one for high mass stars.
+We use the following multiplicative factors to adjust the black body spectrum for HI and HeI ionizing radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
+We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
+
+The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid.
+A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section.
+We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \url{http://www.pa.uky.edu/~verner/photo.html}}
+The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision.
+Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study.png}
-\caption{Resolution comparison at two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.
-Compare to Figure~\ref{fig:phase-statistics}.}
-\label{fig:resolution-phase}
+\includegraphics[width=0.4\linewidth]{Q0}
+\includegraphics[width=0.4\linewidth]{Q1}
+\vspace{0.01cm}
+\includegraphics[width=0.4\linewidth]{L_FUV}
+\includegraphics[width=0.4\linewidth]{L_LW}
+\vspace{0.01cm}
+\includegraphics[width=0.4\linewidth]{E0}
+\includegraphics[width=0.4\linewidth]{E1}
+\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right).
+Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
+\label{fig:stellar radiation properties}
 \end{figure*}
 
+\setcounter{figure}{0}
+\section{Typical Gas Densities in Supernova Injection Regions}
+\label{appendix:SN}
+
+Modeling SN feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of SN feedback.
+Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time.
+However, physically consistent solutions have been developed \citep[e.g][]{Simpson2016} that inject a mixture of kinetic and thermal energy with a ratio that depends on resolution and local gas density.
+Overcooling becomes less important with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each SN.
+We take advantage of our high resolution and employ a simple thermal energy injection model for our SN feedback.
+We demonstrate how well this resolves our SNe in the comparison simulation presented in this work.
+
+The left panel of Figure~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
+As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
+For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations.
+The right panel of Figure ~\ref{fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
+\begin{equation}
+R_{\rm PDS} = 
+\begin{cases}
+49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z \le 0.01 \\
+18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z \ge 0.01 \\
+\end{cases}
+\end{equation}
+where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$.
+\citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the SN explosion with thermal energy injection alone, assuming uniform density in the injection region.
+In practice, the injection region is never uniform.
+We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each SN.
+As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but up to 8.3\% are not well resolved and 2.0\% are completely unresolved (below a single cell width).
+In general, these are SN explosions from the most massive (i.e.
+most prompt) stars.
+We do not expect that resolving these SNe will dramatically alter our results.
+However, we note that using our feedback model at resolutions much less than a few parsecs will require implementing an different injection mechanism.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.4\linewidth]{sn_density_hist}
+\includegraphics[width=0.4\linewidth]{sn_radius_hist}
+\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation.
+{\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each SN assuming a uniform medium at either the peak or average density in the injection region.
+The vertical lines show one and 4.5 cell widths.
+This shows that a fraction of these SNe are certainly unresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
+\label{fig:SN histogram}
+\end{figure*}
+
+\setcounter{figure}{0}
+\section{Cooling and Heating Rates}
+\label{appendix:cooling}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
+\caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background.
+Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the uncorrected (i.e.
+optically thin) metal line cooling rates.
+The regimes where heating dominates are plotted with dashed lines for clarity.}
+\label{fig:cooling comparison}
+\end{figure*}
+
+The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with a self-shielding approximations.
+\citet{Hu2017} details this inconsistency: metal cooling rates computed under the assumption of an optically thin UV background overestimate the electron fraction in regimes where self-shielding is important ($-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$).
+This results in an artificially enhanced metal line cooling rate in regions of self-shielding.
+This can be a significant effect, particularly at higher metallicities.
+We demonstrate this in Figure~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
+The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
+In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
+Figure~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
+We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
+
+For densities where self-shielding is important, we computed \textsc{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
+In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud.
+We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UV background.
+These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}.
+In computing these tables we had to include the cosmic ray ionization that dominates in optically thick clouds.
+Without this effect, \textsc{Cloudy} becomes unstable in entirely neutral regions.
+We adopted a cosmic ray ionization rate of 10\% the Milky Way value, though we note that varying this from 1\% to 100\% the Milky Way value did not have an effect on the extracted metal line cooling rates.
+
+Finally, we note that the cooling and heating rates in our simulation will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
+The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which is not included in these diagrams.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.95\linewidth]{cooling_curve}
+\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}.
+The absolute value of the net cooling or heating
+rate is shown with solid lines.}
+\label{fig:cooling}
+\end{figure*}
+
+\setcounter{figure}{0}
+\section{Resolution Study}
+\label{appendix:resolution_study}
+
+\textbf{Significant changes to the lower resolution runs and the comparison to our fiducial simulation with the change to the H$_2$ production:}
+
+We demonstrate the effect of varying resolution in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}.
+We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines).
+The physics in each simulation remains the same with the exception of star formation, which employs a resolution-dependent density threshold.
+A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.
+As a result, the time at which star formation first occurs varies between the simulations, but we again define t = 0 as the time of first star formation in each simulation.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.33\linewidth]{sfr_resolution_study.png}
+\includegraphics[width=0.33\linewidth]{mass_evolution_resolution.png}
+\includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
+\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted).
+The line colors in the left panel are for better clarity between the SFRs.}
+\label{fig:resolution_study}
+\end{figure*}
+
+Figure~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
+We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
+The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs.
+We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Figure~\ref{fig:SN histogram}.
+However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
+
+Generally ineffective feedback leads to increased, not decreased, star formation rates.
+However, the lower resolution run has the lowest SFR.
+The source of this difference is likely related to the ability to resolve dense, cold gas in the lower resolution simulations.
+In particular, the low resolution simulation clearly is unable to resolve the densities at which gas-phase H$_2$ formation becomes efficient, leading to significantly lower H$_2$ fractions (middle panel) and lower cooling rates.
+In addition, whatever H$_2$ does form at these lower resolutions exists at lower gas densities than in our fiducial run, and is less well protected by self-shielding effects.
+This is shown clearly in the significant plummet in the H$_2$ mass during the phase of first star formation that is less severe in our fiducial run.
+In this low metallicity regime, where H$_2$ is an important coolant, the ability to resolve the densities responsible for H$_2$ formation and self-shielding is important.
+
+Theses differences in densities are shown clearly by comparing Figure~\ref{fig:phase_diagram} with Figure~\ref{fig:phase_resolution}.
+Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.
+In the 7.2~pc run, the gas phases are notably less distinct, with gas more evenly smoothed out in the multi-phase region between cold, dense gas and warm, ionized gas.
+We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature ceiling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.475\linewidth]{3pc_phase.png}
+\includegraphics[width=0.475\linewidth]{6pc_phase.png}
+\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Figure~\ref{fig:phase}.}
+\label{fig:phase_resolution}
+\end{figure*}
+
+Finally, the metal retention fraction (right panel) between the fiducial and 3.6~pc runs are quite similar, but is significantly higher for the lowest resolution simulation.
+It is likely, however, that this is a result of the lower SFR in the 7.2~pc run and is not directly a resolution effect.
+This also affects the fraction of metals ejected outside the virial radius, with less metals being ejected in the lower resolution runs.
+
+\label{lastpage}
+
 \end{document}

### 2018-07-15 main.tex
spelling check and font resize in res plots

@@
-%\documentclass[twocolumn]{aastex61}
-%\pdfoutput=1 %for arXiv submission
 \documentclass[fleqn,usenatbib,useAMS]{mnras}
@@
 
-\hypersetup{draft}
+%\hypersetup{draft}
 %\usepackage{multirow}
@@
 %\usepackage{graphicx}
-
-%\usepackage{apjfonts} 
 %\usepackage{natbib} % bibliography
@@
 
-%\shorttitle{Feedback with Individual Stars}
-%\shortauthors{Emerick, Bryan, Mac Low}
 \newcommand{\msun}{M$_{\odot}$}
 \newcommand{\ccunit}{cm$^{-3}$}
-
-%%%%%%%%%%%%%%%%%%\hypersetup{draft}
-% For bibtex
 
@@
 Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe.
-Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$.
-This is a free parameter in our model; we take $M_{\rm trans} = 8$~M$_{\odot}$ as our fiducial value.
+Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$; we take $M_{\rm trans} = 8$~M$_{\odot}$.
 In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
@@
 This is comparable to the resolution limit of the diffuse HI in observed, gaseous ultrafaint dwarfs.
-At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8--4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Figure~\ref{fig:scale_height}).
+At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Figure~\ref{fig:scale_height}).
 
@@
 
-Theses differences in densities are shown clearly by comparing Figure~\ref{fig:phase_diagram} with Figure~\ref{fig:phase_resolution}.
+Theses differences in densities are shown clearly by comparing Figure~\ref{fig:phase} with Figure~\ref{fig:phase_resolution}.
 Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.

### 2018-07-15 main.tex
wording changes to abstract and conclusion

@@
 In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner dissociating radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
 We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
 We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints.
-We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy.
+We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group, low-mass dwarf galaxy.
 We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
@@
 It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
-It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.
+It is even more unclear how metals are transported and distributed within low-mass dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.
 
@@
 This treatment of feedback, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
-In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy.
+In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P dwarf galaxy.
 We present an overview of the properties of this simulation in this work.
@@
 \begin{enumerate}
-\item Multi-channel feedback is effective in this galaxy in regulating star formation to occur at a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
+\item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
 (See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).
@@
 \item 
-Only $\sim$4\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of ultrafaint dwarfs.
-By the end of the simulation $\sim$45\% of the remaining metals remain within the virial radius (but outside the galaxy) and $\sim$50\%
+Only $\sim$4\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of low-mass dwarfs.
+By the end of the simulation $\sim$45\% of the remaining metals stay within the virial radius (but outside the galaxy), while $\sim$50\%
 have been ejected beyond the virial radius. (See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
@@
 \item 
-The gas scale height is thin ($\sim 50$~pc), yet resolved, 
-beyond our stellar radius, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
-This is comparable to the resolution limit of the diffuse HI in observed, gaseous ultrafaint dwarfs.
+Beyond the stellar radius, the gas scale height is thin ($\sim 50$~pc), yet resolved, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
+This is comparable to the resolution limit of the diffuse HI in observed, gaseous low-mass dwarfs.
 At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Figure~\ref{fig:scale_height}).
@@
 It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
+The importance of radiation feedback in our model will be investigated in a future work.
 (See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
@@
 
-\item Finally, we used O and N as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy.
+\item Finally, we present gas-phase oxygen and nitrogen distributions as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy.
 These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs.

### 2018-07-15 ms.tex
Update on Overleaf.

%%
%% Beginning of file 'sample62.tex'
%%
%% Modified 2018 January
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.2 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass[twocolumn]{aastex62}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figures/}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
%\received{January 1, 2018}
%\revised{January 7, 2018}
%\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.2 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%
%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
%% collaboration" on the front page of this example manuscript.
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{Sample article}
\shortauthors{Emerick et. al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.2 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affilations. The change was necessary to implement 
%% autoindexing of affilations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% arguement which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.2 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.2 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

\correspondingauthor{Andrew Emerick}
\email{emerick@astro.columbia.edu}

\author{Andrew Emerick}
\affil{Columbia University}
\affil{American Museum of Natural History (AMNH)}

\author{Greg L. Bryan}
\affiliation{Columbia University}
\affiliation{Flatiron Institute}

\author{Mordecai-Mark Mac Low}
\affiliation{American Museum of Natural History (AMNH)}
\nocollaboration

\begin{abstract}
Ionizing radiation from recently formed massive stars is important in destroying cold, dense gas around new regions of star formation that would otherwise continue to form stars. Applying a local prescription for this pre-supernova feedback can be sufficient in matching star formation rates in a simulation with full radiative transfer on short timescales. However, the long-range effects of ionizing radiation are important in producing a volume-filling diffuse, warm-ionized medium in the ISM and in the disk-halo interface. This is essential for allowing supernovae to drive significant gas outflows that travel throughout and beyond the virial radius of the galaxy. A simulation with local radiation feedback only is unable to drive significant outflows as the supernovae are trapped well within the inner halo by higher density cold and warm neutral gas.
\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{galaxies -- feedback -- galaxy evolution -- galactic winds}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.
%%
%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\section{Introduction} \label{sec:intro}
Overview of importance of pre-SN feedback in regulating SF. Brief literature overview of recent simulations with full radiative transfer. Brief mention / discussion of current approximations / simplifications made in runs without RT that include something for radiation feedback. Motivate how it is unclear as to whether or not full fancy RT physics is necessary, or if 1) can just do SNe (unlikely), and 2) can just get by with local (e.g. Stromgren) approximation. How might this affect global galaxy properties beyond SFR?

\section{Methods} \label{sec:methods}
See paper I. VERY SHORT summary here

\section{Results}
Plots of SFR, gas mass evolution, phase evolution, mass loading factors. Figure out a reasonable selection of panels to show that demonstrate the characteristic differences in outflow properties. Particularly one early on during first "break-out" of SNe and one at late time. Plot metal mass fraction retention.

\section{Discussion and Conclusion}
Keep this short and to the point.

\begin{thebibliography}{}

\end{thebibliography}

%% This command is needed to show the entire author+affilation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample62.tex'.

### 2018-07-17 ms.tex
including first figures
Update on Overleaf.

@@
-%%
-%% Beginning of file 'sample62.tex'
-%%
-%% Modified 2018 January
-%%
-%% This is a sample manuscript marked up using the
-%% AASTeX v6.2 LaTeX 2e macros.
-%%
-%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
-%% (Copyright 2000-2015).  See the classfile for details.
-
-%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
-%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
-%% All of these external packages should already be present in the modern TeX 
-%% distributions.  If not they can also be obtained at www.ctan.org.
-
-%% The first piece of markup in an AASTeX v6.x document is the \documentclass
-%% command. LaTeX will ignore any data that comes before this command. The 
-%% documentclass can take an optional argument to modify the output style.
-%% The command below calls the preprint style  which will produce a tightly 
-%% typeset, one-column, single-spaced document.  It is the default and thus
-%% does not need to be explicitly stated.
-%%
-%%
-%% using aastex version 6.2
 \documentclass[twocolumn]{aastex62}
 
-%% The default is a single spaced, 10 point font, single spaced article.
-%% There are 5 other style options available via an optional argument. They
-%% can be envoked like this:
-%%
-%% \documentclass[argument]{aastex62}
-%% 
-%% where the layout options are:
-%%
-%%  twocolumn   : two text columns, 10 point font, single spaced article.
-%%                This is the most compact and represent the final published
-%%                derived PDF copy of the accepted manuscript from the publisher
-%%  manuscript  : one text column, 12 point font, double spaced article.
-%%  preprint    : one text column, 12 point font, single spaced article.  
-%%  preprint2   : two text columns, 12 point font, single spaced article.
-%%  modern      : a stylish, single text column, 12 point font, article with
-%% 		  wider left and right margins. This uses the Daniel
-%% 		  Foreman-Mackey and David Hogg design.
-%%  RNAAS       : Preferred style for Research Notes which are by design 
-%%                lacking an abstract and brief. DO NOT use \begin{abstract}
-%%                and \end{abstract} with this style.
-%%
-%% Note that you can submit to the AAS Journals in any of these 6 styles.
-%%
-%% There are other optional arguments one can envoke to allow other stylistic
-%% actions. The available options are:
-%%
-%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
-%%  tighten      : Makes baselineskip slightly smaller, only works with 
-%%                 the twocolumn substyle.
-%%  times        : uses times font instead of the default
-%%  linenumbers  : turn on lineno package.
-%%  trackchanges : required to see the revision mark up and print its output
-%%  longauthor   : Do not use the more compressed footnote style (default) for 
-%%                 the author/collaboration/affiliations. Instead print all
-%%                 affiliation information after each name. Creates a much
-%%                 long author list but may be desirable for short author papers
-%%
-%% these can be used in any combination, e.g.
-%%
-%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
-%%
-%% AASTeX v6.* now includes \hyperref support. While we have built in specific
-%% defaults into the classfile you can manually override them with the
-%% \hypersetup command. For example,
-%%
-%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
-%%
-%% will change the color of the internal links to red, the links to the
-%% bibliography to green, the file links to cyan, and the external links to
-%% magenta. Additional information on \hyperref options can be found here:
-%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
-%%
-%% If you want to create your own macros, you can do so
-%% using \newcommand. Your macros should appear before
-%% the \begin{document} command.
-%%
 \newcommand{\vdag}{(v)^\dagger}
@@
 
-%% Tells LaTeX to search for image files in the 
-%% current directory as well as in the figures/ folder.
 \graphicspath{{./}{figures/}}
 
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
-%\received{January 1, 2018}
-%\revised{January 7, 2018}
-%\accepted{\today}
-%% Command to document which AAS Journal the manuscript was submitted to.
-%% Adds "Submitted to " the arguement.
 \submitjournal{ApJ}
 
-%% Mark up commands to limit the number of authors on the front page.
-%% Note that in AASTeX v6.2 a \collaboration call (see below) counts as
-%% an author in this case.
-%
-%\AuthorCollaborationLimit=3
-%
-%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
-%% collaboration" on the front page of this example manuscript.
-%%
-%% Note that all of the author will be shown in the published article.
-%% This feature is meant to be used prior to acceptance to make the
-%% front end of a long author article more manageable. Please do not use
-%% this functionality for manuscripts with less than 20 authors. Conversely,
-%% please do use this when the number of authors exceeds 40.
-%%
-%% Use \allauthors at the manuscript end to show the full author list.
-%% This command should only be used with \AuthorCollaborationLimit is used.
-
-%% The following command can be used to set the latex table counters.  It
-%% is needed in this document because it uses a mix of latex tabular and
-%% AASTeX deluxetables.  In general it should not be needed.
-%\setcounter{table}{1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%% The following section outlines numerous optional output that
-%% can be displayed in the front matter or as running meta-data.
-%%
-%% If you wish, you may supply running head information, although
-%% this information may be modified by the editorial offices.
-\shorttitle{Sample article}
+\shorttitle{Radiation Feedback in Dwarf Galaxies}
 \shortauthors{Emerick et. al.}
-%%
-%% You can add a light gray and diagonal water-mark to the first page 
-%% with this command:
-% \watermark{text}
-%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
-%% long you can control the water-mark size with:
-%  \setwatermarkfontsize{dimension}
-%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% This is the end of the preamble.  Indicate the beginning of the
-%% manuscript itself with \begin{document}.
 
@@
 \title{Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies}
-
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire. In v6.2 you can include a footnote in the title.
-
-%% A significant change from earlier AASTEX versions is in the structure for 
-%% calling author and affilations. The change was necessary to implement 
-%% autoindexing of affilations which prior was a manual process that could 
-%% easily be tedious in large author manuscripts.
-%%
-%% The \author command is the same as before except it now takes an optional
-%% arguement which is the 16 digit ORCID. The syntax is:
-%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
-%%
-%% This will hyperlink the author name to the author's ORCID page. Note that
-%% during compilation, LaTeX will do some limited checking of the format of
-%% the ID to make sure it is valid.
-%%
-%% Use \affiliation for affiliation information. The old \affil is now aliased
-%% to \affiliation. AASTeX v6.2 will automatically index these in the header.
-%% When a duplicate is found its index will be the same as its previous entry.
-%%
-%% Note that \altaffilmark and \altaffiltext have been removed and thus 
-%% can not be used to document secondary affiliations. If they are used latex
-%% will issue a specific error message and quit. Please use multiple 
-%% \affiliation calls for to document more than one affiliation.
-%%
-%% The new \altaffiliation can be used to indicate some secondary information
-%% such as fellowships. This command produces a non-numeric footnote that is
-%% set away from the numeric \affiliation footnotes.  NOTE that if an
-%% \altaffiliation command is used it must come BEFORE the \affiliation call,
-%% right after the \author command, in order to place the footnotes in
-%% the proper location.
-%%
-%% Use \email to set provide email addresses. Each \email will appear on its
-%% own line so you can put multiple email address in one \email call. A new
-%% \correspondingauthor command is available in V6.2 to identify the
-%% corresponding author of the manuscript. It is the author's responsibility
-%% to make sure this name is also in the author list.
-%%
-%% While authors can be grouped inside the same \author and \affiliation
-%% commands it is better to have a single author for each. This allows for
-%% one to exploit all the new benefits and should make book-keeping easier.
-%%
-%% If done correctly the peer review system will be able to
-%% automatically put the author and affiliation information from the manuscript
-%% and save the corresponding author the trouble of entering it by hand.
 
@@
 
-%% From the front matter, we move on to the body of the paper.
-%% Sections are demarcated by \section and \subsection, respectively.
-%% Observe the use of the LaTeX \label
-%% command after the \subsection to give a symbolic KEY to the
-%% subsection for cross-referencing in a \ref command.
-%% You can use LaTeX's \ref and \label commands to keep track of
-%% cross-references to sections, equations, tables, and figures.
-%% That way, if you change the order of any elements, LaTeX will
-%% automatically renumber them.
-%%
-%% We recommend that authors also use the natbib \citep
-%% and \citet commands to identify citations.  The citations are
-%% tied to the reference list via symbolic KEYs. The KEY corresponds
-%% to the KEY in the \bibitem in the reference list below.
-
 \section{Introduction} \label{sec:intro}
@@
 
-\section{Methods} \label{sec:methods}
-See paper I. VERY SHORT summary here
+Key here is that radiation affects role of SNe in driving galactic winds.
+This is known already (Peters2016, Hu2016, Hu2017, and more), but has not been demonstrated like this for outflowing properties, primarily b/c many methods use approximate effects of RT.
 
-\section{Results}
-Plots of SFR, gas mass evolution, phase evolution, mass loading factors.
-Figure out a reasonable selection of panels to show that demonstrate the characteristic differences in outflow properties.
-Particularly one early on during first "break-out" of SNe and one at late time.
-Plot metal mass fraction retention.
+\section{Methods and Initial Conditions} \label{sec:methods}
+We refer the reader to Paper I for a more detailed description of our methods, briefly summarized here.
+We use the adaptive mesh refinement hydrodynamics code \textsc{Enzo} \citep{Enzo} to evolve an idealized, isolated low mass dwarf galaxy initialized as a smooth exponential disk set in hydrostatic equillibrium with a static dark matter potential with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, and a maximum physical resolution of 1.8~pc.
+We include a UV background, tabulated metal line cooling, and a 9 species non-equillibrium chemistry solver using \textsc{Grackle} \citep{Grackle}.
+Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling the \cite{Salpeter1995} IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range.
+For each star, we include feedback from stellar winds, AGB winds, FUV and LW band radiation which drives photoelectric heating and H$_2$ dissociation respectively, HI and HeI ionizing radiation, and core collapse and Type Ia SNe using thermal energy injection.
+FUV and LW band radiation are both taken to be optically thin, which approximate, local self-shielding alone, but ionizing radiation is followed with radiative transfer (see below).
 
-\section{Discussion and Conclusion}
-Keep this short and to the point.
+\textbf{Stellar Ionizing Radiation Models} $-$ We present a comparison of three simulations in this work, which are identical with the exception of their stellar ionizing radiation feedback.
+In our fiducial simulation, we track the HI and HeI photoionizing radiation using the adaptive ray-tracing radiative transfer method of \citep{MORAY} for all stars above 8$M_{\odot}$ (see Paper I for details on determining the ionizing photon rates for each star).
+We additionally present a simulation run without any stellar ionizing radiation (``noRT'') and a second simulation to test the relative importance of short-range vs.
+long-range effects of the radiation where we follow the full ionizing radiation RT, but delete photons once they have traveled more than 20~pc from their source (``shortrad'').
+This last simulation performs a similar, though significantly more detailed, function as commonly used methods to account for stellar radiation feedback which either deposit thermal energy (citation) or thermal energy and ionization (citations) locally, typically within the Stromgren radius, of each star.
+Each simulation is identical up until the formation of the first star particles, at which point they begin to diverge.
+We note that the stars from the very first star formation event in each run (21 star particles with a total mass of 114 M$_{\odot}$) are the same in each run.
+Of these, one particle emits ionizing radiation ($M_* > 8 $~M$_{\odot}$).
+
+\section{Results} \label{sec:results}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.49\linewidth]{sfr}
+\includegraphics[width=0.49\linewidth]{mass}
+\caption{}
+\label{fig:sfr_mass_evolution}
+\end{figure*}
+
+We compare the resulting star formation rate (left) and gas mass properties (right) of our three simulations in Figure~\ref{fig:sfr_mass_evolution}.
+There is a clear, significant contrast between the runs with and without ionizing radiation.
+Stellar ionizing radiation leads to a factor of $\sim$ 5 reduction in the resulting SFR, as compared to the noRT run.
+Since the shortrad and fiducial simulations are so similar over the first $\sim$~100~Myr, it is clear that stellar radiation acts to significantly reduce the local star formation efficiency around young, massive stars.
+Radiation from these stars quickly ionizes and dissipates surrounding dense gas that would otherwise have gone to fuel a significant amount of additional star formation.
+We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints.
+Although radiative transfer is expensive, this run is substantially more computationally expensive than the fiducial and shortrad runs due to the significantly higher star formation rate.
+
+Looking again at the first $\sim$100~Myr of simulation time, the effects of ionizing radiation beyond our 20~pc cutoff radius are not significant.
+However, these two simulations begin to diverge significantly after this point.
+The shortrad simulations has continual, steady star formation for the entire simulation time, while the star formation rate in our fiducial run is bursty, with periods of active, low-level star formation interspersed with periods (sometimes up to 50~Myr) of no star formation.
+The driver of these differences is clear in the right hand panel.
+Our fiducial run looses a significant amount of total gas and HI mass (black and blue lines) as compared to the shortrad simulation by a factor of XX.
+Clearly, galactic winds and outflows are much more effective in the fiducial case, with full accounting of stellar ionizing radiation feedback, then in the shortrad simulation.
+
+This can be confirmed by examining the mass loading factor and metal retention fraction (the fraction of produced metals retained within the disk of the galaxy) in each simulation.
+As shown in Figure~\ref{fig:metal_retention}, the mass loading factor in the fiducial run is a factor of XXX higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, and is the only simulation with any significant outflow beyond the virial radius.
+This is especially interesting considering the factor 5 increase in SFR of the noRT run.
+The noRT run does have a significant amount of gas mass outflowing at XXXX, but note that its low mass loading factor is due primarily to the significantly larger SFR in this galaxy.
+Radiation feedback, both locally and over longer ranges, is important in determining the ability for SN to drive significant outflows.
+We discuss the reasons for this in the following section.
+
+\section{Discussion} \label{sec:discussion}
+Again, it is known that accounting for feedback from stellar radiation plays a significant role in determining the ability for SN energy to couple to the ISM and therefore drive outflows.
+However, the specific importance of localized ionization vs.
+ionization far from the source star has not been examined.
+As shown above, accounting for stellar radiation feedback locally alone is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
+To explore the cause of this difference we present two panel-plots in Figure~\ref{fig:panel1} and Figure~\ref{fig:panel2} which compare the gas number density (left), temperature (middle), and HI ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote:{See ({\it insert link here}) for a movie of this comparison}
+
+Figure~\ref{fig:panel1}, at XX Myr, shows each just after the first few SN in each simulation.
+Already there are significant differences across runs.
+Gas outside the galaxy is warm ($\sim$~10$^{4}$~K) and ionized out to XX~pc above/below the plane of the disk in our fiducial run.
+This same gas is cold ($<10^4$~K) and neutral in both other runs.
+As a result, the SNe in each are contained, creating very hot diffuse bubbles contained by colder, denser shells close to the disk.
+These mass and energy from the SNe in our fiducial run readily escape the galaxy through the channels of diffuse, ionized gas carved out by long-range stellar radiation feedback.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.99\linewidth]{comparison_panel}
+\caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.}}
+\label{fig:pane1l}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.99\linewidth]{comparison_panel2}
+\caption{Panel}
+\label{fig:pane2}
+\end{figure*}
+
+\section{Conclusion}  \label{sec:conclusion}
+Very short. Just re-iterate points
 

### 2018-07-17 ms.tex

@@
 Already there are significant differences across runs.
-Gas outside the galaxy is warm ($\sim$~10$^{4}$~K) and ionized out to XX~pc above/below the plane of the disk in our fiducial run.
+Gas outside the galaxy is warm ($\sim$~10$^{4}$~K) and ionized up to XX~pc above/below the plane of the disk in our fiducial run.
 This same gas is cold ($<10^4$~K) and neutral in both other runs.
-As a result, the SNe in each are contained, creating very hot diffuse bubbles contained by colder, denser shells close to the disk.
-These mass and energy from the SNe in our fiducial run readily escape the galaxy through the channels of diffuse, ionized gas carved out by long-range stellar radiation feedback.
+The contrast between the fiducial and shortrad radiation is seen most clearly in the ionized region in-plane and to the right of center in the top and bottom panels.
+This region contains massive stars that are capable of generating enough ionizing radiation to carve a channel out to the halo of our fiducial simulation; by construction, this does not occur in the shortrad case.
+The warm / ionized feature towards the center of each galaxy is gas from a recent SN.
+This is much more well contained and hotter in the noRT and shortrad runs than in our fiducial simulation.
 
@@
 \centering
-\includegraphics[width=0.99\linewidth]{comparison_panel}
+\includegraphics[width=0.99\linewidth]{DD0136_fiducial_shortrad_nort}
 \caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.}}
@@
 
+As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow significant outflows from SNe to escape the disk and move well into the halo of our galaxy.
+In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas and unable to driving significant mass loss from the galaxy.
+In the noRT case, outflow does eventually develop, but it takes the factor of 5 increase in SFR for SN gas to finally break out from the neutral gas surrounding the galaxy.
+
 \begin{figure*}
 \centering
-\includegraphics[width=0.99\linewidth]{comparison_panel2}
+\includegraphics[width=0.99\linewidth]{DD0160_fiducial_shortrad_nort}
 \caption{Panel}

### 2018-07-18 ms.tex
Update on Overleaf.

@@
 \graphicspath{{./}{figures/}}
+\usepackage{natbib}
+\bibliographystyle{apj}
 
@@
 \begin{abstract}
-Ionizing radiation from recently formed massive stars is important in destroying cold, dense gas around new regions of star formation that would otherwise continue to form stars.
+Placeholder
+%{\bf Ignore: Ionizing radiation from recently formed massive stars is important in destroying cold, dense gas around new regions of star formation that would otherwise continue to form stars.
 Applying a local prescription for this pre-supernova feedback can be sufficient in matching star formation rates in a simulation with full radiative transfer on short timescales.
@@
 This is essential for allowing supernovae to drive significant gas outflows that travel throughout and beyond the virial radius of the galaxy.
-A simulation with local radiation feedback only is unable to drive significant outflows as the supernovae are trapped well within the inner halo by higher density cold and warm neutral gas.
+A simulation with local radiation feedback only is unable to drive significant outflows as the supernovae are trapped well within the inner halo by higher density cold and warm neutral gas.}
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-Overview of importance of pre-SN feedback in regulating SF.
-Brief literature overview of recent simulations with full radiative transfer.
-Brief mention / discussion of current approximations / simplifications made in runs without RT that include something for radiation feedback.
-Motivate how it is unclear as to whether or not full fancy RT physics is necessary, or if 1) can just do SNe (unlikely), and 2) can just get by with local (e.g.
-Stromgren) approximation.
-How might this affect global galaxy properties beyond SFR?
+Historically, simulations of galaxy formation have suffered from the ``overcooling'' problem, whereby simulations including self-gravity and radiative cooling alone produce galaxies with far too many stars.
+This problem has been addressed by employing various models of feedback physics which produces self-regulating star formation in galaxies.
+Recently, it has become clear that simple models for stellar feedback, which account for supernovae (SNe) alone, are insufficient to fully regulate star formation and set galaxy properties consistent with observations (see \cite{NaabOstriker2017} for a recent review).
+Additional processes, such as stellar radiation, cosmic rays, or AGN, are often employed as additional sources of feedback.
+Modeling these processes in detail, however, is challenging.
 
-Key here is that radiation affects role of SNe in driving galactic winds.
-This is known already (Peters2016, Hu2016, Hu2017, and more), but has not been demonstrated like this for outflowing properties, primarily b/c many methods use approximate effects of RT.
+Radiation from massive stars dominates the total feedback energy output of a stellar population \citep[e.g.][]{Lietherer1999,Agertz2013}, surpassing the energy ejection of supernova ($\sim 10^{51}$~erg) by two orders of magnitude.
+If the radiation couples effectively to the interstellar medium (ISM), it can be a substantial source of additional feedback.
+%Lower mass stars (size range) primarily drive photoelectric heating (cite) and H$_2$ dissociation through radiation in the far ultraviolet and Lyman-Werner bands, while more massive stars (range) emit significant amounts of ionizing radiation.
+Simulations including stellar radiation feedback followed through radiative transfer or radiation-hydrodynamics schemes have found it to be effective in regulating star formation and driving galactic winds \citep[e.g.][]{Wise2012,Kim2013,Sales2014,Rosdahl2015,Ocvirk2015,Pawlik2015,Peters2017}.
+This occurs for four reasons: 1) heating gas and preventing the formation of cold, dense star formation regions, 2) the destruction of cold, dense gas around recently formed stars, preventing further star formation, 3) momentum input by direct absorption of UV radiation by gas and (in some cases) dust through re-emission and scattering in the infrared, and 4) lowering the typical ISM densities in which SNe occur and greatly increasing their effectiveness.
+% the relevance / importance of RP from dust in the IR is beyond the scope of this work...
+
+However, most works that employ stellar radiation feedback to account for these effects do so using various forms of sub-grid, approximate models to avoid the substantial additional cost of full radiative transfer.
+Many works use a Stromgren approximation whereby the particles / cells within the Stromgren radius a radiating star are heated and kept ionized, with additional approximations made to account for overlapping ionized regions \citep[e.g.][]{HQM2011,Hu2016,Hu2017}.
+Other works employ some form of energy or momentum injection localized to the region immediately around a star particle \citep[e.g.][(\textit{need more})]{Agertz2013,Roskar2014,Ceverino2014,Forbes2015}.
+Although some of these approximate methods account for long-range effects of diffuse radiation \citep{HQM2012,Hopkins2018} most cases treat local radiation {\it only}, confined to energy or momentum injection in a limited physical region around a star particle.
+It is unclear what, if any, effect the long-range ionization and heating processes play in regulating star formation and driving galactic winds.
+Although the approximate radiation feedback models are capable of driving significant galactic outflows from galaxies, it is unclear if they capture the full effects of stellar ionizing radiation.
+
+In this work we present a comparison of three simulations of the evolution of an isolated, low mass dwarf galaxy that account for detailed stellar feedback.
+Our fiducial model uses an adaptive ray-tracing radiative transfer method to follow stellar ionizing radiation.
+We test its effectiveness in regulating star formation and driving galactic winds by comparison to a simulation without any ionizing radiation and a simulation with only localized radiation around each star.
+We discuss our methods in Section~\ref{sec:methods} and present our results in Section~\ref{sec:results}.
 
@@
 \includegraphics[width=0.49\linewidth]{mass}
-\caption{}
+\caption{The star formation rate (left) and gas and stellar mass (right) of each of our three simulations over time.}
 \label{fig:sfr_mass_evolution}
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=0.98\linewidth]{metal_retention}
+\caption{The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange).
+As in Figure~\ref{fig:sfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively.}
+\label{fig:metal_retention}
+\end{figure}
+
 \section{Discussion} \label{sec:discussion}
@@
 
-Figure~\ref{fig:panel1}, at XX Myr, shows each just after the first few SN in each simulation.
+Figure~\ref{fig:panel1}, at 17~Myr, shows each just after the first few SN in each simulation.
 Already there are significant differences across runs.
-Gas outside the galaxy is warm ($\sim$~10$^{4}$~K) and ionized up to XX~pc above/below the plane of the disk in our fiducial run.
+Gas outside the galaxy is warm ($\sim$~10$^{4}$~K) and ionized up to $\sim$500~pc above/below the plane of the disk in our fiducial run.
 This same gas is cold ($<10^4$~K) and neutral in both other runs.
@@
 \includegraphics[width=0.99\linewidth]{DD0136_fiducial_shortrad_nort}
-\caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.}}
-\label{fig:pane1l}
+\caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.} Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run.}
+\label{fig:panel1}
 \end{figure*}
@@
 In the noRT case, outflow does eventually develop, but it takes the factor of 5 increase in SFR for SN gas to finally break out from the neutral gas surrounding the galaxy.
+This is shown more clearly in Figure~\ref{fig:panel2}, which gives each simulation 40~Myr after the formation of the first stars.
+Comparing the shortrad and fiducial runs long term (\textit{give sentence on how these panels look 200 + Myr down the line but don't actually show this}).
 
@@
 \includegraphics[width=0.99\linewidth]{DD0160_fiducial_shortrad_nort}
-\caption{Panel}
-\label{fig:pane2}
+\caption{Same as Figure~\ref{fig:panel1}, but at 40~Myr.}
+\label{fig:panel2}
 \end{figure*}
@@
 \section{Conclusion}  \label{sec:conclusion}
-Very short. Just re-iterate points
+In agreement with previous works, we find that stellar radiation is an important source of feedback that helps regulate star formation in dwarf galaxies. (more)
 
-\begin{thebibliography}{}
-
-\end{thebibliography}
+\bibliography{msbib} % if your bibtex file is called example.bib
 

### 2018-07-18 ms.tex
Update on Overleaf.

@@
 %Lower mass stars (size range) primarily drive photoelectric heating (cite) and H$_2$ dissociation through radiation in the far ultraviolet and Lyman-Werner bands, while more massive stars (range) emit significant amounts of ionizing radiation.
-Simulations including stellar radiation feedback followed through radiative transfer or radiation-hydrodynamics schemes have found it to be effective in regulating star formation and driving galactic winds \citep[e.g.][]{Wise2012,Kim2013,Sales2014,Rosdahl2015,Ocvirk2015,Pawlik2015,Peters2017}.
+Simulations including stellar radiation feedback followed through radiative transfer or radiation-hydrodynamics schemes have found it to be effective in regulating star formation and driving galactic winds \citep[e.g.][]{WiseAbel2012,Kim2013a,Sales2014,Oshea2015,Rosdahl2015,Ocvirk2015,Pawlik2015,Peters2017}.
 This occurs for four reasons: 1) heating gas and preventing the formation of cold, dense star formation regions, 2) the destruction of cold, dense gas around recently formed stars, preventing further star formation, 3) momentum input by direct absorption of UV radiation by gas and (in some cases) dust through re-emission and scattering in the infrared, and 4) lowering the typical ISM densities in which SNe occur and greatly increasing their effectiveness.
@@
 Many works use a Stromgren approximation whereby the particles / cells within the Stromgren radius a radiating star are heated and kept ionized, with additional approximations made to account for overlapping ionized regions \citep[e.g.][]{HQM2011,Hu2016,Hu2017}.
-Other works employ some form of energy or momentum injection localized to the region immediately around a star particle \citep[e.g.][(\textit{need more})]{Agertz2013,Roskar2014,Ceverino2014,Forbes2015}.
+Other works employ some form of energy or momentum injection localized to the region immediately around a star particle \citep[e.g.][(\textit{need more})]{Agertz2013,Roskar2014,Ceverino2014,Forbes2016}.
 Although some of these approximate methods account for long-range effects of diffuse radiation \citep{HQM2012,Hopkins2018} most cases treat local radiation {\it only}, confined to energy or momentum injection in a limited physical region around a star particle.
@@
 We refer the reader to Paper I for a more detailed description of our methods, briefly summarized here.
-We use the adaptive mesh refinement hydrodynamics code \textsc{Enzo} \citep{Enzo} to evolve an idealized, isolated low mass dwarf galaxy initialized as a smooth exponential disk set in hydrostatic equillibrium with a static dark matter potential with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, and a maximum physical resolution of 1.8~pc.
-We include a UV background, tabulated metal line cooling, and a 9 species non-equillibrium chemistry solver using \textsc{Grackle} \citep{Grackle}.
-Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling the \cite{Salpeter1995} IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range.
+We use the adaptive mesh refinement hydrodynamics code \textsc{Enzo} \citep{Enzo2014} to evolve an idealized, isolated low mass dwarf galaxy initialized as a smooth exponential disk set in hydrostatic equillibrium with a static dark matter potential \citep{Burkert} with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, and a maximum physical resolution of 1.8~pc.
+We include a UV background, tabulated metal line cooling, and a 9 species non-equillibrium chemistry solver using \textsc{Grackle} \citep{GrackleMethod}.
+Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling the \cite{Salpeter1955} IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range.
 For each star, we include feedback from stellar winds, AGB winds, FUV and LW band radiation which drives photoelectric heating and H$_2$ dissociation respectively, HI and HeI ionizing radiation, and core collapse and Type Ia SNe using thermal energy injection.
@@
 
-\textbf{Stellar Ionizing Radiation Models} $-$ We present a comparison of three simulations in this work, which are identical with the exception of their stellar ionizing radiation feedback.
-In our fiducial simulation, we track the HI and HeI photoionizing radiation using the adaptive ray-tracing radiative transfer method of \citep{MORAY} for all stars above 8$M_{\odot}$ (see Paper I for details on determining the ionizing photon rates for each star).
+%\textbf{Stellar Ionizing Radiation Models} $-$
+We present a comparison of three simulations in this work, which are identical with the exception of their stellar ionizing radiation feedback.
+In our fiducial simulation, we track the HI and HeI photoionizing radiation using the adaptive ray-tracing radiative transfer method of \citep{WiseAbel2011} for all stars above 8$M_{\odot}$ (see Paper I for details on determining the ionizing photon rates for each star).
 We additionally present a simulation run without any stellar ionizing radiation (``noRT'') and a second simulation to test the relative importance of short-range vs.
 long-range effects of the radiation where we follow the full ionizing radiation RT, but delete photons once they have traveled more than 20~pc from their source (``shortrad'').
-This last simulation performs a similar, though significantly more detailed, function as commonly used methods to account for stellar radiation feedback which either deposit thermal energy (citation) or thermal energy and ionization (citations) locally, typically within the Stromgren radius, of each star.
+This last simulation performs a similar, though significantly more detailed, function as the commonly used methods for approximating the local effects of stellar radiation feedback.
 Each simulation is identical up until the formation of the first star particles, at which point they begin to diverge.

### 2018-07-18 main.tex
updated references and bugfix for plots

@@
 \documentclass[fleqn,usenatbib,useAMS]{mnras}
+\pdfoutput=1 
 \usepackage{graphicx}	% Including figure files
@@
 
-\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
+\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars}
 
@@
 We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
-Effective feedback \textbf{drives outflows with a greater metallicity than the ISM}, leading to low metal retention fractions consistent with observations.
+Effective feedback drives outflows with a greater metallicity than the ISM, leading to low metal retention fractions consistent with observations.
 Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
@@
 There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
-%{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
+% editor asked us to reduce citation count here:{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
 These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
@@
 In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
-This can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
-While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficienty high spatial resolution.
+Mixing can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
+While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficiently high spatial resolution.
 Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
@@
 Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
-\textbf{This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
-At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.} Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
+This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
+At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.
+Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
 The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
@@
 
-We refine the mesh whenever the \textbf{thermal} Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
+We refine the mesh whenever the thermal Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
 At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation.
@@
 However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse.
-\textbf{A non-thermal pressure term is added} to cells once their \textbf{thermal} Jeans length becomes unresolved.
+A non-thermal pressure term is added to cells once their thermal Jeans length becomes unresolved.
 This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
@@
 
-\textbf{Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas.
+Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas.
 These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution.
@@
 This threshold decreases the required run-time by factors of a few.
-The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)}
+The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)
 
@@
 In order to resolve individual star formation events on galactic scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
-Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local \textbf{thermal} Jeans mass.
+Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local thermal Jeans mass.
 Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K.
@@
 We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
-At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2017, FIRE2}, as star formation is ultimately self-regulated by feedback.
-
-The stellar mass formed during a timestep $\Delta t$ \textbf{from a region with a total gas mass $M_{\rm gas}$} is
+At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2018, FIRE2}, as star formation is ultimately self-regulated by feedback.
+
+The stellar mass formed during a timestep $\Delta t$ from a region with a total gas mass $M_{\rm gas}$ is
 \begin{equation}
@@
 If it does, we randomly sample from
-the adopted IMF until \textbf{approximately} 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
-\textbf{The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.} We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
+the adopted IMF until approximately 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
+The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.
+We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
 Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
-\textbf{By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.}
+By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.
 
@@
 For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars.
-We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2017}.
+We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2018}.
 This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$.
@@
 We assume complete thermalization of the wind kinetic energy, taking the total injected energy injected in timestep $\Delta t$ as $E_w = \frac{1}{2}\dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
-\textbf{This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle.
+This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle.
 The edges of this spherical region will only partially overlap grid cells.
-We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately.} We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
+We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately.
+We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
 
@@
 This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
-\textbf{In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle.
+In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle.
 For $u \in [0,1]$, we interpolate its position on a pre-tabulated and inverted cumulative probability distribution function to assign a single time at which the WD particle will explode as a Type 1a supernova.
-We institute a minimum delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.}
+We institute a minimum delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.
 
@@
 We ignore HeII photoionization from the UV background entirely.
-{\bf For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.}\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
+For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
 As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
@@
 This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations.
-\textbf{Our chemical work only includes contributions from H, He, and H$_2$ to n$_e$.} Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
+Our chemical network only includes contributions from H, He, and H$_2$ to n$_e$.
+Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
 %This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
@@
 The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
-Leo P is gas rich, with a \textbf{neutral hydrogen mass} $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and \textbf{stellar mass} $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to an \textbf{observed neutral hydrogen radius} $r_{\rm HI} = 500$~pc.
-LeoP has a low metallicity, with \textbf{an oxygen to hydrogen abundance ratio (O/H)} of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
+Leo P is gas rich, with a neutral hydrogen mass $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and stellar mass $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to an observed neutral hydrogen radius $r_{\rm HI} = 500$~pc.
+LeoP has a low metallicity, with an oxygen to hydrogen abundance ratio (O/H) of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
 Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
@@
 We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$.
-We adopt a \citet{Burkert1995} dark matter potential with \textbf{virial mass and radius} $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and \textbf{scale radius} r$_{\rm s} = 990$~pc.
+We adopt a \citet{Burkert1995} dark matter potential with virial mass and radius $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and scale radius r$_{\rm s} = 990$~pc.
 This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc.
@@
 For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
-\textbf{In the final column of Figure~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
+In the final column of Figure~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
 With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
 At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$.
-These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.}
+These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.
 
@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, \textbf{ with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
 The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
@@
 Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
-The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.}
+The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
 
@@
 We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content.
-\textbf{By this definition, although our galaxy certainly contains molecular hydrogen, molecular gas as a phase does not exist; the peak f$_{\rm H_2}$ in any single cell remains below 30\%.} See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
+By this definition, although our galaxy certainly contains molecular hydrogen, molecular gas as a phase does not exist; the peak f$_{\rm H_2}$ in any single cell remains below 30\%.
+See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
 The properties of these phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
@@
 We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
-\textbf{Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left.}  The boxed regime in the lower right corner shows our star formation density and temperature threshold.
+Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left.
+The boxed regime in the lower right corner shows our star formation density and temperature threshold.
 Gas in this regime is rapidly consumed by star formation and subsequent feedback.
@@
 
-\textbf{H2 changes:} The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
+The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
 The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
@@
 
-\textbf{H2 Changes:} These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
+These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
 They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (defined in those works as gas with 100~K$<$T$< 3\times 10^{4}$), with cold gas having between 1 and 10\% of the mass, and occupying negligible volume.
@@
 The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.
-\textbf{The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
-At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.}
-
-\textbf{ The bottom panel gives the HI ionizing photon flux from stellar radiation.
+The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
+At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.
+
+The bottom panel gives the HI ionizing photon flux from stellar radiation.
 The ionizing radiation profile follows a similar trend, yet with significantly more variation, anywhere from two to four orders of magnitude.
@@
 The total fluctuation in both panels is due in part to the low-level, stochastic star formation in our galaxy.
-A higher star formation rate would produce a more regular population of massive stars and more uniform (in time) ISRF.}
+A higher star formation rate would produce a more regular population of massive stars and more uniform (in time) ISRF.
 
@@
 \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift, consistent with our results.
+The fluctuations in both of these panels are directly correlated with the SFR, with increased outflow during periods of star formation, and decreased outflow during periods of quiescence.
 
@@
 
-\textbf{H2 Changes:} Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
+Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
 In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
@@
 Half of the outflowing gas (positive velocities) is moving at velocities below 30 km s$^{-1}$, 75\% at velocities below 70 km s$^{-1}$, and 95\% at velocities below 100 km s$^{-1}$.
-Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-neglibable amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$.
+Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-negligible amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$.
 The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominating at velocities above 200 km s$^{-1}$.
@@
 where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-We note the very large loading factors in the first 20~Myr are artificial, and a byproduct of the initial conditions.
-For half of the evolution, the inner three radii give $\eta_{\rm metal}$ below unity (around 0.6), but it increases at each radius, fluctuating around unity for the second half of the simulation.
+These metal loading factors fluctuate significantly with the SFR, just as was shown in Figure~\ref{fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
+On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5).
 Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}.
@@
 This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
-A more detailed analysis is beyond the scope of this work, but we \textbf{investigate this in detail in Emerick et.
+A more detailed analysis is beyond the scope of this work, but we investigate this in detail in Emerick et.
 al.
-(in prep.).}
+(in prep.).
 
@@
 On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}.
-There is no clear correlation with time in this diagram.} %something is breaking here in compiling
+There is no clear correlation with time in this diagram.}
 \label{fig:KS}
@@
 This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
-\textbf{The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.}
+The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.
 
@@
 \label{sec:molecular gas content}
-\textbf{AE: rewording - changed numbers and text to reflect lower H2 fractions. left discussion of uncertainties in H2 formation in low mass dwarfs and need for further study:}
 The molecular gas content of low-mass dwarf galaxies is generally assumed
@@
 Wise.
+We would additionally like to thank the referee for their careful report.
 A.E.
@@
 
-\textbf{Significant changes to the lower resolution runs and the comparison to our fiducial simulation with the change to the H$_2$ production:}
-
 We demonstrate the effect of varying resolution in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}.

### 2018-07-18 ms.tex

@@
 \begin{abstract}
-Placeholder
 %{\bf Ignore: Ionizing radiation from recently formed massive stars is important in destroying cold, dense gas around new regions of star formation that would otherwise continue to form stars.
@@
 
-Radiation from massive stars dominates the total feedback energy output of a stellar population \citep[e.g.][]{Lietherer1999,Agertz2013}, surpassing the energy ejection of supernova ($\sim 10^{51}$~erg) by two orders of magnitude.
+Radiation from massive stars dominates the total feedback energy output of a stellar population \citep[e.g.][]{Leitherer1999,Agertz2013}, surpassing the energy ejection of supernova ($\sim 10^{51}$~erg) by two orders of magnitude.
 If the radiation couples effectively to the interstellar medium (ISM), it can be a substantial source of additional feedback.
@@
 We refer the reader to Paper I for a more detailed description of our methods, briefly summarized here.
-We use the adaptive mesh refinement hydrodynamics code \textsc{Enzo} \citep{Enzo2014} to evolve an idealized, isolated low mass dwarf galaxy initialized as a smooth exponential disk set in hydrostatic equillibrium with a static dark matter potential \citep{Burkert} with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, and a maximum physical resolution of 1.8~pc.
-We include a UV background, tabulated metal line cooling, and a 9 species non-equillibrium chemistry solver using \textsc{Grackle} \citep{GrackleMethod}.
+We use the adaptive mesh refinement hydrodynamics code \textsc{Enzo} \citep{Enzo2014} to evolve an idealized, isolated low mass dwarf galaxy.
+The galaxy is initialized as a smooth exponential disk set in hydrostatic equillibrium with a static dark matter potential \citep{Burkert1995} with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, and a maximum physical resolution of 1.8~pc.
+We do not model an initial stellar population, but do include random driving from supernovae as an initial source of initial and feedback up until first star formation.
+
+We include a UV background, tabulated metal line cooling, and a 9 species non-equilibrium chemistry solver using \textsc{Grackle} \citep{GrackleMethod}.
 Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling the \cite{Salpeter1955} IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range.
 For each star, we include feedback from stellar winds, AGB winds, FUV and LW band radiation which drives photoelectric heating and H$_2$ dissociation respectively, HI and HeI ionizing radiation, and core collapse and Type Ia SNe using thermal energy injection.
-FUV and LW band radiation are both taken to be optically thin, which approximate, local self-shielding alone, but ionizing radiation is followed with radiative transfer (see below).
+FUV and LW band radiation are both taken to be optically thin, with local (cell-by-cell) attenuation alone.
+Ionizing radiation is followed using radiative transfer, as discussed below.
+\textit{Maybe can leave this out:} Stellar lifetimes, surface gravity, effective temperature, and radii are set by the initial stellar mass and metallicity through interpolation over the PARSEC \citep{Bressan2012} zero age main sequence values.
+These values for surface gravity, effective temperature, and radii are used to set the FUV, LW, and ionizing photon fluxes from each star through interpolation on the OSTAR2002 \citep{LanHubeny2003} grid.
+We only follow the radiation from stars above 8~M$_{\odot}$.
+%tellar wind and supernovae mass loss are determined with the  NuGrid yield tables for $M_* < 25$~M$_{\odot}$ and from Slemer et. al. (in prep) for $M_* > 25$~M$_{\odot}$.
 
 %\textbf{Stellar Ionizing Radiation Models} $-$
-We present a comparison of three simulations in this work, which are identical with the exception of their stellar ionizing radiation feedback.
-In our fiducial simulation, we track the HI and HeI photoionizing radiation using the adaptive ray-tracing radiative transfer method of \citep{WiseAbel2011} for all stars above 8$M_{\odot}$ (see Paper I for details on determining the ionizing photon rates for each star).
-We additionally present a simulation run without any stellar ionizing radiation (``noRT'') and a second simulation to test the relative importance of short-range vs.
-long-range effects of the radiation where we follow the full ionizing radiation RT, but delete photons once they have traveled more than 20~pc from their source (``shortrad'').
-This last simulation performs a similar, though significantly more detailed, function as the commonly used methods for approximating the local effects of stellar radiation feedback.
-Each simulation is identical up until the formation of the first star particles, at which point they begin to diverge.
+In our fiducial simulation, we follow photoionizing radiation using the adaptive ray-tracing radiative transfer method of \cite{WiseAbel2011}.
+This method places and evolves 48 rays on a HEALPix grid around each emitting source star for both HI and HeI ionizing radiation.
+Rays are adaptively split as they propagate away from their source to increase the angular resolution such that the solid angle of the ray remains smaller than 1/3 of the cell area.
+Rays begin on HEALPix refinement level 2, with a maximum refinement level of 13 (or $8.05 \times 10^8$ rays).
+
+We additionally present a simulation run without any stellar ionizing radiation (``noRT'') and a second simulation that includes ionizing radiation, but deletes all photons that travel more than 20~pc from their source (``shortrad'').
+This second simulation tests the relative importance of short-range vs.
+long-range effects of stellar ionizing radiation as a form of feedback.
+Although this is still more accurate than an approximate method, this is meant to function similarly to methods that include only the local effects of stellar radiation feedback.
+Each of our three simulations is identical up until the formation of the first star particles.
+At this point, the differing feedback physics causes each to diverge.
 We note that the stars from the very first star formation event in each run (21 star particles with a total mass of 114 M$_{\odot}$) are the same in each run.
@@
 However, these two simulations begin to diverge significantly after this point.
-The shortrad simulations has continual, steady star formation for the entire simulation time, while the star formation rate in our fiducial run is bursty, with periods of active, low-level star formation interspersed with periods (sometimes up to 50~Myr) of no star formation.
+The shortrad simulation has continual, steady star formation for the entire simulation time, while the star formation rate in our fiducial run is bursty, with periods of active, low-level star formation interspersed with periods (sometimes up to 50~Myr) of no star formation.
 The driver of these differences is clear in the right hand panel.
-Our fiducial run looses a significant amount of total gas and HI mass (black and blue lines) as compared to the shortrad simulation by a factor of XX.
+Our fiducial run looses a significant amount of total gas and HI mass (black and blue lines) as compared to the shortrad simulation by a factor of $\sim$2.
 Clearly, galactic winds and outflows are much more effective in the fiducial case, with full accounting of stellar ionizing radiation feedback, then in the shortrad simulation.
@@
 
+\textbf{We have room for one more figure and a little more text to explain it. Possibly a comparison of mass / volume fractions in certain phases? But maybe not necessary....}
+
 \section{Discussion} \label{sec:discussion}
@@
 However, the specific importance of localized ionization vs.
-ionization far from the source star has not been examined.
+ionization from a diffuse radiation field far from a single star has not been examined.
 As shown above, accounting for stellar radiation feedback locally alone is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
-To explore the cause of this difference we present two panel-plots in Figure~\ref{fig:panel1} and Figure~\ref{fig:panel2} which compare the gas number density (left), temperature (middle), and HI ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote:{See ({\it insert link here}) for a movie of this comparison}
+To explore the cause of this difference we present two panel-plots in Figure~\ref{fig:panel1} and Figure~\ref{fig:panel2} which compare the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote:{See ({\it insert link here once posted}) for a movie of this comparison.}
 
-Figure~\ref{fig:panel1}, at 17~Myr, shows each just after the first few SN in each simulation.
+Figure~\ref{fig:panel1}, at 17~Myr, compares each simulation just after the first few SNe.
 Already there are significant differences across runs.
@@
 This same gas is cold ($<10^4$~K) and neutral in both other runs.
-The contrast between the fiducial and shortrad radiation is seen most clearly in the ionized region in-plane and to the right of center in the top and bottom panels.
-This region contains massive stars that are capable of generating enough ionizing radiation to carve a channel out to the halo of our fiducial simulation; by construction, this does not occur in the shortrad case.
-The warm / ionized feature towards the center of each galaxy is gas from a recent SN.
-This is much more well contained and hotter in the noRT and shortrad runs than in our fiducial simulation.
+The contrast between the effect of ionizing radiation in the fiducial and shortrad runs is seen most clearly in the ionized region in-plane and to the right of center.
+This region contains massive stars that are capable of generating enough ionizing radiation to carve a channel out to the halo of our fiducial simulation; this does not occur in the shortrad case.
+Instead, the HII region is confined by surrounding cold, neutral gas.
 
@@
 
-As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow significant outflows from SNe to escape the disk and move well into the halo of our galaxy.
-In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas and unable to driving significant mass loss from the galaxy.
-In the noRT case, outflow does eventually develop, but it takes the factor of 5 increase in SFR for SN gas to finally break out from the neutral gas surrounding the galaxy.
-This is shown more clearly in Figure~\ref{fig:panel2}, which gives each simulation 40~Myr after the formation of the first stars.
-Comparing the shortrad and fiducial runs long term (\textit{give sentence on how these panels look 200 + Myr down the line but don't actually show this}).
+Although the ISM properties within the HII region in each case are quite similar between the simulations, the SNe that will eventually go off in this region are confined by this neutral gas in the shortrad simulation, but are readily ejected into the galaxy halo in our fiducial case.
+As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe.
+In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas.
+Though they make a significant local impact on the ISM, they are unable to drive significant mass loss from the galaxy.
+In the noRT case, outflow does eventually develop, but it takes the factor of 5 increase in SFR, and corresponding increase in supernova rate, for SNe to finally break out from the neutral gas surrounding the galaxy.
+These differences are shown more clearly in Figure~\ref{fig:panel2}, which gives each simulation 40~Myr after the formation of the first stars.
 

### 2018-07-19 ms.tex
Update on Overleaf.

@@
 \begin{abstract}
+\textit{Will complete at end}
 %{\bf Ignore: Ionizing radiation from recently formed massive stars is important in destroying cold, dense gas around new regions of star formation that would otherwise continue to form stars.
@@
 \section{Introduction} \label{sec:intro}
-Historically, simulations of galaxy formation have suffered from the ``overcooling'' problem, whereby simulations including self-gravity and radiative cooling alone produce galaxies with far too many stars.
-This problem has been addressed by employing various models of feedback physics which produces self-regulating star formation in galaxies.
-Recently, it has become clear that simple models for stellar feedback, which account for supernovae (SNe) alone, are insufficient to fully regulate star formation and set galaxy properties consistent with observations (see \cite{NaabOstriker2017} for a recent review).
-Additional processes, such as stellar radiation, cosmic rays, or AGN, are often employed as additional sources of feedback.
+Historically, simulations of galaxy formation have suffered from the ``overcooling'' problem, whereby the action of self-gravity and radiative cooling alone produces galaxies with far too many stars.
+This problem has been addressed by employing various models of stellar feedback physics which are capable of generating self-regulating star formation in galaxies.
+Recently, it has become clear that the simplest models for stellar feedback, which account for supernovae (SNe) alone, are insufficient \citep{Smith2018} to fully regulate star formation and set galaxy properties consistent with observations (see \cite{NaabOstriker2017} for a recent review).
+Processes, such as stellar radiation, cosmic rays, or AGN, are often employed as additional sources of feedback.
 Modeling these processes in detail, however, is challenging.
+As a result, the relative importance of these additional physics is still uncertain.
 
@@
 However, most works that employ stellar radiation feedback to account for these effects do so using various forms of sub-grid, approximate models to avoid the substantial additional cost of full radiative transfer.
-Many works use a Stromgren approximation whereby the particles / cells within the Stromgren radius a radiating star are heated and kept ionized, with additional approximations made to account for overlapping ionized regions \citep[e.g.][]{HQM2011,Hu2016,Hu2017}.
+Many works use a Str{\"o}mgren approximation whereby the particles / cells within the Str{\"o}mgren radius around a radiating star are heated and kept ionized, with additional approximations made to account for overlapping ionized regions \citep[e.g.][]{HQM2011,Hu2016,Hu2017}.
 Other works employ some form of energy or momentum injection localized to the region immediately around a star particle \citep[e.g.][(\textit{need more})]{Agertz2013,Roskar2014,Ceverino2014,Forbes2016}.
 Although some of these approximate methods account for long-range effects of diffuse radiation \citep{HQM2012,Hopkins2018} most cases treat local radiation {\it only}, confined to energy or momentum injection in a limited physical region around a star particle.
-It is unclear what, if any, effect the long-range ionization and heating processes play in regulating star formation and driving galactic winds.
-Although the approximate radiation feedback models are capable of driving significant galactic outflows from galaxies, it is unclear if they capture the full effects of stellar ionizing radiation.
+Although the approximate radiation feedback models are capable of driving significant galactic outflows, it is unclear if they capture the full effects of stellar ionizing radiation.
+%The 
+%It is unclear what, if any, effect the long-range ionization and heating processes play in regulating star formation and driving galactic winds.
 
@@
 Our fiducial model uses an adaptive ray-tracing radiative transfer method to follow stellar ionizing radiation.
-We test its effectiveness in regulating star formation and driving galactic winds by comparison to a simulation without any ionizing radiation and a simulation with only localized radiation around each star.
+We test its effectiveness in regulating star formation and driving galactic winds by comparison to a simulation without ionizing radiation and a simulation with only localized radiation around each star.
 We discuss our methods in Section~\ref{sec:methods} and present our results in Section~\ref{sec:results}.
@@
 Ionizing radiation is followed using radiative transfer, as discussed below.
-\textit{Maybe can leave this out:} Stellar lifetimes, surface gravity, effective temperature, and radii are set by the initial stellar mass and metallicity through interpolation over the PARSEC \citep{Bressan2012} zero age main sequence values.
-These values for surface gravity, effective temperature, and radii are used to set the FUV, LW, and ionizing photon fluxes from each star through interpolation on the OSTAR2002 \citep{LanHubeny2003} grid.
-We only follow the radiation from stars above 8~M$_{\odot}$.
+Stellar lifetimes, surface gravity, effective temperature, and radii are set by the initial stellar mass and metallicity through interpolation over the PARSEC \citep{Bressan2012} zero age main sequence values.
+These values for surface gravity, effective temperature, and radii are used to set the FUV, LW, and ionizing photon fluxes from each star through interpolation on the OSTAR2002 \citep{LanzHubeny2003} grid.
+We only follow the radiation from stars with masses above 8~M$_{\odot}$.
 %tellar wind and supernovae mass loss are determined with the  NuGrid yield tables for $M_* < 25$~M$_{\odot}$ and from Slemer et. al. (in prep) for $M_* > 25$~M$_{\odot}$.
@@
 
-This can be confirmed by examining the mass loading factor and metal retention fraction (the fraction of produced metals retained within the disk of the galaxy) in each simulation.
-As shown in Figure~\ref{fig:metal_retention}, the mass loading factor in the fiducial run is a factor of XXX higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, and is the only simulation with any significant outflow beyond the virial radius.
-This is especially interesting considering the factor 5 increase in SFR of the noRT run.
-The noRT run does have a significant amount of gas mass outflowing at XXXX, but note that its low mass loading factor is due primarily to the significantly larger SFR in this galaxy.
-Radiation feedback, both locally and over longer ranges, is important in determining the ability for SN to drive significant outflows.
-We discuss the reasons for this in the following section.
+This can be confirmed by examining the metal retention fraction (the fraction of produced metals retained within the disk of the galaxy) and mass outflow rates in each simulation.
+As shown in Figure~\ref{fig:metal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation.
+Given this, the fiducial simulation has an even higher mass loading factor, since the shortrad simulation has a typically higher SFR.
+The fiducial run is also the only simulation with any significant outflow beyond the virial radius, though we note the noRT run has not been simulated long enough for gas to have reached the virial radius.
+The outflow in noRT is nearly the same as the fiducial run, but it requires a 5 times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback.
+Radiation feedback, therefore allows SN to be substantially more effective in driving outflows.
+We provide a physical intuition for these differences in the following section.
 
@@
 \centering
-\includegraphics[width=0.98\linewidth]{metal_retention}
-\caption{The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange).
-As in Figure~\ref{fig:sfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively.}
+\includegraphics[width=0.95\linewidth]{metal_retention}\\
+\includegraphics[width=0.95\linewidth]{mass_loading_comparison}
+\caption{{\bf Top:} The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange).
+As in Figure~\ref{fig:sfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively.
+{\bf Bottom:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed).}
 \label{fig:metal_retention}
@@
 
-\textbf{We have room for one more figure and a little more text to explain it. Possibly a comparison of mass / volume fractions in certain phases? But maybe not necessary....}
+\textbf{We may have room for one more figure and a little more text to explain it. Possibly a comparison of mass / volume fractions in certain phases? But maybe not necessary....}
 
@@
 As shown above, accounting for stellar radiation feedback locally alone is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
-To explore the cause of this difference we present two panel-plots in Figure~\ref{fig:panel1} and Figure~\ref{fig:panel2} which compare the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote:{See ({\it insert link here once posted}) for a movie of this comparison.}
+To explore the cause of this difference we present two panel-plots in Figure~\ref{fig:panel1} and Figure~\ref{fig:panel2} which compare the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
 
@@
 \includegraphics[width=0.99\linewidth]{DD0136_fiducial_shortrad_nort}
-\caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.} Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run.}
+\caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.But for now: TOP: Fiducial.
+MIDDLE: noRT.
+BOTTOM: shortrad} Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run.}
 \label{fig:panel1}
@@
 \section{Conclusion}  \label{sec:conclusion}
-In agreement with previous works, we find that stellar radiation is an important source of feedback that helps regulate star formation in dwarf galaxies. (more)
+In agreement with previous works we find that stellar radiation feedback is effective in regulating star formation and driving outflows in our simulations of an isolated, low mass dwarf galaxy.
+Simulations run without ionizing radiation feedback have star formation rates a factor of five higher than our fiducial simulation.
+In spite of this difference, SNe in our fiducial run are capable of driving larger galactic outflows, aided significantly by the ionizing radiation feedback.
+
+We also demonstrate that simple prescriptions which treat stellar radiation feedback locally do not fully reproduce the same evolution as our fiducial model.
+Our simulation with radiation localized to 20~pc around each star particle does effectively regulate star formation on short time scales, predominately by quickly destroying cold, dense gas around young, hot stars.
+However, this model does not drive the significant outflows seen in our fiducial simulation.
+Long-range ionizing radiation is important for carving channels allowing the release of significant amounts mass and metals from SNe.
+Our simulation with localized radiation feedback retains metals at a significantly higher fraction than expected observationally for low mass dwarf galaxies.
+
+Finally, we note that we have performed this experiment on only one possible type of galaxy.
+Its low virial temperature ($\sim10^{4}$~K) makes this galaxy particularly sensitive to the effects of stellar feedback and ionizing radiation in particular.
+Examining the role of long-range, diffuse stellar ionizing radiation on star formation and galactic winds in more massive galaxies is an important avenue of future research.
 

### 2018-07-24 ms.tex
some revisions, a new reference

@@
 
-Radiation from massive stars dominates the total feedback energy output of a stellar population \citep[e.g.][]{Leitherer1999,Agertz2013}, surpassing the energy ejection of supernova ($\sim 10^{51}$~erg) by two orders of magnitude.
+Radiation from massive stars dominates the total feedback energy output of a stellar population 
+%mm added Abbott1982
+\citep[e.g.][]{Abbott1982,Leitherer1999,Agertz2013}, surpassing the energy ejection of supernova ($\sim 10^{51}$~erg) by two orders of magnitude.
 If the radiation couples effectively to the interstellar medium (ISM), it can be a substantial source of additional feedback.
@@
 Simulations including stellar radiation feedback followed through radiative transfer or radiation-hydrodynamics schemes have found it to be effective in regulating star formation and driving galactic winds \citep[e.g.][]{WiseAbel2012,Kim2013a,Sales2014,Oshea2015,Rosdahl2015,Ocvirk2015,Pawlik2015,Peters2017}.
-This occurs for four reasons: 1) heating gas and preventing the formation of cold, dense star formation regions, 2) the destruction of cold, dense gas around recently formed stars, preventing further star formation, 3) momentum input by direct absorption of UV radiation by gas and (in some cases) dust through re-emission and scattering in the infrared, and 4) lowering the typical ISM densities in which SNe occur and greatly increasing their effectiveness.
+This occurs in four ways: 1) heating
+%mm 
+   of diffuse 
+gas and preventing the formation of cold, dense star formation regions, 2) destruction of cold, dense gas around recently formed stars, preventing further star formation, 3) momentum input by direct absorption of UV radiation by gas and (in some cases) dust through re-emission and scattering in the infrared, and 4) lowering the typical ISM densities in which SNe occur and greatly increasing their effectiveness.
 % the relevance / importance of RP from dust in the IR is beyond the scope of this work...
@@
 We use the adaptive mesh refinement hydrodynamics code \textsc{Enzo} \citep{Enzo2014} to evolve an idealized, isolated low mass dwarf galaxy.
-The galaxy is initialized as a smooth exponential disk set in hydrostatic equillibrium with a static dark matter potential \citep{Burkert1995} with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, and a maximum physical resolution of 1.8~pc.
-We do not model an initial stellar population, but do include random driving from supernovae as an initial source of initial and feedback up until first star formation.
+The galaxy is initialized as a smooth exponential disk set in hydrostatic equillibrium with a static dark matter potential \citep{Burkert1995} with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, on a grid with a maximum physical resolution of 1.8~pc.
+We do not model an initial stellar population, but do include random driving from supernovae as an initial source of feedback up until the first explicit star formation in our model.
 
@@
 \includegraphics[width=0.49\linewidth]{mass}
-\caption{The star formation rate (left) and gas and stellar mass (right) of each of our three simulations over time.}
+\caption{The star formation rate (left) and gas and stellar mass (right) of each of our three simulations over time.
+%mm
+   Time bins with no star formation are left empty. 
+   {\bf legend on first plot has Shortard rather than Shortrad.}}
 \label{fig:sfr_mass_evolution}
@@
 Radiation from these stars quickly ionizes and dissipates surrounding dense gas that would otherwise have gone to fuel a significant amount of additional star formation.
-We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints.
-Although radiative transfer is expensive, this run is substantially more computationally expensive than the fiducial and shortrad runs due to the significantly higher star formation rate.
+We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints
+%mm
+   from the large number of stars formed. 
+Although radiative transfer is computationally expensive, this run is substantially more expensive than the fiducial and shortrad runs due to the significantly higher star formation rate.
 
@@
 The driver of these differences is clear in the right hand panel.
-Our fiducial run looses a significant amount of total gas and HI mass (black and blue lines) as compared to the shortrad simulation by a factor of $\sim$2.
+Our fiducial run loses
+%mm a significant amount of 
+    a factor of $\sim 2$ more 
+total gas and HI mass (black and blue lines) as compared to the shortrad simulation. 
+%mm by a factor of $\sim$2. 
 Clearly, galactic winds and outflows are much more effective in the fiducial case, with full accounting of stellar ionizing radiation feedback, then in the shortrad simulation.
@@
 Radiation feedback, therefore allows SN to be substantially more effective in driving outflows.
-We provide a physical intuition for these differences in the following section.
+We provide a physical
+%mm intuition 
+   explanation
+for these differences in the following section.
 

### 2018-07-25 ms.tex
revisions of results and conclusions.  Still just a bit more to do

@@
 The driver of these differences is clear in the right hand panel.
-Our fiducial run loses
-%mm a significant amount of 
-    a factor of $\sim 2$ more 
+Our fiducial run
+%mm looses a significant amount of 
+    loses a factor of $\sim 2$ more 
 total gas and HI mass (black and blue lines) as compared to the shortrad simulation. 
 %mm by a factor of $\sim$2. 
-Clearly, galactic winds and outflows are much more effective in the fiducial case, with full accounting of stellar ionizing radiation feedback, then in the shortrad simulation.
+Clearly, galactic winds and outflows are much more effective in the fiducial case, with full accounting of stellar ionizing radiation feedback, than in the shortrad simulation.
 
@@
 Given this, the fiducial simulation has an even higher mass loading factor, since the shortrad simulation has a typically higher SFR.
-The fiducial run is also the only simulation with any significant outflow beyond the virial radius, though we note the noRT run has not been simulated long enough for gas to have reached the virial radius.
-The outflow in noRT is nearly the same as the fiducial run, but it requires a 5 times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback.
-Radiation feedback, therefore allows SN to be substantially more effective in driving outflows.
+The fiducial run is also the only
+%mm simulation 
+   one of the three 
+with any significant outflow beyond the virial radius, though we note the noRT run has not been simulated long enough for gas to have reached the virial radius.
+The outflow in noRT is nearly the same as the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback.
+We conclude that radiation feedback allows SN to be substantially more effective in driving outflows.
 We provide a physical
@@
 As in Figure~\ref{fig:sfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively.
-{\bf Bottom:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed).}
+{\bf Bottom:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed).
+%mm
+   {\bf Could you add a panel explicitly showing mass loading factor as discussed in the text?}
+}
 \label{fig:metal_retention}
@@
 
-\textbf{We may have room for one more figure and a little more text to explain it. Possibly a comparison of mass / volume fractions in certain phases? But maybe not necessary....}
+\textbf{We may have room for one more figure and a little more text to explain it. Possibly a comparison of mass / volume fractions in certain phases? But maybe not necessary....
+
+What about vertical profiles of density, temperature, ionization?  These would support your discussion below - MM
+}
 
 \section{Discussion} \label{sec:discussion}
-Again, it is known that accounting for feedback from stellar radiation plays a significant role in determining the ability for SN energy to couple to the ISM and therefore drive outflows.
-However, the specific importance of localized ionization vs.
-ionization from a diffuse radiation field far from a single star has not been examined.
-As shown above, accounting for stellar radiation feedback locally alone is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
-To explore the cause of this difference we present two panel-plots in Figure~\ref{fig:panel1} and Figure~\ref{fig:panel2} which compare the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
+%mm Again, it is known that 
+Accounting for feedback from stellar radiation plays a significant role in determining the ability for SN energy to couple to the ISM and therefore drive outflows. 
+%mm However, the specific 
+     We believe this work is novel in examining the
+importance of localized ionization vs.\ ionization from a diffuse radiation field far from a single star
+%mm has not been examined. As shown above, accounting for 
+    Only modeling 
+stellar radiation feedback locally 
+%mm alone 
+is insufficient to describe the long-term evolution of an isolated dwarf galaxy. To explore the cause of this difference we 
+%mm present two panel-plots in Figure~\ref{fig:panel1} and Figure~\ref{fig:panel2} which 
+compare in Figures~\ref{fig:panel1} and~Figure~\ref{fig:panel2} 
+the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
 
 Figure~\ref{fig:panel1}, at 17~Myr, compares each simulation just after the first few SNe.
-Already there are significant differences across runs.
+Already there are significant differences between the runs.
 Gas outside the galaxy is warm ($\sim$~10$^{4}$~K) and ionized up to $\sim$500~pc above/below the plane of the disk in our fiducial run.
@@
 
-Although the ISM properties within the HII region in each case are quite similar between the simulations, the SNe that will eventually go off in this region are confined by this neutral gas in the shortrad simulation, but are readily ejected into the galaxy halo in our fiducial case.
-As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe.
+Although the ISM properties within the HII region in each case are quite similar between the simulations, the SNe that eventually go off in this region are confined by the neutral gas in the shortrad simulation, but
+%mm are readily ejected
+   readily escape through the lower density ionized gas
+into the galaxy halo in our fiducial case. As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe,
+%mm
+   as shown in  Figure~\ref{fig:panel2}, which shows each simulation 40~Myr after the 
+   formation of the first stars. 
 In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas.
 Though they make a significant local impact on the ISM, they are unable to drive significant mass loss from the galaxy.
-In the noRT case, outflow does eventually develop, but it takes the factor of 5 increase in SFR, and corresponding increase in supernova rate, for SNe to finally break out from the neutral gas surrounding the galaxy.
-These differences are shown more clearly in Figure~\ref{fig:panel2}, which gives each simulation 40~Myr after the formation of the first stars.
+In the noRT case, an outflow does eventually develop, but it takes the factor of five increase in SFR, and corresponding increase in supernova rate, for SNe to finally break out from the neutral gas surrounding the galaxy.
+%mm These differences are shown more clearly in Figure~\ref{fig:panel2}, which shows each simulation 40~Myr after the formation of the first stars.
 
@@
 \section{Conclusion}  \label{sec:conclusion}
-In agreement with previous works we find that stellar radiation feedback is effective in regulating star formation and driving outflows in our simulations of an isolated, low mass dwarf galaxy.
+In agreement with previous work we find that stellar radiation feedback is effective in regulating star formation and driving outflows in our simulations of an isolated, low mass, dwarf galaxy.
 Simulations run without ionizing radiation feedback have star formation rates a factor of five higher than our fiducial simulation.
@@
 
-We also demonstrate that simple prescriptions which treat stellar radiation feedback locally do not fully reproduce the same evolution as our fiducial model.
+We 
+%mm also 
+demonstrate
+%mm
+   for the first time 
+that simple prescriptions 
+%mm which treat stellar radiation feedback locally do not fully reproduce the same
+%evolution as our fiducial model. 
+    of local stellar radiation feedback fail to reproduce the evolution of our fiducial 
+    model.
 Our simulation with radiation localized to 20~pc around each star particle does effectively regulate star formation on short time scales, predominately by quickly destroying cold, dense gas around young, hot stars.

### 2018-07-25 ms.tex
finished first pass

@@
 Long-range ionizing radiation is important for carving channels allowing the release of significant amounts mass and metals from SNe.
-Our simulation with localized radiation feedback retains metals at a significantly higher fraction than expected observationally for low mass dwarf galaxies.
+Our simulation with localized radiation feedback retains a significantly higher fraction of metals than expected observationally for low mass dwarf galaxies.
+%mm
+    {\bf [This point needs to be supported by a paragraph with references in the discussion.]}
 
 Finally, we note that we have performed this experiment on only one possible type of galaxy.
-Its low virial temperature ($\sim10^{4}$~K) makes this galaxy particularly sensitive to the effects of stellar feedback and ionizing radiation in particular.
+Its low virial temperature ($\sim10^{4}$~K) makes this galaxy particularly sensitive to the effects of stellar feedback, and ionizing radiation in particular.
 Examining the role of long-range, diffuse stellar ionizing radiation on star formation and galactic winds in more massive galaxies is an important avenue of future research.

### 2018-07-25 ms.tex
now compiles
Finishing up Mordecais comments and adding new figure. Text for new figure is currently incomplete

@@
 
-Radiation from massive stars dominates the total feedback energy output of a stellar population 
-%mm added Abbott1982
-\citep[e.g.][]{Abbott1982,Leitherer1999,Agertz2013}, surpassing the energy ejection of supernova ($\sim 10^{51}$~erg) by two orders of magnitude.
+Radiation from massive stars dominates the total feedback energy output of a stellar population \citep[e.g.][]{Abbott1982,Leitherer1999,Agertz2013}, surpassing the energy ejection of supernova ($\sim 10^{51}$~erg) by two orders of magnitude.
 If the radiation couples effectively to the interstellar medium (ISM), it can be a substantial source of additional feedback.
@@
 Simulations including stellar radiation feedback followed through radiative transfer or radiation-hydrodynamics schemes have found it to be effective in regulating star formation and driving galactic winds \citep[e.g.][]{WiseAbel2012,Kim2013a,Sales2014,Oshea2015,Rosdahl2015,Ocvirk2015,Pawlik2015,Peters2017}.
-This occurs in four ways: 1) heating
-%mm 
-   of diffuse 
-gas and preventing the formation of cold, dense star formation regions, 2) destruction of cold, dense gas around recently formed stars, preventing further star formation, 3) momentum input by direct absorption of UV radiation by gas and (in some cases) dust through re-emission and scattering in the infrared, and 4) lowering the typical ISM densities in which SNe occur and greatly increasing their effectiveness.
+This occurs in four ways: 1) heating of diffuse gas and preventing the formation of cold, dense star formation regions, 2) destruction of cold, dense gas around recently formed stars, preventing further star formation, 3) momentum input by direct absorption of UV radiation by gas and (in some cases) dust through re-emission and scattering in the infrared, and 4) lowering the typical ISM densities in which SNe occur and greatly increasing their effectiveness.
 % the relevance / importance of RP from dust in the IR is beyond the scope of this work...
@@
 We include a UV background, tabulated metal line cooling, and a 9 species non-equilibrium chemistry solver using \textsc{Grackle} \citep{GrackleMethod}.
-Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling the \cite{Salpeter1955} IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range.
+Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling a
+%  removed to try and limit citation count
+    %\cite{Salpeter1955} 
+Salpeter IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range.
 For each star, we include feedback from stellar winds, AGB winds, FUV and LW band radiation which drives photoelectric heating and H$_2$ dissociation respectively, HI and HeI ionizing radiation, and core collapse and Type Ia SNe using thermal energy injection.
@@
 \includegraphics[width=0.49\linewidth]{mass}
-\caption{The star formation rate (left) and gas and stellar mass (right) of each of our three simulations over time.
-%mm
-   Time bins with no star formation are left empty. 
-   {\bf legend on first plot has Shortard rather than Shortrad.}}
+\caption{The star formation rate (left) and gas and stellar mass (right) of each of our three simulations over time. Time bins with no star formation are left empty. }
 \label{fig:sfr_mass_evolution}
@@
 Radiation from these stars quickly ionizes and dissipates surrounding dense gas that would otherwise have gone to fuel a significant amount of additional star formation.
-We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints
-%mm
-   from the large number of stars formed. 
+We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints from the large number of stars formed.
 Although radiative transfer is computationally expensive, this run is substantially more expensive than the fiducial and shortrad runs due to the significantly higher star formation rate.
@@
 The driver of these differences is clear in the right hand panel.
-Our fiducial run
-%mm looses a significant amount of 
-    loses a factor of $\sim 2$ more 
-total gas and HI mass (black and blue lines) as compared to the shortrad simulation. 
-%mm by a factor of $\sim$2. 
+Our fiducial run loses a factor of $\sim 2$ more total gas and HI mass (black and blue lines) as compared to the shortrad simulation.
 Clearly, galactic winds and outflows are much more effective in the fiducial case, with full accounting of stellar ionizing radiation feedback, than in the shortrad simulation.
@@
 As shown in Figure~\ref{fig:metal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation.
-Given this, the fiducial simulation has an even higher mass loading factor, since the shortrad simulation has a typically higher SFR.
-The fiducial run is also the only
-%mm simulation 
-   one of the three 
-with any significant outflow beyond the virial radius, though we note the noRT run has not been simulated long enough for gas to have reached the virial radius.
+Because of this difference in SFR, the mass loading factor differences across simulations ($\eta = \dot{M}_{\rm out} / <\rm{SFR}>_{100 \rm{Myr}}$) are more significant.
+While the fiducial run reaches a peak $\eta$ of a few hundred, shortrad is consistently an order of magnitude or more below this, while noRT is even lower.
+The fiducial run is also the only one of the three with any significant outflow beyond the virial radius, though we note the noRT run has not been simulated long enough for gas to have reached the virial radius.
 The outflow in noRT is nearly the same as the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback.
 We conclude that radiation feedback allows SN to be substantially more effective in driving outflows.
-We provide a physical
-%mm intuition 
-   explanation
-for these differences in the following section.
+We provide a physical explanation for these differences in the following section.
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=0.95\linewidth]{metal_retention}\\
-\includegraphics[width=0.95\linewidth]{mass_loading_comparison}
-\caption{{\bf Top:} The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange).
+\includegraphics[width=0.32\linewidth]{metal_retention}
+\includegraphics[width=0.32\linewidth]{mass_outflow_comparison} 
+\includegraphics[width=0.32\linewidth]{mass_loading_comparison}
+\caption{{\bf Left:} The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange).
 As in Figure~\ref{fig:sfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively.
-{\bf Bottom:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed).
-%mm
-   {\bf Could you add a panel explicitly showing mass loading factor as discussed in the text?}
+{\bf Middle:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed).
+{\bf Right:} The mass loading factor, calculated as the outflow rate divided by 100~Myr averaged SFR.
 }
 \label{fig:metal_retention}
-\end{figure}
+\end{figure*}
 
-\textbf{We may have room for one more figure and a little more text to explain it. Possibly a comparison of mass / volume fractions in certain phases? But maybe not necessary....
+\begin{figure*}
+\centering
+\includegraphics[width=0.98\linewidth]{density_temperature_ionization_z_profile}
+\caption{Volume-averaged quantities above / below the disk of each galaxy.
+{\bf Left:} number density.
+{\bf Middle:} Temperature {\bf Right:} Hydrogen ionization fraction.
+These profiles correspond to the same point in time as Figure~\ref{fig:panel2}.
+\textbf{New figure.
+We can decide if we want to keep all panels, or stick with just 1 of the 3 quantities}}
+\label{fig:vertical profiles}
+\end{figure*}
 
-What about vertical profiles of density, temperature, ionization?  These would support your discussion below - MM
+\textbf{New text (AE needs work not done yet): Finally, we quantify these findings in Figure~\ref{fig:vertical profiles}, showing the volume-weighted average number density (left), temperature (middle) and hydrogen ionization fraction (right) as a function of distance above/below the disk of our galaxy at the same time as Figure~\ref{fig:panel2}.
+Over the sampled heights, the gas outside the disk of our fiducial simulation is lower density, higher temperature, and has a higher ionization fraction at all heights.
 }
@@
 \section{Discussion} \label{sec:discussion}
-%mm Again, it is known that 
 Accounting for feedback from stellar radiation plays a significant role in determining the ability for SN energy to couple to the ISM and therefore drive outflows.
-%mm However, the specific 
 We believe this work is novel in examining the
-importance of localized ionization vs.\ ionization from a diffuse radiation field far from a single star
-%mm has not been examined. As shown above, accounting for 
-    Only modeling 
-stellar radiation feedback locally 
-%mm alone 
-is insufficient to describe the long-term evolution of an isolated dwarf galaxy. To explore the cause of this difference we 
-%mm present two panel-plots in Figure~\ref{fig:panel1} and Figure~\ref{fig:panel2} which 
-compare in Figures~\ref{fig:panel1} and~Figure~\ref{fig:panel2} 
-the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
+importance of localized ionization vs.\ ionization from a diffuse radiation field far from a single star.
+Only modeling stellar radiation feedback locally is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
+To explore the cause of this difference we compare in Figures~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
 
@@
 
-Although the ISM properties within the HII region in each case are quite similar between the simulations, the SNe that eventually go off in this region are confined by the neutral gas in the shortrad simulation, but
-%mm are readily ejected
-   readily escape through the lower density ionized gas
-into the galaxy halo in our fiducial case. As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe,
-%mm
-   as shown in  Figure~\ref{fig:panel2}, which shows each simulation 40~Myr after the 
-   formation of the first stars. 
+Although the ISM properties within the HII region in each case are quite similar between the simulations, the SNe that eventually go off in this region are confined by the neutral gas in the shortrad simulation, but readily escape through the lower density ionized gas into the galaxy halo in our fiducial case.
+As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe, as shown in  Figure~\ref{fig:panel2}, which shows each simulation 40~Myr after the formation of the first stars.
 In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas.
@@
 In the noRT case, an outflow does eventually develop, but it takes the factor of five increase in SFR, and corresponding increase in supernova rate, for SNe to finally break out from the neutral gas surrounding the galaxy.
-%mm These differences are shown more clearly in Figure~\ref{fig:panel2}, which shows each simulation 40~Myr after the formation of the first stars.
+
+\textbf{New text: As shown in Figure~\ref{fig:metal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy.
+The winds in our fiducial simulation carry nearly all of the metals produced out from the disk of our galaxy.
+This is the only run in agreement with observations of Local Group dwarf galaxies, both dSph's \citep{Kirby2011} and the gaseous, star forming Local Group dwarf galaxy Leo P \citep{McQuinn2015}, with metal ejection fractions of up to 95\%.
+This is in stark contrast to the $\sim$30\% retention fraction in our shortrad simulation.
+This would also influence the chemical enrichment of neighboring galaxies, given the significant differences in metal ejection past the virial radius between these two runs.
+Clearly the effects of feedback on observable chemical properties of galaxies is a key descriminator among models.}
 
@@
 
-We 
-%mm also 
-demonstrate
-%mm
-   for the first time 
-that simple prescriptions 
-%mm which treat stellar radiation feedback locally do not fully reproduce the same
-%evolution as our fiducial model. 
-    of local stellar radiation feedback fail to reproduce the evolution of our fiducial 
-    model.
+We demonstrate for the first time that simple prescriptions of local stellar radiation feedback fail to reproduce the evolution of our fiducial model.
 Our simulation with radiation localized to 20~pc around each star particle does effectively regulate star formation on short time scales, predominately by quickly destroying cold, dense gas around young, hot stars.
@@
 Our simulation with localized radiation feedback retains a significantly higher fraction of metals than expected observationally for low mass dwarf galaxies.
-%mm
-    {\bf [This point needs to be supported by a paragraph with references in the discussion.]}
 
@@
 
-\bibliography{msbib} % if your bibtex file is called example.bib
+\bibliography{msbib}
 

### 2018-07-26 ms.tex
Update on Overleaf.

@@
 We include a UV background, tabulated metal line cooling, and a 9 species non-equilibrium chemistry solver using \textsc{Grackle} \citep{GrackleMethod}.
-Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling a
-%  removed to try and limit citation count
-    %\cite{Salpeter1955} 
-Salpeter IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range.
+Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling a \cite{Salpeter1955} Salpeter IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range.
 For each star, we include feedback from stellar winds, AGB winds, FUV and LW band radiation which drives photoelectric heating and H$_2$ dissociation respectively, HI and HeI ionizing radiation, and core collapse and Type Ia SNe using thermal energy injection.
@@
 
+\section{Discussion} \label{sec:discussion}
+Accounting for feedback from stellar radiation plays a significant role in determining the ability for SN energy to couple to the ISM and therefore drive outflows.
+We believe this work is novel in examining the
+importance of localized ionization vs.\ ionization from a diffuse radiation field far from a single star.
+Only modeling stellar radiation feedback locally is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
+To explore the cause of this difference we compare in Figures~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.99\linewidth]{DD0136_fiducial_shortrad_nort}
+\caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.But for now: TOP: Fiducial.
+MIDDLE: noRT.
+BOTTOM: shortrad} Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run.}
+\label{fig:panel1}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.99\linewidth]{DD0160_fiducial_shortrad_nort}
+\caption{Same as Figure~\ref{fig:panel1}, but at 40~Myr.}
+\label{fig:panel2}
+\end{figure*}
+
+Figure~\ref{fig:panel1}, at 17~Myr, compares each simulation just after the first few SNe.
+Already there are significant differences between the runs.
+Gas outside the galaxy is warm ($\sim$~10$^{4}$~K) and ionized up to $\sim$500~pc above/below the plane of the disk in our fiducial run.
+This same gas is cold ($<10^4$~K) and neutral in both other runs.
+The contrast between the effect of ionizing radiation in the fiducial and shortrad runs is seen most clearly in the ionized region in-plane and to the right of center.
+This region contains massive stars that are capable of generating enough ionizing radiation to carve a channel out to the halo of our fiducial simulation; this does not occur in the shortrad case.
+Instead, the HII region is confined by surrounding cold, neutral gas.
+
+Although the ISM properties within the HII region in each case are quite similar between the simulations, the SNe that eventually go off in this region are confined by the neutral gas in the shortrad simulation, but readily escape through the lower density ionized gas into the galaxy halo in our fiducial case.
+As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe, as shown in  Figure~\ref{fig:panel2}, which shows each simulation 40~Myr after the formation of the first stars.
+In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas.
+Though they make a significant local impact on the ISM, they are unable to drive significant mass loss from the galaxy.
+In the noRT case, an outflow does eventually develop, but it takes the factor of five increase in SFR, and corresponding increase in supernova rate, for SNe to finally break out from the neutral gas surrounding the galaxy.
+
 \begin{figure*}
@@
 
-\textbf{New text (AE needs work not done yet): Finally, we quantify these findings in Figure~\ref{fig:vertical profiles}, showing the volume-weighted average number density (left), temperature (middle) and hydrogen ionization fraction (right) as a function of distance above/below the disk of our galaxy at the same time as Figure~\ref{fig:panel2}.
-Over the sampled heights, the gas outside the disk of our fiducial simulation is lower density, higher temperature, and has a higher ionization fraction at all heights.
-}
-
-\section{Discussion} \label{sec:discussion}
-Accounting for feedback from stellar radiation plays a significant role in determining the ability for SN energy to couple to the ISM and therefore drive outflows.
-We believe this work is novel in examining the
-importance of localized ionization vs.\ ionization from a diffuse radiation field far from a single star.
-Only modeling stellar radiation feedback locally is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
-To explore the cause of this difference we compare in Figures~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
-
-Figure~\ref{fig:panel1}, at 17~Myr, compares each simulation just after the first few SNe.
-Already there are significant differences between the runs.
-Gas outside the galaxy is warm ($\sim$~10$^{4}$~K) and ionized up to $\sim$500~pc above/below the plane of the disk in our fiducial run.
-This same gas is cold ($<10^4$~K) and neutral in both other runs.
-The contrast between the effect of ionizing radiation in the fiducial and shortrad runs is seen most clearly in the ionized region in-plane and to the right of center.
-This region contains massive stars that are capable of generating enough ionizing radiation to carve a channel out to the halo of our fiducial simulation; this does not occur in the shortrad case.
-Instead, the HII region is confined by surrounding cold, neutral gas.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.99\linewidth]{DD0136_fiducial_shortrad_nort}
-\caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.But for now: TOP: Fiducial.
-MIDDLE: noRT.
-BOTTOM: shortrad} Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run.}
-\label{fig:panel1}
-\end{figure*}
-
-Although the ISM properties within the HII region in each case are quite similar between the simulations, the SNe that eventually go off in this region are confined by the neutral gas in the shortrad simulation, but readily escape through the lower density ionized gas into the galaxy halo in our fiducial case.
-As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe, as shown in  Figure~\ref{fig:panel2}, which shows each simulation 40~Myr after the formation of the first stars.
-In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas.
-Though they make a significant local impact on the ISM, they are unable to drive significant mass loss from the galaxy.
-In the noRT case, an outflow does eventually develop, but it takes the factor of five increase in SFR, and corresponding increase in supernova rate, for SNe to finally break out from the neutral gas surrounding the galaxy.
+\textbf{New text: Finally, we quantify these findings in Figure~\ref{fig:vertical profiles}, showing the volume-weighted average number density (left), temperature (middle) and hydrogen ionization fraction (right) as a function of distance above/below the disk of our galaxy at the same time as Figure~\ref{fig:panel2}.
+The gas outside the disk of our fiducial simulation is lower density, higher temperature, and has a higher ionization fraction at all points above the disk.
+The shortrad simulation, which lacks both the enhanced SNR of the noRT run and the long-range ionizing radiation effects, of the fiducial simulation, maintains a denser, cooler, more neutral shell of gas above the disk, preventing significant outflows.}
 
@@
 This would also influence the chemical enrichment of neighboring galaxies, given the significant differences in metal ejection past the virial radius between these two runs.
-Clearly the effects of feedback on observable chemical properties of galaxies is a key descriminator among models.}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.99\linewidth]{DD0160_fiducial_shortrad_nort}
-\caption{Same as Figure~\ref{fig:panel1}, but at 40~Myr.}
-\label{fig:panel2}
-\end{figure*}
+Clearly the effects of feedback on observable chemical properties of galaxies is a key discriminator among models.}
 

### 2018-07-26 ms.tex
revisions

@@
 \affil{Columbia University}
-\affil{American Museum of Natural History (AMNH)}
+\affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}
 
@@
 \author{Mordecai-Mark Mac Low}
-\affiliation{American Museum of Natural History (AMNH)}
+%mm [I've been asked to use my Columbia affiliation when working with CU students]
+\affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}
+\affiliation{Columbia University}
+
 \nocollaboration
@@
 As shown in Figure~\ref{fig:metal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation.
-Because of this difference in SFR, the mass loading factor differences across simulations ($\eta = \dot{M}_{\rm out} / <\rm{SFR}>_{100 \rm{Myr}}$) are more significant.
+Because of this difference in SFR,
+%mm [rewrote to display equation]
+the differences across simulations are more significant for our computed mass loading factor 
+\begin{equation}
+    \eta = \dot{M}_{\rm out} / <\rm{SFR}>_{100 \rm{Myr}}
+\end{equation}. The brackets indicate time averaging over 100~Myr.
+%
 While the fiducial run reaches a peak $\eta$ of a few hundred, shortrad is consistently an order of magnitude or more below this, while noRT is even lower.
+
+%mm [ended the paragraph to leave the previous important sentence in the place of emphasis at the end of the paragraph.]
 The fiducial run is also the only one of the three with any significant outflow beyond the virial radius, though we note the noRT run has not been simulated long enough for gas to have reached the virial radius.
-The outflow in noRT is nearly the same as the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback.
-We conclude that radiation feedback allows SN to be substantially more effective in driving outflows.
-We provide a physical explanation for these differences in the following section.
+The outflow in noRT is
+%mm nearly the same as 
+   only a factor of a few lower than 
+the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback, 
+%mm 
+    so it implies a far lower mass loading factor. 
+We conclude that radiation feedback allows SNe to be substantially more effective in driving outflows. 
+%mm We provide a physical explanation for these differences in the following section.
 
@@
 {\bf Middle:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed).
-{\bf Right:} The mass loading factor, calculated as the outflow rate divided by 100~Myr averaged SFR.
-}
+{\bf Right:} The mass loading factor $\eta$ calculated as the outflow rate divided by the SFR averaged over 100~Myr.
+%mm
+   Inclusion of diffuse ionization makes an order of magnitude difference in $\eta$ in 
+   this case. }
 \label{fig:metal_retention}

### 2018-07-26 ms.tex
brief updates

--- 2018-07-25 ms.tex
@@
 Historically, simulations of galaxy formation have suffered from the ``overcooling'' problem, whereby the action of self-gravity and radiative cooling alone produces galaxies with far too many stars.
-This problem has been addressed by employing various models of stellar feedback physics which are capable of generating self-regulating star formation in galaxies.
-Recently, it has become clear that the simplest models for stellar feedback, which account for supernovae (SNe) alone, are insufficient \citep{Smith2018} to fully regulate star formation and set galaxy properties consistent with observations (see \cite{NaabOstriker2017} for a recent review).
+This problem has been addressed by employing various models of strong stellar feedback physics which are capable of generating self-regulating star formation in galaxies.
+\textbf{Energy injection from supernovae (SNe) has historically been used as the sole form of feedback.
+However, this is generally done heuristically as many simulations lack the ability to resolve the Sedov phase of individual SNe.
+But even with this strong feedback, recent work has argued for the need for pre-SN feedback, from stellar winds and/or stellar radiation, typically modelled simply as additional energy injection around newly formed stars (citations).
+Works that are capable of fulling resolving individual SN \citep{Hu2018,Smith2018} find that XXXXX Modelling these processes in detail, however, is challenging.
+
+%Recently, it has become clear that the simplest models for stellar feedback, which account for supernovae (SNe) alone, are insufficient \citep{Smith2018} to fully regulate star formation and set galaxy properties consistent with observations (see \cite{NaabOstriker2017} for a recent review).
 Processes, such as stellar radiation, cosmic rays, or AGN, are often employed as additional sources of feedback.
@@
 Although some of these approximate methods account for long-range effects of diffuse radiation \citep{HQM2012,Hopkins2018} most cases treat local radiation {\it only}, confined to energy or momentum injection in a limited physical region around a star particle.
-Although the approximate radiation feedback models are capable of driving significant galactic outflows, it is unclear if they capture the full effects of stellar ionizing radiation.
+This is in part because the local destruction of dense clumps of gas around newly formed stars is commonly believed to be the dominant impact of stellar radiation feedback.
+The role of long-range stellar radiation, once ionizing photons break out of star forming regions, is not well characterized.
+Indeed it remains to be seen if modelling only the short-range effects of stellar radiation feedback is sufficient.
+
+%Although the approximate radiation feedback models are capable of driving significant galactic outflows, it is unclear if they capture the full effects of stellar ionizing radiation. 
 %The 
@@
 
-In this work we present a comparison of three simulations of the evolution of an isolated, low mass dwarf galaxy that account for detailed stellar feedback.
-Our fiducial model uses an adaptive ray-tracing radiative transfer method to follow stellar ionizing radiation.
-We test its effectiveness in regulating star formation and driving galactic winds by comparison to a simulation without ionizing radiation and a simulation with only localized radiation around each star.
-We discuss our methods in Section~\ref{sec:methods} and present our results in Section~\ref{sec:results}.
+In this work we use a detailed model for stellar feedback presented in \citep{Emerick2018} to study the role of radiation feedback in dwarf galaxy evolution.
+For the first time in a galaxy-scale simulation, we resolve the HII regions of single stars using an adaptive ray tracing radiative transfer method to follow the ionizing radaition from particles that represent individual stars.
+We focus on adressing two questions: 1) how important is radiation feedback in regulating star formation, and 2) are the long-range effects of radiation feedback important, or is the local destruction of dense gas the dominant effect.
+To investigate this we compare three simulations of the evolution of an isolated, low mass dwarf galaxy.
+Our fiducial model, containing full stellar radiation feedback, is compared against a run without ionziing radiation feedback, and a run with ionizing feedback limited to the local region around a given star.
+We dicuss our methods in Section~\ref{sec:methods} and present our results ion Section~\ref{sec:results}.
 
@@
 We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints from the large number of stars formed.
-Although radiative transfer is computationally expensive, this run is substantially more expensive than the fiducial and shortrad runs due to the significantly higher star formation rate.
+Although radiative transfer is computationally expensive, this run is substantially more expensive than the fiducial and shortrad runs \textbf{due to a lower typical timestep from more shock-heated SN gas and additional work computing the stellar wind and optically thin radiation effects from more star particles}.
 

### 2018-07-26 ms.tex

@@
 {\bf Middle:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed).
-{\bf Right:} The mass loading factor, calculated as the outflow rate divided by 100~Myr averaged SFR.
-}
+{\bf Right:} The mass loading factor $\eta$ calculated as the outflow rate divided by the SFR averaged over 100~Myr.
+%mm
+   Inclusion of diffuse ionization makes an order of magnitude difference in $\eta$ in 
+   this case. }
 \label{fig:metal_retention}
 \end{figure*}
+
+\section{Discussion} \label{sec:discussion}
+Accounting for feedback from stellar radiation plays a significant role in determining the ability for SN energy to couple to the ISM and therefore drive outflows.
+We believe this work is novel in examining the
+importance of localized ionization vs.\ ionization from a diffuse radiation field far from a single star.
+Only modeling stellar radiation feedback locally is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
+To explore the cause of this difference we compare in Figures~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.99\linewidth]{DD0136_fiducial_shortrad_nort}
+\caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.But for now: TOP: Fiducial.
+MIDDLE: noRT.
+BOTTOM: shortrad} Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run.}
+\label{fig:panel1}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.99\linewidth]{DD0160_fiducial_shortrad_nort}
+\caption{Same as Figure~\ref{fig:panel1}, but at 40~Myr.}
+\label{fig:panel2}
+\end{figure*}
+
+Figure~\ref{fig:panel1}, at 17~Myr, compares each simulation just after the first few SNe.
+Already there are significant differences between the runs.
+Gas outside the galaxy is warm ($\sim$~10$^{4}$~K) and ionized up to $\sim$500~pc above/below the plane of the disk in our fiducial run.
+This same gas is cold ($<10^4$~K) and neutral in both other runs.
+The contrast between the effect of ionizing radiation in the fiducial and shortrad runs is seen most clearly in the ionized region in-plane and to the right of center.
+This region contains massive stars that are capable of generating enough ionizing radiation to carve a channel out to the halo of our fiducial simulation; this does not occur in the shortrad case.
+Instead, the HII region is confined by surrounding cold, neutral gas.
+
+Although the ISM properties within the HII region in each case are quite similar between the simulations, the SNe that eventually go off in this region are confined by the neutral gas in the shortrad simulation, but readily escape through the lower density ionized gas into the galaxy halo in our fiducial case.
+As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe, as shown in  Figure~\ref{fig:panel2}, which shows each simulation 40~Myr after the formation of the first stars.
+In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas.
+Though they make a significant local impact on the ISM, they are unable to drive significant mass loss from the galaxy.
+In the noRT case, an outflow does eventually develop, but it takes the factor of five increase in SFR, and corresponding increase in supernova rate, for SNe to finally break out from the neutral gas surrounding the galaxy.
 

### 2018-07-26 ms.tex

@@
 Historically, simulations of galaxy formation have suffered from the ``overcooling'' problem, whereby the action of self-gravity and radiative cooling alone produces galaxies with far too many stars.
-This problem has been addressed by employing various models of strong stellar feedback physics which are capable of generating self-regulating star formation in galaxies.
+This problem has been addressed by employing various models of strong stellar feedback physics which are capable of generating self-regulating star formation in galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews).
 \textbf{Energy injection from supernovae (SNe) has historically been used as the sole form of feedback.
 However, this is generally done heuristically as many simulations lack the ability to resolve the Sedov phase of individual SNe.
-But even with this strong feedback, recent work has argued for the need for pre-SN feedback, from stellar winds and/or stellar radiation, typically modelled simply as additional energy injection around newly formed stars (citations).
-Works that are capable of fulling resolving individual SN \citep{Hu2018,Smith2018} find that XXXXX Modelling these processes in detail, however, is challenging.
-
-%Recently, it has become clear that the simplest models for stellar feedback, which account for supernovae (SNe) alone, are insufficient \citep{Smith2018} to fully regulate star formation and set galaxy properties consistent with observations (see \cite{NaabOstriker2017} for a recent review).
-Processes, such as stellar radiation, cosmic rays, or AGN, are often employed as additional sources of feedback.
-Modeling these processes in detail, however, is challenging.
-As a result, the relative importance of these additional physics is still uncertain.
+But even with this strong feedback, recent work has argued for the need for pre-SN feedback, from stellar winds and/or stellar radiation \citep[e.g.][]{Hu2016,Hopkins2018}, though this is typically modeled simply as additional energy injection around newly formed stars.
+The need for additional feedback is confirmed by simulations that are capable of fulling resolving individual SN \citep[e.g.]{Hu2017,Peters2017}.
+However, modelling these processes in detail is challenging, and their competing effects on galactic evolution is poorly constrained.}
 
@@
 If the radiation couples effectively to the interstellar medium (ISM), it can be a substantial source of additional feedback.
-%Lower mass stars (size range) primarily drive photoelectric heating (cite) and H$_2$ dissociation through radiation in the far ultraviolet and Lyman-Werner bands, while more massive stars (range) emit significant amounts of ionizing radiation.
 Simulations including stellar radiation feedback followed through radiative transfer or radiation-hydrodynamics schemes have found it to be effective in regulating star formation and driving galactic winds \citep[e.g.][]{WiseAbel2012,Kim2013a,Sales2014,Oshea2015,Rosdahl2015,Ocvirk2015,Pawlik2015,Peters2017}.
@@
 
-In this work we use a detailed model for stellar feedback presented in \citep{Emerick2018} to study the role of radiation feedback in dwarf galaxy evolution.
-For the first time in a galaxy-scale simulation, we resolve the HII regions of single stars using an adaptive ray tracing radiative transfer method to follow the ionizing radaition from particles that represent individual stars.
-We focus on adressing two questions: 1) how important is radiation feedback in regulating star formation, and 2) are the long-range effects of radiation feedback important, or is the local destruction of dense gas the dominant effect.
+In this work we use a detailed model for stellar feedback presented in \cite{Emerick2018} to study the role of radiation feedback in dwarf galaxy evolution.
+For the first time in a galaxy-scale simulation, we resolve the HII regions of single stars using an adaptive ray tracing radiative transfer method to follow the ionizing radiation from particles that represent individual stars.
+We focus on addressing two questions: 1) how important is radiation feedback in regulating star formation, and 2) are the long-range effects of radiation feedback important, or is the local destruction of dense gas the dominant effect.
 To investigate this we compare three simulations of the evolution of an isolated, low mass dwarf galaxy.
-Our fiducial model, containing full stellar radiation feedback, is compared against a run without ionziing radiation feedback, and a run with ionizing feedback limited to the local region around a given star.
-We dicuss our methods in Section~\ref{sec:methods} and present our results ion Section~\ref{sec:results}.
+Our fiducial model, containing full stellar radiation feedback, is compared against a run without ionizing radiation feedback, and a run with ionizing feedback limited to the local region around a given star.
+We discuss our methods in Section~\ref{sec:methods} and present our results ion Section~\ref{sec:results}.
 
@@
 \includegraphics[width=0.49\linewidth]{mass}
-\caption{The star formation rate (left) and gas and stellar mass (right) of each of our three simulations over time. Time bins with no star formation are left empty. }
+\caption{The star formation rate (left) and gas and stellar mass (right) of each of our three simulations over time. Time bins with no star formation are left empty.}
 \label{fig:sfr_mass_evolution}
@@
 We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints from the large number of stars formed.
-Although radiative transfer is computationally expensive, this run is substantially more expensive than the fiducial and shortrad runs \textbf{due to a lower typical timestep from more shock-heated SN gas and additional work computing the stellar wind and optically thin radiation effects from more star particles}.
+Although radiative transfer itself is computationally expensive, this run is substantially more costly \textbf{due to a lower typical timestep and increased cost in computing the optically thin radiation effects (photoelectric effect and LW dissociation).}
 
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.98\linewidth]{density_temperature_ionization_z_profile}
-\caption{Volume-averaged quantities above / below the disk of each galaxy.
+%\begin{figure*}
+%\centering
+%\includegraphics[width=0.98\linewidth]{density_temperature_ionization_z_profile}
+%\caption{Volume-averaged quantities above / below the disk of each galaxy.
 {\bf Left:} number density.
@@
 We can decide if we want to keep all panels, or stick with just 1 of the 3 quantities}}
-\label{fig:vertical profiles}
-\end{figure*}
+%\label{fig:vertical profiles}
+%\end{figure*}
 
-\textbf{New text: Finally, we quantify these findings in Figure~\ref{fig:vertical profiles}, showing the volume-weighted average number density (left), temperature (middle) and hydrogen ionization fraction (right) as a function of distance above/below the disk of our galaxy at the same time as Figure~\ref{fig:panel2}.
+%\textbf{Finally, we quantify these findings in Figure~\ref{fig:vertical profiles}, showing the volume-weighted average number density (left), temperature (middle) and hydrogen ionization fraction (right) as a function of distance above/below the disk of our galaxy at the same time as Figure~\ref{fig:panel2}.
 The gas outside the disk of our fiducial simulation is lower density, higher temperature, and has a higher ionization fraction at all points above the disk.
@@
 
-\textbf{New text: As shown in Figure~\ref{fig:metal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy.
+\textbf{As shown in Figure~\ref{fig:metal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy.
 The winds in our fiducial simulation carry nearly all of the metals produced out from the disk of our galaxy.

### 2018-07-26 ms.tex
Update on Overleaf.

@@
 
+% Letter word count:
+%    Text (including captions) : 3500
+%    Abstract                  : 500
+%    # Figures                 : 5
+%       max panels per fig     : 9
+%    # references              : 50
+
 \begin{abstract}
-\textit{Will complete at end}
-%{\bf Ignore: Ionizing radiation from recently formed massive stars is important in destroying cold, dense gas around new regions of star formation that would otherwise continue to form stars.
-Applying a local prescription for this pre-supernova feedback can be sufficient in matching star formation rates in a simulation with full radiative transfer on short timescales.
-However, the long-range effects of ionizing radiation are important in producing a volume-filling diffuse, warm-ionized medium in the ISM and in the disk-halo interface.
-This is essential for allowing supernovae to drive significant gas outflows that travel throughout and beyond the virial radius of the galaxy.
-A simulation with local radiation feedback only is unable to drive significant outflows as the supernovae are trapped well within the inner halo by higher density cold and warm neutral gas.}
+%
+%
+% NOTE: Overleaf includes abstract words in word count in text... subtract
+%       this from the total.
+%
+%
+Effective stellar feedback is used in models of galaxy formation to regulate star formation and to drive realistic galaxy evolution.
+Energy injection from supernovae is used as the dominant form of stellar feedback, albeit often in some form of sub-grid recipe.
+However, it has been recently suggested that pre-SN feedback, from either stellar winds or stellar radiation, is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium.
+As following stellar winds and ionizing radiation is computationally challenging, many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars.
+In this work we use high resolution simulations of an isolated dwarf galaxy with detailed stellar feedback physics tracked on a star-by-star basis.
+By following stellar ionizing radiation with an adaptive ray-tracing radiative transfer method, we test the importance of stellar ionizing radiation in regulating star formation and driving outflows in this galaxy.
+We find that including ionizing radiation reduces the star formation rate by over a factor of 5, and is a necessary component to drive outflows in our galaxy.
+In addition, we find that a localized approximation for radiation feedback is sufficient to reduce the star formation rate but, importantly does not drive significant outflows.
+Short and long range radiation effects are both important in driving the evolution of our modeled galaxy.
 \end{abstract}

### 2018-07-26 ms.tex

@@
 Energy injection from supernovae is used as the dominant form of stellar feedback, albeit often in some form of sub-grid recipe.
-However, it has been recently suggested that pre-SN feedback, from either stellar winds or stellar radiation, is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium.
-As following stellar winds and ionizing radiation is computationally challenging, many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars.
+However, it has been recently suggested that pre-SN feedback, from either stellar winds or stellar radiation, is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM).
+As following stellar winds and ionizing radiation is computationally challenging, many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation.
 In this work we use high resolution simulations of an isolated dwarf galaxy with detailed stellar feedback physics tracked on a star-by-star basis.
 By following stellar ionizing radiation with an adaptive ray-tracing radiative transfer method, we test the importance of stellar ionizing radiation in regulating star formation and driving outflows in this galaxy.
-We find that including ionizing radiation reduces the star formation rate by over a factor of 5, and is a necessary component to drive outflows in our galaxy.
-In addition, we find that a localized approximation for radiation feedback is sufficient to reduce the star formation rate but, importantly does not drive significant outflows.
+We find that including ionizing radiation reduces the star formation rate by over a factor of 5, and is necessary in creating the ISM conditions needed for supernovae to drive significant outflows.
+In addition, we find that a localized approximation for radiation feedback is sufficient to regulate the star formation rate on short time scales, but is unable to drive the same outflows as in our fiducial model.
 Short and long range radiation effects are both important in driving the evolution of our modeled galaxy.

### 2018-07-26 ms.tex
Update on Overleaf.

@@
 Radiation from these stars quickly ionizes and dissipates surrounding dense gas that would otherwise have gone to fuel a significant amount of additional star formation.
-We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints from the large number of stars formed.
-Although radiative transfer itself is computationally expensive, this run is substantially more costly \textbf{due to a lower typical timestep and increased cost in computing the optically thin radiation effects (photoelectric effect and LW dissociation).}
+This is confirmed in Figure~\ref{fig:sf gas}, which shows the gas mass in each simulation above the SF density threshold of $n = 200$~cm$^{-3}$ during the first 100~Myr.
+While our fiducial and shortrad simulations remain roughly the same here, the noRT run, at its peak, has an order of magnitude more cold, dense gas.
+\footnote{We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints from the large number of stars formed.
+Although radiative transfer itself is computationally expensive, this run is substantially more costly \textbf{due to a lower typical timestep and increased cost in computing the optically thin radiation effects (photoelectric effect and LW dissociation).}}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.99\linewidth]{mass_density_cut}
+\caption{The total gas mass at $n > 200$~cm$^{-3}$, our star formation density threshold.}
+\label{fig:panel1}
+\end{figure}
 

### 2018-07-27 ms.tex

@@
 \includegraphics[width=0.99\linewidth]{DD0136_fiducial_shortrad_nort}
-\caption{\textbf{In the final version of this figure I will add labels for each row marking the simulation, and a line giving the scale of each figure.But for now: TOP: Fiducial.
-MIDDLE: noRT.
-BOTTOM: shortrad} Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run.}
+\caption{Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run.
+Each panel is }
 \label{fig:panel1}

### 2018-07-27 ms.tex
Update on Overleaf.

@@
 Effective stellar feedback is used in models of galaxy formation to regulate star formation and to drive realistic galaxy evolution.
-Energy injection from supernovae is used as the dominant form of stellar feedback, albeit often in some form of sub-grid recipe.
+Models typically include energy injection from supernovae as the dominant form of stellar feedback, though often in some form of sub-grid recipe.
 However, it has been recently suggested that pre-SN feedback, from either stellar winds or stellar radiation, is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM).
 As following stellar winds and ionizing radiation is computationally challenging, many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation.
-In this work we use high resolution simulations of an isolated dwarf galaxy with detailed stellar feedback physics tracked on a star-by-star basis.
-By following stellar ionizing radiation with an adaptive ray-tracing radiative transfer method, we test the importance of stellar ionizing radiation in regulating star formation and driving outflows in this galaxy.
+In this work we use high resolution simulations (1.8~pc) of an isolated dwarf galaxy with detailed stellar feedback tracked on a star-by-star basis.
+By following stellar ionizing radiation with an adaptive ray-tracing radiative transfer method, we test its importance in regulating star formation and driving outflows in this galaxy.
 We find that including ionizing radiation reduces the star formation rate by over a factor of 5, and is necessary in creating the ISM conditions needed for supernovae to drive significant outflows.
-In addition, we find that a localized approximation for radiation feedback is sufficient to regulate the star formation rate on short time scales, but is unable to drive the same outflows as in our fiducial model.
+In addition, we find that a localized approximation for radiation feedback is sufficient to regulate the star formation rate on short timescales, but is unable to drive the same outflows as in our fiducial model.
 Short and long range radiation effects are both important in driving the evolution of our modeled galaxy.
@@
 But even with this strong feedback, recent work has argued for the need for pre-SN feedback, from stellar winds and/or stellar radiation \citep[e.g.][]{Hu2016,Hopkins2018}, though this is typically modeled simply as additional energy injection around newly formed stars.
-The need for additional feedback is confirmed by simulations that are capable of fulling resolving individual SN \citep[e.g.]{Hu2017,Peters2017}.
-However, modelling these processes in detail is challenging, and their competing effects on galactic evolution is poorly constrained.}
+The need for additional feedback is confirmed by simulations that are capable of fulling resolving individual SN \citep[e.g.][]{Hu2017,Peters2017}.
+However, modeling these processes in detail is challenging, and their competing effects on galactic evolution are poorly constrained.}
 
 Radiation from massive stars dominates the total feedback energy output of a stellar population \citep[e.g.][]{Abbott1982,Leitherer1999,Agertz2013}, surpassing the energy ejection of supernova ($\sim 10^{51}$~erg) by two orders of magnitude.
-If the radiation couples effectively to the interstellar medium (ISM), it can be a substantial source of additional feedback.
+If radiation couples effectively to the interstellar medium (ISM), it can be a substantial source of additional feedback.
 Simulations including stellar radiation feedback followed through radiative transfer or radiation-hydrodynamics schemes have found it to be effective in regulating star formation and driving galactic winds \citep[e.g.][]{WiseAbel2012,Kim2013a,Sales2014,Oshea2015,Rosdahl2015,Ocvirk2015,Pawlik2015,Peters2017}.
@@
 Many works use a Str{\"o}mgren approximation whereby the particles / cells within the Str{\"o}mgren radius around a radiating star are heated and kept ionized, with additional approximations made to account for overlapping ionized regions \citep[e.g.][]{HQM2011,Hu2016,Hu2017}.
-Other works employ some form of energy or momentum injection localized to the region immediately around a star particle \citep[e.g.][(\textit{need more})]{Agertz2013,Roskar2014,Ceverino2014,Forbes2016}.
+Other works employ some form of energy or momentum injection localized to the region immediately around a star particle \citep[e.g.][]{Agertz2013,Roskar2014,Ceverino2014,Forbes2016}.
 Although some of these approximate methods account for long-range effects of diffuse radiation \citep{HQM2012,Hopkins2018} most cases treat local radiation {\it only}, confined to energy or momentum injection in a limited physical region around a star particle.
-This is in part because the local destruction of dense clumps of gas around newly formed stars is commonly believed to be the dominant impact of stellar radiation feedback.
+\textbf{This is done both because the local destruction of dense clumps of gas around newly formed stars is commonly believed to be the dominant impact of stellar radiation feedback and because it is computationally less expensive to implement.
 The role of long-range stellar radiation, once ionizing photons break out of star forming regions, is not well characterized.
-Indeed it remains to be seen if modelling only the short-range effects of stellar radiation feedback is sufficient.
+Indeed it remains to be seen if modeling only the short-range effects of stellar radiation feedback is sufficient.}
 
@@
 
-In this work we use a detailed model for stellar feedback presented in \cite{Emerick2018} to study the role of radiation feedback in dwarf galaxy evolution.
-For the first time in a galaxy-scale simulation, we resolve the HII regions of single stars using an adaptive ray tracing radiative transfer method to follow the ionizing radiation from particles that represent individual stars.
-We focus on addressing two questions: 1) how important is radiation feedback in regulating star formation, and 2) are the long-range effects of radiation feedback important, or is the local destruction of dense gas the dominant effect.
-To investigate this we compare three simulations of the evolution of an isolated, low mass dwarf galaxy.
+In this work we use a detailed model for stellar feedback presented in \cite{Emerick2018} (hereafter Paper I) to study the role of radiation feedback in dwarf galaxy evolution.
+For the first time in a galaxy-scale simulation, we resolve individual HII using an adaptive ray tracing radiative transfer method to follow the ionizing radiation from particles that represent individual stars.
+We focus on addressing two questions: 1) what role does radiation feedback play in regulating star formation, and 2) are the long-range effects of radiation feedback important, or is the local destruction of dense gas the dominant effect.
+
+To investigate these questions, we compare three simulations of the evolution of an isolated, low mass dwarf galaxy.
 Our fiducial model, containing full stellar radiation feedback, is compared against a run without ionizing radiation feedback, and a run with ionizing feedback limited to the local region around a given star.
@@
 We use the adaptive mesh refinement hydrodynamics code \textsc{Enzo} \citep{Enzo2014} to evolve an idealized, isolated low mass dwarf galaxy.
-The galaxy is initialized as a smooth exponential disk set in hydrostatic equillibrium with a static dark matter potential \citep{Burkert1995} with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, on a grid with a maximum physical resolution of 1.8~pc.
+The galaxy is initialized as a smooth exponential disk set in hydrostatic equilibrium with a static dark matter potential \citep{Burkert1995} with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, on a grid with a maximum physical resolution of 1.8~pc.
 We do not model an initial stellar population, but do include random driving from supernovae as an initial source of feedback up until the first explicit star formation in our model.
@@
 We include a UV background, tabulated metal line cooling, and a 9 species non-equilibrium chemistry solver using \textsc{Grackle} \citep{GrackleMethod}.
-Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling a \cite{Salpeter1955} Salpeter IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range.
+Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling a \cite{Salpeter1955} IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range.
 For each star, we include feedback from stellar winds, AGB winds, FUV and LW band radiation which drives photoelectric heating and H$_2$ dissociation respectively, HI and HeI ionizing radiation, and core collapse and Type Ia SNe using thermal energy injection.
@@
 Stellar lifetimes, surface gravity, effective temperature, and radii are set by the initial stellar mass and metallicity through interpolation over the PARSEC \citep{Bressan2012} zero age main sequence values.
-These values for surface gravity, effective temperature, and radii are used to set the FUV, LW, and ionizing photon fluxes from each star through interpolation on the OSTAR2002 \citep{LanzHubeny2003} grid.
-We only follow the radiation from stars with masses above 8~M$_{\odot}$.
+Stellar surface gravity, effective temperature, and radii are used to set the FUV, LW, and ionizing photon fluxes from each star through interpolation on the OSTAR2002 \citep{LanzHubeny2003} grid.
+We only model the radiation from stars with masses above 8~M$_{\odot}$.
 %tellar wind and supernovae mass loss are determined with the  NuGrid yield tables for $M_* < 25$~M$_{\odot}$ and from Slemer et. al. (in prep) for $M_* > 25$~M$_{\odot}$.
@@
 Although this is still more accurate than an approximate method, this is meant to function similarly to methods that include only the local effects of stellar radiation feedback.
-Each of our three simulations is identical up until the formation of the first star particles.
-At this point, the differing feedback physics causes each to diverge.
-We note that the stars from the very first star formation event in each run (21 star particles with a total mass of 114 M$_{\odot}$) are the same in each run.
-Of these, one particle emits ionizing radiation ($M_* > 8 $~M$_{\odot}$).
+Each of our three simulations is identical up until the formation of the first star particles.\footnote{We note that the stars from the very first star formation event in each run (21 star particles with a total mass of 114 M$_{\odot}$) are the same.
+Of these, one particle emits ionizing radiation ($M_* > 8 $~M$_{\odot}$).}
 
@@
 While our fiducial and shortrad simulations remain roughly the same here, the noRT run, at its peak, has an order of magnitude more cold, dense gas.
-\footnote{We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints from the large number of stars formed.
-Although radiative transfer itself is computationally expensive, this run is substantially more costly \textbf{due to a lower typical timestep and increased cost in computing the optically thin radiation effects (photoelectric effect and LW dissociation).}}
+\footnote{We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints.
+Although radiative transfer itself is computationally expensive, this run is substantially more costly \textbf{due to a lower typical timestep and increased cost in computing the optically thin radiation effects (photoelectric effect and LW dissociation) for the additional star particles.}}
 
@@
 \caption{The total gas mass at $n > 200$~cm$^{-3}$, our star formation density threshold.}
-\label{fig:panel1}
+\label{fig:sf gas}
 \end{figure}
@@
 Looking again at the first $\sim$100~Myr of simulation time, the effects of ionizing radiation beyond our 20~pc cutoff radius are not significant.
-However, these two simulations begin to diverge significantly after this point.
-The shortrad simulation has continual, steady star formation for the entire simulation time, while the star formation rate in our fiducial run is bursty, with periods of active, low-level star formation interspersed with periods (sometimes up to 50~Myr) of no star formation.
+However, these two simulations begin to diverge after this point.
+The shortrad simulation has continual, steady star formation for the entire simulation time, while the star formation rate in our fiducial run is bursty, with periods of active, low-level star formation interspersed with periods of no star formation.
 The driver of these differences is clear in the right hand panel.
 Our fiducial run loses a factor of $\sim 2$ more total gas and HI mass (black and blue lines) as compared to the shortrad simulation.
-Clearly, galactic winds and outflows are much more effective in the fiducial case, with full accounting of stellar ionizing radiation feedback, than in the shortrad simulation.
+Clearly, galactic winds and outflows are much more effective in with full accounting of stellar ionizing radiation feedback.
 
-This can be confirmed by examining the metal retention fraction (the fraction of produced metals retained within the disk of the galaxy) and mass outflow rates in each simulation.
+This can be confirmed by examining the metal retention fraction (the fraction of produced metals retained within the disk of the galaxy) and mass outflow rates across simulations.
 As shown in Figure~\ref{fig:metal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation.
@@
 \begin{equation}
-    \eta = \dot{M}_{\rm out} / <\rm{SFR}>_{100 \rm{Myr}}
+    \eta = \frac{ \dot{M}_{\rm out}}{ <\rm{SFR}>_{100 \rm{Myr}}}
 \end{equation}. The brackets indicate time averaging over 100~Myr.
 %
-While the fiducial run reaches a peak $\eta$ of a few hundred, shortrad is consistently an order of magnitude or more below this, while noRT is even lower.
+While the fiducial run reaches a peak $\eta$ of a few hundred, shortrad is consistently an order of magnitude or more below this. noRT is even lower.
 
-%mm [ended the paragraph to leave the previous important sentence in the place of emphasis at the end of the paragraph.]
-The fiducial run is also the only one of the three with any significant outflow beyond the virial radius, though we note the noRT run has not been simulated long enough for gas to have reached the virial radius.
-The outflow in noRT is
-%mm nearly the same as 
-   only a factor of a few lower than 
-the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback, 
-%mm 
-    so it implies a far lower mass loading factor. 
+The fiducial run is also the only one of the three with any significant outflow beyond the virial radius.
+The outflow in noRT is only a factor of a few lower than the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback, so it implies a far lower mass loading factor.
 We conclude that radiation feedback allows SNe to be substantially more effective in driving outflows.
-%mm We provide a physical explanation for these differences in the following section.
 
@@
 {\bf Right:} The mass loading factor $\eta$ calculated as the outflow rate divided by the SFR averaged over 100~Myr.
-%mm
-   Inclusion of diffuse ionization makes an order of magnitude difference in $\eta$ in 
-   this case. }
+Inclusion of diffuse ionization makes an order of magnitude difference in $\eta$ in this case.
+}
 \label{fig:metal_retention}
@@
 importance of localized ionization vs.\ ionization from a diffuse radiation field far from a single star.
-Only modeling stellar radiation feedback locally is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
+Only modeling local stellar radiation feedback is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
 To explore the cause of this difference we compare in Figures~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
@@
 \caption{Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run.
-Each panel is }
+Each panel is 4 kpc x 4 kpc.}
 \label{fig:panel1}

### 2018-07-27 main.tex
added ref to Fragile+04, revisions to abstract & intro

@@
-\documentclass[fleqn,usenatbib,useAMS]{mnras}
-\pdfoutput=1 
-\usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{multicol}        % Multi-column entries in tables
-\usepackage{bm}		% Bold maths symbols, including upright Greek
-%\usepackage{pdflscape}	% Landscape pages
-
+\documentclass[twocolumn]{aastex61}
+\pdfoutput=1 %for arXiv submission
+\usepackage{amsmath,amstext}
 \usepackage[T1]{fontenc}
-\usepackage{ae,aecompl}
-\usepackage{newtxtext,newtxmath}
-
-%\usepackage{amsmath,amstext}
-%\usepackage[T1]{fontenc}
+\usepackage{apjfonts} 
 \usepackage[figure,figure*]{hypcap}
 
-%\hypersetup{draft}
-%\usepackage{multirow}
-%\usepackage{mathtools}
-%\renewcommand*{\sectionautorefname}{Section} %for \autoref
-%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
-%\usepackage{graphicx}
-%\usepackage{natbib} % bibliography
+\renewcommand*{\sectionautorefname}{Section} %for \autoref
+\renewcommand*{\subsectionautorefname}{Section} %for \autoref
 
-%\usepackage[active,floats,tightpage]{preview}
-%    \setlength\PreviewBorder{1em}
-
-\newcommand{\msun}{M$_{\odot}$}
-\newcommand{\ccunit}{cm$^{-3}$}
-
-\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars}
-
-\author[A. Emerick et. al.]{
-Andrew Emerick,$^{1,2}$
-Greg L. Bryan,$^{1,3}$
-and Mordecai-Mark Mac Low$^{2,1}$
-\\
-$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
-$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
-$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+\shorttitle{Differential Metal Mixing}
 
@@
 
-\label{firstpage}
-%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
+%\title{Evolution of Individual Metals in Galactic Winds and the ISM}
 
-%\author{Andrew Emerick}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\author{Greg L. Bryan}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-%\author{Mordecai-Mark Mac Low}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+% GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
+% AE: Had a hard time coming up with a succinct and interesting sounding title that
+%     fit both of the interesting results: 
+%          1) analytic PDF fits and 2) variations in metal mixing...
+\title{Metal Mixing 
+%mm 
+    and Ejection
+in Dwarf Galaxies is Dependent on Nucleosynthetic Source}
 
-%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}
+%Non-Uniform Metal Distributions in a Dwarf Galaxy Simulation}
+%Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies}
+
+\author{Andrew Emerick}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\author{{\it more...}}
 
 \begin{abstract}
-In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
-We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
-We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints.
-We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group, low-mass dwarf galaxy.
-We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
-Effective feedback drives outflows with a greater metallicity than the ISM, leading to low metal retention fractions consistent with observations.
-Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
+Using a high resolution simulation of an isolated dwarf galaxy, accounting for 
+%mm 
+    multi-channel 
+stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy
+%mm through 
+    by
+galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal 
+%mm + 
+   and
+power-law distribution.
+The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail.
+The PDF properties, and relative significance of these two components, vary within each ISM phase.
+Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component.
+In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe).
+This difference is driven by the differences in
+%mm energetics between each source, particularly the poor coupling of AGB winds to the ISM. 
+    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
+Nearly all of the produced metals are ejected from the galaxy (only 5\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
+In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae.
+We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
 \end{abstract}
 
-\begin{keywords}
-Galaxy -- Hydrodynamics -- Simulation -- Feedback
-\end{keywords}
+\keywords{}
 
 \section{Introduction}
+% can I work "Currents of Space" into this paper somehow (Asimov)?
+Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}).
+One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (from stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas.
 %
-% AE removed below.. MM suggested  skipping both pars.
+% get a sentence with a better punch at the end
 %
-%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade.
-Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc.
-\citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses.
-On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM.
-This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}.
-See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.
-%
-%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution.
-In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense.
-In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships.
-For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.
 
-Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution.
-Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
-There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
-% editor asked us to reduce citation count here:{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
-These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
+One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references).
+While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood.
+This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
+Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}).
+Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows.
+When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly.
+However, these processes are critical components in understanding galactic chemical evolution.
+Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillotta2018}.
+In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.
 
-However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}.
-In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
-Mixing can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
-While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficiently high spatial resolution.
-Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
-Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b, KrumholzTing2018}.
-Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
-the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
-The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
+The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
+That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically
+%mm [added Fragile+ 2004 because they studied distributed metal injection.]
+\citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
+Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
+However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
 
-Increasing physical resolution reduces reliance on sub-grid physics for mixing.
-However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}.
-Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
-This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
-At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.
-Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
-The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
+It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group.
+(\textit{ references to APOGEE, GAIA, GALAH, RAVE, TGAS}).
+Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
+The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM.
+However, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.
 
-We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies.
-The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms.
-We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
-%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies.
-\citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
-Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar winds from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
-We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar far ultra-violet (FUV) radiation, and Lyman-Werner dissociation from stellar radiation.
+In this paper we present the first detailed chemical evolution results from a set of high resolution hydrodynamics simulations in the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014} of an isolated, low mass dwarf galaxy.
+The simulation discussed here was first introduced in detail in Emerick et.
+al.
+2018 (hereafter Paper I).
+To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae.
+This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below.
+We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species.
+We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.
 
-Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime.
-This includes yields from massive and AGB stellar winds, and supernovae (SNe).
-In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
-This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
-This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
-We describe each mode of our multi-channel feedback
-in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.
+The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity.
+Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging.
+[list examples of modelling problems].
+These uncertainties combined with the difficultly in simulating a fully self-consistent galaxy in detail motivates this current study.
+By focusing on a low mass dwarf galaxy, we are capable of capturing detailed feedback and ISM physics at high resolution, while following individual stars, due to their small physical scales and low star formation rates.
+In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios for two reasons.
+First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
+Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies with observational analogs in as much detail as we provide here.
+This work will be the first in several in attempting to bridge this gap.
+With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and low resolution simulations of more massive galaxies with physically motivated sub-grid physics models.
 
-Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.
+We summarize of our methods and physics models in Section~\ref{sec:methods}.
+We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}.
+In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
 
@@
 \label{sec:methods}
-We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
-This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
-To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background.
-We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}).
-We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
-Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
-We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on HI.
-In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
-We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both.
-We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors.
-We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species.
-In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked.
-This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth.
-These methods are discussed in full detail below.
+We refer the reader to Paper I for a detailed description of our numerical methods and feedback models. We briefly summarize the relevant details here.
 
-\subsection{Hydrodynamics and Gravity}
-\label{sec:hydro}
+\textit{Hydrodynamics ---} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}.
+Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
+We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver.
+We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
+Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas and 2) a cell's local Jeans length becomes resolved by less than 8 cells.
+If the cell is within 4 zones of a star particle with active feedback, it is refined to the maximum resolution.
+At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.
 
-We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies.
-\texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions.
-We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick.
-Specifically, simulations presented here were conducted at changeset 7001d99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
-We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}).
-Self-gravity is computed with a multigrid Poisson solver.
-The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.
+\textit{Chemistry, Heating, and Cooling Physics ---} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
+We account for approximate self-shielding of HI against the UV background following \cite{Rahmati2013}.
+We assume HeI self-shields in the same fashion as HI, and ignore HeII heating from the UVB entirely.
+Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}.
+Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.
 
-We refine the mesh whenever the thermal Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
-At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation.
-\citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.
+\textit{Star Formation ---} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
+Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$.
+Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$).
+We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\%.
+Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment.
+We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
 
-We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}).
-Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
-However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse.
-A non-thermal pressure term is added to cells once their thermal Jeans length becomes unresolved.
-This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
-The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.
+\textit{Stellar Feedback and Stellar Yields ---} We track the feedback and yields of 15 metal species for each star individually.
+Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
+Stars above this mass are assumed to direct collapse with no mass or energy injection.
+For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their HI and HeI ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
+We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars.
+Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind.
+Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
+Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et.
+al.
+in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.
 
-Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas.
-These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution.
-At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr.
-We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$.
-These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions.
-This threshold decreases the required run-time by factors of a few.
-The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)
-
-\subsection{Chemistry and Cooling Physics}
-\label{sec:chemistry}
-
-We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset c2c0faf.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes.
-We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.
-We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
-However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}.
-For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
-
-As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
-As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
-Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}.
-To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.
-We have made these new tables public in the main \texttt{Grackle} repository.
-These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
-Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.
-
-\subsection{Star Formation Algorithm}
-\label{sec:star formation}
-In order to resolve individual star formation events on galactic scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
-Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local thermal Jeans mass.
-Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K.
-We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$.
-No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.
-
-We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
-At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2018, FIRE2}, as star formation is ultimately self-regulated by feedback.
-
-The stellar mass formed during a timestep $\Delta t$ from a region with a total gas mass $M_{\rm gas}$ is
-\begin{equation}
-         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
-\end{equation}
-In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution.
-We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses.
-In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
-If it does, we randomly sample from
-the adopted IMF until approximately 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
-The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.
-We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
-Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
-By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.
-
-Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
-This dispersion captures some of the unresolved gas motions below the resolution limit that are smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations.
-Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
-
-Stars evolve during the simulation, by losing mass from stellar winds and SNe as described below, and by changing types, but persist throughout the entire simulation.
-For example, low mass stars are tagged as white dwarfs (WDs) at the end of their life, which may eventually explode as a Type Ia SN (discussed below), after which they persist as massless tracer particle remnants.
-Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a four-cell region at the highest level of refinement.
-This ensures that both stellar winds and SNe feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.
-
-\subsection{Stellar Properties}
-\label{sec:properties}
-Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}).
-We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$.
-Although $T_{\rm eff}$ and $g$ evolve over time for stars, modifying stellar radiative properties, following a stellar evolution track for each of our stars is beyond the scope of this work.
-We instead fix these properties at their zero age main sequence values.
-
-\subsection{Stellar Feedback and Chemical Yields}
-
-\subsubsection{Stellar Yields}
-\label{sec:yields}
-For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars.
-We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2018}.
-This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$.
-We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$.
-We ignore SN yields from these stars (see next paragraph).
-We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth.
-Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation.
-We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017a} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
-
-%
-% KVJ: Possibly include a discussion on uncertainties in stellar yields
-%
-
-Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe.
-Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$; we take $M_{\rm trans} = 8$~M$_{\odot}$.
-In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
-Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics).
-Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
-\citet{Cote2017a} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
-We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
-
-There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}.
-Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
-Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass, metal, or energy ejection.
-
-Type Ia SNe are an important additional source of galactic chemical enrichment.
-These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
-We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
-We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, substantially limiting the number of Type Ia SNe occurring during the initial gigayear in our models.
-
-\subsubsection{Stellar Winds}
-\label{sec:stellar winds}
-Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
-Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback.
-We assume complete thermalization of the wind kinetic energy, taking the total injected energy injected in timestep $\Delta t$ as $E_w = \frac{1}{2}\dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
-This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle.
-The edges of this spherical region will only partially overlap grid cells.
-We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately.
-We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
-
-Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}.
-Satisfying the Courant time step becomes prohibitively expensive following this gas, with time steps dropping to $\Delta t \sim$~100~yr.
-For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
-In our case, we fix massive stellar wind velocities to $v_w = 20$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies.
-Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work.
-These points are discussed in more detail in Sect.~\ref{sec:stellar winds discussion}.
-
-% Injecting 10$^{3}$ km s$^{-1}$ gas onto the grid at these scales leads to super heated, shocked gas at unphysical temperatures of about 10$^{8-9}$ K, particularly when injecting into very low density media.
-This can lead to painfully short time step sizes and crashes in the hydrodynamics solver.
-We adopt the common solution of artifiially reducing the wind velocity from massive stars, choosing $v_{\rm wind} = 500$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-However, this can still be problematic once the star evacuates the local ISM and injects its energy to very low density ($n \lesssim 10^{-3}$ \ccunit) gas.
-We address this issue by mass loading our winds when injection would lead to wind bubble temperatures in the spherical source region above a maximum temperature typical of wind bubble.
-This is a free parameter that we take to be 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
-Mass loading in this manner is (in effect) a sub-grid model for the unresolved ISM mixing at the boundary layer of the wind bubble, which is in fact the source of a majority of the gas mass within the wind bubble \citep{Weaver1977}.
-We take the metal species abundances of the mass loaded ISM to be the average cold / warm ISM abundance on each grid to prevent artificially inflating/deflating the overall abundances.
-We discuss our ability to resolve typical single star wind bubble properties in Appendix ~\ref{appendix:stellar winds}.
-
-%parameterized in this work with the STARBURST99 wind model, \citep{Leitherer1992}:
-%\begin{multline}
-%{\rm log} \left[ v_{\rm wind} {\rm (km~s^{-1})} \right] = 1.23 - 0.30~{\rm log}~\left[L{\rm (L_{\odot})}\right] \\
-% + 0.55~{\rm log}\left[M({\rm M_{\odot}})\right] + 0.64~{\rm log}\left[T_{\rm eff}(K)\right] \\
-% + 0.13~{\rm log}\left[Z({\rm Z_{\odot}})\right].
-%\end{multline}
-
-Stars that only undergo an AGB phase deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks.
-AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$.
-For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars as well.
-
-\subsubsection{Core Collapse SNe}
-\label{sec: core collapse}
-Stars between  $M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
-Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}).
-We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
-We use the same Monte Carlo sampling method as used in our stellar winds to map the spherical injection region to the grid.
-We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle.
-In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.
-
-\subsubsection{Type Ia SNe}
-\label{sec:Type Ia}
-We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as WD particles, marking a subset as Type Ia SN progenitors.
-This is the most self-consistent model for Type Ia SNe in galaxy-scale simulations.
-We note however that for the low SFRs in our isolated dwarf galaxy simulation, the first Type Ia SN only appears after a few hundred megayears of simulation time.
-By the end of the simulation presented here (500~Myr), only 18 have gone off.
-At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
-%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
-%or, 
-%\[
-%M_{\rm WD} = 
-%\begin{cases}
-%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
-%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
-%\end{cases}
-%\]
-%where $M_{\rm *}$ is the initial mass of the WD progenitor.
-We follow the common assumption that progenitor stars with initial masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017a}.
-
-We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution model.
-The Type Ia SN rate is taken to be a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope $\beta$ and normalization $N_{\rm Ia}/M_{\rm SF}$ are observables.
-The latter represents the number of Type Ia SNe per mass of star formation.
-By assuming an IMF  $dN/dm$, one can write down the fraction $\eta$ of stars capable of forming a Type Ia SN progenitor that \textit{will} explode within a Hubble time.
-This is given as
-\begin{equation}
-\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
-\end{equation}
-where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF, and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
-The distribution slope $\beta$ is of order unity, with typical values between 1.0 and 1.2 \citep[see][for a recent review]{Maoz2014}.
-$N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the Type Ia SN rate and integrating over a Hubble time.
-Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
-For our fiducial values, we adopt $\beta = 1.2$ \citep{Maoz2010} and $N_{\rm Ia}/M_{\rm SF} = 0.8\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013}.
-Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.
-
-Finally, we can normalize $\Psi(t)$ to give the probability per unit time $\dot{P}(t)$ that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor.
-Integrating this gives the total probability at any given time as
-\begin{equation}
-P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
-\end{equation}
-where $t_{\rm o}$ is the formation time of the WD and the leading term on the right hand side properly normalizes the total probability over a Hubble time to $\eta$.
-This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
-In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle.
-For $u \in [0,1]$, we interpolate its position on a pre-tabulated and inverted cumulative probability distribution function to assign a single time at which the WD particle will explode as a Type 1a supernova.
-We institute a minimum delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.
-
-\subsubsection{Ionizing Radiation from Discrete Sources}
-\label{sec:ionizing radiation}
-Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies.
-\ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance.
-However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds.
-Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
-As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.
-
-Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation.
-We follow HI and HeI ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
-
-We determine the HI and HeI ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
-We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star.
-Stars less massive than about 15 M$_{\odot}$ and very massive stars with sub-solar metallicity are generally not well sampled by the OSTAR2002 grid.
-In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).
-
-Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}).
-The average energy for HI and HeI ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
-
-We also include the effects of radiation pressure on HI.
-This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}.
-We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared.
-This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}.
-However, the importance of multiple scattering is still unclear.
-Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013a,Reissl2017,Wibking2018}.
-Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.
-
-\subsubsection{Diffuse  Heating}
-\label{sec:diffusive heating}
-We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the FUV (6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles.
-The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the spectral energy distributions for each gridded star.
-Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
-Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
-However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}.
-Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile.
-Only recently has the localization and time variation of these processes been considered.
-
-Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}.
-We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
-We assume HeI ionization generally follows HI.
-This allows us to approximate HeI self-shielding using the same form (A.
-Rahmati, private communication).
-We ignore HeII photoionization from the UV background entirely.
-For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
-As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
-This is described in more detail in Appendix ~\ref{appendix:cooling}.
-
-%Ignoring this effect leads to an overestimation of the cooling rates when in the self-shielding regime.
-%We refer to \citet{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \citet{Gracklemethod} for its specific implementation, as used here.
-
-We assume the galaxy is mostly optically thin to stellar FUV and use only local approximations for shielding.
-We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
-\begin{equation}
-\label{eq:PE}
-\Gamma_{\rm pe} = (1.3 \times 10^{-24} \rm{erg~s^{-1}~cm^{-3}})\, \epsilon n_{\rm H} G_{\rm eff} D 
-\end{equation}
-where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust-to-gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
-Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
-
-The value of $D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
-The extremely low dust-to-gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a ratio $D$ that scales linearly with metallicity at very low metallicity.
-At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit.
-Given that the ambient density of the ISM is generally 1--10~cm$^{-3}$, we can safely assume the FUV field to be optically thin.
-However, we do include a localized attenuation prescription that may influence high-density or metal-enriched regions of the galaxy.
-We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.
-
-Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
-This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations.
-Our chemical network only includes contributions from H, He, and H$_2$ to n$_e$.
-Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
-%This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
-
-\subsubsection{Lyman-Werner Radiation}
-\label{sec:LW}
-In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rate.
-We compute the stellar Lyman-Werner flux again from the OSTAR2002 grid by integrating the spectral energy distributions over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}).
-Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
-We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.
-
-\section{Galaxy Initial Conditions}
-\label{sec:IC}
-We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy.
-The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
-Leo P is gas rich, with a neutral hydrogen mass $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and stellar mass $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to an observed neutral hydrogen radius $r_{\rm HI} = 500$~pc.
-LeoP has a low metallicity, with an oxygen to hydrogen abundance ratio (O/H) of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
-Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
-
-The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential.
-The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
-\begin{equation}
-\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
-\end{equation}
-where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass.
-We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$.
-We adopt a \citet{Burkert1995} dark matter potential with virial mass and radius $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and scale radius r$_{\rm s} = 990$~pc.
-This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc.
-These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}.
-
-Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
-This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
-During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}.
-We stop the artificial driving 25~Myr after the first star particle forms.
-These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
-We note this initial driving is ad hoc in that we do not include other effects from the stellar population that would have caused these SNe.
-
-We emphasize here that our model, with no initial stellar distribution, is not intended to identically reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
-In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations.
-Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances.
-In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution.
-Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe.
-The subsequent metal enrichment from the stars in our simulation can be thought of as tracking a change in abundances from arbitrary initial conditions.
-We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.
+\textit{Initial Conditions ---} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
+We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$.
+The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
+Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium.
+The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
+Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
+Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.
 
 \section{Results}
-\label{sec:results}
-We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms.
-Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run.
-The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical height $|z| < 200$~pc relative to the center of the galaxy.
-ISM properties are calculated considering only the gas contained within the disk of the galaxy.
-We include a resolution study in Appendix \ref{appendix:resolution_study}.
+For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
+This galaxy has an average star formation rate of $1.2~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
+The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy.
+The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$.
+These winds eject 95\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.
 
-Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.
-All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset dd76ad10.
+In this work we focus in detail on how each of the 15 individual metal species evolve in this galaxy.
+We address differences between the ejection fractions of each metal in Section~\ref{sec:ejection} and analyze for the first time the mass-fraction PDFs of the metals retained by the ISM in Section~\ref{sec:mixing}.
 
-\subsection{Morphological Structure and Evolution}
-\label{sec:structure}
+\subsection{Preferential Ejection of Metals from the ISM}
+\label{sec:ejection}
 
-We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
-These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
-This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
-This central region quickly fills with warm and hot gas generated from radiation feedback and SNe respectively.
-Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels.
-The ISM properties are quantified further in Section~\ref{sec:phase}.
+\begin{figure}
+\centering
+\includegraphics[width=0.99\linewidth]{species_bar.png}\\
+\includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
+\caption{The fraction of each metal species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).
+The leftmost bar in each plot shows the sum of all metals.}
+\label{fig:species_fractions}
+\end{figure}
+
+The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
+We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
+Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+
+We find two major results.
+First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases.
+The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
+This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
+Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however,the retention factor varies.
+The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
+This suggests that individual metals \textit{do not} share the same dynamical evolution.
+Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field.
+In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{species_bar_sources.png}\\
+\caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
+These channels differ in both when metals are ejected, as determined by stellar evolution, and the energy with which they are ejected into the ISM.
+We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because only XX of them have exploded by the end of our 500~Myr simulation.}
+% GB(AE): Why are H and He different? Either discuss or remove from plot.
+%  ------ AE removed from plot
+%
+\label{fig:species_sources}
+\end{figure}
+
+The only physics that separates the dynamical evolution of these elements in our simulations is the individual sources of enrichment: AGB winds (stars less than 8~M$_{\odot}$), stellar winds (stars above 8~M$_{\odot}$), core collapse supernovae, and Type Ia supernovae.
+These channels differ in: 1) how long after a given star formation event they occur, 2), by consequence, the typical ISM properties in which they occur, 3) how much energy is associated with each event, which determines ejecta temperature and velocity.
+To understand where each of the elements in Figure~\ref{fig:species_fractions} originated, we show the mass fraction of metals produced through each channel in Figure~\ref{fig:species_sources}.
+Core collapse supernovae are responsible for over 90\% of the total metal enrichment in our galaxy, but this is clearly not true for all elements.
+In particular, a majority of N (74\%) and Ba (65\%) are ejected by AGB winds; both are retained at a higher rate than the rest of the metals.
+That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yields tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through supernovae.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and supernovae.
+However, this cannot be determined as we lack Lagrangian information about individual gas elements.}
+% AE: Actually if there are significant isotope variations between nucleosynthetic sources (i.e.
+N produced in AGB winds is a different isotope than the trace N produced in SNe) then that could be a very cool thing to distinguish if we had good gas-phase abundance measures of various isotopes...
+but maybe not if they aren't very stable....
+ We discuss how this result may extend towards other metal yields that are not well sampled on our relatively short (500 Myr) simulation timescales in Section~\ref{sec:discussion:metal yields}.
+
+AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of supernovae ($\sim$1000~km~s$^{-1}$).
+In addition, their longer timescales (40-100~Myr as compared to $\sim$10~Myr) means that AGB stars are typically removed from their birth regions.
+The changes in typical ISM density and height of these events contributes to these variations.
+We show histograms of the average number density within 20~pc of any given enrichment source (top) and height above/below the disk (bottom) within 1~Myr of each event (as limited by our output cadence) in Figure~\ref{fig:spatial distribution}.
+As shown, SN peak at very low densities, indicating that most explode in superbubbles, regions carved out by previous SNe.
+AGB stars predominately release their metals close to the average ISM density.
+The scale height distributions for both events show no significant differences.
+We do not expect these differences to be the dominant effect in driving the differential evolution of elements ejected by AGB winds vs.
+supernovae, compared to the energetics, but can certainly play a significant role in determining the mixing behavior of individual enrichment events.
+The changes to mixing behavior as a function of ISM properties will be investigated in more detail in a future work.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{SE_density.png}\\
+\includegraphics[width=0.95\linewidth]{SE_z.png}
+\caption{The average gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
+\label{fig:spatial distribution}
+\end{figure}
+
+\subsection{Mixing and Distribution of Metals in the ISM}
+\label{sec:mixing}
+
+Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
+In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}).
+Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances.
+In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
+However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
+To build towards this, we characterize the metal evolution and distributions in our galaxy below.
+
+% Classic chemical evolution models often adopt the simplifying assumption that metals from newly formed stars are instantly deposited back into the ISM \textbf{(examples)}.
+With added complication, this instantaneous recycling approximation (IRA) can be expanded upon by taking into account individual stellar lifetimes (references) which have been shown to produce significant variations in stellar abundances (references) as compared to IRA models.
+However, even in this new model it is unlikely that whatever fraction of a star's yields that remains in the ISM instantaneously enriches star forming gas.
+Rather, these yields are first injected through a hot phase (stellar winds, HII regions, supernovae), cooling over time into star forming gas.
+(refs for models accounting for this).
+We investigate this process in our simulations below, first by outlining a new analytic description of metal distributions in the ISM.
+
+\subsubsection{A Functional Form for Metal PDFs}
+\label{sec:log-normal}
+
+The log-normal distribution is found often in nature, generally describing processes with non-negative values that grow with time.
+In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}.
+In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}.
+Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}.
+It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape.
+This includes a log-normal component, generated by multiplicative processes (shocks and the turbulent cascade in the ISM) and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2017}.
+
+The physics that drives the density PDF is directly related to the process of metal mixing and diffusion.
+However, there is no a priori reason why gas density and metallicity PDFs should have similar functional forms.
+We demonstrate here for the first time that the mass fraction PDFs for each metal species in our simulation can indeed be well fit using a piecewise log-normal + power-law PDF.
+We use a simple conceptual model in Section~\ref{sec:interpretation} to motivate the emergence of this distribution.
+
+We follow \cite{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF.
+We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element.
+This PDF is given as
+\begin{align*}
+  p(Z) = 
+  \begin{cases}
+    \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right], 
+    & Z < Z_{\rm{t}} \\
+    % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
+    N p_o Z^{-\alpha},
+    & Z > Z_{\rm{t}}
+\end{cases}
+\end{align*}
+where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm t}$ is the metal fraction at the transition between the log-normal and power-law components.
+When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm t}$ as free parameters.
+These conditions set $N$ and $p_o$ to
+\begin{equation}
+N = \frac{1}{2} \left[ 1 + \rm{erf}\left( \frac{ln\left(Z_{\rm t}\right) - \mu}{\sigma\sqrt{2}}\right)\right] + \frac{p_o}{\alpha-1}Z_{\rm t}^{-\alpha + 1}
+\end{equation}
+and
+\begin{equation}
+p_o = \frac{1}{\sigma Z_{\rm t} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm t}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm t}) \right]
+\end{equation}.
+
+We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin with of 0.05 dex.
+We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \cite{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins.
+The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted.
+The log-normal + power-law PDF produces the best fit in nearly all cases.
+
+We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
+These PDFs have been computed at an arbitrary single point in time, at 270 Myr.
+For clarity, we only show a subset of the 15 elements we follow.
+As shown, there are clear differences in the PDFs across elements of different nucleosynthetic origins and between each phase.
+However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions.
+We discuss the differences among each phase in more detail in the next section, but note here that the significance of each of these components varies notably across phases.
+In many of these cases, the piecewise log-normal + power-law distribution fits the numerical PDF quite well.
+However, there are often deviations, particularly at low metal fractions, from pure log-normal behavior.
+This manifests as either a very broad, flat PDF at low metal fraction (see N and Ba, for example), or large peaks not well described by $p(Z)$ at low metal fraction.
+In these situations, it is unclear what, if any, portion should be considered as a log-normal, or if there are multiple components within this region.
+
+We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the the metal fraction  PDFs of individual elements in galaxy models.
+The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM.
+In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions.
+Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$.
+As this is the source of star forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
-\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation.
-Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row).
-Each individual main sequence star particle is shown in the number density projections as a single black dot.}
-\label{fig:panel_x}
+\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
+\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), HIM (red), and all the gas in the ISM (black).
+For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
+We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.
+Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
+\label{fig:log-normal}
 \end{figure*}
 
-The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
-This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time.
-Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--120~pc.
-Towards the end of the simulation time, the half-light radius is $391 \pm 19$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
-Although the disk remains thin beyond the half-light radius, with a scale height of around 50~pc, it is fully resolved at all radii.
-By the end of the simulation, the majority of the disk has a scale height of $\sim$100~pc.
+\subsubsection{PDF Variation Across Gas Phase}
+\label{sec:phase-pdfs}
 
-Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging.
-For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
-In the final column of Figure~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
-With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
-At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$.
-These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.
+The various phases represented in Figure~\ref{fig:log-normal} involve variations in density and temperature of more than six orders of magnitude.
+The evolution of each phase is qualitatively different, and the metal mixing behavior of each should vary.
+Mixing timescales over a given length scale should be related to the local sound speed; hot gas, with higher sound speeds, should mix more rapidly than the dense, disconnected clumps of cold gas in the ISM.
+In addition, one would expect a metallicity gradient with gas temperature as enrichment occurs first in the hot phases, cooling and enriching denser gas over time.
+We examine the PDF variations among elements in each phase, as shown in Figure~\ref{fig:log-normal}, in more detail here.
+
+Unsurprisingly the diffuse HIM contains the most metal enriched gas, as it is comprised predominately of metal enriched supernova ejecta.
+Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
+Generally, in colder gas the metal PDFs become less enriched with broader low metal fraction components and steeper, power-law tails.
+Although the extended power-law tail of the HIM leads to a large range of metal fractions, the HIM represents very little mass, and this tail represents recent, un-mixed enrichment.
+The comparatively narrow width in the log-normal regimes of CNM is perhaps surprising.
+Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is more well mixed.
+This runs counter to the idea that mixing times should be long in colder gas unless mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.
+
+Although these trends across phases hold for all elements, there are qualitative differences between elements, particularly between those ejected predominantly by AGB winds (e.g.
+Ba and N) and those ejected by supernovae (e.g.
+O and Mg).
+In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by supernova enrichment.
+The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the CNM.
+Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N produced in supernovae yields.
+Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and supernovae.
+AGB wind elements enrich the WNM and WIM directly, rather than the HIM, which would increase their mixing timescales and broaden their PDFs.
+
+\subsubsection{The Time Evolution of Metal PDFs}
+\label{sec:statistics}
+We focus on the time evolution of the full numerical PDFs in this section.
+Our results here do not depend upon the choice of functional form for $p(Z)$.
+Figure~\ref{fig:phase-statistics} shows the evolution of four different statistics for the O (top) and Ba (bottom) PDFs.
+These two elements are treated as representative elements for supernova and AGB wind production respectively.
+The difference between the mean and median masses of the PDF (second column) is a measure of the skew of the PDF.
+Positive values indicate that metals are preferentially sequestered in metal-rich gas, and are less well mixed throughout the given phase.
+The skew is always positive in these distributions.
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
-\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on views.}
-\label{fig:panel_z}
+\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution.png}
+\caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation.
+The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
+\label{fig:phase-statistics}
 \end{figure*}
+
+For O, the median mass fraction is ordered by phase temperature.
+The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm$ 1 dex over the simulation time.
+The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
+%This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events. 
+Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread.
+The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star forming gas.
+This is the only explanation for how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels).
+Individual enrichment events will have significantly higher metallicities than the ambient ISM in any phase, and will drive an increase in the difference between the mean and median of the PDF.
+These can be seen as the obvious spikes in the HIM and WIM.
+For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.
+
+% In each phase, enrichment events will tend to drive larger differences between mean and median mass fraction,
+
+Although these trends are generally true for Ba, its evolution is much more complicated.
+%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability. 
+Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM.
+The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
+Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in supernovae.
+The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
+These tails represent the most recently enriched gas, and is clearly much more locally confined than O.
+
+%{\bf (move to discussion?)}: 
+The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e.
+the ratio between the total mass of metals and the total mass).
+Assuming star forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex), but significant, for elements released during SNe explosions, but can be very significant, up to $\sim$ 0.8 dex, for elements released in AGB winds.
+Chemical evolution models, especially one-zone models, follow the mean metal fraction, not median.
+These results indicate that these models are biased to overestimate gas and stellar elemental abundances.
+. % However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.
+
+To summarize, this figure demonstrates: 1) there are qualitative differences in how supernova injected elements (e.g.
+O, Mg) and AGB wind injected elements (e.g.
+N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value.
+In the case of supernova injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
+For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.
+
+\section{Discussion}
+\label{sec:discussion}
+We begin with a simple toy model that motivates the power-law tail at high metal fractions of the metal fraction PDFs and a subsequent turnover at low metal fractions in Section~\ref{sec:interpretation}.
+This work is placed in context with previous works focusing on metal mixing in the ISM in Section~\ref{sec:context}.
+Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impact of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
+
+\subsection{Physical Interpretation of the PDF}
+\label{sec:interpretation}
+Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_o = 0$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$.
+Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas.
+In this case, $p(Z)$ takes the form of a double-delta function
+\begin{equation}
+p(Z) = \delta(Z) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
+\end{equation}
+If the enriched material mixes continually with the primordial gas at a constant rate, after some time this gas will have mixed with an equal amount of primordial gas.
+At this point, the high metal fraction delta term becomes $\frac{2M_{\rm ej}}{M_o} \delta(Z - \frac{1}{2}Z_{\rm ej})$.
+This implies an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas, and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$.
+If the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, $p(Z)$ will become a power-law in $Z$, truncated at some time dependent minimum $Z$.
+The slope of the power-law is determined by the rate of injection versus mixing with the ambient medium.
+A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium.
+Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than enrichment.
+If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.
+
+In reality, however, $M_o$ is not an inexhaustible reservoir of primordial gas.
+Eventually the entire ambient medium will become enriched to some $Z > Z_o$, and $p(Z)$ will consist entirely of a continuous, truncated power-law.
+As enrichment proceeds, gas near the low metallicity truncation of $p(Z)$, which still comprises much of the mass of the system, enriches towards higher metallicities in the power-law tail.
+This will produce a turnover at the low $Z$ limit of $p(Z)$.
+The low-turnover limit is produced by diffusion from many different sources, and is thus an additive process, which, as we noted above, tends to produce log-normal distributions.
+The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.
+
+This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases.
+The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions.
+Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low-metallicities.
+Cold, dense gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.
+
+%
+%
+%
+%Although this model is useful to explain these very general features, it is certainly incomplete in practice.
+Enrichment proceeds irregularly through the mulit-phase ISM with a variety of ejection masses and metallicities.
+Phases are not independent, and the hot phase cools and enriches cooler phases in the ISM, distorting $p(Z)$ within each phase.
+Cold gas is heated up and destroyed through feedback, changing the content of the low-metallicity end of the warm and hot phases.
+Finally, gas is removed from the galaxy through feedback driven winds that preferentially remove metal enriched gas.
+Each of these processes has a non-trivial effect on the evolution of the PDF that will cause deviations from the simple toy model outlined here.
+Determining the exact physical processes that drive and set the properties of each PDF is the subject of ongoing work.
+
+%
+% A.E. paragraph may need work
+%
+Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}.
+Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
+This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dnese gas ($\sim$ 1 km s$^{-1}$).
+Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy.
+This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
+It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing supernovae.
+Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star forming gas.
+Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy.
+The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.
+
+\subsection{Context}
+\label{sec:context}
+That metal fraction distributions can be described using a simple analytic log-normal + power-law PDFs, even in a complex, multi-phase ISM, has not been demonstrated prior to this work.
+In addition, this is the first work to demonstrate differential mixing behavior of individual metal species using 3D hydrodynamics simulations.
+However, there does exist a significant body of work investigating the mixing behavior of passive scalars in a variety of contexts, as discussed below.
+\cite{KrumholzTing2018} predict differential behavior for AGB wind and core collapse supernova synthesized elements as a direct consequence of the differences in size of typical planetary nebulae ($\sim$ 0.1~pc) and supernova remnants ($\sim$ 100~pc).
+%We discuss our results further in the context of previous research on metal mixing in the ISM and speculate on the physical processes that drive the evolution of these PDFs across phases.
+
+Previous work on the evolution of metals in the ISM varies from studies concerning the advection of passive scalars in idealized turbulent boxes \citep[e.g.][]{Pope1991, PanScannapieco2010, PanScannapiecoScalo2012, PanScannapiecoScalo2013, YangKrumholz2012, SurPanScannapieco2014, Colbrook2017}
+% cite passive scalar reviews by Warhaft 2000 in fluid mech and scalo + Elmegreen 2004?
+to global galaxy models studying generalized advection and mixing of passive scalars \citep[e.g.][]{deAvillez2002,Petit2015,Goldbaum2016} to models with more detailed self-consistent metal enrichment \citep[e.g.][]{Revaz2009,Escala2018}.
+% summarize conclusions from these works:
+
+The evolution of metallicity PDFs has been investigated previously in some of these works \citep[see ][ and references therein]{PanScannapiecoScalo2012,PanScannapiecoScalo2013}, with effort towards developing closure models to describe the evolution of the PDFs of passive scalars in turbulent media \citep[e.g.][]{EswaranPope1988,Chen1989,Pope1991}.
+The astrophysical context in much of this work was enrichment from the first stars, so the focus was on the low-metallicity tail of the PDF and the timescales over which gas is polluted \citep[e.g.][]{PanScannapiecoScalo2013,Sarmento2017}.
+These works often use isothermal turbulent-box simulations initialized with a double-delta function PDF of pristine gas and enriched gas in some varying spatial distribution, ignoring ongoing enrichment.
+Initial PDFs of this form were demonstrated some time ago to evolve into a Gaussian distribution at late times \citep{EswaranPope1988}, but it is unclear if these could also be described with a log-normal distribution.
+However, these works uniformly do not contain the high metallicity power-law tails shown in our work.
+As suggested by our toy model in Section~\ref{sec:interpretation}, this is due to the lack of ongoing enrichment in these studies.
+
+More detailed models of global galaxy evolution have generally focused on spatial correlations and mixing timescales of initially asymmetric fields, without concern for ongoing enrichment \citep[e.g.][]{deAvillez2002,Petit2015} or focused primarily on the evolution of stellar abundance patterns and metallicity distribution functions \citep[e.g][need more]{Jeon2017,Hirai2017,Escala2018}, without directly examining the evolution of gas-phase metallicity PDFs.
+
+%
+% MM: remove from this section:
+%This is the first work examining the gas-phase properties of metallicity PDFs in a global galaxy simulation with a detailed model for stellar feedback, chemical enrichment, and a multi-phase ISM.
+Since we are far from a complete understanding of galactic chemical evolution, investigating the physics behind what sets the statistical properties of these PDFs, particularly what drives the differences across metal species and phases, is important.
+Although this is beyond the scope of this current work, we use scaling arguments to speculate on the meaning of these results.
+%Metal mixing in the ISM is a diffusive process driven by turbulence.
+
+% Recent works investigating dwarf galaxy chemical enrichment with Lagrangian simulations have shown that the sub-grid diffusion models required to reproduce observed dwarf galaxy abundance properties imply fairly rapid mixing timescales \citep{Escala2018,Hirai2017}.
+In contrast to this work, \cite{Escala2018} finds dwarf galaxy
+%The sub-grid diffusion models in Langrangian simulations of dwarf galaxy chemical enrichment that match the abundance properties of observed dwarf galaxies imply rapid mixing timescales
+
+%
+%
+%  Recent works specifically examining metal mixing in dwarf galaxies. Saving for potential future discussion:
+% \cite{Hirai2017} uses constrains the diffusion parameter in their SPH simulations comparing their simulated dwarf galaxies to observations in [Mg/Fe] vs.
+[Fe/H] and [Ba/Fe] vs.
+[Fe/H] space.
+Suggests Ba/Fe is more powerful constraint and briefly discusses potential differences in mixing between elements but does not do work with this
+% \cite{Jeon2017} 
+% \cite{Escala2018} tests of role of metal diffusion models in producing realistic MDFs in dwarf galaxies. Able to reproduce things like MDF width and [alpha/Fe]vs[Fe/H] scatter.
+
+% The properties of log-normal density PDFs in isothermal simulations are governed by the statistical properties of turbulence (refs) and the relative importance of compressive and solenoidal driving.
+However, the density PDFs in simulations of global galaxies with a resolved, multiphase ISM show significant departures from log-normallity \citep[see][]{Hopkins2013} but are still approximately log-normal within individual phases of the ISM \citep{HopkinsQuataertMurray2012}.
+The properties of the density PDF in multiphase simulations have not been well studied which offers little insight into what sets the mass fraction PDFs for each element.
+We speculate on this here to motivate future study, but note that a detailed characterization is beyond the scope of this work.
+
+% The log-normal density PDFs found in ISM simulations have a variance that is proportional to the mach number \citep[e.g.][(maybe more)]{PNJ1997, Passot1998, Fedderath2008, LemasterStone2009}.
+In our simulations, however,
+
+%We discuss possible caveats to this in Section~\ref{sec:caveats}.
+Does this extend to more massive?
+how does DM potential affect this?
+Are general trends still true in much larger galaxies?
+or are things very different once HIM crossing times are more like 100 Myr (aka MW size galaxies).
+
+\subsection{Timescale Dependence of AGB Ejecta}
+\label{sec:discussion:metal yields}
+We can generally say that metals produced in AGB winds evolve qualitatively differently in dwarf galaxies than metals produced through supernovae.
+However, exactly which metals exhibit these differences, and to what degree, is timescale and metallicity dependent.
+Short-timescales ($\lesssim 100$~Myr) only samples enrichment from the most massive AGB stars, which stars on order of a few solar masses enrich on 1 Gyr timescales or longer.
+In our simulations, which only sample 500 Myr of evolution, N and Ba are dominated from AGB wind ejecta.
+C is commonly used to track AGB wind enrichment, but as it originates from lower mass AGB stars, C enrichment operates on $\sim$ Gyr timescales, longer than we follow in this work.
+This additionally varies with metallicity.
+Sr, for example, is only significantly ejected through AGB winds at our metallicity on $\sim$~Gyr timescales; stellar winds from more massive stars dominate the production of Sr on shorter timescales.
+At higher metallicity, much more Sr is produced through massive AGB stars, decreasing the timescale over which Sr should exhibit a differential chemical evolution as compared to supernovae ejected elements.
+
+To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected through AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times.
+This model was run using \textsc{SYGMA} \citep{Ritter2017}.
+As shown, metal enrichment from AGB winds only begins to dominate for a given species at $\sim$ 100 Myr.
+This includes N and Ba, as followed in our simulations, but this plot indicates that Li should show the strongest differences with respect to metal ejected through supernovae, even on relatively short ($< 100~$~Myr) timescales.
+It takes over a Gyr for C to be dominated from AGB wind ejecta, which is the case for many of the elements shown.
+F, which shows very little contribution from AGB winds at short timescales is dominated by enrichment on longer timescales.
+These dependences on metallicity and timescales certainly adds complications in generalizing our work and in interpreting observations in the context of the results presented here, but these difference could be leveraged to better understand galactic chemical evolution on multiple, distinct timescales.
+Clearly this motivates future work covering Gyr timescales to fully understand how metal mass fraction PDFs evolve with time.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0.png}
+\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, with no continual star formation.
+We only show a sample of some of the elements dominated most by AGB enrichment.
+The horizontal line marks 50\% contribution.}
+\label{fig:agb evolution}
+\end{figure*}
+
+%\begin{figure*}
+%\centering
+%\includegraphics[width=0.95\linewidth]{C_N_evolution.png}
+%\caption{The fractional contribution of AGB winds to the total yields of C and N as a function of time for a simple stellar population at three different metallicities.
+Since the nucleosynthetic source governs the mixing dynamics of a given metal, this plot illustrates how this can change with both time and metallicity for a given species.
+These models were generated using \textsc{SYGMA} \citep{Ritter2017-sygma}}
+%\label{fig:agb evolution}
+%\end{figure*}
+
+\subsection{Impact on Stellar Abundance Patterns}
+\label{sec:stellar abundances}
+% AE: Possibly need better general introduction to CE models / sims and importance of understanding stellar abundances (obs+theory)
+In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star forming gas in our simulations.
+This could be used to help disentangle sources of scatter in observed stellar abundance, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
+If the star forming gas in our simulations can also be well-fit by a log-normal + power-law PDF, and if we can parameterize their evolution as functions of global galaxy properties, this can be used as a powerful and analytic tool for modeling stellar abundance patterns in semi-analytic models.
+This would be a physically motivated way to account for both the intrinsic spread in stellar abundances due to inhomogeneities in the ISM and variations in mixing for different metal species.
+We reserve an analysis of these distributions in abundance space in both the gas and stars for a future work.
+However, we briefly discuss the connection to star forming gas and stellar enrichment below.
+
+Unfortunately, there is insufficient star forming gas at any one time in these simulations to construct a PDF of metal distributions.
+However, star forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, follow a similar PDF to the CNM.
+To verify this, Figure ~\ref{fig:stars} shows the difference between the oxygen mass fraction of stars and the median mass fraction from the CNM PDF at the time that particle formed.
+The large scatter at early times ($<$ 120~Myr) is a result of the early enrichment phase, when the initial gas oxygen mass fraction was zero.
+Stars seem to be sampled evenly around the median of the CNM distribution, with only a slight bias (52\% of stars) towards values below the median.
+However, for stars formed after the initial phase, the median separation from the CNM median is 0.31~dex, and can reach up to $\sim$~0.5~dex.
+Though a significant deviation, this is smaller than the typical IQR of the CNM (see Figure~\ref{fig:phase-statistics}).
+Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
+High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
+
+The first core collapse supernova occurs at 12~Myr,
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{scale_height}
-\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figures~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
-\label{fig:scale_height}
+\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
+\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the within 1~Myr (our time resolution) of each star's formation time.
+The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
+\label{fig:stars}
 \end{figure}
 
-\subsection{Star Formation Rate and Mass Evolution}
-\label{sec:sfr}
+\subsection{Do these results apply to more massive galaxies?}
+\label{sec:massive galaxies}
+One important caveat about our work is that these results are derived from simulations of an isolated, low mass dwarf galaxy whose properties vary dramatically from a more massive galaxy like the Milky Way.
+It is unclear how much of these results apply to more massive galaxies given their deeper potential wells and higher star formation rates.
+Feedback driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
+We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy.
+With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
+If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
+If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+This difference would be greater at later times (higher metallicity) once AGB enrichment becomes significant.
+For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
+At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way.
+Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way.
+However, there has been no definitive explanation for these observations.
+Generalizing our results and detailing their observational consequences is the topic of ongoing work.
 
-We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
-The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$.
-The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation.
-Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.19 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
-We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.
+In contrast, we expect the properties of the enrichment PDFs, and the variations between AGB enriched elements and supernova enriched elements (as presented in Figures~\ref{fig:log-normal} and ~\ref{fig:phase-statistics}), to be general.
+We expect metals to exhibit log-normal + power-law distributions in the ISM of all galaxies, with similar trends with enrichment source and gas phase as outlined here.
+However, the detailed properties of the PDFs (e.g, log-normal width, power-law slope) likely depend non-trivially on global galaxy properties.
+How these results vary as a function of galaxy properties will be investigated in future work.
 
-We note that the granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
-Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
-For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$.
-Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense.
-Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.
+% Talk about CGM at all???
 
-At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
-The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
-For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% at 500~Myr.
-The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy from feedback-driven galactic winds.
-During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM.
-Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
-The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
+%\textit{In addition, hot gas in a galaxy with a deeper potential well is less likely to be ejected from the galaxy, allowing more time for homogenization and possibly smaller metal fraction variation than seen here.}.
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{sfr_snrx100}
-\includegraphics[width=0.475\linewidth]{mass_evolution}
-\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins.
-Broken portions of this histogram are time periods with no star formation or supernovae.
-Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.
-Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
-\label{fig:sfr_mass_evolution}
-\end{figure*}
+%
+% moved to possible to-do list below,
+%
+\subsection{Implications for Exotic Enrichment Sources}
+\label{sec:exotic enrichment}
+We have shown that the dynamical evolution of metals depends upon their nucleosynthetic source, focusing here on AGB synthesized elements and supernova synthesized elements.
+However, these differences should also apply to exotic enrichment sources, such as hypernovae (HNe), neutron-star neutron-star mergers (NSM), and neutron star - black hole mergers.
+These sources have energies that differ significantly from typical supernova (10$^{51}$ erg), reaching $> 10^{52}$ for HNe \citep{Nomoto2004} and $\sim$10$^{49}$~erg for NSMs \citep{Goriely2011}.
+We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to supernovae.
+Based on our results here, we would expect elements from HNe to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe.
+Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies.
+These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
+In particular, low mass dwarf galaxies with unusual r-process enrichment \citep[e.g.][]{Ji2015}, are valuable for constraining the source of these elements, their frequency, and typical yields.
+The differential metal evolution presented in our work both opens up an additional avenue by which elements from distinct nucleosynthetic sources may be distinguished in observations and challenges current assumptions used in interpreting these observations.
 
-\subsection{ISM Properties}
-\label{sec:phase}
+%\subsection{Extra things I could discuss:}
+%\textit{Things I can / will additionally discuss}
+%\begin{itemize}
+%\item Observed N/O in stellar abundances exhibits large spreads at low metallicity.
+Argument has been that this is driven by timescale differences in AGB vs.
+massive star nucleosynthesis.
+However, our results would predict that N/O have a large spread due to mixing efficiency diffein rences between AGB winds and SNe.
+%\end{itemize}
 
-Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
-We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
-We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content.
-By this definition, although our galaxy certainly contains molecular hydrogen, molecular gas as a phase does not exist; the peak f$_{\rm H_2}$ in any single cell remains below 30\%.
-See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-The properties of these phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
-Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.
+\section{Conclusions}
+\label{sec:conclusions}
+For the first time we present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
+This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze how individual metal species couple to the galactic winds and ISM of this galaxy.
+We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, core collapse supernovae, and Type Ia supernovae).
+This difference is most significant in our model between elements ejected predominately through AGB winds and those ejected predominantly by core-collapse supernovae.
+In addition, we find for the first time that the metal mass fraction PDFs of each metal in the ISM can be described using an analytic piece-wise log-normal + power-law PDF.
+The properties of these PDFs vary with both ISM phase and metal species, again driven mostly by differences in enrichment sources.
 
-Figure~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
-One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
-Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
-We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
-Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left.
-The boxed regime in the lower right corner shows our star formation density and temperature threshold.
-Gas in this regime is rapidly consumed by star formation and subsequent feedback.
-Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average.
+We summarize our results as follows:
+\begin{itemize}
 
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{phase_diagram.png}
-\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gas interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr.
-The dashed lines are lines of constant pressure, separated by factors of 10.
-The region in the lower right corner indicates our density and temperature thresholds for star formation.}
-\label{fig:phase}
-\end{figure}
+%\item Elements from lower energy enrichment sources (i.e.
+AGB winds) are preferentially retained in the ISM of low mass dwarf galaxies as compared to those from higher energy sources (supernovae), which are more readily launched in galactic winds.
+This result is likely sensitive to global galaxy properties, becoming less significant with increasing halo mass.
+We predict the abundance ratios between AGB wind dominated metals (s-process elements) and SN dominated metals ($\alpha$ elements) to be higher at fixed metallicity in low mass dwarf galaxies than in more massive galaxies, like the Milky Way.
 
-The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
-The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
-The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run.
-The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation.
-During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1.
-Although the CNM dominates the mass fraction, it is a negligible component of the ISM volume, which is WIM dominated.
-However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
-Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
+\item Power-law tails in metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
 
-These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
-They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (defined in those works as gas with 100~K$<$T$< 3\times 10^{4}$), with cold gas having between 1 and 10\% of the mass, and occupying negligible volume.
-Hot gas (defined as gas with $T > 3\times 10^{4}$~K) occupies 10\% of the volume, with negligible mass, in their galaxy, while our WIM alone occupies $>$ 50\% of the volume.
-Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) and hot gas (by volume fraction) that seen in the more massive dwarf galaxy in these works.
-The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
-We have compared our cooling curves to those used in \citep{Hu2017} and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.
+\item Hotter phases have metal fraction PDFs that are more enriched with significant power-law tails as compared to cold phases, which have a more dominant log-normal structure.
+The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling into dense gas.
+% missing text???????????
 
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
-\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
-\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
-\label{fig:ISM_evolution}
-\end{figure*}
+\item Metal outflow in low mass dwarf galaxies depends upon nucleosynthetic origin.
+Metals from lower energy enrichment events (e.g.
+AGB winds) are preferentially retained in the ISM as compared to those from higher energy events (e.g.
+SNe).
+The degree to which this is true likely depends upon global galaxy properties such as star formation rate, dark matter potential well, and gas geometry.
 
-\subsection{Interstellar Radiation Field}
-\label{sec:ISRF}
+\item Likewise, metals originating in AGB winds are less well mixed in the ISM compared to metals injected through SNe, with spreads of over 1 dex in cold gas, as compared to
 
-The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}.
-This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
-In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
-The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
-The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.
-The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
-At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.
+\item Metal distributions exhibit positive skew, such that the median metal fraction can be anywhere from 0.1 to 1.0 dex above the mean metal fraction.
+Simple chemical evolution models, which generally follow the mean abundance, that are unable to account for complex metal mixing physics are likely biased towards higher enrichment values.
 
-The bottom panel gives the HI ionizing photon flux from stellar radiation.
-The ionizing radiation profile follows a similar trend, yet with significantly more variation, anywhere from two to four orders of magnitude.
-As this radiation is followed through radiative transfer, the profile encodes information about local attenuation by dense, neutral gas.
-This is the main driver of the differences between the two panels.
-The total fluctuation in both panels is due in part to the low-level, stochastic star formation in our galaxy.
-A higher star formation rate would produce a more regular population of massive stars and more uniform (in time) ISRF.
+\end{itemize}
 
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{G_o_profile} \\
-\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
-\caption{
-Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr.
-Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc.
-The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
-The bottom panel gives the HI ionizing stellar radiation flux.
-Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point.
-For this reason we only shade between the first quartile and maximum values.
-HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.}
-\label{fig:ISRF}
-\end{figure}
+We expect these results to be general for more massive galaxies and galaxy properties.
+However, it may be the case that metals couple more uniformly to galactic winds in more massive galaxies as wind driving occurs increasingly through entrainment of the ambient ISM rather than the ejection of individual enrichment events.
+This warrants further examination.
+But interpreting these results for low mass dwarf galaxies, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements, particularly at lower metallicities, 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way, and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements.
 
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
-\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
-\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
-Here, we include all gas within the mid-plane of our dwarf galaxy.
-Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
-This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
-\label{fig:ISRF_2D}
-\end{figure*}
+%\section{Things to cite}
+%Hou, Yu, Lu 2014: Need to read closer, but CE model playing around with SN energy feedback effectiveness finds that weaker feedback leads to more metal enrichment, higher FB, lower metallicities.
+Suggestion of importance of FB driving CE.
 
-To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr.
-This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
-The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
-From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
-Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation.
-In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency.
-It remains to be seen which of these two modes of feedback is more important in regulating star formation.
+\acknowledgments
+Acknowledgments.
 
-\subsection{Outflow Properties}
-\label{sec:outflows}
+\facilities{Yeti, CCA cluster, Stampede, Pleiades} 
+\software{Numpy, Enzo, yt, astropy}
 
-The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}.
-However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
-In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
-We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
-\begin{equation} \label{eq:dotM}
-\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
-\end{equation} 
-We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.
-
-The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
-Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
-For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor.
-The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors between 20--100 throughout the simulation time.
-This declines towards larger radii, however, with substantially less outflow past the virial radius.
-\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift, consistent with our results.
-The fluctuations in both of these panels are directly correlated with the SFR, with increased outflow during periods of star formation, and decreased outflow during periods of quiescence.
-
-Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
-Using a fit provided in \citet{Muratov2015} to extrapolate and compare $\eta$ at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
-These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
-We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find lower mass loading factors even closer to the disk, at 0.05 $R_{\rm vir}$, between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$; certainly this implies even smaller mass loading factors at 0.25 $R_{\rm vir}$.
-
-\begin{figure*}
-\includegraphics[width=0.45\linewidth]{total_mass_outflow}
-\includegraphics[width=0.45\linewidth]{total_mass_loading}
-\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
-\label{fig:mass_outflow}
-\end{figure*}
-
-Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
-In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
-Gas with a negative velocity is moving towards the center of the halo.
-Roughly 25\% of this mass is inflowing, mostly with modest negative velocities, and corresponds to previously ejected gas mixing and recycling throughout the halo.
-Half of the outflowing gas (positive velocities) is moving at velocities below 30 km s$^{-1}$, 75\% at velocities below 70 km s$^{-1}$, and 95\% at velocities below 100 km s$^{-1}$.
-Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-negligible amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$.
-The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominating at velocities above 200 km s$^{-1}$.
-The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling WIM and HIM, consistent with the results in \citet{Hu2016,Hu2017}.
-However, as shown, the HIM, which is mostly the SN ejecta itself, comprises very little of the outflow by mass.
-Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM.
-Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
-The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
-
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
-\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-This is averaged over the same time interval as Figure~\ref{fig:ISRF}.
-The outflowing material is multiphase, broken into WNM, WIM, and HIM.
-See Section~\ref{sec:phase} for definitions of these regimes.
-We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K.
-There is little to no outflowing mass in the CNM.}
-\label{fig:outflow_velocity}
-\end{figure}
-
-\subsection{Metal Evolution} 
-\label{sec:chemical evolution}
-
-\subsubsection{Metal Enriched Outflows}
-Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
-This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
-In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}.
-The parameter used to quantify metal outflow efficiencies varies among works.
-Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
-\begin{equation} \label{eq:eta-metal}
-\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
-\end{equation}
-where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-These metal loading factors fluctuate significantly with the SFR, just as was shown in Figure~\ref{fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
-On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5).
-Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}.
-\cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
-Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.
-
-\begin{figure}
-\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
-\includegraphics[width=0.9\linewidth]{metal_retention}
-\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Figure~\ref{fig:mass_outflow}.
-This is the ratio between the metal outflow rate and the metal production rate.
-{\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
-In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
-\label{fig:metal_evolution}
-\end{figure}
-
-These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
-This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
-After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
-This continues throughout the simulation, with only $\sim$4\% of produced metals residing in the disk of the galaxy.
-It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius until about 350 Myr where the fraction levels off to just above 50\%.
-Likewise, the CGM metal content continually decreases until the end of the simulation from loss through the virial radius of the halo.
-See Section~\ref{sec:obs_metals} for further discussion.
-
-\subsubsection{Differential Evolution of Elements Within the ISM}
-It is important to understand how metals from each source of stellar yields enrich the ISM.
-Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}.
-This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed.
-Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Avillez2002,Tassis2008,YangKrumholz2012}.
-It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
-It is even more unclear how metals are transported and distributed within low-mass dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.
-
-We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
-The left panel gives the abundance ratio of N to O throughout the ISM.
-The right
-two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy.
-These show regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K) connected by cold filaments, warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
-
-\begin{figure*}
-\includegraphics[width=0.98\linewidth]{log_NO_panel}
-\caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances.
-The left slice gives the ratio of the abundance between N and O, normalized to the solar abundance, while the number density and temperature are shown on the right.
-In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occurred in the preceding 5 Myr as black stars and orange diamonds respectively.}
-\label{fig:metal_slices}
-\end{figure*}
-
-As shown in the left panel, [N/O] varies significantly over this section of the ISM with notable differences across the various phases and ISM structures.
-The hottest gas, dominated by recent supernova explosions is overabundant in oxygen, relative to solar (purple).
-However, the relative abundance of nitrogen increases in the WIM and WNM, being overabundant relative to solar (green).
-
-At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars.
-Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
-Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
-The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
-This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
-A more detailed analysis is beyond the scope of this work, but we investigate this in detail in Emerick et.
-al.
-(in prep.).
-
-\section{Discussion}
-\label{sec:discussion}
-
-\subsection{Comparison to Observed Low Mass Dwarf Galaxies}
-\label{sec:observation}
-
-As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs.
-Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of $z = 0$ dwarf galaxies.
-However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies.
-We show that these properties are broadly consistent with observations.
-
-\subsubsection{Gas and Star Formation}
-\label{sec:gas_sf}
-
-The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}.
-However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
-In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.
-
-Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
-We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}.
-We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the area of the disk within the radius of the outermost star formed within the previous 10 Myr.
-Likewise, $\Sigma_{\rm gas} = M_{\rm gas,10} / A_{*,10}$, where M$_{\rm gas,10}$ is the total gas mass within this defined disk.
-However, the total gas content cannot be determined observationally.
-To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He.
-We note that there is generally no correction made for any possible H$_{\rm 2}$ or HII content.
-As shown in Section~\ref{sec:molecular gas content}, these components may be significant.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
-\includegraphics[width=0.475\linewidth]{all_gas_efficiency_evolution.png}
-\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
-See text for details of the calculation.
-Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars.
-On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}.
-There is no clear correlation with time in this diagram.}
-\label{fig:KS}
-\end{figure*}
-
-We include recent observational constraints on these relationships in Figure ~\ref{fig:KS}.
-Our galaxy fluctuates significantly about both relationships with no clear trends in time.
-However, in both cases, it is consistent with the available observational sample.
-At times our galaxy exhibits gas surface densities below the observational constraints.
-The trend is still consistent with higher densities at this point, but with a larger scatter towards lower star formation rate densities and efficiencies.
-
-In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
-It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
-This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
-The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.
-
-\subsubsection{Molecular Gas Content}
-\label{sec:molecular gas content}
-The molecular gas content of low-mass dwarf galaxies is generally assumed
-to be small, but is not well constrained by either theory or observations.
-Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
-As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range.
-H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
-The gas-phase reaction dominates in our low-metallicity galaxy over the other two channels by several orders of magnitude.
-In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
-Thus the presence of some ionizing background is required to generate the molecular fractions we find in our simulations, as confirmed in test simulations run only to the onset of first star formation.
-
-In contrast, \citet{Hu2016} and \citet{Hu2017} find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
-However, although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
-Our model suggests that both H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies.
-Indeed it is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, though it is worth noting that the rate coefficients associated with gas-phase H$_2$ formation are still uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
-Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
-It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
-This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
-
-\subsubsection{Metal Retention}
-\label{sec:obs_metals}
-
-The simulations presented here have not yet been run for the gigayear timescales required to begin to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$.
-However, we can compare to a key observable: the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from closed box stellar evolution models given the galaxy's star formation history.
-This can be done readily with Milky Way dSph's.
-Their stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
-However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
-
-Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich, star forming, low-mass dwarf galaxy, with an observable HII region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
-Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
-However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
-Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
-
-It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium.
-While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
-We find 5.3\% of all metals lie within 1 kpc of the center of our galaxy, 24.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 51\% outside $R_{\rm vir}$.
-This is consistent with previous works, but this is again an evolving quantity.
-In addition, the amount of gas that escapes the virial radius is certainly sensitive to the details of gas accretion from the IGM on this galaxy, which we cannot capture in this model.
-
-The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
-Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return.
-In addition, the accretion of pristine gas from the intergalactic medium could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals.
-This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.
-
-\subsection{Missing Physics}
-Although we include many detailed physical models in our simulations, there remain additional physical processes that may be relevant, which we now discuss.
-
-\subsubsection{Massive Stellar Wind Energy}
-\label{sec:stellar winds discussion}
-Our massive stellar wind model drastically reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$.
-Although our algorithm is entirely capable of generating realistic stellar winds with velocities comparable to those observed, such fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
-When considered in isolation, stellar winds are an important source of pre-SN feedback and can dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
-However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}, unless densities near the ionizing source are high enough to trap the  HII region in the source cell.
-In that case, they can clear out a cavity to allow initial establishment of the HII region.
-
-They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
-Although they likely have minimal dynamical importance at resolutions where peak densities are not anyway high enough to trap ionization fronts, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting closer examination in future work.
-
-\subsubsection{Cosmic Rays} 
-\label{sec:CRs}
-
-Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}.
-These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}.
-Modeling cosmic rays is challenging, however, as they encompass a wide range of energies, and there are significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
-Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy.
-In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM.
-Modeling cosmic ray feedback completely thus requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena.
-Finally, including MHD presents additional difficulties in untangling the effects of each individual feedback mechanism on galaxy chemodynamics.
-
-We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested.
-Mechanically, including this relatively simple treatment of cosmic ray feedback in our model is trivial.
-However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to later work.
-
-\subsection{Detailed Stellar Evolution and Binary Stars}
-\label{sec:binary stars}
-
-Roughly half of massive stars live in binary pairs \citep{Sana2013}.
-Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes.
-This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as SNe.
-This effect could be significant, but is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g.
-STARBURST99).
-For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse SNe occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
-Although they find only $\sim 15\%$ of core collapse SNe explode after 50~Myr, this could still be an important effect.
-Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}.
-Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
-
-Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars.
-This is beyond the scope of this project, but will be investigated in future work.
-
-\section{Conclusion}
-\label{sec:conclusion}
-We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
-For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, using individual star particles to model core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, Lyman-Werner radiation and pollution from AGB and massive stellar winds.
-This treatment of feedback, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
-In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P dwarf galaxy.
-We present an overview of the properties of this simulation in this work.
-
-For our simulated dwarf galaxy, we find:
-\begin{enumerate}
-\item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
-(See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).
-
-\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, falling to $\eta \sim 10$ at R$_{\rm vir}$,  and
-metal mass loading factors near unity.
-By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Figure~\ref{fig:outflow_velocity}).
-
-\item 
-Only $\sim$4\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of low-mass dwarfs.
-By the end of the simulation $\sim$45\% of the remaining metals stay within the virial radius (but outside the galaxy), while $\sim$50\%
-have been ejected beyond the virial radius. (See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
-
-\item 
-Beyond the stellar radius, the gas scale height is thin ($\sim 50$~pc), yet resolved, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
-This is comparable to the resolution limit of the diffuse HI in observed, gaseous low-mass dwarfs.
-At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Figure~\ref{fig:scale_height}).
-
-\item The ISRF of our galaxy varies strongly in both space and time by orders of magnitude.
-It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
-The importance of radiation feedback in our model will be investigated in a future work.
-(See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
-
-\item 
-We find H$_2$ fractions below 5\% in our dwarf galaxy, consistent with the poor constraints on molecular gas formation in low metallicity dwarf galaxies.
-This H$_2$ forms entirely through gas-phase reactions facilitated by H$^{-}$ in self-shielding regions; H$_2$ formation on dust grains and in the three body reaction are both insignificant.
-Cold, neutral hydrogen dominates the mass of our galaxy.
-While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Figure~\ref{fig:sfr_mass_evolution} and Figure~\ref{fig:ISM_evolution}.)
-
-\item Finally, we present gas-phase oxygen and nitrogen distributions as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy.
-These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs.
-SNe), as suggested by \cite{KrumholzTing2018}.
-This will be explored in more detail in future work (Emerick et.
-al.
-\textit{in prep.}).
-\end{enumerate}
-
-\section*{Acknowledgments:} 
-We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
-C\^ot\'e, S.
-Glover, K.
-Hawkins, C.
-Hu, K.
-Johnston, B.
-O'Shea, M.
-Putman, B.
-Smith, J.
-Wall, and J.
-Wise.
-We would additionally like to thank the referee for their careful report.
-A.E.
-is funded by the NSF Graduate Research Fellowship DGE 16-44869.
-G.L.B.
-is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
-M.-M.M.L.
-was partly funded by NASA  grant NNX14AP27G.
-We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute.
-This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.
-These are products of collaborative effort by many independent developers from numerous institutions around the world.
-Their commitment to open science has helped make this work possible.
-
-%\bibliographystyle{yahapj}
-\bibliographystyle{mnras}
+\bibliographystyle{yahapj}
 \bibliography{msbib}
@@
 
-\section{Gas Phases of the ISM}
-\label{appendix:phases}
+\section{Density PDF}
+\label{appendix:density PDF}
+We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}.
+We show the mass-weighted PDF ($dm/Md\rm{log}n$) on the left, and the volume-weighted PDF ($dv/Vd\rm{log}n$) on the right.
+As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution.
+The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.
+The volume weighted PDF is much better described as a multi-component power law.
+The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities.
+These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.
+Finally, \cite{Hopkins2013} suggests a different functional form for describing these PDFs across a range of idealized simulations, but it still may be insufficient to fully describe the density PDF in realistic galaxy simulations.
+Clearly, we are far from a general understanding of mass-weighted and volume-weighted density PDFs in the case of a turbulent, self-gravitating, multi-phase ISM.
 
-To aid in comparison to other works, we define our ISM phases here, as adopted and modified from \citet{Draine2011}, Table 1.3, and used consistently throughout this analysis.
-By construction, these phases are mutually exclusive.
-We take $f_{\rm H_2}$ to be the molecular hydrogen fraction of the total gas mass.
+\begin{figure}
+\centering
+\includegraphics[width=0.475\linewidth]{density_PDF.png} 
+\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted.png}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr.
+The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
+\label{fig:density_pdf}
+\end{figure}
 
-\begin{enumerate}
-\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
-\item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
-\item Warm Neutral Medium (WNM): $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$
-\item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
-\item Molecular: $T < 10^2$~K, $f_{\rm H_2} > 0.5$
-\end{enumerate}
-
-\section{Stellar Radiation Properties}
-\label{appendix:radiation}
-We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Figure~\ref{fig:stellar radiation properties} we plot these properties.
-We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
-This requires two factors for each radiation type, one for low mass and one for high mass stars.
-We use the following multiplicative factors to adjust the black body spectrum for HI and HeI ionizing radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
-We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
-
-The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid.
-A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section.
-We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \url{http://www.pa.uky.edu/~verner/photo.html}}
-The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision.
-Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.
+\section{Resolution Comparison}
+We perform a resolution test to confirm that the key results of this study are convergent, at least qualitatively.
+Given the variations in star formation rate, feedback effectiveness, and stochasticisty in our model, we do not expect exact numerical convergence in any one quantity.
+We conduct two lower resolution simulations with a maximum physical resolution of 3.6 pc and 7.2 pc.
+We refer the reader to Paper I for a previous comparison of these simulations to our fiducial run.
+In Figure~\ref{fig:resolution-phase} we demonstrate that O and Ba abundances behave qualitatively similar in our lower resolution runs as in our fiducial model.
+In both lower resolution runs O has a generally tighter distribution that narrows over time, while Ba is much less well mixed, in agreement with our fiducial simulation.
+The exact numerical values for these spreads are not convergent across simulations, but we do note significant variations in the exact SFH of these lower resolution runs could be driving these differences.
 
@@
 \centering
-\includegraphics[width=0.4\linewidth]{Q0}
-\includegraphics[width=0.4\linewidth]{Q1}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{L_FUV}
-\includegraphics[width=0.4\linewidth]{L_LW}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{E0}
-\includegraphics[width=0.4\linewidth]{E1}
-\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right).
-Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
-\label{fig:stellar radiation properties}
+\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study.png}
+\caption{Resolution comparison at two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.
+Compare to Figure~\ref{fig:phase-statistics}.}
+\label{fig:resolution-phase}
 \end{figure*}
 
-\setcounter{figure}{0}
-\section{Typical Gas Densities in Supernova Injection Regions}
-\label{appendix:SN}
-
-Modeling SN feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of SN feedback.
-Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time.
-However, physically consistent solutions have been developed \citep[e.g][]{Simpson2016} that inject a mixture of kinetic and thermal energy with a ratio that depends on resolution and local gas density.
-Overcooling becomes less important with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each SN.
-We take advantage of our high resolution and employ a simple thermal energy injection model for our SN feedback.
-We demonstrate how well this resolves our SNe in the comparison simulation presented in this work.
-
-The left panel of Figure~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
-As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
-For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations.
-The right panel of Figure ~\ref{fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
-\begin{equation}
-R_{\rm PDS} = 
-\begin{cases}
-49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z \le 0.01 \\
-18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z \ge 0.01 \\
-\end{cases}
-\end{equation}
-where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$.
-\citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the SN explosion with thermal energy injection alone, assuming uniform density in the injection region.
-In practice, the injection region is never uniform.
-We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each SN.
-As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but up to 8.3\% are not well resolved and 2.0\% are completely unresolved (below a single cell width).
-In general, these are SN explosions from the most massive (i.e.
-most prompt) stars.
-We do not expect that resolving these SNe will dramatically alter our results.
-However, we note that using our feedback model at resolutions much less than a few parsecs will require implementing an different injection mechanism.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.4\linewidth]{sn_density_hist}
-\includegraphics[width=0.4\linewidth]{sn_radius_hist}
-\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation.
-{\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each SN assuming a uniform medium at either the peak or average density in the injection region.
-The vertical lines show one and 4.5 cell widths.
-This shows that a fraction of these SNe are certainly unresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
-\label{fig:SN histogram}
-\end{figure*}
-
-\setcounter{figure}{0}
-\section{Cooling and Heating Rates}
-\label{appendix:cooling}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
-\caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background.
-Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the uncorrected (i.e.
-optically thin) metal line cooling rates.
-The regimes where heating dominates are plotted with dashed lines for clarity.}
-\label{fig:cooling comparison}
-\end{figure*}
-
-The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with a self-shielding approximations.
-\citet{Hu2017} details this inconsistency: metal cooling rates computed under the assumption of an optically thin UV background overestimate the electron fraction in regimes where self-shielding is important ($-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$).
-This results in an artificially enhanced metal line cooling rate in regions of self-shielding.
-This can be a significant effect, particularly at higher metallicities.
-We demonstrate this in Figure~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
-The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
-In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
-Figure~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
-We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
-
-For densities where self-shielding is important, we computed \textsc{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
-In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud.
-We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UV background.
-These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}.
-In computing these tables we had to include the cosmic ray ionization that dominates in optically thick clouds.
-Without this effect, \textsc{Cloudy} becomes unstable in entirely neutral regions.
-We adopted a cosmic ray ionization rate of 10\% the Milky Way value, though we note that varying this from 1\% to 100\% the Milky Way value did not have an effect on the extracted metal line cooling rates.
-
-Finally, we note that the cooling and heating rates in our simulation will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
-The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which is not included in these diagrams.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_curve}
-\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}.
-The absolute value of the net cooling or heating
-rate is shown with solid lines.}
-\label{fig:cooling}
-\end{figure*}
-
-\setcounter{figure}{0}
-\section{Resolution Study}
-\label{appendix:resolution_study}
-
-We demonstrate the effect of varying resolution in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}.
-We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines).
-The physics in each simulation remains the same with the exception of star formation, which employs a resolution-dependent density threshold.
-A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.
-As a result, the time at which star formation first occurs varies between the simulations, but we again define t = 0 as the time of first star formation in each simulation.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.33\linewidth]{sfr_resolution_study.png}
-\includegraphics[width=0.33\linewidth]{mass_evolution_resolution.png}
-\includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
-\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted).
-The line colors in the left panel are for better clarity between the SFRs.}
-\label{fig:resolution_study}
-\end{figure*}
-
-Figure~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
-We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
-The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs.
-We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Figure~\ref{fig:SN histogram}.
-However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
-
-Generally ineffective feedback leads to increased, not decreased, star formation rates.
-However, the lower resolution run has the lowest SFR.
-The source of this difference is likely related to the ability to resolve dense, cold gas in the lower resolution simulations.
-In particular, the low resolution simulation clearly is unable to resolve the densities at which gas-phase H$_2$ formation becomes efficient, leading to significantly lower H$_2$ fractions (middle panel) and lower cooling rates.
-In addition, whatever H$_2$ does form at these lower resolutions exists at lower gas densities than in our fiducial run, and is less well protected by self-shielding effects.
-This is shown clearly in the significant plummet in the H$_2$ mass during the phase of first star formation that is less severe in our fiducial run.
-In this low metallicity regime, where H$_2$ is an important coolant, the ability to resolve the densities responsible for H$_2$ formation and self-shielding is important.
-
-Theses differences in densities are shown clearly by comparing Figure~\ref{fig:phase} with Figure~\ref{fig:phase_resolution}.
-Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.
-In the 7.2~pc run, the gas phases are notably less distinct, with gas more evenly smoothed out in the multi-phase region between cold, dense gas and warm, ionized gas.
-We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature ceiling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{3pc_phase.png}
-\includegraphics[width=0.475\linewidth]{6pc_phase.png}
-\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Figure~\ref{fig:phase}.}
-\label{fig:phase_resolution}
-\end{figure*}
-
-Finally, the metal retention fraction (right panel) between the fiducial and 3.6~pc runs are quite similar, but is significantly higher for the lowest resolution simulation.
-It is likely, however, that this is a result of the lower SFR in the 7.2~pc run and is not directly a resolution effect.
-This also affects the fraction of metals ejected outside the virial radius, with less metals being ejected in the lower resolution runs.
-
-\label{lastpage}
-
 \end{document}

### 2018-07-27 main.tex
revisions in section 2

@@
+%mm substantive changes marked like this, others made silently
+
 \documentclass[twocolumn]{aastex61}
@@
 %mm [added Fragile+ 2004 because they studied distributed metal injection.]
-\citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+\citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, 
+and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
 It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
@@
 
-In this paper we present the first detailed chemical evolution results from a set of high resolution hydrodynamics simulations in the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014} of an isolated, low mass dwarf galaxy.
-The simulation discussed here was first introduced in detail in Emerick et.
-al.
-2018 (hereafter Paper I).
-To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae.
+In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}.
+The simulation discussed here was introduced in detail in
+%mm don't forget to introduce into bibliography
+Emerick et al.\ (2018; hereafter Paper I).
+To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
 This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below.
@@
 [list examples of modelling problems].
-These uncertainties combined with the difficultly in simulating a fully self-consistent galaxy in detail motivates this current study.
-By focusing on a low mass dwarf galaxy, we are capable of capturing detailed feedback and ISM physics at high resolution, while following individual stars, due to their small physical scales and low star formation rates.
-In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios for two reasons.
+These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study.
+By focusing on a low mass dwarf galaxy, with small size and low star formation rate, we can capture detailed feedback and ISM physics at high resolution, while following individual stars.
+In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios, for two reasons.
 First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
-Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies with observational analogs in as much detail as we provide here.
-This work will be the first in several in attempting to bridge this gap.
-With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and low resolution simulations of more massive galaxies with physically motivated sub-grid physics models.
+Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies
+%mm with observational analogs 
+  of easily observable size
+in as much detail as done here.
+This work will be the first of several attempting to bridge this gap.
+With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and physically motivated sub-grid physics models for lower resolution simulations of more massive galaxies.
 
-We summarize of our methods and physics models in Section~\ref{sec:methods}.
+We summarize our methods and physics models in Section~\ref{sec:methods}.
 We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}.
 In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
+%mm
+   We discuss our results in Section~\ref{sec:discussion}, and conclude in 
+   Section~\ref{sec:conclusions  }.
 
@@
 
-\textit{Hydrodynamics ---} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}.
+%mm \textit{Hydrodynamics ---} 
+\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}.
 Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
@@
 We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
-Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas and 2) a cell's local Jeans length becomes resolved by less than 8 cells.
+Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas
+%mm and 
+    or
+2) a cell's local Jeans length becomes resolved by less than eight cells.
 If the cell is within 4 zones of a star particle with active feedback, it is refined to the maximum resolution.
@@
 
-\textit{Chemistry, Heating, and Cooling Physics ---} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
+%mm \textit
+\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
 We account for approximate self-shielding of HI against the UV background following \cite{Rahmati2013}.
@@
 
-\textit{Star Formation ---} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
+%mm \textit
+\paragraph{Star Formation} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
 Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$.
@@
 
-\textit{Stellar Feedback and Stellar Yields ---} We track the feedback and yields of 15 metal species for each star individually.
+%mm \textit
+\paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually.
 Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
@@
 
-\textit{Initial Conditions ---} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
+\paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
 We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$.

### 2018-07-29 main.tex
updated ion formatting, other things in methods section

@@
 2) a cell's local Jeans length becomes resolved by less than eight cells.
-If the cell is within 4 zones of a star particle with active feedback, it is refined to the maximum resolution.
+Also, if the cell is within four zones of a star particle with active feedback, it is refined to the maximum resolution.
 At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.
@@
 \paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
-We account for approximate self-shielding of HI against the UV background following \cite{Rahmati2013}.
-We assume HeI self-shields in the same fashion as HI, and ignore HeII heating from the UVB entirely.
+We account for approximate self-shielding of H~{\sc i} against the UV background following \cite{Rahmati2013}.
+We assume He~{\sc i} self-shields in the same fashion as H~{\sc i}, and ignore He~{sc ii} heating from the UVB entirely.
 Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}.
@@
 Stars above this mass are assumed to direct collapse with no mass or energy injection.
-For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their HI and HeI ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
+For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their H~{\sc i} and He~{\sc i} ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
 We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars.
@@
 The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
-We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
+We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (H~{\sc i}M T$\ge 10^{5.5}$~K), and locked in stars (yellow).
 Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
@@
 However, even in this new model it is unlikely that whatever fraction of a star's yields that remains in the ISM instantaneously enriches star forming gas.
-Rather, these yields are first injected through a hot phase (stellar winds, HII regions, supernovae), cooling over time into star forming gas.
+Rather, these yields are first injected through a hot phase (stellar winds, H~{\sc ii} regions, supernovae), cooling over time into star forming gas.
 (refs for models accounting for this).
@@
 \includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
-\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), HIM (red), and all the gas in the ISM (black).
+\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), H~{\sc i}M (red), and all the gas in the ISM (black).
 For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
@@
 
-Unsurprisingly the diffuse HIM contains the most metal enriched gas, as it is comprised predominately of metal enriched supernova ejecta.
+Unsurprisingly the diffuse H~{\sc i}M contains the most metal enriched gas, as it is comprised predominately of metal enriched supernova ejecta.
 Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
 Generally, in colder gas the metal PDFs become less enriched with broader low metal fraction components and steeper, power-law tails.
-Although the extended power-law tail of the HIM leads to a large range of metal fractions, the HIM represents very little mass, and this tail represents recent, un-mixed enrichment.
+Although the extended power-law tail of the H~{\sc i}M leads to a large range of metal fractions, the H~{\sc i}M represents very little mass, and this tail represents recent, un-mixed enrichment.
 The comparatively narrow width in the log-normal regimes of CNM is perhaps surprising.
@@
 O and Mg).
-In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by supernova enrichment.
-The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the CNM.
-Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N produced in supernovae yields.
+In all phases, except the H~{\sc i}M, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by supernova enrichment.
+The power-law component of N and Ba is generally shallower than all other metals across each phase (except the H~{\sc i}M), particularly in the CNM.
+Ba and N do not show significant differences among the rest of the metals in the H~{\sc i}M, though this is likely because the Ba and N present in this phase is dominated by the Ba and N produced in supernovae yields.
 Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and supernovae.
-AGB wind elements enrich the WNM and WIM directly, rather than the HIM, which would increase their mixing timescales and broaden their PDFs.
+AGB wind elements enrich the WNM and WIM directly, rather than the H~{\sc i}M, which would increase their mixing timescales and broaden their PDFs.
 
@@
 For O, the median mass fraction is ordered by phase temperature.
-The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm$ 1 dex over the simulation time.
-The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
+The H~{\sc i}M is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm$ 1 dex over the simulation time.
+The frequent large skew in the H~{\sc i}M (see second panel) and spread in the H~{\sc i}M (right two panels), coupled with its continual fluctuation, suggests that the H~{\sc i}M is not in equilibrium.
 %This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events. 
@@
 Individual enrichment events will have significantly higher metallicities than the ambient ISM in any phase, and will drive an increase in the difference between the mean and median of the PDF.
-These can be seen as the obvious spikes in the HIM and WIM.
+These can be seen as the obvious spikes in the H~{\sc i}M and WIM.
 For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.
@@
 Although these trends are generally true for Ba, its evolution is much more complicated.
-%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability. 
+%In addition, the H~{\sc i}M is much less offset from the rest of the phases than is seen in O, with much less variability. 
 Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM.
-The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
-Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in supernovae.
+The H~{\sc i}M is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
+Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the H~{\sc i}M as in supernovae.
 The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
@@
 O, Mg) and AGB wind injected elements (e.g.
-N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value.
-In the case of supernova injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
+N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the H~{\sc i}M, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value.
+In the case of supernova injected elements, enrichment proceeds quickly through the H~{\sc i}M over the entire galaxy.
 For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.
@@
 This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases.
-The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions.
-Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low-metallicities.
+The H~{\sc i}M is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions.
+Whatever ambient component of the H~{\sc i}M that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low-metallicities.
 Cold, dense gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.
@@
 Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
-This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dnese gas ($\sim$ 1 km s$^{-1}$).
-Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy.
-This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
-It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing supernovae.
-Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star forming gas.
-Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy.
+This would imply rapid mixing timescales in the WIM and H~{\sc i}M, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dnese gas ($\sim$ 1 km s$^{-1}$).
+Our results show, however, that in general the WIM and H~{\sc i}M are the least well mixed, while the CNM is the most well mixed across the galaxy.
+This is particularly curious as the sound crossing time of the H~{\sc i}M across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
+It must be that the H~{\sc i}M is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing supernovae.
+Newly enriched gas must mix through the H~{\sc i}M on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star forming gas.
+Since elements produced in AGB winds do not directly enter the H~{\sc i}M, mixing is less efficient driving larger variations across the galaxy.
 The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.
@@
 Are general trends still true in much larger galaxies?
-or are things very different once HIM crossing times are more like 100 Myr (aka MW size galaxies).
+or are things very different once H~{\sc i}M crossing times are more like 100 Myr (aka MW size galaxies).
 

### 2018-07-29 main.tex
completed revisions to Methods

@@
 We account for approximate self-shielding of H~{\sc i} against the UV background following \cite{Rahmati2013}.
-We assume He~{\sc i} self-shields in the same fashion as H~{\sc i}, and ignore He~{sc ii} heating from the UVB entirely.
-Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}.
-Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.
+We assume He~{\sc i} self-shields in the same fashion as H~{\sc i}, and ignore He~{\sc ii} heating from the UVB entirely.
+Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolev-like method from \cite{Wolcott-Green2011}.
+Finally, we use updated metal line cooling tables that self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal line cooling tables computed under the optically thin assumption.
 
@@
 Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment.
-We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
+We use the zero-age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
 
@@
 \paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually.
-Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
-Stars above this mass are assumed to direct collapse with no mass or energy injection.
-For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their H~{\sc i} and He~{\sc i} ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
+Stars with mass 8~M$_{\odot} < M_{*} < 25$~M$_{\odot}$ explode as core collapse supernovae at the end of their lives, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
+Stars above this mass are assumed to
+%mm direct collapse 
+    directly collapse to black holes with no mass or energy 
+%mm injection. 
+    ejection.
+For all stars above 8~M$_{\odot}$ we follow: their stellar winds assuming continuous mass loss over their lifetimes
+%mm [this is a rather important approximation that should be explicitly noted]
+    but neglecting the energy injection of the winds by reducing their velocities (to 10 
+    km~s$^{-1}$); 
+their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively; and their H~{\sc i} and He~{\sc i} ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
 We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars.
-Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind.
-Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
-Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et.
+Low mass stars with $M_{*} < 8$~M$_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind.
+Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode, injecting 10$^{51}$~erg of thermal energy with yields.
+Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25$~M$_{\odot}$, \textbf{Slemer et.
 al.
-in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.
+in prep} for the stellar winds of stars with $M_{*} > 25$~M$_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.
 
-\paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
-We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$.
+\paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the 
+%mm redshift $z = 0$ 
+properties of 
+%mm an 
+    a modern
+ultrafaint dwarf galaxy, as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015,McQuinn2015a}.
+We initialize a disk with $M_{\rm gas} = 1.8 \times 10^{6} \, M_{\odot}$ distributed in an exponential profile centered on a static \cite{Burkert1995} dark matter potential with
+%mm [added unit of M_odot to M_vir]
+M$_{\rm vir} = 2.5 \times 10^{9}$~M$_{\odot}$. 
 The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
 Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium.
-The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
-Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
+The galaxy contains no initial background stellar population, limiting the number of Type Ia supernovae in our model, but we do provide initial
+%mm
+   randomly placed 
+supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
+Although we set the total metallicity field is initially non-zero, with $Z = 4.3 \times 10^{-4}$, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
 Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.
@@
 \section{Results}
-For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
+%mm For context, in 
+     In
+Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
 This galaxy has an average star formation rate of $1.2~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.

### 2018-07-29 main.tex
update

--- 2018-07-27 main.tex
@@
-%mm substantive changes marked like this, others made silently
-
 \documentclass[twocolumn]{aastex61}
@@
 %          1) analytic PDF fits and 2) variations in metal mixing...
-\title{Metal Mixing 
-%mm 
-    and Ejection
-in Dwarf Galaxies is Dependent on Nucleosynthetic Source}
+\title{Metal Mixing in Dwarf Galaxies is Dependent on Nucleosynthetic Source}
 
@@
 \affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\author{{\it more...}}
+\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+\author{Greg L. Bryan}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+\author{Mordecai-Mark Mac Low}
+\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+\author{Benoit C{\^o}t{\'e}}
+\affiliation{T.B.D.}
+\author{Kathryn V. Johnston}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\author{Brian O'Shea}
+\affiliation{T.B.D.}
 
 \begin{abstract}
-Using a high resolution simulation of an isolated dwarf galaxy, accounting for 
-%mm 
-    multi-channel 
-stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy
-%mm through 
-    by
-galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal 
-%mm + 
-   and
-power-law distribution.
+Using a high resolution simulation of an isolated dwarf galaxy, accounting for stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy through galactic winds.
+For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal + power-law distribution.
 The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail.
@@
 Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component.
-In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe).
-This difference is driven by the differences in
-%mm energetics between each source, particularly the poor coupling of AGB winds to the ISM. 
-    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
-Nearly all of the produced metals are ejected from the galaxy (only 5\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
+In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba in our model) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe).
+This difference is driven by the differences in energetics between each source, particularly the poor coupling of AGB winds to the ISM.
+Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
 In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae.
@@
 Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}).
-Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows.
+Consequently, following metal mixing, if treated in these models, requires assumptions in how metals mix within the ISM and how metals couple to galactic outflows.
 When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly.
@@
 The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically
-%mm [added Fragile+ 2004 because they studied distributed metal injection.]
-\citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, 
-and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
 It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
@@
 
-In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}.
-The simulation discussed here was introduced in detail in
-%mm don't forget to introduce into bibliography
-Emerick et al.\ (2018; hereafter Paper I).
-To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+In this paper we present the first detailed chemical evolution results from a set of high resolution hydrodynamics simulations in the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014} of an isolated, low mass dwarf galaxy.
+The simulation discussed here was first introduced in detail in Emerick et.
+al.
+2018 (hereafter Paper I).
+To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae.
 This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below.
@@
 Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging.
-[list examples of modelling problems].
-These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study.
-By focusing on a low mass dwarf galaxy, with small size and low star formation rate, we can capture detailed feedback and ISM physics at high resolution, while following individual stars.
-In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios, for two reasons.
+%[AE To Do: list examples of modelling problems].
+ These uncertainties combined with the difficultly in simulating a fully self-consistent galaxy in detail motivates this current study.
+By focusing on a low mass dwarf galaxy, we are capable of capturing detailed feedback and ISM physics at high resolution, while following individual stars, due to their small physical scales and low star formation rates.
+In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios for two reasons.
 First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
-Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies
-%mm with observational analogs 
-  of easily observable size
-in as much detail as done here.
-This work will be the first of several attempting to bridge this gap.
-With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and physically motivated sub-grid physics models for lower resolution simulations of more massive galaxies.
+Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies with observational analogs in as much detail as we provide here.
+This work will be the first in several in attempting to bridge this gap.
+With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and low resolution simulations of more massive galaxies with physically motivated sub-grid physics models.
 
-We summarize our methods and physics models in Section~\ref{sec:methods}.
+We summarize of our methods and physics models in Section~\ref{sec:methods}.
 We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}.
 In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
-%mm
-   We discuss our results in Section~\ref{sec:discussion}, and conclude in 
-   Section~\ref{sec:conclusions  }.
 
@@
 
-%mm \textit{Hydrodynamics ---} 
-\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}.
+\textit{Hydrodynamics ---} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}.
 Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
@@
 We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
-Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas
-%mm and 
-    or
-2) a cell's local Jeans length becomes resolved by less than eight cells.
+Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas and 2) a cell's local Jeans length becomes resolved by less than 8 cells.
 If the cell is within 4 zones of a star particle with active feedback, it is refined to the maximum resolution.
@@
 
-%mm \textit
-\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
+\textit{Chemistry, Heating, and Cooling Physics ---} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
 We account for approximate self-shielding of HI against the UV background following \cite{Rahmati2013}.
@@
 
-%mm \textit
-\paragraph{Star Formation} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
+\textit{Star Formation ---} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
 Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$.
@@
 
-%mm \textit
-\paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually.
+\textit{Stellar Feedback and Stellar Yields ---} We track the feedback and yields of 15 metal species for each star individually.
 Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
@@
 
-\paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
+\textit{Initial Conditions ---} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
 We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$.
@@
 
-The first core collapse supernova occurs at 12~Myr,
+%
 
@@
 Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way.
-However, there has been no definitive explanation for these observations.
-Generalizing our results and detailing their observational consequences is the topic of ongoing work.
+In addtion, recent observations find elevationd [Ba/Fe] vs.
+[Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS},
+% AE TODO: Update duggand and kirby if / when the paper comes out
+which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs.
+Given the lack of definitive explanation, clearly generalizing our results and detailing their observational consequences is a valuable area of future research.
 

### 2018-07-29 main.tex

--- 2018-07-29 main.tex
@@
 \affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\author{{\it more...}}
+\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+\author{Greg L. Bryan}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+\author{Mordecai-Mark Mac Low}
+\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+\author{Benoit C{\^o}t{\'e}}
+\affiliation{T.B.D.}
+\author{Kathryn V. Johnston}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\author{Brian O'Shea}
+\affiliation{T.B.D.}
 
@@
     source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
-Nearly all of the produced metals are ejected from the galaxy (only 5\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
+Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
 In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae.

### 2018-07-29 main.tex
Update on Overleaf.

@@
 \section{Introduction}
-% can I work "Currents of Space" into this paper somehow (Asimov)?
 Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}).
@@
 The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically
-%mm [added Fragile+ 2004 because they studied distributed metal injection.]
-\citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004},
-and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
 It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
@@
 In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}.
-The simulation discussed here was introduced in detail in
-%mm don't forget to introduce into bibliography
-Emerick et al.\ (2018; hereafter Paper I).
+The simulation discussed here was introduced in detail in \cite{Emerick2018} (hereafter Paper I).
 To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.

### 2018-07-29 main.tex
section 3.1 revision

--- 2018-07-29 main.tex
@@
 \affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-\author{Greg L. Bryan}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-\author{Mordecai-Mark Mac Low}
-\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-\author{Benoit C{\^o}t{\'e}}
-\affiliation{T.B.D.}
-\author{Kathryn V. Johnston}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\author{Brian O'Shea}
-\affiliation{T.B.D.}
+\author{{\it more...}}
 
@@
 %mm energetics between each source, particularly the poor coupling of AGB winds to the ISM. 
-    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
-Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
+     temperature between fast, shocked supernova ejecta and slow AGB winds.
+%mm [I agree with the argument below that this is secondary]    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
+Nearly all of the produced metals are ejected from the galaxy (only 5\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
 In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae.
@@
 \section{Results}
-For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
-This galaxy has an average star formation rate of $1.2~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
-The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy.
+%mm For context, in 
+     In
+Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the
+%mm 
+   overall rate of 
+retention or ejection of metals from the galaxy.
+This galaxy has an average star formation rate of $1.2~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kennicutt-Schmidt relation
+%mm
+     \citep{Kennicutt1998}.  
+The galaxy exhibits strong, feedback-driven outflows that eject a significant amount of gas and metals from the galaxy.
 The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$.
@@
 We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (H~{\sc i}M T$\ge 10^{5.5}$~K), and locked in stars (yellow).
-Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+%mm Again, with the exception of  H and He, we [H & He aren't metals]
+    We
+only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
 
 We find two major results.
-First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases.
+%mm [reversed order of results to follow figure.  The opposite choice could also be made, by reversing the order of the figure...]
+    First, 
+only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies
+%mm 
+    among elements.
+The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
+This suggests that individual metals \textit{do not} share the same dynamical evolution.
+%mm Clearly
+       Thus, 
+metal enrichment in galaxies is a phenomenon that cannot be fully captured using a single, global metallicity field.
+In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
+
+    Second,
+nearly all of the metals 
+%mm
+    retained in the disk
+reside within neutral gas, mostly in the CNM; only a few percent
+reside in the hot phases.
 The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
 This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
-Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however,the retention factor varies.
-The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
-This suggests that individual metals \textit{do not} share the same dynamical evolution.
-Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field.
-In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
 
@@
 \caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
-These channels differ in both when metals are ejected, as determined by stellar evolution, and the energy with which they are ejected into the ISM.
-We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because only XX of them have exploded by the end of our 500~Myr simulation.}
+These channels differ in both when metals are ejected, as determined by stellar evolution, and the
+%mm energy with which they are ejected into the ISM. 
+     phase of the ISM into which they are ejected.
+We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because 
+%mm
+    no older stellar population was initialized, so 
+only 
+%mm [boldfaced]
+     {\bf XX} 
+of them have exploded by the end of our 500~Myr simulation.}
 % GB(AE): Why are H and He different? Either discuss or remove from plot.
@@
 The only physics that separates the dynamical evolution of these elements in our simulations is the individual sources of enrichment: AGB winds (stars less than 8~M$_{\odot}$), stellar winds (stars above 8~M$_{\odot}$), core collapse supernovae, and Type Ia supernovae.
-These channels differ in: 1) how long after a given star formation event they occur, 2), by consequence, the typical ISM properties in which they occur, 3) how much energy is associated with each event, which determines ejecta temperature and velocity.
+These channels differ in: 1) how long after a given star formation event they occur, 2), by consequence, the typical ISM properties in which they occur, and 3) how much energy is associated with each event, which determines ejecta temperature and velocity.
 To understand where each of the elements in Figure~\ref{fig:species_fractions} originated, we show the mass fraction of metals produced through each channel in Figure~\ref{fig:species_sources}.
@@
 In particular, a majority of N (74\%) and Ba (65\%) are ejected by AGB winds; both are retained at a higher rate than the rest of the metals.
-That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yields tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through supernovae.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and supernovae.
-However, this cannot be determined as we lack Lagrangian information about individual gas elements.}
+That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yield tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through supernovae.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and supernovae.
+However, this cannot be
+%mm determined 
+    proven
+as we lack Lagrangian information about individual gas elements.}
 % AE: Actually if there are significant isotope variations between nucleosynthetic sources (i.e.
@@
 AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of supernovae ($\sim$1000~km~s$^{-1}$).
-In addition, their longer timescales (40-100~Myr as compared to $\sim$10~Myr) means that AGB stars are typically removed from their birth regions.
+In addition, their longer timescales (40--100~Myr as compared to $\sim$10~Myr) means that AGB stars are typically removed from their birth regions
+%mm
+    and randomly distributed through the galactic disk. 
 The changes in typical ISM density and height of these events contributes to these variations.
@@
 We do not expect these differences to be the dominant effect in driving the differential evolution of elements ejected by AGB winds vs.
-supernovae, compared to the energetics, but can certainly play a significant role in determining the mixing behavior of individual enrichment events.
+supernovae, compared to the energetics, but they can certainly play a significant role in determining the mixing behavior of individual enrichment events.
 The changes to mixing behavior as a function of ISM properties will be investigated in more detail in a future work.
@@
 
+%mm should most of this material be in the introduction, and just the last two sentences be here?
 Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
@@
 
-%
+The first core collapse supernova occurs at 12~Myr,
 
@@
 Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way.
-In addtion, recent observations find elevationd [Ba/Fe] vs.
-[Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS},
-% AE TODO: Update duggand and kirby if / when the paper comes out
-which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs.
-Given the lack of definitive explanation, clearly generalizing our results and detailing their observational consequences is a valuable area of future research.
+However, there has been no definitive explanation for these observations.
+Generalizing our results and detailing their observational consequences is the topic of ongoing work.
 

### 2018-07-29 main.tex

@@
 We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
+
 \end{abstract}
@@
 The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically
-%mm [added Fragile+ 2004 because they studied distributed metal injection.]
-\citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, 
-and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
 It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
@@
 We account for approximate self-shielding of H~{\sc i} against the UV background following \cite{Rahmati2013}.
-We assume He~{\sc i} self-shields in the same fashion as H~{\sc i}, and ignore He~{\sc ii} heating from the UVB entirely.
-Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolev-like method from \cite{Wolcott-Green2011}.
-Finally, we use updated metal line cooling tables that self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal line cooling tables computed under the optically thin assumption.
+We assume He~{\sc i} self-shields in the same fashion as H~{\sc i}, and ignore He~{sc ii} heating from the UVB entirely.
+Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}.
+Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.
 

### 2018-07-29 main.tex
updating with Benoits comments. Up until section 4.4

--- 2018-07-29 main.tex
@@
 \author{Benoit C{\^o}t{\'e}}
-\affiliation{T.B.D.}
+\affiliation{Konkoly Observatory, Research Centre for Astronomy and Earth Sciences, Hungarian Academy of Sciences, Konkoly Thege Miklos ut 15-17, H-1121 Budapest, Hungary}
+\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI 48824, USA}
+\affiliation{Joint Institute for Nuclear Astrophysics - Center for the Evolution of the Elements, USA}
 \author{Kathryn V. Johnston}
@@
 \begin{abstract}
-Using a high resolution simulation of an isolated dwarf galaxy, accounting for
-%mm
-    multi-channel
-stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy
-%mm through
-    by
-galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal
-%mm +
-   and
-power-law distribution.
+Using a high resolution simulation of an isolated dwarf galaxy, accounting for multi-channel
+stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy by galactic winds.
+For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal and power-law distribution.
 The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail.
@@
 Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
-In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae.
+In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread compared to elements synthesized in either core collapse or Type Ia supernovae.
 We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
@@
 
-One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references).
+One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation (references).
 While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood.
@@
 The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
 It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
@@
 First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
-Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies
-%mm with observational analogs
-  of easily observable size
-in as much detail as done here.
+Second, there is only a severly limited sample of gas-rich dwarf galaxies of this size that we can use for direct observational comparison, and it is computationally infeasible to simulate galaxies of easily observable size in as much detail as done here.
 This work will be the first of several attempting to bridge this gap.
@@
 In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
-%mm
-   We discuss our results in Section~\ref{sec:discussion}, and conclude in
-   Section~\ref{sec:conclusions  }.
+We discuss our results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusions}.
 
+% AE: Benoit suggested subsections instead of paragraph splits... play with this to see what looks best
 \section{Methods}
@@
 
-%mm \textit{Hydrodynamics ---}
-\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}.
+\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{http://enzo-project.org/} \citep{Enzo2014}.
 Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
@@
 We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
-Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas
-%mm and
-    or
-2) a cell's local Jeans length becomes resolved by less than eight cells.
+Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas or 2) a cell's local Jeans length becomes resolved by less than eight cells.
 Also, if the cell is within four zones of a star particle with active feedback, it is refined to the maximum resolution.
@@
 
-%mm \textit
-\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
+\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (H, H$^+$, He, He$^+$, He$^P{++}$, H$^-$, H$_2$, H$_2^+$, and e$^-$), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
 We account for approximate self-shielding of H~{\sc i} against the UV background following \cite{Rahmati2013}.
@@
 
-%mm \textit
+% AE: From Benoit, maybe make a note of 1 - 100 M_sun sampling may slightly overestimate higher mass stars (people usually do 0.1 to 100 M_sun
 \paragraph{Star Formation} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
@@
 We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars.
-Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind.
-Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
+Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind \citep{Goldman2017}.
+Stars with $3 < M_{*} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
 Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et.
@@
 For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
-This galaxy has an average star formation rate of $1.2~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
+This galaxy has an average star formation rate of $1.2~\times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
 The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy.
@@
 This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
-Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however,the retention factor varies.
+Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies.
 The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
@@
 These channels differ in both when metals are ejected, as determined by stellar evolution, and the energy with which they are ejected into the ISM.
-We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because only XX of them have exploded by the end of our 500~Myr simulation.}
-% GB(AE): Why are H and He different? Either discuss or remove from plot.
-%  ------ AE removed from plot
-%
+We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because only 16 of them have exploded by the end of our 500~Myr simulation.}
 \label{fig:species_sources}
@@
 AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of supernovae ($\sim$1000~km~s$^{-1}$).
-In addition, their longer timescales (40-100~Myr as compared to $\sim$10~Myr) means that AGB stars are typically removed from their birth regions.
+In addition, their longer timescales relative to massive stars means that AGB stars are typically removed from their birth regions.
 The changes in typical ISM density and height of these events contributes to these variations.
@@
 The power-law component of N and Ba is generally shallower than all other metals across each phase (except the H~{\sc i}M), particularly in the CNM.
-Ba and N do not show significant differences among the rest of the metals in the H~{\sc i}M, though this is likely because the Ba and N present in this phase is dominated by the Ba and N produced in supernovae yields.
+Ba and N do not show significant differences among the rest of the metals in the H~{\sc i}M, though this is likely because the Ba and N present in this phase is dominated by the Ba and N included in supernovae yields.
 Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and supernovae.
@@
 This work is placed in context with previous works focusing on metal mixing in the ISM in Section~\ref{sec:context}.
+We discuss the relevance of additional AGB yields not directly followed in this study in Section~\ref{sec:discussion:metal yields}.
 Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impact of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
@@
 Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
-This would imply rapid mixing timescales in the WIM and H~{\sc i}M, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dnese gas ($\sim$ 1 km s$^{-1}$).
+This would imply rapid mixing timescales in the WIM and H~{\sc i}M, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dense gas ($\sim$ 1 km s$^{-1}$).
 Our results show, however, that in general the WIM and H~{\sc i}M are the least well mixed, while the CNM is the most well mixed across the galaxy.
@@
 
-\subsection{Context}
+\subsection{Context With Previous Studies of Metal Mixing}
 \label{sec:context}
@@
 As shown, metal enrichment from AGB winds only begins to dominate for a given species at $\sim$ 100 Myr.
-This includes N and Ba, as followed in our simulations, but this plot indicates that Li should show the strongest differences with respect to metal ejected through supernovae, even on relatively short ($< 100~$~Myr) timescales.
+This includes N and Ba, as followed in our simulations, but this plot indicates that Ag and Pb should show similar bahavior.
 It takes over a Gyr for C to be dominated from AGB wind ejecta, which is the case for many of the elements shown.
@@
 However, for stars formed after the initial phase, the median separation from the CNM median is 0.31~dex, and can reach up to $\sim$~0.5~dex.
-Though a significant deviation, this is smaller than the typical IQR of the CNM (see Figure~\ref{fig:phase-statistics}).
+Though a significant deviation, this is smaller than the typical inner-quartile range (IQR) of the CNM (see Figure~\ref{fig:phase-statistics}).
 Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
@@
 
-\subsection{Do these results apply to more massive galaxies?}
+\subsection{Do These Results Apply to More Massive Galaxies?}
 \label{sec:massive galaxies}

### 2018-07-29 main.tex

@@
 \caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
-These channels differ in both when metals are ejected, as determined by stellar evolution, and the energy with which they are ejected into the ISM.
-We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because only 16 of them have exploded by the end of our 500~Myr simulation.}
+These channels differ in both when metals are ejected, as determined by stellar evolution, and the phase of the ISM into which they are ejected.
+We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because  no older stellar population was initialized, so only 16 of them have exploded by the end of our 500~Myr simulation.}
+
 \label{fig:species_sources}
@@
 In particular, a majority of N (74\%) and Ba (65\%) are ejected by AGB winds; both are retained at a higher rate than the rest of the metals.
-That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yields tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through supernovae.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and supernovae.
-However, this cannot be determined as we lack Lagrangian information about individual gas elements.}
+That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yield tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through supernovae.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and supernovae.
+However, this cannot be
+%mm determined
+    proven
+as we lack Lagrangian information about individual gas elements.}
 % AE: Actually if there are significant isotope variations between nucleosynthetic sources (i.e.
@@
 AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of supernovae ($\sim$1000~km~s$^{-1}$).
-In addition, their longer timescales relative to massive stars means that AGB stars are typically removed from their birth regions.
+In addition, their longer timescales relative to massive stars means that AGB stars are typically removed from their birth regions and randomly distributed through the galactic disk.
 The changes in typical ISM density and height of these events contributes to these variations.

### 2018-07-30 ms.tex
Update on Overleaf.

@@
 But even with this strong feedback, recent work has argued for the need for pre-SN feedback, from stellar winds and/or stellar radiation \citep[e.g.][]{Hu2016,Hopkins2018}, though this is typically modeled simply as additional energy injection around newly formed stars.
-The need for additional feedback is confirmed by simulations that are capable of fulling resolving individual SN \citep[e.g.][]{Hu2017,Peters2017}.
+The need for additional feedback is confirmed by simulations that are capable of fulling resolving individual SN \citep[e.g.][]{Peters2017,Hu2018}.
 However, modeling these processes in detail is challenging, and their competing effects on galactic evolution are poorly constrained.}
@@
 Rays begin on HEALPix refinement level 2, with a maximum refinement level of 13 (or $8.05 \times 10^8$ rays).
+\textbf{We include radiation pressure on hydrogen (single-scattering), but do not investigate its importance in this work (see \cite{WiseAbel2012}).}
 

### 2018-07-30 main.tex
rounding out Benoits comments. updating citations in introduction

@@
 \section{Introduction}
-Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}).
+Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution.
 One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (from stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas.
@@
 
-One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation (references).
-While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood.
+One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}.
+While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challening.
+More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects.
+How to properly account for multi-phase mixing, however, is still poorly understood.
 This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
-Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}).
+Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, Escala2018}.
 Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows.
@@
 However, these processes are critical components in understanding galactic chemical evolution.
-Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillotta2018}.
+Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{FengKrumholz2014,Armillotta2018}.
 In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.
@@
 
-It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group.
-(\textit{ references to APOGEE, GAIA, GALAH, RAVE, TGAS}).
+It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}.
 Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
@@
 
-%mm \textit
 \paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually.
@@
 That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yield tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through supernovae.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and supernovae.
-However, this cannot be
-%mm determined
-    proven
-as we lack Lagrangian information about individual gas elements.}
+However, this cannot be proven as we lack Lagrangian information about individual gas elements.}
 % AE: Actually if there are significant isotope variations between nucleosynthetic sources (i.e.
@@
 If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
-If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
-This difference would be greater at later times (higher metallicity) once AGB enrichment becomes significant.
-For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
+%If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+This difference would be greater at later times, once AGB enrichment becomes significant. 
+% Benoit suggested limiting / eliminating discussion relative to metallicity, since this is a little murky (age-metallicity varies significantly galaxy-to-galaxy).
+In addition, the elevated signals of Ba abundance ratios I mention have some amount of contention....
+%For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
 At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way.
@@
 In addtion, recent observations find elevationd [Ba/Fe] vs.
-[Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS},
-% AE TODO: Update duggand and kirby if / when the paper comes out
-which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs.
+[Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS}, which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs.
 Given the lack of definitive explanation, clearly generalizing our results and detailing their observational consequences is a valuable area of future research.
+If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
 
@@
 However, these differences should also apply to exotic enrichment sources, such as hypernovae (HNe), neutron-star neutron-star mergers (NSM), and neutron star - black hole mergers.
-These sources have energies that differ significantly from typical supernova (10$^{51}$ erg), reaching $> 10^{52}$ for HNe \citep{Nomoto2004} and $\sim$10$^{49}$~erg for NSMs \citep{Goriely2011}.
+These sources can have energies that differ significantly from typical supernova (10$^{51}$ erg), reaching $> 10^{52}$ for HNe \citep{Nomoto2004}.
+In addition, the rarity of these events, approximately $10^{-5}$ per M$_{\odot}$ of star formation for NSMs \citep{Kim2015} in the Milky Way, could significantly influence the typical ISM environments within which they eject their metals.
 We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to supernovae.
@@
 These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
-In particular, low mass dwarf galaxies with unusual r-process enrichment \citep[e.g.][]{Ji2015}, are valuable for constraining the source of these elements, their frequency, and typical yields.
+In particular, low mass dwarf galaxies with unusual r-process enrichment \citep[e.g.][]{Ji2016}, are valuable for constraining the source of these elements, their frequency, and typical yields.
 The differential metal evolution presented in our work both opens up an additional avenue by which elements from distinct nucleosynthetic sources may be distinguished in observations and challenges current assumptions used in interpreting these observations.
@@
 %\subsection{Extra things I could discuss:}
-%\textit{Things I can / will additionally discuss}
+%\textit{Things to maybe}
 %\begin{itemize}
@@
 
-\item Metal distributions exhibit positive skew, such that the median metal fraction can be anywhere from 0.1 to 1.0 dex above the mean metal fraction.
+\item Metal distributions exhibit positive skew, such that the mean metal fraction can be anywhere from 0.1 to 1.0 dex above the median metal fraction.
 Simple chemical evolution models, which generally follow the mean abundance, that are unable to account for complex metal mixing physics are likely biased towards higher enrichment values.
@@
 This warrants further examination.
-But interpreting these results for low mass dwarf galaxies, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements, particularly at lower metallicities, 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way, and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements.
+But interpreting these results for low mass dwarf galaxies, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
 
@@
 \acknowledgments
-Acknowledgments.
+A.E.
+is funded by the NSF Graduate Research Fellowship DGE 16-44869.
+G.L.B.
+is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
+M.-M.M.L.
+was partly funded by NASA  grant NNX14AP27G.
+B.C.
+acknowledges support from the ERC Consolidator Grant (Hungary) funding scheme (project RADIOSTAR, G.A.
+n.
+724560) and from the National Science Foundation (USA) under grant No.
+PHY-1430152 (JINA Center for the Evolution of the Elements).
+\textbf{K.V.J....}.
+\textbf{B.O....}.
+We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute.
+This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.
+These are products of collaborative effort by many independent developers from numerous institutions around the world.
+Their commitment to open science has helped make this work possible.
 

### 2018-07-30 main.tex
Removing doubled citations and comments

@@
 %mm should most of this material be in the introduction, and just the last two sentences be here?
-Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
+%   AE: I agree this is mostly redundant. I removed this
+%Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
 In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}).
@@
 To build towards this, we characterize the metal evolution and distributions in our galaxy below.
-
-% Classic chemical evolution models often adopt the simplifying assumption that metals from newly formed stars are instantly deposited back into the ISM \textbf{(examples)}.
-With added complication, this instantaneous recycling approximation (IRA) can be expanded upon by taking into account individual stellar lifetimes (references) which have been shown to produce significant variations in stellar abundances (references) as compared to IRA models.
-However, even in this new model it is unlikely that whatever fraction of a star's yields that remains in the ISM instantaneously enriches star forming gas.
-Rather, these yields are first injected through a hot phase (stellar winds, H~{\sc ii} regions, supernovae), cooling over time into star forming gas.
-(refs for models accounting for this).
-We investigate this process in our simulations below, first by outlining a new analytic description of metal distributions in the ISM.
 

### 2018-07-30 main.tex
fixing HIM

@@
 One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}.
-While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challening.
+While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challening.
 More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects.
@@
 The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
-We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (H~{\sc i}M T$\ge 10^{5.5}$~K), and locked in stars (yellow).
+We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
 Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
@@
 \includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
-\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), H~{\sc i}M (red), and all the gas in the ISM (black).
+\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), HIM (red), and all the gas in the ISM (black).
 For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
@@
 
-Unsurprisingly the diffuse H~{\sc i}M contains the most metal enriched gas, as it is comprised predominately of metal enriched supernova ejecta.
+Unsurprisingly the diffuse HIM contains the most metal enriched gas, as it is comprised predominately of metal enriched supernova ejecta.
 Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
 Generally, in colder gas the metal PDFs become less enriched with broader low metal fraction components and steeper, power-law tails.
-Although the extended power-law tail of the H~{\sc i}M leads to a large range of metal fractions, the H~{\sc i}M represents very little mass, and this tail represents recent, un-mixed enrichment.
+Although the extended power-law tail of the HIM leads to a large range of metal fractions, the HIM represents very little mass, and this tail represents recent, un-mixed enrichment.
 The comparatively narrow width in the log-normal regimes of CNM is perhaps surprising.
@@
 O and Mg).
-In all phases, except the H~{\sc i}M, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by supernova enrichment.
-The power-law component of N and Ba is generally shallower than all other metals across each phase (except the H~{\sc i}M), particularly in the CNM.
-Ba and N do not show significant differences among the rest of the metals in the H~{\sc i}M, though this is likely because the Ba and N present in this phase is dominated by the Ba and N included in supernovae yields.
+In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by supernova enrichment.
+The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the CNM.
+Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N included in supernovae yields.
 Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and supernovae.
-AGB wind elements enrich the WNM and WIM directly, rather than the H~{\sc i}M, which would increase their mixing timescales and broaden their PDFs.
+AGB wind elements enrich the WNM and WIM directly, rather than the HIM, which would increase their mixing timescales and broaden their PDFs.
 
@@
 For O, the median mass fraction is ordered by phase temperature.
-The H~{\sc i}M is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm$ 1 dex over the simulation time.
-The frequent large skew in the H~{\sc i}M (see second panel) and spread in the H~{\sc i}M (right two panels), coupled with its continual fluctuation, suggests that the H~{\sc i}M is not in equilibrium.
+The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm$ 1 dex over the simulation time.
+The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
 %This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events.
@@
 Individual enrichment events will have significantly higher metallicities than the ambient ISM in any phase, and will drive an increase in the difference between the mean and median of the PDF.
-These can be seen as the obvious spikes in the H~{\sc i}M and WIM.
+These can be seen as the obvious spikes in the HIM and WIM.
 For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.
@@
 Although these trends are generally true for Ba, its evolution is much more complicated.
-%In addition, the H~{\sc i}M is much less offset from the rest of the phases than is seen in O, with much less variability.
+%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability.
 Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM.
-The H~{\sc i}M is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
-Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the H~{\sc i}M as in supernovae.
+The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
+Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in supernovae.
 The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
@@
 O, Mg) and AGB wind injected elements (e.g.
-N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the H~{\sc i}M, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value.
-In the case of supernova injected elements, enrichment proceeds quickly through the H~{\sc i}M over the entire galaxy.
+N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value.
+In the case of supernova injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
 For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.
@@
 This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases.
-The H~{\sc i}M is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions.
-Whatever ambient component of the H~{\sc i}M that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low-metallicities.
+The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions.
+Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low-metallicities.
 Cold, dense gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.
@@
 Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
-This would imply rapid mixing timescales in the WIM and H~{\sc i}M, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dense gas ($\sim$ 1 km s$^{-1}$).
-Our results show, however, that in general the WIM and H~{\sc i}M are the least well mixed, while the CNM is the most well mixed across the galaxy.
-This is particularly curious as the sound crossing time of the H~{\sc i}M across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
-It must be that the H~{\sc i}M is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing supernovae.
-Newly enriched gas must mix through the H~{\sc i}M on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star forming gas.
-Since elements produced in AGB winds do not directly enter the H~{\sc i}M, mixing is less efficient driving larger variations across the galaxy.
+This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dense gas ($\sim$ 1 km s$^{-1}$).
+Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy.
+This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
+It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing supernovae.
+Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star forming gas.
+Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy.
 The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.
@@
 to global galaxy models studying generalized advection and mixing of passive scalars \citep[e.g.][]{deAvillez2002,Petit2015,Goldbaum2016} to models with more detailed self-consistent metal enrichment \citep[e.g.][]{Revaz2009,Escala2018}.
-% summarize conclusions from these works:
 
@@
 
-More detailed models of global galaxy evolution have generally focused on spatial correlations and mixing timescales of initially asymmetric fields, without concern for ongoing enrichment \citep[e.g.][]{deAvillez2002,Petit2015} or focused primarily on the evolution of stellar abundance patterns and metallicity distribution functions \citep[e.g][need more]{Jeon2017,Hirai2017,Escala2018}, without directly examining the evolution of gas-phase metallicity PDFs.
+More detailed models of global galaxy evolution have generally focused on spatial correlations and mixing timescales of initially asymmetric fields, without concern for ongoing enrichment \citep[e.g.][]{deAvillez2002,Petit2015} or focused primarily on the evolution of stellar abundance patterns and metallicity distribution functions \citep[e.g][]{Jeon2017,Hirai2017,Escala2018}, without directly examining the evolution of gas-phase metallicity PDFs.
 
@@
 Are general trends still true in much larger galaxies?
-or are things very different once H~{\sc i}M crossing times are more like 100 Myr (aka MW size galaxies).
+or are things very different once HIM crossing times are more like 100 Myr (aka MW size galaxies).
 

### 2018-07-30 main.tex
toned down NSMs in discussion

@@
 However, these differences should also apply to exotic enrichment sources, such as hypernovae (HNe), neutron-star neutron-star mergers (NSM), and neutron star - black hole mergers.
-These sources can have energies that differ significantly from typical supernova (10$^{51}$ erg), reaching $> 10^{52}$ for HNe \citep{Nomoto2004}.
-In addition, the rarity of these events, approximately $10^{-5}$ per M$_{\odot}$ of star formation for NSMs \citep{Kim2015} in the Milky Way, could significantly influence the typical ISM environments within which they eject their metals.
+These sources can have energies that differ significantly from typical supernova, reaching $> 10^{52}$~erg for HNe \citep{Nomoto2004}, for example.
+In addition, the rarity of these events, for example, there are approximately $10^{-5}$ per M$_{\odot}$ of star formation for NSMs \citep{Kim2015} in the Milky Way, could significantly influence the typical ISM environments within which they eject their metals.
 We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to supernovae.
 Based on our results here, we would expect elements from HNe to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe.
-Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies.
+%Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies. 
+Depending on their injection energy, NSMs could exhibit different mixing behaviors in the ISM.
 These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.

### 2018-07-30 main.tex
fixed HIM (had edited it to H~{\sc i}M!) and revisions in Sect 3

--- 2018-07-30 main.tex
@@
 \author{Benoit C{\^o}t{\'e}}
-\affiliation{Konkoly Observatory, Research Centre for Astronomy and Earth Sciences, Hungarian Academy of Sciences, Konkoly Thege Miklos ut 15-17, H-1121 Budapest, Hungary}
-\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI 48824, USA}
-\affiliation{Joint Institute for Nuclear Astrophysics - Center for the Evolution of the Elements, USA}
+\affiliation{T.B.D.}
 \author{Kathryn V. Johnston}
@@
 \begin{abstract}
-Using a high resolution simulation of an isolated dwarf galaxy, accounting for multi-channel
-stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy by galactic winds.
-For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal and power-law distribution.
+Using a high resolution simulation of an isolated dwarf galaxy, accounting for
+%mm
+    multi-channel
+stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy
+%mm through
+    by
+galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal
+%mm +
+   and
+power-law distribution.
 The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail.
@@
 %mm energetics between each source, particularly the poor coupling of AGB winds to the ISM. 
-    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
-Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
-In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread compared to elements synthesized in either core collapse or Type Ia supernovae.
+     temperature between fast, shocked supernova ejecta and slow AGB winds.
+%mm [I agree with the argument below that this is secondary]    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
+Nearly all of the produced metals are ejected from the galaxy (only 5\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
+In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae.
 We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
+
 \end{abstract}
@@
 \section{Introduction}
-Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution.
+Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution (\textit{references}).
 One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (from stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas.
@@
 
-One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}.
-While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challening.
-More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects.
-How to properly account for multi-phase mixing, however, is still poorly understood.
+One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references).
+While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood.
 This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
-Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, Escala2018}.
+Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}).
 Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows.
@@
 However, these processes are critical components in understanding galactic chemical evolution.
-Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{FengKrumholz2014,Armillotta2018}.
+Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillotta2018}.
 In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.
@@
 The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
 It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
@@
 
-It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}.
+It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group.
+(\textit{ references to APOGEE, GAIA, GALAH, RAVE, TGAS}).
 Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
@@
 First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
-Second, there is only a severly limited sample of gas-rich dwarf galaxies of this size that we can use for direct observational comparison, and it is computationally infeasible to simulate galaxies of easily observable size in as much detail as done here.
+Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies
+%mm with observational analogs
+  of easily observable size
+in as much detail as done here.
 This work will be the first of several attempting to bridge this gap.
@@
 In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
-We discuss our results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusions}.
+%mm
+   We discuss our results in Section~\ref{sec:discussion}, and conclude in
+   Section~\ref{sec:conclusions  }.
 
-% AE: Benoit suggested subsections instead of paragraph splits... play with this to see what looks best
 \section{Methods}
@@
 
-\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{http://enzo-project.org/} \citep{Enzo2014}.
+%mm \textit{Hydrodynamics ---}
+\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}.
 Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
@@
 We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
-Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas or 2) a cell's local Jeans length becomes resolved by less than eight cells.
+Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas
+%mm and
+    or
+2) a cell's local Jeans length becomes resolved by less than eight cells.
 Also, if the cell is within four zones of a star particle with active feedback, it is refined to the maximum resolution.
@@
 
-\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (H, H$^+$, He, He$^+$, He$^P{++}$, H$^-$, H$_2$, H$_2^+$, and e$^-$), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
+%mm \textit
+\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
 We account for approximate self-shielding of H~{\sc i} against the UV background following \cite{Rahmati2013}.
@@
 
-% AE: From Benoit, maybe make a note of 1 - 100 M_sun sampling may slightly overestimate higher mass stars (people usually do 0.1 to 100 M_sun
+%mm \textit
 \paragraph{Star Formation} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
@@
 Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment.
-We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
+We use the zero-age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
 
+%mm \textit
 \paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually.
-Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
-Stars above this mass are assumed to direct collapse with no mass or energy injection.
-For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their H~{\sc i} and He~{\sc i} ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
+Stars with mass 8~M$_{\odot} < M_{*} < 25$~M$_{\odot}$ explode as core collapse supernovae at the end of their lives, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
+Stars above this mass are assumed to
+%mm direct collapse 
+    directly collapse to black holes with no mass or energy 
+%mm injection. 
+    ejection.
+For all stars above 8~M$_{\odot}$ we follow: their stellar winds assuming continuous mass loss over their lifetimes
+%mm [this is a rather important approximation that should be explicitly noted]
+    but neglecting the energy injection of the winds by reducing their velocities (to 10 
+    km~s$^{-1}$); 
+their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively; and their H~{\sc i} and He~{\sc i} ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
 We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars.
-Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind \citep{Goldman2017}.
-Stars with $3 < M_{*} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
-Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et.
+Low mass stars with $M_{*} < 8$~M$_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind.
+Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode, injecting 10$^{51}$~erg of thermal energy with yields.
+Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25$~M$_{\odot}$, \textbf{Slemer et.
 al.
-in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.
+in prep} for the stellar winds of stars with $M_{*} > 25$~M$_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.
 
-\paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
-We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$.
+\paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the 
+%mm redshift $z = 0$ 
+properties of 
+%mm an 
+    a modern
+ultrafaint dwarf galaxy, as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015,McQuinn2015a}.
+We initialize a disk with $M_{\rm gas} = 1.8 \times 10^{6} \, M_{\odot}$ distributed in an exponential profile centered on a static \cite{Burkert1995} dark matter potential with
+%mm [added unit of M_odot to M_vir]
+M$_{\rm vir} = 2.5 \times 10^{9}$~M$_{\odot}$. 
 The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
 Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium.
-The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
-Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
+The galaxy contains no initial background stellar population, limiting the number of Type Ia supernovae in our model, but we do provide initial
+%mm
+   randomly placed 
+supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
+Although we set the total metallicity field is initially non-zero, with $Z = 4.3 \times 10^{-4}$, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
 Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.
@@
 \section{Results}
-For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
-This galaxy has an average star formation rate of $1.2~\times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
-The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy.
+%mm For context, in 
+     In
+Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the
+%mm 
+   overall rate of 
+retention or ejection of metals from the galaxy.
+This galaxy has an average star formation rate of $1.2~\times 10^{4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kennicutt-Schmidt relation
+%mm
+     \citep{Kennicutt1998}.  
+The galaxy exhibits strong, feedback-driven outflows that eject a significant amount of gas and metals from the galaxy.
 The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$.
@@
 We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
-Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+%mm Again, with the exception of  H and He, we [H & He aren't metals]
+    We
+only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
 
 We find two major results.
-First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases.
+%mm [reversed order of results to follow figure.  The opposite choice could also be made, by reversing the order of the figure...]
+    First, 
+only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies
+%mm 
+    among elements.
+The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
+This suggests that individual metals \textit{do not} share the same dynamical evolution.
+%mm Clearly
+       Thus, 
+metal enrichment in galaxies is a phenomenon that cannot be fully captured using a single, global metallicity field.
+In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
+
+    Second,
+nearly all of the metals 
+%mm
+    retained in the disk
+reside within neutral gas, mostly in the CNM; only a few percent
+reside in the hot phases.
 The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
 This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
-Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies.
-The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
-This suggests that individual metals \textit{do not} share the same dynamical evolution.
-Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field.
-In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
 
@@
 \caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
-These channels differ in both when metals are ejected, as determined by stellar evolution, and the phase of the ISM into which they are ejected.
-We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because  no older stellar population was initialized, so only 16 of them have exploded by the end of our 500~Myr simulation.}
-
+These channels differ in both when metals are ejected, as determined by stellar evolution, and the
+%mm energy with which they are ejected into the ISM. 
+     phase of the ISM into which they are ejected.
+We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because 
+%mm
+    no older stellar population was initialized, so 
+only 
+%mm [boldfaced]
+     {\bf XX} 
+of them have exploded by the end of our 500~Myr simulation.}
+% GB(AE): Why are H and He different? Either discuss or remove from plot.
+%  ------ AE removed from plot
+%
 \label{fig:species_sources}
@@
 That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yield tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through supernovae.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and supernovae.
-However, this cannot be proven as we lack Lagrangian information about individual gas elements.}
+However, this cannot be
+%mm determined 
+    proven
+as we lack Lagrangian information about individual gas elements.}
 % AE: Actually if there are significant isotope variations between nucleosynthetic sources (i.e.
@@
 AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of supernovae ($\sim$1000~km~s$^{-1}$).
-In addition, their longer timescales relative to massive stars means that AGB stars are typically removed from their birth regions and randomly distributed through the galactic disk.
+In addition, their longer timescales (40--100~Myr as compared to $\sim$10~Myr) means that AGB stars are typically removed from their birth regions
+%mm
+    and randomly distributed through the galactic disk. 
 The changes in typical ISM density and height of these events contributes to these variations.
@@
 
-%mm should most of this material be in the introduction, and just the last two sentences be here?
-%   AE: I agree this is mostly redundant. I removed this
-%Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
+%mm I think this material duplicates the first paragraph of the introduction.
+% Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
 In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}).
@@
 In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
-However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
+%mm However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
 To build towards this, we characterize the metal evolution and distributions in our galaxy below.
+      We characterize the metal distributions (in Sections~\ref{sec:log-normal} and \ref{sec:phase-pdfs}) and evolution (in Section~\ref{sec:statistics}) in our galaxy to build towards a  a complete model for how metals mix and evolve in the complex, multi-phase ISM of real galaxies.
+
+% Classic chemical evolution models often adopt the simplifying assumption that metals from newly formed stars are instantly deposited back into the ISM \textbf{(examples)}.
+With added complication, this instantaneous recycling approximation (IRA) can be expanded upon by taking into account individual stellar lifetimes (references) which have been shown to produce significant variations in stellar abundances (references) as compared to IRA models.
+However, even in this new model it is unlikely that whatever fraction of a star's yields that remains in the ISM instantaneously enriches star forming gas.
+Rather, these yields are first injected through a hot phase (stellar winds, H~{\sc ii} regions, supernovae), cooling over time into star forming gas.
+(refs for models accounting for this).
+We investigate this process in our simulations below, first by outlining a new analytic description of metal distributions in the ISM.
 
@@
 
-The log-normal distribution is found often in nature, generally describing processes with non-negative values that grow with time.
+The log-normal distribution is found often in nature, generally describing 
+%mm
+    multiplicative
+processes with non-negative values that grow with time.
 In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}.
@@
 It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape.
-This includes a log-normal component, generated by multiplicative processes (shocks and the turbulent cascade in the ISM) and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2017}.
+This includes a log-normal component, generated by multiplicative processes---in this case shocks and the turbulent cascade in the ISM---and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2017}.
 
@@
 
-We follow \cite{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF.
+We follow \citet{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF.
 We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element.
@@
 
-We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin with of 0.05 dex.
+We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin 
+%mm with 
+         width
+of 0.05 dex.
 We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \cite{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins.
@@
 
-We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the the metal fraction  PDFs of individual elements in galaxy models.
+We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the metal fraction  PDFs of individual elements in galaxy models.
 The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM.
@@
 The comparatively narrow width in the log-normal regimes of CNM is perhaps surprising.
-Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is more well mixed.
+Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is better mixed.
 This runs counter to the idea that mixing times should be long in colder gas unless mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.
@@
 The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the CNM.
-Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N included in supernovae yields.
+Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N produced in supernovae yields.
 Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and supernovae.
@@
 This work is placed in context with previous works focusing on metal mixing in the ISM in Section~\ref{sec:context}.
-We discuss the relevance of additional AGB yields not directly followed in this study in Section~\ref{sec:discussion:metal yields}.
 Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impact of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
@@
 Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
-This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dense gas ($\sim$ 1 km s$^{-1}$).
+This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dnese gas ($\sim$ 1 km s$^{-1}$).
 Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy.
@@
 
-\subsection{Context With Previous Studies of Metal Mixing}
+\subsection{Context}
 \label{sec:context}
@@
 to global galaxy models studying generalized advection and mixing of passive scalars \citep[e.g.][]{deAvillez2002,Petit2015,Goldbaum2016} to models with more detailed self-consistent metal enrichment \citep[e.g.][]{Revaz2009,Escala2018}.
+% summarize conclusions from these works:
 
@@
 
-More detailed models of global galaxy evolution have generally focused on spatial correlations and mixing timescales of initially asymmetric fields, without concern for ongoing enrichment \citep[e.g.][]{deAvillez2002,Petit2015} or focused primarily on the evolution of stellar abundance patterns and metallicity distribution functions \citep[e.g][]{Jeon2017,Hirai2017,Escala2018}, without directly examining the evolution of gas-phase metallicity PDFs.
+More detailed models of global galaxy evolution have generally focused on spatial correlations and mixing timescales of initially asymmetric fields, without concern for ongoing enrichment \citep[e.g.][]{deAvillez2002,Petit2015} or focused primarily on the evolution of stellar abundance patterns and metallicity distribution functions \citep[e.g][need more]{Jeon2017,Hirai2017,Escala2018}, without directly examining the evolution of gas-phase metallicity PDFs.
 
@@
 As shown, metal enrichment from AGB winds only begins to dominate for a given species at $\sim$ 100 Myr.
-This includes N and Ba, as followed in our simulations, but this plot indicates that Ag and Pb should show similar bahavior.
+This includes N and Ba, as followed in our simulations, but this plot indicates that Li should show the strongest differences with respect to metal ejected through supernovae, even on relatively short ($< 100~$~Myr) timescales.
 It takes over a Gyr for C to be dominated from AGB wind ejecta, which is the case for many of the elements shown.
@@
 However, for stars formed after the initial phase, the median separation from the CNM median is 0.31~dex, and can reach up to $\sim$~0.5~dex.
-Though a significant deviation, this is smaller than the typical inner-quartile range (IQR) of the CNM (see Figure~\ref{fig:phase-statistics}).
+Though a significant deviation, this is smaller than the typical IQR of the CNM (see Figure~\ref{fig:phase-statistics}).
 Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
@@
 
-\subsection{Do These Results Apply to More Massive Galaxies?}
+\subsection{Do these results apply to more massive galaxies?}
 \label{sec:massive galaxies}
@@
 If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
-%If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
-This difference would be greater at later times, once AGB enrichment becomes significant. 
-% Benoit suggested limiting / eliminating discussion relative to metallicity, since this is a little murky (age-metallicity varies significantly galaxy-to-galaxy).
-In addition, the elevated signals of Ba abundance ratios I mention have some amount of contention....
-%For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
+If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+This difference would be greater at later times (higher metallicity) once AGB enrichment becomes significant.
+For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
 At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way.
@@
 In addtion, recent observations find elevationd [Ba/Fe] vs.
-[Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS}, which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs.
+[Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS},
+% AE TODO: Update duggand and kirby if / when the paper comes out
+which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs.
 Given the lack of definitive explanation, clearly generalizing our results and detailing their observational consequences is a valuable area of future research.
-If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
 
@@
 However, these differences should also apply to exotic enrichment sources, such as hypernovae (HNe), neutron-star neutron-star mergers (NSM), and neutron star - black hole mergers.
-These sources can have energies that differ significantly from typical supernova (10$^{51}$ erg), reaching $> 10^{52}$ for HNe \citep{Nomoto2004}.
-In addition, the rarity of these events, approximately $10^{-5}$ per M$_{\odot}$ of star formation for NSMs \citep{Kim2015} in the Milky Way, could significantly influence the typical ISM environments within which they eject their metals.
+These sources have energies that differ significantly from typical supernova (10$^{51}$ erg), reaching $> 10^{52}$ for HNe \citep{Nomoto2004} and $\sim$10$^{49}$~erg for NSMs \citep{Goriely2011}.
 We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to supernovae.
@@
 These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
-In particular, low mass dwarf galaxies with unusual r-process enrichment \citep[e.g.][]{Ji2016}, are valuable for constraining the source of these elements, their frequency, and typical yields.
+In particular, low mass dwarf galaxies with unusual r-process enrichment \citep[e.g.][]{Ji2015}, are valuable for constraining the source of these elements, their frequency, and typical yields.
 The differential metal evolution presented in our work both opens up an additional avenue by which elements from distinct nucleosynthetic sources may be distinguished in observations and challenges current assumptions used in interpreting these observations.
@@
 %\subsection{Extra things I could discuss:}
-%\textit{Things to maybe}
+%\textit{Things I can / will additionally discuss}
 %\begin{itemize}
@@
 
-\item Metal distributions exhibit positive skew, such that the mean metal fraction can be anywhere from 0.1 to 1.0 dex above the median metal fraction.
+\item Metal distributions exhibit positive skew, such that the median metal fraction can be anywhere from 0.1 to 1.0 dex above the mean metal fraction.
 Simple chemical evolution models, which generally follow the mean abundance, that are unable to account for complex metal mixing physics are likely biased towards higher enrichment values.
@@
 This warrants further examination.
-But interpreting these results for low mass dwarf galaxies, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
+But interpreting these results for low mass dwarf galaxies, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements, particularly at lower metallicities, 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way, and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements.
 
@@
 \acknowledgments
-A.E.
-is funded by the NSF Graduate Research Fellowship DGE 16-44869.
-G.L.B.
-is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
-M.-M.M.L.
-was partly funded by NASA  grant NNX14AP27G.
-B.C.
-acknowledges support from the ERC Consolidator Grant (Hungary) funding scheme (project RADIOSTAR, G.A.
-n.
-724560) and from the National Science Foundation (USA) under grant No.
-PHY-1430152 (JINA Center for the Evolution of the Elements).
-\textbf{K.V.J....}.
-\textbf{B.O....}.
-We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute.
-This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.
-These are products of collaborative effort by many independent developers from numerous institutions around the world.
-Their commitment to open science has helped make this work possible.
+Acknowledgments.
 

### 2018-07-30 main.tex
updateing more references in introduction. significant clarification points from KVJ comments, particularly in interpretation and intro. Still have a couple more KVJ comments to address

--- 2018-07-30 main.tex
@@
 This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
-Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, Escala2018}.
-Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows.
+%Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows. 
+Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018} and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.
+Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.
+
+In addition, it remains to be seen to what degree, if at all, metals of different enrichment origins (AGB winds, core collapse supernovae, Type Ia supernovae, neutron-star neutron-star mergers, etc.) may couple differently to the ISM.
 When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly.
-However, these processes are critical components in understanding galactic chemical evolution.
-Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{FengKrumholz2014,Armillotta2018}.
-In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.
+However, if metals do not behave uniformly in the ISM, if their mixing and ejection behavior depends directly upon the energetics and physical environment of their injection, then this assumption would need to be re-evaluated.
+Differences in metal distributions from ejecta in AGB stars, as compared to supernovae, has been explored recently in \cite{KrumholzTing2018}, but has yet to be demonstrated in hydrodynamics simulations.
 
 The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
-It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
-Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
+That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004,Muratov2017,Corlies2018}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+If there are differences in metal coupling to the ISM, this could potentially impact how metals are driven out of galaxies through galactic winds.
+This has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
+However, examining this process has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
+%It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
+% Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
 However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
 
-It is becoming increasingly important to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}.
+It is becoming increasingly valuable to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}.
 Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
 The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM.
-However, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.
+Furthermore, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.
+\textbf{One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Ting2012, Hogg2016,Jofre2017,Price-Jones2018}.
+Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations.
+Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible recently.}
 
@@
 \label{sec:interpretation}
-Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_o = 0$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$.
+Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_{\rm o}$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$.
 Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas.
-In this case, $p(Z)$ takes the form of a double-delta function
+In this case, $p(t,Z)$ initially takes the form of a double-delta function
 \begin{equation}
-p(Z) = \delta(Z) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
+p(t_{\rm o},Z) = \delta(Z_{\rm o}) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
 \end{equation}
-If the enriched material mixes continually with the primordial gas at a constant rate, after some time this gas will have mixed with an equal amount of primordial gas.
-At this point, the high metal fraction delta term becomes $\frac{2M_{\rm ej}}{M_o} \delta(Z - \frac{1}{2}Z_{\rm ej})$.
-This implies an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas, and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$.
-If the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, $p(Z)$ will become a power-law in $Z$, truncated at some time dependent minimum $Z$.
-The slope of the power-law is determined by the rate of injection versus mixing with the ambient medium.
+If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time this gas will have mixed with an equal amount of primordial gas \textbf{(lets take this time to be $\tau_{\rm mix}$).
+Therefore, we would have $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + \frac{2M_{\rm ej}}{M_o} \delta(Z - \frac{1}{2}Z_{\rm ej})$, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + \frac{4M_{\rm ej}}{M_o} \delta(Z - \frac{1}{4}Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.} This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
+\textbf{The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.}
+
+\textbf{Thus, if the gas is continually enriched by identical, well-separated enrichments events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous $p(t,Z)$, or $p(Z)$, of these many events will be a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$, related to the time since enrichment began, and some maximum, $Z_{\rm ej}$.}
+% and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
+The slope of the power-law, then, is determined by the rate of injection versus mixing with the ambient medium.
 A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium.
@@
 In reality, however, $M_o$ is not an inexhaustible reservoir of primordial gas.
-Eventually the entire ambient medium will become enriched to some $Z > Z_o$, and $p(Z)$ will consist entirely of a continuous, truncated power-law.
+Eventually the entire ambient medium will become enriched to some $Z > Z_o$, and $p(Z)$ will consist entirely of a truncated power-law.
 As enrichment proceeds, gas near the low metallicity truncation of $p(Z)$, which still comprises much of the mass of the system, enriches towards higher metallicities in the power-law tail.

### 2018-07-31 main.tex

@@
 One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}.
-While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challening.
+While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challenging.
 More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects.
@@
 %Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows. 
-Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018} and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.
-Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.
+Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018}
+% KVJ: citations to high-redshift work in this area
+\textbf{and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.} Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.
 
@@
 Furthermore, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.
+% KVJ asked to bring up this area of research and emphasize how it is lacking theoretical input
 \textbf{One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Ting2012, Hogg2016,Jofre2017,Price-Jones2018}.
 Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations.
-Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible recently.}
+Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.}
 
@@
 
+%mm [this all seems to have been deleted in one version, but doesn't look like it should have been.  Down to ">>>>"] <<<<<<< HEAD
+The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
+We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
+%mm Again, with the exception of  H and He, we [H & He aren't metals]
+    We
+only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+
+We find two major results.
+%mm [reversed order of results to follow figure.  The opposite choice could also be made, by reversing the order of the figure...]
+    First, 
+only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies
+%mm 
+    among elements.
+The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
+This suggests that individual metals \textit{do not} share the same dynamical evolution.
+%mm Clearly
+       Thus, 
+metal enrichment in galaxies is a phenomenon that cannot be fully captured using a single, global metallicity field.
+In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
+
+    Second,
+nearly all of the metals 
+%mm
+    retained in the disk
+reside within neutral gas, mostly in the CNM; only a few percent
+reside in the hot phases.
+The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
+This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
+
 The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
@@
 In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
+%mm [end of apparently deleted section] >>>>>>> 134a2fabac2aea2275cb3e8014308282b438742f
 
@@
 
+%mm I think this material duplicates the first paragraph of the introduction.
+% Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
+In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}).
+Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances.
+In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
+%mm However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
+To build towards this, we characterize the metal evolution and distributions in our galaxy below.
+      We characterize the metal distributions (in Sections~\ref{sec:log-normal} and \ref{sec:phase-pdfs}) and evolution (in Section~\ref{sec:statistics}) in our galaxy to build towards a  a complete model for how metals mix and evolve in the complex, multi-phase ISM of real galaxies.
+
 %mm should most of this material be in the introduction, and just the last two sentences be here?
@@
 Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances.
-In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
+%In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
 However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
@@
 For O, the median mass fraction is ordered by phase temperature.
-The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm$ 1 dex over the simulation time.
+The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm 1$ dex over the simulation time.
 The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
@@
 The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star forming gas.
-This is the only explanation for how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels).
-Individual enrichment events will have significantly higher metallicities than the ambient ISM in any phase, and will drive an increase in the difference between the mean and median of the PDF.
+This
+%mm is the only explanation for [that's perhaps too strong a claim]
+    can explain
+how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels). Individual enrichment events 
+%mm will 
+have significantly higher metallicities than the ambient ISM in any phase, and 
+%mm will 
+drive an increase in the difference between the mean and median of the PDF.
 These can be seen as the obvious spikes in the HIM and WIM.
@@
 The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
-These tails represent the most recently enriched gas, and is clearly much more locally confined than O.
+These tails represent the most recently enriched gas,
+%mm and 
+        which
+is clearly much more locally confined than O.
 
 %{\bf (move to discussion?)}:
-The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e.
-the ratio between the total mass of metals and the total mass).
-Assuming star forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex), but significant, for elements released during SNe explosions, but can be very significant, up to $\sim$ 0.8 dex, for elements released in AGB winds.
-Chemical evolution models, especially one-zone models, follow the mean metal fraction, not median.
-These results indicate that these models are biased to overestimate gas and stellar elemental abundances.
+The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e.\ the ratio between the total mass of metals and the total mass).
+Assuming star forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex),
+%mm but
+   though 
+significant, for elements released during SNe explosions, but can be very significant, up to $\sim$ 0.8 dex, for elements released in AGB winds.
+Chemical evolution models, especially one-zone models, follow the mean metal fraction, rather than the median.
+%mm These results indicate that these 
+            Our results indicate that such
+models are biased to overestimate gas and stellar elemental abundances.
 . % However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.
 
-To summarize, this figure demonstrates: 1) there are qualitative differences in how supernova injected elements (e.g.
+To summarize, Figure~\ref{fig:phase-statistics} demonstrates: 1) there are qualitative differences in how supernova injected elements (e.g.
 O, Mg) and AGB wind injected elements (e.g.
-N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM, 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM, and the hotter phases are more directly populated by recent enrichment events, 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM, 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function, and therefore 5) the median metallicity available for star formation rates lies below the mean galactic value.
+N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM; 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM and because the hotter phases are more directly populated by recent enrichment events; 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM; 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function; and therefore 5) the median metallicity available for star formation
+%mm rates 
+lies below the mean galactic value.
 In the case of supernova injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
@@
 \label{sec:interpretation}
+%
+% KVJ wanted clarification on this argument. I believe my added text 
+% does this sufficiently.
 Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_{\rm o}$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$.
@@
 \begin{equation}
+
 p(t_{\rm o},Z) = \delta(Z_{\rm o}) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
 \end{equation}
-If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time this gas will have mixed with an equal amount of primordial gas \textbf{(lets take this time to be $\tau_{\rm mix}$).
-Therefore, we would have $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + \frac{2M_{\rm ej}}{M_o} \delta(Z - \frac{1}{2}Z_{\rm ej})$, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + \frac{4M_{\rm ej}}{M_o} \delta(Z - \frac{1}{4}Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.} This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
+%mm [edited the rest of this paragraph, and the next though I don't think there are any substantive changes unmarked.]
+If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time  $\tau_{\rm mix}$ this gas will have mixed with an equal amount of primordial gas.
+\textbf{At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.} This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
 \textbf{The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.}
 
-\textbf{Thus, if the gas is continually enriched by identical, well-separated enrichments events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous $p(t,Z)$, or $p(Z)$, of these many events will be a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$, related to the time since enrichment began, and some maximum, $Z_{\rm ej}$.}
+\textbf{Thus, if the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous distribution $p(t,Z)$
+%mm , or $p(Z)$, 
+of these many events will be a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.}
 % and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
@@
 A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium.
-Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than enrichment.
+Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than
+%mm enrichment. 
+         injection.
 If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.
@@
 The low-turnover limit is produced by diffusion from many different sources, and is thus an additive process, which, as we noted above, tends to produce log-normal distributions.
+%mm [additive vs multiplicative]
+   {\bf [According to Section~\ref{sec:log-normal}, MULTIPLICATIVE processes produce log-normals. Additive processes produce power-laws.  However, see Mouri (2013) for a possible counterexample...]}
 The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.
@@
 This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases. 
-The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions.
-Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low-metallicities.
+%mm The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions. 
+     Individual enrichment events start at very high metal fractions in the low-density HIM, 
+     so they easily create long power-law tails.
+Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low metallicities.
 Cold, dense gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.
@@
 %
+
 Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}.
@@
 
+% From benoit: more explicit title
 \subsection{Context With Previous Studies of Metal Mixing}
@@
 \label{sec:stellar abundances}
-% AE: Possibly need better general introduction to CE models / sims and importance of understanding stellar abundances (obs+theory)
 In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star forming gas in our simulations.
@@
 
-%
+%KVJ suggested emphasizing that there is much more potential in this work / work like this by examining more dimensions
+\textbf{We emphasize that this study focuses on each chemical dimension independently, as a means to first understand galactic chemical enrichment in the simplest possible framework.
+However, the cross-correlation of multiple metal fractions and abundance ratios is the most useful in revealing key processes in galactic chemodynamics.
+A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiemnts.
+We will examine this more complicated multi-dimensional space with these simulations in future work.}
 
@@
 
+% AE: Capitalized header
 \subsection{Do These Results Apply to More Massive Galaxies?}
@@
 One important caveat about our work is that these results are derived from simulations of an isolated, low mass dwarf galaxy whose properties vary dramatically from a more massive galaxy like the Milky Way.
-It is unclear how much of these results apply to more massive galaxies given their deeper potential wells and higher star formation rates.
+It is unclear how much these results apply to more massive galaxies given their deeper potential wells and higher star formation rates.
 Feedback driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
@@
 With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
+\textbf{We anticipate three potential regimes of metal retention, related directly to dark mater halo mass and SFR, whereby: i) at very low halo mass, below that examined here, there is equally poor retention of metal enrichment from both AGB and SNe, ii) AGB enrichment is preferentially retained, but SNe enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.}.
 If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
-%If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+% AE: rewording given Benoits suggested changes
+%     If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
 This difference would be greater at later times, once AGB enrichment becomes significant. 
@@
 In addition, the elevated signals of Ba abundance ratios I mention have some amount of contention....
-%For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
+%     For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
 At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way.
@@
 Given the lack of definitive explanation, clearly generalizing our results and detailing their observational consequences is a valuable area of future research.
-If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+We would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
 
@@
 
-%
-% moved to possible to-do list below,
-%
 \subsection{Implications for Exotic Enrichment Sources}
 \label{sec:exotic enrichment}
+%   AE: Benoit suggested removing arguments relating to NS-NS merger energetics as I had misred / miscaclulated the energy release values.
+He said greater emphasise on potential differences of mixing due to rarity, rather than energy.
 We have shown that the dynamical evolution of metals depends upon their nucleosynthetic source, focusing here on AGB synthesized elements and supernova synthesized elements.
@@
 Based on our results here, we would expect elements from HNe to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe.
-%Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies. 
+% Benoit suggesed removing this given energy argument removal above
+%    Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies. 
 Depending on their injection energy, NSMs could exhibit different mixing behaviors in the ISM.
@@
 
-\item Metal outflow in low mass dwarf galaxies depends upon nucleosynthetic origin.
+\item Metal outflow in low mass dwarf galaxies depends upon nucleosynthetic site.
 Metals from lower energy enrichment events (e.g.
@@
 But interpreting these results for low mass dwarf galaxies, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
+% Removed as-per Benoit's suggestion:
+% , and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements
 

### 2018-07-31 ms.tex
Update on Overleaf.

--- 2018-07-27 ms.tex
@@
 But even with this strong feedback, recent work has argued for the need for pre-SN feedback, from stellar winds and/or stellar radiation \citep[e.g.][]{Hu2016,Hopkins2018}, though this is typically modeled simply as additional energy injection around newly formed stars.
-The need for additional feedback is confirmed by simulations that are capable of fulling resolving individual SN \citep[e.g.][]{Hu2017,Peters2017}.
+The need for additional feedback is confirmed by simulations that are capable of fully resolving individual SN \citep[e.g.][]{Peters2017,Hu2018}.
 However, modeling these processes in detail is challenging, and their competing effects on galactic evolution are poorly constrained.}
@@
 Rays begin on HEALPix refinement level 2, with a maximum refinement level of 13 (or $8.05 \times 10^8$ rays).
+\textbf{We include radiation pressure on hydrogen (single-scattering), but do not investigate its importance in this work \citet[see][]{WiseAbel2012}.}
 

### 2018-07-31 main.tex
supernova -> SN; more revisions to section 4

@@
 Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component.
-In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe).
+In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment, such as N and Ba, mix less efficiently than elements dominated by supernova enrichment, such as $\alpha$ elements and Fe.
 This difference is driven by the differences in
@@
 Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution.
-One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites (from stellar winds or supernovae) and mix through the phases of the interstellar medium (ISM) into star forming gas.
+One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites from stellar winds or supernovae (SNe) and mix through the phases of the interstellar medium (ISM) into star-forming gas.
 %
@@
 
-In addition, it remains to be seen to what degree, if at all, metals of different enrichment origins (AGB winds, core collapse supernovae, Type Ia supernovae, neutron-star neutron-star mergers, etc.) may couple differently to the ISM.
+In addition, it remains to be seen to what degree, if at all, metals of different enrichment origins (AGB winds, core collapse SNe, Type Ia SNe, neutron-star neutron-star mergers, etc.) may couple differently to the ISM.
 When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly.
 However, if metals do not behave uniformly in the ISM, if their mixing and ejection behavior depends directly upon the energetics and physical environment of their injection, then this assumption would need to be re-evaluated.
-Differences in metal distributions from ejecta in AGB stars, as compared to supernovae, has been explored recently in \cite{KrumholzTing2018}, but has yet to be demonstrated in hydrodynamics simulations.
+Differences in metal distributions from ejecta in AGB stars, as compared to SNe, has been explored recently in \cite{KrumholzTing2018}, but has yet to be demonstrated in hydrodynamics simulations.
 
@@
 It is becoming increasingly valuable to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}.
-Stellar abundances are directly imprinted with the enrichment pattern of their star forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
+Stellar abundances are directly imprinted with the enrichment pattern of their star-forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
 The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM.
@@
 The simulation discussed here was introduced in detail in \cite{Emerick2018} (hereafter Paper I).
-To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia SNe.
 This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below.
@@
 \paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually.
-Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
+Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse SNe at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
 Stars above this mass are assumed to direct collapse with no mass or energy injection.
@@
 Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind \citep{Goldman2017}.
-Stars with $3 < M_{*} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
+Stars with $3 < M_{*} < 8$ are tracked after their death as possible Type Ia SN progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
 Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et.
 al.
-in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.
+in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia SNe.
 
@@
 Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium.
-The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
+The galaxy contains no initial background stellar population, limiting the number of Typa Ia SNe in our model, but we do provide initial SN driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
 Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
@@
 These channels differ in both when metals are ejected, as determined by stellar evolution, and the phase of the ISM into which they are ejected.
-We note that the minimal contribution from Type Ia supernovae for the iron-peak elements is because  no older stellar population was initialized, so only 16 of them have exploded by the end of our 500~Myr simulation.}
+We note that the minimal contribution from Type Ia SNe for the iron-peak elements is because  no older stellar population was initialized, so only 16 of them have exploded by the end of our 500~Myr simulation.}
 
@@
 
-The only physics that separates the dynamical evolution of these elements in our simulations is the individual sources of enrichment: AGB winds (stars less than 8~M$_{\odot}$), stellar winds (stars above 8~M$_{\odot}$), core collapse supernovae, and Type Ia supernovae.
+The only physics that separates the dynamical evolution of these elements in our simulations is the individual sources of enrichment: AGB winds (stars less than 8~M$_{\odot}$), stellar winds (stars above 8~M$_{\odot}$), core collapse SNe, and Type Ia SNe.
 These channels differ in: 1) how long after a given star formation event they occur, 2), by consequence, the typical ISM properties in which they occur, and 3) how much energy is associated with each event, which determines ejecta temperature and velocity.
 To understand where each of the elements in Figure~\ref{fig:species_fractions} originated, we show the mass fraction of metals produced through each channel in Figure~\ref{fig:species_sources}.
-Core collapse supernovae are responsible for over 90\% of the total metal enrichment in our galaxy, but this is clearly not true for all elements.
+Core collapse SNe are responsible for over 90\% of the total metal enrichment in our galaxy, but this is clearly not true for all elements.
 In particular, a majority of N (74\%) and Ba (65\%) are ejected by AGB winds; both are retained at a higher rate than the rest of the metals.
-That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yield tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through supernovae.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and supernovae.
+That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yield tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through SNe.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and SNe.
 However, this cannot be proven as we lack Lagrangian information about individual gas elements.}
@@
 
-AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of supernovae ($\sim$1000~km~s$^{-1}$).
+AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of SNe ($\sim$1000~km~s$^{-1}$).
 In addition, their longer timescales relative to massive stars means that AGB stars are typically removed from their birth regions and randomly distributed through the galactic disk.
@@
 We show histograms of the average number density within 20~pc of any given enrichment source (top) and height above/below the disk (bottom) within 1~Myr of each event (as limited by our output cadence) in Figure~\ref{fig:spatial distribution}.
-As shown, SN peak at very low densities, indicating that most explode in superbubbles, regions carved out by previous SNe.
+As shown, SNe peak at very low densities, indicating that most explode in superbubbles, regions carved out by previous SNe.
 AGB stars predominately release their metals close to the average ISM density.
@@
 We do not expect these differences to be the dominant effect in driving the differential evolution of elements ejected by AGB winds vs.
-supernovae, compared to the energetics, but can certainly play a significant role in determining the mixing behavior of individual enrichment events.
+SNe, compared to the energetics, but can certainly play a significant role in determining the mixing behavior of individual enrichment events.
 The changes to mixing behavior as a function of ISM properties will be investigated in more detail in a future work.
@@
 Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$.
-As this is the source of star forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.
+As this is the source of star-forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.
 
@@
 
-Unsurprisingly the diffuse HIM contains the most metal enriched gas, as it is comprised predominately of metal enriched supernova ejecta.
+Unsurprisingly the diffuse HIM contains the most metal enriched gas, as it is comprised predominately of metal enriched SN ejecta.
 Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
@@
 Although these trends across phases hold for all elements, there are qualitative differences between elements, particularly between those ejected predominantly by AGB winds (e.g.
-Ba and N) and those ejected by supernovae (e.g.
+Ba and N) and those ejected by SNe (e.g.
 O and Mg).
-In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by supernova enrichment.
+In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by SN enrichment.
 The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the CNM.
-Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N included in supernovae yields.
-Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and supernovae.
+Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N included in SNe yields.
+Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and SNe.
 AGB wind elements enrich the WNM and WIM directly, rather than the HIM, which would increase their mixing timescales and broaden their PDFs.
@@
 Figure~\ref{fig:phase-statistics} shows the evolution of four different statistics for the O (top) and Ba (bottom) PDFs.
-These two elements are treated as representative elements for supernova and AGB wind production respectively.
+These two elements are treated as representative elements for SN and AGB wind production respectively.
 The difference between the mean and median masses of the PDF (second column) is a measure of the skew of the PDF.
@@
 Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread.
-The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star forming gas.
+The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star-forming gas.
 This
@@
 The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
-Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in supernovae.
+Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in SNe.
 The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
@@
 The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e.\ the ratio between the total mass of metals and the total mass).
-Assuming star forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex),
+Assuming star-forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex),
 %mm but
@@
 
-To summarize, Figure~\ref{fig:phase-statistics} demonstrates: 1) there are qualitative differences in how supernova injected elements (e.g.
+To summarize, Figure~\ref{fig:phase-statistics} demonstrates: 1) there are qualitative differences in how SN injected elements (e.g.
 O, Mg) and AGB wind injected elements (e.g.
-N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM; 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM and because the hotter phases are more directly populated by recent enrichment events; 3) the cooler, denser phases, particularly for supernova injected elements, are more well mixed than the hot phases of the ISM; 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function; and therefore 5) the median metallicity available for star formation
+N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM; 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM and because the hotter phases are more directly populated by recent enrichment events; 3) the cooler, denser phases, particularly for SN injected elements, are more well mixed than the hot phases of the ISM; 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function; and therefore 5) the median metallicity available for star formation
 %mm rates 
 lies below the mean galactic value.
-In the case of supernova injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
+In the case of SN injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
 For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.
@@
 This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
-It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing supernovae.
-Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star forming gas.
+It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing SNe.
+Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star-forming gas.
 Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy.
@@
 % From benoit: more explicit title
-\subsection{Context With Previous Studies of Metal Mixing}
+\subsection{
+%mm Context With 
+        Comparison with 
+Previous Studies of Metal Mixing}
 \label{sec:context}
-That metal fraction distributions can be described using a simple analytic log-normal + power-law PDFs, even in a complex, multi-phase ISM, has not been demonstrated prior to this work.
+That metal fraction distributions can be described using simple analytic log-normal + power-law PDFs, even in a complex, multi-phase ISM, has not been demonstrated prior to this work.
 In addition, this is the first work to demonstrate differential mixing behavior of individual metal species using 3D hydrodynamics simulations.
-However, there does exist a significant body of work investigating the mixing behavior of passive scalars in a variety of contexts, as discussed below.
-\cite{KrumholzTing2018} predict differential behavior for AGB wind and core collapse supernova synthesized elements as a direct consequence of the differences in size of typical planetary nebulae ($\sim$ 0.1~pc) and supernova remnants ($\sim$ 100~pc).
+However, there does exist a significant body of work investigating the mixing behavior of passive scalars in a variety of contexts.
+%mm , as discussed below.  [ moved KrumholzTing18 to end of following paragraph.]
 %We discuss our results further in the context of previous research on metal mixing in the ISM and speculate on the physical processes that drive the evolution of these PDFs across phases.
@@
 to global galaxy models studying generalized advection and mixing of passive scalars \citep[e.g.][]{deAvillez2002,Petit2015,Goldbaum2016} to models with more detailed self-consistent metal enrichment \citep[e.g.][]{Revaz2009,Escala2018}.
+\cite{KrumholzTing2018} predict differential behavior for AGB wind and core collapse SN synthesized elements as a direct consequence of the differences in size of typical planetary nebulae ($\sim$ 0.1~pc) and SN remnants ($\sim$ 100~pc).
 
@@
 \label{sec:discussion:metal yields}
-We can generally say that metals produced in AGB winds evolve qualitatively differently in dwarf galaxies than metals produced through supernovae.
+We can generally say that metals 
+%mm produced
+    ejected 
+in AGB winds evolve qualitatively differently than metals produced by SNe in 
+%mm dwarf galaxies 
+     our dwarf galaxy. 
 However, exactly which metals exhibit these differences, and to what degree, is timescale and metallicity dependent.
-Short-timescales ($\lesssim 100$~Myr) only samples enrichment from the most massive AGB stars, which stars on order of a few solar masses enrich on 1 Gyr timescales or longer.
-In our simulations, which only sample 500 Myr of evolution, N and Ba are dominated from AGB wind ejecta.
-C is commonly used to track AGB wind enrichment, but as it originates from lower mass AGB stars, C enrichment operates on $\sim$ Gyr timescales, longer than we follow in this work.
-This additionally varies with metallicity.
-Sr, for example, is only significantly ejected through AGB winds at our metallicity on $\sim$~Gyr timescales; stellar winds from more massive stars dominate the production of Sr on shorter timescales.
-At higher metallicity, much more Sr is produced through massive AGB stars, decreasing the timescale over which Sr should exhibit a differential chemical evolution as compared to supernovae ejected elements.
+Short timescales ($\lesssim 100$~Myr) only sample enrichment from the most massive AGB stars,
+%mm which 
+     while 
+stars on order of a few solar masses 
+%mm 
+    only
+enrich on timescales of a gigayear or longer. In our simulations, which only 
+%mm sample
+   simulate 
+500 Myr of evolution, N and Ba are dominated 
+%mm from 
+     by
+AGB wind ejecta.
+C is commonly used to track AGB wind enrichment, but as it originates from lower mass AGB stars, C enrichment operates on gigayear timescales, longer than we follow in this work.
+Enrichment additionally varies with metallicity.
+Sr, for example, is only significantly ejected through AGB winds at our metallicity on gigayear timescales, while stellar winds from more massive stars dominate the production of Sr on shorter timescales.
+At higher metallicity, much more Sr is produced through massive AGB stars, decreasing the timescale over which Sr should exhibit a differential chemical evolution compared to SN-ejected elements.
 
-To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected through AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times.
+To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected by AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times.
 This model was run using \textsc{SYGMA} \citep{Ritter2017}.
-As shown, metal enrichment from AGB winds only begins to dominate for a given species at $\sim$ 100 Myr.
-This includes N and Ba, as followed in our simulations, but this plot indicates that Ag and Pb should show similar bahavior.
-It takes over a Gyr for C to be dominated from AGB wind ejecta, which is the case for many of the elements shown.
-F, which shows very little contribution from AGB winds at short timescales is dominated by enrichment on longer timescales.
-These dependences on metallicity and timescales certainly adds complications in generalizing our work and in interpreting observations in the context of the results presented here, but these difference could be leveraged to better understand galactic chemical evolution on multiple, distinct timescales.
-Clearly this motivates future work covering Gyr timescales to fully understand how metal mass fraction PDFs evolve with time.
+As shown, metal enrichment from AGB winds only begins to dominate for
+%mm a given species at 
+    any elements after 
+$\sim$ 100 Myr. This includes N and Ba, which we follow in our simulations, but this 
+%mm plot indicates
+    model predicts 
+that Ag and Pb 
+%mm should 
+     will
+show similar bahavior.
+It takes over a gigayear for C to be dominated by AGB wind ejecta, which is the case for many of the elements shown.
+F, which shows very little contribution from AGB winds at short timescales, is dominated by enrichment from them on longer timescales.
+These dependences on metallicity and timescales certainly add complications in generalizing our work and in interpreting observations in the context of the results presented here, but these difference could be leveraged to better understand galactic chemical evolution on multiple, distinct timescales.
+Clearly this motivates future work covering gigayear timescales to fully understand how metal mass fraction PDFs evolve with time.
 
@@
 \includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0.png}
-\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, with no continual star formation.
-We only show a sample of some of the elements dominated most by AGB enrichment.
-The horizontal line marks 50\% contribution.}
+\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, without continuing star formation.
+We only show a sample of some of the elements dominated most by AGB enrichment at late times.
+The horizontal line marks a 50\% contribution.}
 \label{fig:agb evolution}
@@
 \label{sec:stellar abundances}
-In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star forming gas in our simulations.
+In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star-forming gas in our simulations.
 This could be used to help disentangle sources of scatter in observed stellar abundance, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
-If the star forming gas in our simulations can also be well-fit by a log-normal + power-law PDF, and if we can parameterize their evolution as functions of global galaxy properties, this can be used as a powerful and analytic tool for modeling stellar abundance patterns in semi-analytic models.
+If the
+%mm star-forming gas in our simulations can also be well-fit by a log-normal + power-law PDF
+        elemental abundances in star-forming gas in our simulations can also be well fit by 
+        log-normal + power-law PDFs,
+and if we can parameterize their evolution as functions of global galaxy properties, this %mm can 
+    could
+be used as a powerful 
+%mm and analytic 
+tool for modeling stellar abundance patterns in semi-analytic models.
 This would be a physically motivated way to account for both the intrinsic spread in stellar abundances due to inhomogeneities in the ISM and variations in mixing for different metal species.
-We reserve an analysis of these distributions in abundance space in both the gas and stars for a future work.
-However, we briefly discuss the connection to star forming gas and stellar enrichment below.
+We reserve an analysis of these distributions in abundance space in both the gas and stars for future work.
+However, we briefly discuss the connection to star-forming gas and stellar enrichment below.
 
-Unfortunately, there is insufficient star forming gas at any one time in these simulations to construct a PDF of metal distributions.
-However, star forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, follow a similar PDF to the CNM.
+Unfortunately, there is insufficient star-forming gas at any one time in our simulations to construct PDFs of 
+%mm metal distributions
+    elemental abundances. 
+However, star-forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, 
+%mm follow a similar PDF 
+   to have abundance PDFs similar
+to the CNM.
 To verify this, Figure ~\ref{fig:stars} shows the difference between the oxygen mass fraction of stars and the median mass fraction from the CNM PDF at the time that particle formed.
@@
 Though a significant deviation, this is smaller than the typical inner-quartile range (IQR) of the CNM (see Figure~\ref{fig:phase-statistics}).
-Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
-High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
+Additionally, if we further subdivide the CNM by density, the
+%mm metal fraction 
+    abundance
+PDFs narrow and tend towards the median value as a function of increasing density. High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
 
@@
 However, the cross-correlation of multiple metal fractions and abundance ratios is the most useful in revealing key processes in galactic chemodynamics.
-A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiemnts.
-We will examine this more complicated multi-dimensional space with these simulations in future work.}
+A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiements.
+We will examine this more complicated multi-dimensional space with these
+%mm simulations 
+   numerical methods
+in future work.}
 
@@
 \includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
-\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the within 1~Myr (our time resolution) of each star's formation time.
-The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
+\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the
+%mm
+    time 
+within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
 \label{fig:stars}
@@
 \label{sec:massive galaxies}
-One important caveat about our work is that these results are derived from simulations of an isolated, low mass dwarf galaxy whose properties vary dramatically from a more massive galaxy like the Milky Way.
-It is unclear how much these results apply to more massive galaxies given their deeper potential wells and higher star formation rates.
-Feedback driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
+%mm One
+   An 
+important caveat about our work is that these results are derived from simulations of an isolated, low mass, dwarf galaxy whose properties vary dramatically from more massive galaxies like the Milky Way.
+It is unclear how much these results apply to more massive galaxies
+%mm given their 
+     with
+deeper potential wells and higher star formation rates.
+Feedback-driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
 We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy.
 With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
-\textbf{We anticipate three potential regimes of metal retention, related directly to dark mater halo mass and SFR, whereby: i) at very low halo mass, below that examined here, there is equally poor retention of metal enrichment from both AGB and SNe, ii) AGB enrichment is preferentially retained, but SNe enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.}.
+\textbf{We anticipate three potential regimes of metal retention,
+%mm related directly to 
+    depending on
+dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB 
+%mm
+    stars 
+and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.}.
 If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
@@
 
-In contrast, we expect the properties of the enrichment PDFs, and the variations between AGB enriched elements and supernova enriched elements (as presented in Figures~\ref{fig:log-normal} and ~\ref{fig:phase-statistics}), to be general.
+In contrast, we expect the properties of the enrichment PDFs, and the variations between AGB enriched elements and SN enriched elements (as presented in Figures~\ref{fig:log-normal} and ~\ref{fig:phase-statistics}), to be general.
 We expect metals to exhibit log-normal + power-law distributions in the ISM of all galaxies, with similar trends with enrichment source and gas phase as outlined here.
@@
 He said greater emphasise on potential differences of mixing due to rarity, rather than energy.
-We have shown that the dynamical evolution of metals depends upon their nucleosynthetic source, focusing here on AGB synthesized elements and supernova synthesized elements.
+We have shown that the dynamical evolution of metals depends upon their nucleosynthetic source, focusing here on AGB synthesized elements and SN synthesized elements.
 However, these differences should also apply to exotic enrichment sources, such as hypernovae (HNe), neutron-star neutron-star mergers (NSM), and neutron star - black hole mergers.
-These sources can have energies that differ significantly from typical supernova, reaching $> 10^{52}$~erg for HNe \citep{Nomoto2004}, for example.
+These sources can have energies that differ significantly from typical SN, reaching $> 10^{52}$~erg for HNe \citep{Nomoto2004}, for example.
 In addition, the rarity of these events, for example, there are approximately $10^{-5}$ per M$_{\odot}$ of star formation for NSMs \citep{Kim2015} in the Milky Way, could significantly influence the typical ISM environments within which they eject their metals.
-We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to supernovae.
+We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to SNe.
 Based on our results here, we would expect elements from HNe to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe.
@@
 This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze how individual metal species couple to the galactic winds and ISM of this galaxy.
-We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, core collapse supernovae, and Type Ia supernovae).
-This difference is most significant in our model between elements ejected predominately through AGB winds and those ejected predominantly by core-collapse supernovae.
+We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, core collapse SNe, and Type Ia SNe).
+This difference is most significant in our model between elements ejected predominately through AGB winds and those ejected predominantly by core-collapse SNe.
 In addition, we find for the first time that the metal mass fraction PDFs of each metal in the ISM can be described using an analytic piece-wise log-normal + power-law PDF.
@@
 %\item Elements from lower energy enrichment sources (i.e.
-AGB winds) are preferentially retained in the ISM of low mass dwarf galaxies as compared to those from higher energy sources (supernovae), which are more readily launched in galactic winds.
+AGB winds) are preferentially retained in the ISM of low mass dwarf galaxies as compared to those from higher energy sources (SNe), which are more readily launched in galactic winds.
 This result is likely sensitive to global galaxy properties, becoming less significant with increasing halo mass.

### 2018-07-31 ms.tex
including Smith references in introduction. couple typos. removing repeated bibtex entries

@@
 \author{Andrew Emerick}
-\affil{Columbia University}
+\affil{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
 \affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}
@@
 \author{Greg L. Bryan}
-\affiliation{Columbia University}
-\affiliation{Flatiron Institute}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
 
@@
 \affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}
-\affiliation{Columbia University}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
 
@@
 But even with this strong feedback, recent work has argued for the need for pre-SN feedback, from stellar winds and/or stellar radiation \citep[e.g.][]{Hu2016,Hopkins2018}, though this is typically modeled simply as additional energy injection around newly formed stars.
-The need for additional feedback is confirmed by simulations that are capable of fully resolving individual SN \citep[e.g.][]{Peters2017,Hu2018}.
+The need for additional feedback is confirmed by simulations that are capable of fully resolving individual SN \citep[e.g.][]{Peters2017,Smith2018a,Smith2018b,Hu2018}.
 However, modeling these processes in detail is challenging, and their competing effects on galactic evolution are poorly constrained.}
@@
 In this work we use a detailed model for stellar feedback presented in \cite{Emerick2018} (hereafter Paper I) to study the role of radiation feedback in dwarf galaxy evolution.
-For the first time in a galaxy-scale simulation, we resolve individual HII using an adaptive ray tracing radiative transfer method to follow the ionizing radiation from particles that represent individual stars.
+For the first time in a galaxy-scale simulation, we resolve individual HII rgeions using an adaptive ray tracing radiative transfer method to follow the ionizing radiation from particles that represent individual stars.
 We focus on addressing two questions: 1) what role does radiation feedback play in regulating star formation, and 2) are the long-range effects of radiation feedback important, or is the local destruction of dense gas the dominant effect.

### 2018-07-31 main.tex
working on conclusions.

@@
 %mm star-forming gas in our simulations can also be well-fit by a log-normal + power-law PDF
-        elemental abundances in star-forming gas in our simulations can also be well fit by 
-        log-normal + power-law PDFs,
-and if we can parameterize their evolution as functions of global galaxy properties, this %mm can 
+        metal mass fractions in star-forming gas in our simulations 
+        can also be well fit by log-normal + power-law PDFs,
+and if we can parameterize their evolution as functions of global galaxy properties, this 
+%mm can 
     could
@@
 %mm metal distributions
-    elemental abundances. 
+    metal mass fractions. 
 However, star-forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, 
 %mm follow a similar PDF 
-   to have abundance PDFs similar
+   to have mass fraction PDFs similar
 to the CNM.
@@
 Though a significant deviation, this is smaller than the typical inner-quartile range (IQR) of the CNM (see Figure~\ref{fig:phase-statistics}).
-Additionally, if we further subdivide the CNM by density, the
-%mm metal fraction 
-    abundance
-PDFs narrow and tend towards the median value as a function of increasing density. High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
+Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
+High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
 
@@
 We have shown that the dynamical evolution of metals depends upon their nucleosynthetic source, focusing here on AGB synthesized elements and SN synthesized elements.
-However, these differences should also apply to exotic enrichment sources, such as hypernovae (HNe), neutron-star neutron-star mergers (NSM), and neutron star - black hole mergers.
-These sources can have energies that differ significantly from typical SN, reaching $> 10^{52}$~erg for HNe \citep{Nomoto2004}, for example.
-In addition, the rarity of these events, for example, there are approximately $10^{-5}$ per M$_{\odot}$ of star formation for NSMs \citep{Kim2015} in the Milky Way, could significantly influence the typical ISM environments within which they eject their metals.
+However, these differences should also apply to exotic enrichment sources, such as hypernovae, neutron-star neutron-star mergers, and neutron-star black-hole mergers.
+These sources can have energies that differ significantly from typical SNe, reaching $> 10^{52}$~erg for hypernovae \citep{Nomoto2004}, for example.
+In addition,
+%mm the rarity of these events, for example,  there are approximately $10^{-5}$ per M$_{\odot}$ of star formation NSM in the Milky Way, could
+     these events are rare.  For example, neutron star mergers occur 
+     at a rate of approximately $10^{-5}$ per M$_{\odot}^{-1}$ of star
+     formation in the Milky Way\citep{Kim2015}.  This rarity could 
+significantly influence the typical ISM environments into which they eject their metals.
 We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to SNe.
-Based on our results here, we would expect elements from HNe to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe.
+Based on our results here,
+%mm
+     for example,
+we would expect elements from hypernovae to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe. 
 % Benoit suggesed removing this given energy argument removal above
 %    Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies. 
-Depending on their injection energy, NSMs could exhibit different mixing behaviors in the ISM.
+Depending on their injection energy, neutron star mergers could exhibit different mixing behaviors in the ISM.
 These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
@@
 \label{sec:conclusions}
-For the first time we present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
-This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze how individual metal species couple to the galactic winds and ISM of this galaxy.
-We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, core collapse SNe, and Type Ia SNe).
-This difference is most significant in our model between elements ejected predominately through AGB winds and those ejected predominantly by core-collapse SNe.
-In addition, we find for the first time that the metal mass fraction PDFs of each metal in the ISM can be described using an analytic piece-wise log-normal + power-law PDF.
+%mm For the first time we 
+We present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
+This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze
+%mm
+      for the first time
+how individual metal species couple to the ISM and galactic wind of this galaxy.
+We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, or core collapse SNe)
+%mm , and Type Ia SNe).  [I'm inclined to leave them out as we really didn't model their influence]
+This difference is most significant in our model between elements ejected predominately by AGB winds and those ejected predominantly by core-collapse SNe. In addition, we find 
+%mm for the first time 
+    the novel result
+that the mass fraction PDFs of each metal in the ISM can be described using an analytic piecewise log-normal + power-law PDF.
 The properties of these PDFs vary with both ISM phase and metal species, again driven mostly by differences in enrichment sources.
@@
 
-\item Power-law tails in metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
+\item Power-law tails 
+%mm in 
+   on log-normal 
+metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
 

### 2018-07-31 ms.tex
typos and rewording

@@
 We use the adaptive mesh refinement hydrodynamics code \textsc{Enzo} \citep{Enzo2014} to evolve an idealized, isolated low mass dwarf galaxy.
-The galaxy is initialized as a smooth exponential disk set in hydrostatic equilibrium with a static dark matter potential \citep{Burkert1995} with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, on a grid with a maximum physical resolution of 1.8~pc.
+The galaxy is initialized as a smooth exponential disk set in hydrostatic equilibrium with a static dark matter potential \citep{Burkert1995} with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, $Z_{\rm gas} = 4\times 10^{-4}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, on a grid with a maximum physical resolution of 1.8~pc.
 We do not model an initial stellar population, but do include random driving from supernovae as an initial source of feedback up until the first explicit star formation in our model.
@@
 Rays begin on HEALPix refinement level 2, with a maximum refinement level of 13 (or $8.05 \times 10^8$ rays).
-\textbf{We include radiation pressure on hydrogen (single-scattering), but do not investigate its importance in this work \citet[see][]{WiseAbel2012}.}
+\textbf{We include radiation pressure on hydrogen (single-scattering), but do not investigate its importance in this work \citep[see][]{WiseAbel2012}.}
 
@@
 As shown in Figure~\ref{fig:metal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation.
+The outflow in noRT is only a factor of a few lower than the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback, so it implies a far lower mass loading factor.
 Because of this difference in SFR,
@@
 \begin{equation}
-    \eta = \frac{ \dot{M}_{\rm out}}{ <\rm{SFR}>_{100 \rm{Myr}}}
-\end{equation}. The brackets indicate time averaging over 100~Myr.
+    \eta = \frac{ \dot{M}_{\rm out}}{ <\rm{SFR}>_{100 \rm{Myr}}}.
+\end{equation} The brackets indicate time averaging over 100~Myr.
 %
@@
 The fiducial run is also the only one of the three with any significant outflow beyond the virial radius.
-The outflow in noRT is only a factor of a few lower than the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback, so it implies a far lower mass loading factor.
 We conclude that radiation feedback allows SNe to be substantially more effective in driving outflows.

### 2018-07-31 ms.tex
updating ocvirk citation

@@
 If radiation couples effectively to the interstellar medium (ISM), it can be a substantial source of additional feedback.
-Simulations including stellar radiation feedback followed through radiative transfer or radiation-hydrodynamics schemes have found it to be effective in regulating star formation and driving galactic winds \citep[e.g.][]{WiseAbel2012,Kim2013a,Sales2014,Oshea2015,Rosdahl2015,Ocvirk2015,Pawlik2015,Peters2017}.
+Simulations including stellar radiation feedback followed through radiative transfer or radiation-hydrodynamics schemes have found it to be effective in regulating star formation and driving galactic winds \citep[e.g.][]{WiseAbel2012,Kim2013a,Sales2014,Oshea2015,Rosdahl2015,Pawlik2015,Ocvirk2016,Peters2017}.
 This occurs in four ways: 1) heating of diffuse gas and preventing the formation of cold, dense star formation regions, 2) destruction of cold, dense gas around recently formed stars, preventing further star formation, 3) momentum input by direct absorption of UV radiation by gas and (in some cases) dust through re-emission and scattering in the infrared, and 4) lowering the typical ISM densities in which SNe occur and greatly increasing their effectiveness.
@@
 Only modeling local stellar radiation feedback is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
-To explore the cause of this difference we compare in Figures~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
+To explore the cause of this difference we compare in Figure~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
 

### 2018-07-31 main.tex
update facilities
Finished my revisions.

@@
 
-\item Hotter phases have metal fraction PDFs that are more enriched with significant power-law tails as compared to cold phases, which have a more dominant log-normal structure.
+\item Hotter phases have metal fraction PDFs that are more enriched, with significant power-law tails as compared to cold phases, which have a more %mm dominant log-normal structure. 
+   prominent log-normal component.
 The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling into dense gas. 
@@
 \item Likewise, metals originating in AGB winds are less well mixed in the ISM compared to metals injected through SNe, with spreads of over 1 dex in cold gas, as compared to 
+%mm [missing text??]
+   {\bf [what?]}
 
 \item Metal distributions exhibit positive skew, such that the mean metal fraction can be anywhere from 0.1 to 1.0 dex above the median metal fraction.
-Simple chemical evolution models, which generally follow the mean abundance, that are unable to account for complex metal mixing physics are likely biased towards higher enrichment values.
+Simple chemical evolution models, which generally follow the mean abundance,
+%mm that are unable to 
+    and thus can not
+account for complex metal mixing physics, are likely biased towards higher enrichment values.
 
@@
 
-We expect these results to be general for more massive galaxies and galaxy properties.
+%mm [you argued above that the wind results would NOT necessarily be general.
+I'm not sure I like the formulation about entrainment of the ambient ISM, though.] We expect these results to be general for more massive galaxies and galaxy properties.
 However, it may be the case that metals couple more uniformly to galactic winds in more massive galaxies as wind driving occurs increasingly through entrainment of the ambient ISM rather than the ejection of individual enrichment events.
 This warrants further examination.
-But interpreting these results for low mass dwarf galaxies, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
+But interpreting these results for low mass dwarf galaxies
+    Extending these results to low-mass dwarf galaxies in general, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
 % Removed as-per Benoit's suggestion:
@@
 We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}.
-We show the mass-weighted PDF ($dm/Md\rm{log}n$) on the left, and the volume-weighted PDF ($dv/Vd\rm{log}n$) on the right.
+We show the mass-weighted PDF ($dm/Md\log n$) on the left, and the volume-weighted PDF ($dv/Vd\log n$) on the right.
 As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution.
@@
 These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.
+
+%mm [you could cut this if you want.]
+     It is worth noting that this PDF shows the rather small cold gas 
+     fraction found in these models in comparison to the Milky Way
+      ISM, where roughly half the mass is found in cold gas 
+      \citep{Ferriere2001}.
 Finally, \cite{Hopkins2013} suggests a different functional form for describing these PDFs across a range of idealized simulations, but it still may be insufficient to fully describe the density PDF in realistic galaxy simulations.
@@
 We perform a resolution test to confirm that the key results of this study are convergent, at least qualitatively.
-Given the variations in star formation rate, feedback effectiveness, and stochasticisty in our model, we do not expect exact numerical convergence in any one quantity.
+Given the variations in star formation rate, feedback effectiveness, and stochasticity in our model, we do not expect exact numerical convergence in any one quantity.
 We conduct two lower resolution simulations with a maximum physical resolution of 3.6 pc and 7.2 pc.
@@
 \includegraphics[width=0.95\linewidth]{O_Ba_resolution_study.png}
-\caption{Resolution comparison at two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.
+\caption{Resolution comparison of two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.
 Compare to Figure~\ref{fig:phase-statistics}.}

### 2018-07-31 main.tex
adding in BWO affils and acknowledgements. minor style edits in text

--- 2018-07-31 main.tex
@@
 \affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI 48824, USA}
-\affiliation{Joint Institute for Nuclear Astrophysics - Center for the Evolution of the Elements, USA}
+\affiliation{Joint Institute for Nuclear Astrophysics -- Center for the Evolution of the Elements, USA}
 \author{Kathryn V. Johnston}
 \affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\author{Brian O'Shea}
-\affiliation{T.B.D.}
+\author{Brian W. O'Shea}
+\affiliation{Department of Computational Mathematics, Science, and Engineering, Michigan State University, East Lansing, MI, 48824, USA}
+\affiliation{Department of Physics and Astronomy, Michigan State University, East Lansing, MI, 48824, USA}
+\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI, 48824, USA}
+\affiliation{Joint Institute for Nuclear Astrophysics -- Center for the Evolution of the Elements, USA}
 
@@
 \begin{equation}
-
 p(t_{\rm o},Z) = \delta(Z_{\rm o}) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
@@
 If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time  $\tau_{\rm mix}$ this gas will have mixed with an equal amount of primordial gas.
-\textbf{At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.} This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
+\textbf{At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$.
+Then, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.} This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
 \textbf{The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.}
@@
 %mm , or $p(Z)$, 
-of these many events will be a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.}
+of these many events will be $\delta(Z_{\rm o})$ plus a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.}
 % and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
@@
 This will produce a turnover at the low $Z$ limit of $p(Z)$.
-The low-turnover limit is produced by diffusion from many different sources, and is thus an additive process, which, as we noted above, tends to produce log-normal distributions.
+The low-turnover limit is produced by diffusion from many different sources, and is thus multiplicative process, which, as we noted above, tends to produce log-normal distributions.
 %mm [additive vs multiplicative]
-   {\bf [According to Section~\ref{sec:log-normal}, MULTIPLICATIVE processes produce log-normals. Additive processes produce power-laws.  However, see Mouri (2013) for a possible counterexample...]}
+   %{\bf [According to Section~\ref{sec:log-normal}, MULTIPLICATIVE processes produce log-normals. Additive processes produce power-laws.  However, see Mouri (2013) for a possible counterexample...]}
 The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.
@@
 PHY-1430152 (JINA Center for the Evolution of the Elements).
-\textbf{K.V.J....}.
-\textbf{B.O....}.
+B.W.O was supported in part by NSF grants PHY-1430152 and AST-1514700, by NASA grants NNX12AC98G, and NNX15AP39G, and by Hubble Theory Grant HST-AR-14315.001-A.
 We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute.
@@
 
-\facilities{Yeti, CCA cluster, Stampede, Pleiades}
+\facilities{XSEDE (Stampede, Stampede-2), ADS} % there is no ApJ kewword for this: NASA HECC (Pleiades)}
 \software{Numpy, Enzo, yt, astropy}

### 2018-07-31 main.tex
commenting out duplicate section in 3.1 from weird merge conflict

@@
 %mm energetics between each source, particularly the poor coupling of AGB winds to the ISM.
-    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
+    source energetics and source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
 Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
@@
 
-The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
+%The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
 We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
@@
 
-We find two major results.
+%We find two major results.
 First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases.
@@
 %mm [you could cut this if you want.]
-     It is worth noting that this PDF shows the rather small cold gas 
-     fraction found in these models in comparison to the Milky Way
-      ISM, where roughly half the mass is found in cold gas 
-      \citep{Ferriere2001}.
+%It is worth noting that this PDF shows the rather small cold gas 
+%     fraction found in these models in comparison to the Milky Way
+%      ISM, where roughly half the mass is found in cold gas 
+%      \citep{Ferriere2001}.
 Finally, \cite{Hopkins2013} suggests a different functional form for describing these PDFs across a range of idealized simulations, but it still may be insufficient to fully describe the density PDF in realistic galaxy simulations.

### 2018-08-01 main.tex
slight updates per BWO comments. Not yet completed. Bolded sections that still need adressing as to not forget

@@
 %Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows. 
-Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018}
+Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017,Sarmento2018}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018}
 % KVJ: citations to high-redshift work in this area
@@
 Differences in metal distributions from ejecta in AGB stars, as compared to SNe, has been explored recently in \cite{KrumholzTing2018}, but has yet to be demonstrated in hydrodynamics simulations.
+Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations \citep[e.g.][]{Cote2018}.
 
@@
 % KVJ asked to bring up this area of research and emphasize how it is lacking theoretical input
-\textbf{One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Ting2012, Hogg2016,Jofre2017,Price-Jones2018}.
+\textbf{One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Freeman2002,Ting2012, Hogg2016,Jofre2017,Price-Jones2018}.
 Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations.
@@
 We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver.
-We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
+We use a 128$^{3}$ base grid with outflow boundary conditions measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
 Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas or 2) a cell's local Jeans length becomes resolved by less than eight cells.
@@
 Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$).
-We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\%.
+We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\% \citep{KrumholzMcKee2005}.
 Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment.
@@
 \paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
-We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$.
+We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an exponential profile with a metal mass fraction of $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$~M$_{\odot}$.
 The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
@@
 This galaxy has an average star formation rate of $1.2~\times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
-The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy.
-The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$.
+The galaxy exhibits strong, feedback-driven outflows that eject a significant amount of gas and metals from the galaxy.
+The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$, where $\eta$ is defined as the mass outflow rate in through a 0.1~$R_{\rm vir}$ annulus centered at 0.25~R$_{\rm vir}$ divided by the 100~Myr averaged SFR.
 These winds eject 95\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.
@@
 \includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
-\caption{The fraction of each metal species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).
-The leftmost bar in each plot shows the sum of all metals.}
+\caption{Top: The mass fraction of each metal species in the \textit{full simulation box} contained in the halo, gas in the galaxy disk, and stars.
+Bottom: The mass fraction of species within \textit{the disk} alone in each phase of the ISM (bottom).
+The leftmost bar in each plot shows the sum of all metals.
+\textbf{AE: Relabel y-axis, space in All Metals and C, larger figures}}
 \label{fig:species_fractions}
-\end{figure}
+\end{figure*}
 
@@
 The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
-We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
+We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).\footnote{The $f_{\rm H_2}$ restriction on the CNM is not relevant in our simulations, as there are no cells with $f_{\rm H_2} > 0.5$.
+$f_{\rm H_2}$ remains below about 0.35 for all cells (see Paper I).}
 %mm Again, with the exception of  H and He, we [H & He aren't metals]
@@
 \label{fig:species_sources}
-\end{figure}
+\end{figure*}
 
@@
 \includegraphics[width=0.95\linewidth]{SE_z.png}
-\caption{The average gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
+\caption{The volume-averaged gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
 \label{fig:spatial distribution}
@@
 of 0.05 dex.
-We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \cite{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins.
+We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \citep{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins.
 The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted.
@@
 We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
-These PDFs have been computed at an arbitrary single point in time, at 270 Myr.
+These PDFs have been computed at an arbitrary single point in time in the middle of the simulation run.
+% 270 Myr
 For clarity, we only show a subset of the 15 elements we follow.
-As shown, there are clear differences in the PDFs across elements of different nucleosynthetic origins and between each phase.
+As shown, there are clear differences in the PDFs across elements of different nucleosynthetic sources (AGB vs.
+SNe) and between each phase.
 However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions.
@@
 We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.
-Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
+Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.
+\textbf{Check colorblindness and add legend}}
 \label{fig:log-normal}
@@
 
+\textbf{cite sarmento and others (see BWO comments)}
 Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}.
@@
 \includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
-\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the
+\caption{\textbf{AE: relabel y axis with [O/H] - [O/H]$_CNM$}The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the
 %mm
@@
 The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling into dense gas.
-% missing text???????????
 
@@
 
-\item Likewise, metals originating in AGB winds are less well mixed in the ISM compared to metals injected through SNe, with spreads of over 1 dex in cold gas, as compared to 
-%mm [missing text??]
-   {\bf [what?]}
+\item Likewise, metals originating in AGB winds are less well mixed in the ISM, with spreads of over 1 dex in cold gas, as compared to metals injected through SNe, with spreads of about 0.5~dex
 
@@
 But interpreting these results for low mass dwarf galaxies
-    Extending these results to low-mass dwarf galaxies in general, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
+    Extending these results to low-mass dwarf galaxies in general, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements released through SNe and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
 % Removed as-per Benoit's suggestion:

### 2018-08-01 ms.tex
Update on Overleaf.

@@
 %
-Effective stellar feedback is used in models of galaxy formation to regulate star formation and to drive realistic galaxy evolution.
-Models typically include energy injection from supernovae as the dominant form of stellar feedback, though often in some form of sub-grid recipe.
+Effective stellar feedback is used in models of galaxy formation to regulate star formation and drive realistic galaxy evolution.
+Models typically include energy injection from supernovae as the dominant form of stellar feedback, often in some form of sub-grid recipe.
 However, it has been recently suggested that pre-SN feedback, from either stellar winds or stellar radiation, is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM).
-As following stellar winds and ionizing radiation is computationally challenging, many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation.
+Following stellar winds and ionizing radiation is computationally challenging, so many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation.
 In this work we use high resolution simulations (1.8~pc) of an isolated dwarf galaxy with detailed stellar feedback tracked on a star-by-star basis.
@@
 %
-While the fiducial run reaches a peak $\eta$ of a few hundred, shortrad is consistently an order of magnitude or more below this. noRT is even lower.
+While the fiducial run reaches a peak $\eta$ of a few hundred, shortrad is consistently an order of magnitude or more below this. The noRT simulation is even lower.
 
@@
 importance of localized ionization vs.\ ionization from a diffuse radiation field far from a single star.
-Only modeling local stellar radiation feedback is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
+Modeling only local stellar ionizing feedback is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
 To explore the cause of this difference we compare in Figure~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
@@
 In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas.
-Though they make a significant local impact on the ISM, they are unable to drive significant mass loss from the galaxy.
-In the noRT case, an outflow does eventually develop, but it takes the factor of five increase in SFR, and corresponding increase in supernova rate, for SNe to finally break out from the neutral gas surrounding the galaxy.
+Though they make an important local impact on the ISM, they are unable to drive significant mass loss from the galaxy.
+In the noRT case, an outflow does eventually develop, but it takes a factor of five increase in SFR, and a corresponding increase in supernova rate, for SNe to finally break out from the neutral gas surrounding the galaxy.
 
@@
 \section{Conclusion}  \label{sec:conclusion}
-In agreement with previous work we find that stellar radiation feedback is effective in regulating star formation and driving outflows in our simulations of an isolated, low mass, dwarf galaxy.
+In agreement with previous work we find that (local) stellar radiation feedback is effective in regulating star formation, but that non-local ionizing radiation is key for driving outflows in our simulations of an isolated, low mass, dwarf galaxy.
 Simulations run without ionizing radiation feedback have star formation rates a factor of five higher than our fiducial simulation.
-In spite of this difference, SNe in our fiducial run are capable of driving larger galactic outflows, aided significantly by the ionizing radiation feedback.
+Despite the lower rate, SNe in our fiducial run are capable of driving larger galactic outflows, aided significantly by the ionizing radiation feedback.
 
@@
 However, this model does not drive the significant outflows seen in our fiducial simulation.
-Long-range ionizing radiation is important for carving channels allowing the release of significant amounts mass and metals from SNe.
+Long-range ionizing radiation is important for carving channels allowing the ejection of significant amounts of mass and metals from the SNe.
 Our simulation with localized radiation feedback retains a significantly higher fraction of metals than expected observationally for low mass dwarf galaxies.

### 2018-08-01 ms.tex
Update on Overleaf.

@@
 This problem has been addressed by employing various models of strong stellar feedback physics which are capable of generating self-regulating star formation in galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews).
-\textbf{Energy injection from supernovae (SNe) has historically been used as the sole form of feedback.
+Energy injection from supernovae (SNe) has historically been used as the sole form of feedback.
 However, this is generally done heuristically as many simulations lack the ability to resolve the Sedov phase of individual SNe.
@@
 The need for additional feedback is confirmed by simulations that are capable of fully resolving individual SN \citep[e.g.][]{Peters2017,Smith2018a,Smith2018b,Hu2018}.
-However, modeling these processes in detail is challenging, and their competing effects on galactic evolution are poorly constrained.}
+However, modeling these processes in detail is challenging, and their competing effects on galactic evolution are poorly constrained.
 
@@
 Although some of these approximate methods account for long-range effects of diffuse radiation \citep{HQM2012,Hopkins2018} most cases treat local radiation {\it only}, confined to energy or momentum injection in a limited physical region around a star particle.
-\textbf{This is done both because the local destruction of dense clumps of gas around newly formed stars is commonly believed to be the dominant impact of stellar radiation feedback and because it is computationally less expensive to implement.
+This is done both because the local destruction of dense clumps of gas around newly formed stars is commonly believed to be the dominant impact of stellar radiation feedback and because it is computationally less expensive to implement.
 The role of long-range stellar radiation, once ionizing photons break out of star forming regions, is not well characterized.
-Indeed it remains to be seen if modeling only the short-range effects of stellar radiation feedback is sufficient.}
+Indeed it remains to be seen if modeling only the short-range effects of stellar radiation feedback is sufficient.
 
@@
 
-To investigate these questions, we compare three simulations of the evolution of an isolated, low mass dwarf galaxy.
+We compare three simulations of the evolution of an isolated, low mass dwarf galaxy.
 Our fiducial model, containing full stellar radiation feedback, is compared against a run without ionizing radiation feedback, and a run with ionizing feedback limited to the local region around a given star.
@@
 \section{Methods and Initial Conditions} \label{sec:methods}
-We refer the reader to Paper I for a more detailed description of our methods, briefly summarized here.
+We refer the reader to Paper I for a more detailed description of our methods.
 We use the adaptive mesh refinement hydrodynamics code \textsc{Enzo} \citep{Enzo2014} to evolve an idealized, isolated low mass dwarf galaxy.
-The galaxy is initialized as a smooth exponential disk set in hydrostatic equilibrium with a static dark matter potential \citep{Burkert1995} with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, $Z_{\rm gas} = 4\times 10^{-4}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, on a grid with a maximum physical resolution of 1.8~pc.
-We do not model an initial stellar population, but do include random driving from supernovae as an initial source of feedback up until the first explicit star formation in our model.
+The galaxy is initialized as a smooth exponential disk set in hydrostatic equilibrium with a static dark matter potential \citep{Burkert1995} with $M_{\rm gas} = 2 \times 10^6~$~M$_{\odot}$, $Z_{\rm gas} = 4\times 10^{-4}$, radial and vertical gas scale heights of 250~pc and 100~pc respectively, and $M_{\rm vir} = 2.48 \times 10^9$~M$_{\odot}$, on a grid with a maximum physical resolution of 1.8~pc.
+We include no initial stellar population, but do include random driving from supernovae as an initial source of feedback up until the onset of star formation.
 
@@
 Star formation occurs stochastically in cold, dense regions ($n > 200$~cm$^{-3}$, $T < 200$~K) by sampling a \cite{Salpeter1955} IMF from 1~M$_{\odot}$ to 100~M$_{\odot}$ and depositing \textit{individual} star particles over this mass range.
-For each star, we include feedback from stellar winds, AGB winds, FUV and LW band radiation which drives photoelectric heating and H$_2$ dissociation respectively, HI and HeI ionizing radiation, and core collapse and Type Ia SNe using thermal energy injection.
+We include feedback from stellar winds, AGB winds, FUV and LW band radiation which drives photoelectric heating and H$_2$ dissociation respectively, HI and HeI ionizing radiation, and core collapse and Type Ia SNe using thermal energy injection.
 FUV and LW band radiation are both taken to be optically thin, with local (cell-by-cell) attenuation alone.
@@
 Stellar lifetimes, surface gravity, effective temperature, and radii are set by the initial stellar mass and metallicity through interpolation over the PARSEC \citep{Bressan2012} zero age main sequence values.
-Stellar surface gravity, effective temperature, and radii are used to set the FUV, LW, and ionizing photon fluxes from each star through interpolation on the OSTAR2002 \citep{LanzHubeny2003} grid.
+These properties are used to set the FUV, LW, and ionizing photon fluxes from each star through interpolation on the OSTAR2002 \citep{LanzHubeny2003} grid.
 We only model the radiation from stars with masses above 8~M$_{\odot}$.
-%tellar wind and supernovae mass loss are determined with the  NuGrid yield tables for $M_* < 25$~M$_{\odot}$ and from Slemer et. al. (in prep) for $M_* > 25$~M$_{\odot}$.
 
-%\textbf{Stellar Ionizing Radiation Models} $-$
-In our fiducial simulation, we follow photoionizing radiation using the adaptive ray-tracing radiative transfer method of \cite{WiseAbel2011}.
+Our fiducial simulation follows photoionizing radiation using the adaptive ray-tracing radiative transfer method of \cite{WiseAbel2011}.
 This method places and evolves 48 rays on a HEALPix grid around each emitting source star for both HI and HeI ionizing radiation.
 Rays are adaptively split as they propagate away from their source to increase the angular resolution such that the solid angle of the ray remains smaller than 1/3 of the cell area.
-Rays begin on HEALPix refinement level 2, with a maximum refinement level of 13 (or $8.05 \times 10^8$ rays).
-\textbf{We include radiation pressure on hydrogen (single-scattering), but do not investigate its importance in this work \citep[see][]{WiseAbel2012}.}
+Rays begin on HEALPix refinement level 2, with a maximum refinement level of 13.
+We include radiation pressure on hydrogen, but do not investigate its importance in this work \citep[see][]{WiseAbel2012}.
 
@@
 \footnote{We are unable to follow the long-term evolution of the noRT galaxy due to computational constraints.
-Although radiative transfer itself is computationally expensive, this run is substantially more costly \textbf{due to a lower typical timestep and increased cost in computing the optically thin radiation effects (photoelectric effect and LW dissociation) for the additional star particles.}}
+Although radiative transfer itself is computationally expensive, this run is substantially more costly due to a lower typical timestep and increased cost in computing the optically thin radiation effects (photoelectric effect and LW dissociation) for the additional star particles.}
 
@@
 
-%\begin{figure*}
-%\centering
-%\includegraphics[width=0.98\linewidth]{density_temperature_ionization_z_profile}
-%\caption{Volume-averaged quantities above / below the disk of each galaxy.
-{\bf Left:} number density.
-{\bf Middle:} Temperature {\bf Right:} Hydrogen ionization fraction.
-These profiles correspond to the same point in time as Figure~\ref{fig:panel2}.
-\textbf{New figure.
-We can decide if we want to keep all panels, or stick with just 1 of the 3 quantities}}
-%\label{fig:vertical profiles}
-%\end{figure*}
-
-%\textbf{Finally, we quantify these findings in Figure~\ref{fig:vertical profiles}, showing the volume-weighted average number density (left), temperature (middle) and hydrogen ionization fraction (right) as a function of distance above/below the disk of our galaxy at the same time as Figure~\ref{fig:panel2}.
-The gas outside the disk of our fiducial simulation is lower density, higher temperature, and has a higher ionization fraction at all points above the disk.
-The shortrad simulation, which lacks both the enhanced SNR of the noRT run and the long-range ionizing radiation effects, of the fiducial simulation, maintains a denser, cooler, more neutral shell of gas above the disk, preventing significant outflows.}
-
-\textbf{As shown in Figure~\ref{fig:metal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy.
+As shown in Figure~\ref{fig:metal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy.
 The winds in our fiducial simulation carry nearly all of the metals produced out from the disk of our galaxy.
@@
 This would also influence the chemical enrichment of neighboring galaxies, given the significant differences in metal ejection past the virial radius between these two runs.
-Clearly the effects of feedback on observable chemical properties of galaxies is a key discriminator among models.}
+Clearly the effects of feedback on observable chemical properties of galaxies is a key discriminator among models.
 
@@
 
+\acknowledgments
+A.E.
+is funded by the NSF Graduate Research Fellowship DGE 16-44869.
+G.L.B.
+is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
+M.-M.M.L.
+was partly funded by NASA  grant NNX14AP27G.
+We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute.
+This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}.
+These are products of collaborative effort by many independent developers from numerous institutions around the world.
+Their commitment to open science has helped make this work possible.
+
 \bibliography{msbib}
 
-%% This command is needed to show the entire author+affilation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
-
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-
 \end{document}
-
-% End of file `sample62.tex'.

### 2018-08-01 ms.tex
text

@@
 Simulations including stellar radiation feedback followed through radiative transfer or radiation-hydrodynamics schemes have found it to be effective in regulating star formation and driving galactic winds \citep[e.g.][]{WiseAbel2012,Kim2013a,Sales2014,Oshea2015,Rosdahl2015,Pawlik2015,Ocvirk2016,Peters2017}.
-This occurs in four ways: 1) heating of diffuse gas and preventing the formation of cold, dense star formation regions, 2) destruction of cold, dense gas around recently formed stars, preventing further star formation, 3) momentum input by direct absorption of UV radiation by gas and (in some cases) dust through re-emission and scattering in the infrared, and 4) lowering the typical ISM densities in which SNe occur and greatly increasing their effectiveness.
-% the relevance / importance of RP from dust in the IR is beyond the scope of this work...
+This occurs in four ways: 1) heating of diffuse gas and preventing the formation of cold, dense star formation regions, 2) destruction of cold, dense gas around recently formed stars, preventing further star formation, 3) momentum input by direct absorption of UV radiation by gas and dust through re-emission and scattering in the infrared, and 4) lowering the typical ISM densities in which SNe occur and greatly increasing their effectiveness.
 
@@
 Indeed it remains to be seen if modeling only the short-range effects of stellar radiation feedback is sufficient.
-
-%Although the approximate radiation feedback models are capable of driving significant galactic outflows, it is unclear if they capture the full effects of stellar ionizing radiation. 
-%The 
-%It is unclear what, if any, effect the long-range ionization and heating processes play in regulating star formation and driving galactic winds.
 

### 2018-08-01 ms.tex
Update on Overleaf.
spelling

--- 2018-08-01 ms.tex
@@
 This occurs in four ways: 1) heating of diffuse gas and preventing the formation of cold, dense star formation regions, 2) destruction of cold, dense gas around recently formed stars, preventing further star formation, 3) momentum input by direct absorption of UV radiation by gas and (in some cases) dust through re-emission and scattering in the infrared, and 4) lowering the typical ISM densities in which SNe occur and greatly increasing their effectiveness.
-% the relevance / importance of RP from dust in the IR is beyond the scope of this work...
 
@@
 
-%Although the approximate radiation feedback models are capable of driving significant galactic outflows, it is unclear if they capture the full effects of stellar ionizing radiation. 
-%The 
-%It is unclear what, if any, effect the long-range ionization and heating processes play in regulating star formation and driving galactic winds.
-
 In this work we use a detailed model for stellar feedback presented in \cite{Emerick2018} (hereafter Paper I) to study the role of radiation feedback in dwarf galaxy evolution.
-For the first time in a galaxy-scale simulation, we resolve individual HII rgeions using an adaptive ray tracing radiative transfer method to follow the ionizing radiation from particles that represent individual stars.
+For the first time in a galaxy-scale simulation, we resolve individual HII regions using an adaptive ray tracing radiative transfer method to follow the ionizing radiation from particles that represent individual stars.
 We focus on addressing two questions: 1) what role does radiation feedback play in regulating star formation, and 2) are the long-range effects of radiation feedback important, or is the local destruction of dense gas the dominant effect.
 
-We compare three simulations of the evolution of an isolated, low mass dwarf galaxy.
+To investigate these questions, we compare three simulations of the evolution of an isolated, low mass dwarf galaxy.
 Our fiducial model, containing full stellar radiation feedback, is compared against a run without ionizing radiation feedback, and a run with ionizing feedback limited to the local region around a given star.

### 2018-08-01 ms.tex
Update on Overleaf.

@@
 %% keywords and the rules for their use.
-\keywords{galaxies -- feedback -- galaxy evolution -- galactic winds}
+\keywords{galaxies -- feedback -- galaxy evolution}
 
@@
 Modeling only local stellar ionizing feedback is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
-To explore the cause of this difference we compare in Figure~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}
+To explore the cause of this difference we compare in Figure~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See https://youtu.be/r1nEW6Yu3xI for a movie of this comparison.}
 

### 2018-08-01 main.tex

@@
 \includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
-\caption{\textbf{AE: relabel y axis with [O/H] - [O/H]$_CNM$}The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the
+\caption{\textbf{Clarify vertical axis label} The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the
 %mm

### 2018-08-02 main.tex
Update on Overleaf.

@@
 Bottom: The mass fraction of species within \textit{the disk} alone in each phase of the ISM (bottom).
-The leftmost bar in each plot shows the sum of all metals.
-\textbf{AE: Relabel y-axis, space in All Metals and C, larger figures}}
+The leftmost bar in each plot shows the sum of all metals.}
 \label{fig:species_fractions}
@@
 Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
-Generally, in colder gas the metal PDFs become less enriched with broader low metal fraction components and steeper, power-law tails.
+Generally, in colder gas the metal PDFs become less enriched with broader, low-metal-fraction components and steeper, power-law tails.
 Although the extended power-law tail of the HIM leads to a large range of metal fractions, the HIM represents very little mass, and this tail represents recent, un-mixed enrichment.
-The comparatively narrow width in the log-normal regimes of CNM is perhaps surprising.
+The comparatively narrow width in the log-normal regimes of the CNM is perhaps surprising.
 Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is more well mixed.
-This runs counter to the idea that mixing times should be long in colder gas unless mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.
+This runs counter to the idea that mixing times should be long in colder gas, unless (as we argue) mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.
 
@@
 Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread.
-The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star-forming gas.
+The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling and/or mixing through multiple phases until enriching star-forming gas.
 This
@@
 %In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability.
-Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM.
+Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM.
 The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
@@
 models are biased to overestimate gas and stellar elemental abundances.
-. % However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.
+% However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.
 
-To summarize, Figure~\ref{fig:phase-statistics} demonstrates: 1) there are qualitative differences in how SN injected elements (e.g.
-O, Mg) and AGB wind injected elements (e.g.
+To summarize, Figure~\ref{fig:phase-statistics} demonstrates: 1) there are qualitative differences in how SN-injected elements (e.g.
+O, Mg) and AGB-wind-injected elements (e.g.
 N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM; 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM and because the hotter phases are more directly populated by recent enrichment events; 3) the cooler, denser phases, particularly for SN injected elements, are more well mixed than the hot phases of the ISM; 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function; and therefore 5) the median metallicity available for star formation
@@
 We begin with a simple toy model that motivates the power-law tail at high metal fractions of the metal fraction PDFs and a subsequent turnover at low metal fractions in Section~\ref{sec:interpretation}.
-This work is placed in context with previous works focusing on metal mixing in the ISM in Section~\ref{sec:context}.
+This work is placed in context with previous papers focusing on metal mixing in the ISM in Section~\ref{sec:context}.
 We discuss the relevance of additional AGB yields not directly followed in this study in Section~\ref{sec:discussion:metal yields}.
-Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impact of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
+Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impacts of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
 
@@
 This will produce a turnover at the low $Z$ limit of $p(Z)$.
-The low-turnover limit is produced by diffusion from many different sources, and is thus multiplicative process, which, as we noted above, tends to produce log-normal distributions.
+The low-turnover limit is produced by diffusion from many different sources, and is thus a multiplicative process, which, as we noted above, tends to produce log-normal distributions.
 %mm [additive vs multiplicative]
@@
 In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star-forming gas in our simulations.
-This could be used to help disentangle sources of scatter in observed stellar abundance, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
+This could be used to help disentangle sources of scatter in observed stellar abundances, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
 If the
@@
 how individual metal species couple to the ISM and galactic wind of this galaxy.
+
 We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, or core collapse SNe)
 %mm , and Type Ia SNe).  [I'm inclined to leave them out as we really didn't model their influence]
-This difference is most significant in our model between elements ejected predominately by AGB winds and those ejected predominantly by core-collapse SNe. In addition, we find 
+This difference is most significant, in our model, between elements ejected predominately by AGB winds and those ejected predominantly by core-collapse SNe. In addition, we find 
 %mm for the first time 
@@
    prominent log-normal component.
-The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling into dense gas.
+The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling and/or mixing into denser gas.
 

### 2018-08-02 main.tex
Updates

@@
 
-%\title{Evolution of Individual Metals in Galactic Winds and the ISM}
-
-% GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
-% AE: Had a hard time coming up with a succinct and interesting sounding title that
-%     fit both of the interesting results:
-%          1) analytic PDF fits and 2) variations in metal mixing...
-\title{Metal Mixing
-%mm
-    and Ejection
-in Dwarf Galaxies is Dependent on Nucleosynthetic Source}
-
-%Non-Uniform Metal Distributions in a Dwarf Galaxy Simulation}
-%Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies}
+\title{Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source}
 
@@
 One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites from stellar winds or supernovae (SNe) and mix through the phases of the interstellar medium (ISM) into star-forming gas.
-%
-% get a sentence with a better punch at the end
-%
 
@@
 This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
-%Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows. 
 Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017,Sarmento2018}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018}
@@
 We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver.
-We use a 128$^{3}$ base grid with outflow boundary conditions measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
+We use a 128$^{3}$ base grid with outflow boundary conditions measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 9 levels of refinement, for a maximum spatial resolution of 1.8~pc.
 Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas or 2) a cell's local Jeans length becomes resolved by less than eight cells.
@@
 This galaxy has an average star formation rate of $1.2~\times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
-The galaxy exhibits strong, feedback-driven outflows that eject a significant amount of gas and metals from the galaxy.
+The galaxy exhibits strong, feedback-driven outflows \citep{Emerick2018b} that eject a significant amount of gas and metals from the galaxy.
 The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$, where $\eta$ is defined as the mass outflow rate in through a 0.1~$R_{\rm vir}$ annulus centered at 0.25~R$_{\rm vir}$ divided by the 100~Myr averaged SFR.
@@
 \label{sec:mixing}
-
-%mm I think this material duplicates the first paragraph of the introduction.
-% Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
-In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}).
-Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances.
-In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
-%mm However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
-To build towards this, we characterize the metal evolution and distributions in our galaxy below.
 We characterize the metal distributions (in Sections~\ref{sec:log-normal} and \ref{sec:phase-pdfs}) and evolution (in Section~\ref{sec:statistics}) in our galaxy to build towards a  a complete model for how metals mix and evolve in the complex, multi-phase ISM of real galaxies.
-
-%mm should most of this material be in the introduction, and just the last two sentences be here?
-%   AE: I agree this is mostly redundant. I removed this
-%Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
-In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}).
-Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances.
-%In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
-However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
-To build towards this, we characterize the metal evolution and distributions in our galaxy below.
 
@@
 
-The log-normal distribution is found often in nature, generally describing 
-%mm
-    multiplicative
-processes with non-negative values that grow with time.
+The log-normal distribution is found often in nature, generally describing multiplicative processes with non-negative values that grow with time.
 In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}.
@@
 \includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
-\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), HIM (red), and all the gas in the ISM (black).
+\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black).
 For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
 We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.
-Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.
-\textbf{Check colorblindness and add legend}}
+Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
 \label{fig:log-normal}
@@
 
-%
-% MM: remove from this section:
-%This is the first work examining the gas-phase properties of metallicity PDFs in a global galaxy simulation with a detailed model for stellar feedback, chemical enrichment, and a multi-phase ISM.
-Since we are far from a complete understanding of galactic chemical evolution, investigating the physics behind what sets the statistical properties of these PDFs, particularly what drives the differences across metal species and phases, is important.
-Although this is beyond the scope of this current work, we use scaling arguments to speculate on the meaning of these results.
-%Metal mixing in the ISM is a diffusive process driven by turbulence.
-
-% Recent works investigating dwarf galaxy chemical enrichment with Lagrangian simulations have shown that the sub-grid diffusion models required to reproduce observed dwarf galaxy abundance properties imply fairly rapid mixing timescales \citep{Escala2018,Hirai2017}.
-In contrast to this work, \cite{Escala2018} finds dwarf galaxy
-%The sub-grid diffusion models in Langrangian simulations of dwarf galaxy chemical enrichment that match the abundance properties of observed dwarf galaxies imply rapid mixing timescales
-
-%
-%
-%  Recent works specifically examining metal mixing in dwarf galaxies. Saving for potential future discussion:
-% \cite{Hirai2017} uses constrains the diffusion parameter in their SPH simulations comparing their simulated dwarf galaxies to observations in [Mg/Fe] vs.
-[Fe/H] and [Ba/Fe] vs.
-[Fe/H] space.
-Suggests Ba/Fe is more powerful constraint and briefly discusses potential differences in mixing between elements but does not do work with this
-% \cite{Jeon2017}
-% \cite{Escala2018} tests of role of metal diffusion models in producing realistic MDFs in dwarf galaxies. Able to reproduce things like MDF width and [alpha/Fe]vs[Fe/H] scatter.
-
-% The properties of log-normal density PDFs in isothermal simulations are governed by the statistical properties of turbulence (refs) and the relative importance of compressive and solenoidal driving.
-However, the density PDFs in simulations of global galaxies with a resolved, multiphase ISM show significant departures from log-normallity \citep[see][]{Hopkins2013} but are still approximately log-normal within individual phases of the ISM \citep{HopkinsQuataertMurray2012}.
-The properties of the density PDF in multiphase simulations have not been well studied which offers little insight into what sets the mass fraction PDFs for each element.
-We speculate on this here to motivate future study, but note that a detailed characterization is beyond the scope of this work.
-
 % The log-normal density PDFs found in ISM simulations have a variance that is proportional to the mach number \citep[e.g.][(maybe more)]{PNJ1997, Passot1998, Fedderath2008, LemasterStone2009}.
@@
 
-%We discuss possible caveats to this in Section~\ref{sec:caveats}.
-Does this extend to more massive?
-how does DM potential affect this?
-Are general trends still true in much larger galaxies?
-or are things very different once HIM crossing times are more like 100 Myr (aka MW size galaxies).
-
 \subsection{Timescale Dependence of AGB Ejecta}
 \label{sec:discussion:metal yields}
-We can generally say that metals 
-%mm produced
-    ejected 
-in AGB winds evolve qualitatively differently than metals produced by SNe in 
-%mm dwarf galaxies 
-     our dwarf galaxy. 
+We can generally say that metals ejected in AGB winds evolve qualitatively differently than metals produced by SNe in our dwarf galaxy.
 However, exactly which metals exhibit these differences, and to what degree, is timescale and metallicity dependent.
-Short timescales ($\lesssim 100$~Myr) only sample enrichment from the most massive AGB stars,
-%mm which 
-     while 
-stars on order of a few solar masses 
-%mm 
-    only
-enrich on timescales of a gigayear or longer. In our simulations, which only 
-%mm sample
-   simulate 
-500 Myr of evolution, N and Ba are dominated 
-%mm from 
-     by
-AGB wind ejecta.
+Short timescales ($\lesssim 100$~Myr) only sample enrichment from the most massive AGB stars, while stars on order of a few solar masses only enrich on timescales of a gigayear or longer.
+In our simulations, which only simulate 500 Myr of evolution, N and Ba are dominated by AGB wind ejecta.
 C is commonly used to track AGB wind enrichment, but as it originates from lower mass AGB stars, C enrichment operates on gigayear timescales, longer than we follow in this work.
@@
 Sr, for example, is only significantly ejected through AGB winds at our metallicity on gigayear timescales, while stellar winds from more massive stars dominate the production of Sr on shorter timescales.
-At higher metallicity, much more Sr is produced through massive AGB stars, decreasing the timescale over which Sr should exhibit a differential chemical evolution compared to SN-ejected elements.
+At higher metallicity, much more Sr is produced through massive AGB stars, decreasing the timescale over which Sr should exhibit a differential chemical evolution compared to SN-ejected elements (see \cite{Ritter2017} and \cite{Ritter2017b} and references therein).
 
@@
 This model was run using \textsc{SYGMA} \citep{Ritter2017}.
-As shown, metal enrichment from AGB winds only begins to dominate for
-%mm a given species at 
-    any elements after 
-$\sim$ 100 Myr. This includes N and Ba, which we follow in our simulations, but this 
-%mm plot indicates
-    model predicts 
-that Ag and Pb 
-%mm should 
-     will
-show similar bahavior.
+As shown, metal enrichment from AGB winds only begins to dominate for any elements after $\sim$ 100 Myr.
+This includes N and Ba, which we follow in our simulations, but this model predicts that Ag and Pb will show similar bahavior.
 It takes over a gigayear for C to be dominated by AGB wind ejecta, which is the case for many of the elements shown.
@@
 
-%\begin{figure*}
-%\centering
-%\includegraphics[width=0.95\linewidth]{C_N_evolution.png}
-%\caption{The fractional contribution of AGB winds to the total yields of C and N as a function of time for a simple stellar population at three different metallicities.
-Since the nucleosynthetic source governs the mixing dynamics of a given metal, this plot illustrates how this can change with both time and metallicity for a given species.
-These models were generated using \textsc{SYGMA} \citep{Ritter2017-sygma}}
-%\label{fig:agb evolution}
-%\end{figure*}
-
 \subsection{Impact on Stellar Abundance Patterns}
@@
 This could be used to help disentangle sources of scatter in observed stellar abundances, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
-If the
-%mm star-forming gas in our simulations can also be well-fit by a log-normal + power-law PDF
-        metal mass fractions in star-forming gas in our simulations 
-        can also be well fit by log-normal + power-law PDFs,
-and if we can parameterize their evolution as functions of global galaxy properties, this 
-%mm can 
-    could
-be used as a powerful 
-%mm and analytic 
-tool for modeling stellar abundance patterns in semi-analytic models.
+If the metal mass fractions in star-forming gas in our simulations can also be well fit by log-normal + power-law PDFs, and if we can parameterize their evolution as functions of global galaxy properties, this could be used as a powerful tool for modeling stellar abundance patterns in semi-analytic models.
 This would be a physically motivated way to account for both the intrinsic spread in stellar abundances due to inhomogeneities in the ISM and variations in mixing for different metal species.
@@
 
-Unfortunately, there is insufficient star-forming gas at any one time in our simulations to construct PDFs of 
-%mm metal distributions
-    metal mass fractions. 
-However, star-forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, 
-%mm follow a similar PDF 
-   to have mass fraction PDFs similar
-to the CNM.
+Unfortunately, there is insufficient star-forming gas at any one time in our simulations to construct PDFs of metal mass fractions.
+However, star-forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, to have mass fraction PDFs similar to the CNM.
 To verify this, Figure ~\ref{fig:stars} shows the difference between the oxygen mass fraction of stars and the median mass fraction from the CNM PDF at the time that particle formed.
@@
 A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiements.
-We will examine this more complicated multi-dimensional space with these
-%mm simulations 
-   numerical methods
-in future work.}
+We will examine this more complicated multi-dimensional space with these numerical methods in future work.}
 
@@
 \includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
-\caption{\textbf{Clarify vertical axis label} The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the
-%mm
-    time 
-within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
+\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the time within 1~Myr (our time resolution) of each star's formation time.
+The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
 \label{fig:stars}
@@
 
-% AE: Capitalized header
 \subsection{Do These Results Apply to More Massive Galaxies?}
 \label{sec:massive galaxies}
-%mm One
-   An 
-important caveat about our work is that these results are derived from simulations of an isolated, low mass, dwarf galaxy whose properties vary dramatically from more massive galaxies like the Milky Way.
-It is unclear how much these results apply to more massive galaxies
-%mm given their 
-     with
-deeper potential wells and higher star formation rates.
+An important caveat about our work is that these results are derived from simulations of an isolated, low mass, dwarf galaxy whose properties vary dramatically from more massive galaxies like the Milky Way.
+It is unclear how much these results apply to more massive galaxies with deeper potential wells and higher star formation rates.
 Feedback-driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
@@
 With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
-\textbf{We anticipate three potential regimes of metal retention,
-%mm related directly to 
-    depending on
-dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB 
-%mm
-    stars 
-and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.}.
+\textbf{We anticipate three potential regimes of metal retention, depending on dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB stars and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.}.
 If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
@@
 
-% Talk about CGM at all???
-
-%\textit{In addition, hot gas in a galaxy with a deeper potential well is less likely to be ejected from the galaxy, allowing more time for homogenization and possibly smaller metal fraction variation than seen here.}.
-
 \subsection{Implications for Exotic Enrichment Sources}
@@
 We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to SNe.
-Based on our results here,
-%mm
-     for example,
-we would expect elements from hypernovae to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe. 
+Based on our results here, for example, we would expect elements from hypernovae to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe.
 % Benoit suggesed removing this given energy argument removal above
@@
 
-%\subsection{Extra things I could discuss:}
-%\textit{Things to maybe}
-%\begin{itemize}
-%\item Observed N/O in stellar abundances exhibits large spreads at low metallicity.
-Argument has been that this is driven by timescale differences in AGB vs.
-massive star nucleosynthesis.
-However, our results would predict that N/O have a large spread due to mixing efficiency diffein rences between AGB winds and SNe.
-%\end{itemize}
-
 \section{Conclusions}
 \label{sec:conclusions}
-%mm For the first time we 
 We present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
-This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze
-%mm
-      for the first time
-how individual metal species couple to the ISM and galactic wind of this galaxy.
+This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze for the first time how individual metal species couple to the ISM and galactic wind of this galaxy.
 
-We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, or core collapse SNe)
-%mm , and Type Ia SNe).  [I'm inclined to leave them out as we really didn't model their influence]
-This difference is most significant, in our model, between elements ejected predominately by AGB winds and those ejected predominantly by core-collapse SNe. In addition, we find 
-%mm for the first time 
-    the novel result
-that the mass fraction PDFs of each metal in the ISM can be described using an analytic piecewise log-normal + power-law PDF.
+We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, or core collapse SNe).
+This difference is most significant, in our model, between elements ejected predominately by AGB winds and those ejected predominantly by core-collapse SNe.
+In addition, we find the novel result that the mass fraction PDFs of each metal in the ISM can be described using an analytic piecewise log-normal + power-law PDF.
 The properties of these PDFs vary with both ISM phase and metal species, again driven mostly by differences in enrichment sources.
@@
 
-\item Power-law tails 
-%mm in 
-   on log-normal 
-metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
+\item Power-law tails on log-normal metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
 
-\item Hotter phases have metal fraction PDFs that are more enriched, with significant power-law tails as compared to cold phases, which have a more %mm dominant log-normal structure. 
-   prominent log-normal component.
+\item Hotter phases have metal fraction PDFs that are more enriched, with significant power-law tails as compared to cold phases, which have a more prominent log-normal component.
 The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling and/or mixing into denser gas.
@@
 \item Metal distributions exhibit positive skew, such that the mean metal fraction can be anywhere from 0.1 to 1.0 dex above the median metal fraction.
-Simple chemical evolution models, which generally follow the mean abundance,
-%mm that are unable to 
-    and thus can not
-account for complex metal mixing physics, are likely biased towards higher enrichment values.
+Simple chemical evolution models, which generally follow the mean abundance, and thus can not account for complex metal mixing physics, are likely biased towards higher enrichment values.
 
@@
 % , and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements
-
-%\section{Things to cite}
-%Hou, Yu, Lu 2014: Need to read closer, but CE model playing around with SN energy feedback effectiveness finds that weaker feedback leads to more metal enrichment, higher FB, lower metallicities.
-Suggestion of importance of FB driving CE.
 

### 2018-08-08 main.tex
Update on Overleaf.

@@
 This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
-Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017,Sarmento2018}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018}
+Recent hydrodynamics simulations have employed parametric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017,Sarmento2018}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018}
 % KVJ: citations to high-redshift work in this area
-\textbf{and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.} Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.
+%\textbf{
+and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.
+%}
+Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.
 
@@
 % KVJ asked to bring up this area of research and emphasize how it is lacking theoretical input
-\textbf{One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Freeman2002,Ting2012, Hogg2016,Jofre2017,Price-Jones2018}.
+%\textbf{
+One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Freeman2002,Ting2012, Hogg2016,Jofre2017,Price-Jones2018}.
 Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations.
-Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.}
+Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.
 
@@
 Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging.
-[list examples of modelling problems]. 
+%[list examples of modeling problems]. 
 These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study.
@@
 Stars with $3 < M_{*} < 8$ are tracked after their death as possible Type Ia SN progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
-Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et.
+Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, Slemer et.
 al.
-in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia SNe.
+in prep for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia SNe.
 
@@
 
-We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the metal fraction  PDFs of individual elements in galaxy models.
+We argue here that the log-normal + power-law PDF can be a powerful tool for modeling the metal fraction  PDFs of individual elements in galaxy models.
 The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM.
@@
 If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time  $\tau_{\rm mix}$ this gas will have mixed with an equal amount of primordial gas.
-\textbf{At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$.
-Then, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.} This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
-\textbf{The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.}
+At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$.
+Then, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.
+This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
+The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.
 
-\textbf{Thus, if the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous distribution $p(t,Z)$
+Thus, if the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous distribution $p(t,Z)$
 %mm , or $p(Z)$, 
-of these many events will be $\delta(Z_{\rm o})$ plus a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.}
+of these many events will be $\delta(Z_{\rm o})$ plus a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.
 % and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
@@
 
-\textbf{cite sarmento and others (see BWO comments)}
-Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}.
+Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012,Sarmento2017,Sarmento2018}.
 Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
@@
 As shown, metal enrichment from AGB winds only begins to dominate for any elements after $\sim$ 100 Myr.
-This includes N and Ba, which we follow in our simulations, but this model predicts that Ag and Pb will show similar bahavior.
+This includes N and Ba, which we follow in our simulations, but this model predicts that Ag and Pb will show similar behavior.
 It takes over a gigayear for C to be dominated by AGB wind ejecta, which is the case for many of the elements shown.
@@
 %KVJ suggested emphasizing that there is much more potential in this work / work like this by examining more dimensions
-\textbf{We emphasize that this study focuses on each chemical dimension independently, as a means to first understand galactic chemical enrichment in the simplest possible framework.
+We emphasize that this study focuses on each chemical dimension independently, as a means to first understand galactic chemical enrichment in the simplest possible framework.
 However, the cross-correlation of multiple metal fractions and abundance ratios is the most useful in revealing key processes in galactic chemodynamics.
-A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiements.
-We will examine this more complicated multi-dimensional space with these numerical methods in future work.}
+A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiments.
+We will examine this more complicated multi-dimensional space with these numerical methods in future work.
 
@@
 With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
-\textbf{We anticipate three potential regimes of metal retention, depending on dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB stars and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.}.
+We anticipate three potential regimes of metal retention, depending on dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB stars and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.
 If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
@@
 We present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
-This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze for the first time how individual metal species couple to the ISM and galactic wind of this galaxy.
+This high resolution simulation, coupled with our star-by-star modeling of stellar nucleosynthetic yields, has allowed us to analyze for the first time how individual metal species couple to the ISM and galactic wind of this galaxy.
 
@@
 We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}.
-We show the mass-weighted PDF ($dm/Md\log n$) on the left, and the volume-weighted PDF ($dv/Vd\log n$) on the right.
+We show the mass-weighted PDF ($dm/Mdn$) on the left, and the volume-weighted PDF ($dv/Vdn$) on the right.
 As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution.

### 2018-08-09 main.tex
models
Update on Overleaf.

@@
 The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004,Muratov2017,Corlies2018}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004,Muratov2017,Corlies2018}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,Bordoloi2014,McQuinn2015}.
 If there are differences in metal coupling to the ISM, this could potentially impact how metals are driven out of galaxies through galactic winds.
@@
 First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
-Second, there is only a severly limited sample of gas-rich dwarf galaxies of this size that we can use for direct observational comparison, and it is computationally infeasible to simulate galaxies of easily observable size in as much detail as done here.
+Second, there is only a limited sample of gas-rich, star forming dwarf galaxies of this size that we can use for direct observational comparison, and it is computationally infeasible to simulate galaxies of easily observable size in as much detail as done here.
 This work will be the first of several attempting to bridge this gap.
@@
 The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$, where $\eta$ is defined as the mass outflow rate in through a 0.1~$R_{\rm vir}$ annulus centered at 0.25~R$_{\rm vir}$ divided by the 100~Myr averaged SFR.
-These winds eject 95\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.
+These winds eject 96\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.
 
@@
 We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}.
-We show the mass-weighted PDF ($dm/Mdn$) on the left, and the volume-weighted PDF ($dv/Vdn$) on the right.
+We show the mass-weighted PDF ($dm/Md\log n$) on the left, and the volume-weighted PDF ($dv/Vd\log n$) on the right.
 As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution.

### 2018-08-20 main.tex
modified text for report 2

--- 2018-08-08 main.tex
@@
-%mm substantive changes marked like this, others made silently
+\documentclass[fleqn,usenatbib,useAMS]{mnras}
+\pdfoutput=1 
+\usepackage{graphicx}	% Including figure files
+\usepackage{amsmath}	% Advanced maths commands
+\usepackage{amssymb}	% Extra maths symbols
+\usepackage{multicol}        % Multi-column entries in tables
+\usepackage{bm}		% Bold maths symbols, including upright Greek
+%\usepackage{pdflscape}	% Landscape pages
 
-\documentclass[twocolumn]{aastex61}
-\pdfoutput=1 %for arXiv submission
-\usepackage{amsmath,amstext}
 \usepackage[T1]{fontenc}
-\usepackage{apjfonts}
+\usepackage{ae,aecompl}
+\usepackage{newtxtext,newtxmath}
+
+%\usepackage{amsmath,amstext}
+%\usepackage[T1]{fontenc}
 \usepackage[figure,figure*]{hypcap}
 
-\renewcommand*{\sectionautorefname}{Section} %for \autoref
-\renewcommand*{\subsectionautorefname}{Section} %for \autoref
+%\hypersetup{draft}
+%\usepackage{multirow}
+%\usepackage{mathtools}
+%\renewcommand*{\sectionautorefname}{Section} %for \autoref
+%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
+%\usepackage{graphicx}
+%\usepackage{natbib} % bibliography
 
-\shorttitle{Differential Metal Mixing}
+%\usepackage[active,floats,tightpage]{preview}
+%    \setlength\PreviewBorder{1em}
+
+\newcommand{\msun}{M$_{\odot}$}
+\newcommand{\ccunit}{cm$^{-3}$}
+
+\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars}
+
+\author[A. Emerick et. al.]{
+Andrew Emerick,$^{1,2}$
+Greg L. Bryan,$^{1,3}$
+and Mordecai-Mark Mac Low$^{2,1}$
+\\
+$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
+$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
+$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
 
@@
 
-\title{Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source}
+\label{firstpage}
+%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\maketitle
+%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
 
-\author{Andrew Emerick}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-\author{Greg L. Bryan}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-\author{Mordecai-Mark Mac Low}
-\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-\author{Benoit C{\^o}t{\'e}}
-\affiliation{Konkoly Observatory, Research Centre for Astronomy and Earth Sciences, Hungarian Academy of Sciences, Konkoly Thege Miklos ut 15-17, H-1121 Budapest, Hungary}
-\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI 48824, USA}
-\affiliation{Joint Institute for Nuclear Astrophysics -- Center for the Evolution of the Elements, USA}
-\author{Kathryn V. Johnston}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\author{Brian W. O'Shea}
-\affiliation{Department of Computational Mathematics, Science, and Engineering, Michigan State University, East Lansing, MI, 48824, USA}
-\affiliation{Department of Physics and Astronomy, Michigan State University, East Lansing, MI, 48824, USA}
-\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI, 48824, USA}
-\affiliation{Joint Institute for Nuclear Astrophysics -- Center for the Evolution of the Elements, USA}
+%\author{Andrew Emerick}
+%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+%\author{Greg L. Bryan}
+%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+%\author{Mordecai-Mark Mac Low}
+%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+
+%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}
 
 \begin{abstract}
-Using a high resolution simulation of an isolated dwarf galaxy, accounting for multi-channel
-stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy by galactic winds.
-For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal and power-law distribution.
-The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail.
-The PDF properties, and relative significance of these two components, vary within each ISM phase.
-Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component.
-In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment, such as N and Ba, mix less efficiently than elements dominated by supernova enrichment, such as $\alpha$ elements and Fe.
-This difference is driven by the differences in
-%mm energetics between each source, particularly the poor coupling of AGB winds to the ISM.
-    source energetics and source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
-Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
-In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread compared to elements synthesized in either core collapse or Type Ia supernovae.
-We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
+In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
+For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
+We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
+We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints.
+We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group, low-mass dwarf galaxy.
+We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
+Effective feedback drives outflows with a greater metallicity than the ISM, leading to low metal retention fractions consistent with observations.
+Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
 \end{abstract}
 
-\keywords{}
+\begin{keywords}
+Galaxy -- Hydrodynamics -- Simulation -- Feedback
+\end{keywords}
 
 \section{Introduction}
-Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution.
-One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites from stellar winds or supernovae (SNe) and mix through the phases of the interstellar medium (ISM) into star-forming gas.
+%
+% AE removed below.. MM suggested  skipping both pars.
+%
+%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade.
+Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc.
+\citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses.
+On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM.
+This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}.
+See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.
+%
+%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution.
+In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense.
+In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships.
+For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.
 
-One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}.
-While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challenging.
-More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects.
-How to properly account for multi-phase mixing, however, is still poorly understood.
-This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
-Recent hydrodynamics simulations have employed parametric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017,Sarmento2018}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018}
-% KVJ: citations to high-redshift work in this area
-%\textbf{
-and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.
-%}
-Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.
+Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution.
+Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
+There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
+% editor asked us to reduce citation count here:{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
+These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
 
-In addition, it remains to be seen to what degree, if at all, metals of different enrichment origins (AGB winds, core collapse SNe, Type Ia SNe, neutron-star neutron-star mergers, etc.) may couple differently to the ISM.
-When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly.
-However, if metals do not behave uniformly in the ISM, if their mixing and ejection behavior depends directly upon the energetics and physical environment of their injection, then this assumption would need to be re-evaluated.
-Differences in metal distributions from ejecta in AGB stars, as compared to SNe, has been explored recently in \cite{KrumholzTing2018}, but has yet to be demonstrated in hydrodynamics simulations.
-Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations \citep[e.g.][]{Cote2018}.
+However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}.
+In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
+Mixing can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
+While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficiently high spatial resolution.
+Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
+Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b, KrumholzTing2018}.
+Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
+the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
+The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
 
-The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004,Muratov2017,Corlies2018}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
-If there are differences in metal coupling to the ISM, this could potentially impact how metals are driven out of galaxies through galactic winds.
-This has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
-However, examining this process has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
-%It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
-% Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
-However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
+Increasing physical resolution reduces reliance on sub-grid physics for mixing.
+However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}.
+Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
+This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
+At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.
+Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
+The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
 
-It is becoming increasingly valuable to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}.
-Stellar abundances are directly imprinted with the enrichment pattern of their star-forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
-The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM.
-Furthermore, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.
-% KVJ asked to bring up this area of research and emphasize how it is lacking theoretical input
-%\textbf{
-One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Freeman2002,Ting2012, Hogg2016,Jofre2017,Price-Jones2018}.
-Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations.
-Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.
+We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies.
+The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms.
+We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
+%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies.
+\citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
+Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar winds from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
+We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar far ultra-violet (FUV) radiation, and Lyman-Werner dissociation from stellar radiation.
 
-In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}.
-The simulation discussed here was introduced in detail in \cite{Emerick2018} (hereafter Paper I).
-To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia SNe.
-This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below.
-We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species.
-We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.
+Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime.
+This includes yields from massive and AGB stellar winds, and supernovae (SNe).
+In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
+This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
+This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
+We describe each mode of our multi-channel feedback
+in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.
 
-The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity.
-Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging.
-%[list examples of modeling problems]. 
-These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study.
-By focusing on a low mass dwarf galaxy, with small size and low star formation rate, we can capture detailed feedback and ISM physics at high resolution, while following individual stars.
-In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios, for two reasons.
-First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
-Second, there is only a severly limited sample of gas-rich dwarf galaxies of this size that we can use for direct observational comparison, and it is computationally infeasible to simulate galaxies of easily observable size in as much detail as done here.
-This work will be the first of several attempting to bridge this gap.
-With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and physically motivated sub-grid physics models for lower resolution simulations of more massive galaxies.
+Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.
 
-We summarize our methods and physics models in Section~\ref{sec:methods}.
-We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}.
-In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
-We discuss our results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusions}.
-
-% AE: Benoit suggested subsections instead of paragraph splits... play with this to see what looks best
 \section{Methods}
 \label{sec:methods}
-We refer the reader to Paper I for a detailed description of our numerical methods and feedback models. We briefly summarize the relevant details here.
+We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
+This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
+To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background.
+We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}).
+We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
+Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
+We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on HI.
+In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
+We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both.
+We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors.
+We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species.
+In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked.
+This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth.
+These methods are discussed in full detail below.
 
-\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{http://enzo-project.org/} \citep{Enzo2014}.
-Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
-We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver.
-We use a 128$^{3}$ base grid with outflow boundary conditions measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 9 levels of refinement, for a maximum spatial resolution of 1.8~pc.
-Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas or 2) a cell's local Jeans length becomes resolved by less than eight cells.
-Also, if the cell is within four zones of a star particle with active feedback, it is refined to the maximum resolution.
-At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.
+\subsection{Hydrodynamics and Gravity}
+\label{sec:hydro}
 
-\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (H, H$^+$, He, He$^+$, He$^P{++}$, H$^-$, H$_2$, H$_2^+$, and e$^-$), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
-We account for approximate self-shielding of H~{\sc i} against the UV background following \cite{Rahmati2013}.
-We assume He~{\sc i} self-shields in the same fashion as H~{\sc i}, and ignore He~{sc ii} heating from the UVB entirely.
-Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}.
-Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.
+We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies.
+\texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions.
+We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick.
+Specifically, simulations presented here were conducted at changeset 7001d99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
+We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}).
+Self-gravity is computed with a multigrid Poisson solver.
+The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.
 
-% AE: From Benoit, maybe make a note of 1 - 100 M_sun sampling may slightly overestimate higher mass stars (people usually do 0.1 to 100 M_sun
-\paragraph{Star Formation} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
-Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$.
-Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$).
-We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\% \citep{KrumholzMcKee2005}.
-Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment.
-We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
+We refine the mesh whenever the thermal Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
+At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation.
+\citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.
 
-\paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually.
-Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse SNe at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
-Stars above this mass are assumed to direct collapse with no mass or energy injection.
-For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their H~{\sc i} and He~{\sc i} ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
-We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars.
-Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind \citep{Goldman2017}.
-Stars with $3 < M_{*} < 8$ are tracked after their death as possible Type Ia SN progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
-Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, Slemer et.
-al.
-in prep for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia SNe.
+We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}).
+Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
+However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse.
+A non-thermal pressure term is added to cells once their thermal Jeans length becomes unresolved.
+This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
+The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.
 
-\paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
-We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an exponential profile with a metal mass fraction of $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$~M$_{\odot}$.
-The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
-Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium.
-The galaxy contains no initial background stellar population, limiting the number of Typa Ia SNe in our model, but we do provide initial SN driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
-Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
-Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.
+Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas.
+These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution.
+At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr.
+We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$.
+These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions.
+This threshold decreases the required run-time by factors of a few.
+The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)
+
+\subsection{Chemistry and Cooling Physics}
+\label{sec:chemistry}
+
+We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset c2c0faf.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes.
+We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.
+We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
+However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}.
+For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
+
+As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
+As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
+Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}.
+To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.
+We have made these new tables public in the main \texttt{Grackle} repository.
+These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
+Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.
+
+\subsection{Star Formation Algorithm}
+\label{sec:star formation}
+In order to resolve individual star formation events on galactic scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
+Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local thermal Jeans mass.
+Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K.
+We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$.
+No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.
+
+We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
+At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2018, FIRE2}, as star formation is ultimately self-regulated by feedback.
+
+The stellar mass formed during a timestep $\Delta t$ from a region with a total gas mass $M_{\rm gas}$ is
+\begin{equation}
+         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
+\end{equation}
+In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution.
+We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses.
+In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
+If it does, we randomly sample from
+the adopted IMF until approximately 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
+The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.
+We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
+Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
+By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.
+
+Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
+This dispersion captures some of the unresolved gas motions below the resolution limit that are smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations.
+Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
+
+Stars evolve during the simulation, by losing mass from stellar winds and SNe as described below, and by changing types, but persist throughout the entire simulation.
+For example, low mass stars are tagged as white dwarfs (WDs) at the end of their life, which may eventually explode as a Type Ia SN (discussed below), after which they persist as massless tracer particle remnants.
+Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a four-cell region at the highest level of refinement.
+This ensures that both stellar winds and SNe feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.
+
+\subsection{Stellar Properties}
+\label{sec:properties}
+Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}).
+We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$.
+Although $T_{\rm eff}$ and $g$ evolve over time for stars, modifying stellar radiative properties, following a stellar evolution track for each of our stars is beyond the scope of this work.
+We instead fix these properties at their zero age main sequence values.
+
+\subsection{Stellar Feedback and Chemical Yields}
+
+\subsubsection{Stellar Yields}
+\label{sec:yields}
+For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars.
+We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2018}.
+This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$.
+We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$.
+We ignore SN yields from these stars (see next paragraph).
+We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth.
+Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation.
+We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017a} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
+
+%
+% KVJ: Possibly include a discussion on uncertainties in stellar yields
+%
+
+Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe.
+Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$; we take $M_{\rm trans} = 8$~M$_{\odot}$.
+In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
+Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics).
+Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
+\citet{Cote2017a} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
+We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
+
+There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}.
+Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
+Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass, metal, or energy ejection.
+
+Type Ia SNe are an important additional source of galactic chemical enrichment.
+These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
+We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
+We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, substantially limiting the number of Type Ia SNe occurring during the initial gigayear in our models.
+
+\subsubsection{Stellar Winds}
+\label{sec:stellar winds}
+Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
+Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback.
+We assume complete thermalization of the wind kinetic energy, taking the total injected energy injected in timestep $\Delta t$ as $E_w = \frac{1}{2}\dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
+This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle.
+The edges of this spherical region will only partially overlap grid cells.
+We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately.
+We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
+
+Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}.
+Satisfying the Courant time step becomes prohibitively expensive following this gas, with time steps dropping to $\Delta t \sim$~100~yr.
+For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
+In our case, we fix massive stellar wind velocities to $v_w = 20$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
+Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies.
+Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work.
+These points are discussed in more detail in Sect.~\ref{sec:stellar winds discussion}.
+
+% Injecting 10$^{3}$ km s$^{-1}$ gas onto the grid at these scales leads to super heated, shocked gas at unphysical temperatures of about 10$^{8-9}$ K, particularly when injecting into very low density media.
+This can lead to painfully short time step sizes and crashes in the hydrodynamics solver.
+We adopt the common solution of artifiially reducing the wind velocity from massive stars, choosing $v_{\rm wind} = 500$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
+However, this can still be problematic once the star evacuates the local ISM and injects its energy to very low density ($n \lesssim 10^{-3}$ \ccunit) gas.
+We address this issue by mass loading our winds when injection would lead to wind bubble temperatures in the spherical source region above a maximum temperature typical of wind bubble.
+This is a free parameter that we take to be 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
+Mass loading in this manner is (in effect) a sub-grid model for the unresolved ISM mixing at the boundary layer of the wind bubble, which is in fact the source of a majority of the gas mass within the wind bubble \citep{Weaver1977}.
+We take the metal species abundances of the mass loaded ISM to be the average cold / warm ISM abundance on each grid to prevent artificially inflating/deflating the overall abundances.
+We discuss our ability to resolve typical single star wind bubble properties in Appendix ~\ref{appendix:stellar winds}.
+
+%parameterized in this work with the STARBURST99 wind model, \citep{Leitherer1992}:
+%\begin{multline}
+%{\rm log} \left[ v_{\rm wind} {\rm (km~s^{-1})} \right] = 1.23 - 0.30~{\rm log}~\left[L{\rm (L_{\odot})}\right] \\
+% + 0.55~{\rm log}\left[M({\rm M_{\odot}})\right] + 0.64~{\rm log}\left[T_{\rm eff}(K)\right] \\
+% + 0.13~{\rm log}\left[Z({\rm Z_{\odot}})\right].
+%\end{multline}
+
+Stars that only undergo an AGB phase deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks.
+AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$.
+For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars as well.
+
+\subsubsection{Core Collapse SNe}
+\label{sec: core collapse}
+Stars between  $M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
+Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}).
+We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
+We use the same Monte Carlo sampling method as used in our stellar winds to map the spherical injection region to the grid.
+We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle.
+In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.
+
+\subsubsection{Type Ia SNe}
+\label{sec:Type Ia}
+We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as WD particles, marking a subset as Type Ia SN progenitors.
+This is the most self-consistent model for Type Ia SNe in galaxy-scale simulations.
+We note however that for the low SFRs in our isolated dwarf galaxy simulation, the first Type Ia SN only appears after a few hundred megayears of simulation time.
+By the end of the simulation presented here (500~Myr), only 18 have gone off.
+At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
+%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
+%or, 
+%\[
+%M_{\rm WD} = 
+%\begin{cases}
+%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
+%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
+%\end{cases}
+%\]
+%where $M_{\rm *}$ is the initial mass of the WD progenitor.
+We follow the common assumption that progenitor stars with initial masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017a}.
+
+We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution model.
+The Type Ia SN rate is taken to be a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope $\beta$ and normalization $N_{\rm Ia}/M_{\rm SF}$ are observables.
+The latter represents the number of Type Ia SNe per mass of star formation.
+By assuming an IMF  $dN/dm$, one can write down the fraction $\eta$ of stars capable of forming a Type Ia SN progenitor that \textit{will} explode within a Hubble time.
+This is given as
+\begin{equation}
+\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
+\end{equation}
+where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF, and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
+The distribution slope $\beta$ is of order unity, with typical values between 1.0 and 1.2 \citep[see][for a recent review]{Maoz2014}.
+$N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the Type Ia SN rate and integrating over a Hubble time.
+Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
+For our fiducial values, we adopt $\beta = 1.2$ \citep{Maoz2010} and $N_{\rm Ia}/M_{\rm SF} = 0.8\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013}.
+Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.
+
+Finally, we can normalize $\Psi(t)$ to give the probability per unit time $\dot{P}(t)$ that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor.
+Integrating this gives the total probability at any given time as
+\begin{equation}
+P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
+\end{equation}
+where $t_{\rm o}$ is the formation time of the WD and the leading term on the right hand side properly normalizes the total probability over a Hubble time to $\eta$.
+This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
+In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle.
+For $u \in [0,1]$, we interpolate its position on a pre-tabulated and inverted cumulative probability distribution function to assign a single time at which the WD particle will explode as a Type 1a supernova.
+We institute a minimum delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.
+
+\subsubsection{Ionizing Radiation from Discrete Sources}
+\label{sec:ionizing radiation}
+Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies.
+\ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance.
+However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds.
+Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
+As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.
+
+Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation.
+We follow HI and HeI ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
+
+We determine the HI and HeI ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
+We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star.
+Stars less massive than about 15 M$_{\odot}$ and very massive stars with sub-solar metallicity are generally not well sampled by the OSTAR2002 grid.
+In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).
+
+Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}).
+The average energy for HI and HeI ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
+
+We also include the effects of radiation pressure on HI.
+This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}.
+We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared.
+This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}.
+However, the importance of multiple scattering is still unclear.
+Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013a,Reissl2017,Wibking2018}.
+Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.
+
+\subsubsection{Diffuse  Heating}
+\label{sec:diffusive heating}
+We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the FUV (6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles.
+The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the spectral energy distributions for each gridded star.
+Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
+Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
+However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}.
+Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile.
+Only recently has the localization and time variation of these processes been considered.
+
+Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}.
+We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
+We assume HeI ionization generally follows HI.
+This allows us to approximate HeI self-shielding using the same form (A.
+Rahmati, private communication).
+We ignore HeII photoionization from the UV background entirely.
+For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
+As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
+This is described in more detail in Appendix ~\ref{appendix:cooling}.
+
+%Ignoring this effect leads to an overestimation of the cooling rates when in the self-shielding regime.
+%We refer to \citet{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \citet{Gracklemethod} for its specific implementation, as used here.
+
+We assume the galaxy is mostly optically thin to stellar FUV and use only local approximations for shielding.
+We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
+\begin{equation}
+\label{eq:PE}
+\Gamma_{\rm pe} = (1.3 \times 10^{-24} \rm{erg~s^{-1}~cm^{-3}})\, \epsilon n_{\rm H} G_{\rm eff} D 
+\end{equation}
+where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust-to-gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
+Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
+
+The value of $D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
+The extremely low dust-to-gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a ratio $D$ that scales linearly with metallicity at very low metallicity.
+At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit.
+Given that the ambient density of the ISM is generally 1--10~cm$^{-3}$, we can safely assume the FUV field to be optically thin.
+However, we do include a localized attenuation prescription that may influence high-density or metal-enriched regions of the galaxy.
+We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.
+
+Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
+This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations.
+Our chemical network only includes contributions from H, He, and H$_2$ to n$_e$.
+Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
+%This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
+
+\subsubsection{Lyman-Werner Radiation}
+\label{sec:LW}
+In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rate.
+We compute the stellar Lyman-Werner flux again from the OSTAR2002 grid by integrating the spectral energy distributions over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}).
+Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
+We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.
+
+\section{Galaxy Initial Conditions}
+\label{sec:IC}
+We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy.
+The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
+Leo P is gas rich, with a neutral hydrogen mass $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and stellar mass $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to an observed neutral hydrogen radius $r_{\rm HI} = 500$~pc.
+LeoP has a low metallicity, with an oxygen to hydrogen abundance ratio (O/H) of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
+Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
+
+The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential.
+The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
+\begin{equation}
+\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
+\end{equation}
+where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass.
+We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$.
+We adopt a \citet{Burkert1995} dark matter potential with virial mass and radius $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and scale radius r$_{\rm s} = 990$~pc.
+This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc.
+These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}.
+
+Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
+This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
+During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}.
+We stop the artificial driving 25~Myr after the first star particle forms.
+These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
+We note this initial driving is ad hoc in that we do not include other effects from the stellar population that would have caused these SNe.
+
+We emphasize here that our model, with no initial stellar distribution, is not intended to identically reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
+In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations.
+Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances.
+In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution.
+Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe.
+The subsequent metal enrichment from the stars in our simulation can be thought of as tracking a change in abundances from arbitrary initial conditions.
+We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.
 
 \section{Results}
-For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
-This galaxy has an average star formation rate of $1.2~\times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
-The galaxy exhibits strong, feedback-driven outflows \citep{Emerick2018b} that eject a significant amount of gas and metals from the galaxy.
-The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$, where $\eta$ is defined as the mass outflow rate in through a 0.1~$R_{\rm vir}$ annulus centered at 0.25~R$_{\rm vir}$ divided by the 100~Myr averaged SFR.
-These winds eject 95\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.
+\label{sec:results}
+We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms.
+Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run.
+The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical height $|z| < 200$~pc relative to the center of the galaxy.
+ISM properties are calculated considering only the gas contained within the disk of the galaxy.
+We include a resolution study in Appendix \ref{appendix:resolution_study}.
 
-In this work we focus in detail on how each of the 15 individual metal species evolve in this galaxy.
-We address differences between the ejection fractions of each metal in Section~\ref{sec:ejection} and analyze for the first time the mass-fraction PDFs of the metals retained by the ISM in Section~\ref{sec:mixing}.
+Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.
+All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset dd76ad10.
 
-\subsection{Preferential Ejection of Metals from the ISM}
-\label{sec:ejection}
+\subsection{Morphological Structure and Evolution}
+\label{sec:structure}
+
+We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
+These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
+This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
+This central region quickly fills with warm and hot gas generated from radiation feedback and SNe respectively.
+Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels.
+The ISM properties are quantified further in Section~\ref{sec:phase}.
 
@@
 \centering
-\includegraphics[width=0.99\linewidth]{species_bar.png}\\
-\includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
-\caption{Top: The mass fraction of each metal species in the \textit{full simulation box} contained in the halo, gas in the galaxy disk, and stars.
-Bottom: The mass fraction of species within \textit{the disk} alone in each phase of the ISM (bottom).
-The leftmost bar in each plot shows the sum of all metals.}
-\label{fig:species_fractions}
+\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
+\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation.
+Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row).
+Each individual main sequence star particle is shown in the number density projections as a single black dot.}
+\label{fig:panel_x}
 \end{figure*}
 
-%mm [this all seems to have been deleted in one version, but doesn't look like it should have been.  Down to ">>>>"] <<<<<<< HEAD
-The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
-We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).\footnote{The $f_{\rm H_2}$ restriction on the CNM is not relevant in our simulations, as there are no cells with $f_{\rm H_2} > 0.5$.
-$f_{\rm H_2}$ remains below about 0.35 for all cells (see Paper I).}
-%mm Again, with the exception of  H and He, we [H & He aren't metals]
-    We
-only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
+This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time.
+Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--120~pc.
+Towards the end of the simulation time, the half-light radius is $391 \pm 19$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
+Although the disk remains thin beyond the half-light radius, with a scale height of around 50~pc, it is fully resolved at all radii.
+By the end of the simulation, the majority of the disk has a scale height of $\sim$100~pc.
 
-We find two major results.
-%mm [reversed order of results to follow figure.  The opposite choice could also be made, by reversing the order of the figure...]
-    First, 
-only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies
-%mm 
-    among elements.
-The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
-This suggests that individual metals \textit{do not} share the same dynamical evolution.
-%mm Clearly
-       Thus, 
-metal enrichment in galaxies is a phenomenon that cannot be fully captured using a single, global metallicity field.
-In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
-
-    Second,
-nearly all of the metals 
-%mm
-    retained in the disk
-reside within neutral gas, mostly in the CNM; only a few percent
-reside in the hot phases.
-The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
-This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
-
-%The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
-We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
-Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
-
-%We find two major results.
-First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases.
-The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
-This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
-Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies.
-The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
-This suggests that individual metals \textit{do not} share the same dynamical evolution.
-Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field.
-In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
-%mm [end of apparently deleted section] >>>>>>> 134a2fabac2aea2275cb3e8014308282b438742f
+Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging.
+For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
+In the final column of Figure~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
+With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
+At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$.
+These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{species_bar_sources.png}\\
-\caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
-These channels differ in both when metals are ejected, as determined by stellar evolution, and the phase of the ISM into which they are ejected.
-We note that the minimal contribution from Type Ia SNe for the iron-peak elements is because  no older stellar population was initialized, so only 16 of them have exploded by the end of our 500~Myr simulation.}
-
-\label{fig:species_sources}
+\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
+\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on views.}
+\label{fig:panel_z}
 \end{figure*}
-
-The only physics that separates the dynamical evolution of these elements in our simulations is the individual sources of enrichment: AGB winds (stars less than 8~M$_{\odot}$), stellar winds (stars above 8~M$_{\odot}$), core collapse SNe, and Type Ia SNe.
-These channels differ in: 1) how long after a given star formation event they occur, 2), by consequence, the typical ISM properties in which they occur, and 3) how much energy is associated with each event, which determines ejecta temperature and velocity.
-To understand where each of the elements in Figure~\ref{fig:species_fractions} originated, we show the mass fraction of metals produced through each channel in Figure~\ref{fig:species_sources}.
-Core collapse SNe are responsible for over 90\% of the total metal enrichment in our galaxy, but this is clearly not true for all elements.
-In particular, a majority of N (74\%) and Ba (65\%) are ejected by AGB winds; both are retained at a higher rate than the rest of the metals.
-That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yield tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through SNe.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and SNe.
-However, this cannot be proven as we lack Lagrangian information about individual gas elements.}
-% AE: Actually if there are significant isotope variations between nucleosynthetic sources (i.e.
-N produced in AGB winds is a different isotope than the trace N produced in SNe) then that could be a very cool thing to distinguish if we had good gas-phase abundance measures of various isotopes...
-but maybe not if they aren't very stable....
-We discuss how this result may extend towards other metal yields that are not well sampled on our relatively short (500 Myr) simulation timescales in Section~\ref{sec:discussion:metal yields}.
-
-AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of SNe ($\sim$1000~km~s$^{-1}$).
-In addition, their longer timescales relative to massive stars means that AGB stars are typically removed from their birth regions and randomly distributed through the galactic disk.
-The changes in typical ISM density and height of these events contributes to these variations.
-We show histograms of the average number density within 20~pc of any given enrichment source (top) and height above/below the disk (bottom) within 1~Myr of each event (as limited by our output cadence) in Figure~\ref{fig:spatial distribution}.
-As shown, SNe peak at very low densities, indicating that most explode in superbubbles, regions carved out by previous SNe.
-AGB stars predominately release their metals close to the average ISM density.
-The scale height distributions for both events show no significant differences.
-We do not expect these differences to be the dominant effect in driving the differential evolution of elements ejected by AGB winds vs.
-SNe, compared to the energetics, but can certainly play a significant role in determining the mixing behavior of individual enrichment events.
-The changes to mixing behavior as a function of ISM properties will be investigated in more detail in a future work.
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{SE_density.png}\\
-\includegraphics[width=0.95\linewidth]{SE_z.png}
-\caption{The volume-averaged gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
-\label{fig:spatial distribution}
+\includegraphics[width=0.975\linewidth]{scale_height}
+\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figures~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
+\label{fig:scale_height}
 \end{figure}
 
-\subsection{Mixing and Distribution of Metals in the ISM}
-\label{sec:mixing}
-We characterize the metal distributions (in Sections~\ref{sec:log-normal} and \ref{sec:phase-pdfs}) and evolution (in Section~\ref{sec:statistics}) in our galaxy to build towards a  a complete model for how metals mix and evolve in the complex, multi-phase ISM of real galaxies.
+\subsection{Star Formation Rate and Mass Evolution}
+\label{sec:sfr}
 
-\subsubsection{A Functional Form for Metal PDFs}
-\label{sec:log-normal}
+We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
+The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$.
+The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation.
+Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.19 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
+We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.
 
-The log-normal distribution is found often in nature, generally describing multiplicative processes with non-negative values that grow with time.
-In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}.
-In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}.
-Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}.
-It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape.
-This includes a log-normal component, generated by multiplicative processes---in this case shocks and the turbulent cascade in the ISM---and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2017}.
+We note that the granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
+Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
+For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$.
+Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense.
+Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.
 
-The physics that drives the density PDF is directly related to the process of metal mixing and diffusion.
-However, there is no a priori reason why gas density and metallicity PDFs should have similar functional forms.
-We demonstrate here for the first time that the mass fraction PDFs for each metal species in our simulation can indeed be well fit using a piecewise log-normal + power-law PDF.
-We use a simple conceptual model in Section~\ref{sec:interpretation} to motivate the emergence of this distribution.
-
-We follow \citet{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF.
-We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element.
-This PDF is given as
-\begin{align*}
-  p(Z) =
-  \begin{cases}
-    \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right],
-    & Z < Z_{\rm{t}} \\
-    % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
-    N p_o Z^{-\alpha},
-    & Z > Z_{\rm{t}}
-\end{cases}
-\end{align*}
-where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm t}$ is the metal fraction at the transition between the log-normal and power-law components.
-When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm t}$ as free parameters.
-These conditions set $N$ and $p_o$ to
-\begin{equation}
-N = \frac{1}{2} \left[ 1 + \rm{erf}\left( \frac{ln\left(Z_{\rm t}\right) - \mu}{\sigma\sqrt{2}}\right)\right] + \frac{p_o}{\alpha-1}Z_{\rm t}^{-\alpha + 1}
-\end{equation}
-and
-\begin{equation}
-p_o = \frac{1}{\sigma Z_{\rm t} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm t}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm t}) \right]
-\end{equation}.
-
-We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin 
-%mm with 
-         width
-of 0.05 dex.
-We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \citep{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins.
-The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted.
-The log-normal + power-law PDF produces the best fit in nearly all cases.
-
-We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
-These PDFs have been computed at an arbitrary single point in time in the middle of the simulation run.
-% 270 Myr
-For clarity, we only show a subset of the 15 elements we follow.
-As shown, there are clear differences in the PDFs across elements of different nucleosynthetic sources (AGB vs.
-SNe) and between each phase.
-However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions.
-We discuss the differences among each phase in more detail in the next section, but note here that the significance of each of these components varies notably across phases.
-In many of these cases, the piecewise log-normal + power-law distribution fits the numerical PDF quite well.
-However, there are often deviations, particularly at low metal fractions, from pure log-normal behavior.
-This manifests as either a very broad, flat PDF at low metal fraction (see N and Ba, for example), or large peaks not well described by $p(Z)$ at low metal fraction.
-In these situations, it is unclear what, if any, portion should be considered as a log-normal, or if there are multiple components within this region.
-
-We argue here that the log-normal + power-law PDF can be a powerful tool for modeling the metal fraction  PDFs of individual elements in galaxy models.
-The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM.
-In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions.
-Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$.
-As this is the source of star-forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.
+At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
+By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
+The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
+For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% at 500~Myr.
+The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy from feedback-driven galactic winds.
+During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM.
+Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
+The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
-\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black).
-For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
-We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.
-Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
-\label{fig:log-normal}
+\includegraphics[width=0.475\linewidth]{sfr_snrx100}
+\includegraphics[width=0.475\linewidth]{mass_evolution}
+\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins.
+Broken portions of this histogram are time periods with no star formation or supernovae.
+Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.
+Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
+\label{fig:sfr_mass_evolution}
 \end{figure*}
 
-\subsubsection{PDF Variation Across Gas Phase}
-\label{sec:phase-pdfs}
+\subsection{ISM Properties}
+\label{sec:phase}
 
-The various phases represented in Figure~\ref{fig:log-normal} involve variations in density and temperature of more than six orders of magnitude.
-The evolution of each phase is qualitatively different, and the metal mixing behavior of each should vary.
-Mixing timescales over a given length scale should be related to the local sound speed; hot gas, with higher sound speeds, should mix more rapidly than the dense, disconnected clumps of cold gas in the ISM.
-In addition, one would expect a metallicity gradient with gas temperature as enrichment occurs first in the hot phases, cooling and enriching denser gas over time.
-We examine the PDF variations among elements in each phase, as shown in Figure~\ref{fig:log-normal}, in more detail here.
+Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
+We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
+We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content.
+By this definition, although our galaxy certainly contains molecular hydrogen, molecular gas as a phase does not exist; the peak f$_{\rm H_2}$ in any single cell remains below 30\%.
+See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
+The properties of these phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
+Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.
 
-Unsurprisingly the diffuse HIM contains the most metal enriched gas, as it is comprised predominately of metal enriched SN ejecta.
-Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
-Generally, in colder gas the metal PDFs become less enriched with broader, low-metal-fraction components and steeper, power-law tails.
-Although the extended power-law tail of the HIM leads to a large range of metal fractions, the HIM represents very little mass, and this tail represents recent, un-mixed enrichment.
-The comparatively narrow width in the log-normal regimes of the CNM is perhaps surprising.
-Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is more well mixed.
-This runs counter to the idea that mixing times should be long in colder gas, unless (as we argue) mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.
+Figure~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
+One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
+Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
+We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
+Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left.
+The boxed regime in the lower right corner shows our star formation density and temperature threshold.
+Gas in this regime is rapidly consumed by star formation and subsequent feedback.
+Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average.
 
-Although these trends across phases hold for all elements, there are qualitative differences between elements, particularly between those ejected predominantly by AGB winds (e.g.
-Ba and N) and those ejected by SNe (e.g.
-O and Mg).
-In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by SN enrichment.
-The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the CNM.
-Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N included in SNe yields.
-Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and SNe.
-AGB wind elements enrich the WNM and WIM directly, rather than the HIM, which would increase their mixing timescales and broaden their PDFs.
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{phase_diagram.png}
+\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gas interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr.
+The dashed lines are lines of constant pressure, separated by factors of 10.
+The region in the lower right corner indicates our density and temperature thresholds for star formation.}
+\label{fig:phase}
+\end{figure}
 
-\subsubsection{The Time Evolution of Metal PDFs}
-\label{sec:statistics}
-We focus on the time evolution of the full numerical PDFs in this section.
-Our results here do not depend upon the choice of functional form for $p(Z)$.
-Figure~\ref{fig:phase-statistics} shows the evolution of four different statistics for the O (top) and Ba (bottom) PDFs.
-These two elements are treated as representative elements for SN and AGB wind production respectively.
-The difference between the mean and median masses of the PDF (second column) is a measure of the skew of the PDF.
-Positive values indicate that metals are preferentially sequestered in metal-rich gas, and are less well mixed throughout the given phase.
-The skew is always positive in these distributions.
+The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
+The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
+The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run.
+The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation.
+During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1.
+Although the CNM dominates the mass fraction, it is a negligible component of the ISM volume, which is WIM dominated.
+However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
+Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
+
+These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
+They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (defined in those works as gas with 100~K$<$T$< 3\times 10^{4}$), with cold gas having between 1 and 10\% of the mass, and occupying negligible volume.
+Hot gas (defined as gas with $T > 3\times 10^{4}$~K) occupies 10\% of the volume, with negligible mass, in their galaxy, while our WIM alone occupies $>$ 50\% of the volume.
+Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) and hot gas (by volume fraction) that seen in the more massive dwarf galaxy in these works.
+The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
+We have compared our cooling curves to those used in \citep{Hu2017} and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.
+
+\begin{figure*}
+%\centering
+\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
+\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
+\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
+\label{fig:ISM_evolution}
+\end{figure*}
+
+\subsection{Interstellar Radiation Field}
+\label{sec:ISRF}
+
+The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}.
+This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
+In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
+The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
+The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.
+The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
+At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.
+
+The bottom panel gives the HI ionizing photon flux from stellar radiation.
+The ionizing radiation profile follows a similar trend, yet with significantly more variation, anywhere from two to four orders of magnitude.
+As this radiation is followed through radiative transfer, the profile encodes information about local attenuation by dense, neutral gas.
+This is the main driver of the differences between the two panels.
+The total fluctuation in both panels is due in part to the low-level, stochastic star formation in our galaxy.
+A higher star formation rate would produce a more regular population of massive stars and more uniform (in time) ISRF.
+
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{G_o_profile} \\
+\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
+\caption{
+Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr.
+Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc.
+The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
+The bottom panel gives the HI ionizing stellar radiation flux.
+Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point.
+For this reason we only shade between the first quartile and maximum values.
+HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.}
+\label{fig:ISRF}
+\end{figure}
+
+\begin{figure*}
+%\centering
+\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
+\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
+\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
+Here, we include all gas within the mid-plane of our dwarf galaxy.
+Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
+This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
+\label{fig:ISRF_2D}
+\end{figure*}
+
+To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr.
+This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
+The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
+From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
+Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation.
+In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency.
+It remains to be seen which of these two modes of feedback is more important in regulating star formation.
+
+\subsection{Outflow Properties}
+\label{sec:outflows}
+
+The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}.
+However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
+In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
+We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
+\begin{equation} \label{eq:dotM}
+\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
+\end{equation} 
+We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.
+
+The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
+Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
+For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor.
+The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors between 20--100 throughout the simulation time.
+This declines towards larger radii, however, with substantially less outflow past the virial radius.
+\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift, consistent with our results.
+The fluctuations in both of these panels are directly correlated with the SFR, with increased outflow during periods of star formation, and decreased outflow during periods of quiescence.
+
+Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
+Using a fit provided in \citet{Muratov2015} to extrapolate and compare $\eta$ at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
+These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
+We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find lower mass loading factors even closer to the disk, at 0.05 $R_{\rm vir}$, between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$; certainly this implies even smaller mass loading factors at 0.25 $R_{\rm vir}$.
+
+\begin{figure*}
+\includegraphics[width=0.45\linewidth]{total_mass_outflow}
+\includegraphics[width=0.45\linewidth]{total_mass_loading}
+\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
+\label{fig:mass_outflow}
+\end{figure*}
+
+Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
+In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
+Gas with a negative velocity is moving towards the center of the halo.
+Roughly 25\% of this mass is inflowing, mostly with modest negative velocities, and corresponds to previously ejected gas mixing and recycling throughout the halo.
+Half of the outflowing gas (positive velocities) is moving at velocities below 30 km s$^{-1}$, 75\% at velocities below 70 km s$^{-1}$, and 95\% at velocities below 100 km s$^{-1}$.
+Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-negligible amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$.
+The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominating at velocities above 200 km s$^{-1}$.
+The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling WIM and HIM, consistent with the results in \citet{Hu2016,Hu2017}.
+However, as shown, the HIM, which is mostly the SN ejecta itself, comprises very little of the outflow by mass.
+Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM.
+Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
+The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
+
+\begin{figure}
+\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
+\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
+This is averaged over the same time interval as Figure~\ref{fig:ISRF}.
+The outflowing material is multiphase, broken into WNM, WIM, and HIM.
+See Section~\ref{sec:phase} for definitions of these regimes.
+We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K.
+There is little to no outflowing mass in the CNM.}
+\label{fig:outflow_velocity}
+\end{figure}
+
+\subsection{Metal Evolution} 
+\label{sec:chemical evolution}
+
+\subsubsection{Metal Enriched Outflows}
+Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
+This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
+In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}.
+The parameter used to quantify metal outflow efficiencies varies among works.
+Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
+\begin{equation} \label{eq:eta-metal}
+\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
+\end{equation}
+where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
+These metal loading factors fluctuate significantly with the SFR, just as was shown in Figure~\ref{fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
+On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5).
+Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}.
+\cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
+Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.
+
+\begin{figure}
+\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
+\includegraphics[width=0.9\linewidth]{metal_retention}
+\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Figure~\ref{fig:mass_outflow}.
+This is the ratio between the metal outflow rate and the metal production rate.
+{\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
+In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
+\label{fig:metal_evolution}
+\end{figure}
+
+These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
+This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
+After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
+This continues throughout the simulation, with only $\sim$4\% of produced metals residing in the disk of the galaxy.
+It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius until about 350 Myr where the fraction levels off to just above 50\%.
+Likewise, the CGM metal content continually decreases until the end of the simulation from loss through the virial radius of the halo.
+See Section~\ref{sec:obs_metals} for further discussion.
+
+\subsubsection{Differential Evolution of Elements Within the ISM}
+It is important to understand how metals from each source of stellar yields enrich the ISM.
+Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}.
+This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed.
+Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Avillez2002,Tassis2008,YangKrumholz2012}.
+It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
+It is even more unclear how metals are transported and distributed within low-mass dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.
+
+We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
+The left panel gives the abundance ratio of N to O throughout the ISM.
+The right
+two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy.
+These show regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K) connected by cold filaments, warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
+
+\begin{figure*}
+\includegraphics[width=0.98\linewidth]{log_NO_panel}
+\caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances.
+The left slice gives the ratio of the abundance between N and O, normalized to the solar abundance, while the number density and temperature are shown on the right.
+In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occurred in the preceding 5 Myr as black stars and orange diamonds respectively.}
+\label{fig:metal_slices}
+\end{figure*}
+
+As shown in the left panel, [N/O] varies significantly over this section of the ISM with notable differences across the various phases and ISM structures.
+The hottest gas, dominated by recent supernova explosions is overabundant in oxygen, relative to solar (purple).
+However, the relative abundance of nitrogen increases in the WIM and WNM, being overabundant relative to solar (green).
+
+At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars.
+Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
+Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
+The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
+This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
+A more detailed analysis is beyond the scope of this work, but we investigate this in detail in Emerick et.
+al.
+(in prep.).
+
+\section{Discussion}
+\label{sec:discussion}
+
+\subsection{Comparison to Observed Low Mass Dwarf Galaxies}
+\label{sec:observation}
+
+As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs.
+Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of $z = 0$ dwarf galaxies.
+However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies.
+We show that these properties are broadly consistent with observations.
+
+\subsubsection{Gas and Star Formation}
+\label{sec:gas_sf}
+
+The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}.
+However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
+In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
+In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.
+
+Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
+We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}.
+We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the area of the disk within the radius of the outermost star formed within the previous 10 Myr.
+Likewise, $\Sigma_{\rm gas} = M_{\rm gas,10} / A_{*,10}$, where M$_{\rm gas,10}$ is the total gas mass within this defined disk.
+However, the total gas content cannot be determined observationally.
+To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He.
+We note that there is generally no correction made for any possible H$_{\rm 2}$ or HII content.
+As shown in Section~\ref{sec:molecular gas content}, these components may be significant.
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution.png}
-\caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation.
-The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
-\label{fig:phase-statistics}
+\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
+\includegraphics[width=0.475\linewidth]{all_gas_efficiency_evolution.png}
+\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
+See text for details of the calculation.
+Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars.
+On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}.
+There is no clear correlation with time in this diagram.}
+\label{fig:KS}
 \end{figure*}
 
-For O, the median mass fraction is ordered by phase temperature.
-The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm 1$ dex over the simulation time.
-The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
-%This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events.
-Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread.
-The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling and/or mixing through multiple phases until enriching star-forming gas.
-This
-%mm is the only explanation for [that's perhaps too strong a claim]
-    can explain
-how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels). Individual enrichment events 
-%mm will 
-have significantly higher metallicities than the ambient ISM in any phase, and 
-%mm will 
-drive an increase in the difference between the mean and median of the PDF.
-These can be seen as the obvious spikes in the HIM and WIM.
-For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.
+We include recent observational constraints on these relationships in Figure ~\ref{fig:KS}.
+Our galaxy fluctuates significantly about both relationships with no clear trends in time.
+However, in both cases, it is consistent with the available observational sample.
+At times our galaxy exhibits gas surface densities below the observational constraints.
+The trend is still consistent with higher densities at this point, but with a larger scatter towards lower star formation rate densities and efficiencies.
 
-% In each phase, enrichment events will tend to drive larger differences between mean and median mass fraction,
+In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
+It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
+This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
+The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.
 
-Although these trends are generally true for Ba, its evolution is much more complicated.
-%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability.
-Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM.
-The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
-Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in SNe.
-The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
-These tails represent the most recently enriched gas,
-%mm and 
-        which
-is clearly much more locally confined than O.
+\subsubsection{Molecular Gas Content}
+\label{sec:molecular gas content}
+The molecular gas content of low-mass dwarf galaxies is generally assumed
+to be small, but is not well constrained by either theory or observations.
+Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
+As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range.
+H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
+The gas-phase reaction dominates in our low-metallicity galaxy over the other two channels by several orders of magnitude.
+In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
+Thus the presence of some ionizing background is required to generate the molecular fractions we find in our simulations, as confirmed in separate test simulations.
+\textbf{Our model does include a contribution from the meta-galactic background to the photodetachment of H$^{-}$.
+However, we note that we do not account for the contribution to this rate from the ISRF.
+We find that the H$_2$ fraction is more strongly dependent upon the Lyman-Werner radiation field, which is followed for each star, than the H$^{-}$ photodetachment rate.
+Our tests suggest that ignoring the stellar contribution to H$^{-}$ may lead to a 10--20\% overestimate in the computed H$_2$ fractions.
+This is discussed in more detail in Appendix~\ref{appendix:H minus}}.
 
-%{\bf (move to discussion?)}:
-The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e.\ the ratio between the total mass of metals and the total mass).
-Assuming star-forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex),
-%mm but
-   though 
-significant, for elements released during SNe explosions, but can be very significant, up to $\sim$ 0.8 dex, for elements released in AGB winds.
-Chemical evolution models, especially one-zone models, follow the mean metal fraction, rather than the median.
-%mm These results indicate that these 
-            Our results indicate that such
-models are biased to overestimate gas and stellar elemental abundances.
-% However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.
+In contrast, \citet{Hu2016} and \citet{Hu2017} find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
+However, although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
+Our model suggests that both H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies.
+Indeed it is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, though it is worth noting that the rate coefficients associated with gas-phase H$_2$ formation are still uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
+Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
+It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
+This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
 
-To summarize, Figure~\ref{fig:phase-statistics} demonstrates: 1) there are qualitative differences in how SN-injected elements (e.g.
-O, Mg) and AGB-wind-injected elements (e.g.
-N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM; 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM and because the hotter phases are more directly populated by recent enrichment events; 3) the cooler, denser phases, particularly for SN injected elements, are more well mixed than the hot phases of the ISM; 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function; and therefore 5) the median metallicity available for star formation
-%mm rates 
-lies below the mean galactic value.
-In the case of SN injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
-For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.
+\subsubsection{Metal Retention}
+\label{sec:obs_metals}
 
-\section{Discussion}
-\label{sec:discussion}
-We begin with a simple toy model that motivates the power-law tail at high metal fractions of the metal fraction PDFs and a subsequent turnover at low metal fractions in Section~\ref{sec:interpretation}.
-This work is placed in context with previous papers focusing on metal mixing in the ISM in Section~\ref{sec:context}.
-We discuss the relevance of additional AGB yields not directly followed in this study in Section~\ref{sec:discussion:metal yields}.
-Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impacts of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
+The simulations presented here have not yet been run for the gigayear timescales required to begin to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$.
+However, we can compare to a key observable: the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from closed box stellar evolution models given the galaxy's star formation history.
+This can be done readily with Milky Way dSph's.
+Their stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
+However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
 
-\subsection{Physical Interpretation of the PDF}
-\label{sec:interpretation}
-%
-% KVJ wanted clarification on this argument. I believe my added text 
-% does this sufficiently.
-Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_{\rm o}$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$.
-Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas.
-In this case, $p(t,Z)$ initially takes the form of a double-delta function
-\begin{equation}
-p(t_{\rm o},Z) = \delta(Z_{\rm o}) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
-\end{equation}
-%mm [edited the rest of this paragraph, and the next though I don't think there are any substantive changes unmarked.]
-If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time  $\tau_{\rm mix}$ this gas will have mixed with an equal amount of primordial gas.
-At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$.
-Then, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.
-This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
-The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.
+Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich, star forming, low-mass dwarf galaxy, with an observable HII region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
+Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
+As discussed in Section~\ref{sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
+However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
+Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
 
-Thus, if the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous distribution $p(t,Z)$
-%mm , or $p(Z)$, 
-of these many events will be $\delta(Z_{\rm o})$ plus a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.
-% and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
-The slope of the power-law, then, is determined by the rate of injection versus mixing with the ambient medium.
-A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium.
-Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than
-%mm enrichment. 
-         injection.
-If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.
+It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium.
+While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
+We find 5.3\% of all metals lie within 1 kpc of the center of our galaxy, 24.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 51\% outside $R_{\rm vir}$.
+This is consistent with previous works, but this is again an evolving quantity.
+In addition, the amount of gas that escapes the virial radius is certainly sensitive to the details of gas accretion from the IGM on this galaxy, which we cannot capture in this model.
 
-In reality, however, $M_o$ is not an inexhaustible reservoir of primordial gas.
-Eventually the entire ambient medium will become enriched to some $Z > Z_o$, and $p(Z)$ will consist entirely of a truncated power-law.
-As enrichment proceeds, gas near the low metallicity truncation of $p(Z)$, which still comprises much of the mass of the system, enriches towards higher metallicities in the power-law tail.
-This will produce a turnover at the low $Z$ limit of $p(Z)$.
-The low-turnover limit is produced by diffusion from many different sources, and is thus a multiplicative process, which, as we noted above, tends to produce log-normal distributions.
-%mm [additive vs multiplicative]
-   %{\bf [According to Section~\ref{sec:log-normal}, MULTIPLICATIVE processes produce log-normals. Additive processes produce power-laws.  However, see Mouri (2013) for a possible counterexample...]}
-The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.
+The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
+Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return.
+In addition, the accretion of pristine gas from the intergalactic medium could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals.
+This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.
 
-This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases. 
-%mm The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions. 
-     Individual enrichment events start at very high metal fractions in the low-density HIM, 
-     so they easily create long power-law tails.
-Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low metallicities.
-Cold, dense gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.
+\subsection{Missing Physics}
+Although we include many detailed physical models in our simulations, there remain additional physical processes that may be relevant, which we now discuss.
 
-%
-%
-%
-%Although this model is useful to explain these very general features, it is certainly incomplete in practice.
-Enrichment proceeds irregularly through the mulit-phase ISM with a variety of ejection masses and metallicities.
-Phases are not independent, and the hot phase cools and enriches cooler phases in the ISM, distorting $p(Z)$ within each phase.
-Cold gas is heated up and destroyed through feedback, changing the content of the low-metallicity end of the warm and hot phases.
-Finally, gas is removed from the galaxy through feedback driven winds that preferentially remove metal enriched gas.
-Each of these processes has a non-trivial effect on the evolution of the PDF that will cause deviations from the simple toy model outlined here.
-Determining the exact physical processes that drive and set the properties of each PDF is the subject of ongoing work.
+\subsubsection{Massive Stellar Wind Energy}
+\label{sec:stellar winds discussion}
+Our massive stellar wind model drastically reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$.
+Although our algorithm is entirely capable of generating realistic stellar winds with velocities comparable to those observed, such fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
+When considered in isolation, stellar winds are an important source of pre-SN feedback and can dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
+However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}, unless densities near the ionizing source are high enough to trap the  HII region in the source cell.
+In that case, they can clear out a cavity to allow initial establishment of the HII region.
 
-%
-% A.E. paragraph may need work
-%
+They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
+Although they likely have minimal dynamical importance at resolutions where peak densities are not anyway high enough to trap ionization fronts, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting closer examination in future work.
 
-Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012,Sarmento2017,Sarmento2018}.
-Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
-This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dense gas ($\sim$ 1 km s$^{-1}$).
-Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy.
-This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
-It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing SNe.
-Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star-forming gas.
-Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy.
-The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.
+\subsubsection{Cosmic Rays} 
+\label{sec:CRs}
 
-% From benoit: more explicit title
-\subsection{
-%mm Context With 
-        Comparison with 
-Previous Studies of Metal Mixing}
-\label{sec:context}
-That metal fraction distributions can be described using simple analytic log-normal + power-law PDFs, even in a complex, multi-phase ISM, has not been demonstrated prior to this work.
-In addition, this is the first work to demonstrate differential mixing behavior of individual metal species using 3D hydrodynamics simulations.
-However, there does exist a significant body of work investigating the mixing behavior of passive scalars in a variety of contexts.
-%mm , as discussed below.  [ moved KrumholzTing18 to end of following paragraph.]
-%We discuss our results further in the context of previous research on metal mixing in the ISM and speculate on the physical processes that drive the evolution of these PDFs across phases.
+Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}.
+These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}.
+Modeling cosmic rays is challenging, however, as they encompass a wide range of energies, and there are significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
+Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy.
+In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM.
+Modeling cosmic ray feedback completely thus requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena.
+Finally, including MHD presents additional difficulties in untangling the effects of each individual feedback mechanism on galaxy chemodynamics.
 
-Previous work on the evolution of metals in the ISM varies from studies concerning the advection of passive scalars in idealized turbulent boxes \citep[e.g.][]{Pope1991, PanScannapieco2010, PanScannapiecoScalo2012, PanScannapiecoScalo2013, YangKrumholz2012, SurPanScannapieco2014, Colbrook2017}
-% cite passive scalar reviews by Warhaft 2000 in fluid mech and scalo + Elmegreen 2004?
-to global galaxy models studying generalized advection and mixing of passive scalars \citep[e.g.][]{deAvillez2002,Petit2015,Goldbaum2016} to models with more detailed self-consistent metal enrichment \citep[e.g.][]{Revaz2009,Escala2018}.
-\cite{KrumholzTing2018} predict differential behavior for AGB wind and core collapse SN synthesized elements as a direct consequence of the differences in size of typical planetary nebulae ($\sim$ 0.1~pc) and SN remnants ($\sim$ 100~pc).
+We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested.
+Mechanically, including this relatively simple treatment of cosmic ray feedback in our model is trivial.
+However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to later work.
 
-The evolution of metallicity PDFs has been investigated previously in some of these works \citep[see ][ and references therein]{PanScannapiecoScalo2012,PanScannapiecoScalo2013}, with effort towards developing closure models to describe the evolution of the PDFs of passive scalars in turbulent media \citep[e.g.][]{EswaranPope1988,Chen1989,Pope1991}.
-The astrophysical context in much of this work was enrichment from the first stars, so the focus was on the low-metallicity tail of the PDF and the timescales over which gas is polluted \citep[e.g.][]{PanScannapiecoScalo2013,Sarmento2017}.
-These works often use isothermal turbulent-box simulations initialized with a double-delta function PDF of pristine gas and enriched gas in some varying spatial distribution, ignoring ongoing enrichment.
-Initial PDFs of this form were demonstrated some time ago to evolve into a Gaussian distribution at late times \citep{EswaranPope1988}, but it is unclear if these could also be described with a log-normal distribution.
-However, these works uniformly do not contain the high metallicity power-law tails shown in our work.
-As suggested by our toy model in Section~\ref{sec:interpretation}, this is due to the lack of ongoing enrichment in these studies.
+\subsection{Detailed Stellar Evolution and Binary Stars}
+\label{sec:binary stars}
 
-More detailed models of global galaxy evolution have generally focused on spatial correlations and mixing timescales of initially asymmetric fields, without concern for ongoing enrichment \citep[e.g.][]{deAvillez2002,Petit2015} or focused primarily on the evolution of stellar abundance patterns and metallicity distribution functions \citep[e.g][]{Jeon2017,Hirai2017,Escala2018}, without directly examining the evolution of gas-phase metallicity PDFs.
+Roughly half of massive stars live in binary pairs \citep{Sana2013}.
+Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes.
+This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as SNe.
+This effect could be significant, but is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g.
+STARBURST99).
+For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse SNe occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
+Although they find only $\sim 15\%$ of core collapse SNe explode after 50~Myr, this could still be an important effect.
+Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}.
+Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
 
-% The log-normal density PDFs found in ISM simulations have a variance that is proportional to the mach number \citep[e.g.][(maybe more)]{PNJ1997, Passot1998, Fedderath2008, LemasterStone2009}.
-In our simulations, however,
+Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars.
+This is beyond the scope of this project, but will be investigated in future work.
 
-\subsection{Timescale Dependence of AGB Ejecta}
-\label{sec:discussion:metal yields}
-We can generally say that metals ejected in AGB winds evolve qualitatively differently than metals produced by SNe in our dwarf galaxy.
-However, exactly which metals exhibit these differences, and to what degree, is timescale and metallicity dependent.
-Short timescales ($\lesssim 100$~Myr) only sample enrichment from the most massive AGB stars, while stars on order of a few solar masses only enrich on timescales of a gigayear or longer.
-In our simulations, which only simulate 500 Myr of evolution, N and Ba are dominated by AGB wind ejecta.
-C is commonly used to track AGB wind enrichment, but as it originates from lower mass AGB stars, C enrichment operates on gigayear timescales, longer than we follow in this work.
-Enrichment additionally varies with metallicity.
-Sr, for example, is only significantly ejected through AGB winds at our metallicity on gigayear timescales, while stellar winds from more massive stars dominate the production of Sr on shorter timescales.
-At higher metallicity, much more Sr is produced through massive AGB stars, decreasing the timescale over which Sr should exhibit a differential chemical evolution compared to SN-ejected elements (see \cite{Ritter2017} and \cite{Ritter2017b} and references therein).
+\section{Conclusion}
+\label{sec:conclusion}
+We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
+For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, using individual star particles to model core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, Lyman-Werner radiation and pollution from AGB and massive stellar winds.
+This treatment of feedback, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
+In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P dwarf galaxy.
+We present an overview of the properties of this simulation in this work.
 
-To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected by AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times.
-This model was run using \textsc{SYGMA} \citep{Ritter2017}.
-As shown, metal enrichment from AGB winds only begins to dominate for any elements after $\sim$ 100 Myr.
-This includes N and Ba, which we follow in our simulations, but this model predicts that Ag and Pb will show similar behavior.
-It takes over a gigayear for C to be dominated by AGB wind ejecta, which is the case for many of the elements shown.
-F, which shows very little contribution from AGB winds at short timescales, is dominated by enrichment from them on longer timescales.
-These dependences on metallicity and timescales certainly add complications in generalizing our work and in interpreting observations in the context of the results presented here, but these difference could be leveraged to better understand galactic chemical evolution on multiple, distinct timescales.
-Clearly this motivates future work covering gigayear timescales to fully understand how metal mass fraction PDFs evolve with time.
+For our simulated dwarf galaxy, we find:
+\begin{enumerate}
+\item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
+(See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).
 
-\begin{figure*}
-\centering
-\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0.png}
-\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, without continuing star formation.
-We only show a sample of some of the elements dominated most by AGB enrichment at late times.
-The horizontal line marks a 50\% contribution.}
-\label{fig:agb evolution}
-\end{figure*}
+\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, falling to $\eta \sim 10$ at R$_{\rm vir}$,  and
+metal mass loading factors near unity.
+By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Figure~\ref{fig:outflow_velocity}).
 
-\subsection{Impact on Stellar Abundance Patterns}
-\label{sec:stellar abundances}
-In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star-forming gas in our simulations.
-This could be used to help disentangle sources of scatter in observed stellar abundances, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
-If the metal mass fractions in star-forming gas in our simulations can also be well fit by log-normal + power-law PDFs, and if we can parameterize their evolution as functions of global galaxy properties, this could be used as a powerful tool for modeling stellar abundance patterns in semi-analytic models.
-This would be a physically motivated way to account for both the intrinsic spread in stellar abundances due to inhomogeneities in the ISM and variations in mixing for different metal species.
-We reserve an analysis of these distributions in abundance space in both the gas and stars for future work.
-However, we briefly discuss the connection to star-forming gas and stellar enrichment below.
+\item 
+Only $\sim$4\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of low-mass dwarfs.
+By the end of the simulation $\sim$45\% of the remaining metals stay within the virial radius (but outside the galaxy), while $\sim$50\%
+have been ejected beyond the virial radius. (See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
 
-Unfortunately, there is insufficient star-forming gas at any one time in our simulations to construct PDFs of metal mass fractions.
-However, star-forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, to have mass fraction PDFs similar to the CNM.
-To verify this, Figure ~\ref{fig:stars} shows the difference between the oxygen mass fraction of stars and the median mass fraction from the CNM PDF at the time that particle formed.
-The large scatter at early times ($<$ 120~Myr) is a result of the early enrichment phase, when the initial gas oxygen mass fraction was zero.
-Stars seem to be sampled evenly around the median of the CNM distribution, with only a slight bias (52\% of stars) towards values below the median.
-However, for stars formed after the initial phase, the median separation from the CNM median is 0.31~dex, and can reach up to $\sim$~0.5~dex.
-Though a significant deviation, this is smaller than the typical inner-quartile range (IQR) of the CNM (see Figure~\ref{fig:phase-statistics}).
-Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
-High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
+\item 
+Beyond the stellar radius, the gas scale height is thin ($\sim 50$~pc), yet resolved, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
+This is comparable to the resolution limit of the diffuse HI in observed, gaseous low-mass dwarfs.
+At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Figure~\ref{fig:scale_height}).
 
-%KVJ suggested emphasizing that there is much more potential in this work / work like this by examining more dimensions
-We emphasize that this study focuses on each chemical dimension independently, as a means to first understand galactic chemical enrichment in the simplest possible framework.
-However, the cross-correlation of multiple metal fractions and abundance ratios is the most useful in revealing key processes in galactic chemodynamics.
-A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiments.
-We will examine this more complicated multi-dimensional space with these numerical methods in future work.
+\item The ISRF of our galaxy varies strongly in both space and time by orders of magnitude.
+It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
+The importance of radiation feedback in our model will be investigated in a future work.
+(See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
 
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
-\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the time within 1~Myr (our time resolution) of each star's formation time.
-The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
-\label{fig:stars}
-\end{figure}
+\item 
+We find H$_2$ fractions below 5\% in our dwarf galaxy, consistent with the poor constraints on molecular gas formation in low metallicity dwarf galaxies.
+This H$_2$ forms entirely through gas-phase reactions facilitated by H$^{-}$ in self-shielding regions; H$_2$ formation on dust grains and in the three body reaction are both insignificant.
+Cold, neutral hydrogen dominates the mass of our galaxy.
+While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Figure~\ref{fig:sfr_mass_evolution} and Figure~\ref{fig:ISM_evolution}.)
 
-\subsection{Do These Results Apply to More Massive Galaxies?}
-\label{sec:massive galaxies}
-An important caveat about our work is that these results are derived from simulations of an isolated, low mass, dwarf galaxy whose properties vary dramatically from more massive galaxies like the Milky Way.
-It is unclear how much these results apply to more massive galaxies with deeper potential wells and higher star formation rates.
-Feedback-driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
-We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy.
-With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
-We anticipate three potential regimes of metal retention, depending on dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB stars and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.
-If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
-% AE: rewording given Benoits suggested changes
-%     If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
-This difference would be greater at later times, once AGB enrichment becomes significant. 
-%     Benoit suggested limiting / eliminating discussion relative to metallicity, since this is a little murky (age-metallicity varies significantly galaxy-to-galaxy).
-In addition, the elevated signals of Ba abundance ratios I mention have some amount of contention....
-%     For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
-At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way.
-Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way.
-In addtion, recent observations find elevationd [Ba/Fe] vs.
-[Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS}, which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs.
-Given the lack of definitive explanation, clearly generalizing our results and detailing their observational consequences is a valuable area of future research.
-We would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+\item Finally, we present gas-phase oxygen and nitrogen distributions as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy.
+These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs.
+SNe), as suggested by \cite{KrumholzTing2018}.
+This will be explored in more detail in future work (Emerick et.
+al.
+\textit{in prep.}).
+\end{enumerate}
 
-In contrast, we expect the properties of the enrichment PDFs, and the variations between AGB enriched elements and SN enriched elements (as presented in Figures~\ref{fig:log-normal} and ~\ref{fig:phase-statistics}), to be general.
-We expect metals to exhibit log-normal + power-law distributions in the ISM of all galaxies, with similar trends with enrichment source and gas phase as outlined here.
-However, the detailed properties of the PDFs (e.g, log-normal width, power-law slope) likely depend non-trivially on global galaxy properties.
-How these results vary as a function of galaxy properties will be investigated in future work.
-
-\subsection{Implications for Exotic Enrichment Sources}
-\label{sec:exotic enrichment}
-%   AE: Benoit suggested removing arguments relating to NS-NS merger energetics as I had misred / miscaclulated the energy release values.
-He said greater emphasise on potential differences of mixing due to rarity, rather than energy.
-We have shown that the dynamical evolution of metals depends upon their nucleosynthetic source, focusing here on AGB synthesized elements and SN synthesized elements.
-However, these differences should also apply to exotic enrichment sources, such as hypernovae, neutron-star neutron-star mergers, and neutron-star black-hole mergers.
-These sources can have energies that differ significantly from typical SNe, reaching $> 10^{52}$~erg for hypernovae \citep{Nomoto2004}, for example.
-In addition,
-%mm the rarity of these events, for example,  there are approximately $10^{-5}$ per M$_{\odot}$ of star formation NSM in the Milky Way, could
-     these events are rare.  For example, neutron star mergers occur 
-     at a rate of approximately $10^{-5}$ per M$_{\odot}^{-1}$ of star
-     formation in the Milky Way\citep{Kim2015}.  This rarity could 
-significantly influence the typical ISM environments into which they eject their metals.
-We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to SNe.
-Based on our results here, for example, we would expect elements from hypernovae to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe.
-% Benoit suggesed removing this given energy argument removal above
-%    Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies. 
-Depending on their injection energy, neutron star mergers could exhibit different mixing behaviors in the ISM.
-These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
-In particular, low mass dwarf galaxies with unusual r-process enrichment \citep[e.g.][]{Ji2016}, are valuable for constraining the source of these elements, their frequency, and typical yields.
-The differential metal evolution presented in our work both opens up an additional avenue by which elements from distinct nucleosynthetic sources may be distinguished in observations and challenges current assumptions used in interpreting these observations.
-
-\section{Conclusions}
-\label{sec:conclusions}
-We present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
-This high resolution simulation, coupled with our star-by-star modeling of stellar nucleosynthetic yields, has allowed us to analyze for the first time how individual metal species couple to the ISM and galactic wind of this galaxy.
-
-We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, or core collapse SNe).
-This difference is most significant, in our model, between elements ejected predominately by AGB winds and those ejected predominantly by core-collapse SNe.
-In addition, we find the novel result that the mass fraction PDFs of each metal in the ISM can be described using an analytic piecewise log-normal + power-law PDF.
-The properties of these PDFs vary with both ISM phase and metal species, again driven mostly by differences in enrichment sources.
-
-We summarize our results as follows:
-\begin{itemize}
-
-%\item Elements from lower energy enrichment sources (i.e.
-AGB winds) are preferentially retained in the ISM of low mass dwarf galaxies as compared to those from higher energy sources (SNe), which are more readily launched in galactic winds.
-This result is likely sensitive to global galaxy properties, becoming less significant with increasing halo mass.
-We predict the abundance ratios between AGB wind dominated metals (s-process elements) and SN dominated metals ($\alpha$ elements) to be higher at fixed metallicity in low mass dwarf galaxies than in more massive galaxies, like the Milky Way.
-
-\item Power-law tails on log-normal metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
-
-\item Hotter phases have metal fraction PDFs that are more enriched, with significant power-law tails as compared to cold phases, which have a more prominent log-normal component.
-The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling and/or mixing into denser gas.
-
-\item Metal outflow in low mass dwarf galaxies depends upon nucleosynthetic site.
-Metals from lower energy enrichment events (e.g.
-AGB winds) are preferentially retained in the ISM as compared to those from higher energy events (e.g.
-SNe).
-The degree to which this is true likely depends upon global galaxy properties such as star formation rate, dark matter potential well, and gas geometry.
-
-\item Likewise, metals originating in AGB winds are less well mixed in the ISM, with spreads of over 1 dex in cold gas, as compared to metals injected through SNe, with spreads of about 0.5~dex
-
-\item Metal distributions exhibit positive skew, such that the mean metal fraction can be anywhere from 0.1 to 1.0 dex above the median metal fraction.
-Simple chemical evolution models, which generally follow the mean abundance, and thus can not account for complex metal mixing physics, are likely biased towards higher enrichment values.
-
-\end{itemize}
-
-%mm [you argued above that the wind results would NOT necessarily be general.
-I'm not sure I like the formulation about entrainment of the ambient ISM, though.] We expect these results to be general for more massive galaxies and galaxy properties.
-However, it may be the case that metals couple more uniformly to galactic winds in more massive galaxies as wind driving occurs increasingly through entrainment of the ambient ISM rather than the ejection of individual enrichment events.
-This warrants further examination.
-But interpreting these results for low mass dwarf galaxies
-    Extending these results to low-mass dwarf galaxies in general, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements released through SNe and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
-% Removed as-per Benoit's suggestion:
-% , and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements
-
-\acknowledgments
+\section*{Acknowledgments:} 
+We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
+C\^ot\'e, S.
+Glover, K.
+Hawkins, C.
+Hu, K.
+Johnston, B.
+O'Shea, M.
+Putman, B.
+Smith, J.
+Wall, and J.
+Wise.
+We would additionally like to thank the referee for their careful report.
 A.E.
@@
 was partly funded by NASA  grant NNX14AP27G.
-B.C.
-acknowledges support from the ERC Consolidator Grant (Hungary) funding scheme (project RADIOSTAR, G.A.
-n.
-724560) and from the National Science Foundation (USA) under grant No.
-PHY-1430152 (JINA Center for the Evolution of the Elements).
-B.W.O was supported in part by NSF grants PHY-1430152 and AST-1514700, by NASA grants NNX12AC98G, and NNX15AP39G, and by Hubble Theory Grant HST-AR-14315.001-A.
 We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute.
@@
 
-\facilities{XSEDE (Stampede, Stampede-2), ADS} % there is no ApJ kewword for this: NASA HECC (Pleiades)}
-\software{Numpy, Enzo, yt, astropy}
-
-\bibliographystyle{yahapj}
+%\bibliographystyle{yahapj}
+\bibliographystyle{mnras}
 \bibliography{msbib}
@@
 
-\section{Density PDF}
-\label{appendix:density PDF}
-We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}.
-We show the mass-weighted PDF ($dm/Mdn$) on the left, and the volume-weighted PDF ($dv/Vdn$) on the right.
-As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution.
-The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.
-The volume weighted PDF is much better described as a multi-component power law.
-The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities.
-These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.
+\section{Gas Phases of the ISM}
+\label{appendix:phases}
 
-%mm [you could cut this if you want.]
-%It is worth noting that this PDF shows the rather small cold gas 
-%     fraction found in these models in comparison to the Milky Way
-%      ISM, where roughly half the mass is found in cold gas 
-%      \citep{Ferriere2001}.
-Finally, \cite{Hopkins2013} suggests a different functional form for describing these PDFs across a range of idealized simulations, but it still may be insufficient to fully describe the density PDF in realistic galaxy simulations.
-Clearly, we are far from a general understanding of mass-weighted and volume-weighted density PDFs in the case of a turbulent, self-gravitating, multi-phase ISM.
+To aid in comparison to other works, we define our ISM phases here, as adopted and modified from \citet{Draine2011}, Table 1.3, and used consistently throughout this analysis.
+By construction, these phases are mutually exclusive.
+We take $f_{\rm H_2}$ to be the molecular hydrogen fraction of the total gas mass.
 
-\begin{figure}
-\centering
-\includegraphics[width=0.475\linewidth]{density_PDF.png}
-\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted.png}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr.
-The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
-\label{fig:density_pdf}
-\end{figure}
+\begin{enumerate}
+\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
+\item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
+\item Warm Neutral Medium (WNM): $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$
+\item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
+\item Molecular: $T < 10^2$~K, $f_{\rm H_2} > 0.5$
+\end{enumerate}
 
-\section{Resolution Comparison}
-We perform a resolution test to confirm that the key results of this study are convergent, at least qualitatively.
-Given the variations in star formation rate, feedback effectiveness, and stochasticity in our model, we do not expect exact numerical convergence in any one quantity.
-We conduct two lower resolution simulations with a maximum physical resolution of 3.6 pc and 7.2 pc.
-We refer the reader to Paper I for a previous comparison of these simulations to our fiducial run.
-In Figure~\ref{fig:resolution-phase} we demonstrate that O and Ba abundances behave qualitatively similar in our lower resolution runs as in our fiducial model.
-In both lower resolution runs O has a generally tighter distribution that narrows over time, while Ba is much less well mixed, in agreement with our fiducial simulation.
-The exact numerical values for these spreads are not convergent across simulations, but we do note significant variations in the exact SFH of these lower resolution runs could be driving these differences.
+\section{Stellar Radiation Properties}
+\label{appendix:radiation}
+We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
+In Figure~\ref{fig:stellar radiation properties} we plot these properties.
+We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
+This requires two factors for each radiation type, one for low mass and one for high mass stars.
+We use the following multiplicative factors to adjust the black body spectrum for HI and HeI ionizing radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
+We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
+
+The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid.
+A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section.
+We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \url{http://www.pa.uky.edu/~verner/photo.html}}
+The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision.
+Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.
 
@@
 \centering
-\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study.png}
-\caption{Resolution comparison of two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.
-Compare to Figure~\ref{fig:phase-statistics}.}
-\label{fig:resolution-phase}
+\includegraphics[width=0.4\linewidth]{Q0}
+\includegraphics[width=0.4\linewidth]{Q1}
+\vspace{0.01cm}
+\includegraphics[width=0.4\linewidth]{L_FUV}
+\includegraphics[width=0.4\linewidth]{L_LW}
+\vspace{0.01cm}
+\includegraphics[width=0.4\linewidth]{E0}
+\includegraphics[width=0.4\linewidth]{E1}
+\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right).
+Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
+\label{fig:stellar radiation properties}
 \end{figure*}
 
+\setcounter{figure}{0}
+\section{Typical Gas Densities in Supernova Injection Regions}
+\label{appendix:SN}
+
+Modeling SN feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of SN feedback.
+Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time.
+However, physically consistent solutions have been developed \citep[e.g][]{Simpson2016} that inject a mixture of kinetic and thermal energy with a ratio that depends on resolution and local gas density.
+Overcooling becomes less important with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each SN.
+We take advantage of our high resolution and employ a simple thermal energy injection model for our SN feedback.
+We demonstrate how well this resolves our SNe in the comparison simulation presented in this work.
+
+The left panel of Figure~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
+As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
+For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations.
+The right panel of Figure ~\ref{fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
+\begin{equation}
+R_{\rm PDS} = 
+\begin{cases}
+49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z \le 0.01 \\
+18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z \ge 0.01 \\
+\end{cases}
+\end{equation}
+where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$.
+\citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the SN explosion with thermal energy injection alone, assuming uniform density in the injection region.
+In practice, the injection region is never uniform.
+We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each SN.
+As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but up to 8.3\% are not well resolved and 2.0\% are completely unresolved (below a single cell width).
+In general, these are SN explosions from the most massive (i.e.
+most prompt) stars.
+We do not expect that resolving these SNe will dramatically alter our results.
+However, we note that using our feedback model at resolutions much less than a few parsecs will require implementing an different injection mechanism.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.4\linewidth]{sn_density_hist}
+\includegraphics[width=0.4\linewidth]{sn_radius_hist}
+\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation.
+{\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each SN assuming a uniform medium at either the peak or average density in the injection region.
+The vertical lines show one and 4.5 cell widths.
+This shows that a fraction of these SNe are certainly unresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
+\label{fig:SN histogram}
+\end{figure*}
+
+\setcounter{figure}{0}
+\section{Cooling and Heating Rates}
+\label{appendix:cooling}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
+\caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background.
+Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the uncorrected (i.e.
+optically thin) metal line cooling rates.
+The regimes where heating dominates are plotted with dashed lines for clarity.}
+\label{fig:cooling comparison}
+\end{figure*}
+
+The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with a self-shielding approximations.
+\citet{Hu2017} details this inconsistency: metal cooling rates computed under the assumption of an optically thin UV background overestimate the electron fraction in regimes where self-shielding is important ($-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$).
+This results in an artificially enhanced metal line cooling rate in regions of self-shielding.
+This can be a significant effect, particularly at higher metallicities.
+We demonstrate this in Figure~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
+The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
+In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
+Figure~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
+We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
+
+For densities where self-shielding is important, we computed \textsc{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
+In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud.
+We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UV background.
+These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}.
+In computing these tables we had to include the cosmic ray ionization that dominates in optically thick clouds.
+Without this effect, \textsc{Cloudy} becomes unstable in entirely neutral regions.
+We adopted a cosmic ray ionization rate of 10\% the Milky Way value, though we note that varying this from 1\% to 100\% the Milky Way value did not have an effect on the extracted metal line cooling rates.
+
+Finally, we note that the cooling and heating rates in our simulation will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
+The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which is not included in these diagrams.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.95\linewidth]{cooling_curve}
+\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}.
+The absolute value of the net cooling or heating
+rate is shown with solid lines.}
+\label{fig:cooling}
+\end{figure*}
+
+\seccounter{figure}{0}
+\section{H$^{-}$ Photodetachment}
+\label{appendix:H minus}
+\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations.
+Accounting for the photodetachment of H$_{-}$ from the stellar radiation field, which can dominate over the UVB, is potentially important for correctly modeling H$_2$ formation in low metallicity gas\citep{WolcottHaiman2012}.
+In addition, radiation from lower mass stars may be important in the is regime as the H$^{-}$ photodetachment threshold is low, or 0.76~eV.
+}
+
+\setcounter{figure}{0}
+\section{Resolution Study}
+\label{appendix:resolution_study}
+
+We demonstrate the effect of varying resolution in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}.
+We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines).
+The physics in each simulation remains the same with the exception of star formation, which employs a resolution-dependent density threshold.
+A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.
+As a result, the time at which star formation first occurs varies between the simulations, but we again define t = 0 as the time of first star formation in each simulation.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.33\linewidth]{sfr_resolution_study.png}
+\includegraphics[width=0.33\linewidth]{mass_evolution_resolution.png}
+\includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
+\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted).
+The line colors in the left panel are for better clarity between the SFRs.}
+\label{fig:resolution_study}
+\end{figure*}
+
+Figure~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
+We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
+The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs.
+We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Figure~\ref{fig:SN histogram}.
+However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
+
+Generally ineffective feedback leads to increased, not decreased, star formation rates.
+However, the lower resolution run has the lowest SFR.
+The source of this difference is likely related to the ability to resolve dense, cold gas in the lower resolution simulations.
+In particular, the low resolution simulation clearly is unable to resolve the densities at which gas-phase H$_2$ formation becomes efficient, leading to significantly lower H$_2$ fractions (middle panel) and lower cooling rates.
+In addition, whatever H$_2$ does form at these lower resolutions exists at lower gas densities than in our fiducial run, and is less well protected by self-shielding effects.
+This is shown clearly in the significant plummet in the H$_2$ mass during the phase of first star formation that is less severe in our fiducial run.
+In this low metallicity regime, where H$_2$ is an important coolant, the ability to resolve the densities responsible for H$_2$ formation and self-shielding is important.
+
+Theses differences in densities are shown clearly by comparing Figure~\ref{fig:phase} with Figure~\ref{fig:phase_resolution}.
+Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.
+In the 7.2~pc run, the gas phases are notably less distinct, with gas more evenly smoothed out in the multi-phase region between cold, dense gas and warm, ionized gas.
+We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature ceiling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.475\linewidth]{3pc_phase.png}
+\includegraphics[width=0.475\linewidth]{6pc_phase.png}
+\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Figure~\ref{fig:phase}.}
+\label{fig:phase_resolution}
+\end{figure*}
+
+Finally, the metal retention fraction (right panel) between the fiducial and 3.6~pc runs are quite similar, but is significantly higher for the lowest resolution simulation.
+It is likely, however, that this is a result of the lower SFR in the 7.2~pc run and is not directly a resolution effect.
+This also affects the fraction of metals ejected outside the virial radius, with less metals being ejected in the lower resolution runs.
+
+\label{lastpage}
+
 \end{document}

### 2018-08-20 main.tex
bugfix
Adding text about G_o UVB value for Figure 7. changing Figure to Fig. (and Figures to Figs.)

@@
 
-We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
+We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}.
 These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
@@
 For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
-In the final column of Figure~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
+In the final column of Fig.~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
 With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
@@
 \includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
-\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on views.}
+\caption{Same as Fig.~\ref{fig:panel_x}, but showing face-on views.}
 \label{fig:panel_z}
@@
 \includegraphics[width=0.975\linewidth]{scale_height}
-\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figures~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
+\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
 \label{fig:scale_height}
@@
 
-We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
+We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Fig.~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
 The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$.
@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
+By the time of first star formation ($t=0$ in Fig.~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
 The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
@@
 
-Figure~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
-One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}).
+Fig.~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
+One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Fig.~\ref{fig:ISM_evolution}).
 Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
@@
 
-The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Figure~\ref{fig:ISM_evolution}.
+The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Fig.~\ref{fig:ISM_evolution}.
 The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
@@
 However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
-Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.
+Together, these figures better quantify the general properties observed in the panel plots in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}.
 
@@
 This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
-In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
+In Fig.~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
 The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
-The contribution from the metagalactic background falls below the lower vertical axis limit on this plot.
 The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
@@
 For this reason we only shade between the first quartile and maximum values.
-HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.}
+HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.
+In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
 \label{fig:ISRF}
@@
 Here, we include all gas within the mid-plane of our dwarf galaxy.
-Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
+Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
 This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
@@
 
-To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr.
+To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Fig.~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr.
 This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
@@
 However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
-In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
+In Fig.~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
 We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
@@
 
-The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}.
+The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Fig.~\ref{fig:mass_outflow}.
 Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
@@
 Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
-In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
+In Fig.~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
 Gas with a negative velocity is moving towards the center of the halo.
@@
 \caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-This is averaged over the same time interval as Figure~\ref{fig:ISRF}.
+This is averaged over the same time interval as Fig.~\ref{fig:ISRF}.
 The outflowing material is multiphase, broken into WNM, WIM, and HIM.
@@
 where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-These metal loading factors fluctuate significantly with the SFR, just as was shown in Figure~\ref{fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
+These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
 On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5).
@@
 \includegraphics[width=0.9\linewidth]{metal_retention}
-\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Figure~\ref{fig:mass_outflow}.
+\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:mass_outflow}.
 This is the ratio between the metal outflow rate and the metal production rate.
@@
 Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
-Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
+Given the variations in Fig.~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
 The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
@@
 \item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
-(See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).
+(See Figs.~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).
 
@@
 metal mass loading factors near unity.
-By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Figure~\ref{fig:outflow_velocity}).
+By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Fig.~\ref{fig:outflow_velocity}).
 
@@
 By the end of the simulation $\sim$45\% of the remaining metals stay within the virial radius (but outside the galaxy), while $\sim$50\%
-have been ejected beyond the virial radius. (See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
+have been ejected beyond the virial radius. (See Figs.~\ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
 
@@
 This is comparable to the resolution limit of the diffuse HI in observed, gaseous low-mass dwarfs.
-At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Figure~\ref{fig:scale_height}).
+At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Fig.~\ref{fig:scale_height}).
 
@@
 The importance of radiation feedback in our model will be investigated in a future work.
-(See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
+(See Figs.~\ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
 
@@
 Cold, neutral hydrogen dominates the mass of our galaxy.
-While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Figure~\ref{fig:sfr_mass_evolution} and Figure~\ref{fig:ISM_evolution}.)
+While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Fig.~\ref{fig:sfr_mass_evolution} and Fig.~\ref{fig:ISM_evolution}.)
 
@@
 We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Figure~\ref{fig:stellar radiation properties} we plot these properties.
+In Fig.~\ref{fig:stellar radiation properties} we plot these properties.
 We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
@@
 
-The left panel of Figure~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
+The left panel of Fig.~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
 As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
@@
 This can be a significant effect, particularly at higher metallicities.
-We demonstrate this in Figure~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
+We demonstrate this in Fig.~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
 The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
 In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
-Figure~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
+Fig.~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
 We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
@@
 
-\seccounter{figure}{0}
+\setcounter{figure}{0}
 \section{H$^{-}$ Photodetachment}
@@
 
-We demonstrate the effect of varying resolution in the evolution of our galaxy model in Figure~\ref{fig:resolution_study}.
+We demonstrate the effect of varying resolution in the evolution of our galaxy model in Fig.~\ref{fig:resolution_study}.
 We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines).
@@
 
-Figure~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
+Fig.~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
 We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
 The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs.
-We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Figure~\ref{fig:SN histogram}.
+We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Fig.~\ref{fig:SN histogram}.
 However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
@@
 
-Theses differences in densities are shown clearly by comparing Figure~\ref{fig:phase} with Figure~\ref{fig:phase_resolution}.
+Theses differences in densities are shown clearly by comparing Fig.~\ref{fig:phase} with Fig.~\ref{fig:phase_resolution}.
 Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.
@@
 \includegraphics[width=0.475\linewidth]{6pc_phase.png}
-\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Figure~\ref{fig:phase}.}
+\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:phase}.}
 \label{fig:phase_resolution}

### 2018-08-20 main.tex
mostly done with updates.. a little more

@@
 \textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations.
-Accounting for the photodetachment of H$_{-}$ from the stellar radiation field, which can dominate over the UVB, is potentially important for correctly modeling H$_2$ formation in low metallicity gas\citep{WolcottHaiman2012}.
-In addition, radiation from lower mass stars may be important in the is regime as the H$^{-}$ photodetachment threshold is low, or 0.76~eV.
-}
+Accounting for the photodetachment of H$_{-}$ from the stellar radiation field, which can dominate over the UVB,can be important for correctly modeling H$_2$ formation in low metallicity gas\citep{WolcottHaiman2012}.
+To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models\footnote{See the ``cooling_cell.py'' example here: https://grackle.readthedocs.io/en/grackle-3.1/Python.html} that iterates through the chemistry and cooling solvers with a constant density (10~cm$^{-3}$).
+In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background.
+As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate.
+In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left).
+A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.}
+
+\textbf{We follow up on the qualitative conclusions of these models by running four full-physics simulations, but with no star formation, at the four points starred in the diagram.
+These vary the radiation bands by factors of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}).
+Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9.
+Applying both scale factors gives a reduction of 7.9.}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{fH2.png}
+\caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation.
+Each model is held at a uniform density $n = 10$~cm$^{-3}$.
+Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor.
+Contours give factors of ten change in the H$_2$ fraction.}
+\label{fig:Grackle grid}
+\end{figure}
+
+\textbf{H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV.
+For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction.
+Although we demonstrate that the H$_2$ fraction is more sensitive to the Lyman-Werner radiation field in our simulations, this radiation is dominated by short-lived massive stars and thus subject to fluctuations.
+Particularly in periods of no star formation, the regulation of H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation.
+Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars.
+Doing so in our current model, applying an optically thin 1/r$^2$ field for each star, would be computationally challenging for the dramatic increase in the number of stars below 8~M$_{\odot}$, our current radiation mass threshold.}
+
+In addition, radiation from lower mass stars may be important in the is regime as the H$^{-}$ photodetachment threshold is low, or 0.76~eV. }
 

### 2018-08-20 main.tex
final draft updates for referee report 2

@@
 Thus the presence of some ionizing background is required to generate the molecular fractions we find in our simulations, as confirmed in separate test simulations.
-\textbf{Our model does include a contribution from the meta-galactic background to the photodetachment of H$^{-}$.
-However, we note that we do not account for the contribution to this rate from the ISRF.
-We find that the H$_2$ fraction is more strongly dependent upon the Lyman-Werner radiation field, which is followed for each star, than the H$^{-}$ photodetachment rate.
-Our tests suggest that ignoring the stellar contribution to H$^{-}$ may lead to a 10--20\% overestimate in the computed H$_2$ fractions.
-This is discussed in more detail in Appendix~\ref{appendix:H minus}}.
 
@@
 Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
-It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
-This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
+
+\textbf{In addition, our model does not account for the stellar component of the radiation field that leads to H$^{-}$ photodetachment (E$_\gamma > 0.76$~eV), though we do account for the contribution from the UVB.
+We find that the H$_2$ fraction is more strongly dependent upon the Lyman-Werner radiation field, which is followed for each star, than the H$^{-}$ photodetachment rate.
+Our tests suggest that, by ignoring the stellar contribution to H$^{-}$ photodetachment, our results may represent upper limits on the H$_2$ mass.
+However, including this component will likely only make a substantial difference during periods of no star formation, when there are no massive stars with significant Lyman-Werner luminosities.
+We do not anticipate this to have a significant dynamical impact on our simulations, as is discussed in more detail in Appendix~\ref{appendix:H minus}}.
+
+It is unclear how the combination of all of the above effects will behave, especially considering that, even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
+These uncertainties certainly warrant further study of molecular gas in low metallicity dwarf galaxies.
 
@@
 \label{appendix:H minus}
+%\textbf{This section is new:}
+
 \textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations.
-Accounting for the photodetachment of H$_{-}$ from the stellar radiation field, which can dominate over the UVB,can be important for correctly modeling H$_2$ formation in low metallicity gas\citep{WolcottHaiman2012}.
-To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models\footnote{See the ``cooling_cell.py'' example here: https://grackle.readthedocs.io/en/grackle-3.1/Python.html} that iterates through the chemistry and cooling solvers with a constant density (10~cm$^{-3}$).
+Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, ca be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}.
+To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https:\/\/grackle.readthedocs.io\/en\/grackle-3.1\/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) for 200~Myr.
 In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background.
@@
 Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor.
-Contours give factors of ten change in the H$_2$ fraction.}
+Contours give factors of ten change in the H$_2$ fraction.
+We note the regime below 1.0 on each axis is somewhat unphysical, and is never reached in our hydrodynamics simulations.}
 \label{fig:Grackle grid}
@@
 Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars.
-Doing so in our current model, applying an optically thin 1/r$^2$ field for each star, would be computationally challenging for the dramatic increase in the number of stars below 8~M$_{\odot}$, our current radiation mass threshold.}
-
-In addition, radiation from lower mass stars may be important in the is regime as the H$^{-}$ photodetachment threshold is low, or 0.76~eV. }
+Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked.
+}
 

### 2018-08-20 main.tex
just fixed a few typos

@@
 
-\textbf{In addition, our model does not account for the stellar component of the radiation field that leads to H$^{-}$ photodetachment (E$_\gamma > 0.76$~eV), though we do account for the contribution from the UVB.
+\textbf{In addition, our model does not account for the stellar component of the radiation field that leads to H$^{-}$ photodetachment ($E_\gamma > 0.76$~eV), though we do account for the contribution from the UVB.
 We find that the H$_2$ fraction is more strongly dependent upon the Lyman-Werner radiation field, which is followed for each star, than the H$^{-}$ photodetachment rate.
@@
 \textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations.
-Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, ca be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}.
+Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB,
+%mm ca 
+    can 
+be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}.
 To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https:\/\/grackle.readthedocs.io\/en\/grackle-3.1\/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) for 200~Myr.

### 2018-08-21 main.tex
added a grant number to the acknowledgments

--- 2018-08-20 main.tex
@@
-\documentclass[fleqn,usenatbib,useAMS]{mnras}
-\pdfoutput=1 
-\usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{multicol}        % Multi-column entries in tables
-\usepackage{bm}		% Bold maths symbols, including upright Greek
-%\usepackage{pdflscape}	% Landscape pages
-
+%mm substantive changes marked like this, others made silently
+
+\documentclass[twocolumn]{aastex61}
+\pdfoutput=1 %for arXiv submission
+\usepackage{amsmath,amstext}
 \usepackage[T1]{fontenc}
-\usepackage{ae,aecompl}
-\usepackage{newtxtext,newtxmath}
-
-%\usepackage{amsmath,amstext}
-%\usepackage[T1]{fontenc}
+\usepackage{apjfonts}
 \usepackage[figure,figure*]{hypcap}
 
-%\hypersetup{draft}
-%\usepackage{multirow}
-%\usepackage{mathtools}
-%\renewcommand*{\sectionautorefname}{Section} %for \autoref
-%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
-%\usepackage{graphicx}
-%\usepackage{natbib} % bibliography
-
-%\usepackage[active,floats,tightpage]{preview}
-%    \setlength\PreviewBorder{1em}
-
-\newcommand{\msun}{M$_{\odot}$}
-\newcommand{\ccunit}{cm$^{-3}$}
-
-\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars}
-
-\author[A. Emerick et. al.]{
-Andrew Emerick,$^{1,2}$
-Greg L. Bryan,$^{1,3}$
-and Mordecai-Mark Mac Low$^{2,1}$
-\\
-$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
-$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
-$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+\renewcommand*{\sectionautorefname}{Section} %for \autoref
+\renewcommand*{\subsectionautorefname}{Section} %for \autoref
+
+\shorttitle{Differential Metal Mixing}
 
@@
 
-\label{firstpage}
-%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
-
-%\author{Andrew Emerick}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\author{Greg L. Bryan}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-%\author{Mordecai-Mark Mac Low}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-
-%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}
+%\title{Evolution of Individual Metals in Galactic Winds and the ISM}
+
+% GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
+% AE: Had a hard time coming up with a succinct and interesting sounding title that
+%     fit both of the interesting results:
+%          1) analytic PDF fits and 2) variations in metal mixing...
+\title{Metal Mixing
+%mm
+    and Ejection
+in Dwarf Galaxies is Dependent on Nucleosynthetic Source}
+
+%Non-Uniform Metal Distributions in a Dwarf Galaxy Simulation}
+%Variations in the Distribution and Evolution of Individual Metals in Dwarf Galaxies}
+
+\author{Andrew Emerick}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+\author{Greg L. Bryan}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+\author{Mordecai-Mark Mac Low}
+\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+\author{Benoit C{\^o}t{\'e}}
+\affiliation{Konkoly Observatory, Research Centre for Astronomy and Earth Sciences, Hungarian Academy of Sciences, Konkoly Thege Miklos ut 15-17, H-1121 Budapest, Hungary}
+\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI 48824, USA}
+\affiliation{Joint Institute for Nuclear Astrophysics - Center for the Evolution of the Elements, USA}
+\author{Kathryn V. Johnston}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\author{Brian O'Shea}
+\affiliation{T.B.D.}
 
 \begin{abstract}
-In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
-We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
-We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints.
-We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group, low-mass dwarf galaxy.
-We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
-Effective feedback drives outflows with a greater metallicity than the ISM, leading to low metal retention fractions consistent with observations.
-Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
+Using a high resolution simulation of an isolated dwarf galaxy, accounting for multi-channel
+stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy by galactic winds.
+For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal and power-law distribution.
+The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail.
+The PDF properties, and relative significance of these two components, vary within each ISM phase.
+Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component.
+In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment, such as N and Ba, mix less efficiently than elements dominated by supernova enrichment, such as $\alpha$ elements and Fe.
+This difference is driven by the differences in
+%mm energetics between each source, particularly the poor coupling of AGB winds to the ISM.
+    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
+Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%.
+In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread compared to elements synthesized in either core collapse or Type Ia supernovae.
+We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
 \end{abstract}
 
-\begin{keywords}
-Galaxy -- Hydrodynamics -- Simulation -- Feedback
-\end{keywords}
+\keywords{}
 
 \section{Introduction}
-%
-% AE removed below.. MM suggested  skipping both pars.
-%
-%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade.
-Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc.
-\citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses.
-On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM.
-This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}.
-See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.
-%
-%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution.
-In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense.
-In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships.
-For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.
-
-Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution.
-Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
-There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
-% editor asked us to reduce citation count here:{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
-These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
-
-However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}.
-In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
-Mixing can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
-While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficiently high spatial resolution.
-Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
-Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b, KrumholzTing2018}.
-Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
-the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
-The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
-
-Increasing physical resolution reduces reliance on sub-grid physics for mixing.
-However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}.
-Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
-This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
-At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.
-Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
-The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
-
-We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies.
-The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms.
-We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
-%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies.
-\citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
-Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar winds from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
-We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar far ultra-violet (FUV) radiation, and Lyman-Werner dissociation from stellar radiation.
-
-Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime.
-This includes yields from massive and AGB stellar winds, and supernovae (SNe).
-In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
-This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
-This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
-We describe each mode of our multi-channel feedback
-in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.
-
-Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.
-
+Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution.
+One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites from stellar winds or supernovae (SNe) and mix through the phases of the interstellar medium (ISM) into star-forming gas.
+%
+% get a sentence with a better punch at the end
+%
+
+One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}.
+While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challenging.
+More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects.
+How to properly account for multi-phase mixing, however, is still poorly understood.
+This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
+%Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows. 
+Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018}
+% KVJ: citations to high-redshift work in this area
+\textbf{and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.} Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.
+
+In addition, it remains to be seen to what degree, if at all, metals of different enrichment origins (AGB winds, core collapse SNe, Type Ia SNe, neutron-star neutron-star mergers, etc.) may couple differently to the ISM.
+When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly.
+However, if metals do not behave uniformly in the ISM, if their mixing and ejection behavior depends directly upon the energetics and physical environment of their injection, then this assumption would need to be re-evaluated.
+Differences in metal distributions from ejecta in AGB stars, as compared to SNe, has been explored recently in \cite{KrumholzTing2018}, but has yet to be demonstrated in hydrodynamics simulations.
+
+The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
+That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004,Muratov2017,Corlies2018}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+If there are differences in metal coupling to the ISM, this could potentially impact how metals are driven out of galaxies through galactic winds.
+This has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
+However, examining this process has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
+%It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
+% Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
+However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
+
+It is becoming increasingly valuable to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}.
+Stellar abundances are directly imprinted with the enrichment pattern of their star-forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
+The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM.
+Furthermore, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.
+% KVJ asked to bring up this area of research and emphasize how it is lacking theoretical input
+\textbf{One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Ting2012, Hogg2016,Jofre2017,Price-Jones2018}.
+Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations.
+Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.}
+
+In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}.
+The simulation discussed here was introduced in detail in \cite{Emerick2018} (hereafter Paper I).
+To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia SNe.
+This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below.
+We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species.
+We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.
+
+The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity.
+Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging.
+[list examples of modelling problems].
+These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study.
+By focusing on a low mass dwarf galaxy, with small size and low star formation rate, we can capture detailed feedback and ISM physics at high resolution, while following individual stars.
+In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios, for two reasons.
+First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
+Second, there is only a severly limited sample of gas-rich dwarf galaxies of this size that we can use for direct observational comparison, and it is computationally infeasible to simulate galaxies of easily observable size in as much detail as done here.
+This work will be the first of several attempting to bridge this gap.
+With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and physically motivated sub-grid physics models for lower resolution simulations of more massive galaxies.
+
+We summarize our methods and physics models in Section~\ref{sec:methods}.
+We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}.
+In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
+We discuss our results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusions}.
+
+% AE: Benoit suggested subsections instead of paragraph splits... play with this to see what looks best
 \section{Methods}
 \label{sec:methods}
-We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
-This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
-To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background.
-We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}).
-We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
-Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
-We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on HI.
-In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
-We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both.
-We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors.
-We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species.
-In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked.
-This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth.
-These methods are discussed in full detail below.
-
-\subsection{Hydrodynamics and Gravity}
-\label{sec:hydro}
-
-We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies.
-\texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions.
-We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick.
-Specifically, simulations presented here were conducted at changeset 7001d99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
-We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}).
-Self-gravity is computed with a multigrid Poisson solver.
-The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.
-
-We refine the mesh whenever the thermal Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
-At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation.
-\citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.
-
-We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}).
-Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
-However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse.
-A non-thermal pressure term is added to cells once their thermal Jeans length becomes unresolved.
-This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
-The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.
-
-Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas.
-These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution.
-At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr.
-We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$.
-These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions.
-This threshold decreases the required run-time by factors of a few.
-The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)
-
-\subsection{Chemistry and Cooling Physics}
-\label{sec:chemistry}
-
-We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset c2c0faf.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes.
-We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.
-We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
-However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}.
-For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
-
-As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
-As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
-Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}.
-To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.
-We have made these new tables public in the main \texttt{Grackle} repository.
-These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
-Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.
-
-\subsection{Star Formation Algorithm}
-\label{sec:star formation}
-In order to resolve individual star formation events on galactic scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
-Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local thermal Jeans mass.
-Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K.
-We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$.
-No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.
-
-We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
-At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2018, FIRE2}, as star formation is ultimately self-regulated by feedback.
-
-The stellar mass formed during a timestep $\Delta t$ from a region with a total gas mass $M_{\rm gas}$ is
+We refer the reader to Paper I for a detailed description of our numerical methods and feedback models. We briefly summarize the relevant details here.
+
+\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{http://enzo-project.org/} \citep{Enzo2014}.
+Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
+We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver.
+We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
+Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas or 2) a cell's local Jeans length becomes resolved by less than eight cells.
+Also, if the cell is within four zones of a star particle with active feedback, it is refined to the maximum resolution.
+At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.
+
+\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (H, H$^+$, He, He$^+$, He$^P{++}$, H$^-$, H$_2$, H$_2^+$, and e$^-$), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
+We account for approximate self-shielding of H~{\sc i} against the UV background following \cite{Rahmati2013}.
+We assume He~{\sc i} self-shields in the same fashion as H~{\sc i}, and ignore He~{sc ii} heating from the UVB entirely.
+Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}.
+Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.
+
+% AE: From Benoit, maybe make a note of 1 - 100 M_sun sampling may slightly overestimate higher mass stars (people usually do 0.1 to 100 M_sun
+\paragraph{Star Formation} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
+Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$.
+Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$).
+We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\%.
+Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment.
+We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
+
+\paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually.
+Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse SNe at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
+Stars above this mass are assumed to direct collapse with no mass or energy injection.
+For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their H~{\sc i} and He~{\sc i} ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
+We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars.
+Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind \citep{Goldman2017}.
+Stars with $3 < M_{*} < 8$ are tracked after their death as possible Type Ia SN progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
+Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et.
+al.
+in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia SNe.
+
+\paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
+We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$.
+The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
+Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium.
+The galaxy contains no initial background stellar population, limiting the number of Typa Ia SNe in our model, but we do provide initial SN driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy.
+Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
+Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.
+
+\section{Results}
+For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
+This galaxy has an average star formation rate of $1.2~\times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
+The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy.
+The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$.
+These winds eject 95\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.
+
+In this work we focus in detail on how each of the 15 individual metal species evolve in this galaxy.
+We address differences between the ejection fractions of each metal in Section~\ref{sec:ejection} and analyze for the first time the mass-fraction PDFs of the metals retained by the ISM in Section~\ref{sec:mixing}.
+
+\subsection{Preferential Ejection of Metals from the ISM}
+\label{sec:ejection}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.99\linewidth]{species_bar.png}\\
+\includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
+\caption{The fraction of each metal species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).
+The leftmost bar in each plot shows the sum of all metals.}
+\label{fig:species_fractions}
+\end{figure}
+
+%mm [this all seems to have been deleted in one version, but doesn't look like it should have been.  Down to ">>>>"] <<<<<<< HEAD
+The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
+We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
+%mm Again, with the exception of  H and He, we [H & He aren't metals]
+    We
+only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+
+We find two major results.
+%mm [reversed order of results to follow figure.  The opposite choice could also be made, by reversing the order of the figure...]
+    First, 
+only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies
+%mm 
+    among elements.
+The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
+This suggests that individual metals \textit{do not} share the same dynamical evolution.
+%mm Clearly
+       Thus, 
+metal enrichment in galaxies is a phenomenon that cannot be fully captured using a single, global metallicity field.
+In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
+
+    Second,
+nearly all of the metals 
+%mm
+    retained in the disk
+reside within neutral gas, mostly in the CNM; only a few percent
+reside in the hot phases.
+The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
+This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
+
+The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
+We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
+Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+
+We find two major results.
+First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases.
+The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
+This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
+Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies.
+The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
+This suggests that individual metals \textit{do not} share the same dynamical evolution.
+Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field.
+In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
+%mm [end of apparently deleted section] >>>>>>> 134a2fabac2aea2275cb3e8014308282b438742f
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{species_bar_sources.png}\\
+\caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
+These channels differ in both when metals are ejected, as determined by stellar evolution, and the phase of the ISM into which they are ejected.
+We note that the minimal contribution from Type Ia SNe for the iron-peak elements is because  no older stellar population was initialized, so only 16 of them have exploded by the end of our 500~Myr simulation.}
+
+\label{fig:species_sources}
+\end{figure}
+
+The only physics that separates the dynamical evolution of these elements in our simulations is the individual sources of enrichment: AGB winds (stars less than 8~M$_{\odot}$), stellar winds (stars above 8~M$_{\odot}$), core collapse SNe, and Type Ia SNe.
+These channels differ in: 1) how long after a given star formation event they occur, 2), by consequence, the typical ISM properties in which they occur, and 3) how much energy is associated with each event, which determines ejecta temperature and velocity.
+To understand where each of the elements in Figure~\ref{fig:species_fractions} originated, we show the mass fraction of metals produced through each channel in Figure~\ref{fig:species_sources}.
+Core collapse SNe are responsible for over 90\% of the total metal enrichment in our galaxy, but this is clearly not true for all elements.
+In particular, a majority of N (74\%) and Ba (65\%) are ejected by AGB winds; both are retained at a higher rate than the rest of the metals.
+That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yield tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through SNe.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and SNe.
+However, this cannot be proven as we lack Lagrangian information about individual gas elements.}
+% AE: Actually if there are significant isotope variations between nucleosynthetic sources (i.e.
+N produced in AGB winds is a different isotope than the trace N produced in SNe) then that could be a very cool thing to distinguish if we had good gas-phase abundance measures of various isotopes...
+but maybe not if they aren't very stable....
+We discuss how this result may extend towards other metal yields that are not well sampled on our relatively short (500 Myr) simulation timescales in Section~\ref{sec:discussion:metal yields}.
+
+AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of SNe ($\sim$1000~km~s$^{-1}$).
+In addition, their longer timescales relative to massive stars means that AGB stars are typically removed from their birth regions and randomly distributed through the galactic disk.
+The changes in typical ISM density and height of these events contributes to these variations.
+We show histograms of the average number density within 20~pc of any given enrichment source (top) and height above/below the disk (bottom) within 1~Myr of each event (as limited by our output cadence) in Figure~\ref{fig:spatial distribution}.
+As shown, SNe peak at very low densities, indicating that most explode in superbubbles, regions carved out by previous SNe.
+AGB stars predominately release their metals close to the average ISM density.
+The scale height distributions for both events show no significant differences.
+We do not expect these differences to be the dominant effect in driving the differential evolution of elements ejected by AGB winds vs.
+SNe, compared to the energetics, but can certainly play a significant role in determining the mixing behavior of individual enrichment events.
+The changes to mixing behavior as a function of ISM properties will be investigated in more detail in a future work.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{SE_density.png}\\
+\includegraphics[width=0.95\linewidth]{SE_z.png}
+\caption{The average gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
+\label{fig:spatial distribution}
+\end{figure}
+
+\subsection{Mixing and Distribution of Metals in the ISM}
+\label{sec:mixing}
+
+%mm I think this material duplicates the first paragraph of the introduction.
+% Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
+In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}).
+Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances.
+In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
+%mm However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
+To build towards this, we characterize the metal evolution and distributions in our galaxy below.
+      We characterize the metal distributions (in Sections~\ref{sec:log-normal} and \ref{sec:phase-pdfs}) and evolution (in Section~\ref{sec:statistics}) in our galaxy to build towards a  a complete model for how metals mix and evolve in the complex, multi-phase ISM of real galaxies.
+
+%mm should most of this material be in the introduction, and just the last two sentences be here?
+%   AE: I agree this is mostly redundant. I removed this
+%Chemical evolution models make varying approximations as to what fraction and on what timescales newly formed metals populate a galaxy's ISM and become available to enrich future generations of stars.
+In the simplest models, new metals are instantaneously available upon the formation of new stars, ignoring delays due to stellar lifetimes (\textit{refs, but maybe not if included in introduction}).
+Accounting for delays due to individual stellar lifetimes, loss from galactic winds, and dilution from accretion of pristine gas leads to models that can more accurately capture a variety of mean chemical properties of galaxies with some ability to account for spreads in abundances.
+%In hydrodynamics simulations, there has been substantial work understanding how metals, often characterized as passive scalar fields, diffuse in both turbulent boxes and global galaxy models.
+However, there is not  yet a complete model for how metals should mix and evolve in the complex, multi-phase ISM of real galaxies.
+To build towards this, we characterize the metal evolution and distributions in our galaxy below.
+
+\subsubsection{A Functional Form for Metal PDFs}
+\label{sec:log-normal}
+
+The log-normal distribution is found often in nature, generally describing 
+%mm
+    multiplicative
+processes with non-negative values that grow with time.
+In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}.
+In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}.
+Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}.
+It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape.
+This includes a log-normal component, generated by multiplicative processes---in this case shocks and the turbulent cascade in the ISM---and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2017}.
+
+The physics that drives the density PDF is directly related to the process of metal mixing and diffusion.
+However, there is no a priori reason why gas density and metallicity PDFs should have similar functional forms.
+We demonstrate here for the first time that the mass fraction PDFs for each metal species in our simulation can indeed be well fit using a piecewise log-normal + power-law PDF.
+We use a simple conceptual model in Section~\ref{sec:interpretation} to motivate the emergence of this distribution.
+
+We follow \citet{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2017} in constructing our piecewise PDF.
+We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element.
+This PDF is given as
+\begin{align*}
+  p(Z) =
+  \begin{cases}
+    \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right],
+    & Z < Z_{\rm{t}} \\
+    % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
+    N p_o Z^{-\alpha},
+    & Z > Z_{\rm{t}}
+\end{cases}
+\end{align*}
+where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm t}$ is the metal fraction at the transition between the log-normal and power-law components.
+When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm t}$ as free parameters.
+These conditions set $N$ and $p_o$ to
 \begin{equation}
-         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
+N = \frac{1}{2} \left[ 1 + \rm{erf}\left( \frac{ln\left(Z_{\rm t}\right) - \mu}{\sigma\sqrt{2}}\right)\right] + \frac{p_o}{\alpha-1}Z_{\rm t}^{-\alpha + 1}
 \end{equation}
-In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution.
-We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses.
-In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
-If it does, we randomly sample from
-the adopted IMF until approximately 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
-The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.
-We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
-Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
-By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.
-
-Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
-This dispersion captures some of the unresolved gas motions below the resolution limit that are smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations.
-Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
-
-Stars evolve during the simulation, by losing mass from stellar winds and SNe as described below, and by changing types, but persist throughout the entire simulation.
-For example, low mass stars are tagged as white dwarfs (WDs) at the end of their life, which may eventually explode as a Type Ia SN (discussed below), after which they persist as massless tracer particle remnants.
-Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a four-cell region at the highest level of refinement.
-This ensures that both stellar winds and SNe feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.
-
-\subsection{Stellar Properties}
-\label{sec:properties}
-Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}).
-We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$.
-Although $T_{\rm eff}$ and $g$ evolve over time for stars, modifying stellar radiative properties, following a stellar evolution track for each of our stars is beyond the scope of this work.
-We instead fix these properties at their zero age main sequence values.
-
-\subsection{Stellar Feedback and Chemical Yields}
-
-\subsubsection{Stellar Yields}
-\label{sec:yields}
-For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars.
-We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2018}.
-This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$.
-We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$.
-We ignore SN yields from these stars (see next paragraph).
-We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth.
-Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation.
-We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017a} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
-
-%
-% KVJ: Possibly include a discussion on uncertainties in stellar yields
-%
-
-Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe.
-Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$; we take $M_{\rm trans} = 8$~M$_{\odot}$.
-In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
-Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics).
-Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
-\citet{Cote2017a} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
-We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
-
-There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}.
-Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
-Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass, metal, or energy ejection.
-
-Type Ia SNe are an important additional source of galactic chemical enrichment.
-These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
-We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
-We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, substantially limiting the number of Type Ia SNe occurring during the initial gigayear in our models.
-
-\subsubsection{Stellar Winds}
-\label{sec:stellar winds}
-Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
-Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback.
-We assume complete thermalization of the wind kinetic energy, taking the total injected energy injected in timestep $\Delta t$ as $E_w = \frac{1}{2}\dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
-This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle.
-The edges of this spherical region will only partially overlap grid cells.
-We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately.
-We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
-
-Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}.
-Satisfying the Courant time step becomes prohibitively expensive following this gas, with time steps dropping to $\Delta t \sim$~100~yr.
-For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
-In our case, we fix massive stellar wind velocities to $v_w = 20$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies.
-Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work.
-These points are discussed in more detail in Sect.~\ref{sec:stellar winds discussion}.
-
-% Injecting 10$^{3}$ km s$^{-1}$ gas onto the grid at these scales leads to super heated, shocked gas at unphysical temperatures of about 10$^{8-9}$ K, particularly when injecting into very low density media.
-This can lead to painfully short time step sizes and crashes in the hydrodynamics solver.
-We adopt the common solution of artifiially reducing the wind velocity from massive stars, choosing $v_{\rm wind} = 500$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-However, this can still be problematic once the star evacuates the local ISM and injects its energy to very low density ($n \lesssim 10^{-3}$ \ccunit) gas.
-We address this issue by mass loading our winds when injection would lead to wind bubble temperatures in the spherical source region above a maximum temperature typical of wind bubble.
-This is a free parameter that we take to be 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
-Mass loading in this manner is (in effect) a sub-grid model for the unresolved ISM mixing at the boundary layer of the wind bubble, which is in fact the source of a majority of the gas mass within the wind bubble \citep{Weaver1977}.
-We take the metal species abundances of the mass loaded ISM to be the average cold / warm ISM abundance on each grid to prevent artificially inflating/deflating the overall abundances.
-We discuss our ability to resolve typical single star wind bubble properties in Appendix ~\ref{appendix:stellar winds}.
-
-%parameterized in this work with the STARBURST99 wind model, \citep{Leitherer1992}:
-%\begin{multline}
-%{\rm log} \left[ v_{\rm wind} {\rm (km~s^{-1})} \right] = 1.23 - 0.30~{\rm log}~\left[L{\rm (L_{\odot})}\right] \\
-% + 0.55~{\rm log}\left[M({\rm M_{\odot}})\right] + 0.64~{\rm log}\left[T_{\rm eff}(K)\right] \\
-% + 0.13~{\rm log}\left[Z({\rm Z_{\odot}})\right].
-%\end{multline}
-
-Stars that only undergo an AGB phase deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks.
-AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$.
-For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars as well.
-
-\subsubsection{Core Collapse SNe}
-\label{sec: core collapse}
-Stars between  $M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
-Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}).
-We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
-We use the same Monte Carlo sampling method as used in our stellar winds to map the spherical injection region to the grid.
-We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle.
-In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.
-
-\subsubsection{Type Ia SNe}
-\label{sec:Type Ia}
-We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as WD particles, marking a subset as Type Ia SN progenitors.
-This is the most self-consistent model for Type Ia SNe in galaxy-scale simulations.
-We note however that for the low SFRs in our isolated dwarf galaxy simulation, the first Type Ia SN only appears after a few hundred megayears of simulation time.
-By the end of the simulation presented here (500~Myr), only 18 have gone off.
-At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
-%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
-%or, 
-%\[
-%M_{\rm WD} = 
-%\begin{cases}
-%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
-%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
-%\end{cases}
-%\]
-%where $M_{\rm *}$ is the initial mass of the WD progenitor.
-We follow the common assumption that progenitor stars with initial masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017a}.
-
-We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution model.
-The Type Ia SN rate is taken to be a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope $\beta$ and normalization $N_{\rm Ia}/M_{\rm SF}$ are observables.
-The latter represents the number of Type Ia SNe per mass of star formation.
-By assuming an IMF  $dN/dm$, one can write down the fraction $\eta$ of stars capable of forming a Type Ia SN progenitor that \textit{will} explode within a Hubble time.
-This is given as
+and
 \begin{equation}
-\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
-\end{equation}
-where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF, and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
-The distribution slope $\beta$ is of order unity, with typical values between 1.0 and 1.2 \citep[see][for a recent review]{Maoz2014}.
-$N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the Type Ia SN rate and integrating over a Hubble time.
-Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
-For our fiducial values, we adopt $\beta = 1.2$ \citep{Maoz2010} and $N_{\rm Ia}/M_{\rm SF} = 0.8\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013}.
-Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.
-
-Finally, we can normalize $\Psi(t)$ to give the probability per unit time $\dot{P}(t)$ that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor.
-Integrating this gives the total probability at any given time as
-\begin{equation}
-P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
-\end{equation}
-where $t_{\rm o}$ is the formation time of the WD and the leading term on the right hand side properly normalizes the total probability over a Hubble time to $\eta$.
-This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
-In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle.
-For $u \in [0,1]$, we interpolate its position on a pre-tabulated and inverted cumulative probability distribution function to assign a single time at which the WD particle will explode as a Type 1a supernova.
-We institute a minimum delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.
-
-\subsubsection{Ionizing Radiation from Discrete Sources}
-\label{sec:ionizing radiation}
-Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies.
-\ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance.
-However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds.
-Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
-As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.
-
-Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation.
-We follow HI and HeI ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
-
-We determine the HI and HeI ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
-We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star.
-Stars less massive than about 15 M$_{\odot}$ and very massive stars with sub-solar metallicity are generally not well sampled by the OSTAR2002 grid.
-In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).
-
-Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}).
-The average energy for HI and HeI ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
-
-We also include the effects of radiation pressure on HI.
-This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}.
-We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared.
-This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}.
-However, the importance of multiple scattering is still unclear.
-Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013a,Reissl2017,Wibking2018}.
-Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.
-
-\subsubsection{Diffuse  Heating}
-\label{sec:diffusive heating}
-We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the FUV (6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles.
-The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the spectral energy distributions for each gridded star.
-Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
-Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
-However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}.
-Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile.
-Only recently has the localization and time variation of these processes been considered.
-
-Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}.
-We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
-We assume HeI ionization generally follows HI.
-This allows us to approximate HeI self-shielding using the same form (A.
-Rahmati, private communication).
-We ignore HeII photoionization from the UV background entirely.
-For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
-As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
-This is described in more detail in Appendix ~\ref{appendix:cooling}.
-
-%Ignoring this effect leads to an overestimation of the cooling rates when in the self-shielding regime.
-%We refer to \citet{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \citet{Gracklemethod} for its specific implementation, as used here.
-
-We assume the galaxy is mostly optically thin to stellar FUV and use only local approximations for shielding.
-We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
-\begin{equation}
-\label{eq:PE}
-\Gamma_{\rm pe} = (1.3 \times 10^{-24} \rm{erg~s^{-1}~cm^{-3}})\, \epsilon n_{\rm H} G_{\rm eff} D 
-\end{equation}
-where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust-to-gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
-Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
-
-The value of $D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
-The extremely low dust-to-gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a ratio $D$ that scales linearly with metallicity at very low metallicity.
-At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit.
-Given that the ambient density of the ISM is generally 1--10~cm$^{-3}$, we can safely assume the FUV field to be optically thin.
-However, we do include a localized attenuation prescription that may influence high-density or metal-enriched regions of the galaxy.
-We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.
-
-Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
-This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations.
-Our chemical network only includes contributions from H, He, and H$_2$ to n$_e$.
-Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
-%This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
-
-\subsubsection{Lyman-Werner Radiation}
-\label{sec:LW}
-In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rate.
-We compute the stellar Lyman-Werner flux again from the OSTAR2002 grid by integrating the spectral energy distributions over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}).
-Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
-We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.
-
-\section{Galaxy Initial Conditions}
-\label{sec:IC}
-We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy.
-The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
-Leo P is gas rich, with a neutral hydrogen mass $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and stellar mass $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to an observed neutral hydrogen radius $r_{\rm HI} = 500$~pc.
-LeoP has a low metallicity, with an oxygen to hydrogen abundance ratio (O/H) of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
-Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
-
-The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential.
-The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
-\begin{equation}
-\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
-\end{equation}
-where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass.
-We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$.
-We adopt a \citet{Burkert1995} dark matter potential with virial mass and radius $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and scale radius r$_{\rm s} = 990$~pc.
-This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc.
-These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}.
-
-Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
-This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
-During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}.
-We stop the artificial driving 25~Myr after the first star particle forms.
-These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
-We note this initial driving is ad hoc in that we do not include other effects from the stellar population that would have caused these SNe.
-
-We emphasize here that our model, with no initial stellar distribution, is not intended to identically reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
-In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations.
-Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances.
-In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution.
-Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe.
-The subsequent metal enrichment from the stars in our simulation can be thought of as tracking a change in abundances from arbitrary initial conditions.
-We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.
-
-\section{Results}
-\label{sec:results}
-We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms.
-Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run.
-The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical height $|z| < 200$~pc relative to the center of the galaxy.
-ISM properties are calculated considering only the gas contained within the disk of the galaxy.
-We include a resolution study in Appendix \ref{appendix:resolution_study}.
-
-Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.
-All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset dd76ad10.
-
-\subsection{Morphological Structure and Evolution}
-\label{sec:structure}
-
-We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}.
-These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
-This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
-This central region quickly fills with warm and hot gas generated from radiation feedback and SNe respectively.
-Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels.
-The ISM properties are quantified further in Section~\ref{sec:phase}.
+p_o = \frac{1}{\sigma Z_{\rm t} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm t}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm t}) \right]
+\end{equation}.
+
+We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin 
+%mm with 
+         width
+of 0.05 dex.
+We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \cite{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins.
+The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted.
+The log-normal + power-law PDF produces the best fit in nearly all cases.
+
+We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
+These PDFs have been computed at an arbitrary single point in time, at 270 Myr.
+For clarity, we only show a subset of the 15 elements we follow.
+As shown, there are clear differences in the PDFs across elements of different nucleosynthetic origins and between each phase.
+However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions.
+We discuss the differences among each phase in more detail in the next section, but note here that the significance of each of these components varies notably across phases.
+In many of these cases, the piecewise log-normal + power-law distribution fits the numerical PDF quite well.
+However, there are often deviations, particularly at low metal fractions, from pure log-normal behavior.
+This manifests as either a very broad, flat PDF at low metal fraction (see N and Ba, for example), or large peaks not well described by $p(Z)$ at low metal fraction.
+In these situations, it is unclear what, if any, portion should be considered as a log-normal, or if there are multiple components within this region.
+
+We argue here that the log-normal + power-law PDF can be a powerful tool for modelling the metal fraction  PDFs of individual elements in galaxy models.
+The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM.
+In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions.
+Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$.
+As this is the source of star-forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
-\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation.
-Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row).
-Each individual main sequence star particle is shown in the number density projections as a single black dot.}
-\label{fig:panel_x}
+\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
+\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), HIM (red), and all the gas in the ISM (black).
+For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
+We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.
+Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
+\label{fig:log-normal}
 \end{figure*}
 
-The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
-This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time.
-Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--120~pc.
-Towards the end of the simulation time, the half-light radius is $391 \pm 19$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
-Although the disk remains thin beyond the half-light radius, with a scale height of around 50~pc, it is fully resolved at all radii.
-By the end of the simulation, the majority of the disk has a scale height of $\sim$100~pc.
-
-Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging.
-For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
-In the final column of Fig.~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
-With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
-At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$.
-These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.
+\subsubsection{PDF Variation Across Gas Phase}
+\label{sec:phase-pdfs}
+
+The various phases represented in Figure~\ref{fig:log-normal} involve variations in density and temperature of more than six orders of magnitude.
+The evolution of each phase is qualitatively different, and the metal mixing behavior of each should vary.
+Mixing timescales over a given length scale should be related to the local sound speed; hot gas, with higher sound speeds, should mix more rapidly than the dense, disconnected clumps of cold gas in the ISM.
+In addition, one would expect a metallicity gradient with gas temperature as enrichment occurs first in the hot phases, cooling and enriching denser gas over time.
+We examine the PDF variations among elements in each phase, as shown in Figure~\ref{fig:log-normal}, in more detail here.
+
+Unsurprisingly the diffuse HIM contains the most metal enriched gas, as it is comprised predominately of metal enriched SN ejecta.
+Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
+Generally, in colder gas the metal PDFs become less enriched with broader low metal fraction components and steeper, power-law tails.
+Although the extended power-law tail of the HIM leads to a large range of metal fractions, the HIM represents very little mass, and this tail represents recent, un-mixed enrichment.
+The comparatively narrow width in the log-normal regimes of CNM is perhaps surprising.
+Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is more well mixed.
+This runs counter to the idea that mixing times should be long in colder gas unless mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.
+
+Although these trends across phases hold for all elements, there are qualitative differences between elements, particularly between those ejected predominantly by AGB winds (e.g.
+Ba and N) and those ejected by SNe (e.g.
+O and Mg).
+In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by SN enrichment.
+The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the CNM.
+Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N included in SNe yields.
+Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and SNe.
+AGB wind elements enrich the WNM and WIM directly, rather than the HIM, which would increase their mixing timescales and broaden their PDFs.
+
+\subsubsection{The Time Evolution of Metal PDFs}
+\label{sec:statistics}
+We focus on the time evolution of the full numerical PDFs in this section.
+Our results here do not depend upon the choice of functional form for $p(Z)$.
+Figure~\ref{fig:phase-statistics} shows the evolution of four different statistics for the O (top) and Ba (bottom) PDFs.
+These two elements are treated as representative elements for SN and AGB wind production respectively.
+The difference between the mean and median masses of the PDF (second column) is a measure of the skew of the PDF.
+Positive values indicate that metals are preferentially sequestered in metal-rich gas, and are less well mixed throughout the given phase.
+The skew is always positive in these distributions.
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
-\caption{Same as Fig.~\ref{fig:panel_x}, but showing face-on views.}
-\label{fig:panel_z}
+\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution.png}
+\caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation.
+The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
+\label{fig:phase-statistics}
 \end{figure*}
+
+For O, the median mass fraction is ordered by phase temperature.
+The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm 1$ dex over the simulation time.
+The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
+%This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events.
+Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread.
+The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling through multiple phases until enriching star-forming gas.
+This
+%mm is the only explanation for [that's perhaps too strong a claim]
+    can explain
+how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels). Individual enrichment events 
+%mm will 
+have significantly higher metallicities than the ambient ISM in any phase, and 
+%mm will 
+drive an increase in the difference between the mean and median of the PDF.
+These can be seen as the obvious spikes in the HIM and WIM.
+For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.
+
+% In each phase, enrichment events will tend to drive larger differences between mean and median mass fraction,
+
+Although these trends are generally true for Ba, its evolution is much more complicated.
+%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability.
+Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} in during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM.
+The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
+Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in SNe.
+The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
+These tails represent the most recently enriched gas,
+%mm and 
+        which
+is clearly much more locally confined than O.
+
+%{\bf (move to discussion?)}:
+The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e.\ the ratio between the total mass of metals and the total mass).
+Assuming star-forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex),
+%mm but
+   though 
+significant, for elements released during SNe explosions, but can be very significant, up to $\sim$ 0.8 dex, for elements released in AGB winds.
+Chemical evolution models, especially one-zone models, follow the mean metal fraction, rather than the median.
+%mm These results indicate that these 
+            Our results indicate that such
+models are biased to overestimate gas and stellar elemental abundances.
+. % However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.
+
+To summarize, Figure~\ref{fig:phase-statistics} demonstrates: 1) there are qualitative differences in how SN injected elements (e.g.
+O, Mg) and AGB wind injected elements (e.g.
+N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM; 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM and because the hotter phases are more directly populated by recent enrichment events; 3) the cooler, denser phases, particularly for SN injected elements, are more well mixed than the hot phases of the ISM; 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function; and therefore 5) the median metallicity available for star formation
+%mm rates 
+lies below the mean galactic value.
+In the case of SN injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
+For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.
+
+\section{Discussion}
+\label{sec:discussion}
+We begin with a simple toy model that motivates the power-law tail at high metal fractions of the metal fraction PDFs and a subsequent turnover at low metal fractions in Section~\ref{sec:interpretation}.
+This work is placed in context with previous works focusing on metal mixing in the ISM in Section~\ref{sec:context}.
+We discuss the relevance of additional AGB yields not directly followed in this study in Section~\ref{sec:discussion:metal yields}.
+Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impact of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
+
+\subsection{Physical Interpretation of the PDF}
+\label{sec:interpretation}
+%
+% KVJ wanted clarification on this argument. I believe my added text 
+% does this sufficiently.
+Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_{\rm o}$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$.
+Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas.
+In this case, $p(t,Z)$ initially takes the form of a double-delta function
+\begin{equation}
+
+p(t_{\rm o},Z) = \delta(Z_{\rm o}) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
+\end{equation}
+%mm [edited the rest of this paragraph, and the next though I don't think there are any substantive changes unmarked.]
+If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time  $\tau_{\rm mix}$ this gas will have mixed with an equal amount of primordial gas.
+\textbf{At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.} This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
+\textbf{The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.}
+
+\textbf{Thus, if the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous distribution $p(t,Z)$
+%mm , or $p(Z)$, 
+of these many events will be a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.}
+% and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
+The slope of the power-law, then, is determined by the rate of injection versus mixing with the ambient medium.
+A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium.
+Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than
+%mm enrichment. 
+         injection.
+If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.
+
+In reality, however, $M_o$ is not an inexhaustible reservoir of primordial gas.
+Eventually the entire ambient medium will become enriched to some $Z > Z_o$, and $p(Z)$ will consist entirely of a truncated power-law.
+As enrichment proceeds, gas near the low metallicity truncation of $p(Z)$, which still comprises much of the mass of the system, enriches towards higher metallicities in the power-law tail.
+This will produce a turnover at the low $Z$ limit of $p(Z)$.
+The low-turnover limit is produced by diffusion from many different sources, and is thus an additive process, which, as we noted above, tends to produce log-normal distributions.
+%mm [additive vs multiplicative]
+   {\bf [According to Section~\ref{sec:log-normal}, MULTIPLICATIVE processes produce log-normals. Additive processes produce power-laws.  However, see Mouri (2013) for a possible counterexample...]}
+The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.
+
+This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases. 
+%mm The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions. 
+     Individual enrichment events start at very high metal fractions in the low-density HIM, 
+     so they easily create long power-law tails.
+Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low metallicities.
+Cold, dense gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.
+
+%
+%
+%
+%Although this model is useful to explain these very general features, it is certainly incomplete in practice.
+Enrichment proceeds irregularly through the mulit-phase ISM with a variety of ejection masses and metallicities.
+Phases are not independent, and the hot phase cools and enriches cooler phases in the ISM, distorting $p(Z)$ within each phase.
+Cold gas is heated up and destroyed through feedback, changing the content of the low-metallicity end of the warm and hot phases.
+Finally, gas is removed from the galaxy through feedback driven winds that preferentially remove metal enriched gas.
+Each of these processes has a non-trivial effect on the evolution of the PDF that will cause deviations from the simple toy model outlined here.
+Determining the exact physical processes that drive and set the properties of each PDF is the subject of ongoing work.
+
+%
+% A.E. paragraph may need work
+%
+
+Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}.
+Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
+This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dense gas ($\sim$ 1 km s$^{-1}$).
+Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy.
+This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
+It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing SNe.
+Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star-forming gas.
+Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy.
+The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.
+
+% From benoit: more explicit title
+\subsection{
+%mm Context With 
+        Comparison with 
+Previous Studies of Metal Mixing}
+\label{sec:context}
+That metal fraction distributions can be described using simple analytic log-normal + power-law PDFs, even in a complex, multi-phase ISM, has not been demonstrated prior to this work.
+In addition, this is the first work to demonstrate differential mixing behavior of individual metal species using 3D hydrodynamics simulations.
+However, there does exist a significant body of work investigating the mixing behavior of passive scalars in a variety of contexts.
+%mm , as discussed below.  [ moved KrumholzTing18 to end of following paragraph.]
+%We discuss our results further in the context of previous research on metal mixing in the ISM and speculate on the physical processes that drive the evolution of these PDFs across phases.
+
+Previous work on the evolution of metals in the ISM varies from studies concerning the advection of passive scalars in idealized turbulent boxes \citep[e.g.][]{Pope1991, PanScannapieco2010, PanScannapiecoScalo2012, PanScannapiecoScalo2013, YangKrumholz2012, SurPanScannapieco2014, Colbrook2017}
+% cite passive scalar reviews by Warhaft 2000 in fluid mech and scalo + Elmegreen 2004?
+to global galaxy models studying generalized advection and mixing of passive scalars \citep[e.g.][]{deAvillez2002,Petit2015,Goldbaum2016} to models with more detailed self-consistent metal enrichment \citep[e.g.][]{Revaz2009,Escala2018}.
+\cite{KrumholzTing2018} predict differential behavior for AGB wind and core collapse SN synthesized elements as a direct consequence of the differences in size of typical planetary nebulae ($\sim$ 0.1~pc) and SN remnants ($\sim$ 100~pc).
+
+The evolution of metallicity PDFs has been investigated previously in some of these works \citep[see ][ and references therein]{PanScannapiecoScalo2012,PanScannapiecoScalo2013}, with effort towards developing closure models to describe the evolution of the PDFs of passive scalars in turbulent media \citep[e.g.][]{EswaranPope1988,Chen1989,Pope1991}.
+The astrophysical context in much of this work was enrichment from the first stars, so the focus was on the low-metallicity tail of the PDF and the timescales over which gas is polluted \citep[e.g.][]{PanScannapiecoScalo2013,Sarmento2017}.
+These works often use isothermal turbulent-box simulations initialized with a double-delta function PDF of pristine gas and enriched gas in some varying spatial distribution, ignoring ongoing enrichment.
+Initial PDFs of this form were demonstrated some time ago to evolve into a Gaussian distribution at late times \citep{EswaranPope1988}, but it is unclear if these could also be described with a log-normal distribution.
+However, these works uniformly do not contain the high metallicity power-law tails shown in our work.
+As suggested by our toy model in Section~\ref{sec:interpretation}, this is due to the lack of ongoing enrichment in these studies.
+
+More detailed models of global galaxy evolution have generally focused on spatial correlations and mixing timescales of initially asymmetric fields, without concern for ongoing enrichment \citep[e.g.][]{deAvillez2002,Petit2015} or focused primarily on the evolution of stellar abundance patterns and metallicity distribution functions \citep[e.g][]{Jeon2017,Hirai2017,Escala2018}, without directly examining the evolution of gas-phase metallicity PDFs.
+
+%
+% MM: remove from this section:
+%This is the first work examining the gas-phase properties of metallicity PDFs in a global galaxy simulation with a detailed model for stellar feedback, chemical enrichment, and a multi-phase ISM.
+Since we are far from a complete understanding of galactic chemical evolution, investigating the physics behind what sets the statistical properties of these PDFs, particularly what drives the differences across metal species and phases, is important.
+Although this is beyond the scope of this current work, we use scaling arguments to speculate on the meaning of these results.
+%Metal mixing in the ISM is a diffusive process driven by turbulence.
+
+% Recent works investigating dwarf galaxy chemical enrichment with Lagrangian simulations have shown that the sub-grid diffusion models required to reproduce observed dwarf galaxy abundance properties imply fairly rapid mixing timescales \citep{Escala2018,Hirai2017}.
+In contrast to this work, \cite{Escala2018} finds dwarf galaxy
+%The sub-grid diffusion models in Langrangian simulations of dwarf galaxy chemical enrichment that match the abundance properties of observed dwarf galaxies imply rapid mixing timescales
+
+%
+%
+%  Recent works specifically examining metal mixing in dwarf galaxies. Saving for potential future discussion:
+% \cite{Hirai2017} uses constrains the diffusion parameter in their SPH simulations comparing their simulated dwarf galaxies to observations in [Mg/Fe] vs.
+[Fe/H] and [Ba/Fe] vs.
+[Fe/H] space.
+Suggests Ba/Fe is more powerful constraint and briefly discusses potential differences in mixing between elements but does not do work with this
+% \cite{Jeon2017}
+% \cite{Escala2018} tests of role of metal diffusion models in producing realistic MDFs in dwarf galaxies. Able to reproduce things like MDF width and [alpha/Fe]vs[Fe/H] scatter.
+
+% The properties of log-normal density PDFs in isothermal simulations are governed by the statistical properties of turbulence (refs) and the relative importance of compressive and solenoidal driving.
+However, the density PDFs in simulations of global galaxies with a resolved, multiphase ISM show significant departures from log-normallity \citep[see][]{Hopkins2013} but are still approximately log-normal within individual phases of the ISM \citep{HopkinsQuataertMurray2012}.
+The properties of the density PDF in multiphase simulations have not been well studied which offers little insight into what sets the mass fraction PDFs for each element.
+We speculate on this here to motivate future study, but note that a detailed characterization is beyond the scope of this work.
+
+% The log-normal density PDFs found in ISM simulations have a variance that is proportional to the mach number \citep[e.g.][(maybe more)]{PNJ1997, Passot1998, Fedderath2008, LemasterStone2009}.
+In our simulations, however,
+
+%We discuss possible caveats to this in Section~\ref{sec:caveats}.
+Does this extend to more massive?
+how does DM potential affect this?
+Are general trends still true in much larger galaxies?
+or are things very different once HIM crossing times are more like 100 Myr (aka MW size galaxies).
+
+\subsection{Timescale Dependence of AGB Ejecta}
+\label{sec:discussion:metal yields}
+We can generally say that metals 
+%mm produced
+    ejected 
+in AGB winds evolve qualitatively differently than metals produced by SNe in 
+%mm dwarf galaxies 
+     our dwarf galaxy. 
+However, exactly which metals exhibit these differences, and to what degree, is timescale and metallicity dependent.
+Short timescales ($\lesssim 100$~Myr) only sample enrichment from the most massive AGB stars,
+%mm which 
+     while 
+stars on order of a few solar masses 
+%mm 
+    only
+enrich on timescales of a gigayear or longer. In our simulations, which only 
+%mm sample
+   simulate 
+500 Myr of evolution, N and Ba are dominated 
+%mm from 
+     by
+AGB wind ejecta.
+C is commonly used to track AGB wind enrichment, but as it originates from lower mass AGB stars, C enrichment operates on gigayear timescales, longer than we follow in this work.
+Enrichment additionally varies with metallicity.
+Sr, for example, is only significantly ejected through AGB winds at our metallicity on gigayear timescales, while stellar winds from more massive stars dominate the production of Sr on shorter timescales.
+At higher metallicity, much more Sr is produced through massive AGB stars, decreasing the timescale over which Sr should exhibit a differential chemical evolution compared to SN-ejected elements.
+
+To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected by AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times.
+This model was run using \textsc{SYGMA} \citep{Ritter2017}.
+As shown, metal enrichment from AGB winds only begins to dominate for
+%mm a given species at 
+    any elements after 
+$\sim$ 100 Myr. This includes N and Ba, which we follow in our simulations, but this 
+%mm plot indicates
+    model predicts 
+that Ag and Pb 
+%mm should 
+     will
+show similar bahavior.
+It takes over a gigayear for C to be dominated by AGB wind ejecta, which is the case for many of the elements shown.
+F, which shows very little contribution from AGB winds at short timescales, is dominated by enrichment from them on longer timescales.
+These dependences on metallicity and timescales certainly add complications in generalizing our work and in interpreting observations in the context of the results presented here, but these difference could be leveraged to better understand galactic chemical evolution on multiple, distinct timescales.
+Clearly this motivates future work covering gigayear timescales to fully understand how metal mass fraction PDFs evolve with time.
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0.png}
+\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, without continuing star formation.
+We only show a sample of some of the elements dominated most by AGB enrichment at late times.
+The horizontal line marks a 50\% contribution.}
+\label{fig:agb evolution}
+\end{figure*}
+
+%\begin{figure*}
+%\centering
+%\includegraphics[width=0.95\linewidth]{C_N_evolution.png}
+%\caption{The fractional contribution of AGB winds to the total yields of C and N as a function of time for a simple stellar population at three different metallicities.
+Since the nucleosynthetic source governs the mixing dynamics of a given metal, this plot illustrates how this can change with both time and metallicity for a given species.
+These models were generated using \textsc{SYGMA} \citep{Ritter2017-sygma}}
+%\label{fig:agb evolution}
+%\end{figure*}
+
+\subsection{Impact on Stellar Abundance Patterns}
+\label{sec:stellar abundances}
+In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star-forming gas in our simulations.
+This could be used to help disentangle sources of scatter in observed stellar abundance, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
+If the
+%mm star-forming gas in our simulations can also be well-fit by a log-normal + power-law PDF
+        metal mass fractions in star-forming gas in our simulations 
+        can also be well fit by log-normal + power-law PDFs,
+and if we can parameterize their evolution as functions of global galaxy properties, this 
+%mm can 
+    could
+be used as a powerful 
+%mm and analytic 
+tool for modeling stellar abundance patterns in semi-analytic models.
+This would be a physically motivated way to account for both the intrinsic spread in stellar abundances due to inhomogeneities in the ISM and variations in mixing for different metal species.
+We reserve an analysis of these distributions in abundance space in both the gas and stars for future work.
+However, we briefly discuss the connection to star-forming gas and stellar enrichment below.
+
+Unfortunately, there is insufficient star-forming gas at any one time in our simulations to construct PDFs of 
+%mm metal distributions
+    metal mass fractions. 
+However, star-forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, 
+%mm follow a similar PDF 
+   to have mass fraction PDFs similar
+to the CNM.
+To verify this, Figure ~\ref{fig:stars} shows the difference between the oxygen mass fraction of stars and the median mass fraction from the CNM PDF at the time that particle formed.
+The large scatter at early times ($<$ 120~Myr) is a result of the early enrichment phase, when the initial gas oxygen mass fraction was zero.
+Stars seem to be sampled evenly around the median of the CNM distribution, with only a slight bias (52\% of stars) towards values below the median.
+However, for stars formed after the initial phase, the median separation from the CNM median is 0.31~dex, and can reach up to $\sim$~0.5~dex.
+Though a significant deviation, this is smaller than the typical inner-quartile range (IQR) of the CNM (see Figure~\ref{fig:phase-statistics}).
+Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
+High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
+
+%KVJ suggested emphasizing that there is much more potential in this work / work like this by examining more dimensions
+\textbf{We emphasize that this study focuses on each chemical dimension independently, as a means to first understand galactic chemical enrichment in the simplest possible framework.
+However, the cross-correlation of multiple metal fractions and abundance ratios is the most useful in revealing key processes in galactic chemodynamics.
+A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiements.
+We will examine this more complicated multi-dimensional space with these
+%mm simulations 
+   numerical methods
+in future work.}
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{scale_height}
-\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
-\label{fig:scale_height}
+\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
+\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the
+%mm
+    time 
+within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
+\label{fig:stars}
 \end{figure}
 
-\subsection{Star Formation Rate and Mass Evolution}
-\label{sec:sfr}
-
-We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Fig.~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
-The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$.
-The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation.
-Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.19 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
-We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.
-
-We note that the granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
-Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
-For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$.
-Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense.
-Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.
-
-At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Fig.~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
-The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
-For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% at 500~Myr.
-The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy from feedback-driven galactic winds.
-During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM.
-Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
-The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{sfr_snrx100}
-\includegraphics[width=0.475\linewidth]{mass_evolution}
-\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins.
-Broken portions of this histogram are time periods with no star formation or supernovae.
-Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.
-Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
-\label{fig:sfr_mass_evolution}
-\end{figure*}
-
-\subsection{ISM Properties}
-\label{sec:phase}
-
-Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
-We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
-We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content.
-By this definition, although our galaxy certainly contains molecular hydrogen, molecular gas as a phase does not exist; the peak f$_{\rm H_2}$ in any single cell remains below 30\%.
-See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-The properties of these phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
-Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.
-
-Fig.~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
-One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Fig.~\ref{fig:ISM_evolution}).
-Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
-We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
-Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left.
-The boxed regime in the lower right corner shows our star formation density and temperature threshold.
-Gas in this regime is rapidly consumed by star formation and subsequent feedback.
-Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average.
-
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{phase_diagram.png}
-\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gas interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr.
-The dashed lines are lines of constant pressure, separated by factors of 10.
-The region in the lower right corner indicates our density and temperature thresholds for star formation.}
-\label{fig:phase}
-\end{figure}
-
-The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Fig.~\ref{fig:ISM_evolution}.
-The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
-The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run.
-The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation.
-During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1.
-Although the CNM dominates the mass fraction, it is a negligible component of the ISM volume, which is WIM dominated.
-However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
-Together, these figures better quantify the general properties observed in the panel plots in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}.
-
-These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
-They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (defined in those works as gas with 100~K$<$T$< 3\times 10^{4}$), with cold gas having between 1 and 10\% of the mass, and occupying negligible volume.
-Hot gas (defined as gas with $T > 3\times 10^{4}$~K) occupies 10\% of the volume, with negligible mass, in their galaxy, while our WIM alone occupies $>$ 50\% of the volume.
-Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) and hot gas (by volume fraction) that seen in the more massive dwarf galaxy in these works.
-The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
-We have compared our cooling curves to those used in \citep{Hu2017} and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.
-
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
-\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
-\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
-\label{fig:ISM_evolution}
-\end{figure*}
-
-\subsection{Interstellar Radiation Field}
-\label{sec:ISRF}
-
-The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}.
-This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
-In Fig.~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
-The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
-The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
-At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.
-
-The bottom panel gives the HI ionizing photon flux from stellar radiation.
-The ionizing radiation profile follows a similar trend, yet with significantly more variation, anywhere from two to four orders of magnitude.
-As this radiation is followed through radiative transfer, the profile encodes information about local attenuation by dense, neutral gas.
-This is the main driver of the differences between the two panels.
-The total fluctuation in both panels is due in part to the low-level, stochastic star formation in our galaxy.
-A higher star formation rate would produce a more regular population of massive stars and more uniform (in time) ISRF.
-
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{G_o_profile} \\
-\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
-\caption{
-Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr.
-Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc.
-The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
-The bottom panel gives the HI ionizing stellar radiation flux.
-Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point.
-For this reason we only shade between the first quartile and maximum values.
-HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.
-In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
-\label{fig:ISRF}
-\end{figure}
-
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
-\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
-\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
-Here, we include all gas within the mid-plane of our dwarf galaxy.
-Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
-This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
-\label{fig:ISRF_2D}
-\end{figure*}
-
-To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Fig.~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr.
-This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
-The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
-From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
-Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation.
-In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency.
-It remains to be seen which of these two modes of feedback is more important in regulating star formation.
-
-\subsection{Outflow Properties}
-\label{sec:outflows}
-
-The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}.
-However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
-In Fig.~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
-We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
-\begin{equation} \label{eq:dotM}
-\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
-\end{equation} 
-We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.
-
-The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Fig.~\ref{fig:mass_outflow}.
-Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
-For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor.
-The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors between 20--100 throughout the simulation time.
-This declines towards larger radii, however, with substantially less outflow past the virial radius.
-\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift, consistent with our results.
-The fluctuations in both of these panels are directly correlated with the SFR, with increased outflow during periods of star formation, and decreased outflow during periods of quiescence.
-
-Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
-Using a fit provided in \citet{Muratov2015} to extrapolate and compare $\eta$ at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
-These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
-We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find lower mass loading factors even closer to the disk, at 0.05 $R_{\rm vir}$, between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$; certainly this implies even smaller mass loading factors at 0.25 $R_{\rm vir}$.
-
-\begin{figure*}
-\includegraphics[width=0.45\linewidth]{total_mass_outflow}
-\includegraphics[width=0.45\linewidth]{total_mass_loading}
-\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
-\label{fig:mass_outflow}
-\end{figure*}
-
-Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
-In Fig.~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
-Gas with a negative velocity is moving towards the center of the halo.
-Roughly 25\% of this mass is inflowing, mostly with modest negative velocities, and corresponds to previously ejected gas mixing and recycling throughout the halo.
-Half of the outflowing gas (positive velocities) is moving at velocities below 30 km s$^{-1}$, 75\% at velocities below 70 km s$^{-1}$, and 95\% at velocities below 100 km s$^{-1}$.
-Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-negligible amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$.
-The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominating at velocities above 200 km s$^{-1}$.
-The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling WIM and HIM, consistent with the results in \citet{Hu2016,Hu2017}.
-However, as shown, the HIM, which is mostly the SN ejecta itself, comprises very little of the outflow by mass.
-Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM.
-Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
-The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
-
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
-\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-This is averaged over the same time interval as Fig.~\ref{fig:ISRF}.
-The outflowing material is multiphase, broken into WNM, WIM, and HIM.
-See Section~\ref{sec:phase} for definitions of these regimes.
-We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K.
-There is little to no outflowing mass in the CNM.}
-\label{fig:outflow_velocity}
-\end{figure}
-
-\subsection{Metal Evolution} 
-\label{sec:chemical evolution}
-
-\subsubsection{Metal Enriched Outflows}
-Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
-This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
-In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}.
-The parameter used to quantify metal outflow efficiencies varies among works.
-Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
-\begin{equation} \label{eq:eta-metal}
-\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
-\end{equation}
-where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
-On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5).
-Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}.
-\cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
-Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.
-
-\begin{figure}
-\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
-\includegraphics[width=0.9\linewidth]{metal_retention}
-\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:mass_outflow}.
-This is the ratio between the metal outflow rate and the metal production rate.
-{\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
-In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
-\label{fig:metal_evolution}
-\end{figure}
-
-These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
-This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
-After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
-This continues throughout the simulation, with only $\sim$4\% of produced metals residing in the disk of the galaxy.
-It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius until about 350 Myr where the fraction levels off to just above 50\%.
-Likewise, the CGM metal content continually decreases until the end of the simulation from loss through the virial radius of the halo.
-See Section~\ref{sec:obs_metals} for further discussion.
-
-\subsubsection{Differential Evolution of Elements Within the ISM}
-It is important to understand how metals from each source of stellar yields enrich the ISM.
-Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}.
-This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed.
-Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Avillez2002,Tassis2008,YangKrumholz2012}.
-It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
-It is even more unclear how metals are transported and distributed within low-mass dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.
-
-We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
-The left panel gives the abundance ratio of N to O throughout the ISM.
-The right
-two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy.
-These show regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K) connected by cold filaments, warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
-
-\begin{figure*}
-\includegraphics[width=0.98\linewidth]{log_NO_panel}
-\caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances.
-The left slice gives the ratio of the abundance between N and O, normalized to the solar abundance, while the number density and temperature are shown on the right.
-In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occurred in the preceding 5 Myr as black stars and orange diamonds respectively.}
-\label{fig:metal_slices}
-\end{figure*}
-
-As shown in the left panel, [N/O] varies significantly over this section of the ISM with notable differences across the various phases and ISM structures.
-The hottest gas, dominated by recent supernova explosions is overabundant in oxygen, relative to solar (purple).
-However, the relative abundance of nitrogen increases in the WIM and WNM, being overabundant relative to solar (green).
-
-At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars.
-Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
-Given the variations in Fig.~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
-The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
-This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
-A more detailed analysis is beyond the scope of this work, but we investigate this in detail in Emerick et.
-al.
-(in prep.).
-
-\section{Discussion}
-\label{sec:discussion}
-
-\subsection{Comparison to Observed Low Mass Dwarf Galaxies}
-\label{sec:observation}
-
-As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs.
-Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of $z = 0$ dwarf galaxies.
-However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies.
-We show that these properties are broadly consistent with observations.
-
-\subsubsection{Gas and Star Formation}
-\label{sec:gas_sf}
-
-The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}.
-However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
-In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.
-
-Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
-We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}.
-We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the area of the disk within the radius of the outermost star formed within the previous 10 Myr.
-Likewise, $\Sigma_{\rm gas} = M_{\rm gas,10} / A_{*,10}$, where M$_{\rm gas,10}$ is the total gas mass within this defined disk.
-However, the total gas content cannot be determined observationally.
-To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He.
-We note that there is generally no correction made for any possible H$_{\rm 2}$ or HII content.
-As shown in Section~\ref{sec:molecular gas content}, these components may be significant.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
-\includegraphics[width=0.475\linewidth]{all_gas_efficiency_evolution.png}
-\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
-See text for details of the calculation.
-Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars.
-On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}.
-There is no clear correlation with time in this diagram.}
-\label{fig:KS}
-\end{figure*}
-
-We include recent observational constraints on these relationships in Figure ~\ref{fig:KS}.
-Our galaxy fluctuates significantly about both relationships with no clear trends in time.
-However, in both cases, it is consistent with the available observational sample.
-At times our galaxy exhibits gas surface densities below the observational constraints.
-The trend is still consistent with higher densities at this point, but with a larger scatter towards lower star formation rate densities and efficiencies.
-
-In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
-It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
-This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
-The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.
-
-\subsubsection{Molecular Gas Content}
-\label{sec:molecular gas content}
-The molecular gas content of low-mass dwarf galaxies is generally assumed
-to be small, but is not well constrained by either theory or observations.
-Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
-As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range.
-H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
-The gas-phase reaction dominates in our low-metallicity galaxy over the other two channels by several orders of magnitude.
-In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
-Thus the presence of some ionizing background is required to generate the molecular fractions we find in our simulations, as confirmed in separate test simulations.
-\textbf{Our model does include a contribution from the meta-galactic background to the photodetachment of H$^{-}$.
-However, we note that we do not account for the contribution to this rate from the ISRF.
-We find that the H$_2$ fraction is more strongly dependent upon the Lyman-Werner radiation field, which is followed for each star, than the H$^{-}$ photodetachment rate.
-Our tests suggest that ignoring the stellar contribution to H$^{-}$ may lead to a 10--20\% overestimate in the computed H$_2$ fractions.
-This is discussed in more detail in Appendix~\ref{appendix:H minus}}.
-
-In contrast, \citet{Hu2016} and \citet{Hu2017} find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
-However, although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
-Our model suggests that both H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies.
-Indeed it is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, though it is worth noting that the rate coefficients associated with gas-phase H$_2$ formation are still uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
-Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
-It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
-This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
-
-\subsubsection{Metal Retention}
-\label{sec:obs_metals}
-
-The simulations presented here have not yet been run for the gigayear timescales required to begin to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$.
-However, we can compare to a key observable: the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from closed box stellar evolution models given the galaxy's star formation history.
-This can be done readily with Milky Way dSph's.
-Their stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
-However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
-
-Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich, star forming, low-mass dwarf galaxy, with an observable HII region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
-Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
-However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
-Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
-
-It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium.
-While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
-We find 5.3\% of all metals lie within 1 kpc of the center of our galaxy, 24.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 51\% outside $R_{\rm vir}$.
-This is consistent with previous works, but this is again an evolving quantity.
-In addition, the amount of gas that escapes the virial radius is certainly sensitive to the details of gas accretion from the IGM on this galaxy, which we cannot capture in this model.
-
-The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
-Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return.
-In addition, the accretion of pristine gas from the intergalactic medium could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals.
-This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.
-
-\subsection{Missing Physics}
-Although we include many detailed physical models in our simulations, there remain additional physical processes that may be relevant, which we now discuss.
-
-\subsubsection{Massive Stellar Wind Energy}
-\label{sec:stellar winds discussion}
-Our massive stellar wind model drastically reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$.
-Although our algorithm is entirely capable of generating realistic stellar winds with velocities comparable to those observed, such fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
-When considered in isolation, stellar winds are an important source of pre-SN feedback and can dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
-However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}, unless densities near the ionizing source are high enough to trap the  HII region in the source cell.
-In that case, they can clear out a cavity to allow initial establishment of the HII region.
-
-They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
-Although they likely have minimal dynamical importance at resolutions where peak densities are not anyway high enough to trap ionization fronts, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting closer examination in future work.
-
-\subsubsection{Cosmic Rays} 
-\label{sec:CRs}
-
-Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}.
-These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}.
-Modeling cosmic rays is challenging, however, as they encompass a wide range of energies, and there are significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
-Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy.
-In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM.
-Modeling cosmic ray feedback completely thus requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena.
-Finally, including MHD presents additional difficulties in untangling the effects of each individual feedback mechanism on galaxy chemodynamics.
-
-We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested.
-Mechanically, including this relatively simple treatment of cosmic ray feedback in our model is trivial.
-However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to later work.
-
-\subsection{Detailed Stellar Evolution and Binary Stars}
-\label{sec:binary stars}
-
-Roughly half of massive stars live in binary pairs \citep{Sana2013}.
-Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes.
-This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as SNe.
-This effect could be significant, but is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g.
-STARBURST99).
-For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse SNe occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
-Although they find only $\sim 15\%$ of core collapse SNe explode after 50~Myr, this could still be an important effect.
-Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}.
-Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
-
-Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars.
-This is beyond the scope of this project, but will be investigated in future work.
-
-\section{Conclusion}
-\label{sec:conclusion}
-We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
-For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, using individual star particles to model core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, Lyman-Werner radiation and pollution from AGB and massive stellar winds.
-This treatment of feedback, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
-In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P dwarf galaxy.
-We present an overview of the properties of this simulation in this work.
-
-For our simulated dwarf galaxy, we find:
-\begin{enumerate}
-\item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
-(See Figs.~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).
-
-\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, falling to $\eta \sim 10$ at R$_{\rm vir}$,  and
-metal mass loading factors near unity.
-By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Fig.~\ref{fig:outflow_velocity}).
-
-\item 
-Only $\sim$4\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of low-mass dwarfs.
-By the end of the simulation $\sim$45\% of the remaining metals stay within the virial radius (but outside the galaxy), while $\sim$50\%
-have been ejected beyond the virial radius. (See Figs.~\ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
-
-\item 
-Beyond the stellar radius, the gas scale height is thin ($\sim 50$~pc), yet resolved, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
-This is comparable to the resolution limit of the diffuse HI in observed, gaseous low-mass dwarfs.
-At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Fig.~\ref{fig:scale_height}).
-
-\item The ISRF of our galaxy varies strongly in both space and time by orders of magnitude.
-It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
-The importance of radiation feedback in our model will be investigated in a future work.
-(See Figs.~\ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
-
-\item 
-We find H$_2$ fractions below 5\% in our dwarf galaxy, consistent with the poor constraints on molecular gas formation in low metallicity dwarf galaxies.
-This H$_2$ forms entirely through gas-phase reactions facilitated by H$^{-}$ in self-shielding regions; H$_2$ formation on dust grains and in the three body reaction are both insignificant.
-Cold, neutral hydrogen dominates the mass of our galaxy.
-While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Fig.~\ref{fig:sfr_mass_evolution} and Fig.~\ref{fig:ISM_evolution}.)
-
-\item Finally, we present gas-phase oxygen and nitrogen distributions as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy.
-These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs.
-SNe), as suggested by \cite{KrumholzTing2018}.
-This will be explored in more detail in future work (Emerick et.
-al.
-\textit{in prep.}).
-\end{enumerate}
-
-\section*{Acknowledgments:} 
-We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
-C\^ot\'e, S.
-Glover, K.
-Hawkins, C.
-Hu, K.
-Johnston, B.
-O'Shea, M.
-Putman, B.
-Smith, J.
-Wall, and J.
-Wise.
-We would additionally like to thank the referee for their careful report.
+% AE: Capitalized header
+\subsection{Do These Results Apply to More Massive Galaxies?}
+\label{sec:massive galaxies}
+%mm One
+   An 
+important caveat about our work is that these results are derived from simulations of an isolated, low mass, dwarf galaxy whose properties vary dramatically from more massive galaxies like the Milky Way.
+It is unclear how much these results apply to more massive galaxies
+%mm given their 
+     with
+deeper potential wells and higher star formation rates.
+Feedback-driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
+We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy.
+With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
+\textbf{We anticipate three potential regimes of metal retention,
+%mm related directly to 
+    depending on
+dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB 
+%mm
+    stars 
+and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.}.
+If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
+% AE: rewording given Benoits suggested changes
+%     If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+This difference would be greater at later times, once AGB enrichment becomes significant. 
+%     Benoit suggested limiting / eliminating discussion relative to metallicity, since this is a little murky (age-metallicity varies significantly galaxy-to-galaxy).
+In addition, the elevated signals of Ba abundance ratios I mention have some amount of contention....
+%     For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
+At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way.
+Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way.
+In addtion, recent observations find elevationd [Ba/Fe] vs.
+[Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS}, which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs.
+Given the lack of definitive explanation, clearly generalizing our results and detailing their observational consequences is a valuable area of future research.
+We would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+
+In contrast, we expect the properties of the enrichment PDFs, and the variations between AGB enriched elements and SN enriched elements (as presented in Figures~\ref{fig:log-normal} and ~\ref{fig:phase-statistics}), to be general.
+We expect metals to exhibit log-normal + power-law distributions in the ISM of all galaxies, with similar trends with enrichment source and gas phase as outlined here.
+However, the detailed properties of the PDFs (e.g, log-normal width, power-law slope) likely depend non-trivially on global galaxy properties.
+How these results vary as a function of galaxy properties will be investigated in future work.
+
+% Talk about CGM at all???
+
+%\textit{In addition, hot gas in a galaxy with a deeper potential well is less likely to be ejected from the galaxy, allowing more time for homogenization and possibly smaller metal fraction variation than seen here.}.
+
+\subsection{Implications for Exotic Enrichment Sources}
+\label{sec:exotic enrichment}
+%   AE: Benoit suggested removing arguments relating to NS-NS merger energetics as I had misred / miscaclulated the energy release values.
+He said greater emphasise on potential differences of mixing due to rarity, rather than energy.
+We have shown that the dynamical evolution of metals depends upon their nucleosynthetic source, focusing here on AGB synthesized elements and SN synthesized elements.
+However, these differences should also apply to exotic enrichment sources, such as hypernovae, neutron-star neutron-star mergers, and neutron-star black-hole mergers.
+These sources can have energies that differ significantly from typical SNe, reaching $> 10^{52}$~erg for hypernovae \citep{Nomoto2004}, for example.
+In addition,
+%mm the rarity of these events, for example,  there are approximately $10^{-5}$ per M$_{\odot}$ of star formation NSM in the Milky Way, could
+     these events are rare.  For example, neutron star mergers occur 
+     at a rate of approximately $10^{-5}$ per M$_{\odot}^{-1}$ of star
+     formation in the Milky Way\citep{Kim2015}.  This rarity could 
+significantly influence the typical ISM environments into which they eject their metals.
+We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to SNe.
+Based on our results here,
+%mm
+     for example,
+we would expect elements from hypernovae to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe. 
+% Benoit suggesed removing this given energy argument removal above
+%    Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies. 
+Depending on their injection energy, neutron star mergers could exhibit different mixing behaviors in the ISM.
+These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
+In particular, low mass dwarf galaxies with unusual r-process enrichment \citep[e.g.][]{Ji2016}, are valuable for constraining the source of these elements, their frequency, and typical yields.
+The differential metal evolution presented in our work both opens up an additional avenue by which elements from distinct nucleosynthetic sources may be distinguished in observations and challenges current assumptions used in interpreting these observations.
+
+%\subsection{Extra things I could discuss:}
+%\textit{Things to maybe}
+%\begin{itemize}
+%\item Observed N/O in stellar abundances exhibits large spreads at low metallicity.
+Argument has been that this is driven by timescale differences in AGB vs.
+massive star nucleosynthesis.
+However, our results would predict that N/O have a large spread due to mixing efficiency diffein rences between AGB winds and SNe.
+%\end{itemize}
+
+\section{Conclusions}
+\label{sec:conclusions}
+%mm For the first time we 
+We present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
+This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze
+%mm
+      for the first time
+how individual metal species couple to the ISM and galactic wind of this galaxy.
+We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, or core collapse SNe)
+%mm , and Type Ia SNe).  [I'm inclined to leave them out as we really didn't model their influence]
+This difference is most significant in our model between elements ejected predominately by AGB winds and those ejected predominantly by core-collapse SNe. In addition, we find 
+%mm for the first time 
+    the novel result
+that the mass fraction PDFs of each metal in the ISM can be described using an analytic piecewise log-normal + power-law PDF.
+The properties of these PDFs vary with both ISM phase and metal species, again driven mostly by differences in enrichment sources.
+
+We summarize our results as follows:
+\begin{itemize}
+
+%\item Elements from lower energy enrichment sources (i.e.
+AGB winds) are preferentially retained in the ISM of low mass dwarf galaxies as compared to those from higher energy sources (SNe), which are more readily launched in galactic winds.
+This result is likely sensitive to global galaxy properties, becoming less significant with increasing halo mass.
+We predict the abundance ratios between AGB wind dominated metals (s-process elements) and SN dominated metals ($\alpha$ elements) to be higher at fixed metallicity in low mass dwarf galaxies than in more massive galaxies, like the Milky Way.
+
+\item Power-law tails 
+%mm in 
+   on log-normal 
+metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
+
+\item Hotter phases have metal fraction PDFs that are more enriched, with significant power-law tails as compared to cold phases, which have a more %mm dominant log-normal structure. 
+   prominent log-normal component.
+The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling into dense gas. 
+% missing text???????????
+
+\item Metal outflow in low mass dwarf galaxies depends upon nucleosynthetic site.
+Metals from lower energy enrichment events (e.g.
+AGB winds) are preferentially retained in the ISM as compared to those from higher energy events (e.g.
+SNe).
+The degree to which this is true likely depends upon global galaxy properties such as star formation rate, dark matter potential well, and gas geometry.
+
+\item Likewise, metals originating in AGB winds are less well mixed in the ISM compared to metals injected through SNe, with spreads of over 1 dex in cold gas, as compared to 
+%mm [missing text??]
+   {\bf [what?]}
+
+\item Metal distributions exhibit positive skew, such that the mean metal fraction can be anywhere from 0.1 to 1.0 dex above the median metal fraction.
+Simple chemical evolution models, which generally follow the mean abundance,
+%mm that are unable to 
+    and thus can not
+account for complex metal mixing physics, are likely biased towards higher enrichment values.
+
+\end{itemize}
+
+%mm [you argued above that the wind results would NOT necessarily be general.
+I'm not sure I like the formulation about entrainment of the ambient ISM, though.] We expect these results to be general for more massive galaxies and galaxy properties.
+However, it may be the case that metals couple more uniformly to galactic winds in more massive galaxies as wind driving occurs increasingly through entrainment of the ambient ISM rather than the ejection of individual enrichment events.
+This warrants further examination.
+But interpreting these results for low mass dwarf galaxies
+    Extending these results to low-mass dwarf galaxies in general, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
+% Removed as-per Benoit's suggestion:
+% , and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements
+
+%\section{Things to cite}
+%Hou, Yu, Lu 2014: Need to read closer, but CE model playing around with SN energy feedback effectiveness finds that weaker feedback leads to more metal enrichment, higher FB, lower metallicities.
+Suggestion of importance of FB driving CE.
+
+\acknowledgments
 A.E.
@@
 M.-M.M.L.
-was partly funded by NASA  grant NNX14AP27G.
+was partly funded by NASA  grant NNX14AP27G and by NSF grant AST18-15461.
+B.C.
+acknowledges support from the ERC Consolidator Grant (Hungary) funding scheme (project RADIOSTAR, G.A.
+n.
+724560) and from the National Science Foundation (USA) under grant No.
+PHY-1430152 (JINA Center for the Evolution of the Elements).
+\textbf{K.V.J....}.
+\textbf{B.O....}.
 We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute.
@@
 
-%\bibliographystyle{yahapj}
-\bibliographystyle{mnras}
+\facilities{Yeti, CCA cluster, Stampede, Pleiades}
+\software{Numpy, Enzo, yt, astropy}
+
+\bibliographystyle{yahapj}
 \bibliography{msbib}
@@
 
-\section{Gas Phases of the ISM}
-\label{appendix:phases}
-
-To aid in comparison to other works, we define our ISM phases here, as adopted and modified from \citet{Draine2011}, Table 1.3, and used consistently throughout this analysis.
-By construction, these phases are mutually exclusive.
-We take $f_{\rm H_2}$ to be the molecular hydrogen fraction of the total gas mass.
-
-\begin{enumerate}
-\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
-\item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
-\item Warm Neutral Medium (WNM): $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$
-\item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
-\item Molecular: $T < 10^2$~K, $f_{\rm H_2} > 0.5$
-\end{enumerate}
-
-\section{Stellar Radiation Properties}
-\label{appendix:radiation}
-We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Fig.~\ref{fig:stellar radiation properties} we plot these properties.
-We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
-This requires two factors for each radiation type, one for low mass and one for high mass stars.
-We use the following multiplicative factors to adjust the black body spectrum for HI and HeI ionizing radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
-We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
-
-The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid.
-A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section.
-We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \url{http://www.pa.uky.edu/~verner/photo.html}}
-The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision.
-Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.
+\section{Density PDF}
+\label{appendix:density PDF}
+We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}.
+We show the mass-weighted PDF ($dm/Md\log n$) on the left, and the volume-weighted PDF ($dv/Vd\log n$) on the right.
+As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution.
+The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.
+The volume weighted PDF is much better described as a multi-component power law.
+The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities.
+These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.
+
+%mm [you could cut this if you want.]
+     It is worth noting that this PDF shows the rather small cold gas 
+     fraction found in these models in comparison to the Milky Way
+      ISM, where roughly half the mass is found in cold gas 
+      \citep{Ferriere2001}.
+Finally, \cite{Hopkins2013} suggests a different functional form for describing these PDFs across a range of idealized simulations, but it still may be insufficient to fully describe the density PDF in realistic galaxy simulations.
+Clearly, we are far from a general understanding of mass-weighted and volume-weighted density PDFs in the case of a turbulent, self-gravitating, multi-phase ISM.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.475\linewidth]{density_PDF.png}
+\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted.png}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr.
+The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
+\label{fig:density_pdf}
+\end{figure}
+
+\section{Resolution Comparison}
+We perform a resolution test to confirm that the key results of this study are convergent, at least qualitatively.
+Given the variations in star formation rate, feedback effectiveness, and stochasticity in our model, we do not expect exact numerical convergence in any one quantity.
+We conduct two lower resolution simulations with a maximum physical resolution of 3.6 pc and 7.2 pc.
+We refer the reader to Paper I for a previous comparison of these simulations to our fiducial run.
+In Figure~\ref{fig:resolution-phase} we demonstrate that O and Ba abundances behave qualitatively similar in our lower resolution runs as in our fiducial model.
+In both lower resolution runs O has a generally tighter distribution that narrows over time, while Ba is much less well mixed, in agreement with our fiducial simulation.
+The exact numerical values for these spreads are not convergent across simulations, but we do note significant variations in the exact SFH of these lower resolution runs could be driving these differences.
 
@@
 \centering
-\includegraphics[width=0.4\linewidth]{Q0}
-\includegraphics[width=0.4\linewidth]{Q1}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{L_FUV}
-\includegraphics[width=0.4\linewidth]{L_LW}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{E0}
-\includegraphics[width=0.4\linewidth]{E1}
-\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right).
-Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
-\label{fig:stellar radiation properties}
+\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study.png}
+\caption{Resolution comparison of two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.
+Compare to Figure~\ref{fig:phase-statistics}.}
+\label{fig:resolution-phase}
 \end{figure*}
 
-\setcounter{figure}{0}
-\section{Typical Gas Densities in Supernova Injection Regions}
-\label{appendix:SN}
-
-Modeling SN feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of SN feedback.
-Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time.
-However, physically consistent solutions have been developed \citep[e.g][]{Simpson2016} that inject a mixture of kinetic and thermal energy with a ratio that depends on resolution and local gas density.
-Overcooling becomes less important with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each SN.
-We take advantage of our high resolution and employ a simple thermal energy injection model for our SN feedback.
-We demonstrate how well this resolves our SNe in the comparison simulation presented in this work.
-
-The left panel of Fig.~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
-As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
-For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations.
-The right panel of Figure ~\ref{fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
-\begin{equation}
-R_{\rm PDS} = 
-\begin{cases}
-49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z \le 0.01 \\
-18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z \ge 0.01 \\
-\end{cases}
-\end{equation}
-where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$.
-\citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the SN explosion with thermal energy injection alone, assuming uniform density in the injection region.
-In practice, the injection region is never uniform.
-We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each SN.
-As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but up to 8.3\% are not well resolved and 2.0\% are completely unresolved (below a single cell width).
-In general, these are SN explosions from the most massive (i.e.
-most prompt) stars.
-We do not expect that resolving these SNe will dramatically alter our results.
-However, we note that using our feedback model at resolutions much less than a few parsecs will require implementing an different injection mechanism.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.4\linewidth]{sn_density_hist}
-\includegraphics[width=0.4\linewidth]{sn_radius_hist}
-\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation.
-{\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each SN assuming a uniform medium at either the peak or average density in the injection region.
-The vertical lines show one and 4.5 cell widths.
-This shows that a fraction of these SNe are certainly unresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
-\label{fig:SN histogram}
-\end{figure*}
-
-\setcounter{figure}{0}
-\section{Cooling and Heating Rates}
-\label{appendix:cooling}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
-\caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background.
-Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the uncorrected (i.e.
-optically thin) metal line cooling rates.
-The regimes where heating dominates are plotted with dashed lines for clarity.}
-\label{fig:cooling comparison}
-\end{figure*}
-
-The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with a self-shielding approximations.
-\citet{Hu2017} details this inconsistency: metal cooling rates computed under the assumption of an optically thin UV background overestimate the electron fraction in regimes where self-shielding is important ($-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$).
-This results in an artificially enhanced metal line cooling rate in regions of self-shielding.
-This can be a significant effect, particularly at higher metallicities.
-We demonstrate this in Fig.~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
-The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
-In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
-Fig.~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
-We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
-
-For densities where self-shielding is important, we computed \textsc{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
-In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud.
-We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UV background.
-These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}.
-In computing these tables we had to include the cosmic ray ionization that dominates in optically thick clouds.
-Without this effect, \textsc{Cloudy} becomes unstable in entirely neutral regions.
-We adopted a cosmic ray ionization rate of 10\% the Milky Way value, though we note that varying this from 1\% to 100\% the Milky Way value did not have an effect on the extracted metal line cooling rates.
-
-Finally, we note that the cooling and heating rates in our simulation will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
-The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which is not included in these diagrams.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_curve}
-\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}.
-The absolute value of the net cooling or heating
-rate is shown with solid lines.}
-\label{fig:cooling}
-\end{figure*}
-
-\setcounter{figure}{0}
-\section{H$^{-}$ Photodetachment}
-\label{appendix:H minus}
-\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations.
-Accounting for the photodetachment of H$_{-}$ from the stellar radiation field, which can dominate over the UVB,can be important for correctly modeling H$_2$ formation in low metallicity gas\citep{WolcottHaiman2012}.
-To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models\footnote{See the ``cooling_cell.py'' example here: https://grackle.readthedocs.io/en/grackle-3.1/Python.html} that iterates through the chemistry and cooling solvers with a constant density (10~cm$^{-3}$).
-In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background.
-As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate.
-In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left).
-A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.}
-
-\textbf{We follow up on the qualitative conclusions of these models by running four full-physics simulations, but with no star formation, at the four points starred in the diagram.
-These vary the radiation bands by factors of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}).
-Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9.
-Applying both scale factors gives a reduction of 7.9.}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{fH2.png}
-\caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation.
-Each model is held at a uniform density $n = 10$~cm$^{-3}$.
-Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor.
-Contours give factors of ten change in the H$_2$ fraction.}
-\label{fig:Grackle grid}
-\end{figure}
-
-\textbf{H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV.
-For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction.
-Although we demonstrate that the H$_2$ fraction is more sensitive to the Lyman-Werner radiation field in our simulations, this radiation is dominated by short-lived massive stars and thus subject to fluctuations.
-Particularly in periods of no star formation, the regulation of H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation.
-Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars.
-Doing so in our current model, applying an optically thin 1/r$^2$ field for each star, would be computationally challenging for the dramatic increase in the number of stars below 8~M$_{\odot}$, our current radiation mass threshold.}
-
-In addition, radiation from lower mass stars may be important in the is regime as the H$^{-}$ photodetachment threshold is low, or 0.76~eV. }
-
-\setcounter{figure}{0}
-\section{Resolution Study}
-\label{appendix:resolution_study}
-
-We demonstrate the effect of varying resolution in the evolution of our galaxy model in Fig.~\ref{fig:resolution_study}.
-We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines).
-The physics in each simulation remains the same with the exception of star formation, which employs a resolution-dependent density threshold.
-A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.
-As a result, the time at which star formation first occurs varies between the simulations, but we again define t = 0 as the time of first star formation in each simulation.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.33\linewidth]{sfr_resolution_study.png}
-\includegraphics[width=0.33\linewidth]{mass_evolution_resolution.png}
-\includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
-\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted).
-The line colors in the left panel are for better clarity between the SFRs.}
-\label{fig:resolution_study}
-\end{figure*}
-
-Fig.~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
-We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
-The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs.
-We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Fig.~\ref{fig:SN histogram}.
-However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
-
-Generally ineffective feedback leads to increased, not decreased, star formation rates.
-However, the lower resolution run has the lowest SFR.
-The source of this difference is likely related to the ability to resolve dense, cold gas in the lower resolution simulations.
-In particular, the low resolution simulation clearly is unable to resolve the densities at which gas-phase H$_2$ formation becomes efficient, leading to significantly lower H$_2$ fractions (middle panel) and lower cooling rates.
-In addition, whatever H$_2$ does form at these lower resolutions exists at lower gas densities than in our fiducial run, and is less well protected by self-shielding effects.
-This is shown clearly in the significant plummet in the H$_2$ mass during the phase of first star formation that is less severe in our fiducial run.
-In this low metallicity regime, where H$_2$ is an important coolant, the ability to resolve the densities responsible for H$_2$ formation and self-shielding is important.
-
-Theses differences in densities are shown clearly by comparing Fig.~\ref{fig:phase} with Fig.~\ref{fig:phase_resolution}.
-Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.
-In the 7.2~pc run, the gas phases are notably less distinct, with gas more evenly smoothed out in the multi-phase region between cold, dense gas and warm, ionized gas.
-We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature ceiling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{3pc_phase.png}
-\includegraphics[width=0.475\linewidth]{6pc_phase.png}
-\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:phase}.}
-\label{fig:phase_resolution}
-\end{figure*}
-
-Finally, the metal retention fraction (right panel) between the fiducial and 3.6~pc runs are quite similar, but is significantly higher for the lowest resolution simulation.
-It is likely, however, that this is a result of the lower SFR in the 7.2~pc run and is not directly a resolution effect.
-This also affects the fraction of metals ejected outside the virial radius, with less metals being ejected in the lower resolution runs.
-
-\label{lastpage}
-
 \end{document}

### 2018-08-22 main.tex

@@
 This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
-%Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows. 
-Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018}
+Recent hydrodynamics simulations have employed parametric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017,Sarmento2018}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Escala2018, Armillotta2018}
 % KVJ: citations to high-redshift work in this area
-\textbf{and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.} Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.
+%\textbf{
+and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.
+%}
+Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.
 
@@
 Differences in metal distributions from ejecta in AGB stars, as compared to SNe, has been explored recently in \cite{KrumholzTing2018}, but has yet to be demonstrated in hydrodynamics simulations.
+Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations \citep[e.g.][]{Cote2018}.
 
 The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
-That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004,Muratov2017,Corlies2018}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}.
+That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004,Muratov2017,Corlies2018}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,Bordoloi2014,McQuinn2015}.
 If there are differences in metal coupling to the ISM, this could potentially impact how metals are driven out of galaxies through galactic winds.
@@
 % KVJ asked to bring up this area of research and emphasize how it is lacking theoretical input
-\textbf{One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Ting2012, Hogg2016,Jofre2017,Price-Jones2018}.
+%\textbf{
+One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Freeman2002,Ting2012, Hogg2016,Jofre2017,Price-Jones2018}.
 Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations.
-Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.}
+Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.
 
@@
 Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging.
-[list examples of modelling problems].
+%[list examples of modeling problems]. 
 These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study.
@@
 We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver.
-We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc.
+We use a 128$^{3}$ base grid with outflow boundary conditions measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 9 levels of refinement, for a maximum spatial resolution of 1.8~pc.
 Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas or 2) a cell's local Jeans length becomes resolved by less than eight cells.
@@
 Stars with $3 < M_{*} < 8$ are tracked after their death as possible Type Ia SN progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
-Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et.
+Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, Slemer et.
 al.
-in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia SNe.
+in prep for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia SNe.
 
 \paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
-We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$.
+We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an exponential profile with a metal mass fraction of $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$~M$_{\odot}$.
 The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
@@
 This galaxy has an average star formation rate of $1.2~\times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
-The galaxy exhibits strong, feedback driven outflows that eject a significant amount of gas and metals from the galaxy.
-The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$.
-These winds eject 95\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.
+The galaxy exhibits strong, feedback-driven outflows \citep{Emerick2018b} that eject a significant amount of gas and metals from the galaxy.
+The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$, where $\eta$ is defined as the mass outflow rate in through a 0.1~$R_{\rm vir}$ annulus centered at 0.25~R$_{\rm vir}$ divided by the 100~Myr averaged SFR.
+These winds eject 96\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.
 
@@
 \includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
-\caption{The fraction of each metal species in the full simulation box contained in the halo, gas in the galaxy disk, and stars (top), and the fraction of species within the disk alone in each phase of the ISM (bottom).
+\caption{Top: The mass fraction of each metal species in the \textit{full simulation box} contained in the halo, gas in the galaxy disk, and stars.
+Bottom: The mass fraction of species within \textit{the disk} alone in each phase of the ISM (bottom).
 The leftmost bar in each plot shows the sum of all metals.}
 \label{fig:species_fractions}
-\end{figure}
+\end{figure*}
 
@@
 \includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
-\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (blue), WNM (green), WIM (purple), HIM (red), and all the gas in the ISM (black).
+\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black).
 For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
@@
 If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time  $\tau_{\rm mix}$ this gas will have mixed with an equal amount of primordial gas.
-\textbf{At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.} This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
-\textbf{The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.}
+At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$.
+Then, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.
+This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
+The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.
 
-\textbf{Thus, if the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous distribution $p(t,Z)$
+Thus, if the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous distribution $p(t,Z)$
 %mm , or $p(Z)$, 
-of these many events will be a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.}
+of these many events will be $\delta(Z_{\rm o})$ plus a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.
 % and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
@@
 This will produce a turnover at the low $Z$ limit of $p(Z)$.
-The low-turnover limit is produced by diffusion from many different sources, and is thus an additive process, which, as we noted above, tends to produce log-normal distributions.
+The low-turnover limit is produced by diffusion from many different sources, and is thus a multiplicative process, which, as we noted above, tends to produce log-normal distributions.
 %mm [additive vs multiplicative]
-   {\bf [According to Section~\ref{sec:log-normal}, MULTIPLICATIVE processes produce log-normals. Additive processes produce power-laws.  However, see Mouri (2013) for a possible counterexample...]}
+   %{\bf [According to Section~\ref{sec:log-normal}, MULTIPLICATIVE processes produce log-normals. Additive processes produce power-laws.  However, see Mouri (2013) for a possible counterexample...]}
 The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.
@@
 
-Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012}.
+Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012,Sarmento2017,Sarmento2018}.
 Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
@@
 This model was run using \textsc{SYGMA} \citep{Ritter2017}.
-As shown, metal enrichment from AGB winds only begins to dominate for
-%mm a given species at 
-    any elements after 
-$\sim$ 100 Myr. This includes N and Ba, which we follow in our simulations, but this 
-%mm plot indicates
-    model predicts 
-that Ag and Pb 
-%mm should 
-     will
-show similar bahavior.
+As shown, metal enrichment from AGB winds only begins to dominate for any elements after $\sim$ 100 Myr.
+This includes N and Ba, which we follow in our simulations, but this model predicts that Ag and Pb will show similar behavior.
 It takes over a gigayear for C to be dominated by AGB wind ejecta, which is the case for many of the elements shown.
@@
 In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star-forming gas in our simulations.
-This could be used to help disentangle sources of scatter in observed stellar abundance, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
-If the
-%mm star-forming gas in our simulations can also be well-fit by a log-normal + power-law PDF
-        metal mass fractions in star-forming gas in our simulations 
-        can also be well fit by log-normal + power-law PDFs,
-and if we can parameterize their evolution as functions of global galaxy properties, this 
-%mm can 
-    could
-be used as a powerful 
-%mm and analytic 
-tool for modeling stellar abundance patterns in semi-analytic models.
+This could be used to help disentangle sources of scatter in observed stellar abundances, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
+If the metal mass fractions in star-forming gas in our simulations can also be well fit by log-normal + power-law PDFs, and if we can parameterize their evolution as functions of global galaxy properties, this could be used as a powerful tool for modeling stellar abundance patterns in semi-analytic models.
 This would be a physically motivated way to account for both the intrinsic spread in stellar abundances due to inhomogeneities in the ISM and variations in mixing for different metal species.
@@
 %KVJ suggested emphasizing that there is much more potential in this work / work like this by examining more dimensions
-\textbf{We emphasize that this study focuses on each chemical dimension independently, as a means to first understand galactic chemical enrichment in the simplest possible framework.
+We emphasize that this study focuses on each chemical dimension independently, as a means to first understand galactic chemical enrichment in the simplest possible framework.
 However, the cross-correlation of multiple metal fractions and abundance ratios is the most useful in revealing key processes in galactic chemodynamics.
-A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiements.
-We will examine this more complicated multi-dimensional space with these
-%mm simulations 
-   numerical methods
-in future work.}
+A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiments.
+We will examine this more complicated multi-dimensional space with these numerical methods in future work.
 
@@
 \includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
-\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the
-%mm
-    time 
-within 1~Myr (our time resolution) of each star's formation time. The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
+\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the time within 1~Myr (our time resolution) of each star's formation time.
+The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
 \label{fig:stars}
@@
 With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
-\textbf{We anticipate three potential regimes of metal retention,
-%mm related directly to 
-    depending on
-dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB 
-%mm
-    stars 
-and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.}.
+We anticipate three potential regimes of metal retention, depending on dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB stars and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.
 If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
@@
 
-%\subsection{Extra things I could discuss:}
-%\textit{Things to maybe}
-%\begin{itemize}
-%\item Observed N/O in stellar abundances exhibits large spreads at low metallicity.
-Argument has been that this is driven by timescale differences in AGB vs.
-massive star nucleosynthesis.
-However, our results would predict that N/O have a large spread due to mixing efficiency diffein rences between AGB winds and SNe.
-%\end{itemize}
-
 \section{Conclusions}
 \label{sec:conclusions}
-%mm For the first time we 
 We present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
-This high resolution simulation, coupled with our star-by-star modelling of stellar nucleosynthetic yields, has allowed us to analyze
-%mm
-      for the first time
-how individual metal species couple to the ISM and galactic wind of this galaxy.
-We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, or core collapse SNe)
-%mm , and Type Ia SNe).  [I'm inclined to leave them out as we really didn't model their influence]
-This difference is most significant in our model between elements ejected predominately by AGB winds and those ejected predominantly by core-collapse SNe. In addition, we find 
-%mm for the first time 
-    the novel result
-that the mass fraction PDFs of each metal in the ISM can be described using an analytic piecewise log-normal + power-law PDF.
+This high resolution simulation, coupled with our star-by-star modeling of stellar nucleosynthetic yields, has allowed us to analyze for the first time how individual metal species couple to the ISM and galactic wind of this galaxy.
+
+We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, or core collapse SNe).
+This difference is most significant, in our model, between elements ejected predominately by AGB winds and those ejected predominantly by core-collapse SNe.
+In addition, we find the novel result that the mass fraction PDFs of each metal in the ISM can be described using an analytic piecewise log-normal + power-law PDF.
 The properties of these PDFs vary with both ISM phase and metal species, again driven mostly by differences in enrichment sources.
@@
 
-\item Power-law tails 
-%mm in 
-   on log-normal 
-metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
+\item Power-law tails on log-normal metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
 
-\item Hotter phases have metal fraction PDFs that are more enriched, with significant power-law tails as compared to cold phases, which have a more %mm dominant log-normal structure. 
-   prominent log-normal component.
-The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling into dense gas. 
-% missing text???????????
+\item Hotter phases have metal fraction PDFs that are more enriched, with significant power-law tails as compared to cold phases, which have a more prominent log-normal component.
+The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling and/or mixing into denser gas.
 
@@
 
-\item Likewise, metals originating in AGB winds are less well mixed in the ISM compared to metals injected through SNe, with spreads of over 1 dex in cold gas, as compared to 
-%mm [missing text??]
-   {\bf [what?]}
+\item Likewise, metals originating in AGB winds are less well mixed in the ISM, with spreads of over 1 dex in cold gas, as compared to metals injected through SNe, with spreads of about 0.5~dex
 
 \item Metal distributions exhibit positive skew, such that the mean metal fraction can be anywhere from 0.1 to 1.0 dex above the median metal fraction.
-Simple chemical evolution models, which generally follow the mean abundance,
-%mm that are unable to 
-    and thus can not
-account for complex metal mixing physics, are likely biased towards higher enrichment values.
+Simple chemical evolution models, which generally follow the mean abundance, and thus can not account for complex metal mixing physics, are likely biased towards higher enrichment values.
 
@@
 But interpreting these results for low mass dwarf galaxies
-    Extending these results to low-mass dwarf galaxies in general, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
+    Extending these results to low-mass dwarf galaxies in general, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements released through SNe and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
 % Removed as-per Benoit's suggestion:
 % , and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements
-
-%\section{Things to cite}
-%Hou, Yu, Lu 2014: Need to read closer, but CE model playing around with SN energy feedback effectiveness finds that weaker feedback leads to more metal enrichment, higher FB, lower metallicities.
-Suggestion of importance of FB driving CE.
 

### 2018-08-24 ms.tex
Update on Overleaf.
added a grant number

@@
 \author{Mordecai-Mark Mac Low}
-%mm [I've been asked to use my Columbia affiliation when working with CU students]
 \affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}
@@
 Models typically include energy injection from supernovae as the dominant form of stellar feedback, often in some form of sub-grid recipe.
-However, it has been recently suggested that pre-SN feedback, from either stellar winds or stellar radiation, is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM).
-Following stellar winds and ionizing radiation is computationally challenging, so many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation.
-In this work we use high resolution simulations (1.8~pc) of an isolated dwarf galaxy with detailed stellar feedback tracked on a star-by-star basis.
+However, it has been recently suggested that pre-SN feedback (stellar winds or radiation) is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM).
+However, following these processes is computationally challenging,
+%Following stellar winds and ionizing radiation is computationally challenging, 
+so many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation.
+In this work we examine high resolution simulations (1.8~pc) of an isolated dwarf galaxy with detailed stellar feedback tracked on a star-by-star basis.
 By following stellar ionizing radiation with an adaptive ray-tracing radiative transfer method, we test its importance in regulating star formation and driving outflows in this galaxy.
-We find that including ionizing radiation reduces the star formation rate by over a factor of 5, and is necessary in creating the ISM conditions needed for supernovae to drive significant outflows.
-In addition, we find that a localized approximation for radiation feedback is sufficient to regulate the star formation rate on short timescales, but is unable to drive the same outflows as in our fiducial model.
-Short and long range radiation effects are both important in driving the evolution of our modeled galaxy.
+We find that including ionizing radiation reduces the star formation rate (SFR) by over a factor of 5, and is necessary in creating the ISM conditions needed for supernovae to drive significant outflows.
+We find that a localized approximation for radiation feedback is sufficient to regulate the SFR on short timescales, but is unable to drive significant outflows.
+Short and long range radiation effects are both important in driving the evolution of our \textbf{low-metallicity, low-mass dwarf galaxy.
+Generalization of these results to more massive galaxies would be a valuable avenue of future research.}
 \end{abstract}
@@
 Rays begin on HEALPix refinement level 2, with a maximum refinement level of 13.
-We include radiation pressure on hydrogen, but do not investigate its importance in this work \citep[see][]{WiseAbel2012}.
+We include radiation pressure on hydrogen, but do not investigate its importance in this work \citep[see][ and references therein]{Krumholz2018}.
 
@@
 Each of our three simulations is identical up until the formation of the first star particles.\footnote{We note that the stars from the very first star formation event in each run (21 star particles with a total mass of 114 M$_{\odot}$) are the same.
-Of these, one particle emits ionizing radiation ($M_* > 8 $~M$_{\odot}$).}
+Of these, one particle emits ionizing radiation ($M_* > 8 $~M$_{\odot}$).
+\textbf{The sampled stellar masses differ across runs after this point.
+Stochastic effects from differences in IMF sampling may be important in the regime of low mass, low SFR dwarf galaxies.
+Multiple re-simulations of identical initial conditions may result in significant scatter in their final properties \citep{Keller2018}.
+We find our main conclusions are likely to be insensitive to these stochastic variations, as we find that the total radiation output across multiple re-samplings of a fixed star formation history is small after the IMF is fully sampled ($<50$~Myr).}}
+
+\textbf{As shown in Paper I, the maximum densities reached in these simulations is below 10$^{3}$~cm$^{-3}$.
+Our inability to resolve the high densities in star forming regions ($\sim 10^5$~cm$^{-3}$) means that we likely underestimate initial photon absorption and overestimate the initial long-range effects of newly formed stars.
+However, in the Milky Way, newly formed O stars have been observed to spend no more than  10 -- 20\% of their main sequence lifetimes embedded in ultracompact HII regions within dense molecular clouds \citep{WoodChurchwell1989}.
+This short dispersal timescale is confirmed by high resolution simulations of massive star formation \citep[e.g.][]{Peters2010,Dale2014,Kim2018}.
+Therefore, we do not consider our neglect of this phase to be likely to lead to substantial errors at the galactic scale.}
 
@@
 The driver of these differences is clear in the right hand panel.
-Our fiducial run loses a factor of $\sim 2$ more total gas and HI mass (black and blue lines) as compared to the shortrad simulation.
+Our fiducial run loses a factor of $\sim 2$ more total gas and HI mass (orange and blue lines) as compared to the shortrad simulation.
 Clearly, galactic winds and outflows are much more effective in with full accounting of stellar ionizing radiation feedback.
@@
 Modeling only local stellar ionizing feedback is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
-To explore the cause of this difference we compare in Figure~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See https://youtu.be/r1nEW6Yu3xI for a movie of this comparison.}
+To explore the cause of this difference we compare in Figure~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.
 
@@
 \caption{Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run.
-Each panel is 4 kpc x 4 kpc.}
+Each panel is 4 kpc x 4 kpc.
+\textbf{The full movie of this evolution is included for further clarification of the comparison between this figure and Fig.~\ref{fig:panel2}}}
 \label{fig:panel1}
@@
 
+\textbf{These results show that long-range ionization effects are an important consideration in models of stellar feedback.
+However, it warrants further study as to how much this effect can be accounted for without resorting to full radiative transfer calculations.
+Approximate, Stromgren-like feedback models which allow for ionization far from a single source \citep[e.x.][]{Hopkins2018} may be sufficient to capture the effects shown here.
+Fully localized methods, or methods which set a maximum for the ionization radius may underestimate galactic wind properties in dwarf galaxies.
+However, both methods are mass biased \citep[see the discussion in ][]{Hu2017}, preferentially over-ionizing dense gas that would otherwise be missed by photons leaking through channels carved through lower-density gas.
+These remaining uncertainties motivate a continued examination of the feedback prescriptions adopted in high resolution simulations of galaxy evolution.}
+
 \section{Conclusion}  \label{sec:conclusion}
@@
 M.-M.M.L.
-was partly funded by NASA  grant NNX14AP27G.
+was partly funded by NASA  grant NNX14AP27G and NSF grant AST18-15461.
 We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute.
@@
 
+\software{astropy \citep{astropy} matplotlib \citep{matplotlib}, Numpy \citep{numpy}, SciPy \citep{scipy}, IPython \citep{Ipython}, yt \citep{yt}, Enzo \citep{Enzo2014}, Grackle \citep{GrackleMethod}, CLOUDY \citep{cloudy}, HDF5}
+
 \bibliography{msbib}

### 2018-08-24 ms.tex
removed one word from asbtract

@@
 Models typically include energy injection from supernovae as the dominant form of stellar feedback, often in some form of sub-grid recipe.
-However, it has been recently suggested that pre-SN feedback (stellar winds or radiation) is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM).
+However, it has been recently suggested that pre-SN feedback (stellar winds / radiation) is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM).
 However, following these processes is computationally challenging,

### 2018-08-24 main.tex
reference update. typos.

--- 2018-08-20 main.tex
@@
 However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
-Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
+Although more than half of these metals are expected to eventually re-accrete \citep{Christensen2016,Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
 
@@
 \label{appendix:H minus}
-%\textbf{This section is new:}
 
 \textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations.
-Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB,
-%mm ca 
-    can 
-be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}.
-To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https:\/\/grackle.readthedocs.io\/en\/grackle-3.1\/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) for 200~Myr.
+Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, can be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}.
+Our current model does not include this contribution.
+To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https://grackle.readthedocs.io/en/latest/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) and initial temperature of 10$^{4}$~K for 200~Myr.
 In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background.
@@
 Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9.
-Applying both scale factors gives a reduction of 7.9.}
+Applying both scale factors gives a reduction of 7.9.
+Thus, we see that the difference between the more realistic case in which both rates increase by the same factor, and the case assumed in the simulations, is only about 20\%.}
 
@@
 For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction.
-Although we demonstrate that the H$_2$ fraction is more sensitive to the Lyman-Werner radiation field in our simulations, this radiation is dominated by short-lived massive stars and thus subject to fluctuations.
-Particularly in periods of no star formation, the regulation of H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation.
+The Lyman-Werner radiation field is dominated by short-lived massive stars, with some contribution from older stars up to a few hundred Myr, and is thus subject to significant fluctuations, particularly in periods of no star formation.
+During these times, H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation.
 Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars.
-Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked.
-}
+Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked.}
+
+\textbf{As emphasized in Section~\ref{sec:molecular gas content}, further work modeling low-metallicity dwarf galaxies with a more detailed chemistry model would be useful to clarify the role of various competing phenomena in driving the molecular properties of these galaxies.}
 

### 2018-09-04 ms.tex
removed one word from asbtract
typo and acknowledgement fix

--- 2018-08-24 ms.tex
@@
 %
-Effective stellar feedback is used in models of galaxy formation to regulate star formation and drive realistic galaxy evolution.
+Effective stellar feedback is used in models of galaxy formation to 
+%regulate star formation and 
+drive realistic galaxy evolution.
 Models typically include energy injection from supernovae as the dominant form of stellar feedback, often in some form of sub-grid recipe.
@@
 However, it warrants further study as to how much this effect can be accounted for without resorting to full radiative transfer calculations.
-Approximate, Stromgren-like feedback models which allow for ionization far from a single source \citep[e.x.][]{Hopkins2018} may be sufficient to capture the effects shown here.
+Approximate, Str{\"o}mgren-like feedback models which allow for ionization far from a single source \citep[e.g.][]{Hopkins2018} may be sufficient to capture the effects shown here.
 Fully localized methods, or methods which set a maximum for the ionization radius may underestimate galactic wind properties in dwarf galaxies.
-However, both methods are mass biased \citep[see the discussion in ][]{Hu2017}, preferentially over-ionizing dense gas that would otherwise be missed by photons leaking through channels carved through lower-density gas.
+In addition, both methods are mass biased \citep[see the discussion in ][]{Hu2017}, preferentially over-ionizing dense gas that would otherwise be missed by photons leaking through channels carved through lower-density gas.
 These remaining uncertainties motivate a continued examination of the feedback prescriptions adopted in high resolution simulations of galaxy evolution.}
@@
 G.L.B.
-is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
+acknowledges support from NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
 M.-M.M.L.

### 2018-09-11 main.tex
removed bold changes from last revision. draft of changes for this final revision

@@
 Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row).
-Each individual main sequence star particle is shown in the number density projections as a single black dot.}
+Each individual main sequence star particle is shown in the number density projections as a single white dot.}
 \label{fig:panel_x}
@@
 
-\textbf{As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations.
+As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations.
 Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, can be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}.
@@
 In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left).
-A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.}
-
-\textbf{We follow up on the qualitative conclusions of these models by running four full-physics simulations, but with no star formation, at the four points starred in the diagram.
+A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.
+
+We follow up on the qualitative conclusions of these models by running four \textbf{hydrodynamics} simulations, but with no star formation, at the four points starred in the diagram.
 These vary the radiation bands by factors of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}).
@@
 Applying both scale factors gives a reduction of 7.9.
-Thus, we see that the difference between the more realistic case in which both rates increase by the same factor, and the case assumed in the simulations, is only about 20\%.}
+Thus, we see that the difference between the more realistic case in which both rates increase by the same factor, and the case assumed in the simulations, is only about 20\%.
 
@@
 
-\textbf{H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV.
+H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV.
 For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction.
@@
 Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars.
-Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked.}
-
-\textbf{As emphasized in Section~\ref{sec:molecular gas content}, further work modeling low-metallicity dwarf galaxies with a more detailed chemistry model would be useful to clarify the role of various competing phenomena in driving the molecular properties of these galaxies.}
+Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked.
+
+\textbf{Although the lack of star formation in these models produced qualitatively different galaxy properties, these represent simulations with maximal H$_2$ formation.
+We demonstrate that, even in this case, there is not a dramatic change in the total H$_2$ formation and that the effect of varying the H- photodetachment rate is sub-dominant to other factors.
+Therefore, we do not expect that ignoring this component of the stellar radiation field to have a significant dynamical impact on our galaxy evolution.}
+
+As emphasized in Section~\ref{sec:molecular gas content}, further work modeling low-metallicity dwarf galaxies with a more detailed chemistry model would be useful to clarify the role of various competing phenomena in driving the molecular properties of these galaxies.
 

### 2018-09-13 main.tex
revisions 3

@@
 
-We follow up on the qualitative conclusions of these models by running four \textbf{hydrodynamics} simulations, but with no star formation, at the four points starred in the diagram.
-These vary the radiation bands by factors of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}).
+We follow up on the qualitative conclusions of these models by running four simulations at the four points in the diagram.
+\textbf{These runs have identical initial conditions, SNe driving, cooling, heating, and chemistry as our fiducial simulation, but with no star formation.} In each, we vary the radiation band by a factor of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}).
 Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9.
@@
 Thus, we see that the difference between the more realistic case in which both rates increase by the same factor, and the case assumed in the simulations, is only about 20\%.
+
+\textbf{Although the lack of star formation in these models produces qualitatively different galaxy properties, the point of these simulations is to be maximal models of H$_2$ formation.
+We demonstrate that, even in this case, there is not a dramatic change in the total H$_2$ formation and that the effect of varying the H- photodetachment rate is sub-dominant to other factors.
+Therefore, we do not expect that ignoring this component of the stellar radiation field will have a significant dynamical impact on our galaxy evolution.}
 
@@
 
-\textbf{Although the lack of star formation in these models produced qualitatively different galaxy properties, these represent simulations with maximal H$_2$ formation.
-We demonstrate that, even in this case, there is not a dramatic change in the total H$_2$ formation and that the effect of varying the H- photodetachment rate is sub-dominant to other factors.
-Therefore, we do not expect that ignoring this component of the stellar radiation field to have a significant dynamical impact on our galaxy evolution.}
-
 As emphasized in Section~\ref{sec:molecular gas content}, further work modeling low-metallicity dwarf galaxies with a more detailed chemistry model would be useful to clarify the role of various competing phenomena in driving the molecular properties of these galaxies.

### 2018-09-18 main.tex
updating references with published versions

@@
 Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
-Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017b, KrumholzTing2018}.
+Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2018, KrumholzTing2018}.
 Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
@@
 At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.
-Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2017b}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
+Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2018}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
 The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
@@
 However, the importance of multiple scattering is still unclear.
-Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013a,Reissl2017,Wibking2018}.
+Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013a,Krumholz2018,Reissl2018,Wibking2018}.
 Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.

### 2018-09-18 main.tex
mordecai comments

@@
 We follow up on the qualitative conclusions of these models by running four simulations at the four points in the diagram.
-\textbf{These runs have identical initial conditions, SNe driving, cooling, heating, and chemistry as our fiducial simulation, but with no star formation.} In each, we vary the radiation band by a factor of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}).
+\textbf{These runs have identical initial conditions, random SN driving, cooling, heating, and chemistry as our fiducial simulation, but with no star formation.} We vary the Lyman-Werner radiation and the H$^{-}$ photodetachment rate by the factors shown, which are comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}).
 Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9.
@@
 
-\textbf{Although the lack of star formation in these models produces qualitatively different galaxy properties, the point of these simulations is to be maximal models of H$_2$ formation.
+\textbf{Although the replacement of star formation by random SNe in these models produces qualitatively different galaxy properties, the point of these simulations is to be maximal models of H$_2$ formation.
 We demonstrate that, even in this case, there is not a dramatic change in the total H$_2$ formation and that the effect of varying the H- photodetachment rate is sub-dominant to other factors.

### 2018-09-18 main.tex
final edits and reference updates

@@
 This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
+\textbf{In \cite{Emerick2018b} we investigate the importance of ionizing radiation in regulating star formation and driving outflows in our galaxy.
+In \cite{Emerick2018c} we explore how individual metal species mix within the ISM and are ejected via galactic winds.}
+
 We describe each mode of our multi-channel feedback 
 in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.
-
 Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.
@@
 This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
-A more detailed analysis is beyond the scope of this work, but we investigate this in detail in Emerick et.
-al.
-(in prep.).
+A more detailed analysis is beyond the scope of this work, but we investigate this in \textbf{detail in \cite{Emerick2018c}}.
 
@@
 However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
-Although more than half of these metals are expected to eventually re-accrete \citep{Christensen2016,Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
+Although more than half of these metals are expected to eventually re-accrete \citep{Christensen2016,Christensen2018,Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
 
@@
 Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}.
-Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
+Extending the lifetimes of these stars combined with accounting for binary effects that change the luminosities of these stars \citep{Gotberg2017,Gotberg2018} could increase the importance of radiation feedback; however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
 
@@
 It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
-The importance of radiation feedback in our model will be investigated in a future work.
-(See Figs.~\ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
+The importance of radiation feedback in our model is investigated in more \textbf{detail in \cite{Emerick2018b}.} (See Figs.~\ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
 
@@
 SNe), as suggested by \cite{KrumholzTing2018}.
-This will be explored in more detail in future work (Emerick et.
-al.
-\textit{in prep.}).
+This is explored in more \textbf{detail in \citep{Emerick2018c}.}
 \end{enumerate}

### 2018-09-19 ms.tex
final edits for acceptance

@@
 %
-Effective stellar feedback is used in models of galaxy formation to 
-%regulate star formation and 
-drive realistic galaxy evolution.
+Effective stellar feedback is used in models of galaxy formation to drive realistic galaxy evolution.
 Models typically include energy injection from supernovae as the dominant form of stellar feedback, often in some form of sub-grid recipe.
 However, it has been recently suggested that pre-SN feedback (stellar winds or radiation) is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM).
-However, following these processes is computationally challenging,
-%Following stellar winds and ionizing radiation is computationally challenging, 
-so many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation.
+Following these processes is computationally challenging, so many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation.
 In this work we examine high resolution simulations (1.8~pc) of an isolated dwarf galaxy with detailed stellar feedback tracked on a star-by-star basis.
 By following stellar ionizing radiation with an adaptive ray-tracing radiative transfer method, we test its importance in regulating star formation and driving outflows in this galaxy.
-We find that including ionizing radiation reduces the star formation rate (SFR) by over a factor of 5, and is necessary in creating the ISM conditions needed for supernovae to drive significant outflows.
-We find that a localized approximation for radiation feedback is sufficient to regulate the SFR on short timescales, but is unable to drive significant outflows.
-Short and long range radiation effects are both important in driving the evolution of our \textbf{low-metallicity, low-mass dwarf galaxy.
-Generalization of these results to more massive galaxies would be a valuable avenue of future research.}
+We find that including ionizing radiation reduces the star formation rate (SFR) by over a factor of 5, and is necessary to produce the ISM conditions needed for supernovae to drive significant outflows.
+We find that a localized approximation for radiation feedback is sufficient to regulate the SFR on short timescales, but does not allow significant outflows.
+Short and long range radiation effects are both important in driving the evolution of our low-metallicity, low-mass dwarf galaxy.
+Generalizing these results to more massive galaxies would be a valuable avenue of future research.
 \end{abstract}
@@
 Of these, one particle emits ionizing radiation ($M_* > 8 $~M$_{\odot}$).
-\textbf{The sampled stellar masses differ across runs after this point.
+The sampled stellar masses differ across runs after this point.
 Stochastic effects from differences in IMF sampling may be important in the regime of low mass, low SFR dwarf galaxies.
 Multiple re-simulations of identical initial conditions may result in significant scatter in their final properties \citep{Keller2018}.
-We find our main conclusions are likely to be insensitive to these stochastic variations, as we find that the total radiation output across multiple re-samplings of a fixed star formation history is small after the IMF is fully sampled ($<50$~Myr).}}
+We find our main conclusions are likely to be insensitive to these stochastic variations, as we find that the total radiation output across multiple re-samplings of a fixed star formation history is small after the IMF is fully sampled.}
 
-\textbf{As shown in Paper I, the maximum densities reached in these simulations is below 10$^{3}$~cm$^{-3}$.
+As shown in Paper I, the maximum densities reached in these simulations is below 10$^{3}$~cm$^{-3}$.
 Our inability to resolve the high densities in star forming regions ($\sim 10^5$~cm$^{-3}$) means that we likely underestimate initial photon absorption and overestimate the initial long-range effects of newly formed stars.
 However, in the Milky Way, newly formed O stars have been observed to spend no more than  10 -- 20\% of their main sequence lifetimes embedded in ultracompact HII regions within dense molecular clouds \citep{WoodChurchwell1989}.
-This short dispersal timescale is confirmed by high resolution simulations of massive star formation \citep[e.g.][]{Peters2010,Dale2014,Kim2018}.
-Therefore, we do not consider our neglect of this phase to be likely to lead to substantial errors at the galactic scale.}
+This short dispersal timescale agrees with high resolution simulations of massive star formation \citep[e.g.][]{Peters2010,Dale2014,Kim2018}.
+Therefore, we do not consider our neglect of this phase to be likely to lead to substantial errors at the galactic scale.
 
@@
 Each panel is 4 kpc x 4 kpc.
-\textbf{The full movie of this evolution is included for further clarification of the comparison between this figure and Fig.~\ref{fig:panel2}}}
+The full movie of this evolution is included for further clarification of the comparison between this figure and Fig.~\ref{fig:panel2}.}
 \label{fig:panel1}
@@
 
-\textbf{These results show that long-range ionization effects are an important consideration in models of stellar feedback.
-However, it warrants further study as to how much this effect can be accounted for without resorting to full radiative transfer calculations.
-Approximate, Str{\"o}mgren-like feedback models which allow for ionization far from a single source \citep[e.g.][]{Hopkins2018} may be sufficient to capture the effects shown here.
+These results show that long-range ionization effects are an important consideration in models of stellar feedback. However,
+further study is warranted of how this effect can be approximated without resorting to full radiative transfer calculations.
+Approximate, Str{\"o}mgren-like feedback models that allow for ionization far from a single source \citep[e.g.][]{Hopkins2018} may be sufficient to capture the effects shown here.
 Fully localized methods, or methods which set a maximum for the ionization radius may underestimate galactic wind properties in dwarf galaxies.
 In addition, both methods are mass biased \citep[see the discussion in ][]{Hu2017}, preferentially over-ionizing dense gas that would otherwise be missed by photons leaking through channels carved through lower-density gas.
-These remaining uncertainties motivate a continued examination of the feedback prescriptions adopted in high resolution simulations of galaxy evolution.}
+These remaining uncertainties motivate a continued examination of the feedback prescriptions adopted in high resolution simulations of galaxy evolution.
 
@@
 
-\software{astropy \citep{astropy} matplotlib \citep{matplotlib}, Numpy \citep{numpy}, SciPy \citep{scipy}, IPython \citep{Ipython}, yt \citep{yt}, Enzo \citep{Enzo2014}, Grackle \citep{GrackleMethod}, CLOUDY \citep{cloudy}, HDF5}
+\software{astropy \citep{astropy} matplotlib \citep{matplotlib}, Numpy \citep{numpy}, SciPy \citep{scipy}, IPython \citep{Ipython}, yt \citep{yt}, Enzo \citep{Enzo2014}, Grackle \citep{GrackleMethod}, CLOUDY \citep{cloudy}, HDF5 \citep{HDF5}}
 

### 2018-10-22 main.tex
Update on Overleaf.

--- 2018-09-18 main.tex
@@
 
-\label{firstpage}
-%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
-
-%\author{Andrew Emerick}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\author{Greg L. Bryan}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-%\author{Mordecai-Mark Mac Low}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-
-%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}
+\title{Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source}
+
+\author{Andrew Emerick}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+\author{Greg L. Bryan}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
+\author{Mordecai-Mark Mac Low}
+\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
+\author{Benoit C{\^o}t{\'e}}
+\affiliation{Konkoly Observatory, Research Centre for Astronomy and Earth Sciences, Hungarian Academy of Sciences, Konkoly Thege Miklos ut 15-17, H-1121 Budapest, Hungary}
+\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI 48824, USA}
+\affiliation{Joint Institute for Nuclear Astrophysics -- Center for the Evolution of the Elements, USA}
+\author{Kathryn V. Johnston}
+\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
+\author{Brian W. O'Shea}
+\affiliation{Department of Computational Mathematics, Science, and Engineering, Michigan State University, East Lansing, MI, 48824, USA}
+\affiliation{Department of Physics and Astronomy, Michigan State University, East Lansing, MI, 48824, USA}
+\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI, 48824, USA}
+\affiliation{Joint Institute for Nuclear Astrophysics -- Center for the Evolution of the Elements, USA}
 
 \begin{abstract}
-In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
-We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba.
-We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints.
-We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group, low-mass dwarf galaxy.
-We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship.
-Effective feedback drives outflows with a greater metallicity than the ISM, leading to low metal retention fractions consistent with observations.
-Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
+Using a high resolution simulation of an isolated dwarf galaxy, accounting for multi-channel
+stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy by galactic winds.
+For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal and power-law distribution.
+The PDF properties vary within each ISM phase.
+Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is predominately log-normal.
+In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (e.g.
+N and Ba) mix less efficiently than elements dominated by supernova enrichment (e.g.
+$\alpha$ elements and Fe).
+This result is driven by the differences in source energetics and source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
+Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but over 20\% of metals dominated by AGB enrichment are retained.
+In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread compared to elements synthesized in either core collapse or Type Ia supernovae.
+We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
 \end{abstract}
 
-\begin{keywords}
-Galaxy -- Hydrodynamics -- Simulation -- Feedback
-\end{keywords}
+\keywords{}
 
 \section{Introduction}
-%
-% AE removed below.. MM suggested  skipping both pars.
-%
-%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade.
-Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc.
-\citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses.
-On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM.
-This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}.
-See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.
-%
-%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution.
-In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense.
-In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships.
-For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.
-
-Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution.
-Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models.
-There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
-% editor asked us to reduce citation count here:{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
-These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .
-
-However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}.
-In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution.
-Mixing can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}.
-While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficiently high spatial resolution.
-Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}.
-Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2018, KrumholzTing2018}.
-Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of
-the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however.
-The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.
-
-Increasing physical resolution reduces reliance on sub-grid physics for mixing.
-However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}.
-Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations.
-This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$).
-At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles.
-Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2018}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}.
-The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.
-
-We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies.
-The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms.
-We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
-%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies.
-\citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies.
-Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar winds from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.
-We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar far ultra-violet (FUV) radiation, and Lyman-Werner dissociation from stellar radiation.
-
-Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime.
-This includes yields from massive and AGB stellar winds, and supernovae (SNe).
-In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars.
-This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.
-This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution.
-We describe each mode of our multi-channel feedback
-in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.
-
-Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.
-
+Understanding galactic chemical evolution for all metal species across galaxy mass scales remains one of the most challenging aspects of modeling galaxy evolution.
+One of the most pressing difficulties is a lack of understanding in exactly how metals propagate from their injection sites from stellar winds or supernovae (SNe) and mix through the phases of the interstellar medium (ISM) into star-forming gas.
+
+One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}.
+While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challenging.
+More complex models \citep[e.g.][]{SchonrichBinney2009,Pezzulli2016} employ multiple (usually radial) zones or follow multiple gas phases to attempt to account for these effects.
+How to properly account for multi-phase mixing, however, is still poorly understood.
+This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly.
+Recent hydrodynamics simulations have employed parametric models to account for unresolved sub-grid metal mixing \citep{PanScannapiecoScalo2013,Sarmento2017,Sarmento2018}, which plays an important role in determining the chemical properties of galaxies \citep[e.g.][]{Shen2010, Pilkington2012, Few2012, Brook2014, FengKrumholz2014, Armillotta2018, Escala2018, Rennehan2018}
+% KVJ: citations to high-redshift work in this area
+%\textbf{
+and the enrichment process and chemical signatures of the first stars \citep[e.g.][]{Jeon2015,Ritter2015,Smith2015}.
+%}
+Detailed hydrodynamics simulations incorporating a multi-phase ISM and detailed stellar feedback are required to understand the details of metal mixing and metal outflows in galaxies.
+
+In addition, it remains to be seen to what degree, if at all, metals of different enrichment origins (AGB winds, core collapse SNe, Type Ia SNe, neutron-star neutron-star mergers, etc.) may couple differently to the ISM.
+When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly.
+However, if metals do not behave uniformly in the ISM, if their mixing and ejection behavior depends directly upon the energetics and physical environment of their injection, then this assumption would need to be re-evaluated.
+Differences in metal distributions from ejecta in AGB stars, as compared to SNe, has been explored recently in \cite{KrumholzTing2018}, but has yet to be demonstrated in hydrodynamics simulations.
+Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations \citep[e.g.][]{Cote2018}.
+
+The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution.
+That dwarf galaxies efficiently pollute the circumgalactic medium and intergalactic medium (IGM) with metals has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004,Muratov2017,Corlies2018}, and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,Bordoloi2014,McQuinn2015}.
+If there are differences in metal coupling to the ISM, this could potentially impact how metals are driven out of galaxies through galactic winds.
+This has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
+However, examining this process has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
+%It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}.
+% Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations.
+However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.
+
+It is becoming increasingly valuable to develop a concrete theoretical understanding of galactic chemical evolution as a result of multiple, recent observational campaigns to probe detailed stellar abundances in our Milky Way and the Local Group, such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, and GALAH \citep{Buder2018}.
+Stellar abundances are directly imprinted with the enrichment pattern of their star-forming cloud, whose chemical properties are determined by the process of turbulent metal mixing in the ISM.
+The degree to which we can associate "chemically tagged" stars as co-eval depends directly upon our understanding of metal enrichment and metal mixing in the ISM.
+Furthermore, this understanding is critical for using these observations to further deduce properties of a galaxy's evolutionary history.
+% KVJ asked to bring up this area of research and emphasize how it is lacking theoretical input
+%\textbf{
+
+One key aspect of this work has been a significant effort to characterize the number of independent dimensions accessible by the multi-dimensional chemical abundances observed in these studies \citep[e.g][]{Freeman2002,Ting2012, Hogg2016,Jofre2017,Price-Jones2018}.
+Thus far, these studies have remained uninformed by hydrodynamics simulations and, conversely, these results cannot yet be used to constrain simulations.
+Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.
+\textbf{Recent work has suggested that low-mass dwarf galaxies are perhaps the best regime to begin understanding these processes \citep[e.g.][]{Bland-Hawthorn2010a,Bland-Hawthorn2010b,Karlsson2012,Webster2016}.
+This is advantageous, as their small physical size and low star formation rates makes conducting high resolution, hydrodynamics simulations of these systems computationally feasible.}
+
+In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}.
+The simulation discussed here was introduced in detail in \cite{Emerick2018} (hereafter Paper I).
+To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia SNe.
+This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below.
+We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species.
+We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.
+
+The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity.
+Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging.
+%[list examples of modeling problems]. 
+These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study.
+By focusing on a low mass dwarf galaxy, with small size and low star formation rate, we can capture detailed feedback and ISM physics at high resolution, while following individual stars.
+In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios, for two reasons.
+First, we would like to build our understanding of galactic chemical evolution from a fundamental level.
+Second, there is only a limited sample of gas-rich, star forming dwarf galaxies of this size that we can use for direct observational comparison, and it is computationally infeasible to simulate galaxies of easily observable size in as much detail as done here.
+This work will be the first of several attempting to bridge this gap.
+With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and physically motivated sub-grid physics models for lower resolution simulations of more massive galaxies.
+
+We summarize our methods and physics models in Section~\ref{sec:methods}.
+We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}.
+In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
+We discuss our results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusions}.
+
+% AE: Benoit suggested subsections instead of paragraph splits... play with this to see what looks best
 \section{Methods}
 \label{sec:methods}
-We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
-This allows us to follow star-by-star variations in feedback physics and stellar yields in detail.
-To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background.
-We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}).
-We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$).
-Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback.
-We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on HI.
-In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen.
-We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both.
-We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors.
-We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species.
-In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked.
-This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth.
-These methods are discussed in full detail below.
-
-\subsection{Hydrodynamics and Gravity}
-\label{sec:hydro}
-
-We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies.
-\texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions.
-We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick.
-Specifically, simulations presented here were conducted at changeset 7001d99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
-We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}).
-Self-gravity is computed with a multigrid Poisson solver.
-The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.
-
-We refine the mesh whenever the thermal Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc).
-At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation.
-\citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.
-
-We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}).
-Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
-However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse.
-A non-thermal pressure term is added to cells once their thermal Jeans length becomes unresolved.
-This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit.
-The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.
-
-Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas.
-These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution.
-At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr.
-We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$.
-These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions.
-This threshold decreases the required run-time by factors of a few.
-The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)
-
-\subsection{Chemistry and Cooling Physics}
-\label{sec:chemistry}
-
-We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset c2c0faf.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes.
-We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.
-We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
-However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}.
-For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
-
-As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
-As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
-Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}.
-To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.
-We have made these new tables public in the main \texttt{Grackle} repository.
-These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
-Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.
-
-\subsection{Star Formation Algorithm}
-\label{sec:star formation}
-In order to resolve individual star formation events on galactic scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
-Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local thermal Jeans mass.
-Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K.
-We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$.
-No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.
-
-We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
-At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2018, FIRE2}, as star formation is ultimately self-regulated by feedback.
-
-The stellar mass formed during a timestep $\Delta t$ from a region with a total gas mass $M_{\rm gas}$ is
+We refer the reader to Paper I for a detailed description of our numerical methods and feedback models. We briefly summarize the relevant details here.
+
+\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{http://enzo-project.org/} \citep{Enzo2014}.
+Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers.
+We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver.
+We use a 128$^{3}$ base grid with outflow boundary conditions measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 9 levels of refinement, for a maximum spatial resolution of 1.8~pc.
+Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas or 2) a cell's local Jeans length becomes resolved by less than eight cells.
+Also, if the cell is within four zones of a star particle with active feedback, it is refined to the maximum resolution.
+At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.
+
+\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (H, H$^+$, He, He$^+$, He$^P{++}$, H$^-$, H$_2$, H$_2^+$, and e$^-$), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}.
+We account for approximate self-shielding of H~{\sc i} against the UV background following \cite{Rahmati2013}.
+We assume He~{\sc i} self-shields in the same fashion as H~{\sc i}, and ignore He~{\sc ii} heating from the UVB entirely.
+Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}.
+Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.
+
+% AE: From Benoit, maybe make a note of 1 - 100 M_sun sampling may slightly overestimate higher mass stars (people usually do 0.1 to 100 M_sun
+\paragraph{Star Formation} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$.
+Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$.
+Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$).
+We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\% \citep{KrumholzMcKee2005}.
+Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment.
+We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).
+
+\paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually.
+Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse SNe at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution.
+Stars above this mass are assumed to direct collapse with no mass or energy injection.
+For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their H~{\sc i} and He~{\sc i} ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}.
+We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars.
+Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind \citep{Goldman2017}.
+Stars with $3 < M_{*} < 8$ are tracked after their death as possible Type Ia SN progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields.
+Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2018} for all stars with $M_{*} < 25~M_{\odot}$, Slemer et.
+al.
+in prep for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia SNe.
+
+\paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}.
+We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an exponential profile with a metal mass fraction of $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$~M$_{\odot}$.
+The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc.
+Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium.
+The galaxy contains no initial background stellar population, limiting the number of Typa Ia SNe in our model.
+We include initial SN driving to limit the transient burst of star formation from the initial cooling and collapse of the galaxy.
+\textbf{These SNe are randomly distributed with the same radial and vertical scale heights as the gas disk at a rate of 0.4~Myr$^{-1}$; this corresponds to the current SFR of Leo P, $\sim 4\times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ \citep{McQuinn2015a}, assuming 1 SNe per 100 M$_{\odot}$ of star formation.
+The metal yields from these SNe are set to the mean ISM abundances, and thus do not contribute to the chemical evolution of the galaxy.} Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
+Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.
+
+\section{Results}
+For context, in Paper I we focused on the global properties of the evolution of this dwarf galaxy, including an analysis of the galaxy's gas mass and star formation evolution, the ISM properties in terms of mass fractions, volume fractions, and phase diagrams, the interstellar radiation field in each tracked radiation band, the gas outflow rates and galactic wind velocities, and the retention / ejection of metals from the galaxy.
+This galaxy has an average star formation rate of $1.2~\times 10^{-4}$ M$_{\odot}$ yr$^{-1}$ and is consistent with observed low mass dwarfs galaxies in the Kenicutt-Schmidt relation.
+The galaxy exhibits strong, feedback-driven outflows \citep{Emerick2018b} that eject a significant amount of gas and metals from the galaxy.
+The mass loading factor at 0.25~R$_{\rm vir}$ was found to be $\eta \sim 50$, where $\eta$ is defined as the mass outflow rate in through a 0.1~$R_{\rm vir}$ annulus centered at 0.25~R$_{\rm vir}$ divided by the 100~Myr averaged SFR.
+These winds eject 96\% of the metals produced in the galaxy, with 50\% of all metals leaving the virial radius by the end of the simulation time.
+
+In this work we focus in detail on how each of the 15 individual metal species evolve in this galaxy.
+We address differences between the ejection fractions of each metal in Section~\ref{sec:ejection} and analyze for the first time the mass-fraction PDFs of the metals retained by the ISM in Section~\ref{sec:mixing}.
+
+\subsection{Preferential Ejection of Metals from the ISM}
+\label{sec:ejection}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.99\linewidth]{species_bar.png}\\
+\includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
+\caption{Top: The mass fraction of each metal species in the \textit{full simulation box} contained in the halo, gas in the galaxy disk, and stars.
+Bottom: The mass fraction of species within \textit{the disk} alone in each phase of the ISM (bottom).
+The leftmost bar in each plot shows the sum of all metals.}
+\label{fig:species_fractions}
+\end{figure*}
+
+%mm [this all seems to have been deleted in one version, but doesn't look like it should have been.  Down to ">>>>"] <<<<<<< HEAD
+The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
+We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).\footnote{The $f_{\rm H_2}$ restriction on the CNM is not relevant in our simulations, as there are no cells with $f_{\rm H_2} > 0.5$.
+$f_{\rm H_2}$ remains below about 0.35 for all cells (see Paper I).}
+%mm Again, with the exception of  H and He, we [H & He aren't metals]
+    We
+only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+
+We find two major results.
+%mm [reversed order of results to follow figure.  The opposite choice could also be made, by reversing the order of the figure...]
+    First, 
+only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies
+%mm 
+    among elements.
+The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
+This suggests that individual metals \textit{do not} share the same dynamical evolution.
+%mm Clearly
+       Thus, 
+metal enrichment in galaxies is a phenomenon that cannot be fully captured using a single, global metallicity field.
+In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
+
+    Second,
+nearly all of the metals 
+%mm
+    retained in the disk
+reside within neutral gas, mostly in the CNM; only a few percent
+reside in the hot phases.
+The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
+This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
+
+%The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
+We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
+Again, with the exception of H and He, we only consider metals produced self-consistently through our star formation and stellar feedback methods; the initial mass of each metal species is zero.
+
+%We find two major results.
+First, nearly all of the metals reside within neutral gas, mostly in the CNM; only a few percent reside in the hot phases.
+The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
+This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
+Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies.
+The top panel shows a qualitative disagreement between the retention fractions of N and Ba (about 20\% for each) as compared to the rest of the metals ($\sim$ 4 -- 5\%).
+This suggests that individual metals \textit{do not} share the same dynamical evolution.
+Clearly, metal enrichment in galaxies is a phenomenon that cannot be fully captured using single, global metallicity field.
+In this particular case, assuming that all metals behave the same would underestimate the N and Ba enrichment by a factor of up to five, at least for low mass dwarf galaxies.
+%mm [end of apparently deleted section] >>>>>>> 134a2fabac2aea2275cb3e8014308282b438742f
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.95\linewidth]{species_bar_sources.png}\\
+\caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
+These channels differ in both when metals are ejected, as determined by stellar evolution, and the phase of the ISM into which they are ejected.
+We note that the minimal contribution from Type Ia SNe for the iron-peak elements is because  no older stellar population was initialized, so only 16 of them have exploded by the end of our 500~Myr simulation.}
+
+\label{fig:species_sources}
+\end{figure*}
+
+The only physics that separates the dynamical evolution of these elements in our simulations is the individual sources of enrichment: AGB winds (stars less than 8~M$_{\odot}$), stellar winds (stars above 8~M$_{\odot}$), core collapse SNe, and Type Ia SNe.
+These channels differ in: 1) how long after a given star formation event they occur, 2), by consequence, the typical ISM properties in which they occur, and 3) how much energy is associated with each event, which determines ejecta temperature and velocity.
+To understand where each of the elements in Figure~\ref{fig:species_fractions} originated, we show the mass fraction of metals produced through each channel in Figure~\ref{fig:species_sources}.
+Core collapse SNe are responsible for over 90\% of the total metal enrichment in our galaxy, but this is clearly not true for all elements.
+In particular, a majority of N (74\%) and Ba (65\%) are ejected by AGB winds; both are retained at a higher rate than the rest of the metals.
+That this behavior exists for N and Ba in our simulations is dependent upon the metallicity of our galaxy and choice of stellar yield tables, but we can generalize this result to say that, for any assumed set of yields, low mass galaxies should more easily retain \textit{any} elements synthesized predominately in AGB winds, as compared to elements synthesized through SNe.\footnote{One might expect that much of the N and Ba that is ejected by galactic winds is comprised mostly of the $\sim$30\% of each species produced through the stellar winds of more massive stars and SNe.
+However, this cannot be proven as we lack Lagrangian information about individual gas elements.}
+% AE: Actually if there are significant isotope variations between nucleosynthetic sources (i.e.
+N produced in AGB winds is a different isotope than the trace N produced in SNe) then that could be a very cool thing to distinguish if we had good gas-phase abundance measures of various isotopes...
+but maybe not if they aren't very stable....
+We discuss how this result may extend towards other metal yields that are not well sampled on our relatively short (500 Myr) simulation timescales in Section~\ref{sec:discussion:metal yields}.
+
+AGB winds have low energy and velocities (10~km~s$^{-1}$) as compared to the energy and typical expansion velocities of SNe ($\sim$1000~km~s$^{-1}$).
+In addition, their longer timescales relative to massive stars means that AGB stars are typically removed from their birth regions and randomly distributed through the galactic disk.
+The changes in typical ISM density and height of these events contributes to these variations.
+We show histograms of the average number density within 20~pc of any given enrichment source (top) and height above/below the disk (bottom) within 1~Myr of each event (as limited by our output cadence) in Figure~\ref{fig:spatial distribution}.
+As shown, SNe peak at very low densities, indicating that most explode in superbubbles, regions carved out by previous SNe.
+AGB stars predominately release their metals close to the average ISM density.
+The scale height distributions for both events show no significant differences.
+We do not expect these differences to be the dominant effect in driving the differential evolution of elements ejected by AGB winds vs.
+SNe, compared to the energetics, but can certainly play a significant role in determining the mixing behavior of individual enrichment events.
+The changes to mixing behavior as a function of ISM properties will be investigated in more detail in a future work.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{SE_density.png}\\
+\includegraphics[width=0.95\linewidth]{SE_z.png}
+\caption{The volume-averaged gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
+\label{fig:spatial distribution}
+\end{figure}
+
+\subsection{Mixing and Distribution of Metals in the ISM}
+\label{sec:mixing}
+We characterize the metal distributions (in Sections~\ref{sec:log-normal} and \ref{sec:phase-pdfs}) and evolution (in Section~\ref{sec:statistics}) in our galaxy to build towards a  a complete model for how metals mix and evolve in the complex, multi-phase ISM of real galaxies.
+
+\subsubsection{A Functional Form for Metal PDFs}
+\label{sec:log-normal}
+
+The log-normal distribution is found often in nature, generally describing multiplicative processes with non-negative values that grow with time.
+In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}.
+In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}.
+Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}.
+It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape \textbf{\citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2018}}.
+This includes a log-normal component, generated by multiplicative processes---in this case shocks and the turbulent cascade in the ISM---and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures .
+
+The physics that drives the density PDF is directly related to the process of metal mixing and diffusion.
+However, there is no a priori reason why gas density and metallicity PDFs should have similar functional forms.
+We demonstrate here for the first time that the mass fraction PDFs for each metal species in our simulation can indeed be well fit using a piecewise log-normal + power-law PDF.
+We use a simple conceptual model in Section~\ref{sec:interpretation} to motivate the emergence of this distribution.
+
+We follow \citet{Collins2012}, \citet{Burkhart2017}, and \citet{Chen2018} in constructing our piecewise PDF.
+We define the distribution of metals in the ISM as a function of the fraction of mass contained at a given metallicity, $Z$, or metal mass fraction, $Z_i$, where $i$ denotes an individual element.
+This PDF is given as
+\begin{align*}
+  p(Z) =
+  \begin{cases}
+    \frac{N}{\sigma Z \sqrt{2\pi}} \rm{exp}\left[-\frac{(\rm{ln}(Z) - \mu)^2}{2\sigma^2}\right],
+    & Z < Z_{\rm{t}} \\
+    % \multicolumn{1}{@{}c@{\quad}}{1} % variant with \multicolumn
+    N p_o Z^{-\alpha},
+    & Z > Z_{\rm{t}}
+\end{cases}
+\end{align*}
+where $N$ is a normalization constant, $p_o$ ensures continuity between the two components, $\mu$ and $\sigma$ are the log-mean and width of the log-normal component, $\alpha$ is the power-law slope,  and Z$_{\rm t}$ is the metal fraction at the transition between the log-normal and power-law components.
+When fitting this PDF, we only enforce continuity and $\int_0^{\infty} p(Z) dZ = 1$, leaving $\alpha$, $\mu$, $\sigma$, and $Z_{\rm t}$ as free parameters.
+These conditions set $N$ and $p_o$ to
 \begin{equation}
-         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
+N = \frac{1}{2} \left[ 1 + \rm{erf}\left( \frac{ln\left(Z_{\rm t}\right) - \mu}{\sigma\sqrt{2}}\right)\right] + \frac{p_o}{\alpha-1}Z_{\rm t}^{-\alpha + 1}
 \end{equation}
-In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution.
-We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses.
-In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs.
-If it does, we randomly sample from
-the adopted IMF until approximately 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$.
-The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation.
-We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$.
-Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution.
-By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.
-
-Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion.
-This dispersion captures some of the unresolved gas motions below the resolution limit that are smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations.
-Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.
-
-Stars evolve during the simulation, by losing mass from stellar winds and SNe as described below, and by changing types, but persist throughout the entire simulation.
-For example, low mass stars are tagged as white dwarfs (WDs) at the end of their life, which may eventually explode as a Type Ia SN (discussed below), after which they persist as massless tracer particle remnants.
-Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a four-cell region at the highest level of refinement.
-This ensures that both stellar winds and SNe feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.
-
-\subsection{Stellar Properties}
-\label{sec:properties}
-Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}).
-We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$.
-Although $T_{\rm eff}$ and $g$ evolve over time for stars, modifying stellar radiative properties, following a stellar evolution track for each of our stars is beyond the scope of this work.
-We instead fix these properties at their zero age main sequence values.
-
-\subsection{Stellar Feedback and Chemical Yields}
-
-\subsubsection{Stellar Yields}
-\label{sec:yields}
-For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars.
-We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2018}.
-This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$.
-We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$.
-We ignore SN yields from these stars (see next paragraph).
-We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth.
-Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation.
-We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017a} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.
-
-%
-% KVJ: Possibly include a discussion on uncertainties in stellar yields
-%
-
-Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe.
-Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$; we take $M_{\rm trans} = 8$~M$_{\odot}$.
-In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
-Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics).
-Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
-\citet{Cote2017a} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
-We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
-
-There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}.
-Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}.
-Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass, metal, or energy ejection.
-
-Type Ia SNe are an important additional source of galactic chemical enrichment.
-These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
-We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
-We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, substantially limiting the number of Type Ia SNe occurring during the initial gigayear in our models.
-
-\subsubsection{Stellar Winds}
-\label{sec:stellar winds}
-Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
-Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback.
-We assume complete thermalization of the wind kinetic energy, taking the total injected energy injected in timestep $\Delta t$ as $E_w = \frac{1}{2}\dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$.
-This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle.
-The edges of this spherical region will only partially overlap grid cells.
-We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately.
-We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).
-
-Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}.
-Satisfying the Courant time step becomes prohibitively expensive following this gas, with time steps dropping to $\Delta t \sim$~100~yr.
-For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}.
-In our case, we fix massive stellar wind velocities to $v_w = 20$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies.
-Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work.
-These points are discussed in more detail in Sect.~\ref{sec:stellar winds discussion}.
-
-% Injecting 10$^{3}$ km s$^{-1}$ gas onto the grid at these scales leads to super heated, shocked gas at unphysical temperatures of about 10$^{8-9}$ K, particularly when injecting into very low density media.
-This can lead to painfully short time step sizes and crashes in the hydrodynamics solver.
-We adopt the common solution of artifiially reducing the wind velocity from massive stars, choosing $v_{\rm wind} = 500$~km~s$^{-1}$ for stars above 8 M$_{\odot}$.
-However, this can still be problematic once the star evacuates the local ISM and injects its energy to very low density ($n \lesssim 10^{-3}$ \ccunit) gas.
-We address this issue by mass loading our winds when injection would lead to wind bubble temperatures in the spherical source region above a maximum temperature typical of wind bubble.
-This is a free parameter that we take to be 2 $\times$ 10$^{6}$ K \citep{Weaver1977}.
-Mass loading in this manner is (in effect) a sub-grid model for the unresolved ISM mixing at the boundary layer of the wind bubble, which is in fact the source of a majority of the gas mass within the wind bubble \citep{Weaver1977}.
-We take the metal species abundances of the mass loaded ISM to be the average cold / warm ISM abundance on each grid to prevent artificially inflating/deflating the overall abundances.
-We discuss our ability to resolve typical single star wind bubble properties in Appendix ~\ref{appendix:stellar winds}.
-
-%parameterized in this work with the STARBURST99 wind model, \citep{Leitherer1992}:
-%\begin{multline}
-%{\rm log} \left[ v_{\rm wind} {\rm (km~s^{-1})} \right] = 1.23 - 0.30~{\rm log}~\left[L{\rm (L_{\odot})}\right] \\
-% + 0.55~{\rm log}\left[M({\rm M_{\odot}})\right] + 0.64~{\rm log}\left[T_{\rm eff}(K)\right] \\
-% + 0.13~{\rm log}\left[Z({\rm Z_{\odot}})\right].
-%\end{multline}
-
-Stars that only undergo an AGB phase deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks.
-AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$.
-For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars as well.
-
-\subsubsection{Core Collapse SNe}
-\label{sec: core collapse}
-Stars between  $M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
-Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}).
-We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions.
-We use the same Monte Carlo sampling method as used in our stellar winds to map the spherical injection region to the grid.
-We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle.
-In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.
-
-\subsubsection{Type Ia SNe}
-\label{sec:Type Ia}
-We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as WD particles, marking a subset as Type Ia SN progenitors.
-This is the most self-consistent model for Type Ia SNe in galaxy-scale simulations.
-We note however that for the low SFRs in our isolated dwarf galaxy simulation, the first Type Ia SN only appears after a few hundred megayears of simulation time.
-By the end of the simulation presented here (500~Myr), only 18 have gone off.
-At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}.
-%mm \textbf{I originally reproduced the equations here, but it is currently commented out. - AE}
-%or, 
-%\[
-%M_{\rm WD} = 
-%\begin{cases}
-%0.134 M_{\rm i} + 0.331 & 1.7~{\rm M_{\odot}} \le M_{\rm *} \le 4~{\rm M_{\odot}} \\
-%0.047 M_{\rm i} + 0.679 & 4~{\rm M_{\odot}} \le M_{\rm *}
-%\end{cases}
-%\]
-%where $M_{\rm *}$ is the initial mass of the WD progenitor.
-We follow the common assumption that progenitor stars with initial masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017a}.
-
-We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution model.
-The Type Ia SN rate is taken to be a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope $\beta$ and normalization $N_{\rm Ia}/M_{\rm SF}$ are observables.
-The latter represents the number of Type Ia SNe per mass of star formation.
-By assuming an IMF  $dN/dm$, one can write down the fraction $\eta$ of stars capable of forming a Type Ia SN progenitor that \textit{will} explode within a Hubble time.
-This is given as
+and
 \begin{equation}
-\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
-\end{equation}
-where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF, and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates.
-The distribution slope $\beta$ is of order unity, with typical values between 1.0 and 1.2 \citep[see][for a recent review]{Maoz2014}.
-$N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the Type Ia SN rate and integrating over a Hubble time.
-Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}.
-For our fiducial values, we adopt $\beta = 1.2$ \citep{Maoz2010} and $N_{\rm Ia}/M_{\rm SF} = 0.8\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013}.
-Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.
-
-Finally, we can normalize $\Psi(t)$ to give the probability per unit time $\dot{P}(t)$ that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor.
-Integrating this gives the total probability at any given time as
-\begin{equation}
-P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
-\end{equation}
-where $t_{\rm o}$ is the formation time of the WD and the leading term on the right hand side properly normalizes the total probability over a Hubble time to $\eta$.
-This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
-In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle.
-For $u \in [0,1]$, we interpolate its position on a pre-tabulated and inverted cumulative probability distribution function to assign a single time at which the WD particle will explode as a Type 1a supernova.
-We institute a minimum delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.
-
-\subsubsection{Ionizing Radiation from Discrete Sources}
-\label{sec:ionizing radiation}
-Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies.
-\ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance.
-However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds.
-Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
-As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.
-
-Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation.
-We follow HI and HeI ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.
-
-We determine the HI and HeI ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}.
-We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star.
-Stars less massive than about 15 M$_{\odot}$ and very massive stars with sub-solar metallicity are generally not well sampled by the OSTAR2002 grid.
-In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).
-
-Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}).
-The average energy for HI and HeI ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.
-
-We also include the effects of radiation pressure on HI.
-This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}.
-We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared.
-This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}.
-However, the importance of multiple scattering is still unclear.
-Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013a,Krumholz2018,Reissl2018,Wibking2018}.
-Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.
-
-\subsubsection{Diffuse  Heating}
-\label{sec:diffusive heating}
-We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the FUV (6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles.
-The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the spectral energy distributions for each gridded star.
-Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
-Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
-However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}.
-Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile.
-Only recently has the localization and time variation of these processes been considered.
-
-Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}.
-We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}.
-We assume HeI ionization generally follows HI.
-This allows us to approximate HeI self-shielding using the same form (A.
-Rahmati, private communication).
-We ignore HeII photoionization from the UV background entirely.
-For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}).
-As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription.
-This is described in more detail in Appendix ~\ref{appendix:cooling}.
-
-%Ignoring this effect leads to an overestimation of the cooling rates when in the self-shielding regime.
-%We refer to \citet{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \citet{Gracklemethod} for its specific implementation, as used here.
-
-We assume the galaxy is mostly optically thin to stellar FUV and use only local approximations for shielding.
-We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
-\begin{equation}
-\label{eq:PE}
-\Gamma_{\rm pe} = (1.3 \times 10^{-24} \rm{erg~s^{-1}~cm^{-3}})\, \epsilon n_{\rm H} G_{\rm eff} D 
-\end{equation}
-where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust-to-gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
-Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
-
-The value of $D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
-The extremely low dust-to-gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a ratio $D$ that scales linearly with metallicity at very low metallicity.
-At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit.
-Given that the ambient density of the ISM is generally 1--10~cm$^{-3}$, we can safely assume the FUV field to be optically thin.
-However, we do include a localized attenuation prescription that may influence high-density or metal-enriched regions of the galaxy.
-We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.
-
-Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
-This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations.
-Our chemical network only includes contributions from H, He, and H$_2$ to n$_e$.
-Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
-%This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
-
-\subsubsection{Lyman-Werner Radiation}
-\label{sec:LW}
-In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rate.
-We compute the stellar Lyman-Werner flux again from the OSTAR2002 grid by integrating the spectral energy distributions over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}).
-Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section.
-We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.
-
-\section{Galaxy Initial Conditions}
-\label{sec:IC}
-We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy.
-The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy.
-Leo P is gas rich, with a neutral hydrogen mass $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and stellar mass $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to an observed neutral hydrogen radius $r_{\rm HI} = 500$~pc.
-LeoP has a low metallicity, with an oxygen to hydrogen abundance ratio (O/H) of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}).
-Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.
-
-The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential.
-The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
-\begin{equation}
-\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
-\end{equation}
-where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass.
-We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$.
-We adopt a \citet{Burkert1995} dark matter potential with virial mass and radius $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and scale radius r$_{\rm s} = 990$~pc.
-This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc.
-These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}.
-
-Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM.
-This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation.
-During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}.
-We stop the artificial driving 25~Myr after the first star particle forms.
-These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances.
-We note this initial driving is ad hoc in that we do not include other effects from the stellar population that would have caused these SNe.
-
-We emphasize here that our model, with no initial stellar distribution, is not intended to identically reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales.
-In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations.
-Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances.
-In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution.
-Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe.
-The subsequent metal enrichment from the stars in our simulation can be thought of as tracking a change in abundances from arbitrary initial conditions.
-We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.
-
-\section{Results}
-\label{sec:results}
-We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms.
-Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run.
-The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical height $|z| < 200$~pc relative to the center of the galaxy.
-ISM properties are calculated considering only the gas contained within the disk of the galaxy.
-We include a resolution study in Appendix \ref{appendix:resolution_study}.
-
-Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}.
-All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset dd76ad10.
-
-\subsection{Morphological Structure and Evolution}
-\label{sec:structure}
-
-We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}.
-These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
-This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds.
-This central region quickly fills with warm and hot gas generated from radiation feedback and SNe respectively.
-Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels.
-The ISM properties are quantified further in Section~\ref{sec:phase}.
+p_o = \frac{1}{\sigma Z_{\rm t} \sqrt{2 \pi}} {\rm exp}\left[-\frac{({\rm ln}(Z_{\rm t}) - \mu)^2}{2 \sigma^2} + \alpha {\rm ln}(Z_{\rm t}) \right]
+\end{equation}.
+
+We compute the numerical metal mass fraction PDFs for each metal species in our simulation using a fixed bin 
+%mm with 
+         width
+of 0.05 dex.
+We fit $p(Z)$ to each of these using a Levenberg-Marquardt algorithm as implemented in \textsc{SciPy} \citep{SciPy}, stepping through possible values for $Z_{\rm t}$, set to the centers of each of these bins.
+The best of these fits is then compared to best fits using only a log-normal component or only a power-law component, and the best of these three is accepted.
+The log-normal + power-law PDF produces the best fit in nearly all cases.
+
+We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
+These PDFs have been computed at an arbitrary single point in time in the middle of the simulation run.
+% 270 Myr
+For clarity, we only show a subset of the 15 elements we follow.
+As shown, there are clear differences in the PDFs across elements of different nucleosynthetic sources (AGB vs.
+SNe) and between each phase.
+However, each of these distributions are characterized by a power-law tail towards high metal fractions and a turnover of varying width at low metal fractions.
+We discuss the differences among each phase in more detail in the next section, but note here that the significance of each of these components varies notably across phases.
+In many of these cases, the piecewise log-normal + power-law distribution fits the numerical PDF quite well.
+However, there are often deviations, particularly at low metal fractions, from pure log-normal behavior.
+This manifests as either a very broad, flat PDF at low metal fraction (see N and Ba, for example), or large peaks not well described by $p(Z)$ at low metal fraction.
+In these situations, it is unclear what, if any, portion should be considered as a log-normal, or if there are multiple components within this region.
+
+We argue here that the log-normal + power-law PDF can be a powerful tool for modeling the metal fraction  PDFs of individual elements in galaxy models.
+The fits are not uniformly perfect but some deviation from a simple analytic model is expected in a complex, multi-phase ISM.
+In addition, some of this deviation, particularly in the WNM and WIM, could be caused by grouping together qualitatively distinct gas in a single phase; this would tend to broaden the distributions.
+Most importantly, however, the PDFs of the CNM, are indeed well fit by the adopted $p(Z)$.
+As this is the source of star-forming gas in the ISM, the log-normal + power-law PDF appears useful to account for intrinsic scatter in stellar abundances in galaxy evolution models.
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
-\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation.
-Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row).
-Each individual main sequence star particle is shown in the number density projections as a single white dot.}
-\label{fig:panel_x}
+\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
+\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black).
+For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
+We note the vertical axis normalization is such that integrating over the shown PDF gives the mass fraction of that phase in the disk.
+Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
+\label{fig:log-normal}
 \end{figure*}
 
-The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
-This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time.
-Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--120~pc.
-Towards the end of the simulation time, the half-light radius is $391 \pm 19$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.
-Although the disk remains thin beyond the half-light radius, with a scale height of around 50~pc, it is fully resolved at all radii.
-By the end of the simulation, the majority of the disk has a scale height of $\sim$100~pc.
-
-Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging.
-For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
-In the final column of Fig.~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
-With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
-At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$.
-These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.
+\subsubsection{PDF Variation Across Gas Phase}
+\label{sec:phase-pdfs}
+
+The various phases represented in Figure~\ref{fig:log-normal} involve variations in density and temperature of more than six orders of magnitude.
+The evolution of each phase is qualitatively different, and the metal mixing behavior of each should vary.
+Mixing timescales over a given length scale should be related to the local sound speed; hot gas, with higher sound speeds, should mix more rapidly than the dense, disconnected clumps of cold gas in the ISM.
+In addition, one would expect a metallicity gradient with gas temperature as enrichment occurs first in the hot phases, cooling and enriching denser gas over time.
+We examine the PDF variations among elements in each phase, as shown in Figure~\ref{fig:log-normal}, in more detail here.
+
+Unsurprisingly the diffuse HIM \textbf{is the most metal rich phase}, as it is comprised predominately of metal enriched SN ejecta.
+Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
+Generally, in colder gas the metal PDFs become less enriched with broader, low-metal-fraction components and steeper, power-law tails.
+Although the extended power-law tail of the HIM leads to a large range of metal fractions, the HIM represents very little mass, and this tail represents recent, un-mixed enrichment.
+The comparatively narrow width in the log-normal regimes of the CNM is perhaps surprising.
+Although this gas is at lower metal fraction than the WNM and WIM, it would appear that it is more well mixed.
+This runs counter to the idea that mixing times should be long in colder gas, unless (as we argue) mixing first proceeds rapidly in the hot phases before mixing in with cold, disconnected structures across the galaxy.
+
+Although these trends across phases hold for all elements, there are qualitative differences between elements, particularly between those ejected predominantly by AGB winds (e.g.
+Ba and N) and those ejected by SNe (e.g.
+O and Mg).
+In all phases, except the HIM, the AGB-wind elements have broader distributions that are less well described by our adopted $p(Z)$ than the metals dominated by SN enrichment.
+The power-law component of N and Ba is generally shallower than all other metals across each phase (except the HIM), particularly in the CNM.
+Ba and N do not show significant differences among the rest of the metals in the HIM, though this is likely because the Ba and N present in this phase is dominated by the Ba and N included in SNe yields.
+Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and SNe.
+\textbf{AGB wind elements enrich the WNM and WIM directly, rather than the HIM.
+This leads to longer mixing timescales and broader PDFs for these elements.}
+
+\subsubsection{The Time Evolution of Metal PDFs}
+\label{sec:statistics}
+We focus on the time evolution of the full numerical PDFs in this section.
+Our results here do not depend upon the choice of functional form for $p(Z)$.
+Figure~\ref{fig:phase-statistics} shows the evolution of four different statistics for the O (top) and Ba (bottom) PDFs.
+These two elements are treated as representative elements for SN and AGB wind production respectively.
+The difference between the mean and median masses of the PDF (second column) is a measure of the skew of the PDF.
+Positive values indicate that metals are preferentially sequestered in metal-rich gas, and are less well mixed throughout the given phase.
+The skew is always positive in these distributions.
 
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
-\caption{Same as Fig.~\ref{fig:panel_x}, but showing face-on views.}
-\label{fig:panel_z}
+\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution.png}
+\caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation.
+The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
+\label{fig:phase-statistics}
 \end{figure*}
 
-\begin{figure}
-\centering
-\includegraphics[width=0.975\linewidth]{scale_height}
-\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
-\label{fig:scale_height}
-\end{figure}
-
-\subsection{Star Formation Rate and Mass Evolution}
-\label{sec:sfr}
-
-We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Fig.~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
-The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$.
-The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation.
-Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.19 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
-We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.
-
-We note that the granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured.
-Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$.
-For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$.
-Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense.
-Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.
-
-At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Fig.~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
-The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
-For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% at 500~Myr.
-The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy from feedback-driven galactic winds.
-During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM.
-Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
-The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{sfr_snrx100}
-\includegraphics[width=0.475\linewidth]{mass_evolution}
-\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins.
-Broken portions of this histogram are time periods with no star formation or supernovae.
-Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR.
-Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
-\label{fig:sfr_mass_evolution}
-\end{figure*}
-
-\subsection{ISM Properties}
-\label{sec:phase}
-
-Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy.
-We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM).
-We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content.
-By this definition, although our galaxy certainly contains molecular hydrogen, molecular gas as a phase does not exist; the peak f$_{\rm H_2}$ in any single cell remains below 30\%.
-See Appendix \ref{appendix:phases} for a quantitative definition of these phases.
-The properties of these phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution.
-Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.
-
-Fig.~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
-One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Fig.~\ref{fig:ISM_evolution}).
-Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
-We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
-Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left.
-The boxed regime in the lower right corner shows our star formation density and temperature threshold.
-Gas in this regime is rapidly consumed by star formation and subsequent feedback.
-Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average.
-
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{phase_diagram.png}
-\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gas interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr.
-The dashed lines are lines of constant pressure, separated by factors of 10.
-The region in the lower right corner indicates our density and temperature thresholds for star formation.}
-\label{fig:phase}
-\end{figure}
-
-The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Fig.~\ref{fig:ISM_evolution}.
-The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
-The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run.
-The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation.
-During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1.
-Although the CNM dominates the mass fraction, it is a negligible component of the ISM volume, which is WIM dominated.
-However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
-Together, these figures better quantify the general properties observed in the panel plots in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}.
-
-These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}.
-They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (defined in those works as gas with 100~K$<$T$< 3\times 10^{4}$), with cold gas having between 1 and 10\% of the mass, and occupying negligible volume.
-Hot gas (defined as gas with $T > 3\times 10^{4}$~K) occupies 10\% of the volume, with negligible mass, in their galaxy, while our WIM alone occupies $>$ 50\% of the volume.
-Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) and hot gas (by volume fraction) that seen in the more massive dwarf galaxy in these works.
-The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work.
-We have compared our cooling curves to those used in \citep{Hu2017} and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.
-
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
-\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
-\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
-\label{fig:ISM_evolution}
-\end{figure*}
-
-\subsection{Interstellar Radiation Field}
-\label{sec:ISRF}
-
-The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}.
-This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
-In Fig.~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
-The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
-The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
-At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.
-
-The bottom panel gives the HI ionizing photon flux from stellar radiation.
-The ionizing radiation profile follows a similar trend, yet with significantly more variation, anywhere from two to four orders of magnitude.
-As this radiation is followed through radiative transfer, the profile encodes information about local attenuation by dense, neutral gas.
-This is the main driver of the differences between the two panels.
-The total fluctuation in both panels is due in part to the low-level, stochastic star formation in our galaxy.
-A higher star formation rate would produce a more regular population of massive stars and more uniform (in time) ISRF.
-
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{G_o_profile} \\
-\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
-\caption{
-Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr.
-Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc.
-The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line.
-The bottom panel gives the HI ionizing stellar radiation flux.
-Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point.
-For this reason we only shade between the first quartile and maximum values.
-HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.
-In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
-\label{fig:ISRF}
-\end{figure}
-
-\begin{figure*}
-%\centering
-\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
-\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
-\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
-Here, we include all gas within the mid-plane of our dwarf galaxy.
-Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
-This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
-\label{fig:ISRF_2D}
-\end{figure*}
-
-To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Fig.~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr.
-This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
-The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps).
-From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile.
-Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation.
-In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency.
-It remains to be seen which of these two modes of feedback is more important in regulating star formation.
-
-\subsection{Outflow Properties}
-\label{sec:outflows}
-
-The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}.
-However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
-In Fig.~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
-We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
-\begin{equation} \label{eq:dotM}
-\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
-\end{equation} 
-We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.
-
-The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Fig.~\ref{fig:mass_outflow}.
-Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
-For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor.
-The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors between 20--100 throughout the simulation time.
-This declines towards larger radii, however, with substantially less outflow past the virial radius.
-\citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift, consistent with our results.
-The fluctuations in both of these panels are directly correlated with the SFR, with increased outflow during periods of star formation, and decreased outflow during periods of quiescence.
-
-Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few.
-Using a fit provided in \citet{Muratov2015} to extrapolate and compare $\eta$ at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find.
-These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison.
-We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find lower mass loading factors even closer to the disk, at 0.05 $R_{\rm vir}$, between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$; certainly this implies even smaller mass loading factors at 0.25 $R_{\rm vir}$.
-
-\begin{figure*}
-\includegraphics[width=0.45\linewidth]{total_mass_outflow}
-\includegraphics[width=0.45\linewidth]{total_mass_loading}
-\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
-\label{fig:mass_outflow}
-\end{figure*}
-
-Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
-In Fig.~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
-Gas with a negative velocity is moving towards the center of the halo.
-Roughly 25\% of this mass is inflowing, mostly with modest negative velocities, and corresponds to previously ejected gas mixing and recycling throughout the halo.
-Half of the outflowing gas (positive velocities) is moving at velocities below 30 km s$^{-1}$, 75\% at velocities below 70 km s$^{-1}$, and 95\% at velocities below 100 km s$^{-1}$.
-Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-negligible amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$.
-The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominating at velocities above 200 km s$^{-1}$.
-The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling WIM and HIM, consistent with the results in \citet{Hu2016,Hu2017}.
-However, as shown, the HIM, which is mostly the SN ejecta itself, comprises very little of the outflow by mass.
-Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM.
-Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however.
-The amount of transfer between phases in the halo of our galaxy will be investigated in future work.
-
-\begin{figure}
-\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
-\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-This is averaged over the same time interval as Fig.~\ref{fig:ISRF}.
-The outflowing material is multiphase, broken into WNM, WIM, and HIM.
-See Section~\ref{sec:phase} for definitions of these regimes.
-We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K.
-There is little to no outflowing mass in the CNM.}
-\label{fig:outflow_velocity}
-\end{figure}
-
-\subsection{Metal Evolution} 
-\label{sec:chemical evolution}
-
-\subsubsection{Metal Enriched Outflows}
-Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}.
-This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
-In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}.
-The parameter used to quantify metal outflow efficiencies varies among works.
-Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
-\begin{equation} \label{eq:eta-metal}
-\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
-\end{equation}
-where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
-On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5).
-Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}.
-\cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity.
-Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.
-
-\begin{figure}
-\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
-\includegraphics[width=0.9\linewidth]{metal_retention}
-\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:mass_outflow}.
-This is the ratio between the metal outflow rate and the metal production rate.
-{\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
-In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
-\label{fig:metal_evolution}
-\end{figure}
-
-These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
-This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
-After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
-This continues throughout the simulation, with only $\sim$4\% of produced metals residing in the disk of the galaxy.
-It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius until about 350 Myr where the fraction levels off to just above 50\%.
-Likewise, the CGM metal content continually decreases until the end of the simulation from loss through the virial radius of the halo.
-See Section~\ref{sec:obs_metals} for further discussion.
-
-\subsubsection{Differential Evolution of Elements Within the ISM}
-It is important to understand how metals from each source of stellar yields enrich the ISM.
-Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}.
-This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed.
-Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Avillez2002,Tassis2008,YangKrumholz2012}.
-It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species.
-It is even more unclear how metals are transported and distributed within low-mass dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.
-
-We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
-The left panel gives the abundance ratio of N to O throughout the ISM.
-The right
-two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy.
-These show regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K) connected by cold filaments, warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).
-
-\begin{figure*}
-\includegraphics[width=0.98\linewidth]{log_NO_panel}
-\caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances.
-The left slice gives the ratio of the abundance between N and O, normalized to the solar abundance, while the number density and temperature are shown on the right.
-In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occurred in the preceding 5 Myr as black stars and orange diamonds respectively.}
-\label{fig:metal_slices}
-\end{figure*}
-
-As shown in the left panel, [N/O] varies significantly over this section of the ISM with notable differences across the various phases and ISM structures.
-The hottest gas, dominated by recent supernova explosions is overabundant in oxygen, relative to solar (purple).
-However, the relative abundance of nitrogen increases in the WIM and WNM, being overabundant relative to solar (green).
-
-At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars.
-Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
-Given the variations in Fig.~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
-The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
-This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
-A more detailed analysis is beyond the scope of this work, but we investigate this in detail in Emerick et.
-al.
-(in prep.).
+For O, the median mass fraction is ordered by phase temperature.
+The HIM is significantly more enriched than the cooler phases by anywhere from 0.1 dex to 4 dex, fluctuating by $\pm 1$ dex over the simulation time.
+The frequent large skew in the HIM (see second panel) and spread in the HIM (right two panels), coupled with its continual fluctuation, suggests that the HIM is not in equilibrium.
+%This phase is poorly mixed because it is short lived, either cooling into different phases of the ISM or being ejected from the galaxy, and is continually enriched by new SN events.
+Each cooler phase in O is progressively less enriched (lower median), with smaller skew and spread.
+The offset between phases and increasingly well mixed gas from hot to cold indicates that metal enrichment in the ISM of galaxies proceeds first through mixing on large scales in a hot phase, before progressively cooling and/or mixing through multiple phases until enriching star-forming gas.
+This
+%mm is the only explanation for [that's perhaps too strong a claim]
+    can explain
+how the cold gas can rapidly homogenize over the whole galaxy within $\sim$50 Myr, roughly when the cold phase exhibits a nearly constant spread (right panels). Individual enrichment events 
+%mm will 
+have significantly higher metallicities than the ambient ISM in any phase, and 
+%mm will 
+drive an increase in the difference between the mean and median of the PDF.
+These can be seen as the obvious spikes in the HIM and WIM.
+For O, the lack of these spikes in the two cold phases suggests again that enrichment does not occur directly in these phases, but proceeds more gradually through the warmer phases first.
+
+% In each phase, enrichment events will tend to drive larger differences between mean and median mass fraction,
+
+Although these trends are generally true for Ba, its evolution is much more complicated.
+%In addition, the HIM is much less offset from the rest of the phases than is seen in O, with much less variability.
+Unlike O, the spread and skew in Ba for the CNM, WNM, and WIM \textit{increase} during the evolution, reaching differences in 90$^{\rm th}$ and 10$^{\rm th}$ percentiles of nearly 2 dex in the CNM and over 2 dex in the WNM and WIM.
+The HIM is seemingly unaffected by this trend, and simply fluctuates throughout the simulation.
+Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in SNe.
+The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
+These tails represent the most recently enriched gas,
+%mm and 
+        which
+is clearly much more locally confined than O.
+
+%{\bf (move to discussion?)}:
+The positive skew in all of the PDFs presented here implies that most of the mass of the galaxy has a metal fraction below what one would normally adopt as the average metallicity (i.e.\ the ratio between the total mass of metals and the total mass).
+Assuming star-forming gas follows the same properties as the cold gas, this distinction is small ($\sim$ 0.2 dex),
+%mm but
+   though 
+significant, for elements released during SNe explosions, but can be very significant, up to $\sim$ 0.8 dex, for elements released in AGB winds.
+Chemical evolution models, especially one-zone models, follow the mean metal fraction, rather than the median.
+%mm These results indicate that these 
+            Our results indicate that such
+models are biased to overestimate gas and stellar elemental abundances.
+% However star formation may not be unbiased, and may preferentially come from gas sitting on the higher metal fraction tails.
+
+To summarize, Figure~\ref{fig:phase-statistics} demonstrates: 1) there are qualitative differences in how SN-injected elements (e.g.
+O, Mg) and AGB-wind-injected elements (e.g.
+N, Ba) are distributed through the ISM, with the latter having a broader range of variation and being less well mixed in all phases except the HIM; 2) hotter phases are more metal enriched, both because the cooler phases make up most of the initially unenriched mass of the ISM and because the hotter phases are more directly populated by recent enrichment events; 3) the cooler, denser phases, particularly for SN injected elements, are more well mixed than the hot phases of the ISM; 4) the PDFs of metal mass fraction are best fit by a log-normal + power law function; and therefore 5) the median metallicity available for star formation
+%mm rates 
+lies below the mean galactic value.
+In the case of SN injected elements, enrichment proceeds quickly through the HIM over the entire galaxy.
+For AGB injected elements, enrichment proceeds through the WIM and WNM, leading to longer mixing timescales and larger metal fraction variations in the ISM.
 
@@
 \label{sec:discussion}
-
-\subsection{Comparison to Observed Low Mass Dwarf Galaxies}
-\label{sec:observation}
-
-As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs.
-Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of $z = 0$ dwarf galaxies.
-However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies.
-We show that these properties are broadly consistent with observations.
-
-\subsubsection{Gas and Star Formation}
-\label{sec:gas_sf}
-
-The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}.
-However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
-In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.
-
-Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
-We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}.
-We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the area of the disk within the radius of the outermost star formed within the previous 10 Myr.
-Likewise, $\Sigma_{\rm gas} = M_{\rm gas,10} / A_{*,10}$, where M$_{\rm gas,10}$ is the total gas mass within this defined disk.
-However, the total gas content cannot be determined observationally.
-To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He.
-We note that there is generally no correction made for any possible H$_{\rm 2}$ or HII content.
-As shown in Section~\ref{sec:molecular gas content}, these components may be significant.
+We begin with a simple toy model that motivates the power-law tail at high metal fractions of the metal fraction PDFs and a subsequent turnover at low metal fractions in Section~\ref{sec:interpretation}.
+This work is placed in context with previous papers focusing on metal mixing in the ISM in Section~\ref{sec:context}.
+We discuss the relevance of additional AGB yields not directly followed in this study in Section~\ref{sec:discussion:metal yields}.
+Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impacts of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
+
+\subsection{Physical Interpretation of the PDF}
+\label{sec:interpretation}
+%
+% KVJ wanted clarification on this argument. I believe my added text 
+% does this sufficiently.
+Take the simple case of an initially primordial, uniform, isothermal medium of mass $M_o$ with initial metallicity $Z_{\rm o}$, containing a single, un-mixed enrichment event of mass $M_{\rm ej}$ whose size is small compared to the system and mass $M_{\rm ej} / M_o \ll 1$.
+Thus the background medium represents a virtually inexhaustible (but finite) source of un-enriched gas.
+In this case, $p(t,Z)$ initially takes the form of a double-delta function
+\begin{equation}
+p(t_{\rm o},Z) = \delta(Z_{\rm o}) + \frac{M_{\rm ej}}{M_o}\delta(Z - Z_{\rm ej}).
+\end{equation}
+%mm [edited the rest of this paragraph, and the next though I don't think there are any substantive changes unmarked.]
+If the enriched material mixes continually with the un-enriched gas at a constant rate, after some time  $\tau_{\rm mix}$ this gas will have mixed with an equal amount of primordial gas.
+At this time, $p(\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (2M_{\rm ej}/M_o) \delta(Z - (1/2)Z_{\rm ej})$.
+Then, $p(2\tau_{\rm mix},Z) = \delta(Z_{\rm o}) + (4M_{\rm ej}/M_o)\delta(Z - (1/4) Z_{\rm ej})$, and so on for other multiples of $\tau_{\rm mix}$.
+This represents an inverse relationship between the mass of enriched gas and the metallicity of the enriched gas.
+The superposition of the distributions of a single event evolving in time will appear as a power-law distribution with slope $\alpha = 1$.
+
+Thus, if the gas is continually enriched by identical, well-separated enrichment events of mass $M_{\rm ej}$ and metallicity $Z_{\rm ej}$, the instantaneous distribution $p(t,Z)$
+%mm , or $p(Z)$, 
+of these many events will be $\delta(Z_{\rm o})$ plus a power law in $Z$ with slope $\alpha = 1$, truncated at some minimim $Z$ (related to the time since enrichment began) and some maximum, $Z_{\rm ej}$.
+% and thus a power-law evolution in time of the high metallicity portion of $p(Z)$ with slope $\alpha = 1$. 
+The slope of the power-law, then, is determined by the rate of injection versus mixing with the ambient medium.
+A power-law index $\alpha < 1$ can occur when injection occurs more rapidly than the newly enriched gas can mix with the ambient medium.
+Steeper power-laws, $\alpha > 1$, develop when mixing occurs more rapidly than
+%mm enrichment. 
+         injection.
+If the ambient, primordial gas were truly infinite, the power-law would never completely encompass the delta function at $Z = Z_o$.
+
+In reality, however, $M_o$ is not an inexhaustible reservoir of primordial gas.
+Eventually the entire ambient medium will become enriched to some $Z > Z_o$, and $p(Z)$ will consist entirely of a truncated power-law.
+As enrichment proceeds, gas near the low metallicity truncation of $p(Z)$, which still comprises much of the mass of the system, enriches towards higher metallicities in the power-law tail.
+This will produce a turnover at the low $Z$ limit of $p(Z)$.
+The low-turnover limit is produced by diffusion from many different sources, and is thus a multiplicative process, which, as we noted above, tends to produce log-normal distributions.
+%mm [additive vs multiplicative]
+   %{\bf [According to Section~\ref{sec:log-normal}, MULTIPLICATIVE processes produce log-normals. Additive processes produce power-laws.  However, see Mouri (2013) for a possible counterexample...]}
+The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.
+
+This toy model provides a physical intuition for the general trends in the PDFs presented here across ISM phases. 
+%mm The HIM is comprised predominantly of gas from individual enrichment events that, due to its low density, easily create large power-law tails beginning at very high metal fractions. 
+     Individual enrichment events start at very high metal fractions in the low-density HIM, 
+     so they easily create long power-law tails.
+Whatever ambient component of the HIM that exists is well mixed, leading to a narrow and sub-dominant log-normal component at low metallicities.
+Cold, dense gas, which is almost never directly impacted by these individual enrichment events, is enriched almost entirely by diffusion, and thus has an almost completely log-normal PDF with very little, if any, power-law tail.
+
+%
+%
+%
+%Although this model is useful to explain these very general features, it is certainly incomplete in practice.
+Enrichment proceeds irregularly through the mulit-phase ISM with a variety of ejection masses and metallicities.
+Phases are not independent, and the hot phase cools and enriches cooler phases in the ISM, distorting $p(Z)$ within each phase.
+Cold gas is heated up and destroyed through feedback, changing the content of the low-metallicity end of the warm and hot phases.
+Finally, gas is removed from the galaxy through feedback driven winds that preferentially remove metal enriched gas.
+Each of these processes has a non-trivial effect on the evolution of the PDF that will cause deviations from the simple toy model outlined here.
+Determining the exact physical processes that drive and set the properties of each PDF is the subject of ongoing work.
+
+%
+% A.E. paragraph may need work
+%
+
+Mixing timescales are likely proportional to the eddy turnover times at the injection scale \citep{PanScannapieco2010, Colbrook2017} and the properties of turbulence in the ISM \citep{YangKrumholz2012,Sarmento2017,Sarmento2018}.
+Mixing within a phase is likely dependent upon the phase's sound speed and velocity dispersion.
+This would imply rapid mixing timescales in the WIM and HIM, with typical velocity dispersions of $\sim$~30 km~s$^{-1}$ and $\sim$~100~km~s$^{-1}$ respectively, and long mixing timescales in cold, dense gas ($\sim$ 1 km s$^{-1}$).
+Our results show, however, that in general the WIM and HIM are the least well mixed, while the CNM is the most well mixed across the galaxy.
+This is particularly curious as the sound crossing time of the HIM across the galaxy ($\sim 1$ kpc) is $\sim$10~Myr, compared to $\sim$~1~Gyr for the coldest gas.
+It must be that the HIM is far from equillibrium throughout the simulation, in part due to the continual enrichment by ongoing SNe.
+Newly enriched gas must mix through the HIM on galaxy scales, becoming well mixed and less enriched by the time it cools into the CNM and eventually star-forming gas.
+Since elements produced in AGB winds do not directly enter the HIM, mixing is less efficient driving larger variations across the galaxy.
+The idea of metals processing first through the hot ISM has been proposed before to explain observed metallicity trends in the outskirts of more massive galaxies \citep{Tassis2008,Werk2011}.
+
+% From benoit: more explicit title
+\subsection{
+%mm Context With 
+        Comparison with 
+Previous Studies of Metal Mixing}
+\label{sec:context}
+That metal fraction distributions can be described using simple analytic log-normal + power-law PDFs, even in a complex, multi-phase ISM, has not been demonstrated prior to this work.
+In addition, this is the first work to demonstrate differential mixing behavior of individual metal species using 3D hydrodynamics simulations.
+However, there does exist a significant body of work investigating the mixing behavior of passive scalars in a variety of contexts.
+%mm , as discussed below.  [ moved KrumholzTing18 to end of following paragraph.]
+%We discuss our results further in the context of previous research on metal mixing in the ISM and speculate on the physical processes that drive the evolution of these PDFs across phases.
+
+Previous work on the evolution of metals in the ISM varies from studies concerning the advection of passive scalars in idealized turbulent boxes \citep[e.g.][]{Pope1991, PanScannapieco2010, PanScannapiecoScalo2012, PanScannapiecoScalo2013, YangKrumholz2012, SurPanScannapieco2014, Colbrook2017}
+% cite passive scalar reviews by Warhaft 2000 in fluid mech and scalo + Elmegreen 2004?
+to global galaxy models studying generalized advection and mixing of passive scalars \citep[e.g.][]{deAvillez2002,Petit2015,Goldbaum2016} to models with more detailed self-consistent metal enrichment \citep[e.g.][]{Revaz2009,Escala2018}.
+\cite{KrumholzTing2018} predict differential behavior for AGB wind and core collapse SN synthesized elements as a direct consequence of the differences in size of typical planetary nebulae ($\sim$ 0.1~pc) and SN remnants ($\sim$ 100~pc).
+
+The evolution of metallicity PDFs has been investigated previously in some of these works \citep[see ][ and references therein]{PanScannapiecoScalo2012,PanScannapiecoScalo2013}, with effort towards developing closure models to describe the evolution of the PDFs of passive scalars in turbulent media \citep[e.g.][]{EswaranPope1988,Chen1989,Pope1991}.
+The astrophysical context in much of this work was enrichment from the first stars, so the focus was on the low-metallicity tail of the PDF and the timescales over which gas is polluted \citep[e.g.][]{PanScannapiecoScalo2013,Sarmento2017}.
+These works often use isothermal turbulent-box simulations initialized with a double-delta function PDF of pristine gas and enriched gas in some varying spatial distribution, ignoring ongoing enrichment.
+Initial PDFs of this form were demonstrated some time ago to evolve into a Gaussian distribution at late times \citep{EswaranPope1988}, but it is unclear if these could also be described with a log-normal distribution.
+However, these works uniformly do not contain the high metallicity power-law tails shown in our work.
+As suggested by our toy model in Section~\ref{sec:interpretation}, this is due to the lack of ongoing enrichment in these studies.
+
+More detailed models of global galaxy evolution have generally focused on spatial correlations and mixing timescales of initially asymmetric fields, without concern for ongoing enrichment \citep[e.g.][]{deAvillez2002,Petit2015} or focused primarily on the evolution of stellar abundance patterns and metallicity distribution functions \citep[e.g][]{Jeon2017,Hirai2017,Escala2018}, without directly examining the evolution of gas-phase metallicity PDFs.
+
+% The log-normal density PDFs found in ISM simulations have a variance that is proportional to the mach number \citep[e.g.][(maybe more)]{PNJ1997, Passot1998, Fedderath2008, LemasterStone2009}.
+In our simulations, however,
+
+\subsection{Timescale Dependence of AGB Ejecta}
+\label{sec:discussion:metal yields}
+We can generally say that metals ejected in AGB winds evolve qualitatively differently than metals produced by SNe in our dwarf galaxy.
+However, exactly which metals exhibit these differences, and to what degree, is timescale and metallicity dependent.
+Short timescales ($\lesssim 100$~Myr) only sample enrichment from the most massive AGB stars, while stars on order of a few solar masses only enrich on timescales of a gigayear or longer.
+In our simulations, which only simulate 500 Myr of evolution, N and Ba are dominated by AGB wind ejecta.
+C is commonly used to track AGB wind enrichment, but as it originates from lower mass AGB stars, C enrichment operates on gigayear timescales, longer than we follow in this work.
+Enrichment additionally varies with metallicity.
+Sr, for example, is only significantly ejected through AGB winds at our metallicity on gigayear timescales, while stellar winds from more massive stars dominate the production of Sr on shorter timescales.
+At higher metallicity, much more Sr is produced through massive AGB stars, decreasing the timescale over which Sr should exhibit a differential chemical evolution compared to SN-ejected elements (see \cite{Ritter2018} and \cite{Ritter2018b} and references therein).
+
+To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected by AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times.
+This model was run using \textsc{SYGMA} \citep{Ritter2018b}.
+As shown, metal enrichment from AGB winds only begins to dominate for any elements after $\sim$ 100 Myr.
+This includes N and Ba, which we follow in our simulations, but this model predicts that Ag and Pb will show similar behavior.
+It takes over a gigayear for C to be dominated by AGB wind ejecta, which is the case for many of the elements shown.
+F, which shows very little contribution from AGB winds at short timescales, is dominated by enrichment from them on longer timescales.
+These dependences on metallicity and timescales certainly add complications in generalizing our work and in interpreting observations in the context of the results presented here, but these difference could be leveraged to better understand galactic chemical evolution on multiple, distinct timescales.
+Clearly this motivates future work covering gigayear timescales to fully understand how metal mass fraction PDFs evolve with time.
 
@@
 \centering
-\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
-\includegraphics[width=0.475\linewidth]{all_gas_efficiency_evolution.png}
-\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
-See text for details of the calculation.
-Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars.
-On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}.
-There is no clear correlation with time in this diagram.}
-\label{fig:KS}
+\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0.png}
+\caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, without continuing star formation.
+We only show a sample of some of the elements dominated most by AGB enrichment at late times.
+The horizontal line marks a 50\% contribution.}
+\label{fig:agb evolution}
 \end{figure*}
 
-We include recent observational constraints on these relationships in Figure ~\ref{fig:KS}.
-Our galaxy fluctuates significantly about both relationships with no clear trends in time.
-However, in both cases, it is consistent with the available observational sample.
-At times our galaxy exhibits gas surface densities below the observational constraints.
-The trend is still consistent with higher densities at this point, but with a larger scatter towards lower star formation rate densities and efficiencies.
-
-In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
-It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
-This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
-The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.
-
-\subsubsection{Molecular Gas Content}
-\label{sec:molecular gas content}
-The molecular gas content of low-mass dwarf galaxies is generally assumed
-to be small, but is not well constrained by either theory or observations.
-Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
-As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range.
-H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
-The gas-phase reaction dominates in our low-metallicity galaxy over the other two channels by several orders of magnitude.
-In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$.
-Thus the presence of some ionizing background is required to generate the molecular fractions we find in our simulations, as confirmed in separate test simulations.
-
-In contrast, \citet{Hu2016} and \citet{Hu2017} find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$).
-However, although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field.
-Our model suggests that both H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies.
-Indeed it is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, though it is worth noting that the rate coefficients associated with gas-phase H$_2$ formation are still uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
-Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.
-
-\textbf{In addition, our model does not account for the stellar component of the radiation field that leads to H$^{-}$ photodetachment ($E_\gamma > 0.76$~eV), though we do account for the contribution from the UVB.
-We find that the H$_2$ fraction is more strongly dependent upon the Lyman-Werner radiation field, which is followed for each star, than the H$^{-}$ photodetachment rate.
-Our tests suggest that, by ignoring the stellar contribution to H$^{-}$ photodetachment, our results may represent upper limits on the H$_2$ mass.
-However, including this component will likely only make a substantial difference during periods of no star formation, when there are no massive stars with significant Lyman-Werner luminosities.
-We do not anticipate this to have a significant dynamical impact on our simulations, as is discussed in more detail in Appendix~\ref{appendix:H minus}}.
-
-It is unclear how the combination of all of the above effects will behave, especially considering that, even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}.
-These uncertainties certainly warrant further study of molecular gas in low metallicity dwarf galaxies.
-
-\subsubsection{Metal Retention}
-\label{sec:obs_metals}
-
-The simulations presented here have not yet been run for the gigayear timescales required to begin to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$.
-However, we can compare to a key observable: the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from closed box stellar evolution models given the galaxy's star formation history.
-This can be done readily with Milky Way dSph's.
-Their stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}.
-However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.
-
-Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich, star forming, low-mass dwarf galaxy, with an observable HII region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment.
-Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
-However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
-Although more than half of these metals are expected to eventually re-accrete \citep{Christensen2016,Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.
-
-It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium.
-While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
-We find 5.3\% of all metals lie within 1 kpc of the center of our galaxy, 24.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 51\% outside $R_{\rm vir}$.
-This is consistent with previous works, but this is again an evolving quantity.
-In addition, the amount of gas that escapes the virial radius is certainly sensitive to the details of gas accretion from the IGM on this galaxy, which we cannot capture in this model.
-
-The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies.
-Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return.
-In addition, the accretion of pristine gas from the intergalactic medium could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals.
-This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.
-
-\subsection{Missing Physics}
-Although we include many detailed physical models in our simulations, there remain additional physical processes that may be relevant, which we now discuss.
-
-\subsubsection{Massive Stellar Wind Energy}
-\label{sec:stellar winds discussion}
-Our massive stellar wind model drastically reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$.
-Although our algorithm is entirely capable of generating realistic stellar winds with velocities comparable to those observed, such fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical.
-When considered in isolation, stellar winds are an important source of pre-SN feedback and can dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}.
-However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}, unless densities near the ionizing source are high enough to trap the  HII region in the source cell.
-In that case, they can clear out a cavity to allow initial establishment of the HII region.
-
-They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}.
-Although they likely have minimal dynamical importance at resolutions where peak densities are not anyway high enough to trap ionization fronts, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting closer examination in future work.
-
-\subsubsection{Cosmic Rays} 
-\label{sec:CRs}
-
-Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}.
-These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}.
-Modeling cosmic rays is challenging, however, as they encompass a wide range of energies, and there are significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}.
-Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy.
-In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM.
-Modeling cosmic ray feedback completely thus requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena.
-Finally, including MHD presents additional difficulties in untangling the effects of each individual feedback mechanism on galaxy chemodynamics.
-
-We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested.
-Mechanically, including this relatively simple treatment of cosmic ray feedback in our model is trivial.
-However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to later work.
-
-\subsection{Detailed Stellar Evolution and Binary Stars}
-\label{sec:binary stars}
-
-Roughly half of massive stars live in binary pairs \citep{Sana2013}.
-Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes.
-This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as SNe.
-This effect could be significant, but is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g.
-STARBURST99).
-For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse SNe occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr.
-Although they find only $\sim 15\%$ of core collapse SNe explode after 50~Myr, this could still be an important effect.
-Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}.
-Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.
-
-Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars.
-This is beyond the scope of this project, but will be investigated in future work.
-
-\section{Conclusion}
-\label{sec:conclusion}
-We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
-For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, using individual star particles to model core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, Lyman-Werner radiation and pollution from AGB and massive stellar winds.
-This treatment of feedback, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail.
-In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P dwarf galaxy.
-We present an overview of the properties of this simulation in this work.
-
-For our simulated dwarf galaxy, we find:
-\begin{enumerate}
-\item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
-(See Figs.~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).
-
-\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, falling to $\eta \sim 10$ at R$_{\rm vir}$,  and
-metal mass loading factors near unity.
-By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Fig.~\ref{fig:outflow_velocity}).
-
-\item 
-Only $\sim$4\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of low-mass dwarfs.
-By the end of the simulation $\sim$45\% of the remaining metals stay within the virial radius (but outside the galaxy), while $\sim$50\%
-have been ejected beyond the virial radius. (See Figs.~\ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
-
-\item 
-Beyond the stellar radius, the gas scale height is thin ($\sim 50$~pc), yet resolved, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius.
-This is comparable to the resolution limit of the diffuse HI in observed, gaseous low-mass dwarfs.
-At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Fig.~\ref{fig:scale_height}).
-
-\item The ISRF of our galaxy varies strongly in both space and time by orders of magnitude.
-It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile.
-The importance of radiation feedback in our model will be investigated in a future work.
-(See Figs.~\ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
-
-\item 
-We find H$_2$ fractions below 5\% in our dwarf galaxy, consistent with the poor constraints on molecular gas formation in low metallicity dwarf galaxies.
-This H$_2$ forms entirely through gas-phase reactions facilitated by H$^{-}$ in self-shielding regions; H$_2$ formation on dust grains and in the three body reaction are both insignificant.
-Cold, neutral hydrogen dominates the mass of our galaxy.
-While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Fig.~\ref{fig:sfr_mass_evolution} and Fig.~\ref{fig:ISM_evolution}.)
-
-\item Finally, we present gas-phase oxygen and nitrogen distributions as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy.
-These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs.
-SNe), as suggested by \cite{KrumholzTing2018}.
-This will be explored in more detail in future work (Emerick et.
-al.
-\textit{in prep.}).
-\end{enumerate}
-
-\section*{Acknowledgments:} 
-We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B.
-C\^ot\'e, S.
-Glover, K.
-Hawkins, C.
-Hu, K.
-Johnston, B.
-O'Shea, M.
-Putman, B.
-Smith, J.
-Wall, and J.
-Wise.
-We would additionally like to thank the referee for their careful report.
+\subsection{Impact on Stellar Abundance Patterns}
+\label{sec:stellar abundances}
+In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star-forming gas in our simulations.
+This could be used to help disentangle sources of scatter in observed stellar abundances, including radial/azimuthal abundance gradients and stellar migration, redshift evolution, asymmetric accretion of pristine gas, and the intrinsic scatter in ISM abundances.
+If the metal mass fractions in star-forming gas in our simulations can also be well fit by log-normal + power-law PDFs, and if we can parameterize their evolution as functions of global galaxy properties, this could be used as a powerful tool for modeling stellar abundance patterns in semi-analytic models.
+This would be a physically motivated way to account for both the intrinsic spread in stellar abundances due to inhomogeneities in the ISM and variations in mixing for different metal species.
+We reserve an analysis of these distributions in abundance space in both the gas and stars for future work.
+However, we briefly discuss the connection to star-forming gas and stellar enrichment below.
+
+Unfortunately, there is insufficient star-forming gas at any one time in our simulations to construct PDFs of metal mass fractions.
+However, star-forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, to have mass fraction PDFs similar to the CNM.
+To verify this, Figure ~\ref{fig:stars} shows the difference between the oxygen mass fraction of stars and the median mass fraction from the CNM PDF at the time that particle formed.
+The large scatter at early times ($<$ 120~Myr) is a result of the early enrichment phase, when the initial gas oxygen mass fraction was zero.
+Stars seem to be sampled evenly around the median of the CNM distribution, with only a slight bias (52\% of stars) towards values below the median.
+However, for stars formed after the initial phase, the median separation from the CNM median is 0.31~dex, and can reach up to $\sim$~0.5~dex.
+Though a significant deviation, this is smaller than the typical inner-quartile range (IQR) of the CNM (see Figure~\ref{fig:phase-statistics}).
+Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
+High density gas, from which star formation occurs, is not biased towards higher metallicity in cold gas.
+
+%KVJ suggested emphasizing that there is much more potential in this work / work like this by examining more dimensions
+We emphasize that this study focuses on each chemical dimension independently, as a means to first understand galactic chemical enrichment in the simplest possible framework.
+However, the cross-correlation of multiple metal fractions and abundance ratios is the most useful in revealing key processes in galactic chemodynamics.
+A study in this multi-dimensional chemical space is key to understand the relative timescales over which certain enrichment events become important, the number of distinct nucleosynthetic channels that determine observed stellar abundance patterns, and is required for chemical tagging experiments.
+We will examine this more complicated multi-dimensional space with these numerical methods in future work.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
+\caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the time within 1~Myr (our time resolution) of each star's formation time.
+The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
+\label{fig:stars}
+\end{figure}
+
+\subsection{Do These Results Apply to More Massive Galaxies?}
+\label{sec:massive galaxies}
+An important caveat about our work is that these results are derived from simulations of an isolated, low mass, dwarf galaxy whose properties vary dramatically from more massive galaxies like the Milky Way.
+It is unclear how much these results apply to more massive galaxies with deeper potential wells and higher star formation rates.
+Feedback-driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
+We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy.
+With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
+We anticipate three potential regimes of metal retention, depending on dark matter halo mass and SFR: i) at very low halo mass, even below that examined here, there is equally poor retention of metal enrichment from both AGB stars and SNe, ii) AGB enrichment is preferentially retained, but SN enrichment is ejected efficiently (as is the case in this study), and iii) both sources are well retained in the galaxy's ISM.
+If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform.
+% AE: rewording given Benoits suggested changes
+%     If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+This difference would be greater at later times, once AGB enrichment becomes significant. 
+%     Benoit suggested limiting / eliminating discussion relative to metallicity, since this is a little murky (age-metallicity varies significantly galaxy-to-galaxy).
+In addition, the elevated signals of Ba abundance ratios I mention have some amount of contention....
+%     For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}.
+At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way.
+Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way.
+In addtion, recent observations find elevationd [Ba/Fe] vs.
+[Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS}, which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs.
+Given the lack of definitive explanation, clearly generalizing our results and detailing their observational consequences is a valuable area of future research.
+We would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way.
+
+In contrast, we expect the properties of the enrichment PDFs, and the variations between AGB enriched elements and SN enriched elements (as presented in Figures~\ref{fig:log-normal} and ~\ref{fig:phase-statistics}), to be general.
+We expect metals to exhibit log-normal + power-law distributions in the ISM of all galaxies, with similar trends with enrichment source and gas phase as outlined here.
+However, the detailed properties of the PDFs (e.g, log-normal width, power-law slope) likely depend non-trivially on global galaxy properties.
+How these results vary as a function of galaxy properties will be investigated in future work.
+
+\subsection{Implications for Exotic Enrichment Sources}
+\label{sec:exotic enrichment}
+%   AE: Benoit suggested removing arguments relating to NS-NS merger energetics as I had misred / miscaclulated the energy release values.
+He said greater emphasise on potential differences of mixing due to rarity, rather than energy.
+We have shown that the dynamical evolution of metals depends upon their nucleosynthetic source, focusing here on AGB synthesized elements and SN synthesized elements.
+However, these differences should also apply to exotic enrichment sources, such as hypernovae, neutron-star neutron-star mergers, and neutron-star black-hole mergers.
+These sources can have energies that differ significantly from typical SNe, reaching $> 10^{52}$~erg for hypernovae \citep{Nomoto2004}, for example.
+In addition,
+%mm the rarity of these events, for example,  there are approximately $10^{-5}$ per M$_{\odot}$ of star formation NSM in the Milky Way, could
+     these events are rare.  For example, neutron star mergers occur 
+     at a rate of approximately $10^{-5}$ per M$_{\odot}^{-1}$ of star
+     formation in the Milky Way\citep{Kim2015}.  This rarity could 
+significantly influence the typical ISM environments into which they eject their metals.
+We would therefore expect different mixing behaviors for metals synthesized through these channels as compared to SNe.
+Based on our results here, for example, we would expect elements from hypernovae to be more well mixed in the ISM of all galaxies, but more readily ejected in dwarf galaxies, as compared to elements from SNe.
+% Benoit suggesed removing this given energy argument removal above
+%    Elements from NSMs, a significant source of r-process enrichment, would be less well-mixed in the ISM of all galaxies and more easily retained than SNe elements in dwarf galaxies. 
+Depending on their injection energy, neutron star mergers could exhibit different mixing behaviors in the ISM.
+These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
+In particular, low mass dwarf galaxies with unusual (compared to Milky Way, solar abundances) r-process enrichment \citep[e.g.][]{Ji2016,Ji2018,Duggan2018}, are valuable for constraining the source of these elements, their frequency, and typical yields.
+The differential metal evolution presented in our work both opens up an additional avenue by which elements from distinct nucleosynthetic sources may be distinguished in observations and challenges current assumptions used in interpreting these observations.
+
+\subsection{Individual Stars vs. Averaged Yields}
+\label{sec:SSP yields}
+\textbf{Typical models for chemical enrichment in galaxy-scale simulations apply some form of IMF-averaged nucleosynthetic yields.
+Unfortunately, it is beyond the scope of this work to investigate how our results might change when adopting an IMF-averaged yield model.
+However, to what degree stochastic IMF sampling, mass-dependent nucleosynthetic yields, and the dynamical decoupling of individual enrichment sources play in galactic chemical evolution are valuable questions to address in future research.
+We speculate that an IMF-averaged enrichment model will only capture the differences between enrichment sources seen here if the model: 1) captures a multi-phase, turbulent ISM, 2) accounts for the energetic differences between yields from different enrichment sources, and 3) accounts for the time-delay between different enrichment sources.
+Models which average over an entire stellar population and ignore these effects may be unable to reproduce our results.}
+
+\section{Conclusions}
+\label{sec:conclusions}
+We present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
+This high resolution simulation, coupled with our star-by-star modeling of stellar nucleosynthetic yields, has allowed us to analyze for the first time how individual metal species couple to the ISM and galactic wind of this galaxy.
+
+We find that individual metal species do not share the same dynamical evolution, with differences directly related to nucleosynthetic origin (AGB winds, winds from massive stars, or core collapse SNe).
+This difference is most significant, in our model, between elements ejected predominately by AGB winds and those ejected predominantly by core-collapse SNe.
+In addition, we find the novel result that the mass fraction PDFs of each metal in the ISM can be described using an analytic piecewise log-normal + power-law PDF.
+The properties of these PDFs vary with both ISM phase and metal species, again driven mostly by differences in enrichment sources.
+
+We summarize our results as follows:
+\begin{itemize}
+
+%\item Elements from lower energy enrichment sources (i.e.
+AGB winds) are preferentially retained in the ISM of low mass dwarf galaxies as compared to those from higher energy sources (SNe), which are more readily launched in galactic winds.
+This result is likely sensitive to global galaxy properties, becoming less significant with increasing halo mass.
+We predict the abundance ratios between AGB wind dominated metals (s-process elements) and SN dominated metals ($\alpha$ elements) to be higher at fixed metallicity in low mass dwarf galaxies than in more massive galaxies, like the Milky Way.
+
+\item Power-law tails on log-normal metal fraction PDFs are a natural consequence of ongoing chemical enrichment, with the power-law slope related to the rate at which mixing dilutes newly enriched gas.
+
+\item Hotter phases have metal fraction PDFs that are more enriched, with significant power-law tails as compared to cold phases, which have a more prominent log-normal component.
+The lack of significant tails in the cold-phase PDFs indicates that metal mixing occurs rapidly in hotter phases before cooling and/or mixing into denser gas.
+
+\item Metal outflow in low mass dwarf galaxies depends upon nucleosynthetic site.
+Metals from lower energy enrichment events (e.g.
+AGB winds) are preferentially retained in the ISM as compared to those from higher energy events (e.g.
+SNe).
+The degree to which this is true likely depends upon global galaxy properties such as star formation rate, dark matter potential well, and gas geometry.
+
+\item Likewise, metals originating in AGB winds are less well mixed in the ISM, with spreads of over 1 dex in cold gas, as compared to metals injected through SNe, with spreads of about 0.5~dex
+
+\item Metal distributions exhibit positive skew, such that the mean metal fraction can be anywhere from 0.1 to 1.0 dex above the median metal fraction.
+Simple chemical evolution models, which generally follow the mean abundance, and thus can not account for complex metal mixing physics, are likely biased towards higher enrichment values.
+
+\end{itemize}
+
+%mm [you argued above that the wind results would NOT necessarily be general.
+I'm not sure I like the formulation about entrainment of the ambient ISM, though.] We expect these results to be general for more massive galaxies and galaxy properties.
+However, it may be the case that metals couple more uniformly to galactic winds in more massive galaxies as wind driving occurs increasingly through entrainment of the ambient ISM rather than the ejection of individual enrichment events.
+This warrants further examination.
+But interpreting these results for low mass dwarf galaxies
+    Extending these results to low-mass dwarf galaxies in general, we expect that: 1) s-process elements from AGB winds should exhibit larger spreads than $\alpha$ elements released through SNe and 2) these elements should be overabundant in dwarf galaxies at fixed age, as compared to massive galaxies like the Milky Way.
+% Removed as-per Benoit's suggestion:
+% , and 3) that r-process enrichment from NS-NS mergers should behave similarly to s-process elements from AGB winds, as compared to $\alpha$ elements
+
+\acknowledgments
 A.E.
@@
 M.-M.M.L.
-was partly funded by NASA  grant NNX14AP27G.
+was partly funded by NASA  grant NNX14AP27G and by NSF grant AST18-15461.
+B.C.
+acknowledges support from the ERC Consolidator Grant (Hungary) funding scheme (project RADIOSTAR, G.A.
+n.
+724560) and from the National Science Foundation (USA) under grant No.
+PHY-1430152 (JINA Center for the Evolution of the Elements).
+B.W.O was supported in part by NSF grants PHY-1430152 and AST-1514700, by NASA grants NNX12AC98G, and NNX15AP39G, and by Hubble Theory Grant HST-AR-14315.001-A.
 We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute.
@@
 
-%\bibliographystyle{yahapj}
-\bibliographystyle{mnras}
+\facilities{XSEDE (Stampede, Stampede-2), ADS} % there is no ApJ kewword for this: NASA HECC (Pleiades)}
+\software{Numpy, Enzo, yt, astropy}
+
+\bibliographystyle{yahapj}
 \bibliography{msbib}
@@
 
-\section{Gas Phases of the ISM}
-\label{appendix:phases}
-
-To aid in comparison to other works, we define our ISM phases here, as adopted and modified from \citet{Draine2011}, Table 1.3, and used consistently throughout this analysis.
-By construction, these phases are mutually exclusive.
-We take $f_{\rm H_2}$ to be the molecular hydrogen fraction of the total gas mass.
-
-\begin{enumerate}
-\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
-\item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
-\item Warm Neutral Medium (WNM): $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$
-\item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
-\item Molecular: $T < 10^2$~K, $f_{\rm H_2} > 0.5$
-\end{enumerate}
-
-\section{Stellar Radiation Properties}
-\label{appendix:radiation}
-We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Fig.~\ref{fig:stellar radiation properties} we plot these properties.
-We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
-This requires two factors for each radiation type, one for low mass and one for high mass stars.
-We use the following multiplicative factors to adjust the black body spectrum for HI and HeI ionizing radiation respectively: [0.1, 3.2] and [0.0001, 4.0].
-We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.
-
-The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid.
-A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section.
-We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \url{http://www.pa.uky.edu/~verner/photo.html}}
-The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision.
-Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.
+\section{Density PDF}
+\label{appendix:density PDF}
+We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}.
+We show the mass-weighted PDF ($dm/Md\log n$) on the left, and the volume-weighted PDF ($dv/Vd\log n$) on the right.
+As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution.
+The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.
+The volume weighted PDF is much better described as a multi-component power law.
+The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities.
+These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.
+
+%mm [you could cut this if you want.]
+%It is worth noting that this PDF shows the rather small cold gas 
+%     fraction found in these models in comparison to the Milky Way
+%      ISM, where roughly half the mass is found in cold gas 
+%      \citep{Ferriere2001}.
+Finally, \cite{Hopkins2013} suggests a different functional form for describing these PDFs across a range of idealized simulations, but it still may be insufficient to fully describe the density PDF in realistic galaxy simulations.
+Clearly, we are far from a general understanding of mass-weighted and volume-weighted density PDFs in the case of a turbulent, self-gravitating, multi-phase ISM.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.475\linewidth]{density_PDF.png}
+\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted.png}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr.
+The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
+\label{fig:density_pdf}
+\end{figure}
+
+\section{Resolution Comparison}
+We perform a resolution test to confirm that the key results of this study are convergent, at least qualitatively.
+Given the variations in star formation rate, feedback effectiveness, and stochasticity in our model, we do not expect exact numerical convergence in any one quantity.
+We conduct two lower resolution simulations with a maximum physical resolution of 3.6 pc and 7.2 pc.
+We refer the reader to Paper I for a previous comparison of these simulations to our fiducial run.
+In Figure~\ref{fig:resolution-phase} we demonstrate that O and Ba abundances behave qualitatively similar in our lower resolution runs as in our fiducial model.
+In both lower resolution runs O has a generally tighter distribution that narrows over time, while Ba is much less well mixed, in agreement with our fiducial simulation.
+The exact numerical values for these spreads are not convergent across simulations, but we do note significant variations in the exact SFH of these lower resolution runs could be driving these differences.
 
@@
 \centering
-\includegraphics[width=0.4\linewidth]{Q0}
-\includegraphics[width=0.4\linewidth]{Q1}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{L_FUV}
-\includegraphics[width=0.4\linewidth]{L_LW}
-\vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{E0}
-\includegraphics[width=0.4\linewidth]{E1}
-\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right).
-Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
-\label{fig:stellar radiation properties}
+\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study.png}
+\caption{Resolution comparison of two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.
+Compare to Figure~\ref{fig:phase-statistics}.}
+\label{fig:resolution-phase}
 \end{figure*}
 
-\setcounter{figure}{0}
-\section{Typical Gas Densities in Supernova Injection Regions}
-\label{appendix:SN}
-
-Modeling SN feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of SN feedback.
-Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time.
-However, physically consistent solutions have been developed \citep[e.g][]{Simpson2016} that inject a mixture of kinetic and thermal energy with a ratio that depends on resolution and local gas density.
-Overcooling becomes less important with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each SN.
-We take advantage of our high resolution and employ a simple thermal energy injection model for our SN feedback.
-We demonstrate how well this resolves our SNe in the comparison simulation presented in this work.
-
-The left panel of Fig.~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
-As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
-For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations.
-The right panel of Figure ~\ref{fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
-\begin{equation}
-R_{\rm PDS} = 
-\begin{cases}
-49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z \le 0.01 \\
-18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z \ge 0.01 \\
-\end{cases}
-\end{equation}
-where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$.
-\citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the SN explosion with thermal energy injection alone, assuming uniform density in the injection region.
-In practice, the injection region is never uniform.
-We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each SN.
-As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but up to 8.3\% are not well resolved and 2.0\% are completely unresolved (below a single cell width).
-In general, these are SN explosions from the most massive (i.e.
-most prompt) stars.
-We do not expect that resolving these SNe will dramatically alter our results.
-However, we note that using our feedback model at resolutions much less than a few parsecs will require implementing an different injection mechanism.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.4\linewidth]{sn_density_hist}
-\includegraphics[width=0.4\linewidth]{sn_radius_hist}
-\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation.
-{\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each SN assuming a uniform medium at either the peak or average density in the injection region.
-The vertical lines show one and 4.5 cell widths.
-This shows that a fraction of these SNe are certainly unresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
-\label{fig:SN histogram}
-\end{figure*}
-
-\setcounter{figure}{0}
-\section{Cooling and Heating Rates}
-\label{appendix:cooling}
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
-\caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background.
-Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the uncorrected (i.e.
-optically thin) metal line cooling rates.
-The regimes where heating dominates are plotted with dashed lines for clarity.}
-\label{fig:cooling comparison}
-\end{figure*}
-
-The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with a self-shielding approximations.
-\citet{Hu2017} details this inconsistency: metal cooling rates computed under the assumption of an optically thin UV background overestimate the electron fraction in regimes where self-shielding is important ($-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$).
-This results in an artificially enhanced metal line cooling rate in regions of self-shielding.
-This can be a significant effect, particularly at higher metallicities.
-We demonstrate this in Fig.~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
-The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
-In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
-Fig.~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
-We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
-
-For densities where self-shielding is important, we computed \textsc{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length.
-In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud.
-We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UV background.
-These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}.
-In computing these tables we had to include the cosmic ray ionization that dominates in optically thick clouds.
-Without this effect, \textsc{Cloudy} becomes unstable in entirely neutral regions.
-We adopted a cosmic ray ionization rate of 10\% the Milky Way value, though we note that varying this from 1\% to 100\% the Milky Way value did not have an effect on the extracted metal line cooling rates.
-
-Finally, we note that the cooling and heating rates in our simulation will deviate from these curves, as they depend upon local conditions that cannot be accounted for here.
-The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which is not included in these diagrams.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.95\linewidth]{cooling_curve}
-\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}.
-The absolute value of the net cooling or heating
-rate is shown with solid lines.}
-\label{fig:cooling}
-\end{figure*}
-
-\setcounter{figure}{0}
-\section{H$^{-}$ Photodetachment}
-\label{appendix:H minus}
-
-As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations.
-Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, can be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}.
-Our current model does not include this contribution.
-To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https://grackle.readthedocs.io/en/latest/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) and initial temperature of 10$^{4}$~K for 200~Myr.
-In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background.
-As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate.
-In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left).
-A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.
-
-We follow up on the qualitative conclusions of these models by running four simulations at the four points in the diagram.
-\textbf{These runs have identical initial conditions, SNe driving, cooling, heating, and chemistry as our fiducial simulation, but with no star formation.} In each, we vary the radiation band by a factor of 100 each, which is comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}).
-Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9.
-Applying both scale factors gives a reduction of 7.9.
-Thus, we see that the difference between the more realistic case in which both rates increase by the same factor, and the case assumed in the simulations, is only about 20\%.
-
-\textbf{Although the lack of star formation in these models produces qualitatively different galaxy properties, the point of these simulations is to be maximal models of H$_2$ formation.
-We demonstrate that, even in this case, there is not a dramatic change in the total H$_2$ formation and that the effect of varying the H- photodetachment rate is sub-dominant to other factors.
-Therefore, we do not expect that ignoring this component of the stellar radiation field will have a significant dynamical impact on our galaxy evolution.}
-
-\begin{figure}
-\centering
-\includegraphics[width=0.95\linewidth]{fH2.png}
-\caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation.
-Each model is held at a uniform density $n = 10$~cm$^{-3}$.
-Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor.
-Contours give factors of ten change in the H$_2$ fraction.
-We note the regime below 1.0 on each axis is somewhat unphysical, and is never reached in our hydrodynamics simulations.}
-\label{fig:Grackle grid}
-\end{figure}
-
-H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV.
-For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction.
-The Lyman-Werner radiation field is dominated by short-lived massive stars, with some contribution from older stars up to a few hundred Myr, and is thus subject to significant fluctuations, particularly in periods of no star formation.
-During these times, H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation.
-Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars.
-Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked.
-
-As emphasized in Section~\ref{sec:molecular gas content}, further work modeling low-metallicity dwarf galaxies with a more detailed chemistry model would be useful to clarify the role of various competing phenomena in driving the molecular properties of these galaxies.
-
-\setcounter{figure}{0}
-\section{Resolution Study}
-\label{appendix:resolution_study}
-
-We demonstrate the effect of varying resolution in the evolution of our galaxy model in Fig.~\ref{fig:resolution_study}.
-We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines).
-The physics in each simulation remains the same with the exception of star formation, which employs a resolution-dependent density threshold.
-A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively.
-As a result, the time at which star formation first occurs varies between the simulations, but we again define t = 0 as the time of first star formation in each simulation.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.33\linewidth]{sfr_resolution_study.png}
-\includegraphics[width=0.33\linewidth]{mass_evolution_resolution.png}
-\includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
-\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted).
-The line colors in the left panel are for better clarity between the SFRs.}
-\label{fig:resolution_study}
-\end{figure*}
-
-Fig.~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
-We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
-The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs.
-We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Fig.~\ref{fig:SN histogram}.
-However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
-
-Generally ineffective feedback leads to increased, not decreased, star formation rates.
-However, the lower resolution run has the lowest SFR.
-The source of this difference is likely related to the ability to resolve dense, cold gas in the lower resolution simulations.
-In particular, the low resolution simulation clearly is unable to resolve the densities at which gas-phase H$_2$ formation becomes efficient, leading to significantly lower H$_2$ fractions (middle panel) and lower cooling rates.
-In addition, whatever H$_2$ does form at these lower resolutions exists at lower gas densities than in our fiducial run, and is less well protected by self-shielding effects.
-This is shown clearly in the significant plummet in the H$_2$ mass during the phase of first star formation that is less severe in our fiducial run.
-In this low metallicity regime, where H$_2$ is an important coolant, the ability to resolve the densities responsible for H$_2$ formation and self-shielding is important.
-
-Theses differences in densities are shown clearly by comparing Fig.~\ref{fig:phase} with Fig.~\ref{fig:phase_resolution}.
-Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.
-In the 7.2~pc run, the gas phases are notably less distinct, with gas more evenly smoothed out in the multi-phase region between cold, dense gas and warm, ionized gas.
-We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature ceiling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.
-
-\begin{figure*}
-\centering
-\includegraphics[width=0.475\linewidth]{3pc_phase.png}
-\includegraphics[width=0.475\linewidth]{6pc_phase.png}
-\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:phase}.}
-\label{fig:phase_resolution}
-\end{figure*}
-
-Finally, the metal retention fraction (right panel) between the fiducial and 3.6~pc runs are quite similar, but is significantly higher for the lowest resolution simulation.
-It is likely, however, that this is a result of the lower SFR in the 7.2~pc run and is not directly a resolution effect.
-This also affects the fraction of metals ejected outside the virial radius, with less metals being ejected in the lower resolution runs.
-
-\label{lastpage}
-
 \end{document}

### 2018-10-29 main.tex
removing textbfs for final version

@@
 Doing so requires the kinds of high resolution, galaxy-scale multi-element chemodynamical simulations that have only become feasible in recent years.
-\textbf{Recent work has suggested that low-mass dwarf galaxies are perhaps the best regime to begin understanding these processes \citep[e.g.][]{Bland-Hawthorn2010a,Bland-Hawthorn2010b,Karlsson2012,Webster2016}.
-This is advantageous, as their small physical size and low star formation rates makes conducting high resolution, hydrodynamics simulations of these systems computationally feasible.}
+Recent work has suggested that low-mass dwarf galaxies are perhaps the best regime to begin understanding these processes \citep[e.g.][]{Bland-Hawthorn2010a,Bland-Hawthorn2010b,Karlsson2012,Webster2016}.
+This is advantageous, as their small physical size and low star formation rates makes conducting high resolution, hydrodynamics simulations of these systems computationally feasible.
 
@@
 We include initial SN driving to limit the transient burst of star formation from the initial cooling and collapse of the galaxy.
-\textbf{These SNe are randomly distributed with the same radial and vertical scale heights as the gas disk at a rate of 0.4~Myr$^{-1}$; this corresponds to the current SFR of Leo P, $\sim 4\times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ \citep{McQuinn2015a}, assuming 1 SNe per 100 M$_{\odot}$ of star formation.
-The metal yields from these SNe are set to the mean ISM abundances, and thus do not contribute to the chemical evolution of the galaxy.} Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
+These SNe are randomly distributed with the same radial and vertical scale heights as the gas disk at a rate of 0.4~Myr$^{-1}$; this corresponds to the current SFR of Leo P, $\sim 4\times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ \citep{McQuinn2015a}, assuming 1 SNe per 100 M$_{\odot}$ of star formation.
+The metal yields from these SNe are set to the mean ISM abundances, and thus do not contribute to the chemical evolution of the galaxy.
+Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero.
 Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.
@@
 Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}.
-It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape \textbf{\citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2018}}.
+It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2018}.
 This includes a log-normal component, generated by multiplicative processes---in this case shocks and the turbulent cascade in the ISM---and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures .
@@
 
-Unsurprisingly the diffuse HIM \textbf{is the most metal rich phase}, as it is comprised predominately of metal enriched SN ejecta.
+Unsurprisingly the diffuse HIM is the most metal rich phase, as it is comprised predominately of metal enriched SN ejecta.
 Clearly this leads to long power-law tails towards high metal fractions for each species, with a very narrow, poorly defined peak at low metal fractions.
@@
 Again these differences between yield sources could be driven both by differences in their enrichment timescales and therefore differences in the typical ISM environment each event encounters, and the differences in energetics between AGB winds and SNe.
-\textbf{AGB wind elements enrich the WNM and WIM directly, rather than the HIM.
-This leads to longer mixing timescales and broader PDFs for these elements.}
+AGB wind elements enrich the WNM and WIM directly, rather than the HIM.
+This leads to longer mixing timescales and broader PDFs for these elements.
 
@@
 \label{sec:SSP yields}
-\textbf{Typical models for chemical enrichment in galaxy-scale simulations apply some form of IMF-averaged nucleosynthetic yields.
+Typical models for chemical enrichment in galaxy-scale simulations apply some form of IMF-averaged nucleosynthetic yields.
 Unfortunately, it is beyond the scope of this work to investigate how our results might change when adopting an IMF-averaged yield model.
@@
 We speculate that an IMF-averaged enrichment model will only capture the differences between enrichment sources seen here if the model: 1) captures a multi-phase, turbulent ISM, 2) accounts for the energetic differences between yields from different enrichment sources, and 3) accounts for the time-delay between different enrichment sources.
-Models which average over an entire stellar population and ignore these effects may be unable to reproduce our results.}
+Models which average over an entire stellar population and ignore these effects may be unable to reproduce our results.
 

### 2019-03-07 ms.tex
cpation update

@@
 Each panel is 4 kpc x 4 kpc.
-The full movie of this evolution is included for further clarification of the comparison between this figure and Fig.~\ref{fig:panel2}.}
+The full movie of this evolution \textbf{from 0 to 118 Myr} is included for further clarification.
+\textbf{This movie demonstrates that the differences in outflows between the simulations depends on the ability for feedback to carve low-density, ionized channels along which SNe can launch gas beyond the disk of the galaxy.
+These channels are readily created by ionizing radiation in the fiducial simulation, or to some degree by SNe in the noRT simulation due to its much higher SN rate.
+However, SNe launched gas is trapped by neutral, cold shells in the shortrad simulation, unable to easily escape from the disk of the simulated galaxy.
+These same insights can also be gained by comparing this figure with Figure~\ref{panel2}.}}
+\label{fig:panel1}}
 \label{fig:panel1}

### 2019-03-07 pdf.sh
commit

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+convert DD0136_fiducial_shortrad_nort.png DD0136_fiducial_shortrad_nort.pdf
+convert DD0160_fiducial_shortrad_nort.png DD0160_fiducial_shortrad_nort.pdf
+convert mass_density_cut.png mass_density_cut.pdf
+convert mass_loading_comparison.png mass_loading_comparison.pdf
+convert mass_outflow_comparison.png mass_outflow_comparison.pdf
+convert mass.png mass.pdf
+convert metal_retention.png metal_retention.pdf
+convert sfr.png sfr.pdf

### 2019-03-07 ms2.tex
commit

--- 2018-09-04 ms.tex
@@
 However, it warrants further study as to how much this effect can be accounted for without resorting to full radiative transfer calculations.
-Approximate, Str{\"o}mgren-like feedback models which allow for ionization far from a single source \citep[e.g.][]{Hopkins2018} may be sufficient to capture the effects shown here.
+Approximate, Stromgren-like feedback models which allow for ionization far from a single source \citep[e.x.][]{Hopkins2018} may be sufficient to capture the effects shown here.
 Fully localized methods, or methods which set a maximum for the ionization radius may underestimate galactic wind properties in dwarf galaxies.
-In addition, both methods are mass biased \citep[see the discussion in ][]{Hu2017}, preferentially over-ionizing dense gas that would otherwise be missed by photons leaking through channels carved through lower-density gas.
+However, both methods are mass biased \citep[see the discussion in ][]{Hu2017}, preferentially over-ionizing dense gas that would otherwise be missed by photons leaking through channels carved through lower-density gas.
 These remaining uncertainties motivate a continued examination of the feedback prescriptions adopted in high resolution simulations of galaxy evolution.}
@@
 G.L.B.
-acknowledges support from NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
+is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955.
 M.-M.M.L.
@@
 
-\bibliography{msbib}
+\begin{thebibliography}{}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Abbott}(1982)}]{Abbott1982}
+{Abbott}, D.~C. 1982, \apj, 263, 723
+
+\bibitem[{{Agertz} {et~al.}(2013){Agertz}, {Kravtsov}, {Leitner}, \&
+  {Gnedin}}]{Agertz2013}
+{Agertz}, O., {Kravtsov}, A.~V., {Leitner}, S.~N., \& {Gnedin}, N.~Y. 2013,
+  \apj, 770, 25
+
+\bibitem[{{Bressan} {et~al.}(2012){Bressan}, {Marigo}, {Girardi}, {Salasnich},
+  {Dal Cero}, {Rubele}, \& {Nanni}}]{Bressan2012}
+{Bressan}, A., {Marigo}, P., {Girardi}, L., {et~al.} 2012, \mnras, 427, 127
+
+\bibitem[{{Bryan} {et~al.}(2014){Bryan}, {Norman}, {O'Shea}, {Abel}, {Wise},
+  {Turk}, {Reynolds}, {Collins}, {Wang}, {Skillman}, {Smith}, {Harkness},
+  {Bordner}, {Kim}, {Kuhlen}, {Xu}, {Goldbaum}, {Hummels}, {Kritsuk}, {Tasker},
+  {Skory}, {Simpson}, {Hahn}, {Oishi}, {So}, {Zhao}, {Cen}, {Li}, \& {The Enzo
+  Collaboration}}]{Enzo2014}
+{Bryan}, G.~L., {Norman}, M.~L., {O'Shea}, B.~W., {et~al.} 2014, \apjs, 211, 19
+
+\bibitem[{{Burkert}(1995)}]{Burkert1995}
+{Burkert}, A. 1995, \apjl, 447, L25
+
+\bibitem[{{Ceverino} {et~al.}(2014){Ceverino}, {Klypin}, {Klimek},
+  {Trujillo-Gomez}, {Churchill}, {Primack}, \& {Dekel}}]{Ceverino2014}
+{Ceverino}, D., {Klypin}, A., {Klimek}, E.~S., {et~al.} 2014, \mnras, 442, 1545
+
+\bibitem[{{Dale} {et~al.}(2014){Dale}, {Ngoumou}, {Ercolano}, \&
+  {Bonnell}}]{Dale2014}
+{Dale}, J.~E., {Ngoumou}, J., {Ercolano}, B., \& {Bonnell}, I.~A. 2014, \mnras,
+  442, 694
+
+\bibitem[{{Emerick} {et~al.}(2018){Emerick}, {Bryan}, \& {Mac
+  Low}}]{Emerick2018}
+{Emerick}, A., {Bryan}, G.~L., \& {Mac Low}, M.-M. 2018, ArXiv e-prints,
+  arXiv:1807.07182
+
+\bibitem[{{Ferland} {et~al.}(2017){Ferland}, {Chatzikos}, {Guzm{\'a}n},
+  {Lykins}, {van Hoof}, {Williams}, {Abel}, {Badnell}, {Keenan}, {Porter}, \&
+  {Stancil}}]{cloudy}
+{Ferland}, G.~J., {Chatzikos}, M., {Guzm{\'a}n}, F., {et~al.} 2017, \rmxaa, 53,
+  385
+
+\bibitem[{{Forbes} {et~al.}(2016){Forbes}, {Krumholz}, {Goldbaum}, \&
+  {Dekel}}]{Forbes2016}
+{Forbes}, J.~C., {Krumholz}, M.~R., {Goldbaum}, N.~J., \& {Dekel}, A. 2016,
+  \nat, 535, 523
+
+\bibitem[{{Hopkins} {et~al.}(2011){Hopkins}, {Quataert}, \& {Murray}}]{HQM2011}
+{Hopkins}, P.~F., {Quataert}, E., \& {Murray}, N. 2011, \mnras, 417, 950
+
+\bibitem[{{Hopkins} {et~al.}(2012){Hopkins}, {Quataert}, \& {Murray}}]{HQM2012}
+---. 2012, \mnras, 421, 3488
+
+\bibitem[{{Hopkins} {et~al.}(2018){Hopkins}, {Wetzel}, {Kere{\v s}},
+  {Faucher-Gigu{\`e}re}, {Quataert}, {Boylan-Kolchin}, {Murray}, {Hayward},
+  {Garrison-Kimmel}, {Hummels}, {Feldmann}, {Torrey}, {Ma},
+  {Angl{\'e}s-Alc{\'a}zar}, {Su}, {Orr}, {Schmitz}, {Escala}, {Sanderson},
+  {Grudi{\'c}}, {Hafen}, {Kim}, {Fitts}, {Bullock}, {Wheeler}, {Chan},
+  {Elbert}, \& {Narayanan}}]{Hopkins2018}
+{Hopkins}, P.~F., {Wetzel}, A., {Kere{\v s}}, D., {et~al.} 2018, \mnras,
+  arXiv:1702.06148
+
+\bibitem[{{Hu}(2018)}]{Hu2018}
+{Hu}, C.-Y. 2018, ArXiv e-prints, arXiv:1805.06614
+
+\bibitem[{{Hu} {et~al.}(2017){Hu}, {Naab}, {Glover}, {Walch}, \&
+  {Clark}}]{Hu2017}
+{Hu}, C.-Y., {Naab}, T., {Glover}, S.~C.~O., {Walch}, S., \& {Clark}, P.~C.
+  2017, \mnras, 471, 2151
+
+\bibitem[{{Hu} {et~al.}(2016){Hu}, {Naab}, {Walch}, {Glover}, \&
+  {Clark}}]{Hu2016}
+{Hu}, C.-Y., {Naab}, T., {Walch}, S., {Glover}, S.~C.~O., \& {Clark}, P.~C.
+  2016, \mnras, 458, 3528
+
+\bibitem[{Hunter(2007)}]{matplotlib}
+Hunter, J.~D. 2007, Computing In Science \& Engineering, 9, 90
+
+\bibitem[{Jones {et~al.}(2001--)Jones, Oliphant, Peterson, {et~al.}}]{scipy}
+Jones, E., Oliphant, T., Peterson, P., {et~al.} 2001--, {SciPy}: Open source
+  scientific tools for {Python}, [Online; accessed <today>]
+
+\bibitem[{{Keller} {et~al.}(2018){Keller}, {Wadsley}, {Wang}, \&
+  {Kruijssen}}]{Keller2018}
+{Keller}, B.~W., {Wadsley}, J.~W., {Wang}, L., \& {Kruijssen}, J.~M.~D. 2018,
+  ArXiv e-prints, arXiv:1803.05445
+
+\bibitem[{{Kim} {et~al.}(2018){Kim}, {Kim}, \& {Ostriker}}]{Kim2018}
+{Kim}, J.-G., {Kim}, W.-T., \& {Ostriker}, E.~C. 2018, \apj, 859, 68
+
+\bibitem[{{Kim} {et~al.}(2013){Kim}, {Krumholz}, {Wise}, {Turk}, {Goldbaum}, \&
+  {Abel}}]{Kim2013a}
+{Kim}, J.-h., {Krumholz}, M.~R., {Wise}, J.~H., {et~al.} 2013, \apj, 775, 109
+
+\bibitem[{{Kirby} {et~al.}(2011){Kirby}, {Martin}, \& {Finlator}}]{Kirby2011}
+{Kirby}, E.~N., {Martin}, C.~L., \& {Finlator}, K. 2011, \apjl, 742, L25
+
+\bibitem[{{Krumholz}(2018)}]{Krumholz2018}
+{Krumholz}, M.~R. 2018, \mnras, arXiv:1805.00210
+
+\bibitem[{{Lanz} \& {Hubeny}(2003)}]{LanzHubeny2003}
+{Lanz}, T., \& {Hubeny}, I. 2003, \apjs, 146, 417
+
+\bibitem[{{Leitherer} {et~al.}(1999){Leitherer}, {Schaerer}, {Goldader},
+  {Delgado}, {Robert}, {Kune}, {de Mello}, {Devost}, \&
+  {Heckman}}]{Leitherer1999}
+{Leitherer}, C., {Schaerer}, D., {Goldader}, J.~D., {et~al.} 1999, \apjs, 123,
+  3
+
+\bibitem[{{McQuinn} {et~al.}(2015){McQuinn}, {Skillman}, {Dolphin}, {Cannon},
+  {Salzer}, {Rhode}, {Adams}, {Berg}, {Giovanelli}, \& {Haynes}}]{McQuinn2015}
+{McQuinn}, K.~B.~W., {Skillman}, E.~D., {Dolphin}, A., {et~al.} 2015, \apjl,
+  815, L17
+
+\bibitem[{{Naab} \& {Ostriker}(2017)}]{NaabOstriker2017}
+{Naab}, T., \& {Ostriker}, J.~P. 2017, \araa, 55, 59
+
+\bibitem[{{Ocvirk} {et~al.}(2016){Ocvirk}, {Gillet}, {Shapiro}, {Aubert},
+  {Iliev}, {Teyssier}, {Yepes}, {Choi}, {Sullivan}, {Knebe}, {Gottl{\"o}ber},
+  {D'Aloisio}, {Park}, {Hoffman}, \& {Stranex}}]{Ocvirk2016}
+{Ocvirk}, P., {Gillet}, N., {Shapiro}, P.~R., {et~al.} 2016, \mnras, 463, 1462
+
+\bibitem[{{O'Shea} {et~al.}(2015){O'Shea}, {Wise}, {Xu}, \&
+  {Norman}}]{Oshea2015}
+{O'Shea}, B.~W., {Wise}, J.~H., {Xu}, H., \& {Norman}, M.~L. 2015, \apjl, 807,
+  L12
+
+\bibitem[{{Pawlik} {et~al.}(2015){Pawlik}, {Schaye}, \& {Dalla
+  Vecchia}}]{Pawlik2015}
+{Pawlik}, A.~H., {Schaye}, J., \& {Dalla Vecchia}, C. 2015, \mnras, 451, 1586
+
+\bibitem[{P\'erez \& Granger(2007)}]{Ipython}
+P\'erez, F., \& Granger, B.~E. 2007, Computing in Science and Engineering, 9,
+  21
+
+\bibitem[{{Peters} {et~al.}(2010){Peters}, {Klessen}, {Mac Low}, \&
+  {Banerjee}}]{Peters2010}
+{Peters}, T., {Klessen}, R.~S., {Mac Low}, M.-M., \& {Banerjee}, R. 2010, \apj,
+  725, 134
+
+\bibitem[{{Peters} {et~al.}(2017){Peters}, {Naab}, {Walch}, {Glover},
+  {Girichidis}, {Pellegrini}, {Klessen}, {W{\"u}nsch}, {Gatto}, \&
+  {Baczynski}}]{Peters2017}
+{Peters}, T., {Naab}, T., {Walch}, S., {et~al.} 2017, \mnras, 466, 3293
+
+\bibitem[{{Rosdahl} {et~al.}(2015){Rosdahl}, {Schaye}, {Teyssier}, \&
+  {Agertz}}]{Rosdahl2015}
+{Rosdahl}, J., {Schaye}, J., {Teyssier}, R., \& {Agertz}, O. 2015, \mnras, 451,
+  34
+
+\bibitem[{{Ro{\v s}kar} {et~al.}(2014){Ro{\v s}kar}, {Teyssier}, {Agertz},
+  {Wetzstein}, \& {Moore}}]{Roskar2014}
+{Ro{\v s}kar}, R., {Teyssier}, R., {Agertz}, O., {Wetzstein}, M., \& {Moore},
+  B. 2014, \mnras, 444, 2837
+
+\bibitem[{{Sales} {et~al.}(2014){Sales}, {Marinacci}, {Springel}, \&
+  {Petkova}}]{Sales2014}
+{Sales}, L.~V., {Marinacci}, F., {Springel}, V., \& {Petkova}, M. 2014, \mnras,
+  439, 2990
+
+\bibitem[{{Salpeter}(1955)}]{Salpeter1955}
+{Salpeter}, E.~E. 1955, \apj, 121, 161
+
+\bibitem[{{Smith} {et~al.}(2017){Smith}, {Bryan}, {Glover}, {Goldbaum}, {Turk},
+  {Regan}, {Wise}, {Schive}, {Abel}, {Emerick}, {O'Shea}, {Anninos}, {Hummels},
+  \& {Khochfar}}]{GrackleMethod}
+{Smith}, B.~D., {Bryan}, G.~L., {Glover}, S.~C.~O., {et~al.} 2017, \mnras, 466,
+  2217
+
+\bibitem[{{Smith} {et~al.}(2018{\natexlab{a}}){Smith}, {Sijacki}, \&
+  {Shen}}]{Smith2018a}
+{Smith}, M.~C., {Sijacki}, D., \& {Shen}, S. 2018{\natexlab{a}}, ArXiv
+  e-prints, arXiv:1807.04288
+
+\bibitem[{{Smith} {et~al.}(2018{\natexlab{b}}){Smith}, {Sijacki}, \&
+  {Shen}}]{Smith2018b}
+---. 2018{\natexlab{b}}, \mnras, 478, 302
+
+\bibitem[{{Somerville} \& {Dav{\'e}}(2015)}]{SomervilleDave2015}
+{Somerville}, R.~S., \& {Dav{\'e}}, R. 2015, \araa, 53, 51
+
+\bibitem[{{The Astropy Collaboration} {et~al.}(2018){The Astropy
+  Collaboration}, {Price-Whelan}, {Sip{\H o}cz}, {G{\"u}nther}, {Lim},
+  {Crawford}, {Conseil}, {Shupe}, {Craig}, {Dencheva}, {Ginsburg},
+  {VanderPlas}, {Bradley}, {P{\'e}rez-Su{\'a}rez}, {de Val-Borro}, {Aldcroft},
+  {Cruz}, {Robitaille}, {Tollerud}, {Ardelean}, {Babej}, {Bachetti}, {Bakanov},
+  {Bamford}, {Barentsen}, {Barmby}, {Baumbach}, {Berry}, {Biscani}, {Boquien},
+  {Bostroem}, {Bouma}, {Brammer}, {Bray}, {Breytenbach}, {Buddelmeijer},
+  {Burke}, {Calderone}, {Cano Rodr{\'{\i}}guez}, {Cara}, {Cardoso},
+  {Cheedella}, {Copin}, {Crichton}, {D{\'A}vella}, {Deil}, {Depagne},
+  {Dietrich}, {Donath}, {Droettboom}, {Earl}, {Erben}, {Fabbro}, {Ferreira},
+  {Finethy}, {Fox}, {Garrison}, {Gibbons}, {Goldstein}, {Gommers}, {Greco},
+  {Greenfield}, {Groener}, {Grollier}, {Hagen}, {Hirst}, {Homeier}, {Horton},
+  {Hosseinzadeh}, {Hu}, {Hunkeler}, {Ivezi{\'c}}, {Jain}, {Jenness}, {Kanarek},
+  {Kendrew}, {Kern}, {Kerzendorf}, {Khvalko}, {King}, {Kirkby}, {Kulkarni},
+  {Kumar}, {Lee}, {Lenz}, {Littlefair}, {Ma}, {Macleod}, {Mastropietro},
+  {McCully}, {Montagnac}, {Morris}, {Mueller}, {Mumford}, {Muna}, {Murphy},
+  {Nelson}, {Nguyen}, {Ninan}, {N{\"o}the}, {Ogaz}, {Oh}, {Parejko}, {Parley},
+  {Pascual}, {Patil}, {Patil}, {Plunkett}, {Prochaska}, {Rastogi}, {Reddy
+  Janga}, {Sabater}, {Sakurikar}, {Seifert}, {Sherbert}, {Sherwood-Taylor},
+  {Shih}, {Sick}, {Silbiger}, {Singanamalla}, {Singer}, {Sladen}, {Sooley},
+  {Sornarajah}, {Streicher}, {Teuben}, {Thomas}, {Tremblay}, {Turner},
+  {Terr{\'o}n}, {van Kerkwijk}, {de la Vega}, {Watkins}, {Weaver}, {Whitmore},
+  {Woillez}, \& {Zabalza}}]{astropy}
+{The Astropy Collaboration}, {Price-Whelan}, A.~M., {Sip{\H o}cz}, B.~M.,
+  {et~al.} 2018, ArXiv e-prints, arXiv:1801.02634
+
+\bibitem[{{Turk} {et~al.}(2011){Turk}, {Smith}, {Oishi}, {Skory}, {Skillman},
+  {Abel}, \& {Norman}}]{yt}
+{Turk}, M.~J., {Smith}, B.~D., {Oishi}, J.~S., {et~al.} 2011, \apjs, 192, 9
+
+\bibitem[{{Van Der Walt} {et~al.}(2011){Van Der Walt}, {Colbert}, \&
+  {Varoquaux}}]{numpy}
+{Van Der Walt}, S., {Colbert}, S.~C., \& {Varoquaux}, G. 2011, ArXiv e-prints,
+  arXiv:1102.1523
+
+\bibitem[{{Wise} \& {Abel}(2011)}]{WiseAbel2011}
+{Wise}, J.~H., \& {Abel}, T. 2011, \mnras, 414, 3458
+
+\bibitem[{{Wise} {et~al.}(2012){Wise}, {Abel}, {Turk}, {Norman}, \&
+  {Smith}}]{WiseAbel2012}
+{Wise}, J.~H., {Abel}, T., {Turk}, M.~J., {Norman}, M.~L., \& {Smith}, B.~D.
+  2012, \mnras, 427, 311
+
+\bibitem[{{Wood} \& {Churchwell}(1989)}]{WoodChurchwell1989}
+{Wood}, D.~O.~S., \& {Churchwell}, E. 1989, \apj, 340, 265
+
+\end{thebibliography}
 

### 2019-03-07 method_paper/main.tex

\documentclass[fleqn,usenatbib,useAMS]{mnras}
\pdfoutput=1 
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
%\usepackage{pdflscape}	% Landscape pages

\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{newtxtext,newtxmath}

%\usepackage{amsmath,amstext}
%\usepackage[T1]{fontenc}
\usepackage[figure,figure*]{hypcap}

%\hypersetup{draft}
%\usepackage{multirow}
%\usepackage{mathtools}
%\renewcommand*{\sectionautorefname}{Section} %for \autoref
%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
%\usepackage{graphicx}
%\usepackage{natbib} % bibliography

%\usepackage[active,floats,tightpage]{preview}
%    \setlength\PreviewBorder{1em}

\newcommand{\msun}{M$_{\odot}$}
\newcommand{\ccunit}{cm$^{-3}$}

\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars}

\author[A. Emerick et. al.]{
Andrew Emerick,$^{1,2}$
Greg L. Bryan,$^{1,3}$
and Mordecai-Mark Mac Low$^{2,1,3}$
\\
$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}

\begin{document}

\label{firstpage}
%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle
%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}

%\author{Andrew Emerick}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
%\author{Greg L. Bryan}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
%\author{Mordecai-Mark Mac Low}
%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}

%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}

\begin{abstract}
In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. We furthermore follow the star-by-star chemical yields using tracer fields for 15 metal species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We include the yields ejected in massive stellar winds, but greatly reduce the winds' velocities due to computational constraints. We describe these methods in detail in this work and present the first results from 500~Myr of evolution of an isolated dwarf galaxy with properties similar to a Local Group, low-mass dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives outflows with a greater metallicity than the ISM, leading to low metal retention fractions consistent with observations. Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
\end{abstract}

\begin{keywords}
Galaxy -- Hydrodynamics -- Simulation -- Feedback
\end{keywords}

\section{Introduction}
%
% AE removed below.. MM suggested  skipping both pars.
%
%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade. Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc. \citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses. On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM. This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}. See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics. 
%
%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution. In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense. In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships. For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.

Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution. Examining these in more detail in galaxy scale simulations is an important and exciting new discriminator between models. There is a considerable body of work studying the chemodynamical evolution of galaxies using cosmological hydrodynamics simulations \citep[e.g.][]{OppenheimerDave2008,Wiersma2009,Shen2010,Simpson2013,Snaith2015,OWLS,EAGLE,FIRE}.
% editor asked us to reduce citation count here:{Lia2002,KawataGibson2003,Kobayashi2004,Tornatore2004,Romeo2005,OppenheimerDave2008,Wiersma2009,Shen2010,MUGS2010,ErisSimulation,Simpson2013,Brook2014,Snaith2015,Oppenheimer2016,OWLS,EAGLE,FIRE}.
These simulations, coupled with additional attention to feedback processes, have made remarkable progress in reproducing global galaxy trends such as evolution of the mass-metallicity relationship \citep[e.g.][]{Obreja2014, Ma2016, Dave2017, Torrey2017} and more detailed quantities such as metallicity distribution functions (MDFs) and the evolution of individual species abundances \citep{Marcolini2008,Revaz2009,Sawala2010,RevazJablonka2012,Jeon2017,Hirai2017} .

However, much of this work has been done with Lagrangian smoothed particle hydrodynamics schemes, with a few recent exceptions  \citep{Few2012,Simpson2013,Few2014,Vorobyov2015,Corlies2018}. In its original form, this scheme does not capture mixing between chemically inhomogeneous particles, as necessary for chemical evolution. Mixing can be modeled with sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010,Shen2013,Brook2014,Su2017a,Escala2018}, but there are many possible models and each is not necessarily applicable in every regime \citep[see ][]{Revaz2016}. While mixing occurs in Eulerian codes even without sub-grid models, numerical diffusion tends to result in over-mixing in simulations without sufficiently high spatial resolution. Molecular diffusion or even turbulent mixing is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2018, KrumholzTing2018}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) that inject metals into different phases of 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution.

Increasing physical resolution reduces reliance on sub-grid physics for mixing.  However, at high particle mass resolution ($M \lesssim 10^3$ M$_{\odot}$) standard schemes for modeling stars as simple stellar populations lose validity  \citep[as studied in detail by][]{Revaz2016}. Below 10$^4$ M$_{\odot}$, such schemes do not fully sample the initial mass function (IMF), and cannot be considered average representations of stellar populations. This is acutely problematic at low star formation rate densities with star particle masses comparable to or below the mass of the most massive individual star ($\sim 100$ M$_{\odot}$). At high star formation rate densities, an undersampled IMF in a single low mass star particle can be compensated for by having many adjacent star particles. Various approaches exist to address this issue \citep[e.g.][]{Kobayashi2000,WeidnerKroupa2004,Pflamm-AltenburgKroupa2006,RevazJablonka2012,Kroupa2013,Rosdahl2015,Su2018}, but none are without caveats \citep{Revaz2016}, save for schemes which begin to track the star-by-star information within a given particle by directly sampling the IMF at formation time \citep[e.g.][]{Hu2017}. The most straightforward solution is to remove the single stellar population formalism entirely and simply track stars as individual particles.

We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies. The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies. \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies. 
Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advances: 1) direct star-by-star modeling, 2) stellar winds from both massive and asymptotic giant branch (AGB) stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation. We also include core collapse and Type Ia supernova feedback, photoelectric heating from stellar far ultra-violet (FUV) radiation, and Lyman-Werner dissociation from stellar radiation.

Using star-by-star modeling, we capture in more detail the stellar yields from individual stars released over their lifetime. This includes yields from massive and AGB stellar winds, and supernovae (SNe). In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This ability opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed distributions of chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}. This paper is the first in a series examining in detail the role that individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. In \cite{Emerick2018b} we investigate the importance of ionizing radiation in regulating star formation and driving outflows in our galaxy. In \cite{Emerick2018c} we explore how individual metal species mix within the ISM and are ejected via galactic winds.

We describe each mode of our multi-channel feedback 
in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}. Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.

\section{Methods}
\label{sec:methods}
We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
This allows us to follow star-by-star variations in feedback physics and stellar yields in detail. To properly model the ISM, we track non-equilibrium, primordial chemistry (including molecular hydrogen) using \texttt{Grackle} \citep{GrackleMethod}, with heating and approximate self-shielding from a metagalactic ultraviolet (UV) background. We assume collisional ionization equilibrium for all other elements and use updated \texttt{Cloudy} metal-line cooling tables consistent with our self-shielding approximation (see Appendix~\ref{appendix:cooling}). We also include an updated observationally motivated dust model for the low metallicity regimes studied here ($Z \lesssim 0.1$ Z$_{\odot}$). Each star is assigned basic properties including surface gravity, effective temperature, radius, and lifetime from tabulated stellar evolution models, which inform how the stars deposit their feedback. We directly track ionizing radiation from massive stars using an adaptive ray tracing radiative transfer method that includes the effects of radiation pressure on HI. In addition, we follow the optically thin, non-ionizing UV radiation from these stars that cause photoelectric heating and Lyman-Werner dissociation of molecular hydrogen. We track the stellar wind feedback and SNe from these stars, depositing individual metal yields from both. We include AGB wind feedback and yields for lower mass stars, and track these directly as Type Ia SN progenitors. We follow yields for 15 individual metal species (C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba), chemically tagging each star as it forms with the associated local gas abundances for each species. In addition, we track a total metal density field which is the sum of all metals, including those not directly tracked. This field is used to inform the heating/cooling physics, and determines the metallicity of each star at birth. These methods are discussed in full detail below.

\subsection{Hydrodynamics and Gravity}
\label{sec:hydro}

We use the adaptive mesh refinement hydrodynamics and N-body code \texttt{Enzo}\footnote{http://www.enzo-project.org} to simulate the chemodynamical evolution and detailed feedback physics in a set of high resolution, isolated, low-mass dwarf galaxies. \texttt{Enzo} is an open-source code that is undergoing continual, active development by many researchers across several institutions. We use a substantially modified version of the current development version of \texttt{Enzo} (version 2.X) in this work.\footnote{This version is contained in a publicly available fork of the main repository: https://bitbucket.org/aemerick/enzo-emerick. Specifically, simulations presented here were conducted at changeset 7001d99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies. We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}). Self-gravity is computed with a multigrid Poisson solver. The collisionless star particles are evolved with an adaptive particle-mesh N-body solver at an effective force resolution of $\sim 2 \Delta x$, where $\Delta x$ is the local cell size.

We refine the mesh whenever the thermal Jeans length is no longer resolved by a minimum of 8 cells, continually refining a given region until this criterion is met or until the region reaches the maximum resolution (1.8~pc). At maximum resolution, the Jeans length can become under-resolved, leading to artificial numerical fragmentation. \citet{Truelove1997} showed that resolving the Jeans length by at least 4 cells is required to suppress this fragmentation.

We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}). Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved. However, since star formation is not instantaneous, we employ a pressure floor to support gas against artificial fragmentation and collapse. A non-thermal pressure term is added to cells once their thermal Jeans length becomes unresolved. This prevents dense, self-gravitating gas from rapidly reaching densities significantly above our resolution limit. The use of a pressure floor is common in galaxy scale simulations with limited dynamic range \citep[e.g][]{Machacek2001, 2008ApJ...680.1083R}.

Due to computational constraints we found it necessary to institute a temperature ceiling in low density, diffuse gas. These high temperatures, typically well above 10$^{7}$~K and up to 10$^{8}$~K, would place an onerous constraint on the limiting time step at high spatial resolution. At these temperatures, with typical velocities up to $\sim$10$^{3}$~km~s$^{-1}$, satisfying the Courant condition requires time steps on order of 100~yr. We institute a maximum temperature of 8$\times 10^6$~K in gas with densities between 10$^{-30}$~g~cm$^{-3}$ and 10$^{-26}$~g~cm$^{-3}$. These densities were somewhat arbitrarily chosen, but ensure that this threshold does not impact very low density gas in the halo of our dwarf galaxy or higher density gas in supernova injection regions. This threshold decreases the required run-time by factors of a few. The value of the temperature threshold was chosen to ensure the affected hot gas remained just above the high-temperature minimum of our cooling curve (see Appendix~\ref{appendix:cooling}.)

\subsection{Chemistry and Cooling Physics}
\label{sec:chemistry}

We use the chemistry and cooling library \texttt{Grackle}\footnote{https://grackle.readthedocs.io/en/grackle-3.0/} v 3.0 to follow a nine species non-equilibrium chemistry network (H, H$^+$, He, He$^+$, He$^{++}$, e$^{-}$, H$_2$, H$^{-}$, and H$_{2}$) which includes radiative heating and cooling from these species and metals.\footnote{We use a slightly modified version of the the main \texttt{Grackle} repository, available at https://bitbucket.org/aemerick/grackle-emerick at changeset c2c0faf.} \texttt{Grackle} is a freely available, open source, multi-code library, designed to interface with a wide variety of astrophysical codes. We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code. We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}. However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}. For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.

As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background. As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background. Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}. To address this issue, we use re-computed metal line tables consistent with the self-shielding approximation.  We have made these new tables public in the main \texttt{Grackle} repository. These are discussed in greater detail in Appendix ~\ref{appendix:cooling}. Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.

\subsection{Star Formation Algorithm}
\label{sec:star formation}
In order to resolve individual star formation events on galactic scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}. Each cell at the maximum refinement level is capable of forming stars if it contains gas that meets the following local criteria on number density $n$, temperature $T$, cell mass $M$, and velocity $\vec{v}$: 1) $n > n_{\rm thresh}$, 2) $T < T_{\rm thresh}$, 3) $M > M_{\rm Jeans}$, and 4) $\vec{\nabla} \cdot \vec{v} < 0$, where $n_{\rm thresh}$ is a resolution dependent density threshold, $T_{\rm thresh}$ is a temperature threshold, and $M_{\rm Jeans}$ is the local thermal Jeans mass. Our fiducial values are $n_{\rm thresh} =  200 \mbox{ cm}^{-3}$ and $T_{\rm thresh}= 200$~K. We limit the fraction of a cell's gas mass that is converted into stars by requiring $M > f_{\rm thresh} M_{\rm max,*}$, where $f_{\rm thresh} = 2.0 $ and the maximum star mass $M_{\rm max,*} = 100 \mbox{ M}_{\odot}$. No star formation occurs when $M < f_{\rm thresh} M_{\rm max,*}$, ensuring that a star formation episode can not produce negative densities.

We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$. At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2018, FIRE2}, as star formation is ultimately self-regulated by feedback.

The stellar mass formed during a timestep $\Delta t$ from a region with a total gas mass $M_{\rm gas}$ is
\begin{equation}
         M_* = \epsilon_{\rm f} M_{\rm gas} \frac{\Delta t}{\tau_{\rm ff}}
\end{equation}
In practice, $\Delta t/\tau_{\rm ff} \ll 1$, and $M_*$ is smaller than the minimum star particle mass at parsec scale resolution. We therefore allow star formation to proceed stochastically, following the methods in \citet{Goldbaum2015, Goldbaum2016}, modified for variable stellar masses. In each cell that could potentially form stars, we compute the probability that 100 M$_{\odot}$ of gas will be converted into stars in that time step, and use a random number draw to determine whether or not star formation actually occurs. If it does, we randomly sample from
the adopted IMF until approximately 100 M$_{\odot}$ of stars form, keeping the last sampled particle when the total stellar mass formed exceeds 100 M$_{\odot}$. The total mass of formed star particles is subtracted from the gas mass in the star forming region to ensure mass conservation. We assume a Salpeter IMF \citep{Salpeter1955} with $\alpha = 2.35$, sampling over the range between a minimum stellar mass of 1 M$_{\odot}$ and an arbitrarily chosen maximum stellar mass of 100 M$_{\odot}$. Our lower limit on stellar masses ensures that we are able to both directly track all particles that contribute in some way to feedback and metal enrichment, and follow longer lived star particles, while reducing the computational expense of following a large number of low mass stars that have no dynamical impact on the galaxy evolution. By ignoring the formation of stars below 1~M$_{\odot}$, our model in effect spreads this mass into higher mass stars, changing the normalization of the IMF slightly from what would be expected for an IMF that extends below  1~M$_{\odot}$.

Formed stars are deposited with random positions within the star forming cell and assigned velocities equal to the cell bulk velocity with a 1~km~s$^{-1}$ velocity dispersion. This dispersion captures some of the unresolved gas motions below the resolution limit that are smoothed out by numerical diffusion; it is comparable to, but less than, the velocity dispersion of the coldest gas in our simulations. Stars are assigned metallicities corresponding to the metallicity of the star forming zone, and are chemically tagged with the 17 individual species abundances (H, He, and the 15 metals) that we follow in our simulations.

Stars evolve during the simulation, by losing mass from stellar winds and SNe as described below, and by changing types, but persist throughout the entire simulation. For example, low mass stars are tagged as white dwarfs (WDs) at the end of their life, which may eventually explode as a Type Ia SN (discussed below), after which they persist as massless tracer particle remnants. Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a four-cell region at the highest level of refinement. This ensures that both stellar winds and SNe feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.

\subsection{Stellar Properties}
\label{sec:properties}
Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}). We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$. Although $T_{\rm eff}$ and $g$ evolve over time for stars, modifying stellar radiative properties, following a stellar evolution track for each of our stars is beyond the scope of this work. We instead fix these properties at their zero age main sequence values.

\subsection{Stellar Feedback and Chemical Yields}

\subsubsection{Stellar Yields}
\label{sec:yields}
For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars. We adopt the NuGrid\footnote{http://www.nugridstars.org} collaboration's set of stellar yields given on a uniformly sampled grid in stellar mass and metallicity with 12 mass bins over $M_{*} \in \left[1.0, 25.0\right]$ M$_{\odot}$ and five metallicity bins at metal fractions of $Z =$ 0.02, 0.01, 0.006, 0.001, and 10$^{-4}$ \citep{Pignatari2016, Ritter2018}. This grid includes yields from the AGB phase of stars from 1--7 M$_{\odot}$, as well as yields from both stellar winds and core collapse SNe of massive stars from 12--25 M$_{\odot}$. We complement these tables with tables from Slemer et al.\ (in prep), based on the PARSEC stellar evolution tracks \citep{Bressan2012, Tang2014}, to track stellar winds for stars more massive than 25 M$_{\odot}$. We ignore SN yields from these stars (see next paragraph). We combine all stable isotope yields for a given element into a single elemental abundance for all stable elements from hydrogen to bismuth. Although we can in principle follow an arbitrary number of metal species, practical considerations of memory use prevent this in any given simulation. We refer the reader to previous uses of the NuGrid yields in one-zone galactic chemical enrichment models \citep{Cote2016,  Cote2016_feb,Cote2017a} for a detailed discussion of how various model uncertainties can influence galactic chemical evolution.

%
% KVJ: Possibly include a discussion on uncertainties in stellar yields
%

Above some mass $M_{\rm trans}$ within the unsampled range of 7--12 M$_{\odot}$, stars no longer undergo AGB wind phases but end their lives instead as core collapse SNe. Where this transition occurs is uncertain, but is commonly taken to be at a mass $M_{\rm trans} \sim 8$--10~M$_{\odot}$; we take $M_{\rm trans} = 8$~M$_{\odot}$. In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr). Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics). Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds. \citet{Cote2017a} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model. We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.

There are large uncertainties in stellar yields for stars more massive than 25 M$_{\odot}$ \citep[see ][and references therein]{Cote2016}. Indeed, even the exact fate of these stars is uncertain \citep[e.g.][]{Woosley2002,Zhang2008,Ugliano2012}, particularly as a function of metallicity \citep{Fryer2012} with potentially multiple stable and unstable regimes as a function of mass \citep{Heger2003}. Due to this uncertainty, and to avoid erroneously extrapolating from our yield tables, we adopt the simplest model and assume all stars above 25 M$_{\odot}$ end their life through direct collapse to a compact object with no further mass, metal, or energy ejection.

Type Ia SNe are an important additional source of galactic chemical enrichment. These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams. We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}. We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, substantially limiting the number of Type Ia SNe occurring during the initial gigayear in our models.

\subsubsection{Stellar Winds}
\label{sec:stellar winds}
Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars. Although the energy injected via winds over the lifetime of a cluster of stars is much less than that from SNe and radiation \citep{Shull1995}, stellar winds are potentially important sources of pre-SN feedback. We assume complete thermalization of the wind kinetic energy, taking the total injected energy injected in timestep $\Delta t$ as $E_w = \frac{1}{2}\dot{M}  v^2_w\Delta t  + E_{\rm th}$, where $E_{\rm th}$ is the thermal energy of the ejected gas mass $M_w = \dot{M}\Delta t$ given the star's interpolated effective temperature $T_{\rm eff}$. This mass and energy is injected evenly over a three-cell radius spherical volume centered on the star particle. The edges of this spherical region will only partially overlap grid cells. We use a Monte Carlo sampling method to properly compute the volume of this overlap to scale the injection in these cells appropriately. We assume constant mass loss rates for all winds as set by the yield tables over either the lifetime of the star (for massive stars) or the length of the AGB phase (for low mass stars).

Massive stellar winds have typical velocities of order 10$^{3}$ km s$^{-1}$ \citep{Leitherer1992}. Satisfying the Courant time step becomes prohibitively expensive following this gas, with time steps dropping to $\Delta t \sim$~100~yr. For this reason, we adopt the common simplification of reducing the wind velocity \citep[e.g][]{Offner2015}. In our case, we fix massive stellar wind velocities to $v_w = 20$~km~s$^{-1}$ for stars above 8 M$_{\odot}$. Our initial tests show that turning off energy injection from stellar winds like this does not significantly affect the global star formation rate of our galaxies. Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work. These points are discussed in more detail in Sect.~\ref{sec:stellar winds discussion}.

% Injecting 10$^{3}$ km s$^{-1}$ gas onto the grid at these scales leads to super heated, shocked gas at unphysical temperatures of about 10$^{8-9}$ K, particularly when injecting into very low density media. This can lead to painfully short time step sizes and crashes in the hydrodynamics solver. We adopt the common solution of artifiially reducing the wind velocity from massive stars, choosing $v_{\rm wind} = 500$~km~s$^{-1}$ for stars above 8 M$_{\odot}$. However, this can still be problematic once the star evacuates the local ISM and injects its energy to very low density ($n \lesssim 10^{-3}$ \ccunit) gas. We address this issue by mass loading our winds when injection would lead to wind bubble temperatures in the spherical source region above a maximum temperature typical of wind bubble. This is a free parameter that we take to be 2 $\times$ 10$^{6}$ K \citep{Weaver1977}. Mass loading in this manner is (in effect) a sub-grid model for the unresolved ISM mixing at the boundary layer of the wind bubble, which is in fact the source of a majority of the gas mass within the wind bubble \citep{Weaver1977}. We take the metal species abundances of the mass loaded ISM to be the average cold / warm ISM abundance on each grid to prevent artificially inflating/deflating the overall abundances. We discuss our ability to resolve typical single star wind bubble properties in Appendix ~\ref{appendix:stellar winds}.

%parameterized in this work with the STARBURST99 wind model, \citep{Leitherer1992}:
%\begin{multline}
%{\rm log} \left[ v_{\rm wind} {\rm (km~s^{-1})} \right] = 1.23 - 0.30~{\rm log}~\left[L{\rm (L_{\odot})}\right] \\
% + 0.55~{\rm log}\left[M({\rm M_{\odot}})\right] + 0.64~{\rm log}\left[T_{\rm eff}(K)\right] \\
% + 0.13~{\rm log}\left[Z({\rm Z_{\odot}})\right].
%\end{multline}

Stars that only undergo an AGB phase deposit their feedback at the end of their lives, as determined by the PARSEC evolution tracks. AGB wind velocities vary dramatically over their relatively short lifetimes, but are typically on the order of 10 km s$^{-1}$. For simplicity, we adopt a fixed wind velocity of 20 km s$^{-1}$ for all AGB stars as well.

\subsubsection{Core Collapse SNe}
\label{sec: core collapse}
Stars between  $M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy. Due to the high resolution of our simulations (1.8~pc), we generally resolve the Sedov phase of each SN explosion well (see Appendix~\ref{appendix:SN}). We inject thermal energy alone in a three-cell radius spherical region around the star particle, which we find to be sufficient to resolve the SN explosions. We use the same Monte Carlo sampling method as used in our stellar winds to map the spherical injection region to the grid. We continue to track any remaining stellar mass after the SNe occurs as a massive remnant tracer particle. In future work these particles can be used to self-consistently account for more exotic sources of feedback and chemical enrichment such as X-ray binaries and neutron-star binary merger events which, while rare, could be important in long term galaxy evolution \citep[e.g.][]{Artale2015}.

\subsubsection{Type Ia SNe}
\label{sec:Type Ia}
We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as WD particles, marking a subset as Type Ia SN progenitors. This is the most self-consistent model for Type Ia SNe in galaxy-scale simulations. We note however that for the low SFRs in our isolated dwarf galaxy simulation, the first Type Ia SN only appears after a few hundred megayears of simulation time. By the end of the simulation presented here (500~Myr), only 18 have gone off. At the end of their life, we assign a new mass to these particles following the initial-to-final-mass relation of \citet{Salaris2009}. We follow the common assumption that progenitor stars with initial masses between 3 and 8 M$_{\odot}$ form WDs that are Type Ia progenitors \citep[see][ and references therein]{Cote2017a}.

We compute the probability that a given Type Ia progenitor will explode as a function of time using an observationally motivated delay time distribution model. The Type Ia SN rate is taken to be a power law in time, $\Psi (t) \propto t^{-\beta}$, whose slope $\beta$ and normalization $N_{\rm Ia}/M_{\rm SF}$ are observables. The latter represents the number of Type Ia SNe per mass of star formation.  By assuming an IMF  $dN/dm$, one can write down the fraction $\eta$ of stars capable of forming a Type Ia SN progenitor that \textit{will} explode within a Hubble time. This is given as
\begin{equation}
\eta = \frac{N_{\rm Ia}}{M_{\rm SF}} \frac{\int_{M_{\rm min}}^{M_{\rm max}} m (dN/dm) dm }{\int_{M_{1}}^{M_{2}} (dN/dm) dm},
\end{equation}
where $M_{\rm min}$ and $M_{\rm max}$ are the lower and upper bounds of the IMF, and $M_{1}$ and $M_{2}$ are the lower and upper bounds of the range of stars that can form Type Ia candidates. The distribution slope $\beta$ is of order unity, with typical values between 1.0 and 1.2 \citep[see][for a recent review]{Maoz2014}. $N_{\rm Ia}/M_{\rm SF}$ can be derived by taking observed values of the Type Ia SN rate and integrating over a Hubble time. Typical values for this are on order of 10$^{-3}$ M$_{\odot}^{-1}$ \citep{Maoz2014}. For our fiducial values, we adopt $\beta = 1.2$ \citep{Maoz2010} and $N_{\rm Ia}/M_{\rm SF} = 0.8\times 10^{-3}$ M$_{\odot}^{-1}$ \citep{GraurMaoz2013}. Given our choice of IMF, and with $M_{\rm min} = 1$~M$_{\odot}$, $M_{\rm max}=100$~M$_{\odot}$, $M_{1}=3$~M$_{\odot}$, and $M_{2}=8$~M$_{\odot}$, this gives $\eta = 0.041$.

Finally, we can normalize $\Psi(t)$ to give the probability per unit time $\dot{P}(t)$ that a Type Ia candidate will explode at a time $t$ after the formation of its main sequence progenitor. Integrating this gives the total probability at any given time as
\begin{equation}
P(t) = \int \dot{P}(t)dt = \frac{\eta}{{ \int_{t_{\rm o}}^{t_{\rm H} + t_{\rm o}} \tau^{-\beta} d\tau}} \int t^{-\beta} dt,
\end{equation}
where $t_{\rm o}$ is the formation time of the WD and the leading term on the right hand side properly normalizes the total probability over a Hubble time to $\eta$. This naturally accounts for both a prompt and delayed Type Ia SN population in our simulations.
In practice, rather than drawing a random number for each candidate every timestep, we make a single random number draw, $u$, at the formation time of the white dwarf particle. For $u \in [0,1]$, we interpolate its position on a pre-tabulated and inverted cumulative probability distribution function to assign a single time at which the WD particle will explode as a Type 1a supernova. We institute a minimum delay time by defining $P(t)$ only for $t > t_o$, such that a particle cannot be assigned an explosion time before its formation time.

\subsubsection{Ionizing Radiation from Discrete Sources}
\label{sec:ionizing radiation}
Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies. \ion{H}{2} regions carved out by stellar radiation change the ISM structure in regions where SNe eventually explode, generally increasing their dynamical importance. However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds. Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing. As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.

Enzo includes an adaptive ray tracing implementation, \textsc{Enzo+Moray} \citep{WiseAbel2011}, to solve the equations of radiative transfer coupled to the hydrodynamics of the simulation. We follow HI and HeI ionizing photons which are coupled to the \texttt{Grackle} primordial chemistry and heating and cooling routines to track photoionization and heating, as well as radiation pressure on hydrogen.

We determine the HI and HeI ionizing photon rates for each star using the OSTAR2002 \citep{Lanz2003} grid of O-type stellar models, appropriate for $M_{*} \gtrsim 15$~M$_{\odot}$ at solar metallicity\footnote{The exact stellar mass range on the OSTAR2002 grid is model dependent and a function of metallicity}. We use linear interpolation in stellar effective temperature, surface gravity, and metallicity to compute the ionizing photon fluxes and rates for each star. Stars less massive than about 15 M$_{\odot}$ and very massive stars with sub-solar metallicity are generally not well sampled by the OSTAR2002 grid. In this case, we integrate a black body spectrum at $T_{\rm eff}$ to obtain the ionizing photon fluxes, but normalize the result to be continuous with the OSTAR2002 grid (see Appendix \ref{appendix:radiation}).

Instead of assigning a fixed ionizing photon energy across all sources, we integrate over each star's blackbody curve to compute the average ionizing photon energy individually for each source (see Appendix~\ref{appendix:radiation}). The average energy for HI and HeI ionizing photons changes significantly over the OSTAR2002 temperature range $\log(T_{4,\rm{eff}} [K]) \in \left[2.75,5.5\right]$, ranging from 15.72 eV to 20.07 eV and 26.52 eV to 31.97 eV respectively.

We also include the effects of radiation pressure on HI. This has been shown to be important in suppressing the star formation rates of dwarf galaxies by influencing turbulence and the dense gas content of the ISM \citep{WiseAbel2012,Ceverino2014}. We ignore the absorption of ionizing radiation by dust and re-radiation in the infrared. This is included in other models \citep[e.g.][]{Rosdahl2015,FIRE,FIRE2} as this may increase by a factor of a few to several the effective radiation pressure \citep{ZhangDavis2017}. However, the importance of multiple scattering is still unclear. Other works have shown the effect to only increase the radiation pressure by a factor of order unity \citep{Krumholz2012,Krumholz2013a,Krumholz2018,Reissl2018,Wibking2018}. Due to these uncertainties, and given that our dwarf galaxy has a low dust content, and therefore a low infrared opacity, we ignore this effect.

\subsubsection{Diffuse  Heating}
\label{sec:diffusive heating}
We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the FUV (6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles. The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the spectral energy distributions for each gridded star. Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}). Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}. However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}. Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile. Only recently has the localization and time variation of these processes been considered.

Self-shielding of gas against the metagalactic UV background is important in high-resolution simulations, particularly for low-mass, low-metallicity dwarf galaxies where the UV background is capable of gradually photoevaporating unshielded gas from the galaxy \citep{Simpson2013}. We have implemented the \citet{Rahmati2013} approximate self-shielding method in \texttt{Grackle} to account for HI self-shielding against the UV background \citep[see][ for more details of this implementation]{GrackleMethod}. We assume HeI ionization generally follows HI. This allows us to approximate HeI self-shielding using the same form (A. Rahmati, private communication). We ignore HeII photoionization from the UV background entirely. For consistency, we additionally reduce the reaction rates for direct H$_2$ ionization (15.4 eV) and H$_2^+$ destruction (30 eV) by the same shielding factors computed for HI and HeI shielding.\footnote{Ignoring this effect leads to unrealistically high electron fractions in self-shielding gas from direct $H_2$ ionization, which drives significant production of H$_2$ via gas-phase reactions.} Accounting for self-shielding in this manner leads to an inconsistency in using tabulated, optically-thin metal line cooling rates from \textsc{Cloudy} (see Section 4.1.1 of \citet{Hu2017}). As mentioned previously, we have re-computed metal line cooling tables using \textsc{Cloudy} models of optically thick clouds to be consistent with our self-shielding prescription. This is described in more detail in Appendix ~\ref{appendix:cooling}.

%Ignoring this effect leads to an overestimation of the cooling rates when in the self-shielding regime. %We refer to \citet{2006agna.book.....O,2010MNRAS.408.1945M,2012MNRAS.421.2232F,Rahmati2013} for a more detailed description of this approximation and \citet{Gracklemethod} for its specific implementation, as used here.

We assume the galaxy is mostly optically thin to stellar FUV and use only local approximations for shielding.  We calculate the stellar FUV flux in each cell as summed over the contributions from each star to parameterize the local photoelectric heating rate as \citep{BakesTielens1994,Wolfire2003,Bergin2004}
\begin{equation}
\label{eq:PE}
\Gamma_{\rm pe} = (1.3 \times 10^{-24} \rm{erg~s^{-1}~cm^{-3}})\, \epsilon n_{\rm H} G_{\rm eff} D 
\end{equation}
where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust-to-gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}. Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.

The value of $D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}. The extremely low dust-to-gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a ratio $D$ that scales linearly with metallicity at very low metallicity. At these low metallicities, the FUV field only becomes optically thick at length scales of $\sim$ 100 pc for densities of $n \sim 10^2$~\ccunit. Given that the ambient density of the ISM is generally 1--10~cm$^{-3}$, we can safely assume the FUV field to be optically thin. However, we do include a localized attenuation prescription that may influence high-density or metal-enriched regions of the galaxy. We approximate $N_{\rm H}$ given in the equation above locally, as $n_{\rm H}\Delta x$, where $\Delta x$ is the cell width; this approximation is necessarily resolution dependent, but substantially more computationally efficient than direct ray tracing.

Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$. This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations. Our chemical network only includes contributions from H, He, and H$_2$ to n$_e$. Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$. %This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.

\subsubsection{Lyman-Werner Radiation}
\label{sec:LW}
In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rate. We compute the stellar Lyman-Werner flux again from the OSTAR2002 grid by integrating the spectral energy distributions over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}). Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section. We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.

\section{Galaxy Initial Conditions}
\label{sec:IC}
We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy. The galaxy is constructed to have initial properties similar to those observed for the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy. Leo P is gas rich, with a neutral hydrogen mass $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and stellar mass $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to an observed neutral hydrogen radius $r_{\rm HI} = 500$~pc. LeoP has a low metallicity, with an oxygen to hydrogen abundance ratio (O/H) of $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity of $Z \sim 5.4\times10^{-4}$ ($Z/Z_{\odot} = 0.03$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}). Our dwarf galaxy model is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$, of which $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$, and $Z = 4.3\times 10^{-4}$, comparable to the average redshift $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.

The galaxy initially consists of a smooth, exponential gas disk in hydrostatic equilibrium with a static, background dark matter potential. The gas profile follows \citet{Tonnesen2009} and \citet{Salem2015}, with
\begin{equation}
\rho_{\rm gas} (R,z) = \frac{M_{\rm o}}{2\pi a^2_{\rm gas}b_{\rm gas}} 0.5^2{\rm sech}\left(\frac{R}{a_{\rm gas}}\right){\rm sech}\left(\frac{z}{b_{\rm gas}}\right)
\end{equation}
where $a_{\rm gas}$ and $b_{\rm gas}$ are the radial and vertical gas disk scale heights, and $M_{\rm o}$ is approximately 70\% of the total gas mass. We set $a_{\rm gas} = 250$~pc, $b_{\rm gas} = 100$~pc, and $M_o = 1.26\times 10^6$~M$_{\odot}$. We adopt a \citet{Burkert1995} dark matter potential with virial mass and radius $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc as defined in \citep{BryanNorman1998} and scale radius r$_{\rm s} = 990$~pc. This gives a maximum circular velocity $V_{\rm max} = 30.1$~km~s$^{-1}$ at $R_{\rm vmax}~=~3.2$~kpc. These parameters were adopted specifically to match the observed dynamical mass of Leo P interior to 500 pc of $M_{\rm dyn} (r < 500~\rm{pc}) = 2.7\times 10^{7}$ M$_{\odot}$, and represent virial properties within the halo mass expected for galaxies of this size \citep{Ferrero2012,Read2017}.

Following the initialization procedure of \citet{Hu2017}, we use artificial SN driving to generate realistic initial densities and turbulent properties in the galaxy ISM. This prevents an otherwise uniform collapse of the gas disk at the beginning of the simulation. During this period, SNe explode at a fixed rate of $0.4$~Myr$^{-1}$, corresponding to the SFR obtained given the central HI surface density and the relation presented in \citep{Roychowdhury2009}. We stop the artificial driving 25~Myr after the first star particle forms. These artificial SNe do not drive chemical evolution of the galaxy; their metal yields correspond to the mean ISM abundances. We note this initial driving is ad hoc in that we do not include other effects from the stellar population that would have caused these SNe.

We emphasize here that our model, with no initial stellar distribution, is not intended to identically reproduce the evolution of Leo P, which has formed stars continuously over cosmological timescales. In addition, the mass fractions for the individual metals we track are set to zero so that we follow only the evolution of metals self-consistently produced in the simulations. Otherwise, the galaxy chemical properties would be dominated by the somewhat arbitrary choice of initial abundances. In some ways this is similar to the first pollution of pristine gas in the early Universe, but we note that we cannot directly make this comparison as the environmental conditions and UVB properties were different at high redshift, and we explicitly ignore Pop III and Pop II stellar evolution. Instead, this work is intended as a numerical experiment to investigate how metal enrichment from ongoing star formation proceeds in a gas / dark matter environment similar to low mass halos at both low redshift and the early Universe. The subsequent metal enrichment from the stars in our simulation can be thought of as tracking a change in abundances from arbitrary initial conditions. We will discuss how to make proper comparisons to observed stellar and gas abundance properties of dwarf galaxies in future work, where we will investigate the abundance evolution of our simulations in more detail.

\section{Results}
\label{sec:results}
We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms. Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run. The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and vertical height $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy. We include a resolution study in Appendix \ref{appendix:resolution_study}.

Our analysis makes extensive use of the open-source \textsc{yt} toolkit \citep{yt}. All analysis scripts used in this work can be found at https://github.com/aemerick/galaxy-analysis at changeset dd76ad10.

\subsection{Morphological Structure and Evolution}
\label{sec:structure}

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}. These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution. This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds. This central region quickly fills with warm and hot gas generated from radiation feedback and SNe respectively. Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels. The ISM properties are quantified further in Section~\ref{sec:phase}.

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation. Shown are the density weighted projection of number density (top row), temperature slices (second row), HI column density (third row), and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single white dot.}
\label{fig:panel_x}
\end{figure*}

The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}. This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time. Stellar feedback acts to heat up this initially thin disk substantially, creating typical scale heights of 50--120~pc. Towards the end of the simulation time, the half-light radius is $391 \pm 19$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr. Although the disk remains thin beyond the half-light radius, with a scale height of around 50~pc, it is fully resolved at all radii. By the end of the simulation, the majority of the disk has a scale height of $\sim$100~pc.

Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging. For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}. In the final column of Fig.~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc. With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view. At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$. These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
\caption{Same as Fig.~\ref{fig:panel_x}, but showing face-on views.}
\label{fig:panel_z}
\end{figure*}

\begin{figure}
\centering
\includegraphics[width=0.975\linewidth]{scale_height}
\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
\label{fig:scale_height}
\end{figure}

\subsection{Star Formation Rate and Mass Evolution}
\label{sec:sfr}

We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Fig.~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr. The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$. The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation. Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.19 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$. We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.

We note that the granularity in our star formation algorithm creates a lower limit to the SFR that depends on the period $\Delta t$ over which the SFR is measured. Since we produce stars in $\sim 100$~M$_{\odot}$ sets, the smallest value for our measured SFR is $\sim 100/ \Delta t$. For $\Delta t = 10$ Myr this is 10$^{-5}$ yr$^{-1}$. Removing the granularity requires a fundamental change in our star formation algorithm, likely at the cost of increased complexity and computational expense. Sink particles, which track pre-main sequence stellar mass accumulation, would be the most viable way to do this \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017}.

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Fig.~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%. The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback. For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% at 500~Myr. The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy from feedback-driven galactic winds. During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{sfr_snrx100}
\includegraphics[width=0.475\linewidth]{mass_evolution}
\caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins. Broken portions of this histogram are time periods with no star formation or supernovae.  Note that the SN rate has been scaled by a factor of 100 to fit on the same vertical axis as the SFR. Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
\label{fig:sfr_mass_evolution}
\end{figure*}

\subsection{ISM Properties}
\label{sec:phase}

Our simulations include sufficient resolution and microphysics to capture a multi-phase medium within the ISM and halo of our simulated galaxy. We define five different gas phases following those defined in \citep{Draine2011}: molecular gas, cold neutral medium (CNM), warm neutral medium (WNM), warm ionized medium (WIM), and hot ionized medium (HIM). We emphasize that the molecular ISM phase is defined as all cells with M$_{\rm H_2}$/M$_{\rm gas} = $~f$_{\rm H_2} > 0.5$, and is thus somewhat different than simply considering the total H$_2$ content. By this definition, although our galaxy certainly contains molecular hydrogen, molecular gas as a phase does not exist; the peak f$_{\rm H_2}$ in any single cell remains below 30\%. See Appendix \ref{appendix:phases} for a quantitative definition of these phases. The properties of these phases are regulated by the complex interplay between cooling, turbulence, self-gravity, and radiative and shock heating from stellar feedback throughout the galaxy's evolution. Here we discuss the thermodynamic properties of the gas within the inner halo of our dwarf galaxy.

Fig.~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr. One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Fig.~\ref{fig:ISM_evolution}). Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium. We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results. Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left. The boxed regime in the lower right corner shows our star formation density and temperature threshold. Gas in this regime is rapidly consumed by star formation and subsequent feedback. Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average.

\begin{figure}
\includegraphics[width=0.95\linewidth]{phase_diagram.png}
\caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gas interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr. The dashed lines are lines of constant pressure, separated by factors of 10. The region in the lower right corner indicates our density and temperature thresholds for star formation.}
\label{fig:phase}
\end{figure}

The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Fig.~\ref{fig:ISM_evolution}. The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component. The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run. The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation. During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1. Although the CNM dominates the mass fraction, it is a negligible component of the ISM volume, which is WIM dominated. However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable. Together, these figures better quantify the general properties observed in the panel plots in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}.

These results are in contrast with those found for the more massive dwarf galaxy modeled by \citet{Hu2016,Hu2017}. They find the mass and volume fraction of the ISM are nearly entirely dominated by warm gas (defined in those works as gas with 100~K$<$T$< 3\times 10^{4}$), with cold gas having between 1 and 10\% of the mass, and occupying negligible volume. Hot gas (defined as gas with $T > 3\times 10^{4}$~K) occupies 10\% of the volume, with negligible mass, in their galaxy, while our WIM alone occupies $>$ 50\% of the volume. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) and hot gas (by volume fraction) that seen in the more massive dwarf galaxy in these works. The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future work. We have compared our cooling curves to those used in \citep{Hu2017} and found them to be comparable; though this could contribute to the differences, it is likely not the dominant source.

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
\caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
\label{fig:ISM_evolution}
\end{figure*}

\subsection{Interstellar Radiation Field}
\label{sec:ISRF}

The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}. This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve. In Fig.~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr. The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}). The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions. At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.

The bottom panel gives the HI ionizing photon flux from stellar radiation. The ionizing radiation profile follows a similar trend, yet with significantly more variation, anywhere from two to four orders of magnitude. As this radiation is followed through radiative transfer, the profile encodes information about local attenuation by dense, neutral gas. This is the main driver of the differences between the two panels. The total fluctuation in both panels is due in part to the low-level, stochastic star formation in our galaxy. A higher star formation rate would produce a more regular population of massive stars and more uniform (in time) ISRF.

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the HI ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values. HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity. In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
\label{fig:ISRF}
\end{figure}

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Fig.~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr. This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower. The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps). From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile. Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation. In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency. It remains to be seen which of these two modes of feedback is more important in regulating star formation.

\subsection{Outflow Properties}
\label{sec:outflows}

The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}. However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}. In Fig.~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy. We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
\begin{equation} \label{eq:dotM}
\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
\end{equation} 
We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.

The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Fig.~\ref{fig:mass_outflow}. Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor. For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor. The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors between 20--100 throughout the simulation time. This declines towards larger radii, however, with substantially less outflow past the virial radius. \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift, consistent with our results. The fluctuations in both of these panels are directly correlated with the SFR, with increased outflow during periods of star formation, and decreased outflow during periods of quiescence.

Interestingly, the v$_{\rm c}\sim$ 30 km s$^{-1}$ halos examined in \citet{Muratov2015} are more massive than the M$_{\rm vir} = 2.5\times 10^9$ M$_{\odot}$ halo examined here by a factor of a few. Using a fit provided in \citet{Muratov2015} to extrapolate and compare $\eta$ at fixed halo mass, one would expect mass loading factors on order of 100 at 0.25 R$_{\rm vir}$ for our dwarf galaxy, a factor of a few higher than what we find. These differences could be attributed to our lack of cosmological evolution in these isolated simulations, but ultimately requires a larger set of dwarf galaxy simulations to make a more robust comparison. We note, however, that our results are closer to the \citet{Muratov2015} results than those in \citet{Hu2016,Hu2017}, which find lower mass loading factors even closer to the disk, at 0.05 $R_{\rm vir}$, between 1 and 10 for a dwarf galaxy with M$_{\rm vir} = 10^{10}$ M$_{\odot}$; certainly this implies even smaller mass loading factors at 0.25 $R_{\rm vir}$.

\begin{figure*}
\includegraphics[width=0.45\linewidth]{total_mass_outflow}
\includegraphics[width=0.45\linewidth]{total_mass_loading}
\caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
\label{fig:mass_outflow}
\end{figure*}

Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations. In Fig.~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases. Gas with a negative velocity is moving towards the center of the halo. Roughly 25\% of this mass is inflowing, mostly with modest negative velocities, and corresponds to previously ejected gas mixing and recycling throughout the halo. Half of the outflowing gas (positive velocities) is moving at velocities below 30 km s$^{-1}$, 75\% at velocities below 70 km s$^{-1}$, and 95\% at velocities below 100 km s$^{-1}$. Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-negligible amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$. The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominating at velocities above 200 km s$^{-1}$. The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling WIM and HIM, consistent with the results in \citet{Hu2016,Hu2017}. However, as shown, the HIM, which is mostly the SN ejecta itself, comprises very little of the outflow by mass. Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM. Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however. The amount of transfer between phases in the halo of our galaxy will be investigated in future work.

\begin{figure}
\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy. This is averaged over the same time interval as Fig.~\ref{fig:ISRF}. The outflowing material is multiphase, broken into WNM, WIM, and HIM. See Section~\ref{sec:phase} for definitions of these regimes. We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K. There is little to no outflowing mass in the CNM.}
\label{fig:outflow_velocity}
\end{figure}

\subsection{Metal Evolution} 
\label{sec:chemical evolution}

\subsubsection{Metal Enriched Outflows}
Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}. This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}. In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}. The parameter used to quantify metal outflow efficiencies varies among works. Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
\begin{equation} \label{eq:eta-metal}
\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
\end{equation}
where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars. These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5. On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5). Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}. \cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity. Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.

\begin{figure}
\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
\includegraphics[width=0.9\linewidth]{metal_retention}
\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:mass_outflow}. This is the ratio between the metal outflow rate and the metal production rate. {\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:metal_evolution}
\end{figure}

These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk. This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time. After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo. This continues throughout the simulation, with only $\sim$4\% of produced metals residing in the disk of the galaxy. It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius until about 350 Myr where the fraction levels off to just above 50\%. Likewise, the CGM metal content continually decreases until the end of the simulation from loss through the virial radius of the halo. See Section~\ref{sec:obs_metals} for further discussion.

\subsubsection{Differential Evolution of Elements Within the ISM}
It is important to understand how metals from each source of stellar yields enrich the ISM. Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}. This requires that metal mixing and transport occur on hundred megayear timescales, much more rapidly than the gigayear timescale expected from assuming transport at the cold gas sound speed. Therefore, either metals are transported first through a hot phase with high sound speed, or through efficient turbulent mixing within the ISM \citep[e.g.][]{Avillez2002,Tassis2008,YangKrumholz2012}. It remains uncertain how metal abundances vary in detail within these galaxies, beyond one-dimensional radial profiles, and whether or not abundance distributions depend on the metal species. It is even more unclear how metals are transported and distributed within low-mass dwarf galaxies, which generally host too few \ion{H}{2} regions for a detailed examination.

We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}. The left panel gives the abundance ratio of N to O throughout the ISM. The right 
two panels give the slices of number density (top right) and temperature (bottom right) in the mid-plane of a portion of our dwarf galaxy. These show regions with dense, cold gas clouds ($n \sim 100~\rm{cm}^{-2}$, $T \lesssim 100~$K) connected by cold filaments, warm, diffuse gas ($n\sim 0.1$~cm$^{-3}$, $T\sim 10^{4}$~K), and hot gas from a recent SN explosion ($T\sim10^{6}$~K).

\begin{figure*}
\includegraphics[width=0.98\linewidth]{log_NO_panel}
\caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances. The left slice gives the ratio of the abundance between N and O, normalized to the solar abundance, while the number density and temperature are shown on the right. In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occurred in the preceding 5 Myr as black stars and orange diamonds respectively.}
\label{fig:metal_slices}
\end{figure*}

As shown in the left panel, [N/O] varies significantly over this section of the ISM with notable differences across the various phases and ISM structures. The hottest gas, dominated by recent supernova explosions is overabundant in oxygen, relative to solar (purple). However, the relative abundance of nitrogen increases in the WIM and WNM, being overabundant relative to solar (green).

At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars. Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$). Given the variations in Fig.~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy. The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM. This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent. A more detailed analysis is beyond the scope of this work, but we investigate this in detail in \cite{Emerick2018c}.

\section{Discussion}
\label{sec:discussion}

\subsection{Comparison to Observed Low Mass Dwarf Galaxies}
\label{sec:observation}

As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs. Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of $z = 0$ dwarf galaxies. However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies. We show that these properties are broadly consistent with observations.

\subsubsection{Gas and Star Formation}
\label{sec:gas_sf}

The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted HI surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}. However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small. In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies. In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.

Although simple to measure in simulations, these quantities are challenging to directly compare to observations. We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}. We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the area of the disk within the radius of the outermost star formed within the previous 10 Myr. Likewise, $\Sigma_{\rm gas} = M_{\rm gas,10} / A_{*,10}$, where M$_{\rm gas,10}$ is the total gas mass within this defined disk. However, the total gas content cannot be determined observationally. To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He. We note that there is generally no correction made for any possible H$_{\rm 2}$ or HII content. As shown in Section~\ref{sec:molecular gas content}, these components may be significant.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
\includegraphics[width=0.475\linewidth]{all_gas_efficiency_evolution.png}
\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late. See text for details of the calculation. Recent observations from the SHIELD sample \protect\citep{Teich2016} are plotted as black points with error bars. On the left, we also give the best fit line to galaxies from the FIGGS sample from \protect\cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \protect\cite{Shi2011}. There is no clear correlation with time in this diagram.}
\label{fig:KS}
\end{figure*}

We include recent observational constraints on these relationships in Figure ~\ref{fig:KS}. Our galaxy fluctuates significantly about both relationships with no clear trends in time. However, in both cases, it is consistent with the available observational sample. At times our galaxy exhibits gas surface densities below the observational constraints. The trend is still consistent with higher densities at this point, but with a larger scatter towards lower star formation rate densities and efficiencies.

In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters. It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy. This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk. The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.

\subsubsection{Molecular Gas Content}
\label{sec:molecular gas content}
The molecular gas content of low-mass dwarf galaxies is generally assumed
to be small, but is not well constrained by either theory or observations. Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values. As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range. H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$. The gas-phase reaction dominates in our low-metallicity galaxy over the other two channels by several orders of magnitude. In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$. Thus the presence of some ionizing background is required to generate the molecular fractions we find in our simulations, as confirmed in separate test simulations.

In contrast, \citet{Hu2016} and \citet{Hu2017} find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$). However, although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field. Our model suggests that both H$^{-}$ and the UV background are critical components in H$_2$ formation in small dwarf galaxies. Indeed it is not surprising that the gas phase reactions dominate over grain catalysis at low metallicity \citep{Glover2003}, though it is worth noting that the rate coefficients associated with gas-phase H$_2$ formation are still uncertain by an order of magnitude \citep{Glover2006,Glover2007}. Our model does lack additional chemistry that may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays.

In addition, our model does not account for the stellar component of the radiation field that leads to H$^{-}$ photodetachment ($E_\gamma > 0.76$~eV), though we do account for the contribution from the UVB. We find that the H$_2$ fraction is more strongly dependent upon the Lyman-Werner radiation field, which is followed for each star, than the H$^{-}$ photodetachment rate. Our tests suggest that, by ignoring the stellar contribution to H$^{-}$ photodetachment, our results may represent upper limits on the H$_2$ mass. However, including this component will likely only make a substantial difference during periods of no star formation, when there are no massive stars with significant Lyman-Werner luminosities. We do not anticipate this to have a significant dynamical impact on our simulations, as is discussed in more detail in Appendix~\ref{appendix:H minus}.

It is unclear how the combination of all of the above effects will behave, especially considering that, even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}. These uncertainties certainly warrant further study of molecular gas in low metallicity dwarf galaxies.

\subsubsection{Metal Retention}
\label{sec:obs_metals}

The simulations presented here have not yet been run for the gigayear timescales required to begin to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$. However, we can compare to a key observable: the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from closed box stellar evolution models given the galaxy's star formation history. This can be done readily with Milky Way dSph's. Their stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}. However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.

Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gas-rich, star forming, low-mass dwarf galaxy, with an observable HII region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment. Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}. As discussed in Section~\ref{sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations. However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs. Although more than half of these metals are expected to eventually re-accrete \citep{Christensen2016,Christensen2018,Angles-Alcazar2017}, it is still possible that most of the metals that have been produced at these early times will remain outside the galaxy disk.

It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium. While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}. We find 5.3\% of all metals lie within 1 kpc of the center of our galaxy, 24.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 51\% outside $R_{\rm vir}$. This is consistent with previous works, but this is again an evolving quantity. In addition, the amount of gas that escapes the virial radius is certainly sensitive to the details of gas accretion from the IGM on this galaxy, which we cannot capture in this model.

The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies. Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return. In addition, the accretion of pristine gas from the intergalactic medium could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals. This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.

\subsection{Missing Physics}
Although we include many detailed physical models in our simulations, there remain additional physical processes that may be relevant, which we now discuss.

\subsubsection{Massive Stellar Wind Energy}
\label{sec:stellar winds discussion}
Our massive stellar wind model drastically reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$. Although our algorithm is entirely capable of generating realistic stellar winds with velocities comparable to those observed, such fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical. When considered in isolation, stellar winds are an important source of pre-SN feedback and can dramatically influence dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}. However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or  individual giant molecular clouds \citep{Dale2014}, unless densities near the ionizing source are high enough to trap the  HII region in the source cell. In that case, they can clear out a cavity to allow initial establishment of the HII region.

They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}. Although they likely have minimal dynamical importance at resolutions where peak densities are not anyway high enough to trap ionization fronts, a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting closer examination in future work.

\subsubsection{Cosmic Rays} 
\label{sec:CRs}

Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2018}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}. These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}. Modeling cosmic rays is challenging, however, as they encompass a wide range of energies, and there are significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}. Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy. In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM. Modeling cosmic ray feedback completely thus requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena. Finally, including MHD presents additional difficulties in untangling the effects of each individual feedback mechanism on galaxy chemodynamics.

We do note that an isotropic, two-fluid model for cosmic ray feedback exists in  \textsc{Enzo} \citep{SalemBryan2014,Salem2015} and has been well tested. Mechanically, including this relatively simple treatment of cosmic ray feedback in our model is trivial. However, the cosmic ray population, their diffusion coefficient, and the magnetic field structure of the lowest mass dwarf galaxies each have significant enough uncertainties to warrant reserving their full inclusion into our model to later work.

\subsection{Detailed Stellar Evolution and Binary Stars}
\label{sec:binary stars}

Roughly half of massive stars live in binary pairs \citep{Sana2013}. Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes. This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as SNe. This effect could be significant, but is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g. STARBURST99). For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse SNe occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr. Although they find only $\sim 15\%$ of core collapse SNe explode after 50~Myr, this could still be an important effect. Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}. Extending the lifetimes of these stars combined with accounting for binary effects that change the luminosities of these stars \citep{Gotberg2017,Gotberg2018} could increase the importance of radiation feedback; however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}.

Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars. This is beyond the scope of this project, but will be investigated in future work.

\section{Conclusion}
\label{sec:conclusion}
We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment. For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, using individual star particles to model core collapse and Type Ia SNe, ionizing radiation followed through radiative transfer, photoelectric heating, Lyman-Werner radiation and pollution from AGB and massive stellar winds. This treatment of feedback, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail. In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P dwarf galaxy. We present an overview of the properties of this simulation in this work.

For our simulated dwarf galaxy, we find:
\begin{enumerate}
\item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies. (See Figs.~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).

\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, falling to $\eta \sim 10$ at R$_{\rm vir}$,  and
metal mass loading factors near unity. By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Fig.~\ref{fig:outflow_velocity}).

\item 
Only $\sim$4\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of low-mass dwarfs.  By the end of the simulation $\sim$45\% of the remaining metals stay within the virial radius (but outside the galaxy), while $\sim$50\% 
have been ejected beyond the virial radius. (See Figs.~\ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)

\item 
Beyond the stellar radius, the gas scale height is thin ($\sim 50$~pc), yet resolved, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius. This is comparable to the resolution limit of the diffuse HI in observed, gaseous low-mass dwarfs. At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Fig.~\ref{fig:scale_height}).

\item The ISRF of our galaxy varies strongly in both space and time by orders of magnitude. It is unclear how important these fluctuations are as a source of feedback, or if the affect can be approximated with a time-averaged radial profile. The importance of radiation feedback in our model is investigated in more detail in \cite{Emerick2018b}. (See Figs.~\ref{fig:ISRF} and \ref{fig:ISRF_2D}.)

\item 
We find H$_2$ fractions below 5\% in our dwarf galaxy, consistent with the poor constraints on molecular gas formation in low metallicity dwarf galaxies. This H$_2$ forms entirely through gas-phase reactions facilitated by H$^{-}$ in self-shielding regions; H$_2$ formation on dust grains and in the three body reaction are both insignificant. Cold, neutral hydrogen dominates the mass of our galaxy. While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Fig.~\ref{fig:sfr_mass_evolution} and Fig.~\ref{fig:ISM_evolution}.)

\item Finally, we present gas-phase oxygen and nitrogen distributions as examples to briefly demonstrate that there are marked differences in how individual metal species are distributed within the ISM of our galaxy. These variations could be tied to differences in elemental yields among different sources (for example, AGB winds vs. SNe), as suggested by \cite{KrumholzTing2018}. This is explored in more detail in \citep{Emerick2018c}.
\end{enumerate}

\section*{Acknowledgments:} 
We would like to thank the following for their advice and valuable discussions, without which this work would not have been possible: B. C\^ot\'e, S. Glover, K. Hawkins, C. Hu, K. Johnston, B. O'Shea, M. Putman, B. Smith, J. Wall, and J. Wise. We would additionally like to thank the referee for their careful report. A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. G.L.B. is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955. M.-M.M.L. was partly funded by NASA  grant NNX14AP27G. We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}. These are products of collaborative effort by many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible.

%\bibliographystyle{yahapj}
\bibliographystyle{mnras}
\bibliography{msbib}

\appendix
\renewcommand\thefigure{\thesection.\arabic{figure}}    
\setcounter{figure}{0}

\section{Gas Phases of the ISM}
\label{appendix:phases}

To aid in comparison to other works, we define our ISM phases here, as adopted and modified from \citet{Draine2011}, Table 1.3, and used consistently throughout this analysis. By construction, these phases are mutually exclusive. We take $f_{\rm H_2}$ to be the molecular hydrogen fraction of the total gas mass.

\begin{enumerate}
\item Hot Ionized Medium (HIM): $T \geq 10^{5.5}$ K
\item Warm Ionized Medium (WIM): $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $
\item Warm Neutral Medium (WNM): $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$
\item Cold Neutral Medium (CNM): $T < 10^2$ K, $f_{\rm H_2} \leq 0.5$
\item Molecular: $T < 10^2$~K, $f_{\rm H_2} > 0.5$
\end{enumerate}

\section{Stellar Radiation Properties}
\label{appendix:radiation}
We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set. In Fig.~\ref{fig:stellar radiation properties} we plot these properties. We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass. This requires two factors for each radiation type, one for low mass and one for high mass stars. We use the following multiplicative factors to adjust the black body spectrum for HI and HeI ionizing radiation respectively: [0.1, 3.2] and [0.0001, 4.0]. We do not find this adjustment to be necessary for the FUV and Lyman-Werner radiation bands.

The ionizing radiation photon energies are taken as the average ionizing photon energy for a black body of the star's given T$_{\rm eff}$ obtained from the PARSEC grid. A more accurate approach to compute this energy would convolve the full stellar spectrum and the frequency-dependent absorption cross section. We tested this approach using the frequency-dependent photoionization cross sections from \citet{1996ApJ...465..487V}.\footnote{Source code containing the analytic fits given in \citet{1996ApJ...465..487V} was obtained from \url{http://www.pa.uky.edu/~verner/photo.html}} 
The blackbody approximation is accurate to within 5\%, yet substantially easier to compute on the fly, as integrals over the blackbody spectrum can be expressed as infinite series that rapidly converge to high precision. Unlike for the ionizing radiation, we assume constant FUV and Lyman-Werner band energies for each star, at 9.8 eV and 12.8 eV respectively.

\begin{figure*}
\centering
\includegraphics[width=0.4\linewidth]{Q0}
\includegraphics[width=0.4\linewidth]{Q1}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{L_FUV}
\includegraphics[width=0.4\linewidth]{L_LW}
\vspace{0.01cm}
\includegraphics[width=0.4\linewidth]{E0}
\includegraphics[width=0.4\linewidth]{E1}
\caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right). Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
\label{fig:stellar radiation properties}
\end{figure*}

\setcounter{figure}{0}
\section{Typical Gas Densities in Supernova Injection Regions}
\label{appendix:SN}

Modeling SN feedback with the injection of thermal energy alone can lead to rapid overcooling of the injected energy, and a significant underestimate of the effects of SN feedback. Often, ad hoc solutions to this problem are used in large simulations with coarse resolution, such as momentarily turning off cooling in feedback affected regions or decoupling affected regions from the hydrodynamics for some time. However, physically consistent solutions have been developed \citep[e.g][]{Simpson2016} that inject a mixture of kinetic and thermal energy with a ratio that depends on resolution and local gas density. Overcooling becomes less important with higher resolution and lower ISM densities, until eventually pure thermal energy injection is sufficient to resolve each SN. We take advantage of our high resolution and employ a simple thermal energy injection model for our SN feedback. We demonstrate how well this resolves our SNe in the comparison simulation presented in this work.

The left panel of Fig.~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation. As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$. For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations. The right panel of Figure ~\ref{fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
\begin{equation}
R_{\rm PDS} = 
\begin{cases}
49.3E^{1/4}_{51}n^{-1/2}_{o} & if  Z \le 0.01 \\
18.5E^{2/7}_{51}n^{-3/7}_{o}Z^{-1/7} & if  Z \ge 0.01 \\
\end{cases}
\end{equation}
where $E_{51}$ is the injection energy in units of 10$^{51}$~erg, $n_{o}$ is the number density of the medium, and $Z$ is the metallicity in units of $Z_{o}$. \citet{Simpson2016} found that $R_{\rm PDS} > 4.5 \Delta x$ is needed to resolve the SN explosion with thermal energy injection alone, assuming uniform density in the injection region. In practice, the injection region is never uniform. We give $R_{\rm PDS}$ assuming uniform density at both the average and maximum number density in the injection region of each SN. As shown, a majority of SNe are resolved (to the right of the 4.5$\Delta x$ line), but up to 8.3\% are not well resolved and 2.0\% are completely unresolved (below a single cell width). In general, these are SN explosions from the most massive (i.e. most prompt) stars. We do not expect that resolving these SNe will dramatically alter our results. However, we note that using our feedback model at resolutions much less than a few parsecs will require implementing an different injection mechanism.

\begin{figure*}
\centering
\includegraphics[width=0.4\linewidth]{sn_density_hist}
\includegraphics[width=0.4\linewidth]{sn_radius_hist}
\caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation. {\em Right:} Distribution of the radius of the pressure-driven snowplow phase for each SN assuming a uniform medium at either the peak or average density in the injection region. The vertical lines show one and 4.5 cell widths. This shows that a fraction of these SNe are certainly unresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
\label{fig:SN histogram}
\end{figure*}

\setcounter{figure}{0}
\section{Cooling and Heating Rates}
\label{appendix:cooling}

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
\caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background. Our model (black) uses self-consistent metal line cooling rates, and is compared to an incorrect model (orange) that adopts the uncorrected (i.e. optically thin) metal line cooling rates. The regimes where heating dominates are plotted with dashed lines for clarity.}
\label{fig:cooling comparison}
\end{figure*}

The cooling curves used in this work include a correction to a significant conceptual inconsistency one may encounter when using tabulated metal line cooling rates in combination with a self-shielding approximations. \citet{Hu2017} details this inconsistency: metal cooling rates computed under the assumption of an optically thin UV background overestimate the electron fraction in regimes where self-shielding is important ($-0.5 \leq \rm{log(n~[cm^{-3}])} < 2$). This results in an artificially enhanced metal line cooling rate in regions of self-shielding. This can be a significant effect, particularly at higher metallicities. We demonstrate this in Fig.~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities. The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher. In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas. Fig.~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy. We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.

For densities where self-shielding is important, we computed \textsc{Cloudy} models of one-dimensional clouds at each temperature and density pair with a physical size corresponding to the Jeans length. In cases where the Jeans length is very large, we limit the size to 100 pc, a reasonable approximation for the maximum size of a self-gravitating cloud. We then adopt the metal line cooling rates obtained from the center of these clouds, whose outside is exposed to the UV background. These models were computed with a modified version of the \texttt{CIAOLoop}\footnote{https://bitbucket.org/brittonsmith/cloudy\_cooling\_tools (our version: https://github.com/aemerick/cloudy\_tools)} code used in \citet{2008MNRAS.385.1443S}. In computing these tables we had to include the cosmic ray ionization that dominates in optically thick clouds. Without this effect, \textsc{Cloudy} becomes unstable in entirely neutral regions. We adopted a cosmic ray ionization rate of 10\% the Milky Way value, though we note that varying this from 1\% to 100\% the Milky Way value did not have an effect on the extracted metal line cooling rates.

Finally, we note that the cooling and heating rates in our simulation will deviate from these curves, as they depend upon local conditions that cannot be accounted for here. The primordial cooling and heating rates are computed consistently with the non-equilibrium chemistry solver, leading to deviations from the tabulated primordial rates, and the heating rates depend upon the local stellar radiation field, which is not included in these diagrams.

\begin{figure*}
\centering
\includegraphics[width=0.95\linewidth]{cooling_curve}
\caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}. The absolute value of the net cooling or heating
rate is shown with solid lines.}
\label{fig:cooling}
\end{figure*}

\setcounter{figure}{0}
\section{H$^{-}$ Photodetachment}
\label{appendix:H minus}

As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations. Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, can be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}. Our current model does not include this contribution. To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https://grackle.readthedocs.io/en/latest/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) and initial temperature of 10$^{4}$~K for 200~Myr. In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background. As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate. In effect, our simulations move left-to-right in this diagram (only) as stars form (right) or die (left). A complete model, including the stellar contribution to H$^{-}$ photodetachment, would move somewhat diagonally.

We follow up on the qualitative conclusions of these models by running four simulations at the four points in the diagram. These runs have identical initial conditions, random SN driving, cooling, heating, and chemistry as our fiducial simulation, but with no star formation. We vary the Lyman-Werner radiation and the H$^{-}$ photodetachment rate by the factors shown, which are comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}). Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9. Applying both scale factors gives a reduction of 7.9. Thus, we see that the difference between the more realistic case in which both rates increase by the same factor, and the case assumed in the simulations, is only about 20\%.

Although the replacement of star formation by random SNe in these models produces qualitatively different galaxy properties, the point of these simulations is to be maximal models of H$_2$ formation. We demonstrate that, even in this case, there is not a dramatic change in the total H$_2$ formation and that the effect of varying the H- photodetachment rate is sub-dominant to other factors. Therefore, we do not expect that ignoring this component of the stellar radiation field will have a significant dynamical impact on our galaxy evolution.

\begin{figure}
\centering
\includegraphics[width=0.95\linewidth]{fH2.png}
\caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation. Each model is held at a uniform density $n = 10$~cm$^{-3}$. Each model varies either the H$^{-}$ photodetachment rate or the Lyman-Werner background over their respective UVB values by a given scale factor. Contours give factors of ten change in the H$_2$ fraction. We note the regime below 1.0 on each axis is somewhat unphysical, and is never reached in our hydrodynamics simulations.}
\label{fig:Grackle grid}
\end{figure}

H$^-$ photodetachment arises from lower energy photons, above 0.76~eV, with a peak in effectiveness around 2~eV. For this reason, low mass stars may contribute significantly, if not dominate, the radiation field responsible for this reaction. The Lyman-Werner radiation field is dominated by short-lived massive stars, with some contribution from older stars up to a few hundred Myr, and is thus subject to significant fluctuations, particularly in periods of no star formation. During these times, H$^-$ photodetachment from low energy photons may play a non-negligible role in regulating H$_2$ formation. Indeed there is H$_2$ growth during these periods due to a decrease in the Lyman-Werner field, but it is unclear how much of this would be attenuated by accounting for photons from lower mass stars. Doing so in our current model, applying an optically thin $1/R^2$ field for each star, would be computationally challenging due to the dramatic increase in the number of stars whose radiation would need to be tracked.

As emphasized in Section~\ref{sec:molecular gas content}, further work modeling low-metallicity dwarf galaxies with a more detailed chemistry model would be useful to clarify the role of various competing phenomena in driving the molecular properties of these galaxies.

\setcounter{figure}{0}
\section{Resolution Study}
\label{appendix:resolution_study}

We demonstrate the effect of varying resolution in the evolution of our galaxy model in Fig.~\ref{fig:resolution_study}. We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines). The physics in each simulation remains the same with the exception of star formation, which employs a resolution-dependent density threshold. A factor of two decrease in resolution translates to a factor of four decrease in the star formation density threshold, from 200~cm$^{-3}$ in our fiducial runs, to 50~cm$^{-3}$ and 12.5~cm$^{-3}$ in our 3.6~pc and 7.2~pc resolution runs respectively. As a result, the time at which star formation first occurs varies between the simulations, but we again define t = 0 as the time of first star formation in each simulation.

\begin{figure*}
\centering
\includegraphics[width=0.33\linewidth]{sfr_resolution_study.png}
\includegraphics[width=0.33\linewidth]{mass_evolution_resolution.png}
\includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
\caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted). The line colors in the left panel are for better clarity between the SFRs.}
\label{fig:resolution_study}
\end{figure*}

Fig.~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few. We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation. The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs. We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Fig.~\ref{fig:SN histogram}. However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.

Generally ineffective feedback leads to increased, not decreased, star formation rates. However, the lower resolution run has the lowest SFR. The source of this difference is likely related to the ability to resolve dense, cold gas in the lower resolution simulations. In particular, the low resolution simulation clearly is unable to resolve the densities at which gas-phase H$_2$ formation becomes efficient, leading to significantly lower H$_2$ fractions (middle panel) and lower cooling rates. In addition, whatever H$_2$ does form at these lower resolutions exists at lower gas densities than in our fiducial run, and is less well protected by self-shielding effects. This is shown clearly in the significant plummet in the H$_2$ mass during the phase of first star formation that is less severe in our fiducial run. In this low metallicity regime, where H$_2$ is an important coolant, the ability to resolve the densities responsible for H$_2$ formation and self-shielding is important.

Theses differences in densities are shown clearly by comparing Fig.~\ref{fig:phase} with Fig.~\ref{fig:phase_resolution}. Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations. In the 7.2~pc run, the gas phases are notably less distinct, with gas more evenly smoothed out in the multi-phase region between cold, dense gas and warm, ionized gas. We note the 7.2~pc simulation, which ran quickly, was conducted without the temperature ceiling used in the 3.6~pc and fiducial runs; we do not expect this to have a significant effect on the comparison.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{3pc_phase.png}
\includegraphics[width=0.475\linewidth]{6pc_phase.png}
\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:phase}.}
\label{fig:phase_resolution}
\end{figure*}

Finally, the metal retention fraction (right panel) between the fiducial and 3.6~pc runs are quite similar, but is significantly higher for the lowest resolution simulation. It is likely, however, that this is a result of the lower SFR in the 7.2~pc run and is not directly a resolution effect. This also affects the fraction of metals ejected outside the virial radius, with less metals being ejected in the lower resolution runs.

\label{lastpage}

\end{document}

### 2019-03-07 radiation_letter/arxiv/ms.tex

--- 2018-09-19 ms.tex
@@
 %
-Effective stellar feedback is used in models of galaxy formation to drive realistic galaxy evolution.
+Effective stellar feedback is used in models of galaxy formation to 
+%regulate star formation and 
+drive realistic galaxy evolution.
 Models typically include energy injection from supernovae as the dominant form of stellar feedback, often in some form of sub-grid recipe.
 However, it has been recently suggested that pre-SN feedback (stellar winds or radiation) is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM).
-Following these processes is computationally challenging, so many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation.
+Following these processes is computationally challenging,
+%Following stellar winds and ionizing radiation is computationally challenging, 
+so many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation.
 In this work we examine high resolution simulations (1.8~pc) of an isolated dwarf galaxy with detailed stellar feedback tracked on a star-by-star basis.

### 2019-03-07 individual_metals/main.tex

--- 2018-10-29 main.tex
@@
 \centering
-\includegraphics[width=0.99\linewidth]{species_bar.png}\\
-\includegraphics[width=0.99\linewidth]{species_bar_ISM.png}
+\includegraphics[width=0.99\linewidth]{species_bar}\\
+\includegraphics[width=0.99\linewidth]{species_bar_ISM}
 \caption{Top: The mass fraction of each metal species in the \textit{full simulation box} contained in the halo, gas in the galaxy disk, and stars.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{species_bar_sources.png}\\
+\includegraphics[width=0.95\linewidth]{species_bar_sources}\\
 \caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{SE_density.png}\\
-\includegraphics[width=0.95\linewidth]{SE_z.png}
+\includegraphics[width=0.95\linewidth]{SE_density}\\
+\includegraphics[width=0.95\linewidth]{SE_z}
 \caption{The volume-averaged gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
@@
 \centering
-\includegraphics[width=0.95\linewidth]{DD0390_element_by_element.png}
+\includegraphics[width=0.95\linewidth]{DD0390_element_by_element}
 \caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black).
@@
 \centering
-\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution.png}
+\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution}
 \caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0.png}
+\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0}
 \caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, without continuing star formation.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{stellar_CNM_distance.png}
+\includegraphics[width=0.95\linewidth]{stellar_CNM_distance}
 \caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the time within 1~Myr (our time resolution) of each star's formation time.
@@
 \centering
-\includegraphics[width=0.475\linewidth]{density_PDF.png}
-\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted.png}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr.
+\includegraphics[width=0.475\linewidth]{density_PDF}
+\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr.
 The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
@@
 \centering
-\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study.png}
+\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study}
 \caption{Resolution comparison of two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.

### 2019-03-07 get_all_citations.py
first commit. Gathers all of the citations for each paper and prints to screen

@@ -1,0 +1,30 @@
+"""
+Simple script to gather all of the included bibtex
+citation information for all papers and print
+to screen.
+
+Simply run as:
+  $ python get_all_citations.py
+"""
+
+import glob
+import numpy as np
+
+def grab_files(fpath = "."):
+    files = np.sort(glob.glob(fpath + '/*/citation.bib'))
+    return files
+
+def print_files(files):
+
+    for fname in files:
+        f = open(fname,'r')
+        print (f.read())
+        f.close()
+
+    return
+
+
+if __name__ == "__main__":
+
+    files = grab_files()
+    print_files(files)

### 2019-03-08 thesis/abstract.tex
moving thesis directory

%
% Abstract
%

\thispagestyle{empty}
\begin{center}

{\Large \bf ABSTRACT}

\vskip.35in
{\Large \bf TITLE HERE}

\vskip.35in
{\large YOUR NAME} \\
\vskip.35in
\end{center}
In this \thesis... TEXT HERE

### 2019-03-08 thesis/chapters/ch_chapter1.tex
First pass at adding in a chapter. Some of the refs are broken.

--- 2019-03-07 method_paper/main.tex
@@
-\documentclass[fleqn,usenatbib,useAMS]{mnras}
-\pdfoutput=1 
-\usepackage{graphicx}	% Including figure files
-\usepackage{amsmath}	% Advanced maths commands
-\usepackage{amssymb}	% Extra maths symbols
-\usepackage{multicol}        % Multi-column entries in tables
-\usepackage{bm}		% Bold maths symbols, including upright Greek
-%\usepackage{pdflscape}	% Landscape pages
-
-\usepackage[T1]{fontenc}
-\usepackage{ae,aecompl}
-\usepackage{newtxtext,newtxmath}
-
-%\usepackage{amsmath,amstext}
-%\usepackage[T1]{fontenc}
-\usepackage[figure,figure*]{hypcap}
-
-%\hypersetup{draft}
-%\usepackage{multirow}
-%\usepackage{mathtools}
-%\renewcommand*{\sectionautorefname}{Section} %for \autoref
-%\renewcommand*{\subsectionautorefname}{Section} %for \autoref
-%\usepackage{graphicx}
-%\usepackage{natbib} % bibliography
-
-%\usepackage[active,floats,tightpage]{preview}
-%    \setlength\PreviewBorder{1em}
-
-\newcommand{\msun}{M$_{\odot}$}
-\newcommand{\ccunit}{cm$^{-3}$}
-
-\title[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars}
-
-\author[A. Emerick et. al.]{
-Andrew Emerick,$^{1,2}$
-Greg L. Bryan,$^{1,3}$
-and Mordecai-Mark Mac Low$^{2,1,3}$
-\\
-$^{1}$Department of Astronomy, Columbia University, New York, NY, 10027, USA\\
-$^{2}$Department of Astrophysics, American Museum of Natural History, New York, NY, USA\\
-$^{3}$Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-
-\begin{document}
-
-\label{firstpage}
-%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
-%\title{Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars}
-
-%\author{Andrew Emerick}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\author{Greg L. Bryan}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-%\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-%\author{Mordecai-Mark Mac Low}
-%\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-%\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-
-%\affiliation{Institut f{\"u}r Theoretische Astrophysik, Zentrum f{\"u}r Astronomie der Universit{\"a}t Heidelberg, Heidelberg, Germany}
-
-\begin{abstract}
-In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
+\chapter[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars \label{ch:chapter1}}
+\let\thefootnote\relax\footnotetext{This section contains text from an article published in \cite{Emerick2019}}
+
+%
+% Copy paste paper here, without abstract or keywords
+%
+%
+% Abstract left here for documenation purposes
+%
+%\begin{abstract}
+%In order to better understand the relationship between feedback and galactic chemical evolution, we have developed a new model for stellar feedback at grid resolutions of only a few parsecs in global disk simulations, using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
 For the first time in galaxy scale simulations, we simulate detailed stellar feedback from individual stars including asymptotic giant branch winds, photoelectric heating, Lyman-Werner radiation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae.
@@
 Finally, we demonstrate that these simulations yield valuable information on the variation in mixing behavior of individual metal species within the multi-phase interstellar medium.
-\end{abstract}
-
-\begin{keywords}
-Galaxy -- Hydrodynamics -- Simulation -- Feedback
-\end{keywords}
+%\end{abstract}
+
+\newcommand{\ccunit}{cm$^{-3}$}
 
 \section{Introduction}
-%
-% AE removed below.. MM suggested  skipping both pars.
-%
-%Cosmological simulations of galaxy evolution have shown increasing agreement with observations over the past decade.
-Recent works have been able to well capture the star forming main sequence, the stellar mass to halo mass relationship, mass metallicity relationship, etc.
-\citep[e.g.][]{EAGLE,Illustris1,Illustris2,FIRE,Dave2017} across a wide range of galaxy masses.
-On small scales, simulations have been able to resolve the long standing disagreement between $\Lambda$CDM cosmology and observed galaxies on the low-mass end without invoking new physics beyond $\Lambda$CDM.
-This includes the missing satellites problem \citep{Moore1999,Klypin1999}, too big to fail \citep{MBK2011,MBK2012,GK2014}, and the observed coring of inner dark matter profiles \citep[e.g.][]{Oh2011}.
-See both \citet{SomervilleDave2015} and \citet{NaabOstriker2016} for recent reviews on these topics.
-%
-%These simulations generally owe their successes to a combination of better accounting of the baryonic physics that governs galaxy evolution and higher resolution.
-In particular, a detailed accounting of both multi-channel stellar feedback processes and AGN has shown significant promise over schemes that include supernovae alone, albeit at much greater computational expense.
-In spite of this progress, practical considerations still limit large cosmological simulations to using sub-grid, phenomenological feedback models, often tuned to reproduce observed galaxy relationships.
-For this reason, we still have yet to arrive at a complete, self-consistent picture of how feedback governs galaxy evolution.
-
 Detailed interstellar medium (ISM) and chemical abundance properties of galaxies are sensitive tests of the underlying physical processes that govern galaxy evolution.
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
+\includegraphics[width=0.975\linewidth]{figures/ch1/multiplot_4x4_x.png}
 \caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0, 150, 300, and 500 Myr after the beginning of star formation.
@@
 \centering
-\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
+\includegraphics[width=0.975\linewidth]{figures/ch1/multiplot_4x4_z.png}
 \caption{Same as Fig.~\ref{fig:panel_x}, but showing face-on views.}
@@
 \centering
-\includegraphics[width=0.975\linewidth]{scale_height}
+\includegraphics[width=0.975\linewidth]{figures/ch1/scale_height}
 \caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
@@
 \centering
-\includegraphics[width=0.475\linewidth]{sfr_snrx100}
-\includegraphics[width=0.475\linewidth]{mass_evolution}
+\includegraphics[width=0.475\linewidth]{figures/ch1/sfr_snrx100}
+\includegraphics[width=0.475\linewidth]{figures/ch1/mass_evolution}
 \caption{Left: The SFR and core collapse SN rate in our dwarf galaxy in 10 Myr bins.
@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{phase_diagram.png}
+\includegraphics[width=0.95\linewidth]{figures/ch1/phase_diagram.png}
 \caption{The temperature vs.\ number density phase diagram of our dwarf galaxy simulation showing all gas interior to 0.25~$R_{\rm vir}$, averaged over a 50~Myr period from t~=~300~Myr to t~=~350~Myr.
@@
 %\centering
-\includegraphics[width=0.45\linewidth]{phase_mass_fraction_evolution_log.png}
-\includegraphics[width=0.45\linewidth]{phase_volume_fraction_evolution_log.png}
+\includegraphics[width=0.45\linewidth]{figures/ch1/phase_mass_fraction_evolution_log.png}
+\includegraphics[width=0.45\linewidth]{figures/ch1/phase_volume_fraction_evolution_log.png}
 \caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{G_o_profile} \\
-\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
+\includegraphics[width=0.95\linewidth]{figures/ch1/G_o_profile} \\
+\includegraphics[width=0.95\linewidth]{figures/ch1/ionizing_photon_profile}
 \caption{
@@
 %\centering
-\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
-\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
+\includegraphics[width=0.45\linewidth]{figures/ch1/g_o_2D_phase}
+\includegraphics[width=0.45\linewidth]{figures/ch1/q_o_2D_phase}
 \caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
@@
 \begin{figure*}
-\includegraphics[width=0.45\linewidth]{total_mass_outflow}
-\includegraphics[width=0.45\linewidth]{total_mass_loading}
+\includegraphics[width=0.45\linewidth]{figures/ch1/total_mass_outflow}
+\includegraphics[width=0.45\linewidth]{figures/ch1/total_mass_loading}
 \caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
+\includegraphics[width=0.95\linewidth]{figures/ch1/velocity_distribution_time_average}
 \caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
@@
 \begin{figure}
-\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
-\includegraphics[width=0.9\linewidth]{metal_retention}
+\includegraphics[width=0.9\linewidth]{figures/ch1/metal_mass_loading} \\
+\includegraphics[width=0.9\linewidth]{figures/ch1/metal_retention}
 \caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:mass_outflow}.
@@
 \begin{figure*}
-\includegraphics[width=0.98\linewidth]{log_NO_panel}
+\includegraphics[width=0.98\linewidth]{figures/ch1/log_NO_panel}
 \caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances.
@@
 \centering
-\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution.png}
-\includegraphics[width=0.475\linewidth]{all_gas_efficiency_evolution.png}
+\includegraphics[width=0.475\linewidth]{figures/ch1/all_gas_schmidt_law_evolution.png}
+\includegraphics[width=0.475\linewidth]{figures/ch1/all_gas_efficiency_evolution.png}
 \caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
@@
 %\bibliographystyle{yahapj}
-\bibliographystyle{mnras}
-\bibliography{msbib}
+%\bibliographystyle{mnras}
+%\bibliography{msbib}
+
+%************* APPENDICES ************************%
+
+%\clearpage
+%\appendix
 
@@
 \centering
-\includegraphics[width=0.4\linewidth]{Q0}
-\includegraphics[width=0.4\linewidth]{Q1}
+\includegraphics[width=0.4\linewidth]{figures/ch1/Q0}
+\includegraphics[width=0.4\linewidth]{figures/ch1/Q1}
 \vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{L_FUV}
-\includegraphics[width=0.4\linewidth]{L_LW}
+\includegraphics[width=0.4\linewidth]{figures/ch1/L_FUV}
+\includegraphics[width=0.4\linewidth]{figures/ch1/L_LW}
 \vspace{0.01cm}
-\includegraphics[width=0.4\linewidth]{E0}
-\includegraphics[width=0.4\linewidth]{E1}
+\includegraphics[width=0.4\linewidth]{figures/ch1/E0}
+\includegraphics[width=0.4\linewidth]{figures/ch1/E1}
 \caption{Radiation properties for our model stars, showing the ionizing photon luminosities for HI (top left) and HeI (top right) for each star, the FUV (middle left) and Lyman-Werner (middle right) luminosities, and finally the average ionizing photon energy for HI (bottom left) and HeI (bottom right).
@@
 \centering
-\includegraphics[width=0.4\linewidth]{sn_density_hist}
-\includegraphics[width=0.4\linewidth]{sn_radius_hist}
+\includegraphics[width=0.4\linewidth]{figures/ch1/sn_density_hist}
+\includegraphics[width=0.4\linewidth]{figures/ch1/sn_radius_hist}
 \caption{{\em Left:} Distribution of peak (orange) and average (black) gas densities in the injection region of each of the SNe from the simulation.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{cooling_model_comparison}
+\includegraphics[width=0.95\linewidth]{figures/ch1/cooling_model_comparison}
 \caption{The absolute value of the net cooling or heating rate in two models that account for self-shielding of primordial gas against a metagalactic UV background.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{cooling_curve}
+\includegraphics[width=0.95\linewidth]{figures/ch1/cooling_curve}
 \caption{The total heating (dotted) and cooling (dashed) rates extracted from the core of a Jeans-length sized cloud irradiated by a \citet{HM2012} metagalactic UV background as modeled in \textsc{Cloudy}.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{fH2.png}
+\includegraphics[width=0.95\linewidth]{figures/ch1/fH2.png}
 \caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation.
@@
 \centering
-\includegraphics[width=0.33\linewidth]{sfr_resolution_study.png}
-\includegraphics[width=0.33\linewidth]{mass_evolution_resolution.png}
-\includegraphics[width=0.33\linewidth]{metal_retention_resolution.png}
+\includegraphics[width=0.33\linewidth]{figures/ch1/sfr_resolution_study.png}
+\includegraphics[width=0.33\linewidth]{figures/ch1/mass_evolution_resolution.png}
+\includegraphics[width=0.33\linewidth]{figures/ch1/metal_retention_resolution.png}
 \caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted).
@@
 \centering
-\includegraphics[width=0.475\linewidth]{3pc_phase.png}
-\includegraphics[width=0.475\linewidth]{6pc_phase.png}
+\includegraphics[width=0.475\linewidth]{figures/ch1/3pc_phase.png}
+\includegraphics[width=0.475\linewidth]{figures/ch1/6pc_phase.png}
 \caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:phase}.}
@@
 
-\label{lastpage}
-
-\end{document}
+%\label{lastpage}
+
+\setcounter{section}{0}%
+\renewcommand\thesection{\thechapter.\Alph{section}}
+
+\renewcommand\thesection{\thechapter.\arabic{section}}

### 2019-03-08 thesis/chapters/ch_chapter2.tex
first commit of radiation paper

--- 2019-03-07 ms.tex
@@
-\documentclass[twocolumn]{aastex62}
+\chapter[Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies]{Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies \label{ch:chapter2}}
+\let\thefootnote\relax\footnotetext{This section contains text from an article published originally as \cite{Emerick2018a}}
 
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
-
-\graphicspath{{./}{figures/}}
-\usepackage{natbib}
-\bibliographystyle{apj}
-
-\submitjournal{ApJ}
-
-\shorttitle{Radiation Feedback in Dwarf Galaxies}
-\shortauthors{Emerick et. al.}
-
-\begin{document}
-
-\title{Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies}
-
-\correspondingauthor{Andrew Emerick}
-\email{emerick@astro.columbia.edu}
-
-\author{Andrew Emerick}
-\affil{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}
-
-\author{Greg L. Bryan}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-
-\author{Mordecai-Mark Mac Low}
-\affil{Department of Astrophysics, American Museum of Natural History, New York, NY 10024}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-
-\nocollaboration
-
-% Letter word count:
-%    Text (including captions) : 3500
-%    Abstract                  : 500
-%    # Figures                 : 5
-%       max panels per fig     : 9
-%    # references              : 50
-
-\begin{abstract}
 %
+% Copy paste paper here, without abstract or keywords
 %
-% NOTE: Overleaf includes abstract words in word count in text... subtract
-%       this from the total.
+%\begin{abstract}
 %
-%
-Effective stellar feedback is used in models of galaxy formation to drive realistic galaxy evolution.
+%Effective stellar feedback is used in models of galaxy formation to drive realistic galaxy evolution.
 Models typically include energy injection from supernovae as the dominant form of stellar feedback, often in some form of sub-grid recipe.
@@
 Generalizing these results to more massive galaxies would be a valuable avenue of future research.
-\end{abstract}
-
-%% Keywords should appear after the \end{abstract} command. 
-%% See the online documentation for the full list of available subject
-%% keywords and the rules for their use.
-\keywords{galaxies -- feedback -- galaxy evolution}
+%\end{abstract}
 
@@
 
-In this work we use a detailed model for stellar feedback presented in \cite{Emerick2018} (hereafter Paper I) to study the role of radiation feedback in dwarf galaxy evolution.
+In this work we use a detailed model for stellar feedback presented in \cite{Emerick2019} (hereafter Paper I) to study the role of radiation feedback in dwarf galaxy evolution.
 For the first time in a galaxy-scale simulation, we resolve individual HII regions using an adaptive ray tracing radiative transfer method to follow the ionizing radiation from particles that represent individual stars.
@@
 Stellar lifetimes, surface gravity, effective temperature, and radii are set by the initial stellar mass and metallicity through interpolation over the PARSEC \citep{Bressan2012} zero age main sequence values.
-These properties are used to set the FUV, LW, and ionizing photon fluxes from each star through interpolation on the OSTAR2002 \citep{LanzHubeny2003} grid.
+These properties are used to set the FUV, LW, and ionizing photon fluxes from each star through interpolation on the OSTAR2002 \citep{Lanz2003} grid.
 We only model the radiation from stars with masses above 8~M$_{\odot}$.
@@
 \centering
-\includegraphics[width=0.49\linewidth]{sfr}
-\includegraphics[width=0.49\linewidth]{mass}
+\includegraphics[width=0.49\linewidth]{figures/ch2/sfr}
+\includegraphics[width=0.49\linewidth]{figures/ch2/mass}
 \caption{The star formation rate (left) and gas and stellar mass (right) of each of our three simulations over time. Time bins with no star formation are left empty.}
@@
 \centering
-\includegraphics[width=0.99\linewidth]{mass_density_cut}
+\includegraphics[width=0.99\linewidth]{figures/ch2/mass_density_cut}
 \caption{The total gas mass at $n > 200$~cm$^{-3}$, our star formation density threshold.}
@@
 \centering
-\includegraphics[width=0.32\linewidth]{metal_retention}
-\includegraphics[width=0.32\linewidth]{mass_outflow_comparison} 
-\includegraphics[width=0.32\linewidth]{mass_loading_comparison}
+\includegraphics[width=0.32\linewidth]{figures/ch2/metal_retention}
+\includegraphics[width=0.32\linewidth]{figures/ch2/mass_outflow_comparison} 
+\includegraphics[width=0.32\linewidth]{figures/ch2/mass_loading_comparison}
 \caption{{\bf Left:} The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange).
@@
 \centering
-\includegraphics[width=0.99\linewidth]{DD0136_fiducial_shortrad_nort}
+\includegraphics[width=0.99\linewidth]{figures/ch2/DD0136_fiducial_shortrad_nort}
 \caption{Edge-on slices of each simulation showing gas number density (left), temperature (middle), and hydrogen ionization fraction (right) 17~Myr after the formation of the first star in each run.
 Each panel is 4 kpc x 4 kpc.
-The full movie of this evolution \textbf{from 0 to 118 Myr} is included for further clarification.
-\textbf{This movie demonstrates that the differences in outflows between the simulations depends on the ability for feedback to carve low-density, ionized channels along which SNe can launch gas beyond the disk of the galaxy.
+The full movie of this evolution from 0 to 118 Myr is included for further clarification.
+This movie demonstrates that the differences in outflows between the simulations depends on the ability for feedback to carve low-density, ionized channels along which SNe can launch gas beyond the disk of the galaxy.
 These channels are readily created by ionizing radiation in the fiducial simulation, or to some degree by SNe in the noRT simulation due to its much higher SN rate.
 However, SNe launched gas is trapped by neutral, cold shells in the shortrad simulation, unable to easily escape from the disk of the simulated galaxy.
-These same insights can also be gained by comparing this figure with Figure~\ref{panel2}.}}
-\label{fig:panel1}}
+These same insights can also be gained by comparing this figure with Figure~\ref{fig:panel2}.}
 \label{fig:panel1}
@@
 \centering
-\includegraphics[width=0.99\linewidth]{DD0160_fiducial_shortrad_nort}
+\includegraphics[width=0.99\linewidth]{figures/ch2/DD0160_fiducial_shortrad_nort}
 \caption{Same as Figure~\ref{fig:panel1}, but at 40~Myr.}
@@
 
-\acknowledgments
+\section*{Acknowledgments:} 
 A.E.
@@
 
-\software{astropy \citep{astropy} matplotlib \citep{matplotlib}, Numpy \citep{numpy}, SciPy \citep{scipy}, IPython \citep{Ipython}, yt \citep{yt}, Enzo \citep{Enzo2014}, Grackle \citep{GrackleMethod}, CLOUDY \citep{cloudy}, HDF5 \citep{HDF5}}
+%\software{astropy \citep{astropy} matplotlib \citep{matplotlib}, Numpy \citep{numpy}, SciPy \citep{scipy}, IPython \citep{Ipython}, yt \citep{yt}, Enzo \citep{Enzo2014}, Grackle \citep{GrackleMethod}, CLOUDY \citep{cloudy}, HDF5 \citep{HDF5}}
 
-\bibliography{msbib}
+%************* APPENDICES ************************%
 
-\end{document}
+%\clearpage
+%\appendix
+\setcounter{section}{0}%
+\renewcommand\thesection{\thechapter.\Alph{section}}
+
+\renewcommand\thesection{\thechapter.\arabic{section}}

### 2019-03-08 thesis/chapters/ch_chapter1.tex
Final edits to fit with thesis style

@@
-\chapter[Feedback with Individual Stars]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars \label{ch:chapter1}}
-\let\thefootnote\relax\footnotetext{This section contains text from an article published in \cite{Emerick2019}}
+\chapter[Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars ]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars \label{ch:chapter1}}
+\let\thefootnote\relax\footnotetext{This section contains text from an article published originally as \cite{Emerick2019}}
 
@@
 In \cite{Emerick2018b} we investigate the importance of ionizing radiation in regulating star formation and driving outflows in our galaxy.
-In \cite{Emerick2018c} we explore how individual metal species mix within the ISM and are ejected via galactic winds.
+In \cite{Emerick2018b} we explore how individual metal species mix within the ISM and are ejected via galactic winds.
 
@@
 However, accounting for angular effects, radiation can also allow energy from SNe to dissipate more readily by escaping out of channels carved through dense clouds.
-Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HopkinsQuataertMurray2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
+Radiation feedback effects have been included with various approximations in a wide range of simulations \citep[e.g.][]{OppenheimerDave2006, Krumholz2007, HQM2012, Agertz2013, Renaud2013, Stinson2013, Roskar2014, Ceverino2014, FIRE, AgertzKravtsov2015, Forbes2016, Hu2016, Hu2017, FIRE2}, with a smaller subset using full radiation hydrodynamics \citep{WiseAbel2012,Wise2012a,Wise2014,Kim2013a, Kim2013b,Pawlik2013,Rosdahl2015,Aubert2015,Ocvirk2016,BaczynskiGloverKlessen2015,Pawlik2017} due to the additional computational expense of direct ray tracing.
 As we seek a complete accounting of stellar feedback physics, we follow HI and HeI ionizing radiation from our stars through the ray tracing methods described below.
@@
 This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent.
-A more detailed analysis is beyond the scope of this work, but we investigate this in detail in \cite{Emerick2018c}.
+A more detailed analysis is beyond the scope of this work, but we investigate this in detail in \cite{Emerick2018b}.
 
@@
 SNe), as suggested by \cite{KrumholzTing2018}.
-This is explored in more detail in \citep{Emerick2018c}.
+This is explored in more detail in \citep{Emerick2018b}.
 \end{enumerate}
@@
 %\appendix
-
-\appendix
-\renewcommand\thefigure{\thesection.\arabic{figure}}    
-\setcounter{figure}{0}
+\setcounter{section}{0}%
+\renewcommand\thesection{\thechapter.\Alph{section}}
 
@@
 
-\setcounter{section}{0}%
-\renewcommand\thesection{\thechapter.\Alph{section}}
-
 \renewcommand\thesection{\thechapter.\arabic{section}}

### 2019-03-08 thesis/chapters/ch_chapter3.tex
adding third chapter - individual metals paper

--- 2019-03-07 individual_metals/main.tex
@@
-%mm substantive changes marked like this, others made silently
+\chapter[Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source]{Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source \label{ch:chapter3}}
+\let\thefootnote\relax\footnotetext{This section contains text from an article published originally as \cite{Emerick2018b}}
 
-\documentclass[twocolumn]{aastex61}
-\pdfoutput=1 %for arXiv submission
-\usepackage{amsmath,amstext}
-\usepackage[T1]{fontenc}
-\usepackage{apjfonts}
-\usepackage[figure,figure*]{hypcap}
+%
+% Copy paste paper here, without abstract or keywords
+%
 
-\renewcommand*{\sectionautorefname}{Section} %for \autoref
-\renewcommand*{\subsectionautorefname}{Section} %for \autoref
-
-\shorttitle{Differential Metal Mixing}
-
-\begin{document}
-
-\title{Metal Mixing and Ejection in Dwarf Galaxies is Dependent on Nucleosynthetic Source}
-
-\author{Andrew Emerick}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-\author{Greg L. Bryan}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
-\author{Mordecai-Mark Mac Low}
-\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
-\author{Benoit C{\^o}t{\'e}}
-\affiliation{Konkoly Observatory, Research Centre for Astronomy and Earth Sciences, Hungarian Academy of Sciences, Konkoly Thege Miklos ut 15-17, H-1121 Budapest, Hungary}
-\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI 48824, USA}
-\affiliation{Joint Institute for Nuclear Astrophysics -- Center for the Evolution of the Elements, USA}
-\author{Kathryn V. Johnston}
-\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
-\author{Brian W. O'Shea}
-\affiliation{Department of Computational Mathematics, Science, and Engineering, Michigan State University, East Lansing, MI, 48824, USA}
-\affiliation{Department of Physics and Astronomy, Michigan State University, East Lansing, MI, 48824, USA}
-\affiliation{National Superconducting Cyclotron Laboratory, Michigan State University, East Lansing, MI, 48824, USA}
-\affiliation{Joint Institute for Nuclear Astrophysics -- Center for the Evolution of the Elements, USA}
-
-\begin{abstract}
-Using a high resolution simulation of an isolated dwarf galaxy, accounting for multi-channel
-stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy by galactic winds.
+%\begin{abstract}
+%Using a high resolution simulation of an isolated dwarf galaxy, accounting for multi-channel
+%stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy by galactic winds.
 For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal and power-law distribution.
@@
 We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
-\end{abstract}
+%\end{abstract}
 
-\keywords{}
+%\section*{Acknowledgments}
 
@@
 
-One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017,Andrews2017}.
+One-zone chemical evolution models assume homoegeneous mixing of metals from recent star formation into gas available for future star formation \citep[e.g.][]{Lanfranchi2006b,Kirby2011-III,Cote2017a,Andrews2017}.
 While this assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, accounting for this process is challenging.
@@
 In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}.
-The simulation discussed here was introduced in detail in \cite{Emerick2018} (hereafter Paper I).
+The simulation discussed here was introduced in detail in \cite{Emerick2019} (hereafter Paper I).
 To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia SNe.
@@
 \centering
-\includegraphics[width=0.99\linewidth]{species_bar}\\
-\includegraphics[width=0.99\linewidth]{species_bar_ISM}
+\includegraphics[width=0.99\linewidth]{figures/ch3/species_bar}\\
+\includegraphics[width=0.99\linewidth]{figures/ch3/species_bar_ISM}
 \caption{Top: The mass fraction of each metal species in the \textit{full simulation box} contained in the halo, gas in the galaxy disk, and stars.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{species_bar_sources}\\
+\includegraphics[width=0.95\linewidth]{figures/ch3/species_bar_sources}\\
 \caption{The fraction of total mass in each metal species produced by each of the four possible nucleosynthetic channels in our model.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{SE_density}\\
-\includegraphics[width=0.95\linewidth]{SE_z}
+\includegraphics[width=0.95\linewidth]{figures/ch3/SE_density}\\
+\includegraphics[width=0.95\linewidth]{figures/ch3/SE_z}
 \caption{The volume-averaged gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
@@
 In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}.
-Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HopkinsQuataertMurray2012}.
+Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HWM2012}.
 It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2018}.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{DD0390_element_by_element}
+\includegraphics[width=0.95\linewidth]{figures/ch3/DD0390_element_by_element}
 \caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black).
@@
 \centering
-\includegraphics[width=0.95\linewidth]{O_Ba_distribution_evolution}
+\includegraphics[width=0.95\linewidth]{figures/ch3/O_Ba_distribution_evolution}
 \caption{Time evolution of three different statistics for the full distributions of O (top) and Ba (bottom) in each phase of our simulation.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{Half_AGB_Fraction_elements_s0}
+\includegraphics[width=0.95\linewidth]{figures/ch3/Half_AGB_Fraction_elements_s0}
 \caption{The fraction of a given metal ejected through AGB winds at various times for a model of a single-age stellar population at $Z = 10^{-4}$ metal mass fraction, without continuing star formation.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{stellar_CNM_distance}
+\includegraphics[width=0.95\linewidth]{figures/ch3/stellar_CNM_distance}
 \caption{The separation (in dex) of each star's oxygen fraction from the median value of the CNM oxygen mass fraction PDF for the time within 1~Myr (our time resolution) of each star's formation time.
@@
 
-\acknowledgments
+\section*{Acknowledgements}
 A.E.
@@
 
-\facilities{XSEDE (Stampede, Stampede-2), ADS} % there is no ApJ kewword for this: NASA HECC (Pleiades)}
-\software{Numpy, Enzo, yt, astropy}
+%\facilities{XSEDE (Stampede, Stampede-2), ADS} % there is no ApJ kewword for this: NASA HECC (Pleiades)}
+%\software{Numpy, Enzo, yt, astropy}
 
-\bibliographystyle{yahapj}
-\bibliography{msbib}
+%\bibliographystyle{yahapj}
+%\bibliography{msbib}
 
-\appendix
-\renewcommand\thefigure{\thesection.\arabic{figure}}
-\setcounter{figure}{0}
+%************* APPENDICES ************************%
+
+%\clearpage
+%\appendix
+\setcounter{section}{0}%
+\renewcommand\thesection{\thechapter.\Alph{section}}
 
@@
 \centering
-\includegraphics[width=0.475\linewidth]{density_PDF}
-\includegraphics[width=0.475\linewidth]{density_PDF_volume_weighted}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr.
+\includegraphics[width=0.475\linewidth]{figures/ch3/density_PDF}
+\includegraphics[width=0.475\linewidth]{figures/ch3/density_PDF_volume_weighted}\caption{The mass-weighted (left) and volume weighted (right) density PDFs of our dwarf galaxy at an arbitrarily chosen time of 250~Myr.
 The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
@@
 \centering
-\includegraphics[width=0.95\linewidth]{O_Ba_resolution_study}
+\includegraphics[width=0.95\linewidth]{figures/ch3/O_Ba_resolution_study}
 \caption{Resolution comparison of two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.
@@
 
-\end{document}
+\renewcommand\thesection{\thechapter.\arabic{section}}

### 2019-03-08 thesis/chapters/ch_chapter4.tex
adding placeholder for chapter 4 on current WIP

\chapter[Mixing Properties of Individual Enrichment Sources as a Function of Energy]{Mixing Properties of Individual Enrichment Sources as a Function of Energy\label{ch:chapter4}}
\let\thefootnote\relax\footnotetext{This section contains unpublished work-in-progress}

%
% Copy paste paper here, without abstract or keywords
%

\section{Introduction}

\section*{Acknowledgments}

%************* APPENDICES ************************%

%\clearpage
%\appendix - Liklely DO NOT use this command
\setcounter{section}{0}%
\renewcommand\thesection{\thechapter.\Alph{section}}

%
% Place appendix here
%

\renewcommand\thesection{\thechapter.\arabic{section}}

### 2019-03-08 thesis/chapters/ch_introduction.tex
updates to outline

\chapter[Introduction]{Introduction}
\label{ch:intro}
\vspace{-16pt} \begin{chapquote}{----} \singlespacing Some cool quote (optional)
\end{chapquote} \vspace{-8pt}
\noindent\makebox[\linewidth]{\rule{0.5\textwidth}{0.5pt}} \vspace{1pt}

%
% \beq
% \frac{\mathrm{d}}{\mathrm{d}t} \int_S \mathbf{B} \cdot \mathrm{d}S = 0,f
% \eeq

Text

\section{Ingredients of Galactic Evolution}

Very broadly give a picture of galactic evolution, focusing in on the physics needed to simulate galaxies (cooling, heating, chemistry, feedback). Touch on inflows, outflows, mixing, ISM physics, etc. Bring up CE and feedback obviously but reserve for next section(s). But maybe this can all go in the intro-intro

\section{Galactic Chemical Evolution}
\label{sec:CE}

\subsection{Nucleosynthetic Sources}

Cover (briefly) each enrichment source and dominant production elements.

% maybe a section on our own galaxy

\subsection{Metals in Local Group Dwarfs}

\subsubsection{Metal Retention / Ejection}

\subsubsection{Stellar Abundances}

\subsubsection{Sources of Enrichment}

\subsection{Modelling Chemical Evolution}

\subsubsection{Hydrodynamics Simulations}

\subsubsection{Semi-analytic Models / One-zone models}

Definitely have a lot here. Motivate need for better understanding of mixing processes in galaxies. \citep{SchonrichWeinberg2019}

\section{Stellar Feedback}\label{sec:section1}

Overview

% maybe a section on each FB method? R

\subsection{Star Particles in Simulations}

%
%
%

\section{Structure of Dissertation}\label{sec:structure}

In Chapter \ref{ch:chapter1} I...

%In Chapter \ref{ch:chapter2}

We conclude in Chapter \ref{ch:conclusion} and briefly discuss future work as extensions of this Dissertation.

### 2019-03-11 thesis/chapters/ch_introduction.tex
Got started on introduction. Saving rough updates. Still very rough

@@
 \label{ch:intro}
-\vspace{-16pt} \begin{chapquote}{----} \singlespacing Some cool quote (optional)
+\vspace{-16pt} 
+\begin{chapquote}{Isaac Asimov} \singlespacing The most exciting phrase to hear in science, the one that heralds discoveries, is not ‘Eureka!’ but ‘Now that’s funny…
 \end{chapquote} \vspace{-8pt}
+\begin{chapquote}{Brian W.
+Kernighan} \singlespacing Debugging is twice as hard as writing the code in the first place.
+Therefore, if you write the code as cleverly as possible, you are, by definition, not smart enough to debug it
+\end{chapquote} \vspace{-8pt}
+
 \noindent\makebox[\linewidth]{\rule{0.5\textwidth}{0.5pt}} \vspace{1pt}
@@
 
-Text
+Galaxies are amalgamations of gas and stars embedded in dark matter halos, formed over cosmic time as the products of the hierarchical assembly that follows from the collapse of primordial density fluctuations that arose after the Big Bang.
+The gravitational pull of dark matter controls the growth of structure in the Universe which, as is predicted from $\Lambda$CDM cosmology, TEXT HERE.
+While, broadly speaking, the evolution of baryons is dominated by the gravitational pull of dark matter, the beautiful simplicity of the evolution of dark matter and $\Lambda$CDM is muddied by their existence.
+The complexities of hydrodynamics, magnetohydrodynamics, thermodynamics, chemistry, radiative processes, and nucleosynthesis -- or, ``astrophysics'' for short -- drives these deviations and gives rise to the Universe that we observe and interact with and -- not least of all -- us.
+It is understanding the rich set of physics that formed our own Galaxy and the countless galaxies scattered throughout the Universe that motivates this work.
+
+A substantial slice of modern astrophysics has been devoted towards understanding the chemical evolution -- the abundances of individual elements in space and time -- of the Universe.
+With the exception of H, He, and trace amounts of light elements, such as Li, all of the elements in the Universe are produced in nuclear reactions in the cores of stars, massive star stellar winds, asymptotic giant branch (AGB) winds of low mass stars, and more exotic sites like nuetron star - neutron star mergers (NS-NS).
+See \cite{Nomoto2013, Thielmann2017, Frebel2018} for recent reviews on this topic as it applies to studies of galactic and stellar evolution.
+
+Discuss interest in galactic CE today with observational landscape (and upcoming observations).
+
+Mention simulations here somewhere (a la naab and ostriker)
+
+Mention study of dwarf galaxies instead of MW first as way to simulate physics in detail and build up undserstanding to more massive regimes. Lead into physics that is important below.
+
+\section{Star Formation and Stellar Feedback}\label{sec:section1}
+
+As elements are synthesized throughout stellar evolution, any framework for modelling galactic evolution requires an understanding of both where, how, and with what properties stars form in a galaxy.
+
+As described above, the nucleosynthetic sites of
+
+% maybe a section on each FB method? R
+
+\subsection{Star Particles in Simulations}
+
+\subsection{Stellar Radiation Feedback}
+\ref{sec:radiation}
 
@@
 
-\subsubsection{Metal Retention / Ejection}
+Until recently, the study of chemical evolution in Local Group dwarf galaxies has focused predominantly on the stellar component.
+This is due in large part because, though dwarf galaxies have higher gas fractions than more massive galaxies \citep{Geha2006}, many of these galaxies have undergone environmental stripping processes, rendering them devoid of a measurable gas component \citep{GrcevichPutman2009}.
+
+% mention difficulties of measuring gas phase abundances in dwarf galaxies?
+
+\subsubsection{Galactic Winds: Metal Retention / Ejection}
+
+Stellar feedback drives outflows, galactic winds, from galaxies across all scales (references).
+Dwarf galaxies in particular, with their relatively shallow potential wells, drive effective galactic winds, with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) ranging from XXX to XXX (cite, muratov etc.).
+How exactly stellar feedback couples to the ISM to drive these stellar winds is still uncertain, and is the topic of substantial ongoing research, but effective winds
 
@@
 
-\section{Stellar Feedback}\label{sec:section1}
-
-Overview
-
-% maybe a section on each FB method? R
-
-\subsection{Star Particles in Simulations}
-
 %
@@
 
-In Chapter \ref{ch:chapter1} I...
+In this work we investigate the role of both stellar feedback and mixing in a multi-phase ISM in driving galactic chemical evolution.
+Using a novel method for following star formation and stellar feedabck in galaxy-scale hydrodynamics simulations, we provide significant insight into how individual metals from distinct nucleosynthetic sites enrich the ISM, how their abundances are set and imprinted upon newly formed stars, and how they are ejected from galaxies through galactic winds.
 
-%In Chapter \ref{ch:chapter2}
+In Chapter \ref{ch:chapter1} \citep[published as ][]{Emerick2019}, we motivate the need for a new model of star formation and stellar feedback to address the open uncertainties in galactic chemical evolution.
+We implement such a model, which follows stars as individual star particles over a fully sampled IMF, in hydrodynamics simulations of an isolated, low-mass dwarf galaxy.
+We describe in detail the physics included in these simulations, including a stellar feedback model that follows stellar radiation, stellar winds, and supernovae.
+We find that RESULTS
 
-We conclude in Chapter \ref{ch:conclusion} and briefly discuss future work as extensions of this Dissertation.
+In Chapter \ref{ch:chapter2} \citep[published as ][]{Emerick2018a}, we investigate how stellar ionizing radiation feedback impacts the evolution of our simulated low mass dwarf galaxy.
+We confirm the findings in recent works, as dicsussed in Section~\ref{sec:radiation}, that find that stellar radiation is an important source of pre-supernova feedback that regulates star formation and can help drive galactic outflows outflows.
+We additionally investigate how radiation feedback couples to the ISM to drive galactic winds by demonstrating that the ionization of gas far from individual ionzing sources, out into the disk-halo interface of our galaxy, creates low-density channels through which supernovae can readily drive gas and metals into and beyond the galaxy's CGM.
+This suggests that not only is the local deposition of energy from stellar radiation important, which quickly destroys dense gas in stellar birth-sites, but also long-range effects are important to consider in a consistent model of stellar feedback.
+
+In Chapter \ref{ch:chapter3} \citep[published as ][]{Emerick2018b}, we dive in detail into the evolution of each of the 15 individual metal species that we follow in our simulation.
+We focus primarily on the evolution of the gas-phase abundances of these metals, and how the site of nucleosynthesis (e.g.
+AGB winds or SNe) drives the subsequent evolution of each species.
+We find that elements released in lower energy enrichment sources (e.g.
+AGB winds) mix less effectively in the ISM across all phases than elements released in higher energy enrichment sources (e.g.
+SNe).
+Likewise, energy difference associated with their enrichment directly impacts their ability to couple to galactic outflows.
+We find that elements released in AGB winds are retained at a higher fraction (by a factor of $\sim$ 4-5) than elements released in SNe.
+
+In Chapter \ref{ch:chapter4} we discuss recent, unpublished results which build upon the work in Chapter~\ref{ch:chapter3} by investigating in more detail how energy, spatial location within the galaxy, and galaxy SFR affect the mixing and ejection of metals for individual enrichment events.
+With a more detailed study, we again confirm that metal mixing in the ISM and ejection in galactic winds depends upon the energy of the enrichment event, sampling event energies from AGB winds ($\sim$ erg) to hypernovae ($\sim 10^{52}$~erg).
+
+Finally, we conclude in Chapter \ref{ch:conclusion} and briefly discuss future work as extensions of this Dissertation.

### 2019-03-12 thesis/chapters/ch_introduction.tex
Continuing to write the introduction

@@
 The complexities of hydrodynamics, magnetohydrodynamics, thermodynamics, chemistry, radiative processes, and nucleosynthesis -- or, ``astrophysics'' for short -- drives these deviations and gives rise to the Universe that we observe and interact with and -- not least of all -- us.
+In spite of a concerted effort spanning nearly a century, we are far from a self-consistent theory of galaxy evolution \citep[see ][ for a recent review of outstanding problems in galactic evolution]{NaabOstriker2017}.
 It is understanding the rich set of physics that formed our own Galaxy and the countless galaxies scattered throughout the Universe that motivates this work.
@@
 With the exception of H, He, and trace amounts of light elements, such as Li, all of the elements in the Universe are produced in nuclear reactions in the cores of stars, massive star stellar winds, asymptotic giant branch (AGB) winds of low mass stars, and more exotic sites like nuetron star - neutron star mergers (NS-NS).
-See \cite{Nomoto2013, Thielmann2017, Frebel2018} for recent reviews on this topic as it applies to studies of galactic and stellar evolution.
+See \cite{Nomoto2013}, \cite{Thielmann2017}, and \cite{Frebel2018} for recent reviews on this topic as it applies to studies of galactic and stellar evolution.
+Much work has been done in studying the global metallicity evolution of galaxies through the mass-metallicity relationship \citep[e.g.][]{Lequeux1979,Tremonti2004,Lee2006,Zahid2012}, the metallicity gradient in our own and nearby galaxies \citep[e.g.][]{}, and detailed stellar abundances in galaxies with spectroscopically resolved stellar populations \citep[e.g.][]{}.
 
-Discuss interest in galactic CE today with observational landscape (and upcoming observations).
+Developing a complete model for galactic chemical evolution is a daunting task.
+One is faced with the already non-trivial prospect nailing down a complete model of stellar structure, stellar evolution, and the rates of individual nuclear reactions.
+One must then perscribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas into the disk of the galaxy, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos.
+One can then worry about knowing where, how, and with what masses stars form in the first place from this gas, which requires understanding the hydrodynamic and magnetohydrodynamic properties of the multi-scale, multi-phase turbulent interstellar medium (ISM).
+This in turn requires one to a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and supernovae -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies.
+Once this is understood, one can then color in the gas in the galaxy over time with the individual metal yields of stellar populations released over their lifetime.
+With a complete understanding of stellar feedback and the ISM, one can then be sure that they completely capture the mixing of these metals in the ISM over time, and will produce a stellar population with accurate metal abundance ratios.
+In addition, one would then produce realistic galactic winds, removing the correct amount of metals from the galaxy and enriching the CGM and the intergalactic medium (IGM).
+Finally, one can layer this model ad nauseum on top of a $\Lambda CDM$ model for the cosmological evolution of many galaxies, reproducing all observed properties of galactic chemical evolution as a function of both mass and redshift.....
+
+ It should be obvious now to the reader why there remains so much to be learned about galactic chemical evolution.
+Yet it makes clear that this field offers an incredibly exciting test of an incredible range of physics.
+
+The observational landscape today is primed for developing a more detailed understanding these processes. Recent observational campaigns
+
+CE models
 
@@
 
-\section{Star Formation and Stellar Feedback}\label{sec:section1}
-
-As elements are synthesized throughout stellar evolution, any framework for modelling galactic evolution requires an understanding of both where, how, and with what properties stars form in a galaxy.
-
-As described above, the nucleosynthetic sites of
-
-% maybe a section on each FB method? R
-
-\subsection{Star Particles in Simulations}
-
-\subsection{Stellar Radiation Feedback}
-\ref{sec:radiation}
-
-\section{Ingredients of Galactic Evolution}
+\section{Ingredients of Galactic Chemical Evolution}
 
@@
 
-\section{Galactic Chemical Evolution}
-\label{sec:CE}
-
-\subsection{Nucleosynthetic Sources}
+\subsection{Nucleosynthesis and Stellar Evolution}
 
@@
 % maybe a section on our own galaxy
+
+\subsection{Star Formation and Stellar Feedback}\label{sec:section1}
+
+As elements are synthesized throughout stellar evolution, any framework for modelling galactic evolution requires an understanding of both where, how, and with what properties stars form in a galaxy.
+
+\subsubsection{Star Formation}
+
+In galaxy-scale hydrodynamics, star formation is typically treated simplistically.
+
+% maybe a section on each FB method? R
+
+\subsubsection{Stars in Simulations}
+
+Stars, particularly large-scale cosmological simulations, are commonly represented as simple stellar populations (SSPs), or particles with IMF-averaged properties of stellar feedback and metal enrichment.
+As demonstrated in \cite{Revaz2016}, this approach is reasonable so long as the mass of the star particle is large enough to fully sample the IMF ($> 10^{4}$~M$_{\odot}$).
+In high resolution simulations, particularly simulations of small, low-mass systems like dwarf galaxies, this is no longer the case.
+This leads to inconsistencies in both the effective metal yield of the modelled stars, and (often) an artificial reduction of the effects of stellar feedback.
+Recent works have developed new models to address this issue, discretizing (rather than averaging over) individual feedback events \citep[e.g.][]{Stinson2010,Hopkins2014,Hopkins2018,Rosdahl2018} or accounting for stochastic sampling of the IMF \citep{Hu2016,Hu2017,Applebaum2018,Su2018}.
+However, each of these methods utilizes a sub-grid recipe in some fashion to improve upon the SSPs.
+On the other extreme are highly resolved simulations which model star formation with ``sink particles'' \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017} that account for the gradual accretion of gas in the growth of a single star (or group of stars) and protostellar feedback.
+These recipes are often computationally expensive, however, restricting their use over long timescales (100's to 1000's of Myr or more) in galaxy-scale simulations.
+
+In this dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF.
+This allows us to place unprecidented detail on both the stellar feedback and metal yields associated with each star, spatially and temporally resolving differences in both of these channels as a function of stellar mass and metallicity.
+
+\subsubsection{Stellar Radiation Feedback}
+\ref{sec:radiation}
 

### 2019-03-13 thesis/chapters/ch_chapter3.tex
updating reference

@@
 In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}.
-Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HWM2012}.
+Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HQM2012}.
 It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2018}.
@@
 \label{appendix:density PDF}
-We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}.
+We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HQM2012}.
 We show the mass-weighted PDF ($dm/Md\log n$) on the left, and the volume-weighted PDF ($dv/Vd\log n$) on the right.

### 2019-03-13 thesis/chapters/ch_introduction.tex
rearranged sections a bit
updating introduction and references. Hydrodynamics section, more in opening intro (observational campaigns), and some in radiation section

@@
 
+\newcommand{\code}{\textsc}
+
 %
@@
 While, broadly speaking, the evolution of baryons is dominated by the gravitational pull of dark matter, the beautiful simplicity of the evolution of dark matter and $\Lambda$CDM is muddied by their existence.
-The complexities of hydrodynamics, magnetohydrodynamics, thermodynamics, chemistry, radiative processes, and nucleosynthesis -- or, ``astrophysics'' for short -- drives these deviations and gives rise to the Universe that we observe and interact with and -- not least of all -- us.
+The complexities of hydrodynamics, magnetohydrodynamics, thermodynamics, chemistry, radiative processes, and nucleosynthesis -- or, ``astrophysics" for short -- drives these deviations and gives rise to the Universe that we observe and interact with and -- not least of all -- us.
 In spite of a concerted effort spanning nearly a century, we are far from a self-consistent theory of galaxy evolution \citep[see ][ for a recent review of outstanding problems in galactic evolution]{NaabOstriker2017}.
@@
 A substantial slice of modern astrophysics has been devoted towards understanding the chemical evolution -- the abundances of individual elements in space and time -- of the Universe.
-With the exception of H, He, and trace amounts of light elements, such as Li, all of the elements in the Universe are produced in nuclear reactions in the cores of stars, massive star stellar winds, asymptotic giant branch (AGB) winds of low mass stars, and more exotic sites like nuetron star - neutron star mergers (NS-NS).
+With the exception of H, He, and trace amounts of light elements, all of the elements in the Universe are produced in nuclear reactions in the cores of stars, massive star stellar winds, asymptotic giant branch (AGB) winds of low mass stars, and more exotic sites like nuetron star - neutron star mergers (NS-NS).
 See \cite{Nomoto2013}, \cite{Thielmann2017}, and \cite{Frebel2018} for recent reviews on this topic as it applies to studies of galactic and stellar evolution.
@@
 
-Developing a complete model for galactic chemical evolution is a daunting task.
-One is faced with the already non-trivial prospect nailing down a complete model of stellar structure, stellar evolution, and the rates of individual nuclear reactions.
+%Developing a complete model for galactic chemical evolution is a daunting task.
+Here is a recipe for constructing a complete model of galactic chemical evolution as it is understood today.
+One begins first with the simple step of nailing down a complete model of stellar structure, stellar evolution, and learning from nuclear physicists the reaction rates of every nuclear reaction and lifetimes of individual isotopes.
 One must then perscribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas into the disk of the galaxy, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos.
-One can then worry about knowing where, how, and with what masses stars form in the first place from this gas, which requires understanding the hydrodynamic and magnetohydrodynamic properties of the multi-scale, multi-phase turbulent interstellar medium (ISM).
-This in turn requires one to a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and supernovae -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies.
+One can then worry about knowing where, how, and with what masses stars form in the first place from this gas, which requires understanding the hydrodynamic
+%and magnetohydrodynamic 
+properties of the multi-scale, multi-phase turbulent interstellar medium (ISM).
+This in turn requires one to toss in a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and supernovae -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies.
 Once this is understood, one can then color in the gas in the galaxy over time with the individual metal yields of stellar populations released over their lifetime.
@@
 Finally, one can layer this model ad nauseum on top of a $\Lambda CDM$ model for the cosmological evolution of many galaxies, reproducing all observed properties of galactic chemical evolution as a function of both mass and redshift.....
+Wait...
+I forgot about magnetic fields and cosmic rays...
 
 It should be obvious now to the reader why there remains so much to be learned about galactic chemical evolution.
-Yet it makes clear that this field offers an incredibly exciting test of an incredible range of physics.
+Developing a complete model for galactic chemical evolution is a daunting task.
+Yet it is clear that this field offers an incredibly exciting test of an incredible range of physics.
 
-The observational landscape today is primed for developing a more detailed understanding these processes. Recent observational campaigns
+The observational landscape today is primed for developing a more detailed understanding these processes.
+Recent observational campaigns such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, the Gaia-ESO survey \citep{Gaia}, APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, GALAH \citep{GALAH,Buder2018}, as well as upcoming observations, such as the Local Volume Mapper as part of SDSS-V, have generated tremendous amounts of information on detailed stellar abundnaces and stellar kinematics in our Milky Way and nearby Local Group dwarf galaxies.
+One of the most powerful proposed uses of this enormous trove of data is chemical tagging \citep{Freeman2002}, whereby stellar populations are analyzed in chemical space and 6D phase space to identify co-eval and co-natal groups of stars.
+This process of galactic archeaology aims to break down and identify each distinct stellar component of our Galaxy, explaining the process of their formation and evolution.
+Substantial work has been made recently to determine the efficacy of this approach \citep[e.g.][]{Armillotta2018}, yet the physical processes that give rise to stellar abundances as we observe them today are still uncertain.
+The excitement at the availability of this data does not even mention
 
-CE models
+One of the most common ways to model and understand the stellar populations of galaxies in high-dimensional chemical space is through simplified one-zone (or many-zone) models.
+This treatment extends back to XXX, where galaxies were treated as closed-box systems of gas and stars with simple approximations such as the instantaneous recycling of metal yields from massive stars and homogenous mixing.
+While simple, these models have been used extensively to explain the mean evolution of stars in chemical space in individual galaxies.
 
@@
 Mention study of dwarf galaxies instead of MW first as way to simulate physics in detail and build up undserstanding to more massive regimes. Lead into physics that is important below.
+
+\section{Observations of Local Group Dwarf Galaxies}
+
+\subsection{Metals in Local Group Dwarfs}
+
+Until recently, the study of chemical evolution in Local Group dwarf galaxies has focused predominantly on the stellar component.
+This is due in large part because, though dwarf galaxies have higher gas fractions than more massive galaxies \citep{Geha2006}, many of these galaxies have undergone environmental stripping processes, rendering them devoid of a measurable gas component \citep{GrcevichPutman2009}.
+
+% mention difficulties of measuring gas phase abundances in dwarf galaxies?
+
+\subsubsection{Galactic Winds: Metal Retention / Ejection}
+
+Stellar feedback drives outflows, galactic winds, from galaxies across all scales (references).
+Dwarf galaxies in particular, with their relatively shallow potential wells, drive effective galactic winds, with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) ranging from XXX to XXX (cite, muratov etc.).
+How exactly stellar feedback couples to the ISM to drive these stellar winds is still uncertain, and is the topic of substantial ongoing research, but effective winds
 
@@
 This leads to inconsistencies in both the effective metal yield of the modelled stars, and (often) an artificial reduction of the effects of stellar feedback.
-Recent works have developed new models to address this issue, discretizing (rather than averaging over) individual feedback events \citep[e.g.][]{Stinson2010,Hopkins2014,Hopkins2018,Rosdahl2018} or accounting for stochastic sampling of the IMF \citep{Hu2016,Hu2017,Applebaum2018,Su2018}.
+Recent works have developed new models to address this issue, discretizing (rather than averaging over) individual feedback events \citep[e.g.][]{MUGS2010,FIRE,Hopkins2018,Rosdahl2018} or accounting for stochastic sampling of the IMF \citep{Hu2016,Hu2017,Applebaum2018,Su2018}.
 However, each of these methods utilizes a sub-grid recipe in some fashion to improve upon the SSPs.
-On the other extreme are highly resolved simulations which model star formation with ``sink particles'' \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017} that account for the gradual accretion of gas in the growth of a single star (or group of stars) and protostellar feedback.
+On the other extreme are highly resolved simulations which model star formation with ``sink particles" \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017} that account for the gradual accretion of gas in the growth of a single star (or group of stars) and protostellar feedback.
 These recipes are often computationally expensive, however, restricting their use over long timescales (100's to 1000's of Myr or more) in galaxy-scale simulations.
@@
 
-\subsection{Metals in Local Group Dwarfs}
+We only briefly discuss this method of feedback here, as it is discussed in much more detail in both Chapters~\ref{ch:chapter_1} and \ref{ch:chapter_2}.
+In brief, \cite{Agertz2013} demonstrated that stellar radiation, accounts for a substantial fraction of the energy output of a stellar population.
+Ionizing photons contribute
 
-Until recently, the study of chemical evolution in Local Group dwarf galaxies has focused predominantly on the stellar component.
-This is due in large part because, though dwarf galaxies have higher gas fractions than more massive galaxies \citep{Geha2006}, many of these galaxies have undergone environmental stripping processes, rendering them devoid of a measurable gas component \citep{GrcevichPutman2009}.
-
-% mention difficulties of measuring gas phase abundances in dwarf galaxies?
-
-\subsubsection{Galactic Winds: Metal Retention / Ejection}
-
-Stellar feedback drives outflows, galactic winds, from galaxies across all scales (references).
-Dwarf galaxies in particular, with their relatively shallow potential wells, drive effective galactic winds, with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) ranging from XXX to XXX (cite, muratov etc.).
-How exactly stellar feedback couples to the ISM to drive these stellar winds is still uncertain, and is the topic of substantial ongoing research, but effective winds
-
-\subsubsection{Stellar Abundances}
-
-\subsubsection{Sources of Enrichment}
-
-\subsection{Modelling Chemical Evolution}
-
-\subsubsection{Hydrodynamics Simulations}
-
-\subsubsection{Semi-analytic Models / One-zone models}
+\section{Semi-Analytic Models / One-zone Models}
 
@@
 
-%
-%
-%
+\section{Hydrodynamics}
+\textit{(This will be a sub-section of something, but putting here for now as placeholder).}
+
+Astrophysical hydrodynamics simulations are first distinguished by the numerical methods employed to solve the Euler equations that describe the time ($t$) evolution of the energy density ($E$), density ($\rho$), pressure ($p$), and peculiar velocity ($\bm{v}$) of a fluid:
+\begin{equation}
+  \frac{\delta \rho}{\delta t} + \nabla \cdot \left(\rho \bm{v}\right)  = 0,\\
+  \frac{\delta \rho \bm{v}}{\delta t} + \nabla \cdot \left(\rho \bm{v}\bm{v} + \bm{I}p \right) = 0,\\
+  \frac{\delta E}{\delta t} + \nabla \cdot \left[\left(E +p\right)\bm{v}\right] = 0.
+\end{equation}
+
+Historically, codes fall into one of two camps: 1) Eulerian grid-based codes, including the popular codes / algorithms commonly in use (in some way) today such as \code{Zeus} \citep{StoneNorman1992}, \code{FLASH} \citep{FLASH}, \code{RAMSES} \citep{Teyssier2002}, \code{Athena} \citep{Athena}, \code{ART-II} \citep{Rudd2008}, and \code{Enzo} \citep{Enzo2014}, and 2) particle-based Lagrangian methods known as smooth particle hydrodynamics (SPH), such as \code{Gadget} \citep{Springel2005}, \code{PKDGRAV-2} \citep{Stadel2001}, \code{Gasoline} \citep{Wadsley2004}, and \code{Changa} \citep{Menon2015}.
+However, recent codes blur the lines between these distinctions with new algorithms for solving the fluid equations on a moving-mesh (e.g.
+\code{AREPO} \citep{Springel2010}), or meshless finite-mass / finite-volume methods (such as those implemented in \code{Gizmo} \citep{Hopkins2015}).
+Given the large variance in numerical methods, recent studies have examined the differences between these numerical implementations \citep[e.g.][]{Agertz2007}, including large-scale code comparison projects \citep[e.g.][]{AGORA,AGORA2}.
+While developing a notion of which code is ``correct" is an ill-posed problem, these studies have allowed for improvement across implementations and an insight into how numerical methods themselves drive uncertainty in our understanding of astrophysical problems.
+
+In this Dissertation, we make use of the adaptive-mesh refinement (AMR) hydrodynamics code \code{Enzo}, as described in greater detail in Chapter~\ref{ch:chapter_1}.
+As it pertains to galactic chemical evolution, however, the use of a grid-based code has the advantage that metals (which are advected as passive scalars that follow the fluid-flow in the simulations) are allowed to mix and diffuse naturally across fluid elements (grid cells).
+This is not possible in native SPH implementations, yet is necessary to reproduce realistic galactic chemical evolution properties as shown by multiple recent works testing implementations of diffusion in SPH simulations \citep[e.g.][]{Shen2010,Su2017a,Escala2018}.
+The disadvantage of the diffusion in \code{Enzo}, however, is that it is entirely numerical, and therefore its exact properties are challenging to characterize and are strongly resolution dependent.
+Throughout this dissertation we attempt to account for the effects of resolution on our results, but do not explicitly examine the properties of numerical diffusion itself.
 

### 2019-03-13 thesis/chapters/ch_introduction.tex
star formation, star particle section updates. radiation updates. moving hydro into new section. preface to ingredients of GE section

@@
 
-Very broadly give a picture of galactic evolution, focusing in on the physics needed to simulate galaxies (cooling, heating, chemistry, feedback).
-Touch on inflows, outflows, mixing, ISM physics, etc.
-Bring up CE and feedback obviously but reserve for next section(s).
-But maybe this can all go in the intro-intro
+We give a primer on how to model galactic evolution in hydrodynamics simulations.
+We focus on the physics needed to simulate galaxies (cooling, heating, chemistry, star formation, feedback, etc.) as it pertains to the aspects of galactic chemical evolution examined in this dissertation.
+This is meant to be a broad overview of the physical processes modelled in such simulations, focusing on aspects of their implementation rather than the derivation of theory behind such processes.
+While important, the latter is better reserved for a much more detailed work (i.e.
+textbook), and focusing on the former gives a much more accurate represenation of the actual work done for this dissertation.
+This discussion includes a very brief overview of hydrodynamics and the numerical methods used in this work in Section~\ref{intro:sec:hydrodynamics}, nucleosynthesis and stellar evolution in Section~\ref{intro:sec:nucleosynthesis}, star formation and star particles in Section~\ref{intro:sec:sf} and Section~\ref{intro:sec:stars},
 
-\subsection{Nucleosynthesis and Stellar Evolution}
-
-Cover (briefly) each enrichment source and dominant production elements.
-
-% maybe a section on our own galaxy
-
-\subsection{Star Formation and Stellar Feedback}\label{sec:section1}
-
-As elements are synthesized throughout stellar evolution, any framework for modelling galactic evolution requires an understanding of both where, how, and with what properties stars form in a galaxy.
-
-\subsubsection{Star Formation}
-
-In galaxy-scale hydrodynamics, star formation is typically treated simplistically.
-
-% maybe a section on each FB method? R
-
-\subsubsection{Stars in Simulations}
-
-Stars, particularly large-scale cosmological simulations, are commonly represented as simple stellar populations (SSPs), or particles with IMF-averaged properties of stellar feedback and metal enrichment.
-As demonstrated in \cite{Revaz2016}, this approach is reasonable so long as the mass of the star particle is large enough to fully sample the IMF ($> 10^{4}$~M$_{\odot}$).
-In high resolution simulations, particularly simulations of small, low-mass systems like dwarf galaxies, this is no longer the case.
-This leads to inconsistencies in both the effective metal yield of the modelled stars, and (often) an artificial reduction of the effects of stellar feedback.
-Recent works have developed new models to address this issue, discretizing (rather than averaging over) individual feedback events \citep[e.g.][]{MUGS2010,FIRE,Hopkins2018,Rosdahl2018} or accounting for stochastic sampling of the IMF \citep{Hu2016,Hu2017,Applebaum2018,Su2018}.
-However, each of these methods utilizes a sub-grid recipe in some fashion to improve upon the SSPs.
-On the other extreme are highly resolved simulations which model star formation with ``sink particles" \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017} that account for the gradual accretion of gas in the growth of a single star (or group of stars) and protostellar feedback.
-These recipes are often computationally expensive, however, restricting their use over long timescales (100's to 1000's of Myr or more) in galaxy-scale simulations.
-
-In this dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF.
-This allows us to place unprecidented detail on both the stellar feedback and metal yields associated with each star, spatially and temporally resolving differences in both of these channels as a function of stellar mass and metallicity.
-
-\subsubsection{Stellar Radiation Feedback}
-\ref{sec:radiation}
-
-We only briefly discuss this method of feedback here, as it is discussed in much more detail in both Chapters~\ref{ch:chapter_1} and \ref{ch:chapter_2}.
-In brief, \cite{Agertz2013} demonstrated that stellar radiation, accounts for a substantial fraction of the energy output of a stellar population.
-Ionizing photons contribute
-
-\section{Semi-Analytic Models / One-zone Models}
-
-Definitely have a lot here. Motivate need for better understanding of mixing processes in galaxies. \citep{SchonrichWeinberg2019}
-
-\section{Hydrodynamics}
+\subsection{Hydrodynamics}
 \textit{(This will be a sub-section of something, but putting here for now as placeholder).}
@@
 
-In this Dissertation, we make use of the adaptive-mesh refinement (AMR) hydrodynamics code \code{Enzo}, as described in greater detail in Chapter~\ref{ch:chapter_1}.
+In this Dissertation, we make use of the adaptive-mesh refinement (AMR) hydrodynamics code \code{Enzo}, as described in greater detail in Chapter~\ref{ch:chapter1}.
 As it pertains to galactic chemical evolution, however, the use of a grid-based code has the advantage that metals (which are advected as passive scalars that follow the fluid-flow in the simulations) are allowed to mix and diffuse naturally across fluid elements (grid cells).
@@
 
-\section{Structure of Dissertation}\label{sec:structure}
+\subsection{Nucleosynthesis and Stellar Evolution} \label{intro:sec:nucleosynthesis}
+
+Cover (briefly) each enrichment source and dominant production elements.
+
+% maybe a section on our own galaxy
+
+%\subsection{Star Formation and Stellar Feedback}\label{intro:sec:sffb}
+%
+%As elements are synthesized throughout stellar evolution, any framework for modelling galactic evolution requires an understanding of both where, how, and with what properties stars form in a galaxy.
+
+\subsection{Star Formation} \label{intro:sec:sf}
+
+In galaxy-scale hydrodynamics, star formation is typically treated as a process that occurs by a sub-grid model, with an assumed rate and assumed efficiency, in fluid elements that surpass a variety of threshold conditions.
+Usually, simulators set these thresholds to fully encompass gas whose Jeans-length (and thus dynamical behavior) becomes unresolved according to the widely-used \cite{Truelove1997} criterion.
+Often, this means a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\div \bm{v} < 0$), that gas surpass some virial threshold \citep[e.g.][]{}, or that gas also meet a minimum $H_2$ mass fraction \citep[e.g.][]{}.
+One a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars.
+Briefly, some form of the following equation is usually adopted,
+\begin{equation}
+\label{intro:eq:sfr}
+ \rm{SFR} \propto 
+\end{equation}
+,.
+Some works adopt modifications of this simple perscription, with varying star formation efficiency ($\eta$) (refs), or XXXX.
+Others, for application in high-resolution simulations where the mass of stars that would form in a single timestep ($dt \times \rm{SFR}$) is far less than a single star particle mass, allow stars to form out of star forming fluid elements stochastically \citep[e.g.][]{Goldbaum2015}.
+
+Recent work has demonstrated that variations in these implemenations can lead to dramatic differences in the outcome of the simulated galaxies (refs, incl brooks/munshi work).
+However, it is generally found that the differences between implementations decrease in simulations with sufficient resolution ($\sim$ 10~pc or better spatial, or $\sim$ $100$ M$_{\odot}$ or better in mass) and with a sufficiently high density threshold for star formation ($n > 100$~cm$^{-3}$) (fire ref).
+
+% maybe a section on each FB method? R
+
+\subsection{Stars in Simulations} \label{intro:sec:stars}
+
+Stars, particularly large-scale cosmological simulations, are commonly represented as simple stellar populations (SSPs), or particles with IMF-averaged properties of stellar feedback and metal enrichment.
+As demonstrated in \cite{Revaz2016}, this approach is reasonable so long as the mass of the star particle is large enough to fully sample the IMF ($> 10^{4}$~M$_{\odot}$).
+In high resolution simulations, particularly simulations of small, low-mass systems like dwarf galaxies, this is no longer the case.
+This leads to inconsistencies in both the effective metal yield of the modelled stars, and (often) an artificial reduction of the effects of stellar feedback.
+Recent works have developed new models to address this issue, discretizing (rather than averaging over) individual feedback events \citep[e.g.][]{MUGS2010,FIRE,Hopkins2018,Rosdahl2018} or accounting for stochastic sampling of the IMF \citep{Hu2016,Hu2017,Applebaum2018,Su2018}.
+However, each of these methods utilizes a sub-grid recipe in some fashion to improve upon the SSPs.
+On the other extreme are highly resolved simulations which model star formation with ``sink particles" \citep[see for example ][]{Krumholz2004,Federrath2010,GongOstriker2013,BleulerTeyssier2014,Sormani2017} that account for the gradual accretion of gas in the growth of a single star (or group of stars) and protostellar feedback.
+These recipes are often computationally expensive, however, restricting their use over long timescales (100's to 1000's of Myr or more) in galaxy-scale simulations.
+
+In this dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF.
+This allows us to place unprecidented detail on both the stellar feedback and metal yields associated with each star, spatially and temporally resolving differences in both of these channels as a function of stellar mass and metallicity.
+
+\subsection{Stellar Feedback} \label{intro:sec:feedback}
+
+\subsubsection{Stellar Radiation Feedback}
+\label{intro:sec:radiation}
+
+We only briefly discuss this method of feedback here, as it is discussed in much more detail in both Chapters~\ref{ch:chapter1} and \ref{ch:chapter2}.
+In brief, \cite{Leitherer1999}, \cite{Agertz2013}, and others demonstrated that stellar radiation, accounts for a substantial fraction of the total energy output of a stellar population.
+Ionizing photons from young, massive stars can photoionize and photoheat the gas surrounding sites of recent star formation.
+This effectively pre-processes the local environment within which SNe occur, often increasing the effectiveness of SNe in regulating star formation and driving outflows \citep{Hu2016}.
+In addition, radiation pressure in the single-scattering limit (from UV photons) and rescattered infrared photons has been used as an additional source of pre-SN feedback \citep[e.g.][]{FIRE}.
+However, due in part to differences in how ionizing radition is followed across simulations, there is disagreement as to exactly how and in what conditions this acts as a source of feedback (see \cite{Krumholz2018} for a detailed examination of this problem).
+
+Non-ionizing radiation also contributes to the regulation of star formation and the multi-phase ISM.
+Far ultraviolet (FUV) photons contribute to gas heating via the photoelectric heating of dust grains.
+This is a significant heating mechanism in higher metallicity environments, like the Milky Way \citep{Parravano2003,Wolfire2003}, but may still be important in setting temperature floor of cold dense gas in lower mass galaxies \citep{Forbes2016,Hu2017}.
+Lyman-Werner (LW) band radiation regulates the $H_2$ abundance, which is particularly important in low-metallicity environments where $H_2$ is a dominant coolant \citep[e.g.][]{Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation perscriptions that depend upon the local $H_2$ mass fraction.} As the goal of this dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of the processes in some fashion, including the use of an adaptive ray-tracing radiative transfer scheme to track the stellar ionizing photons.
+
+%
+%
+%
+%\section{Semi-Analytic Models / One-zone Models}
+%
+%Definitely have a lot here. Motivate need for better understanding of mixing processes in galaxies. \citep{SchonrichWeinberg2019}
+%
+%
+
+\section{Structure of Dissertation}\label{intro:sec:structure}
 
@@
 In Chapter \ref{ch:chapter2} \citep[published as ][]{Emerick2018a}, we investigate how stellar ionizing radiation feedback impacts the evolution of our simulated low mass dwarf galaxy.
-We confirm the findings in recent works, as dicsussed in Section~\ref{sec:radiation}, that find that stellar radiation is an important source of pre-supernova feedback that regulates star formation and can help drive galactic outflows outflows.
+We confirm the findings in recent works, as dicsussed in Section~\ref{intro:sec:radiation}, that find that stellar radiation is an important source of pre-supernova feedback that regulates star formation and can help drive galactic outflows outflows.
 We additionally investigate how radiation feedback couples to the ISM to drive galactic winds by demonstrating that the ionization of gas far from individual ionzing sources, out into the disk-halo interface of our galaxy, creates low-density channels through which supernovae can readily drive gas and metals into and beyond the galaxy's CGM.

### 2019-03-14 thesis/chapters/ch_introduction.tex
Some slight rewording. Added intro to feedback section. Added supernova section cleaned up a bit of the radiation section. added stellar winds section. Feedback draft should be complete.

@@
 
-\subsubsection{Stellar Radiation Feedback}
+The first models of galacitc evolution produced galaxies with stellar masses far in excess of what is observed in the Universe, converting a substantial fraction of their baryons into stars.
+From these initial works, it was clear that some form of feedback process must take place to self-regulate star formation within galaxies.
+With observations of metal abundances in the CGM around galaxies \citep[see][ for a recent review]{Tumlinson2017}, and of fast-moving outflows from star forming galxaies \citep[see][ for a review]{Veilleux2005}, it was additionally clear that some mechanism must exist to drive these outflows.
+Stellar feedback became the clear physical mechanism to account for both of these phenomena.\footnote{Except maybe for more massive galaxies, where active galactic nuclei likely plan some role in regulating star formation and certainly play a role in driving outflows \citep[e.g.][]{Fabian2012}.}
+
+Initial models for stellar feedback relied primarily on the energy injection from supernovae (SNe, see Section~\ref{intro:sec:supernovae}) to regulate star formation and drive outflows, but it has become clear that this mechanism alone cannot completely account for all of the star formation, ISM, outflow, CGM, and even intergalactic medium (IGM) properties of observed galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews and more detailed discussion of how feedback impacts outstanding problems in galactic evolution).
+Other sources of effective stellar feedback have been identified since \citep[e.g.][]{Agertz2013}, which serve to regulate star formation on different timescales and help develop and ISM and CGM with different phase and ionization properties, and includes stellar radiation (Section~\ref{intro:sec:radiation}) and stellar winds (Section~\ref{intro:sec:stellarwinds}).
+
+Although not included in this dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution.
+A substantial amount of recent research has been dedicated towards the examination of supernova-driven cosmic ray feedback (see Section~\ref{ch1:sec:CRs} for a more detailed discussion and references).
+In brief, cosmic rays can be a dominant source of heading in very dense gas and act as a source of non-thermal pressure in the ISM, which can drive galactic winds with qualitatively different phase structures \citep[e.g.][]{SalemBryanCorlies}.
+In addition, binarity is often ignored in models of stellar feedback, but can dramatically extend the timescales over which ionizing radiation and supernovae act in a newly formed stellar populations, typically increasing their total energy output and decreasing the typical ISM densities in which SNe explode, increasing their effectiveness (see Section~\ref{ch1:sec:binary stars}).
+Finally, exoctic sources of stellar feedback, such as hupernovae, high-mass X-ray binaries, and neutron star neutron star mergers can also be a potentially important source of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}.
+However, the uncertainties in the frequency and delay time distributions for when these events should occur, and there relative rarity preclude including these effects in this dissertation.
+
+\subsubsection{Supernova Feedback}
+\label{intro:sec:supernovae}
+
+In the simplest model, supernova feedback is treated as the injection of pure thermal energy (and mass) into the fluid element(s) that are host / closest to the chosen site of a supernova explosion.
+In self-consistent models of star formation and feedback these sites are usually actual star particles, but this does not have to be the case.
+The first models which included supernova feedback lacked the spatial / mass resolution to resolve individual (or even collective) SN events.
+This is the source of the commonly known ``overcooling" problem, whereby too little energy is injected into too much mass such that the affected region only reaches modest temperatures ($T \lessim 10^5$~K, as opposed to $T > 10^7$~K, or so).
+This temperature is right around the peak of the cooling curve, and thus the energy is rapidly radiated away before the injected energy has any time to make a significant dynamical impact of the galaxy.
+This is still a problem today in large-box simulations of cosmological volumes which have insufficient resulution to resolve individual SNe.
+While some of the initial, ad-hoc fixes for this problem (e.g.
+turning off cooling for some time in SN affected fluid elements, decoupling SN affected SPH particles from the hydrodynamics for some time) are still in use today, some notable advancements have been made to employ some combination of kinetic, momentum, and thermal energy feedback to attempt to capture SNe in a more consistent fashion \citep[e.g.][]{Hopkins2014,Simpson2015,Hopkins2018}.
+
+High resolution simulations, like those developed in this dissertation, can typically resort to utilizing pure thermal energy injection into the fluid elements surrounding the supernova site and avoiding artificial ``overcooling".
+This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}.
+However, a spatial resolution requirement is a density dependent statement; in this case supernovae that occur in the densest gas ($n > 10^{2-3}$~cm$^{-3}$) may still be under-resolved and ineffective.
+In this case, accounting for feedback processes from massive stars that occur before the first core collapse SN in a given star formation event becomes critical \citep{Hu2016}.
+Including these physics, as discussed below, greatly reduces the typical ISM densities in which SNe occur, greatly increasing the likelihood that these events are well resolved.
+
+\subsubsection{Stellar Radiation}
 \label{intro:sec:radiation}
@@
 
+\subsubsection{Stellar Winds}
+\label{intro:sec:stellarwinds}
+
+Stellar winds, in addition to stellar radiation, are a potentially important source of pre-SN feedback that helps regulate star formation in / around the birth clouds of newly formed stars.
+However, the hot ($T>10^{6}$~K), fast ($v \sim 10^{3}$~km~s$^{-1}$) winds from massive stars \citep{Weaver1977} are challenging to model self-consistently in galaxy-scale simulations.
+For this reason, there has been comparatively little research on how they affect global galaxy properties, even though some models do include their energy injection in an integrated / approximate fashion \citep[e.g.][]{FIRE}.
+However, stellar winds, from both massive stars and weaker winds from the AGB phase of low mass stars, are important sources of metal enrichment.
+For these reasons we do include a simplified model for stellar wind feedback in this disseration.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in experimental simulations where radiation feedback is ignored.
+It is thus likely subdominant to radiation feedback.}
 %

### 2019-03-14 thesis/chapters/ch_chapter1.tex
redoing section labels for Chapter 1 to be consistent with full project

@@
 We describe each mode of our multi-channel feedback 
-in detail in Section~\ref{sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{sec:IC}, show results from this simulation in Section~\ref{sec:results}, discuss the results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusion}.
-Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{sec:methods}, which contains a complete---yet brief---summary of the included physics.
+in detail in Section~\ref{ch1:sec:methods}, describe their implementation in an isolated dwarf galaxy simulation in Section~\ref{ch1:sec:IC}, show results from this simulation in Section~\ref{ch1:sec:results}, discuss the results in Section~\ref{ch1:sec:discussion}, and conclude in Section~\ref{ch1:sec:conclusion}.
+Readers who may want to only briefly skim (or skip) over the details of our included physics are advised to just read the beginning of Section~\ref{ch1:sec:methods}, which contains a complete---yet brief---summary of the included physics.
 
 \section{Methods}
-\label{sec:methods}
+\label{ch1:sec:methods}
 We produce high-resolution, galaxy-scale simulations tracking stars not as single stellar populations, but as individual stars sampled from an assumed IMF.
@@
 \subsection{Hydrodynamics and Gravity}
-\label{sec:hydro}
+\label{ch1:sec:hydro}
 
@@
 Specifically, simulations presented here were conducted at changeset 7001d99.} We solve the equations of hydrodynamics using a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} and a two-shock approximate Riemann solver with progressive fallback to more diffusive Riemann solvers in the event that higher order methods produce negative densities or energies.
-We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{sec:IC}).
+We compute the total gravitational potential from gas self-gravity, stars, and a static background dark matter potential (see Section~\ref{ch1:sec:IC}).
 Self-gravity is computed with a multigrid Poisson solver.
@@
 
-We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{sec:star formation}).
+We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{ch1:sec:star formation}).
 Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
@@
 \subsection{Chemistry and Cooling Physics}
-\label{sec:chemistry}
+\label{ch1:sec:chemistry}
 
@@
 As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
-As discussed in more detail in Section~\ref{sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
+As discussed in more detail in Section~\ref{ch1:sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
 Using this prescription with metal line cooling tables computed under an optically thin assumption can lead to an order of magnitude overestimation of the cooling rate at certain densities, as discussed in \citet{Hu2017} and  Appendix~\ref{appendix:cooling}.
@@
 These are discussed in greater detail in Appendix ~\ref{appendix:cooling}.
-Finally, we ignore the effect the stellar radiation field (see Section~\ref{sec:diffusive heating}) may have on the interpolated metal line cooling rates.
+Finally, we ignore the effect the stellar radiation field (see Section~\ref{ch1:sec:diffusive heating}) may have on the interpolated metal line cooling rates.
 
 \subsection{Star Formation Algorithm}
-\label{sec:star formation}
+\label{ch1:sec:star formation}
 In order to resolve individual star formation events on galactic scales, we implement a stochastic star formation algorithm adopted from \citet{Goldbaum2015,Goldbaum2016}.
@@
 \subsection{Stellar Properties}
-\label{sec:properties}
-Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{sec:ionizing radiation}).
+\label{ch1:sec:properties}
+Given each star's birth mass and metallicity, we interpolate over the PARSEC grid of stellar evolution tracks \citep{Bressan2012} to assign a lifetime and AGB phase start time (if any) to it, as well as the effective temperature $T_{\rm eff}$ and surface gravity $g$ used in computing radiation properties (see Section \ref{ch1:sec:ionizing radiation}).
 We use the largest subset of the PARSEC models that are regularly sampled in our mass/metallicity space of interest, with 26 mass bins over M$_{*} \in \left[0.95, 120.0 \right] {\rm M_{\odot}}$ and 11 metallicity bins over $Z \in \left[10^{-4}, 0.017 \right]$.
@@
 \subsubsection{Stellar Yields}
-\label{sec:yields}
+\label{ch1:sec:yields}
 For the first time in galaxy-scale simulations, we track galactic chemodynamical evolution using stellar yields ejected from star particles that represent individual stars.
@@
 In our model, stars below this mass eject their wind yields in an AGB phase only at the end of their lives, typically over a period comparable to or less than a few time steps ($\lesssim 10$ kyr).
-Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{sec:stellar winds} for details on the wind energetics).
+Stars above this mass are assumed to eject their stellar yields via line-driven stellar winds at a constant mass loss rate throughout their lifetime (neglecting Wolf-Rayet and luminous blue variable phases), ending their lives as a core-collapse SN (see Sect.~\ref{ch1:sec:stellar winds} for details on the wind energetics).
 Varying $M_{\rm trans}$ changes both the time at which yields for stars around this mass are ejected (for reference, the lifetime of an 8 M$_{\odot}$ star is about 35--40~Myr), and the energy injection from these winds.
 \citet{Cote2017a} explores how the choice of $M_{\rm trans}$ affects galaxy abundances in a one-zone model.
-We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{sec:binary stars}.
+We neglect the effects of binary star evolution on stellar feedback, and discuss the significance of this in Sect.~\ref{ch1:sec:binary stars}.
 
@@
 These iron group rich events are responsible for the $\sim$1 Gyr timescale turnover, or ``knee", in $[\alpha/\rm{Fe}]$ vs $[\rm{Fe}/\rm{H}]$ diagrams.
-We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{sec:Type Ia}.
+We use the Type Ia SN yields given in \citet{Thielemann1986}, adopting a Type Ia SN model as discussed in Sect.~\ref{ch1:sec:Type Ia}.
 We emphasize that we only track Type Ia SNe occurring within the population of stars formed in this model, neglecting SNe from any possible pre-existing population, substantially limiting the number of Type Ia SNe occurring during the initial gigayear in our models.
@@
 \subsubsection{Stellar Winds}
-\label{sec:stellar winds}
+\label{ch1:sec:stellar winds}
 Stellar winds are important sources of enrichment and feedback in galaxies at both early times from massive stars and late times from AGB stars.
@@
 Due to the substantial additional computational expense of following stellar winds for gigayear timescales, we reserve examining the detailed importance of winds to future work.
-These points are discussed in more detail in Sect.~\ref{sec:stellar winds discussion}.
+These points are discussed in more detail in Sect.~\ref{ch1:sec:stellar winds discussion}.
 
@@
 \subsubsection{Core Collapse SNe}
-\label{sec: core collapse}
+\label{ch1:sec: core collapse}
 Stars between  $M_{\rm trans} = 8$ M$_{\odot}$ and 25 M$_{\odot}$ end their lives as core collapse SNe, ejecting mass and metals as determined by the NuGrid stellar yield tables, along with 10$^{51}$ erg of thermal energy.
@@
 \subsubsection{Type Ia SNe}
-\label{sec:Type Ia}
+\label{ch1:sec:Type Ia}
 We continue to track low mass stars ($M < 8$ M$_{\odot}$) after their death as WD particles, marking a subset as Type Ia SN progenitors.
@@
 \subsubsection{Ionizing Radiation from Discrete Sources}
-\label{sec:ionizing radiation}
+\label{ch1:sec:ionizing radiation}
 Radiation feedback, including ionization, ionization heating, and radiation pressure, is an important source of feedback in galaxies.
@@
 \subsubsection{Diffuse  Heating}
-\label{sec:diffusive heating}
+\label{ch1:sec:diffusive heating}
 We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the FUV (6 eV $<h\nu< 13.6$ eV) radiation from each of our star particles.
 The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the spectral energy distributions for each gridded star.
-Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
+Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Sect.~\ref{ch1:sec:ionizing radiation} and Appendix~\ref{appendix:radiation}).
 Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}.
@@
 
-The value of $D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{sec:chemistry}.
+The value of $D$ is computed consistently with our \texttt{Grackle} dust model, using the broken power law fit from \citet{Remy-Ruyer2014}, as described in Section~\ref{ch1:sec:chemistry}.
 The extremely low dust-to-gas ratio in our modeled galaxies leads to a reduction in the photoelectric heating rate by approximately two orders of magnitude, as compared to a model that assumes a ratio $D$ that scales linearly with metallicity at very low metallicity.
@@
 \subsubsection{Lyman-Werner Radiation}
-\label{sec:LW}
+\label{ch1:sec:LW}
 In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rate.
@@
 \section{Galaxy Initial Conditions}
-\label{sec:IC}
+\label{ch1:sec:IC}
 We apply these methods to a first test case of the evolution of an isolated, low mass dwarf galaxy.
@@
 \section{Results}
-\label{sec:results}
-We present our initial results here, providing an overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms.
+\label{ch1:sec:results}
+We present our initial results here, providing an overview of the morphological (Section~\ref{ch1:sec:structure}), star formation (Section~\ref{ch1:sec:sfr}), ISM (Section~\ref{ch1:sec:phase}), radiation field (Section~\ref{ch1:sec:ISRF}), outflow (Section~\ref{ch1:sec:outflows}), and chemical (Section~\ref{ch1:sec:chemical evolution}) properties of our dwarf galaxy during the 500~Myr after the first new star forms.
 Unless otherwise noted, $t = 0$ is defined as the time at which that first star particle forms, which is 43~Myr after the actual beginning of the simulation run.
@@
 \subsection{Morphological Structure and Evolution}
-\label{sec:structure}
+\label{ch1:sec:structure}
 
@@
 Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels.
-The ISM properties are quantified further in Section~\ref{sec:phase}.
+The ISM properties are quantified further in Section~\ref{ch1:sec:phase}.
 
@@
 \subsection{Star Formation Rate and Mass Evolution}
-\label{sec:sfr}
+\label{ch1:sec:sfr}
 
@@
 Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.19 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$.
-We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.
+We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{ch1:sec:observation}.
 
@@
 Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}.
-The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.
+The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{ch1:sec:observation}.
 
@@
 \subsection{ISM Properties}
-\label{sec:phase}
+\label{ch1:sec:phase}
 
@@
 We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results.
-Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left.
+Our artificial temperature ceiling in diffuse gas (see Section~\ref{ch1:sec:hydro}) is seen clearly by the horizontal feature in the top left.
 The boxed regime in the lower right corner shows our star formation density and temperature threshold.
@@
 \subsection{Interstellar Radiation Field}
-\label{sec:ISRF}
+\label{ch1:sec:ISRF}
 
@@
 In Fig.~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
-The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}).
+The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{ch1:sec:diffusive heating}).
 The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions.
@@
 \subsection{Outflow Properties}
-\label{sec:outflows}
+\label{ch1:sec:outflows}
 
@@
 The outflowing material is multiphase, broken into WNM, WIM, and HIM.
-See Section~\ref{sec:phase} for definitions of these regimes.
+See Section~\ref{ch1:sec:phase} for definitions of these regimes.
 We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K.
@@
 \subsection{Metal Evolution} 
-\label{sec:chemical evolution}
+\label{ch1:sec:chemical evolution}
 
@@
 Likewise, the CGM metal content continually decreases until the end of the simulation from loss through the virial radius of the halo.
-See Section~\ref{sec:obs_metals} for further discussion.
+See Section~\ref{ch1:sec:obs_metals} for further discussion.
 
@@
 \section{Discussion}
-\label{sec:discussion}
+\label{ch1:sec:discussion}
 
 \subsection{Comparison to Observed Low Mass Dwarf Galaxies}
-\label{sec:observation}
-
-As noted in Section~\ref{sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs.
+\label{ch1:sec:observation}
+
+As noted in Section~\ref{ch1:sec:IC}, our galaxy model is not intended to directly reproduce the observed properties of Local Group ultra-faint dwarfs.
 Notably, our initial conditions neglect a pre-existing stellar population and are only followed for 500~Myr, a fraction of the age of $z = 0$ dwarf galaxies.
-However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{sec:gas_sf}), molecular gas (Section~\ref{sec:molecular gas content}), and metal retention fraction (Section~\ref{sec:obs_metals}) properties of observed dwarf galaxies.
+However, we can still place our model in context with observations using simple comparisons to the star formation rate (Section~\ref{ch1:sec:gas_sf}), molecular gas (Section~\ref{ch1:sec:molecular gas content}), and metal retention fraction (Section~\ref{ch1:sec:obs_metals}) properties of observed dwarf galaxies.
 We show that these properties are broadly consistent with observations.
@@
 \subsubsection{Gas and Star Formation}
-\label{sec:gas_sf}
+\label{ch1:sec:gas_sf}
 
@@
 We note that there is generally no correction made for any possible H$_{\rm 2}$ or HII content.
-As shown in Section~\ref{sec:molecular gas content}, these components may be significant.
+As shown in Section~\ref{ch1:sec:molecular gas content}, these components may be significant.
 
@@
 \subsubsection{Molecular Gas Content}
-\label{sec:molecular gas content}
+\label{ch1:sec:molecular gas content}
 The molecular gas content of low-mass dwarf galaxies is generally assumed
@@
 Assuming the relationship in \citet{Leroy2013} and \citet{Momose2013}, \citet{Roychowdhury2014} finds typical molecular gas mass fractions can be anywhere from $f_{\rm H_2} = 0.05$ to $f_{\rm H_2} = 0.5$; a significant range in values.
-As discussed in Section~\ref{sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range.
+As discussed in Section~\ref{ch1:sec:properties}, our galaxy has $f_{H_2}$ of 0.001 -- 0.05, just overlapping with this range.
 H$_2$ formation in our model is possible through formation on dust, the three body interaction, or the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$.
@@
 \subsubsection{Metal Retention}
-\label{sec:obs_metals}
+\label{ch1:sec:obs_metals}
 
@@
 Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}.
-As discussed in Section~\ref{sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
+As discussed in Section~\ref{ch1:sec:chemical evolution}, more than 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk, agreeing with observations.
 However, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs.
@@
 \subsubsection{Massive Stellar Wind Energy}
-\label{sec:stellar winds discussion}
+\label{ch1:sec:stellar winds discussion}
 Our massive stellar wind model drastically reduces the injected wind velocity from $\sim$1000~km~s$^{-1}$ to 20~km~s$^{-1}$.
@@
 \subsubsection{Cosmic Rays} 
-\label{sec:CRs}
+\label{ch1:sec:CRs}
 
@@
 \subsection{Detailed Stellar Evolution and Binary Stars}
-\label{sec:binary stars}
+\label{ch1:sec:binary stars}
 
@@
 \section{Conclusion}
-\label{sec:conclusion}
+\label{ch1:sec:conclusion}
 We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment.
@@
 
-As discussed in Section~\ref{sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations.
+As discussed in Section~\ref{ch1:sec:molecular gas content}, H$_2$ formation is dominated by the gas-phase H$^{-}$ channel in our simulations.
 Accounting for the photodetachment of H$^{-}$ from the stellar radiation field, which may dominate over the UVB, can be important for correctly modeling H$_2$ formation in low metallicity gas~\citep{Wolcott-Green2012}.
@@
 
-As emphasized in Section~\ref{sec:molecular gas content}, further work modeling low-metallicity dwarf galaxies with a more detailed chemistry model would be useful to clarify the role of various competing phenomena in driving the molecular properties of these galaxies.
+As emphasized in Section~\ref{ch1:sec:molecular gas content}, further work modeling low-metallicity dwarf galaxies with a more detailed chemistry model would be useful to clarify the role of various competing phenomena in driving the molecular properties of these galaxies.
 

### 2019-03-14 thesis/chapters/ch_chapter1.tex
redoing figure labels to be consistent with project

@@
 
-We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}.
+We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Fig.~\ref{fig:ch1:panel_x} and Fig.~\ref{fig:ch1:panel_z}.
 These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
@@
 Each individual main sequence star particle is shown in the number density projections as a single white dot.}
-\label{fig:panel_x}
-\end{figure*}
-
-The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:scale_height}.
+\label{fig:ch1:panel_x}
+\end{figure*}
+
+The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:ch1:scale_height}.
 This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time.
@@
 For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
-In the final column of Fig.~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
+In the final column of Fig.~\ref{fig:ch1:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
 With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
@@
 \includegraphics[width=0.975\linewidth]{figures/ch1/multiplot_4x4_z.png}
-\caption{Same as Fig.~\ref{fig:panel_x}, but showing face-on views.}
-\label{fig:panel_z}
+\caption{Same as Fig.~\ref{fig:ch1:panel_x}, but showing face-on views.}
+\label{fig:ch1:panel_z}
 \end{figure*}
@@
 \includegraphics[width=0.975\linewidth]{figures/ch1/scale_height}
-\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
-\label{fig:scale_height}
+\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:ch1:panel_x} and ~\ref{fig:ch1:panel_z}.}
+\label{fig:ch1:scale_height}
 \end{figure}
@@
 
-We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Fig.~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
+We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Fig.~\ref{fig:ch1:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
 The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$.
@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Fig.~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
+By the time of first star formation ($t=0$ in Fig.~\ref{fig:ch1:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
 The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
@@
 Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
-\label{fig:sfr_mass_evolution}
+\label{fig:ch1:sfr_mass_evolution}
 \end{figure*}
@@
 
-Fig.~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
-One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Fig.~\ref{fig:ISM_evolution}).
+Fig.~\ref{fig:ch1:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
+One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Fig.~\ref{fig:ch1:ISM_evolution}).
 Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
@@
 The region in the lower right corner indicates our density and temperature thresholds for star formation.}
-\label{fig:phase}
+\label{fig:ch1:phase}
 \end{figure}
 
-The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Fig.~\ref{fig:ISM_evolution}.
+The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Fig.~\ref{fig:ch1:ISM_evolution}.
 The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
@@
 However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
-Together, these figures better quantify the general properties observed in the panel plots in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}.
+Together, these figures better quantify the general properties observed in the panel plots in Fig.~\ref{fig:ch1:panel_x} and Fig.~\ref{fig:ch1:panel_z}.
 
@@
 \caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
-\label{fig:ISM_evolution}
+\label{fig:ch1:ISM_evolution}
 \end{figure*}
@@
 This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
-In Fig.~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
+In Fig.~\ref{fig:ch1:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
 The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{ch1:sec:diffusive heating}).
@@
 In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
-\label{fig:ISRF}
+\label{fig:ch1:ISRF}
 \end{figure}
@@
 Here, we include all gas within the mid-plane of our dwarf galaxy.
-Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
+Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:ch1:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
 This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
-\label{fig:ISRF_2D}
-\end{figure*}
-
-To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Fig.~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr.
+\label{fig:ch1:ISRF_2D}
+\end{figure*}
+
+To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Fig.~\ref{fig:ch1:ISRF_2D} at a single snapshot at 300~Myr.
 This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
@@
 However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
-In Fig.~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
+In Fig.~\ref{fig:ch1:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
 We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
@@
 
-The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Fig.~\ref{fig:mass_outflow}.
+The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Fig.~\ref{fig:ch1:mass_outflow}.
 Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
@@
 \caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
-\label{fig:mass_outflow}
+\label{fig:ch1:mass_outflow}
 \end{figure*}
@@
 Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
-In Fig.~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
+In Fig.~\ref{fig:ch1:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
 Gas with a negative velocity is moving towards the center of the halo.
@@
 \caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-This is averaged over the same time interval as Fig.~\ref{fig:ISRF}.
+This is averaged over the same time interval as Fig.~\ref{fig:ch1:ISRF}.
 The outflowing material is multiphase, broken into WNM, WIM, and HIM.
@@
 There is little to no outflowing mass in the CNM.}
-\label{fig:outflow_velocity}
+\label{fig:ch1:outflow_velocity}
 \end{figure}
@@
 This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
-In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}.
+In the top panel of Fig.~\ref{fig:ch1:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}.
 The parameter used to quantify metal outflow efficiencies varies among works.
@@
 where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
+These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{fig:ch1:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
 On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5).
@@
 \includegraphics[width=0.9\linewidth]{figures/ch1/metal_retention}
-\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:mass_outflow}.
+\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}.
 This is the ratio between the metal outflow rate and the metal production rate.
@@
 In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
-\label{fig:metal_evolution}
+\label{fig:ch1:metal_evolution}
 \end{figure}
@@
 These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
-This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
+This is quantified in the lower panel of Fig.~\ref{fig:ch1:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
 After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
@@
 
-We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:metal_slices}.
+We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:ch1:metal_slices}.
 The left panel gives the abundance ratio of N to O throughout the ISM.
@@
 In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occurred in the preceding 5 Myr as black stars and orange diamonds respectively.}
-\label{fig:metal_slices}
+\label{fig:ch1:metal_slices}
 \end{figure*}
@@
 Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
-Given the variations in Fig.~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
+Given the variations in Fig.~\ref{fig:ch1:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
 The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
@@
 However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
+In Figure ~\ref{fig:ch1:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
 In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.
@@
 There is no clear correlation with time in this diagram.}
-\label{fig:KS}
-\end{figure*}
-
-We include recent observational constraints on these relationships in Figure ~\ref{fig:KS}.
+\label{fig:ch1:KS}
+\end{figure*}
+
+We include recent observational constraints on these relationships in Figure ~\ref{fig:ch1:KS}.
 Our galaxy fluctuates significantly about both relationships with no clear trends in time.
@@
 In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
-It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
+It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:ch1:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
 This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
@@
 \item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
-(See Figs.~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).
+(See Figs.~\ref{fig:ch1:sfr_mass_evolution} and \ref{fig:ch1:KS}).
 
@@
 metal mass loading factors near unity.
-By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Fig.~\ref{fig:outflow_velocity}).
+By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Fig.~\ref{fig:ch1:outflow_velocity}).
 
@@
 By the end of the simulation $\sim$45\% of the remaining metals stay within the virial radius (but outside the galaxy), while $\sim$50\%
-have been ejected beyond the virial radius. (See Figs.~\ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.)
+have been ejected beyond the virial radius. (See Figs.~\ref{fig:ch1:mass_outflow}, \ref{fig:ch1:outflow_velocity}, and \ref{fig:ch1:metal_evolution}.)
 
@@
 This is comparable to the resolution limit of the diffuse HI in observed, gaseous low-mass dwarfs.
-At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Fig.~\ref{fig:scale_height}).
+At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Fig.~\ref{fig:ch1:scale_height}).
 
@@
 The importance of radiation feedback in our model is investigated in more detail in \cite{Emerick2018b}.
-(See Figs.~\ref{fig:ISRF} and \ref{fig:ISRF_2D}.)
+(See Figs.~\ref{fig:ch1:ISRF} and \ref{fig:ch1:ISRF_2D}.)
 
@@
 Cold, neutral hydrogen dominates the mass of our galaxy.
-While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Fig.~\ref{fig:sfr_mass_evolution} and Fig.~\ref{fig:ISM_evolution}.)
+While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Fig.~\ref{fig:ch1:sfr_mass_evolution} and Fig.~\ref{fig:ch1:ISM_evolution}.)
 
@@
 We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Fig.~\ref{fig:stellar radiation properties} we plot these properties.
+In Fig.~\ref{fig:ch1:stellar radiation properties} we plot these properties.
 We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
@@
 Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
-\label{fig:stellar radiation properties}
+\label{fig:ch1:stellar radiation properties}
 \end{figure*}
@@
 
-The left panel of Fig.~\ref{fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
+The left panel of Fig.~\ref{fig:ch1:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
 As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
 For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations.
-The right panel of Figure ~\ref{fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
+The right panel of Figure ~\ref{fig:ch1:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
 \begin{equation}
@@
 This shows that a fraction of these SNe are certainly unresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
-\label{fig:SN histogram}
+\label{fig:ch1:SN histogram}
 \end{figure*}
@@
 The regimes where heating dominates are plotted with dashed lines for clarity.}
-\label{fig:cooling comparison}
+\label{fig:ch1:cooling comparison}
 \end{figure*}
@@
 This can be a significant effect, particularly at higher metallicities.
-We demonstrate this in Fig.~\ref{fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
+We demonstrate this in Fig.~\ref{fig:ch1:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
 The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
 In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
-Fig.~\ref{fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
+Fig.~\ref{fig:ch1:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
 We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
@@
 rate is shown with solid lines.}
-\label{fig:cooling}
+\label{fig:ch1:cooling}
 \end{figure*}
@@
 To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https://grackle.readthedocs.io/en/latest/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) and initial temperature of 10$^{4}$~K for 200~Myr.
-In Fig.~\ref{fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background.
+In Fig.~\ref{fig:ch1:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background.
 As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate.
@@
 These runs have identical initial conditions, random SN driving, cooling, heating, and chemistry as our fiducial simulation, but with no star formation.
-We vary the Lyman-Werner radiation and the H$^{-}$ photodetachment rate by the factors shown, which are comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ISRF}).
+We vary the Lyman-Werner radiation and the H$^{-}$ photodetachment rate by the factors shown, which are comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ch1:ISRF}).
 Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9.
@@
 We note the regime below 1.0 on each axis is somewhat unphysical, and is never reached in our hydrodynamics simulations.}
-\label{fig:Grackle grid}
+\label{fig:ch1:Grackle grid}
 \end{figure}
@@
 
-We demonstrate the effect of varying resolution in the evolution of our galaxy model in Fig.~\ref{fig:resolution_study}.
+We demonstrate the effect of varying resolution in the evolution of our galaxy model in Fig.~\ref{fig:ch1:resolution_study}.
 We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines).
@@
 The line colors in the left panel are for better clarity between the SFRs.}
-\label{fig:resolution_study}
-\end{figure*}
-
-Fig.~\ref{fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
+\label{fig:ch1:resolution_study}
+\end{figure*}
+
+Fig.~\ref{fig:ch1:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
 We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
 The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs.
-We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Fig.~\ref{fig:SN histogram}.
+We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Fig.~\ref{fig:ch1:SN histogram}.
 However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
@@
 
-Theses differences in densities are shown clearly by comparing Fig.~\ref{fig:phase} with Fig.~\ref{fig:phase_resolution}.
+Theses differences in densities are shown clearly by comparing Fig.~\ref{fig:ch1:phase} with Fig.~\ref{fig:ch1:phase_resolution}.
 Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.
@@
 \includegraphics[width=0.475\linewidth]{figures/ch1/6pc_phase.png}
-\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:phase}.}
-\label{fig:phase_resolution}
+\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:ch1:phase}.}
+\label{fig:ch1:phase_resolution}
 \end{figure*}

### 2019-03-14 thesis/chapters/ch_chapter2.tex
redoing figure and section labels to be consistent with project

@@
 
-\section{Introduction} \label{sec:intro}
+\section{Introduction} \label{ch2:sec:intro}
 Historically, simulations of galaxy formation have suffered from the ``overcooling'' problem, whereby the action of self-gravity and radiative cooling alone produces galaxies with far too many stars.
@@
 Our fiducial model, containing full stellar radiation feedback, is compared against a run without ionizing radiation feedback, and a run with ionizing feedback limited to the local region around a given star.
-We discuss our methods in Section~\ref{sec:methods} and present our results ion Section~\ref{sec:results}.
+We discuss our methods in Section~\ref{ch2:sec:methods} and present our results ion Section~\ref{ch2:sec:results}.
 
-\section{Methods and Initial Conditions} \label{sec:methods}
+\section{Methods and Initial Conditions} \label{ch2:sec:methods}
 We refer the reader to Paper I for a more detailed description of our methods.
@@
 
-\section{Results} \label{sec:results}
+\section{Results} \label{ch2:sec:results}
 
@@
 \caption{The star formation rate (left) and gas and stellar mass (right) of each of our three simulations over time. Time bins with no star formation are left empty.}
-\label{fig:sfr_mass_evolution}
+\label{fig:ch2:sfr_mass_evolution}
 \end{figure*}
 
-We compare the resulting star formation rate (left) and gas mass properties (right) of our three simulations in Figure~\ref{fig:sfr_mass_evolution}.
+We compare the resulting star formation rate (left) and gas mass properties (right) of our three simulations in Figure~\ref{fig:ch2:sfr_mass_evolution}.
 There is a clear, significant contrast between the runs with and without ionizing radiation.
@@
 Radiation from these stars quickly ionizes and dissipates surrounding dense gas that would otherwise have gone to fuel a significant amount of additional star formation.
-This is confirmed in Figure~\ref{fig:sf gas}, which shows the gas mass in each simulation above the SF density threshold of $n = 200$~cm$^{-3}$ during the first 100~Myr.
+This is confirmed in Figure~\ref{fig:ch2:sf gas}, which shows the gas mass in each simulation above the SF density threshold of $n = 200$~cm$^{-3}$ during the first 100~Myr.
 While our fiducial and shortrad simulations remain roughly the same here, the noRT run, at its peak, has an order of magnitude more cold, dense gas.
@@
 \caption{The total gas mass at $n > 200$~cm$^{-3}$, our star formation density threshold.}
-\label{fig:sf gas}
+\label{fig:ch2:sf gas}
 \end{figure}
@@
 This can be confirmed by examining the metal retention fraction (the fraction of produced metals retained within the disk of the galaxy) and mass outflow rates across simulations.
-As shown in Figure~\ref{fig:metal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation.
+As shown in Figure~\ref{fig:ch2:metal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation.
 The outflow in noRT is only a factor of a few lower than the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback, so it implies a far lower mass loading factor.
@@
 \caption{{\bf Left:} The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange).
-As in Figure~\ref{fig:sfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively.
+As in Figure~\ref{fig:ch2:sfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively.
 {\bf Middle:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed).
@@
 }
-\label{fig:metal_retention}
+\label{fig:ch2:metal_retention}
 \end{figure*}
 
-\section{Discussion} \label{sec:discussion}
+\section{Discussion} \label{ch2:sec:discussion}
 Accounting for feedback from stellar radiation plays a significant role in determining the ability for SN energy to couple to the ISM and therefore drive outflows.
@@
 Modeling only local stellar ionizing feedback is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
-To explore the cause of this difference we compare in Figure~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.
+To explore the cause of this difference we compare in Figure~\ref{fig:ch2:panel1} and~Figure~\ref{fig:ch2:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.
 
@@
 However, SNe launched gas is trapped by neutral, cold shells in the shortrad simulation, unable to easily escape from the disk of the simulated galaxy.
-These same insights can also be gained by comparing this figure with Figure~\ref{fig:panel2}.}
-\label{fig:panel1}
+These same insights can also be gained by comparing this figure with Figure~\ref{fig:ch2:panel2}.}
+\label{fig:ch2:panel1}
 \end{figure*}
@@
 \includegraphics[width=0.99\linewidth]{figures/ch2/DD0160_fiducial_shortrad_nort}
-\caption{Same as Figure~\ref{fig:panel1}, but at 40~Myr.}
-\label{fig:panel2}
+\caption{Same as Figure~\ref{fig:ch2:panel1}, but at 40~Myr.}
+\label{fig:ch2:panel2}
 \end{figure*}
 
-Figure~\ref{fig:panel1}, at 17~Myr, compares each simulation just after the first few SNe.
+Figure~\ref{fig:ch2:panel1}, at 17~Myr, compares each simulation just after the first few SNe.
 Already there are significant differences between the runs.
@@
 Although the ISM properties within the HII region in each case are quite similar between the simulations, the SNe that eventually go off in this region are confined by the neutral gas in the shortrad simulation, but readily escape through the lower density ionized gas into the galaxy halo in our fiducial case.
-As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe, as shown in  Figure~\ref{fig:panel2}, which shows each simulation 40~Myr after the formation of the first stars.
+As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe, as shown in  Figure~\ref{fig:ch2:panel2}, which shows each simulation 40~Myr after the formation of the first stars.
 In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas.
@@
 
-As shown in Figure~\ref{fig:metal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy.
+As shown in Figure~\ref{fig:ch2:metal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy.
 The winds in our fiducial simulation carry nearly all of the metals produced out from the disk of our galaxy.
@@
 
-\section{Conclusion}  \label{sec:conclusion}
+\section{Conclusion}  \label{ch2:sec:conclusion}
 In agreement with previous work we find that (local) stellar radiation feedback is effective in regulating star formation, but that non-local ionizing radiation is key for driving outflows in our simulations of an isolated, low mass, dwarf galaxy.

### 2019-03-14 thesis/chapters/ch_introduction.tex
Updates throughotu intro. onez models. metals intro. jargon intro.

@@
 
-One of the most common ways to model and understand the stellar populations of galaxies in high-dimensional chemical space is through simplified one-zone (or many-zone) models.
-This treatment extends back to XXX, where galaxies were treated as closed-box systems of gas and stars with simple approximations such as the instantaneous recycling of metal yields from massive stars and homogenous mixing.
+%
+% 
+%
+\textbf{Not quite sure if onez models should be its own section:} One of the most common ways to model and understand the stellar populations of galaxies in high-dimensional chemical space is through simplified one-zone (or many-zone) models.
+This treatment extends back many decades \citep[e.g.][]{Schmidt1963,TalbotArnett1971,Lynden-Bell1975}, where galaxies and their total metal abundance were treated as closed-box systems of gas and stars.
+Over the interveaning decades these models have improved, including perscriptions for gas outflow (a ``leaky-box") or gas inflow (``accreting box"), or both (a ``bathtub" model, e.g.
+\cite{FinlatorDave2008,Bouche2010}).
+The assumptions that go into these models vary dramatically with complexity.
+Simple models can assume, for example, that long-lived low mass stars do not contribute to metal enrichment while metals from massive stars are instantaneously recylced into the galaxy's gas reservoir (i.e.
+ignoring stellar lifetimes) or that all metals mix instantly and homogenously.
+More complex models .
+
+Regardless of the assumptions that go into these models, they are powerful tools used
+
+ with simple approximations such as the instantaneous recycling of metal yields from massive stars and homogenous mixing.
 While simple, these models have been used extensively to explain the mean evolution of stars in chemical space in individual galaxies.
@@
 Mention study of dwarf galaxies instead of MW first as way to simulate physics in detail and build up undserstanding to more massive regimes. Lead into physics that is important below.
-
-\section{Observations of Local Group Dwarf Galaxies}
-
-\subsection{Metals in Local Group Dwarfs}
-
-Until recently, the study of chemical evolution in Local Group dwarf galaxies has focused predominantly on the stellar component.
-This is due in large part because, though dwarf galaxies have higher gas fractions than more massive galaxies \citep{Geha2006}, many of these galaxies have undergone environmental stripping processes, rendering them devoid of a measurable gas component \citep{GrcevichPutman2009}.
-
-% mention difficulties of measuring gas phase abundances in dwarf galaxies?
-
-\subsubsection{Galactic Winds: Metal Retention / Ejection}
-
-Stellar feedback drives outflows, galactic winds, from galaxies across all scales (references).
-Dwarf galaxies in particular, with their relatively shallow potential wells, drive effective galactic winds, with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) ranging from XXX to XXX (cite, muratov etc.).
-How exactly stellar feedback couples to the ISM to drive these stellar winds is still uncertain, and is the topic of substantial ongoing research, but effective winds
 
@@
 This discussion includes a very brief overview of hydrodynamics and the numerical methods used in this work in Section~\ref{intro:sec:hydrodynamics}, nucleosynthesis and stellar evolution in Section~\ref{intro:sec:nucleosynthesis}, star formation and star particles in Section~\ref{intro:sec:sf} and Section~\ref{intro:sec:stars},
+
+But first, we note that Astronomy jargon is full of idiosyncrisies.
+As metioned before, the word ``chemical" in the ``galactic chemical evolution" is a bit of a misnomer.
+This is commonly applied simply to refer to studies interested in the evolution of metal abundances (either as a whole, or for individual isotopes) in galaxies over time, and less often to the astrochemistry that those elements may participate in.
+Likewise, ``metals" refers broadly to every element except H and He.
+Throughout this dissertation we often refer to the metallicity ($Z$) of a galaxy, its gas, or its stars.
+This quantity represents the total mass fraction of all metals -- and is computed as such in our simulations -- but we note that this is impossible to measure the abundances of all metals in astrophysical contexts outside our own Solar System.
+The metallicity of our own Sun ($Z_{\odot}$), for example, is still uncertain \citep{Asplund2009}.
+Instead, most observational works adopt Fe as a proxy for total metallicity in stars (due to its many, strong absorption lines) and O as a proxy in gas abundances (as it is the most abundant metal in the Universe and has convenient, strong emisson lines).
+These metallicity proxies are commonly reported in some form of normalized abundance ratio.
+For stellar metallicities, this is given in the form [A/B], where [A/B] = log($N_A / N_B$) - log($N_A / N_B$)$_{\odot}$, and $N$ refers to the number of atoms of a given element (usually as [Fe/H]).
+Confusingly, gas-phase abundances are commonly reported as just log($N_A / N_B$), often with the somewhat arbitrary normalization of 12, or log(O/H) + 12, for example.
 
@@
 \subsection{Nucleosynthesis and Stellar Evolution} \label{intro:sec:nucleosynthesis}
-
-Cover (briefly) each enrichment source and dominant production elements.
-
-% maybe a section on our own galaxy
-
-%\subsection{Star Formation and Stellar Feedback}\label{intro:sec:sffb}
-%
-%As elements are synthesized throughout stellar evolution, any framework for modelling galactic evolution requires an understanding of both where, how, and with what properties stars form in a galaxy.
 
@@
 The first models which included supernova feedback lacked the spatial / mass resolution to resolve individual (or even collective) SN events.
-This is the source of the commonly known ``overcooling" problem, whereby too little energy is injected into too much mass such that the affected region only reaches modest temperatures ($T \lessim 10^5$~K, as opposed to $T > 10^7$~K, or so).
+This is the source of the commonly known ``overcooling" problem, whereby too little energy is injected into too much mass such that the affected region only reaches modest temperatures ($T \lesssim 10^5$~K, as opposed to $T > 10^7$~K, or so).
 This temperature is right around the peak of the cooling curve, and thus the energy is rapidly radiated away before the injected energy has any time to make a significant dynamical impact of the galaxy.
@@
 It is thus likely subdominant to radiation feedback.}
+
+\section{Observations of Local Group Dwarf Galaxies}
+
+\subsection{Metals in Local Group Dwarfs}
+
+Until recently, the study of chemical evolution in Local Group dwarf galaxies has focused predominantly on the stellar component.
+This is due in large part because, though dwarf galaxies have higher gas fractions than more massive galaxies \citep{Geha2006}, many of these galaxies have undergone environmental stripping processes, rendering them devoid of a measurable gas component \citep{GrcevichPutman2009}.
+
+% mention difficulties of measuring gas phase abundances in dwarf galaxies?
+
+\subsection{Metals in the ISM and CGM of Dwarf Galaxies}
+
+The proximity of Milky Way dwarf galaxy satellites allows us to make some of the most detailed extragalactic stellar abundances measurements.
+
+Stellar feedback drives outflows, galactic winds, from galaxies across all scales (references).
+Dwarf galaxies in particular, with their relatively shallow potential wells, drive effective galactic winds, with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) ranging from XXX to XXX (cite, muratov etc.).
+How exactly stellar feedback couples to the ISM to drive these stellar winds is still uncertain, and is the topic of substantial ongoing research, but effective winds
+
+\subsection{Leo P: A Case Study}
+
+We dedicate this section to a specific Local Group dwarf galaxy, Leo P, as its observed properties motivate the initial conditions of the simulations developed in this dissertation.
+This galaxy is remarkable for being one of the lowest mass dwarf galaxies with observed, ongoing star formation.
+It is located at a distance of $\sim$ XXX (cite), and was first discovered in HI (cite).
+Since then, multiple studies have examined its star formation history (cite), gas phase metal abundance as traced through emission in an HII region (cite), stellar abundances (cite), and, most recently, resolved spectroscopy of both the gas and stars
+
 %

### 2019-03-14 thesis/chapters/ch_introduction.tex
final edits for the day. DJD is here

@@
 ignoring stellar lifetimes) or that all metals mix instantly and homogenously.
-More complex models .
-
-Regardless of the assumptions that go into these models, they are powerful tools used
-
- with simple approximations such as the instantaneous recycling of metal yields from massive stars and homogenous mixing.
-While simple, these models have been used extensively to explain the mean evolution of stars in chemical space in individual galaxies.
-
-Mention simulations here somewhere (a la naab and ostriker)
+More complex models account for individual stellar lifetimes (to some degree), or may try and account for some aspects of inhomogenous mixing by constructing mulit-zone models that may separate a galaxy in radial bins (with or without mixing between bins), may account for a hot and cold component separately, with mixing between the two, or account for separate ISM and CGM components.
+The output of these models is typically the mean metal abundance evolution within each of the tracked components.
+There is generally no self-consistent perscription to account for the scatter in any abundance relationship in these models, which, when needed, is often added ad-hoc in post-processing.
+Regardless of the assumptions that go into these models, they are powerful tools that can be used to probe the general physical processes that govern galactic chemical evolution, and explore the vast, uncertain parameter space associated with the models that characterize these processes \citep[e.g.][]{Cote2017a}.
 
@@
 textbook), and focusing on the former gives a much more accurate represenation of the actual work done for this dissertation.
-This discussion includes a very brief overview of hydrodynamics and the numerical methods used in this work in Section~\ref{intro:sec:hydrodynamics}, nucleosynthesis and stellar evolution in Section~\ref{intro:sec:nucleosynthesis}, star formation and star particles in Section~\ref{intro:sec:sf} and Section~\ref{intro:sec:stars},
+This discussion includes a very brief overview of hydrodynamics and the numerical methods used in this work in Section~\ref{intro:sec:hydrodynamics}, nucleosynthesis and stellar evolution in Section~\ref{intro:sec:nucleosynthesis}, radiative cooling and chemistry (actual chemistry) in Section~\ref{intro:sec:cooling}, star formation and star particles in Section~\ref{intro:sec:sf} and Section~\ref{intro:sec:stars}, and stellar feedback in Section~\ref{intro:sec:feedback}.
 
@@
 For stellar metallicities, this is given in the form [A/B], where [A/B] = log($N_A / N_B$) - log($N_A / N_B$)$_{\odot}$, and $N$ refers to the number of atoms of a given element (usually as [Fe/H]).
-Confusingly, gas-phase abundances are commonly reported as just log($N_A / N_B$), often with the somewhat arbitrary normalization of 12, or log(O/H) + 12, for example.
+Confusingly, gas-phase abundances are commonly reported as just log($N_A / N_B$), often with the somewhat arbitrary normalization of 12, or log(O/H) + 12, for example.\footnote{And I am not going to mention issues in normalizatiion across methods of deriving these abundances...
+\citep[e.g.][]{KewleyEllison2008}.}
 
@@
 \subsection{Nucleosynthesis and Stellar Evolution} \label{intro:sec:nucleosynthesis}
+
+\subsection{Radiative Processes and Chemistry}
+\label{intro:sec:cooling}
+
+Radiative processes are of fundamental importance in properly modelling the diversity of density, temperature, and ionization states in a multi-phase ISM.
+It is via radiative cooling that gas, heated by gravitational accretion onto dark matter halos, can cool, condense, become self-gravitating, and (eventually) collapse to form stars.
+Conversly heating, via radiative absorption or scatterings, from stellar sources within galaxies and the extragalactic sources that comprises the cosmic UV background (UVB, e.g.
+\cite{HM2001,HM2012,FG2011}).
 

### 2019-03-15 thesis/chapters/ch_introduction.tex
update to onezone section and Leo P section

@@
 
-%
-% 
-%
-\textbf{Not quite sure if onez models should be its own section:} One of the most common ways to model and understand the stellar populations of galaxies in high-dimensional chemical space is through simplified one-zone (or many-zone) models.
-This treatment extends back many decades \citep[e.g.][]{Schmidt1963,TalbotArnett1971,Lynden-Bell1975}, where galaxies and their total metal abundance were treated as closed-box systems of gas and stars.
-Over the interveaning decades these models have improved, including perscriptions for gas outflow (a ``leaky-box") or gas inflow (``accreting box"), or both (a ``bathtub" model, e.g.
-\cite{FinlatorDave2008,Bouche2010}).
-The assumptions that go into these models vary dramatically with complexity.
-Simple models can assume, for example, that long-lived low mass stars do not contribute to metal enrichment while metals from massive stars are instantaneously recylced into the galaxy's gas reservoir (i.e.
-ignoring stellar lifetimes) or that all metals mix instantly and homogenously.
-More complex models account for individual stellar lifetimes (to some degree), or may try and account for some aspects of inhomogenous mixing by constructing mulit-zone models that may separate a galaxy in radial bins (with or without mixing between bins), may account for a hot and cold component separately, with mixing between the two, or account for separate ISM and CGM components.
-The output of these models is typically the mean metal abundance evolution within each of the tracked components.
-There is generally no self-consistent perscription to account for the scatter in any abundance relationship in these models, which, when needed, is often added ad-hoc in post-processing.
-Regardless of the assumptions that go into these models, they are powerful tools that can be used to probe the general physical processes that govern galactic chemical evolution, and explore the vast, uncertain parameter space associated with the models that characterize these processes \citep[e.g.][]{Cote2017a}.
-
 Mention study of dwarf galaxies instead of MW first as way to simulate physics in detail and build up undserstanding to more massive regimes. Lead into physics that is important below.
@@
 \section{Ingredients of Galactic Chemical Evolution}
+\label{intro:sec:ingredients}
 
@@
 This galaxy is remarkable for being one of the lowest mass dwarf galaxies with observed, ongoing star formation.
-It is located at a distance of $\sim$ XXX (cite), and was first discovered in HI (cite).
-Since then, multiple studies have examined its star formation history (cite), gas phase metal abundance as traced through emission in an HII region (cite), stellar abundances (cite), and, most recently, resolved spectroscopy of both the gas and stars
+It is located at a distance of $1.62\pm 0.15$~Mpc \citep{McQuinn2015a}, and was first characterized as part of the ALFALFA survey \citep{Giovanelli2013,Rhode2013,Skillman2013,McQuinn2013,Bernstein-Cooper2014}.
+These studies have characterized its star formation history as low and roughly continuous over the age of the Universe (value, cite), its stellar mass ($M_{*} = 5.7 \times 10^{5}$~M$_{\odot}$, \cite{McQuinn2013}), its HI and dynamical mass ($M_{\rm HI}(r<r_{\rm HI}) = 9.5\times 10^{5}$~M$_{\odot}$, $M_{\rm dyn}(r<r_{\rm HI}) = 2.6 \times 10^{7}$~M$_{\odot}$, $r_{\rm HI} = $, \cite{Bernstein-Cooper2014}), and gas-phase abundances from an HII region (12 + log(O/H) = 7.17$\pm$0.04 \cite{Skillman2013}).
+Finally, we chose to focus on a Leo P like galaxy in our simulations in part to allow for comparisons to the work in \cite{McQuinn2015}, which makes an accounting of the total metals (as traced by O) contained in the ISM and stars in Leo P, estimating the fraction that must have been ejected over the lifetime of the galaxy.
+This is an important measurement as prior estaimtes of this number for low mass dwarf galaxies were restricted to Milky Way dSph's, which are devoid of gas and contaminated by environmental affects.
+As of this writing, Leo P is one of the only low mass dwarf galaxies with both gas-phase and stellar metal abundance measurements, but there is ongoing work to greatly expand this sample in the near future.
 
-%
-%
-%
-%\section{Semi-Analytic Models / One-zone Models}
-%
-%Definitely have a lot here. Motivate need for better understanding of mixing processes in galaxies. \citep{SchonrichWeinberg2019}
-%
-%
+\section{Onezone Models of Galactic Chemical Evolution}
+\label{intro:sec:onezone}
+
+This dissertation utilizes high-resolution hydrodynamics simulations that are expensive to run in both walltime ($\sim$ weeks to months) and computational time ($\sim 10^{5-6}$ CPU hours).
+For this reason,
+
+ One of the most common ways to model and understand the stellar populations of galaxies in high-dimensional chemical space is through simplified one-zone (or many-zone) models.
+This treatment extends back many decades \citep[e.g.][]{Schmidt1963,TalbotArnett1971,Lynden-Bell1975}, where galaxies and their total metal abundance were treated as closed-box systems of gas and stars.
+Over the interveaning decades these models have improved, including perscriptions for gas outflow (a ``leaky-box") or gas inflow (``accreting box"), or both (a ``bathtub" model, e.g.
+\cite{FinlatorDave2008,Bouche2010}).
+The assumptions that go into these models vary dramatically with complexity.
+Simple models can assume, for example, that long-lived low mass stars do not contribute to metal enrichment while metals from massive stars are instantaneously recylced into the galaxy's gas reservoir (i.e.
+ignoring stellar lifetimes) or that all metals mix instantly and homogenously.
+More complex models account for individual stellar lifetimes (to some degree), or may try and account for some aspects of inhomogenous mixing by constructing mulit-zone models that may separate a galaxy in radial bins (with or without mixing between bins), may account for a hot and cold component separately, with mixing between the two, or account for separate ISM and CGM components.
+The output of these models is typically the mean metal abundance evolution within each of the tracked components.
+There is generally no self-consistent perscription to account for the scatter in any abundance relationship in these models, which, when needed, is often added ad-hoc in post-processing.
+Regardless of the assumptions that go into these models, they are powerful tools that can be used to probe the general physical processes that govern galactic chemical evolution, and explore the vast, uncertain parameter space associated with the models that characterize these processes \citep[e.g.][]{Cote2017a}.
+
+One final motivation of this dissertation is to improve the assumptions within these models by better charaterizing the process of inhomogenous mixing in the ISM, and the coupling of metals to galactic winds and outflows.
+This is particularly important if the behavior differs between elements from different nucleosynthetic sites.
+In addition, this work could be used to account for the spread and higher-order statistics of stellar abundance distributions, which would be a powerful tool for better leveraging the wealth of observations in the Milky Way and Local Group.
+Yet, as discussed, the current state of the art perscriptions for these processes are ad-hoc, lacking physical motivation.
+Recent analytic work in \cite{KrumholzTing2018} lays down a framework to evaluate the correlation between individual metals in different galactic environments and predicts that the correlations will differ for different nucleosynthetic sites (e.g.
+AGB winds vs.
+SNe).
+We characterize these differences in detail in Chapter~\ref{ch:chapter3}, laying the groundwork for how one could potentially incorporate this insight into improving these models.
+We build upong this idea more in Chapter~\ref{ch:chapter4}, and plan to explore the connection between our simulations and analytic models in the future.
+Recent work by \cite{SchonrichWeinberg2019} is a great example of how this could greatly impact current models for galactic chemical evolution.
+They how adopting a two-phase onezone model (hot and cold ISM), along with parameters for how metals are injected and mix between the phases whose values differ depending on nucleosynthetic origin of the metal, can reconcile long-standing problems in understanding the r-process abundance evolution of stars in the Milky Way.
+And in fact, they argue that it would be impossible to reproduce observed r-process abundances in the Milky Way (namely [Eu/Fe], [Eu/Si], and [Eu/Mg] as functions of [Fe/H]) with a standard one-phase model.
 

### 2019-03-15 thesis/chapters/ch_introduction.tex
updates

@@
 
+We are motivated by using a properly formed model for galactic chemical evolution in dwarf galaxies to interpret and explain observations of Local Group dwarfs.
+As any good theoretical work should maintain a close connection to the observations that motivate the study in the first place in order to better make predictions for future observations, we devote some time here to summarize relevant observations of Local Group dwarfs.
+
+\subsection{Milky Way and Local Group Dwarf Galaxies}
+
+The Milky Way and its local environment is host to a diverse collection of dwarf galaxies.
+The properties of these galaxies have been nicely summarized in a recent review \citep{Tolstoy2009}, and again in \cite{McConnachie2012}.
+However, the number of known Local Group dwarf galaxies has increased dramatically since that time, particularly for the Milky Way, whose known satellite population has more than doubled.
+This is due in large part to tremendous improvements in our ability to detect galaxies on the faintest end of the luminosity function, called ultrafaint galaxies (UFDs, \cite{Willman2005}).\footnote{See \cite{Simon2019} for a recent review}.
+The Dark Energy Survey \citep[e.g.][]{Drlica-Wagner2015} and Hyper Supbrime-Cam \citep[e.g.][]{Greco2018} have made tremendous advances to this end, with the upcoming Large Synoptic Survey Telescope producing an even greater increase in the known population of faint galaxies in the Local Group \citep{Haynes2019,Weisz2019}.
+
+While there is no real sharp transition where a galaxy is considered a ``dwarf" galaxy, historical definitions are based on luminosity, using the SMC and LMC as rough anchor points for the upper-end of the dwarf galaxy scale.
+\cite{Bullock2017} suggests a deliniation based on stellar mass.
+For this dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M_${\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.
+
 \subsection{Metals in Local Group Dwarfs}
@@
 It is located at a distance of $1.62\pm 0.15$~Mpc \citep{McQuinn2015a}, and was first characterized as part of the ALFALFA survey \citep{Giovanelli2013,Rhode2013,Skillman2013,McQuinn2013,Bernstein-Cooper2014}.
-These studies have characterized its star formation history as low and roughly continuous over the age of the Universe (value, cite), its stellar mass ($M_{*} = 5.7 \times 10^{5}$~M$_{\odot}$, \cite{McQuinn2013}), its HI and dynamical mass ($M_{\rm HI}(r<r_{\rm HI}) = 9.5\times 10^{5}$~M$_{\odot}$, $M_{\rm dyn}(r<r_{\rm HI}) = 2.6 \times 10^{7}$~M$_{\odot}$, $r_{\rm HI} = $, \cite{Bernstein-Cooper2014}), and gas-phase abundances from an HII region (12 + log(O/H) = 7.17$\pm$0.04 \cite{Skillman2013}).
+These studies have characterized its star formation history as low and roughly continuous over the age of the Universe (SFR = $4.3\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$, \cite{McQuinn2015a}), its stellar mass ($M_{*} = 5.7 \times 10^{5}$~M$_{\odot}$, \cite{McQuinn2013}), its HI and dynamical mass ($M_{\rm HI}(r<r_{\rm HI}) = 9.5\times 10^{5}$~M$_{\odot}$, $M_{\rm dyn}(r<r_{\rm HI}) = 2.6 \times 10^{7}$~M$_{\odot}$, $r_{\rm HI} \sim 500$~pc, \cite{Bernstein-Cooper2014}), and gas-phase abundances from an HII region (12 + log(O/H) = 7.17$\pm$0.04 \cite{Skillman2013}).
 Finally, we chose to focus on a Leo P like galaxy in our simulations in part to allow for comparisons to the work in \cite{McQuinn2015}, which makes an accounting of the total metals (as traced by O) contained in the ISM and stars in Leo P, estimating the fraction that must have been ejected over the lifetime of the galaxy.

### 2019-03-17 thesis/chapters/ch_introduction.tex
typo fix

@@
 \cite{Bullock2017} suggests a deliniation based on stellar mass.
-For this dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M_${\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.
+For this dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M$_{\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.
 

### 2019-03-17 thesis/chapters/ch_introduction.tex
rewording in opening intro

@@
 Galaxies are amalgamations of gas and stars embedded in dark matter halos, formed over cosmic time as the products of the hierarchical assembly that follows from the collapse of primordial density fluctuations that arose after the Big Bang.
-The gravitational pull of dark matter controls the growth of structure in the Universe which, as is predicted from $\Lambda$CDM cosmology, TEXT HERE.
-While, broadly speaking, the evolution of baryons is dominated by the gravitational pull of dark matter, the beautiful simplicity of the evolution of dark matter and $\Lambda$CDM is muddied by their existence.
-The complexities of hydrodynamics, magnetohydrodynamics, thermodynamics, chemistry, radiative processes, and nucleosynthesis -- or, ``astrophysics" for short -- drives these deviations and gives rise to the Universe that we observe and interact with and -- not least of all -- us.
+The gravitational pull of dark matter -- as predicted from $\Lambda$CDM cosmology -- controls the hierarchical growth of structure in the Universe.
+While, broadly speaking, the evolution of baryons is dominated by the gravitational pull of dark matter, the beautiful simplicity of $\Lambda$CDM cosmology is muddied by their existence.
+The complexities of hydrodynamics, magnetohydrodynamics, thermodynamics, chemistry, radiative processes, and nucleosynthesis -- or, ``astrophysics" for short -- drives these deviations and gives rise to the Universe that we observe and -- not least of all -- us.
 In spite of a concerted effort spanning nearly a century, we are far from a self-consistent theory of galaxy evolution \citep[see ][ for a recent review of outstanding problems in galactic evolution]{NaabOstriker2017}.
@@
 Much work has been done in studying the global metallicity evolution of galaxies through the mass-metallicity relationship \citep[e.g.][]{Lequeux1979,Tremonti2004,Lee2006,Zahid2012}, the metallicity gradient in our own and nearby galaxies \citep[e.g.][]{}, and detailed stellar abundances in galaxies with spectroscopically resolved stellar populations \citep[e.g.][]{}.
+Yet in spite of increased number and quality of observations of galactic chemical evolution, developing a complete model is still a daunting task.
 
 %Developing a complete model for galactic chemical evolution is a daunting task.
-Here is a recipe for constructing a complete model of galactic chemical evolution as it is understood today.
-One begins first with the simple step of nailing down a complete model of stellar structure, stellar evolution, and learning from nuclear physicists the reaction rates of every nuclear reaction and lifetimes of individual isotopes.
-One must then perscribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas into the disk of the galaxy, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos.
+To give an impression of the difficulties involved, here is a recipe for constructing a complete model of galactic chemical evolution.
+One must first perscribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas into the disk of the galaxy, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos.
 One can then worry about knowing where, how, and with what masses stars form in the first place from this gas, which requires understanding the hydrodynamic
@@
 This in turn requires one to toss in a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and supernovae -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies.
-Once this is understood, one can then color in the gas in the galaxy over time with the individual metal yields of stellar populations released over their lifetime.
+Simultaneously, one makes the simple step of nailing down a complete model of stellar structure, stellar evolution, the reaction rates and cross sections of every nuclear reaction, and the lifetimes of individual isotopes.
+Once all of this is understood, one can then color in the gas in the galaxy over time with the individual metal yields of stellar populations released over their lifetime.
 With a complete understanding of stellar feedback and the ISM, one can then be sure that they completely capture the mixing of these metals in the ISM over time, and will produce a stellar population with accurate metal abundance ratios.
@@
 Substantial work has been made recently to determine the efficacy of this approach \citep[e.g.][]{Armillotta2018}, yet the physical processes that give rise to stellar abundances as we observe them today are still uncertain.
-The excitement at the availability of this data does not even mention
 
-Mention study of dwarf galaxies instead of MW first as way to simulate physics in detail and build up undserstanding to more massive regimes. Lead into physics that is important below.
+Dwarf galaxies have been called the building blocks of the Universe, and represent some of the best laboratories to study the fundamental physics of galactic evolution.
+From a theoretical perspective, their small physical size, relatively quiet accretion history, and low star formation rates make simulating their evolution in detail at high resolution substantially less computationally intensive than more massive galaxies like the Milky Way.
+
+\textit{Mention study of dwarf galaxies instead of MW first as way to simulate physics in detail and build up undserstanding to more massive regimes. Lead into physics that is important below.}
 
@@
 \section{Observations of Local Group Dwarf Galaxies}
+\label{intro:sec:LG dwarfs}
 
@@
 
-\subsection{Milky Way and Local Group Dwarf Galaxies}
+\subsection{Known Dwarf Galaxies of the Local Group}
 

### 2019-03-18 thesis/chapters/ch_introduction.tex
Thesis intro updates

@@
 From a theoretical perspective, their small physical size, relatively quiet accretion history, and low star formation rates make simulating their evolution in detail at high resolution substantially less computationally intensive than more massive galaxies like the Milky Way.
+Although their lower brightness limits the number of dwarf galaxies that we can observe, the abundance and relative proximity of dwarf galaxies in the Local Group allows for a significant sample of galaxies with resolved stellar populations.
+Observations of these resolved stellar populations can be used to derive detailed star formation histories and chemical abundances that can be used together to test our theoretical understanding of galactic chemical evolution in a variety of contexts.
 
-\textit{Mention study of dwarf galaxies instead of MW first as way to simulate physics in detail and build up undserstanding to more massive regimes. Lead into physics that is important below.}
+\textbf{need final par}
 
@@
 
-\subsection{Nucleosynthesis and Stellar Evolution} \label{intro:sec:nucleosynthesis}
+\subsection{Nucleosynthesis} \label{intro:sec:nucleosynthesis}
 
@@
 For this dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M$_{\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.
+In general, dwarf galaxies are extremely dark matter dominated, with mass to light ratios over 10$^2$, \citep{SimonGeha2007,Strigari2009,Wolf2010}, convert gas into stars at a lower efficiency than more massive galaxies (cite), and, for the lowest mass dwarf galaxies, exhibit bursty star formation histories driven by stochasticity in the process of both star formation and the effects of stellar feedback (cite).
 
@@
 
-Until recently, the study of chemical evolution in Local Group dwarf galaxies has focused predominantly on the stellar component.
-This is due in large part because, though dwarf galaxies have higher gas fractions than more massive galaxies \citep{Geha2006}, many of these galaxies have undergone environmental stripping processes, rendering them devoid of a measurable gas component \citep{GrcevichPutman2009}.
-
-% mention difficulties of measuring gas phase abundances in dwarf galaxies?
-
-\subsection{Metals in the ISM and CGM of Dwarf Galaxies}
-
-The proximity of Milky Way dwarf galaxy satellites allows us to make some of the most detailed extragalactic stellar abundances measurements.
+The first studies of stellar abundances in the Local Group focused on stars in nearby dSph's, and massive stars in the LMC, SMC, and similar, more massive dwarf galaxies \citep[e.g.][]{}.
+These studies typically obtained abundances for only a small sample ($\sim$ 10) stars, limiting the extent to which they can be used to test models of galacitc chemical evolution.
+However, the advent of high-resolution spectrographs at both Keck and the Very Large Telescope -- capable of obtaining the spectra of many stars with a single pointing -- have dramatically increased the sample size of stellar abundances in nearby dwarf galaxies \citep[e.g.][]{}.
 
 Stellar feedback drives outflows, galactic winds, from galaxies across all scales (references).
-Dwarf galaxies in particular, with their relatively shallow potential wells, drive effective galactic winds, with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) ranging from XXX to XXX (cite, muratov etc.).
-How exactly stellar feedback couples to the ISM to drive these stellar winds is still uncertain, and is the topic of substantial ongoing research, but effective winds
+Dwarf galaxies in particular, with their relatively shallow potential wells, are expected to drive effective galactic winds \citep{MacLowFerrara1999} with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) above XXX \citep{Muratov2015,Christensen2018}.
+Not only does this correspond to a significant amount of mass outflow from these galaxies, but these winds should also carry out a substantial amount of metals from these galaxies.
+\cite{Kirby2011-metals} used measurements of the stellar abundances in Local Group dSph's and their resolved star formation histories to determine that their stars contain less than 5\% of the metals synthesized in each galaxy.
+However, since these galaxies have lost their gas through environmental processes as satellites of the Milky Way (ram pressure and tidal stripping), it was unclear if this loss could be attributed entirely to feedback.
+However, using gas and stellar abundances \cite{McQuinn2015} showed that Leo P -- a gas-rich Local Group dwarf galaxy -- has also ejected $\sim$95\% of its metals.
+This is significant evidence for metal-enriched, feedback-driven galactic winds operating in these low mass dwarf galaxies.
+
+Finally, the low metallicities of the lowest mass dwarf galaxies make them ideal places to better constrain large uncertainties in stellar nucleosynthesis \citep{FrebelNorris2015,Frebel2018}.
+At these low metallicities, the number of possible enrichment events that could have possibly contributed to the observed stellar abundances decreases significantly, increasing the possibility of using these abundance patterns to constrain the yields of individual sources.
+This is particularly true for exotic enrichment events, like those expected to be significant sources of r-process elements, which are potentially so rare that only one or fewer events would be expected in an individual low-mass galaxy.
+
+The most prominant example of these types of studies has been of the UFD Reticulum II, where \cite{Ji2016} used the extreme r-process enhancement in its stars to argue in favor of a neutron star -  neutron star origin for the enrichment.
+This conclusion has been supported by observations in additional Local Group dwarf galaxies \citep{Duggan2018}, but there is still some disagreement as to this conclusion \citep[e.g.][]{Siegel2018}.
+Interestingly, the lack of these extreme r-process abundances in other UFDs suggests that another source of r-process must exist \citep{Ji2016b}.
+Some of the significant uncertainties in interpreting these observations lie with understanding how r-process elements mix within the ISM and are ejected from low mass dwarf galaxies.
+Recent research has examined how metals from individual enrichement events may mix and evolve in a variety of contexts \citep[e.g.][]{Bland-Hawthorn2015,Ritter2015,Montes2016,Safarzadeh2017}, but there is still much to be understood about this process.
+In particular, there is still much to be gained from adapting insights from these types of simulations to the modelling used to interpret observations of stellar abundances (as discussed in more detail in Section~\ref{intro:sec:onezone}).
 
 \subsection{Leo P: A Case Study}
+
+\textbf{Include a figure? Maybe from recent spectra paper? Or HI from ALFALFA? or both?}
 

### 2019-03-18 thesis/chapters/ch_introduction.tex
Updates to nucleosynthesis section

@@
 \subsection{Nucleosynthesis} \label{intro:sec:nucleosynthesis}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.75\linewidth]{./figures/intro/periodic_table}
+  \caption{The periodic table of elements colored by the relative fraction of the nucleosynthetic processes that naturally occur in the Universe that produce each element.
+\textbf{Image Credit:} A modified version of the table created by Anna Frebel (\url{https://www.dropbox.com/sh/ib3agt2bkxqqk2u/AACbEw1warp74qzUh2AcWqfja?dl=0}), accessed on 03-18-19.}
+\end{figure}
+
+A variety of nucleosynthetic processes occur within stars and during their deaths that lead to the production of all of the elements of the periodic table.
+This is illustrated well in Figure~\ref{intro:fig:periodic table}, which shows the periodic table colored by the fractional importance of the nucleosynthetic processes that create each element.
+Due to the diversity in production sources across the periodic table, multi-element metal abundance measurements in stars can be used to to better understand and constrain how and where each metal is produced.
+Exactly which reactions occur where depend strongly on the initial abundances of elements in stars, their stellar masses, and, for heavy nuclei, the neutron density.
+
+This means that elements from different nucleosynthetic channels are produced on different timescales during a galaxy's evolution, as set by the lifetimes of the stars in which they occur, and are released into the galaxy at different energies, with different spatial distributions within the galaxy, and at different rates.
+For example, O, an $\Alpha$-element is produced predominately in massive stars and is therefore released via core collapse supernovae on timescales of $\sim$~10~Myr after a star formation event, near their stellar birth sites.
+By contrast, Sr is produced predominately via the s-process (discussed more below) which occurs in the asymptotic giant branch (AGB) winds of lower mass stars ($M < 8$~M$_{\odot}$) at much lower energies and on timescales of $\sim 100$~Myr - $1$~Gyr.
+By this time, these stars would have diffused farther away from their birth sites, potentially sampling a qualitatively different portion of the ISM than earlier core collapse SNe.
+Generally the differences in how different timescales affect observed stellar abundances patterns are well understood and easily modelled.\footnote{The canonical example of this is the ``knee" feature in a $[\Alpha/$Fe] vs.
+[Fe/H] diagram, where the location of this knee signifies the point at which Type Ia enrichment (which produces significant Fe, but little to no $\Alpha$ elements) begins to have a significant contribution over core collapse SNe (rich in $\Alpha$ elements, but not Fe) \citep[e.g.[]{MatteucciBrocato1990, Geisler2005, Hill2018}.
+The location of this knee shifts in a galaxy depending on its SFH.} However, it is not well understood how differences in where and with what energies these events occur affect observed stellar abundance patterns.
+Investigating these differences is a key motivation of this dissertation.
+
+As relevant to this work, we briefly summarize a few of the important nucleosynthetic channels shown in Figure~\ref{intro:fig:periodic table} and their sites.
+$\Alpha$-elements, notably O, Mg, Si, Ca, and Ti, are produced during the lifetime of massive stars (O, Mg) or during the core collapse supernova explosion itself.
+In either case, these elements are
 

### 2019-03-18 thesis/chapters/ch_chapter3.tex
Finalized draft updates to nucleosynthesis section. Adding new references. Removing redundant references. Renaming Ji+2018 references

@@
 These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
-In particular, low mass dwarf galaxies with unusual (compared to Milky Way, solar abundances) r-process enrichment \citep[e.g.][]{Ji2016,Ji2018,Duggan2018}, are valuable for constraining the source of these elements, their frequency, and typical yields.
+In particular, low mass dwarf galaxies with unusual (compared to Milky Way, solar abundances) r-process enrichment \citep[e.g.][]{Ji2016,Ji2018b,Duggan2018}, are valuable for constraining the source of these elements, their frequency, and typical yields.
 The differential metal evolution presented in our work both opens up an additional avenue by which elements from distinct nucleosynthetic sources may be distinguished in observations and challenges current assumptions used in interpreting these observations.

### 2019-03-18 thesis/chapters/ch_introduction.tex
Finalized draft updates to nucleosynthesis section. Adding new references. Removing redundant references. Renaming Ji+2018 references

@@
 This means that elements from different nucleosynthetic channels are produced on different timescales during a galaxy's evolution, as set by the lifetimes of the stars in which they occur, and are released into the galaxy at different energies, with different spatial distributions within the galaxy, and at different rates.
-For example, O, an $\Alpha$-element is produced predominately in massive stars and is therefore released via core collapse supernovae on timescales of $\sim$~10~Myr after a star formation event, near their stellar birth sites.
+For example, O, an $\alpha$-element is produced predominately in massive stars and is therefore released via core collapse supernovae on timescales of $\sim$~10~Myr after a star formation event, near their stellar birth sites.
 By contrast, Sr is produced predominately via the s-process (discussed more below) which occurs in the asymptotic giant branch (AGB) winds of lower mass stars ($M < 8$~M$_{\odot}$) at much lower energies and on timescales of $\sim 100$~Myr - $1$~Gyr.
 By this time, these stars would have diffused farther away from their birth sites, potentially sampling a qualitatively different portion of the ISM than earlier core collapse SNe.
-Generally the differences in how different timescales affect observed stellar abundances patterns are well understood and easily modelled.\footnote{The canonical example of this is the ``knee" feature in a $[\Alpha/$Fe] vs.
-[Fe/H] diagram, where the location of this knee signifies the point at which Type Ia enrichment (which produces significant Fe, but little to no $\Alpha$ elements) begins to have a significant contribution over core collapse SNe (rich in $\Alpha$ elements, but not Fe) \citep[e.g.[]{MatteucciBrocato1990, Geisler2005, Hill2018}.
+Generally the differences in how different timescales affect observed stellar abundances patterns are well understood and easily modelled.\footnote{The canonical example of this is the ``knee" feature in a $[\alpha/$Fe] vs.
+[Fe/H] diagram, where the location of this knee signifies the point at which Type Ia enrichment (which produces significant Fe, but little to no $\alpha$ elements) begins to have a significant contribution over core collapse SNe (rich in $\alpha$ elements, but not Fe) \citep[e.g.[]{MatteucciBrocato1990, Geisler2005, Hill2018}.
 The location of this knee shifts in a galaxy depending on its SFH.} However, it is not well understood how differences in where and with what energies these events occur affect observed stellar abundance patterns.
@@
 As relevant to this work, we briefly summarize a few of the important nucleosynthetic channels shown in Figure~\ref{intro:fig:periodic table} and their sites.
-$\Alpha$-elements, notably O, Mg, Si, Ca, and Ti, are produced during the lifetime of massive stars (O, Mg) or during the core collapse supernova explosion itself.
-In either case, these elements are
+$\alpha$-elements, notably O, Mg, Si, Ca, and Ti, are produced during the lifetime of massive stars (O, Mg) or during the core collapse supernova explosion itself.
+In either case, these elements are synthesized through the capture of an $\alpha$ nucleus, progressing towards increasingly heavier nuclei in intervals of 4/2 in mass/atomic number (as $\alpha$ = $^{4}_2He$) from $^8_4Be$ to the stable $^{52}_{26}Fe$ and unstable $^{56}_{28}Ni$ (which days to $^{56}_{26}Fe$).
+The iron group elements, notably Fe, Mn, Co, and Ni, are produced predominately in Type Ia supernovae, with variations depending on a single vs.
+double degenerate scenario and the initial composition of exploding white dwarf(s) (WD).
+
+The presence of these heavier elements in stars enables the formation of even heavier nuclei through neutron capture.
+This is categorized into two processes, slow (or s-) and rapid (or r-) process.
+In the former, neutron densities are typically low enough that the product of each neutron capture beta decays to a more stable isotope before capturing another neucleon.
+In r-process, however, the rate of neutron capture exceeds beta decay, alowing for the production of different, typically heavier, nuclei.
+As shown in the diagram, ligher elements are produced via the s-process and heavier via the r-process, with notable overlap in certain elements, such as Ba.\footnote{For the sake of this discussion, the light neutron-capture primary process elemnts (sometimes referred to as ``lighter element primary process") should be considered s-process elements.
+This different nucleosynthetic channel, first identified in \cite{Travaglio2004}, arose from an apparent disagreement between models of s-process enrichment in galactic chemical evolution studies andnd abundances of elements including Sr, Y, and Zr.
+However there is still uncertainty as to whether or not these differences can be explained with different models of weak s-process (which can occur in the winds of massive stars) \citep[e.g.][]{Prantzos2018}.} The s-process occurs predominately in the low-energy winds of low mass (1-8 M$_{\odot}$) AGB stars on time scales of 100's of Myr up to 1 Gyr.
+Exactly which elements are produced in a given AGB star varies with stellar mass and depends strongly on metallicity, which determines the available heavy seed nuclei.
+Sr, Y, Zr, and Ba, as well as C, N and F, are commonly used as tracers of this nucleosynthetic channel.
+
+The dominant origin of r-process enrichment is highly uncertain, though possible channels include neutron star - neutron star and neutron star - black hole mergers, netrino driven winds in core collapse SNe, and exotic SNe, such as magnetic, jet-driven SNe, collapsars, hypernovae, and long-duration gamma-ray bursts \citep[see ][ for recent reviews]{Frebel2018, Cowan2019}.
+Eu is the most commonly used (and easy to observe) unambigious observational tracer of r-process enrichment; Ba is also often studied as a tracer, but requires care due to the significant contribution from s-process enricment.
+More detailed spectra \citep[e.g.][]{Ji2018a} can trace many more of these elements, which can be used as an important discriminator between nucleosynthetic models.
+
+Finally, although the production of elements unaffected by the r-process are comparatively well understood, there are still large uncertainties in both nuclear reaction rates and stellar evolution properties such that there is generally significant variations in yields for any given element between groups who compute nucleosynthetic yield tables.
 

### 2019-03-18 thesis/chapters/ch_introduction.tex
reformatting hydro equations and removing uneeded comment

@@
 \subsection{Hydrodynamics}
-\textit{(This will be a sub-section of something, but putting here for now as placeholder).}
-
 Astrophysical hydrodynamics simulations are first distinguished by the numerical methods employed to solve the Euler equations that describe the time ($t$) evolution of the energy density ($E$), density ($\rho$), pressure ($p$), and peculiar velocity ($\bm{v}$) of a fluid:
-\begin{equation}
-  \frac{\delta \rho}{\delta t} + \nabla \cdot \left(\rho \bm{v}\right)  = 0,\\
-  \frac{\delta \rho \bm{v}}{\delta t} + \nabla \cdot \left(\rho \bm{v}\bm{v} + \bm{I}p \right) = 0,\\
-  \frac{\delta E}{\delta t} + \nabla \cdot \left[\left(E +p\right)\bm{v}\right] = 0.
-\end{equation}
+\begin{align}
+  \frac{\delta \rho}{\delta t} + \nabla \cdot \left(\rho \bm{v}\right)  &= 0,\\
+  \frac{\delta \rho \bm{v}}{\delta t} + \nabla \cdot \left(\rho \bm{v}\bm{v} + \bm{I}p \right) &= 0,\\
+  \frac{\delta E}{\delta t} + \nabla \cdot \left[\left(E +p\right)\bm{v}\right] &= 0.
+\end{align}
 
@@
 Usually, simulators set these thresholds to fully encompass gas whose Jeans-length (and thus dynamical behavior) becomes unresolved according to the widely-used \cite{Truelove1997} criterion.
-Often, this means a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\div \bm{v} < 0$), that gas surpass some virial threshold \citep[e.g.][]{}, or that gas also meet a minimum $H_2$ mass fraction \citep[e.g.][]{}.
-One a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars.
+Often, this means a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\nabla \bm{v} < 0$), that gas surpass some virial threshold (describing how bound a cloud may be)
+%cite?, 
+or that gas meet a minimum $H_2$ mass fraction
+%\citep[e.g.][]{}
+.
+Once a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars.
 Briefly, some form of the following equation is usually adopted,

### 2019-03-18 thesis/chapters/ch_chapter1.tex
Finalizing draft of radiative cooling and heating section. Renaming references to better names and changing in chapters for consistency. New refs

@@
 We outline specific model choices made in our simulations and refer the reader to \citet{GrackleMethod} for a detailed discussion of the code.
-We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{2000ApJ...534..809O} and \citet{2005ApJ...626..627O} as included in \texttt{Grackle}.
+We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{Omukai2000} and \citet{Omukai2005} as included in \texttt{Grackle}.
 However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}.

### 2019-03-18 thesis/chapters/ch_introduction.tex
Finalizing draft of radiative cooling and heating section. Renaming references to better names and changing in chapters for consistency. New refs

@@
 While important, the latter is better reserved for a much more detailed work (i.e.
-textbook), and focusing on the former gives a much more accurate represenation of the actual work done for this dissertation.
+a textbook), and focusing on the former gives a much more accurate represenation of the actual work done for this dissertation.
 This discussion includes a very brief overview of hydrodynamics and the numerical methods used in this work in Section~\ref{intro:sec:hydrodynamics}, nucleosynthesis and stellar evolution in Section~\ref{intro:sec:nucleosynthesis}, radiative cooling and chemistry (actual chemistry) in Section~\ref{intro:sec:cooling}, star formation and star particles in Section~\ref{intro:sec:sf} and Section~\ref{intro:sec:stars}, and stellar feedback in Section~\ref{intro:sec:feedback}.
@@
 
-Finally, although the production of elements unaffected by the r-process are comparatively well understood, there are still large uncertainties in both nuclear reaction rates and stellar evolution properties such that there is generally significant variations in yields for any given element between groups who compute nucleosynthetic yield tables.
+Finally, although the production of elements unaffected by the r-process are comparatively well understood, there are still large uncertainties in both nuclear reaction rates and stellar evolution properties that affect the computed yields for any given element.
+As including self-consistent nuclear reactions in the interior of stars is nearly computationally impossible in galaxy-scale simulations, metal yields are generally included as averaged over an entire stellar population (see Section\ref{intro:sec:stars}) as determined from a tabulated set of yields.
+These uncertainties, however, mean there are often significant variations and inconsistencies between tables produced by separate groups, which can make some times make interpreting the results of galactic chemical evolution models challenging.
 
@@
 \cite{HM2001,HM2012,FG2011}).
+Tied to both of these processes is the actual chemistry that occurs in the ISM, from the primordial chemical reactions between H, He, and free electrons to substantially more complicated reactions that occur once significant amounts of metals are present in the ISM (particularly, C, O, and Si).
+These metals by themselves  act as additional radiative coolants, which strongly dictate the shape of the cooling curve which allows for a multi-phase medium in the first place \citep[e.g.][]{McKeeOstriker1977}.
+The molecules produced in chemical reactions with these metals produce additional coolants in the ISM \citep{HollenbackMcKee1979}, including dust, which has its own rich array of associated physical processes \citep{Omukai2000,Omukai2005}.
+
+A full, detailed model of radiative cooling, heating, non-equillibrium chemistry, and dust is generally far too computationally expensive to include in galaxy-scale simulations.
+For this reason, many large-scale cosmological simulations assume that all gas is optically thin and that all molecules and ionization states exist in equillibrium.
+This allows for the quick use of tabulated look-up tables for radiative cooling and heating, often produced using \code{CLOUDY} \citep{Cloudy2013}, that depend on gas density, temperature, metallicity, and redshift (which sets the UVB heating rate).
+More complex simulations often track some form of $< 10$ species primordial chemistry in order to better account for non-equillibrium effects and $H_2$ production, though with noted increases in memory requirements and computational cost.
+Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2015,Richings2018}; but these are typically prohibitively expensive to run on massive scales.
+In this dissertation we adopt the chemistry and radiative cooling and heating physics models availble in the newly developed, open-source library \code{GRACKLE} \citep{GrackleMethod}.
+The exact physics included in our simulations are discussed in greater detail in Chapter~\ref{ch:chapter1}, but we note that improvements to \code{GRACKLE} have been made as the direct result of the research conducted during this dissertation.
+%mention that I made improvements to this?
 

### 2019-03-18 thesis/chapters/ch_introduction.tex
New Figure for Leo P in introduction. cleaned up some bad figure labels and references. cleaned up some formatting

@@
 \newcommand{\code}{\textsc}
+\newcommand{\Hmolecular}{H$_2$}
+%\newcommand{\hii}{H\sc{I}}
+%\newcommand{\hii}{H{\sc{II}}}
 
@@
 \textbf{Image Credit:} A modified version of the table created by Anna Frebel (\url{https://www.dropbox.com/sh/ib3agt2bkxqqk2u/AACbEw1warp74qzUh2AcWqfja?dl=0}), accessed on 03-18-19.}
+  \label{intro:fig:periodic table}
 \end{figure}
@@
 $\alpha$-elements, notably O, Mg, Si, Ca, and Ti, are produced during the lifetime of massive stars (O, Mg) or during the core collapse supernova explosion itself.
-In either case, these elements are synthesized through the capture of an $\alpha$ nucleus, progressing towards increasingly heavier nuclei in intervals of 4/2 in mass/atomic number (as $\alpha$ = $^{4}_2He$) from $^8_4Be$ to the stable $^{52}_{26}Fe$ and unstable $^{56}_{28}Ni$ (which days to $^{56}_{26}Fe$).
+In either case, these elements are synthesized through the capture of an $\alpha$ nucleus, progressing towards increasingly heavier nuclei in intervals of 4/2 in mass/atomic number (as $\alpha$ = $^{4}_2$He) from $^8_4$Be to the stable $^{52}_{26}$Fe and unstable $^{56}_{28}$Ni (which days to $^{56}_{26}$Fe).
 The iron group elements, notably Fe, Mn, Co, and Ni, are produced predominately in Type Ia supernovae, with variations depending on a single vs.
@@
 This allows for the quick use of tabulated look-up tables for radiative cooling and heating, often produced using \code{CLOUDY} \citep{Cloudy2013}, that depend on gas density, temperature, metallicity, and redshift (which sets the UVB heating rate).
-More complex simulations often track some form of $< 10$ species primordial chemistry in order to better account for non-equillibrium effects and $H_2$ production, though with noted increases in memory requirements and computational cost.
+More complex simulations often track some form of $< 10$ species primordial chemistry in order to better account for non-equillibrium effects and \Hmolecular production, though with noted increases in memory requirements and computational cost.
 Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2015,Richings2018}; but these are typically prohibitively expensive to run on massive scales.
@@
 %cite?, 
-or that gas meet a minimum $H_2$ mass fraction
+or that gas meet a minimum \Hmolecular mass fraction
 %\citep[e.g.][]{}
@@
 While some of the initial, ad-hoc fixes for this problem (e.g.
-turning off cooling for some time in SN affected fluid elements, decoupling SN affected SPH particles from the hydrodynamics for some time) are still in use today, some notable advancements have been made to employ some combination of kinetic, momentum, and thermal energy feedback to attempt to capture SNe in a more consistent fashion \citep[e.g.][]{Hopkins2014,Simpson2015,Hopkins2018}.
+turning off cooling for some time in SN affected fluid elements, decoupling SN affected SPH particles from the hydrodynamics for some time) are still in use today, some notable advancements have been made to employ some combination of kinetic, momentum, and thermal energy feedback to attempt to capture SNe in a more consistent fashion \citep[e.g.][]{FIRE,Simpson2015,Hopkins2018}.
 
@@
 This is a significant heating mechanism in higher metallicity environments, like the Milky Way \citep{Parravano2003,Wolfire2003}, but may still be important in setting temperature floor of cold dense gas in lower mass galaxies \citep{Forbes2016,Hu2017}.
-Lyman-Werner (LW) band radiation regulates the $H_2$ abundance, which is particularly important in low-metallicity environments where $H_2$ is a dominant coolant \citep[e.g.][]{Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation perscriptions that depend upon the local $H_2$ mass fraction.} As the goal of this dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of the processes in some fashion, including the use of an adaptive ray-tracing radiative transfer scheme to track the stellar ionizing photons.
+Lyman-Werner (LW) band radiation regulates the \Hmolecular abundance, which is particularly important in low-metallicity environments where \Hmolecular is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation perscriptions that depend upon the local \Hmolecular mass fraction.} As the goal of this dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of the processes in some fashion, including the use of an adaptive ray-tracing radiative transfer scheme to track the stellar ionizing photons.
 
@@
 However, stellar winds, from both massive stars and weaker winds from the AGB phase of low mass stars, are important sources of metal enrichment.
-For these reasons we do include a simplified model for stellar wind feedback in this disseration.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in experimental simulations where radiation feedback is ignored.
+For these reasons we include stellar wind feedback in this disseration, albeit in a simplified fashion.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in experimental simulations where radiation feedback is ignored.
 It is thus likely subdominant to radiation feedback.}
@@
 For this dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M$_{\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.
-In general, dwarf galaxies are extremely dark matter dominated, with mass to light ratios over 10$^2$, \citep{SimonGeha2007,Strigari2009,Wolf2010}, convert gas into stars at a lower efficiency than more massive galaxies (cite), and, for the lowest mass dwarf galaxies, exhibit bursty star formation histories driven by stochasticity in the process of both star formation and the effects of stellar feedback (cite).
+In general, dwarf galaxies are extremely dark matter dominated, with mass to light ratios over 10$^2$, \citep{SimonGeha2007,Strigari2008,Wolf2010}, convert gas into stars at a lower efficiency than more massive galaxies (cite), and, for the lowest mass dwarf galaxies, exhibit bursty star formation histories driven by stochasticity in the process of both star formation and the effects of stellar feedback (cite).
 
@@
 Stellar feedback drives outflows, galactic winds, from galaxies across all scales (references).
-Dwarf galaxies in particular, with their relatively shallow potential wells, are expected to drive effective galactic winds \citep{MacLowFerrara1999} with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) above XXX \citep{Muratov2015,Christensen2018}.
+Dwarf galaxies in particular, with their relatively shallow potential wells, are expected to drive effective galactic winds \citep{MacLowFerrara1999} with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) above 100 \citep{Muratov2015,Christensen2018}.
 Not only does this correspond to a significant amount of mass outflow from these galaxies, but these winds should also carry out a substantial amount of metals from these galaxies.
@@
 However, since these galaxies have lost their gas through environmental processes as satellites of the Milky Way (ram pressure and tidal stripping), it was unclear if this loss could be attributed entirely to feedback.
-However, using gas and stellar abundances \cite{McQuinn2015} showed that Leo P -- a gas-rich Local Group dwarf galaxy -- has also ejected $\sim$95\% of its metals.
+However, using gas and stellar abundances \cite{McQuinn2015} showed that Leo P -- a gas-rich Local Group dwarf galaxy -- has also ejected $\sim$95\% of its metals (see Section~\ref{intro:sec:Leo P}).
 This is significant evidence for metal-enriched, feedback-driven galactic winds operating in these low mass dwarf galaxies.
@@
 \subsection{Leo P: A Case Study}
+\label{intro:sec:Leo P}
 
-\textbf{Include a figure? Maybe from recent spectra paper? Or HI from ALFALFA? or both?}
+\begin{figure}
+ \centering
+ \includegraphics[width=0.975\linewidth]{figures/intro/Leo_P}
+ \caption{The Leo P dwarf galaxy.
+\textbf{Left:} \hi contours from the VLA at 32'' resolution (the lowest resolution available) overlaid on top of an optical LBT image.
+This image is adopted from the top-left panel of Figure 4 in \cite{Bernstein-Cooper2014}.
+\textbf{Right:} H$\alpha$ emission (contours) overlaid on top of an HST optical image.
+The \hii region analyzed in \cite{McQuinn2015} to obtain gas-phase metallicities is the blue clump of H$\alpha$ at the bottom of the image.
+This image is adopted from Figure 10 of \cite{Evans2019}.
+\textit{Note:} the veritcal axes are inverted between the left and right panels.}
+ \label{intro:fig:Leo P}
+\end{figure}
 
@@
 It is located at a distance of $1.62\pm 0.15$~Mpc \citep{McQuinn2015a}, and was first characterized as part of the ALFALFA survey \citep{Giovanelli2013,Rhode2013,Skillman2013,McQuinn2013,Bernstein-Cooper2014}.
-These studies have characterized its star formation history as low and roughly continuous over the age of the Universe (SFR = $4.3\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$, \cite{McQuinn2015a}), its stellar mass ($M_{*} = 5.7 \times 10^{5}$~M$_{\odot}$, \cite{McQuinn2013}), its HI and dynamical mass ($M_{\rm HI}(r<r_{\rm HI}) = 9.5\times 10^{5}$~M$_{\odot}$, $M_{\rm dyn}(r<r_{\rm HI}) = 2.6 \times 10^{7}$~M$_{\odot}$, $r_{\rm HI} \sim 500$~pc, \cite{Bernstein-Cooper2014}), and gas-phase abundances from an HII region (12 + log(O/H) = 7.17$\pm$0.04 \cite{Skillman2013}).
+These studies have characterized its star formation history as low and roughly continuous over the age of the Universe (SFR = $4.3\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$, \cite{McQuinn2015a}), its stellar mass ($M_{*} = 5.7 \times 10^{5}$~M$_{\odot}$, \cite{McQuinn2013}), its \hi and dynamical mass ($M_{\rm HI}(r<r_{\rm HI}) = 9.5\times 10^{5}$~M$_{\odot}$, $M_{\rm dyn}(r<r_{\rm HI}) = 2.6 \times 10^{7}$~M$_{\odot}$, $r_{\rm HI} \sim 500$~pc, \cite{Bernstein-Cooper2014}), and gas-phase abundances from an \hii region (12 + log(O/H) = 7.17$\pm$0.04 \cite{Skillman2013}).
+HI, optical, and H$\alpha$ observations of Leo P are given in Figure~\ref{intro:fig:Leo P}.
 Finally, we chose to focus on a Leo P like galaxy in our simulations in part to allow for comparisons to the work in \cite{McQuinn2015}, which makes an accounting of the total metals (as traced by O) contained in the ISM and stars in Leo P, estimating the fraction that must have been ejected over the lifetime of the galaxy.
@@
 This dissertation utilizes high-resolution hydrodynamics simulations that are expensive to run in both walltime ($\sim$ weeks to months) and computational time ($\sim 10^{5-6}$ CPU hours).
-For this reason,
+For this reason, it is computationally infeasible to directly explore many of the uncertainties associated with each of the components of the model as discussed in Section~\ref{intro:sec:ingredients}.
+For this reason, substantially cheaper semi-analytic models are valuable tools that can be used to better understand galactic evolution.
 

### 2019-03-19 thesis/abstract.tex
title and name
Wrote first draft of abstract. Changing title to use command for consistency

@@
 \vskip.35in
-{\Large \bf TITLE HERE}
+{\Large \bf \thesistitle}
 
 \vskip.35in
-{\large YOUR NAME} \\
+{\large Andrew J. Emerick} \\
 \vskip.35in
 \end{center}
-In this \thesis... TEXT HERE
+Motivated by the desire to better understand two of the largest outstanding problems in galacitc evolution -- stellar feedback and galactic chemical evolution -- 
+%In this \thesis
+we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual star particles along with the multi-channel stellar feedback and multi-element metal yields associated with each star.
+We developed these simulations as a means to better understand the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couple to the interstellar medium (ISM) and regulate star formation and drive outflows in dwarf galaxies.
+In addition, we follow the evolution of the individual metal yields associated with these stars in order to better understand how metals mix within the ISM and are ejected into the circumgalactic and itergalactic media (CGM, IGM) through outflows.
+This study is directed with the goal of better understanding the ever increasing quality of stellar abundance measurements within our own Milky Way galaxy and in nearby dwarf galaxies.
+
+Our simulations follow the evolution of an idealized, isolated low mass dwarf galaxy ($M_{\rm vir} \sim 10^{9}$~M$_{\odot}$) over $\sim$ 500 Myr timescales using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
+We implemented a new star formation routine which deposts stars individually during star formation using an assumed initial mass function.
+Using tabulated stellar properties, we follow the stellar feedback from each of these stars individually.
+For massive stars ($M_* > 8$~M$_{\odot}$) we follow their stellar winds, ionizing radiation (as followed using an adaptive ray-tracing radiative transfer method), FUV radiation which leads to photoelectric heating of dust grains, Lyman-Werner radiation which leads to H$_2$ dissociation, and core collapse supernovae.
+In addition, we follow the asymptotic giant branch (AGB) winds of low-mass stars ($M_* < 8$~M$_{\odot}$) and Type Ia supernovae.
+We investigate how this detailed model for stellar feedback regulates the properties of the ISM of this low mass dwarf galaxies, its star formation, and outflows.
+We find agreement with previous studies that these low mass dwarf galaxies exhibit bursty, irregular star formation histories with significant feedback driven winds.
+
+We investigate the role that stellar radiation feedback plays in the evolution of low mass galaxies using three comparison simulations that vary the effects of stellar ionizing radiation.
+First, a fiducial, full-physics simulation, second, a simulation with ionizing radiation restricted to the region immediately around massive star particles, and third, a simulation with no ionizing radiation feedback.
+In the regime of low mass dwarf galaxies, we find that the local effects of stellar radiation (within $\sim$ 10~pc of the massive, ionizing star) act to regulate star formation by rapidly destroying cold, dense gas around newly formed stars.
+For the first time, we find that the long-range radiation effects far from the birth sites are vital for carving channels of diffuse gas in the ISM which dramatically increase the effect of supernovae.
+We find this effect is necessary to drive strong winds with significant mass loading factors and has a significant impact on the metal content of the ISM.
+
+Focusing on the evolution of individual metals within this galaxy, it remains an outstanding question as to what degree (if any) metal mixing processes in a multi-phase ISM influence observed stellar abundance patterns.
+To address this issue, we characterize the time evolution of the metal mass fraction distributions of each of the tracked elements in our simulation in each phase of the ISM.
+For the first time, we demonstrate that there are significant differences in how individual metals are sequestered in each gas phase (from cold, netrual gas up to hot, ionized gas) that depends upon the energetics of the enrichment sources that dominate the production of a given metal species.
+We find that AGB wind elements have much broader distributions (i.e.
+mix poorly) as compared to elements released in supernovae.
+In addition, we demonstrate for the first time that elements dominated by AGB wind production are retained at a much higher fraction than elements released in core collapse supernovae (by a factor of $\sim$ 5).
+
+We expand upon these findings with a more careful study of how varying the energy and spatial location of a given enrichment event changes how its metal yields mix within the ISM.
+We play particular attention to events that could be associated with different channels of r-process enrichment (for example, nuetron star - nuetron star mergers vs.
+hypernovae) as a way to characterize how mixing / ejection differences may manifest themselves in observed abundance patters in low mass dawrf galaxies.
+\textbf{section not done, so revisit}
+
+Finally, we summarize how this new understanding of galactic chemical evolution -- that metal mixing and ejection from galaxies is not uniform across metal species -- can be used to improve significantly upon current state of the art galactic chemical evolution models.
+These improvements stand to help improve our understanding of galactic chemical evolution and reconcile outstanding disagreements between current models and observations.

### 2019-03-19 thesis/abstract.tex
minor copyediting

@@
 Our simulations follow the evolution of an idealized, isolated low mass dwarf galaxy ($M_{\rm vir} \sim 10^{9}$~M$_{\odot}$) over $\sim$ 500 Myr timescales using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
-We implemented a new star formation routine which deposts stars individually during star formation using an assumed initial mass function.
-Using tabulated stellar properties, we follow the stellar feedback from each of these stars individually.
+We implemented a new star formation routine which deposts stars individually during star formation with masses sampled from an initial mass function.
+Using tabulated stellar properties, we follow the stellar feedback from each star.
 For massive stars ($M_* > 8$~M$_{\odot}$) we follow their stellar winds, ionizing radiation (as followed using an adaptive ray-tracing radiative transfer method), FUV radiation which leads to photoelectric heating of dust grains, Lyman-Werner radiation which leads to H$_2$ dissociation, and core collapse supernovae.

### 2019-03-19 thesis/chapters/ch_introduction.tex
Updates to first half of introduction (to Stars section). Cleaned up text, added references, and included final bit in intro

@@
 % \eeq
-
-Galaxies are amalgamations of gas and stars embedded in dark matter halos, formed over cosmic time as the products of the hierarchical assembly that follows from the collapse of primordial density fluctuations that arose after the Big Bang.
+Galaxies are amalgamations of gas and stars embedded in dark matter halos.
+They are formed over cosmic time as the products of the hierarchical assembly that follows from the collapse of the primordial density fluctuations that arose after the Big Bang.
 The gravitational pull of dark matter -- as predicted from $\Lambda$CDM cosmology -- controls the hierarchical growth of structure in the Universe.
-While, broadly speaking, the evolution of baryons is dominated by the gravitational pull of dark matter, the beautiful simplicity of $\Lambda$CDM cosmology is muddied by their existence.
-The complexities of hydrodynamics, magnetohydrodynamics, thermodynamics, chemistry, radiative processes, and nucleosynthesis -- or, ``astrophysics" for short -- drives these deviations and gives rise to the Universe that we observe and -- not least of all -- us.
-In spite of a concerted effort spanning nearly a century, we are far from a self-consistent theory of galaxy evolution \citep[see ][ for a recent review of outstanding problems in galactic evolution]{NaabOstriker2017}.
+While, broadly speaking, the evolution of baryons is dominated by this pull, the beautiful simplicity of $\Lambda$CDM cosmology is muddied by their existence.
+The complexities of hydrodynamics, magnetohydrodynamics, thermodynamics, chemistry, radiative processes, and nucleosynthesis -- or, ``astrophysics" for short -- drives these deviations and gives rise to the Universe that we observe.
+In spite of a concerted effort spanning nearly a century, we are far from a self-consistent theory of galaxy evolution (see \citet{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews).
 It is understanding the rich set of physics that formed our own Galaxy and the countless galaxies scattered throughout the Universe that motivates this work.
@@
 A substantial slice of modern astrophysics has been devoted towards understanding the chemical evolution -- the abundances of individual elements in space and time -- of the Universe.
-With the exception of H, He, and trace amounts of light elements, all of the elements in the Universe are produced in nuclear reactions in the cores of stars, massive star stellar winds, asymptotic giant branch (AGB) winds of low mass stars, and more exotic sites like nuetron star - neutron star mergers (NS-NS).
+With the exception of H, He, and trace amounts of light elements, all of the elements in the Universe are produced in nuclear reactions associated with stellar evolution, either in the cores of stars, stellar winds, asymptotic giant branch (AGB) winds of low mass stars, and more exotic sites like neutron star - neutron star mergers (NS-NS).
 See \cite{Nomoto2013}, \cite{Thielmann2017}, and \cite{Frebel2018} for recent reviews on this topic as it applies to studies of galactic and stellar evolution.
-Much work has been done in studying the global metallicity evolution of galaxies through the mass-metallicity relationship \citep[e.g.][]{Lequeux1979,Tremonti2004,Lee2006,Zahid2012}, the metallicity gradient in our own and nearby galaxies \citep[e.g.][]{}, and detailed stellar abundances in galaxies with spectroscopically resolved stellar populations \citep[e.g.][]{}.
-Yet in spite of increased number and quality of observations of galactic chemical evolution, developing a complete model is still a daunting task.
+Much work has been done in studying the global metallicity evolution of galaxies through the mass-metallicity relationship \citep[e.g.][]{Lequeux1979,Tremonti2004,Lee2006,Zahid2012,AndrewsMartini2013}, the metallicity gradient in our own and nearby galaxies \citep[e.g.][]{Searle1971,Shaver1983,Belfiore2017,SanchezMenguiano2017}, and detailed stellar abundances in nearby dwarf galaxies with spectroscopically resolved stars (see the review in \cite{Tolstoy2009}).
+Yet in spite of increased number and quality of observations of galactic chemical evolution, developing a complete model of galactic chemical evolution is still a daunting task.
 
 %Developing a complete model for galactic chemical evolution is a daunting task.
-To give an impression of the difficulties involved, here is a recipe for constructing a complete model of galactic chemical evolution.
-One must first perscribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas into the disk of the galaxy, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos.
-One can then worry about knowing where, how, and with what masses stars form in the first place from this gas, which requires understanding the hydrodynamic
+To give an impression of the difficulties involved, we outline a recipe for constructing a complete model of galactic chemical evolution.
+One must first prescribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas into the disk of the galaxy, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos.
+One can then worry about knowing where, when, how, and with what masses stars form in the first place from this gas.
+This requires understanding the hydrodynamic
 %and magnetohydrodynamic
-properties of the multi-scale, multi-phase turbulent interstellar medium (ISM).
+properties of the multi-scale, multi-phase turbulent interstellar medium (ISM) and the radiative processes and chemistry that operate within the ISM.
 This in turn requires one to toss in a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and supernovae -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies.
@@
 Wait...
-I forgot about magnetic fields and cosmic rays...
+I forgot about magnetic fields, active galactic nuclei, and cosmic rays...
 
 It should be obvious now to the reader why there remains so much to be learned about galactic chemical evolution.
-Developing a complete model for galactic chemical evolution is a daunting task.
-Yet it is clear that this field offers an incredibly exciting test of an incredible range of physics.
+Yet it is clear that this field offers an incredibly exciting test of a wide range of physical processes.
 
 The observational landscape today is primed for developing a more detailed understanding these processes.
-Recent observational campaigns such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, the Gaia-ESO survey \citep{Gaia}, APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, GALAH \citep{GALAH,Buder2018}, as well as upcoming observations, such as the Local Volume Mapper as part of SDSS-V, have generated tremendous amounts of information on detailed stellar abundnaces and stellar kinematics in our Milky Way and nearby Local Group dwarf galaxies.
+Recent observational campaigns such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, the Gaia-ESO survey \citep{Gaia}, APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, GALAH \citep{GALAH,Buder2018}, as well as upcoming observations, such as the Local Volume Mapper as part of SDSS-V, have generated tremendous amounts of information on detailed stellar abundances and stellar kinematics in our Milky Way and nearby Local Group dwarf galaxies.
 One of the most powerful proposed uses of this enormous trove of data is chemical tagging \citep{Freeman2002}, whereby stellar populations are analyzed in chemical space and 6D phase space to identify co-eval and co-natal groups of stars.
-This process of galactic archeaology aims to break down and identify each distinct stellar component of our Galaxy, explaining the process of their formation and evolution.
-Substantial work has been made recently to determine the efficacy of this approach \citep[e.g.][]{Armillotta2018}, yet the physical processes that give rise to stellar abundances as we observe them today are still uncertain.
+This process of galactic archeology aims to break down and identify each distinct stellar component of our Galaxy, explaining the process of their formation and evolution.
+Substantial work has been made recently to determine the efficacy of this approach \citep[e.g.][]{Ting2012,Hogg2016,Jofre107,Price-Jones2018,Armillotta2018}, yet the physical processes that give rise to stellar abundances as we observe them today are still uncertain.
+
+% I could maybe add a paragraph here mentioning work on galactic outflows and metals in the CGM and how studying
+% how this occurs is very important (peeples metal census?)
 
@@
 
-\textbf{need final par}
+In order to better understand galactic chemical evolution as a whole, we study the detailed process of metal enrichment in the ISM and the ejection of metals into the CGM through high-resolution hydrodynamics simulations of individual galaxies.
+In the remainder of this introduction, we discuss the physical process that we consider in constructing a complete model of galactic evolution in Section~\ref{intro:sec:ingredients} with an emphasis on how these processes are treated in simulations, a summary of relevant observations of the nearby dwarf galaxies relevant to this study in Section~\ref{intro:sec:dwarf galaxies}, a discussion of alternative approaches to modeling galactic chemical evolution in Section~\ref{intro:sec:onezone}, and an outline of the rest of this \dissertation in Section~\ref{intro:sec:structure}.
 
@@
 
-We give a primer on how to model galactic evolution in hydrodynamics simulations.
-We focus on the physics needed to simulate galaxies (cooling, heating, chemistry, star formation, feedback, etc.) as it pertains to the aspects of galactic chemical evolution examined in this dissertation.
-This is meant to be a broad overview of the physical processes modelled in such simulations, focusing on aspects of their implementation rather than the derivation of theory behind such processes.
-While important, the latter is better reserved for a much more detailed work (i.e.
-a textbook), and focusing on the former gives a much more accurate represenation of the actual work done for this dissertation.
+The following is a primer on how to model galactic evolution in hydrodynamics simulations.
+We focus on the physics needed to simulate galaxies (cooling, heating, chemistry, star formation, feedback, etc.) as it pertains to the aspects of galactic chemical evolution examined in this \dissertation.
+This is meant to be a broad overview of the physical processes treated in such simulations, focusing more on aspects of their implementation rather than the derivation of theory behind each process.
+While important, the latter is beyond the scope of this introduction and would readily turn into a full textbook.
+Focusing on implementation gives a much more accurate representation of the actual work done and skills learned during work on this \dissertation.
 This discussion includes a very brief overview of hydrodynamics and the numerical methods used in this work in Section~\ref{intro:sec:hydrodynamics}, nucleosynthesis and stellar evolution in Section~\ref{intro:sec:nucleosynthesis}, radiative cooling and chemistry (actual chemistry) in Section~\ref{intro:sec:cooling}, star formation and star particles in Section~\ref{intro:sec:sf} and Section~\ref{intro:sec:stars}, and stellar feedback in Section~\ref{intro:sec:feedback}.
 
-But first, we note that Astronomy jargon is full of idiosyncrisies.
-As metioned before, the word ``chemical" in the ``galactic chemical evolution" is a bit of a misnomer.
-This is commonly applied simply to refer to studies interested in the evolution of metal abundances (either as a whole, or for individual isotopes) in galaxies over time, and less often to the astrochemistry that those elements may participate in.
+But first, we note that Astronomy jargon is full of idiosyncrasies.
+As mentioned before, the word ``chemical" in ``galactic chemical evolution" is a bit of a misnomer.
+This is commonly applied simply to refer to studies interested in the evolution of metal abundances (either as a whole, or for individual isotopes) in galaxies over time, and less often to the chemical reactions that those elements may participate in.
+Unfortunately ``chemistry" is often used with both meanings in the same work requiring context to decipher the intended meaning.
 Likewise, ``metals" refers broadly to every element except H and He.
-Throughout this dissertation we often refer to the metallicity ($Z$) of a galaxy, its gas, or its stars.
-This quantity represents the total mass fraction of all metals -- and is computed as such in our simulations -- but we note that this is impossible to measure the abundances of all metals in astrophysical contexts outside our own Solar System.
+Throughout this \dissertation we often refer to the metallicity ($Z$) of a galaxy, its gas, or its stars.
+This quantity represents the total mass fraction of all metals -- and is computed as such in our simulations -- but we note that it is generally impossible to measure the abundances of all metals in astrophysical contexts outside our own Solar System (and even then, it is challenging).
 The metallicity of our own Sun ($Z_{\odot}$), for example, is still uncertain \citep{Asplund2009}.
-Instead, most observational works adopt Fe as a proxy for total metallicity in stars (due to its many, strong absorption lines) and O as a proxy in gas abundances (as it is the most abundant metal in the Universe and has convenient, strong emisson lines).
-These metallicity proxies are commonly reported in some form of normalized abundance ratio.
-For stellar metallicities, this is given in the form [A/B], where [A/B] = log($N_A / N_B$) - log($N_A / N_B$)$_{\odot}$, and $N$ refers to the number of atoms of a given element (usually as [Fe/H]).
-Confusingly, gas-phase abundances are commonly reported as just log($N_A / N_B$), often with the somewhat arbitrary normalization of 12, or log(O/H) + 12, for example.\footnote{And I am not going to mention issues in normalizatiion across methods of deriving these abundances...
+Instead, most observational works adopt Fe as a proxy for total metallicity in stars (due to its many, strong absorption lines), O as a proxy in gas-phase abundances in the ISM (as it is the most abundant metal in the Universe and has convenient, strong emission lines), and O or C in gas-phase abundances of the CGM when observed in absorption (primarily through the lines OVI and CIV).
+These metallicity proxies are usually reported in some form of normalized abundance ratio.
+For stellar metallicities, this is given in the form [A/B].
+[A/B] = log($N_A / N_B$) - log($N_A / N_B$)$_{\odot}$, where $N$ refers to the number of atoms of a given element (e.g.
+[Fe/H]).
+Confusingly, gas-phase abundances are commonly reported as just log($N_A / N_B$), often with the somewhat arbitrary normalization of +12, or log(O/H) + 12, for example; converting between the two definitions is straightforward (albeit annoying) and requires adopting a value for the solar abundance.
+\footnote{This is not to mention issues in normalization across methods of deriving these abundances...
 \citep[e.g.][]{KewleyEllison2008}.}
@@
 \subsection{Hydrodynamics}
-Astrophysical hydrodynamics simulations are first distinguished by the numerical methods employed to solve the Euler equations that describe the time ($t$) evolution of the energy density ($E$), density ($\rho$), pressure ($p$), and peculiar velocity ($\bm{v}$) of a fluid:
+\label{intro:sec:hydrodynamics}
+
+Astrophysical hydrodynamics simulations are first differentiated by the numerical methods they employ to solve the Euler equations.
+These equations describe the time ($t$) evolution of the energy density ($E$), density ($\rho$), pressure ($p$), and peculiar velocity ($\bm{v}$) of a fluid:
 \begin{align}
@@
 \code{AREPO} \citep{Springel2010}), or meshless finite-mass / finite-volume methods (such as those implemented in \code{Gizmo} \citep{Hopkins2015}).
+Traditionally these codes were designed to run exclusively on CPUs, but significant work has been made recently to offload various portions onto GPUs (for example \code{GAMER} and \code{GAMER-2} \citep{Schive2010,Schive2018}, \code{GPUGAS} \code{Kulikov2014}, and \code{CHOLLA} \citep{Schneider2015}).
 Given the large variance in numerical methods, recent studies have examined the differences between these numerical implementations \citep[e.g.][]{Agertz2007}, including large-scale code comparison projects \citep[e.g.][]{AGORA,AGORA2}.
-While developing a notion of which code is ``correct" is an ill-posed problem, these studies have allowed for improvement across implementations and an insight into how numerical methods themselves drive uncertainty in our understanding of astrophysical problems.
+While developing even a notion of which code is ``correct" is an ill-posed problem, these studies have allowed for improvement across implementations and an insight into how numerical methods themselves drive uncertainty in our understanding of astrophysical problems.
 
-In this Dissertation, we make use of the adaptive-mesh refinement (AMR) hydrodynamics code \code{Enzo}, as described in greater detail in Chapter~\ref{ch:chapter1}.
+In this \dissertation, we make use of the adaptive-mesh refinement (AMR) hydrodynamics code \code{Enzo}, as described in greater detail in Chapter~\ref{ch:chapter1}.
 As it pertains to galactic chemical evolution, however, the use of a grid-based code has the advantage that metals (which are advected as passive scalars that follow the fluid-flow in the simulations) are allowed to mix and diffuse naturally across fluid elements (grid cells).
@@
 The disadvantage of the diffusion in \code{Enzo}, however, is that it is entirely numerical, and therefore its exact properties are challenging to characterize and are strongly resolution dependent.
-Throughout this dissertation we attempt to account for the effects of resolution on our results, but do not explicitly examine the properties of numerical diffusion itself.
+Throughout this \dissertation we attempt to account for the effects of resolution on our results, but do not explicitly examine the properties of numerical diffusion itself.
 
@@
 
-A variety of nucleosynthetic processes occur within stars and during their deaths that lead to the production of all of the elements of the periodic table.
-This is illustrated well in Figure~\ref{intro:fig:periodic table}, which shows the periodic table colored by the fractional importance of the nucleosynthetic processes that create each element.
+A variety of nucleosynthetic processes occur within stars and during their deaths that lead to the production of all of the elements in the periodic table.
+This is illustrated well in Figure~\ref{intro:fig:periodic table}, which shows the periodic table colored by the fractional importance of the nucleosynthetic processes that produce each element.
 Due to the diversity in production sources across the periodic table, multi-element metal abundance measurements in stars can be used to to better understand and constrain how and where each metal is produced.
@@
 For example, O, an $\alpha$-element is produced predominately in massive stars and is therefore released via core collapse supernovae on timescales of $\sim$~10~Myr after a star formation event, near their stellar birth sites.
-By contrast, Sr is produced predominately via the s-process (discussed more below) which occurs in the asymptotic giant branch (AGB) winds of lower mass stars ($M < 8$~M$_{\odot}$) at much lower energies and on timescales of $\sim 100$~Myr - $1$~Gyr.
-By this time, these stars would have diffused farther away from their birth sites, potentially sampling a qualitatively different portion of the ISM than earlier core collapse SNe.
-Generally the differences in how different timescales affect observed stellar abundances patterns are well understood and easily modelled.\footnote{The canonical example of this is the ``knee" feature in a $[\alpha/$Fe] vs.
+By contrast, Sr is produced predominately via the s-process (discussed more below) which occurs in part in the asymptotic giant branch (AGB) winds of lower mass stars ($M < 8$~M$_{\odot}$) at much lower energies and on timescales of $\sim 100$~Myr - $1$~Gyr.
+By this time, these stars would have diffused farther away from their birth sites, potentially sampling a qualitatively different portion of the ISM than the preceeding core collapse SNe.
+Generally, how different timescales affect observed stellar abundances patterns are well understood and easily modeled.\footnote{The canonical example of this is the ``knee" feature in a $[\alpha/$Fe] vs.
 [Fe/H] diagram, where the location of this knee signifies the point at which Type Ia enrichment (which produces significant Fe, but little to no $\alpha$ elements) begins to have a significant contribution over core collapse SNe (rich in $\alpha$ elements, but not Fe) \citep[e.g.[]{MatteucciBrocato1990, Geisler2005, Hill2018}.
-The location of this knee shifts in a galaxy depending on its SFH.} However, it is not well understood how differences in where and with what energies these events occur affect observed stellar abundance patterns.
-Investigating these differences is a key motivation of this dissertation.
+The location of this knee in this diagram shifts for a given galaxy depending on its SFH.} However, it is not well understood how differences in where and with what energies these events occur affect observed stellar abundance patterns.
+Investigating these differences is a key motivation of this \dissertation.
 
@@
 $\alpha$-elements, notably O, Mg, Si, Ca, and Ti, are produced during the lifetime of massive stars (O, Mg) or during the core collapse supernova explosion itself.
-In either case, these elements are synthesized through the capture of an $\alpha$ nucleus, progressing towards increasingly heavier nuclei in intervals of 4/2 in mass/atomic number (as $\alpha$ = $^{4}_2$He) from $^8_4$Be to the stable $^{52}_{26}$Fe and unstable $^{56}_{28}$Ni (which days to $^{56}_{26}$Fe).
+In either case, these elements are synthesized through the capture of an $\alpha$ nucleus, progressing towards increasingly heavier nuclei in intervals of 4/2 in mass/atomic number (as $\alpha$ = $^{4}_2$He) from $^8_4$Be all the way to the stable $^{52}_{26}$Fe and unstable $^{56}_{28}$Ni (which days to $^{56}_{26}$Fe).
 The iron group elements, notably Fe, Mn, Co, and Ni, are produced predominately in Type Ia supernovae, with variations depending on a single vs.
-double degenerate scenario and the initial composition of exploding white dwarf(s) (WD).
+double degenerate scenario, the initial composition of exploding white dwarf(s) (WD), and the dynamics of the explosion itself.
 
 The presence of these heavier elements in stars enables the formation of even heavier nuclei through neutron capture.
-This is categorized into two processes, slow (or s-) and rapid (or r-) process.
-In the former, neutron densities are typically low enough that the product of each neutron capture beta decays to a more stable isotope before capturing another neucleon.
-In r-process, however, the rate of neutron capture exceeds beta decay, alowing for the production of different, typically heavier, nuclei.
-As shown in the diagram, ligher elements are produced via the s-process and heavier via the r-process, with notable overlap in certain elements, such as Ba.\footnote{For the sake of this discussion, the light neutron-capture primary process elemnts (sometimes referred to as ``lighter element primary process") should be considered s-process elements.
-This different nucleosynthetic channel, first identified in \cite{Travaglio2004}, arose from an apparent disagreement between models of s-process enrichment in galactic chemical evolution studies andnd abundances of elements including Sr, Y, and Zr.
+This is categorized into two processes, the slow (or s-) and rapid (or r-) process.
+In the former, neutron densities are typically low enough that the product of each neutron capture beta decays to a more stable isotope before capturing another nucleon.
+In r-process, however, the rate of neutron capture exceeds beta decay, allowing for the production of different, typically heavier, nuclei.
+As shown in the diagram, lighter elements are produced via the s-process and heavier via the r-process, with notable overlap in certain elements, such as Ba.\footnote{For the sake of this discussion, the light neutron-capture primary process elements (sometimes referred to as ``lighter element primary process") should be considered s-process elements.
+Briefly, this different nucleosynthetic channel, first identified in \cite{Travaglio2004}, arose from the disagreement between models of s-process enrichment and stellar abundances of elements including Sr, Y, and Zr.
 However there is still uncertainty as to whether or not these differences can be explained with different models of weak s-process (which can occur in the winds of massive stars) \citep[e.g.][]{Prantzos2018}.} The s-process occurs predominately in the low-energy winds of low mass (1-8 M$_{\odot}$) AGB stars on time scales of 100's of Myr up to 1 Gyr.
 Exactly which elements are produced in a given AGB star varies with stellar mass and depends strongly on metallicity, which determines the available heavy seed nuclei.
-Sr, Y, Zr, and Ba, as well as C, N and F, are commonly used as tracers of this nucleosynthetic channel.
+Sr, Y, Zr, and Ba, as well as C, N and F, are commonly used as observational tracers of this nucleosynthetic channel.
 
-The dominant origin of r-process enrichment is highly uncertain, though possible channels include neutron star - neutron star and neutron star - black hole mergers, netrino driven winds in core collapse SNe, and exotic SNe, such as magnetic, jet-driven SNe, collapsars, hypernovae, and long-duration gamma-ray bursts \citep[see ][ for recent reviews]{Frebel2018, Cowan2019}.
-Eu is the most commonly used (and easy to observe) unambigious observational tracer of r-process enrichment; Ba is also often studied as a tracer, but requires care due to the significant contribution from s-process enricment.
+The dominant origin of r-process enrichment is highly uncertain, though possible channels include NS-NS and neutron star - black hole mergers, neutrino driven winds in core collapse SNe, and exotic SNe, such as magnetic, jet-driven SNe, collapsars, hypernovae, and long-duration gamma-ray bursts \citep[see ][ for recent reviews]{Frebel2018, Cowan2019}.
+Eu is the most commonly used (and easy to observe) unambiguous observational tracer of r-process enrichment; Ba is also often studied as a tracer, but requires care due to the significant contribution from s-process enrichment.
 More detailed spectra \citep[e.g.][]{Ji2018a} can trace many more of these elements, which can be used as an important discriminator between nucleosynthetic models.
@@
 Finally, although the production of elements unaffected by the r-process are comparatively well understood, there are still large uncertainties in both nuclear reaction rates and stellar evolution properties that affect the computed yields for any given element.
-As including self-consistent nuclear reactions in the interior of stars is nearly computationally impossible in galaxy-scale simulations, metal yields are generally included as averaged over an entire stellar population (see Section\ref{intro:sec:stars}) as determined from a tabulated set of yields.
-These uncertainties, however, mean there are often significant variations and inconsistencies between tables produced by separate groups, which can make some times make interpreting the results of galactic chemical evolution models challenging.
+As including self-consistent nuclear reactions in the interior of stars is nearly computationally impossible in galaxy-scale simulations, metal yields are generally included as averaged over an entire stellar population (see Section\ref{intro:sec:stars}) as obtained from a tabulated set of yields.
+These yields for a given star in a simulation are typically IMF-averaged, and occasionally mass and metallicity dependent depending on the level of detail desired in the simulation.
+Often, only the global metallicity is tracked in simulations, but tracking individual metal species (especially C, O, and Si which can affect the chemistry and cooling physics in the ISM) is becoming more common.
+The uncertainties across tabulated yields, however, mean there are often significant variations and inconsistencies between tables produced by separate groups.
+These can sometimes make interpreting the results of galactic chemical evolution models challenging.
 
@@
 
-Radiative processes are of fundamental importance in properly modelling the diversity of density, temperature, and ionization states in a multi-phase ISM.
+Radiative processes are of fundamental importance in properly modeling the diversity of density, temperature, and ionization states in a multi-phase ISM.
 It is via radiative cooling that gas, heated by gravitational accretion onto dark matter halos, can cool, condense, become self-gravitating, and (eventually) collapse to form stars.
-Conversly heating, via radiative absorption or scatterings, from stellar sources within galaxies and the extragalactic sources that comprises the cosmic UV background (UVB, e.g.
+Conversely heating, via radiative absorption or scatterings, from stellar sources within galaxies and the extragalactic sources that comprises the cosmic UV background (UVB, e.g.
 \cite{HM2001,HM2012,FG2011}).
 Tied to both of these processes is the actual chemistry that occurs in the ISM, from the primordial chemical reactions between H, He, and free electrons to substantially more complicated reactions that occur once significant amounts of metals are present in the ISM (particularly, C, O, and Si).
-These metals by themselves  act as additional radiative coolants, which strongly dictate the shape of the cooling curve which allows for a multi-phase medium in the first place \citep[e.g.][]{McKeeOstriker1977}.
-The molecules produced in chemical reactions with these metals produce additional coolants in the ISM \citep{HollenbackMcKee1979}, including dust, which has its own rich array of associated physical processes \citep{Omukai2000,Omukai2005}.
+These metals by themselves act as additional radiative coolants, which strongly dictate the shape of the cooling curve that helps establish a multi-phase medium in the first place \citep[e.g.][]{McKeeOstriker1977}.
+The molecules produced in chemical reactions with these metals produce additional coolants in the ISM \citep{HollenbackMcKee1979}, including dust, which has its own rich array of associated physical processes \citep{Omukai2000,Omukai2005,Draine2011}.
 
 A full, detailed model of radiative cooling, heating, non-equillibrium chemistry, and dust is generally far too computationally expensive to include in galaxy-scale simulations.
-For this reason, many large-scale cosmological simulations assume that all gas is optically thin and that all molecules and ionization states exist in equillibrium.
+For this reason, many large-scale cosmological simulations assume that all gas is optically thin and that all molecules and ionization states exist in equilibrium.
 This allows for the quick use of tabulated look-up tables for radiative cooling and heating, often produced using \code{CLOUDY} \citep{Cloudy2013}, that depend on gas density, temperature, metallicity, and redshift (which sets the UVB heating rate).
-More complex simulations often track some form of $< 10$ species primordial chemistry in order to better account for non-equillibrium effects and \Hmolecular production, though with noted increases in memory requirements and computational cost.
-Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2015,Richings2018}; but these are typically prohibitively expensive to run on massive scales.
-In this dissertation we adopt the chemistry and radiative cooling and heating physics models availble in the newly developed, open-source library \code{GRACKLE} \citep{GrackleMethod}.
-The exact physics included in our simulations are discussed in greater detail in Chapter~\ref{ch:chapter1}, but we note that improvements to \code{GRACKLE} have been made as the direct result of the research conducted during this dissertation.
+More complex simulations often track some number (usually $< 10$) of species involved in primordial chemistry in order to better account for non-equilibrium effects and \Hmolecular production, though with noted increases in memory requirements and computational cost.
+Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2015,Richings2018}; but these are typically prohibitively expensive to run on large scales.
+In this \dissertation we adopt the chemistry and radiative cooling and heating physics models available in the newly developed, open-source library \code{GRACKLE} \citep{GrackleMethod}.
+The exact physics included in our simulations are discussed in greater detail in Chapter~\ref{ch:chapter1}, but we note that improvements to \code{GRACKLE} have been made as the direct result of the research conducted during this \dissertation.
 %mention that I made improvements to this?
@@
 
-In galaxy-scale hydrodynamics, star formation is typically treated as a process that occurs by a sub-grid model, with an assumed rate and assumed efficiency, in fluid elements that surpass a variety of threshold conditions.
+In galaxy-scale hydrodynamics, the costs in resolving the spatial scales and gas densities required to directly follow star formation relegates this process to a sub-grid model.
+Stars form from fluid elements that surpass a variety of threshold conditions at an assumed rate and efficiency.
 Usually, simulators set these thresholds to fully encompass gas whose Jeans-length (and thus dynamical behavior) becomes unresolved according to the widely-used \cite{Truelove1997} criterion.
-Often, this means a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\nabla \bm{v} < 0$), that gas surpass some virial threshold (describing how bound a cloud may be)
+Often, gas is required to surpass a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\nabla \bm{v} < 0$), that gas surpass some virial threshold (describing how bound a cloud may be)
 %cite?,
-or that gas meet a minimum \Hmolecular mass fraction
+or that gas meet a minimum \Hmolecular mass fraction \citep[e.g.][]{Kuhlen2012}
 %\citep[e.g.][]{}
@@
 Once a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars.
-Briefly, some form of the following equation is usually adopted,
+Briefly, some form of the following equation is usually adopted to describe the star formation rate density ($\dot{\rho}_{\rm SF}$),
 \begin{equation}
 \label{intro:eq:sfr}
- \rm{SFR} \propto 
+ \dot{\rho}_{\rm SF} = \epsilon \frac{\rho_{\rm gas}}{t_*},
 \end{equation}
-,.
-Some works adopt modifications of this simple perscription, with varying star formation efficiency ($\eta$) (refs), or XXXX.
-Others, for application in high-resolution simulations where the mass of stars that would form in a single timestep ($dt \times \rm{SFR}$) is far less than a single star particle mass, allow stars to form out of star forming fluid elements stochastically \citep[e.g.][]{Goldbaum2015}.
+, where $\rho_{\rm gas}$ is the local gas density, $\epsilon$ is some fixed or variable star formation efficiency, and the timescale, $t_*$, is often adopted as the local free fall time, or
+\begin{equation}
+  t_* = t_{\rm ff} = \sqrt{\frac{3\pi}{32 \rm{G} \rho_{\rm gas}}}.
+\end{equation}
+In many cases, $\epsilon$ is fixed to some small value ($\sim$ 0.01) \citep{KrumholzTan2007} meant to represent a galaxy-scale average of star formation efficiency, even though this may vary significantly between individual molecular clouds \citep{Grudic2018}.
+High-resolution simulations, where the mass of stars that would form in a single time step ($dt \times \rm{SFR}$) is far less than a single star particle mass, allow stars to form out of star forming fluid elements stochastically \citep[e.g.][]{Goldbaum2015}.
 
-Recent work has demonstrated that variations in these implemenations can lead to dramatic differences in the outcome of the simulated galaxies (refs, incl brooks/munshi work).
-However, it is generally found that the differences between implementations decrease in simulations with sufficient resolution ($\sim$ 10~pc or better spatial, or $\sim$ $100$ M$_{\odot}$ or better in mass) and with a sufficiently high density threshold for star formation ($n > 100$~cm$^{-3}$) (fire ref).
+Recent work has demonstrated that variations in these implementations can lead to dramatic differences in the outcome of the simulated galaxies \citep[e.g.][]{Hopkins2013,Munshi2018}.
+However, it is generally found that the differences between implementations decrease in simulations with sufficient resolution ($\sim$ 10~pc or better spatial, or $\sim$ $100$ M$_{\odot}$ or better in mass) and with a sufficiently high density threshold for star formation ($n > 100$~cm$^{-3}$).
 
@@
 
-In this dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF.
+In this \dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF.
 This allows us to place unprecidented detail on both the stellar feedback and metal yields associated with each star, spatially and temporally resolving differences in both of these channels as a function of stellar mass and metallicity.
@@
 
-Although not included in this dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution.
+Although not included in this \dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution.
 A substantial amount of recent research has been dedicated towards the examination of supernova-driven cosmic ray feedback (see Section~\ref{ch1:sec:CRs} for a more detailed discussion and references).
@@
 Finally, exoctic sources of stellar feedback, such as hupernovae, high-mass X-ray binaries, and neutron star neutron star mergers can also be a potentially important source of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}.
-However, the uncertainties in the frequency and delay time distributions for when these events should occur, and there relative rarity preclude including these effects in this dissertation.
+However, the uncertainties in the frequency and delay time distributions for when these events should occur, and there relative rarity preclude including these effects in this \dissertation.
 
@@
 
-High resolution simulations, like those developed in this dissertation, can typically resort to utilizing pure thermal energy injection into the fluid elements surrounding the supernova site and avoiding artificial ``overcooling".
+High resolution simulations, like those developed in this \dissertation, can typically resort to utilizing pure thermal energy injection into the fluid elements surrounding the supernova site and avoiding artificial ``overcooling".
 This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}.
@@
 This is a significant heating mechanism in higher metallicity environments, like the Milky Way \citep{Parravano2003,Wolfire2003}, but may still be important in setting temperature floor of cold dense gas in lower mass galaxies \citep{Forbes2016,Hu2017}.
-Lyman-Werner (LW) band radiation regulates the \Hmolecular abundance, which is particularly important in low-metallicity environments where \Hmolecular is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation perscriptions that depend upon the local \Hmolecular mass fraction.} As the goal of this dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of the processes in some fashion, including the use of an adaptive ray-tracing radiative transfer scheme to track the stellar ionizing photons.
+Lyman-Werner (LW) band radiation regulates the \Hmolecular abundance, which is particularly important in low-metallicity environments where \Hmolecular is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation perscriptions that depend upon the local \Hmolecular mass fraction.} As the goal of this \dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of the processes in some fashion, including the use of an adaptive ray-tracing radiative transfer scheme to track the stellar ionizing photons.
 
@@
 \subsection{Known Dwarf Galaxies of the Local Group}
+\label{intro:sec:dwarf galaxies}
 
@@
 \cite{Bullock2017} suggests a deliniation based on stellar mass.
-For this dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M$_{\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.
+For this \dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M$_{\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.
 In general, dwarf galaxies are extremely dark matter dominated, with mass to light ratios over 10$^2$, \citep{SimonGeha2007,Strigari2008,Wolf2010}, convert gas into stars at a lower efficiency than more massive galaxies (cite), and, for the lowest mass dwarf galaxies, exhibit bursty star formation histories driven by stochasticity in the process of both star formation and the effects of stellar feedback (cite).
@@
 \subsection{Metals in Local Group Dwarfs}
+\label{intro:sec:metals in LG}
 
@@
 
-The most prominant example of these types of studies has been of the UFD Reticulum II, where \cite{Ji2016} used the extreme r-process enhancement in its stars to argue in favor of a neutron star -  neutron star origin for the enrichment.
+The most prominant example of these types of studies has been of the UFD Reticulum II, where \cite{Ji2016} used the extreme r-process enhancement in its stars to argue in favor of a NS-NS origin for the enrichment.
 This conclusion has been supported by observations in additional Local Group dwarf galaxies \citep{Duggan2018}, but there is still some disagreement as to this conclusion \citep[e.g.][]{Siegel2018}.
@@
 
-We dedicate this section to a specific Local Group dwarf galaxy, Leo P, as its observed properties motivate the initial conditions of the simulations developed in this dissertation.
+We dedicate this section to a specific Local Group dwarf galaxy, Leo P, as its observed properties motivate the initial conditions of the simulations developed in this \dissertation.
 This galaxy is remarkable for being one of the lowest mass dwarf galaxies with observed, ongoing star formation.
@@
 
-This dissertation utilizes high-resolution hydrodynamics simulations that are expensive to run in both walltime ($\sim$ weeks to months) and computational time ($\sim 10^{5-6}$ CPU hours).
+This \dissertation utilizes high-resolution hydrodynamics simulations that are expensive to run in both walltime ($\sim$ weeks to months) and computational time ($\sim 10^{5-6}$ CPU hours).
 For this reason, it is computationally infeasible to directly explore many of the uncertainties associated with each of the components of the model as discussed in Section~\ref{intro:sec:ingredients}.
@@
 
-One final motivation of this dissertation is to improve the assumptions within these models by better charaterizing the process of inhomogenous mixing in the ISM, and the coupling of metals to galactic winds and outflows.
+One final motivation of this \dissertation is to improve the assumptions within these models by better charaterizing the process of inhomogenous mixing in the ISM, and the coupling of metals to galactic winds and outflows.
 This is particularly important if the behavior differs between elements from different nucleosynthetic sites.
@@
 
-\section{Structure of Dissertation}\label{intro:sec:structure}
+\section{Structure of \dissertation}\label{intro:sec:structure}
+\label{intro:sec:structure}
 
@@
 
-Finally, we conclude in Chapter \ref{ch:conclusion} and briefly discuss future work as extensions of this Dissertation.
+Finally, we conclude in Chapter \ref{ch:conclusion} and briefly discuss future work as extensions of this \dissertation.

### 2019-03-19 thesis/chapters/ch_chapter1.tex
adding reference

@@
 
-We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$.
+We make the common ansatz that star formation occurs by converting gas into stars in a free fall time $\tau_{\rm ff}$ with a star formation efficiency, $\epsilon_{\rm f} \simeq 0.02$ \citep{KrumholzTan2007}.
 At high resolution, the choice of $\epsilon_{\rm f}$ should be irrelevant \citep{Orr2018, FIRE2}, as star formation is ultimately self-regulated by feedback.

### 2019-03-19 thesis/chapters/ch_introduction.tex
Finalized proof read of introduction. First draft of intro complete. Updating and adding references.

@@
 Usually, simulators set these thresholds to fully encompass gas whose Jeans-length (and thus dynamical behavior) becomes unresolved according to the widely-used \cite{Truelove1997} criterion.
-Often, gas is required to surpass a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\nabla \bm{v} < 0$), that gas surpass some virial threshold (describing how bound a cloud may be)
+Often, gas is required to surpass a simple mass or number density threshold, on top of which simulators can also require that the local gas cells be in a converging flow ($\nabla \cdot \bm{v} < 0$), that gas surpass some virial threshold (describing how bound a cloud may be)
 %cite?,
@@
 Once a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars.
-Briefly, some form of the following equation is usually adopted to describe the star formation rate density ($\dot{\rho}_{\rm SF}$),
+Briefly, some form of the following equation is usually adopted to describe the star formation rate density,
 \begin{equation}
@@
 \end{equation}
-, where $\rho_{\rm gas}$ is the local gas density, $\epsilon$ is some fixed or variable star formation efficiency, and the timescale, $t_*$, is often adopted as the local free fall time, or
+where $\rho_{\rm gas}$ is the local gas density, $\epsilon$ is some fixed or variable star formation efficiency, and the timescale, $t_*$, is often adopted as the local free fall time, or
 \begin{equation}
@@
 Recent work has demonstrated that variations in these implementations can lead to dramatic differences in the outcome of the simulated galaxies \citep[e.g.][]{Hopkins2013,Munshi2018}.
-However, it is generally found that the differences between implementations decrease in simulations with sufficient resolution ($\sim$ 10~pc or better spatial, or $\sim$ $100$ M$_{\odot}$ or better in mass) and with a sufficiently high density threshold for star formation ($n > 100$~cm$^{-3}$).
+However, it is generally found that the differences between implementations decrease in simulations with sufficient resolution ($\sim$ 10~pc or better spatial, or $\sim$ $100$ M$_{\odot}$ or better in mass) and with a sufficiently high density threshold for star formation ($n > 100$~cm$^{-3}$) \citep{Orr2018,FIRE2}.
 
@@
 
-Stars, particularly large-scale cosmological simulations, are commonly represented as simple stellar populations (SSPs), or particles with IMF-averaged properties of stellar feedback and metal enrichment.
+Stars, particularly in large-scale cosmological simulations, are commonly represented as simple stellar populations (SSPs), or particles with IMF-averaged properties of stellar feedback and metal enrichment.
 As demonstrated in \cite{Revaz2016}, this approach is reasonable so long as the mass of the star particle is large enough to fully sample the IMF ($> 10^{4}$~M$_{\odot}$).
 In high resolution simulations, particularly simulations of small, low-mass systems like dwarf galaxies, this is no longer the case.
-This leads to inconsistencies in both the effective metal yield of the modelled stars, and (often) an artificial reduction of the effects of stellar feedback.
+This leads to inconsistencies in both the effective metal yield of the modeled stars, and (often) an artificial reduction of the effects of stellar feedback.
 Recent works have developed new models to address this issue, discretizing (rather than averaging over) individual feedback events \citep[e.g.][]{MUGS2010,FIRE,Hopkins2018,Rosdahl2018} or accounting for stochastic sampling of the IMF \citep{Hu2016,Hu2017,Applebaum2018,Su2018}.
@@
 In this \dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF.
-This allows us to place unprecidented detail on both the stellar feedback and metal yields associated with each star, spatially and temporally resolving differences in both of these channels as a function of stellar mass and metallicity.
+This allows us to place unprecedented detail on both the stellar feedback and metal yields associated with each star, spatially and temporally resolving differences in both of these channels as a function of stellar mass and metallicity.
 
@@
 
-The first models of galacitc evolution produced galaxies with stellar masses far in excess of what is observed in the Universe, converting a substantial fraction of their baryons into stars.
+The first models of galactic evolution produced galaxies with stellar masses far in excess of what is observed in the Universe.
+%, converting a substantial fraction of their baryons into stars.
 From these initial works, it was clear that some form of feedback process must take place to self-regulate star formation within galaxies.
-With observations of metal abundances in the CGM around galaxies \citep[see][ for a recent review]{Tumlinson2017}, and of fast-moving outflows from star forming galxaies \citep[see][ for a review]{Veilleux2005}, it was additionally clear that some mechanism must exist to drive these outflows.
-Stellar feedback became the clear physical mechanism to account for both of these phenomena.\footnote{Except maybe for more massive galaxies, where active galactic nuclei likely plan some role in regulating star formation and certainly play a role in driving outflows \citep[e.g.][]{Fabian2012}.}
+With observations of metal abundances in the CGM around galaxies \citep[see][ for a recent review]{Tumlinson2017}, and of fast-moving outflows from star forming galaxies \citep[see][ for a review]{Veilleux2005}, it was additionally clear that some mechanism must exist to drive these outflows.
+Stellar feedback became the clear physical mechanism to account for both of these phenomena.\footnote{Except maybe for more massive galaxies, where active galactic nuclei may play some role in regulating star formation and certainly play a role in driving outflows \citep[e.g.][]{Fabian2012}.
+We do not discuss this source of feedback further in this \dissertation aside from noting that it is another significant uncertainty in our understanding of galactic evolution.}
 
 Initial models for stellar feedback relied primarily on the energy injection from supernovae (SNe, see Section~\ref{intro:sec:supernovae}) to regulate star formation and drive outflows, but it has become clear that this mechanism alone cannot completely account for all of the star formation, ISM, outflow, CGM, and even intergalactic medium (IGM) properties of observed galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews and more detailed discussion of how feedback impacts outstanding problems in galactic evolution).
-Other sources of effective stellar feedback have been identified since \citep[e.g.][]{Agertz2013}, which serve to regulate star formation on different timescales and help develop and ISM and CGM with different phase and ionization properties, and includes stellar radiation (Section~\ref{intro:sec:radiation}) and stellar winds (Section~\ref{intro:sec:stellarwinds}).
+Other sources of effective stellar feedback have been identified since \citep[e.g.][]{Agertz2013}, which serve to regulate star formation on different timescales and help develop and ISM and CGM with different phase and ionization properties.
+This includes both stellar radiation (Section~\ref{intro:sec:radiation}) and stellar winds (Section~\ref{intro:sec:stellarwinds}).
 
@@
 A substantial amount of recent research has been dedicated towards the examination of supernova-driven cosmic ray feedback (see Section~\ref{ch1:sec:CRs} for a more detailed discussion and references).
-In brief, cosmic rays can be a dominant source of heading in very dense gas and act as a source of non-thermal pressure in the ISM, which can drive galactic winds with qualitatively different phase structures \citep[e.g.][]{SalemBryanCorlies}.
-In addition, binarity is often ignored in models of stellar feedback, but can dramatically extend the timescales over which ionizing radiation and supernovae act in a newly formed stellar populations, typically increasing their total energy output and decreasing the typical ISM densities in which SNe explode, increasing their effectiveness (see Section~\ref{ch1:sec:binary stars}).
-Finally, exoctic sources of stellar feedback, such as hupernovae, high-mass X-ray binaries, and neutron star neutron star mergers can also be a potentially important source of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}.
-However, the uncertainties in the frequency and delay time distributions for when these events should occur, and there relative rarity preclude including these effects in this \dissertation.
+In brief, cosmic rays can be a dominant source of heating in very dense gas and act as a source of non-thermal pressure in the ISM, which can drive galactic winds with qualitatively different phase structures \citep[e.g.][]{SalemBryanCorlies}.
+Binarity is often ignored in models of stellar feedback.
+The effects of binary evolution can dramatically extend the timescales over which ionizing radiation and supernovae act in a newly formed stellar populations.
+Typically, this increases their total energy output and decreases the ISM densities in which SNe explode, increasing their effectiveness (see Section~\ref{ch1:sec:binary stars}).
+Finally, exotic sources of stellar feedback, such as hypernovae, high-mass X-ray binaries, and NS-NS mergers can also be a potentially important sources of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}.
+However, the uncertainties in the frequency and delay time distributions for when these events should occur, and their relative rarity, preclude including these effects in this \dissertation.
 
@@
 This is the source of the commonly known ``overcooling" problem, whereby too little energy is injected into too much mass such that the affected region only reaches modest temperatures ($T \lesssim 10^5$~K, as opposed to $T > 10^7$~K, or so).
-This temperature is right around the peak of the cooling curve, and thus the energy is rapidly radiated away before the injected energy has any time to make a significant dynamical impact of the galaxy.
-This is still a problem today in large-box simulations of cosmological volumes which have insufficient resulution to resolve individual SNe.
+This temperature is right around the peak of the cooling curve, and thus the energy is rapidly radiated away before it has time to make a significant dynamical impact of the galaxy.
+This is still a problem today in large-box simulations of cosmological volumes which have insufficient resolution to resolve individual SNe.
 While some of the initial, ad-hoc fixes for this problem (e.g.
-turning off cooling for some time in SN affected fluid elements, decoupling SN affected SPH particles from the hydrodynamics for some time) are still in use today, some notable advancements have been made to employ some combination of kinetic, momentum, and thermal energy feedback to attempt to capture SNe in a more consistent fashion \citep[e.g.][]{FIRE,Simpson2015,Hopkins2018}.
+turning off cooling for some time in SN affected fluid elements or decoupling SN affected SPH particles from the hydrodynamics for some time) are still in use today, some notable advancements have been made to employ some combination of kinetic, momentum, and thermal energy feedback to attempt to capture SNe in a more consistent fashion \citep[e.g.][]{FIRE,Simpson2015,Hopkins2018}.
 
-High resolution simulations, like those developed in this \dissertation, can typically resort to utilizing pure thermal energy injection into the fluid elements surrounding the supernova site and avoiding artificial ``overcooling".
-This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}.
+High resolution simulations, like those developed in this \dissertation, can typically rely on using pure thermal energy injection while still avoiding artificial overcooling.\footnote{This is advantageous because it is often substantially easier to implement than kinetic / momentum injection methods while being less susceptible to numerical artifacts, especially for grid-based codes.} This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}.
 However, a spatial resolution requirement is a density dependent statement; in this case supernovae that occur in the densest gas ($n > 10^{2-3}$~cm$^{-3}$) may still be under-resolved and ineffective.
@@
 We only briefly discuss this method of feedback here, as it is discussed in much more detail in both Chapters~\ref{ch:chapter1} and \ref{ch:chapter2}.
-In brief, \cite{Leitherer1999}, \cite{Agertz2013}, and others demonstrated that stellar radiation, accounts for a substantial fraction of the total energy output of a stellar population.
-Ionizing photons from young, massive stars can photoionize and photoheat the gas surrounding sites of recent star formation.
-This effectively pre-processes the local environment within which SNe occur, often increasing the effectiveness of SNe in regulating star formation and driving outflows \citep{Hu2016}.
+In brief, \cite{Leitherer1999}, \cite{Agertz2013}, and others have demonstrated that stellar radiation accounts for a substantial fraction of the total energy output of a stellar population.
+Ionizing photons from young, massive stars can photoionize and heat the gas surrounding sites of recent star formation.
+This pre-processes the local environment within which SNe occur, often increasing the effectiveness of SNe in regulating star formation and driving outflows \citep{Hu2016}.
 In addition, radiation pressure in the single-scattering limit (from UV photons) and rescattered infrared photons has been used as an additional source of pre-SN feedback \citep[e.g.][]{FIRE}.
-However, due in part to differences in how ionizing radition is followed across simulations, there is disagreement as to exactly how and in what conditions this acts as a source of feedback (see \cite{Krumholz2018} for a detailed examination of this problem).
+However, due in part to differences in how ionizing radiation is followed across simulations, there is disagreement as to exactly how and in what conditions this acts as a source of feedback (see \cite{Krumholz2018} for a detailed examination of this problem).
 
@@
 This is a significant heating mechanism in higher metallicity environments, like the Milky Way \citep{Parravano2003,Wolfire2003}, but may still be important in setting temperature floor of cold dense gas in lower mass galaxies \citep{Forbes2016,Hu2017}.
-Lyman-Werner (LW) band radiation regulates the \Hmolecular abundance, which is particularly important in low-metallicity environments where \Hmolecular is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation perscriptions that depend upon the local \Hmolecular mass fraction.} As the goal of this \dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of the processes in some fashion, including the use of an adaptive ray-tracing radiative transfer scheme to track the stellar ionizing photons.
+Lyman-Werner (LW) band radiation regulates the \Hmolecular~ abundance, which is particularly important in low-metallicity environments where \Hmolecular~ is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation perscriptions that depend upon the local \Hmolecular mass fraction.} As the goal of this \dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of these processes in some fashion.
+
+The simplest way to model stellar radiation feedback is to apply an optically thin, analytic radiation profile, such as the galaxy-centered exponential photoelectric heating profile used in \cite{Tasker2009}, or $1/r^2$ profiles from individual sources \citep[e.g.][]{Forbes2016}.
+However, radiative transfer effects, such as gas self-shielding, are often important, particularly for ionizing radiation.
+Solving the equations of radiative transfer directly in simulations -- as is done with ray tracing methods -- is computationally expensive and scales significantly with the number of sources.
+For this reason, approximate methods, such as flux-limited diffusion, treat radiation as a fluid, removing the scaling of computational cost with the number of sources.
+In this \dissertation, we follow the evolution of galaxies that have at most $10 - 100$ ionizing sources at one time, making it computationally feasible to use the accurate adaptive ray-tracing radiative transfer method implemented in \code{Enzo}.
 
@@
 However, stellar winds, from both massive stars and weaker winds from the AGB phase of low mass stars, are important sources of metal enrichment.
-For these reasons we include stellar wind feedback in this disseration, albeit in a simplified fashion.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in experimental simulations where radiation feedback is ignored.
-It is thus likely subdominant to radiation feedback.}
+For this reason we include stellar wind feedback in this \dissertation, albeit in a simplified fashion.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in simulations where radiation feedback is ignored.
+It is thus likely sub-dominant to radiation feedback.}
 
@@
 However, the number of known Local Group dwarf galaxies has increased dramatically since that time, particularly for the Milky Way, whose known satellite population has more than doubled.
-This is due in large part to tremendous improvements in our ability to detect galaxies on the faintest end of the luminosity function, called ultrafaint galaxies (UFDs, \cite{Willman2005}).\footnote{See \cite{Simon2019} for a recent review}.
-The Dark Energy Survey \citep[e.g.][]{Drlica-Wagner2015} and Hyper Supbrime-Cam \citep[e.g.][]{Greco2018} have made tremendous advances to this end, with the upcoming Large Synoptic Survey Telescope producing an even greater increase in the known population of faint galaxies in the Local Group \citep{Haynes2019,Weisz2019}.
+This is due in large part to tremendous improvements in our ability to detect galaxies on the faintest end of the luminosity function, called ultrafaint dwarf galaxies (UFDs, \cite{Willman2005}).\footnote{See \cite{Simon2019} for a recent review}.
+The Dark Energy Survey \citep[e.g.][]{Drlica-Wagner2015} and Hyper Supbrime-Cam \citep[e.g.][]{Greco2018} have made tremendous advances to this end, with the upcoming Large Synoptic Survey Telescope expected to produce an even greater increase in the known population of faint galaxies in the Local Group \citep{Haynes2019,Weisz2019}.
 
-While there is no real sharp transition where a galaxy is considered a ``dwarf" galaxy, historical definitions are based on luminosity, using the SMC and LMC as rough anchor points for the upper-end of the dwarf galaxy scale.
-\cite{Bullock2017} suggests a deliniation based on stellar mass.
+While there is no true sharp transition below which a galaxy is considered ``dwarf", historical definitions are based on luminosity cuts, using the SMC and LMC as rough anchor points for the upper-end of the dwarf galaxy scale.
+\cite{Bullock2017} suggests a delineation based on stellar mass.
 For this \dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M$_{\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.
-In general, dwarf galaxies are extremely dark matter dominated, with mass to light ratios over 10$^2$, \citep{SimonGeha2007,Strigari2008,Wolf2010}, convert gas into stars at a lower efficiency than more massive galaxies (cite), and, for the lowest mass dwarf galaxies, exhibit bursty star formation histories driven by stochasticity in the process of both star formation and the effects of stellar feedback (cite).
+In general, dwarf galaxies are extremely dark matter dominated, with mass to light ratios over 10$^2$ \citep{SimonGeha2007,Strigari2008,Wolf2010}, convert gas into stars at a lower efficiency than more massive galaxies (cite), and, for the lowest mass dwarf galaxies
+% need citations
+, exhibit bursty star formation histories driven by stochasticity in the process of both star formation and the effects of stellar feedback
+% need citations
+.
 
@@
 
-The first studies of stellar abundances in the Local Group focused on stars in nearby dSph's, and massive stars in the LMC, SMC, and similar, more massive dwarf galaxies \citep[e.g.][]{}.
-These studies typically obtained abundances for only a small sample ($\sim$ 10) stars, limiting the extent to which they can be used to test models of galacitc chemical evolution.
-However, the advent of high-resolution spectrographs at both Keck and the Very Large Telescope -- capable of obtaining the spectra of many stars with a single pointing -- have dramatically increased the sample size of stellar abundances in nearby dwarf galaxies \citep[e.g.][]{}.
+The first studies of stellar abundances in the Local Group focused on stars in nearby dwarf spheroidals (dSph's), and massive stars in the LMC, SMC, and similar, more massive dwarf galaxies.
+These studies typically obtained abundances for only a small sample ($\sim$ 10) stars, limiting the extent to which they can be used to test models of galactic chemical evolution.
+However, the advent of high-resolution spectrographs at both Keck and the Very Large Telescope -- capable of obtaining the spectra of many stars with a single pointing -- have dramatically increased the sample size of stellar abundances in nearby dwarf galaxies.
 
-Stellar feedback drives outflows, galactic winds, from galaxies across all scales (references).
+Stellar feedback drives outflows, galactic winds, from galaxies across all scales
+%(references).
 Dwarf galaxies in particular, with their relatively shallow potential wells, are expected to drive effective galactic winds \citep{MacLowFerrara1999} with mass loading factors ($\eta$ = $\dot{\rm{M}}_{\rm out} / {\rm SFR}$) above 100 \citep{Muratov2015,Christensen2018}.
@@
 \cite{Kirby2011-metals} used measurements of the stellar abundances in Local Group dSph's and their resolved star formation histories to determine that their stars contain less than 5\% of the metals synthesized in each galaxy.
-However, since these galaxies have lost their gas through environmental processes as satellites of the Milky Way (ram pressure and tidal stripping), it was unclear if this loss could be attributed entirely to feedback.
+However, since these galaxies have lost their gas through environmental processes as satellites of the Milky Way (primarily ram pressure and tidal stripping), it was unclear if this loss could be attributed entirely to feedback.
 However, using gas and stellar abundances \cite{McQuinn2015} showed that Leo P -- a gas-rich Local Group dwarf galaxy -- has also ejected $\sim$95\% of its metals (see Section~\ref{intro:sec:Leo P}).
@@
 At these low metallicities, the number of possible enrichment events that could have possibly contributed to the observed stellar abundances decreases significantly, increasing the possibility of using these abundance patterns to constrain the yields of individual sources.
-This is particularly true for exotic enrichment events, like those expected to be significant sources of r-process elements, which are potentially so rare that only one or fewer events would be expected in an individual low-mass galaxy.
+This is particularly true for exotic enrichment events, like those expected to be sources of r-process elements, which are potentially so rare that only one or fewer events would be expected in an individual low-mass galaxy.
 
-The most prominant example of these types of studies has been of the UFD Reticulum II, where \cite{Ji2016} used the extreme r-process enhancement in its stars to argue in favor of a NS-NS origin for the enrichment.
-This conclusion has been supported by observations in additional Local Group dwarf galaxies \citep{Duggan2018}, but there is still some disagreement as to this conclusion \citep[e.g.][]{Siegel2018}.
+The most prominent example of these types of studies has been of the UFD Reticulum II, where \cite{Ji2016} used the extreme r-process enhancement in its stars to argue in favor of a NS-NS of r-process enrichment.
+This conclusion has been supported by observations in additional Local Group dwarf galaxies \citep{Duggan2018}, but there is still some disagreement as to the dominant source of r-process enrichment \citep[e.g.][]{Siegel2018}.
 Interestingly, the lack of these extreme r-process abundances in other UFDs suggests that another source of r-process must exist \citep{Ji2016b}.
 Some of the significant uncertainties in interpreting these observations lie with understanding how r-process elements mix within the ISM and are ejected from low mass dwarf galaxies.
-Recent research has examined how metals from individual enrichement events may mix and evolve in a variety of contexts \citep[e.g.][]{Bland-Hawthorn2015,Ritter2015,Montes2016,Safarzadeh2017}, but there is still much to be understood about this process.
-In particular, there is still much to be gained from adapting insights from these types of simulations to the modelling used to interpret observations of stellar abundances (as discussed in more detail in Section~\ref{intro:sec:onezone}).
+Recent research has examined how metals from individual enrichment events may mix and evolve in a variety of contexts \citep[e.g.][]{Bland-Hawthorn2015,Ritter2015,Montes2016,Safarzadeh2017}, but there is still much to be understood about this process.
+In particular, there is still much to be gained from adapting insights from these types of simulations to the modeling used to interpret observations of stellar abundances (as discussed in more detail in Section~\ref{intro:sec:onezone}).
 
@@
  \caption{The Leo P dwarf galaxy.
-\textbf{Left:} \hi contours from the VLA at 32'' resolution (the lowest resolution available) overlaid on top of an optical LBT image.
+\textbf{Left:} \hi contours from the Very Large Array (VLA) at 32'' resolution overlaid on top of an optical Large Binocular Telescope image.
+32'' is the lowest resolution \hi observation available of Leo P from the VLA, which best traces diffuse, warm ($T \sim 10^3$~K) \hi in the galaxy and exhibits the full spatial extent of its gas content.
 This image is adopted from the top-left panel of Figure 4 in \cite{Bernstein-Cooper2014}.
-\textbf{Right:} H$\alpha$ emission (contours) overlaid on top of an HST optical image.
-The \hii region analyzed in \cite{McQuinn2015} to obtain gas-phase metallicities is the blue clump of H$\alpha$ at the bottom of the image.
+\textbf{Right:} H$\alpha$ emission (contours) overlaid on top of a Hubble Space Telescope (HST) optical image.
+The \hii region analyzed in \cite{McQuinn2015} to obtain gas-phase metallicities is the blue clump of H$\alpha$ towards the bottom of the image.
 This image is adopted from Figure 10 of \cite{Evans2019}.
-\textit{Note:} the veritcal axes are inverted between the left and right panels.}
+Note the inversion in the vertical axes between the left and right panels.}
  \label{intro:fig:Leo P}
@@
 It is located at a distance of $1.62\pm 0.15$~Mpc \citep{McQuinn2015a}, and was first characterized as part of the ALFALFA survey \citep{Giovanelli2013,Rhode2013,Skillman2013,McQuinn2013,Bernstein-Cooper2014}.
-These studies have characterized its star formation history as low and roughly continuous over the age of the Universe (SFR = $4.3\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$, \cite{McQuinn2015a}), its stellar mass ($M_{*} = 5.7 \times 10^{5}$~M$_{\odot}$, \cite{McQuinn2013}), its \hi and dynamical mass ($M_{\rm HI}(r<r_{\rm HI}) = 9.5\times 10^{5}$~M$_{\odot}$, $M_{\rm dyn}(r<r_{\rm HI}) = 2.6 \times 10^{7}$~M$_{\odot}$, $r_{\rm HI} \sim 500$~pc, \cite{Bernstein-Cooper2014}), and gas-phase abundances from an \hii region (12 + log(O/H) = 7.17$\pm$0.04 \cite{Skillman2013}).
+These studies have characterized its star formation history as low and roughly continuous over the age of the Universe ($<$SFR$>$ = $4.3\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$, \cite{McQuinn2015a}), its stellar mass ($M_{*} = 5.7 \times 10^{5}$~M$_{\odot}$, \cite{McQuinn2013}), its \hi and dynamical mass ($M_{\rm HI}(r<r_{\rm HI}) = 9.5\times 10^{5}$~M$_{\odot}$, $M_{\rm dyn}(r<r_{\rm HI}) = 2.6 \times 10^{7}$~M$_{\odot}$, $r_{\rm HI} \sim 500$~pc, \cite{Bernstein-Cooper2014}), and gas-phase abundances from an \hii region (12 + log(O/H) = 7.17$\pm$0.04 \cite{Skillman2013}).
 HI, optical, and H$\alpha$ observations of Leo P are given in Figure~\ref{intro:fig:Leo P}.
-Finally, we chose to focus on a Leo P like galaxy in our simulations in part to allow for comparisons to the work in \cite{McQuinn2015}, which makes an accounting of the total metals (as traced by O) contained in the ISM and stars in Leo P, estimating the fraction that must have been ejected over the lifetime of the galaxy.
-This is an important measurement as prior estaimtes of this number for low mass dwarf galaxies were restricted to Milky Way dSph's, which are devoid of gas and contaminated by environmental affects.
+
+We chose to focus on a Leo P like galaxy in our simulations in part to allow for comparisons to the work in \cite{McQuinn2015}, which makes an accounting of the total metals (as traced by O) contained in the ISM and stars in Leo P, estimating the fraction that must have been ejected over the lifetime of the galaxy.
+%This is an important measurement as prior estimates of this number for low mass dwarf galaxies were restricted to Milky Way dSph's, which are devoid of gas and contaminated by environmental affects.
 As of this writing, Leo P is one of the only low mass dwarf galaxies with both gas-phase and stellar metal abundance measurements, but there is ongoing work to greatly expand this sample in the near future.
@@
 
-This \dissertation utilizes high-resolution hydrodynamics simulations that are expensive to run in both walltime ($\sim$ weeks to months) and computational time ($\sim 10^{5-6}$ CPU hours).
+This \dissertation utilizes high-resolution hydrodynamics simulations that are expensive to run in terms of both wall-time ($\sim$ weeks to months) and computational time ($\sim 10^{5-6}$ CPU hours).
 For this reason, it is computationally infeasible to directly explore many of the uncertainties associated with each of the components of the model as discussed in Section~\ref{intro:sec:ingredients}.
@@
 One of the most common ways to model and understand the stellar populations of galaxies in high-dimensional chemical space is through simplified one-zone (or many-zone) models.
-This treatment extends back many decades \citep[e.g.][]{Schmidt1963,TalbotArnett1971,Lynden-Bell1975}, where galaxies and their total metal abundance were treated as closed-box systems of gas and stars.
-Over the interveaning decades these models have improved, including perscriptions for gas outflow (a ``leaky-box") or gas inflow (``accreting box"), or both (a ``bathtub" model, e.g.
+This treatment extends back many decades \citep[e.g.][]{Schmidt1963,TalbotArnett1971,Lynden-Bell1975}, where galaxies and their total metal abundances were treated in closed-box systems of gas and stars.
+Over the intervening decades these models have improved, including prescriptions for gas outflow (a ``leaky-box") or gas inflow (an ``accreting box"), or both (a ``bathtub" model, e.g.
 \cite{FinlatorDave2008,Bouche2010}).
 The assumptions that go into these models vary dramatically with complexity.
-Simple models can assume, for example, that long-lived low mass stars do not contribute to metal enrichment while metals from massive stars are instantaneously recylced into the galaxy's gas reservoir (i.e.
-ignoring stellar lifetimes) or that all metals mix instantly and homogenously.
-More complex models account for individual stellar lifetimes (to some degree), or may try and account for some aspects of inhomogenous mixing by constructing mulit-zone models that may separate a galaxy in radial bins (with or without mixing between bins), may account for a hot and cold component separately, with mixing between the two, or account for separate ISM and CGM components.
+Simple models can assume, for example, that long-lived low mass stars do not contribute to metal enrichment while metals from massive stars are instantaneously recycled into the galaxy's gas reservoir (i.e.
+ignoring stellar lifetimes) or that all metals mix instantly and homogeneously.
+More complex models account for individual stellar lifetimes (to some degree), or may try and account for some aspects of inhomogeneous mixing by constructing multi-zone models that may separate a galaxy in radial bins (with or without mixing between bins), may account for a hot and cold component separately (with mixing between the two), or account for separate ISM and CGM components.
 The output of these models is typically the mean metal abundance evolution within each of the tracked components.
-There is generally no self-consistent perscription to account for the scatter in any abundance relationship in these models, which, when needed, is often added ad-hoc in post-processing.
+There is generally no self-consistent prescription to account for the scatter in any abundance relationship in these models, which, when needed, is often added ad-hoc in post-processing.
 Regardless of the assumptions that go into these models, they are powerful tools that can be used to probe the general physical processes that govern galactic chemical evolution, and explore the vast, uncertain parameter space associated with the models that characterize these processes \citep[e.g.][]{Cote2017a}.
 
-One final motivation of this \dissertation is to improve the assumptions within these models by better charaterizing the process of inhomogenous mixing in the ISM, and the coupling of metals to galactic winds and outflows.
+One final motivation of this \dissertation is to improve the assumptions within these models by better characterizing the process of inhomogeneous mixing in the ISM, and the coupling of metals to galactic winds and outflows.
 This is particularly important if the behavior differs between elements from different nucleosynthetic sites.
 In addition, this work could be used to account for the spread and higher-order statistics of stellar abundance distributions, which would be a powerful tool for better leveraging the wealth of observations in the Milky Way and Local Group.
-Yet, as discussed, the current state of the art perscriptions for these processes are ad-hoc, lacking physical motivation.
+Yet, as discussed, the current state of the art prescriptions for these processes are ad-hoc.
 Recent analytic work in \cite{KrumholzTing2018} lays down a framework to evaluate the correlation between individual metals in different galactic environments and predicts that the correlations will differ for different nucleosynthetic sites (e.g.
@@
 We characterize these differences in detail in Chapter~\ref{ch:chapter3}, laying the groundwork for how one could potentially incorporate this insight into improving these models.
-We build upong this idea more in Chapter~\ref{ch:chapter4}, and plan to explore the connection between our simulations and analytic models in the future.
-Recent work by \cite{SchonrichWeinberg2019} is a great example of how this could greatly impact current models for galactic chemical evolution.
-They how adopting a two-phase onezone model (hot and cold ISM), along with parameters for how metals are injected and mix between the phases whose values differ depending on nucleosynthetic origin of the metal, can reconcile long-standing problems in understanding the r-process abundance evolution of stars in the Milky Way.
-And in fact, they argue that it would be impossible to reproduce observed r-process abundances in the Milky Way (namely [Eu/Fe], [Eu/Si], and [Eu/Mg] as functions of [Fe/H]) with a standard one-phase model.
+We build upon this idea more in Chapter~\ref{ch:chapter4}, and plan to explore the connection between our simulations and analytic models in the future.
+Recent work by \cite{SchonrichWeinberg2019} is a great example of how this could impact current models for galactic chemical evolution.
+The authors show how adopting a two-phase model (hot and cold ISM), along with parameters for how metals are injected and mix between the phases whose values differ depending on nucleosynthetic origin of the metal, can reconcile long-standing problems in understanding the r-process abundance evolution of stars in the Milky Way.
+In fact, they argue that it would be impossible to reproduce observed r-process abundances in the Milky Way (namely [Eu/Fe], [Eu/Si], and [Eu/Mg] as functions of [Fe/H]) with a standard one-phase model.
 
@@
 In this work we investigate the role of both stellar feedback and mixing in a multi-phase ISM in driving galactic chemical evolution.
-Using a novel method for following star formation and stellar feedabck in galaxy-scale hydrodynamics simulations, we provide significant insight into how individual metals from distinct nucleosynthetic sites enrich the ISM, how their abundances are set and imprinted upon newly formed stars, and how they are ejected from galaxies through galactic winds.
+Using a novel method for following star formation and stellar feedback in galaxy-scale hydrodynamics simulations, we provide significant insight into how individual metals from distinct nucleosynthetic sites enrich the ISM, how their abundances are set and imprinted upon newly formed stars, and how they are ejected from galaxies through galactic winds.
 
-In Chapter \ref{ch:chapter1} \citep[published as ][]{Emerick2019}, we motivate the need for a new model of star formation and stellar feedback to address the open uncertainties in galactic chemical evolution.
+In Chapter \ref{ch:chapter1} \citep[published as][]{Emerick2019}, we motivate the need for a new model of star formation and stellar feedback to address the open uncertainties in galactic chemical evolution.
 We implement such a model, which follows stars as individual star particles over a fully sampled IMF, in hydrodynamics simulations of an isolated, low-mass dwarf galaxy.
 We describe in detail the physics included in these simulations, including a stellar feedback model that follows stellar radiation, stellar winds, and supernovae.
-We find that RESULTS
+We find that the implemented set of physics give rise to a multi-phase ISM with a highly variable stellar radiation profiles, star formation rates, and galactic outflows.
+In agreement with previous works, we find that multi-channel feedback is able to drive outflows with high mass-loading factors while maintaining a fluctuating star formation rate density consistent with observations of low mass dwarf galaxies.
+Finally, we characterize the \Hmolecular~ properties of this galaxy, which remains unconstrained in observations of dwarf galaxies at this mass scale.
 
-In Chapter \ref{ch:chapter2} \citep[published as ][]{Emerick2018a}, we investigate how stellar ionizing radiation feedback impacts the evolution of our simulated low mass dwarf galaxy.
-We confirm the findings in recent works, as dicsussed in Section~\ref{intro:sec:radiation}, that find that stellar radiation is an important source of pre-supernova feedback that regulates star formation and can help drive galactic outflows outflows.
-We additionally investigate how radiation feedback couples to the ISM to drive galactic winds by demonstrating that the ionization of gas far from individual ionzing sources, out into the disk-halo interface of our galaxy, creates low-density channels through which supernovae can readily drive gas and metals into and beyond the galaxy's CGM.
+In Chapter \ref{ch:chapter2} \citep[published as][]{Emerick2018a}, we investigate how stellar ionizing radiation feedback impacts the evolution of our simulated low mass dwarf galaxy.
+We confirm the findings in recent works, as discussed in Section~\ref{intro:sec:radiation}, that find that stellar radiation is an important source of pre-supernova feedback that regulates star formation and can help drive galactic outflows.
+We additionally investigate how radiation feedback couples to the ISM to drive galactic winds by demonstrating that the ionization of gas far from individual ionizing sources, out into the disk-halo interface of our galaxy, creates low-density channels through which supernovae can readily drive gas and metals into and beyond the galaxy's CGM.
 This suggests that not only is the local deposition of energy from stellar radiation important, which quickly destroys dense gas in stellar birth-sites, but also long-range effects are important to consider in a consistent model of stellar feedback.
 
-In Chapter \ref{ch:chapter3} \citep[published as ][]{Emerick2018b}, we dive in detail into the evolution of each of the 15 individual metal species that we follow in our simulation.
+In Chapter \ref{ch:chapter3} \citep[published as][]{Emerick2018b}, we dive in detail into the evolution of each of the 15 individual metal species that we follow in our simulation.
 We focus primarily on the evolution of the gas-phase abundances of these metals, and how the site of nucleosynthesis (e.g.
@@
 SNe).
-Likewise, energy difference associated with their enrichment directly impacts their ability to couple to galactic outflows.
+Likewise, energy differences associated with their enrichment directly impacts their ability to couple to galactic outflows.
 We find that elements released in AGB winds are retained at a higher fraction (by a factor of $\sim$ 4-5) than elements released in SNe.

### 2019-03-19 thesis/acknowledgments.tex
adding year and location

%
%
% Acknoledgements
%
%

\newpage

\begin{center}

{\large \bf ACKNOWLEDGMENTS } % leave this title

\end{center}

\vspace{0.8cm}
% Thank people, places, things, existential concepts, etc. here. Length varies
% but usually something like 1-2 pages
\textit{To-do}

\vspace{1.8cm}
2019, New York, NY

%\setlength{\baselineskip}{1.11111 \baselineskip}

### 2019-03-19 thesis/chapters/ch_introduction.tex
reformatting some of the parenthetical citations

@@
 See \cite{Nomoto2013}, \cite{Thielmann2017}, and \cite{Frebel2018} for recent reviews on this topic as it applies to studies of galactic and stellar evolution.
-Much work has been done in studying the global metallicity evolution of galaxies through the mass-metallicity relationship \citep[e.g.][]{Lequeux1979,Tremonti2004,Lee2006,Zahid2012,AndrewsMartini2013}, the metallicity gradient in our own and nearby galaxies \citep[e.g.][]{Searle1971,Shaver1983,Belfiore2017,SanchezMenguiano2017}, and detailed stellar abundances in nearby dwarf galaxies with spectroscopically resolved stars (see the review in \cite{Tolstoy2009}).
+Much work has been done in studying the global metallicity evolution of galaxies through the mass-metallicity relationship \citep[e.g.][]{Lequeux1979,Tremonti2004,Lee2006,Zahid2012,AndrewsMartini2013}, the metallicity gradient in our own and nearby galaxies \citep[e.g.][]{Searle1971,Shaver1983,Belfiore2017,SanchezMenguiano2017}, and detailed stellar abundances in nearby dwarf galaxies with spectroscopically resolved stars \citep[see the review in][]{Tolstoy2009}.
 Yet in spite of increased number and quality of observations of galactic chemical evolution, developing a complete model of galactic chemical evolution is still a daunting task.
@@
 Historically, codes fall into one of two camps: 1) Eulerian grid-based codes, including the popular codes / algorithms commonly in use (in some way) today such as \code{Zeus} \citep{StoneNorman1992}, \code{FLASH} \citep{FLASH}, \code{RAMSES} \citep{Teyssier2002}, \code{Athena} \citep{Athena}, \code{ART-II} \citep{Rudd2008}, and \code{Enzo} \citep{Enzo2014}, and 2) particle-based Lagrangian methods known as smooth particle hydrodynamics (SPH), such as \code{Gadget} \citep{Springel2005}, \code{PKDGRAV-2} \citep{Stadel2001}, \code{Gasoline} \citep{Wadsley2004}, and \code{Changa} \citep{Menon2015}.
-However, recent codes blur the lines between these distinctions with new algorithms for solving the fluid equations on a moving-mesh (e.g.
-\code{AREPO} \citep{Springel2010}), or meshless finite-mass / finite-volume methods (such as those implemented in \code{Gizmo} \citep{Hopkins2015}).
-Traditionally these codes were designed to run exclusively on CPUs, but significant work has been made recently to offload various portions onto GPUs (for example \code{GAMER} and \code{GAMER-2} \citep{Schive2010,Schive2018}, \code{GPUGAS} \code{Kulikov2014}, and \code{CHOLLA} \citep{Schneider2015}).
+However, recent codes blur the lines between these distinctions with new algorithms for solving the fluid equations on a moving-mesh \citep[e.g.
+\code{AREPO}][]{Springel2010}, or meshless finite-mass / finite-volume methods \citep[such as those implemented in \code{Gizmo}][]{Hopkins2015}.
+Traditionally these codes were designed to run exclusively on CPUs, but significant work has been made recently to offload various portions onto GPUs, such as \code{GAMER} and \code{GAMER-2} \citep{Schive2010,Schive2018}, \code{GPUGAS} \citep{Kulikov2014}, and \code{CHOLLA} \citep{Schneider2015}.
 Given the large variance in numerical methods, recent studies have examined the differences between these numerical implementations \citep[e.g.][]{Agertz2007}, including large-scale code comparison projects \citep[e.g.][]{AGORA,AGORA2}.
@@
 However, the number of known Local Group dwarf galaxies has increased dramatically since that time, particularly for the Milky Way, whose known satellite population has more than doubled.
-This is due in large part to tremendous improvements in our ability to detect galaxies on the faintest end of the luminosity function, called ultrafaint dwarf galaxies (UFDs, \cite{Willman2005}).\footnote{See \cite{Simon2019} for a recent review}.
+This is due in large part to tremendous improvements in our ability to detect galaxies on the faintest end of the luminosity function, called ultrafaint dwarf galaxies \citep[UFDs][]{Willman2005}.\footnote{See \cite{Simon2019} for a recent review}.
 The Dark Energy Survey \citep[e.g.][]{Drlica-Wagner2015} and Hyper Supbrime-Cam \citep[e.g.][]{Greco2018} have made tremendous advances to this end, with the upcoming Large Synoptic Survey Telescope expected to produce an even greater increase in the known population of faint galaxies in the Local Group \citep{Haynes2019,Weisz2019}.
@@
 It is located at a distance of $1.62\pm 0.15$~Mpc \citep{McQuinn2015a}, and was first characterized as part of the ALFALFA survey \citep{Giovanelli2013,Rhode2013,Skillman2013,McQuinn2013,Bernstein-Cooper2014}.
-These studies have characterized its star formation history as low and roughly continuous over the age of the Universe ($<$SFR$>$ = $4.3\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$, \cite{McQuinn2015a}), its stellar mass ($M_{*} = 5.7 \times 10^{5}$~M$_{\odot}$, \cite{McQuinn2013}), its \hi and dynamical mass ($M_{\rm HI}(r<r_{\rm HI}) = 9.5\times 10^{5}$~M$_{\odot}$, $M_{\rm dyn}(r<r_{\rm HI}) = 2.6 \times 10^{7}$~M$_{\odot}$, $r_{\rm HI} \sim 500$~pc, \cite{Bernstein-Cooper2014}), and gas-phase abundances from an \hii region (12 + log(O/H) = 7.17$\pm$0.04 \cite{Skillman2013}).
-HI, optical, and H$\alpha$ observations of Leo P are given in Figure~\ref{intro:fig:Leo P}.
+These studies have characterized its star formation history as low and roughly continuous over the age of the Universe \citep[$<$SFR$>$ = $4.3\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$,][]{McQuinn2015a}, its stellar mass \citep[$M_{*} = 5.7 \times 10^{5}$~M$_{\odot}$,][]{McQuinn2013}, its \hi and dynamical mass \citep[$M_{\rm HI}(r<r_{\rm HI}) = 9.5\times 10^{5}$~M$_{\odot}$, $M_{\rm dyn}(r<r_{\rm HI}) = 2.6 \times 10^{7}$~M$_{\odot}$, $r_{\rm HI} \sim 500$~pc,][]{Bernstein-Cooper2014}, and gas-phase abundances from an \hii region \citep[12 + log(O/H) = 7.17$\pm$0.04][]{Skillman2013}.
+HI, optical, and H$\alpha$ observations of Leo P are shown inf Figure~\ref{intro:fig:Leo P}.
 
@@
 This treatment extends back many decades \citep[e.g.][]{Schmidt1963,TalbotArnett1971,Lynden-Bell1975}, where galaxies and their total metal abundances were treated in closed-box systems of gas and stars.
-Over the intervening decades these models have improved, including prescriptions for gas outflow (a ``leaky-box") or gas inflow (an ``accreting box"), or both (a ``bathtub" model, e.g.
-\cite{FinlatorDave2008,Bouche2010}).
+Over the intervening decades these models have improved, including prescriptions for gas outflow (a ``leaky-box") or gas inflow (an ``accreting box"), or both \citep[a ``bathtub" model, e.g.][]{FinlatorDave2008,Bouche2010}.
 The assumptions that go into these models vary dramatically with complexity.

### 2019-03-19 thesis/abstract.tex
Proof read edits. Fixing typos and spelling

--- 2019-03-08 thesis/abstract.tex
@@
 \vskip.35in
-{\Large \bf TITLE HERE}
+{\Large \bf \thesistitle}
 
 \vskip.35in
-{\large YOUR NAME} \\
+{\large Andrew J. Emerick} \\
 \vskip.35in
 \end{center}
-In this \thesis... TEXT HERE
+Motivated by the desire to better understand two of the largest outstanding problems in galactic evolution -- stellar feedback and galactic chemical evolution --
+%In this \thesis
+we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and the multi-channel stellar feedback and multi-element metal yields associated with each star.
+We developed these simulations as a means to better understand the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies.
+We follow the evolution of the individual metal yields associated with these stars in order to better understand how metals mix within the ISM and are ejected into the circumgalactic and itergalactic media (CGM, IGM) through outflows.
+This study is directed with the goal of better understanding the ever increasing quality of stellar abundance measurements within our own Milky Way galaxy and in nearby dwarf galaxies.
+
+Our simulations follow the evolution of an idealized, isolated low mass dwarf galaxy ($M_{\rm vir} \sim 10^{9}$~M$_{\odot}$) over $\sim$ 500 Myr timescales using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
+We implemented a new star formation routine which deposits stars individually from 1~M$_{\odot}$ to 100~M$_{\odot}$.
+Using tabulated stellar properties, we follow the stellar feedback from each star.
+For massive stars ($M_* > 8$~M$_{\odot}$) we follow their stellar winds, ionizing radiation (using an adaptive ray-tracing radiative transfer method), the FUV radiation which leads to photoelectric heating of dust grains, Lyman-Werner radiation, which leads to H$_2$ dissociation, and core collapse supernovae.
+In addition, we follow the asymptotic giant branch (AGB) winds of low-mass stars ($M_* < 8$~M$_{\odot}$) and Type Ia supernovae.
+We investigate how this detailed model for stellar feedback drives the evolution of low mass galaxies.
+We find agreement with previous studies that these low mass dwarf galaxies exhibit bursty, irregular star formation histories with significant feedback-driven winds.
+
+Using these simulations, we investigate the role that stellar radiation feedback plays in the evolution of low mass galaxies.
+% a fiducial, full-physics simulation, second, a simulation with ionizing radiation restricted to the region immediately around massive star particles, and third, a simulation with no ionizing radiation feedback.
+I
+In the regime of low mass dwarf galaxies, we find that the local effects of stellar radiation (within $\sim$ 10~pc of the massive, ionizing source star) act to regulate star formation by rapidly destroying cold, dense gas around newly formed stars.
+For the first time, we find that the long-range radiation effects far from the birth sites are vital for carving channels of diffuse gas in the ISM which dramatically increase the effect of supernovae.
+We find this effect is necessary to drive strong winds with significant mass loading factors and has a significant impact on the metal content of the ISM.
+
+Focusing on the evolution of individual metals within this galaxy, it remains an outstanding question as to what degree (if any) metal mixing processes in a multi-phase ISM influence observed stellar abundance patterns.
+To address this issue, we characterize the time evolution of the metal mass fraction distributions of each of the tracked elements in our simulation in each phase of the ISM.
+For the first time, we demonstrate that there are significant differences in how individual metals are sequestered in each gas phase (from cold, neutral gas up to hot, ionized gas) that depends upon the energetics of the enrichment sources that dominate the production of a given metal species.
+We find that AGB wind elements have much broader distributions (i.e.
+are poorly mixed) as compared to elements released in supernovae.
+In addition, we demonstrate that elements dominated by AGB wind production are retained at a much higher fraction than elements released in core collapse supernovae (by a factor of $\sim$ 5).
+
+We expand upon these findings with a more careful study of how varying the energy and spatial location of a given enrichment event changes how its metal yields mix within the ISM.
+We play particular attention to events that could be associated with different channels of r-process enrichment (for example, neutron star - neutron star mergers vs.
+hypernovae) as a way to characterize how mixing / ejection differences may manifest themselves in observed abundance patters in low mass dwarf galaxies.
+\textbf{Note to self to revisit once this chapter is written...}
+
+Finally, we summarize how this new understanding of galactic chemical evolution -- that metal mixing and ejection from galaxies is not uniform across metal species -- can be used to improve significantly upon current state of the art galactic chemical evolution models.
+These improvements stand to help improve our understanding of galactic chemical evolution and reconcile outstanding disagreements between current models and observations.

### 2019-03-19 thesis/chapters/ch_introduction.tex
reformatting code cases

@@
 
-Historically, codes fall into one of two camps: 1) Eulerian grid-based codes, including the popular codes / algorithms commonly in use (in some way) today such as \code{Zeus} \citep{StoneNorman1992}, \code{FLASH} \citep{FLASH}, \code{RAMSES} \citep{Teyssier2002}, \code{Athena} \citep{Athena}, \code{ART-II} \citep{Rudd2008}, and \code{Enzo} \citep{Enzo2014}, and 2) particle-based Lagrangian methods known as smooth particle hydrodynamics (SPH), such as \code{Gadget} \citep{Springel2005}, \code{PKDGRAV-2} \citep{Stadel2001}, \code{Gasoline} \citep{Wadsley2004}, and \code{Changa} \citep{Menon2015}.
+Historically, codes fall into one of two camps: 1) Eulerian grid-based codes, including the popular codes / algorithms commonly in use (in some way) today such as \code{Zeus} \citep{StoneNorman1992}, \code{flash} \citep{FLASH}, \code{ramses} \citep{Teyssier2002}, \code{Athena} \citep{Athena}, \code{art-II} \citep{Rudd2008}, and \code{Enzo} \citep{Enzo2014}, and 2) particle-based Lagrangian methods known as smooth particle hydrodynamics (SPH), such as \code{Gadget} \citep{Springel2005}, \code{pkdgrav-2} \citep{Stadel2001}, \code{Gasoline} \citep{Wadsley2004}, and \code{Changa} \citep{Menon2015}.
 However, recent codes blur the lines between these distinctions with new algorithms for solving the fluid equations on a moving-mesh \citep[e.g.
-\code{AREPO}][]{Springel2010}, or meshless finite-mass / finite-volume methods \citep[such as those implemented in \code{Gizmo}][]{Hopkins2015}.
-Traditionally these codes were designed to run exclusively on CPUs, but significant work has been made recently to offload various portions onto GPUs, such as \code{GAMER} and \code{GAMER-2} \citep{Schive2010,Schive2018}, \code{GPUGAS} \citep{Kulikov2014}, and \code{CHOLLA} \citep{Schneider2015}.
+\code{arepo}][]{Springel2010}, or meshless finite-mass / finite-volume methods \citep[such as those implemented in \code{Gizmo}][]{Hopkins2015}.
+Traditionally these codes were designed to run exclusively on CPUs, but significant work has been made recently to offload various portions onto GPUs, such as \code{gamer} and \code{gamer-2} \citep{Schive2010,Schive2018}, \code{gpugas} \citep{Kulikov2014}, and \code{cholla} \citep{Schneider2015}.
 Given the large variance in numerical methods, recent studies have examined the differences between these numerical implementations \citep[e.g.][]{Agertz2007}, including large-scale code comparison projects \citep[e.g.][]{AGORA,AGORA2}.

### 2019-03-19 thesis/chapters/ch_introduction.tex
reformatting code cases

@@
 For this reason, many large-scale cosmological simulations assume that all gas is optically thin and that all molecules and ionization states exist in equilibrium.
-This allows for the quick use of tabulated look-up tables for radiative cooling and heating, often produced using \code{CLOUDY} \citep{Cloudy2013}, that depend on gas density, temperature, metallicity, and redshift (which sets the UVB heating rate).
+This allows for the quick use of tabulated look-up tables for radiative cooling and heating, often produced using \code{cloudy} \citep{Cloudy2013}, that depend on gas density, temperature, metallicity, and redshift (which sets the UVB heating rate).
 More complex simulations often track some number (usually $< 10$) of species involved in primordial chemistry in order to better account for non-equilibrium effects and \Hmolecular production, though with noted increases in memory requirements and computational cost.

### 2019-03-22 thesis/chapters/ch_chapter1.tex
Rearranging figures a bit for style. Finished most of them but not complete. Need to double check that left/right (top/bottom) makes sense throughout

@@
 \centering
-\includegraphics[width=0.975\linewidth]{figures/ch1/scale_height}
+\includegraphics[width=0.75\linewidth]{figures/ch1/scale_height}
 \caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:ch1:panel_x} and ~\ref{fig:ch1:panel_z}.}
@@
 %\centering
-\includegraphics[width=0.45\linewidth]{figures/ch1/phase_mass_fraction_evolution_log.png}
-\includegraphics[width=0.45\linewidth]{figures/ch1/phase_volume_fraction_evolution_log.png}
+\includegraphics[width=0.475\linewidth]{figures/ch1/phase_mass_fraction_evolution_log.png}
+\includegraphics[width=0.475\linewidth]{figures/ch1/phase_volume_fraction_evolution_log.png}
 \caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{figures/ch1/G_o_profile} \\
-\includegraphics[width=0.95\linewidth]{figures/ch1/ionizing_photon_profile}
+\includegraphics[width=0.475\linewidth]{figures/ch1/G_o_profile}
+\includegraphics[width=0.475\linewidth]{figures/ch1/ionizing_photon_profile}
 \caption{
@@
 
-\begin{figure*}
+\begin{figure}
 %\centering
-\includegraphics[width=0.45\linewidth]{figures/ch1/g_o_2D_phase}
-\includegraphics[width=0.45\linewidth]{figures/ch1/q_o_2D_phase}
+\includegraphics[width=0.475\linewidth]{figures/ch1/g_o_2D_phase}
+\includegraphics[width=0.475\linewidth]{figures/ch1/q_o_2D_phase}
 \caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
@@
 \label{fig:ch1:ISRF_2D}
-\end{figure*}
+\end{figure}
 
@@
 \begin{figure*}
-\includegraphics[width=0.45\linewidth]{figures/ch1/total_mass_outflow}
-\includegraphics[width=0.45\linewidth]{figures/ch1/total_mass_loading}
+\includegraphics[width=0.475\linewidth]{figures/ch1/total_mass_outflow}
+\includegraphics[width=0.475\linewidth]{figures/ch1/total_mass_loading}
 \caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
@@
 \begin{figure}
-\includegraphics[width=0.95\linewidth]{figures/ch1/velocity_distribution_time_average}
+\centering
+\includegraphics[width=0.75\linewidth]{figures/ch1/velocity_distribution_time_average}
 \caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
@@
 This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
-In the top panel of Fig.~\ref{fig:ch1:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}.
+In the left panel of Fig.~\ref{fig:ch1:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}.
 The parameter used to quantify metal outflow efficiencies varies among works.
@@
 \begin{figure}
-\includegraphics[width=0.9\linewidth]{figures/ch1/metal_mass_loading} \\
-\includegraphics[width=0.9\linewidth]{figures/ch1/metal_retention}
-\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}.
+\includegraphics[width=0.475\linewidth]{figures/ch1/metal_mass_loading}
+\includegraphics[width=0.475\linewidth]{figures/ch1/metal_retention}
+\caption{{\bf Left}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}.
 This is the ratio between the metal outflow rate and the metal production rate.
-{\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
+{\bf Right}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time.
 In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
@@
 These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
-This is quantified in the lower panel of Fig.~\ref{fig:ch1:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
+This is quantified in the right panel of Fig.~\ref{fig:ch1:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
 After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
@@
 \centering
-\includegraphics[width=0.475\linewidth]{figures/ch1/all_gas_schmidt_law_evolution.png}
-\includegraphics[width=0.475\linewidth]{figures/ch1/all_gas_efficiency_evolution.png}
-\caption{The Kennicutt-Schmidt law (left) and extended Schmidt law (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
+\includegraphics[width=0.5\linewidth]{figures/ch1/all_gas_schmidt_law_evolution.png}\\
+\includegraphics[width=0.5\linewidth]{figures/ch1/all_gas_efficiency_evolution.png}
+\caption{The Kennicutt-Schmidt law (top) and extended Schmidt law (bottom) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late.
 See text for details of the calculation.
@@
 \centering
-\includegraphics[width=0.95\linewidth]{figures/ch1/fH2.png}
+\includegraphics[width=0.75\linewidth]{figures/ch1/fH2.png}
 \caption{The final H$_2$ mass fraction in a grid of one-zone Grackle cooling models run with the same Grackle parameters and metallicity as our full hydrodynamics simulation.
@@
 \centering
-\includegraphics[width=0.33\linewidth]{figures/ch1/sfr_resolution_study.png}
-\includegraphics[width=0.33\linewidth]{figures/ch1/mass_evolution_resolution.png}
-\includegraphics[width=0.33\linewidth]{figures/ch1/metal_retention_resolution.png}
+\includegraphics[width=0.475\linewidth]{figures/ch1/sfr_resolution_study.png}
+\includegraphics[width=0.475\linewidth]{figures/ch1/mass_evolution_resolution.png}\\
+\includegraphics[width=0.475\linewidth]{figures/ch1/metal_retention_resolution.png}
 \caption{A comparison of the SFR (left), disk gas mass (middle), and metal retention (right) evolution for our fiducial run (solid), 3.6~pc run (dotted), 3.6~pc run with a doubled initial supernova driving rate (dashed), and 7.2~pc run (dash-dotted).
@@
 \centering
-\includegraphics[width=0.475\linewidth]{figures/ch1/3pc_phase.png}
-\includegraphics[width=0.475\linewidth]{figures/ch1/6pc_phase.png}
+\includegraphics[width=0.75\linewidth]{figures/ch1/3pc_phase.png}\\
+\includegraphics[width=0.75\linewidth]{figures/ch1/6pc_phase.png}
 \caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:ch1:phase}.}

### 2019-03-27 thesis/chapters/ch_chapter3.tex
updated section and figure labels with ch3 prepend to be consistent within thesis

@@
 
-We summarize our methods and physics models in Section~\ref{sec:methods}.
-We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}.
-In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
-We discuss our results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusions}.
+We summarize our methods and physics models in Section~\ref{ch3:sec:methods}.
+We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{ch3:sec:ejection}.
+In Section~\ref{ch3:sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.
+We discuss our results in Section~\ref{ch3:sec:discussion}, and conclude in Section~\ref{ch3:sec:conclusions}.
 
@@
 \section{Methods}
-\label{sec:methods}
+\label{ch3:sec:methods}
 We refer the reader to Paper I for a detailed description of our numerical methods and feedback models. We briefly summarize the relevant details here.
@@
 In this work we focus in detail on how each of the 15 individual metal species evolve in this galaxy.
-We address differences between the ejection fractions of each metal in Section~\ref{sec:ejection} and analyze for the first time the mass-fraction PDFs of the metals retained by the ISM in Section~\ref{sec:mixing}.
+We address differences between the ejection fractions of each metal in Section~\ref{ch3:sec:ejection} and analyze for the first time the mass-fraction PDFs of the metals retained by the ISM in Section~\ref{ch3:sec:mixing}.
 
 \subsection{Preferential Ejection of Metals from the ISM}
-\label{sec:ejection}
+\label{ch3:sec:ejection}
 
@@
 The leftmost bar in each plot shows the sum of all metals.}
-\label{fig:species_fractions}
+\label{ch3:fig:species_fractions}
 \end{figure*}
@@
 %mm [this all seems to have been deleted in one version, but doesn't look like it should have been.  Down to ">>>>"] <<<<<<< HEAD
-The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
+The top panel of Figure~\ref{ch3:fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
 We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).\footnote{The $f_{\rm H_2}$ restriction on the CNM is not relevant in our simulations, as there are no cells with $f_{\rm H_2} > 0.5$.
@@
 The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
-This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
+This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{ch3:sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
 
-%The top panel of Figure~\ref{fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
+%The top panel of Figure~\ref{ch3:fig:species_fractions} gives the mass fraction of each element at the end of the simulation (500~Myr) in each of four reservoirs: locked in stars (yellow), in the ISM (blue), outside the galaxy but within the virial radius (purple), and outside the virial radius (salmon), including gas that has left the domain.
 We subdivide the ISM by phase in the bottom panel, giving the mass fractions of each element in the cold neutral medium (CNM, $f_{\rm H_2} < 0.5$,  T$< 100$~K), warm neutral medium (WNM, $10^2~\rm{K}\le \rm{T} < 10^4~\rm{K}$), warm ionized medium (WIM, $10^4~\rm{K}\le \rm{T} < 10^{5.5}~\rm{K}$), the hot ionized medium (HIM T$\ge 10^{5.5}$~K), and locked in stars (yellow).
@@
 The exact fraction varies with each species, most notably for carbon; these fluctuations are at most $\sim 10$\%.
-This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
+This is not surprising, as the cold phases represent the majority of the mass in the ISM, but, as shown in Section~\ref{ch3:sec:statistics}, even though the cold phases harbor most of the metals, the hot phases have significantly higher metal mass fractions.
 Second, only a small fraction of produced metals are retained within the dwarf galaxy, in agreement with observations of nearby dwarf galaxies \citep[see][]{Kirby2011-metals, McQuinn2015}; however, the retention factor varies.
@@
 
-\label{fig:species_sources}
+\label{ch3:fig:species_sources}
 \end{figure*}
@@
 These channels differ in: 1) how long after a given star formation event they occur, 2), by consequence, the typical ISM properties in which they occur, and 3) how much energy is associated with each event, which determines ejecta temperature and velocity.
-To understand where each of the elements in Figure~\ref{fig:species_fractions} originated, we show the mass fraction of metals produced through each channel in Figure~\ref{fig:species_sources}.
+To understand where each of the elements in Figure~\ref{ch3:fig:species_fractions} originated, we show the mass fraction of metals produced through each channel in Figure~\ref{ch3:fig:species_sources}.
 Core collapse SNe are responsible for over 90\% of the total metal enrichment in our galaxy, but this is clearly not true for all elements.
@@
 but maybe not if they aren't very stable....
-We discuss how this result may extend towards other metal yields that are not well sampled on our relatively short (500 Myr) simulation timescales in Section~\ref{sec:discussion:metal yields}.
+We discuss how this result may extend towards other metal yields that are not well sampled on our relatively short (500 Myr) simulation timescales in Section~\ref{ch3:sec:discussion:metal yields}.
 
@@
 The changes in typical ISM density and height of these events contributes to these variations.
-We show histograms of the average number density within 20~pc of any given enrichment source (top) and height above/below the disk (bottom) within 1~Myr of each event (as limited by our output cadence) in Figure~\ref{fig:spatial distribution}.
+We show histograms of the average number density within 20~pc of any given enrichment source (top) and height above/below the disk (bottom) within 1~Myr of each event (as limited by our output cadence) in Figure~\ref{ch3:fig:spatial distribution}.
 As shown, SNe peak at very low densities, indicating that most explode in superbubbles, regions carved out by previous SNe.
@@
 \caption{The volume-averaged gas number densities within 20~pc of a given event (top) and vertical position above/below the disk (bottom) within 1~Myr before the event.}
-\label{fig:spatial distribution}
+\label{ch3:fig:spatial distribution}
 \end{figure}
@@
 \subsection{Mixing and Distribution of Metals in the ISM}
-\label{sec:mixing}
-We characterize the metal distributions (in Sections~\ref{sec:log-normal} and \ref{sec:phase-pdfs}) and evolution (in Section~\ref{sec:statistics}) in our galaxy to build towards a  a complete model for how metals mix and evolve in the complex, multi-phase ISM of real galaxies.
+\label{ch3:sec:mixing}
+We characterize the metal distributions (in Sections~\ref{ch3:sec:log-normal} and \ref{ch3:sec:phase-pdfs}) and evolution (in Section~\ref{ch3:sec:statistics}) in our galaxy to build towards a  a complete model for how metals mix and evolve in the complex, multi-phase ISM of real galaxies.
 
 \subsubsection{A Functional Form for Metal PDFs}
-\label{sec:log-normal}
+\label{ch3:sec:log-normal}
 
@@
 We demonstrate here for the first time that the mass fraction PDFs for each metal species in our simulation can indeed be well fit using a piecewise log-normal + power-law PDF.
-We use a simple conceptual model in Section~\ref{sec:interpretation} to motivate the emergence of this distribution.
+We use a simple conceptual model in Section~\ref{ch3:sec:interpretation} to motivate the emergence of this distribution.
 
@@
 
-We show in Figure~\ref{fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
+We show in Figure~\ref{ch3:fig:log-normal} the numerical PDFs (solid histograms) and log-normal + power-law fits (dashed lines) across individual gas phases.
 These PDFs have been computed at an arbitrary single point in time in the middle of the simulation run.
@@
 \includegraphics[width=0.95\linewidth]{figures/ch3/DD0390_element_by_element}
-\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black).
+\caption{The numerical PDFs (solid histograms) and the associated log-normal + power-law fits (dashed lines) for a subset of the elements tracked in our simulation in each of the four gas phases defined in Section~\ref{ch3:sec:ejection}: CNM (dark blue), WNM (light blue), WIM (light orange), HIM (red), and all the gas in the ISM (black).
 For clarity, each distribution is normalized to the mode of the full-disk PDF (black) and is centered on the median value of the full-disk PDF.
@@
 Since the CNM dominates the mass fraction of our galaxy, the black curve is often obscured at low metal fractions.}
-\label{fig:log-normal}
+\label{ch3:fig:log-normal}
 \end{figure*}
@@
 \subsubsection{PDF Variation Across Gas Phase}
-\label{sec:phase-pdfs}
+\label{ch3:sec:phase-pdfs}
 
-The various phases represented in Figure~\ref{fig:log-normal} involve variations in density and temperature of more than six orders of magnitude.
+The various phases represented in Figure~\ref{ch3:fig:log-normal} involve variations in density and temperature of more than six orders of magnitude.
 The evolution of each phase is qualitatively different, and the metal mixing behavior of each should vary.
@@
 In addition, one would expect a metallicity gradient with gas temperature as enrichment occurs first in the hot phases, cooling and enriching denser gas over time.
-We examine the PDF variations among elements in each phase, as shown in Figure~\ref{fig:log-normal}, in more detail here.
+We examine the PDF variations among elements in each phase, as shown in Figure~\ref{ch3:fig:log-normal}, in more detail here.
 
@@
 \subsubsection{The Time Evolution of Metal PDFs}
-\label{sec:statistics}
+\label{ch3:sec:statistics}
 We focus on the time evolution of the full numerical PDFs in this section.
 Our results here do not depend upon the choice of functional form for $p(Z)$.
-Figure~\ref{fig:phase-statistics} shows the evolution of four different statistics for the O (top) and Ba (bottom) PDFs.
+Figure~\ref{ch3:fig:phase-statistics} shows the evolution of four different statistics for the O (top) and Ba (bottom) PDFs.
 These two elements are treated as representative elements for SN and AGB wind production respectively.
@@
 The panels show log$_{10}$ of the median (left), the difference, in dex, between the mean and the median (middle), and the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile difference in dex (right).}
-\label{fig:phase-statistics}
+\label{ch3:fig:phase-statistics}
 \end{figure*}
@@
 Given their lower energies, AGB winds more directly enrich the WNM and WIM, not the HIM as in SNe.
-The consequence of this is clear in Figure~\ref{fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
+The consequence of this is clear in Figure~\ref{ch3:fig:log-normal} by the wider PDFs and longer power-law tails in Ba in these phases.
 These tails represent the most recently enriched gas,
@@
 
-To summarize, Figure~\ref{fig:phase-statistics} demonstrates: 1) there are qualitative differences in how SN-injected elements (e.g.
+To summarize, Figure~\ref{ch3:fig:phase-statistics} demonstrates: 1) there are qualitative differences in how SN-injected elements (e.g.
 O, Mg) and AGB-wind-injected elements (e.g.
@@
 \section{Discussion}
-\label{sec:discussion}
-We begin with a simple toy model that motivates the power-law tail at high metal fractions of the metal fraction PDFs and a subsequent turnover at low metal fractions in Section~\ref{sec:interpretation}.
-This work is placed in context with previous papers focusing on metal mixing in the ISM in Section~\ref{sec:context}.
-We discuss the relevance of additional AGB yields not directly followed in this study in Section~\ref{sec:discussion:metal yields}.
-Finally, in Section~\ref{sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{sec:massive galaxies}, and discuss possible impacts of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{sec:exotic enrichment}.
+\label{ch3:sec:discussion}
+We begin with a simple toy model that motivates the power-law tail at high metal fractions of the metal fraction PDFs and a subsequent turnover at low metal fractions in Section~\ref{ch3:sec:interpretation}.
+This work is placed in context with previous papers focusing on metal mixing in the ISM in Section~\ref{ch3:sec:context}.
+We discuss the relevance of additional AGB yields not directly followed in this study in Section~\ref{ch3:sec:discussion:metal yields}.
+Finally, in Section~\ref{ch3:sec:stellar abundances} we discuss how these results relate to stellar abundances, make generalizations to more massive galaxies in Section~\ref{ch3:sec:massive galaxies}, and discuss possible impacts of these results on chemical enrichment from more exotic nucleosynthetic sources in Section~\ref{ch3:sec:exotic enrichment}.
 
 \subsection{Physical Interpretation of the PDF}
-\label{sec:interpretation}
+\label{ch3:sec:interpretation}
 %
@@
 %mm [additive vs multiplicative]
-   %{\bf [According to Section~\ref{sec:log-normal}, MULTIPLICATIVE processes produce log-normals. Additive processes produce power-laws.  However, see Mouri (2013) for a possible counterexample...]}
+   %{\bf [According to Section~\ref{ch3:sec:log-normal}, MULTIPLICATIVE processes produce log-normals.
+Additive processes produce power-laws.
+However, see Mouri (2013) for a possible counterexample...]}
 The physical interpretation of these two components is that the power-law tail represents newly enriched and poorly mixed gas that is above the average gas metallicity and is undergoing dilution, while the log-normal component represents the ambient medium that lies below the average gas metallicity and is undergoing enrichment.
@@
 Previous Studies of Metal Mixing}
-\label{sec:context}
+\label{ch3:sec:context}
 That metal fraction distributions can be described using simple analytic log-normal + power-law PDFs, even in a complex, multi-phase ISM, has not been demonstrated prior to this work.
@@
 However, these works uniformly do not contain the high metallicity power-law tails shown in our work.
-As suggested by our toy model in Section~\ref{sec:interpretation}, this is due to the lack of ongoing enrichment in these studies.
+As suggested by our toy model in Section~\ref{ch3:sec:interpretation}, this is due to the lack of ongoing enrichment in these studies.
 
@@
 \subsection{Timescale Dependence of AGB Ejecta}
-\label{sec:discussion:metal yields}
+\label{ch3:sec:discussion:metal yields}
 We can generally say that metals ejected in AGB winds evolve qualitatively differently than metals produced by SNe in our dwarf galaxy.
@@
 
-To illustrate some of these differences, Figure~\ref{fig:agb evolution} gives the fraction of a given metal ejected by AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times.
+To illustrate some of these differences, Figure~\ref{ch3:fig:agb evolution} gives the fraction of a given metal ejected by AGB winds relative to the total amount of that metal produced in a single-age stellar population with a metal fraction of $Z = 10^{-4}$ at four different times.
 This model was run using \textsc{SYGMA} \citep{Ritter2018b}.
@@
 The horizontal line marks a 50\% contribution.}
-\label{fig:agb evolution}
+\label{ch3:fig:agb evolution}
 \end{figure*}
@@
 \subsection{Impact on Stellar Abundance Patterns}
-\label{sec:stellar abundances}
+\label{ch3:sec:stellar abundances}
 In order to better understand the physics driving stellar abundance patterns and distributions it is important to characterize the chemical evolution of star-forming gas in our simulations.
@@
 However, star-forming gas originates from the CNM, so it is reasonable to expect that this gas, and therefore stars themselves, to have mass fraction PDFs similar to the CNM.
-To verify this, Figure ~\ref{fig:stars} shows the difference between the oxygen mass fraction of stars and the median mass fraction from the CNM PDF at the time that particle formed.
+To verify this, Figure ~\ref{ch3:fig:stars} shows the difference between the oxygen mass fraction of stars and the median mass fraction from the CNM PDF at the time that particle formed.
 The large scatter at early times ($<$ 120~Myr) is a result of the early enrichment phase, when the initial gas oxygen mass fraction was zero.
@@
 However, for stars formed after the initial phase, the median separation from the CNM median is 0.31~dex, and can reach up to $\sim$~0.5~dex.
-Though a significant deviation, this is smaller than the typical inner-quartile range (IQR) of the CNM (see Figure~\ref{fig:phase-statistics}).
+Though a significant deviation, this is smaller than the typical inner-quartile range (IQR) of the CNM (see Figure~\ref{ch3:fig:phase-statistics}).
 Additionally, if we further subdivide the CNM by density, the metal fraction PDFs narrow and tend towards the median value as a function of increasing density.
@@
 The median deviation is given in the plot for stars formed after the initial star formation and enrichment period (120~Myr.)}
-\label{fig:stars}
+\label{ch3:fig:stars}
 \end{figure}
@@
 \subsection{Do These Results Apply to More Massive Galaxies?}
-\label{sec:massive galaxies}
+\label{ch3:sec:massive galaxies}
 An important caveat about our work is that these results are derived from simulations of an isolated, low mass, dwarf galaxy whose properties vary dramatically from more massive galaxies like the Milky Way.
@@
 Feedback-driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas.
-We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy.
+We expect the results presented in Figure~\ref{ch3:fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy.
 With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate.
@@
 
-In contrast, we expect the properties of the enrichment PDFs, and the variations between AGB enriched elements and SN enriched elements (as presented in Figures~\ref{fig:log-normal} and ~\ref{fig:phase-statistics}), to be general.
+In contrast, we expect the properties of the enrichment PDFs, and the variations between AGB enriched elements and SN enriched elements (as presented in Figures~\ref{ch3:fig:log-normal} and ~\ref{ch3:fig:phase-statistics}), to be general.
 We expect metals to exhibit log-normal + power-law distributions in the ISM of all galaxies, with similar trends with enrichment source and gas phase as outlined here.
@@
 \subsection{Implications for Exotic Enrichment Sources}
-\label{sec:exotic enrichment}
+\label{ch3:sec:exotic enrichment}
 %   AE: Benoit suggested removing arguments relating to NS-NS merger energetics as I had misred / miscaclulated the energy release values.
@@
 \subsection{Individual Stars vs. Averaged Yields}
-\label{sec:SSP yields}
+\label{ch3:sec:SSP yields}
 Typical models for chemical enrichment in galaxy-scale simulations apply some form of IMF-averaged nucleosynthetic yields.
@@
 \section{Conclusions}
-\label{sec:conclusions}
+\label{ch3:sec:conclusions}
 We present a detailed analysis of galactic chemodynamics and metal mixing on an element-by-element basis in a low mass dwarf galaxy with hydrodynamics simulations that simultaneously capture multi-channel stellar feedback in detail with a multi-phase ISM.
@@
 \section{Density PDF}
-\label{appendix:density PDF}
-We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HQM2012}.
+\label{ch3:appendix:density PDF}
+We show the density PDF in Figure~\ref{ch3:fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HQM2012}.
 We show the mass-weighted PDF ($dm/Md\log n$) on the left, and the volume-weighted PDF ($dv/Vd\log n$) on the right.
@@
 The total distribution is given in black, sub-divided by the contributions of the individual phases in the ISM.}
-\label{fig:density_pdf}
+\label{ch3:fig:density_pdf}
 \end{figure}
@@
 We refer the reader to Paper I for a previous comparison of these simulations to our fiducial run.
-In Figure~\ref{fig:resolution-phase} we demonstrate that O and Ba abundances behave qualitatively similar in our lower resolution runs as in our fiducial model.
+In Figure~\ref{ch3:fig:resolution-phase} we demonstrate that O and Ba abundances behave qualitatively similar in our lower resolution runs as in our fiducial model.
 In both lower resolution runs O has a generally tighter distribution that narrows over time, while Ba is much less well mixed, in agreement with our fiducial simulation.
@@
 \caption{Resolution comparison of two lower resolution runs giving the log difference between the 90$^{\rm th}$ decile and 10$^{\rm th}$ decile in dex for the metal PDFS of O and Ba across all phases.
-Compare to Figure~\ref{fig:phase-statistics}.}
-\label{fig:resolution-phase}
+Compare to Figure~\ref{ch3:fig:phase-statistics}.}
+\label{ch3:fig:resolution-phase}
 \end{figure*}

### 2019-03-27 thesis/chapters/ch_chapter4.tex
Began writing

@@
 \section*{Acknowledgments}
+
+\section{Methods}
+\label{ch4:sec:methods}
+We refer the reader to the previous chapters for more detailed descriptions of our numerical methods and feedback models.
+The mixing experiments discussed below are conducted in restarted versions of the same low-mass, isolated galaxy simulations used throughout this work.
+
+%We refer the reader to Paper I for a detailed description of our numerical methods and feedback models. We briefly summarize the relevant details here.
+
+% Summarize details here for the paper, but I'm not sure if its needed for the thesis chapter.
+
+\subsection{Mixing Experiment Setup}
+\label{ch4:sec:experiment}
+We restart our fiducial, full-physics simulation at three different times, 100 Myr, 180 Myr, and 360 Myr; runs at these times are labelled as I, II, and III respectively.
+These correspond to three different times in the galaxy's SFR evolution, testing how much variance is expected in the metal mixing and ejection with the star formation rate.
+I occurs in the last $\sim$ 20 Myr of the initial burst of star formation, II occur during the lull in star formation following this peak, and III in an extended period of little to no ongoing star formation.
+We attempted to to evolve each simulation for 150 Myr, but due to computational constrains (particularly with the I runs) this was not always possible.
+
+At the beginning of each restart, we place by-hand one or more enrichment events at assigned positions throughout the galaxy, with thermal injection energies ($E_{\rm ej}$), masses ($m_{\rm ej}$), and metal fractions ($Z_{\rm ej}$).
+We note that the injection masses, particularly the metal fractions, are somewhat arbitrary as they are likely dynamically insigificant relative to the ambient ISM mass in which they occur.
+The important parameter here is $E_{\rm ej}$, which we vary to sample the range of ejection energies associated with significant sources of chemical enrichment, including AGB winds ($10^{46}$~erg)\footnote{Assuming full thermalization of the total mechanical energy output of an AGB wind.}, NS-NS mergers ($10^{49} - 10^{50}$~erg), supernovae (10$^{51}$~erg), and exotic enrichment sources, such as hypernovae, that can reach much higher energies (10$^{52}$~erg).
+Each run contains only sources from a single event type, as indicated in the run-name by the log of the injection energy in ergs.
+For example, the run beginning at 180~Myr with AGB-like events is labelled ``II_E46".
+The metal enrichment from each source is tracked and evolved with a unique passive scalar tied to the individual source and separate from any additional chemical enrichement that may occur within the galaxy over time.
+
+Each run contains multiple events spread over the galaxy to test how radial and azimuthal position in the galaxy affects mixing and ejection, but limited to ensure that the events do not overlap and influence each other dynamically.
+For the low-energy events, we are able to run 19 events per restart, while the $10^{49}-10^{51}$~erg runs contain 7 events, and the 10$^{52}$~erg runs only contain a single event.
+
+Most of this analysis refers to these average behavior of the metals from these enrichment events over time as a way to gain a general appreciation for how $E_{\rm ej}$ and galactic properties affect the evolution of metals.
+However, we do note that this is not fair statistically, as the higher energy runs are undersampled.
+
+%We discuss how radial and azimuthal position affects the evolution in
+
+\section{Results}
+
+Perhaps the three most important paramters to quantify for each enrichment event are: 1) what fraction of released metals are immediately available for star formation, 2) what fraction of metals are carried out of the galaxy in outflows, and 3) how and over what timescale do metals cool from hot phases into star forming gas.
+We discuss each of these points in Section~\ref{ch4:sec:ISM CGM}.
+In Section~\ref{ch4:sec:spreads} we go further and address the relative homogeneity of the metals retained by the ISM for each enrichment source.
+
+We focus this analysis primarily on the results from run II, and save a discussion of how these results vary across runs and across specific source positions in Section XXX \textit{(maybe take out if don't have time)}.
+
+\subsection{Enrichment of the ISM and CGM}
+\label{ch4:sec:ISM CGM}
+
+We summarize the source-averaged results for all enrichment events in runs II_E46, II_E49, II_E50, II_E51, and II_E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid).
+These plots show a clear, immediate trend across $E_{\rm ej}$ for all lines in the figure, but the differences are most striking for the ISM (black, solid), CGM (black, dashed) lines.
+
+\subsection{Homogeneity of Mixing}
+\label{ch4:sec:spreads}
 

### 2019-03-27 thesis/chapters/ch_chapter4.tex
more writing

@@
 At the beginning of each restart, we place by-hand one or more enrichment events at assigned positions throughout the galaxy, with thermal injection energies ($E_{\rm ej}$), masses ($m_{\rm ej}$), and metal fractions ($Z_{\rm ej}$).
-We note that the injection masses, particularly the metal fractions, are somewhat arbitrary as they are likely dynamically insigificant relative to the ambient ISM mass in which they occur.
+We note that the injection masses, particularly the metal fractions, are somewhat arbitrary as they are likely dynamically insignificant relative to the ambient ISM mass in which they occur.
 The important parameter here is $E_{\rm ej}$, which we vary to sample the range of ejection energies associated with significant sources of chemical enrichment, including AGB winds ($10^{46}$~erg)\footnote{Assuming full thermalization of the total mechanical energy output of an AGB wind.}, NS-NS mergers ($10^{49} - 10^{50}$~erg), supernovae (10$^{51}$~erg), and exotic enrichment sources, such as hypernovae, that can reach much higher energies (10$^{52}$~erg).
 Each run contains only sources from a single event type, as indicated in the run-name by the log of the injection energy in ergs.
-For example, the run beginning at 180~Myr with AGB-like events is labelled ``II_E46".
-The metal enrichment from each source is tracked and evolved with a unique passive scalar tied to the individual source and separate from any additional chemical enrichement that may occur within the galaxy over time.
+For example, the run beginning at 180~Myr with AGB-like events is labeled ``II\_E46".
+The metal enrichment from each source is tracked and evolved with a unique passive scalar tied to the individual source and separate from any additional chemical enrichment that may occur within the galaxy over time.
 
@@
 
-Perhaps the three most important paramters to quantify for each enrichment event are: 1) what fraction of released metals are immediately available for star formation, 2) what fraction of metals are carried out of the galaxy in outflows, and 3) how and over what timescale do metals cool from hot phases into star forming gas.
+Perhaps the three most important parameters to quantify for each enrichment event are: 1) what fraction of released metals are immediately available for star formation, 2) what fraction of metals are carried out of the galaxy in outflows, and 3) how and over what timescale do metals cool from hot phases into star forming gas.
 We discuss each of these points in Section~\ref{ch4:sec:ISM CGM}.
@@
 
-We summarize the source-averaged results for all enrichment events in runs II_E46, II_E49, II_E50, II_E51, and II_E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid).
+We summarize the source-averaged results for all enrichment events in runs II\_E46, II\_E49, II\_E50, II\_E51, and II\_E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid).
 These plots show a clear, immediate trend across $E_{\rm ej}$ for all lines in the figure, but the differences are most striking for the ISM (black, solid), CGM (black, dashed) lines.
+In Chapter~\ref{ch:chapter3}
+% \citep{Emerick2019}
+we demonstrated that there was a significant difference in metal ejection fraction, $f_{\rm ej}$, for metals from AGB sources as compared to metals released in SNe.
+Here, we confirm that this is driven predominantly by differences in the energy of the events, and not necessarily when or where they occur in the ISM.
+The clear trend in Figure~\ref{ch4:fig:ISM_CGM} shows that events with higher $E_{\rm ej}$ are much more readily ejected from the disk of the galaxy, while events with lower $E_{\rm ej}$ couple poorly to the same galactic outflows.
+\textit{statement on how immediate enrichement is after events}
+% By 10~Myr after the enrichment events,
+The high-energy events rapidly converge on a peak $f_{\rm ej}$ within about 20~Myr of the event, with only a gradual increase towards the end of the 150~Myr as the metals in the ISM are swept up in additional outflows.
+The lower energy events evolve more gradually.
+The lowest energy event, corresponding to AGB winds, reaches $f_{\rm ej}$ ~ 0.68, which increases to 0.87 for the 10$^{51}$~erg events, and 0.95 for the 10$^{52}$~erg event.
+This implies that, if one to were assume that all metals behaved the same and adopted an $f_{\rm ej}$ of $\sim$0.9, typical of SNe-like events (and which is comparable to that observed for O in Local Group dwarf galaxies, \citep{Kirby2011,McQuinn2015}), one would underestimate the amount of AGB metals in the ISM by a factor of $\sim$ 3, and overestimate exotic, high-energy sources by a factor of $\sim$2.
+% This ejection fraction is a critical ingredient in chemical evolution models, and the fact that it varies with enrichment source can
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.45\linewidth]{figures/ch4/AGB1_enrichment_evolution_average_CGM}
+\includegraphics[width=0.45\linewidth]{figures/ch4/NSNS1_enrichment_evolution_average_CGM} \\
+\includegraphics[width=0.45\linewidth]{figures/ch4/SNE1_enrichment_evolution_average_CGM}
+\includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
+\caption{Time evolution of the }
+\label{fig:ch4:ISM_CGM}
+\end{figure*}
+
+% make a figure here showing JUST the CNM evolution of the ISM for each source
 

### 2019-03-28 thesis/chapters/ch_chapter4.tex
updates

@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=0.45\linewidth]{figures/ch4/AGB1_enrichment_evolution_average_CGM}
+\includegraphics[width=0.45\linewidth]{figures/ch4/NSNS1_enrichment_evolution_average_CGM} \\
+\includegraphics[width=0.45\linewidth]{figures/ch4/SNE1_enrichment_evolution_average_CGM}
+\includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
+\caption{Time evolution of the }
+\label{ch4:fig:ISM_CGM}
+\end{figure*}
+
 We summarize the source-averaged results for all enrichment events in runs II\_E46, II\_E49, II\_E50, II\_E51, and II\_E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid).
@@
 The lowest energy event, corresponding to AGB winds, reaches $f_{\rm ej}$ ~ 0.68, which increases to 0.87 for the 10$^{51}$~erg events, and 0.95 for the 10$^{52}$~erg event.
-This implies that, if one to were assume that all metals behaved the same and adopted an $f_{\rm ej}$ of $\sim$0.9, typical of SNe-like events (and which is comparable to that observed for O in Local Group dwarf galaxies, \citep{Kirby2011,McQuinn2015}), one would underestimate the amount of AGB metals in the ISM by a factor of $\sim$ 3, and overestimate exotic, high-energy sources by a factor of $\sim$2.
-% This ejection fraction is a critical ingredient in chemical evolution models, and the fact that it varies with enrichment source can
+This implies that, if one to were assume that all metals behaved the same and adopted an $f_{\rm ej}$ of $\sim$0.9 -- typical for the total metal ejection fraction in simulations that do not track individual enrichment channels \citep[e.g.][]{Muratov2017,Christensen2018}, and consistent with observations of the O abundance in Local Group dwarf galaxies \citep[e.g.][]{Kirby2011,McQuinn2015} -- one would underestimate the amount of AGB metals in the ISM by a factor of $\sim$ 3, and overestimate exotic, high-energy sources by a factor of $\sim$ 2.
+In each case, these are metals that cannot participate in the enrichment of future stellar populations.
+
+In all cases, the metals contained with the ISM are deposited predominately in the ionized phases of the ISM, the WIM or the HIM, with the relative fraction in each phase driven by the energy of the event.
+Metals in the ISM injected with $E_{\rm ej} > 10^{49}$~erg are initially located predominately in the HIM, roughly 1/2 for $E_{\rm ej} = 10^{49}$~erg and nearly all for $E_{\rm ej} > 10^{52}$~erg.
+The lowest energy events are initially in the WIM and WNM, tracing the two dominant volume-filling components of the ISM (see Chatper~\ref{ch:chapter1}), as these events do not have sufficient energy to generate the HIM phase by themselves.
+In general, very few of these elements are available for immediate star formation in the CNM.
+However, we note that we may not have sufficient resolution to properly resolve the details of the initial mixing of individual enrichment events in the ISM.
+In addition, we are missing important physical processes, like dust production in AGB winds and core collapse SNe, that may affect these results for specific enrichment channels in ways that do not depend solely on $E_{\rm ej}$.
+Resolving these processes in detail in galaxy-scale simulations is computationally infeasible.
+
+Finally, we are interested in the long-term evolution of the metals from each of these sources, and how long it takes for these metals to propogate from the warm / hot phases of the ISM to cold, star forming gas.
+Gas above the star formation threshold in our simulations is limited and short-lived due to the low gas surface densities and star formation rates in this galaxy and the efficiency of stellar feedback from newly formed stars.
+As a proxy, we examine the evolution of the CNM, out of which the star forming gas forms.
+In Figure~\ref{ch4:fig:CNM}, we examine the evolution of the metal fraction of the CNM \textit{for just those elements retained in the ISM] for the average behavior of each enrichment event.
 
@@
   \centering
-\includegraphics[width=0.45\linewidth]{figures/ch4/AGB1_enrichment_evolution_average_CGM}
-\includegraphics[width=0.45\linewidth]{figures/ch4/NSNS1_enrichment_evolution_average_CGM} \\
-\includegraphics[width=0.45\linewidth]{figures/ch4/SNE1_enrichment_evolution_average_CGM}
-\includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
-\caption{Time evolution of the }
-\label{fig:ch4:ISM_CGM}
+  \includegraphics[width=0.75\linewidth]{figures/ch4/CNM_evolution_average}
+  \caption{Time evolution of the metal fraction of the CNM for just those metals retained in the ISM for each enrichment source. In other words,
+           these are the same CNM lines as shown in Figure~\ref{ch4:fig:ISM_CGM}, but are divided by the black, dashed lines in each panel.}
+  \label{ch4:fig:CNM}
 \end{figure*}
-
 % make a figure here showing JUST the CNM evolution of the ISM for each source

### 2019-03-28 thesis/chapters/ch_chapter1.tex
Changing figure labels and references to something more logical

@@
 
-We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Fig.~\ref{fig:ch1:panel_x} and Fig.~\ref{fig:ch1:panel_z}.
+We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Fig.~\ref{ch1:figpanel_x} and Fig.~\ref{ch1:figpanel_z}.
 These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
@@
 Each individual main sequence star particle is shown in the number density projections as a single white dot.}
-\label{fig:ch1:panel_x}
-\end{figure*}
-
-The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{fig:ch1:scale_height}.
+\label{ch1:figpanel_x}
+\end{figure*}
+
+The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{ch1:figscale_height}.
 This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time.
@@
 For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
-In the final column of Fig.~\ref{fig:ch1:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
+In the final column of Fig.~\ref{ch1:figpanel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
 With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
@@
 \includegraphics[width=0.975\linewidth]{figures/ch1/multiplot_4x4_z.png}
-\caption{Same as Fig.~\ref{fig:ch1:panel_x}, but showing face-on views.}
-\label{fig:ch1:panel_z}
+\caption{Same as Fig.~\ref{ch1:figpanel_x}, but showing face-on views.}
+\label{ch1:figpanel_z}
 \end{figure*}
@@
 \includegraphics[width=0.75\linewidth]{figures/ch1/scale_height}
-\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:ch1:panel_x} and ~\ref{fig:ch1:panel_z}.}
-\label{fig:ch1:scale_height}
+\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{ch1:figpanel_x} and ~\ref{ch1:figpanel_z}.}
+\label{ch1:figscale_height}
 \end{figure}
@@
 
-We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Fig.~\ref{fig:ch1:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
+We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Fig.~\ref{ch1:figsfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
 The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$.
@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Fig.~\ref{fig:ch1:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
+By the time of first star formation ($t=0$ in Fig.~\ref{ch1:figsfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
 The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
@@
 Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
-\label{fig:ch1:sfr_mass_evolution}
+\label{ch1:figsfr_mass_evolution}
 \end{figure*}
@@
 
-Fig.~\ref{fig:ch1:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
-One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Fig.~\ref{fig:ch1:ISM_evolution}).
+Fig.~\ref{ch1:figphase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
+One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Fig.~\ref{ch1:figISM_evolution}).
 Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
@@
 The region in the lower right corner indicates our density and temperature thresholds for star formation.}
-\label{fig:ch1:phase}
+\label{ch1:figphase}
 \end{figure}
 
-The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Fig.~\ref{fig:ch1:ISM_evolution}.
+The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Fig.~\ref{ch1:figISM_evolution}.
 The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
@@
 However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
-Together, these figures better quantify the general properties observed in the panel plots in Fig.~\ref{fig:ch1:panel_x} and Fig.~\ref{fig:ch1:panel_z}.
+Together, these figures better quantify the general properties observed in the panel plots in Fig.~\ref{ch1:figpanel_x} and Fig.~\ref{ch1:figpanel_z}.
 
@@
 \caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
-\label{fig:ch1:ISM_evolution}
+\label{ch1:figISM_evolution}
 \end{figure*}
@@
 This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
-In Fig.~\ref{fig:ch1:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
+In Fig.~\ref{ch1:figISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
 The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{ch1:sec:diffusive heating}).
@@
 In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
-\label{fig:ch1:ISRF}
+\label{ch1:figISRF}
 \end{figure}
@@
 Here, we include all gas within the mid-plane of our dwarf galaxy.
-Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:ch1:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
+Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{ch1:figphase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
 This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
-\label{fig:ch1:ISRF_2D}
+\label{ch1:figISRF_2D}
 \end{figure}
 
-To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Fig.~\ref{fig:ch1:ISRF_2D} at a single snapshot at 300~Myr.
+To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Fig.~\ref{ch1:figISRF_2D} at a single snapshot at 300~Myr.
 This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
@@
 However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
-In Fig.~\ref{fig:ch1:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
+In Fig.~\ref{ch1:figmass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
 We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
@@
 
-The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Fig.~\ref{fig:ch1:mass_outflow}.
+The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Fig.~\ref{ch1:figmass_outflow}.
 Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
@@
 \caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
-\label{fig:ch1:mass_outflow}
+\label{ch1:figmass_outflow}
 \end{figure*}
@@
 Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
-In Fig.~\ref{fig:ch1:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
+In Fig.~\ref{ch1:figoutflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
 Gas with a negative velocity is moving towards the center of the halo.
@@
 \caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-This is averaged over the same time interval as Fig.~\ref{fig:ch1:ISRF}.
+This is averaged over the same time interval as Fig.~\ref{ch1:figISRF}.
 The outflowing material is multiphase, broken into WNM, WIM, and HIM.
@@
 There is little to no outflowing mass in the CNM.}
-\label{fig:ch1:outflow_velocity}
+\label{ch1:figoutflow_velocity}
 \end{figure}
@@
 This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
-In the left panel of Fig.~\ref{fig:ch1:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}.
+In the left panel of Fig.~\ref{ch1:figmetal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{ch1:figmass_outflow}.
 The parameter used to quantify metal outflow efficiencies varies among works.
@@
 where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{fig:ch1:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
+These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{ch1:figmass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
 On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5).
@@
 \includegraphics[width=0.475\linewidth]{figures/ch1/metal_retention}
-\caption{{\bf Left}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:ch1:mass_outflow}.
+\caption{{\bf Left}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{ch1:figmass_outflow}.
 This is the ratio between the metal outflow rate and the metal production rate.
@@
 In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
-\label{fig:ch1:metal_evolution}
+\label{ch1:figmetal_evolution}
 \end{figure}
@@
 These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
-This is quantified in the right panel of Fig.~\ref{fig:ch1:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
+This is quantified in the right panel of Fig.~\ref{ch1:figmetal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
 After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
@@
 
-We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{fig:ch1:metal_slices}.
+We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{ch1:figmetal_slices}.
 The left panel gives the abundance ratio of N to O throughout the ISM.
@@
 In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occurred in the preceding 5 Myr as black stars and orange diamonds respectively.}
-\label{fig:ch1:metal_slices}
+\label{ch1:figmetal_slices}
 \end{figure*}
@@
 Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
-Given the variations in Fig.~\ref{fig:ch1:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
+Given the variations in Fig.~\ref{ch1:figmetal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
 The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
@@
 However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{fig:ch1:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
+In Figure ~\ref{ch1:figKS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
 In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.
@@
 There is no clear correlation with time in this diagram.}
-\label{fig:ch1:KS}
-\end{figure*}
-
-We include recent observational constraints on these relationships in Figure ~\ref{fig:ch1:KS}.
+\label{ch1:figKS}
+\end{figure*}
+
+We include recent observational constraints on these relationships in Figure ~\ref{ch1:figKS}.
 Our galaxy fluctuates significantly about both relationships with no clear trends in time.
@@
 In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
-It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:ch1:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
+It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{ch1:figKS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
 This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
@@
 \item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
-(See Figs.~\ref{fig:ch1:sfr_mass_evolution} and \ref{fig:ch1:KS}).
+(See Figs.~\ref{ch1:figsfr_mass_evolution} and \ref{ch1:figKS}).
 
@@
 metal mass loading factors near unity.
-By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Fig.~\ref{fig:ch1:outflow_velocity}).
+By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Fig.~\ref{ch1:figoutflow_velocity}).
 
@@
 By the end of the simulation $\sim$45\% of the remaining metals stay within the virial radius (but outside the galaxy), while $\sim$50\%
-have been ejected beyond the virial radius. (See Figs.~\ref{fig:ch1:mass_outflow}, \ref{fig:ch1:outflow_velocity}, and \ref{fig:ch1:metal_evolution}.)
+have been ejected beyond the virial radius. (See Figs.~\ref{ch1:figmass_outflow}, \ref{ch1:figoutflow_velocity}, and \ref{ch1:figmetal_evolution}.)
 
@@
 This is comparable to the resolution limit of the diffuse HI in observed, gaseous low-mass dwarfs.
-At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Fig.~\ref{fig:ch1:scale_height}).
+At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Fig.~\ref{ch1:figscale_height}).
 
@@
 The importance of radiation feedback in our model is investigated in more detail in \cite{Emerick2018b}.
-(See Figs.~\ref{fig:ch1:ISRF} and \ref{fig:ch1:ISRF_2D}.)
+(See Figs.~\ref{ch1:figISRF} and \ref{ch1:figISRF_2D}.)
 
@@
 Cold, neutral hydrogen dominates the mass of our galaxy.
-While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Fig.~\ref{fig:ch1:sfr_mass_evolution} and Fig.~\ref{fig:ch1:ISM_evolution}.)
+While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Fig.~\ref{ch1:figsfr_mass_evolution} and Fig.~\ref{ch1:figISM_evolution}.)
 
@@
 We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Fig.~\ref{fig:ch1:stellar radiation properties} we plot these properties.
+In Fig.~\ref{ch1:figstellar radiation properties} we plot these properties.
 We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
@@
 Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
-\label{fig:ch1:stellar radiation properties}
+\label{ch1:figstellar radiation properties}
 \end{figure*}
@@
 
-The left panel of Fig.~\ref{fig:ch1:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
+The left panel of Fig.~\ref{ch1:figSN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
 As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
 For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations.
-The right panel of Figure ~\ref{fig:ch1:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
+The right panel of Figure ~\ref{ch1:figSN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
 \begin{equation}
@@
 This shows that a fraction of these SNe are certainly unresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
-\label{fig:ch1:SN histogram}
+\label{ch1:figSN histogram}
 \end{figure*}
@@
 The regimes where heating dominates are plotted with dashed lines for clarity.}
-\label{fig:ch1:cooling comparison}
+\label{ch1:figcooling comparison}
 \end{figure*}
@@
 This can be a significant effect, particularly at higher metallicities.
-We demonstrate this in Fig.~\ref{fig:ch1:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
+We demonstrate this in Fig.~\ref{ch1:figcooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
 The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
 In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
-Fig.~\ref{fig:ch1:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
+Fig.~\ref{ch1:figcooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
 We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
@@
 rate is shown with solid lines.}
-\label{fig:ch1:cooling}
+\label{ch1:figcooling}
 \end{figure*}
@@
 To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https://grackle.readthedocs.io/en/latest/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) and initial temperature of 10$^{4}$~K for 200~Myr.
-In Fig.~\ref{fig:ch1:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background.
+In Fig.~\ref{ch1:figGrackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background.
 As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate.
@@
 These runs have identical initial conditions, random SN driving, cooling, heating, and chemistry as our fiducial simulation, but with no star formation.
-We vary the Lyman-Werner radiation and the H$^{-}$ photodetachment rate by the factors shown, which are comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{fig:ch1:ISRF}).
+We vary the Lyman-Werner radiation and the H$^{-}$ photodetachment rate by the factors shown, which are comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{ch1:figISRF}).
 Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9.
@@
 We note the regime below 1.0 on each axis is somewhat unphysical, and is never reached in our hydrodynamics simulations.}
-\label{fig:ch1:Grackle grid}
+\label{ch1:figGrackle grid}
 \end{figure}
@@
 
-We demonstrate the effect of varying resolution in the evolution of our galaxy model in Fig.~\ref{fig:ch1:resolution_study}.
+We demonstrate the effect of varying resolution in the evolution of our galaxy model in Fig.~\ref{ch1:figresolution_study}.
 We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines).
@@
 The line colors in the left panel are for better clarity between the SFRs.}
-\label{fig:ch1:resolution_study}
-\end{figure*}
-
-Fig.~\ref{fig:ch1:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
+\label{ch1:figresolution_study}
+\end{figure*}
+
+Fig.~\ref{ch1:figresolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
 We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
 The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs.
-We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Fig.~\ref{fig:ch1:SN histogram}.
+We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Fig.~\ref{ch1:figSN histogram}.
 However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
@@
 
-Theses differences in densities are shown clearly by comparing Fig.~\ref{fig:ch1:phase} with Fig.~\ref{fig:ch1:phase_resolution}.
+Theses differences in densities are shown clearly by comparing Fig.~\ref{ch1:figphase} with Fig.~\ref{ch1:figphase_resolution}.
 Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.
@@
 \includegraphics[width=0.75\linewidth]{figures/ch1/6pc_phase.png}
-\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{fig:ch1:phase}.}
-\label{fig:ch1:phase_resolution}
+\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{ch1:figphase}.}
+\label{ch1:figphase_resolution}
 \end{figure*}

### 2019-03-28 thesis/chapters/ch_chapter2.tex
Changing figure labels and references to something more logical

@@
 \caption{The star formation rate (left) and gas and stellar mass (right) of each of our three simulations over time. Time bins with no star formation are left empty.}
-\label{fig:ch2:sfr_mass_evolution}
+\label{ch2:figsfr_mass_evolution}
 \end{figure*}
 
-We compare the resulting star formation rate (left) and gas mass properties (right) of our three simulations in Figure~\ref{fig:ch2:sfr_mass_evolution}.
+We compare the resulting star formation rate (left) and gas mass properties (right) of our three simulations in Figure~\ref{ch2:figsfr_mass_evolution}.
 There is a clear, significant contrast between the runs with and without ionizing radiation.
@@
 Radiation from these stars quickly ionizes and dissipates surrounding dense gas that would otherwise have gone to fuel a significant amount of additional star formation.
-This is confirmed in Figure~\ref{fig:ch2:sf gas}, which shows the gas mass in each simulation above the SF density threshold of $n = 200$~cm$^{-3}$ during the first 100~Myr.
+This is confirmed in Figure~\ref{ch2:figsf gas}, which shows the gas mass in each simulation above the SF density threshold of $n = 200$~cm$^{-3}$ during the first 100~Myr.
 While our fiducial and shortrad simulations remain roughly the same here, the noRT run, at its peak, has an order of magnitude more cold, dense gas.
@@
 \caption{The total gas mass at $n > 200$~cm$^{-3}$, our star formation density threshold.}
-\label{fig:ch2:sf gas}
+\label{ch2:figsf gas}
 \end{figure}
@@
 This can be confirmed by examining the metal retention fraction (the fraction of produced metals retained within the disk of the galaxy) and mass outflow rates across simulations.
-As shown in Figure~\ref{fig:ch2:metal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation.
+As shown in Figure~\ref{ch2:figmetal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation.
 The outflow in noRT is only a factor of a few lower than the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback, so it implies a far lower mass loading factor.
@@
 \caption{{\bf Left:} The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange).
-As in Figure~\ref{fig:ch2:sfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively.
+As in Figure~\ref{ch2:figsfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively.
 {\bf Middle:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed).
@@
 }
-\label{fig:ch2:metal_retention}
+\label{ch2:figmetal_retention}
 \end{figure*}
@@
 Modeling only local stellar ionizing feedback is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
-To explore the cause of this difference we compare in Figure~\ref{fig:ch2:panel1} and~Figure~\ref{fig:ch2:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.
+To explore the cause of this difference we compare in Figure~\ref{ch2:figpanel1} and~Figure~\ref{ch2:figpanel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.
 
@@
 However, SNe launched gas is trapped by neutral, cold shells in the shortrad simulation, unable to easily escape from the disk of the simulated galaxy.
-These same insights can also be gained by comparing this figure with Figure~\ref{fig:ch2:panel2}.}
-\label{fig:ch2:panel1}
+These same insights can also be gained by comparing this figure with Figure~\ref{ch2:figpanel2}.}
+\label{ch2:figpanel1}
 \end{figure*}
@@
 \includegraphics[width=0.99\linewidth]{figures/ch2/DD0160_fiducial_shortrad_nort}
-\caption{Same as Figure~\ref{fig:ch2:panel1}, but at 40~Myr.}
-\label{fig:ch2:panel2}
+\caption{Same as Figure~\ref{ch2:figpanel1}, but at 40~Myr.}
+\label{ch2:figpanel2}
 \end{figure*}
 
-Figure~\ref{fig:ch2:panel1}, at 17~Myr, compares each simulation just after the first few SNe.
+Figure~\ref{ch2:figpanel1}, at 17~Myr, compares each simulation just after the first few SNe.
 Already there are significant differences between the runs.
@@
 Although the ISM properties within the HII region in each case are quite similar between the simulations, the SNe that eventually go off in this region are confined by the neutral gas in the shortrad simulation, but readily escape through the lower density ionized gas into the galaxy halo in our fiducial case.
-As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe, as shown in  Figure~\ref{fig:ch2:panel2}, which shows each simulation 40~Myr after the formation of the first stars.
+As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe, as shown in  Figure~\ref{ch2:figpanel2}, which shows each simulation 40~Myr after the formation of the first stars.
 In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas.
@@
 
-As shown in Figure~\ref{fig:ch2:metal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy.
+As shown in Figure~\ref{ch2:figmetal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy.
 The winds in our fiducial simulation carry nearly all of the metals produced out from the disk of our galaxy.

### 2019-03-28 thesis/chapters/ch_chapter4.tex
Updates to chapter 4 including a new figure.

@@
 The clear trend in Figure~\ref{ch4:fig:ISM_CGM} shows that events with higher $E_{\rm ej}$ are much more readily ejected from the disk of the galaxy, while events with lower $E_{\rm ej}$ couple poorly to the same galactic outflows.
-\textit{statement on how immediate enrichement is after events}
+\textit{statement on how immediate enrichment is after events}
 % By 10~Myr after the enrichment events,
@@
 The lowest energy event, corresponding to AGB winds, reaches $f_{\rm ej}$ ~ 0.68, which increases to 0.87 for the 10$^{51}$~erg events, and 0.95 for the 10$^{52}$~erg event.
+To emphasize these differences, we plot each line separately in the left panel of Figure~\ref{ch4:fig:CGM_CNM}
+
 This implies that, if one to were assume that all metals behaved the same and adopted an $f_{\rm ej}$ of $\sim$0.9 -- typical for the total metal ejection fraction in simulations that do not track individual enrichment channels \citep[e.g.][]{Muratov2017,Christensen2018}, and consistent with observations of the O abundance in Local Group dwarf galaxies \citep[e.g.][]{Kirby2011,McQuinn2015} -- one would underestimate the amount of AGB metals in the ISM by a factor of $\sim$ 3, and overestimate exotic, high-energy sources by a factor of $\sim$ 2.
@@
 Metals in the ISM injected with $E_{\rm ej} > 10^{49}$~erg are initially located predominately in the HIM, roughly 1/2 for $E_{\rm ej} = 10^{49}$~erg and nearly all for $E_{\rm ej} > 10^{52}$~erg.
-The lowest energy events are initially in the WIM and WNM, tracing the two dominant volume-filling components of the ISM (see Chatper~\ref{ch:chapter1}), as these events do not have sufficient energy to generate the HIM phase by themselves.
-In general, very few of these elements are available for immediate star formation in the CNM.
-However, we note that we may not have sufficient resolution to properly resolve the details of the initial mixing of individual enrichment events in the ISM.
-In addition, we are missing important physical processes, like dust production in AGB winds and core collapse SNe, that may affect these results for specific enrichment channels in ways that do not depend solely on $E_{\rm ej}$.
-Resolving these processes in detail in galaxy-scale simulations is computationally infeasible.
+The lowest energy events are initially in the WIM and WNM, tracing the two dominant volume-filling components of the ISM (see Chapter~\ref{ch:chapter1}), as these events do not have sufficient energy to generate the HIM phase by themselves.
 
-Finally, we are interested in the long-term evolution of the metals from each of these sources, and how long it takes for these metals to propogate from the warm / hot phases of the ISM to cold, star forming gas.
 Gas above the star formation threshold in our simulations is limited and short-lived due to the low gas surface densities and star formation rates in this galaxy and the efficiency of stellar feedback from newly formed stars.
 As a proxy, we examine the evolution of the CNM, out of which the star forming gas forms.
-In Figure~\ref{ch4:fig:CNM}, we examine the evolution of the metal fraction of the CNM \textit{for just those elements retained in the ISM] for the average behavior of each enrichment event.
+In general, very few of these elements are available for immediate star formation in the CNM ($<< 1\%$, see Figure~\ref{ch4:fig:CGM_CNM}).
+However, we note that we may not have sufficient resolution to properly resolve the details of the initial mixing of individual enrichment events in the ISM.
+In addition, this value will be sensitive to whether or not a given event occurs in the vicinity of or inside an active, star forming region -- as is likely for core collapse SNe, and unlikely for other events.
+Thus, this is a quantity that does not depend solely on $E_{\rm ej}$ and is sensitive to whether or not self-enrichment of star forming regions is an important factor in galactic chemical evolution.
+We are also missing important physical processes, like dust production in AGB winds and core collapse SNe, that may affect these results for specific enrichment channels in ways that do not depend solely on $E_{\rm ej}$.
+Investigating the fraction of metals immediately available for star formation will require additional, high-resolution simulations of metal mixing in and around individual star forming regions.
+% add references (maybe) to high res simulation of dust production in AGB winds and SNe ???
+
+What we can examine, however, is the final quantity of interest: the long-term evolution of the metals from each of these sources, and how long it takes for these metals to propagate from the warm / hot phases of the ISM to cold, star forming gas.
+In the right panel of Figure~\ref{ch4:fig:CGM_CNM}, we examine the evolution of the metal fraction of the CNM \textit{for just those elements retained in the ISM}.
+Although the initial CNM fractions are about the same for each source, the evolution over the first $\sim$50~Myr is qualitatively different.
+the higher energy sources, $E_{\rm ej} > 10^{49}$~erg, are more rapidly incorporated into the CNM than E46, even though each retains a lower fraction of metals in the ISM.
+This is most significant at $\sim$20~Myr, when the fraction of metals in the CNM from these sources is a factor of $\sim$3-4 higher than the E46 metals.
+By $\sim$50~Myr, the evolutions become intermingled and complex, with no clear trend as a function of $E_{\rm ej}$.
 
@@
   \centering
-  \includegraphics[width=0.75\linewidth]{figures/ch4/CNM_evolution_average}
-  \caption{Time evolution of the metal fraction of the CNM for just those metals retained in the ISM for each enrichment source. In other words,
-           these are the same CNM lines as shown in Figure~\ref{ch4:fig:ISM_CGM}, but are divided by the black, dashed lines in each panel.}
-  \label{ch4:fig:CNM}
+  \includegraphics[width=0.45\linewidth]{figures/ch4/CGM_average_evolution}
+  \includegraphics[width=0.45\linewidth]{figures/ch4/CNM_average_evolution}
+  \caption{Time evolution of the fraction of enrichment source metals contained in the CGM over time (left), and the fraction of metals in the CNM just those metals retained in the ISM for each enrichment source (right).
+These are the same as the lines in Figure~\ref{ch4:fig:ISM_CGM}, but the CNM lines are normalized by the black, dashed total ISM line in Figure~\ref{ch4:fig:ISM_CGM}.}
+  \label{ch4:fig:CGM_CNM}
 \end{figure*}
 % make a figure here showing JUST the CNM evolution of the ISM for each source
+
+However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, corresponding to the mass fraction of the CNM at this point in the galaxy's evolution (see Figure~\ref{ch1:fig:}).
+This trend -- that the fraction of metals contained in a given phases tends towards the mass fraction of that phase -- is true across all phases in the simulation.
+Therefore, we can consider that the metals for each source are well-mixed across the \textit{phases} of the ISM on timescales of $\sim$100-150~Myr.
+\textbf{Compute the cooling timescale of each phase (maybe with a phase diagram?) and also the dynamical timescale and make comparisons here.}.
+These two results suggest that the delay-time between when metals are available to enrich ongoing star formation is on order of $\sim$10~Myr across sources, and only significant for the lowest (E46, AGB-like) energy sources.
+Although well-mixed across phases, we emphasize that this does not imply that the abundances are the same across phases nor that the metals are spatially well-mixed across the galaxy.
+We investigate this second point further below.
 

### 2019-03-28 thesis/chapters/ch_chapter4.tex
updates to ch4

@@
 
+In Chapter~\ref{ch:chapter3} we investigate the metal enrichment distributions in the ISM as characterized by the metal fraction PDFs (see Figure~\ref{ch3:fig:log-normal} and Figure~\ref{ch3:fig:phase-statistics}).
+We find that this PDF is generally well described as log-normal with a power law tail towards high metal fractions, and characterize its mean, median, interquartile range (IQR), interdecile range (IDR), and the difference between the mean and median (as a measure of skew) of each distribution.
+In general, we find that elements released in AGB-wind events are less well-mixed than elements released in SNe, as indicated by the relative size of the IQR, IDR, and mean-median difference between the two types of elements.
+However, these distributions arise from the contribution of many individual enrichment events across multiple sources over long periods of time.
+It is unclear how metals from a \textit{single} enrichment event are distributed across a galaxy over time, and how the energy associated with the event affects the homogeneity of its distribution.
+
+To frame this analysis, lets first examine what processes affect the metal mass fraction PDF.
+The mean metal mass fraction for a collection of gas is simply the total metal mass divided by the total gas mass.
+For a collection of gas elements, the mean metal mass fraction is defined as $Z_{\rm gas} = \frac{ \Sigma Z_{\rm i}M_{\rm gas,i}}{\Sigma M_{\rm gas,i}}$, where $M_{\rm gas,i}$ is the mass of the i$^{\rm th}$ homogeneous blob of gas, and $Z_{i}$ its metal mass fraction.
+A completely homogenous ISM would have a $\delta$ function metal mass fraction PDF at the mean metal fraction, or $p(Z) = \delta(Z_{\rm gas})$.
+By definition, a completely homogeneous distribution will have
+
 %************* APPENDICES ************************%

### 2019-03-29 thesis/chapters/ch_chapter4.tex
More writing

@@
 For a collection of gas elements, the mean metal mass fraction is defined as $Z_{\rm gas} = \frac{ \Sigma Z_{\rm i}M_{\rm gas,i}}{\Sigma M_{\rm gas,i}}$, where $M_{\rm gas,i}$ is the mass of the i$^{\rm th}$ homogeneous blob of gas, and $Z_{i}$ its metal mass fraction.
-A completely homogenous ISM would have a $\delta$ function metal mass fraction PDF at the mean metal fraction, or $p(Z) = \delta(Z_{\rm gas})$.
-By definition, a completely homogeneous distribution will have
+A completely homogeneous ISM would have a $\delta$ function metal mass fraction PDF at the mean metal fraction, or $p(Z) = \delta(Z_{\rm gas})$.
+By definition, then, a homogeneous distribution will have a zero-width IQR, IDR, and mean-median difference.
+Non-uniform enrichment in a homogeneous medium will increase each of these quantities, while mixing in a non-uniform medium will tend to decrease each.
+In simple models of galactic chemical evolution, the mean gas abundance -- not the median -- is followed, even though the median is more indicative of the abundance of a ``typical" gas element.
+Because these two quantities provide a more immediate conceptual understanding of how metals are distributed in the ISM, we focus on characterizing the inhomogeneity of the followed metals by examining the mean-median difference.
+Though this quantity being zero is necessary for metals to be homogeneously distributed in a medium, we do note that it is not a sufficient condition.
+However, as noted, its evolution is easy to interpret conceptually.
+Enrichment increases this quantity by raising the mean metal fraction while keeping the median value fixed (or only slightly increasing), so long as the newly enriched mass is a small fraction of the total gas mass (as is usually the case).
+Conversely, preferential removal of metals from a medium will lower this quantity.
+And finally, the mixing of metal-rich gas elements with metal-poor will gradually bring the mean and median values to parity.
+For our numerical experiments, enrichment in the whole ISM only occurs once, while ejection from the ISM is easy to follow.
+This allows for a more clean interpretation of the evolution than examining either the IQR or the IDR.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.75\linewidth]{figures/ch4/ISM_CNM_average_mean-median}
+  \caption{Time evolution of the difference (in dex) between the mean metal mass fraction of each source and the median metal mass fraction of each source in all of the gas in the ISM (left) and in the CNM only (right).}
+  \label{ch4:fig:CGM_CNM}
+\end{figure*}
+
+In Figure~\ref{ch4:fig:mean-median} we examine the average behavior of the mean-median metal mass fractions for the whole ISM in each run (left) and the CNM only (right).
+In all cases, enrichment drives the dramatic increase of this value from zero to over 10 dex.
+This large value is due entirely because the initial abundance for each metal is zero.
+This is followed by a significant decrease in spread over he first 25~Myr or so as metals are preferentially ejected from the ISM via outflows.
+The delay in this spike in the CNM (compared to the galaxy as a whole) is due to the different timescales over which most of the metals are incorporated into the cold gas, as shown in Figure~\ref{ch4:fig:ISM_CGM}.
+
+Clearly, at no point can any of these distributions be considered well-mixed within the 150~Myr simulation time.
+\textit{Need to fix up: This is in agreement with the understanding that the mxiing timescales should correspond to XXX, which suggests that it would take $\sim$X~Gyr (1 Gyr?) for the metals to be fully mixed}.
+Interestingly, however, the injection energy for a given sources leaves an indelible impact on the subsequent evolution of those metals in the ISM throughout the simulation time.
+We demonstrate that variations in abundance spread across elements may be driven significantly by the enrichment site and its associated $E_{\rm ej}$.
+Metals from II\_E46 are significantly less well-mixed than their higher-energy counterparts at II\_E51 and II\_E52.
+Interestingly, II\_E49 behaves much more similarly to II\_E46 -- with poor mixing -- even though it is much closer in energy to the II\_E51.
+For what mixing does occur in the CNM for these elements, it is apparent that it happens much faster ($\sim$20~Myr) for the highest energy event than the lower energy events which take longer to plateau to a consistent value.
+
+We note that these results are given for \textit{single} enrichment events.
+If many events occur throughout the galaxy with similar metal yields then this would tend to decrease the abundance variations across the galaxy.
+However, the AGB wind metals examined in Chapter~\ref{ch:chapter3} are still more heterogeneously distributed than core collapse SNe elements in spite of the fact that these events are both more common than SNe and are more evenly distributed throughout the galaxy.
+
+What this does suggest, however, is that in utilizing stars with unusual abundances at low metallicities to infer the yields of exotic enrichment sources, the spread of abundances in those stars may provide an important insight into the origin of those metals.
+For example, r-process enrichment from exotic enrichment events like hypernovae should manifest itself as more well-mixed than if the elements originated in lower energy NS-NS mergers.
+\textbf{Go back to reticulum papers and see what the spreads on these are}
+
+\section{Discussion}
+
+Not sure how much to put in here, and may very well need to just pull out some of the above and put it here.
 

### 2019-04-01 thesis/chapters/ch_chapter4.tex
plots and text for variations in results

@@
 
-\section{Discussion}
+\subsection{Event-by-Event Variation}
+
+For clarity we focused on the \textit{mean} evolution of individual enrichment events at fixed injection energy in the results thus far, but we turn now to discuss how much variety exists among these individual events.
+For each of the discussed runs (from set II), Figure~\ref{ch4:fig:CGM_CNM_variance} shows the fraction of metals ejected from the galaxy (left) and the fraction of metals in the ISM within the CNM (right) as a function of source energy at two different times, 20~Myr (blue) and 100~Myr (orange).
+The averaged values at each energy are shown as points, and the bars denote the min/max value for each event energy.\footnote{While the standard deviation or IQR may be more informative here, rather than min / max, the sample size at each energy, with the exception of the E46 runs, is too small to reliably do so.} As shown, there is substantial variation at each energy.
+This is particularly striking for the E46 events, which seemingly can have effectively any value for $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ at any point during the evolution.
+It is clear that the trends discussed thus far applies to the average behavior of events at a fixed $E_{\rm ej}$, but not for an individual event.
+In addition, a higher $E_{\rm ej}$ seems to increase the minimum $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ expected, but the behavior of any one event must depend on additional factors.
+
+ \begin{figure*}
+   \centering
+   \includegraphics[width=0.8\linewidth]{figures/ch4/II_Ej_CNM_average}
+   \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} that demonstrate the significant variation in $f_{\rm CGM}$ and
+   $f_{\rm CNM} / f_{\rm Disk}$ at fixed injection energy. The points give the average values at each energy at two different times, while the
+   error bars show the min/max values at each energy.
+The points at different times have been offset slightly along the horizontal axes for clarity.
+Since they are only two points, we show the results from II_E52_r0 and II_E52_r300 without averaging.}
+   \label{ch4:fig:CGM_CNM_variance}
+ \end{figure*}
+
+But what causes this variation among individual events?
+Do additional properties about the injection site (ISM density, position, local SFR), determine the subsequent evolution?
+Or is this the result of a complex, non-deterministic set of complex interactions the metals from a given event experience over their lifetime in the galaxy?
+We investigate the dependence on a few of these properties below.
+
+\subsection{Dependence on Radial Position}
+\label{ch4:sec:radial position}
+We place each source in regular, but arbitrary, positions in the galaxy without consideration for the local ISM conditions at injection.
+Sources are placed at the center of the galaxy ($r = 0$~pc) or at various radii (at cardinal positions at 300~pc, and 600~pc), all in the mid-place of the galaxy.
+Since the E46 events were likely to not self-interact, we additionally placed events at $r = 100$~pc and one event at each $r$ at about one scale height above the disk ($z = 50$~pc).
+For each II run, we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ as a function of radial position in the galaxy for each event.
+The points, error bars, and colors are the same as in Figure~\ref{ch4:fig:CGM_CNM_variance}.
+
+ \begin{figure*}
+   \centering
+   \includegraphics[width=0.95\linewidth]{figures/ch4/II_radial_dependence}
+   \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} that demonstrate the significant variation in $f_{\rm CGM}$ and
+   $f_{\rm CNM} / f_{\rm Disk}$ at fixed injection energy. The points give the average values at each energy at two different times, while the
+   error bars show the min/max values at each energy.
+The points at different times have been offset slightly along the horizontal axes for clarity.
+Since they are only two points, we show the results from II_E52_r0 and II_E52_r300 without averaging.}
+   \label{ch4:fig:CGM_CNM_variance}
+ \end{figure*}
+
+\subsection{Variation with Local ISM Conditions}
+\label{ch4:sec:ISM density}
+
+ Although the exact positions of each event are arbitrarily chosen, we compute the average ISM properties within a 4-zone radius ($4 \times dx$=7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each II run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event.
+
+ \begin{figure*}
+   \centering
+   \includegraphics[width=0.95\linewidth]{figures/ch4/II_n_dependence}
+   \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} that demonstrate the significant variation in $f_{\rm CGM}$ and
+   $f_{\rm CNM} / f_{\rm Disk}$ at fixed injection energy. The points give the average values at each energy at two different times, while the
+   error bars show the min/max values at each energy.
+The points at different times have been offset slightly along the horizontal axes for clarity.
+Since they are only two points, we show the results from II_E52_r0 and II_E52_r300 without averaging.}
+   \label{ch4:fig:CGM_CNM_variance}
+ \end{figure*}
+
+\subsubsection{Variation with SFR}
+\label{ch4:sec:SFR}
+
+Finally, we examine the companion runs (I and III) to see if the global star formation rate of the galaxy drives variation in these results.
+Although this does not help to directly account for the variation seen in the previous plots, this could provide insight into how SFR (in an averaged sense) affects the evolution of metals.
+We note that correlation with SFR is of interest not because the formation of stars by themselves, but rather the increase in feedback associated with a higher SFR (and thus a warmer / hotter ISM, greater turbulence in the ISM, and more significant outflows).
+
+\section{Discussion and Conclusions}
+
+Galactic chemical evolution is far from ``one-zone" and metal mixing is clearly neither homogeneous nor instantaneous. In addition, the
+
+Variations with individual events in the above results suggests that it would be challenging to make any conclusive statements about the enrichment behavior of single enrichment sources.
+This is problematic for interpreting the chemical abundances in UFDs that are likely to have been host to just a single, exotic enrichment event.
+Using these observations to constrain the total nucelosynthetic yields of these sources requires implicit assumptions about how quickly metals are available in star forming gas, how homogenously they are distributed throughout the galaxy, and what fraction are ejected from the galaxy.
+It is likely that none of these quantities can be determined as simple parameters based upon the feedback properties of a single enrichment source or even the global properties of a galaxy (such as $M_{\rm halo}$, $\Sigma_{\rm SFR}$, $\Sigma_{\rm gas}$).
+However, this study has shown that these parameters can be characterized in an averaged sense, even though the exact result is subject to substantial stochastic effects.
+This, combined with some mechanism to provide this stochasticity, can be used in combination with many runs of a simple galactic chemical evolution model to understand the possible outcomes for various XXXXX.
+Then, the observed properties of an individual galaxy can be mapped to this XXXXXX
 

### 2019-04-01 thesis/chapters/ch_chapter4.tex
more text in radial analysis

@@
 \section{Introduction}
-
-\section*{Acknowledgments}
 
@@
    \centering
-   \includegraphics[width=0.8\linewidth]{figures/ch4/II_Ej_CNM_average}
+   \includegraphics[width=0.8\linewidth]{figures/ch4/II_Eej_CNM_avg}
    \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} that demonstrate the significant variation in $f_{\rm CGM}$ and
@@
 The points at different times have been offset slightly along the horizontal axes for clarity.
-Since they are only two points, we show the results from II_E52_r0 and II_E52_r300 without averaging.}
+Since they are only two points, we show the results from II\_E52\_r0 and II\_E52\_r300 without averaging.}
    \label{ch4:fig:CGM_CNM_variance}
@@
 Since the E46 events were likely to not self-interact, we additionally placed events at $r = 100$~pc and one event at each $r$ at about one scale height above the disk ($z = 50$~pc).
-For each II run, we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ as a function of radial position in the galaxy for each event.
+For each II run, we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ as a function of radial position in the galaxy for each event in Figure~\ref{ch4:fig:radial position}.
 The points, error bars, and colors are the same as in Figure~\ref{ch4:fig:CGM_CNM_variance}.
@@
    \includegraphics[width=0.95\linewidth]{figures/ch4/II_radial_dependence}
-   \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} that demonstrate the significant variation in $f_{\rm CGM}$ and
-   $f_{\rm CNM} / f_{\rm Disk}$ at fixed injection energy. The points give the average values at each energy at two different times, while the
-   error bars show the min/max values at each energy.
-The points at different times have been offset slightly along the horizontal axes for clarity.
-Since they are only two points, we show the results from II_E52_r0 and II_E52_r300 without averaging.}
-   \label{ch4:fig:CGM_CNM_variance}
+   \caption{The dependence of $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ on the radial position of each event at two different times in the evolution of the galaxy.
+The meaning of each point, the error bars, and colors are the same as in Figure~\ref{ch4:fig:CGM_CNM_variance}.}
+   \label{ch4:fig:radial position}
  \end{figure*}
+
+Across runs, there is no clear dependence on the radial position of the event and the fraction of metals ejected beyond the galaxy for any of the displayed runs at either 20~Myr or 100~Myr.
+There is a slight increase in the minimum fraction of metals ejected from the galaxy as a function of radius for the higher energy runs ($>10^{50}$~erg).
+This perhaps not surprising for the largest radii as 600~pc is right near the very edge of the galaxy's disk.
+But again, the trend is weak and there is clearly still a great variance at both fixed $E_{\rm ej}$ and $r$.
 
@@
 
- Although the exact positions of each event are arbitrarily chosen, we compute the average ISM properties within a 4-zone radius ($4 \times dx$=7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each II run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event.
+We compute the average ISM properties within a 4-zone radius ($4 \times dx$=7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each II run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event.
 
@@
    \includegraphics[width=0.95\linewidth]{figures/ch4/II_n_dependence}
-   \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} that demonstrate the significant variation in $f_{\rm CGM}$ and
-   $f_{\rm CNM} / f_{\rm Disk}$ at fixed injection energy. The points give the average values at each energy at two different times, while the
-   error bars show the min/max values at each energy.
-The points at different times have been offset slightly along the horizontal axes for clarity.
-Since they are only two points, we show the results from II_E52_r0 and II_E52_r300 without averaging.}
-   \label{ch4:fig:CGM_CNM_variance}
+   \caption{.}
+   \label{ch4:fig:ISM_variance}
  \end{figure*}
@@
 
+%\section*{Acknowledgments}
+
 %\clearpage

### 2019-04-02 thesis/chapters/ch_chapter4.tex
Updates to results in CH4 and figures... nearing end of draft of this

@@
 For clarity we focused on the \textit{mean} evolution of individual enrichment events at fixed injection energy in the results thus far, but we turn now to discuss how much variety exists among these individual events.
-For each of the discussed runs (from set II), Figure~\ref{ch4:fig:CGM_CNM_variance} shows the fraction of metals ejected from the galaxy (left) and the fraction of metals in the ISM within the CNM (right) as a function of source energy at two different times, 20~Myr (blue) and 100~Myr (orange).
+For each of the discussed runs (from set II), Figure~\ref{ch4:fig:CGM_CNM_variance} shows the fraction of metals ejected from the galaxy (left) and the fraction of metals in the ISM within the CNM (center) as a function of source energy at two different times, 20~Myr (blue) and 100~Myr (orange).
+In the right panel, we show how the spread at each of these times varies for each event.
 The averaged values at each energy are shown as points, and the bars denote the min/max value for each event energy.\footnote{While the standard deviation or IQR may be more informative here, rather than min / max, the sample size at each energy, with the exception of the E46 runs, is too small to reliably do so.} As shown, there is substantial variation at each energy.
 This is particularly striking for the E46 events, which seemingly can have effectively any value for $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ at any point during the evolution.
-It is clear that the trends discussed thus far applies to the average behavior of events at a fixed $E_{\rm ej}$, but not for an individual event.
-In addition, a higher $E_{\rm ej}$ seems to increase the minimum $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ expected, but the behavior of any one event must depend on additional factors.
+Finally, the right panel shows that the degree of inhomogeneous mixing for each event varies significantly as well.
+However, there is a more clear trend for each of the mean, min, and max values of the spread at 100~Myr (decreasing as a function of increasing $E_{\rm ej}$).
 
@@
    \includegraphics[width=0.8\linewidth]{figures/ch4/II_Eej_CNM_avg}
-   \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} that demonstrate the significant variation in $f_{\rm CGM}$ and
-   $f_{\rm CNM} / f_{\rm Disk}$ at fixed injection energy. The points give the average values at each energy at two different times, while the
-   error bars show the min/max values at each energy.
+   \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} and Figure~\ref{ch4:fig:CGM_CNM} that demonstrates the significant variation in $f_{\rm CGM}$, $f_{\rm CNM} / f_{\rm Disk}$, and the mean-median separate at fixed injection energy.
+The points give the average values at each energy at two different times, while the error bars show the min/max values at each energy.
 The points at different times have been offset slightly along the horizontal axes for clarity.
@@
 
+It is clear that the trends discussed thus far applies to the average behavior of events at a fixed $E_{\rm ej}$, but not for an individual event.
+In addition, a higher $E_{\rm ej}$ seems to increase the minimum $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ expected, but the behavior of any one event must depend on additional factors.
 But what causes this variation among individual events?
@@
 But again, the trend is weak and there is clearly still a great variance at both fixed $E_{\rm ej}$ and $r$.
+The fraction of metals in the ISM that are contained within the CNM (middle row) does not show any obvious trend at E46, but does seem to generally be lowest for the higher energy sources at the outskirts of the galaxy.
+Finally, the radial position does seem to somewhat affect the mixing behavior.
+Sources at the outskirts of the galaxy tend to be more inhomogeneous than sources at smaller radii, especially at 20~Myr for the higher energy events, and the variation in behavior for these sources decreases substantially, particularly at 100~Myr.
+It is unclear what exactly drives these mixing differences.
+If feedback-driven turbulence is the dominate driver of ISM mixing in this dwarf galaxy -- as it likely is -- then sources near the center are more likely to be affected by more feedback events (due to a slightly higher $\Sigma_{\rm SFR}$) and mix more efficiently.
 
@@
 We compute the average ISM properties within a 4-zone radius ($4 \times dx$=7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each II run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event.
+The E46 events clearly do a better job sampling the ISM density PDF, with a slight trend of decreasing $f_{\rm CGM}$ (more retained metals) with local ISM number density.
+This difference is even true after 100~Myr of evoltuion, but still with significant variation at fixed $n$.
+The number statistics limit a conclusive result for the higher energy events, but generally there does not appear to be an obvious trend in behavior of $f_{\rm CGM}$ as a function of $n$.
+This is perhaps because these energies are sufficient to heat up and dramatically reduce the density of the ISM in the injection region anyway, such that $n$ before the event is not as important as it is for the E46 events which are much less dynamically important.
+$f_{\rm CNM} / f_{\rm Disk}$ does not display any significant variation with $n$ at 100~Myr, but is slightly elevated at 20~Myr at higher densities.
+There is still a variety of behavior at fixed $n$.
+Finally, we note no obvious trends of the spread of the metal PDFs as a function of $n$ for all but the E46 run.
+Again, the local ISM densities is likely not too dynamically relevant to the higher energy events -- hence their lack of variation with $n$ -- but this is not true for E46.
+There is a fairly clear trend of increasing inhomogeneity in the CNM as a function of the initial $n$ in the injection region for E46, that is not present at 20~Myr, but is obvious at 100~Myr.
 
@@
    \includegraphics[width=0.95\linewidth]{figures/ch4/II_n_dependence}
-   \caption{.}
+   \caption{The variation of $f_{\rm CGM}$, $f_{\rm CNM} / f_{\rm Disk}$, and the spread of the metal fraction PDFs in the ISM as a function of the local ISM number density ($n$) within the injection region of the event just prior (within 0.1~Myr) of the event.
+Points, lines, and line colors mean the same as shown in Figure~\ref{ch4:fig:CGM_CNM_variance}}
    \label{ch4:fig:ISM_variance}

### 2019-04-02 thesis/chapters/ch_chapter4.tex
Finished text (mostly) to chapter 4 with exception of the introduction. Just need to re-read and regenerate plots with updated results

@@
 %
+
+\newcommand{\runone}{I\_}
+\newcommand{\runonenu}{I}
+\newcommand{\runtwo}{II\_}
+\newcommand{\runtwonu}{II}
 
@@
 \label{ch4:sec:experiment}
-We restart our fiducial, full-physics simulation at three different times, 100 Myr, 180 Myr, and 360 Myr; runs at these times are labelled as I, II, and III respectively.
-These correspond to three different times in the galaxy's SFR evolution, testing how much variance is expected in the metal mixing and ejection with the star formation rate.
-I occurs in the last $\sim$ 20 Myr of the initial burst of star formation, II occur during the lull in star formation following this peak, and III in an extended period of little to no ongoing star formation.
-We attempted to to evolve each simulation for 150 Myr, but due to computational constrains (particularly with the I runs) this was not always possible.
+We restart our fiducial, full-physics simulation at two different times, 180 Myr, and 360 Myr, labeled as runs \runonenu~ and \runtwonu~ respectively.
+These correspond to two different times in the galaxy's SFR evolution, testing how much variance is expected in the metal mixing and ejection with the star formation rate.
+\runonenu~ occurs during the lull in star formation following the initial SFR peak, and \runtwonu~ occurs in an extended period of little to no ongoing star formation.
+We attempted to to evolve each simulation for 150 Myr, but due to computational constrains this was not always possible.\footnote{We began runs during the peak of star formation ($\sim 100$~Myr), but the computational cost increases substantially during this time.
+These runs were abandoned.}
+
+% I occurs in the last $\sim$ 20 Myr of the initial burst of star formation,
 
@@
 Each run contains only sources from a single event type, as indicated in the run-name by the log of the injection energy in ergs.
-For example, the run beginning at 180~Myr with AGB-like events is labeled ``II\_E46".
+For example, the run beginning at 180~Myr with AGB-like events is labeled ``\runone E46".
 The metal enrichment from each source is tracked and evolved with a unique passive scalar tied to the individual source and separate from any additional chemical enrichment that may occur within the galaxy over time.
@@
 
-We focus this analysis primarily on the results from run II, and save a discussion of how these results vary across runs and across specific source positions in Section XXX \textit{(maybe take out if don't have time)}.
-
 \subsection{Enrichment of the ISM and CGM}
@@
 
-We summarize the source-averaged results for all enrichment events in runs II\_E46, II\_E49, II\_E50, II\_E51, and II\_E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid).
+We summarize the source-averaged results for all enrichment events in runs \runone E46, \runone E49, \runone E50, \runone E51, and \runone E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid).
 These plots show a clear, immediate trend across $E_{\rm ej}$ for all lines in the figure, but the differences are most striking for the ISM (black, solid), CGM (black, dashed) lines.
@@
 The clear trend in Figure~\ref{ch4:fig:ISM_CGM} shows that events with higher $E_{\rm ej}$ are much more readily ejected from the disk of the galaxy, while events with lower $E_{\rm ej}$ couple poorly to the same galactic outflows.
-\textit{statement on how immediate enrichment is after events}
+%\textit{statement on how immediate enrichment is after events}
 % By 10~Myr after the enrichment events,
@@
 This implies that, if one to were assume that all metals behaved the same and adopted an $f_{\rm ej}$ of $\sim$0.9 -- typical for the total metal ejection fraction in simulations that do not track individual enrichment channels \citep[e.g.][]{Muratov2017,Christensen2018}, and consistent with observations of the O abundance in Local Group dwarf galaxies \citep[e.g.][]{Kirby2011,McQuinn2015} -- one would underestimate the amount of AGB metals in the ISM by a factor of $\sim$ 3, and overestimate exotic, high-energy sources by a factor of $\sim$ 2.
-In each case, these are metals that cannot participate in the enrichment of future stellar populations.
+In each case, these are metals that cannot participate in the enrichment of future stellar populations and will make a significant difference on the output stellar abundances in chemical evolution models.
+We explore this impact in different works.
 
 In all cases, the metals contained with the ISM are deposited predominately in the ionized phases of the ISM, the WIM or the HIM, with the relative fraction in each phase driven by the energy of the event.
-Metals in the ISM injected with $E_{\rm ej} > 10^{49}$~erg are initially located predominately in the HIM, roughly 1/2 for $E_{\rm ej} = 10^{49}$~erg and nearly all for $E_{\rm ej} > 10^{52}$~erg.
-The lowest energy events are initially in the WIM and WNM, tracing the two dominant volume-filling components of the ISM (see Chapter~\ref{ch:chapter1}), as these events do not have sufficient energy to generate the HIM phase by themselves.
+Metals in the ISM injected with $E_{\rm ej} > 10^{49}$~erg are initially located predominately in the HIM, roughly 1/2 for $E_{\rm ej} = 10^{49}$~erg and nearly all for $E_{\rm ej} > 10^{51}$~erg.
+The lowest energy events are initially in the WIM and WNM, tracing the two dominant volume-filling components of the ISM (see Chapter~\ref{ch:chapter1}), as these events do not have sufficient energy to generate the HIM by themselves.
 
@@
 Although the initial CNM fractions are about the same for each source, the evolution over the first $\sim$50~Myr is qualitatively different.
-the higher energy sources, $E_{\rm ej} > 10^{49}$~erg, are more rapidly incorporated into the CNM than E46, even though each retains a lower fraction of metals in the ISM.
+The higher energy sources, $E_{\rm ej} > 10^{49}$~erg, are more rapidly incorporated into the CNM than E46, even though each retains a lower fraction of metals in the ISM.
 This is most significant at $\sim$20~Myr, when the fraction of metals in the CNM from these sources is a factor of $\sim$3-4 higher than the E46 metals.
@@
 
-However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, corresponding to the mass fraction of the CNM at this point in the galaxy's evolution (see Figure~\ref{ch1:fig:}).
+However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, corresponding to the mass fraction of the CNM at this point in the galaxy's evolution (see Figure~\ref{ch1:figISM_evolution}).
 This trend -- that the fraction of metals contained in a given phases tends towards the mass fraction of that phase -- is true across all phases in the simulation.
@@
 Because these two quantities provide a more immediate conceptual understanding of how metals are distributed in the ISM, we focus on characterizing the inhomogeneity of the followed metals by examining the mean-median difference.
-Though this quantity being zero is necessary for metals to be homogeneously distributed in a medium, we do note that it is not a sufficient condition.
-However, as noted, its evolution is easy to interpret conceptually.
-Enrichment increases this quantity by raising the mean metal fraction while keeping the median value fixed (or only slightly increasing), so long as the newly enriched mass is a small fraction of the total gas mass (as is usually the case).
+Though it is necessary for this quantity to be zero for metals to be homogeneously distributed in a medium, we do note that it is not a sufficient condition (the mean of a symmetric distribution is equal to the median).
+However, its evolution is easy to interpret conceptually.
+Enrichment increases this quantity by raising the mean metal fraction while keeping the median value fixed (or only slightly increasing), so long as the newly enriched mass is a small fraction of the total gas mass (as is almost always the case).
 Conversely, preferential removal of metals from a medium will lower this quantity.
 And finally, the mixing of metal-rich gas elements with metal-poor will gradually bring the mean and median values to parity.
-For our numerical experiments, enrichment in the whole ISM only occurs once, while ejection from the ISM is easy to follow.
+For our numerical experiments, enrichment in the whole ISM only occurs once and ejection from the ISM is easy to follow.
 This allows for a more clean interpretation of the evolution than examining either the IQR or the IDR.
@@
   \centering
-  \includegraphics[width=0.75\linewidth]{figures/ch4/ISM_CNM_average_mean-median}
+  \includegraphics[width=0.975\linewidth]{figures/ch4/ISM_CNM_average_mean-median}
   \caption{Time evolution of the difference (in dex) between the mean metal mass fraction of each source and the median metal mass fraction of each source in all of the gas in the ISM (left) and in the CNM only (right).}
-  \label{ch4:fig:CGM_CNM}
+  \label{ch4:fig:mean-median}
 \end{figure*}
@@
 In all cases, enrichment drives the dramatic increase of this value from zero to over 10 dex.
-This large value is due entirely because the initial abundance for each metal is zero.
-This is followed by a significant decrease in spread over he first 25~Myr or so as metals are preferentially ejected from the ISM via outflows.
+This large value is due entirely because the initial abundance for each metal is near zero and thus a majority of the gas (by mass) is at an arbitrarily small metal mass fraction.
+This is followed by a significant decrease in spread over the first 25~Myr or so as metals are preferentially ejected from the ISM via outflows.
 The delay in this spike in the CNM (compared to the galaxy as a whole) is due to the different timescales over which most of the metals are incorporated into the cold gas, as shown in Figure~\ref{ch4:fig:ISM_CGM}.
@@
 \textit{Need to fix up: This is in agreement with the understanding that the mxiing timescales should correspond to XXX, which suggests that it would take $\sim$X~Gyr (1 Gyr?) for the metals to be fully mixed}.
-Interestingly, however, the injection energy for a given sources leaves an indelible impact on the subsequent evolution of those metals in the ISM throughout the simulation time.
+Interestingly, however, the injection energy for a given source leaves an indelible impact on the subsequent evolution of those metals in the ISM throughout the simulation time.
 We demonstrate that variations in abundance spread across elements may be driven significantly by the enrichment site and its associated $E_{\rm ej}$.
-Metals from II\_E46 are significantly less well-mixed than their higher-energy counterparts at II\_E51 and II\_E52.
-Interestingly, II\_E49 behaves much more similarly to II\_E46 -- with poor mixing -- even though it is much closer in energy to the II\_E51.
+Metals from \runone E46 are significantly less well-mixed than their higher-energy counterparts at \runone E51 and \runone E52.
+Interestingly, \runone E49 behaves much more similarly to \runone E46 -- with poor mixing -- even though it is much closer in energy to the \runone E51.
 For what mixing does occur in the CNM for these elements, it is apparent that it happens much faster ($\sim$20~Myr) for the highest energy event than the lower energy events which take longer to plateau to a consistent value.
 
-We note that these results are given for \textit{single} enrichment events.
+We note that these results are given for the average behavior of \textit{single} enrichment events.
 If many events occur throughout the galaxy with similar metal yields then this would tend to decrease the abundance variations across the galaxy.
-However, the AGB wind metals examined in Chapter~\ref{ch:chapter3} are still more heterogeneously distributed than core collapse SNe elements in spite of the fact that these events are both more common than SNe and are more evenly distributed throughout the galaxy.
+Indeed, the recovered metal mass fraction spreads from our fiducial simulations in Chapter~\ref{ch:chapter3} are much lower ($\sim$~1- 2 dex) than the $\sim$~2-5 dex widths we find here.
+However, it is still true that the the AGB wind metals examined in Chapter~\ref{ch:chapter3} are more heterogeneously distributed than core collapse SNe elements in spite of the fact that these events are both more common than SNe and are more evenly distributed throughout the galaxy.
 
@@
 \subsection{Event-by-Event Variation}
+\label{ch4:sec:individual event variation}
 
-For clarity we focused on the \textit{mean} evolution of individual enrichment events at fixed injection energy in the results thus far, but we turn now to discuss how much variety exists among these individual events.
-For each of the discussed runs (from set II), Figure~\ref{ch4:fig:CGM_CNM_variance} shows the fraction of metals ejected from the galaxy (left) and the fraction of metals in the ISM within the CNM (center) as a function of source energy at two different times, 20~Myr (blue) and 100~Myr (orange).
+For clarity we have focused on the \textit{mean} evolution of individual enrichment events at fixed injection energy in the results thus far.
+We turn now to discuss how much variety exists among these individual events.
+For each of the discussed runs (from set \runonenu), Figure~\ref{ch4:fig:CGM_CNM_variance} shows the fraction of metals ejected from the galaxy (left) and the fraction of metals in the ISM within the CNM (center) as a function of source energy at two different times, 20~Myr (blue) and 100~Myr (orange).
 In the right panel, we show how the spread at each of these times varies for each event.
@@
    \centering
-   \includegraphics[width=0.8\linewidth]{figures/ch4/II_Eej_CNM_avg}
+   \includegraphics[width=0.975\linewidth]{figures/ch4/II_Eej_CNM_avg}
    \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} and Figure~\ref{ch4:fig:CGM_CNM} that demonstrates the significant variation in $f_{\rm CGM}$, $f_{\rm CNM} / f_{\rm Disk}$, and the mean-median separate at fixed injection energy.
@@
 The points at different times have been offset slightly along the horizontal axes for clarity.
-Since they are only two points, we show the results from II\_E52\_r0 and II\_E52\_r300 without averaging.}
+Since they are only two points, we show the results from \runone E52\_r0 and \runone E52\_r300 without averaging.}
    \label{ch4:fig:CGM_CNM_variance}
@@
 Since the E46 events were likely to not self-interact, we additionally placed events at $r = 100$~pc and one event at each $r$ at about one scale height above the disk ($z = 50$~pc).
-For each II run, we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ as a function of radial position in the galaxy for each event in Figure~\ref{ch4:fig:radial position}.
+For each \runonenu~ run, we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ as a function of radial position in the galaxy for each event in Figure~\ref{ch4:fig:radial position}.
 The points, error bars, and colors are the same as in Figure~\ref{ch4:fig:CGM_CNM_variance}.
@@
 
-We compute the average ISM properties within a 4-zone radius ($4 \times dx$=7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each II run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event.
+We compute the average ISM properties within a 4-zone radius ($4 \times dx$=7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each \runonenu~ run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event.
 The E46 events clearly do a better job sampling the ISM density PDF, with a slight trend of decreasing $f_{\rm CGM}$ (more retained metals) with local ISM number density.
@@
 
-Finally, we examine the companion runs (I and III) to see if the global star formation rate of the galaxy drives variation in these results.
+Finally, we examine the companion run (\runtwonu) to see if the global star formation rate of the galaxy drives variation in these results.
 Although this does not help to directly account for the variation seen in the previous plots, this could provide insight into how SFR (in an averaged sense) affects the evolution of metals.
 We note that correlation with SFR is of interest not because the formation of stars by themselves, but rather the increase in feedback associated with a higher SFR (and thus a warmer / hotter ISM, greater turbulence in the ISM, and more significant outflows).
+We compare these two runs in Figure~\ref{ch4:fig:SFR_comparison_CGM_CNM}, showing runs from \runonenu~ in green and runs at the lower SFR, \runtwonu, in purple.
+$f_{\rm CGM}$ increases much more rapidly across injection energies in \runonenu.
+However, this value seems to be similar across runs for E49 and E51 by $\sim$50 Myr, with an additional increase again in the \runonenu~ simulations towards the end of the time.
+This initial spike, lull, and second increase corresponds to the period of active star formation, slightly lull, and increase in SFR experienced during the \runonenu~ simulations (see Figure~\ref{ch1:figsfr_mass_evolution}; the lull occurs between 40 and 80 Myr after the enrichment events, or during 220 - 260 Myr in that figure).
+The SFR is consistently low (or zero) throughout \runtwonu, with just a couple brief increases in SFR.
+Although E49 and E51 exhibit similar behavior across global differences in SFR, the difference in E46 is significant throughout the examined time period.
+As these sources do not contain enough energy to eject their metals from the galaxy by themselves, they are only ejected from the galaxy by being swept up in the ISM during other feedback events.
+The evolution of these events are therefore much more dependent upon the global galaxy properties.
+
+The fraction of metals contained within the CNM of the ISM does not seem to depend too strongly on the SFR, unlike $f_{\rm CGM}$.
+It is generally true that after the initial $\sim$50 Myr of enrichment, a greater fraction of the metals in the ISM are contained in the CNM during the run with the lower SFR (\runtwonu), but this difference is not large and is only significant for the higher energy events.
+In addition, the mass fraction of the CNM is greater during run \runtwonu~ than in run \runonenu, so it may simply be that the long-term evolution of the fraction of metals in the CNM is more dependent upon the phase structure of the ISM -- which is regulated by stellar feedback -- than the feedback directly.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.45\linewidth]{figures/ch4/combined_CGM_average_evolution}
+  \includegraphics[width=0.45\linewidth]{figures/ch4/combined_CNM_average_evolution}\\
+  \includegraphics[width=0.45\linewidth]{figures/ch4/combined_CNM_average_mean-median}
+  \caption{The same as Figure~\ref{ch4:fig:CGM_CNM}, but comparing across both sets of runs with different SFRs.
+Comparing across line colors for a fixed linestyle compares the difference the global SFR has on the average enrichment evolution for both $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$.}
+  \label{ch4:fig:SFR_comparison_CGM_CNM}
+\end{figure*}
+
+\textbf{Discuss Mean-median evolution here once AGB400 is up}
 
@@
 
-Galactic chemical evolution is far from ``one-zone" and metal mixing is clearly neither homogeneous nor instantaneous. In addition, the
+Galactic chemical evolution is far from ``one-zone" and metal mixing is clearly neither homogeneous nor instantaneous.
+As demonstrated in our simulations published as \cite{Emerick2018b} and as found in the analytic work of \cite{KrumholzTing2018}, the properties of metal mixing in the ISM of various galaxies depends upon the characteristics of the individual sources -- namely the energy with which they eject metals into the ISM.
+This sets the thermal phase in which these metals couple to most effectively, and the volume over which they are initial injected before additional mixing by global galactic dynamics begins to dominate.
+In short, lower energy enrichment events, like those from AGB winds, mix much more slowly throughout the ISM than metals from higher energy events, like supernovae.
+As found in \cite{Emerick2018b}, this difference is still present even when accounting for the fact that AGB events are both more common and evenly distributed in the galaxy than SNe.
+In the new work discussed in this chapter, we further explore this behavior to try and determine the evolution of individual enrichment sources -- rather than just the average behavior of many sources -- and to explore how $E_{\rm ej}$, radial position in the galaxy, local ISM density, and global galaxy SFR affects the evolution of these metals.
+
+We confirm the average trends found in previous works that sources with lower $E_{\rm ej}$ have larger abundance spreads in the ISM and lower ejection fractions, on average.
+In addition, we find that $E_{\rm ej}$ of the event and the global SFR during the time at which the event occurs produce the greatest variation in how many metals are retained by the galaxy, what fraction of those metals are contained within the CNM, and their homogeneity.
+Metals are in general ejected more effectively and mix more efficiently during periods of higher SFR than low, corresponding to periods of more effective galactic outflows and greater turbulence in the ISM.
+Although we have limited statistics to determine a conclusive trend, we generally find that the radial position at which the event occurs and the local ISM density in which the event occurs to not have a significant effect on the average behavior of enrichment events, with the exception of the lower energy (E46) events.
+However, we find these results to only be loose trends about the average behavior of enrichment sources.
+The evolution of individual events can be dramatically different, even at fixed energy and global galaxy SFR.
 
 Variations with individual events in the above results suggests that it would be challenging to make any conclusive statements about the enrichment behavior of single enrichment sources.
-This is problematic for interpreting the chemical abundances in UFDs that are likely to have been host to just a single, exotic enrichment event.
+\textbf{Go back and look again at one-shot enrichment paper} This is problematic for interpreting the chemical abundances in UFDs that are likely to have been host to just a single, exotic enrichment event.
 Using these observations to constrain the total nucelosynthetic yields of these sources requires implicit assumptions about how quickly metals are available in star forming gas, how homogenously they are distributed throughout the galaxy, and what fraction are ejected from the galaxy.
@@
 Then, the observed properties of an individual galaxy can be mapped to this XXXXXX
-
-Not sure how much to put in here, and may very well need to just pull out some of the above and put it here.
 

### 2019-04-03 thesis/chapters/ch_chapter3.tex
Updated references and new refences for ch4

@@
 These differences could provide important signatures for distinguishing individual, exotic enrichment sources from observed stellar abundance patterns in our own Milky Way and in nearby dwarf galaxies.
-In particular, low mass dwarf galaxies with unusual (compared to Milky Way, solar abundances) r-process enrichment \citep[e.g.][]{Ji2016,Ji2018b,Duggan2018}, are valuable for constraining the source of these elements, their frequency, and typical yields.
+In particular, low mass dwarf galaxies with unusual (compared to Milky Way, solar abundances) r-process enrichment \citep[e.g.][]{Ji2016,Duggan2018,Ji2019}, are valuable for constraining the source of these elements, their frequency, and typical yields.
 The differential metal evolution presented in our work both opens up an additional avenue by which elements from distinct nucleosynthetic sources may be distinguished in observations and challenges current assumptions used in interpreting these observations.

### 2019-04-03 thesis/chapters/ch_introduction.tex
Updated references and new refences for ch4

@@
 This process of galactic archeology aims to break down and identify each distinct stellar component of our Galaxy, explaining the process of their formation and evolution.
-Substantial work has been made recently to determine the efficacy of this approach \citep[e.g.][]{Ting2012,Hogg2016,Jofre107,Price-Jones2018,Armillotta2018}, yet the physical processes that give rise to stellar abundances as we observe them today are still uncertain.
+Substantial work has been made recently to determine the efficacy of this approach \citep[e.g.][]{Ting2012,Hogg2016,Jofre2017,Price-Jones2018,Armillotta2018}, yet the physical processes that give rise to stellar abundances as we observe them today are still uncertain.
 
@@
 These metals by themselves act as additional radiative coolants, which strongly dictate the shape of the cooling curve that helps establish a multi-phase medium in the first place \citep[e.g.][]{McKeeOstriker1977}.
-The molecules produced in chemical reactions with these metals produce additional coolants in the ISM \citep{HollenbackMcKee1979}, including dust, which has its own rich array of associated physical processes \citep{Omukai2000,Omukai2005,Draine2011}.
+The molecules produced in chemical reactions with these metals produce additional coolants in the ISM \citep{HollenbachMcKee1979}, including dust, which has its own rich array of associated physical processes \citep{Omukai2000,Omukai2005,Draine2011}.
 
@@
 More complex simulations often track some number (usually $< 10$) of species involved in primordial chemistry in order to better account for non-equilibrium effects and \Hmolecular production, though with noted increases in memory requirements and computational cost.
-Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2015,Richings2018}; but these are typically prohibitively expensive to run on large scales.
+Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2016,Richings2018}; but these are typically prohibitively expensive to run on large scales.
 In this \dissertation we adopt the chemistry and radiative cooling and heating physics models available in the newly developed, open-source library \code{GRACKLE} \citep{GrackleMethod}.

### 2019-04-03 thesis/chapters/ch_chapter4.tex
Finished draft (mostly). Just a few spots to compute numbers and check references

@@
 \section{Introduction}
+
+The elemental abundances of a galaxy over time are sensitive to the nuclear physics and stellar astrophysics that determines which stars make what elements and when.
+The stellar abundance patters within a given galaxy also depend on the details of how those metals are released into the ISM through various forms of stellar feedback, and the hydrodynamic interactions that ultimately mix those elements into the ISM or eject them from the galaxy in galactic winds.
+Stellar abundance patterns in old, metal poor systems are the result of enrichment from substantially fewer sources than younger, more metal rich stellar populations.
+Because of this, studying abundance patterns in these environments allows us to place constraints on the yields of individual enrichment events and the nucleosynthetic sites of each element.
+The lowest mass dwarf galaxies in the Local Group, UFDs, offer some of the best constraints on these processes.
+These environments can potentially be used to trace and constrain enrichment from the first stars \citep[e.g.][]{FrebelBromm2012,Ji2015,Ritter2015,Jeon2017,Hartwig2018}.
+and have been used to place constraints on the variety of possible astrophysical sources of r-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Ojima2018,Duggan2018}.
+It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way is much more uniform, averaging over the variety of complex hydrodynamics and feedback-driven turbulence interactions that may be driving much of the significant variance in stellar abundances seen at low metallicity.
+Stochasticity, which has been shown to be important for setting the width of stellar abundance patterns low metallicity environments of the Milky Way \citep[e.g.][]{Cescutti2008,Cescutti2014}, plays an even greater role in the evolution of these low mass dwarf galaxies \citep{Applebaum2018}.
+This complicates the interpretation of abundance patters in these galaxies, particularly for constraining individual enrichment events.
+
+Recent cosmological zoom simulations have attained sufficient resolution to follow the evolution of individual UFDs (or their progenitors at high redshift) (references) and begin investigating their chemical properties \citep{Jeon2017,Corlies2018,Escala2018}.
+Additional works have conducted more direct investigations into what drives the enrichment process for individual sources using both hydrodynamics simulations \citep{PanScannapiecoScalo2013,Ritter2015,Safarzadeh2017,Hirai2015,Hirai2017,Emerick2018b,Haynes2019} and semi-analytic models \citep{Beniamani2018,KrumholzTing2018}.
+In \cite{Emerick2018b} we demonstrate that elements released through AGB winds have both wider abundance distributions in the ISM and lower ejection fractions from the galaxy than elements released in supernovae.
+It is becoming increasingly clear that enrichment is quite inhomogeneous in low mass dwarf galaxies (refs?), and also that the behavior of metals from any one enrichment event depends on a significant number of complex interactions.
+In spite of this progress, there is still substantial work to be done in understanding the physical processes that drive both evolution of both the mean and width of stellar abundances in low-mass dwarf galaxies.
+
+In this Chapter we utilize the simulations analyzed in prior chapters to conduct a controlled set of ``mixing experiments'' whereby we restart each simulation with enrichment events placed by-hand in order to more directly investigate the evolution of metals from an individual event.
+While elemental yields were tracked for each star in our simulation, we lacked the necessary Lagrangian information about the metals once they were released into the ISM to be able to trace the evolution of single enrichment events.
+We investigate primarily how the feedback ejection energy of individual sources ($E_{\rm ej}$) and global star formation rate at the time of enrichment affects how metals are ejected from the galaxy in galactic winds and metal mixing in the ISM.
+In Section~\ref{ch4:sec:methods} we briefly outline our methods and discuss the setup of these mixing experiments.
+In Section~\ref{ch4:sec:results} we discuss the results of these experiments and the role of $E_{\rm ej}$, global SFR, radial position of the enrichment event, and local ISM density around each enrichment sources affects the evolution of its metals, and discuss and conclude in Section~\ref{ch4:sec:discussion conclusion}.
 
@@
 \section{Results}
-
+\label{ch4:sec:results}
 Perhaps the three most important parameters to quantify for each enrichment event are: 1) what fraction of released metals are immediately available for star formation, 2) what fraction of metals are carried out of the galaxy in outflows, and 3) how and over what timescale do metals cool from hot phases into star forming gas.
@@
 The averaged values at each energy are shown as points, and the bars denote the min/max value for each event energy.\footnote{While the standard deviation or IQR may be more informative here, rather than min / max, the sample size at each energy, with the exception of the E46 runs, is too small to reliably do so.} As shown, there is substantial variation at each energy.
-This is particularly striking for the E46 events, which seemingly can have effectively any value for $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ at any point during the evolution.
+This is particularly striking for the E46 events, which seemingly can have any value of $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ at any point during the evolution.
 Finally, the right panel shows that the degree of inhomogeneous mixing for each event varies significantly as well.
@@
 Do additional properties about the injection site (ISM density, position, local SFR), determine the subsequent evolution?
-Or is this the result of a complex, non-deterministic set of complex interactions the metals from a given event experience over their lifetime in the galaxy?
+Or is this the result of a non-deterministic set of complex interactions the metals from a given event experience over their lifetime in the galaxy?
 We investigate the dependence on a few of these properties below.
@@
 \label{ch4:sec:radial position}
-We place each source in regular, but arbitrary, positions in the galaxy without consideration for the local ISM conditions at injection.
+We place each source at regular, but arbitrary, positions in the galaxy without consideration for the local ISM conditions at injection.
 Sources are placed at the center of the galaxy ($r = 0$~pc) or at various radii (at cardinal positions at 300~pc, and 600~pc), all in the mid-place of the galaxy.
@@
    \centering
-   \includegraphics[width=0.95\linewidth]{figures/ch4/II_radial_dependence}
+   \includegraphics[angle=90,width=0.99\linewidth]{figures/ch4/II_radial_dependence}
    \caption{The dependence of $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ on the radial position of each event at two different times in the evolution of the galaxy.
@@
 There is a slight increase in the minimum fraction of metals ejected from the galaxy as a function of radius for the higher energy runs ($>10^{50}$~erg).
-This perhaps not surprising for the largest radii as 600~pc is right near the very edge of the galaxy's disk.
+This is perhaps not surprising for the largest radii as 600~pc is right near the very edge of the galaxy's disk.
 But again, the trend is weak and there is clearly still a great variance at both fixed $E_{\rm ej}$ and $r$.
-The fraction of metals in the ISM that are contained within the CNM (middle row) does not show any obvious trend at E46, but does seem to generally be lowest for the higher energy sources at the outskirts of the galaxy.
-Finally, the radial position does seem to somewhat affect the mixing behavior.
-Sources at the outskirts of the galaxy tend to be more inhomogeneous than sources at smaller radii, especially at 20~Myr for the higher energy events, and the variation in behavior for these sources decreases substantially, particularly at 100~Myr.
+The fraction of metals in the ISM that are contained within the CNM (middle row) do not show any obvious trend at E46, but does seem to generally be lowest for the higher energy sources at the outskirts of the galaxy.
+Finally, the radial position does seem to affect the mixing behavior.
+Sources at the outskirts of the galaxy tend to be more inhomogeneous than sources at inner radii, especially at 20~Myr for the higher energy events, and the variation in behavior for these sources decreases substantially, particularly at 100~Myr.
 It is unclear what exactly drives these mixing differences.
@@
 
-We compute the average ISM properties within a 4-zone radius ($4 \times dx$=7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each \runonenu~ run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event.
+We compute the average ISM properties within a 4-zone radius ($4 \times dx$~=~7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each \runonenu~ run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event.
 The E46 events clearly do a better job sampling the ISM density PDF, with a slight trend of decreasing $f_{\rm CGM}$ (more retained metals) with local ISM number density.
-This difference is even true after 100~Myr of evoltuion, but still with significant variation at fixed $n$.
+This difference is even true after 100~Myr of evolution, but still with significant variation at fixed $n$.
 The number statistics limit a conclusive result for the higher energy events, but generally there does not appear to be an obvious trend in behavior of $f_{\rm CGM}$ as a function of $n$.
-This is perhaps because these energies are sufficient to heat up and dramatically reduce the density of the ISM in the injection region anyway, such that $n$ before the event is not as important as it is for the E46 events which are much less dynamically important.
+This is perhaps because these energies are sufficient to heat up and dramatically reduce the density of the ISM in the injection region regardless of $n$.
+This is not the case for the E46 events.
 $f_{\rm CNM} / f_{\rm Disk}$ does not display any significant variation with $n$ at 100~Myr, but is slightly elevated at 20~Myr at higher densities.
@@
    \centering
-   \includegraphics[width=0.95\linewidth]{figures/ch4/II_n_dependence}
+   \includegraphics[angle=90,width=0.99\linewidth]{figures/ch4/II_n_dependence}
    \caption{The variation of $f_{\rm CGM}$, $f_{\rm CNM} / f_{\rm Disk}$, and the spread of the metal fraction PDFs in the ISM as a function of the local ISM number density ($n$) within the injection region of the event just prior (within 0.1~Myr) of the event.
@@
 \section{Discussion and Conclusions}
+\label{ch4:sec:discussion conclusion}
 
@@
 \textbf{Go back and look again at one-shot enrichment paper} This is problematic for interpreting the chemical abundances in UFDs that are likely to have been host to just a single, exotic enrichment event.
-Using these observations to constrain the total nucelosynthetic yields of these sources requires implicit assumptions about how quickly metals are available in star forming gas, how homogenously they are distributed throughout the galaxy, and what fraction are ejected from the galaxy.
+Using these observations to constrain the total nucleosynthetic yields of these sources requires implicit assumptions about how quickly metals are available in star forming gas, how homogeneously they are distributed throughout the galaxy, and what fraction are ejected from the galaxy.
 It is likely that none of these quantities can be determined as simple parameters based upon the feedback properties of a single enrichment source or even the global properties of a galaxy (such as $M_{\rm halo}$, $\Sigma_{\rm SFR}$, $\Sigma_{\rm gas}$).
 However, this study has shown that these parameters can be characterized in an averaged sense, even though the exact result is subject to substantial stochastic effects.
-This, combined with some mechanism to provide this stochasticity, can be used in combination with many runs of a simple galactic chemical evolution model to understand the possible outcomes for various XXXXX.
-Then, the observed properties of an individual galaxy can be mapped to this XXXXXX
+This, combined with some mechanism to provide this stochasticity, can be used in combination with many runs of a simple galactic chemical evolution model to understand the possible outcomes for various galaxies.
+Developing such a model will be a powerful tool for interpreting the irregular stellar abundance patterns observed in low mass dwarf galaxies in the nearby Universe.
 

### 2019-04-03 thesis/chapters/ch_chapter4.tex
FIxed citation typo. Fixed reference with same first name authors

@@
 Recent cosmological zoom simulations have attained sufficient resolution to follow the evolution of individual UFDs (or their progenitors at high redshift) (references) and begin investigating their chemical properties \citep{Jeon2017,Corlies2018,Escala2018}.
-Additional works have conducted more direct investigations into what drives the enrichment process for individual sources using both hydrodynamics simulations \citep{PanScannapiecoScalo2013,Ritter2015,Safarzadeh2017,Hirai2015,Hirai2017,Emerick2018b,Haynes2019} and semi-analytic models \citep{Beniamani2018,KrumholzTing2018}.
+Additional works have conducted more direct investigations into what drives the enrichment process for individual sources using both hydrodynamics simulations \citep{PanScannapiecoScalo2013,Ritter2015,Safarzadeh2017,Hirai2015,Hirai2017,Emerick2018b,HaynesKobayashi2019} and semi-analytic models \citep{Beniamini2018,KrumholzTing2018}.
 In \cite{Emerick2018b} we demonstrate that elements released through AGB winds have both wider abundance distributions in the ISM and lower ejection fractions from the galaxy than elements released in supernovae.

### 2019-04-03 thesis/chapters/ch_chapter4.tex
finalized draft of chapter 4 with references

@@
-\chapter[Mixing Properties of Individual Enrichment Sources as a Function of Energy]{Mixing Properties of Individual Enrichment Sources as a Function of Energy\label{ch:chapter4}}
+\chapter[Mixing Properties of Individual Enrichment Sources]{Mixing Properties of Individual Enrichment Sources\label{ch:chapter4}}
+\begingroup
 \let\thefootnote\relax\footnotetext{This section contains unpublished work-in-progress}
+\endgroup
 
@@
 These environments can potentially be used to trace and constrain enrichment from the first stars \citep[e.g.][]{FrebelBromm2012,Ji2015,Ritter2015,Jeon2017,Hartwig2018}.
-and have been used to place constraints on the variety of possible astrophysical sources of r-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Ojima2018,Duggan2018}.
+and have been used to place constraints on the variety of possible astrophysical sources of r-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Duggan2018,Nagasawa2018,Ojima2018}.
 It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way is much more uniform, averaging over the variety of complex hydrodynamics and feedback-driven turbulence interactions that may be driving much of the significant variance in stellar abundances seen at low metallicity.
 Stochasticity, which has been shown to be important for setting the width of stellar abundance patterns low metallicity environments of the Milky Way \citep[e.g.][]{Cescutti2008,Cescutti2014}, plays an even greater role in the evolution of these low mass dwarf galaxies \citep{Applebaum2018}.
+Indeed the increase in scatter in the stellar abundance patters of low mass dwarf galaxies and UFDs has been attributed to inhomogeneous mixing and stochastic effects \citep[e.g.][]{Norris2010a,Simon2015,Mashonkina2017,Suda2017}.
 This complicates the interpretation of abundance patters in these galaxies, particularly for constraining individual enrichment events.
 
-Recent cosmological zoom simulations have attained sufficient resolution to follow the evolution of individual UFDs (or their progenitors at high redshift) (references) and begin investigating their chemical properties \citep{Jeon2017,Corlies2018,Escala2018}.
+% Maybe cite Norris2010a, Simon2015, Nissen1994 for abundance spreads in UFDs?
+
+Recent cosmological zoom simulations have attained sufficient resolution to follow the evolution of individual UFDs (or their progenitors at high redshift) and can investigate their chemical properties \citep{Jeon2017,Corlies2018,Escala2018,Christensen2018}.
 Additional works have conducted more direct investigations into what drives the enrichment process for individual sources using both hydrodynamics simulations \citep{PanScannapiecoScalo2013,Ritter2015,Safarzadeh2017,Hirai2015,Hirai2017,Emerick2018b,HaynesKobayashi2019} and semi-analytic models \citep{Beniamini2018,KrumholzTing2018}.
@@
 Therefore, we can consider that the metals for each source are well-mixed across the \textit{phases} of the ISM on timescales of $\sim$100-150~Myr.
-\textbf{Compute the cooling timescale of each phase (maybe with a phase diagram?) and also the dynamical timescale and make comparisons here.}.
+This is comparable, but less than, the dynamical timescale of the galaxy, $\sim$200~Myr.
 These two results suggest that the delay-time between when metals are available to enrich ongoing star formation is on order of $\sim$10~Myr across sources, and only significant for the lowest (E46, AGB-like) energy sources.
@@
 For example, r-process enrichment from exotic enrichment events like hypernovae should manifest itself as more well-mixed than if the elements originated in lower energy NS-NS mergers.
-\textbf{Go back to reticulum papers and see what the spreads on these are}
+Conducting this analysis requires measured r-process abundances for a large sample of stars in an individual dwarf galaxy.
+This is challenging for the lowest mass, most metal poor dwarf galaxies, which typically only have a few to 10 stars with measured abundances, but could be done for more a few low mass dwarfs like Ursa Minor, and for more massive dwarfs like Carina, and Fornax \citep{Suda2017}.
+% somerthing about needing cool onezone chemical models to try and model data with many free params might be nice here.
 
@@
 
-\textbf{Discuss Mean-median evolution here once AGB400 is up}
+Finally, examining the last panel of Figure~\ref{ch4:fig:SFR_comparison_CGM_CNM}, it does appear that the mixing efficiency of metals for each source increases with increasing global SFR.
+In the initial evolution, all events in run \runtwonu exhibit larger abundance spreads that take longer to begin mixing substantially than their counterparts in \runonenu.
+In general, \runtwonu~abundances remains larger for the first 100~Myr.
+The differences depend on the ejection energy, with the most significant difference found in comparing the E46 runs.
+% May need more text here
 

### 2019-04-03 thesis/chapters/ch_chapter2.tex
Correceted footnotes. updated references. adjusting figures for fit

@@
 \chapter[Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies]{Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies \label{ch:chapter2}}
+\begingroup
 \let\thefootnote\relax\footnotetext{This section contains text from an article published originally as \cite{Emerick2018a}}
-
+\endgroup
 %
@@
 \centering
-\includegraphics[width=0.99\linewidth]{figures/ch2/mass_density_cut}
+\includegraphics[width=0.65\linewidth]{figures/ch2/mass_density_cut}
 \caption{The total gas mass at $n > 200$~cm$^{-3}$, our star formation density threshold.}
@@
 Each panel is 4 kpc x 4 kpc.
-The full movie of this evolution from 0 to 118 Myr is included for further clarification.
-This movie demonstrates that the differences in outflows between the simulations depends on the ability for feedback to carve low-density, ionized channels along which SNe can launch gas beyond the disk of the galaxy.
+%The full movie of this evolution from 0 to 118 Myr is included for further clarification.
+See \cite{Emerick2018a} for a movie of this evolution.}
+%The movie demonstrates that the differences in outflows between the simulations depends on the ability for feedback to carve low-density, ionized channels along which SNe can launch gas beyond the disk of the galaxy.
 These channels are readily created by ionizing radiation in the fiducial simulation, or to some degree by SNe in the noRT simulation due to its much higher SN rate.

### 2019-04-03 thesis/chapters/ch_chapter1.tex
Correceted footnotes. updated references. adjusting figures for fit
Final plot size shifting for chapters. Fixing ch1 figure labels.

@@
 \chapter[Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars ]{Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars \label{ch:chapter1}}
+\begingroup
 \let\thefootnote\relax\footnotetext{This section contains text from an article published originally as \cite{Emerick2019}}
-
+\endgroup
 %
@@
 
-We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Fig.~\ref{ch1:figpanel_x} and Fig.~\ref{ch1:figpanel_z}.
+We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Fig.~\ref{ch1:fig:panel_x} and Fig.~\ref{ch1:fig:panel_z}.
 These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution.
@@
 Each individual main sequence star particle is shown in the number density projections as a single white dot.}
-\label{ch1:figpanel_x}
-\end{figure*}
-
-The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{ch1:figscale_height}.
+\label{ch1:fig:panel_x}
+\end{figure*}
+
+The initially puffy gas distribution collapses to a thin disk, with scale heights between 10--30~pc, as shown by the blue line in Fig~\ref{ch1:fig:scale_height}.
 This figure shows the scale height of all gas in the disk, averaged over 20~Myr periods centered on each given time.
@@
 For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}.
-In the final column of Fig.~\ref{ch1:figpanel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
+In the final column of Fig.~\ref{ch1:fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc.
 With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view.
@@
 \includegraphics[width=0.975\linewidth]{figures/ch1/multiplot_4x4_z.png}
-\caption{Same as Fig.~\ref{ch1:figpanel_x}, but showing face-on views.}
-\label{ch1:figpanel_z}
+\caption{Same as Fig.~\ref{ch1:fig:panel_x}, but showing face-on views.}
+\label{ch1:fig:panel_z}
 \end{figure*}
@@
 \includegraphics[width=0.75\linewidth]{figures/ch1/scale_height}
-\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{ch1:figpanel_x} and ~\ref{ch1:figpanel_z}.}
-\label{ch1:figscale_height}
+\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{ch1:fig:panel_x} and ~\ref{ch1:fig:panel_z}.}
+\label{ch1:fig:scale_height}
 \end{figure}
@@
 
-We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Fig.~\ref{ch1:figsfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
+We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Fig.~\ref{ch1:fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr.
 The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$.
@@
 At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component.
-By the time of first star formation ($t=0$ in Fig.~\ref{ch1:figsfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
+By the time of first star formation ($t=0$ in Fig.~\ref{ch1:fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%.
 The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback.
@@
 Right: The evolution of the total gas mass (black), HI mass (blue), H$_2$ mass (orange), and stellar mass (red) in the disk of our galaxy over time.}
-\label{ch1:figsfr_mass_evolution}
+\label{ch1:fig:sfr_mass_evolution}
 \end{figure*}
@@
 
-Fig.~\ref{ch1:figphase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
-One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Fig.~\ref{ch1:figISM_evolution}).
+Fig.~\ref{ch1:fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr.
+One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Fig.~\ref{ch1:fig:ISM_evolution}).
 Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium.
@@
 The region in the lower right corner indicates our density and temperature thresholds for star formation.}
-\label{ch1:figphase}
+\label{ch1:fig:phase}
 \end{figure}
 
-The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Fig.~\ref{ch1:figISM_evolution}.
+The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Fig.~\ref{ch1:fig:ISM_evolution}.
 The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component.
@@
 However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable.
-Together, these figures better quantify the general properties observed in the panel plots in Fig.~\ref{ch1:figpanel_x} and Fig.~\ref{ch1:figpanel_z}.
+Together, these figures better quantify the general properties observed in the panel plots in Fig.~\ref{ch1:fig:panel_x} and Fig.~\ref{ch1:fig:panel_z}.
 
@@
 \caption{The evolution of the mass and volume fractions for each phase of the model galaxy's ISM. See Appendix~\ref{appendix:phases} for definitions of each phase.}
-\label{ch1:figISM_evolution}
+\label{ch1:fig:ISM_evolution}
 \end{figure*}
@@
 This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve.
-In Fig.~\ref{ch1:figISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
+In Fig.~\ref{ch1:fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr.
 The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{ch1:sec:diffusive heating}).
@@
 In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
-\label{ch1:figISRF}
+\label{ch1:fig:ISRF}
 \end{figure}
@@
 \begin{figure}
-%\centering
-\includegraphics[width=0.475\linewidth]{figures/ch1/g_o_2D_phase}
-\includegraphics[width=0.475\linewidth]{figures/ch1/q_o_2D_phase}
+\centering
+\includegraphics[width=0.62\linewidth]{figures/ch1/g_o_2D_phase}\\
+\includegraphics[width=0.62\linewidth]{figures/ch1/q_o_2D_phase}
 \caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy.
 Here, we include all gas within the mid-plane of our dwarf galaxy.
-Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{ch1:figphase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
+Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{ch1:fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram.
 This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
-\label{ch1:figISRF_2D}
+\label{ch1:fig:ISRF_2D}
 \end{figure}
 
-To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Fig.~\ref{ch1:figISRF_2D} at a single snapshot at 300~Myr.
+To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Fig.~\ref{ch1:fig:ISRF_2D} at a single snapshot at 300~Myr.
 This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower.
@@
 However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}.
-In Fig.~\ref{ch1:figmass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
+In Fig.~\ref{ch1:fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy.
 We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
@@
 
-The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Fig.~\ref{ch1:figmass_outflow}.
+The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Fig.~\ref{ch1:fig:mass_outflow}.
 Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor.
@@
 \caption{Spherical mass outflow rates (Eq.~[\ref{eq:dotM}]) and mass loading rates over time at 4 different radii from the galaxy.}
-\label{ch1:figmass_outflow}
+\label{ch1:fig:mass_outflow}
 \end{figure*}
@@
 Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations.
-In Fig.~\ref{ch1:figoutflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
+In Fig.~\ref{ch1:fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases.
 Gas with a negative velocity is moving towards the center of the halo.
@@
 \caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy.
-This is averaged over the same time interval as Fig.~\ref{ch1:figISRF}.
+This is averaged over the same time interval as Fig.~\ref{ch1:fig:ISRF}.
 The outflowing material is multiphase, broken into WNM, WIM, and HIM.
@@
 There is little to no outflowing mass in the CNM.}
-\label{ch1:figoutflow_velocity}
+\label{ch1:fig:outflow_velocity}
 \end{figure}
@@
 This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}.
-In the left panel of Fig.~\ref{ch1:figmetal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{ch1:figmass_outflow}.
+In the left panel of Fig.~\ref{ch1:fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{ch1:fig:mass_outflow}.
 The parameter used to quantify metal outflow efficiencies varies among works.
@@
 where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars.
-These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{ch1:figmass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
+These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{ch1:fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5.
 On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5).
@@
 \includegraphics[width=0.475\linewidth]{figures/ch1/metal_retention}
-\caption{{\bf Left}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{ch1:figmass_outflow}.
+\caption{{\bf Left}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{ch1:fig:mass_outflow}.
 This is the ratio between the metal outflow rate and the metal production rate.
@@
 In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
-\label{ch1:figmetal_evolution}
+\label{ch1:fig:metal_evolution}
 \end{figure}
@@
 These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk.
-This is quantified in the right panel of Fig.~\ref{ch1:figmetal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
+This is quantified in the right panel of Fig.~\ref{ch1:fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time.
 After the first 20 Myr, SN-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo.
@@
 
-We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{ch1:figmetal_slices}.
+We demonstrate the power of our simulations, which capture a realistic ISM at high resolution with multiple feedback sources, by addressing these questions in Fig~\ref{ch1:fig:metal_slices}.
 The left panel gives the abundance ratio of N to O throughout the ISM.
@@
 In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occurred in the preceding 5 Myr as black stars and orange diamonds respectively.}
-\label{ch1:figmetal_slices}
+\label{ch1:fig:metal_slices}
 \end{figure*}
@@
 Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$).
-Given the variations in Fig.~\ref{ch1:figmetal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
+Given the variations in Fig.~\ref{ch1:fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy.
 The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM.
@@
 However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small.
-In Figure ~\ref{ch1:figKS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
+In Figure ~\ref{ch1:fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt relation and extended Schmidt law for low mass galaxies.
 In both diagrams, our simulations are given by the colored points, sampled every megayear throughout the entire simulation.
@@
 There is no clear correlation with time in this diagram.}
-\label{ch1:figKS}
-\end{figure*}
-
-We include recent observational constraints on these relationships in Figure ~\ref{ch1:figKS}.
+\label{ch1:fig:KS}
+\end{figure*}
+
+We include recent observational constraints on these relationships in Figure ~\ref{ch1:fig:KS}.
 Our galaxy fluctuates significantly about both relationships with no clear trends in time.
@@
 In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters.
-It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{ch1:figKS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
+It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{ch1:fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy.
 This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
@@
 \item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies.
-(See Figs.~\ref{ch1:figsfr_mass_evolution} and \ref{ch1:figKS}).
+(See Figs.~\ref{ch1:fig:sfr_mass_evolution} and \ref{ch1:fig:KS}).
 
@@
 metal mass loading factors near unity.
-By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Fig.~\ref{ch1:figoutflow_velocity}).
+By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Fig.~\ref{ch1:fig:outflow_velocity}).
 
@@
 By the end of the simulation $\sim$45\% of the remaining metals stay within the virial radius (but outside the galaxy), while $\sim$50\%
-have been ejected beyond the virial radius. (See Figs.~\ref{ch1:figmass_outflow}, \ref{ch1:figoutflow_velocity}, and \ref{ch1:figmetal_evolution}.)
+have been ejected beyond the virial radius. (See Figs.~\ref{ch1:fig:mass_outflow}, \ref{ch1:fig:outflow_velocity}, and \ref{ch1:fig:metal_evolution}.)
 
@@
 This is comparable to the resolution limit of the diffuse HI in observed, gaseous low-mass dwarfs.
-At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Fig.~\ref{ch1:figscale_height}).
+At a spatial resolution of 100~pc, our galaxy has a peak HI column density $N_{\rm HI} = 2.8-4.3 \times 10^{20}$~cm$^{-2}$, depending on inclination (See Fig.~\ref{ch1:fig:scale_height}).
 
@@
 The importance of radiation feedback in our model is investigated in more detail in \cite{Emerick2018b}.
-(See Figs.~\ref{ch1:figISRF} and \ref{ch1:figISRF_2D}.)
+(See Figs.~\ref{ch1:fig:ISRF} and \ref{ch1:fig:ISRF_2D}.)
 
@@
 Cold, neutral hydrogen dominates the mass of our galaxy.
-While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Fig.~\ref{ch1:figsfr_mass_evolution} and Fig.~\ref{ch1:figISM_evolution}.)
+While warm, neutral hydrogen is present, it does not dominate the mass fraction (See Fig.~\ref{ch1:fig:sfr_mass_evolution} and Fig.~\ref{ch1:fig:ISM_evolution}.)
 
@@
 We determine the radiation properties of our model stars as a function of stellar mass and metallicity from the OSTAR2002 grid \citep{Lanz2003} in the regime that it covers, or integrated from an adjusted black body curve for other stars, given the ZAMS stellar radius obtained from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution data set.
-In Fig.~\ref{ch1:figstellar radiation properties} we plot these properties.
+In Fig.~\ref{ch1:fig:stellar radiation properties} we plot these properties.
 We use a constant factor across metallicities for stars not sampled on the OSTAR2002 grid to shift the black body radiation fluxes to be roughly continuous with the ionizing photon rates and luminosities as a function of stellar mass.
@@
 Note, we only track radiation from stars above 8.0 \msun, which dominate over less massive stars, even when accounting for IMF weighting.}
-\label{ch1:figstellar radiation properties}
+\label{ch1:fig:stellar radiation properties}
 \end{figure*}
@@
 
-The left panel of Fig.~\ref{ch1:figSN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
+The left panel of Fig.~\ref{ch1:fig:SN histogram} gives the distributions of the peak and average ISM number densities in the SN injection regions for each SN in our fiducial simulation.
 As shown, a majority explode in regions at substantially lower densities than the star formation threshold of 200~cm$^{-3}$.
 For most SNe, $n_{\rm max} \le 1.0$~cm$^{-3}$, which is due to the substantial pre-SN feedback included in our simulations.
-The right panel of Figure ~\ref{ch1:figSN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
+The right panel of Figure ~\ref{ch1:fig:SN histogram} gives the fractional distribution of the calculated radius of the pressure-driven snowplow ($R_{\rm PDS}$) phase of the Sedov-Taylor expansion, adopting the definitions from \citet{Simpson2016}
 \begin{equation}
@@
 This shows that a fraction of these SNe are certainly unresolved, with R$_{\rm PDS}$ less than a single cell size, and somewhat more don't satisfy the 4.5 cell criterion, but the majority are well resolved.}
-\label{ch1:figSN histogram}
+\label{ch1:fig:SN histogram}
 \end{figure*}
@@
 The regimes where heating dominates are plotted with dashed lines for clarity.}
-\label{ch1:figcooling comparison}
+\label{ch1:fig:cooling comparison}
 \end{figure*}
@@
 This can be a significant effect, particularly at higher metallicities.
-We demonstrate this in Fig.~\ref{ch1:figcooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
+We demonstrate this in Fig.~\ref{ch1:fig:cooling comparison}, which gives the absolute value of the net cooling rate for our full model at $Z = 0.1$~Z$_{\odot}$ (discussed below) as compared to a model using the optically thin metal line cooling rates at a range of densities.
 The effect is most significant at moderate densities, where the net cooling rate can be an order of magnitude higher.
 In low temperature regions, this can significantly shift the inferred equilibrium temperature and reduce the cooling time of dense gas.
-Fig.~\ref{ch1:figcooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
+Fig.~\ref{ch1:fig:cooling} shows the net cooling rate and the individual heating and cooling rates from our generated tables at low metallicity, $Z = 0.01$~Z$_{\odot}$, comparable to that used in our dwarf galaxy.
 We have made these tables publicly available in the main distribution of \texttt{Grackle} and discuss how they were generated below.
@@
 rate is shown with solid lines.}
-\label{ch1:figcooling}
+\label{ch1:fig:cooling}
 \end{figure*}
@@
 To test the significance of this radiation in determining the final H$_2$ mass we run a grid of one-zone Grackle cooling models.\footnote{See the ``cooling\_cell.py'' example here for more details: https://grackle.readthedocs.io/en/latest/Python.html}  These runs iterate through the non-equillibrium chemistry and cooling solvers with a constant density (10~cm$^{-3}$) and initial temperature of 10$^{4}$~K for 200~Myr.
-In Fig.~\ref{ch1:figGrackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background.
+In Fig.~\ref{ch1:fig:Grackle grid} we plot the final H$_2$ mass fraction in these cells for variations over five orders of magnitude in the adopted H$^{-}$ photodetachment rate and the Lyman-Werner radiation background.
 As shown, the H$_2$ mass fraction is much more sensitive to the Lyman-Werner radiation field than the H$^-$ photodetachment rate.
@@
 These runs have identical initial conditions, random SN driving, cooling, heating, and chemistry as our fiducial simulation, but with no star formation.
-We vary the Lyman-Werner radiation and the H$^{-}$ photodetachment rate by the factors shown, which are comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{ch1:figISRF}).
+We vary the Lyman-Werner radiation and the H$^{-}$ photodetachment rate by the factors shown, which are comparable to the ratio between the typical ISRF and the UVB in the disk of our galaxy (see Fig.~\ref{ch1:fig:ISRF}).
 Changing the background H$^{-}$ photodetachment rate by a factor of 100 only (top left star) leads to a reduction in the final H$_2$ mass fraction by 3, while changing the Lyman-Werner background by a factor of 100 (bottom right point) decreases the H$_2$ mass by a factor of 6.9.
@@
 We note the regime below 1.0 on each axis is somewhat unphysical, and is never reached in our hydrodynamics simulations.}
-\label{ch1:figGrackle grid}
+\label{ch1:fig:Grackle grid}
 \end{figure}
@@
 
-We demonstrate the effect of varying resolution in the evolution of our galaxy model in Fig.~\ref{ch1:figresolution_study}.
+We demonstrate the effect of varying resolution in the evolution of our galaxy model in Fig.~\ref{ch1:fig:resolution_study}.
 We compare the star formation rate, mass evolution, and metal ejection / retention fractions between our fiducial high-resolution simulation (solid lines) with the same simulation at two lower maximum resolutions, 3.6~pc (dashed lines), and 7.2~pc (dash-dotted lines).
@@
 The line colors in the left panel are for better clarity between the SFRs.}
-\label{ch1:figresolution_study}
-\end{figure*}
-
-Fig.~\ref{ch1:figresolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
+\label{ch1:fig:resolution_study}
+\end{figure*}
+
+Fig.~\ref{ch1:fig:resolution_study} shows that, while decreasing the resolution certainly changes the evolution, the simulations are similar to within a factor of a few.
 We argue that these differences are within the stochastic variation one would expect from simulations with stochastic star formation.
 The star formation rate and total stellar mass is correlated with resolution, with our fiducial run having the highest SFR and stellar mass among the three runs.
-We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Fig.~\ref{ch1:figSN histogram}.
+We note that the self-consistent SNe are still resolved in the 3.6~pc runs since these still explode at the low densities seen in Fig.~\ref{ch1:fig:SN histogram}.
 However, although feedback in general is still effective in the 7.2~pc run, SNe are not well resolved at this resolution.
@@
 
-Theses differences in densities are shown clearly by comparing Fig.~\ref{ch1:figphase} with Fig.~\ref{ch1:figphase_resolution}.
+Theses differences in densities are shown clearly by comparing Fig.~\ref{ch1:fig:phase} with Fig.~\ref{ch1:fig:phase_resolution}.
 Although the lowest temperature reached in each simulation is comparable, there is less gas in the coldest, densest portion of the phase diagram in each of the lower resolution simulations.
@@
 \includegraphics[width=0.75\linewidth]{figures/ch1/6pc_phase.png}
-\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{ch1:figphase}.}
-\label{ch1:figphase_resolution}
+\caption{Temperature-density phase diagrams for our 3.6~pc run (left) and 7.2~pc run (right), as presented for our fiducial run in Fig.~\ref{ch1:fig:phase}.}
+\label{ch1:fig:phase_resolution}
 \end{figure*}

### 2019-04-03 thesis/chapters/ch_chapter4.tex
Final plot size shifting for chapters. Fixing ch1 figure labels.

@@
 \includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
-\caption{Time evolution of the }
+\caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines), the galaxy's disk (black, solid), and the CGM (black, dashed) as averaged across all events at a given $E_{\rm ej}$.
+The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases (colored lines) sum to the black, solid line.
+\textbf{Need to remake these figures}}
 \label{ch4:fig:ISM_CGM}
@@
 
-However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, corresponding to the mass fraction of the CNM at this point in the galaxy's evolution (see Figure~\ref{ch1:figISM_evolution}).
+However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, corresponding to the mass fraction of the CNM at this point in the galaxy's evolution (see Figure~\ref{ch1:fig:ISM_evolution}).
 This trend -- that the fraction of metals contained in a given phases tends towards the mass fraction of that phase -- is true across all phases in the simulation.
@@
    \centering
-   \includegraphics[angle=90,width=0.99\linewidth]{figures/ch4/II_radial_dependence}
+   \includegraphics[angle=90,width=0.9\linewidth]{figures/ch4/II_radial_dependence}
    \caption{The dependence of $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ on the radial position of each event at two different times in the evolution of the galaxy.
@@
    \centering
-   \includegraphics[angle=90,width=0.99\linewidth]{figures/ch4/II_n_dependence}
+   \includegraphics[angle=90,width=0.9\linewidth]{figures/ch4/II_n_dependence}
    \caption{The variation of $f_{\rm CGM}$, $f_{\rm CNM} / f_{\rm Disk}$, and the spread of the metal fraction PDFs in the ISM as a function of the local ISM number density ($n$) within the injection region of the event just prior (within 0.1~Myr) of the event.
@@
 However, this value seems to be similar across runs for E49 and E51 by $\sim$50 Myr, with an additional increase again in the \runonenu~ simulations towards the end of the time.
-This initial spike, lull, and second increase corresponds to the period of active star formation, slightly lull, and increase in SFR experienced during the \runonenu~ simulations (see Figure~\ref{ch1:figsfr_mass_evolution}; the lull occurs between 40 and 80 Myr after the enrichment events, or during 220 - 260 Myr in that figure).
+This initial spike, lull, and second increase corresponds to the period of active star formation, slightly lull, and increase in SFR experienced during the \runonenu~ simulations (see Figure~\ref{ch1:fig:sfr_mass_evolution}; the lull occurs between 40 and 80 Myr after the enrichment events, or during 220 - 260 Myr in that figure).
 The SFR is consistently low (or zero) throughout \runtwonu, with just a couple brief increases in SFR.

### 2019-04-03 thesis/abstract.tex
update with ch4 finished

@@
 We play particular attention to events that could be associated with different channels of r-process enrichment (for example, neutron star - neutron star mergers vs.
-hypernovae) as a way to characterize how mixing / ejection differences may manifest themselves in observed abundance patters in low mass dwarf galaxies.
-\textbf{Note to self to revisit once this chapter is written...}
+hypernovae) as a way to characterize how mixing / ejection differences may manifest themselves in observed abundance patterns in low mass dwarf galaxies.
+We find that -- on average -- the injection energy of a given enrichment source and the galaxy's global SFR at the time of injection play the strongest roles in regulating the mixing and ejection behavior of metals.
+Lower energy events are retained at a greater fraction and are more inhomogeneously distributed than metals from more energetic sources.
+However, the behavior of any single source varies dramatically, particularly for the low energy enrichment events.
+We further characterize the
+effect of radial position and local ISM density on the evolution of metals from single enrichment events.
 

### 2019-04-05 thesis/acknowledgments.tex
started writing

@@
 
+To my wife Ellen, who moved across the country for me to N.Y.C. and has put up
+with so much over the past six years just so that I could pursue my dream.
+
+I want to thank all of the other graduate students at Columbia that I have overlapped
+with over the years. This includes especially Sarah, Steven, Dan, Jeff, Adrian,
+Munier, Andrea, Alejandro, and Susan. \textit{a little more here}
+
+Thank you to everyone I have met in the NYC climbing community who have collectively
+help keep me sane throughout my time in graduate school. Over the past few years
+I have learned the importance of a proper work-life balance, and climbing has helped
+me keep that balance (... maybe a bit too well...). Thank you especially to my
+regular climbing partners -- Daniel, Hunter, Dennis, and Lauren A. -- who I've trusted
+with my life countless times, and the handful of other astronomer-climbers that I've
+climbed with throughout graduate school (Jeff, Matt, Lauren A., Dan D'Orazio,
+Dan Foreman-Mackey, and Andrea).
+
 \vspace{1.8cm}

### 2019-04-05 thesis/chapters/ch_conclusion.tex
Started writing

\chapter[Conclusion]{Conclusion}
\label{ch:conclusion}

%Summarize key results

This \dissertation has focused on building an understanding of galactic chemical evolution from the assumption that the same feedback processes that regulate star formation and drive galactic winds in galaxies also play a fundamental role in their metal enrichment. It is understood that stellar feedback plays an important role in driving metals out into the CGM and beyond in galaxies, but the exact coupling of metals to galactic winds is not well understood. This is in part because how metals mix within a multi-phase ISM to eventually be swept up in galactic outflows or mix within cold, star forming gas is not well constrained. Even more, how metals from the full range of nucleosynthetic sources, including AGB winds, stellar winds, core collapse and Type Ia supernovae, and NS-NS mergers, participate in these processes -- mixing and galactic winds -- differently has only recently been examined in efforts to better understand results from the ever increasing availability of high-quality stellar abundance measurements of stars in our own Milky Way and in nearby dwarf galaxies. In order to understand these processes and build a complete picture of metal evolution in the Universe, we have developed a new model for star formation, stellar feedback, and chemical enrichment to follow these processes in simulations of isolated dwarf galaxies. Using this model, we have made critical advancements in understanding both how stellar feedback governs the evolution of low mass dwarf galaxies and how individual metals are distributed in (and beyond) these galaxies over time. We summarize these results below, and conclude with a discussion of future research.

\section{A New Model for Galactic Chemical Enrichment}

In order to address these outstanding issues in galactic evolution, we developed a new model for galactic chemical evolution that -- for the first time in galaxy-scale simulations -- follows star particles as individual stars along with their detailed feedback and metal yields. As detailed in Chapter~\ref{ch:chapter_2} we use the AMR hydrodynamics code \textsc{Enzo}, we produce a set of simulations using this model of an idealized, isolated low-mass dwarf galaxy ($M_{\rm gas} \sim 10^{6}$~M$_{\odot}$, $M_{\rm halo} \sim 3 \times 10^{9}$~M$_{\odot}$) embedded in a static dark matter potential. Using a detailed model for gas chemistry and radiative cooling, we follow the evolution of this galaxy and its multi-phase ISM as it forms stars, depositing individual star particles sampled over 1 to 100 M$_{\odot}$. We follow the feedback processes from each of these stars, including the AGB winds from low mass stars, Lyman-Werner radiation, FUV radiation (and photoelectric heating), and ionizing radiation from massive stars, and both core collapse and Type Ia supernovae. We track the metal yields for each of these stars, following 15 individual metal species as they mix within the ISM and imprint their abundances onto the sites of future star formation or are ejected from the galaxy altogether.

summarize results here

In ongoing work we are extending these methods by implementing them in cosmological simulations of UFD galaxy evolution. Our detailed model tracking the feedback and yields from individual stars will build substantially upon recent works investigating metal enrichment at high redshift and in UFDs and their progenitors \citep[e.g.][]{Ritter2015,Jeon2017,Corlies2018}. This work includes additional improvements to the simulations presented in this \dissertation, including a model for Pop III star formation and chemical enrichment adapted from \cite{Wise2012a}, a new IMF sampling scheme that allows us to follow very low mass stars ($M_* \lesssim 2$~M$_{\odot}$) -- which have no significant feedback or metal enrichment, but are important long-lived tracers of galactic chemical enrichment -- aggregated together into a single particle during each star formation event, and improvements to the numerical implementation to ease memory consumption in these significantly larger simulations.

Finally, as part of this \dissertation we additionally produced a significant set of companion simulations at lower resolution (3.6~pc instead of 1.8~pc) turning on and off each independent feedback process (ionizing radiation, radiation pressure, LW and FUV radiation, and supernovae). With these runs, we sought to build upon recent works examining the various effects of each stellar feedback process in driving the evolution of low mass dwarf galaxies \citep{Hu2016,Hu2017,Hu2018,Forbes2016}. In future work we will examine these completed runs in more detail to better understand the complex, interconnected role multi-channel stellar feedback plays in galactic evolution. With our simulations, we can place greater emphasis on how each feedback channel drives the mixing and ejection of individual metals within and beyond low mass dwarf galaxies.
% Until recently, most (if not all) simulations of galaxy formation and evolution followed metal enrichment with a single, global metallicity field, ignoring the potential differential evolution across individual metals. Models for star formation and stellar feedback have also -- until recently -- made extensive use of phenomenological prescriptions to capture their effects on galactic evolution. With the increase in computational power

\section{Stellar Radiation Feedback in Dwarf Galaxies}

\section{Mixing and Ejection of Individual Metals}

\section{Mixing Behavior of Single-Sources}

\section{Future Work}

### 2019-04-05 thesis/chapters/ch_conclusion.tex
more written

@@
 
-summarize results here
+\textbf{summarize results from Ch 1 here}
 
@@
 
+Stellar radiation has recently been invoked as an important source of feedback -- in addition to supernovae -- that helps to regulate star formation and drive galactic winds in galaxies across the mass scale.
+This feedback channel acts immediately after the formation of massive stars and is thus an important source of pre-SN feedback.
+In addition to destroying cold gas in star forming regions, this acts to dramatically reduce the typical ISM densities in which SNe explode, increasing their impact.
+While often invoked as a source of feedback, modeling stellar radiation in galaxies in detail can be computationally expensive, with a variety of approximate methods available to reduce this expense.
+In our simulations we track the ionizing radiation from massive stars accurately using an adaptive ray-tracing radiative transfer method with sufficient resolution to capture the HII regions from individual stars.
+In Chapter~\ref{ch:chapter_2} we demonstrate that stellar ionizing radiation dramatically reduces the star formation rate and generally increases the effectiveness of galactic winds at our low-mass dwarf galaxy simulations.
+
+In addition, we explore the mechanism by which stellar radiation acts to regulate star formation and drive outflows by comparing our fiducial simulations to simulations that only account for localized ($< 20$~pc) ionization around massive stars.
+This second set of runs approximates the behavior of various approximations for stellar radiation feedback which do not follow radiation propagation in detail, but rather deposit energy / ionize gas in the immediate vicinity of newly formed stars.
+We find that star formation is regulated by ionizing radiation locally -- destroying cold gas around young, massive stars that would otherwise have formed stars -- as the $< 20$~pc restricted run (initially) shares a very similar SFR to our fiducial run.
+However, we find that these simulations exhibit dramatically different outflow properties, which drive long-term differences in galactic properties including SFR and metal retention.
+Stellar radiation at larger distance scales is important for carving out diffuse channels of gas in the ISM and into the CGM of our dwarf galaxy through which SNe can effectively blow out mass and metals from the ISM.
+This suggests that -- at least in low mass dwarf galaxies -- localized approximations of radiation feedback are likely insufficient to capturing the full effects of stellar radiation.
+
+\textbf{Maybe mention radiation comparison runs that will be examined in the future?}.
+
 \section{Mixing and Ejection of Individual Metals}
+
+\textbf{Summarize results}
 
@@
 
+\textbf{very briefly sSummarize results}
+
 \section{Future Work}
+
+\textbf{Cosmological simulations may already be mentioned above....} if so, just focus on how I implemented stuff into a onezone model to match the simualtiosn and play around iwth the effects of f$_{ej}$ and mixing timescales.
+say we will explore how this works and implement in larger onezone / semi-analytic models (cote).

### 2019-04-08 thesis/chapters/ch_chapter2.tex
Fixing figure size and labels

@@
 \caption{The star formation rate (left) and gas and stellar mass (right) of each of our three simulations over time. Time bins with no star formation are left empty.}
-\label{ch2:figsfr_mass_evolution}
+\label{ch2:fig:sfr_mass_evolution}
 \end{figure*}
 
-We compare the resulting star formation rate (left) and gas mass properties (right) of our three simulations in Figure~\ref{ch2:figsfr_mass_evolution}.
+We compare the resulting star formation rate (left) and gas mass properties (right) of our three simulations in Figure~\ref{ch2:fig:sfr_mass_evolution}.
 There is a clear, significant contrast between the runs with and without ionizing radiation.
@@
 Radiation from these stars quickly ionizes and dissipates surrounding dense gas that would otherwise have gone to fuel a significant amount of additional star formation.
-This is confirmed in Figure~\ref{ch2:figsf gas}, which shows the gas mass in each simulation above the SF density threshold of $n = 200$~cm$^{-3}$ during the first 100~Myr.
+This is confirmed in Figure~\ref{ch2:fig:sf gas}, which shows the gas mass in each simulation above the SF density threshold of $n = 200$~cm$^{-3}$ during the first 100~Myr.
 While our fiducial and shortrad simulations remain roughly the same here, the noRT run, at its peak, has an order of magnitude more cold, dense gas.
@@
 \caption{The total gas mass at $n > 200$~cm$^{-3}$, our star formation density threshold.}
-\label{ch2:figsf gas}
+\label{ch2:fig:sf gas}
 \end{figure}
@@
 This can be confirmed by examining the metal retention fraction (the fraction of produced metals retained within the disk of the galaxy) and mass outflow rates across simulations.
-As shown in Figure~\ref{ch2:figmetal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation.
+As shown in Figure~\ref{ch2:fig:metal_retention}, the mass outflow rate in the fiducial run peaks at an order of magnitude higher at 0.25~R$_{\rm vir}$ than the shortrad simulation, declining only due to a comparative drop off in star formation.
 The outflow in noRT is only a factor of a few lower than the fiducial run, but it requires a five times higher supernova rate in this simulation to match the same outflow seen with full stellar radiation feedback, so it implies a far lower mass loading factor.
@@
 \centering
-\includegraphics[width=0.32\linewidth]{figures/ch2/metal_retention}
-\includegraphics[width=0.32\linewidth]{figures/ch2/mass_outflow_comparison}
-\includegraphics[width=0.32\linewidth]{figures/ch2/mass_loading_comparison}
-\caption{{\bf Left:} The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange).
-As in Figure~\ref{ch2:figsfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively.
-{\bf Middle:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed).
-{\bf Right:} The mass loading factor $\eta$ calculated as the outflow rate divided by the SFR averaged over 100~Myr.
+\includegraphics[width=0.45\linewidth]{figures/ch2/metal_retention}
+\includegraphics[width=0.45\linewidth]{figures/ch2/mass_outflow_comparison}\\
+\includegraphics[width=0.45\linewidth]{figures/ch2/mass_loading_comparison}
+\caption{{\bf Top Left:} The fraction of metals contained within the ISM of each galaxy (blue) and the fraction ejected beyond the virial radius (orange).
+As in Figure~\ref{ch2:fig:sfr_mass_evolution}, the fiducial run is given as solid lines, while the noRT and shortrad are dash-dotted and dashed respectively.
+{\bf Top Right:} The mass outflow rate for each run at 0.25~R$_{\rm vir}$ (solid) and R$_{\rm vir}$ (dashed).
+{\bf Bottom:} The mass loading factor $\eta$ calculated as the outflow rate divided by the SFR averaged over 100~Myr.
 Inclusion of diffuse ionization makes an order of magnitude difference in $\eta$ in this case.
 }
-\label{ch2:figmetal_retention}
+\label{ch2:fig:metal_retention}
 \end{figure*}
@@
 Modeling only local stellar ionizing feedback is insufficient to describe the long-term evolution of an isolated dwarf galaxy.
-To explore the cause of this difference we compare in Figure~\ref{ch2:figpanel1} and~Figure~\ref{ch2:figpanel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.
+To explore the cause of this difference we compare in Figure~\ref{ch2:fig:panel1} and~Figure~\ref{ch2:fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.
 
@@
 However, SNe launched gas is trapped by neutral, cold shells in the shortrad simulation, unable to easily escape from the disk of the simulated galaxy.
-These same insights can also be gained by comparing this figure with Figure~\ref{ch2:figpanel2}.}
-\label{ch2:figpanel1}
+These same insights can also be gained by comparing this figure with Figure~\ref{ch2:fig:panel2}.}
+\label{ch2:fig:panel1}
 \end{figure*}
@@
 \includegraphics[width=0.99\linewidth]{figures/ch2/DD0160_fiducial_shortrad_nort}
-\caption{Same as Figure~\ref{ch2:figpanel1}, but at 40~Myr.}
-\label{ch2:figpanel2}
+\caption{Same as Figure~\ref{ch2:fig:panel1}, but at 40~Myr.}
+\label{ch2:fig:panel2}
 \end{figure*}
 
-Figure~\ref{ch2:figpanel1}, at 17~Myr, compares each simulation just after the first few SNe.
+Figure~\ref{ch2:fig:panel1}, at 17~Myr, compares each simulation just after the first few SNe.
 Already there are significant differences between the runs.
@@
 Although the ISM properties within the HII region in each case are quite similar between the simulations, the SNe that eventually go off in this region are confined by the neutral gas in the shortrad simulation, but readily escape through the lower density ionized gas into the galaxy halo in our fiducial case.
-As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe, as shown in  Figure~\ref{ch2:figpanel2}, which shows each simulation 40~Myr after the formation of the first stars.
+As these simulations evolve, the existence of these diffuse, ionized channels in the fiducial run easily allow continual and significant outflows from SNe, as shown in  Figure~\ref{ch2:fig:panel2}, which shows each simulation 40~Myr after the formation of the first stars.
 In contrast, the same SNe in the other two simulations are well contained, surrounded by shells of denser, neutral gas.
@@
 
-As shown in Figure~\ref{ch2:figmetal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy.
+As shown in Figure~\ref{ch2:fig:metal_retention} the differences in ionization structure and its effect on galactic winds has direct consequences for the chemical evolution of our dwarf galaxy.
 The winds in our fiducial simulation carry nearly all of the metals produced out from the disk of our galaxy.

### 2019-04-08 thesis/acknowledgments.tex
adding software

@@
 
+Finally, I would like to thank the numerous developers and contributors to the
+open-source software packages without which this \dissertation would not be
+possible. This includes more general software, such as \textsc{Python}, \textsc{IPython}, \textsc{NumPy},
+\textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py},
+and \textsc{deepdish}, and more astronomy-specific projects like  \textsc{yt}, \textsc{Enzo},
+\textsc{Grackle}, \textsc{AstroPy}, and \textsc{Cloudy}. In particular I would like
+to thank the many developers of \textsc{yt}, \textsc{Enzo}, and \textsc{Grackle}
+who have helped answer questions, debug code, and implement new features on
+my behalf throughout this process. This includes: Britton Smith, Nathan Goldbaum,
+John Wise, Matt Turk, Greg Bryan, Simon Glover, Munier Salem, Cameron Hummels,
+Christine Simpson, and Brian O'Shea.
+
 \vspace{1.8cm}

### 2019-04-08 thesis/chapters/ch_conclusion.tex
Finishing conclusion draft and updating Ch4 figures

@@
 Even more, how metals from the full range of nucleosynthetic sources, including AGB winds, stellar winds, core collapse and Type Ia supernovae, and NS-NS mergers, participate in these processes -- mixing and galactic winds -- differently has only recently been examined in efforts to better understand results from the ever increasing availability of high-quality stellar abundance measurements of stars in our own Milky Way and in nearby dwarf galaxies.
-In order to understand these processes and build a complete picture of metal evolution in the Universe, we have developed a new model for star formation, stellar feedback, and chemical enrichment to follow these processes in simulations of isolated dwarf galaxies.
+In order to build a complete picture of metal evolution in the Universe, we have developed a new model for star formation, stellar feedback, and chemical enrichment to follow these processes in simulations of isolated dwarf galaxies.
 Using this model, we have made critical advancements in understanding both how stellar feedback governs the evolution of low mass dwarf galaxies and how individual metals are distributed in (and beyond) these galaxies over time.
@@
 \section{A New Model for Galactic Chemical Enrichment}
+\label{conclusion:sec:ch1}
 
 In order to address these outstanding issues in galactic evolution, we developed a new model for galactic chemical evolution that -- for the first time in galaxy-scale simulations -- follows star particles as individual stars along with their detailed feedback and metal yields.
-As detailed in Chapter~\ref{ch:chapter_2} we use the AMR hydrodynamics code \textsc{Enzo}, we produce a set of simulations using this model of an idealized, isolated low-mass dwarf galaxy ($M_{\rm gas} \sim 10^{6}$~M$_{\odot}$, $M_{\rm halo} \sim 3 \times 10^{9}$~M$_{\odot}$) embedded in a static dark matter potential.
+As detailed in Chapter~\ref{ch:chapter2} we use the AMR hydrodynamics code \textsc{Enzo}, we produce a set of simulations using this model of an idealized, isolated low-mass dwarf galaxy ($M_{\rm gas} \sim 10^{6}$~M$_{\odot}$, $M_{\rm halo} \sim 3 \times 10^{9}$~M$_{\odot}$) embedded in a static dark matter potential.
 Using a detailed model for gas chemistry and radiative cooling, we follow the evolution of this galaxy and its multi-phase ISM as it forms stars, depositing individual star particles sampled over 1 to 100 M$_{\odot}$.
@@
 
-\textbf{summarize results from Ch 1 here}
+We find that this model -- which contains no independently tuned free parameters -- is sufficient to generate a multi-phase ISM with star formation, gas scale-height, and outflow properties that match expectations from observations.
+The global metal retention fraction for this galaxy is low ($\lesssim$ 5\%), with typical outflow velocities of $\sim$100~km~s$^{-1}$, and up to 1000~km~s$^{-1}$.
+We find that stellar radiation feedback is important, but that the ISRF is highly variable -- driven by stochastic IMF sampling in this low SFR galaxy.
+The mass fraction of the ISM is dominated by the cold (T$\sim$100~K) and warm-neutral (T$\sim$1000~K) components, while the warm-ionized and hot phases dominated the volume fraction.
+The WIM and HIM in the galaxy also exhibit significant time variation due to stochastic IMF sampling and a bursty SFH.
+Finally, we find that H$_2$ comprises $\lesssim$~5\% of the galaxy by mass, formed primarily through H$-$ gas-phase reactions.
 
 In ongoing work we are extending these methods by implementing them in cosmological simulations of UFD galaxy evolution.
-Our detailed model tracking the feedback and yields from individual stars will build substantially upon recent works investigating metal enrichment at high redshift and in UFDs and their progenitors \citep[e.g.][]{Ritter2015,Jeon2017,Corlies2018}.
-This work includes additional improvements to the simulations presented in this \dissertation, including a model for Pop III star formation and chemical enrichment adapted from \cite{Wise2012a}, a new IMF sampling scheme that allows us to follow very low mass stars ($M_* \lesssim 2$~M$_{\odot}$) -- which have no significant feedback or metal enrichment, but are important long-lived tracers of galactic chemical enrichment -- aggregated together into a single particle during each star formation event, and improvements to the numerical implementation to ease memory consumption in these significantly larger simulations.
+Our detailed model tracking the feedback and yields from individual stars will build substantially upon recent works investigating metal enrichment at high redshift and in UFDs and their progenitors \citep[e.g.][]{Ritter2015,Jeon2017,Corlies2018,Wheeler2018,Agertz2019}.
+This work includes additional improvements to the simulations presented in this \dissertation, including a model for Pop III star formation and chemical enrichment adapted from \cite{Wise2012a}, a new IMF sampling scheme that allows us to follow very low mass stars ($M_* \lesssim 2$~M$_{\odot}$) -- which have no significant feedback or metal enrichment, but are important long-lived tracers of galactic chemical enrichment -- aggregated together into a single particle during each star formation event, improvements to the numerical implementation to ease memory consumption in these significantly larger simulations, and new metal tracer fields to follow the contribution of AGB, core collapse SNe, Type Ia SNe, and PopIII stars to the total metal content of each cell independently.
 
-Finally, as part of this \dissertation we additionally produced a significant set of companion simulations at lower resolution (3.6~pc instead of 1.8~pc) turning on and off each independent feedback process (ionizing radiation, radiation pressure, LW and FUV radiation, and supernovae).
+Finally, as part of this \dissertation we additionally produced a significant set of companion simulations at $2 \times$ lower resolution (3.6~pc instead of 1.8~pc) turning on and off each independent feedback process (ionizing radiation, radiation pressure, LW and FUV radiation, and supernovae).
 With these runs, we sought to build upon recent works examining the various effects of each stellar feedback process in driving the evolution of low mass dwarf galaxies \citep{Hu2016,Hu2017,Hu2018,Forbes2016}.
@@
 With our simulations, we can place greater emphasis on how each feedback channel drives the mixing and ejection of individual metals within and beyond low mass dwarf galaxies.
-% Until recently, most (if not all) simulations of galaxy formation and evolution followed metal enrichment with a single, global metallicity field, ignoring the potential differential evolution across individual metals.
-Models for star formation and stellar feedback have also -- until recently -- made extensive use of phenomenological prescriptions to capture their effects on galactic evolution.
-With the increase in computational power
 
 \section{Stellar Radiation Feedback in Dwarf Galaxies}
+\label{conclusion:sec:ch2}
 
@@
 In our simulations we track the ionizing radiation from massive stars accurately using an adaptive ray-tracing radiative transfer method with sufficient resolution to capture the HII regions from individual stars.
-In Chapter~\ref{ch:chapter_2} we demonstrate that stellar ionizing radiation dramatically reduces the star formation rate and generally increases the effectiveness of galactic winds at our low-mass dwarf galaxy simulations.
+In Chapter~\ref{ch:chapter2} we demonstrate that stellar ionizing radiation dramatically reduces the star formation rate and generally increases the effectiveness of galactic winds at our low-mass dwarf galaxy simulations.
 
 In addition, we explore the mechanism by which stellar radiation acts to regulate star formation and drive outflows by comparing our fiducial simulations to simulations that only account for localized ($< 20$~pc) ionization around massive stars.
-This second set of runs approximates the behavior of various approximations for stellar radiation feedback which do not follow radiation propagation in detail, but rather deposit energy / ionize gas in the immediate vicinity of newly formed stars.
+This second set of runs mimics the behavior of various approximations for stellar radiation feedback which do not follow radiation propagation in detail, but rather deposit energy / ionize gas in the immediate vicinity of newly formed stars.
 We find that star formation is regulated by ionizing radiation locally -- destroying cold gas around young, massive stars that would otherwise have formed stars -- as the $< 20$~pc restricted run (initially) shares a very similar SFR to our fiducial run.
@@
 
-\textbf{Maybe mention radiation comparison runs that will be examined in the future?}.
+%sAlthough we include the effects of photoelectric heating, Lyman-Werner radiation, and radiation pressure, we have not investigated their individual importance in this work.
+Recent works have demonstrated the importance of photoelectric heating in dwarf galaxies \citep{Hu2016,Forbes2016},
 
 \section{Mixing and Ejection of Individual Metals}
+\label{conclusion:sec:ch3}
 
-\textbf{Summarize results}
+As argued in \cite{KrumholzTing2018}, differences in how metals are released into the ISM (due to the variation in energetics between their nucleosynthetic sites) should drive discernible differences in their mixing behavior in the ISM.
+We demonstrate these differences for the first time in hydrodynamics simulations in Chapter~\ref{ch:chapter3} by examining the evolution of each of the 15 metals species tracked in our simulations.
+Although we are not the first to follow a large number of individual metal species from different nucleosynthetic channels in a galaxy-scale simulation, that we follow individual stars and follow the feedback for each independently has allowed us to capture these effects.
+Notably, we find that -- for low mass dwarf galaxies -- metals released in AGB winds are retained in the galaxy's ISM at a much higher fraction than metals released in either core collapse or Type Ia supernovae.
+This implies that if one were to construct a chemical evolution model of a low mass dwarf galaxy and adopt the high metal ejection fractions as seen in observations\footnote{Which typically trace O, an element released predominately in core collapse supernovae.} \citep{Kirby2011-metals,McQuinn2015}, one could \textit{underestimate} the mass of AGB-wind dominated metals (such as Sr and Ba, and possibly C and N) in the ISM by a factor of $\sim$ 4-5.
+This effect is important in matching observations of stellar abundances in low mass dwarf galaxies, but how this ratio depends on galaxy properties (e.g.
+$M_*$, $M_{\rm halo}$, $\Sigma_{\rm SFR}$, $\Sigma_{\rm gas}$) is uncertain and warrants future research.
+
+In agreement with predictions from \cite{KrumholzTing2018}, we find that the abundances of the AGB-wind metals are more inhomogeneous than the abundances of metals from supernovae.
+This spread can be significant, over 1~dex for the AGB-wind elements.
+We predict then that -- at least in the low metallicity environments of low mass dwarf galaxies -- the observed stellar abundance distributions for AGB-wind elements should be characterized by markedly greater spreads than abundance distributions for SNe elements (e.g.
+O, Mg).
+Indeed, this is observed in the stellar abundance patters of dwarf galaxies in the Local Group \citep{Suda2017}, but it remains to be seen if this is a conclusive signature of these mixing differences or perhaps is due to larger differences in star-to-star metal yields for these elements.
+Finally, we were able to characterize the metal mass fraction PDFs for each element across each phase of the ISM, and found that each were generically well-fit by a combined log-normal PDF with a power-law tail towards higher metal mass fractions.
+We hope that this characterization lends itself well to developing a physically-motivated semi-analytic prescription for stellar abundance spreads to be used in semi-analytic (and one-zone) models of galactic chemical evolution.
 
 \section{Mixing Behavior of Single-Sources}
+\label{conclusion:sec:ch4}
 
-\textbf{very briefly sSummarize results}
+To expand upon the results of Chapter~\ref{ch:chapter3} and understand how metals are distributed throughout the ISM on a source-by-source level, we carry out a series of ``mixing experiments'' in Chapter~\ref{ch:chapter4} to test how metal mixing and metal ejection behaviors vary with the injection energy of the source.
+We confirm that lower energy events (e.g.
+AGB-winds) are retained at a higher fraction in the ISM and mix poorly compared to higher energy events (e.g.
+SNe) \textit{on average}.
+We demonstrate this by following the evolution of metals of individual sources at injection energies of 10$^{46}$~erg (AGB winds), 10$^{49}$~erg and 10$^{50}$~erg (NS-NS mergers), 10$^{51}$~erg (SNe and possibly NS-NS mergers), and 10$^{52}$~erg (hypernovae).
+However, we find that the behavior of any single source exhibits a substantial amount of variance -- particularly at lower energies -- as it is clear that the injection energy is not the only dominant factor in determining mixing behavior.
+We investigate other possible factors, including radial position, global galaxy SFR, and local ISM density, and find that the global galaxy SFR has the greatest effect on the mixing and ejection behavior of each metal, particularly for lower energy events.
+Whiles these results suggest that these behavioral differences can be accounted for in an average sense, the full picture is subject to substantial stochasticity based purely on the randomness with which when and where different events occur in a galaxy.
+Abundances associated with rare enrichment sources -- such as the r-process enrichment candidates -- which may only occur once (if at all) in the lowest mass dwarf galaxies should therefore exhibit the most significant galaxy-to-galaxy abundance variations for galaxies at fixed stellar mass.
 
 \section{Future Work}
+\label{conclusion:sec:future}
 
-\textbf{Cosmological simulations may already be mentioned above....} if so, just focus on how I implemented stuff into a onezone model to match the simualtiosn and play around iwth the effects of f$_{ej}$ and mixing timescales.
-say we will explore how this works and implement in larger onezone / semi-analytic models (cote).
+One of the primary goals of this \dissertation was to develop a physical understanding of the processes that contribute generally to galactic chemical evolution and specifically to metal mixing and ejection from galaxies -- a process that was previously not well understood.
+With a novel model for star formation and stellar feedback we have made substantial contributions to this understanding, but continued work is necessary.
+Specifically, the conclusions reached in this \dissertation have all been made in the context of the evolution of a low-mass dwarf galaxy with idealized initial conditions and limited cosmological context.
+Although we can speculate, it remains to be seen how these results can vary over cosmological timescales for a single galaxy as well as how they vary across the galaxy mass scale.
+Besides conducting a suite of simulations sampling a variety of galaxy parameters, which could prove too computationally expensive at higher galaxy masses, semi-analytic and one-zone models provide the ideal testing ground for identifying what regimes may be sensitive to the metal mixing behaviors identified in this work.
+The ultimate goal would be to use a suite of hydrodynamics simulations to construct physically motivated prescriptions for use in these one-zone models.
+Until then, however, future work can make significant strides with the results presented here alone.
+
+To aid in this development, we have built a one-zone model, \textsc{OneZ}, that has been designed to match the physical model used in our hydrodynamics simulations.\footnote{https://github.com/aemerick/OneZ}.
+This model uses an equivalent star formation recipe as our hydrodynamics simulations, stochastically forming individual star particles and following their yields.
+Given an input SFH and $f_{\rm ej}$ for each metal from our hydrodynamics simulations, we can match the mean metal abundance evolution from these simulations and can explore how varying $f_{\rm ej}$ (element-by-element) affects the resultant stellar abundance patterns.
+In future work, we plan to implement a two-phase model like that in \cite{SchonrichWeinberg2019} that includes parameters for how each metal first enters the hot and cold phases, how each metal mixes between the two phases, and a stochastic mixing-zone method as used in \cite{Cescutti2008}.
+With these additions, we will: 1) explore how these physics manifest themselves in galaxies with a wide range of star formation and halo properties, 2) use these insights to begin to match observed stellar abundance patterns mass dwarf galaxies, 3) make predictions for expected multi-element abundances spreads in dwarf galaxies for comparison to future observations in upcoming surveys, and 4) better constrain the relative importance of stochastic sampling of the IMF and inhomogeneous mixing in setting these abundance spreads.
+In addition, we can more easily use this model to explore a wide variety of nucleosynthetic yield tables to better constrain the -- highly uncertain -- yields themselves.
+This is a particularly exciting tool that can be used to better constrain the sources of r-process enrichment in low mass dwarf galaxies.

### 2019-04-09 thesis/chapters/ch_chapter4.tex
Final text on mixing timescales with eddy turnover and sound speed. removing one-shot TBD

@@
 The lower energy events evolve more gradually.
-The lowest energy event, corresponding to AGB winds, reaches $f_{\rm ej}$ ~ 0.68, which increases to 0.87 for the 10$^{51}$~erg events, and 0.95 for the 10$^{52}$~erg event.
+The lowest energy event, corresponding to AGB winds, reaches $f_{\rm ej} \sim$~0.68, which increases to 0.87 for the 10$^{51}$~erg events, and 0.95 for the 10$^{52}$~erg event.
 To emphasize these differences, we plot each line separately in the left panel of Figure~\ref{ch4:fig:CGM_CNM}
@@
 Clearly, at no point can any of these distributions be considered well-mixed within the 150~Myr simulation time.
-\textit{Need to fix up: This is in agreement with the understanding that the mxiing timescales should correspond to XXX, which suggests that it would take $\sim$X~Gyr (1 Gyr?) for the metals to be fully mixed}.
-Interestingly, however, the injection energy for a given source leaves an indelible impact on the subsequent evolution of those metals in the ISM throughout the simulation time.
+Prior studies of passive scalar mixing in isothermal turbulent boxes find typical mixing timescales\footnote{Defined roughly as the time it takes for the r.m.s.
+abundance to equilibrate, not the time it takes to completely homogenize, which tends towards infinity.} on order of the eddy turnover timescale \citep[e.g.][]{SurPanScannapieco2014} ($t_{\rm ed}$).
+Typically, $t_{\rm ed}$ is defined as the relevant length scale (e.g.
+the diameter of our galaxy) divided by the r.m.s gas velocity.
+Although extending these results to multi-phase, global-galaxy simulations is non-trivial, we find typical $t_{\rm ed}$ in the CNM of $\sim$100~Myr and in the HIM of $\sim$10~Myr.\footnote{For comparison, the isothermal sound speed in these phases are $\sim$4~Gyr and $\sim$10~Myr respectively.} In order to properly evaluate the mixing timescale we would need to run each simulation for significantly longer, for several $t_{\rm ed}$.
+
+Interestingly, the injection energy for a given source leaves an indelible impact on the subsequent evolution of those metals in the ISM throughout the simulation time.
 We demonstrate that variations in abundance spread across elements may be driven significantly by the enrichment site and its associated $E_{\rm ej}$.
@@
 Variations with individual events in the above results suggests that it would be challenging to make any conclusive statements about the enrichment behavior of single enrichment sources.
-\textbf{Go back and look again at one-shot enrichment paper} This is problematic for interpreting the chemical abundances in UFDs that are likely to have been host to just a single, exotic enrichment event.
+This is problematic for interpreting the chemical abundances in UFDs that are likely to have been host to just a single, exotic enrichment event.
 Using these observations to constrain the total nucleosynthetic yields of these sources requires implicit assumptions about how quickly metals are available in star forming gas, how homogeneously they are distributed throughout the galaxy, and what fraction are ejected from the galaxy.

### 2019-04-09 thesis/chapters/ch_introduction.tex
new references
fixed italics

@@
 In addition, one would then produce realistic galactic winds, removing the correct amount of metals from the galaxy and enriching the CGM and the intergalactic medium (IGM).
-Finally, one can layer this model ad nauseum on top of a $\Lambda CDM$ model for the cosmological evolution of many galaxies, reproducing all observed properties of galactic chemical evolution as a function of both mass and redshift.....
+Finally, one can layer this model ad nauseum on top of a $\Lambda$CDM model for the cosmological evolution of many galaxies, reproducing all observed properties of galactic chemical evolution as a function of both mass and redshift.....
 Wait...
@@
 Not only does this correspond to a significant amount of mass outflow from these galaxies, but these winds should also carry out a substantial amount of metals from these galaxies.
+In fact, the differences with which different models for feedback-driven winds drive metals in outflows in low mass galaxies can be an important constrain on the underlying physics \citep[e.g.]{Wheeler2018,Agertz2019}.
 \cite{Kirby2011-metals} used measurements of the stellar abundances in Local Group dSph's and their resolved star formation histories to determine that their stars contain less than 5\% of the metals synthesized in each galaxy.

### 2019-04-09 thesis/acknowledgments.tex
almost completed draft of ack

--- 2019-03-19 thesis/acknowledgments.tex
@@
 % but usually something like 1-2 pages
-\textit{To-do}
+
+To my wife Ellen, who moved across the country for me to NYC and will be moving
+across the country again in the next few months, who has patiently put up with
+all of my travel and time away at conferences in the past few years,
+who has worked longer hours at much more demanding jobs than the work I have put
+into this \dissertation, and who has continued to support me through this
+entire journey, all just so that I could pursue my dream. A simple ``thank you" is
+entirely insufficient to repay her for these sacrifices, but its a good thing
+I have the rest of my life to show how grateful I am.
+
+To my parents and my family who have continued to support me in countless ways
+throughout my life. \textbf{...more...}
+
+I have had many research advisors over the years, but am most indebted to
+my thesis advisors, Greg and Mordecai, and my committee, Mary and Kathryn. Their
+thoughts, advice, and encouragement over the past six years have been invaluable.
+This \dissertation  is as much a testament of my formation as a scientist as it
+is of the quality of their mentorship. I would also like to thank my various
+undergraduate thesis advisors at the University of Minnesota,
+Larry Rudnick, Tom Jones, and Priscilla Cushman, my REU advisor at
+Texas A\&M University, Ralf Rapp, and Pablo Yepes at Rice University.
+
+I want to thank all of the other graduate students at Columbia that I have overlapped
+with over the years. This includes especially Sarah, Steven, and Dan,
+and also Susan, Andrea, Munier, Alejandro, Jeff, and Adrian.
+Their support and advice -- and shared laughs and beers --
+already make me look back on this time with fond memories.
+
+While I have spent much of my time working in my office(s) at either Columbia,
+AMNH, or the Flatiron Institute, a surprising fraction of this \dissertation
+and the published works it is based upon were written outside of these
+places. I want to thank and acknowledge the many coffee shops, bars, breweries,
+and the work space in my climbing gym in which I have been
+surprisingly productive in times when I found my office uninspiring.
+
+Thank you to everyone I have met in the NYC climbing community who have collectively
+helped keep me sane throughout my time in graduate school. Over the past few years
+I have learned the importance of a proper work-life balance, and climbing has helped
+me keep that balance (... maybe a bit too well...). Thank you especially to my
+regular climbing partners -- Daniel Negless, Hunter Whaley, Dennis Kramer, and Lauren Anderson -- who I've trusted
+with my life countless times, and the handful of other astronomer-climbers that I've
+climbed with throughout graduate school (Jeff Andrews, Matt Wilde, Lauren Anderson, Dan D'Orazio,
+Dan Foreman-Mackey, and Andrea Derdzinski).
+
+I would like to thank the numerous developers and contributors to the
+open-source software packages without which this \dissertation would not be
+possible. This includes more general software, such as \textsc{Python}, \textsc{IPython}, \textsc{NumPy},
+\textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py},
+and \textsc{deepdish}, and more astronomy-specific projects,  \textsc{yt}, \textsc{Enzo},
+\textsc{Grackle}, \textsc{AstroPy}, and \textsc{Cloudy}. In particular I would like
+to thank the many developers of \textsc{yt}, \textsc{Enzo}, and \textsc{Grackle}
+who have helped answer questions, debug code, review my pull requests, and implement
+new features on my behalf throughout this process. This includes: Britton Smith, Nathan Goldbaum,
+John Wise, Matt Turk, Greg Bryan, Simon Glover, Munier Salem, Cameron Hummels,
+Christine Simpson, Brian O'Shea, and others who I may have forgotten.
+
+Finally, I would like to thank you -- the reader -- for deciding that this
+\dissertation is worth your attention.
 

### 2019-04-10 thesis/chapters/ch_introduction.tex
Proof read of introduction updates. New dissertation command

@@
 Galaxies are amalgamations of gas and stars embedded in dark matter halos.
-They are formed over cosmic time as the products of the hierarchical assembly that follows from the collapse of the primordial density fluctuations that arose after the Big Bang.
+They are formed over cosmic time as the products of the hierarchical assembly that follows from the collapse of the primordial density fluctuations which arose after the Big Bang.
 The gravitational pull of dark matter -- as predicted from $\Lambda$CDM cosmology -- controls the hierarchical growth of structure in the Universe.
@@
 Much work has been done in studying the global metallicity evolution of galaxies through the mass-metallicity relationship \citep[e.g.][]{Lequeux1979,Tremonti2004,Lee2006,Zahid2012,AndrewsMartini2013}, the metallicity gradient in our own and nearby galaxies \citep[e.g.][]{Searle1971,Shaver1983,Belfiore2017,SanchezMenguiano2017}, and detailed stellar abundances in nearby dwarf galaxies with spectroscopically resolved stars \citep[see the review in][]{Tolstoy2009}.
-Yet in spite of increased number and quality of observations of galactic chemical evolution, developing a complete model of galactic chemical evolution is still a daunting task.
+Yet in spite of increased number and quality of observations tracing galactic chemical evolution, developing a complete model of galactic chemical evolution is still a daunting task.
 
@@
 To give an impression of the difficulties involved, we outline a recipe for constructing a complete model of galactic chemical evolution.
-One must first prescribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas into the disk of the galaxy, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos.
+One must first prescribe a galaxy's connection to its large scale structure to understand the inflow of pristine, metal-free gas and growth of its gaseous disk, and the accretion (via mergers) of stars formed previously in galaxies hosted by different dark matter halos.
 One can then worry about knowing where, when, how, and with what masses stars form in the first place from this gas.
@@
 This in turn requires one to toss in a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and supernovae -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies.
-Simultaneously, one makes the simple step of nailing down a complete model of stellar structure, stellar evolution, the reaction rates and cross sections of every nuclear reaction, and the lifetimes of individual isotopes.
+Simultaneously, one must make the simple step of nailing down a complete model of stellar structure, stellar evolution, the reaction rates and cross sections of every nuclear reaction, and the lifetimes of individual isotopes.
 Once all of this is understood, one can then color in the gas in the galaxy over time with the individual metal yields of stellar populations released over their lifetime.
@@
 The following is a primer on how to model galactic evolution in hydrodynamics simulations.
-We focus on the physics needed to simulate galaxies (cooling, heating, chemistry, star formation, feedback, etc.) as it pertains to the aspects of galactic chemical evolution examined in this \dissertation.
+We focus on the physics needed to simulate galaxies (cooling, heating, chemistry, star formation, feedback, etc.) as it pertains to the aspects of galactic chemical evolution examined in this \Dissertation.
 This is meant to be a broad overview of the physical processes treated in such simulations, focusing more on aspects of their implementation rather than the derivation of theory behind each process.
 While important, the latter is beyond the scope of this introduction and would readily turn into a full textbook.
-Focusing on implementation gives a much more accurate representation of the actual work done and skills learned during work on this \dissertation.
+Focusing on implementation gives a much more accurate representation of the actual work done and skills learned during this \Dissertation.
 This discussion includes a very brief overview of hydrodynamics and the numerical methods used in this work in Section~\ref{intro:sec:hydrodynamics}, nucleosynthesis and stellar evolution in Section~\ref{intro:sec:nucleosynthesis}, radiative cooling and chemistry (actual chemistry) in Section~\ref{intro:sec:cooling}, star formation and star particles in Section~\ref{intro:sec:sf} and Section~\ref{intro:sec:stars}, and stellar feedback in Section~\ref{intro:sec:feedback}.
@@
 Unfortunately ``chemistry" is often used with both meanings in the same work requiring context to decipher the intended meaning.
-Likewise, ``metals" refers broadly to every element except H and He.
+``Metals" refers broadly to every element except H and He.
 Throughout this \dissertation we often refer to the metallicity ($Z$) of a galaxy, its gas, or its stars.
@@
 These metallicity proxies are usually reported in some form of normalized abundance ratio.
-For stellar metallicities, this is given in the form [A/B].
-[A/B] = log($N_A / N_B$) - log($N_A / N_B$)$_{\odot}$, where $N$ refers to the number of atoms of a given element (e.g.
+For stellar metallicities, this is given in the form [A/B] = log($N_A / N_B$) - log($N_A / N_B$)$_{\odot}$, where $N$ refers to the number of atoms of a given element (e.g.
 [Fe/H]).
@@
 
-In this \dissertation, we make use of the adaptive-mesh refinement (AMR) hydrodynamics code \code{Enzo}, as described in greater detail in Chapter~\ref{ch:chapter1}.
+In this \Dissertation, we make use of the adaptive-mesh refinement (AMR) hydrodynamics code \code{Enzo}, as described in greater detail in Chapter~\ref{ch:chapter1}.
 As it pertains to galactic chemical evolution, however, the use of a grid-based code has the advantage that metals (which are advected as passive scalars that follow the fluid-flow in the simulations) are allowed to mix and diffuse naturally across fluid elements (grid cells).
-This is not possible in native SPH implementations, yet is necessary to reproduce realistic galactic chemical evolution properties as shown by multiple recent works testing implementations of diffusion in SPH simulations \citep[e.g.][]{Shen2010,Su2017a,Escala2018}.
-The disadvantage of the diffusion in \code{Enzo}, however, is that it is entirely numerical, and therefore its exact properties are challenging to characterize and are strongly resolution dependent.
+This is not possible in native SPH implementations, yet is necessary to reproduce realistic galactic chemical evolution properties as shown by multiple recent works testing implementations of diffusion in SPH simulations \citep[e.g.][]{Shen2010,Revaz2016,Hirai2017,Su2017a,Escala2018}.
+The disadvantage of the diffusion in \code{Enzo}, however, is that it is entirely numerical.
+Therefore, its exact properties are challenging to characterize and are resolution dependent.
 Throughout this \dissertation we attempt to account for the effects of resolution on our results, but do not explicitly examine the properties of numerical diffusion itself.
@@
 The location of this knee in this diagram shifts for a given galaxy depending on its SFH.} However, it is not well understood how differences in where and with what energies these events occur affect observed stellar abundance patterns.
-Investigating these differences is a key motivation of this \dissertation.
+Investigating these differences is a key motivation of this \Dissertation.
 
@@
 $\alpha$-elements, notably O, Mg, Si, Ca, and Ti, are produced during the lifetime of massive stars (O, Mg) or during the core collapse supernova explosion itself.
-In either case, these elements are synthesized through the capture of an $\alpha$ nucleus, progressing towards increasingly heavier nuclei in intervals of 4/2 in mass/atomic number (as $\alpha$ = $^{4}_2$He) from $^8_4$Be all the way to the stable $^{52}_{26}$Fe and unstable $^{56}_{28}$Ni (which days to $^{56}_{26}$Fe).
+In either case, these elements are synthesized through the capture of an $\alpha$ nucleus, progressing towards increasingly heavier nuclei in intervals of 4/2 in mass/atomic number (as $\alpha$ = $^{4}_2$He) from $^8_4$Be all the way to the stable $^{52}_{26}$Fe and unstable $^{56}_{28}$Ni (which decays to $^{56}_{26}$Fe).
 The iron group elements, notably Fe, Mn, Co, and Ni, are produced predominately in Type Ia supernovae, with variations depending on a single vs.
@@
 As including self-consistent nuclear reactions in the interior of stars is nearly computationally impossible in galaxy-scale simulations, metal yields are generally included as averaged over an entire stellar population (see Section\ref{intro:sec:stars}) as obtained from a tabulated set of yields.
-These yields for a given star in a simulation are typically IMF-averaged, and occasionally mass and metallicity dependent depending on the level of detail desired in the simulation.
+The yields for a given star in a simulation are typically IMF-averaged, and occasionally mass and metallicity dependent depending on the level of detail desired in the simulation.
 Often, only the global metallicity is tracked in simulations, but tracking individual metal species (especially C, O, and Si which can affect the chemistry and cooling physics in the ISM) is becoming more common.
@@
 This allows for the quick use of tabulated look-up tables for radiative cooling and heating, often produced using \code{cloudy} \citep{Cloudy2013}, that depend on gas density, temperature, metallicity, and redshift (which sets the UVB heating rate).
-More complex simulations often track some number (usually $< 10$) of species involved in primordial chemistry in order to better account for non-equilibrium effects and \Hmolecular production, though with noted increases in memory requirements and computational cost.
+More complex simulations often track some number (usually $< 10$) of species involved in primordial chemistry in order to better account for non-equilibrium effects and \Hmolecular~production, though with noted increases in memory requirements and computational cost.
 Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2016,Richings2018}; but these are typically prohibitively expensive to run on large scales.
 In this \dissertation we adopt the chemistry and radiative cooling and heating physics models available in the newly developed, open-source library \code{GRACKLE} \citep{GrackleMethod}.
-The exact physics included in our simulations are discussed in greater detail in Chapter~\ref{ch:chapter1}, but we note that improvements to \code{GRACKLE} have been made as the direct result of the research conducted during this \dissertation.
+The exact physics included in our simulations are discussed in greater detail in Chapter~\ref{ch:chapter1}, but we note that improvements to \code{GRACKLE} have been made as the direct result of the research conducted during this \Dissertation.
 %mention that I made improvements to this?
@@
 %cite?,
-or that gas meet a minimum \Hmolecular mass fraction \citep[e.g.][]{Kuhlen2012}
+or that gas meet a minimum \Hmolecular~mass fraction \citep[e.g.][]{Kuhlen2012}
 %\citep[e.g.][]{}
@@
 
-In this \dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF.
+In this \Dissertation, we develop the first implementation that breaks the SSP formalism entirely by following stars as individual star particles sampled from an adopted IMF.
 This allows us to place unprecedented detail on both the stellar feedback and metal yields associated with each star, spatially and temporally resolving differences in both of these channels as a function of stellar mass and metallicity.
@@
 
-Although not included in this \dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution.
+Although not included in this \Dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution.
 A substantial amount of recent research has been dedicated towards the examination of supernova-driven cosmic ray feedback (see Section~\ref{ch1:sec:CRs} for a more detailed discussion and references).
-In brief, cosmic rays can be a dominant source of heating in very dense gas and act as a source of non-thermal pressure in the ISM, which can drive galactic winds with qualitatively different phase structures \citep[e.g.][]{SalemBryanCorlies}.
+In brief, cosmic rays can be a dominant source of heating in very dense, optically-thick gas and act as a source of non-thermal pressure in the ISM, which can drive galactic winds with qualitatively different phase structures \citep[e.g.][]{SalemBryanCorlies}.
 Binarity is often ignored in models of stellar feedback.
@@
 Finally, exotic sources of stellar feedback, such as hypernovae, high-mass X-ray binaries, and NS-NS mergers can also be a potentially important sources of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}.
-However, the uncertainties in the frequency and delay time distributions for when these events should occur, and their relative rarity, preclude including these effects in this \dissertation.
+However, the uncertainties in the frequency and delay time distributions for when these events should occur, and their relative rarity, preclude including these effects in this \Dissertation.
 
@@
 
-High resolution simulations, like those developed in this \dissertation, can typically rely on using pure thermal energy injection while still avoiding artificial overcooling.\footnote{This is advantageous because it is often substantially easier to implement than kinetic / momentum injection methods while being less susceptible to numerical artifacts, especially for grid-based codes.} This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}.
+High resolution simulations, like those developed in this \Dissertation, can typically rely on using pure thermal energy injection while still avoiding artificial overcooling.\footnote{This is advantageous because it is often substantially easier to implement than kinetic / momentum injection methods while being less susceptible to numerical artifacts, especially for grid-based codes.} This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}.
 However, a spatial resolution requirement is a density dependent statement; in this case supernovae that occur in the densest gas ($n > 10^{2-3}$~cm$^{-3}$) may still be under-resolved and ineffective.
@@
 This is a significant heating mechanism in higher metallicity environments, like the Milky Way \citep{Parravano2003,Wolfire2003}, but may still be important in setting temperature floor of cold dense gas in lower mass galaxies \citep{Forbes2016,Hu2017}.
-Lyman-Werner (LW) band radiation regulates the \Hmolecular~ abundance, which is particularly important in low-metallicity environments where \Hmolecular~ is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation perscriptions that depend upon the local \Hmolecular mass fraction.} As the goal of this \dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of these processes in some fashion.
+Lyman-Werner (LW) band radiation regulates the \Hmolecular~abundance, which is particularly important in low-metallicity environments where \Hmolecular~is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation prescriptions that depend upon the local \Hmolecular~mass fraction.} As the goal of this \dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of these processes in some fashion.
 
@@
 For this reason, approximate methods, such as flux-limited diffusion, treat radiation as a fluid, removing the scaling of computational cost with the number of sources.
-In this \dissertation, we follow the evolution of galaxies that have at most $10 - 100$ ionizing sources at one time, making it computationally feasible to use the accurate adaptive ray-tracing radiative transfer method implemented in \code{Enzo}.
+In this \Dissertation, we follow the evolution of galaxies that have at most $10 - 100$ ionizing sources at one time, making it computationally feasible to use the accurate adaptive ray-tracing radiative transfer method implemented in \code{Enzo}.
 
@@
 However, stellar winds, from both massive stars and weaker winds from the AGB phase of low mass stars, are important sources of metal enrichment.
-For this reason we include stellar wind feedback in this \dissertation, albeit in a simplified fashion.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in simulations where radiation feedback is ignored.
+For this reason we include stellar wind feedback in this \Dissertation, albeit in a simplified fashion.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in simulations where radiation feedback is ignored.
 It is thus likely sub-dominant to radiation feedback.}
@@
 \cite{Bullock2017} suggests a delineation based on stellar mass.
-For this \dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M$_{\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.
-In general, dwarf galaxies are extremely dark matter dominated, with mass to light ratios over 10$^2$ \citep{SimonGeha2007,Strigari2008,Wolf2010}, convert gas into stars at a lower efficiency than more massive galaxies (cite), and, for the lowest mass dwarf galaxies
+For this \Dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M$_{\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.
+In general, dwarf galaxies are extremely dark matter dominated, with mass to light ratios over 10$^2$ \citep{SimonGeha2007,Strigari2008,Wolf2010}, convert gas into stars at a lower efficiency than more massive galaxies,
+%(cite)
+and, for the lowest mass dwarf galaxies
 % need citations
@@
 Not only does this correspond to a significant amount of mass outflow from these galaxies, but these winds should also carry out a substantial amount of metals from these galaxies.
-In fact, the differences with which different models for feedback-driven winds drive metals in outflows in low mass galaxies can be an important constrain on the underlying physics \citep[e.g.]{Wheeler2018,Agertz2019}.
+In fact, the differences with which different models for feedback-driven winds drive metals in outflows in low mass galaxies can be an important constrain on the underlying physics \citep[e.g.][]{Wheeler2018,Agertz2019}.
 \cite{Kirby2011-metals} used measurements of the stellar abundances in Local Group dSph's and their resolved star formation histories to determine that their stars contain less than 5\% of the metals synthesized in each galaxy.
@@
 
-We dedicate this section to a specific Local Group dwarf galaxy, Leo P, as its observed properties motivate the initial conditions of the simulations developed in this \dissertation.
+We dedicate this section to a specific Local Group dwarf galaxy, Leo P, as its observed properties motivate the initial conditions of the simulations developed in this \Dissertation.
 This galaxy is remarkable for being one of the lowest mass dwarf galaxies with observed, ongoing star formation.
@@
 These studies have characterized its star formation history as low and roughly continuous over the age of the Universe \citep[$<$SFR$>$ = $4.3\times 10^{-5}$~M$_{\odot}$~yr$^{-1}$,][]{McQuinn2015a}, its stellar mass \citep[$M_{*} = 5.7 \times 10^{5}$~M$_{\odot}$,][]{McQuinn2013}, its \hi and dynamical mass \citep[$M_{\rm HI}(r<r_{\rm HI}) = 9.5\times 10^{5}$~M$_{\odot}$, $M_{\rm dyn}(r<r_{\rm HI}) = 2.6 \times 10^{7}$~M$_{\odot}$, $r_{\rm HI} \sim 500$~pc,][]{Bernstein-Cooper2014}, and gas-phase abundances from an \hii region \citep[12 + log(O/H) = 7.17$\pm$0.04][]{Skillman2013}.
-HI, optical, and H$\alpha$ observations of Leo P are shown inf Figure~\ref{intro:fig:Leo P}.
+HI, optical, and H$\alpha$ observations of Leo P are shown in Figure~\ref{intro:fig:Leo P}.
 
@@
 This treatment extends back many decades \citep[e.g.][]{Schmidt1963,TalbotArnett1971,Lynden-Bell1975}, where galaxies and their total metal abundances were treated in closed-box systems of gas and stars.
-Over the intervening decades these models have improved, including prescriptions for gas outflow (a ``leaky-box") or gas inflow (an ``accreting box"), or both \citep[a ``bathtub" model, e.g.][]{FinlatorDave2008,Bouche2010}.
+Over the intervening years these models have improved, including prescriptions for gas outflow (a ``leaky-box") or gas inflow (an ``accreting box"), or both \citep[a ``bathtub" model, e.g.][]{FinlatorDave2008,Bouche2010}.
 The assumptions that go into these models vary dramatically with complexity.
@@
 In agreement with previous works, we find that multi-channel feedback is able to drive outflows with high mass-loading factors while maintaining a fluctuating star formation rate density consistent with observations of low mass dwarf galaxies.
-Finally, we characterize the \Hmolecular~ properties of this galaxy, which remains unconstrained in observations of dwarf galaxies at this mass scale.
+Finally, we characterize the \Hmolecular~properties of this galaxy, which remains unconstrained in observations of dwarf galaxies at this mass scale.
 
@@
 
-Finally, we conclude in Chapter \ref{ch:conclusion} and briefly discuss future work as extensions of this \dissertation.
+Finally, we conclude in Chapter \ref{ch:conclusion} and briefly discuss future work as extensions of this \Dissertation.

### 2019-04-10 thesis/chapters/ch_conclusion.tex
new dissertation command

@@
 Our detailed model tracking the feedback and yields from individual stars will build substantially upon recent works investigating metal enrichment at high redshift and in UFDs and their progenitors \citep[e.g.][]{Ritter2015,Jeon2017,Corlies2018,Wheeler2018,Agertz2019}.
-This work includes additional improvements to the simulations presented in this \dissertation, including a model for Pop III star formation and chemical enrichment adapted from \cite{Wise2012a}, a new IMF sampling scheme that allows us to follow very low mass stars ($M_* \lesssim 2$~M$_{\odot}$) -- which have no significant feedback or metal enrichment, but are important long-lived tracers of galactic chemical enrichment -- aggregated together into a single particle during each star formation event, improvements to the numerical implementation to ease memory consumption in these significantly larger simulations, and new metal tracer fields to follow the contribution of AGB, core collapse SNe, Type Ia SNe, and PopIII stars to the total metal content of each cell independently.
+This work includes additional improvements to the simulations presented in this \Dissertation, including a model for Pop III star formation and chemical enrichment adapted from \cite{Wise2012a}, a new IMF sampling scheme that allows us to follow very low mass stars ($M_* \lesssim 2$~M$_{\odot}$) -- which have no significant feedback or metal enrichment, but are important long-lived tracers of galactic chemical enrichment -- aggregated together into a single particle during each star formation event, improvements to the numerical implementation to ease memory consumption in these significantly larger simulations, and new metal tracer fields to follow the contribution of AGB, core collapse SNe, Type Ia SNe, and PopIII stars to the total metal content of each cell independently.
 

### 2019-04-10 thesis/abstract.tex
Proof read updates

@@
 We developed these simulations as a means to better understand the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies.
-We follow the evolution of the individual metal yields associated with these stars in order to better understand how metals mix within the ISM and are ejected into the circumgalactic and itergalactic media (CGM, IGM) through outflows.
+We follow the evolution of the individual metal yields associated with these stars in order to better understand how metals mix within the ISM and are ejected into the circumgalactic and intergalactic media (CGM, IGM) through outflows.
 This study is directed with the goal of better understanding the ever increasing quality of stellar abundance measurements within our own Milky Way galaxy and in nearby dwarf galaxies.

### 2019-04-13 thesis/chapters/ch_chapter4.tex
proof read updates

@@
 The elemental abundances of a galaxy over time are sensitive to the nuclear physics and stellar astrophysics that determines which stars make what elements and when.
-The stellar abundance patters within a given galaxy also depend on the details of how those metals are released into the ISM through various forms of stellar feedback, and the hydrodynamic interactions that ultimately mix those elements into the ISM or eject them from the galaxy in galactic winds.
+The stellar abundance patterns within a given galaxy also depend on the details of how those metals are released into the ISM through various forms of stellar feedback, and the hydrodynamic interactions that ultimately mix those elements into the ISM or eject them from the galaxy in galactic winds.
 Stellar abundance patterns in old, metal poor systems are the result of enrichment from substantially fewer sources than younger, more metal rich stellar populations.
@@
 The lowest mass dwarf galaxies in the Local Group, UFDs, offer some of the best constraints on these processes.
-These environments can potentially be used to trace and constrain enrichment from the first stars \citep[e.g.][]{FrebelBromm2012,Ji2015,Ritter2015,Jeon2017,Hartwig2018}.
-and have been used to place constraints on the variety of possible astrophysical sources of r-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Duggan2018,Nagasawa2018,Ojima2018}.
+These environments can potentially be used to trace and constrain enrichment from the first stars \citep[e.g.][]{FrebelBromm2012,Ji2015,Ritter2015,Jeon2017,Hartwig2018} and have been used to place constraints on the variety of possible astrophysical sources of r-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Duggan2018,Nagasawa2018,Ojima2018}.
 It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way is much more uniform, averaging over the variety of complex hydrodynamics and feedback-driven turbulence interactions that may be driving much of the significant variance in stellar abundances seen at low metallicity.
-Stochasticity, which has been shown to be important for setting the width of stellar abundance patterns low metallicity environments of the Milky Way \citep[e.g.][]{Cescutti2008,Cescutti2014}, plays an even greater role in the evolution of these low mass dwarf galaxies \citep{Applebaum2018}.
-Indeed the increase in scatter in the stellar abundance patters of low mass dwarf galaxies and UFDs has been attributed to inhomogeneous mixing and stochastic effects \citep[e.g.][]{Norris2010a,Simon2015,Mashonkina2017,Suda2017}.
-This complicates the interpretation of abundance patters in these galaxies, particularly for constraining individual enrichment events.
+Stochasticity, which has been shown to be important for setting the width of stellar abundance patterns in low metallicity environments of the Milky Way halo \citep[e.g.][]{Cescutti2008,Cescutti2014}, plays an even greater role in the evolution of these low mass dwarf galaxies \citep{Applebaum2018}.
+Indeed the increase in scatter in the stellar abundance patterns of low mass dwarf galaxies and UFDs has been attributed to inhomogeneous mixing and stochastic effects \citep[e.g.][]{Norris2010a,Simon2015,Mashonkina2017,Suda2017}.
+This complicates the interpretation of abundance patterns in these galaxies, particularly for constraining individual enrichment events.
 
@@
 In \cite{Emerick2018b} we demonstrate that elements released through AGB winds have both wider abundance distributions in the ISM and lower ejection fractions from the galaxy than elements released in supernovae.
-It is becoming increasingly clear that enrichment is quite inhomogeneous in low mass dwarf galaxies (refs?), and also that the behavior of metals from any one enrichment event depends on a significant number of complex interactions.
+% It is becoming increasingly clear that enrichment is quite inhomogeneous in low mass dwarf galaxies (refs?), and also that the behavior of metals from any one enrichment event depends on a significant number of complex interactions.
 In spite of this progress, there is still substantial work to be done in understanding the physical processes that drive both evolution of both the mean and width of stellar abundances in low-mass dwarf galaxies.
@@
 \label{ch4:sec:experiment}
-We restart our fiducial, full-physics simulation at two different times, 180 Myr, and 360 Myr, labeled as runs \runonenu~ and \runtwonu~ respectively.
+We restart our fiducial, full-physics simulation at two different times, 180 Myr, and 360 Myr, labeled as runs \runonenu~and \runtwonu~respectively.
 These correspond to two different times in the galaxy's SFR evolution, testing how much variance is expected in the metal mixing and ejection with the star formation rate.
-\runonenu~ occurs during the lull in star formation following the initial SFR peak, and \runtwonu~ occurs in an extended period of little to no ongoing star formation.
+\runonenu~occurs during the lull in star formation following the initial SFR peak, and \runtwonu~occurs in an extended period of little to no ongoing star formation.
 We attempted to to evolve each simulation for 150 Myr, but due to computational constrains this was not always possible.\footnote{We began runs during the peak of star formation ($\sim 100$~Myr), but the computational cost increases substantially during this time.
@@
 \caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines), the galaxy's disk (black, solid), and the CGM (black, dashed) as averaged across all events at a given $E_{\rm ej}$.
-The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases (colored lines) sum to the black, solid line.
-\textbf{Need to remake these figures}}
+The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases (colored lines) sum to the black, solid line.}
 \label{ch4:fig:ISM_CGM}
@@
 However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, corresponding to the mass fraction of the CNM at this point in the galaxy's evolution (see Figure~\ref{ch1:fig:ISM_evolution}).
-This trend -- that the fraction of metals contained in a given phases tends towards the mass fraction of that phase -- is true across all phases in the simulation.
+This trend -- that the fraction of metals contained in a given phase tends towards the mass fraction of that phase -- is true across all phases in the simulation.
 Therefore, we can consider that the metals for each source are well-mixed across the \textit{phases} of the ISM on timescales of $\sim$100-150~Myr.
@@
 For our numerical experiments, enrichment in the whole ISM only occurs once and ejection from the ISM is easy to follow.
-This allows for a more clean interpretation of the evolution than examining either the IQR or the IDR.
+This allows for a cleaner interpretation of the evolution than examining either the IQR or the IDR.
 
@@
 Since the E46 events were likely to not self-interact, we additionally placed events at $r = 100$~pc and one event at each $r$ at about one scale height above the disk ($z = 50$~pc).
-For each \runonenu~ run, we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ as a function of radial position in the galaxy for each event in Figure~\ref{ch4:fig:radial position}.
+For each \runonenu~run, we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ as a function of radial position in the galaxy for each event in Figure~\ref{ch4:fig:radial position}.
 The points, error bars, and colors are the same as in Figure~\ref{ch4:fig:CGM_CNM_variance}.
@@
 It is unclear what exactly drives these mixing differences.
-If feedback-driven turbulence is the dominate driver of ISM mixing in this dwarf galaxy -- as it likely is -- then sources near the center are more likely to be affected by more feedback events (due to a slightly higher $\Sigma_{\rm SFR}$) and mix more efficiently.
+If feedback-driven turbulence is the dominant driver of ISM mixing in this dwarf galaxy -- as it likely is -- then sources near the center are more likely to be affected by more feedback events (due to a slightly higher $\Sigma_{\rm SFR}$) and mix more efficiently.
 
@@
 
-We compute the average ISM properties within a 4-zone radius ($4 \times dx$~=~7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each \runonenu~ run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event.
+We compute the average ISM properties within a 4-zone radius ($4 \times dx$~=~7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties.\footnote{Note that the injection region for each event is a 3-cell radius sphere mapped onto the grid with a CIC interpolation scheme.} In Figure~\ref{ch4:fig:ISM_variance} we plot $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ for each \runonenu~run as a function of the average number density ($<n>$) in the injection region within 0.1~Myr (our time resolution) of the event.
 The E46 events clearly do a better job sampling the ISM density PDF, with a slight trend of decreasing $f_{\rm CGM}$ (more retained metals) with local ISM number density.
@@
 We note that correlation with SFR is of interest not because the formation of stars by themselves, but rather the increase in feedback associated with a higher SFR (and thus a warmer / hotter ISM, greater turbulence in the ISM, and more significant outflows).
-We compare these two runs in Figure~\ref{ch4:fig:SFR_comparison_CGM_CNM}, showing runs from \runonenu~ in green and runs at the lower SFR, \runtwonu, in purple.
+We compare these two runs in Figure~\ref{ch4:fig:SFR_comparison_CGM_CNM}, showing runs from \runonenu~in green and runs at the lower SFR, \runtwonu, in purple.
 $f_{\rm CGM}$ increases much more rapidly across injection energies in \runonenu.
-However, this value seems to be similar across runs for E49 and E51 by $\sim$50 Myr, with an additional increase again in the \runonenu~ simulations towards the end of the time.
-This initial spike, lull, and second increase corresponds to the period of active star formation, slightly lull, and increase in SFR experienced during the \runonenu~ simulations (see Figure~\ref{ch1:fig:sfr_mass_evolution}; the lull occurs between 40 and 80 Myr after the enrichment events, or during 220 - 260 Myr in that figure).
+However, this value seems to be similar across runs for E49 and E51 by $\sim$50 Myr, with an additional increase again in the \runonenu~simulations towards the end of the time.
+This initial spike, lull, and second increase corresponds to the period of active star formation, slightly lull, and increase in SFR experienced during the \runonenu~simulations (see Figure~\ref{ch1:fig:sfr_mass_evolution}; the lull occurs between 40 and 80 Myr after the enrichment events, or during 220 - 260 Myr in that figure).
 The SFR is consistently low (or zero) throughout \runtwonu, with just a couple brief increases in SFR.
@@
 It is generally true that after the initial $\sim$50 Myr of enrichment, a greater fraction of the metals in the ISM are contained in the CNM during the run with the lower SFR (\runtwonu), but this difference is not large and is only significant for the higher energy events.
-In addition, the mass fraction of the CNM is greater during run \runtwonu~ than in run \runonenu, so it may simply be that the long-term evolution of the fraction of metals in the CNM is more dependent upon the phase structure of the ISM -- which is regulated by stellar feedback -- than the feedback directly.
+In addition, the mass fraction of the CNM is greater during run \runtwonu~than in run \runonenu, so it may simply be that the long-term evolution of the fraction of metals in the CNM is more dependent upon the phase structure of the ISM -- which is regulated by stellar feedback -- than the feedback directly.
 

### 2019-04-13 thesis/chapters/ch_conclusion.tex
proof read updates

@@
 O, Mg).
-Indeed, this is observed in the stellar abundance patters of dwarf galaxies in the Local Group \citep{Suda2017}, but it remains to be seen if this is a conclusive signature of these mixing differences or perhaps is due to larger differences in star-to-star metal yields for these elements.
+Indeed, this is observed in the stellar abundance patterns of dwarf galaxies in the Local Group \citep{Suda2017}, but it remains to be seen if this is a conclusive signature of these mixing differences or perhaps is due to larger differences in star-to-star metal yields for these elements.
 Finally, we were able to characterize the metal mass fraction PDFs for each element across each phase of the ISM, and found that each were generically well-fit by a combined log-normal PDF with a power-law tail towards higher metal mass fractions.

### 2019-04-17 thesis/acknowledgments.tex
finalizing

@@
 \vspace{0.8cm}
-% Thank people, places, things, existential concepts, etc. here. Length varies
-% but usually something like 1-2 pages
 
-To my wife Ellen, who moved across the country for me to NYC and will be moving
-across the country again in the next few months, who has patiently put up with
+To my wife Ellen, who moved across the country for me to NYC
+(and across the country again in the next few months), who has patiently put up with
 all of my travel and time away at conferences in the past few years,
@@
 
-To my parents and my family who have continued to support me in countless ways
-throughout my life. \textbf{...more...}
+To my family who have continued to support me in countless ways.
+In many ways my parents are directly responsible for me pursuing a career in Astronomy.
+They enabled me to have a good education throughout my life that prepared me
+well for graduate school. But maybe more importantly, they provided me with my
+first exposure to the wonders of the Universe which gave me the desire to
+pursue the path that led me to where I am today.
 

### 2019-04-17 thesis/acknowledgments.tex
remvoing space

@@
 who has worked longer hours at much more demanding jobs than the work I have put
-into this \dissertation, and who has continued to support me through this
+into this \Dissertation, and who has continued to support me through this
 entire journey, all just so that I could pursue my dream. A simple ``thank you" is

### 2019-05-28 thesis/abstract.tex
Edits from KVJ, JT, and MM for abstract and intro

--- 2019-04-03 thesis/abstract.tex
@@
 \end{center}
-Motivated by the desire to better understand two of the largest outstanding problems in galactic evolution -- stellar feedback and galactic chemical evolution --
+Motivated by the desire to investigate two of the largest outstanding problems in galactic evolution -- stellar feedback and galactic chemical evolution --
 %In this \thesis
 we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and the multi-channel stellar feedback and multi-element metal yields associated with each star.
-We developed these simulations as a means to better understand the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies.
-We follow the evolution of the individual metal yields associated with these stars in order to better understand how metals mix within the ISM and are ejected into the circumgalactic and itergalactic media (CGM, IGM) through outflows.
-This study is directed with the goal of better understanding the ever increasing quality of stellar abundance measurements within our own Milky Way galaxy and in nearby dwarf galaxies.
+We developed these simulations to probe the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies.
+We follow the evolution of the individual metal yields associated with these stars in order to trace how metals mix within the ISM and are ejected into the circumgalactic and intergalactic media (CGM, IGM) through outflows.
+This study is directed with the ultimate goal of leveraging the ever increasing quality of stellar abundance measurements within our own Milky Way galaxy and in nearby dwarf galaxies to understand galactic evolution.
 
@@
 To address this issue, we characterize the time evolution of the metal mass fraction distributions of each of the tracked elements in our simulation in each phase of the ISM.
-For the first time, we demonstrate that there are significant differences in how individual metals are sequestered in each gas phase (from cold, neutral gas up to hot, ionized gas) that depends upon the energetics of the enrichment sources that dominate the production of a given metal species.
+For the first time, we demonstrate that there are significant differences in how individual metals are sequestered in each gas phase (from cold, neutral gas up to hot, ionized gas) that depend upon the energetics of the enrichment sources that dominate the production of a given metal species.
 We find that AGB wind elements have much broader distributions (i.e.
@@
 
-Finally, we summarize how this new understanding of galactic chemical evolution -- that metal mixing and ejection from galaxies is not uniform across metal species -- can be used to improve significantly upon current state of the art galactic chemical evolution models.
+Finally, we summarize how this improved physical model of galactic chemical evolution that demonstrates that metal mixing and ejection from galaxies is not uniform across metal species can be used to improve significantly upon current state of the art galactic chemical evolution models.
 These improvements stand to help improve our understanding of galactic chemical evolution and reconcile outstanding disagreements between current models and observations.

### 2019-05-28 thesis/acknowledgments.tex
Edits from KVJ, JT, and MM for abstract and intro

@@
 entire journey, all just so that I could pursue my dream. A simple ``thank you" is
-entirely insufficient to repay her for these sacrifices, but its a good thing
+entirely insufficient to repay her for these sacrifices, but it is a good thing
 I have the rest of my life to show how grateful I am.

### 2019-05-28 thesis/chapters/ch_introduction.tex
started writing appendxi to intro to mention other work (cluster Lyalpha, RPS / feedback in dwarfs, grackle) but decided to not do this
Edits from KVJ, JT, and MM for abstract and intro

@@
 \vspace{-16pt}
-\begin{chapquote}{Isaac Asimov} \singlespacing The most exciting phrase to hear in science, the one that heralds discoveries, is not ‘Eureka!’ but ‘Now that’s funny…
+\begin{chapquote}{Isaac Asimov} \singlespacing The most exciting phrase to hear in science, the one that heralds discoveries, is not ``Eureka!'' but ``Now that's'' funny…
 \end{chapquote} \vspace{-8pt}
@@
 A substantial slice of modern astrophysics has been devoted towards understanding the chemical evolution -- the abundances of individual elements in space and time -- of the Universe.
-With the exception of H, He, and trace amounts of light elements, all of the elements in the Universe are produced in nuclear reactions associated with stellar evolution, either in the cores of stars, stellar winds, asymptotic giant branch (AGB) winds of low mass stars, and more exotic sites like neutron star - neutron star mergers (NS-NS).
+With the exception of H, He, and trace amounts of light elements, all of the elements in the Universe are produced in nuclear reactions associated with stellar evolution -- in the cores of stars -- and released in stellar winds, asymptotic giant branch (AGB) winds of low mass stars, SNe, and more exotic sources, like neutron star - neutron star mergers (NS-NS).
 See \cite{Nomoto2013}, \cite{Thielmann2017}, and \cite{Frebel2018} for recent reviews on this topic as it applies to studies of galactic and stellar evolution.
@@
 properties of the multi-scale, multi-phase turbulent interstellar medium (ISM) and the radiative processes and chemistry that operate within the ISM.
-This in turn requires one to toss in a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and supernovae -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies.
+This in turn requires one to toss in a detailed understanding of the stellar feedback physics -- stellar radiation, stellar winds, and SNe -- that helps to regulate star formation by destroying cold, star forming gas, driving the multi-phase structure of the ISM, and by driving outflows of gas into the circumgalactic medium (CGM) around galaxies.
 Simultaneously, one must make the simple step of nailing down a complete model of stellar structure, stellar evolution, the reaction rates and cross sections of every nuclear reaction, and the lifetimes of individual isotopes.
@@
 
-The observational landscape today is primed for developing a more detailed understanding these processes.
+The observational landscape today is primed for developing a more detailed understanding of these processes.
 Recent observational campaigns such as SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, the Gaia-ESO survey \citep{Gaia}, APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, GALAH \citep{GALAH,Buder2018}, as well as upcoming observations, such as the Local Volume Mapper as part of SDSS-V, have generated tremendous amounts of information on detailed stellar abundances and stellar kinematics in our Milky Way and nearby Local Group dwarf galaxies.
@@
   \includegraphics[width=0.75\linewidth]{./figures/intro/periodic_table}
-  \caption{The periodic table of elements colored by the relative fraction of the nucleosynthetic processes that naturally occur in the Universe that produce each element.
-\textbf{Image Credit:} A modified version of the table created by Anna Frebel (\url{https://www.dropbox.com/sh/ib3agt2bkxqqk2u/AACbEw1warp74qzUh2AcWqfja?dl=0}), accessed on 03-18-19.}
+  \caption{The periodic table of elements colored by the relative fraction of the astrophysical source for each element. \textbf{Image Credit:} Figure 1 of \cite{Johnson2019}.}
   \label{intro:fig:periodic table}
@@
 A variety of nucleosynthetic processes occur within stars and during their deaths that lead to the production of all of the elements in the periodic table.
-This is illustrated well in Figure~\ref{intro:fig:periodic table}, which shows the periodic table colored by the fractional importance of the nucleosynthetic processes that produce each element.
-Due to the diversity in production sources across the periodic table, multi-element metal abundance measurements in stars can be used to to better understand and constrain how and where each metal is produced.
+Different astrophysical sources reach conditions that enable different nuclear reactions, as is well-illustrated in Figure~\ref{intro:fig:periodic table}.
+This image shows the periodic table colored by the fractional importance of the astrophysical source that produce each element.
+Due to the diversity in production sources across the periodic table, multi-element metal abundance measurements in stars can be used to better understand and constrain how and where each metal is produced.
 Exactly which reactions occur where depend strongly on the initial abundances of elements in stars, their stellar masses, and, for heavy nuclei, the neutron density.
@@
 This means that elements from different nucleosynthetic channels are produced on different timescales during a galaxy's evolution, as set by the lifetimes of the stars in which they occur, and are released into the galaxy at different energies, with different spatial distributions within the galaxy, and at different rates.
-For example, O, an $\alpha$-element is produced predominately in massive stars and is therefore released via core collapse supernovae on timescales of $\sim$~10~Myr after a star formation event, near their stellar birth sites.
-By contrast, Sr is produced predominately via the s-process (discussed more below) which occurs in part in the asymptotic giant branch (AGB) winds of lower mass stars ($M < 8$~M$_{\odot}$) at much lower energies and on timescales of $\sim 100$~Myr - $1$~Gyr.
-By this time, these stars would have diffused farther away from their birth sites, potentially sampling a qualitatively different portion of the ISM than the preceeding core collapse SNe.
+For example, O, an $\alpha$-element is produced predominantly in massive stars and is therefore released via core collapse SNe on timescales of $\sim$~10~Myr after a star formation event, near their stellar birth sites.
+By contrast, Sr is produced predominately via the s-process (discussed more below) which occurs in low mass stars and released in asymptotic giant branch (AGB) winds ($M < 8$~M$_{\odot}$) at much lower energies and on timescales of $\sim 100$~Myr - $1$~Gyr.
+By this time, these stars would have diffused farther away from their birth sites, potentially sampling a qualitatively different portion of the ISM than the preceding core collapse SNe.
 Generally, how different timescales affect observed stellar abundances patterns are well understood and easily modeled.\footnote{The canonical example of this is the ``knee" feature in a $[\alpha/$Fe] vs.
-[Fe/H] diagram, where the location of this knee signifies the point at which Type Ia enrichment (which produces significant Fe, but little to no $\alpha$ elements) begins to have a significant contribution over core collapse SNe (rich in $\alpha$ elements, but not Fe) \citep[e.g.[]{MatteucciBrocato1990, Geisler2005, Hill2018}.
+[Fe/H] diagram, where the location of this knee signifies the point at which Type Ia enrichment (which produces significant Fe, but little to no $\alpha$ elements) begins to have a significant contribution over core collapse SNe (rich in $\alpha$ elements, but not Fe) \citep[e.g.][]{MatteucciBrocato1990, Geisler2005, Hill2018}.
 The location of this knee in this diagram shifts for a given galaxy depending on its SFH.} However, it is not well understood how differences in where and with what energies these events occur affect observed stellar abundance patterns.
@@
 As relevant to this work, we briefly summarize a few of the important nucleosynthetic channels shown in Figure~\ref{intro:fig:periodic table} and their sites.
-$\alpha$-elements, notably O, Mg, Si, Ca, and Ti, are produced during the lifetime of massive stars (O, Mg) or during the core collapse supernova explosion itself.
+$\alpha$-elements, notably O, Mg, Si, Ca, and Ti, are produced during the lifetime of massive stars (O, Mg) or during the core collapse SN explosion itself.
 In either case, these elements are synthesized through the capture of an $\alpha$ nucleus, progressing towards increasingly heavier nuclei in intervals of 4/2 in mass/atomic number (as $\alpha$ = $^{4}_2$He) from $^8_4$Be all the way to the stable $^{52}_{26}$Fe and unstable $^{56}_{28}$Ni (which decays to $^{56}_{26}$Fe).
-The iron group elements, notably Fe, Mn, Co, and Ni, are produced predominately in Type Ia supernovae, with variations depending on a single vs.
+The iron group elements, notably Fe, Mn, Co, and Ni, are produced predominately in Type Ia SNe, with variations depending on a single vs.
 double degenerate scenario, the initial composition of exploding white dwarf(s) (WD), and the dynamics of the explosion itself.
@@
 In r-process, however, the rate of neutron capture exceeds beta decay, allowing for the production of different, typically heavier, nuclei.
-As shown in the diagram, lighter elements are produced via the s-process and heavier via the r-process, with notable overlap in certain elements, such as Ba.\footnote{For the sake of this discussion, the light neutron-capture primary process elements (sometimes referred to as ``lighter element primary process") should be considered s-process elements.
+The lighter heavy nuclei elements (Rb through Pb, though with exceptions) are produced via the s-process and heavier (Te through Bi, again, with exceptions) via the r-process, with notable overlap in certain elements, such as Ba.
+%\footnote{For the sake of this discussion, the light neutron-capture primary process elements (sometimes referred to as ``lighter element primary process") should be considered s-process elements.
 Briefly, this different nucleosynthetic channel, first identified in \cite{Travaglio2004}, arose from the disagreement between models of s-process enrichment and stellar abundances of elements including Sr, Y, and Zr.
-However there is still uncertainty as to whether or not these differences can be explained with different models of weak s-process (which can occur in the winds of massive stars) \citep[e.g.][]{Prantzos2018}.} The s-process occurs predominately in the low-energy winds of low mass (1-8 M$_{\odot}$) AGB stars on time scales of 100's of Myr up to 1 Gyr.
+However there is still uncertainty as to whether or not these differences can be explained with different models of weak s-process (which can occur in the winds of massive stars) \citep[e.g.][]{Prantzos2018}.}
+The s-process occurs predominately in low mass (1-8 M$_{\odot}$) stars and is released at the end of their lives via AGB winds on time scales of 100's of Myr up to 1 Gyr.
 Exactly which elements are produced in a given AGB star varies with stellar mass and depends strongly on metallicity, which determines the available heavy seed nuclei.
@@
 
-The dominant origin of r-process enrichment is highly uncertain, though possible channels include NS-NS and neutron star - black hole mergers, neutrino driven winds in core collapse SNe, and exotic SNe, such as magnetic, jet-driven SNe, collapsars, hypernovae, and long-duration gamma-ray bursts \citep[see ][ for recent reviews]{Frebel2018, Cowan2019}.
+The dominant origin of r-process enrichment is highly uncertain, though (as indicated in Figure~\ref{fig:periodic table}) possible channels include NS-NS mergers, neutron star - black hole mergers, neutrino driven winds in core collapse SNe, and exotic SNe, such as magnetic, jet-driven SNe, collapsars, hypernovae, and long-duration gamma-ray bursts \citep[see ][ for recent reviews]{Frebel2018, Cowan2019}.
 Eu is the most commonly used (and easy to observe) unambiguous observational tracer of r-process enrichment; Ba is also often studied as a tracer, but requires care due to the significant contribution from s-process enrichment.
@@
 
-A full, detailed model of radiative cooling, heating, non-equillibrium chemistry, and dust is generally far too computationally expensive to include in galaxy-scale simulations.
+A full, detailed model of radiative cooling, heating, non-equilibrium chemistry, and dust is generally far too computationally expensive to include in galaxy-scale simulations.
 For this reason, many large-scale cosmological simulations assume that all gas is optically thin and that all molecules and ionization states exist in equilibrium.
@@
 More complex simulations often track some number (usually $< 10$) of species involved in primordial chemistry in order to better account for non-equilibrium effects and \Hmolecular~production, though with noted increases in memory requirements and computational cost.
-Some of the most advance models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2016,Richings2018}; but these are typically prohibitively expensive to run on large scales.
+Some of the most advanced models to-date can account for well over 10$^2$ individual chemical reactions involving $>$ 20 elements and molecules \citep[e.g.][]{Richings2016,Richings2018}; but these are typically prohibitively expensive to run on large scales.
 In this \dissertation we adopt the chemistry and radiative cooling and heating physics models available in the newly developed, open-source library \code{GRACKLE} \citep{GrackleMethod}.
@@
 
-In galaxy-scale hydrodynamics, the costs in resolving the spatial scales and gas densities required to directly follow star formation relegates this process to a sub-grid model.
+In galaxy-scale hydrodynamics, the extreme computational cost of resolving the spatial scales and gas densities required to directly follow star formation relegates this process to a sub-grid model.
 Stars form from fluid elements that surpass a variety of threshold conditions at an assumed rate and efficiency.
@@
 %cite?,
-or that gas meet a minimum \Hmolecular~mass fraction \citep[e.g.][]{Kuhlen2012}
+or that gas meet a minimum \Hmolecular~mass fraction or that density high enough to support \Hmolecular~formation \citep[e.g.][]{Kuhlen2012}.
 %\citep[e.g.][]{}
-.
-Once a fluid element is flagged as star forming, simulators have a few options to choose from in how to determine what fraction and with what rate that mass is converted into stars.
+Once a fluid element is flagged as star forming, simulators have a few options for how to compute the fraction and rate at which gas is turned into stars.
 Briefly, some form of the following equation is usually adopted to describe the star formation rate density,
@@
 \end{equation}
+% AE still need to address mm comments here :
 In many cases, $\epsilon$ is fixed to some small value ($\sim$ 0.01) \citep{KrumholzTan2007} meant to represent a galaxy-scale average of star formation efficiency, even though this may vary significantly between individual molecular clouds \citep{Grudic2018}.
@@
 
-Initial models for stellar feedback relied primarily on the energy injection from supernovae (SNe, see Section~\ref{intro:sec:supernovae}) to regulate star formation and drive outflows, but it has become clear that this mechanism alone cannot completely account for all of the star formation, ISM, outflow, CGM, and even intergalactic medium (IGM) properties of observed galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews and more detailed discussion of how feedback impacts outstanding problems in galactic evolution).
-Other sources of effective stellar feedback have been identified since \citep[e.g.][]{Agertz2013}, which serve to regulate star formation on different timescales and help develop and ISM and CGM with different phase and ionization properties.
+Initial models for stellar feedback relied primarily on the energy injection from supernovae (SNe, see Section~\ref{intro:sec:SNe}) to regulate star formation and drive outflows, but it has become clear that this mechanism alone cannot completely account for all of the star formation, ISM, outflow, CGM, and even intergalactic medium (IGM) properties of observed galaxies (see \cite{SomervilleDave2015} and \cite{NaabOstriker2017} for recent reviews and more detailed discussion of how feedback impacts outstanding problems in galactic evolution).
+Other sources of effective stellar feedback have been identified \citep[e.g.][]{Agertz2013}, which serve to regulate star formation on different timescales and help develop an ISM and CGM with different phase and ionization properties.
 This includes both stellar radiation (Section~\ref{intro:sec:radiation}) and stellar winds (Section~\ref{intro:sec:stellarwinds}).
 
-Although not included in this \Dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution.
-A substantial amount of recent research has been dedicated towards the examination of supernova-driven cosmic ray feedback (see Section~\ref{ch1:sec:CRs} for a more detailed discussion and references).
+Although not included in this \Dissertation, for the sake of completeness, we mention a few additional sources of stellar feedback that likely contribute to the full picture of galactic evolution: 1) cosmic rays, 2) stellar binary evolution, and 3) hypernovae and other exotic sources of feedback.
+First, a substantial amount of recent research has been dedicated to the examination of SN-driven cosmic ray feedback (see Section~\ref{ch1:sec:CRs} for a more detailed discussion and references).
 In brief, cosmic rays can be a dominant source of heating in very dense, optically-thick gas and act as a source of non-thermal pressure in the ISM, which can drive galactic winds with qualitatively different phase structures \citep[e.g.][]{SalemBryanCorlies}.
-Binarity is often ignored in models of stellar feedback.
-The effects of binary evolution can dramatically extend the timescales over which ionizing radiation and supernovae act in a newly formed stellar populations.
-Typically, this increases their total energy output and decreases the ISM densities in which SNe explode, increasing their effectiveness (see Section~\ref{ch1:sec:binary stars}).
-Finally, exotic sources of stellar feedback, such as hypernovae, high-mass X-ray binaries, and NS-NS mergers can also be a potentially important sources of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}.
+Second, binarity is often ignored in models of stellar feedback.
+The effects of binary evolution can dramatically extend the timescales over which ionizing radiation and SNe act in a newly formed stellar population.
+Typically, this increases their total energy output and decreases the ISM densities in which SN explode, increasing their effectiveness (see Section~\ref{ch1:sec:binary stars}).
+Third, exotic sources of stellar feedback, such as hypernovae, high-mass X-ray binaries, and NS-NS mergers can also be a potentially important sources of feedback, particularly in the lowest mass halos \citep[e.g.][]{Artale2015}.
 However, the uncertainties in the frequency and delay time distributions for when these events should occur, and their relative rarity, preclude including these effects in this \Dissertation.
 
-\subsubsection{Supernova Feedback}
-\label{intro:sec:supernovae}
+\subsubsection{SNFeedback}
+\label{intro:sec:SNe}
 
-In the simplest model, supernova feedback is treated as the injection of pure thermal energy (and mass) into the fluid element(s) that are host / closest to the chosen site of a supernova explosion.
+In the simplest model, SNfeedback is treated as the injection of pure thermal energy (and mass) into the fluid element(s) that are host / closest to the chosen site of a SNexplosion.
 In self-consistent models of star formation and feedback these sites are usually actual star particles, but this does not have to be the case.
-The first models which included supernova feedback lacked the spatial / mass resolution to resolve individual (or even collective) SN events.
+The first models which included SNfeedback lacked the spatial / mass resolution to resolve individual (or even collective) SN events.
 This is the source of the commonly known ``overcooling" problem, whereby too little energy is injected into too much mass such that the affected region only reaches modest temperatures ($T \lesssim 10^5$~K, as opposed to $T > 10^7$~K, or so).
@@
 High resolution simulations, like those developed in this \Dissertation, can typically rely on using pure thermal energy injection while still avoiding artificial overcooling.\footnote{This is advantageous because it is often substantially easier to implement than kinetic / momentum injection methods while being less susceptible to numerical artifacts, especially for grid-based codes.} This is true for simulations with typical spatial / mass resolutions better than a few pc / 10 M$_{\odot}$ \citep{Simpson2015,Hu2018,Smith2018b}.
-However, a spatial resolution requirement is a density dependent statement; in this case supernovae that occur in the densest gas ($n > 10^{2-3}$~cm$^{-3}$) may still be under-resolved and ineffective.
+However, a spatial resolution requirement is a density dependent statement; in this case SNe that occur in the densest gas ($n > 10^{2-3}$~cm$^{-3}$) may still be under-resolved and ineffective.
 In this case, accounting for feedback processes from massive stars that occur before the first core collapse SN in a given star formation event becomes critical \citep{Hu2016}.
@@
 We only briefly discuss this method of feedback here, as it is discussed in much more detail in both Chapters~\ref{ch:chapter1} and \ref{ch:chapter2}.
-In brief, \cite{Leitherer1999}, \cite{Agertz2013}, and others have demonstrated that stellar radiation accounts for a substantial fraction of the total energy output of a stellar population.
+In brief, \cite{Abbott1982}, \cite{Reynolds1990}, \cite{Leitherer1999}, \cite{Agertz2013}, and others have demonstrated that stellar radiation accounts for a substantial fraction of the total energy output of a stellar population.
 Ionizing photons from young, massive stars can photoionize and heat the gas surrounding sites of recent star formation.
@@
 Far ultraviolet (FUV) photons contribute to gas heating via the photoelectric heating of dust grains.
-This is a significant heating mechanism in higher metallicity environments, like the Milky Way \citep{Parravano2003,Wolfire2003}, but may still be important in setting temperature floor of cold dense gas in lower mass galaxies \citep{Forbes2016,Hu2017}.
+This is a significant heating mechanism in higher metallicity environments, like the Milky Way \citep{Parravano2003,Wolfire2003}, but may still be important in setting the temperature floor of cold dense gas in lower mass galaxies \citep{Forbes2016,Hu2017}.
 Lyman-Werner (LW) band radiation regulates the \Hmolecular~abundance, which is particularly important in low-metallicity environments where \Hmolecular~is a dominant coolant \citep[e.g.][]{Glover2003,Wolcott-Green2012}.\footnote{And is arguably even more important when using star formation prescriptions that depend upon the local \Hmolecular~mass fraction.} As the goal of this \dissertation is to develop an as-complete-as-possible model of galactic chemical evolution, we account for each of these processes in some fashion.
@@
 For this reason we include stellar wind feedback in this \Dissertation, albeit in a simplified fashion.\footnote{Although we do not have conclusive results to this end, initial examination of our simulations has shown that our stellar wind model is only globally important in simulations where radiation feedback is ignored.
-It is thus likely sub-dominant to radiation feedback.}
+It is thus likely sub-dominant to radiation feedback \citep{Abbott1982,McKee1984}.}
 
@@
 However, the number of known Local Group dwarf galaxies has increased dramatically since that time, particularly for the Milky Way, whose known satellite population has more than doubled.
-This is due in large part to tremendous improvements in our ability to detect galaxies on the faintest end of the luminosity function, called ultrafaint dwarf galaxies \citep[UFDs][]{Willman2005}.\footnote{See \cite{Simon2019} for a recent review}.
-The Dark Energy Survey \citep[e.g.][]{Drlica-Wagner2015} and Hyper Supbrime-Cam \citep[e.g.][]{Greco2018} have made tremendous advances to this end, with the upcoming Large Synoptic Survey Telescope expected to produce an even greater increase in the known population of faint galaxies in the Local Group \citep{Haynes2019,Weisz2019}.
+This is due in large part to tremendous improvements in our ability to detect galaxies on the faintest end of the luminosity function, called ultrafaint dwarf galaxies \citep[UFDs,][]{Willman2005}.\footnote{See \cite{Simon2019} for a recent review}.
+The Dark Energy Survey \citep[e.g.][]{Drlica-Wagner2015} and Hyper Suprime-Cam \citep[e.g.][]{Greco2018} have made tremendous advances to this end, with the upcoming Large Synoptic Survey Telescope expected to produce an even greater increase in the known population of faint galaxies in the Local Group \citep{Haynes2019,Weisz2019}.
 
@@
 %(cite)
-and, for the lowest mass dwarf galaxies
+and, for the lowest mass dwarf galaxies,
 % need citations
-, exhibit bursty star formation histories driven by stochasticity in the process of both star formation and the effects of stellar feedback
+exhibit bursty star formation histories driven by stochasticity in the process of both star formation and the effects of stellar feedback
 % need citations
@@
 Not only does this correspond to a significant amount of mass outflow from these galaxies, but these winds should also carry out a substantial amount of metals from these galaxies.
-In fact, the differences with which different models for feedback-driven winds drive metals in outflows in low mass galaxies can be an important constrain on the underlying physics \citep[e.g.][]{Wheeler2018,Agertz2019}.
+In fact, the differences with which different models for feedback-driven winds drive metals in outflows in low mass galaxies can be an important constraint on the underlying physics \citep[e.g.][]{Wheeler2018,Agertz2019}.
 \cite{Kirby2011-metals} used measurements of the stellar abundances in Local Group dSph's and their resolved star formation histories to determine that their stars contain less than 5\% of the metals synthesized in each galaxy.
@@
 
-The most prominent example of these types of studies has been of the UFD Reticulum II, where \cite{Ji2016} used the extreme r-process enhancement in its stars to argue in favor of a NS-NS of r-process enrichment.
+The most prominent example of these types of studies has been of the UFD Reticulum II, where \cite{Ji2016} used the extreme r-process enhancement in its stars to argue in favor of a NS-NS origin of r-process enrichment.
 This conclusion has been supported by observations in additional Local Group dwarf galaxies \citep{Duggan2018}, but there is still some disagreement as to the dominant source of r-process enrichment \citep[e.g.][]{Siegel2018}.
@@
 Yet, as discussed, the current state of the art prescriptions for these processes are ad-hoc.
-Recent analytic work in \cite{KrumholzTing2018} lays down a framework to evaluate the correlation between individual metals in different galactic environments and predicts that the correlations will differ for different nucleosynthetic sites (e.g.
-AGB winds vs.
+Recent analytic work in \cite{KrumholzTing2018} lays down a framework to evaluate the correlation between individual metals in different galactic environments and predicts that the correlations will differ for sources that trace different nucleosynthetic sites (e.g.
+AGB wind vs.
 SNe).
@@
 We implement such a model, which follows stars as individual star particles over a fully sampled IMF, in hydrodynamics simulations of an isolated, low-mass dwarf galaxy.
-We describe in detail the physics included in these simulations, including a stellar feedback model that follows stellar radiation, stellar winds, and supernovae.
+We describe in detail the physics included in these simulations, including a stellar feedback model that follows stellar radiation, stellar winds, and SNe.
 We find that the implemented set of physics give rise to a multi-phase ISM with a highly variable stellar radiation profiles, star formation rates, and galactic outflows.
@@
 In Chapter \ref{ch:chapter2} \citep[published as][]{Emerick2018a}, we investigate how stellar ionizing radiation feedback impacts the evolution of our simulated low mass dwarf galaxy.
-We confirm the findings in recent works, as discussed in Section~\ref{intro:sec:radiation}, that find that stellar radiation is an important source of pre-supernova feedback that regulates star formation and can help drive galactic outflows.
-We additionally investigate how radiation feedback couples to the ISM to drive galactic winds by demonstrating that the ionization of gas far from individual ionizing sources, out into the disk-halo interface of our galaxy, creates low-density channels through which supernovae can readily drive gas and metals into and beyond the galaxy's CGM.
+We confirm the findings in recent works, as discussed in Section~\ref{intro:sec:radiation}, that find that stellar radiation is an important source of pre-SNfeedback that regulates star formation and can help drive galactic outflows.
+We additionally investigate how radiation feedback couples to the ISM to drive galactic winds by demonstrating that the ionization of gas far from individual ionizing sources, out into the disk-halo interface of our galaxy, creates low-density channels through which SNe can readily drive gas and metals into and beyond the galaxy's CGM.
 This suggests that not only is the local deposition of energy from stellar radiation important, which quickly destroys dense gas in stellar birth-sites, but also long-range effects are important to consider in a consistent model of stellar feedback.
@@
 In Chapter \ref{ch:chapter3} \citep[published as][]{Emerick2018b}, we dive in detail into the evolution of each of the 15 individual metal species that we follow in our simulation.
-We focus primarily on the evolution of the gas-phase abundances of these metals, and how the site of nucleosynthesis (e.g.
-AGB winds or SNe) drives the subsequent evolution of each species.
+We focus primarily on the evolution of the gas-phase abundances of these metals, and how the origin of nucleosynthesis (e.g.
+AGB stars or SNe) drives the subsequent evolution of each species.
 We find that elements released in lower energy enrichment sources (e.g.
@@
 Finally, we conclude in Chapter \ref{ch:conclusion} and briefly discuss future work as extensions of this \Dissertation.
+
+%\setcounter{section}{0}%
+%\renewcommand\thesection{\thechapter.\Alph{section}}
+%
+%\section{Other Works}
+%For the sake of maintaining a well-focused \Dissertation -- on stellar feedback and galactic chemical evolution -- we leave out discussion of work done that, while related to galactic evolution,

### 2019-06-03 thesis/chapters/ch_chapter4.tex
chapter 5 edits from mordecai. Still have figure edits to do

@@
 These environments can potentially be used to trace and constrain enrichment from the first stars \citep[e.g.][]{FrebelBromm2012,Ji2015,Ritter2015,Jeon2017,Hartwig2018} and have been used to place constraints on the variety of possible astrophysical sources of r-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Duggan2018,Nagasawa2018,Ojima2018}.
-It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way is much more uniform, averaging over the variety of complex hydrodynamics and feedback-driven turbulence interactions that may be driving much of the significant variance in stellar abundances seen at low metallicity.
+It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way exhibits smaller abundance spreads, averaging over the variety of complex hydrodynamics and feedback-driven turbulence that may be driving much of the significant variance in stellar abundances seen at low metallicity.
 Stochasticity, which has been shown to be important for setting the width of stellar abundance patterns in low metallicity environments of the Milky Way halo \citep[e.g.][]{Cescutti2008,Cescutti2014}, plays an even greater role in the evolution of these low mass dwarf galaxies \citep{Applebaum2018}.
-Indeed the increase in scatter in the stellar abundance patterns of low mass dwarf galaxies and UFDs has been attributed to inhomogeneous mixing and stochastic effects \citep[e.g.][]{Norris2010a,Simon2015,Mashonkina2017,Suda2017}.
+Indeed the increase in scatter in the stellar abundance patterns of low mass dwarf galaxies and UFDs has been attributed to inhomogeneous mixing and stochastic effects \citep[e.g.][]{Norris2010a,Lee2013,Simon2015,Mashonkina2017,Suda2017}.
 This complicates the interpretation of abundance patterns in these galaxies, particularly for constraining individual enrichment events.
@@
 In this Chapter we utilize the simulations analyzed in prior chapters to conduct a controlled set of ``mixing experiments'' whereby we restart each simulation with enrichment events placed by-hand in order to more directly investigate the evolution of metals from an individual event.
-While elemental yields were tracked for each star in our simulation, we lacked the necessary Lagrangian information about the metals once they were released into the ISM to be able to trace the evolution of single enrichment events.
+While elemental yields were tracked for each star in our simulation, we lacked the necessary Lagrangian information\footnote{The history of a given fluid element, which is followed natively in SPH codes, but not in the grid-based hydrodynamics simulations used here.} about the metals once they were released into the ISM to be able to trace the evolution of single enrichment events.
 We investigate primarily how the feedback ejection energy of individual sources ($E_{\rm ej}$) and global star formation rate at the time of enrichment affects how metals are ejected from the galaxy in galactic winds and metal mixing in the ISM.
@@
 These correspond to two different times in the galaxy's SFR evolution, testing how much variance is expected in the metal mixing and ejection with the star formation rate.
-\runonenu~occurs during the lull in star formation following the initial SFR peak, and \runtwonu~occurs in an extended period of little to no ongoing star formation.
-We attempted to to evolve each simulation for 150 Myr, but due to computational constrains this was not always possible.\footnote{We began runs during the peak of star formation ($\sim 100$~Myr), but the computational cost increases substantially during this time.
+Run \runonenu~occurs during the lull in star formation following the initial SFR peak, and run \runtwonu~occurs in an extended period of little to no ongoing star formation.
+We attempted to to evolve each simulation for 150 Myr, but due to computational constraints this was not always possible.\footnote{We began runs during the peak of star formation ($\sim 100$~Myr), but the computational cost increases substantially during this time.
 These runs were abandoned.}
@@
 At the beginning of each restart, we place by-hand one or more enrichment events at assigned positions throughout the galaxy, with thermal injection energies ($E_{\rm ej}$), masses ($m_{\rm ej}$), and metal fractions ($Z_{\rm ej}$).
-We note that the injection masses, particularly the metal fractions, are somewhat arbitrary as they are likely dynamically insignificant relative to the ambient ISM mass in which they occur.
+We note that the injection masses, particularly the metal fractions, are somewhat arbitrary.
+The injected metal masses are dynamically insignificant relative to the ambient ISM mass in which they occur; these fields, therefore, act as tracers and do not impact the dynamics or cooling physics of the simulations.
 The important parameter here is $E_{\rm ej}$, which we vary to sample the range of ejection energies associated with significant sources of chemical enrichment, including AGB winds ($10^{46}$~erg)\footnote{Assuming full thermalization of the total mechanical energy output of an AGB wind.}, NS-NS mergers ($10^{49} - 10^{50}$~erg), supernovae (10$^{51}$~erg), and exotic enrichment sources, such as hypernovae, that can reach much higher energies (10$^{52}$~erg).
@@
 \includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
-\caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines), the galaxy's disk (black, solid), and the CGM (black, dashed) as averaged across all events at a given $E_{\rm ej}$.
+\caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines), the galaxy's disk (black, dashed), and the CGM (black, solid) as averaged across all events at a given $E_{\rm ej}$.
 The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases (colored lines) sum to the black, solid line.}
@@
 We summarize the source-averaged results for all enrichment events in runs \runone E46, \runone E49, \runone E50, \runone E51, and \runone E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid).
-These plots show a clear, immediate trend across $E_{\rm ej}$ for all lines in the figure, but the differences are most striking for the ISM (black, solid), CGM (black, dashed) lines.
+These plots show a clear, immediate trend across $E_{\rm ej}$ for all lines in the figure, but the differences are most striking for the ISM (black, dashed), CGM (black, solid) lines.
 In Chapter~\ref{ch:chapter3}
@@
 This implies that, if one to were assume that all metals behaved the same and adopted an $f_{\rm ej}$ of $\sim$0.9 -- typical for the total metal ejection fraction in simulations that do not track individual enrichment channels \citep[e.g.][]{Muratov2017,Christensen2018}, and consistent with observations of the O abundance in Local Group dwarf galaxies \citep[e.g.][]{Kirby2011,McQuinn2015} -- one would underestimate the amount of AGB metals in the ISM by a factor of $\sim$ 3, and overestimate exotic, high-energy sources by a factor of $\sim$ 2.
-In each case, these are metals that cannot participate in the enrichment of future stellar populations and will make a significant difference on the output stellar abundances in chemical evolution models.
-We explore this impact in different works.
+In each case, these are metals that cannot participate in the enrichment of future stellar populations and will make a significant difference to the output stellar abundances in chemical evolution models.
+% We explore this impact in different works.
 
-In all cases, the metals contained with the ISM are deposited predominately in the ionized phases of the ISM, the WIM or the HIM, with the relative fraction in each phase driven by the energy of the event.
+In all cases, the metals contained within the ISM are deposited predominantly in the ionized phases of the ISM, the WIM or the HIM, with the relative fraction in each phase driven by the energy of the event.
 Metals in the ISM injected with $E_{\rm ej} > 10^{49}$~erg are initially located predominately in the HIM, roughly 1/2 for $E_{\rm ej} = 10^{49}$~erg and nearly all for $E_{\rm ej} > 10^{51}$~erg.
@@
   \includegraphics[width=0.45\linewidth]{figures/ch4/CNM_average_evolution}
-  \caption{Time evolution of the fraction of enrichment source metals contained in the CGM over time (left), and the fraction of metals in the CNM just those metals retained in the ISM for each enrichment source (right).
+  \caption{Time evolution of the fraction of enrichment source metals contained in the CGM over time (left), and the fraction of metals in the CNM relative to just those metals retained in the ISM for each enrichment source (right).
 These are the same as the lines in Figure~\ref{ch4:fig:ISM_CGM}, but the CNM lines are normalized by the black, dashed total ISM line in Figure~\ref{ch4:fig:ISM_CGM}.}
@@
 
-However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, corresponding to the mass fraction of the CNM at this point in the galaxy's evolution (see Figure~\ref{ch1:fig:ISM_evolution}).
+However, the metals from each source do gradually trend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time.
+This value corresponds to the total mass fraction of the CNM (see Figure~\ref{ch1:fig:ISM_evolution}).
 This trend -- that the fraction of metals contained in a given phase tends towards the mass fraction of that phase -- is true across all phases in the simulation.
 Therefore, we can consider that the metals for each source are well-mixed across the \textit{phases} of the ISM on timescales of $\sim$100-150~Myr.
-This is comparable, but less than, the dynamical timescale of the galaxy, $\sim$200~Myr.
+This is comparable to, but less than, the dynamical timescale of the galaxy, $\sim$200~Myr.
 These two results suggest that the delay-time between when metals are available to enrich ongoing star formation is on order of $\sim$10~Myr across sources, and only significant for the lowest (E46, AGB-like) energy sources.
@@
 
-To frame this analysis, lets first examine what processes affect the metal mass fraction PDF.
+To frame this analysis, let us first examine what processes affect the metal mass fraction PDF.
 The mean metal mass fraction for a collection of gas is simply the total metal mass divided by the total gas mass.
-For a collection of gas elements, the mean metal mass fraction is defined as $Z_{\rm gas} = \frac{ \Sigma Z_{\rm i}M_{\rm gas,i}}{\Sigma M_{\rm gas,i}}$, where $M_{\rm gas,i}$ is the mass of the i$^{\rm th}$ homogeneous blob of gas, and $Z_{i}$ its metal mass fraction.
+For a collection of gas elements, the mean metal mass fraction is defined as $Z_{\rm gas} =  \Sigma Z_{\rm i}M_{\rm gas,i} / \Sigma M_{\rm gas,i}$, where $M_{\rm gas,i}$ is the mass of the i$^{\rm th}$ homogeneous blob of gas, and $Z_{i}$ its metal mass fraction.
 A completely homogeneous ISM would have a $\delta$ function metal mass fraction PDF at the mean metal fraction, or $p(Z) = \delta(Z_{\rm gas})$.
@@
 the diameter of our galaxy) divided by the r.m.s gas velocity.
-Although extending these results to multi-phase, global-galaxy simulations is non-trivial, we find typical $t_{\rm ed}$ in the CNM of $\sim$100~Myr and in the HIM of $\sim$10~Myr.\footnote{For comparison, the isothermal sound speed in these phases are $\sim$4~Gyr and $\sim$10~Myr respectively.} In order to properly evaluate the mixing timescale we would need to run each simulation for significantly longer, for several $t_{\rm ed}$.
+Although extending these results to multi-phase, global-galaxy simulations is non-trivial, we find typical $t_{\rm ed}$ in the CNM of $\sim$100~Myr and in the HIM of $\sim$10~Myr.\footnote{For comparison, the isothermal sound crossing time in these phases are $\sim$4~Gyr and $\sim$10~Myr respectively.} In order to properly evaluate the mixing timescale we would need to run each simulation for significantly longer, for several $t_{\rm ed}$.
 
@@
 Conducting this analysis requires measured r-process abundances for a large sample of stars in an individual dwarf galaxy.
-This is challenging for the lowest mass, most metal poor dwarf galaxies, which typically only have a few to 10 stars with measured abundances, but could be done for more a few low mass dwarfs like Ursa Minor, and for more massive dwarfs like Carina, and Fornax \citep{Suda2017}.
+This is challenging for the lowest mass, most metal poor dwarf galaxies, which typically only have a few to 10 stars with measured abundances, but could be done for low mass dwarfs like Ursa Minor, and for more massive dwarfs like Carina, and Fornax \citep{Suda2017}.
 % somerthing about needing cool onezone chemical models to try and model data with many free params might be nice here.
@@
 We turn now to discuss how much variety exists among these individual events.
-For each of the discussed runs (from set \runonenu), Figure~\ref{ch4:fig:CGM_CNM_variance} shows the fraction of metals ejected from the galaxy (left) and the fraction of metals in the ISM within the CNM (center) as a function of source energy at two different times, 20~Myr (blue) and 100~Myr (orange).
+For each of the discussed runs (from set \runonenu), Figure~\ref{ch4:fig:CGM_CNM_variance} shows the fraction of event tracer metals ejected from the galaxy (left) and the fraction of metals in the ISM within the CNM (center) as a function of source energy at two different times, 20~Myr (blue) and 100~Myr (orange).
 In the right panel, we show how the spread at each of these times varies for each event.
@@
 
-It is clear that the trends discussed thus far applies to the average behavior of events at a fixed $E_{\rm ej}$, but not for an individual event.
+It is clear that the trends discussed thus far apply to the average behavior of events at a fixed $E_{\rm ej}$, but not for an individual event.
 In addition, a higher $E_{\rm ej}$ seems to increase the minimum $f_{\rm CGM}$ and $f_{\rm CNM} / f_{\rm Disk}$ expected, but the behavior of any one event must depend on additional factors.
@@
 We place each source at regular, but arbitrary, positions in the galaxy without consideration for the local ISM conditions at injection.
-Sources are placed at the center of the galaxy ($r = 0$~pc) or at various radii (at cardinal positions at 300~pc, and 600~pc), all in the mid-place of the galaxy.
+Sources are placed at the center of the galaxy ($r = 0$~pc) or at various radii (at cardinal positions at 300~pc, and 600~pc), all in the mid-plane of the galaxy.
 Since the E46 events were likely to not self-interact, we additionally placed events at $r = 100$~pc and one event at each $r$ at about one scale height above the disk ($z = 50$~pc).
@@
 But again, the trend is weak and there is clearly still a great variance at both fixed $E_{\rm ej}$ and $r$.
-The fraction of metals in the ISM that are contained within the CNM (middle row) do not show any obvious trend at E46, but does seem to generally be lowest for the higher energy sources at the outskirts of the galaxy.
+The fraction of metals in the ISM that are contained within the CNM (middle row) does not show any obvious trend at E46, but does seem to generally be lowest for the higher energy sources at the outskirts of the galaxy.
 Finally, the radial position does seem to affect the mixing behavior.
@@
 Finally, we note no obvious trends of the spread of the metal PDFs as a function of $n$ for all but the E46 run.
-Again, the local ISM densities is likely not too dynamically relevant to the higher energy events -- hence their lack of variation with $n$ -- but this is not true for E46.
+Again, the local ISM densities are likely not too dynamically relevant to the higher energy events -- hence their lack of variation with $n$ -- but this is not true for E46.
 There is a fairly clear trend of increasing inhomogeneity in the CNM as a function of the initial $n$ in the injection region for E46, that is not present at 20~Myr, but is obvious at 100~Myr.
@@
 Although this does not help to directly account for the variation seen in the previous plots, this could provide insight into how SFR (in an averaged sense) affects the evolution of metals.
-We note that correlation with SFR is of interest not because the formation of stars by themselves, but rather the increase in feedback associated with a higher SFR (and thus a warmer / hotter ISM, greater turbulence in the ISM, and more significant outflows).
+We note that correlation with SFR is of interest not because the formation of stars by themselves affects metal evolution, but rather the increase in feedback associated with a higher SFR (and thus a warmer / hotter ISM, greater turbulence in the ISM, and more significant outflows).
 We compare these two runs in Figure~\ref{ch4:fig:SFR_comparison_CGM_CNM}, showing runs from \runonenu~in green and runs at the lower SFR, \runtwonu, in purple.
@@
 Finally, examining the last panel of Figure~\ref{ch4:fig:SFR_comparison_CGM_CNM}, it does appear that the mixing efficiency of metals for each source increases with increasing global SFR.
-In the initial evolution, all events in run \runtwonu exhibit larger abundance spreads that take longer to begin mixing substantially than their counterparts in \runonenu.
-In general, \runtwonu~abundances remains larger for the first 100~Myr.
+In the initial evolution, all events in run \runtwonu~exhibit larger abundance spreads that take longer to begin mixing substantially than their counterparts in \runonenu.
+In general, \runtwonu~abundances remain larger for the first 100~Myr.
 The differences depend on the ejection energy, with the most significant difference found in comparing the E46 runs.
@@
 
-Galactic chemical evolution is far from ``one-zone" and metal mixing is clearly neither homogeneous nor instantaneous.
-As demonstrated in our simulations published as \cite{Emerick2018b} and as found in the analytic work of \cite{KrumholzTing2018}, the properties of metal mixing in the ISM of various galaxies depends upon the characteristics of the individual sources -- namely the energy with which they eject metals into the ISM.
-This sets the thermal phase in which these metals couple to most effectively, and the volume over which they are initial injected before additional mixing by global galactic dynamics begins to dominate.
+Galactic chemical evolution is far from ``one-zone" and metal mixing is clearly neither homogeneous nor instantaneous. As demonstrated in Chapter~\ref{ch:chapter3}
+% our simulations published as \cite{Emerick2018b}
+and as found in the analytic work of \cite{KrumholzTing2018}, the properties of metal mixing in the ISM of various galaxies depend upon the characteristics of the individual sources -- namely the energy with which they eject metals into the ISM.
+This sets the thermal phase to which these metals couple to most effectively, and the volume over which they are initially injected before additional mixing by global galactic dynamics begins to dominate.
 In short, lower energy enrichment events, like those from AGB winds, mix much more slowly throughout the ISM than metals from higher energy events, like supernovae.
-As found in \cite{Emerick2018b}, this difference is still present even when accounting for the fact that AGB events are both more common and evenly distributed in the galaxy than SNe.
-In the new work discussed in this chapter, we further explore this behavior to try and determine the evolution of individual enrichment sources -- rather than just the average behavior of many sources -- and to explore how $E_{\rm ej}$, radial position in the galaxy, local ISM density, and global galaxy SFR affects the evolution of these metals.
+As found in Chapter~\ref{ch:chapter3},
+%\cite{Emerick2018b},
+this difference is still present even when accounting for the fact that AGB events are both more common and evenly distributed in the galaxy than SNe.
+In the new work discussed in this chapter, we further explore this behavior to try and determine the evolution of individual enrichment sources -- rather than just the average behavior of many sources -- and to explore how $E_{\rm ej}$, radial position in the galaxy, local ISM density, and global galaxy SFR affect the evolution of these metals.
 

### 2019-06-03 thesis/chapters/ch_chapter4.tex
edits to chapter4 - still need to fix figures

@@
 These environments can potentially be used to trace and constrain enrichment from the first stars \citep[e.g.][]{FrebelBromm2012,Ji2015,Ritter2015,Jeon2017,Hartwig2018} and have been used to place constraints on the variety of possible astrophysical sources of r-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Duggan2018,Nagasawa2018,Ojima2018}.
-It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way exhibits smaller abundance spreads, averaging over the variety of complex hydrodynamics and feedback-driven turbulence that may be driving much of the significant variance in stellar abundances seen at low metallicity.
+It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way exhibits smaller abundance spreads.
+The size of more massive galaxies reduces the relevance of stochasticity, averaging over the variety of complex hydrodynamics and feedback-driven turbulence that may be driving much of the significant vgariance in stellar abundances seen at low metallicity.
 Stochasticity, which has been shown to be important for setting the width of stellar abundance patterns in low metallicity environments of the Milky Way halo \citep[e.g.][]{Cescutti2008,Cescutti2014}, plays an even greater role in the evolution of these low mass dwarf galaxies \citep{Applebaum2018}.
@@
 \label{ch4:sec:results}
-Perhaps the three most important parameters to quantify for each enrichment event are: 1) what fraction of released metals are immediately available for star formation, 2) what fraction of metals are carried out of the galaxy in outflows, and 3) how and over what timescale do metals cool from hot phases into star forming gas.
-We discuss each of these points in Section~\ref{ch4:sec:ISM CGM}.
-In Section~\ref{ch4:sec:spreads} we go further and address the relative homogeneity of the metals retained by the ISM for each enrichment source.
+Perhaps the three most important parameters to quantify for each enrichment event are: 1) what fraction of released metals are immediately available for star formation, 2) how does this fraction evolve over time as metals cool from hot phases into star forming gas, and 3) what fraction of metals are carried out of the galaxy in outflows.
+We discuss each of these points in Section~\ref{ch4:sec:ISM CGM}, focusing on the average behavior of multiple enrichment events at fixed ejection energy.
+In Section~\ref{ch4:sec:spreads} we go further and address the relative homogeneity (over time) of the metals retained by the ISM for each enrichment source.
+Finally, in Section~\ref{ch4:sec:individual event variation} we discuss how these parameters vary with individual events, and, in Sections~\ref{ch4:sec:radial position} through ~\ref{ch4:sec:SFR}, how they vary with radial position in the galaxy, ISM properties in the event region, and global galaxy SFR.
 
@@
 Investigating the fraction of metals immediately available for star formation will require additional, high-resolution simulations of metal mixing in and around individual star forming regions.
+This will be useful for understanding stellar enrichment patterns that may arise from star formation in regions whose metal abundance patters arise directly from unmixed ejecta of a single enrichment source.
+% cite
 % add references (maybe) to high res simulation of dust production in AGB winds and SNe ???
@@
 Conducting this analysis requires measured r-process abundances for a large sample of stars in an individual dwarf galaxy.
-This is challenging for the lowest mass, most metal poor dwarf galaxies, which typically only have a few to 10 stars with measured abundances, but could be done for low mass dwarfs like Ursa Minor, and for more massive dwarfs like Carina, and Fornax \citep{Suda2017}.
+This is challenging for the lowest mass, most metal poor dwarf galaxies, which typically only have a few to 10 stars with measured abundances, but could be done for low mass dwarfs like Ursa Minor, for more massive dwarfs like Carina, and Fornax \citep{Suda2017}, and for the low-metallicity stellar halo of the Milky Way \citep[e.g.][]{Hansen2018,Sakari2018}.
 % somerthing about needing cool onezone chemical models to try and model data with many free params might be nice here.
@@
    \includegraphics[width=0.975\linewidth]{figures/ch4/II_Eej_CNM_avg}
-   \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} and Figure~\ref{ch4:fig:CGM_CNM} that demonstrates the significant variation in $f_{\rm CGM}$, $f_{\rm CNM} / f_{\rm Disk}$, and the mean-median separate at fixed injection energy.
+   \caption{A summary of the results presented in Figure~\ref{ch4:fig:CGM_CNM} and Figure~\ref{ch4:fig:mean-median} that demonstrates the significant variation in $f_{\rm CGM}$, $f_{\rm CNM} / f_{\rm Disk}$, and the mean-median separate at fixed injection energy.
 The points give the average values at each energy at two different times, while the error bars show the min/max values at each energy.

### 2019-06-03 thesis/chapters/ch_chapter1.tex
All edits complete, except some of mary's suggestions, chapter 5 figure issues, and a par needed in conclusion,

@@
 
-We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit (as discussed further in Section~\ref{ch1:sec:star formation}).
+We set the star formation density threshold to the value at which the Jeans length becomes resolved by only 4 cells in sub-200 K gas, or about 200 \ccunit~(as discussed further in Section~\ref{ch1:sec:star formation}).
 Forming stars from this gas will reduce the local density, ensuring the Jeans length is resolved.
@@
 We apply the \citet{Glover2008} three-body rate for H$_{2}$ formation and include a model for H$_2$ formation on dust, dust heating, and dust cooling following the methods in \citet{Omukai2000} and \citet{Omukai2005} as included in \texttt{Grackle}.
-However, we update the default dust to gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}.
+However, we update the default dust-to-gas ratio scaling in \texttt{Grackle} to account for the steeper scaling in low metallicity regimes ($Z \lesssim 0.1 Z_{\odot}$), using the broken power law scalings from \citet{Remy-Ruyer2014}.
 For metallicities above $\sim 0.1 Z_{\odot}$, this is equivalent to the default behavior of \texttt{Grackle}, where dust content scales linearly with metallicity.
 
-As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy} \citep{Cloudy2013} \footnote{http://www.nublado.org/} tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
+As part of the \texttt{Grackle} package, metal line cooling is modeled using pre-computed \texttt{Cloudy}\footnote{http://www.nublado.org/} \citep{Cloudy2013}  tables interpolated as a function of density, temperature, and redshift, using the \citet{HM2012} UV metagalactic background.
 As discussed in more detail in Section~\ref{ch1:sec:diffusive heating}, we account for approximate self-shielding of H and He against this UV background.
@@
 For example, low mass stars are tagged as white dwarfs (WDs) at the end of their life, which may eventually explode as a Type Ia SN (discussed below), after which they persist as massless tracer particle remnants.
-Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a four-cell region at the highest level of refinement.
+Finally, each star is marked as a ``must refine'' particle, requiring that it be surrounded by a $4^3$ region at the highest level of refinement.
 This ensures that both stellar winds and SNe feedback are maximally resolved, and that any ejected yields are deposited over a consistent physical scale throughout the simulation.
@@
 \label{eq:PE}
-\Gamma_{\rm pe} = (1.3 \times 10^{-24} \rm{erg~s^{-1}~cm^{-3}})\, \epsilon n_{\rm H} G_{\rm eff} D
+\Gamma_{\rm pe} = (1.3 \times 10^{-24} \rm{erg~s^{-1}~cm^{-3}})\, \epsilon_{\rm PE} n_{\rm H} G_{\rm eff} D
 \end{equation}
-where $\epsilon$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust-to-gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
+where $\epsilon_{\rm PE}$ is an efficiency factor that depends on $G_{\rm{o}} T^{1/2} /n_{\rm{e}}$, the attenuated local FUV flux \begin{equation} G_{\rm eff} = G_{\rm o}~\exp(-1.33\times10^{-21}~D~N_{\rm H}), \end{equation} $D$ is the dust-to-gas ratio, normalized to the solar value, and $G_{\rm o}$ is the local FUV flux normalized to the solar neighborhood \citep{Habing1968}.
 Aside from a different treatment of $D$ and the attenuation, both discussed below, this is equivalent to the method used in \citet{Hu2016,Hu2017}.
@@
 
-Properly computing $\epsilon$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
+Properly computing $\epsilon_{\rm PE}$ in Eq.~\ref{eq:PE} requires an accurate account of the electron number density $n_e$.
 This is non-trivial in dense, neutral regions where $n_e$ is dominated by contributions from carbon, dust, and PAH ionizations.
 Our chemical network only includes contributions from H, He, and H$_2$ to n$_e$.
-Instead, we use a power-law fit of $\epsilon$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon = 0.0148n_{\rm{H}}^{0.235}$.
-%This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
+Instead, we use a power-law fit of $\epsilon_{\rm PE}$ as a function of $n_{\rm H}$ from the \citet{Wolfire2003} model of $\Gamma_{\rm{Pe}}$ in the solar neighborhood (see Figure 10b of that work); we adopt $\epsilon_{\rm PE} = 0.0148n_{\rm{H}}^{0.235}$.
+This is a more accurate model than adopting a constant efficiency (Matthew Smith, private comm.).
+% This is a compromise between adoption of a constant efficiency, as in \citet{Forbes2016}, and a more detailed model with more detailed non-equilibrium chemistry \citet[e.x.][]{Hu2016}.
 
@@
 Although simple to measure in simulations, these quantities are challenging to directly compare to observations.
-We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citet[see ][]{Roychowdhury2014}.
+We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs \citep[see ][]{Roychowdhury2014}.
 We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the area of the disk within the radius of the outermost star formed within the previous 10 Myr.
@@
 This result is consistent with galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics \citep[see ][ and references therein]{NaabOstriker2017} and with the demonstration by \citet{Li2005} that the Kennicutt-Schmidt law can be reproduced by gravitation acting on an isothermal disk.
-The net result of the complex interactions of heating, cooling , chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.
+The net result of the complex interactions of heating, cooling, chemistry, and feedback physics on star formation is to offset to a level not too dissimilar to more simple simulations considering gravity alone.
 
@@
 It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium.
-While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
+While this is very challenging to determine observationally for dwarf galaxies at this mass, cosmological simulations of an $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}.
 We find 5.3\% of all metals lie within 1 kpc of the center of our galaxy, 24.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 51\% outside $R_{\rm vir}$.

### 2019-06-03 thesis/chapters/ch_conclusion.tex
All edits complete, except some of mary's suggestions, chapter 5 figure issues, and a par needed in conclusion,

@@
 
-This \dissertation has focused on building an understanding of galactic chemical evolution from the assumption that the same feedback processes that regulate star formation and drive galactic winds in galaxies also play a fundamental role in their metal enrichment.
+This \dissertation has focused on building an understanding of galactic chemical evolution with the point of view that the same feedback processes that regulate star formation and drive galactic winds in galaxies also play a fundamental role in their metal enrichment.
 It is understood that stellar feedback plays an important role in driving metals out into the CGM and beyond in galaxies, but the exact coupling of metals to galactic winds is not well understood.
@@
 In order to address these outstanding issues in galactic evolution, we developed a new model for galactic chemical evolution that -- for the first time in galaxy-scale simulations -- follows star particles as individual stars along with their detailed feedback and metal yields.
-As detailed in Chapter~\ref{ch:chapter2} we use the AMR hydrodynamics code \textsc{Enzo}, we produce a set of simulations using this model of an idealized, isolated low-mass dwarf galaxy ($M_{\rm gas} \sim 10^{6}$~M$_{\odot}$, $M_{\rm halo} \sim 3 \times 10^{9}$~M$_{\odot}$) embedded in a static dark matter potential.
+As detailed in Chapter~\ref{ch:chapter2} we use the AMR hydrodynamics code \textsc{Enzo} to produce a set of simulations using this model of an idealized, isolated low-mass dwarf galaxy ($M_{\rm gas} \sim 10^{6}$~M$_{\odot}$, $M_{\rm halo} \sim 3 \times 10^{9}$~M$_{\odot}$) embedded in a static dark matter potential.
 Using a detailed model for gas chemistry and radiative cooling, we follow the evolution of this galaxy and its multi-phase ISM as it forms stars, depositing individual star particles sampled over 1 to 100 M$_{\odot}$.
@@
 In addition to destroying cold gas in star forming regions, this acts to dramatically reduce the typical ISM densities in which SNe explode, increasing their impact.
-While often invoked as a source of feedback, modeling stellar radiation in galaxies in detail can be computationally expensive, with a variety of approximate methods available to reduce this expense.
+Modeling stellar radiation in galaxies in detail can be computationally expensive, with a variety of approximate methods available to reduce this expense.
 In our simulations we track the ionizing radiation from massive stars accurately using an adaptive ray-tracing radiative transfer method with sufficient resolution to capture the HII regions from individual stars.
-In Chapter~\ref{ch:chapter2} we demonstrate that stellar ionizing radiation dramatically reduces the star formation rate and generally increases the effectiveness of galactic winds at our low-mass dwarf galaxy simulations.
+In Chapter~\ref{ch:chapter2} we demonstrate that stellar ionizing radiation dramatically reduces the star formation rate and generally increases the effectiveness of galactic winds in our low-mass dwarf galaxy simulations.
 
@@
 Stellar radiation at larger distance scales is important for carving out diffuse channels of gas in the ISM and into the CGM of our dwarf galaxy through which SNe can effectively blow out mass and metals from the ISM.
-This suggests that -- at least in low mass dwarf galaxies -- localized approximations of radiation feedback are likely insufficient to capturing the full effects of stellar radiation.
+This suggests that -- at least in low mass dwarf galaxies -- localized approximations of radiation feedback are likely insufficient for capturing the full effects of stellar radiation.
 
@@
 Indeed, this is observed in the stellar abundance patterns of dwarf galaxies in the Local Group \citep{Suda2017}, but it remains to be seen if this is a conclusive signature of these mixing differences or perhaps is due to larger differences in star-to-star metal yields for these elements.
-Finally, we were able to characterize the metal mass fraction PDFs for each element across each phase of the ISM, and found that each were generically well-fit by a combined log-normal PDF with a power-law tail towards higher metal mass fractions.
+Finally, we were able to characterize the metal mass fraction PDFs for each element across each phase of the ISM, and found that they generically well-fit by a combined log-normal PDF with a power-law tail towards higher metal mass fractions.
 We hope that this characterization lends itself well to developing a physically-motivated semi-analytic prescription for stellar abundance spreads to be used in semi-analytic (and one-zone) models of galactic chemical evolution.
@@
 We investigate other possible factors, including radial position, global galaxy SFR, and local ISM density, and find that the global galaxy SFR has the greatest effect on the mixing and ejection behavior of each metal, particularly for lower energy events.
-Whiles these results suggest that these behavioral differences can be accounted for in an average sense, the full picture is subject to substantial stochasticity based purely on the randomness with which when and where different events occur in a galaxy.
+While these results suggest that these behavioral differences can be accounted for in an average sense, the full picture is subject to substantial stochasticity based purely on the randomness with which both when and where different events occur in a galaxy.
 Abundances associated with rare enrichment sources -- such as the r-process enrichment candidates -- which may only occur once (if at all) in the lowest mass dwarf galaxies should therefore exhibit the most significant galaxy-to-galaxy abundance variations for galaxies at fixed stellar mass.
@@
 In future work, we plan to implement a two-phase model like that in \cite{SchonrichWeinberg2019} that includes parameters for how each metal first enters the hot and cold phases, how each metal mixes between the two phases, and a stochastic mixing-zone method as used in \cite{Cescutti2008}.
-With these additions, we will: 1) explore how these physics manifest themselves in galaxies with a wide range of star formation and halo properties, 2) use these insights to begin to match observed stellar abundance patterns mass dwarf galaxies, 3) make predictions for expected multi-element abundances spreads in dwarf galaxies for comparison to future observations in upcoming surveys, and 4) better constrain the relative importance of stochastic sampling of the IMF and inhomogeneous mixing in setting these abundance spreads.
+With these additions, we will: 1) explore how these physics manifest themselves in galaxies with a wide range of star formation and halo properties, 2) use these insights to begin to match observed stellar abundance patterns in low-mass dwarf galaxies, 3) make predictions for expected multi-element abundance spreads in dwarf galaxies for comparison to future observations in upcoming surveys, and 4) better constrain the relative importance of stochastic sampling of the IMF and inhomogeneous mixing in setting these abundance spreads.
 In addition, we can more easily use this model to explore a wide variety of nucleosynthetic yield tables to better constrain the -- highly uncertain -- yields themselves.
+These insights can be used to improve more complex chemical evolution models that account for the cosmological and hierarchical evolution of galaxies over time.
 This is a particularly exciting tool that can be used to better constrain the sources of r-process enrichment in low mass dwarf galaxies.
+
+% Write simulation "next steps" here 1) cosmological, 2) feedback variance

### 2019-06-10 thesis/chapters/ch_chapter4.tex
Bugfix with extra sub in subsection

@@
 \includegraphics[width=0.45\linewidth]{figures/ch4/HNE1_enrichment_evolution_average_CGM}
-\caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines), the galaxy's disk (black, dashed), and the CGM (black, solid) as averaged across all events at a given $E_{\rm ej}$.
-The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases (colored lines) sum to the black, solid line.}
+\caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines; CNM: dark blue, WNM: light blue, WIM: orange, HIM: red), the galaxy's disk (black, dashed), and the CGM (black, solid) as averaged across all events at a given $E_{\rm ej}$.
+The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases sum to the black, dashed line.
+}
 \label{ch4:fig:ISM_CGM}
@@
 
-\subsubsection{Variation with SFR}
+\subsection{Variation with SFR}
 \label{ch4:sec:SFR}

### 2019-06-10 thesis/chapters/ch_conclusion.tex
draft of next steps for feedback physics comparison

@@
 
+In addition, this work can be readily extended to further investigate how feedback governs the evolution of dwarf galaxies.
+We have already produced a suite of comparison simulations at a factor two lower resolution (3.6~pc) than our fiducial resolution, turning on and off each individual feedback process to understand the significance and characterize the mechanism by which each operates to regulate star formation, drive galactic winds, and govern chemical evolution.
+The feedback tested here includes supernovae, stellar ionizing radiation, photoelectric heating, Lyman-Werner radiation, and radiation pressure.
+The suite contains simulations including ``all-but-one" of each process, in addition to several combinations where multiple effects are excluded, and a set where the effectiveness of radiation pressure is artificially increased and decreased.
+Comparing the evolution of these dwarfs to our fiducial simulations presented in this \dissertation will improve our understanding of these processes, building upon previous works that have conducted similar studies in more massive dwarf galaxies \citep{Hu2016,Hu2017,Forbes2016,Hopkins2018}.
+
 % Write simulation "next steps" here 1) cosmological, 2) feedback variance

### 2019-06-10 thesis/chapters/ch_chapter4.tex
typos and small edits

@@
 \caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines; CNM: dark blue, WNM: light blue, WIM: orange, HIM: red), the galaxy's disk (black, dashed), and the CGM (black, solid) as averaged across all events at a given $E_{\rm ej}$.
-The fractions are all normalized to the total amount of metals initially injected in each event, and the individual ISM phases sum to the black, dashed line.
+The fractions are all normalized to the total amount of metals initially injected in each event.
+The individual ISM phases sum to the black, dashed line.
 }
@@
 We summarize the source-averaged results for all enrichment events in runs \runone E46, \runone E49, \runone E50, \runone E51, and \runone E52 in Figure~\ref{ch4:fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid).
-These plots show a clear, immediate trend across $E_{\rm ej}$ for all lines in the figure, but the differences are most striking for the ISM (black, dashed), CGM (black, solid) lines.
+These plots show a clear, immediate trend across $E_{\rm ej}$ for all lines in the figure, but the differences are most striking for the ISM (black, dashed) and CGM (black, solid) lines.
 In Chapter~\ref{ch:chapter3}

### 2019-06-10 thesis/chapters/ch_conclusion.tex
typos and small edits

@@
 This \dissertation has focused on building an understanding of galactic chemical evolution with the point of view that the same feedback processes that regulate star formation and drive galactic winds in galaxies also play a fundamental role in their metal enrichment.
-It is understood that stellar feedback plays an important role in driving metals out into the CGM and beyond in galaxies, but the exact coupling of metals to galactic winds is not well understood.
+It is understood that stellar feedback plays an important role in driving metals out into the CGM around galaxies and beyond, but the exact coupling of metals to galactic winds is not well understood.
 This is in part because how metals mix within a multi-phase ISM to eventually be swept up in galactic outflows or mix within cold, star forming gas is not well constrained.
@@
 
-In ongoing work we are extending these methods by implementing them in cosmological simulations of UFD galaxy evolution.
+%In ongoing work we are extending these methods by implementing them in cosmological simulations of UFD galaxy evolution.
 Our detailed model tracking the feedback and yields from individual stars will build substantially upon recent works investigating metal enrichment at high redshift and in UFDs and their progenitors \citep[e.g.][]{Ritter2015,Jeon2017,Corlies2018,Wheeler2018,Agertz2019}.
@@
 
-Finally, as part of this \dissertation we additionally produced a significant set of companion simulations at $2 \times$ lower resolution (3.6~pc instead of 1.8~pc) turning on and off each independent feedback process (ionizing radiation, radiation pressure, LW and FUV radiation, and supernovae).
+%Finally, as part of this \dissertation we additionally produced a significant set of companion simulations at $2 \times$ lower resolution (3.6~pc instead of 1.8~pc) turning on and off each independent feedback process (ionizing radiation, radiation pressure, LW and FUV radiation, and supernovae).
 With these runs, we sought to build upon recent works examining the various effects of each stellar feedback process in driving the evolution of low mass dwarf galaxies \citep{Hu2016,Hu2017,Hu2018,Forbes2016}.
@@
 In addition, this work can be readily extended to further investigate how feedback governs the evolution of dwarf galaxies.
-We have already produced a suite of comparison simulations at a factor two lower resolution (3.6~pc) than our fiducial resolution, turning on and off each individual feedback process to understand the significance and characterize the mechanism by which each operates to regulate star formation, drive galactic winds, and govern chemical evolution.
+We have already produced a suite of comparison simulations at a factor two lower resolution (3.6~pc) than our fiducial resolution, turning on and off each individual feedback process to understand the significance and characterize the mechanism by which each operates to regulate star formation and drive galactic winds.
 The feedback tested here includes supernovae, stellar ionizing radiation, photoelectric heating, Lyman-Werner radiation, and radiation pressure.
@@
 Comparing the evolution of these dwarfs to our fiducial simulations presented in this \dissertation will improve our understanding of these processes, building upon previous works that have conducted similar studies in more massive dwarf galaxies \citep{Hu2016,Hu2017,Forbes2016,Hopkins2018}.
+Our unique contribution to this field will be in examining how these processes change how metals are retained / ejected by galactic winds and mix within the ISM.
+
+Finally, in ongoing work we are implementing these methods in zoom-in cosmological simulations of UFD galaxy evolution.
+Our detailed model tracking the feedback and yields from individual stars will build substantially upon recent works investigating metal enrichment at high redshift and in UFDs and their progenitors \citep[e.g.][]{Ritter2015,Jeon2017,Corlies2018,Wheeler2018,Agertz2019}.
+This work includes additional improvements to the simulations presented in this \Dissertation, including a model for Pop III star formation and chemical enrichment adapted from \cite{Wise2012a}, a new IMF sampling scheme that allows us to follow very low mass stars ($M_* \lesssim 2$~M$_{\odot}$) -- which have no significant feedback or metal enrichment, but are important long-lived tracers of galactic chemical enrichment -- aggregated together into a single particle during each star formation event, improvements to the numerical implementation to ease memory consumption in these significantly larger simulations, and new metal tracer fields to follow the contribution of AGB, core collapse SNe, Type Ia SNe, and PopIII stars to the total metal content of each cell independently.
+This will provide a more direct, fundamental test of the underlying physics that governs galactic evolution and produce simulated galaxies that can be more readily compared to observations of nearby dwarf galaxies.
 

### 2019-06-13 thesis/abstract.tex
abstract edits

@@
 %In this \thesis
-we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and the multi-channel stellar feedback and multi-element metal yields associated with each star.
+we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and their associated multi-channel stellar feedback and multi-element metal yields.
 We developed these simulations to probe the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies.
@@
 
-Our simulations follow the evolution of an idealized, isolated low mass dwarf galaxy ($M_{\rm vir} \sim 10^{9}$~M$_{\odot}$) over $\sim$ 500 Myr timescales using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
+Our simulations follow the evolution of an idealized, isolated, low mass dwarf galaxy ($M_{\rm vir} \sim 10^{9}$~M$_{\odot}$) for $\sim$ 500 Myr using the adaptive mesh refinement hydrodynamics code \textsc{Enzo}.
 We implemented a new star formation routine which deposits stars individually from 1~M$_{\odot}$ to 100~M$_{\odot}$.
@@
 
-Using these simulations, we investigate the role that stellar radiation feedback plays in the evolution of low mass galaxies.
+Using these simulations, we investigate the role that stellar radiation feedback plays in the evolution of low mass dwarf galaxies.
 % a fiducial, full-physics simulation, second, a simulation with ionizing radiation restricted to the region immediately around massive star particles, and third, a simulation with no ionizing radiation feedback.
 I
-In the regime of low mass dwarf galaxies, we find that the local effects of stellar radiation (within $\sim$ 10~pc of the massive, ionizing source star) act to regulate star formation by rapidly destroying cold, dense gas around newly formed stars.
+In this regime, we find that the local effects of stellar radiation (within $\sim$ 10~pc of the massive, ionizing source star) act to regulate star formation by rapidly destroying cold, dense gas around newly formed stars.
 For the first time, we find that the long-range radiation effects far from the birth sites are vital for carving channels of diffuse gas in the ISM which dramatically increase the effect of supernovae.

### 2019-06-17 thesis/chapters/ch_chapter4.tex
Correcting appendix figure numbering
edits

@@
 It is likely that chemical enrichment in more massive, metal rich systems with ongoing star formation like the Milky Way exhibits smaller abundance spreads.
-The size of more massive galaxies reduces the relevance of stochasticity, averaging over the variety of complex hydrodynamics and feedback-driven turbulence that may be driving much of the significant vgariance in stellar abundances seen at low metallicity.
+The size of more massive galaxies reduces the relevance of stochasticity, averaging over the variety of complex hydrodynamics and feedback-driven turbulence that may be driving much of the variance in stellar abundances seen at low metallicity.
 Stochasticity, which has been shown to be important for setting the width of stellar abundance patterns in low metallicity environments of the Milky Way halo \citep[e.g.][]{Cescutti2008,Cescutti2014}, plays an even greater role in the evolution of these low mass dwarf galaxies \citep{Applebaum2018}.
@@
 \renewcommand\thesection{\thechapter.\Alph{section}}
+\counterwithin{figure}{section}
 

### 2019-06-17 thesis/abstract.tex
removing comments

@@
 \end{center}
-Motivated by the desire to investigate two of the largest outstanding problems in galactic evolution -- stellar feedback and galactic chemical evolution --
-%In this \thesis
-we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and their associated multi-channel stellar feedback and multi-element metal yields.
+Motivated by the desire to investigate two of the largest outstanding problems in galactic evolution -- stellar feedback and galactic chemical evolution -- we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and their associated multi-channel stellar feedback and multi-element metal yields.
 We developed these simulations to probe the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies.
@@
 Using these simulations, we investigate the role that stellar radiation feedback plays in the evolution of low mass dwarf galaxies.
-% a fiducial, full-physics simulation, second, a simulation with ionizing radiation restricted to the region immediately around massive star particles, and third, a simulation with no ionizing radiation feedback.
-I
 In this regime, we find that the local effects of stellar radiation (within $\sim$ 10~pc of the massive, ionizing source star) act to regulate star formation by rapidly destroying cold, dense gas around newly formed stars.

### 2019-06-17 thesis/chapters/ch_introduction.tex
Fixing figure references

@@
 
-The dominant origin of r-process enrichment is highly uncertain, though (as indicated in Figure~\ref{fig:periodic table}) possible channels include NS-NS mergers, neutron star - black hole mergers, neutrino driven winds in core collapse SNe, and exotic SNe, such as magnetic, jet-driven SNe, collapsars, hypernovae, and long-duration gamma-ray bursts \citep[see ][ for recent reviews]{Frebel2018, Cowan2019}.
+The dominant origin of r-process enrichment is highly uncertain, though (as indicated in Figure~\ref{intro:fig:periodic table}) possible channels include NS-NS mergers, neutron star - black hole mergers, neutrino driven winds in core collapse SNe, and exotic SNe, such as magnetic, jet-driven SNe, collapsars, hypernovae, and long-duration gamma-ray bursts \citep[see ][ for recent reviews]{Frebel2018, Cowan2019}.
 Eu is the most commonly used (and easy to observe) unambiguous observational tracer of r-process enrichment; Ba is also often studied as a tracer, but requires care due to the significant contribution from s-process enrichment.

### 2021-01-19 XSEDE-April2020-Mar2021/main.tex
backup

\documentclass[12pt]{article} % font size here: some require 11 or 12 point
\usepackage{setspace}
\usepackage{fancyvrb}
\usepackage{epsfig}
\usepackage{fullpage}
\usepackage[small,compact]{titlesec}
\usepackage{times}
\usepackage{enumitem}
\usepackage{wrapfig}
\setlength{\topmargin}{+0.0in}   %%%%%%%%% this is hacked (from +.0.1in) so that it looks right when converted.
\setlength{\oddsidemargin}{-0.0in}
\setlength{\evensidemargin}{-0.0in}
\setlength{\textheight}{9.0in}
\setlength{\textwidth}{6.5in}
\usepackage[margin=1.0in,headheight=0pt,footskip=20pt,headsep=0.2in]{geometry}
\usepackage{natbib}
% ----------------------------------------------------
\usepackage{setspace}
\singlespacing
%\onehalfspacing % may need to switch to single spacing

\usepackage{natbib}
\usepackage{color}
\bibliographystyle{apj}
\newcommand{\apj}{ApJ}
\newcommand{\apss}{Astrophysics and Space Science}
\newcommand{\aj}{AJ}
\newcommand{\apjl}{ApJL}
\newcommand{\mnras}{MNRAS}
\newcommand{\apjs}{ApJS}
\newcommand{\pasp}{PASP}
\newcommand{\araa}{ARA\&A}
\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\pasj}{PASJ}
\newcommand{\prd}{Phys. Rev. D}
\newcommand{\nat}{Nature}
\newcommand{\nar}{New Astronomy Review}
\newcommand{\ao}{Applied Optics}
\newcommand{\physrep}{Physics Reports}
\newcommand{\etal}{et al}
\def\subsun{\mbox{$_{\odot}$}}
\def\lesssim{\mathrel{\hbox{\rlap{\hbox{%
 \lower4pt\hbox{$\sim$}}}\hbox{$<$}}}}
\def\gtrsim{\mathrel{\hbox{\rlap{\hbox{%
 \lower4pt\hbox{$\sim$}}}\hbox{$>$}}}}
\RequirePackage{natbib}
%\usepackage{setspace}
\setlength{\bibsep}{0.0pt}
\newenvironment{itemize*}%
{\begin{itemize}%
  \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
{\end{itemize}}

\newenvironment{enumerate*}%
{\begin{enumerate}%
  \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
{\end{enumerate}}

\usepackage{fancyhdr}
\pagestyle{fancy}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Dwarf Galaxies with Individual Stars}
\rhead{}

%\usepackage[pagestyles]{titlesec}
%\newpagestyle{mystyle}{\sethead{}{}{Name -- Number}\setfoot{}{\thepage}{}}
%\pagestyle{mystyle}

\title{\vspace{-5ex} \Large Galactic Chemical Evolution in the Smallest Galaxies with Individual Stars
       \vspace{-2ex}}
\author{\small PI: Andrew Emerick, Carnegie Observatories and California Institute of Technology, Pasadena, CA \\
\small co-I: Alex Ji, Carnegie Observatories, Pasadena, CA \\
\small co-I: John Wise, Georgia Institute of Technology, Atlanta, GA
}
%\author{Co-I:}
\date{\vspace{-5ex}}
\begin{document} \thispagestyle{empty}

% Star-by-Star Stellar Feedback and Chemical Evolution in Dwarf Galaxies

\maketitle

\begin{changemargin}{0.75cm}{0.75cm} 
\begin{center}\centering \textbf{Summary}\end{center}

We request \textbf{XXX SUs} on the TACC machine Stampede2 utilizing SKX nodes to run the first ever set of cosmological hydrodynamics simulations following the chemical evolution of the first galaxies with individual star particles using the well-tested code \textsc{Enzo}. We request \textbf{7.3 TB} of archival storage on the TACC Ranch system for the data products from this run.
\end{changemargin}

\section{Introduction}
The early formation histories of [ultra-faint?] dwarf galaxies probe some of the most important and extreme regimes of galaxy formation, nucleosynthesis, and cosmology.

Stellar abundances are the key for understanding the early formation histories of dwarf galaxies.

\textbf{In the past decade, observations of stellar abundances in dwarf galaxies have outpaced models for these abundances.}

We currently tend to model mean trends but not the scatter, because scatter is hard and requires simulations.

For the early history of dwarf galaxies, it is now computationally feasible to...

Present-day stellar abundance patterns are tracers of the integrated history of galactic evolution. Ongoing and upcoming observations of detailed stellar abundance patterns, including SEGUE \citep{Yanny2009}, RAVE \citep{Kunder2017}, APOGEE \citep{Anders2014}, APOGEE-2 \citep{Majewski2016}, GALAH \citep{Buder2018}, and the Pristine survey \citep{Starkenburg2017} have obtained an unprecedented number of stars with detailed, multi-element abundances in both the Milky Way and dwarf galaxies in the Local Group. This is in addition to the ongoing work obtaining detailed abundances of $\sim$100 or more stars by multiple groups \cite[e.g.][ (need more!) ]{Hill2019} in low-mass dwarf galaxies in the Local Group. This allows us to directly probe the information-rich scatter in stellar abundance patterns across a range of environments and at low metallicities where the scatter is a more sensitive tracer of underlying galaxy evolution physics. These abundance patterns are the convolution of a galaxy's accretion and merger history, star formation history, internal dynamic structure, mixing timescales and efficiencies in the interstellar medium (ISM), stellar nucleosynthesis, and the effectiveness of stellar feedback in driving metal-rich galactic outflows. \textbf{last sentence}

The quality of these observations are rapidly outpacing our ability to simulate them, in large part because constructing such a model is complex.  Since most metals are released through stellar winds, supernovae, or other similar energetic events, this model requires a detailed understanding of the role of stellar feedback in driving galactic evolution, a current open question in our field.  In addition, models of galactic chemical evolution often lack an exact description for how metals mix within a multi-phase interstellar medium (ISM) and enrich future populations of stars.

\textbf{motivate need to study high-z galaxy formation and evolution and connection to UFDs and low mass dwarfs}

Since \cite{Tinsley1980}, its been understood that the evolution of stellar abundance ratios as a function of metallicity (or, commonly, [Fe/H]) traces different chemical enrichment timescales. The most common example is the ``knee" feature seen in plots of $[\alpha$/Fe] vs. [Fe/H] which represents the transition from core collapse supernova dominant enrichment (high $[\alpha$/Fe]) to significant contributions of Type Ia SNe (Fe, but no $\alpha$). Similar trends can be expected for elements of different nucleosynthetic channels, such as the s-process in AGB stars, and elements with trends in yields as a function of stellar mass. Each of these probe unique timescales in chemical evolution history. However, extracting information about these timescales from stellar abundances is complicated by the fact that the details of galaxy evolution -- stellar feedback, star formation rate, IMF slope, and efficiencies of metal mixing in the ISM -- drives significant scatter in elemental abundances ratios that makes interpreting any evolution quantitatively nearly impossible.

Doing this requires the type of simulations proposed here whereby the details of galaxy evolution are resolved to high-resolution, including star formation, stellar feedback, turbulent mixing, the formation of a multi-phase ISM, and a multi-element chemical evolution model that follows the abundances from individual stars. \textbf{These types of simulations have not yet been performed}. By following detailed chemical enrichment in the early Universe in our simulations, we will be able to unlock the connection between stellar abundances in Local Group ultrafaint dwarf galaxies and physics of galaxy evolution in the early Universe.

%\textbf{Emphasize need for sims with multi-channel enrichment, including mass-dependent yields from SN and AGB channels}

\subsection{Key Scientific Questions and Goals}

We provide a summary of the key scientific questions addressed by the simulations proposed in this project. These simulations are uniquely suited to address each of these issues, and the use of Stampede-2 is necessary to carry these out:

\begin{itemize}
    \item 
\end{itemize}

\section{Proposed Computational Method and Model}

Our simulations will be carried out using the publicly available cosmological adaptive mesh refinement (AMR) hydrodynamics and N-body code \textsc{Enzo} \citep{Enzo2014,Enzo2019}. \textsc{Enzo} is well-tested and has been used extensively in a variety of applications including studies of the ISM and molecular clouds \citep[e.g.][]{Slyz2005,TaskerBryan2008,Jin2017}, the intergalactic medium \citep[e.g.][]{BryanMachacek2000,FangBryan2001,Tonnesen2017}, the first stars and galaxies \citep[e.g.][]{Wise2012a,Oshea2015,Regan2019}, and the roles of stellar feedback in galactic evolution \citep[e.g][]{SalemBryan2014,Goldbaum2016,Forbes2016,Li2019}. We discuss our proposed simulations and relevant methods below, and include a more detailed description of the grid hierarchy and parallelization strategy (including load balancing) in the scaling document.

\subsection{Initial Conditions}

We build upon the work in \citep{Wise2012a,WiseAbel2012,Wise2014,Corlies2018}, combined with the new star formation and stellar feedback model from \citep{Emerick2019a} following individual star particles, described below. We will use the same set of cosmological initial conditions used in \citep{Wise2012a} to follow the formation of the first generation of dwarf galaxies. The simulation domain is a 1 Mpc (co-moving) box with a root-grid resolution of 256$^3$ and dark matter mass resolution of 1840~M$_{\odot}$. The simulation will be run with a maximum of 12 levels of additional refinement for a maximum resolution of 1~pc (co-moving) using a super-Lagrangian refinement scheme \citep{OsheaNorma2008} to refine on baryon overdensities of $3\times 2^{-0.2l}$, where $l$ is the refinement level, dark matter overdensities of 3, and resolving the local Jeans length by at least 4 cells. In addition, we ensure that stellar feedback, metal enrichment, and metal mixing is well-resolved by forcing refinement in a 4-zone sphere around each star particle with active stellar feedback to at least a co-moving resolution of 4~pc. The simulation will begin at redshift z = 130 and we plan to run the simulation until a redshift of z = 7 ($\sim$ 750 Myr), capturing the evolution of dark matter halos between 10$^6$ and 10$^9$ M$_{\odot}$ with anticipated stellar masses between 10$^3$ and 10$^6$ M$_{\odot}$.

\subsection{Hydrodynamics and Gravity}

For this work we employ a direct-Eulerian piecewise parabolic method \citep{ColellaWoodward1984, Bryan1995} to solve the equations of hydrodynamics. This is an explicit, higher-order accurate version of Godunov's method for ideal gas hydrodynamics that uses spatially third-order accurate piecewise parabolic monotonic interpolation. Shock capturing is handled with a nonlinear Riemann solver. This base method is extended to multiple dimensions using directional splitting, resulting in a final algorithm that is second-order accurate in space and time; we explicitly conserve mass, linear momentum, and energy \citep{Hawley1984, NormanWinkler1986}. We use a dual energy formalism to track the total energy and thermal energy separately, preventing substantial numerical errors that arise when the thermal energy is very small compared to the total energy. We default to using the two-shock approximate Riemann solver \citep{Toro1997}, with progressive fallback to more diffusive approximate Riemann solvers when higher order methods produce negative densities or energies \citep{LemasterStone2009}. 
%In this situation, we fall back to either the Harten-Lax-van Leer (HLL) \citep{Toro1997} method with contact discontinuities -- a three-wave, four-state solver -- or the basic HLL -- a two-state, three-wave solver. 
The hydrodynamics time step is set by the Courant-Friedrichs-Levy (CFL) condition for stability, scaling linearly with cell size ($\Delta x$) and inversely proportional to the sum of the bulk velocity and sound speed in each cell in a given direction. 
%The multidimensional CFL limited time step is the harmonic average of the limiting CFL time step in each dimension.

Gas self-gravity and the gravitational forces of the massive star particles are computed together to compute the gravitational acceleration on each cell and particle. On the root grid, we use a cloud-in-cell (CIC) method \citep{HockneyEastwood1988} to map particles to a time-centered density field, including the effects of particles across sub-grids and neighboring domains; a similar time-centered density field is computed for the baryons in each grid cell. The gravitational potential is solved for using a fast Fourier transform (FFT) in isolated boundary conditions \citep{James1977}; accelerations are computed with a two-point centered difference scheme using the transformed real-space potential. For accuracy on sub-grids, we employ the seven-point, second-order finite difference approximation to Poisson's equation, solving the given Dirichlet boundary conditions with multigrid relaxation. Unwanted oscillations and errors across grids are reduced using expanded buffer zones around each grid, coupled with an iterative relaxation process between sibling grids. Particle accelerations are computed from the grid potential using linear CIC mapping. \texttt{Enzo} employs the particle-mesh N-body method from \cite{HockneyEastwood1988} to evolve the collisionless star particles with an effective force resolution of approximately 2$\Delta x$.

\subsection{Star Formation}

We outline the details of our physics models here, which includes some updates designed specifically for this project since their first development as described in detail in \cite{Emerick2019a}. Star formation occurs stochastically in cells containing cold, dense gas (10$^3$ cm$^{-3}$, $T < 500 K$)) with a converging flow ($\nabla \cdot v < 0$) following a Schmidt law whereby the star formation rate density is given by $\rho_* = \epsilon_{\rm ff} \frac{\rho_g}{t_{\rm ff}}$, where $\rho_g$ is the gas density, $t_{\rm ff}$ is the local gas free-fall time, and $\epsilon_{\rm ff}$ is the efficiency per free-fall time, which we set to 1. In these cells, we stochastically form stars by computing the probability that 200~M$_{\odot}$ of gas will be turned into stars in a given time step. If this occurs, we random sample the stellar initial mass function, depositing individual star particles until at least 200~M$_{\odot}$ of stars form.

We follow both Pop III star formation and Pop II star formation, with the former occurring only in cells with $Z < 10^{-4} Z_{\odot}$ and $f_{\rm H_2} > 5\times 10^{-4}$ and the latter in metal enriched cells with $Z > 10^{-4} Z_{\odot}$. We adopt a \cite{Salpeter1955}-like IMF for Pop III star formation  above 100~M$_{\odot}$ with an exponential cutoff below this mass and a minimum and maximum particle mass of 11~M$_{\odot}$ and maximum mass of 300~M$_{\odot}$. Pop II star formation follows a \cite{Kroupa2001} IMF with a minimum and maximum mass of 0.08~M$_{\odot}$ and 100~M$_{\odot}$. Upon formation, the stellar abundances of each particle are written to file adopting the local gas abundances from which the stars form.

To reduce computational expense, we merge all Pop II star particles below 2~M$_{\odot}$ in each star forming cell into a single particle. These stars do not have significant feedback or metal enrichment on the timescale of these simulations ($\sim$ 1~Gyr), but still need to be followed as they are the key tracers of stellar abundances in present-day low mass dwarf galaxies.

\subsection{Stellar Feedback}
\textbf{Need to decide what we're doing with PISN. Include them or no? Interesting in both cases, but not sure what would be best?}

We follow a multi-channel stellar feedback prescription capturing stellar winds from massive stars and AGB stars, core collapse and Type Ia supernova, ionizing radiation, Lyman-Werner radiation, and FUV radiation. For both stellar winds and supernovae, mass and energy are deposited into 3-zone radius spherical regions around each star particle. We assume Pop III stars between 11 -40 M$_{\odot}$ and 140 - 260 M$_{\odot}$ and Pop II stars between 8 - 25 M$_{\odot}$ explode as core collapse supernovae at the end of their lives with 10$^{51}$~erg of thermal energy. Stars above 25~M${\odot}$ outside these ranges are assumed to direct collapse with no energy or mass ejection. Stellar surface temperature, surface gravity, and radius (which help set the radiative properties of stars), and lifetimes are adopted from the PARSEC \citep{Bressan2012,Tang2014} stellar evolution grid.

While stellar winds are potentially an important source of pre-SN feedback \citep{Agertz2013}, their effects are sub-dominant to ionizing radiation. To reduce the computational expense of continually evolving fast ($\sim 10^{3} \rm{km} \rm{s}^{-1}$), hot ($T > 10^{6}$~K) gas for the lifetime of massive stars, we greatly reduce the velocities and energies of our stellar winds to just 10~km~s$^{-1}$ and a thermal energy equivalent to the surface temperature of the star. AGB star winds occur at the end of main sequence for stars below 8~M$_{\odot}$. Their length is determined by the PARSEC stellar evolution tables, and we assume the same fixed velocity of 10~km~s$^{-1}$ as for the winds from more massive stars. 
\subsubsection{Stellar Radiation and Radiative Transfer}

We follow the H and He ionizing radiation for all stars above 8~M$_{\odot}$ using \cite{Schaerer2002} for Pop III stars and the OSTAR2002 \citep{Lanz2003} grid of stellar spectra for Pop II stars. Ionizing radiation is followed using the well-tested adaptive ray tracing radiative transfer method of \citep{WiseAbel2011} where photons packages are evolved as rays mapped to a \textsc{HEALPix} grid, adaptively refined as they radiate from their source. To reduce computational expense -- particularly in optically thin regions -- we use source clustering to allow rays to merge once they have travelled far from their source, and limit photon refinement once they have travelled \textbf{XX} kpc from their source. The latter dramatically reduced computational expense when photons escape their galaxy and travel through an optically thin IGM. FUV and LW radiation are both assumed to be optically thin. FUV radiation leads to photoelectric heating of dust grains in the ISM following \cite{Wolfire2003} and the dust-to-gas ratio scaling in \cite{Remy-Ruyer2014}. LW radiation is important for regulating cooling in metal-poor environments by dissociating the dominant coolant, $H_2$. We account for local self-shielding of LW radiation using the method from \cite{Wolcott-Green2011}. To dramatically reduce the computational expense of computing $1/r^2$ radiation for each star particle on each cell, we take advantage of the source clustering tree to speed up this computation by over an order of magnitude when the source count is larger than about 10.

\subsection{Chemical Evolution}

Since we follow individual star particles we can capture detailed, stochastic chemical evolution in our simulations -- a significant improvement over commonly used IMF-averaged yield sets. We use the NuGrid set of stellar yields \citep{Pignatari2016,Ritter2018} to follow the mass and metallicity dependent stellar wind and core collapse supernova abundances of Pop II stars, including AGB winds. This is supplemented with abundances from Slemer et. al. \textit{in prep.} for the stellar winds of stars above the upper mass limit of the NuGrid set, 25~M$_{\odot}$. For Pop III stars, we adopt the core-collapse SNe metal-free yields from \cite{Nomoto2006} for stars between 13~M$_{\odot}$ and 40~M$_{\odot}$ and the PISN yields of \cite{HegerWoosley2002} for stars between 60~M$_{\odot}$ and 130~M$_{\odot}$. Yields for Pop III stars that explode and release metals at the end of their life that are outside these mass ranges adopt the abundances of the closest grid point, scaled by mass. For Type Ia supernovae, we adopt the yields from \cite{Thielemann1986}.

We plan to follow the metal abundances of 8 elements from each of these sources, C, N, O, Mg, Ca, Fe, Sr, and Ba, in addition to the total metallicity and separate fields tracking the fractional contribution of Pop III stars, Pop II core collapse SN, Type Ia SN, and AGB stars to the total metallicity, and a tracer field to model r-process enrichment (discussed below). This gives us a total of 14 metal tracer fields on top of the 9 non-equillibrium chemistry fields. These elements were chosen carefully to maximize both the ability to resolve distinct nucleosynthetic channels and stellar enrichment timescales and usefulness for comparisons to observations, while minimizing the significant additional memory overhead for each additional field.\footnote{Assuming a typical simulation has $\sim10^8$ zones, each tracer field incurs a \textit{minimum} additional run-time memory requirement of 800~MB  (64-bits $\times$ 10$^8$). This represents the on-disk memory requirements for each field in the output data files. In practice, however, the actual run-time overhead is much larger as this does not include the requirements for ghost zones around each grid and additional space in communication buffers. The minimum memory requirement for all 14+9 species fields is 18.4 GB.} \textbf{AE: Do I need this justification for each element?:} O, Mg, and Ca are all produced in significant amounts in core collapse SN, and show a noticeable evolution with supernova progenitor mass, tracing short-timescale ($10~$Myr) chemical evolution. Fe is produced in both core collapse and Type Ia supernova, and the relative abundances of O, Mg, and Ca to Fe traces the evolution between these two yields sources on timescales of 100~Myr to 1~Gyr.\footnote{Additional Type Ia elemental yields (e.g. Ni and Mn) can readily be post-processed using the Type Ia tracer field.}. N, Sr, and Ba all trace s-process enrichment in low-mass AGB stars on timescales of 100~Myr to 1~Gyr, with N and Ba tracing the most massive (4-8~M$_{\odot}$) AGB stars and Sr the less massive ($<4$~M$_{\odot}$). C also has significant production in low-mass AGB stars, but is also produced in core collapse supernova. The C to Fe ratio is an important tracer of early Pop III enrichment. All of these elements are readily observed in a majority of low to medium stellar spectra, with the exception of O. However, O is the most abundant metal species and is used as an important tracer of gas-phase abundances.

Finally, as the origin of r-process enrichment is still highly debated and that possible sources of enrichment are rare and therefore strongly subject to stochastic variations in our simulation volume, we do not include an explicit channel for r-process enrichment. However, as XX - XX M$_{\odot}$ stars are expected to be possible sources of r-process enrichment, we follow their metal enrichment as a separate tracer field that can be used to post-process individual r-process abundances given models for their yields and scaling their expected frequency per XX - XX M$_{\odot}$ supernovae in the simulation. While this does not directly account for NS-NS r-process enrichment, this will test what -- if any -- r-process features in observed abundance patterns can be explained by CCSNe alone, and what features likely require an additional source of enrichment.

\subsection{Test Simulation}

\begin{figure}
\centering
\includegraphics[width=0.45\linewidth]{figures/DD0081_Projection_y_number_density_Metal_Density.png}
\includegraphics[width=0.45\linewidth]{figures/DD0081_Projection_y_Temperature_Metal_Density.png} \\ 
\includegraphics[width=0.45\linewidth]{figures/DD0081_Projection_y_Fe_over_H_Metal_Density.png}
\includegraphics[width=0.45\linewidth]{figures/DD0081_Projection_y_HI_kph_Metal_Density.png}
\caption{\textbf{I'll make this prettier for the final version}. Projections of gas number density, temperature, [Fe/H], and HI ionization rate in a small, low-resolution test simulations using our model of individual star formation and stellar feedback at z = 9.17. Stars are marked as points, with the black diamonds denoting PopIII SN remnants, black stars current main sequence PopIII stars, and orange stars current main sequence Pop II stars.}
\label{fig:test}
\end{figure}

In Figure~\ref{fig:test} we show the results of applying the methods discussed below to a low-resolution (61 co-moving pc, or 6.0~pc at z = 9.0) proof-of-concept test simulation with nested refinement on a single halo. The panels show projections of gas number density, temperature, [Fe/H], and HI ionization rate in the central region of the simulation box. Star particles are marked as black points. By this point in the simulation, a total mass  of $5.0 \times 10^{5}$~M$_{\odot}$ of stars have formed, a majority of which is Pop II star formation, as the Pop III stars that do form ($5.5 \times 10^{3}$~M$_{\odot}$) rapidly enrich this region to above the critial metallicity threshold.
%In addition, in Figure~\ref{fig:test2} we show the gas-phase distributions of

\section{Proposed Computational Resources}

\textbf{The proposed simulation is an incredibly valuable and novel exploration of the questions outlined in the beginning of this proposal.} This will be the first time a simulation of the evolution of the first stars and galaxies using individual star formation and stellar feedback will be performed. For this reason, we propose to devote the resources in our proposal to a single simulation and reserve a wider exploration of the effect of individual feedback processes on this evolution for future work.

We aim to run our simulations to redshift z $\sim$ 7 as was performed in \cite{Wise2012a}, with regular, frequent data dumps every 5~Myr and 20 targeted redshift outputs at staggered intervals extending from z = 25 to z = 7. These frequent time outputs will be rapidly analyzed to produce significantly smaller data products and images that can be readily stored long-term on local resources for continued analysis. z = 7 corresponds to a simulation time of $\sim$750~Myr, implying a total of 150 + 20 = 170 data outputs. Based on prior experience with the runs in \cite{Wise2012a} and \cite{Emerick2019a}, we anticipate a total cell count of approximately $\sim$10$^{8}$ throughout this simulation (though note that the initial outputs will contain much fewer, with a lower limit of 256$^3$ cells, or $1.68\times10^{7}$). In addition, there will be 256$^3$ dark matter particles. The dark matter particle count will be significantly larger than the star particle count and dominate the particle memory useage, but if we assume a comparable total stellar mass formed as in \cite{Wise2012a} of about $\sim 10^{7}$~M$_{\odot}$ and given the average particle mass in our simulations of 34~M$_{\odot}$ (this is large because we group all stars below 2~M$_{\odot}$ into a single particle per star formation event), we anticipate a total star particle count of about $3 \times 10^{5}$. Our simulation contains 51 total baryon fields and 15 particle fields each stored to high precision as a 64-bit float. This gives us a storage requirement of 64$\times 51 \times 10^8$ + 64$\times 15 \times (1.68\times10^7 + 3\times10^5) = 42.9$~GB per data dump for a \textbf{total storage requirement of 42.9 $\times$ 170 = 7.3~TB.}

The original simulations of \cite{Wise2012a} utilized $\sim$250,000 CPU hours running on 512 cores on a NASA machine. This run -- if used on the Stampede 2 SKX nodes and ignoring processor differences -- translates to 5371 SU (250,000/512 $\times$ 11, where 11 is the number of 48-core nodes needed to have at least 512 total cores) if run on Stampede-2. However, we expect this simulation to be more expensive due to the treatment of stars as individual particles, increasing the star particle count by a factor of $\sim$ 100. This matters most by increasing the number of ionizing sources and the number of distinct particles that are simultaneously interacting with the grid by depositing stellar feedback. The largest increase in cost here is for the ionizing sources. However, the total luminosity should be comparable, and the use of the source clustering algorithm should reduce the raw expense of this increase somewhat.

Based on our test simulations, we achieve \textbf{scaling results and costs here}

\begin{tabular}{c|c|c|c|c|c|c}
\hline
\hline
 Run & Parameter 1 & Parameter 2 & \#cores & \#Nodes & Wall Time (days) & \textbf{SUs} \\
 \hline
     & & & & & & \\
 \hline
 & & & & & Total &
\end{tabular}

\section{Project Team Qualifications}

\textbf{PI Emerick} is a Pasadena Fellow in Theoretical Astrophysics jointly appointed to Carnegie Observatories and the California Institute of Technology in Pasadena, CA. He is a recent PhD recipient from Columbia University advised by collaborator Greg Bryan and collaborator Mordecai-Mark Mac Low. Emerick is a core developer of the \textsc{Enzo}, \textsc{Enzo-E}, and \textsc{Grackle} public-source astrophysical code projects and the primary developer of the star formation, stellar feedback, and chemical evolution routines that will be used in this proposal. He has used \textsc{Enzo} and \textsc{Grackle} in multiple prior publications \citep{Emerick2015,Emerick2018a,Emerick2018b,Emerick2019a,Emerick2019b} and was co-I on a prior successful XSEDE proposal (TG-MCA99S024, "Star Formation, Feedback, and Chemical Evolution of Dwarf Galaxies", PI: Mordecai-Mark Mac Low, 45389.0 SUs on Stampede2) used to conduct the first simulations using the methods outlined in this proposal.

\textbf{co-I JI}

\textbf{co-I Wise}

\section{Management}
\subsection{Summary}

These simulations and any necessary additional code development will be carried out by PI Emerick. The code is currently ready to immediately begin production runs, but we plan to make minor improvements for use ability and efficiency by the allocation start on April 1. co-I Wise developed the initial conditions for these simulations as well as the radiative transfer algorithm, and will advise carrying out and analyzing this work. \textbf{co-I Ji }. In addition, this project will be carried out with collaboration from Greg Bryan (Columbia University / Flatiron Institute) and Mordecai-Mark Mac Low (American Museum of Natural History / Flatiron Institute).

\subsection{Local Computing Environment}

PI Emerick and co-I Ji have access to a computing cluster with 1 PB of total storage and 100 compute nodes each with Intel Xeon E5-2680 v3 (Haswell) processes with 12 cores, 128 Gb of memory. This resource is shared across all of eight of the Carnegie Science institutions and will be valuable for long-term storage of data products from this work and continued analysis, but its shared nature and maximum walltime limit of 2 hours prevents use of this resource for carrying out the proposed simulations. In addition, PI Emerick has access to the ``Wheeler'' $\sim$ 2000 core cluster -- also with Haswell nodes -- at the California Institute of Technology, shared among multiple departments. Its shared nature and small per-user storage ($<$ 2~TB) also prevents using this cluster for more than code development and analysis. \textbf{co-I Wise has...}

\subsection{Other Supercomputing Support}

PI Emerick has access to time on Stampede-2 through allocation TG-AST140064 "Simulating the Milky Way with the LMC" (PI Andrew Wetzel), which is focused on an unrelated project with a different hydrodynamics code, and is PI on startup allocation TG-AST190062 "Chemical Evolution of Ultrafaint Dwarf Galaxies" which was used to perform the scaling tests for this proposal. PI Emerick has recently had access to computing time on NASA Pleiades and Blue Waters, but does not currently have an active allocation with either system and has not applied for computing time for this project on any other resource.
\textbf{co-I Wise...}

------

\pagebreak
\textbf{AE: References will be a separate document and not count towards 10 page limit}
\def\bibfont{\footnotesize}
\bibliographystyle{apj}
\bibliography{msbib}%\thispagestyle{empty}

\end{document}

### 2021-01-19 XSEDE-April2020-Mar2021/scaling.tex
backup

\documentclass[12pt]{article} % font size here: some require 11 or 12 point
\usepackage{setspace}
\usepackage{fancyvrb}
\usepackage{epsfig}
\usepackage{fullpage}
\usepackage[small,compact]{titlesec}
\usepackage{times}
\usepackage{enumitem}
\usepackage{wrapfig}
\setlength{\topmargin}{+0.0in}   %%%%%%%%% this is hacked (from +.0.1in) so that it looks right when converted.
\setlength{\oddsidemargin}{-0.0in}
\setlength{\evensidemargin}{-0.0in}
\setlength{\textheight}{9.0in}
\setlength{\textwidth}{6.5in}
\usepackage[margin=1.0in,headheight=0pt,footskip=20pt,headsep=0.2in]{geometry}
\usepackage{natbib}
% ----------------------------------------------------
\usepackage{setspace}
\onehalfspacing % may need to switch to single spacing

\usepackage{natbib}
\usepackage{color}
\bibliographystyle{apj}
\newcommand{\apj}{ApJ}
\newcommand{\apss}{Astrophysics and Space Science}
\newcommand{\aj}{AJ}
\newcommand{\apjl}{ApJL}
\newcommand{\mnras}{MNRAS}
\newcommand{\apjs}{ApJS}
\newcommand{\pasp}{PASP}
\newcommand{\araa}{ARA\&A}
\newcommand{\aap}{A\&A}
\newcommand{\aaps}{A\&AS}
\newcommand{\pasj}{PASJ}
\newcommand{\prd}{Phys. Rev. D}
\newcommand{\nat}{Nature}
\newcommand{\nar}{New Astronomy Review}
\newcommand{\ao}{Applied Optics}
\newcommand{\physrep}{Physics Reports}
\newcommand{\etal}{et al}
\def\subsun{\mbox{$_{\odot}$}}
\def\lesssim{\mathrel{\hbox{\rlap{\hbox{%
 \lower4pt\hbox{$\sim$}}}\hbox{$<$}}}}
\def\gtrsim{\mathrel{\hbox{\rlap{\hbox{%
 \lower4pt\hbox{$\sim$}}}\hbox{$>$}}}}
\RequirePackage{natbib}
%\usepackage{setspace}
\setlength{\bibsep}{0.0pt}
\newenvironment{itemize*}%
{\begin{itemize}%
  \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
{\end{itemize}}

\newenvironment{enumerate*}%
{\begin{enumerate}%
  \setlength{\itemsep}{0pt}%
    \setlength{\parskip}{0pt}}%
{\end{enumerate}}

\usepackage{fancyhdr}
\pagestyle{fancy}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\rhead{Performance and Scaling}

%\usepackage[pagestyles]{titlesec}
%\newpagestyle{mystyle}{\sethead{}{}{Name -- Number}\setfoot{}{\thepage}{}}
%\pagestyle{mystyle}

\title{\vspace{-5ex} Performance and Scaling
       \vspace{-2ex}}

\begin{document} \thispagestyle{empty}

% Star-by-Star Stellar Feedback and Chemical Evolution in Dwarf Galaxies

\maketitle

\textsc{Enzo} has been used extensively a range of large-scale computing resources including Blue Waters, NASA Pleiades, and Frontera \textbf{AE: need more?}, in addition to both \textsc{Stampede} and \textsc{Stampede-2}, the proposed resource. Generally, \textsc{Enzo} has been shown to achieve very good weak scaling in unigrid cosmological simulations on up to 4096 cores, and speed-ups in strong scaling tests of a 512$^3$ adamtive mesh refinement (AMR) simulation with 6 levels of refinement on up to 4096 cores. We present here the performance and scaling properties of \textsc{Enzo} in the particular context of typical computational loads of our proposed cosmological simulations.

In this situation, we are primarily concerned with the strong scaling properties of \textsc{Enzo} given our proposed problem size, AMR hierarchy depth, and included physics in order to find the optimum core / node count and node type (SKX or KNL) for our desired problem. We discuss the numerical methods employed in \textsc{Enzo} relevant to our proposed problem in the main document, and begin here with a description of the methods used to achieve high-performance and good scaling on HPC systems.

\section{Computational Methods and Problem}

As described in the main document, our AMR cosmological simulations are initialized in a (1~Mpc co-moving)$^3$ box with a 256$^3$ cell root-grid with 256$^3$ dark matter particles. This AMR simulation has a maximum of 12 levels of refinement to a resolution of 1~pc co-moving.

\subsection{Grid Hierarchy and Parallelization Strategy}

\texttt{Enzo} AMR simulations begin with a defined rectilinear root grid encompassing the computational domain. Additional levels of refinement take the form of child sub-grids nested within the root grid, generating a nested tree comprised of grid parents, children, and siblings; for our purposes, additional sub-grids increase resolution by a factor of two. \textsc{Enzo} utilizes a patch-based AMR approach allowing for arbitrary sub-grid sizes and dimensions, which tends to reduce refinement to only those zones where it is needed, as opposed to other AMR schemes with fixed grid dimensions (e.g. oct-tree block structured AMR). Each grid is comprised of active zones and ghost zones that store boundary information from sibling grids. Each level in this tree is evolved on independent time steps, reducing unneeded computation on lower levels of refinement.

Using grid objects as fundamental units that exist entirely on a single processor, \texttt{Enzo} has been parallelized with the message passing interface (MPI). Grids are therefore distributed among processors in such a way to attempt to balance the computational load across processors. This is simple for the root grid, which is evenly divided in tiles to all processors, but is more complicated for higher refinement levels, which usually are not uniformly distributed in the simulation volume. Higher levels of refinement are initially placed on the processors that host their parent grids, but are subsequently distributed among other processors to reduce computational load. Load is estimated as the number of active zones on each grid. We use a simple load-balancing option to progressively move grids from processors with high computational loads to processors with the lowest computational loads until the load ratio of the most-to-least loaded processors is less than 1.05. To improve performance further, \texttt{Enzo} dynamically adjusts the size of each sub-grid on a given level depending on the number of zones on the given level and the load balance across processors on that level. This reduces communication time across processors on each level while also improving the effectiveness of load-balancing.

Each processor contains a copy of the entire grid hierarchy meta data, allowing for easy non-blocking communication across processors; the additional memory overhead of storing this data on each processor is negligible. In addition, all star particle information is stored on each processor (again, with negligible memory overhead), removing the need for communication when injecting feedback from stars close to grid boundaries.

\textbf{Radiative transfer communication and load balancing}

%\subsection{Radiative Transfer Methods}

%\cite{WiseAbel2011} implemented radiative transfer capabilities in \texttt{Enzo}, performing rigorous tests of its capabilities, and has been used in a variety of applications \citep[e.g.][]{Wise2012a,WiseAbel2012,Wise2014, Smith2015, OShea2015, Koh2016, Regan2016a, Regan2016b}. The equations of radiative transfer are solved directly on the computational domain following directly traced rays from individual point sources. This is an inherently computationally expensive process. To improve efficiency \texttt{Enzo} employs an adaptive ray tracing method \citep{AbelWandelt2002} where rays are mapped from a point source to HEALPix pixels surrounding the source. The resulting rays are advanced through the grid, progressively refining rays by splitting them into child rays once the ratio of the cell face area to ray solid angle drops sufficiently. In a given time step, rays propagate a distance $c\times dt$, or until they either leave the computational domain or their flux drops by 99.99\% or more in a single cell. If the rays still exist at the end of the ray tracing step, their evolution is halted and stored for the next time step. The resulting ionization and heating rates due to the radiation field are computed assuming the photo-ionization and absorption rate are equal, ensuring photon conservation \citep{Abel1999, Mellema2006}. These are passed to the \texttt{Grackle} chemistry solver to update the correct ionization, chemical, and energy states in each cell.

\section{Performance and Scaling Results}

Profiling the exact scaling and performance results of a cosmological AMR simulation is challenging, as the total number of computational grids can vary significantly over a run. In general, however, computational expense will increase as a simulation progresses as the number of cells grow to follow dense, star forming gas, and the number of star particles grows. We tested various compile-time options for our simulations to find the optimal configuration for running on SKX nodes: compiling without the recommended SKX/KNL optimization flags, compiling with the recommended SKX-only flags (-xCORE-AVX512), and compiling with the recommended SKX/KNL flags using the TACC\_VEC\_FLAGS environment variable. For each case, we tested -O2 and -O3 optimization. We found that for fixed core counts (48 cores / node), running on SKX nodes is at least a factor a four times faster than running on KNL nodes when running on reach with SKX-only and KNL-only compiler settings respectively. Although KNL nodes allow more cores per SU -- which could make this resource the cheaper -- our computation is memory intensive. The much lower available RAM per process on KNL nodes compared to SKX makes this unavailable. For these reasons, we plan to use SKX nodes for this study. We find in each case that -O3 optimizations leads to a $\sim$25-30\% slower computation than -O2, compiling with the -xCORE-AVX512 flag leads to a $\sim$10\% speed-up, and compiling with the general TACC\_VEC\_FLAGS option is a 2-5\% slower than using the SKX-specific settings. We will use the -O2 and -xCORE-AVX512 compiler settings for this project and the remainder of these tests.

In Figure~\ref{fig:weak_scaling} we present strong scaling results of our fiducial simulation run at redshift

\def\bibfont{\footnotesize}
\bibliographystyle{apj}
\bibliography{msbib}%\thispagestyle{empty}

\end{document}

### 2021-01-19 mixing_experiment_apj/main.tex
backup

\documentclass[twocolumn]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
%\usepackage{deluxetable}

\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref

\newcommand{\runone}{A\_}
\newcommand{\runonenu}{A}
\newcommand{\runtwo}{B\_}
\newcommand{\runtwonu}{B}

%% Define new commands here
\newcommand\latex{La\TeX}

\begin{document}

\title{Simulating Metal Mixing of Both Common and Rare Enrichment Sources in a Low Mass Dwarf Galaxy}

\correspondingauthor{Andrew Emerick}
\email{aemerick@carnegiescience.edu}

%\author{}
%\altaffiliation{}
%\affiliation{}
%% The \author command can take an optional ORCID.
\author[0000-0003-2807-328X]{Andrew Emerick}
\altaffiliation{Carnegie Fellow in Theoretical Astrophysics}
\affiliation{Carnegie Observatories, Pasadena, CA, 91101, USA}
\affiliation{TAPIR, California Institute of Technology, Pasadena, CA, 91125, USA}
\author[0000-0003-2630-9228]{Greg L. Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10010, USA}
\author[0000-0003-0064-4060]{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, 10024, USA}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10010, USA}

\keywords{Galaxy chemical evolution---Dwarf galaxies---Chemical enrichment---Hydrodynamics}

\begin{abstract}
%Stellar abundance patterns provide valuable insight into both galactic evolution and stellar nucleosynthesis.
One-zone models constructed to match observed stellar abundance patterns have been used extensively to constrain the sites of nucleosynthesis with sophisticated libraries of stellar evolution and stellar yields. The metal mixing included in these models is usually highly simplified, although it is likely to be a significant driver of abundance evolution. In this work we use high-resolution hydrodynamics simulations to investigate how metals from individual enrichment events with varying source energies $E_{\rm ej}$ mix throughout the multi-phase interstellar medium (ISM) of a low-mass ($M_{\rm gas}=2\times 10^{6}$~M$_{\odot}$), low-metallicity, isolated dwarf galaxy. These events correspond to the characteristic energies of both common and exotic astrophysical sites of nucleosynthesis, including: asymptotic giant branch winds ($E_{\rm ej}\sim$10$^{46}$~erg), neutron star-neutron star mergers ($E_{\rm ej}\sim$10$^{49}$~erg), supernovae ($E_{\rm ej}\sim$10$^{51}$~erg), and hypernovae ($E_{\rm ej}\sim$10$^{52}$~erg). We find the mixing timescales for individual enrichment sources in our dwarf galaxy to be long (100~Myr--1~Gyr), with a clear trend of increasing homogeneity for the more energetic events. Given these timescales, we conclude that the spatial distribution and frequency of events are important drivers of abundance homogeneity on large scales; rare, low $E_{\rm ej}$ events should be characterized by particularly broad abundance distributions. The source energy $E_{\rm ej}$ also correlates with the fraction of metals ejected in galactic winds, ranging anywhere from 60\% at the lowest energy to 95\% for hypernovae. We conclude by examining how the radial position, local ISM density, and global star formation rate influence these results.
%Detailed metal mixing and ejection properties are important considerations in one-zone models of low-mass dwarf galaxy stellar abundances.
\end{abstract}

\section{Introduction}

The elemental abundances of a galaxy over time are sensitive to the nuclear physics and stellar astrophysics that determines which stars make what elements and when. The stellar abundance patterns within a given galaxy also depend on the details of how those metals are released into the interstellar medium (ISM) through various forms of stellar feedback, and the hydrodynamic interactions that ultimately mix those elements into the ISM or eject them from the galaxy in galactic winds.

Old, metal poor systems are enriched by substantially fewer sources than younger, more metal rich stellar populations. Studying abundance patterns in these environments allows us to place constraints on the nucleosynthetic sites of each element and the total yields of individual enrichment events. Therefore, the lowest mass dwarf galaxies in the Local Group, ultra-faint dwarfs (UFDs), offer some of the best constraints on these processes. For example, these environments can potentially be used to trace and constrain enrichment from the first stars \citep[e.g.][]{FrebelBromm2012,Ji2015,Ritter2015,Jeon2017,Hartwig2018} and have been used to place constraints on the variety of possible astrophysical sources of $r$-process enrichment \citep[e.g.][]{Ji2016a,Ji2016b,Ji2018a,Ji2019,Tsujimoto2017,Duggan2018,Nagasawa2018,Ojima2018,Skuladottir2019}.

The stochastic sampling of individual enrichment events in regimes with low star formation rates has been shown to be important for setting the width of stellar abundance patterns in low metallicity environments of the Milky Way halo \citep[e.g.][]{Cescutti2008,Cescutti2014}, can play an even greater role in the physical evolution of these low mass dwarf galaxies \citep{Applebaum2018,Su2018} and their abundances \citep[e.g.][]{RomanoStarkenburg2013,Romano2015,Ojima2018}. Indeed the increase in scatter in the stellar abundance patterns of low mass dwarf galaxies and UFDs has been attributed to inhomogeneous mixing and stochastic effects \citep[e.g.][]{Norris2010a,Lee2013,Simon2015,Mashonkina2017,Suda2017}. While chemical evolution models can account for some of these effects, they are largely unable to account for the detailed hydrodynamics interactions and turbulent mixing in a multi-phase ISM that may enhance (or smooth over) these stochastic effects. This complicates the interpretation of abundance patterns in these galaxies, particularly in attempting to assign a single (or small number) of enrichment events to specific abundance features \citep[e.g.][]{Ji2015,Fraser2017,Chen2017,Ishigaki2018,Welsh2019,Hartwig2019}

Recent cosmological zoom simulations have attained sufficient resolution to follow the evolution of individual low mass dwarf galaxies and UFDs (or their progenitors at high redshift) and can investigate their chemical properties \citep{Jeon2017,Maccio2017,Christensen2018,Corlies2018,Escala2018,Munshi2018,RevazJablonka2018,wheeler2019,Agertz2019}. 
In particular, \cite{Cote2018} compares high-resolution hydrodynamics simulations directly with one-zone models, finding the importance of non-uniform mixing in driving abundance spreads in these galaxies, and characterize multiple hydrodynamics effects that are challenging to parameterize in current one-zone models. Additional works have conducted more direct investigations into what drives the enrichment process for individual sources using both hydrodynamics simulations \citep{PanScannapiecoScalo2013,Ritter2015,Safarzadeh2017,Hirai2015,Hirai2017,Emerick2018b,HaynesKobayashi2019} and semi-analytic models \citep[e.g.][]{KrumholzTing2018}. 
% It is becoming increasingly clear that enrichment is quite inhomogeneous in low mass dwarf galaxies (refs?), and also that the behavior of metals from any one enrichment event depends on a significant number of complex interactions.
In spite of this progress, there is still substantial work to be done in understanding the physical processes that drive evolution of both the mean and width of stellar abundances in low-mass dwarf galaxies.

The astrophysical origin of $r$-process enrichment is still highly uncertain (see \citet{Thielmann2017}, \citet{Frebel2018}, \citet{Cote2019}, and \citet{Cowan2019} and references therein) with possible origins including core collapse supernovae, binary neutron star (NS) mergers, NS-black hole mergers, magneto-rotational supernovae (SNe) \citep[e.g.][]{Winteler2012}, jet-driven SNe, and collapsars \citep[e.g.][]{Siegel2019} . Metal poor stars in the Milky Way's halo and nearby dwarf galaxies provide some of the greatest sensitivity to potential $r$-process sources. The $r$-process origin in these environments has has been investigated in analytic or semi-analytic models \citep[e.g.][]{Beniamini2018,Macias2018,Macias2019,SchonrichWeinberg2019,Wehmeyer2019} and directly in cosmological hydrodynamics simulations which either directly included models of $r$-process enrichment or placed these enrichment events in halos by-hand \citep[e.g.][]{Shen2015,vandeVoort2015,vandeVoort2019,Safarzadeh2017}. Broadly, these works generally find a preferred source of $r$-process enrichment to best match observations, but no model has yet been able to reproduce all observed stellar abundance trends across environments. However, as discussed earlier, non-uniform mixing plays an important role in galactic chemical evolution and its significance in these environments (the Milky Way halo and UFDs) may dramatically influence how one should use abundance patterns to constrain $r$-process yields. In addition, if much of these metals are ejected from low mass UFDs through galactic winds, this will change estimates for the total mass of $r$-process yields implied by observed stellar abundances. Finally, if metal mixing and ejection properties vary significantly between different sources (e.g. NS-NS merger and collapsars), this may provide an additional important discriminator between potential sites of $r$-process enrichment. Investigating these effects in detail requires simulations capable of capturing individual enrichment events with distinct injection energies, as compared to models utilizing smoothed enrichment from simple stellar populations.

In \cite{Emerick2018b} we examined metal mixing in simulations of an isolated, low-mass dwarf galaxy following stellar feedback and chemical enrichment on a star-by-star basis. By following individual enrichment sources---asymptotic giant branch (AGB) winds, massive stellar winds, core collapse SNe, and Type Ia SNe---we were able to resolve differences in how metals from these sources evolve in a low mass dwarf galaxy. We found that elements released through AGB winds (e.g. s-process elements) have broader abundance distributions in the ISM than elements released in SNe (e.g. $\alpha$ and Fe-peak elements). In addition, AGB wind elements coupled more weakly to the significant galactic winds from this dwarf galaxy, and were retained at a much higher fraction ($\sim 20\%$) than elements from SNe ($\sim 5\%$). However, this is the result from many enrichment sources over an extended period of time in an isolated dwarf galaxy. It is unclear how much metal mixing varies across individual sources.

In this work we utilize the detailed simulations introduced in \cite{Emerick2019} to conduct a controlled set of ``mixing experiments'' whereby we restart each simulation with enrichment events placed by hand in order to more directly investigate the evolution of metals from an individual event. While elemental yields were tracked for each star in our simulation, we lacked the necessary Lagrangian information\footnote{The history of a given mass element---which is followed natively in smoothed particle hydrodynamics and other Lagrangian codes---but not in the Eulerian grid-based hydrodynamics simulations used here.} about the metals once they were released into the ISM to be able to trace the evolution of single enrichment events. We investigate primarily how the feedback ejection energy of individual sources $E_{\rm ej}$ and global star formation rate (SFR) at the time of enrichment affect how metals are ejected from the galaxy in galactic winds and mix into the ISM. In Section~\ref{sec:methods} we briefly outline our methods and discuss the setup of these mixing experiments. In Section~\ref{sec:results} we discuss the role that $E_{\rm ej}$, global SFR, radial position of the enrichment event, and local ISM density around each enrichment event affects metal abundance evolution. We discuss these results and conclude in Section~\ref{sec:discussion conclusion}.

\section{Methods}
\label{sec:methods}
We refer the reader to \cite{Emerick2019} for a detailed description of our numerical methods, initial conditions, feedback, and chemical evolution model. We briefly summarize the key components of these methods below.

This work follows the evolution of an idealized, isolated, low-mass dwarf galaxy with an initial gas mass of $M_{\rm gas} = 1.80 \times 10^6$~M$_{\odot}$ initialized as an exponential disk with radial and vertical scale heights of 250~pc and 100~pc respectively. This galaxy is embedded in a static, \cite{Burkert1995} dark matter potential with virial mass and radius $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc. This is evolved using the adaptive mesh refinement hydrodynamics code \textsc{Enzo} \citep{Enzo2014}, with a minimum/maximum spatial resolution of 921.6~pc / 1.8~pc. The grid is refined to maintain a mass resolution of 50~M$_{\odot}$ per cell, and to ensure that the Jeans length is resolved by at least eight cells. In addition, a three-zone radius region around any star particle that has active feedback (stellar winds or SNe) is refined to the maximum grid resolution. We use the chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to solve a nine species non-equillibrium chemistry model that includes gas-phase and dust H$_2$ formation, a uniform UV background, and localized self-shielding.

\subsection{Star Formation and Stellar Feedback}
Our simulation stochastically forms star particles in dense gas ($n > 200$~cm$^{-3}$) by randomly sampling a \cite{Salpeter1955} IMF and depositing individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$. For stars above 8~M$_{\odot}$, we follow their H~{\sc i} and He~{\sc i} ionizing radiation using the adaptive ray-tracing radiative transfer method of \cite{WiseAbel2011}, and trace their radiation in the Lyman-Werner and FUV bands using an optically thin approximation. These stars eject mass and energy over their lifetimes through stellar winds, and we include mass and thermal energy injection of both core collapse and Type Ia SNe. Stars below 8~M$_{\odot}$ have no feedback during their lifetime, except mass and energy deposition of their AGB winds at the end of their life. For stellar winds and SNe, mass, energy, and metals are injected to the grid by mapping a three-cell spherical region ($r=3 \times dx = 7.2~$pc) to the grid using a cloud-in-cell interpolation scheme.

\subsection{Mixing Experiment Setup}
\label{sec:experiment}
We restart the fiducial, full-physics simulation described in \cite{Emerick2019} at two different times: 180 Myr, and 360 Myr, labeled as runs \runonenu~and \runtwonu~respectively. These correspond to two different points in the galaxy's star formation history, testing how much variance with the SFR is expected in the metal mixing and ejection. Run \runonenu~occurs during the lull in star formation ($\dot{M}_{*} \sim 6 \times 10^{-5}$~M$_{\odot}$~yr$^{-1}$) following the initial SFR peak ($\dot{M}_{*} \sim 10^{-3}$~M$_{\odot}$~yr$^{-1}$), and run \runtwonu~occurs in an extended period of little to no ongoing star formation ($\dot{M}_{*} < 1 \times 10^{-5}$~M$_{\odot}$~yr$^{-1}$). We attempted to to evolve each simulation for 150 Myr, but due to computational constraints this was not always possible.
%\footnote{We also began runs during the peak of star formation ($\sim 100$~Myr), but the computational cost increases substantially during this time. These runs were abandoned.}

% I occurs in the last $\sim$ 20 Myr of the initial burst of star formation,

\begin{deluxetable}{cccc}

\tablecaption{Energy and mass injected for each type of source tested. Energy is injected as pure thermal energy to the simulation grid, but we compute the corresponding ejection velocities for comparison to the escape velocity (see text for more detail).
\label{table:setup}}
%It should be noted that in every case, the mass of swept up ISM in both the 7.2~pc spherical injection region and that accumulated during the events evolution reduces typical velocities to well below the implied $v_{\rm ej}$}
\tablehead{
\colhead{Energy (erg)} & \colhead{$m_{\rm ej}$ (M$_{\odot}$)} & \colhead{$v_{\rm ej}$ (10$^{3}$ km s$^{-1}$)} \\
}
\startdata
$10^{46}$ & 2.0  & $22.$ \\
$10^{49}$ & 0.01 & $10.$ \\
$10^{50}$ & 0.01 & $32$ \\
$10^{51}$ & 10.0 & $0.31$ \\
$10^{52}$ & 2.5  & $22.$ \\
\enddata
\end{deluxetable}

At the beginning of each restart, we place by hand one or more enrichment events at assigned positions throughout the galaxy, with thermal injection energies ($E_{\rm ej}$) and masses ($m_{\rm ej}$) as given in Table~\ref{table:setup}. We compute the corresponding ejection velocity assuming injection into a vacuum (ignoring swept-up ISM mass, which can be significant) as $v_{\rm ej} = \sqrt{2 E_{\rm ej}/m_{\rm ej}}$. The escape velocity throughout the galaxy is nearly constant at about 81~km~s$^{-1}$. We vary $E_{\rm ej}$ and $m_{\rm ej}$ to sample the range of ejection energies associated with significant sources of chemical enrichment,  including AGB winds ($10^{46}$~erg; $\sim 2$ M$_{\odot}$), NS-NS mergers ($10^{49} - 10^{50}$~erg; $\sim 0.01$ M$_{\odot}$), SNe (10$^{51}$~erg; $\sim 10$ M$_{\odot}$), and exotic enrichment sources, such as hypernovae (HNe), that can reach much higher energies (10$^{52}$~erg; $\sim 10$ M$_{\odot}$). \footnote{We note that---due to an error in the setup of these runs---$m_{\rm ej}$ for the HNe-like event (10$^{52}$~erg) is low by a factor of four. We do not expect this to significantly impact the conclusions of this paper.} The injection masses are intended to be order of magnitude estimates of corresponding astrophysical sources, but we note that they are ultimately somewhat arbitrary as they are often small compared to total ISM mass in the 3-zone radius injection region, let alone in the swept-up ISM outside this region (for reference, the total mass in an injection region for $n_{\rm ISM} \sim 1$~cm$^{-3}$ is about 20~M${\odot}$).

Each event deposits mass into a corresponding passive scalar tracer field---unique to that event---to trace how the metals from these sources mix in the ISM over time. Each run contains only sources from a single event type, as indicated in the run-name by the log of the injection energy in ergs. For example, the run beginning at 180~Myr with AGB-like events is labeled ``\runone E46". We place multiple events per run, spread over the galaxy to test how radial and azimuthal position in the galaxy affects mixing and ejection, but limited to ensure that the events do not overlap and influence each other dynamically. For the low-energy events, we are able to use 19 events per run, while the $10^{49}-10^{51}$~erg runs contain 7 events, and the 10$^{52}$~erg runs only contain a single event.

\section{Results}
\label{sec:results}
Perhaps the four most important parameters to quantify for each enrichment event are: 1) what fraction of released metals are immediately available for star formation, 2) how does this fraction evolve over time as metals cool from hot phases into star forming gas, 3) what fraction of metals are carried out of the galaxy in outflows, and 4) how homogeneously distributed are the released metals as a function of time. We discuss the first three points in Section~\ref{sec:ISM CGM}, focusing on the average behavior of multiple enrichment events at fixed ejection energy and address the final quantity in Section~\ref{sec:spreads} and Section~\ref{sec:inhomogeneity}. Finally, in Section~\ref{sec:individual event variation} we discuss how these properties vary with individual events, and, in Sections~\ref{sec:radial position} through ~\ref{sec:SFR}, how they vary with radial position in the galaxy, ISM properties in the event region, and global galaxy SFR.

For simplicity, throughout this work we consider the ISM of our dwarf galaxy to be all gas within a fixed cylindrical region of radius 600~pc and $|z| < 200$~pc centered on the galaxy. The circumgalactic medium (CGM) is all gas outside of this disk, but within the virial radius (27.4~kpc). We split the ISM into four phases: cold neutral medium (CNM; $T < 10^2$~K), warm neutral medium (WNM; $10^{2}~\rm{K} \leq T < 10^{4}~ \rm{K}$), warm ionized medium (WIM; $10^{4}~\rm{K} \leq T < 10^{5.5}~\rm{K} $), and hot ionized medium (HIM; $T \geq 10^{5.5}$~K). Unless otherwise specified, when we refer to metals ejected from our dwarf galaxy we mean metals that are no longer within the ISM, and are either within the CGM or have been ejected beyond the virial radius.

\subsection{Enrichment of the ISM and CGM}
\label{sec:ISM CGM}

\begin{figure*}
\centering
\includegraphics[width=0.45\linewidth]{AGB1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{NSNS1_enrichment_evolution_average_CGM} \\
\includegraphics[width=0.45\linewidth]{SNE1_enrichment_evolution_average_CGM}
\includegraphics[width=0.45\linewidth]{HNE1_enrichment_evolution_average_CGM}
\caption{Time evolution of the fraction of metals in each phase of the ISM (colored lines; CNM: dark blue, WNM: light blue, WIM: orange, HIM: red), the galaxy's disk (black, dashed), and the CGM (black, solid) as averaged across all events at a given $E_{\rm ej}$. The fractions are all normalized to the total amount of metals initially injected in each event. The individual ISM phases sum to the black, dashed line.}
\label{fig:ISM_CGM}
\end{figure*}

We summarize the source-averaged results for all types of enrichment events in Figure~\ref{fig:ISM_CGM} by showing the fraction of source metals contained within each phase of the ISM (colored lines, which sum to the black dashed line), and the CGM (black, solid). These plots show a clear, immediate trend across $E_{\rm ej}$ for all phases shown in the figure, as well as for the distribution between ISM (black, dashed) and CGM (black, solid) lines. In \cite{Emerick2018b}
we demonstrated that there was a significant difference in metal ejection fraction, $f_{\rm ej}$, for metals from AGB sources as compared to metals released in SNe. Here, we confirm that this is driven by differences in the energy of the events. Figure~\ref{fig:ISM_CGM} shows that material ejected in events with higher $E_{\rm ej}$ is much more readily ejected from the disk of the galaxy than material from lower $E_{\rm ej}$ events. 
% By 10~Myr after the enrichment events,
The high-energy events rapidly converge on a peak $f_{\rm ej}$ within about 20~Myr of the event, with only a gradual increase towards the end of the 150~Myr as metals in the ISM are swept up in additional outflows. The lower energy events evolve more gradually. The lowest energy event, corresponding to AGB winds, reaches $f_{\rm ej} \sim$~0.68 by the end of the simulation, lower than the 0.87 for the 10$^{51}$~erg events, and 0.95 for the 10$^{52}$~erg event. To emphasize these differences, we plot all the CGM fractions together
in the left panel of Figure~\ref{fig:CGM_CNM}.

In all cases, the tracer metals are initially deposited predominantly in the ionized phases of the ISM, the WIM or the HIM, with the relative fraction in each phase driven by the energy of the event. Metals in the ISM injected with $E_{\rm ej} > 10^{49}$~erg are initially located predominantly in the HIM, roughly half for $E_{\rm ej} = 10^{49}$~erg and nearly all for $E_{\rm ej} > 10^{51}$~erg. The lowest energy events are initially in the WIM and WNM, tracing the two dominant volume-filling components of the ISM. These events do not have sufficient energy to generate HIM by themselves, while the E46 events can only ionize gas at lower densities (n~$\lesssim 0.1$~cm$^{-3}$).

Gas above the star formation threshold in our simulations is limited at any one snapshot, and short-lived. As a proxy, we examine the evolution of the CNM, from which the star forming gas originates. In the right panel of Figure~\ref{fig:CGM_CNM}, we examine the evolution of the metal fraction of the CNM \textit{for just those elements retained in the ISM}. In general, very few of these elements are available for immediate star formation in the CNM ($<< 1\%$, see Figure~\ref{fig:CGM_CNM}). Although the initial CNM fractions are about the same for each source, the evolution over the first $\sim$50~Myr is qualitatively different.  The metals from higher energy sources with $E_{\rm ej} > 10^{49}$~erg are more rapidly incorporated into the CNM than the metals in E46, even though the former models retain a lower fraction of metals in the ISM. This is most significant at $\sim$20~Myr, when the fraction of metals in the CNM from these sources is a factor of $\sim$3--4 higher than the E46 metals. By $\sim$50~Myr, the fractions become similar, with no clear trend as a function of $E_{\rm ej}$. Thus, metals from the lowest energy sources (i.e. AGB stars) only start to become available for enrichment of future sites of star formation $\sim$20 Myr after metals from higher energy sources.

\cite{SchonrichWeinberg2019} find that models of $r$-process enrichment in the Milky Way can better fit observations provided the fraction of metals immediately available for star formation from NS-NS mergers is greater than that of SNe. Based on our simulation, we do not find evidence that this fraction is different immediately after each event, nor do we find a clear trend between longer term differences and injection energy for sources with 10$^{49}$-10$^{51}$~erg. However, we note that we may not have sufficient resolution to properly resolve the details of the initial mixing of individual enrichment events in the ISM. In addition, this value will be sensitive to whether or not a given event is more (or less) likely to occur in the vicinity of or inside an active, star forming region, or far from dense gas in the ISM. We are also missing important physical processes, such as dust production in AGB winds and core collapse SNe and differences in cooling rates with the abundances of individual elements, which may change how rapidly elements from a given source are incorporated into the cold ISM. Investigating the fraction of metals immediately available for star formation requires even higher resolution simulations of metal mixing, such as those that following mixing in and around individual star forming regions \citep[e.g.][]{Kuffmeier2016,Armillotta2018}.
%This will be additionally useful for understanding stellar enrichment patterns that may arise from star formation in regions whose metal abundance patterns arise directly from unmixed ejecta of a single enrichment source. % cite

\begin{figure*}
  \centering
  \includegraphics[width=0.45\linewidth]{paper_CGM_average_evolution}
  \includegraphics[width=0.45\linewidth]{paper_CNM_average_evolution}
  \caption{Time evolution of the fraction of enrichment source tracer metals ejected from the galaxy (left), and the fraction of tracer metals within the ISM that are in the CNM (right). These show the same data as the lines in Figure~\ref{fig:ISM_CGM}, but the CNM lines are now normalized by the black, dashed total ISM line in Figure~\ref{fig:ISM_CGM}.  }
  \label{fig:CGM_CNM}
\end{figure*}

The metals from each source do gradually tend towards a fraction of $\sim$0.8 by the end of the 150~Myr simulation time, which is approximately the total mass fraction of the CNM. This trend---that the fraction of metals contained in a given phase tends towards the mass fraction of that phase---is true across all phases in the simulation. Therefore, we can conclude that the metals for each source are well-mixed across the \textit{phases} of the ISM on timescales of $\sim$100--150~Myr over the whole galaxy. This is comparable to, but less than, the dynamical timescale of the galaxy, $\sim$200~Myr. Although well-mixed across phases, we emphasize that this does not imply that the abundances are the same across phases nor that the metals are spatially well-mixed across the galaxy. We investigate this second point further below.

\subsection{Homogeneity of Mixing}
\label{sec:spreads}

We show the spatial evolution of metals for different enrichment energies in Figures~\ref{fig:mixing_panel} and Figures~\ref{fig:mixing_panel2} to build intuition on how metals evolve in this galaxy over time. Each figure shows the time evolution of the abundance of a single tracer field (right three panels) associated with an enrichment event placed in the center of the galaxy (Figure~\ref{fig:mixing_panel}) and another event in the mid-plane, placed 300~pc from the center (Figure~\ref{fig:mixing_panel2}). The left panels show projections of the disk number density to illustrate the structure of the ISM in the galaxy over the four sampled points in time after the initial injection. The abundance panels show (left to right) the evolution of an E46, E51, and E52 source, corresponding to an AGB-like, SN-like, and HNe-like enrichment event.

\begin{figure*}
\centering

\includegraphics[width=0.9\linewidth]{mixing_test_center.png}
\caption{Face-on evolution of the enrichment from sources placed at the center of the galaxy. We show a projection of the gas number density in the ISM (far left) and the enrichment evolution of an E46, E51, and E52 event at times after the initial injection of 0.2 Myr, 10 Myr, 50 Myr, and 75 Myr. The enrichment panels show the total mass of the tracer metal in each pixel. The right three panels have no weighting except a uniform normalization to maintain the same color scaling across the three injection sources. Since the initial injection mass of each event varies and the amount ejected / retained by the ISM varies, each panel is normalized by both the mass of tracer metal initially injected and the mass of that metal retained in the ISM.}
\label{fig:mixing_panel}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{mixing_test_offcenter.png}
\caption{The same as Figure~\ref{fig:mixing_panel}, but for enrichment events placed in the mid-plane, 300~pc from the center of the galaxy.}
\label{fig:mixing_panel2}
\end{figure*}

These figures demonstrate that the injection energy of each enrichment event drives qualitative differences in where and how quickly the tracer metals are distributed over the galaxy. In both cases, the tracer metals from the lowest energy event (E46) take longer to evolve out of the initial injection region, and reach a smaller volume of the galaxy by the final panel. In the central injection event, the two higher energy sources distribute their metals over much of the galaxy within 10~Myr, enriching comparable (but not identical) regions by the final panel. Comparing the enrichment panels to the gas number density, there is a significant amount of tracer metals contained within dense clumps of gas.\footnote{As noted in the caption to Figure~\ref{fig:mixing_panel}, we emphasize that the images in the right three panels are not weighted. The color field is the total mass of the tracer metal in each pixel with a normalization.} However, although they contain much of the metals, these dense regions are considered metal poor; they have low metal mass fractions due to their significant total mass. While the total mass of tracer metals contained in the diffuse gas is less than that of these cold dense clumps, the diffuse gas is more highly enriched due to their higher metal mass fractions. Metals locked in these cold regions remain there, mixing poorly with the rest of the ISM, unless blown apart through star formation and stellar feedback. % AJE: this could be a key point to re-emphasize in the conclusion

Comparing Figure~\ref{fig:mixing_panel} with Figure~\ref{fig:mixing_panel2}, the position of the enrichment source in the galaxy does make a noticeable difference in the evolution of the tracer metals for a fixed injection energy. In all cases, the tracer metals mix with a much smaller volume of the galaxy than their counterparts injected at the center of the galaxy. By the final panel, the tracer metals are still confined to about half (or less) of the galaxy. We better quantify the inhomogeneity of this mixing and how it varies with injection energy, event position, and galaxy properties below.

\subsection{Quantifying Inhomogeneity}
\label{sec:inhomogeneity}

To frame this analysis, let us first examine what processes affect the distribution of metals---the metal mass fraction PDF---in the ISM. The mean metal mass fraction for a collection of gas is simply the total mass in metals within that gas divided by the total gas mass. For a collection of $i$ distinct, homogeneous, parcels of gas, the mean metal mass fraction 
\begin{equation}Z_{\rm gas} =  \Sigma_i Z_iM_{{\rm gas},i} / \Sigma_i M_{{\rm gas},i}, \end{equation}
where $M_{{\rm gas},i}$ is the mass of the $i^{\rm th}$ parcel of gas, and $Z_{i}$ its metal mass fraction. A completely homogeneous ISM would have a $\delta$-function metal mass fraction PDF located at the mean metal fraction: $p(Z) = \delta(Z_{\rm gas})$. Metal mixing in real galaxies does not produce perfectly homogeneous distributions, but rather tends towards a Gaussian at long timescales \citep[e.g.][]{EswaranPope1988}; a "well-mixed" medium will still have non-zero spread. Here we would like to characterize how this spread evolves for single enrichment sources. In particular, we characterize how well the assumption of instantaneous, homogeneous mixing---commonly adopted in one-zone chemical evolution models---describes actual abundance evolution in a low mass dwarf galaxy.

%By definition, then, a homogeneous distribution will have zero spread, for any definition of spread
%such as the interquartile range (IQR) and the mean-median difference. 
%Non-uniform enrichment in a homogeneous medium will increase both of these quantities, while mixing in a non-uniform medium will tend to decrease each.

%One-zone models of galactic chemical evolution track the mean gas abundance---not the median---even though the median is more indicative of the abundance of a typical parcel of gas.

\subsection{Abundance PDFs}
\label{sec:PDF}
We begin by examining in Figure~\ref{fig:CNM-PDFS} the probability distribution functions (PDFs) and the corresponding cumulative distribution functions (CDFs) of the tracer metals at the same times as Figure~\ref{fig:mixing_panel} and Figure~\ref{fig:mixing_panel2}. We focus on the cold neutral medium---the source of star forming gas---as it dominates the total mass fraction in the disk of this galaxy. In each panel, the median mass fraction is denoted by the downwards pointing arrow, while the mean is denoted by the upwards triangle. Initially---in all cases---nearly all of the gas in the galaxy contains arbitrarily little tracer metal mass as it it confined to a relatively small volume. However, this rapidly evolves, forming a broad distribution over many orders of magnitude in tracer metal abundance with no clear distinct enriched and un-enriched components.\footnote{At early times the rate at which this occurs is controlled by the significance of numerical diffusion in our simulation. Therefore, this behavior depends on the exact numerical methods used to model with problem. While characterizing the numerical diffusion with an effective diffusion coefficient would aid in comparing to results across simulation methods, doing so in grid-based codes is possible only in very particular contexts \citep[see][]{deAvillez2002}.
}

Three general trends can be seen in these distributions: 1) the mean abundance evolves minimally after 10~Myr, corresponding to the timescale at which $f_{\rm ej}$ plateaus (Figure~\ref{fig:CGM_CNM}), 2) the mean abundance is greater than the median at all times, and by many orders of magnitude, and 3) higher energy injection events evolve more rapidly towards higher abundances with narrower distributions. We quantify further the time evolution of the width of these distributions in the next section.

\begin{figure*}
    \hspace*{-1.8cm}
  \includegraphics[width=1.2\linewidth]{CNM_PDF_histograms_marked}
     \hspace*{-1.8cm}
  \includegraphics[width=1.2\linewidth]{CNM_CDF_histograms_marked}  
  \caption{The averaged metal mass fraction PDF (top) and CDF (bottom) for each enrichment event at times corresponding to the spatial distributions in Figure~\ref{fig:mixing_panel} and Figure~\ref{fig:mixing_panel2} (we use 1.2~Myr here instead of 0.2~Myr since the initial PDF is effectively a delta function at zero abundance). The median value of each PDF is marked by the downward pointing arrow, and the mean is given by the upward pointing triangle (and is to the right of the median in all cases). 
  Median arrows are not shown when less than half the gas has been enriched above the initial abundance (10$^{-20}$). For brevity, we plot only the distributions in the CNM (see text). In both, the bin spacing is 0.2~dex.}
  \label{fig:CNM-PDFS}
\end{figure*}

\subsection{Spread}
\label{sec:spread}

We use two quantities to characterize the spreads of these distributions. Both show the same general trends with energy (as discussed below), but serve two purposes.
The difference between the mean and median metal abundances represents the difference between abundances assuming perfect homogeneous mixing (mean) and the abundance of a typical collection of gas (median) in the ISM. Due to numerical diffusion, this difference in our simulations is a rough lower limit on the offset between typical gas-phase abundances in an inhomogeneous ISM and that assumed in a one-zone model.  While informative, comparing this quantity across simulations and with real galaxies is not straightforward. To aid in this comparison, we also compute the root-mean-square (rms) abundance deviation for only gas enriched above a fixed fraction, 10$^{-5}$, of the mean abundance at any given time. The exact choice of this value is somewhat arbitrary, but provides a consistent basis for comparison across works. As in Section~\ref{sec:PDF}, we focus on inhomogeneity in the CNM alone.

% The mean-median difference provides a more immediate conceptual understanding of how metals are distributed in the ISM. We focus on characterizing the inhomogeneity of the tracer metals in our simulations using this difference. We note that this should not be directly interpreted to mean the same---or even be similar to---observed abundance spreads, which are often discussed in terms of standard deviation or min/max variation. Though it is necessary for this quantity to be zero for metals to be homogeneously distributed in a medium, we do note that it is not a sufficient condition (the mean of a symmetric distribution is equal to the median).

In Figure~\ref{fig:mean-median} we plot the time evolution of these measures of inhomogeneity for each source energy: the difference between log(mean) and log(median) (left, referred to as the mean-median difference for the remainder of this work), and the rms deviation of enriched gas (right). The evolution of the mean-median difference is easy to interpret conceptually. Enrichment in an initially pristine medium increases the mean-median difference by raising the mean metal fraction while keeping the median value fixed, so long as the newly enriched mass is a small fraction of the total gas mass. This is exactly the case for the enrichment experiments performed in this work. Conversely, preferential removal of metals from a medium will lower this quantity. Finally, the mixing of metal-rich gas elements with metal-poor will gradually bring the mean and median values to parity. The initial value for this spread is small in all cases, growing large (many dex) within the first 10~Myr. This delay is due to the different timescales over which most of the metals are incorporated into the cold gas, as shown in Figure~\ref{fig:ISM_CGM}. The large value of this spread is the result of the near-zero initial abundance of each tracer metal. Because of this, the exact magnitude of this initial spread is arbitrary, but it is its evolution---and how it compares across injection energies---that we are concerned with. The spread decreases significantly over the first 25~Myr or so, in part because metals are preferentially ejected from the ISM via outflows (lowering the average abundance, but leaving the median fixed) and in part due to mixing into the ambient ISM.

%For our numerical experiments, enrichment in the whole ISM only occurs once and ejection from the ISM is easy to follow. This allows for a cleaner interpretation of the evolution than examining the IQR or standard deviation of these distributions.

\begin{figure*}
  \centering
%  \caption{Time evolution of the difference (in dex) between the mean and the median metal mass fraction of each source in all of the ISM gas ({\em left}) and in the CNM only ({\em right}).}
\includegraphics[width=0.475\linewidth]{CNM_average_mean-median}
\includegraphics[width=0.475\linewidth]{CNM_average_rms}
\caption{The evolution of two measures of inhomogenity in the tracer abundances, the log(mean)-log(median) difference (in dex, left) and the rms deviation for all gas enriched to at least 10$^{-5}$ the mean abundance (right). At late times these two quantities are similar. Note the different vertical axis limits.}
  \label{fig:mean-median}
\end{figure*}

%In Figure~\ref{fig:mean-median} we examine the average behavior of the mean-median metal mass fractions for the whole ISM in each run (left) and the CNM only (right).

As shown qualitatively in Figures~\ref{fig:mixing_panel} and~\ref{fig:mixing_panel2}, the injection energy for a given source leaves an indelible impact on the subsequent evolution of those metals in the ISM. Metals from \runone E46 are significantly less well-mixed than their higher-energy counterparts, \runone E51 and \runone E52. The evolution of this spread is qualitatively similar for the CNM. Across injection energies, there is an initial phase of more rapid mixing from the expansion of the initial injection event (most dramatic for \runone E52). Afterwards, mixing proceeds more slowly as the tracer metals diffuse throughout the galaxy via turbulent mixing in the ISM. The exact slope of this evolution is different for each event energy, and is more rapid for the higher energy events. Generally, these spreads appear to approach a plateau in their evolution, as most obvious in \runone E52. It is unclear if this value (about two dex in the CNM for \runone E52) will be the same for all energies, or at exactly what timescale it is reached for the lower energy events.

\begin{figure}
  \centering
\includegraphics[width=0.95\linewidth]{CNM_enriched}
\caption{The fraction (by mass) of the CNM that is enriched to within 10$^{-5}$ or more of the mean abundance for each enrichment source as a function of time.}
  \label{fig:enrichment_fraction}
\end{figure}

In the right hand panel of Figure~\ref{fig:mean-median} we isolate the inhomogeneity within enriched gas alone. Unlike the mean-median difference, this quantity exhibits significantly less evolution in each case. Ignoring the initial spike within the first Myr, the rms deviation decreases by---at most---a dex in each case. However, this quantity is still large, exceeding two dex. In general, the spreads here are ordered by energy, with higher energy events having a smaller spread, but the evolution of the lower energy events ($\leq$10$^{50}$~erg) are much closer to one another, and even intersect towards the end of the simulation time. At no point can any of these distributions be considered well-mixed within the 150~Myr simulation time, using either measure of inhomogeneity. Comparing these two measures of abundance spreads, it is clear that the different enrichment energies drive how much of the galaxy (by mass) is enriched to abundances near the mean tracer abundance. We confirm this in Figure~\ref{fig:enrichment_fraction}, which shows the enriched fraction---the mass fraction of gas in the CNM with abundance greater than 10$^{-5}$ times the mean abundance---for each source as a function of time. The enriched fraction is greater for higher energy enrichment events, driven predominantly by the initial growth of this quantity during the first $20-25$~Myr or so. After this point, the rate at which gas becomes enriched above 10$^{-5}$ times the mean is roughly the same across enrichment energies.

We emphasize that these results show the behavior of metal enrichment from \textit{single} enrichment events over time. The mean-median / rms differences seen at the end of the simulation here are significant ($\sim$ 2--5 dex and $\sim$1.8--2.5 dex respectively). Our previous analysis of the total metal enrichment of all sources in this galaxy presented in \cite{Emerick2018b} found much smaller values: $\sim$0.2 dex for elements released in core collapse SNe and $\sim$0.5--0.8 dex for elements released in AGB winds. The only difference here is that the latter two values represent the abundance spreads obtained considering the ongoing contribution of many sources over the entire galaxy. As expected from prior works, this suggests that how common, how evenly, and how widely (spatially) distributed enrichment events are in a galaxy is an important determinant of abundance homogeneity. We demonstrate this point in Figure~\ref{fig:combined spread} by plotting the mean-median abundance difference for the total tracer metal fractions from all 19 \runone E46 events (see caption for more details), as compared to the averaged behavior as shown previously. The mean-median difference for the combined tracer (solid lines) is significantly lower than the typical value for a single source, dropping even below the spread seen in the highest energy single event. However, the rms deviation of enriched gas (dashed lines) is similar in both cases. The enrichment event frequency and distribution throughout the galaxy significantly affects the scatter in the associated abundances by changing the fraction of the ISM that is enriched.

\begin{figure}
  \centering
  \includegraphics[width=0.975\linewidth]{combined_mean-median}
  \caption{A comparison of the log(mean)-log(median) difference (solid lines) and the rms deviation (dashed lines) for the combined tracer metals of all 19 \runone E46 events (blue) to the typical behavior of a single event (the average of all 19, black). The combined field is computed by summing over the individual tracer fractions in each cell in the simulation, and thus represents the enrichment evolution of 19 identical, simultaneous events spread over the entire galaxy.}
  \label{fig:combined spread}
\end{figure}

\subsection{Event-by-Event Variation}
\label{sec:individual event variation}

For clarity we have focused on the \textit{mean} evolution of individual enrichment events at fixed injection energy. We turn now to discuss how much variety exists among these individual events. For each run from set \runonenu, Figure~\ref{fig:CGM_CNM_variance} shows the fraction of event tracer metals ejected from the galaxy (left), the fraction of metals in the ISM within the CNM (center), and the mean-median difference (right, black) and the rms deviation of enriched gas (right, blue) 75 Myr after each enrichment event. The median values at each energy are shown as points, while the error bars denote interquartile range (IQR). With the exception of the rms deviation of enriched gas, there is substantial variation at each energy for these quantities, with greater variation at lower energies. The similar spreads in enriched gas for different enrichment events suggests that abundance spreads in the ISM---once enriched---are driven predominantly by global galactic properties and not the details of the enrichment itself. Although there is a general trend in each of these quantities with injection energy, it is clearly not the only determining factor in the evolution of the tracer metals from each source. We investigate the dependence on a few of these properties below.

 \begin{figure*}
   \centering
   \includegraphics[width=0.975\linewidth]{combined_rms_Eej_CNM_avg}
   \caption{The variance in the fractions of metals ejected $f_{\rm ej}$ and retained in the CNM $f_{\rm CNM, ISM}$ (Fig.~\ref{fig:CGM_CNM}), and the mean-median separation and rms deviation of enriched gas (Fig.~\ref{fig:mean-median}). The rms deviation of enriched gas is plotted with a slight horizontal offset for clarity. There is significant variation in each quantity at fixed injection energy, with the exception of the rms deviation of enriched gas. We give the median values for each quantity at each energy (squares) at 75~Myr after the injection event, while the error bars represent the IQR at each energy. We show the results from \runone E52\_r0 and \runone E52\_r300 as individual points and do not estimate their IQR.}
   \label{fig:CGM_CNM_variance}
 \end{figure*}

\subsection{Dependence on Radial Position}
\label{sec:radial position}
We place each source at regular, but arbitrary, positions in the galaxy without consideration for the local ISM conditions at injection. Sources are placed at the center of the galaxy ($r = 0$~pc) or at various radii (at cardinal positions at 300~pc, and 600~pc), all in the mid-plane of the galaxy. Since the E46 events were likely to not self-interact, we additionally placed events at $r = 100$~pc and one event at each $r$ at about one scale height above the disk ($z = 50$~pc). For each \runonenu~run, we plot $f_{\rm ej}$, $f_{\rm CNM, ISM}$, and the mean-median difference as a function of radial position in the galaxy for each event---averaging over energy---in Figure~\ref{fig:radial position}. We do not consider the events above the mid-plane here since they sampled only a single injection energy.

\begin{figure*}
   \centering
   \includegraphics[width=0.95\linewidth]{Eej_rms_combined_radial_dependence}
   \caption{The dependence of $f_{\rm ej}$, $f_{\rm CNM, ISM}$, and the abundance spread on the radial position of each event at 75~Myr after injection as averaged over injection energy. As in Figure~\ref{fig:CGM_CNM_variance}, the points give the median at each radius and the error bars show the IQR.}
   \label{fig:radial position}
 \end{figure*}

The dependence of each of these quantities on the radial position is interesting. The ejection fraction $f_{\rm ej}$ increases with radius until the outermost edge, with significant spreads at each position. Star formation and the cold gas distribution in this galaxy is not uniformly distributed throughout the evolution, as can be seen in the number density panels of Figure~\ref{fig:mixing_panel}. Most of the star formation and feedback during this period occurs off-center from the galaxy, closer to the inner edge of the ring of dense clumps, and little to no star formation occurs at the outer edge. The increase of $f_{\rm ej}$ at intermediate radii could be explained by stronger feedback and outflows at these points that drive out metals. With this picture in mind, it is interesting that f$_{\rm CNM, ISM}$ decreases with radius, even though the outer region of the galaxy contains the most cold gas. This behavior stems from the E50 and E51 events (E46 and E49 show flat trends in median $f_{\rm CNM, ISM}$ with radius). 
Finally, the right panel shows that the galaxy-wide mean-median difference is not well correlated with position, with the exception of the farthest radius which is significantly less well mixed than events towards the inner galaxy. As in Figure~\ref{fig:CGM_CNM_variance}, the rms deviation of enriched gas does not show significant variations at fixed radii, but does show a very slight trend, decreasing with radius.

\subsection{Variation with Local ISM Conditions}
\label{sec:ISM density}

We compute the average ISM properties within a four-zone radius ($4~dx $~=~7.2~pc) around each injection site to examine any potential correlations in evolution with ISM properties. This fully envelopes the injection region for each event (a three-cell radius sphere mapped onto the grid with a cloud-in-cell interpolation scheme). In Figure~\ref{fig:ISM_variance} we plot $f_{\rm ej}$, $f_{\rm CNM, ISM}$, and the mean-median difference as a function of the average number density $\langle n \rangle$ in this region within 0.1~Myr (our time resolution) of the event. The ejection fraction $f_{\rm ej}$ is typically highest at low densities ($\log(n ~[\rm{cm}^{-3}]) < -1$). Metals ejected into this phase for higher energy events are less likely to be trapped by colder, dense gas, and more likely to be swept up in outflows from SN feedback; this value decreases significantly just above $\log(n ~[\rm{cm}^{-3}]) = -1$, and spikes again at the highest densities. At these high densities, gas is more likely to be star forming; feedback from newly formed stars readily removes the tracer metals from the galaxy. Interestingly $f_{\rm CNM,ISM}$ appears to be relatively independent of ISM density. The same processes that drive the trend in $f_{\rm ej}$ can explain the observed trend in the mean-median difference. Metals are more easily mixed when injected into low density gas, which allows for a larger initial expansion of the enrichment event and better coupling to the turbulent motions from stellar feedback; this is except for the highest density which, again, is affected by nearby star formation.

 \begin{figure*}
   \centering
   \includegraphics[width=0.95\linewidth]{combined_rms_n_dependence}
   \caption{The variation of $f_{\rm ej}$, $f_{\rm CNM, ISM}$, and the spread of the metal fraction PDFs in the ISM as a function of the average local ISM number density ($n$) within the injection region of the event just prior (within 0.1~Myr) of the event. Results are binned using 1~dex bins in $n$. Points show the median value in each $n$ bin and error bars show the IQR (same as Figure~\ref{fig:CGM_CNM_variance}.)}
   \label{fig:ISM_variance}
 \end{figure*}

\subsection{Variation with SFR}
\label{sec:SFR}
Finally, we examine the companion run (\runtwonu) to see if the global SFR of the galaxy drives variation in these results. The correlation with SFR is of interest not because the formation of stars by themselves affects metal evolution, but rather the increase in feedback associated with a higher SFR (and thus a warmer / hotter ISM, greater turbulence in the ISM, and more significant outflows). We compare these two runs in Figure~\ref{fig:SFR_comparison_CGM_CNM}, showing runs from \runonenu~in as solid lines at higher concurrent SFR and runs at the lower SFR, \runtwonu, as dashed lines. $f_{\rm ej}$ increases much more rapidly across injection energies in \runonenu. However, this value seems to be similar across runs for E49 and E51 by $\sim$50 Myr, with an additional increase again in the \runonenu~simulations towards the end of the time. This initial spike, lull, and second increase corresponds to the period of active star formation, slight lull, and increase in SFR experienced during the \runonenu~simulations; the lull occurs between 40 and 80 Myr after the enrichment events. The SFR is consistently low (or zero) throughout \runtwonu. Although E49 and E51 exhibit similar behavior across global differences in SFR, the difference in E46 is significant throughout the examined time period. As these sources do not contain enough energy to eject their metals from the galaxy by themselves, they are only ejected from the galaxy by being swept up in the ISM during other feedback events. The evolution of these events are therefore much more dependent upon the global galaxy properties.

The fraction of metals contained within the CNM of the ISM does not seem to depend too strongly on the SFR, unlike $f_{\rm ej}$. It is generally true that after the initial $\sim$50 Myr of enrichment, a greater fraction of the metals in the ISM are contained in the CNM during the run with the lower SFR (\runtwonu), but this difference is not large and is only significant for the higher energy events. In addition, the mass fraction of the CNM is greater during run \runtwonu~than in run \runonenu, so it may simply be that the long-term evolution of the fraction of metals in the CNM is more dependent upon the phase structure of the ISM---which is regulated by stellar feedback---than the feedback directly.

\begin{figure*}
  \centering
  \includegraphics[width=0.45\linewidth]{combined_CGM_average_evolution}
  \includegraphics[width=0.45\linewidth]{combined_CNM_average_evolution}\\
  \includegraphics[width=0.45\linewidth]{combined_CNM_average_mean-median}
   \includegraphics[width=0.45\linewidth]{combined_CNM_average_rms}
  \caption{The same as Figure~\ref{fig:CGM_CNM} and Figure~\ref{fig:mean-median}, but comparing across both sets of runs with different SFRs. Line color corresponds to a fixed enrichment energy event, while the solid lines correspond to the higher SFR runs discussed throughout this work, and the dashed lines the lower SFR runs. See text for more details.}
  \label{fig:SFR_comparison_CGM_CNM}
\end{figure*}

Finally, examining the last two panels of Figure~\ref{fig:SFR_comparison_CGM_CNM}, it does appear that the mixing efficiency of metals for each source increases with increasing global SFR. In the initial evolution, all events in run \runtwonu~exhibit larger abundance spreads that take longer to begin mixing substantially than their counterparts in \runonenu. In general, \runtwonu~abundances remain larger for the first 100~Myr. The differences depend on the ejection energy, with the most significant difference found in comparing the E46 runs.
% May need more text here

\section{Discussion and Conclusions}
\label{sec:discussion conclusion}

Galactic chemical evolution is far from single zone and metal mixing is clearly neither homogeneous nor instantaneous. As demonstrated in recent works \citep{Safarzadeh2017,Emerick2018b,KrumholzTing2018}, the properties of metal mixing in the ISM of various galaxies depends upon the characteristics of the individual sources. The energy of each source sets the thermal phase to which these metals couple to most effectively, and the volume over which they are initially injected before additional mixing by global galactic dynamics begins to dominate. In short, lower energy enrichment events, like those from AGB winds, mix much more slowly throughout the ISM than metals from higher energy events, like SNe. As found in \cite{Emerick2018b},
this difference is still present even when accounting for the fact that AGB events are both more common and evenly distributed in the galaxy than SNe.

We confirm the average trends found in previous works that sources with lower $E_{\rm ej}$ have larger abundance spreads in the ISM and lower ejection fractions, on average \citep{KrumholzTing2018,Emerick2018b}.%
% might be a couple more?
\footnote{Interestingly, \cite{Safarzadeh2017} finds that the resulting abundance patterns in a UFD candidate at high redshift are generally insensitive to the energy of the injection event. However, they focus on enrichment events from a smaller range of injection energies: 10$^{50}$ - 10$^{51}$ erg.}
We additionally find that $E_{\rm ej}$ of the event and the global SFR during the time at which the event occurs produce the greatest variation in how many metals are retained by the galaxy, what fraction of those metals are contained within the CNM, and their homogeneity. Metals are in general ejected more effectively and mix more efficiently during periods of higher SFR than lower SFR, corresponding to periods of more effective galactic outflows and greater turbulence in the ISM. Although we have limited statistics to determine a conclusive trend, we generally find that neither the radial position of the event nor the local ISM density in which the event occurs has a significant effect on the average behavior of enrichment events, with the exception of the lower energy (E46) events.

 However, we find that the evolution of individual events can vary dramatically depending on the combination of each of these factors. This suggests that it would be challenging to make any conclusive statements about the enrichment behavior of single enrichment events. This is problematic for interpreting the chemical abundances in individual UFDs with abundance patterns that can be explained by a single, exotic enrichment event. Using these observations to constrain the total nucleosynthetic yields of these sources requires implicit assumptions about how quickly metals are available in star forming gas, how homogeneously they are distributed throughout the galaxy, and what fraction are ejected from the galaxy. It is likely that none of these quantities can be determined as simple parameters based upon the feedback properties of a single enrichment source or even the global properties of a galaxy. However, this study has shown that these parameters can be characterized in an averaged sense, even though the exact result is subject to substantial stochastic effects. Although interpreting the abundances of individual galaxies may be problematic, observations of stars across many UFDs with signatures of single, rare enrichment events might be leveraged to identify consistent trends. This, combined with one-zone models with paramaterization for these stochastic variations can be used to understand the possible outcomes for populations of these galaxies. Developing such a model will be a powerful tool for interpreting the irregular stellar abundance patterns observed in low mass dwarf galaxies in the nearby Universe.

Our results suggest that the spreads of stellar abundances at low metallicities may offer valuable insight into the origin of those metals. Lower energy events should generate larger abundances spreads than more energetic sources, as will particularly rare events. For example, $r$-process enrichment from exotic enrichment events like HNe should manifest itself as significantly more well-mixed than if the elements originated in lower energy NS-NS mergers. Unfortunately, the degeneracy between source energy and event frequency / distribution may make distinguishing different sources in observed stellar abundances challenging. However, the much more efficient expulsion of metals by high energy events might be able to break this degeneracy. Given these complications, turning these results into unique observational predictions requires further work. While the lowest mass, most metal poor dwarf galaxies are ideal environments to conduct this analysis, they typically only have a few to tens of measured stellar abundances. For better statistics, larger low-mass dwarfs, like Ursa Minor, Draco, Sextans, Sculptor, Carina and Fornax \citep[e.g][]{Suda2017,Duggan2018,Skuladottir2019}, and the low-metallicity stellar halo of the Milky Way \citep[e.g.][]{Hansen2018,Sakari2018} are likely the best regimes to try and use stellar abundances to infer the nucleosynthetic origin of elements and metal mixing properties in the ISM.

Our simulated galaxy lies in the regime where the turbulent driving is generated almost exclusively by supernova explosions (as opposed to gravitational driving from the inflow of gas, for example). Following the discussion in \cite{PanScannapiecoScalo2013}, mixing over the whole galaxy ($L_G$) must therefore occur slowly, as a random walk process of enrichment between individual, independent polluted regions in the galaxy on the transport timescale \begin{equation} \tau_{\rm trans} = L_{\rm G}^2 / (L_{\rm turb}v_{\rm rms}), \end{equation} 
where $L_{\rm turb}$ is the turbulent driving scale, comparable here to the typical size of a supernova remnant. Roughly, $L_{\rm G} \sim 1~{\rm kpc}$, $L_{\rm turb} \sim 100~{\rm pc}$, and $v_{\rm rms} \sim 10~{\rm km}~{\rm s}^{-1}$ for our galaxy, giving a mixing / transport timescale of $\sim$~1~Gyr. Our results, demonstrate that, for single enrichment sources, the mixing timescales are indeed quite long, with significant abundance variations remaining after 150~Myr of simulation time. For this reason, the frequency of enrichment events and their spatial distribution are key drivers of abundance homogenization in this regime, as demonstrated here. In addition, we find agreement with the analytic model in \cite{KrumholzTing2018} that the size of the initial enrichment region---which is directly correlated with injection energy---also determines the relative scatter in abundances throughout the ISM.

Current state-of-the-art semi-analytic models of galactic chemical evolution cannot readily capture the complex hydrodynamics effects governing the metal mixing process examined in this work. However, incorporating these effects could stand to dramatically improve the ability for these models to match not only the mean trends observed in stellar abundance patterns, but also their spreads. In turn, this could help better leverage these observations to understand both the nucleosynthetic origin of various elements, and also the properties of turbulent metal mixing operating within the ISM. We plan to incorporate the understanding gained from this work in such a model in future work.

%\acknowledgments
\section*{Acknowledgments} We would like to thank Brian O'Shea, Benoit C{\^o}t{\'e}, Kathryn V.~Johnston, and Jason Tumlinson for valuable discussions and comments on a previous version of this work which appeared as a chapter in the first author's dissertation. In addition, we thank the anonymous referee whose comments have significantly improved this work. AE was supported by a Blue Waters Graduate Fellowship. GLB acknowledges support from NSF grants AST-1615955 and OAC-1835509 and NASA grant NNX15AB20G. M-MML was partly supported by NSF grant AST18-15461. We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages. These are products of collaborative effort by many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible.

\software{\textsc{yt} \citep{yt}, \textsc{Enzo} \citep{Enzo2014}, \textsc{Grackle} \citep{GrackleMethod}, \textsc{Python} \citep{VanRossum1995python}, \textsc{IPython} \citep{perez2007ipython}, \textsc{NumPy} \citep{oliphant2006guide}, \textsc{SciPy} \citep{SciPy}, \textsc{Matplotlib} \citep{hunter2007matplotlib}, \textsc{HDF5} \citep{Fortner1998HDF,Koranne2011}, \textsc{h5py} \citep{h5py}, \textsc{Astropy} \citep{astropy:2013,astropy:2018}, \textsc{Cloudy} \citep{Cloudy2013}, and \textsc{deepdish}}

%************* APPENDICES ************************%

%\section*{Acknowledgments}

%\clearpage
%\appendix - Liklely DO NOT use this command
%\setcounter{section}{0}%
%\renewcommand\thesection{\thechapter.\Alph{section}}
%\counterwithin{figure}{section}

%
% Place appendix here
%

\bibliographystyle{yahapj}
\bibliography{refs}

\end{document}

### 2021-01-19 phsyics_evolution/main.tex
backup

% mm comments and significant changes noted like this.

%rnaastex.cls is the classfile used for Research Notes. It is derived
%% from aastex61.cls with a few tweaks to allow for the unique format required.
%% (10/15/17)
%% (01/08/18)
\documentclass[twocolumn]{aastex62}
%\pdfoutput=1 %for arXiv submission
\usepackage{amsmath,amstext}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
%\usepackage{deluxetable}

\renewcommand*{\sectionautorefname}{Section} %for \autoref
\renewcommand*{\subsectionautorefname}{Section} %for \autoref

% citation for method paper
\newcommand{\methodpaper}{Paper I}

% line colors
\newcommand{\fiducialstyle}{black}
\newcommand{\snionstyle}{orange}
\newcommand{\snpelwstyle}{red}
\newcommand{\snonly}{dark red}

\newcommand{\shortradstyle}{light orange}
\newcommand{\RPzerostyle}{yellow}

\newcommand{\radstyle}{light blue}
\newcommand{\ionstyle}{blue}
\newcommand{\pelwstyle}{dark blue}

\newcommand{\sfrunits}{M$_{\odot}$~yr$^{-1}$}

\newcommand{\HI}{HI}

%comment commands:
\newcommand{\aje}[1]{\textcolor{blue}{\textbf{(AJE: #1)}}}
\newcommand{\changed}[1]{\textcolor{black}{\textbf{(AJE-update): #1}}}

%% Define new commands here
\newcommand\latex{La\TeX}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
%\graphicspath{{./}{figures}}

\begin{document}

\title{The Role of Stellar Feedback in the Chemical Evolution in a Low Mass Dwarf Galaxy}

%% Note that the corresponding author command and emails has to come
%% before everything else. Also place all the emails in the \email
%% command instead of using multiple \email calls.
\correspondingauthor{Andrew Emerick}
\email{aemerick@carnegiescience.edu}

%\author{}
%\altaffiliation{}
%\affiliation{}
%% The \author command can take an optional ORCID.
\author[0000-0003-2807-328X]{Andrew Emerick}
\altaffiliation{Carnegie Fellow in Theoretical Astrophysics}
\affiliation{Carnegie Observatories, Pasadena, CA, 91101, USA}
\affiliation{TAPIR, California Institute of Technology, Pasadena, CA, 91125, USA}
\author[0000-0003-2630-9228]{Greg L. Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10010, USA}
\author[0000-0003-0064-4060]{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, 10024, USA}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10010, USA}

\keywords{Galaxy chemical evolution -- Dwarf galaxies -- Chemical enrichment -- Hydrodynamics}

\begin{abstract}
Using a suite of high-resolution simulations, we investigate how each aspect of a multi-channel stellar feedback model drives the evolution of a low-mass, isolated dwarf galaxy. Our model for star formation and stellar feedback follows individual star particles sampled randomly from an adopted initial mass function, considering independently feedback from: massive star stellar winds, AGB winds, photoelectric heating of dust grains from stellar far-ultraviolet radiation, H$_2$ dissociation from stellar Lyman-Werner radiation, and ionization, ionization heating, and radiation pressure from stellar radiation as traced with a ray-tracing radiative transfer method. We consider the effects each of these processes have on regulating the star formation rate, global gas properties and morphologies, the multi-phase interstellar medium (ISM), and driving galactic winds. In addition to total metallicity, we follow individual metal species from distinct nucleosynthetic channels (AGB winds, massive star stellar winds, core collapse supernovae, and Type Ia supernovae) and pay particular attention to how these feedback processes regulate turbulent metal mixing in the ISM, the metal content of galactic outflows, and the stellar abundances patters in our dwarf galaxy. In summary, we find that -- for a low-metallicity, low-mass dwarf galaxy -- stellar radiation, particularly ionizing radiation and H$_2$ dissociation from LW radiation, are important sources of stellar feedback whose effects are subdominant to photoelectric heating and HI radiation pressure. However, these feedback channels are coupled non-linearly, and the inclusion / exclusion of each does have non-neglible effects on particular properties of our galaxy.
\end{abstract}

\section{Introduction}

It is clear that the complex, multi-physics story of galaxy evolution is driven significantly by stellar feedback. Feedback processes regulate the formation of stars by destroying cold, star-forming gas, providing thermal pressure support and energy to prevent gas from cooling and collapsing into star-forming regions, and by driving metal-rich outflows (see \citet{Zhang2018} for a recent review), depleting galaxies of the gas required to form more stars. In addition, stellar feedback helps to drive turbulence in the interstellar medium (ISM) of galaxies, which in turn helps to mix new metal enrichment from stellar winds and supernovae in the ISM, driving galactic chemical evolution, and regulates the phases of galaxies' multi-phase ISM. The successes of modern theoretical models of galaxy evolution (see \citet{Vogelsberger2020}) are owed in large part to advances made in modelling the complex process of stellar feedback (see \citet{SomervilleDave2015} and \citet{NaabOstriker2017} for recent reviews). It has become evident that supernovae feedback alone -- a significant source of thermal and kinetic energy and momentum feedback in galaxies -- is insufficient for fully modelling the evolution of galaxies. This has driven the push for models of multi-channel stellar feedback which may include models for stellar winds, stellar radiation, and cosmic rays in addition to supernovae (give some references) \citep[e.g.][]{FIRE2,Hopkins2020}. However, the complexities in following each of these processes has precluded the development of a fully self-consistent model for multi-channel stellar feedback capable of faithfully reproducing all galaxy properties. 
%In particular, how stellar feedback couples to the multi-phase ISM and

In pursuing this goal, high-resolution simulations of galaxy evolution capable of resolving the effects of individual feedback processes are required. The small physical sizes, low star formation rates, and relative simplicity of low-mass dwarf galaxies offers a computationally feasible regime to explore different mechanisms of stellar feedback. Simulations of dwarf galaxies have been used extensively in recent literature for this exact purpose. These models have been used to determine the efficacy of various mechanisms for depositing the energy and momentum associated with supernova feedback \citep{Smith2018b,Hu2019}, the importance of discrete, stochastic sampling of the initial mass function (IMF) in modelling individual supernova explosions \citep[e.g.]{Revaz2016,Su2018,Applebaum2020}, the role of various forms of feedback in driving metal-rich galactic winds and dwarf galaxy self-quenching \citep[e.g.][]{MacLowFerrara1999,RecchiHensler2013,Robles-Valdez2017}, with recent focus particularly on the lowest mass dwarf galaxies \citep[e.g.][]{Bland-Hawthorn2015,Cashmore2017,Romano2019}, the role of photoelectric heating in concert with other mechanisms for stellar feedback in regulating star formation and the warm, neutral ISM in dwarf galaxies \citep{Forbes2016,Hu2015,Hu2017}, the importance of ionizing radiation and radiation pressure in driving dwarf galaxy evolution \citep[e.g.][]{WiseAbel2012, Emerick2018a, Agertz2020}, feedback from high-mass X-ray binaries \citep{Artale2015,Garratt-Smithson2019}, momentum injection from resonant Ly$\alpha$ scattering \citep{Kimm2018}, the role of cosmic rays in dwarf galaxy evolution \citep[e.g.][more]{Chen2016}, and how stellar feedback drives turbulent metal-mixing in dwarf galaxies \citep[e.g.][]{Ritter2015,Corlies2018}.

The general conclusions from these studies are that stellar feedback in low-mass dwarf galaxies is effective, driving significant, metal-rich galactic winds. While SNe are perhaps the dominant mechanism by which these winds are driven, these works demonstrate that a feedback phase before the first supernova occurs in a star formation event ($\sim$ 40~Myr) is a critical component to a complete model for stellar feedback. Stellar radiation (e.g. ionization, ionization heating, radiation pressure, photoelectric heating, and Lyman-Werner dissociation of H$_2$) and, to a lesser degree, stellar winds, are important sources of this pre-SNe feedback. Not only do these processes help regulate star formation, ISM properties, and drive outflows in their own right, but these works demonstrate that they couple non-linearly to SNe feedback, decreasing he typical densities and modifying ISM structure within which SNe explode, increasing their effectiveness.

In spite of this progress in our understanding of the role of stellar feedback in galaxy evolution, there remains gaps in our understanding. \textbf{Motivate why we need another study (mine) of this... maybe just motivate attention to chemE here}.

%\citet{Hu2015,Hu2017} SNe, radiation, PE heating
%\citet{Hu2019} individual SN models
%\citet{Forbes2016} PE heating
%\citet{WiseAbel2012} Radiation pressure
%\citet{Su2018} discrete IMF sampling in dwarfs
%\citet{Applebaum2020} discrete IMF sampling
%\citet{Agertz2020} special focus on this. with / without RT
%\citet{Kimm2018}
% ------------------ \citet{Lahen2020} detailed Hu-feedback + clusters in DG merger but no explicit testing of feedback model
% \citet{Smith2018a} \citet{Smith2018b} high res dwarfs with different models for SN feedback, concluding that other processes are important
%-------------- \citet{Koudmani2019} AGN in dwarfs

%\citet{Garratt-Smithson2019} defs summarize 
% \citet{Romano2019}

%more massive galaxies:
%FIRE (obviously)
%\citet{Benincasa2019} (and 2016?) FUV in MW galaxy. FUV alone doesn't work, but does drive WNM and leads to "softer" feedback than SN alone while still getting right masses.

%reviews:
%winds \citet{Zhang2018}
%\citet{Vogelsberger2020} defs cite somehow

This work builds upon the simulations presented in \citet{Emerick2019} (hereafter, \methodpaper) by examining in greater detail the effects of each component of our multi-channel model for stellar feedback. Our fiducial model follows star formation using individual star particles, capturing the feedback from massive star stellar winds, AGB winds, H~I and HeI ionizing radiation followed with ray-tracing radiative transfer, HI radiation pressure, photoelectric heating from far-ultraviolet (FUV) band radiation, H$_2$ dissociation from Lyman-Werner band radiation, and core collapse and Type Ia supernovae. In \citet{Emerick2018a}, we investigate the impact stellar ionizing radiation has on regulating the star formation and driving outflows in our simulated dwarf galaxy by comparing our fiducial simulation to a run without ionizing radiation and a run with only localized (within XX~pc of a massive star) ionizing radiation feedback. Expanding this analysis significantly, in this work we utilize a suite of 15 simulations which turn on / off each of these processes and examine how each drives the evolution of a low-mass ($M_{\rm vir} \sim 10^{9}$), isolated dwarf galaxy. Complimenting previous works in this regime, we pay unique attention to the role these feedback processes have on driving the individual gas-phase and stellar abundance patterns in our simulated galaxy.

\section{Methods} 
\label{sec:methods}
We refer the reader to Paper I for a detailed description of our numerical methods, initial conditions, and feedback and chemical evolution model. We briefly summarize the key components of these methods most relevant to this work below.

We follows the evolution of an idealized, isolated, low-mass dwarf galaxy with an initial gas mass of $M_{\rm gas} = 1.80 \times 10^6$~M$_{\odot}$ initialized as an exponential disk with radial and vertical scale heights of 250~pc and 100~pc respectively. This galaxy is embedded in a static, \cite{Burkert1995} dark matter potential with virial mass and radius $M_{\rm vir} = 2.48\times 10^{9}~M_{\odot}$ and $R_{\rm vir}~=~27.4$~kpc. This is evolved using the adaptive mesh refinement hydrodynamics code \textsc{Enzo} \citep{Enzo2014}, with a minimum/maximum spatial resolution of 921.6~pc / 1.8~pc in the simulations presented in Paper I. Due to computational constraints, we were unable to perform this study at full resolution, and instead adopt 3.6~pc as the maximum resolution. We refer the reader to the resolution studies comparing maximum resolutions of 1.8~pc, 3.6~pc, and 7.2~pc performed in Paper I and \cite{Emerick2018b}. % I may need to say more here about what exactly the resolution studies show. Mostly 1.8 / 3.6 is OK but definitely large difference moving to 7.2 pc. 
The grid is refined to maintain a mass resolution of 50~M$_{\odot}$ per cell, and to ensure that the Jeans length is resolved by at least eight cells. In addition, a three-zone radius region around any star particle that has active feedback (stellar winds or SNe) is refined to the maximum grid resolution. We use the chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to solve a nine species non-equillibrium chemistry model that includes gas-phase and dust H$_2$ formation, a uniform UV background, and localized self-shielding. This galaxy has an initial total metal mass fraction of $5.4 \times 10^{-4}$ (or $0.03 Z_{\odot}$ taking $Z_{\odot}$ = 0.018 from \cite{Asplund2009}). We follow the evolution of 15 individual metal species, C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba, whose initial mass fractions are initialized to near-zero (10$^{-20}$). Only the total metallicity affects the physics in our simulation, not the individual metal abundances.

\subsection{Star Formation and Stellar Feedback}
\label{sec:sf feedback}

Our simulation stochastically forms star particles in dense gas ($n > 50$~cm$^{-3}$ in the 3.6~pc resolution runs presented here) by randomly sampling a \cite{Salpeter1955} IMF and depositing individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$. For stars above 8~M$_{\odot}$, we follow their H~{\sc i} and He~{\sc i} ionizing radiation using the adaptive ray-tracing radiative transfer method of \cite{WiseAbel2011}, and trace their radiation in the Lyman-Werner and FUV bands using an optically thin approximation. These stars eject mass and energy over their lifetimes through stellar winds, and we include mass and thermal energy injection of both core collapse and Type Ia SNe. Stars below 8~M$_{\odot}$ have no feedback during their lifetime, except mass and energy deposition of their AGB winds at the end of their life. For stellar winds and SNe, mass, energy, and metals are injected to the grid by mapping a three-cell spherical region ($r=3 \times dx = 7.2~$pc) to the grid using a cloud-in-cell interpolation scheme. To reduce the significant computational expense of following a continuous source of hot ($T > 10^6$~K), fast ($v \sim 10^{3}$~km~s$^{-1}$) moving gas, we greatly reduce all stellar wind velocities to 10~km~s$^{-1}$. Given this reduction, we cannot make any strong statements as to the role of stellar wind feedback in the evolution of low mass dwarf galaxies.

Both HI and HeI ionizing radiation is followed using the adaptive ray-tracing radiative transfer method of \cite{WiseAbel2011} and coupled to the non-equillibrium chemistry and cooling / heating routines in \textsc{GRACKLE}. Stars in our simulation use the \textsc{OSTAR2002} \citep{Lanz2003} grid of O-type stellar models to compute the HI, HeI, FUV, and LW band fluxes as a function of stellar surface gravity and surface temperature. These latter two quantities, in addition to stellar radius, are taken as a function of mass and metallicity from the \textsc{Parsec} \citep{Bressan2012,Tang2014} grid of stellar models. For stars with stellar properties off of the \textsc{OSTAR2002} grid, we adopt the associated black body flux given the stellar surface temperature. The resulting black body fluxes were adjusted to produce a continuous curve of flux as a function of stellar mass, separately in each band. Rather than adopting fixed HI and HeI photon energies for each star, we adopt the average photon energy weighted by the associated black body curve in each band, leading to HI and HeI ionzing photon energies that span the range 13.6-22.5~eV and 25.0-32.5~eV respectively, depending on stellar surface temperature. We refer the reader to Appendix~B of Paper I which contains plots of each of these quantities. In our fiducial simulations, we include the effects of radiation pressure on \HI but ignore the absorption of ionizing radiation by dust and re-radiation in the infrared.

We assume FUV and LW band radiation are both optically thin, with local (cell-by-cell) attenuation. LW radiation causes $H_2$ dissociation, while FUV radiation leads to PE heating of dust grains. We follow the PE heating models from \cite{Wolfire2003} and assuming the dust-to-gas scaling with metallicity in \cite{Remy-Ruyer2014} which shows a significant decline in the dust content at low-metallicities ($Z < 0.1$~Z$_{\odot}$). Our photoelectric heating rate is given as
\begin{equation}
    \Gamma_{\rm PE} = (1.3 \times 10^{-24} \rm{erg s^{-1} cm^{-3}}) \epsilon n_{\rm H} G_{\rm eff} D
\end{equation}
where $\epsilon$ is an efficiency factor that in detail depends upon $G_o$, temperature, and the electron number density, but which we adopt to scale weakly with $n_{\rm H}$ (see Paper I), $D$ is the dust-to-gas ratio, and
\begin{equation}
    G_{\rm eff} = G_o \rm{exp}(-1.33\times 10^{-21} D N_{\rm H})
\end{equation}
is the locally-attenuated FUV flux. $G_o$ is the FUV flux normalized to the solar neighborhood \citep{Habing1968} and $D$ is normalized to the solar value, 6.617 $\times 10^{-3}$. This model is similar to that used in both \cite{Forbes2016} and \cite{Hu2017}, with the exception of the treatment of $\epsilon$ and $D$. However, we note that both of their galaxies were at or above the $Z > 0.1$~Z$_{\odot}$ threshold and therefore have a significantly higher (but still low) dust content. We do not account for $H^-$ photodetachment due to the ISRF, which plays an important role in producing $H_2$ in our low-metallicity, low-dust content galaxy. However, we find that this effect is likely subdominant as long as either ionization or LW radiation are followed (see Appendix E of Paper I).

\section{Simulations}
\label{sec:runs}

We present the 17 different simulations run varying feedback effects in Table~\ref{table:runs}. Each simulation turns on / off various feedback processes as shown in the table. In each case, supernovae and stellar winds are included as a pair in each simulation, though again we note that we do not fully capture the effects of stellar winds in our simulations. All runs contain the same total metal enrichment from SN, massive star stellar winds, and AGB winds. In runs without SN and stellar winds, the mass and metal ejecta from these channels are instead injected at low velocity (10 km~s$^{-1}$) with a thermal energy equal to the stellar surface temperature. All runs with ionizing radiation include radiation pressure on \HI, except when noted. We test the role of radiation pressure by varying its strength with a constant factor, turning it off in RPx0, and increasing it in RPx2, RPx5, and RPx10. The shortrad simulation is the same as the fiducial simulation, but photons are deleted once they have travelled more than 20~pc from their source. This is an attempt to approximate localized prescriptions for ionizing radiation feedback which only deposit energy / ionize gas in a localized region around a star particle. We examine the effects of stellar ionizing radiation in our high-resolution (1.8~pc) simulations in \cite{Emerick2018a}, comparing our fiducial run with a shortrad simulation and a simulation without ionizing radiation (i.e. SN+PE+LW), each at 1.8~pc resolution.

All simulations are restarted from the same output after the initial collapse phase of the galaxy and formation of the first star particles.\footnote{Due to minor updates to this version of \textsc{Enzo} and the master branch of \textsc{Grackle} since publication of \methodpaper, the 3.6~pc fiducial resolution simulation presented here was re-run in its entirety and is not the same showed in the Appendix of that work.} Therefore, each run starts with the same 38 initial stars, with total stellar mass of 100 M$_{\odot}$. Three of these stars are above the 8~M$_{\odot}$ threshold for radiation and CCSNe, the most massive of which is 11 M$_{\odot}$.

% but differs only in the assumed efficiency parameter ($\epsilon$). \cite{Forbes2016} adopts a constant $\epsilon$ (\aje{I'm not sure the exact value}) while \cite{Hu2017} uses the full temperature and electron number density ($n_e$) dependent form from \cite{Wolfire2003}. However, we do not follow the necessary carbon chemistry needed to accurately follow $n_e$ in dense, neutral regions. Instead, we adopt a weak power-law fit in $n_H$

\begin{deluxetable*}{c|c|c|c|c|c|c}
\label{table:runs}
\tablecaption{A list of the feedback physics included in each of our runs. In every case, metal enrichment from SNe and stellar winds are kept fixed. Runs with SNe and stellar winds turned off simply replace the proper energy injection with return equal to the stellar surface temperature. The Shortrad simulation does include full radiative transfer, but deletes photons once they have travelled 25~pc from their source. The final column lists the final run time of each simulation.}
\tablehead{
\colhead{Run Name} & \colhead{SN} & \colhead{Stellar Winds} & \colhead{Ionizing Radiation} & \colhead{PE Heating + LW Radiation} & \colhead{Radiation Pressure Factor} & \colhead{End Time (Myr)}
}
\startdata
 Fiducial  & Yes & Yes & Yes & Yes       & 1  & 750 \\
 SN+Ion+PE & Yes & Yes & Yes & PE only   & -  & 552 \\
 SN+Ion+LW & Yes & Yes & Yes & LW only   & -  & 626 \\ 
 SN+Ion    & Yes & Yes & Yes & No        & 1  & 750 \\
 SN+PE+LW  & Yes & Yes & No  & Yes       & 1  & 360 \\
 SN+PE     & Yes & Yes & No  & PE only   & - & 300 \\
 SN+LW     & Yes & Yes & No  & LW only   & - & 412 \\ 
 SN-only   & Yes & Yes & No  & No        & -   & 142 \\
 RPx0      & Yes & Yes & Yes & Yes       & 0   & 750 \\
 RPx2      & Yes & Yes & Yes & Yes       & 2   & 704 \\
 RPx5      & Yes & Yes & Yes & Yes       & 5   & 750 \\
 RPx10     & Yes & Yes & Yes & Yes       & 10  & 717 \\
 Shortrad  & Yes & Yes & Yes* & Yes      & 1  & 613 \\
 Ion+PE+LW & No & No & Yes & Yes    & 1 & 750 \\ 
 Ion       & No & No & Yes & No    & 1 & 750 \\ 
 PE+LW     & No & No & No & Yes & - & 750 \\
 NoFeed    & No & No & No & No  & - & 60 
\enddata

\end{deluxetable*}

\section{Results}

\subsection{Star Formation Regulation}
\label{sec:sfr}

In Figure~\ref{fig:SFR} we compare the star formation rate as a function of time for each of our runs. As discussed in \methodpaper, the SFR evolution for the higher resolution fiducial simulation exhibits an initial burst up to $1 \times 10^{-3}$~M$_{\odot}$~yr$^{-1}$ followed by a lower-average, bursty SFR ($<$SFR$> = 1.19\times 10^{-4}$~M$_{\odot}$~yr$^{-1}$) with periods of up to 50-100~Myr with no star formation. This behavior is found also in the lower resolution fiducial simulation shown here (\fiducialstyle), albeit with a lower initial peak SFR and less dramatic fluctuations in SFR.
%\footnote{Our star formation algorithm has a minimum threshold gas mass to convert into stars in a single time-step, 100~$M_{\odot}$. SFR here is plotted in 10~Myr bins, yielding an effective SFR floor of $10^{-6}$ \sfrunits in Figure~\ref{fig:SFR}.} 
The most immediately visible difference between each of the runs is the magnitude of the initial burst of star formation in the first $\sim$100~Myr. Aside from the NoFeed simulation (grey) -- which rapidly forms more stars in 50~Myr than the cumulative throughout of any of the other simulations -- the SN only run (red) forms the most stars during this time. The peak SFR for each run is ranked quite nicely depending upon the feedback physics included, with PE heating producing the least change from the SN only run, up to ionizing radiation producing the largest change. PE seems to have very little effect on the initial evolution, with LW radiation and ionizing radiation generating the most significant changes. In fact, SN+Ion+LW and the three runs with no SN but do include either LW or ionizing radiation all have very similar initial bursts of star formation. The only exception to this trend is the shortrad run and Ion+PW+LW, which both have slightly smaller initial bursts. These similarities and the irrelevance of SN feedback on this early phase are clear indications that pre-SN feedback through radiation is important for star formation regulation. %During this initial phase, these runs show that, while together PE heating and LW radiation do have an effect on the SFR in the absence of ionizing radiation, ionizing radiation dominates when all three effects are included.

\begin{figure*}
  \centering
  \includegraphics[width=0.98\linewidth]{figures/physics_comparison_sfr}
  \caption{The 50~Myr time-averaged SFR in each of our runs, comparing those with SN feedback (left) to those without SN (right). The fiducial simulation, which includes all physics, is plotted in both panels (\fiducialstyle) for comparison. \changed{[Smoothed in 50Myr]}}
  \label{fig:SFR}
\end{figure*}

After the first 100~Myr, the differences between runs by the inclusion of SN feedback becomes obvious. 
% AE: NOTE TO INCLUDE FOLLOWING RESULT AS A SUMMARY POINT (conclusion)
Each of the SN-included runs (left panel) show various degrees of bursty star formation for the remainder of the simulation time, with lower average star formation rate than the ionization runs. The run with only PE heating and LW radiation, PE+LW (\pelwstyle), shows the most steady SFR, indicating that this feedback channel alone is capable of producing a self-regulating SFR in this galaxy, but not the bursty star formation that is seen with the inclusion of any other feedback channel. Ionization alone (\ionstyle) and the combined radiation run (\radstyle) both show bursty star formation like the SN runs, but still have a higher average SFR and more consistent SF through the end of the simulation. The SN runs have progressively lower SFR and longer quiescent periods as each simulation proceeds.

%(\aje{Maybe show summary table of comparison values? average SFR, average retention fractions, average outflow, etc.?... maybe do this in discussion?})

\subsection{Galaxy Morphology}
\label{sec:morphology}

We show a comparison of gas morphology of our low-mass dwarf galaxy in edge-on and face-on density-weighted projections of gas number density in Figure~\ref{fig:panel_plot_1} and Figure~\ref{fig:panel_plot_2} respectively at 125~Myr for each simulation. In every simulation with SNe (top two rows and bottom left), the gas disk is puffier with a larger scale height, and with significant diffuse, outflowing gas above and below the disk. This is not true for the runs with only radiation (bottom row), which exhibit thin disks with no significant outflowing gas; however though ionizing radiation is capable of heating the disk somewhat.

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/proj_plot_n_x_125.png}
  \caption{Edge-on projections of gas number density for each of our runs at time $t=125$~Myr.}
  \label{fig:panel_plot_1}
\end{figure*}

A subset of these runs show significant extra-planar gas structures, both in the form of diffuse shells of gas and small ($\sim$10~pc), dense clumps of gas above / below the disk (most significantly, SN, SN+Ion+PE, and SN+PE). Based upon visual analysis of the evolution of these panels, some of the diffuse shells are gas captured in an outflow / re-accretion cycle, while others are gradually pushed out due to continuing outflows. The dense clumps generally originate in the ISM and are entrained in the outflows. These clumps are still bound to the galaxy, and are ablated by the more rapidly moving diffuse gas outflows, giving rise to trailing tails of gas. In some cases these clumps are fully ablated and destroyed, while in others they persist, remain bound to the galaxy, and fall back in on an orbit with larger vertical motions than what is typical of other cold gas in the disk. These clumps do appear at some point in all simulations with either SNe or ionizing radiation, but to a much smaller extent than the obvious cases shown here. Our higher resolution fiducial simulation presented in Paper~I did show some of these features, but again not to the extreme shown here. \changed{This suggests that the presence of these clumps may be the resolution dependent, and the result of artificially strong cohesion in under resolved dense gas \citep{MacLowZahnle1994}. Confirming the physical nature of these clumps will require additional work.} H

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/proj_plot_n_z_125.png}
  \caption{The same panels as Figure~\ref{fig:panel_plot_1}, but face-on.}
  \label{fig:panel_plot_2}
\end{figure*}

In the face-on panels, each galaxy with SNe or ionizing radiation shows a low-density, carved-out circular region at the center, surrounded by a ring of dense gas. The lack of gas in the center of each galaxy is a particular consequence of the large initial burst of star formation present in every case. However, the stellar feedback from SNe and ionization radiation are (alone and together) effective at heating up and driving out cold ISM in the center of galaxy as stars form, which leads to a reduction of the central gas content even outside of this burst phase. Only the Pe+LW run is incapable of removing gas from the center, maintaining a more more uniform and more massive gas disk with localized patches of diffuse gas around newly formed stars. In runs with / without LW and PE (comparing SN+Ion+LW to SN+Ion+PE and SN+LW to SN+PE), LW radiation tends to decrease the presence of dense clumps of gas leading to smaller density contrasts in the inner ISM. As discussed later, this is likely due to the suppression of H$_2$ formation in runs with LW, an important coolant in this low metallicity dwarf galaxy. Many of the clumps seen within the diffuse central region in each simulation are there as projection effects, lying mostly outside the mid-plane of the galaxy.

In Appendix~\ref{appendix:panels}, we show projection panels at two other points in time for the available simulations to contrast with the panels here, show relatively early in the galaxy's evolution.

\subsection{Global Galaxy Properties}
\label{sec:galaxy properties}

In Figure~\ref{fig:properties} we compare the time evolution of the total \HI~mass, stellar mass, H$_2$ mass fraction, and average ISM metallicity for each of our runs. The \HI~mass in the fiducial simulation declines with time as stars form, radiation ionizes the ISM, and SN feedback drives significant mass loss. Interestingly the H$_2$ fraction increases significantly during this time, but, as shown in Paper~I, this is mostly due to the preferential retention of the cold, dense gas where the H$_2$ resides, rather than the generation of a significant amount of mass of molecular hydrogen. In the bottom right panel we show the evolution of only those metals self-consistently produced by stars formed in the simulation; the initial metal fraction for these species is 10$^{-20}$. In the fiducial run, the mean ISM metallicity remains well below what could be expected for a closed-box, one-zone model (grey, dashed) with the same star formation history. As discussed in Section~\ref{sec:outflows} this is due to the significant outflows generated by feedback in this galaxy.

\begin{figure*}
  \centering
  \includegraphics[width=0.98\linewidth]{figures/physics_comparison_masses}
  \caption{The evolution of four global galaxy properties for each of our simulations. Clockwise from top left: \HI mass, stellar mass, H$_2$ fraction, and mean ISM metallicity. $M_{\rm \HI}$ and $M_{*}$ have the same vertical axis limits for comparison of the stellar mass fraction between runs. The $<Z_{\rm ISM}>$ shown here only includes metals self-consistently produced by stars in this simulation (see text). \changed{In the final panel, the grey dashed line shows the corresponding closed-box metallicity evolution for the fiducial simulation.}}
  \label{fig:properties}
\end{figure*}

SN+Ion (along with SN+Ion+PE) generally has the lowest \HI~mass of all of the runs. Compared to the fiducial simulation, this is likely due to the increase in stellar mass and associated increases in feedback strength from both SNe and ionization, which both removes gas in outflows and ionizes \HI~in the ISM. The importance of ionizing radiation in driving the \HI~content is seen clearly comparing to the elevated \HI~masses of all runs without ionizing radiation, especially considering that these runs generally have a higher stellar content. The importance of outflows in regulating the gas content can be seen by comparing Ion+PE+LW (\radstyle) to the fiducial, which shows a similar total stellar mass but greater \HI~content, and the ionization only run (\ionstyle) which has a stellar mass higher than both the fiducial and SN+Ion runs but a comparable \HI~mass to the fiducial run. At the extreme, PE+LW radiation alone clearly is incapable of ionizing or removing any \HI~from this galaxy, in spite of its comparatively high stellar mass. Although the shortrad simulation does contain some ionizing radiation, this localized (within 25~pc) ionizing feedback is clearly insufficient to ionize and remove as much gas as many of the other runs. Looking at the runs with / without PE and LW, including PE from SN to SN+PE (or removing it from the fiducial to SN+Ion+LW) provides little difference in any of these properties. However, adding / removing LW radiation does produce a noticeable effect. 
%We will discuss outflows in more detail in Section~\ref{sec:outflows}.

There appears to be three general groupings in the evolution of the molecular fraction between runs. Runs without LW all exhibit the highest H$_2$ fractions with the smoothest evolution. The remaining runs with LW result in overall lower and more variable H$_2$ fractions. The runs with the lowest H$_2$ content tend to be those that include LW but are missing another form of feedback, leading to increased stellar masses and an increase in the total LW flux in the galaxy.

%With the exception of Ion+PE+LW (\radstyle) and PW+LW (\pelwstyle) runs, the molecular hydrogen fraction is quite similar throughout the galaxy's evolution. What is most clear from this plot is that stellar LW radiation is indeed important to consider if attempting to model the molecular gas content. The two runs without LW radiation (SN+Ion and ionization-only) show fewer fluctuations in the molecular gas content than the other runs, most obvious during the initial 100~Myr burst where the $H_2$ fractions drop dramatically for those runs with LW radiation.

Understandably, the differences in stellar mass evolution and gas content in these runs leads to a significant variation in the mean ISM metal fraction. The fiducial run, RPx0, and SN+Ion+LW show the lowest mean ISM metallicities, a factor of $\sim$4 below that of the closed-box model with the same SFH as the fiducial simulation. The remaining simulations show increasing ISM metallicity, driven by a combination of both increased star formation and decreased outflows (greater metal retention). This interplay can be inferred by the fact that the relative differences in $<Z_{\rm ISM}>$ between the various runs and the fiducial simulation are much larger than the same differences in total $M_{*}$. An extreme example of this is comparing PE+LW with SN+PE and SN+LW. All three have somewhat similar total stellar masses by 500~Myr, but significantly different ISM metallicities. We will discuss outflows in more detail in Section~\ref{sec:outflows}.

\subsection{Multi-Phase Gas}
\label{sec:phase diagrams}

%\aje{Its a bit hard to be very precise about this comparison since it's not easy to distinguish feedback effects directly from there just being less / more SF and SNe due to changes in effectiveness of feedback (best example is the RPx0 comparison... I'd expect very little differences, but there are some and its likely not due to lack of RP, but more likely to due sligly different SFR over this time)....might be worth mentioning this as a caution?:}
The properties of the multi-phase ISM for our galaxy simulations is feedback-driven as shown in the temperature-density phase diagrams Figure~\ref{fig:phase_diagram}, and the 1D temperature and density PDFs in Figure~\ref{fig:1D_phase}. Both figures show only gas contained within the disk of each galaxy, and are averaged over a 20~Myr period from 100-120~Myr in each simulation. As indicated by the 2D phase diagrams, the most obvious differences are in the presence / absence of warm/hot ISM ($T > 10^5$~K) driven by SNe that is non-existent in the radiation only runs (bottom right three panels), and the complete absence of diffuse, warm ($T \sim 10^4$~K) gas at $n < 10^{-2}$~cm$^{-3}$ in the run without any feedback.

Comparing the runs with and without ionization radiation, it is also clear that this feedback component is necessary to maintain a significant amount of gas in the warm, diffuse phases ($10^4~ {\rm K}~ T < 10^5~ {\rm K}$, $n < 1$~cm$^{-3}$). This is most obvious comparing the runs without supernova, but it is also clear that the SN+PE+LW and SN-only runs also have less gas in this regime. Surprisingly, while shortrad does have ionizing radiation feedback, its limited physical extent also reduced the amount of warm, ionized gas compared to simulations with full ionizing feedback. PE and LW radiation seems to have only slight, subtle effects on the gas phases in these figures. However, comparing SN+LW to SN+PE, the latter has slightly more cold, dense gas. The general trends in these diagrams are that including additional feedback sources tends to (overall) broaden the distribution of gas with different densities / temperatures at fixed temperature / density. SNe are necessary to generate hot gas, but are less efficient at sustaining warm/hot, ionized gas. This requires ionizing radiation -- and more than just short-range ionization and heating.

These differences are more distinct in the 1D phase diagrams in Figure~\ref{fig:1D_phase}, giving the full PDFs in the top row and the PDFs normalized to the fiducial simulation in the bottom. Again its clear that runs without SNe lack hot gas, and that this gas is instead piled into the warm phase right around 10$^4$~K. These same runs also have much more cold, dense gas as the lack of SNe makes it challenging to destroy cold gas in the ISM. As suggested previously, LW radiation is important for regulating the presence of cold, dense gas, with SN+PE and SN+Ion+PE havng elevated cold gas compared to their counterparts with LW instead of PE.  
%Comparing the Fiducial simulation with SN+Ion and the radiation only with the ionization only runs, turning off PE+LW has a much less significant effect than turning off ionizing radiation, but it does seem to cha

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/phase_plot_nT_disk_4x2}
  \caption{The temperature - density phase diagrams for each simulation averaged over the 20~Myr period from 100-120~Myr in each simulation. Lines of constant pressure are given as dashed lines.}
  \label{fig:phase_diagram}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/1D_phase_plot_2panel_nT_phase_disk}
  \caption{The 1D density and temperature PDFs (top) corresponding to Figure~\ref{fig:phase_diagram}, along with each PDF relative to the fiducial simulation (bottom). Line-styles are the same as in Figure~\ref{fig:properties}. \changed{[Changed bin sizes for smoother curves and added legend.]}}
  \label{fig:1D_phase}
\end{figure*}

\subsection{Outflows}
\label{sec:outflows}

Galactic outflows are a natural consequence of stellar feedback, and have been demonstrated to be significant in low mass dwarf galaxies. In Figure~\ref{fig:outflow_evolution} we present the mass outflow rate as measured through an annulus with thickness 0.05~R$_{\rm vir}$ centered at two radii from the galaxy, 0.1~R$_{\rm vir}$ and R$_{\rm vir}$ (again, R$_{\rm vir}$ = 27.2kpc). The total outflow rates in the inner halo are within factors of a few of each other during the first $\sim$200~Myr for all of the simulations except shortrad and PE+LW, which are unable to drive significant outflows. Clearly, some combination of full stellar ionizing radiation and/or supernovae are necessary to drive outflows in low mass dwarf galaxies.

After this point, the runs differentiate, but generally fluctuate between similar minimum / maximum values. Runs with SN feedback and ionizing radiation tend to maintain a higher, more consistent outflow rate. \changed{The equivalent mass loading factors ($\eta_M \equiv \dot{M}_{\rm out} / \dot{M}_{\rm *}$, and defined in more detail later) for these runs at 0.1~$R_{\rm vir}$ can be between 100 and 400 for all runs including ionizing radiation, and is generally lower (10-50) for those without (and below 1 for PE+LW). This shows that ionizing radiation is important for driving significant outflows, acting on concert with SNe; and in the case of this low mass dwarf galaxy, ionizing radiation alone is capable of driving $\eta \sim$~100 outflows near the disk of the galaxy. It is somewhat surprising that runs without SNe can still reach these large values, but it is the case that 0.1$R_{\rm vir}$ represents a small distance from our galaxy center (2.7~kpc). Only runs with both SNe and ionizing radiation are capable of driving substantial outflows ($\eta > 10$) at the virial radius; PE and LW alone have little impact on the outflows. In agreement with the findings in \citet{Emerick2018a}, how the ionizing radiation feedback is implemented is important, as shown by the low $\eta$ at $R_{\rm vir}$ in the shortrad simulation.}

The efficiency with which stellar feedback drives outflows is often characterized using the mass loading factor, $\eta_M$, metal mass loading factor, $\eta_Z$, and energy loading factor $\eta_E$. We define each of these quantities following \cite{LiBryan2020}: $\eta_M \equiv \dot{M}_{\rm out} / \dot{M}_{\rm *}$, $\eta_Z \equiv \dot{M}_{Z,\rm{out},\rm{SN}} / \dot{M}_{Z,\rm{SN}}$, and $\eta_E \equiv \dot{E}_{\rm out}$. By definition, $\eta_Z$ is always $<$~1 and represents the fraction of SNe-synthesiszed metals that go into outflows. There is some variety in how exactly $\eta_M$ is computed in simulations, even with this definition. $\dot{M}_{\rm out}$ is the instantaneous mass outflow rate, but $\dot{M}_{\rm *}$ is rarely taken to be the instantaneous star formation rate, often time-averaged on anywhere from 1 to 100~Myr. Particularly for galaxies with bursty star formation, as is the case here, exactly how $\dot{M}_{\rm *}$ is averaged can lead to a large variability in $\eta_M$. To smooth over these fluctuations, we use 100~Myr time-averaged $\dot{M}_{\rm *}$ and compute $\eta_M$, $\eta_Z$, and $\eta_E$ every 5~Myr in each simulation for both the hot ($T \geq 3 \times 10^5$~K) and cool ($T < 3\times10^5$~K) phases. \changed{For consistency with the works in \citet{LiBryan2020}, we compute the outflow quantities at a height of 1~kpc above and below the disk of our galaxy.}  We present the average of each of these quantities for each simulation over their entire run-time in Figure~\ref{fig:loading_factors}, as a function of their average star formation rate density.

In general, our simulations show significant amounts of mass and energy driven out via cooler outflows, as the hot loading factors are comparable to or much less than the cooler loading factors. This is qualitatively different from the suite of simulations presented in \cite{LiBryan2020} (see also TIGRESS paper), \changed{[clarified:] where the hot phase carries at least as much mass and energy out as the cold phase.} However, although there is some overlap in $\Sigma_{\rm SFR}$ between our galaxies and a few of the simulations considered in that work, our galaxy has a much lower total mass and gravitational potential. Since the virial temperature of our halo is $1.4 \times 10^4$~K, it is not surprising that both mass and energy can flow out of our galaxy without reaching temperatures above 10$^5$-10$^6$~K. This is further shown by the fact that the two runs with ionization but no SNe have larger mass loading factors driven only by cold gas.

Comparing each run, only the runs with supernovae contain any hot outflows. In general, there is a decreasing trend with $\eta_M$ and star formation rate. However, this trend generally follows the line of constant $\dot{M}_{\rm out}$ for each simulation, suggesting that each galaxy sustains a similar total mass outflow rate, but it is just the efficiency of stellar feedback in driving those outflows that changes by including / excluding different modes of feedback. As shown above, runs with both ionizing radiation and SNe produce the most effiecient outflows -- ejecting more gas per solar mass of star formation than runs without either source of feedback. PE+LW generates the least efficient outflow (near unity $\eta_M$, no metal outflow, and very small $\eta_E$); the SN only run has the highest metal loading, but at a lower mass and energy loading than achieved by also including ionizing radiation.

It is again insteresting to not the behavior of the shortrad simulation here. It has one of the lowest mass loading factors of runs with SNe, and a metal and energy loading factors more similar to runs without SNe, in spite of the fact that it includes both SNe and ionizing radiation. With reference to the analysis in \citet{Emerick2018a}, it is clear the ionizing radiation is effective at limiting the local star formation in this galaxy, but is not punching diffuse, ionized channels of gas needed for SNe to effectively drive out mass, metals, and energy. This hot gas is trapped, leading to the very low hot loading factors across all three quantities. In runs without ionizing radiation, this is compensated for with extra SNe feedback as the result of additional star formation.

% point for conclusion: self-consistent feedback is key for getting everything right. Not just a matter of getting stellar mass right, but also in concert with outflows and abundances  (AE)

% point for conclusion:, adding in additional non-SN feedback sources changes the mode of outflows from hot-dominated to more cool, (most dramatically with ionization). (AE)

% \aje{Is it worth making a statement about how it might be hard to differentiate between outflow efficiencies if outflows are saturated (at some point, adding more feedback energy won't increase the outflow rate).}

The total $\eta_Z$, which again represents the fraction of SNe-produced metals that outflow relative to the total produced, is fairly uniform for all runs with SNe ($\eta_Z > 0.5$), but significantly lower for those without ($\eta_Z \lesssim 0.1$) and zero for the PE+LW-only run. Comparing to the differences across simulations in $\eta_M$, this raises two important points: 1) while ionizing radiation alone can drive outflows in the inner-halo of this low-mass dwarf galaxy, SNe are necessary to drive metal-enriched outflows, 2) the metal content of SNe-driven outflows in this low-mass dwarf galaxy is less sensitive to additional feedback processes than the total outflows. Cool outflows carry a majority of the metals out of the ISM of our galaxy in each simulation (as is the case for $\eta_M$).

$\eta_E$ shows similar trends except that the differences in energy content between hot and cool outflows are much smaller for some of the runs, and for others $\eta_{E,h}$ exceeds $\eta_{E,c}$ by factors of a few. There appears to be a transition $\Sigma_{\rm SFR}$ around 10$^{-4}$~M$_{\odot}$~kpc$^{-2}$~yr$^{-1}$ above which hot outflows dominate over cold in carrying energy.

Finally, \citet{LiBryan2020} find a strong correlation between the $\eta_{E,h}$ and $\eta_{Z,h}$ across their examined simulations. We plot the relationship between $\eta_{E}$ and $\eta_{Z}$ and $\eta_{E,h}$ and $\eta_{Z,h}$ in Figure~\ref{fig:loading_relation} (black points) as compared to the simulations presented in \citet{LiBryan2020} (grey points). [changed{[clarified following statement:] We find that there is no strong correlation between the energy loading factor and metal loading factor (left panel) in our simulations; the total energy loading factor is more sensitive to the varying feedback physics than the total metal loading factor. In general, increasing the sources of feedback (particularly SNe and ionization) increases the energy loading factor.} Although our simulations without SNe do not contain any hot outflows, the right panel shows that our simulations exhibit a similar linear relationship between $\eta_{E,h}$ and $\eta_{Z,h}$, but at a slightly higher value ($\sim$1) than in \citet{LiBryan2020} ($\sim$0.4).

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/physics_comparison_outflow_loading}
  \caption{The total mass outflow rate (top) and mass loading factor (bottom) measured at different radii for each of our galaxies. \changed{[added legend]}.}
  \label{fig:outflow_evolution}
\end{figure*}

%\begin{figure*}
%  \centering
%  \includegraphics[width=0.95\linewidth]{figures/physics_comparison_outflow_loading}
%  \caption{The mass loading factor measured at different radii for each of our galaxies. For ease of comparison, we use the average SFR over the each entire simulation as the denominator when computing $\eta_M$.}
%  \label{fig:outflow_evolution}
%\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/phys_comparison_mass_metal_hot_cold_SFR}
  \caption{The mass loading factor ($\eta_M$), metal loading factor ($\eta_Z$), and energy loading factor ($\eta_E$) for both hot (orange, $T \geq 3 \times 10^5$~K) and cold (blue, $T < 3 \times 10^5$~K) gas and their ratios for each of our simulations computed at a height of 1~kpc above and below the disk of our galaxy. The totals are shown in the top panel in black, except for the runs without SNe which contain no hot outflows and are left as blue. Each simulation is labelled, but for clarity our fiducial simulation is shown with a plus, simulations with SNe feedback as stars, those without SNe with diamonds, and SN-only with an X. For clarity, the runs without SNe are not separately labelled, but are -- in order of increasing $\Sigma_{\rm SFR}$ -- radiation-only, ionization-only, and PE+LW-only. \aje{I will add in labels by-hand to the SNe runs in final plot. For now, to match up the points with runs, the * runs are (in order of increasing SFR): RPx0, SN+Ion, Shortrad, SN+PE+LW}. The rad-only runs are: radiation, ionization-only, and pe+lw-only}
  \label{fig:loading_factors}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/phys_comparison_E_loading_Z_loading}
  \caption{A comparison of the total and hot energy and metal loading factor relationships for our simulations (black points) as compared to the suite of simulations presented in \citet{LiBryan2020} (grey points), which includes data from \citet{Li2017,KimOstriker2018,Fielding2018,Hu2018,Armillotta2019,Martizzi2016} and \citet{Creasey2015}. Lines of constant $\eta_E / \eta_Z$ are shown.}
  \label{fig:loading_relation}
\end{figure*}

\subsection{Evolution of Individual Metals}
\label{sec:metals}

As explored in \citep{Emerick2018b}, metals released into the ISM in core collapse supernova are ejected from the galaxy through outflows at a higher efficiency than metals from AGB winds. In addition, these same metals showed smaller gas-phase abundance variations -- pointing to more efficient mixing -- than elements from AGB winds. We explore how feedback affects these differences here.

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/physics_comparison_retention}
  \caption{The retention fraction of CCSN elements (left, traced by O) and AGB elements (right, traced by Ba) in the disk of each galaxy as a function of time. Line styles are the same as in Figure~\ref{fig:properties}. \changed{[added legend]}.}
  \label{fig:retention}
\end{figure*}

In Figure~\ref{fig:retention} we plot the fraction of metals produced within the disk at each point in time for a CCSN proxy (O, left)\footnote{We note that this quantity does not vary significantly for other SNe-dominated elements, like Mg.} and an AGB enrichment proxy (Ba, right). The fiducial simulation shows a fairly consistent CCSN retention fraction of $\sim$5\% after the first 100~Myr. The AGB retention fraction drops during the first 100~Myr until the first AGB stars begin producing significant Ba; the retention fraction then grows and oscillates with the SFR, but remains between 20\% and 40\%, significantly higher than that for CCSN elements. In general, runs with both SN feedback and ionization show low CCSN element retention. Runs without ionization (SN+PE, SN+LW, SN+PE+LW) retain a much larger fraction of their CCSNe elements (20-40\%), but still have a slightly higher AGB-element retention fractions (40-60\%). Only runs without SNe show similar retention fractions across both CCSNe and AGB elements. The large fluctuations in the shortrad run and Ion and Ion+PE+LW are caused by gas that is removed beyond our formal definition of the disk region, but is not ejected far into the halo and eventually re-accretes onto the galaxy. This is additional confirmation that this difference is due in large part to the difference in energetics between the SN and AGB events, as expected from the analysis in \citet{Emerick2020a}. Retention fractions are similar for different elements if the mode of outflows is dominated by swept-up ISM rather than the direct release of metals from the enrichment source itself (in this case, SNe).

Although the mass of this galaxy is likely too low to observe the metal content of its circumgalactic medium, where the metals end up beyond the disk of the galaxy may also be an important discriminator between feedback models. We explore this here but for brevity the associated figure is not shown. We find that the fraction of metals in the CGM for CCSN is initially large after the first burst of star formation ($\sim$80-90\%) for all SN runs, but gradually declines to $\sim$20-30\% by the end of the simulation. Since this lost mass is not being re-accreted into the ISM, it is ejected from the halo. Although AGB elements show significantly different disk retention fractions, the CGM fractions are very similar to the CCSN elements. This is possibly because whatever AGB elements do end up in the halo were carried out through the same processes as the CCSN elements, leading to the very similar evolution in the CGM.

%In Figure~\ref{fig:CGM} we plot the gravitationally bound

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/physics_comparison_IQR}
  \caption{A comparison of the evolution of the inner quartile range (IQR) of the gas-phase abundances of CCSN elements (left, traced by O) and AGB wind elements (right, traced by Ba) in the cold ISM ($T < 10^2$~K). Run Pe+LW (\pelwstyle) remains well above the vertical bounds for the duration of the simulation, and is omitted for clarity (see text).}
  \label{fig:mixing}
\end{figure*}

Finally, we explore the metal mixing differences between these runs and these two elements in Figure~\ref{fig:mixing}. We compare the inner quartile range (IQR) abundance spread of the cold gas for O, the CCSN element proxy, and Ba, the AGB element proxy, for each run. In the fiducial simulation, the CCSN elements show a declining spread throughout the evolution, reaching an IQR of $\sim$0.25 dex by the end of the simulation time. As was seen in the retention fraction, the AGB elements follow the same evolution until the point in time when they are first produced by AGB, at which point the width rises significantly, to around 0.7~dex, and remains well above the CCSN elements until the end of the simulation, though declines to about 0.4~dex. All of the simulations including SN feedback show very similar general trends and final IQR values for O, with the exception of shortrad which takes longer to reach the initial plateu at about 0.4~dex, and stays above the fiducial simulation for the remainder of the time. The comparison here and to the radiation only runs shows the importance that hot-phase mixing has on the evolution of these elements. While the runs with SN hit a roughly consistent IQR after the first $\sim$150~Myr, the runs without SNe take more than twice as long to reach this point. This is in spite of the fact that the radiation-only runs have a higher global SFR with more continual and uniformly distributed enrichment that should allow for more rapid homogenization. However, the radiation only runs do not have SN depositing their elements first in a volume-filling hot phase, which is necessary for rapid mixing over the whole galaxy \citep{Emerick2018b}. However, ionizing radiation does generates some sufficiently warm / hot gas to increasing the mixing timescales over what is present in PE+LW, which is not shown in either panel for clarity. PE+LW exhibits mixing timescales on order or more than the dynamical time of the galaxy ($\sim$1~Gyr); by 300~Myr, this run has an IQR of 10~dex for both elements, declining to 2~dex by 750~Myr in both cases.

Since SN and AGB winds have the same injection energy in the radiation only runs, they exhibit very similar abundance spreads. This suggests that, not only is the mean abundance of individual elements an important discriminator between feedback models, but also the scatter in individual abundances can contain information about the stellar feedback that drives metal mixing in the ISM. Future work correlating gas-phase abundance spreads with ISM properties for a range of feedback models would be useful in making the connection from observed gas-phase abundances to stellar feedback parameters.

\subsection{Stellar abundances}
\label{sec:stellar abundances}

\changed{[removed Type Ia SNe discussion (Fe)]}

The previous discussion focused on the time evolution of the instantaneous gas-phase abundances of the simulated galaxies. But the best observable of galactic chemical evolution in low mass dwarf galaxies is their stellar abundances, which are the convolution of the instantaneous gas-phase abundance distributions and the SFR. To examine the effect of feedback on stellar abundances patterns, we plot the normalized 1D metallicity distribution functions (MDFs) for the abundance ratios [Mg/H]\footnote{The notation [A/B] represents the abundance of element A relative to B, normalized to the solar ratio, in logscale: [A/B]~$\equiv$~log$_{10}$(N$_{\rm A}$/N$_{\rm B}$)~-~log$_{10}$(N$_{\rm A,\odot}$/N$_{\rm B,\odot}$).}, and [Ba/H] in Figure~\ref{fig:MDF1}.\footnote{ While our simulated galaxy is modelled after the $z=0$ properties of the Leo~P dwarf galaxy (see Paper~I), we emphasize that these stellar abundances are likely not representative of the actual abundance patterns in a Leo P like dwarf galaxy ($M_* \sim 10^6 M_{\odot}$) given that we only capture 1~Gyr of evolution. \changed{[added:] It is also for this reason why we do not consider [Fe/H] here or any similar tracer of Type Ia SNe enrichment, as the simulation has not been evolved for a long enough time period for any element to be dominated by this channel (see Figure 2 of \citet{Emerick2018b}).} However, this provides insight into possible abundance variations in lower mass dwarf galaxies who form a majority of their stars over timescales of $\sim$1~Gyr in the early Universe.} These columns represent typical enrichment from ccSNe and s-process enrichment from AGB winds respectively.

There are three general properties to compare across these MDFs: the location of the peak abundance, the width of the distributions, and the tails towards both higher and lower abundances. The increased peaks in nearly all simulations (compared to the fiducial), with the exception of those in the top panel with both SN feebdack and ionization, is driven by the increase in ISM metals in each case, driven both by lower metal ejection fractions and higher star formation. These distributions are interesting with reference to Figure~\ref{fig:properties}. Simulations with similar $<Z_{\rm ISM}>$ at the point of comparison here, for example, 500 Myr for the shortrad run and $\sim$350 Myr for SN+PE+LW (and also comparing to SN+PE and SN+LW, with slightly higher but still similar $<Z_{\rm ISM}>$) can manifest larger offsets in the peak of their stellar MDFs. This suggests that there is a third mechanism with which stellar feedback regulates stellar abundances. The two obvious, as discussed previously: 1) by modifying the amount of stars that form and thus the number of metals produced and 2) by driving out some fraction of those metals from the ISM, but also  -- more subtle -- 3) by determining how quickly ISM metals can be incorporated into new stars before being ejected.

The runs with only radiation (bottom panels) also show the higher enrichment compared with the fiducial run, most significantly for PE+LW. Ion and Ion+PE+LW exhibit more similarly peaked MDFs to the remaining SN runs.

\begin{figure}
  \centering
  \includegraphics[width=1.1\linewidth]{figures/MgH_BaH_stellar_MDFs}
  \caption{Stellar MDFs for all stars in each simulation at t = 500~Myr (for simulations with final run times less than 500~Myr, we only take those stars that would be alive at 500~Myr). \changed{[removed Fe/H]}}
  \label{fig:MDF1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1.1\linewidth]{figures/CaMg_BaMg__stellar_MDFs}
  \caption{The same as Figure~\ref{fig:MDF1}, but for the abundance ratios [Ca/Mg], and [Ba/Mg]. Mg and Ca both trace enrichment from ccSNe, while and Ba traces enrichment from s-process via AGB winds.\changed{[removed Fe/H - still figuring out best linestyles. Using different ratios now]}}
  \label{fig:MDF2}
\end{figure}

While the distribution of stellar abundances in terms of total metal fractions ([X/H]) provides additional insight into the effects of feedback on galactic evolution, this does not necessarily provide any additional constraints that cannot be determined by examining just the total metallicity alone. To examine if individual abundances could provide additional constraints, we plot two abundance ratios in Figure~\ref{fig:MDF2}, [Ca/Mg] and [Ba/Mg]. As shown, the largest differences across all runs lie in the widths of the distributions as compared to the fiducial simulation. In every case, the fiducial simulation produces a broader distribution for each abundance ratio.

\textbf{(AJE) New:
In [Ca/Mg], the additional star formation and enrichment in each scenario drives the MDF of the distribution closer to the IMF-averaged value of [Ca/Mg] for our yield set ([Ca/Mg] $\sim$ 0.22), homogenizing over some of the mass dependence between these two abundance ratios. This occurs most prominently for the runs with only radiation, and less so for the remaining runs. This is interesteing, because Ca and Mg production varies with supernova type in our yield model, with the most massive (M$_*$ = 25~M$_{\odot}$) producing [Ca/Mg] = -2.96, and least massive (M$_*$ = 8~M$_{\odot}$) having [Ca/Mg] = 0.77 at stellar metal fractions of $Z = 10^{-4}$. The runs with peaks slightly less than the fiducial simulation have peak [Ca/Mg] closer to solar. This suggests a difference in how metals from the first vs. last SNe in a given star formation event are mixed in the ISM and released through outflows. This is an interesting signature of the effects of stellar feedback on stellar abundances beyond differences already shown between metals of different nucleosynthetic sources. However, determining this effect on mass-dependent SNe yields conclusively requires further analysis, in particular the use of tracer particles or separate passive scalar fields in stellar mass bins to conclusively trace the evolution of elements from different SNe.}

In [Ba/Mg], the fiducial simulation and those with both SN and ionizing radiation exhibit broad, nearly flat MDFs across a large range (> 2 dex). The remaining runs all have more narrowly peaked (but still more broad than [Ca/Mg]) distributions around or below [Ba/Mg] of -2. The unifying origin of this difference is in how metals are retained / ejected (Figure~\ref{fig:retention}) across runs. Those with more narrow [Ba/Mg] distributions exhibit greater and more similar retention fractions of both species. It is precisely the relative difference in increased retention fractions between these two species that drives this broadening of these distributions (more retained Mg relative to Ba drives lower [Ba/Mg]). This indicates a second mode for increasing the width of abundance ratio spreads beyond the mixing differences discussed in Section~\ref{sec:metals} and previously in \citet{Emerick2018b}.

This all demonstrates that there are indeed differences in the resulting abundances for models with different stellar feedback, driven by how stellar feedback regulates the SFH of a galaxy relative to the enrichment timescales of different nucleosythnetic processes, and the retention / ejection of different elements in galactic winds.

%A feedback prescription that allows for more rapid, efficient star formation in a galaxy could produce elevated [Mg/Fe] prior to the onset of significant Type Ia contributions. In addition, simulations with less powerful feedback can lead to narrower, more peaked MDFs in multiple abundance ratios. However, these results are not conclusive without additional tests on a range of galaxies with a larger variation in star formation history and galaxy mass. \aje{need a little more here}.

\section{Discussion}

\subsection{Role of Photoelectric Heating}

While photoelectric heating of dust grains is an important source of heating in dense gas of more metal-rich environments like the Milky Way ISM \citep[e.g.][]{BakesTielens1994,Wolfire2003}, its role in low-metallicity dwarf galaxies is unclear. Recently, \cite{Hu2017} found photoelectric heating to be unimportant in a galaxy with stellar mass $\sim$10$^{7}$~M$_{\odot}$ and $Z\sim$0.1~Z$_{\odot}$, in contrast to \cite{Forbes2016} who found it to be a significant source of feedback in their dwarf galaxy of similar mass and metallicity.\footnote{Though see discussion in \cite{Hu2017} which argues the difference was due to a different treatment of metal line cooling in self-shielded gas.} Our results here show more conclusively that photoelectric heating is not a significant source of stellar feedback in the low-metallicity regime of our low mass dwarf galaxy. There is no significant difference between the SN and SN+Pe and the SN+Ion and SN+Ion+PE runs for the properties studied here. Far more important, however, is LW radiation, which does have a significant effect through regulating the H$_2$ content of this galaxy, which is a dominant coolant in this low-metallicity regime.

\subsection{Radiation Pressure}

The role of radiation pressure in galaxy evolution is also of some debate as to its importance in various regimes \citep[e.g.][]{HQM2011,HQM2012,Agertz2013,Ceverino2014,Sales2015,Rosdahl2015,Kannan2020} (and see also the detailed analysis and discussions in \citet{Krumholz2018} and \citet{Hopkins2019}). In the low-mass dwarf galaxy regime, radiation pressure is sub-dominant to photoheating and ionization, but can still play a significant role in star formation regulation \citep{WiseAbel2012}. We focus here the role of radiation pressure in a low-mass dwarf galaxy in the single-scattering limit, ignoring the potential increase in deposited momentum from resonant re-scattering of UV photons into the IR. In Figure~\ref{fig:RP} we show the cumulative stellar mass, $<Z_{\rm ISM}>$, and mass loading factor $\eta_{M}$ at 0.1$R_{\rm vir}$ for our fiducial simulation and each of the runs varying radiation pressure by a constant multiplicative factor. While there are differences between these runs, the evolution in the first there is no clear trend in any of these results with the radiation pressure factor. RPx0 and RPx2 do not show significant differences from the fiducial simulation. RPx5 and RPx10 do behave differently, but RPx5 forms more stars and RPx10 less than the fiducial. The properties in the reminaing panels do not appear to be dramtically different between these runs.

As this is only a single, isolated low-mass dwarf galaxy we cannot universally say that radiation pressure is subdominant in this regime, but it appears to be unlikely for galaxies much like ours. This is in disagreement with the results from \citet{WiseAbel2012}, which uses the same radiation feedback methods. However, that work studied star formation across a population of dwarf galaxies with different stellar masses and morphologies than the galaxy examined here. This conclusion may also be resolution dependent; higher resolution simulations capable of resolving higher gas densities may see a larger impact from adjusting the effectiveness of radiation pressure.

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/physics_RP_comparison}
  \caption{A comparison of some of the quantities for the runs varying the effectiveness of radiation pressure.}
  \label{fig:RP}
\end{figure*}

%
% Brainstorm notes: looking at just Fiducial, no ot, no ion, no lw, no pe
%
%   OK. Taking the SN+Ion simulation (solid orange). 
%   Turning ON PE heating leads to a slightly surpressed total SF (so yes PE heating seems to have an effect on galaxy evolution, but not DRAMATIC. This has a similar Z to this run and simular total molecular H. Gas mass (HI) is also similar. So global galaxy props don't change toooo much but just surpressed SFR (just slight heating of disk)?
%
%  SN+Ion, turning ON LW (no PE) leads to FAR surpressed SF (2-3), likely due to the significantly surpressed H_2 fraction in the galaxy (early on especially but also lasting for a while). This leads to a lower ISM metallicity due partly to outflows?
%
%  Ok. here is where it gets fun. Turning BOTH on leads to a more similar evolution to just PE. Seems like LW+PE might serve to 1) kill off some H_2 which affects SF, but PE keeps disk overall stable against SF keeping SFR down as well? Turning off Ionization makes way more stars than everything.
%
% I think I'm going to have to look at a phase diagram and movie of these... really don't know.
%

\section{Conclusion}

\subsection{Dominant Modes of Stellar Feedback in Low Mass Dwarf Galaxies}

In a set of simulations studying the evolution of a low-mass, isolated dwarf galaxy modelled after the z = 0 properties of the Leo~P dwarf galaxy, we explore the effects that each part of a star-by-star model for multi-channel stellar feedback has on the galaxy's evolution. We test the role that PE heating, LW radiation, ionizing radiation, radiation pressure, and SNe have on this galaxy through 17 different simulations at moderately high (3.6~pc) resolution. We find that each form of feedback are capable of generating some form of self-regulated star formation in our dwarf galaxy. However, the combination of these processes produce qualitatively different star formation rates and galaxy properties. Even in cases where the total stellar mass formed is similar across runs, the different feedback channels can produce significant changes in other galaxy properties. We pay particular attention to their ability to drive metal-enriched outflows, metal-mixing, and stellar abundance patterns for different elements in our galaxy.

Due to the complex interplay of different forms of stellar feedback, it is ill-posed to choose one that is the ``most'' important or effective. However, we can conclude the relative effects on galaxy evolution in models that do or do not include certain feedback processes. We find that SNe and ionizing radiation \textit{together} are the dominant sources of stellar feedback regulating star formation, the multi-phase ISM, and driving outflows in this model of a low-mass dwarf galaxy. These feedback channels act together, with ionizing radiation decreasing the ambient ISM density in which SNe explode and carving channels of diffuse gas needed to vent significant amounts of mass, metals, and SNe in outflows. All of our feedback models generate outflows dominated by cool mass and metal loading, in contrast to the hotter outflows in more massive galaxies; this is less true for energy loading, with more comparable hot / cold loading factors in some runs, and larger hot loading factors in runs with $\Sigma_{\rm SFR} > 10^{-4}$~M$_{\odot}$~kpc$^{-2}$~yr$^{-1}$. In general, including ionizing radiation feedback produces cooler mass and metal outflows while increasing the total mass and metal loading factors (more efficient feeedback).

We find that the destruction of H$_2$ through LW radiation is an important source of feedback in our low-metallicity dwarf galaxy. In this regime, H$_2$ is a dominant coolant and the dominant source of dust formation. This feedback source produces a far greater effect on the star formation and outflow properties of our dwarf galaxy than PE heating from FUV radiation, also due to the limited dust content in this low-mass dwarf galaxy. We additionally explore the effects of radiation pressure and find that an order of magnitude boost in the radiation pressure effectiveness in the single-scattering limit is necessary to noticeably affect the evolution of the galaxy, but the trend as a function of this boost factor is not clear. We conclude that radiation pressure is not a signficant source of feedback for this particular galaxy.

In driving metal-enriched outflows, the presence of stellar feedback changes how metals are retained by and mixed within our galaxy. This manifests itself across simulations as a difference in the ISM metal abundances and abundance spreads which have a significant impact on the stellar abundance patterns in this galaxy. This is predominately observable by examining the total abundance of a given element, but also imprints itself upon the abundance ratios in stellar abundance space. As we found in \citet{Emerick2018b}, elements released in SNe vs. AGB winds are ejected at larger rates and mix more efficiently in our fiducial simulation. The difference between the behavior of these two elements decreases in runs with less forms of feedback than our fiducial run, with turning off ionization and SNe having the largest effects (respectively). We find that runs without ionizing radiation (and also without SNe) produced significantly narrower abundance spreads in [Ba/Mg] (proxies of AGB and core collapse SNe elements, resepctively) than our fiducial simulation. In addition, each simulation shows differences in stellar [Ca/Mg] -- both released in SNe, but with a ratio that is strongly dependent on stellar mass.

In summary, this analysis shows that including a diverse set of stellar feedback modes can drive significantly different star formation, outflow, and chemical abundance properties in low mass dwarf galaxies. While SNe and ionizing radiation are dominant in this regime, LW radiation is also important. Feedback's abilities to drive metal mixing in the ISM and metal enriched outflows, and how it does this differently for elements from distinct sources (e.g. AGB winds vs. SNe) inlfuences the resulting stellar abundance patterns of our dwarf galaxy. This points to the importance of comparing simulations of galaxy to the detailed stellar abundance patterns in observed galaxies as a particularly strong constraint on the underlying physics. This would be best done in high resolution cosmological simulations of galaxy evolution, capable of capturing the details of halo growth and accretion in more realistic environments than the idealized set-up presented here.

%\acknowledgments
\section*{Acknowledgments} AE was supported by \aje{fill in}. \aje{double check:} GLB acknowledges support from NSF grants AST-1615955 and OAC-1835509 and NASA grant NNX15AB20G. M-MML was partly supported by NSF grant AST18-15461. We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages. These are products of collaborative effort by many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible.

%mm many citations from citebay.com.  Don't know what to cite for deepdish, so just put a placeholder in.
\software{\textsc{yt} \citep{yt}, \textsc{Enzo} \citep{Enzo2014}, \textsc{Grackle} \citep{GrackleMethod}, \textsc{Python} \citep{VanRossum1995python}, \textsc{IPython} \citep{perez2007ipython}, \textsc{NumPy} \citep{oliphant2006guide}, \textsc{SciPy} \citep{SciPy}, \textsc{Matplotlib} \citep{hunter2007matplotlib}, \textsc{HDF5} \citep{Fortner1998HDF,Koranne2011}, \textsc{h5py} \citep{h5py}, \textsc{Astropy} \citep{astropy:2013,astropy:2018}, \textsc{Cloudy} \citep{Cloudy2013}, and \textsc{deepdish}}

%\begin{figure*}
%  \centering
%  \includegraphics[width=0.45\linewidth]{figures/combined_CGM_average_evolution}
%  \includegraphics[width=0.45\linewidth]{figures/combined_CNM_average_evolution}\\
%  \includegraphics[width=0.45\linewidth]{figures/combined_CNM_average_mean-median}
%   \includegraphics[width=0.45\linewidth]{figures/combined_CNM_average_rms}
%  \caption{The same as Figure~\ref{fig:CGM_CNM} and Figure~\ref{fig:mean-median}, but comparing across both sets of runs with different SFRs. Line color corresponds to a fixed enrichment energy event, while the solid lines correspond to the higher SFR runs discussed throughout this work, and the dashed lines the lower SFR runs. See text for more details.}
%  \label{fig:SFR_comparison_CGM_CNM}
%\end{figure*}

%************* APPENDICES ************************%

%\section*{Acknowledgments}

%\clearpage
\appendix - Liklely DO NOT use this command
\setcounter{section}{0}%
\renewcommand\thesection{\thechapter.\Alph{section}}
\counterwithin{figure}{section}

\section{Morphological Properties}

In Section~\ref{sec:morphology}, we discuss the morphology of our galaxy early in its evolution (125~Myr), just after the initial star formation burst for each simulation and at a time reached by each simulation. We explore here the gas morphology at later, more quiescent times, which are not reached by all simulations.

In Figure~\ref{fig:panel_plot_3} and Figure~\ref{fig:panel_plot_4} we show face-on projections of gas number density at 350~Myr for each simulation. In the edge-on panels, the same general trends seen in Section~\ref{sec:morphology} across runs can be seen here. The largest difference in each panel is the decrease in each case of the amount and morphology of gas beyond the disk of the galaxy. During this period of low SFR for all but the shortrad simulation, the extraplanar gas around the disk is more uniform and less extended than during times of higher SFR.

This is visible as well in the edge-on panels, which still exhibit the similar lower-density cores and higher-density rings as appeared at t=125~Myr. The key difference is that the lower-density, inner regions have a higher typical density than when the galaxy was actively star forming. In addition, at 350~Myr, the outer rings in each galaxy tends to be clumpier and less continuous, broken up by star formation and feedback over the preceding 250~Myr. PE+LW shows the least variability between these two times, and also has the most uniform SFR of all the simulations.

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/proj_plot_n_x_350.png}
  \caption{Edge-on projections of gas number density for each of our runs at time $t=350$~Myr for all but the SN-only simulation.}
  \label{fig:panel_plot_3}
\end{figure*}

\begin{figure*}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/proj_plot_n_z_350.png}
  \caption{Same as Figure~\ref{fig:panel_plot_3}, but face-on.}
  \label{fig:panel_plot_4}
\end{figure*}
%
%
% Place appendix here%

\bibliographystyle{yahapj}
\bibliography{refs}

\end{document}
